### 2021-05-28 paper/paper.tex
Paper

\documentclass[a4paper,english,cleveref,autoref,thm-restate]{article}

\usepackage[utf8x]{inputenc}
\usepackage{t1enc}

\usepackage{hyperref}
%\usepackage{proof}
\usepackage{fullpage}
\usepackage{amssymb}
\usepackage{stmaryrd}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{color}
%\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{yfonts}
\usepackage[all]{xy}
\xyoption{2cell}
\UseAllTwocells

\makeatletter
\newcommand{\Overrightarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#2}$}}{}$}}
\newcommand{\Overleftarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Leftarrowfill@{\mbox{${#2}$}}{}$}}
%\newcommand{\Overrightarrow}[1]{\raisebox{1.4ex}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#1}$}}{}$}}
\makeatother

\newcommand{\highlight}[1]{\emph{#1}}

\include{macros}
\newcommand{\Type}{\mathsf{Type}}
\newcommand{\Set}{\mathsf{Set}}
\newcommand{\Prop}{\mathsf{Prop}}
\newcommand{\refl}[1]{\mathsf{refl}\,{#1}}
\newcommand{\mkmlidtype}[3]{{#1} =^{\mathrm{id}}_{#2} {#3}}
\newcommand{\mkmleqdep}[3]{{#1} =^{\mathrm{dep}}_{#2} {#3}}
\newcommand{\hrefl}[1]{\mathsf{refl^{\mathrm{dep}}}\,{#1}}
\newcommand{\mluniv}{\mathsf{U}}
\newcommand{\Jdep}[2]{\mathsf{J}\;{#1}\;{#2}}

\newcommand{\nth}[1]{{#1}^{\mbox{\scriptsize th}}}
\newcommand{\binomial}[2]{\left(\begin{array}{c}#1\\#2\end{array}\right)}

\newcommand{\wfctx}[1]{{#1}~\mathsf{ok}}

\newcommand{\mkover}[1]{\widetilde{#1}}
\newcommand{\mkoverdim}[2]{\widetilde{#2}^{#1}}
%\newcommand{\mkover}[1]{\dot{#1}}
%\newcommand{\mkprod}[3]{\Pi {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkprod}[3]{\Pi {#2}.\,{#3}}
\newcommand{\mkprodovereq}[3]{\mkover{\Pi} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkprodovereqopp}[3]{\opp{\mkover{\Pi}} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkboundedprod}[4]{\Pi {#3}\!:\!{#1}\leq{#2}.\,{#4}}
%\newcommand{\mklam}[3]{\lambda {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mklam}[3]{\lambda^{#2}.\,{#3}}
\newcommand{\mkboundedlam}[4]{\lambda {#3}\!:\!{#1}\leq{#2}.\,{#4}}
\newcommand{\mkapp}[2]{{#1}\,{#2}}
\newcommand{\prodsort}[2]{\Pi ({#1},{#2})}

% selecting kind of treatment of sorts
\newcommand{\typeorsort}[2]{{#2}}

%\newcommand{\mksigma}[3]{\Sigma {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mksigma}[3]{\Sigma {#2}.\,{#3}}
\newcommand{\mksigmaovereq}[3]{\mkover{\Sigma} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mksigmaovereqopp}[3]{\opp{\mkover{\Sigma}} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkpair}[2]{\langle{#1},{#2}\rangle}
\newcommand{\mkfst}[1]{{#1}.1}
\newcommand{\mksnd}[1]{{#1}.2}
\newcommand{\sigsort}[2]{\Sigma ({#1},{#2})}

\newcommand{\sortsort}[1]{{\mathcal S}_{#1}}

\newcommand{\Sone}{\mathbb{S}^1}
\newcommand{\casesone}[5]
  {\mathsf{case}\;{#1}\;\mathsf{of}\;{#2}\;\Rightarrow\;{#3}\;|\;{#4}\;\Rightarrow\;{#5}\;\mathsf{end}}
\newcommand{\base}{\mathsf{base}}
\newcommand{\loopsone}{\mathsf{loop}}
\newcommand{\Sonesort}{l_{\mathbb{S}^1}}

\newcommand{\emptyctx}{\boxbox}

\newcommand{\sort}[1]{\mathsf{U}_{#1}}
\newcommand{\univ}{\boxempty}
%\newcommand{\istype}{~:~S}
\newcommand{\typeannot}{\mathsf{type}}
\newcommand{\istype}{~\typeannot}

\newcommand{\mkeq}[3]{{#1} =_{#2} {#3}}
\newcommand{\mkhomeq}[3]{{#1} =_{#2} {#3}}
\newcommand{\mkeqovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}}
\newcommand{\mkeqovereqdim}[4]{{#2} \,\mkoverdim{#1}{=}_{#3}\, {#4}}
%\newcommand{\mkeqtype}[3]{{#1} =_{#2} {#3}} % case where we can write either s or refl{s}
\newcommand{\mkeqtype}[3]{{#1} =_{\typeannot} {#3}}
\newcommand{\mkeqtypeovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}} % case where we can write either s or refl{s}
\newcommand{\mkeqarray}[3]{\begin{array}{c}{#1}\\ =_{#2}\\ {#3}\end{array}}
\newcommand{\mkfaces}[3]{\mkeq{#1}{#2}{#3}}
\newcommand{\mkfacesarray}[3]{\mkeqarray{#1}{#2}{#3}}
\newcommand{\mkfacesover}[3]{\mkeqovereq{#1}{#2}{#3}}
\newcommand{\lameq}[2]{\lambda {#1}.{#2}}
%\newcommand{\reflterm}[1]{\textsf{refl}{#1}}
\newcommand{\reflterm}[1]{\widehat{#1}}
\newcommand{\overreflterm}[1]{{\mkover{\reflterm{#1}}}}
\newcommand{\refltermdim}[2]{{\widehat{#2}}^{#1}}
%\newcommand{\reflterm}[1]{\lambda{#1}}
%\newcommand{\refltype}[1]{\lambda{#1}}
\newcommand{\refltype}[1]{\reflterm{#1}}
\newcommand{\purerewlr}[1]{\overrightarrow{#1}}
\newcommand{\purerewrl}[1]{\overleftarrow{#1}}
%\newcommand{\rewlr}[2]{\mathsf{rew}^\rightarrow\;{#1}\;\mathsf{in}\;{#2}}
%\newcommand{\rewrl}[2]{\mathsf{rew}^\leftarrow\;{#1}\;\mathsf{in}\;{#2}}
\newcommand{\rewlr}[2]{\overrightarrow{#1}(#2)}
\newcommand{\rewrl}[2]{\overleftarrow{#1}(#2)}
\newcommand{\deprewlr}[1]{\raisebox{0em}{$\ulcorner$}\!#1}
\newcommand{\deprewrl}[1]{{#1}\raisebox{-0.2em}{$\!\lrcorner$}}
\newcommand{\rewlrspec}[2]{{#1}^{\rightarrow}(#2)}
\newcommand{\rewrlspec}[2]{{#1}^{\leftarrow}(#2)}
\newcommand{\rewlrrevspec}[2]{{#1}_-^{\rightarrow}(#2)}
\newcommand{\rewrlrevspec}[2]{{#1}_-^{\leftarrow}(#2)}
\newcommand{\rewlrrevspecin}[2]{{#1}_+^{\rightarrow}(#2)}
\newcommand{\rewrlrevspecin}[2]{{#1}_+^{\leftarrow}(#2)}
\newcommand{\doublerewlr}[2]{\Overrightarrow{1.4ex}{#1}({#2})}
\newcommand{\doublerewrl}[2]{\Overleftarrow{1.4ex}{#1}({#2})}
%\newcommand{\mktuple}[6]{\{#1\mapsto #3(#1); #2\mapsto #4(#2); #1\mapsto #5(#1); #2\mapsto #6(#2)\}}
\newcommand{\mktuple}[6]{\{#3; #4; #5; #6\}_{#1,#2}}
\newcommand{\mktupleshort}[6]{\{#3; #4; #5; #6\}}
\newcommand{\opp}[1]{{#1}^{-1}}
\newcommand{\oppi}[2]{\appi{#1}{(\opp{#2}/{#2})}}

\newcommand{\weakensquarelr}[2]{{#1}_L(#2)}
\newcommand{\weakensquarerl}[2]{{#1}_R(#2)}

\newcommand{\rewlrmkeq}[4]{\mkeq{\rewlr{#1}{#2}}{#3}{#4}}

% Version basse
%% \newcommand{\appi}[2]{{#1}_{#2}}
%% \newcommand{\appidep}[2]{{#1}_{({#2})}}
%% \newcommand{\bp}[1]{{#1}_0}
%% \newcommand{\ep}[1]{{#1}_1}
%% \newcommand{\bpdep}[1]{{#1}_{(0)}}
%% \newcommand{\epdep}[1]{{#1}_{(1}}}
% Version haute
% \newcommand{\metaappi}[2]{{#1}_{[{#2}]}}
\newcommand{\appi}[2]{{#1}\;\!{#2}}
\newcommand{\appidep}[2]{{#1}_{#2}}
\newcommand{\bp}[1]{{#1}{\scriptstyle 0}}
\newcommand{\ep}[1]{{#1}{\scriptstyle 1}}
\newcommand{\bpoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{0}}}
\newcommand{\epoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{1}}}
\newcommand{\bpdep}[1]{{#1}_0}
\newcommand{\epdep}[1]{{#1}_1}

\newcommand{\bpsubstexpl}[2]{{#2}_{\{0/{#1}\}}}
\newcommand{\epsubstexpl}[2]{{#2}_{\{1/{#1}\}}}
\newcommand{\eqsubstexpl}[2]{{#2}_{\{\star/{#1}\}}}
\newcommand{\bpsubstexplcons}[2]{{#2}\}\{0/{#1}}
\newcommand{\epsubstexplcons}[2]{{#2}\}\{1/{#1}}
\newcommand{\eqsubstexplcons}[2]{{#2}\}\{\star/{#1}}
\newcommand{\bpsubst}[2]{{#2}{[0/{#1}]}}
\newcommand{\epsubst}[2]{{#2}{[1/{#1}]}}
\newcommand{\bpsubstctx}[3]{{#3}{[0/{#2}]}^{#1}}
\newcommand{\epsubstctx}[3]{{#3}{[1/{#2}]}^{#1}}
\newcommand{\takebpface}[2]{\partial^{#1}_0{#2}}
\newcommand{\takeepface}[2]{\partial^{#1}_1{#2}}

\newcommand{\dimvalid}[2]{{#1} \in {#2}}
\newcommand{\dimdeclare}[1]{{#1}}
\newcommand{\dimlength}[1]{|#1|_{\mathit{dim}}}
\newcommand{\dimindex}[2]{\#_{#1}{#2}}

\newcommand{\substminus}[2]{{#1}-{#2}}
\newcommand{\substminusbernardymoulin}[2]{{#1}/{#2}}

\newcommand{\N}{\mathbb{N}}
\newcommand{\expand}[2]{\mathsf{expand}(#1,#2)}

\newcommand{\defeq}{\triangleq}
%\newcommand{\metaequiv}{=\!\!\!=}
\newcommand{\metaequiv}{\cong}
\newcommand{\metaletin}[3]{\mathit{let}\;{#1}\;\defeq\;{#2}\;\mathit{in}\;{#3}}
\newcommand{\map}[2]{\mathsf{ap}\,{#1}\,{#2}}
\newcommand{\depmap}[2]{\mathsf{apd}\,{#1}\,{#2}}
\newcommand{\transport}[3]{\mathsf{transport}\,{#1}\,{#2}\,{#3}}
\newcommand{\deptransport}[3]{\mathsf{transportd}\,{#1}\,{#2}\,{#3}}
%\newcommand{\swap}[1]{\mathsf{swap}(#1)}
%\newcommand{\swapbracket}[1]{\mathsf{swap}(#1)}
%\newcommand{\swaptype}[1]{\mathsf{swap}(#1)}
\newcommand{\swap}[1]{{#1}^{\circ}}
\newcommand{\swapbracket}[1]{({#1})^{\circ}}
\newcommand{\swaptype}[1]{{#1}^{\circ}}
\newcommand{\swapoverdim}[2]{{#2}^{\mkoverdim{#1}{\circ}}}
\newcommand{\homsquare}[1]{\mathsf{homsquare}(#1)}
\newcommand{\permute}[2]{\mathsf{permute}_{#1}(#2)}
\newcommand{\swapprodeq}[2]{\mathsf{swap}_{\Pi=}^{#1}(#2)}
\newcommand{\swapeqprod}[2]{\mathsf{swap}_{=\Pi}^{#1}(#2)}
\newcommand{\swapeqprodlr}[2]{\mathsf{swap}_{=\Pi}^{\rightarrow}({#1})(#2)}
\newcommand{\swapeqprodrl}[2]{\mathsf{swap}_{=\Pi}^{\leftarrow}({#1})(#2)}
\newcommand{\swapsigmaeq}[1]{\mathsf{swap}_{\Sigma=}(#1)}
\newcommand{\swapeqsigma}[1]{\mathsf{swap}_{=\Sigma}(#1)}

\newcommand{\bool}{\mathsf{bool}}
\newcommand{\booldeux}{\bool^2}
\newcommand{\boolexp}{\bool^{\bool}}

\newcommand{\reduce}{\;\triangleright\;}

\newcommand{\emptysubst}{\emptyctx}

\newcommand{\sortrule}{\sort{}}
\newcommand{\axrule}{\mathsf{Ax}}
\newcommand{\ctxemptyrule}{\mathsf{Ctx}_{\emptyctx}}
\newcommand{\ctxconsrule}{\mathsf{Ctx}_{\mathsf{cons}}}
\newcommand{\convrule}{\mathsf{Conv}}
\newcommand{\convconvrule}{\mathsf{Conv}-\mathsf{Conv}}
\newcommand{\univrule}{\mathsf{\univ}}
\newcommand{\convruleredright}{\reduce_R}
\newcommand{\convruleredleft}{\reduce_L}
\newcommand{\convrulerefl}{\equiv_{\mathsf{refl}}}
\newcommand{\convruletrans}{\equiv_{\mathsf{trans}}}
\newcommand{\convruleredtyperight}{\reduce_R^{\typeannot}}
\newcommand{\convruleredtypeleft}{\reduce_L^{\typeannot}}
\newcommand{\convruletyperefl}{\equiv_{\mathsf{refl}}^{\typeannot}}
\newcommand{\convruletypetrans}{\equiv_{\mathsf{trans}}^{\typeannot}}

\newcommand{\circovereq}{\;\mkover{\circ}\;}
\newcommand{\circsigma}{\circ_{\Sigma}}

\newcommand{\comprule}{R_{\mathsf{\circ}}}
\newcommand{\opprule}{R_{\mathsf{\opp}}}

\newcommand{\idleftredrule}{\mathsf{Id_L}}
\newcommand{\idrightredrule}{\mathsf{Id_R}}
\newcommand{\idoppredrule}{\mathsf{\opp{Id}}}
\newcommand{\oppoppredrule}{\mathsf{\opp{(\opp{\_})}}}
\newcommand{\assoccompredrule}{\mathsf{Assoc}}
\newcommand{\distriboppcompredrule}{\mathsf{\opp{\circ}}}
\newcommand{\squaredownredrule}{\circ_{=_{\mkover{=}}}}
\newcommand{\exchangerule}{\mathsf{Exch}}
\newcommand{\compeqovereqredrule}{\circ_{\mkover{=}}}
\newcommand{\squareprodredrule}{\circ_{=_{\mkover{\Pi}}}}

\newcommand{\depmapdef}{\mathsf{ApD}}
\newcommand{\funextpuredef}{\mathsf{LiftDim}}
\newcommand{\funextdeppuredef}{\mathsf{LiftDepDim}}
\newcommand{\funextdepdeppuredef}{\mathsf{LiftDepDim}}
\newcommand{\funextdef}{\mathsf{FunExt}}
\newcommand{\funextdepdef}{\mathsf{FunDepExt}}
\newcommand{\funext}[1]{\mathsf{funext}(#1)}
\newcommand{\funextdep}[1]{\mathsf{fundepext}(#1)}
\newcommand{\funextpure}[1]{\mathsf{liftdim}(#1)}
\newcommand{\funextdeppure}[1]{\mathsf{liftdepdim}(#1)}

\newcommand{\OMEGATT}{\omega\mathsf{TT}}

\begin{document}

\title{An indexed construction of semi-cubical types}

\maketitle

\newcommand{\emptysigma}{\bullet}
\newcommand{\itsemterm}[4]{\llbracket #4 \rrbracket^{#2;#3}_{#1}}
\newcommand{\itsemtype}[4]{\llbracket #4 \rrbracket^{#2;#3}_{#1}}
\newcommand{\semterm}[3]{\llbracket #3 \rrbracket^{#1;#2}}
\newcommand{\semtype}[3]{\llbracket #3 \rrbracket^{#1;#2}}
\newcommand{\incrstep}[3]{\mathsf{split}_{#1}{#3}(#2)}
\newcommand{\distrstep}[3]{\mathsf{distr}_{#1}{#3}(#2)}
\newcommand{\applytype}[4]{\mathsf{apptype}_{#1}^{#2}(#3,#4)}
\newcommand{\shrink}[3]{\mathsf{shrink}_{#1}\,{#2}\,#3}
\newcommand{\under}[3]{\mathsf{under}_{#1}\,{#2}\,#3}
\newcommand{\undertau}[3]{\mathsf{under}_{#1}^{#2}\,#3}
\newcommand{\proj}[3]{\pi_{#1}^{#2}\,#3}
\newcommand{\elt}[2]{\mathsf{El}_{#1}\,#2}
\newcommand{\semtypenew}[2]{| #2 |_{#1}}
\newcommand{\semnew}[2]{\llbracket #2 \rrbracket_{#1}}
\newcommand{\semctx}[2]{\llbracket #2 \rrbracket_{#1}}
\newcommand{\semlam}[5]{\mathsf{lam}_{#1}^{#2}\,#4\,(#3)\,#5}
\newcommand{\semlambis}[5]{\mathsf{lam'}_{#1}^{#2}\,#4\,(#3)\,#5}
\newcommand{\semapp}[3]{\mathsf{app}_{#1}#2\,#3}
\newcommand{\semprod}[5]{\mathsf{prod}_{#1}^{#2}\,#4\,(#3)\,#5}
\newcommand{\access}[2]{\mathsf{get}_{#1}(#2)}
\newcommand{\accesstyped}[3]{\mathsf{get}_{#1}^{#2}(#3)}
\newcommand{\lift}[1]{\mathsf{lift}\, {#1}}
\newcommand{\liftlr}[1]{\mathsf{lift}^\rightarrow\, {#1}}
\newcommand{\liftrl}[1]{\mathsf{lift}^\leftarrow\, {#1}}
\newcommand{\diag}[2]{\mathsf{diag}_{#1}(#2)}
\newcommand{\semsort}[1]{\mathsf{sort}_{#1}}
\newcommand{\reflsort}[1]{\mathsf{refl}^{\sort{}}_{#1}}
\newcommand{\mktuplenew}[6]{\{#4\,|\begin{array}{l} #5 \\ #6 \end{array}\}_{#1,#2,#3}}
\newcommand{\mktuplein}[4]{{#1}; {#2}; {#3}; {#4}}
\newcommand{\nwconn}[2]{\deprewlr{#2}_{#1}}
\newcommand{\seconn}[2]{\deprewrl{#2}_{#1}}
\newcommand{\refltermn}[3]{\mathsf{reflterm}_{#1}(#3)}
\newcommand{\refltypen}[2]{\mathsf{refltype}_{#1}(#2)}

\newcommand{\restrict}{\mathsf{restrict}}
\newcommand{\MofL}{\mathsf{underlying}}
\newcommand{\defequiv}{\mathsf{\simeq}}
\newcommand{\isequivalence}{\mathsf{isequiv}}
\newcommand{\gpdlevel}{\mathsf{gpdlevel}}
\newcommand{\regrefl}{\mathsf{regrefl}}

\newcommand{\homoname}{}
\newcommand{\heteroname}{het}
\newcommand{\mycubsetcomp}[2]{\mathsf{cubset}_{#1}^{=#2}}

\newcommand{\informalcube}{\mathsf{cube}}
\newcommand{\informalcubeover}{\mathsf{\cubeovername}}

%\newcommand{\cubeovername}{cubeover}
%\newcommand{\Cubeovername}{Cubeover}
\newcommand{\cubeovername}{cube}
\newcommand{\Cubeovername}{Cube}
\newcommand{\pboxname}{box}
\newcommand{\pBoxname}{Box}

\newcommand{\mybox}[1]{\mathsf{{\homoname}box}_{#1}}
\newcommand{\mylayer}[1]{\mathsf{{\homoname}layer}_{#1}}
\newcommand{\mycube}[1]{\mathsf{{\homoname}\cubeovername}_{#1}}
\newcommand{\downbox}[2]{\mathsf{sub{\homoname}box}_{#1}^{#2}}
\newcommand{\downlayer}[2]{\mathsf{sub{\homoname}layer}_{#1}^{#2}}
\newcommand{\downcube}[2]{\mathsf{sub{\homoname}cube}_{#1}^{#2}}
\newcommand{\cohbox}[2]{\mathsf{coh{\homoname}box}_{#1}^{#2}}
\newcommand{\cohlayer}[2]{\mathsf{coh{\homoname}layer}_{#1}^{#2}}
\newcommand{\cohcube}[2]{\mathsf{coh{\homoname}\cubeovername}_{#1,#2}}
\newcommand{\myfullbox}[1]{\mathsf{full{\homoname}box}_{#1}}
\newcommand{\fulldownbox}[2]{\mathsf{subfull{\homoname}box}_{#1}^{#2}}
\newcommand{\fulldowncube}[2]{\mathsf{subfull{\homoname}cube}_{#1}^{#2}}

\newcommand{\myheterobox}[2]{\mathsf{{\heteroname}box}_{#1}^{#2}}
\newcommand{\myheterolayer}[2]{\mathsf{{\heteroname}layer}_{#1}^{#2}}
\newcommand{\myheterocube}[2]{\mathsf{{\heteroname}\cubeovername}_{#1}^{#2}}
\newcommand{\myheteroboxtype}[2]{\mathsf{Box}_{#1}^{#2}}
\newcommand{\myheterolayertype}[2]{\mathsf{Layer}_{#1}^{#2}}
\newcommand{\myheterocubetype}[2]{\mathsf{\Cubeovername}_{#1}^{#2}}

\newcommand{\myfulldepheterobox}[3]{\mathsf{fulldepBox}_{#1}^{#2,#3}}
\newcommand{\mydepheterobox}[3]{\mathsf{depBox}_{#1}^{#2,#3}}
\newcommand{\mydepheterolayer}[3]{\mathsf{depLayer}_{#1}^{#2,#3}}
\newcommand{\mydepheterocube}[3]{\mathsf{dep\Cubeovername}_{#1}^{#2,#3}}
\newcommand{\liftfulldepheterobox}[3]{\mathsf{liftfullBox}_{#1}^{#2,#3}}
\newcommand{\liftdepheterobox}[3]{\mathsf{liftBox}_{#1}^{#2,#3}}
\newcommand{\liftdepheterolayer}[3]{\mathsf{liftLayer}_{#1}^{#2,#3}}
\newcommand{\liftdepheterocube}[3]{\mathsf{lift\Cubeovername}_{#1}^{#2,#3}}

\newcommand{\expandheterocube}[2]{\mathsf{expand\Cubeovername}_{#1}^{#2}}
\newcommand{\expandheterolayer}[2]{\mathsf{expandLayer}_{#1}^{#2}}
\newcommand{\expanddownbox}[2]{\mathsf{expandsub{\homoname}box}_{#1}^{#2}}
\newcommand{\expanddownlayer}[2]{\mathsf{expandsub{\homoname}layer}_{#1}^{#2}}
\newcommand{\expanddowncube}[2]{\mathsf{expandsub{\homoname}cube}_{#1}^{#2}}

%\newcommand{\heteroofliftbox}[3]{\mathsf{subliftBox}_{#1}^{#2,#3}}
%\newcommand{\heteroofliftlayer}[3]{\mathsf{subliftLayer}_{#1}^{#2,#3}}
%\newcommand{\heteroofliftcube}[3]{\mathsf{subliftCube}_{#1}^{#2,#3}}

\newcommand{\depdownbox}[2]{\mathsf{depsub{\homoname}box}_{#1}^{#2}}
\newcommand{\depdownlayer}[2]{\mathsf{depsub{\homoname}layer}_{#1}^{#2}}
\newcommand{\depdowncube}[2]{\mathsf{depsub{\homoname}cube}_{#1}^{#2}}
\newcommand{\depdownboxbis}[2]{\mathsf{depsublift{\homoname}box}_{#1}^{#2}}
\newcommand{\depdownlayerbis}[2]{\mathsf{depsublift{\homoname}layer}_{#1}^{#2}}
\newcommand{\depdowncubebis}[2]{\mathsf{depsublift{\homoname}cube}_{#1}^{#2}}
\newcommand{\depdownboxter}[2]{\mathsf{depsublift{\homoname}box'}_{#1}^{#2}}
\newcommand{\depdownlayerter}[2]{\mathsf{depsublift{\homoname}layer'}_{#1}^{#2}}
\newcommand{\depdowncubeter}[2]{\mathsf{depsublift{\homoname}cube'}_{#1}^{#2}}

\newcommand{\depcohbox}[2]{\mathsf{depcoh{\homoname}box}_{#1}^{#2}}
\newcommand{\depcohlayer}[2]{\mathsf{depcoh{\homoname}layer}_{#1}^{#2}}
\newcommand{\depcohcube}[2]{\mathsf{depcoh{\homoname}cube}_{#1}^{#2}}
\newcommand{\depcohboxbis}[2]{\mathsf{depcohlift{\homoname}box}_{#1}^{#2}}
\newcommand{\depcohlayerbis}[2]{\mathsf{depcohlift{\homoname}layer}_{#1}^{#2}}
\newcommand{\depcohcubebis}[2]{\mathsf{depcohlift{\homoname}cube}_{#1}^{#2}}
\newcommand{\depcohboxter}[2]{\mathsf{depcohlift{\homoname}box'}_{#1}^{#2}}
\newcommand{\depcohlayerter}[2]{\mathsf{depcohlift{\homoname}layer'}_{#1}^{#2}}
\newcommand{\depcohcubeter}[2]{\mathsf{depcohlift{\homoname}cube'}_{#1}^{#2}}

\newcommand{\univfullcube}[2]{\mathsf{UnivfullCube}_{#1}^{#2}}
\newcommand{\univfullbox}[2]{\mathsf{UnivfullBox}_{#1}^{#2}}
\newcommand{\univbox}[2]{\mathsf{UnivBox}_{#1}^{#2}}
\newcommand{\univlayer}[2]{\mathsf{UnivLayer}_{#1}^{#2}}
\newcommand{\univcube}[2]{\mathsf{UnivCube}_{#1}^{#2}}
\newcommand{\univfiller}[2]{\mathsf{UnivFiller}_{#1}^{#2}}
\newcommand{\cubeofuniv}[2]{\mathsf{cubeofuniv}_{#1}^{#2}}
\newcommand{\extend}[2]{\mathsf{extendcube}_{#1}^{#2}}

\newcommand{\powersetfullcube}[2]{\mathsf{powersetfullCube}_{#1}^{#2}}

%\newcommand{\downboxleft}{\mathsf{subbox}^L}
%\newcommand{\downboxright}{\mathsf{subbox}^R}
%\newcommand{\downlayerleft}{\mathsf{sublayer}^L}
%\newcommand{\downlayerright}{\mathsf{sublayer}^R}
%\newcommand{\downcubeleft}{\mathsf{sub\cubeovername}^L}
%\newcommand{\downcuberight}{\mathsf{sub\cubeovername}^R}
%% \newcommand{\downboxleft}{\downarrow^{\mathsf{box},L}}
%% \newcommand{\downboxright}{\downarrow^{\mathsf{box},R}}
%% \newcommand{\downlayerleft}{\downarrow^{\mathsf{layer},L}}
%% \newcommand{\downlayerright}{\downarrow^{\mathsf{layer},R}}
%% \newcommand{\downcubeleft}{\downarrow^{\mathsf{cube},L}}
%% \newcommand{\downcuberight}{\downarrow^{\mathsf{cube},R}}
\newcommand{\heterodownbox}[2]{\mathsf{sub{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterodownlayer}[2]{\mathsf{sub{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterodowncube}[2]{\mathsf{sub{\heteroname}\cubeovername}_{#1}^{#2}}
\newcommand{\depdownboxtype}[2]{\mathsf{Subdep{\homoname}box}_{#1}^{#2}}
\newcommand{\depdownlayertype}[2]{\mathsf{Subdep{\homoname}layer}_{#1}^{#2}}
\newcommand{\depdowncubetype}[2]{\mathsf{Subdep{\homoname}\cubeovername}_{#1}^{#2}}
\newcommand{\downboxtype}[2]{\mathsf{Subbox}_{#1}^{#2}}
%\newcommand{\downboxtypelarge}[1]{\mathsf{Subbox'}_{#1}}
\newcommand{\downlayertype}[2]{\mathsf{Sublayer}_{#1}^{#2}}
\newcommand{\downcubetype}[2]{\mathsf{Sub\cubeovername}_{#1}^{#2}}
\newcommand{\cohreflbox}[1]{\mathsf{cohreflbox}_{#1}}
\newcommand{\cohrefllayer}[1]{\mathsf{cohrefllayer}_{#1}}
\newcommand{\cohreflcube}[1]{\mathsf{cohreflcube}_{#1}}
\newcommand{\cohrefleqbox}[1]{\mathsf{cohrefleqbox}_{#1}}
\newcommand{\cohrefleqlayer}[1]{\mathsf{cohrefleqlayer}_{#1}}
\newcommand{\cohrefleqcube}[1]{\mathsf{cohrefleqcube}_{#1}}
\newcommand{\cohboxtype}[2]{\mathsf{Cohbox}_{#1}^{#2}}
%\newcommand{\cohboxtypelarge}[1]{\mathsf{Cohbox'}_{#1}}
\newcommand{\cohlayertype}[2]{\mathsf{Cohlayer}_{#1}^{#2}}
\newcommand{\cohcubetype}[2]{\mathsf{Coh\cubeovername}_{#1}^{#2}}
\newcommand{\heterocohbox}[2]{\mathsf{coh{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterocohlayer}[2]{\mathsf{coh{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterocohcube}[2]{\mathsf{coh{\heteroname}\cubeovername}_{#1}^{#2}}
\newcommand{\myappdepbox}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdeplayer}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcube}[1]{\mathsf{homoapp\cubeovername}_{#1}}
\newcommand{\myappdepfullcube}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myappdepboxtype}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdepfullboxtype}[1]{\mathsf{homoappfullbox}_{#1}}
\newcommand{\myappdeplayertype}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcubetype}[1]{\mathsf{homoapp\cubeovername}_{#1}}
\newcommand{\myappdepfullcubetype}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myfullcube}[1]{\mathsf{full{\homoname}cube}_{#1}}
\newcommand{\myfullheteroboxtype}[2]{\mathsf{fullBox}_{#1}^{#2}}
\newcommand{\myfullheterobox}[2]{\mathsf{full{\heteroname}box}_{#1}^{#2}}
\newcommand{\reflfullcube}[1]{\mathsf{reflfullcube}_{#1}}
\newcommand{\unitpoint}{\star}
\newcommand{\unittype}{\mathsf{unit}}
\newcommand{\eqett}{\equiv_{\mathit{ETT}}}
\newcommand{\reflett}{\mathsf{refl}_{\mathit{ETT}}}
\newcommand{\mygpd}{\mathsf{gpd}}

\newcommand{\mycubset}[1]{\mathsf{cubset}_{#1}}
\newcommand{\mycubsetfrom}[2]{\mathsf{cubset}_{#1}^{\geq#2}}
\newcommand{\partialcubset}[2]{\mathsf{cubset}_{#1}^{<#2}}
\newcommand{\mydepcubset}[1]{\mathsf{dephomocubset}_{#1}}
\newcommand{\mydepcubsetfrom}[2]{\mathsf{dephomocubset}_{#1}^{\geq#2}}
\newcommand{\mydepcubsetcomp}[2]{\mathsf{dephomocubset}_{#1}^{=#2}}
\newcommand{\deppartialcubset}[2]{\mathsf{dephomocubset}_{#1}^{<#2}}
\newcommand{\properheterocubetype}[2]{\mathsf{Filler}_{#1}^{#2}}

\newcommand{\mydepheterocubset}[2]{\mathsf{depcubset}_{#1}^{#2}}
\newcommand{\mydepheterocubsetfrom}[3]{\mathsf{depcubset}_{#1}^{#2,\geq#3}}
\newcommand{\mydepheterocubsetcomp}[3]{\mathsf{depcubset}_{#1}^{#2,=#3}}
\newcommand{\deppartialheterocubset}[3]{\mathsf{depcubset}_{#1}^{#2,<#3}}
\newcommand{\myappheterodepbox}[1]{\mathsf{appbox}_{#1}}
\newcommand{\myappheterodeplayer}[1]{\mathsf{applayer}_{#1}}
\newcommand{\myappheterodepcube}[1]{\mathsf{app\cubeovername}_{#1}}
\newcommand{\myappheterodepfullcube}[1]{\mathsf{appfullcube}_{#1}}
\newcommand{\myappheterodepboxtype}[1]{\mathsf{appbox}_{#1}}
\newcommand{\myappheterodepfullboxtype}[3]{\mathsf{appfullbox}_{#1}^{#2,#3}}
\newcommand{\myappheterodeplayertype}[1]{\mathsf{applayer}_{#1}}
\newcommand{\myappheterodepcubetype}[1]{\mathsf{app\cubeovername}_{#1}}
\newcommand{\myappheterodepfullcubetype}[1]{\mathsf{appfullcube}_{#1}}

\newcommand{\typecubset}{\mathsf{typecubset}}
\newcommand{\mysymcubset}{\mathsf{symcubset}}
\newcommand{\issymcubset}{\mathsf{issymcubset}}
\newcommand{\partialsymcubset}{\mathsf{symcubset}}
\newcommand{\mypermute}{\mathsf{permute}}
\newcommand{\partialhascomp}{\mathsf{partialhascomp}}
\newcommand{\hascomp}{\mathsf{hascomp}}
\newcommand{\tube}[1]{\mathsf{{\homoname}tube}_{#1}}
\newcommand{\propercube}[1]{\mathsf{proper{\homoname}filler}_{#1}}
\newcommand{\properheterocube}[2]{\mathsf{{\heteroname}filler}_{#1}^{#2}}
\newcommand{\border}[1]{\mathsf{{\homoname}border}_{#1}}
\newcommand{\bordertype}[1]{\mathsf{Boxofcube}_{#1}}
\newcommand{\cohbordertype}[1]{\mathsf{Cohboxofcube}_{#1}}
\newcommand{\myheteroborder}[1]{\mathsf{{\heteroname}border}_{#1}}
\newcommand{\fullheterocubetype}[2]{\mathsf{fullCube}_{#1}^{#2}}
\newcommand{\fullheterocube}[1]{\mathsf{full{\heteroname}cube}_{#1}}
\newcommand{\heterotubetype}[1]{\mathsf{Tube}_{#1}}
\newcommand{\heterotube}[1]{\mathsf{{\heteroname}tube}_{#1}}
\newcommand{\mygroundedcube}[1]{\mathsf{grounded{\homoname}cube}_{#1}}
\newcommand{\mygroundedheterocubetype}[1]{\mathsf{groundedCube}_{#1}}
\newcommand{\mygroundedheterocube}[1]{\mathsf{grounded{\heteroname}cube}_{#1}}
\newcommand{\reflexive}[1]{\mathsf{reflexive}_{#1}}
\newcommand{\permutation}{\mathsf{permutation}}
\newcommand{\diagonal}{\mathsf{diagonal}}
\newcommand{\connection}{\mathsf{connection}}
\newcommand{\diagprop}{\mathsf{diag}}
\newcommand{\reglr}{\rightarrow-\mathsf{reg}}
\newcommand{\regrl}{\leftarrow-\mathsf{reg}}
\newcommand{\coercivelr}{\rightarrow-\mathsf{def}}
\newcommand{\coerciverl}{\leftarrow-\mathsf{def}}
\newcommand{\regularitylr}{\rightarrow-\mathsf{regularity}}
\newcommand{\regularityrl}{\leftarrow-\mathsf{regularity}}
\newcommand{\Reglr}{\Rightarrow-\mathsf{reg}}
\newcommand{\Regrl}{\Leftarrow-\mathsf{reg}}
\newcommand{\Coercivelr}{\Rightarrow-\mathsf{def}}
\newcommand{\Coerciverl}{\Leftarrow-\mathsf{def}}
\newcommand{\Regularitylr}{\Rightarrow-\mathsf{regularity}}
\newcommand{\Regularityrl}{\Leftarrow-\mathsf{regularity}}
\newcommand{\coebacklr}{\overrightarrow{\mathsf{coe}}}
\newcommand{\coebackrl}{\overleftarrow{\mathsf{coe}}}
\newcommand{\backcoercivelr}{\overrightarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\backcoerciverl}{\overleftarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\regbacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regbackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regularitybacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\regularitybackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Coebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coercivebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Coercivebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Regbacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regbackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regularitybacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Regularitybackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}

\newcommand{\reflbox}[1]{\mathsf{reflbox}_{#1}}
\newcommand{\refllayer}[1]{\mathsf{refllayer}_{#1}}
\newcommand{\reflcube}[1]{\mathsf{reflcube}_{#1}}
\newcommand{\permutebox}{\mathsf{permutebox}}
\newcommand{\diagbox}{\mathsf{diagbox}}
\newcommand{\connbox}{\mathsf{connbox}}
%% \newcommand{\cohbox}{\mathsf{coh}^{\mathsf{box}}}
%% \newcommand{\cohlayer}{\mathsf{coh}^{\mathsf{layer}}}
\newcommand{\hd}{\mathsf{hd}}
\newcommand{\tl}{\mathsf{tl}}
\newcommand{\first}{\mathsf{first}}
\newcommand{\groupoid}{\mathsf{groupoid}}
\newcommand{\groupoidn}{\mathsf{groupoidn}}
\newcommand{\letinsplit}[3]{\!\!\begin{array}{l}\mathbf{let}~{#1}=#2\;\mathbf{in}~\\#3\end{array}}

\newcommand{\UIP}{\mathsf{UIP}}

\tableofcontents

\section{Introduction}

\section{Semi-cubical sets}
\label{sec:truncated-cubical-sets}

In this section, we give the core of the definition of semi-cubical
sets as the coinductive limit (see Figure~\ref{fig:barecubicalset}) of a
construction of truncated semi-cubical sets.

\subsection{Truncated semi-cubical sets}

The definition is dispatched over
Figures~\ref{fig:barecubicalsetstructurecore},
\ref{fig:barecubicalsetstructure}, \ref{fig:barecubicalsetfaces} and
\ref{fig:barecubicalsetcoherences}. It describes the structure of the
underlying higher-dimensional relations on which cubes and boxes are
built, together with the definition of homogeneous $n$-boxes,
homogeneous $n$-cubes, together with face operations on boxes and
cubes, together with commutation properties of the face
operations. All are mutually defined as types of the target language
ETT. Note that such relational structure, cubes and boxes are relative
to a universe.

Note the presence of a coherence condition $\cohbox{l}{}$ to
ensuring that both sides of the equality in $\downlayer{l}{}$ and $\downcube{l}{}$
are in the same type. The proof of $\cohbox{l}{}$ itself requires
an higher-dimensional coherence condition which we obtain by
working here in ETT where all proofs of an
equality are identified (principle of Unicity of Identity Proofs). Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many 
higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a
discussion on the de facto need for recursive higher-dimensional
coherence conditions in formulating higher-dimensional structures in
type theory). Note also that for a given
$n$, the coherence conditions evaluate to a reflexivity proof, so that
the construction evaluates to an effective sequence of types of
iterated relations not mentioning $\downbox{l}{}$ nor $\cohbox{l}{}$ anymore.

When reflexivities are excepted, we call the structure thus defined
\emph{bare truncated cubical sets}: \emph{bare} because it can be seen
as defining a cubical equivalent to semi-simplicial sets with only
faces as part of the structure (otherwise said, another terminology
could have been ``semi-cubical'' sets); \emph{truncated} because we
consider only such cubical sets up to some fixed dimension.

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\multicolumn{4}{c}{\mbox{\textit{Type of truncated cubical sets}}}\\
\\
\partialcubset{l}{n} && : & \sort{l+1}\\
\partialcubset{l}{0} && \defeq & \unittype\\
\partialcubset{l}{n'+1} && \defeq & \Sigma D:\partialcubset{l}{n'}.\,\mycubsetcomp{l}{n'}(D)\\
\\
\multicolumn{4}{c}{\mbox{\textit{Structure carried at each dimension}}}\\
\\
\mycubsetcomp{l}{n} & (D:\partialcubset{l}{n}) & : & \sort{l}\\
\mycubsetcomp{l}{n} & D & \defeq & \myfullbox{l}^{n}(D)\imp \sort{l}\\
\end{array}
$
}}
\caption{Definition of a truncated cubical set (main part of the higher-dimensional relation structure)}
\label{fig:barecubicalsetstructurecore}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\multicolumn{4}{c}{\mbox{\textit{Full homogeneous $n$-boxes}}}\\
\\
\myfullbox{l}^{n} & (D:\partialcubset{l}{n}) & : & \sort{l}\\
\myfullbox{l}^{n} & D & \defeq & \mybox{l}^{n,n}(D)\\
\\
\multicolumn{4}{c}{\mbox{\textit{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}}}\\
\\
\mybox{l}^{n,p,[p \leq n]} & (D:\partialcubset{l}{n}) & : & \sort{l}\\
\mybox{l}^{n,0} & D & \defeq & \unittype\\
\mybox{l}^{n,p'+1} & D & \defeq & \Sigma d:\mybox{l}^{n,p'}(D).\,\mylayer{l}^{n,p'}(D)(d)\\
\\
\mylayer{l}^{n,p,[p < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array}& : & \sort{l}\\
\mylayer{l}^{n,p} & D~d & \defeq & \!\!\begin{array}{l}\mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\\times\; \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))\end{array}\\
\\
\mycube{l}^{n,p,[p \leq n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\end{array} & : & \sort{l}\\
\mycube{l}^{n,p,[p = n]} & D~E~d & \defeq & E.\mathsf{rel}(d)\\
\mycube{l}^{n,p,[p < n]} & D~E~d & \defeq & \Sigma b:\mylayer{l}^{n,p}(D)(d).\,\mycube{l}^{n,p+1}(D)(E)(d,b)\\
\end{array}
$
}}
\caption{Definition of a truncated cubical set (boxes)}
\label{fig:barecubicalsetstructure}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{small}
\begin{array}{llcl}
\downbox{l,\epsilon,q}{n,p,[p \leq q < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array}& : & \mybox{l}^{n-1,p}(\hd(D))\\
\downbox{l,\epsilon,q}{n,0} & D~\unitpoint & \defeq & \unitpoint\\
\downbox{l,\epsilon,q}{n,p'+1} & D~(d,b) & \defeq & (\downbox{l,\epsilon,q}{n,p'}(D)(d),\downlayer{l,\epsilon,q}{n,p'}(D)(d)(b))\\
\\
\downlayer{l,\epsilon,q}{n,p,[p < q < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array}& : & \mylayer{l}^{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))\\
\downlayer{l,\epsilon,q}{n,p} & D~d~c & \defeq & \!\!\begin{array}{l}(\overrightarrow{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L)),\\\;\overrightarrow{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R)))\end{array}\\
\\
\downcube{l,\epsilon,q}{n,p,[p \leq q < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array}& : & \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))\\
\downcube{l,\epsilon,q}{n,p,[p=q]} & D~E~d~(b,\_) & \defeq & b_{\epsilon}\\
\downcube{l,\epsilon,q}{n,p,[p<q]} & D~E~d~(b,c) & \defeq & (\downlayer{l,\epsilon,q}{n,p}(D)(d)(b),\downcube{l,\epsilon,q}{n,p+1}(D)(E)(d,b)(c))\\
\\
\end{array}
\end{small}
$
}}
\caption{Definition of a homogeneous bare cubical set ($q$-th projection)}
\label{fig:barecubicalsetfaces}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{small}
\begin{array}{llcl}
\cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\tiny\begin{array}{l}n,p\\\mbox{}[p \leq r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array}& : & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q-1}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r-1}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))\end{array}\\
\cohbox{l,\epsilon,\epsilon',q,r}{n,0} & D~\unitpoint & \defeq & \reflett(\unitpoint)\\
\cohbox{l,\epsilon,\epsilon',q,r}{n,p'+1} & D~(d,b) & \defeq & (\cohbox{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d)(b))\\
\\
\cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\tiny\begin{array}{l}n,p\\\mbox{}[p < r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array}& : & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))(\downlayer{l,\epsilon,q}{n,p}(D)(d)(b))\end{array}\\
\cohlayer{l,\epsilon,\epsilon',q,r}{n,p} & D~d~c & \defeq & \!\!\begin{array}{l}(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L),\\\;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))\end{array}\\
\\
\cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\tiny\begin{array}{l}n,p\\\mbox{}[p \leq r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array}& : & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))(\downcube{l,\epsilon,q}{n,p}(D)(E)(d)(b))\end{array}\\
\cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]} & D~E~d~(b,\_) & \defeq & \reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon}))\\
\cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]} & D~E~d~(b,c) & \defeq & \!\!\begin{array}{l}(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))\end{array}\\
\end{array}
\end{small}
$
}}
\caption{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}
\label{fig:barecubicalsetcoherences}
\end{figure*}

\subsection{Derived notions}
\label{sec:derived-notions}

On top of the basic definitions on
Figures~\ref{fig:barecubicalsetstructure},
\ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences},
we can define on Figures~\ref{fig:macros} and~\ref{fig:macroscont} a few other concepts at a
more standard level of abstraction. In particular, a homogeneous
$n$-box in the above sense is defined to be an object of type
$\myfullbox{l}^{n}(D_{n})$ for $D_{n} \defeq (A,=_A,...,=^n_A)$ the initial
segment of $n$-th first iterated equalities over $A$ (by convention, a
homogeneous $0$-box shall be the canonical singleton type). A $n$-tube
is of type $\mybox{l}^{n+1,n}(D_{n+1})$. An homogeneous (proper) $n$-cube
in some $n$-box $d$ is of type $\mycube{l}^{n+1,n}(\hd(D_{n+1}))(\tl(D_{n+1}))(d)$ and a
full $n$-cube is of type $\mycube{l}^{n+1,0}(\hd(D_{n+1}))(\tl(D_{n+1})))(\star)$.

Note that the components of an $n$-box or $n$-tube are tuples
associated to the left. For cubes, the components can be associated to
the left, and we call this a full $n$-cube or to the right, which we
call grounded $n$-cube, and which corresponds to ``complete'' partial
cubes, i.e. to partial cubes over the empty
box. Figure~\ref{fig:macros} show how to compute the $n$-box
surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated
equalities (see $\border{}$).

Figure~\ref{fig:macros} also shows how to compute the faces of a box or of a cube.

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\multicolumn{4}{c}{\mbox{Full (non-truncated) cubical sets with degeneracies}}\\
\\
\mycubset{l} && : & \sort{l+1}\\
\mycubset{l} && \defeq & \mycubsetfrom{l}{0}(\star)\\
\\
\mycubsetfrom{l}{n} & (D:\partialcubset{l}{n}) & : & \sort{l+1}\\
\mycubsetfrom{l}{n} & D & \defeq & \Sigma R:\mycubsetcomp{l}{n}(D).\,\mycubsetfrom{l}{n+1}(D,R)
\end{array}
$
}}
\caption{Definition of a bare cubical set (coinductive structure)}
\label{fig:barecubicalset}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\multicolumn{4}{c}{\mbox{\textit{Type of full $n$-cubes}}}\\
\\
\myfullcube{l}^{n} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n+1})\end{array}& : & \sort{l}\\
\myfullcube{l}^{n} & (D,E) & \defeq & \Sigma d:\myfullbox{l}^{n}(D).\, E.\mathsf{rel}(d)\\
\\
\multicolumn{4}{c}{\mbox{\textit{Type of $n$-tubes}}}\\
\\
\tube{l}^{n} & (D:\partialcubset{l}{n+1}) & : & \sort{l}\\
\tube{l}^{n} & D & \defeq & \mybox{l}^{n+1,n}(D)\\
\\
\multicolumn{4}{c}{\mbox{\textit{Type of grounded $n$-cubes}}}\\
\\
\mygroundedcube{l}^{n} & (D:\partialcubset{l}{n+1}) & : & \sort{l}\\
\mygroundedcube{l}^{n} & (D,E) & \defeq & \mycube{l}^{n,0}(D)(E)(\star)\\
\\
\multicolumn{4}{c}{\mbox{\textit{Type of fillers of some $n$-box}}}\\
\\
\propercube{l}^{n} & (D:\partialcubset{l}{n+1})~(d:\myfullbox{l}^{n}(\hd(D))) & : & \sort{l}\\
\propercube{l}^{n} & (D,E)~d & \defeq & E.\mathsf{rel}(d)\\
\\
\multicolumn{4}{c}{\mbox{\textit{Border of a grounded $n$-cube}}}\\
\\
\border{l}^{n} & (D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D)) & : & \myfullbox{l}^{n}(\hd(D))\\
\border{l}^{n} & D~c & \defeq & \border{l}^{n,0}(D)(\star)(c)\\
\\
\multicolumn{4}{c}{\mbox{\textit{where the border of partial cubes is defined by}}}\\
\\
\border{l}^{n,p} & (D:\partialcubset{l}{n+1})~(d:\mybox{l}^{n,p}(\hd(D)))~(c:\mycube{l}^{n,p}(\hd(D))(\tl(D))(d)) & : & \myfullbox{l}^{n}(\hd(D))\\
\border{l}^{n,p,[p=n]} & D~d~c & \defeq & d\\
\border{l}^{n,p,[p<n]} & D~d~(b,c) & \defeq & \border{l}^{n,p+1}(D)(d,b)(c)\\
\end{array}
$
}}
\caption{Standard derived notions}
\label{fig:macros}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\multicolumn{4}{c}{\mbox{$q$-th projection of an $n$-box}}\\
\\
\fulldownbox{l,\epsilon,q}{n,[q < n]} & (D:\partialcubset{l}{n})~(d:\myfullbox{l}^{n}(D)) &:& \myfullbox{l}^{n-1}(\hd(D))\\
\fulldownbox{l,\epsilon,q}{n} & D~(d,\_) &\defeq& \downbox{l,\epsilon,q}{n,n-1}(D)(d)\\
\\
\multicolumn{4}{c}{\mbox{$q$-th face of an $n$-cube}}\\
\\
\fulldowncube{l,\epsilon,q}{n,[q < n]} & (D:\partialcubset{l}{n+1})~(c:\myfullcube{l}^{n}(D)) &:& \myfullcube{l}^{n-1}(\hd(D))\\
\fulldowncube{l,\epsilon,q}{n} & (D,E)~c &\defeq& \downcube{l,\epsilon,q}{n,0}(D)(E)(\star)(c)\\
\\
\multicolumn{4}{c}{\mbox{\textit{where the extension of $\downbox{l}{}$ to $p>q$ is}}}\\
\\
\downbox{l,\epsilon,q}{n,p,[q < p < n]} & (D:\partialcubset{l}{n})~(d:\mybox{l}^{n,p}(D))& : & \myfullbox{l}^{n-1}(\hd(D))\\
\downbox{l,\epsilon,q}{n,q+1} & D~(d,b) & \defeq & \border{l}^{n-1,q}(\hd(D))(\downbox{l,\epsilon,q}{n,q}(D)(d))(b_{\epsilon})\\
\downbox{l,\epsilon,q}{n,p,[q < p-1]} & D~(d,b) & \defeq & \downbox{l,\epsilon,q}{n,p-1}(D)(d)
\end{array}
$
}}
\caption{Standard derived notions (continued)}
\label{fig:macroscont}
\end{figure*}

\bibliographystyle{plain}
\bibliography{biblio-en,extra}

\end{document}

### 2021-05-31 paper/paper.tex
[paper] A bit of house-keeping

@@
-\documentclass[a4paper,english,cleveref,autoref,thm-restate]{article}
+\documentclass[a4paper]{article}
 
-\usepackage[utf8x]{inputenc}
-\usepackage{t1enc}
+\usepackage{hyperref, fullpage, amssymb, stmaryrd, url, color, amsmath}
+\usepackage{bookmark, fontspec}
+\usepackage[backend=biber, style=apa, natbib=true, sorting=nyt, url=false,isbn=false,doi=false]{biblatex}
 
-\usepackage{hyperref}
-%\usepackage{proof}
-\usepackage{fullpage}
-\usepackage{amssymb}
-\usepackage{stmaryrd}
-%\usepackage{txfonts}
-\usepackage{url}
-\usepackage{color}
-%\usepackage{textcomp}
-\usepackage{amsmath}
-\usepackage{yfonts}
-\usepackage[all]{xy}
-\xyoption{2cell}
-\UseAllTwocells
+% Add biblio-en.bib to the database
+\addbibresource{biblio-en.bib}
 
@@
 \newcommand{\Overleftarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Leftarrowfill@{\mbox{${#2}$}}{}$}}
-%\newcommand{\Overrightarrow}[1]{\raisebox{1.4ex}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#1}$}}{}$}}
 \makeatother
@@
 \newcommand{\mkoverdim}[2]{\widetilde{#2}^{#1}}
-%\newcommand{\mkover}[1]{\dot{#1}}
-%\newcommand{\mkprod}[3]{\Pi {#1}\!:\!{#2}.\,{#3}}
 \newcommand{\mkprod}[3]{\Pi {#2}.\,{#3}}
@@
 \newcommand{\mkboundedprod}[4]{\Pi {#3}\!:\!{#1}\leq{#2}.\,{#4}}
-%\newcommand{\mklam}[3]{\lambda {#1}\!:\!{#2}.\,{#3}}
 \newcommand{\mklam}[3]{\lambda^{#2}.\,{#3}}
@@
 
-%\newcommand{\mksigma}[3]{\Sigma {#1}\!:\!{#2}.\,{#3}}
 \newcommand{\mksigma}[3]{\Sigma {#2}.\,{#3}}
@@
 \newcommand{\univ}{\boxempty}
-%\newcommand{\istype}{~:~S}
 \newcommand{\typeannot}{\mathsf{type}}
@@
 \newcommand{\mkeqovereqdim}[4]{{#2} \,\mkoverdim{#1}{=}_{#3}\, {#4}}
-%\newcommand{\mkeqtype}[3]{{#1} =_{#2} {#3}} % case where we can write either s or refl{s}
 \newcommand{\mkeqtype}[3]{{#1} =_{\typeannot} {#3}}
@@
 \newcommand{\lameq}[2]{\lambda {#1}.{#2}}
-%\newcommand{\reflterm}[1]{\textsf{refl}{#1}}
 \newcommand{\reflterm}[1]{\widehat{#1}}
@@
 \newcommand{\refltermdim}[2]{{\widehat{#2}}^{#1}}
-%\newcommand{\reflterm}[1]{\lambda{#1}}
-%\newcommand{\refltype}[1]{\lambda{#1}}
 \newcommand{\refltype}[1]{\reflterm{#1}}
@@
 \newcommand{\purerewrl}[1]{\overleftarrow{#1}}
-%\newcommand{\rewlr}[2]{\mathsf{rew}^\rightarrow\;{#1}\;\mathsf{in}\;{#2}}
-%\newcommand{\rewrl}[2]{\mathsf{rew}^\leftarrow\;{#1}\;\mathsf{in}\;{#2}}
 \newcommand{\rewlr}[2]{\overrightarrow{#1}(#2)}
@@
 \newcommand{\doublerewrl}[2]{\Overleftarrow{1.4ex}{#1}({#2})}
-%\newcommand{\mktuple}[6]{\{#1\mapsto #3(#1); #2\mapsto #4(#2); #1\mapsto #5(#1); #2\mapsto #6(#2)\}}
 \newcommand{\mktuple}[6]{\{#3; #4; #5; #6\}_{#1,#2}}
@@
 
-% Version basse
-%% \newcommand{\appi}[2]{{#1}_{#2}}
-%% \newcommand{\appidep}[2]{{#1}_{({#2})}}
-%% \newcommand{\bp}[1]{{#1}_0}
-%% \newcommand{\ep}[1]{{#1}_1}
-%% \newcommand{\bpdep}[1]{{#1}_{(0)}}
-%% \newcommand{\epdep}[1]{{#1}_{(1}}}
-% Version haute
-% \newcommand{\metaappi}[2]{{#1}_{[{#2}]}}
 \newcommand{\appi}[2]{{#1}\;\!{#2}}
@@
 \newcommand{\defeq}{\triangleq}
-%\newcommand{\metaequiv}{=\!\!\!=}
 \newcommand{\metaequiv}{\cong}
@@
 \newcommand{\deptransport}[3]{\mathsf{transportd}\,{#1}\,{#2}\,{#3}}
-%\newcommand{\swap}[1]{\mathsf{swap}(#1)}
-%\newcommand{\swapbracket}[1]{\mathsf{swap}(#1)}
-%\newcommand{\swaptype}[1]{\mathsf{swap}(#1)}
 \newcommand{\swap}[1]{{#1}^{\circ}}
@@
 
-\begin{document}
-
-\title{An indexed construction of semi-cubical types}
-
-\maketitle
-
 \newcommand{\emptysigma}{\bullet}
@@
 
-%\newcommand{\cubeovername}{cubeover}
-%\newcommand{\Cubeovername}{Cubeover}
 \newcommand{\cubeovername}{cube}
@@
 
-%\newcommand{\heteroofliftbox}[3]{\mathsf{subliftBox}_{#1}^{#2,#3}}
-%\newcommand{\heteroofliftlayer}[3]{\mathsf{subliftLayer}_{#1}^{#2,#3}}
-%\newcommand{\heteroofliftcube}[3]{\mathsf{subliftCube}_{#1}^{#2,#3}}
-
 \newcommand{\depdownbox}[2]{\mathsf{depsub{\homoname}box}_{#1}^{#2}}
@@
 
-%\newcommand{\downboxleft}{\mathsf{subbox}^L}
-%\newcommand{\downboxright}{\mathsf{subbox}^R}
-%\newcommand{\downlayerleft}{\mathsf{sublayer}^L}
-%\newcommand{\downlayerright}{\mathsf{sublayer}^R}
-%\newcommand{\downcubeleft}{\mathsf{sub\cubeovername}^L}
-%\newcommand{\downcuberight}{\mathsf{sub\cubeovername}^R}
-%% \newcommand{\downboxleft}{\downarrow^{\mathsf{box},L}}
-%% \newcommand{\downboxright}{\downarrow^{\mathsf{box},R}}
-%% \newcommand{\downlayerleft}{\downarrow^{\mathsf{layer},L}}
-%% \newcommand{\downlayerright}{\downarrow^{\mathsf{layer},R}}
-%% \newcommand{\downcubeleft}{\downarrow^{\mathsf{cube},L}}
-%% \newcommand{\downcuberight}{\downarrow^{\mathsf{cube},R}}
 \newcommand{\heterodownbox}[2]{\mathsf{sub{\heteroname}box}_{#1}^{#2}}
@@
 \newcommand{\downboxtype}[2]{\mathsf{Subbox}_{#1}^{#2}}
-%\newcommand{\downboxtypelarge}[1]{\mathsf{Subbox'}_{#1}}
 \newcommand{\downlayertype}[2]{\mathsf{Sublayer}_{#1}^{#2}}
@@
 \newcommand{\cohboxtype}[2]{\mathsf{Cohbox}_{#1}^{#2}}
-%\newcommand{\cohboxtypelarge}[1]{\mathsf{Cohbox'}_{#1}}
 \newcommand{\cohlayertype}[2]{\mathsf{Cohlayer}_{#1}^{#2}}
@@
 \newcommand{\connbox}{\mathsf{connbox}}
-%% \newcommand{\cohbox}{\mathsf{coh}^{\mathsf{box}}}
-%% \newcommand{\cohlayer}{\mathsf{coh}^{\mathsf{layer}}}
 \newcommand{\hd}{\mathsf{hd}}
@@
 
+\title{An indexed construction of semi-cubical types}
+\author{Hugo Herbelin}
+\author{Ramkumar Ramachandra}
+
+\begin{document}
+\maketitle
+
 \tableofcontents
@@
 \section{Introduction}
-
 \section{Semi-cubical sets}
@@
 
-The definition is dispatched over
-Figures~\ref{fig:barecubicalsetstructurecore},
-\ref{fig:barecubicalsetstructure}, \ref{fig:barecubicalsetfaces} and
-\ref{fig:barecubicalsetcoherences}. It describes the structure of the
-underlying higher-dimensional relations on which cubes and boxes are
-built, together with the definition of homogeneous $n$-boxes,
-homogeneous $n$-cubes, together with face operations on boxes and
-cubes, together with commutation properties of the face
-operations. All are mutually defined as types of the target language
-ETT. Note that such relational structure, cubes and boxes are relative
-to a universe.
+The definition is dispatched over Figures~\ref{fig:barecubicalsetstructurecore}, \ref{fig:barecubicalsetstructure}, \ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences}.
+It describes the structure of the underlying higher-dimensional relations on which cubes and boxes are built, together with the definition of homogeneous $n$-boxes, homogeneous $n$-cubes, together with face operations on boxes and cubes, together with commutation properties of the face operations.
+All are mutually defined as types of the target language ETT.
+Note that such relational structure, cubes and boxes are relative to a universe.
+Note the presence of a coherence condition $\cohbox{l}{}$ to ensuring that both sides of the equality in $\downlayer{l}{}$ and $\downcube{l}{}$ are in the same type.
+The proof of $\cohbox{l}{}$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
+Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
+Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\downbox{l}{}$ nor $\cohbox{l}{}$ anymore.
 
-Note the presence of a coherence condition $\cohbox{l}{}$ to
-ensuring that both sides of the equality in $\downlayer{l}{}$ and $\downcube{l}{}$
-are in the same type. The proof of $\cohbox{l}{}$ itself requires
-an higher-dimensional coherence condition which we obtain by
-working here in ETT where all proofs of an
-equality are identified (principle of Unicity of Identity Proofs). Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many 
-higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a
-discussion on the de facto need for recursive higher-dimensional
-coherence conditions in formulating higher-dimensional structures in
-type theory). Note also that for a given
-$n$, the coherence conditions evaluate to a reflexivity proof, so that
-the construction evaluates to an effective sequence of types of
-iterated relations not mentioning $\downbox{l}{}$ nor $\cohbox{l}{}$ anymore.
-
-When reflexivities are excepted, we call the structure thus defined
-\emph{bare truncated cubical sets}: \emph{bare} because it can be seen
-as defining a cubical equivalent to semi-simplicial sets with only
-faces as part of the structure (otherwise said, another terminology
-could have been ``semi-cubical'' sets); \emph{truncated} because we
-consider only such cubical sets up to some fixed dimension.
+When reflexivities are excepted, we call the structure thus defined \emph{bare truncated cubical sets}: \emph{bare} because it can be seen as defining a cubical equivalent to semi-simplicial sets with only faces as part of the structure (otherwise said, another terminology could have been ``semi-cubical'' sets); \emph{truncated} because we consider only such cubical sets up to some fixed dimension.
 
@@
         \begin{array}{llcl}
-\multicolumn{4}{c}{\mbox{\textit{Type of truncated cubical sets}}}\\
+          \multicolumn{4}{c}{\mbox{\textit{Type of truncated cubical sets}}}                                                     \\
           \\
-\partialcubset{l}{n} && : & \sort{l+1}\\
-\partialcubset{l}{0} && \defeq & \unittype\\
-\partialcubset{l}{n'+1} && \defeq & \Sigma D:\partialcubset{l}{n'}.\,\mycubsetcomp{l}{n'}(D)\\
+          \partialcubset{l}{n}    &                          & :      & \sort{l+1}                                               \\
+          \partialcubset{l}{0}    &                          & \defeq & \unittype                                                \\
+          \partialcubset{l}{n'+1} &                          & \defeq & \Sigma D:\partialcubset{l}{n'}.\,\mycubsetcomp{l}{n'}(D) \\
           \\
-\multicolumn{4}{c}{\mbox{\textit{Structure carried at each dimension}}}\\
+          \multicolumn{4}{c}{\mbox{\textit{Structure carried at each dimension}}}                                                \\
           \\
-\mycubsetcomp{l}{n} & (D:\partialcubset{l}{n}) & : & \sort{l}\\
-\mycubsetcomp{l}{n} & D & \defeq & \myfullbox{l}^{n}(D)\imp \sort{l}\\
+          \mycubsetcomp{l}{n}     & (D:\partialcubset{l}{n}) & :      & \sort{l}                                                 \\
+          \mycubsetcomp{l}{n}     & D                        & \defeq & \myfullbox{l}^{n}(D)\imp \sort{l}                        \\
         \end{array}
@@
         \begin{array}{llcl}
-\multicolumn{4}{c}{\mbox{\textit{Full homogeneous $n$-boxes}}}\\
+          \multicolumn{4}{c}{\mbox{\textit{Full homogeneous $n$-boxes}}}                                                                            \\
           \\
-\myfullbox{l}^{n} & (D:\partialcubset{l}{n}) & : & \sort{l}\\
-\myfullbox{l}^{n} & D & \defeq & \mybox{l}^{n,n}(D)\\
+          \myfullbox{l}^{n}           & (D:\partialcubset{l}{n})        & :      & \sort{l}                                                         \\
+          \myfullbox{l}^{n}           & D                               & \defeq & \mybox{l}^{n,n}(D)                                               \\
           \\
-\multicolumn{4}{c}{\mbox{\textit{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}}}\\
+          \multicolumn{4}{c}{\mbox{\textit{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}}}                                       \\
           \\
-\mybox{l}^{n,p,[p \leq n]} & (D:\partialcubset{l}{n}) & : & \sort{l}\\
-\mybox{l}^{n,0} & D & \defeq & \unittype\\
-\mybox{l}^{n,p'+1} & D & \defeq & \Sigma d:\mybox{l}^{n,p'}(D).\,\mylayer{l}^{n,p'}(D)(d)\\
+          \mybox{l}^{n,p,[p \leq n]}  & (D:\partialcubset{l}{n})        & :      & \sort{l}                                                         \\
+          \mybox{l}^{n,0}             & D                               & \defeq & \unittype                                                        \\
+          \mybox{l}^{n,p'+1}          & D                               & \defeq & \Sigma d:\mybox{l}^{n,p'}(D).\,\mylayer{l}^{n,p'}(D)(d)          \\
           \\
-\mylayer{l}^{n,p,[p < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array}& : & \sort{l}\\
-\mylayer{l}^{n,p} & D~d & \defeq & \!\!\begin{array}{l}\mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\\times\; \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))\end{array}\\
+          \mylayer{l}^{n,p,[p < n]}   & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \sort{l}                                                         \\
+          \mylayer{l}^{n,p}           & D~d                             & \defeq & \!\!\begin{array}{l}\mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\\times\; \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))\end{array}                                    \\
           \\
-\mycube{l}^{n,p,[p \leq n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\end{array} & : & \sort{l}\\
-\mycube{l}^{n,p,[p = n]} & D~E~d & \defeq & E.\mathsf{rel}(d)\\
-\mycube{l}^{n,p,[p < n]} & D~E~d & \defeq & \Sigma b:\mylayer{l}^{n,p}(D)(d).\,\mycube{l}^{n,p+1}(D)(E)(d,b)\\
+          \mycube{l}^{n,p,[p \leq n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \sort{l}                                                         \\
+          \mycube{l}^{n,p,[p = n]}    & D~E~d                           & \defeq & E.\mathsf{rel}(d)                                                \\
+          \mycube{l}^{n,p,[p < n]}    & D~E~d                           & \defeq & \Sigma b:\mylayer{l}^{n,p}(D)(d).\,\mycube{l}^{n,p+1}(D)(E)(d,b) \\
         \end{array}
@@
   \centerline{ \framebox{$
-\begin{small}
         \begin{array}{llcl}
-\downbox{l,\epsilon,q}{n,p,[p \leq q < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array}& : & \mybox{l}^{n-1,p}(\hd(D))\\
-\downbox{l,\epsilon,q}{n,0} & D~\unitpoint & \defeq & \unitpoint\\
-\downbox{l,\epsilon,q}{n,p'+1} & D~(d,b) & \defeq & (\downbox{l,\epsilon,q}{n,p'}(D)(d),\downlayer{l,\epsilon,q}{n,p'}(D)(d)(b))\\
+          \downbox{l,\epsilon,q}{n,p,[p \leq q < n]}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \mybox{l}^{n-1,p}(\hd(D))                                                             \\
+          \downbox{l,\epsilon,q}{n,0}                 & D~\unitpoint                    & \defeq & \unitpoint                                                                            \\
+          \downbox{l,\epsilon,q}{n,p'+1}              & D~(d,b)                         & \defeq & (\downbox{l,\epsilon,q}{n,p'}(D)(d),\downlayer{l,\epsilon,q}{n,p'}(D)(d)(b))          \\
           \\
-\downlayer{l,\epsilon,q}{n,p,[p < q < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array}& : & \mylayer{l}^{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))\\
-\downlayer{l,\epsilon,q}{n,p} & D~d~c & \defeq & \!\!\begin{array}{l}(\overrightarrow{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L)),\\\;\overrightarrow{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R)))\end{array}\\
+          \downlayer{l,\epsilon,q}{n,p,[p < q < n]}   & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array} & :      & \mylayer{l}^{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))                        \\
+          \downlayer{l,\epsilon,q}{n,p}               & D~d~c                           & \defeq & \!\!\begin{array}{l}(\overrightarrow{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L)),\\\;\overrightarrow{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R)))\end{array}                                                         \\
           \\
-\downcube{l,\epsilon,q}{n,p,[p \leq q < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array}& : & \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))\\
-\downcube{l,\epsilon,q}{n,p,[p=q]} & D~E~d~(b,\_) & \defeq & b_{\epsilon}\\
-\downcube{l,\epsilon,q}{n,p,[p<q]} & D~E~d~(b,c) & \defeq & (\downlayer{l,\epsilon,q}{n,p}(D)(d)(b),\downcube{l,\epsilon,q}{n,p+1}(D)(E)(d,b)(c))\\
+          \downcube{l,\epsilon,q}{n,p,[p \leq q < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array} & :      & \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))                 \\
+          \downcube{l,\epsilon,q}{n,p,[p=q]}          & D~E~d~(b,\_)                    & \defeq & b_{\epsilon}                                                                          \\
+          \downcube{l,\epsilon,q}{n,p,[p<q]}          & D~E~d~(b,c)                     & \defeq & (\downlayer{l,\epsilon,q}{n,p}(D)(d)(b),\downcube{l,\epsilon,q}{n,p+1}(D)(E)(d,b)(c)) \\
           \\
         \end{array}
-\end{small}
-$
-}}
+      $}}
   \caption{Definition of a homogeneous bare cubical set ($q$-th projection)}
@@
   \centerline{ \framebox{$
-\begin{small}
         \begin{array}{llcl}
-\cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\tiny\begin{array}{l}n,p\\\mbox{}[p \leq r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array}& : & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q-1}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r-1}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))\end{array}\\
-\cohbox{l,\epsilon,\epsilon',q,r}{n,0} & D~\unitpoint & \defeq & \reflett(\unitpoint)\\
-\cohbox{l,\epsilon,\epsilon',q,r}{n,p'+1} & D~(d,b) & \defeq & (\cohbox{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d)(b))\\
+          \cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r < q < n]\end{array}}    & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q-1}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r-1}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))\end{array}                                                                             \\
+          \cohbox{l,\epsilon,\epsilon',q,r}{n,0}                                & D~\unitpoint                     & \defeq & \reflett(\unitpoint)                                                                                         \\
+          \cohbox{l,\epsilon,\epsilon',q,r}{n,p'+1}                             & D~(d,b)                          & \defeq & (\cohbox{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d)(b))           \\
           \\
-\cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\tiny\begin{array}{l}n,p\\\mbox{}[p < r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array}& : & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))(\downlayer{l,\epsilon,q}{n,p}(D)(d)(b))\end{array}\\
-\cohlayer{l,\epsilon,\epsilon',q,r}{n,p} & D~d~c & \defeq & \!\!\begin{array}{l}(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L),\\\;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))\end{array}\\
+          \cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p < r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))(\downlayer{l,\epsilon,q}{n,p}(D)(d)(b))\end{array}                                                                             \\
+          \cohlayer{l,\epsilon,\epsilon',q,r}{n,p}                              & D~d~c                            & \defeq & \!\!\begin{array}{l}(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L),\\\;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))\end{array}                                                                               \\
           \\
-\cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\tiny\begin{array}{l}n,p\\\mbox{}[p \leq r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array}& : & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))(\downcube{l,\epsilon,q}{n,p}(D)(E)(d)(b))\end{array}\\
-\cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]} & D~E~d~(b,\_) & \defeq & \reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon}))\\
-\cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]} & D~E~d~(b,c) & \defeq & \!\!\begin{array}{l}(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))\end{array}\\
+          \cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r < q < n]\end{array}}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))(\downcube{l,\epsilon,q}{n,p}(D)(E)(d)(b))\end{array}                                                                             \\
+          \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]}                         & D~E~d~(b,\_)                     & \defeq & \reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon})) \\
+          \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]}                         & D~E~d~(b,c)                      & \defeq & \!\!\begin{array}{l}(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))\end{array}                                                                               \\
         \end{array}
-\end{small}
-$
-}}
+      $}}
   \caption{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}
@@
 
-On top of the basic definitions on
-Figures~\ref{fig:barecubicalsetstructure},
-\ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences},
-we can define on Figures~\ref{fig:macros} and~\ref{fig:macroscont} a few other concepts at a
-more standard level of abstraction. In particular, a homogeneous
-$n$-box in the above sense is defined to be an object of type
-$\myfullbox{l}^{n}(D_{n})$ for $D_{n} \defeq (A,=_A,...,=^n_A)$ the initial
-segment of $n$-th first iterated equalities over $A$ (by convention, a
-homogeneous $0$-box shall be the canonical singleton type). A $n$-tube
-is of type $\mybox{l}^{n+1,n}(D_{n+1})$. An homogeneous (proper) $n$-cube
-in some $n$-box $d$ is of type $\mycube{l}^{n+1,n}(\hd(D_{n+1}))(\tl(D_{n+1}))(d)$ and a
-full $n$-cube is of type $\mycube{l}^{n+1,0}(\hd(D_{n+1}))(\tl(D_{n+1})))(\star)$.
+On top of the basic definitions on Figures~\ref{fig:barecubicalsetstructure}, \ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences}, we can define on Figures~\ref{fig:macros} and~\ref{fig:macroscont} a few other concepts at a more standard level of abstraction.
+In particular, a homogeneous $n$-box in the above sense is defined to be an object of type $\myfullbox{l}^{n}(D_{n})$ for $D_{n} \defeq (A,=_A,...,=^n_A)$ the initial segment of $n$-th first iterated equalities over $A$ (by convention, a homogeneous $0$-box shall be the canonical singleton type).
+A $n$-tube is of type $\mybox{l}^{n+1,n}(D_{n+1})$.
+An homogeneous (proper) $n$-cube in some $n$-box $d$ is of type $\mycube{l}^{n+1,n}(\hd(D_{n+1}))(\tl(D_{n+1}))(d)$ and a full $n$-cube is of type $\mycube{l}^{n+1,0}(\hd(D_{n+1}))(\tl(D_{n+1})))(\star)$.
 
-Note that the components of an $n$-box or $n$-tube are tuples
-associated to the left. For cubes, the components can be associated to
-the left, and we call this a full $n$-cube or to the right, which we
-call grounded $n$-cube, and which corresponds to ``complete'' partial
-cubes, i.e. to partial cubes over the empty
-box. Figure~\ref{fig:macros} show how to compute the $n$-box
-surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated
-equalities (see $\border{}$).
+Note that the components of an $n$-box or $n$-tube are tuples associated to the left.
+For cubes, the components can be associated to the left, and we call this a full $n$-cube or to the right, which we call grounded $n$-cube, and which corresponds to ``complete'' partial cubes, i.e.
+to partial cubes over the empty box.
+Figure~\ref{fig:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see $\border{}$).
 
@@
         \begin{array}{llcl}
-\multicolumn{4}{c}{\mbox{Full (non-truncated) cubical sets with degeneracies}}\\
+          \multicolumn{4}{c}{\mbox{Full (non-truncated) cubical sets with degeneracies}}                                         \\
           \\
-\mycubset{l} && : & \sort{l+1}\\
-\mycubset{l} && \defeq & \mycubsetfrom{l}{0}(\star)\\
+          \mycubset{l}        &                          & :      & \sort{l+1}                                                   \\
+          \mycubset{l}        &                          & \defeq & \mycubsetfrom{l}{0}(\star)                                   \\
           \\
-\mycubsetfrom{l}{n} & (D:\partialcubset{l}{n}) & : & \sort{l+1}\\
+          \mycubsetfrom{l}{n} & (D:\partialcubset{l}{n}) & :      & \sort{l+1}                                                   \\
           \mycubsetfrom{l}{n} & D                        & \defeq & \Sigma R:\mycubsetcomp{l}{n}(D).\,\mycubsetfrom{l}{n+1}(D,R)
@@
         \begin{array}{llcl}
-\multicolumn{4}{c}{\mbox{\textit{Type of full $n$-cubes}}}\\
+          \multicolumn{4}{c}{\mbox{\textit{Type of full $n$-cubes}}}                                                                                                                            \\
           \\
-\myfullcube{l}^{n} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n+1})\end{array}& : & \sort{l}\\
-\myfullcube{l}^{n} & (D,E) & \defeq & \Sigma d:\myfullbox{l}^{n}(D).\, E.\mathsf{rel}(d)\\
+          \myfullcube{l}^{n}     & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n+1})\end{array}                                                               & :      & \sort{l}                                           \\
+          \myfullcube{l}^{n}     & (D,E)                                                                                          & \defeq & \Sigma d:\myfullbox{l}^{n}(D).\, E.\mathsf{rel}(d) \\
           \\
-\multicolumn{4}{c}{\mbox{\textit{Type of $n$-tubes}}}\\
+          \multicolumn{4}{c}{\mbox{\textit{Type of $n$-tubes}}}                                                                                                                                 \\
           \\
-\tube{l}^{n} & (D:\partialcubset{l}{n+1}) & : & \sort{l}\\
-\tube{l}^{n} & D & \defeq & \mybox{l}^{n+1,n}(D)\\
+          \tube{l}^{n}           & (D:\partialcubset{l}{n+1})                                                                     & :      & \sort{l}                                           \\
+          \tube{l}^{n}           & D                                                                                              & \defeq & \mybox{l}^{n+1,n}(D)                               \\
           \\
-\multicolumn{4}{c}{\mbox{\textit{Type of grounded $n$-cubes}}}\\
+          \multicolumn{4}{c}{\mbox{\textit{Type of grounded $n$-cubes}}}                                                                                                                        \\
           \\
-\mygroundedcube{l}^{n} & (D:\partialcubset{l}{n+1}) & : & \sort{l}\\
-\mygroundedcube{l}^{n} & (D,E) & \defeq & \mycube{l}^{n,0}(D)(E)(\star)\\
+          \mygroundedcube{l}^{n} & (D:\partialcubset{l}{n+1})                                                                     & :      & \sort{l}                                           \\
+          \mygroundedcube{l}^{n} & (D,E)                                                                                          & \defeq & \mycube{l}^{n,0}(D)(E)(\star)                      \\
           \\
-\multicolumn{4}{c}{\mbox{\textit{Type of fillers of some $n$-box}}}\\
+          \multicolumn{4}{c}{\mbox{\textit{Type of fillers of some $n$-box}}}                                                                                                                   \\
           \\
-\propercube{l}^{n} & (D:\partialcubset{l}{n+1})~(d:\myfullbox{l}^{n}(\hd(D))) & : & \sort{l}\\
-\propercube{l}^{n} & (D,E)~d & \defeq & E.\mathsf{rel}(d)\\
+          \propercube{l}^{n}     & (D:\partialcubset{l}{n+1})~(d:\myfullbox{l}^{n}(\hd(D)))                                       & :      & \sort{l}                                           \\
+          \propercube{l}^{n}     & (D,E)~d                                                                                        & \defeq & E.\mathsf{rel}(d)                                  \\
           \\
-\multicolumn{4}{c}{\mbox{\textit{Border of a grounded $n$-cube}}}\\
+          \multicolumn{4}{c}{\mbox{\textit{Border of a grounded $n$-cube}}}                                                                                                                     \\
           \\
-\border{l}^{n} & (D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D)) & : & \myfullbox{l}^{n}(\hd(D))\\
-\border{l}^{n} & D~c & \defeq & \border{l}^{n,0}(D)(\star)(c)\\
+          \border{l}^{n}         & (D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D))                                       & :      & \myfullbox{l}^{n}(\hd(D))                          \\
+          \border{l}^{n}         & D~c                                                                                            & \defeq & \border{l}^{n,0}(D)(\star)(c)                      \\
           \\
-\multicolumn{4}{c}{\mbox{\textit{where the border of partial cubes is defined by}}}\\
+          \multicolumn{4}{c}{\mbox{\textit{where the border of partial cubes is defined by}}}                                                                                                   \\
           \\
-\border{l}^{n,p} & (D:\partialcubset{l}{n+1})~(d:\mybox{l}^{n,p}(\hd(D)))~(c:\mycube{l}^{n,p}(\hd(D))(\tl(D))(d)) & : & \myfullbox{l}^{n}(\hd(D))\\
-\border{l}^{n,p,[p=n]} & D~d~c & \defeq & d\\
-\border{l}^{n,p,[p<n]} & D~d~(b,c) & \defeq & \border{l}^{n,p+1}(D)(d,b)(c)\\
+          \border{l}^{n,p}       & (D:\partialcubset{l}{n+1})~(d:\mybox{l}^{n,p}(\hd(D)))~(c:\mycube{l}^{n,p}(\hd(D))(\tl(D))(d)) & :      & \myfullbox{l}^{n}(\hd(D))                          \\
+          \border{l}^{n,p,[p=n]} & D~d~c                                                                                          & \defeq & d                                                  \\
+          \border{l}^{n,p,[p<n]} & D~d~(b,c)                                                                                      & \defeq & \border{l}^{n,p+1}(D)(d,b)(c)                      \\
         \end{array}
@@
         \begin{array}{llcl}
-\multicolumn{4}{c}{\mbox{$q$-th projection of an $n$-box}}\\
+          \multicolumn{4}{c}{\mbox{$q$-th projection of an $n$-box}}                                                                                                                            \\
           \\
-\fulldownbox{l,\epsilon,q}{n,[q < n]} & (D:\partialcubset{l}{n})~(d:\myfullbox{l}^{n}(D)) &:& \myfullbox{l}^{n-1}(\hd(D))\\
-\fulldownbox{l,\epsilon,q}{n} & D~(d,\_) &\defeq& \downbox{l,\epsilon,q}{n,n-1}(D)(d)\\
+          \fulldownbox{l,\epsilon,q}{n,[q < n]}   & (D:\partialcubset{l}{n})~(d:\myfullbox{l}^{n}(D))    & :      & \myfullbox{l}^{n-1}(\hd(D))                                                 \\
+          \fulldownbox{l,\epsilon,q}{n}           & D~(d,\_)                                             & \defeq & \downbox{l,\epsilon,q}{n,n-1}(D)(d)                                         \\
           \\
-\multicolumn{4}{c}{\mbox{$q$-th face of an $n$-cube}}\\
+          \multicolumn{4}{c}{\mbox{$q$-th face of an $n$-cube}}                                                                                                                                 \\
           \\
-\fulldowncube{l,\epsilon,q}{n,[q < n]} & (D:\partialcubset{l}{n+1})~(c:\myfullcube{l}^{n}(D)) &:& \myfullcube{l}^{n-1}(\hd(D))\\
-\fulldowncube{l,\epsilon,q}{n} & (D,E)~c &\defeq& \downcube{l,\epsilon,q}{n,0}(D)(E)(\star)(c)\\
+          \fulldowncube{l,\epsilon,q}{n,[q < n]}  & (D:\partialcubset{l}{n+1})~(c:\myfullcube{l}^{n}(D)) & :      & \myfullcube{l}^{n-1}(\hd(D))                                                \\
+          \fulldowncube{l,\epsilon,q}{n}          & (D,E)~c                                              & \defeq & \downcube{l,\epsilon,q}{n,0}(D)(E)(\star)(c)                                \\
           \\
-\multicolumn{4}{c}{\mbox{\textit{where the extension of $\downbox{l}{}$ to $p>q$ is}}}\\
+          \multicolumn{4}{c}{\mbox{\textit{where the extension of $\downbox{l}{}$ to $p>q$ is}}}                                                                                                \\
           \\
-\downbox{l,\epsilon,q}{n,p,[q < p < n]} & (D:\partialcubset{l}{n})~(d:\mybox{l}^{n,p}(D))& : & \myfullbox{l}^{n-1}(\hd(D))\\
-\downbox{l,\epsilon,q}{n,q+1} & D~(d,b) & \defeq & \border{l}^{n-1,q}(\hd(D))(\downbox{l,\epsilon,q}{n,q}(D)(d))(b_{\epsilon})\\
+          \downbox{l,\epsilon,q}{n,p,[q < p < n]} & (D:\partialcubset{l}{n})~(d:\mybox{l}^{n,p}(D))      & :      & \myfullbox{l}^{n-1}(\hd(D))                                                 \\
+          \downbox{l,\epsilon,q}{n,q+1}           & D~(d,b)                                              & \defeq & \border{l}^{n-1,q}(\hd(D))(\downbox{l,\epsilon,q}{n,q}(D)(d))(b_{\epsilon}) \\
           \downbox{l,\epsilon,q}{n,p,[q < p-1]}   & D~(d,b)                                              & \defeq & \downbox{l,\epsilon,q}{n,p-1}(D)(d)
@@
 
-\bibliographystyle{plain}
-\bibliography{biblio-en,extra}
+\printbibliography
 

### 2021-06-30 paper/paper.tex
[Cubical] Introduce PartialCubeBase
One fix of indices for r + shifting q by 1 in sublayer and all coq*

@@
 \newcommand{\downcube}[2]{\mathsf{sub{\homoname}cube}_{#1}^{#2}}
-\newcommand{\cohbox}[2]{\mathsf{coh{\homoname}box}_{#1}^{#2}}
+\newcommand{\cohbox}[2]{\mathsf{coh{\homoname}box}_{{#1}}^{{#2}}}
 \newcommand{\cohlayer}[2]{\mathsf{coh{\homoname}layer}_{#1}^{#2}}
@@
 
+\newcommand{\BDelta}{\ensuremath{\boldsymbol{\Delta}}}
+\newcommand{\Simplex}[1][n]{\ensuremath{\boldsymbol{\Delta^{#1}}}}
+\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
+\newcommand{\SSet}{\ensuremath{\text{Set}_{\boldsymbol{\Delta}}}}
+
 \title{An indexed construction of semi-cubical types}
+\author{Ramkumar Ramachandra}
 \author{Hugo Herbelin}
-\author{Ramkumar Ramachandra}
 
@@
 
-\section{Introduction}
+\section{The intuition from \SSet}
+
 \section{Semi-cubical sets}
@@
         \begin{array}{llcl}
-          \downbox{l,\epsilon,q}{n,p,[p \leq q < n]}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \mybox{l}^{n-1,p}(\hd(D))                                                             \\
+          \downbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \mybox{l}^{n-1,p}(\hd(D))                                                             \\
           \downbox{l,\epsilon,q}{n,0}                 & D~\unitpoint                    & \defeq & \unitpoint                                                                            \\
-          \downbox{l,\epsilon,q}{n,p'+1}              & D~(d,b)                         & \defeq & (\downbox{l,\epsilon,q}{n,p'}(D)(d),\downlayer{l,\epsilon,q}{n,p'}(D)(d)(b))          \\
+          \downbox{l,\epsilon,q}{n,p'+1}              & D~(d,b)                         & \defeq & (\downbox{l,\epsilon,q}{n,p'}(D)(d),\downlayer{l,\epsilon,q-1}{n,p'}(D)(d)(b))          \\
           \\
-          \downlayer{l,\epsilon,q}{n,p,[p < q < n]}   & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array} & :      & \mylayer{l}^{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))                        \\
-          \downlayer{l,\epsilon,q}{n,p}               & D~d~c                           & \defeq & \!\!\begin{array}{l}(\overrightarrow{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L)),\\\;\overrightarrow{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R)))\end{array}                                                         \\
+          \downlayer{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]}   & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array} & :      & \mylayer{l}^{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))                        \\
+          \downlayer{l,\epsilon,q}{n,p}               & D~d~c                           & \defeq & \!\!\begin{array}{l}(\overrightarrow{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L)),\\\;\overrightarrow{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R)))\end{array}                                                         \\
           \\
-          \downcube{l,\epsilon,q}{n,p,[p \leq q < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array} & :      & \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))                 \\
+          \downcube{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array} & :      & \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))                 \\
           \downcube{l,\epsilon,q}{n,p,[p=q]}          & D~E~d~(b,\_)                    & \defeq & b_{\epsilon}                                                                          \\
@@
         \begin{array}{llcl}
-          \cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r < q < n]\end{array}}    & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q-1}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r-1}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))\end{array}                                                                             \\
+          \cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}    & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r-1}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))\end{array}                                                                             \\
           \cohbox{l,\epsilon,\epsilon',q,r}{n,0}                                & D~\unitpoint                     & \defeq & \reflett(\unitpoint)                                                                                         \\
@@
           \\
-          \cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p < r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))(\downlayer{l,\epsilon,q}{n,p}(D)(d)(b))\end{array}                                                                             \\
+          \cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p < r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))\end{array}                                                                             \\
           \cohlayer{l,\epsilon,\epsilon',q,r}{n,p}                              & D~d~c                            & \defeq & \!\!\begin{array}{l}(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L),\\\;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))\end{array}                                                                               \\
           \\
-          \cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r < q < n]\end{array}}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q}{n,p}(D)(d))(\downcube{l,\epsilon,q}{n,p}(D)(E)(d)(b))\end{array}                                                                             \\
+          \cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))\end{array}                                                                             \\
           \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]}                         & D~E~d~(b,\_)                     & \defeq & \reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon})) \\

### 2021-06-30 paper/paper.tex
One other fix of indices for r

@@
         \begin{array}{llcl}
-          \cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}    & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r-1}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))\end{array}                                                                             \\
+          \cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}    & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))\end{array}                                                                             \\
           \cohbox{l,\epsilon,\epsilon',q,r}{n,0}                                & D~\unitpoint                     & \defeq & \reflett(\unitpoint)                                                                                         \\

### 2021-07-01 paper/paper.tex
[paper] Cleanup in progress

@@
-\documentclass[a4paper]{article}
+\documentclass{article}
 
-\usepackage{hyperref, fullpage, amssymb, stmaryrd, url, color, amsmath}
-\usepackage{bookmark, fontspec}
-\usepackage[backend=biber, style=apa, natbib=true, sorting=nyt, url=false,isbn=false,doi=false]{biblatex}
+\usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
+\usepackage{bookmark, titling, fontspec, xargs, multirow, polyglossia, luacode, fancyhdr, lastpage, amssymb}
+\usepackage{listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace}
+\usepackage[compact]{titlesec}
+\usepackage[margin=0.5in]{geometry}
+
+\usepackage[backend=biber, style=apa, natbib=true, sorting=nyt, url=false,isbn=false, doi=false]{biblatex}
 
@@
 \include{macros}
-\newcommand{\Type}{\mathsf{Type}}
-\newcommand{\Set}{\mathsf{Set}}
-\newcommand{\Prop}{\mathsf{Prop}}
-\newcommand{\refl}[1]{\mathsf{refl}\,{#1}}
+\newcommand{\imp}{\ensuremath{\rightarrow}}
+\newcommand{\revimp}{\ensuremath{\leftarrow}}
+
+\newcommand{\Type}{\ensuremath{\mathsf{Type}}}
+\newcommand{\Set}{\ensuremath{\mathsf{Set}}}
+\newcommand{\Prop}{\ensuremath{\mathsf{Prop}}}
+\newcommand{\refl}[1]{\ensuremath{\mathsf{refl}\,{#1}}}
 \newcommand{\mkmlidtype}[3]{{#1} =^{\mathrm{id}}_{#2} {#3}}
 \newcommand{\mkmleqdep}[3]{{#1} =^{\mathrm{dep}}_{#2} {#3}}
-\newcommand{\hrefl}[1]{\mathsf{refl^{\mathrm{dep}}}\,{#1}}
-\newcommand{\mluniv}{\mathsf{U}}
-\newcommand{\Jdep}[2]{\mathsf{J}\;{#1}\;{#2}}
+\newcommand{\hrefl}[1]{\ensuremath{\mathsf{refl^{\mathrm{dep}}}\,{#1}}}
+\newcommand{\mluniv}{\ensuremath{\mathsf{U}}}
+\newcommand{\Jdep}[2]{\ensuremath{\mathsf{J}\;{#1}\;{#2}}}
 
@@
 
-\newcommand{\sort}[1]{\mathsf{U}_{#1}}
+\newcommand{\sort}[1]{\ensuremath{\mathsf{U}_{#1}}}
 \newcommand{\univ}{\boxempty}
@@
 
-\newcommand{\defeq}{\triangleq}
+\newcommand{\defeq}{\ensuremath{\triangleq}}
 \newcommand{\metaequiv}{\cong}
@@
 
-\newcommand{\homoname}{}
 \newcommand{\heteroname}{het}
-\newcommand{\mycubsetcomp}[2]{\mathsf{cubset}_{#1}^{=#2}}
+\newcommand{\mycubsetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}
 
@@
 
-\newcommand{\mybox}[1]{\mathsf{{\homoname}box}_{#1}}
-\newcommand{\mylayer}[1]{\mathsf{{\homoname}layer}_{#1}}
-\newcommand{\mycube}[1]{\mathsf{{\homoname}\cubeovername}_{#1}}
-\newcommand{\downbox}[2]{\mathsf{sub{\homoname}box}_{#1}^{#2}}
-\newcommand{\downlayer}[2]{\mathsf{sub{\homoname}layer}_{#1}^{#2}}
-\newcommand{\downcube}[2]{\mathsf{sub{\homoname}cube}_{#1}^{#2}}
-\newcommand{\cohbox}[2]{\mathsf{coh{\homoname}box}_{{#1}}^{{#2}}}
-\newcommand{\cohlayer}[2]{\mathsf{coh{\homoname}layer}_{#1}^{#2}}
-\newcommand{\cohcube}[2]{\mathsf{coh{\homoname}\cubeovername}_{#1,#2}}
-\newcommand{\myfullbox}[1]{\mathsf{full{\homoname}box}_{#1}}
-\newcommand{\fulldownbox}[2]{\mathsf{subfull{\homoname}box}_{#1}^{#2}}
-\newcommand{\fulldowncube}[2]{\mathsf{subfull{\homoname}cube}_{#1}^{#2}}
+\newcommand{\mybox}[1]{\mathsf{box}_{#1}}
+\newcommand{\mylayer}[1]{\mathsf{layer}_{#1}}
+\newcommand{\mycube}[1]{\mathsf{\cubeovername}_{#1}}
+\newcommand{\downbox}[2]{\mathsf{subbox}_{#1}^{#2}}
+\newcommand{\downlayer}[2]{\mathsf{sublayer}_{#1}^{#2}}
+\newcommand{\downcube}[2]{\mathsf{subcube}_{#1}^{#2}}
+\newcommand{\cohbox}[2]{\mathsf{cohbox}_{{#1}}^{{#2}}}
+\newcommand{\cohlayer}[2]{\mathsf{cohlayer}_{#1}^{#2}}
+\newcommand{\cohcube}[2]{\mathsf{coh\cubeovername}_{#1,#2}}
+\newcommand{\myfullbox}[2]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
+\newcommand{\fulldownbox}[2]{\mathsf{subfullbox}_{#1}^{#2}}
+\newcommand{\fulldowncube}[2]{\mathsf{subfullcube}_{#1}^{#2}}
 
@@
 \newcommand{\expandheterolayer}[2]{\mathsf{expandLayer}_{#1}^{#2}}
-\newcommand{\expanddownbox}[2]{\mathsf{expandsub{\homoname}box}_{#1}^{#2}}
-\newcommand{\expanddownlayer}[2]{\mathsf{expandsub{\homoname}layer}_{#1}^{#2}}
-\newcommand{\expanddowncube}[2]{\mathsf{expandsub{\homoname}cube}_{#1}^{#2}}
+\newcommand{\expanddownbox}[2]{\mathsf{expandsubbox}_{#1}^{#2}}
+\newcommand{\expanddownlayer}[2]{\mathsf{expandsublayer}_{#1}^{#2}}
+\newcommand{\expanddowncube}[2]{\mathsf{expandsubcube}_{#1}^{#2}}
 
-\newcommand{\depdownbox}[2]{\mathsf{depsub{\homoname}box}_{#1}^{#2}}
-\newcommand{\depdownlayer}[2]{\mathsf{depsub{\homoname}layer}_{#1}^{#2}}
-\newcommand{\depdowncube}[2]{\mathsf{depsub{\homoname}cube}_{#1}^{#2}}
-\newcommand{\depdownboxbis}[2]{\mathsf{depsublift{\homoname}box}_{#1}^{#2}}
-\newcommand{\depdownlayerbis}[2]{\mathsf{depsublift{\homoname}layer}_{#1}^{#2}}
-\newcommand{\depdowncubebis}[2]{\mathsf{depsublift{\homoname}cube}_{#1}^{#2}}
-\newcommand{\depdownboxter}[2]{\mathsf{depsublift{\homoname}box'}_{#1}^{#2}}
-\newcommand{\depdownlayerter}[2]{\mathsf{depsublift{\homoname}layer'}_{#1}^{#2}}
-\newcommand{\depdowncubeter}[2]{\mathsf{depsublift{\homoname}cube'}_{#1}^{#2}}
+\newcommand{\depdownbox}[2]{\mathsf{depsubbox}_{#1}^{#2}}
+\newcommand{\depdownlayer}[2]{\mathsf{depsublayer}_{#1}^{#2}}
+\newcommand{\depdowncube}[2]{\mathsf{depsubcube}_{#1}^{#2}}
+\newcommand{\depdownboxbis}[2]{\mathsf{depsubliftbox}_{#1}^{#2}}
+\newcommand{\depdownlayerbis}[2]{\mathsf{depsubliftlayer}_{#1}^{#2}}
+\newcommand{\depdowncubebis}[2]{\mathsf{depsubliftcube}_{#1}^{#2}}
+\newcommand{\depdownboxter}[2]{\mathsf{depsubliftbox'}_{#1}^{#2}}
+\newcommand{\depdownlayerter}[2]{\mathsf{depsubliftlayer'}_{#1}^{#2}}
+\newcommand{\depdowncubeter}[2]{\mathsf{depsubliftcube'}_{#1}^{#2}}
 
-\newcommand{\depcohbox}[2]{\mathsf{depcoh{\homoname}box}_{#1}^{#2}}
-\newcommand{\depcohlayer}[2]{\mathsf{depcoh{\homoname}layer}_{#1}^{#2}}
-\newcommand{\depcohcube}[2]{\mathsf{depcoh{\homoname}cube}_{#1}^{#2}}
-\newcommand{\depcohboxbis}[2]{\mathsf{depcohlift{\homoname}box}_{#1}^{#2}}
-\newcommand{\depcohlayerbis}[2]{\mathsf{depcohlift{\homoname}layer}_{#1}^{#2}}
-\newcommand{\depcohcubebis}[2]{\mathsf{depcohlift{\homoname}cube}_{#1}^{#2}}
-\newcommand{\depcohboxter}[2]{\mathsf{depcohlift{\homoname}box'}_{#1}^{#2}}
-\newcommand{\depcohlayerter}[2]{\mathsf{depcohlift{\homoname}layer'}_{#1}^{#2}}
-\newcommand{\depcohcubeter}[2]{\mathsf{depcohlift{\homoname}cube'}_{#1}^{#2}}
+\newcommand{\depcohbox}[2]{\mathsf{depcohbox}_{#1}^{#2}}
+\newcommand{\depcohlayer}[2]{\mathsf{depcohlayer}_{#1}^{#2}}
+\newcommand{\depcohcube}[2]{\mathsf{depcohcube}_{#1}^{#2}}
+\newcommand{\depcohboxbis}[2]{\mathsf{depcohliftbox}_{#1}^{#2}}
+\newcommand{\depcohlayerbis}[2]{\mathsf{depcohliftlayer}_{#1}^{#2}}
+\newcommand{\depcohcubebis}[2]{\mathsf{depcohliftcube}_{#1}^{#2}}
+\newcommand{\depcohboxter}[2]{\mathsf{depcohliftbox'}_{#1}^{#2}}
+\newcommand{\depcohlayerter}[2]{\mathsf{depcohliftlayer'}_{#1}^{#2}}
+\newcommand{\depcohcubeter}[2]{\mathsf{depcohliftcube'}_{#1}^{#2}}
 
@@
 \newcommand{\heterodowncube}[2]{\mathsf{sub{\heteroname}\cubeovername}_{#1}^{#2}}
-\newcommand{\depdownboxtype}[2]{\mathsf{Subdep{\homoname}box}_{#1}^{#2}}
-\newcommand{\depdownlayertype}[2]{\mathsf{Subdep{\homoname}layer}_{#1}^{#2}}
-\newcommand{\depdowncubetype}[2]{\mathsf{Subdep{\homoname}\cubeovername}_{#1}^{#2}}
+\newcommand{\depdownboxtype}[2]{\mathsf{Subdepbox}_{#1}^{#2}}
+\newcommand{\depdownlayertype}[2]{\mathsf{Subdeplayer}_{#1}^{#2}}
+\newcommand{\depdowncubetype}[2]{\mathsf{Subdep\cubeovername}_{#1}^{#2}}
 \newcommand{\downboxtype}[2]{\mathsf{Subbox}_{#1}^{#2}}
@@
 \newcommand{\myappdepfullcubetype}[1]{\mathsf{homoappfullcube}_{#1}}
-\newcommand{\myfullcube}[1]{\mathsf{full{\homoname}cube}_{#1}}
+\newcommand{\myfullcube}[1]{\mathsf{fullcube}_{#1}}
 \newcommand{\myfullheteroboxtype}[2]{\mathsf{fullBox}_{#1}^{#2}}
@@
 \newcommand{\unitpoint}{\star}
-\newcommand{\unittype}{\mathsf{unit}}
+\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
 \newcommand{\eqett}{\equiv_{\mathit{ETT}}}
@@
 \newcommand{\mycubsetfrom}[2]{\mathsf{cubset}_{#1}^{\geq#2}}
-\newcommand{\partialcubset}[2]{\mathsf{cubset}_{#1}^{<#2}}
+\newcommand{\partialcubset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
 \newcommand{\mydepcubset}[1]{\mathsf{dephomocubset}_{#1}}
@@
 \newcommand{\hascomp}{\mathsf{hascomp}}
-\newcommand{\tube}[1]{\mathsf{{\homoname}tube}_{#1}}
-\newcommand{\propercube}[1]{\mathsf{proper{\homoname}filler}_{#1}}
+\newcommand{\tube}[1]{\mathsf{tube}_{#1}}
+\newcommand{\propercube}[1]{\mathsf{properfiller}_{#1}}
 \newcommand{\properheterocube}[2]{\mathsf{{\heteroname}filler}_{#1}^{#2}}
-\newcommand{\border}[1]{\mathsf{{\homoname}border}_{#1}}
+\newcommand{\border}[1]{\mathsf{border}_{#1}}
 \newcommand{\bordertype}[1]{\mathsf{Boxofcube}_{#1}}
@@
 \newcommand{\heterotube}[1]{\mathsf{{\heteroname}tube}_{#1}}
-\newcommand{\mygroundedcube}[1]{\mathsf{grounded{\homoname}cube}_{#1}}
+\newcommand{\mygroundedcube}[1]{\mathsf{groundedcube}_{#1}}
 \newcommand{\mygroundedheterocubetype}[1]{\mathsf{groundedCube}_{#1}}
@@
 
+% Simplicial set macros
 \newcommand{\BDelta}{\ensuremath{\boldsymbol{\Delta}}}
@@
 \newcommand{\SSet}{\ensuremath{\text{Set}_{\boldsymbol{\Delta}}}}
+
+% The eqntable environment, displaying the various
+\NewDocumentEnvironment{eqntable}{m}{\table[h!]\tabularx{\linewidth}{l c c c}}
+{\endtabularx\caption{#1}\endtable}
+
+% A block in the eqntable environment
+\newcommand{\eqnline}[4]{#1 & #2 & #3 & #4 \\}
+\newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}
 
@@
 
-\section{The intuition from \SSet}
-
 \section{Semi-cubical sets}
-\label{sec:truncated-cubical-sets}
 
@@
 
-\begin{figure*}
-  \centerline{ \framebox{$
-        \begin{array}{llcl}
-          \multicolumn{4}{c}{\mbox{\textit{Type of truncated cubical sets}}}                                                     \\
+\begin{eqntable}{Definition of a truncated cubical set (main part of the higher-dimensional relation structure)}
+  \mc{Type of truncated cubical sets} \\
+  \eqnline{\partialcubset{l}{n}}{}{:}{\sort{l+1}}
+  \eqnline{\partialcubset{l}{0}}{}{\defeq}{\unittype}
+  \eqnline{\partialcubset{l}{n'+1}}{}{\defeq}{\ensuremath{\Sigma}D:\partialcubset{l}{n'}.\,\mycubsetcomp{l}{n'}(D)}
   \\
-          \partialcubset{l}{n}    &                          & :      & \sort{l+1}                                               \\
-          \partialcubset{l}{0}    &                          & \defeq & \unittype                                                \\
-          \partialcubset{l}{n'+1} &                          & \defeq & \Sigma D:\partialcubset{l}{n'}.\,\mycubsetcomp{l}{n'}(D) \\
+  \mc{Structure carried at each dimension}
+  \eqnline{\mycubsetcomp{l}{n}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
+  \eqnline{\mycubsetcomp{l}{n}}{D}{\defeq}{\myfullbox{l}{n}(D)\imp \sort{l}}
+\end{eqntable}
+
+\begin{eqntable}{Definition of a truncated cubical set (boxes)}
+  \mc{Full homogeneous $n$-boxes}
+  \eqnline{\myfullbox{l}{n}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
+  \eqnline{\myfullbox{l}{n}}{D}{}{\defeq}{\mybox{l}^{n,n}(D)}
   \\
-          \multicolumn{4}{c}{\mbox{\textit{Structure carried at each dimension}}}                                                \\
+  \mc{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}
+  \eqnline{\mybox{l}^{n,p,[p \leq n]}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
+  \eqnline{\mybox{l}^{n,0}}{D}{\defeq}{ \unittype}
+  \eqnline{\mybox{l}^{n,p'+1}}{D}{\defeq}{\Sigma d:\mybox{l}^{n,p'}(D).\,\mylayer{l}^{n,p'}(D)(d)}
   \\
-          \mycubsetcomp{l}{n}     & (D:\partialcubset{l}{n}) & :      & \sort{l}                                                 \\
-          \mycubsetcomp{l}{n}     & D                        & \defeq & \myfullbox{l}^{n}(D)\imp \sort{l}                        \\
-        \end{array}
-      $
-    }}
-  \caption{Definition of a truncated cubical set (main part of the higher-dimensional relation structure)}
-  \label{fig:barecubicalsetstructurecore}
-\end{figure*}
-
-\begin{figure*}
-  \centerline{ \framebox{$
-        \begin{array}{llcl}
-          \multicolumn{4}{c}{\mbox{\textit{Full homogeneous $n$-boxes}}}                                                                            \\
+  \eqnline{\mylayer{l}^{n,p,[p < n]}{\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array}}{:}{\sort{l}}
+  \eqnline{\mylayer{l}^{n,p}}{D~d}{\defeq}{\begin{array}{l}\mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\\times\; \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))\end{array}}
   \\
-          \myfullbox{l}^{n}           & (D:\partialcubset{l}{n})        & :      & \sort{l}                                                         \\
-          \myfullbox{l}^{n}           & D                               & \defeq & \mybox{l}^{n,n}(D)                                               \\
-          \\
-          \multicolumn{4}{c}{\mbox{\textit{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}}}                                       \\
-          \\
-          \mybox{l}^{n,p,[p \leq n]}  & (D:\partialcubset{l}{n})        & :      & \sort{l}                                                         \\
-          \mybox{l}^{n,0}             & D                               & \defeq & \unittype                                                        \\
-          \mybox{l}^{n,p'+1}          & D                               & \defeq & \Sigma d:\mybox{l}^{n,p'}(D).\,\mylayer{l}^{n,p'}(D)(d)          \\
-          \\
-          \mylayer{l}^{n,p,[p < n]}   & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \sort{l}                                                         \\
-          \mylayer{l}^{n,p}           & D~d                             & \defeq & \!\!\begin{array}{l}\mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\\times\; \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))\end{array}                                    \\
-          \\
-          \mycube{l}^{n,p,[p \leq n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \sort{l}                                                         \\
-          \mycube{l}^{n,p,[p = n]}    & D~E~d                           & \defeq & E.\mathsf{rel}(d)                                                \\
-          \mycube{l}^{n,p,[p < n]}    & D~E~d                           & \defeq & \Sigma b:\mylayer{l}^{n,p}(D)(d).\,\mycube{l}^{n,p+1}(D)(E)(d,b) \\
-        \end{array}
-      $
-    }}
-  \caption{Definition of a truncated cubical set (boxes)}
-  \label{fig:barecubicalsetstructure}
-\end{figure*}
+  \eqnline{\mycube{l}^{n,p,[p \leq n]}}{\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\end{array}}{:}{\sort{l}}
+  \eqnline{\mycube{l}^{n,p,[p = n]}}{D~E~d}{\defeq}{E.\mathsf{rel}(d)}
+  \eqnline{\mycube{l}^{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma b:\mylayer{l}^{n,p}(D)(d).\,\mycube{l}^{n,p+1}(D)(E)(d,b)}
+\end{eqntable}
 
@@
 On top of the basic definitions on Figures~\ref{fig:barecubicalsetstructure}, \ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences}, we can define on Figures~\ref{fig:macros} and~\ref{fig:macroscont} a few other concepts at a more standard level of abstraction.
-In particular, a homogeneous $n$-box in the above sense is defined to be an object of type $\myfullbox{l}^{n}(D_{n})$ for $D_{n} \defeq (A,=_A,...,=^n_A)$ the initial segment of $n$-th first iterated equalities over $A$ (by convention, a homogeneous $0$-box shall be the canonical singleton type).
+In particular, a homogeneous $n$-box in the above sense is defined to be an object of type $\myfullbox{l}{n}(D_{n})$ for $D_{n} \defeq (A,=_A,...,=^n_A)$ the initial segment of $n$-th first iterated equalities over $A$ (by convention, a homogeneous $0$-box shall be the canonical singleton type).
 A $n$-tube is of type $\mybox{l}^{n+1,n}(D_{n+1})$.
@@
           \myfullcube{l}^{n}     & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n+1})\end{array}                                                               & :      & \sort{l}                                          \\
-          \myfullcube{l}^{n}     & (D,E)                                                                                          & \defeq & \Sigma d:\myfullbox{l}^{n}(D).\, E.\mathsf{rel}(d) \\
+          \myfullcube{l}^{n}     & (D,E)                                                                                          & \defeq & \Sigma d:\myfullbox{l}{n}(D).\, E.\mathsf{rel}(d) \\
           \\
@@
           \\
-          \propercube{l}^{n}     & (D:\partialcubset{l}{n+1})~(d:\myfullbox{l}^{n}(\hd(D)))                                       & :      & \sort{l}                                           \\
+          \propercube{l}^{n}     & (D:\partialcubset{l}{n+1})~(d:\myfullbox{l}{n}(\hd(D)))                                        & :      & \sort{l}                                          \\
           \propercube{l}^{n}     & (D,E)~d                                                                                        & \defeq & E.\mathsf{rel}(d)                                 \\
@@
           \\
-          \border{l}^{n}         & (D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D))                                       & :      & \myfullbox{l}^{n}(\hd(D))                          \\
+          \border{l}^{n}         & (D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D))                                       & :      & \myfullbox{l}{n}(\hd(D))                          \\
           \border{l}^{n}         & D~c                                                                                            & \defeq & \border{l}^{n,0}(D)(\star)(c)                     \\
@@
           \\
-          \border{l}^{n,p}       & (D:\partialcubset{l}{n+1})~(d:\mybox{l}^{n,p}(\hd(D)))~(c:\mycube{l}^{n,p}(\hd(D))(\tl(D))(d)) & :      & \myfullbox{l}^{n}(\hd(D))                          \\
+          \border{l}^{n,p}       & (D:\partialcubset{l}{n+1})~(d:\mybox{l}^{n,p}(\hd(D)))~(c:\mycube{l}^{n,p}(\hd(D))(\tl(D))(d)) & :      & \myfullbox{l}{n}(\hd(D))                          \\
           \border{l}^{n,p,[p=n]} & D~d~c                                                                                          & \defeq & d                                                 \\
@@
           \\
-          \fulldownbox{l,\epsilon,q}{n,[q < n]}   & (D:\partialcubset{l}{n})~(d:\myfullbox{l}^{n}(D))    & :      & \myfullbox{l}^{n-1}(\hd(D))                                                 \\
+          \fulldownbox{l,\epsilon,q}{n,[q < n]}   & (D:\partialcubset{l}{n})~(d:\myfullbox{l}{n}(D))     & :      & \myfullbox{l}{n-1}(\hd(D))                                                  \\
           \fulldownbox{l,\epsilon,q}{n}           & D~(d,\_)                                             & \defeq & \downbox{l,\epsilon,q}{n,n-1}(D)(d)                                         \\
@@
           \\
-          \downbox{l,\epsilon,q}{n,p,[q < p < n]} & (D:\partialcubset{l}{n})~(d:\mybox{l}^{n,p}(D))      & :      & \myfullbox{l}^{n-1}(\hd(D))                                                 \\
+          \downbox{l,\epsilon,q}{n,p,[q < p < n]} & (D:\partialcubset{l}{n})~(d:\mybox{l}^{n,p}(D))      & :      & \myfullbox{l}{n-1}(\hd(D))                                                  \\
           \downbox{l,\epsilon,q}{n,q+1}           & D~(d,b)                                              & \defeq & \border{l}^{n-1,q}(\hd(D))(\downbox{l,\epsilon,q}{n,q}(D)(d))(b_{\epsilon}) \\

### 2021-07-06 paper/paper.tex
[Cubical] Finish the O branch of cohboxSn
[paper] Fix build

@@
 
-\makeatletter
-\newcommand{\Overrightarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#2}$}}{}$}}
-\newcommand{\Overleftarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Leftarrowfill@{\mbox{${#2}$}}{}$}}
-\makeatother
-
 \newcommand{\highlight}[1]{\emph{#1}}
@@
 \include{macros}
+
+% Head and tail
+\newcommand{\hd}{\ensuremath{\mathsf{hd}}}
+\newcommand{\tl}{\ensuremath{\mathsf{tl}}}
+
+% Universes
+\newcommand{\sort}[1]{\ensuremath{\mathsf{U}_{#1}}}
+
+% The unit type
+\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
+
+% Definitional equality
+\newcommand{\defeq}{\ensuremath{\triangleq}}
+
+% Box, layer, and cube
+\newcommand{\mybox}[2]{\ensuremath{\mathsf{box}_{#1}^{#2}}}
+\newcommand{\mylayer}[2]{\ensuremath{\mathsf{layer}_{#1}^{#2}}}
+\newcommand{\mycube}[2]{\ensuremath{\mathsf{cube}_{#1}^{#2}}}
+
+% Subbox, sublayer, and subcube
+\newcommand{\downbox}[2]{\ensuremath{\mathsf{subbox}_{#1}^{#2}}}
+\newcommand{\downlayer}[2]{\ensuremath{\mathsf{sublayer}_{#1}^{#2}}}
+\newcommand{\downcube}[2]{\ensuremath{\mathsf{subcube}_{#1}^{#2}}}
+\newcommand{\myfullbox}[2]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
+
+% Coherence conditions
+\newcommand{\cohbox}[2]{\ensuremath{\mathsf{cohbox}_{{#1}}^{{#2}}}}
+\newcommand{\cohcube}[2]{\ensuremath{\mathsf{cohcube}_{#1,#2}}}
+\newcommand{\cohlayer}[2]{\ensuremath{\mathsf{cohlayer}_{#1}^{#2}}}
+
+\newcommand{\partialcubset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
+\newcommand{\mycubsetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}
+
+% Logical implication
 \newcommand{\imp}{\ensuremath{\rightarrow}}
+
+% Simplicial set macros
+\newcommand{\BDelta}{\ensuremath{\boldsymbol{\Delta}}}
+\newcommand{\Simplex}[1][n]{\ensuremath{\boldsymbol{\Delta^{#1}}}}
+\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
+\newcommand{\SSet}{\ensuremath{\text{Set}_{\boldsymbol{\Delta}}}}
+
+% The eqntable environment, displaying the various
+\NewDocumentEnvironment{eqntable}{m}{\table[h!]
+\tabularx{\textwidth}{@{} l X c X @{}}\toprule}
+{\endtabularx\hrule\caption{#1}\endtable}
+
+% A block in the eqntable environment
+\newcommand{\eqnline}[4]{#1 & #2 & #3 & #4 \\}
+\newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}
+
+% Junk follows
+
 \newcommand{\revimp}{\ensuremath{\leftarrow}}
@@
 
-\newcommand{\sort}[1]{\ensuremath{\mathsf{U}_{#1}}}
 \newcommand{\univ}{\boxempty}
@@
 
-\newcommand{\defeq}{\ensuremath{\triangleq}}
 \newcommand{\metaequiv}{\cong}
@@
 \newcommand{\heteroname}{het}
-\newcommand{\mycubsetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}
 
 \newcommand{\informalcube}{\mathsf{cube}}
-\newcommand{\informalcubeover}{\mathsf{\cubeovername}}
+\newcommand{\informalcubeover}{\mathsf{cube}}
 
-\newcommand{\cubeovername}{cube}
-\newcommand{\Cubeovername}{Cube}
 \newcommand{\pboxname}{box}
@@
 
-\newcommand{\mybox}[1]{\mathsf{box}_{#1}}
-\newcommand{\mylayer}[1]{\mathsf{layer}_{#1}}
-\newcommand{\mycube}[1]{\mathsf{\cubeovername}_{#1}}
-\newcommand{\downbox}[2]{\mathsf{subbox}_{#1}^{#2}}
-\newcommand{\downlayer}[2]{\mathsf{sublayer}_{#1}^{#2}}
-\newcommand{\downcube}[2]{\mathsf{subcube}_{#1}^{#2}}
-\newcommand{\cohbox}[2]{\mathsf{cohbox}_{{#1}}^{{#2}}}
-\newcommand{\cohlayer}[2]{\mathsf{cohlayer}_{#1}^{#2}}
-\newcommand{\cohcube}[2]{\mathsf{coh\cubeovername}_{#1,#2}}
-\newcommand{\myfullbox}[2]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
 \newcommand{\fulldownbox}[2]{\mathsf{subfullbox}_{#1}^{#2}}
@@
 \newcommand{\myheterolayer}[2]{\mathsf{{\heteroname}layer}_{#1}^{#2}}
-\newcommand{\myheterocube}[2]{\mathsf{{\heteroname}\cubeovername}_{#1}^{#2}}
+\newcommand{\myheterocube}[2]{\mathsf{{\heteroname}cube}_{#1}^{#2}}
 \newcommand{\myheteroboxtype}[2]{\mathsf{Box}_{#1}^{#2}}
 \newcommand{\myheterolayertype}[2]{\mathsf{Layer}_{#1}^{#2}}
-\newcommand{\myheterocubetype}[2]{\mathsf{\Cubeovername}_{#1}^{#2}}
+\newcommand{\myheterocubetype}[2]{\mathsf{Cube}_{#1}^{#2}}
 
@@
 \newcommand{\mydepheterolayer}[3]{\mathsf{depLayer}_{#1}^{#2,#3}}
-\newcommand{\mydepheterocube}[3]{\mathsf{dep\Cubeovername}_{#1}^{#2,#3}}
+\newcommand{\mydepheterocube}[3]{\mathsf{depCube}_{#1}^{#2,#3}}
 \newcommand{\liftfulldepheterobox}[3]{\mathsf{liftfullBox}_{#1}^{#2,#3}}
@@
 \newcommand{\liftdepheterolayer}[3]{\mathsf{liftLayer}_{#1}^{#2,#3}}
-\newcommand{\liftdepheterocube}[3]{\mathsf{lift\Cubeovername}_{#1}^{#2,#3}}
+\newcommand{\liftdepheterocube}[3]{\mathsf{liftCube}_{#1}^{#2,#3}}
 
-\newcommand{\expandheterocube}[2]{\mathsf{expand\Cubeovername}_{#1}^{#2}}
+\newcommand{\expandheterocube}[2]{\mathsf{expandCube}_{#1}^{#2}}
 \newcommand{\expandheterolayer}[2]{\mathsf{expandLayer}_{#1}^{#2}}
@@
 \newcommand{\heterodownlayer}[2]{\mathsf{sub{\heteroname}layer}_{#1}^{#2}}
-\newcommand{\heterodowncube}[2]{\mathsf{sub{\heteroname}\cubeovername}_{#1}^{#2}}
+\newcommand{\heterodowncube}[2]{\mathsf{sub{\heteroname}cube}_{#1}^{#2}}
 \newcommand{\depdownboxtype}[2]{\mathsf{Subdepbox}_{#1}^{#2}}
 \newcommand{\depdownlayertype}[2]{\mathsf{Subdeplayer}_{#1}^{#2}}
-\newcommand{\depdowncubetype}[2]{\mathsf{Subdep\cubeovername}_{#1}^{#2}}
+\newcommand{\depdowncubetype}[2]{\mathsf{Subdepcube}_{#1}^{#2}}
 \newcommand{\downboxtype}[2]{\mathsf{Subbox}_{#1}^{#2}}
 \newcommand{\downlayertype}[2]{\mathsf{Sublayer}_{#1}^{#2}}
-\newcommand{\downcubetype}[2]{\mathsf{Sub\cubeovername}_{#1}^{#2}}
+\newcommand{\downcubetype}[2]{\mathsf{Subcube}_{#1}^{#2}}
 \newcommand{\cohreflbox}[1]{\mathsf{cohreflbox}_{#1}}
@@
 \newcommand{\cohlayertype}[2]{\mathsf{Cohlayer}_{#1}^{#2}}
-\newcommand{\cohcubetype}[2]{\mathsf{Coh\cubeovername}_{#1}^{#2}}
+\newcommand{\cohcubetype}[2]{\mathsf{Cohcube}_{#1}^{#2}}
 \newcommand{\heterocohbox}[2]{\mathsf{coh{\heteroname}box}_{#1}^{#2}}
 \newcommand{\heterocohlayer}[2]{\mathsf{coh{\heteroname}layer}_{#1}^{#2}}
-\newcommand{\heterocohcube}[2]{\mathsf{coh{\heteroname}\cubeovername}_{#1}^{#2}}
+\newcommand{\heterocohcube}[2]{\mathsf{coh{\heteroname}cube}_{#1}^{#2}}
 \newcommand{\myappdepbox}[1]{\mathsf{homoappbox}_{#1}}
 \newcommand{\myappdeplayer}[1]{\mathsf{homoapplayer}_{#1}}
-\newcommand{\myappdepcube}[1]{\mathsf{homoapp\cubeovername}_{#1}}
+\newcommand{\myappdepcube}[1]{\mathsf{homoappcube}_{#1}}
 \newcommand{\myappdepfullcube}[1]{\mathsf{homoappfullcube}_{#1}}
@@
 \newcommand{\myappdeplayertype}[1]{\mathsf{homoapplayer}_{#1}}
-\newcommand{\myappdepcubetype}[1]{\mathsf{homoapp\cubeovername}_{#1}}
+\newcommand{\myappdepcubetype}[1]{\mathsf{homoappcube}_{#1}}
 \newcommand{\myappdepfullcubetype}[1]{\mathsf{homoappfullcube}_{#1}}
@@
 \newcommand{\unitpoint}{\star}
-\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
 \newcommand{\eqett}{\equiv_{\mathit{ETT}}}
@@
 \newcommand{\mycubsetfrom}[2]{\mathsf{cubset}_{#1}^{\geq#2}}
-\newcommand{\partialcubset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
 \newcommand{\mydepcubset}[1]{\mathsf{dephomocubset}_{#1}}
@@
 \newcommand{\myappheterodeplayer}[1]{\mathsf{applayer}_{#1}}
-\newcommand{\myappheterodepcube}[1]{\mathsf{app\cubeovername}_{#1}}
+\newcommand{\myappheterodepcube}[1]{\mathsf{appcube}_{#1}}
 \newcommand{\myappheterodepfullcube}[1]{\mathsf{appfullcube}_{#1}}
@@
 \newcommand{\myappheterodeplayertype}[1]{\mathsf{applayer}_{#1}}
-\newcommand{\myappheterodepcubetype}[1]{\mathsf{app\cubeovername}_{#1}}
+\newcommand{\myappheterodepcubetype}[1]{\mathsf{appcube}_{#1}}
 \newcommand{\myappheterodepfullcubetype}[1]{\mathsf{appfullcube}_{#1}}
@@
 \newcommand{\connbox}{\mathsf{connbox}}
-\newcommand{\hd}{\mathsf{hd}}
-\newcommand{\tl}{\mathsf{tl}}
 \newcommand{\first}{\mathsf{first}}
@@
 \newcommand{\UIP}{\mathsf{UIP}}
-
-% Simplicial set macros
-\newcommand{\BDelta}{\ensuremath{\boldsymbol{\Delta}}}
-\newcommand{\Simplex}[1][n]{\ensuremath{\boldsymbol{\Delta^{#1}}}}
-\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
-\newcommand{\SSet}{\ensuremath{\text{Set}_{\boldsymbol{\Delta}}}}
-
-% The eqntable environment, displaying the various
-\NewDocumentEnvironment{eqntable}{m}{\table[h!]\tabularx{\linewidth}{l c c c}}
-{\endtabularx\caption{#1}\endtable}
-
-% A block in the eqntable environment
-\newcommand{\eqnline}[4]{#1 & #2 & #3 & #4 \\}
-\newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}
 
@@
   \eqnline{\myfullbox{l}{n}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
-  \eqnline{\myfullbox{l}{n}}{D}{}{\defeq}{\mybox{l}^{n,n}(D)}
+  \eqnline{\myfullbox{l}{n}}{D}{\defeq}{\mybox{l}{n,n}(D)}
   \\
   \mc{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}
-  \eqnline{\mybox{l}^{n,p,[p \leq n]}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
-  \eqnline{\mybox{l}^{n,0}}{D}{\defeq}{ \unittype}
-  \eqnline{\mybox{l}^{n,p'+1}}{D}{\defeq}{\Sigma d:\mybox{l}^{n,p'}(D).\,\mylayer{l}^{n,p'}(D)(d)}
+  \eqnline{\mybox{l}{n,p,[p \leq n]}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
+  \eqnline{\mybox{l}{n,0}}{D}{\defeq}{\unittype}
+  \eqnline{\mybox{l}{n,p'+1}}{D}{\defeq}{\Sigma d:\mybox{l}{n,p'}(D).\,\mylayer{l}{n,p'}(D)(d)}
   \\
-  \eqnline{\mylayer{l}^{n,p,[p < n]}{\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array}}{:}{\sort{l}}
-  \eqnline{\mylayer{l}^{n,p}}{D~d}{\defeq}{\begin{array}{l}\mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\\times\; \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))\end{array}}
+  \eqnline{\mylayer{l}{n,p,[p < n]}}{\shortstack{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}
+  \eqnline{\mylayer{l}{n,p}}{D~d}{\defeq}{\shortstack{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\ \times\; \mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))}}
   \\
-  \eqnline{\mycube{l}^{n,p,[p \leq n]}}{\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\end{array}}{:}{\sort{l}}
-  \eqnline{\mycube{l}^{n,p,[p = n]}}{D~E~d}{\defeq}{E.\mathsf{rel}(d)}
-  \eqnline{\mycube{l}^{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma b:\mylayer{l}^{n,p}(D)(d).\,\mycube{l}^{n,p+1}(D)(E)(d,b)}
+  \eqnline{\mycube{l}{n,p,[p \leq n]}}{\shortstack{(D:\partialcubset{l}{n}) \\(E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}
+  \eqnline{\mycube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{E.\ensuremath{\mathsf{rel}}(d)}
+  \eqnline{\mycube{l}{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma b:\mylayer{l}{n,p}(D)(d).\,\mycube{l}{n,p+1}(D)(E)(d,b)}
 \end{eqntable}
@@
         \begin{array}{llcl}
-          \downbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}   & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \mybox{l}^{n-1,p}(\hd(D))                                                             \\
+          \downbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}   & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\end{array} & :      & \mybox{l}{n-1,p}(\hd(D))                                                              \\
           \downbox{l,\epsilon,q}{n,0}                         & D~\unitpoint                    & \defeq & \unitpoint                                                                            \\
@@
           \\
-          \downlayer{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array} & :      & \mylayer{l}^{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))                      \\
+          \downlayer{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\\(b:\mylayer{l}{n,p}(D)(d))\end{array} & :      & \mylayer{l}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))                       \\
           \downlayer{l,\epsilon,q}{n,p}                       & D~d~c                           & \defeq & \!\!\begin{array}{l}(\overrightarrow{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L)),\\\;\overrightarrow{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R)))\end{array}                                                         \\
           \\
-          \downcube{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array} & :      & \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))               \\
+          \downcube{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}{n,p}(D))\\(b:\mycube{l}{n,p}(D)(E)(d))\end{array} & :      & \mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))                \\
           \downcube{l,\epsilon,q}{n,p,[p=q]}                  & D~E~d~(b,\_)                    & \defeq & b_{\epsilon}                                                                          \\
@@
         \begin{array}{llcl}
-          \cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}    & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))\end{array}                                                                             \\
+          \cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}    & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\end{array}  & :      & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))\end{array}                                                                              \\
           \cohbox{l,\epsilon,\epsilon',q,r}{n,0}                                & D~\unitpoint                     & \defeq & \reflett(\unitpoint)                                                                                         \\
@@
           \\
-          \cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p < r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))\end{array}                                                                             \\
+          \cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p < r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\\(b:\mylayer{l}{n,p}(D)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))\end{array}                                                                             \\
           \cohlayer{l,\epsilon,\epsilon',q,r}{n,p}                              & D~d~c                            & \defeq & \!\!\begin{array}{l}(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L),\\\;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))\end{array}                                                                               \\
           \\
-          \cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))\end{array}                                                                             \\
+          \cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}{n,p}(D))\\(b:\mycube{l}{n,p}(D)(E)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))\end{array}                                                                             \\
           \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]}                         & D~E~d~(b,\_)                     & \defeq & \reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon})) \\
@@
 In particular, a homogeneous $n$-box in the above sense is defined to be an object of type $\myfullbox{l}{n}(D_{n})$ for $D_{n} \defeq (A,=_A,...,=^n_A)$ the initial segment of $n$-th first iterated equalities over $A$ (by convention, a homogeneous $0$-box shall be the canonical singleton type).
-A $n$-tube is of type $\mybox{l}^{n+1,n}(D_{n+1})$.
-An homogeneous (proper) $n$-cube in some $n$-box $d$ is of type $\mycube{l}^{n+1,n}(\hd(D_{n+1}))(\tl(D_{n+1}))(d)$ and a full $n$-cube is of type $\mycube{l}^{n+1,0}(\hd(D_{n+1}))(\tl(D_{n+1})))(\star)$.
+A $n$-tube is of type $\mybox{l}{n+1,n}(D_{n+1})$.
+An homogeneous (proper) $n$-cube in some $n$-box $d$ is of type $\mycube{l}{n+1,n}(\hd(D_{n+1}))(\tl(D_{n+1}))(d)$ and a full $n$-cube is of type $\mycube{l}{n+1,0}(\hd(D_{n+1}))(\tl(D_{n+1})))(\star)$.
 
@@
           \tube{l}^{n}           & (D:\partialcubset{l}{n+1})                                                                   & :      & \sort{l}                                          \\
-          \tube{l}^{n}           & D                                                                                              & \defeq & \mybox{l}^{n+1,n}(D)                              \\
+          \tube{l}^{n}           & D                                                                                            & \defeq & \mybox{l}{n+1,n}(D)                               \\
           \\
@@
           \mygroundedcube{l}^{n} & (D:\partialcubset{l}{n+1})                                                                   & :      & \sort{l}                                          \\
-          \mygroundedcube{l}^{n} & (D,E)                                                                                          & \defeq & \mycube{l}^{n,0}(D)(E)(\star)                     \\
+          \mygroundedcube{l}^{n} & (D,E)                                                                                        & \defeq & \mycube{l}{n,0}(D)(E)(\star)                      \\
           \\
@@
           \\
-          \border{l}^{n,p}       & (D:\partialcubset{l}{n+1})~(d:\mybox{l}^{n,p}(\hd(D)))~(c:\mycube{l}^{n,p}(\hd(D))(\tl(D))(d)) & :      & \myfullbox{l}{n}(\hd(D))                          \\
+          \border{l}^{n,p}       & (D:\partialcubset{l}{n+1})~(d:\mybox{l}{n,p}(\hd(D)))~(c:\mycube{l}{n,p}(\hd(D))(\tl(D))(d)) & :      & \myfullbox{l}{n}(\hd(D))                          \\
           \border{l}^{n,p,[p=n]} & D~d~c                                                                                        & \defeq & d                                                 \\
@@
           \\
-          \downbox{l,\epsilon,q}{n,p,[q < p < n]} & (D:\partialcubset{l}{n})~(d:\mybox{l}^{n,p}(D))      & :      & \myfullbox{l}{n-1}(\hd(D))                                                  \\
+          \downbox{l,\epsilon,q}{n,p,[q < p < n]} & (D:\partialcubset{l}{n})~(d:\mybox{l}{n,p}(D))       & :      & \myfullbox{l}{n-1}(\hd(D))                                                  \\
           \downbox{l,\epsilon,q}{n,q+1}           & D~(d,b)                                              & \defeq & \border{l}^{n-1,q}(\hd(D))(\downbox{l,\epsilon,q}{n,q}(D)(d))(b_{\epsilon}) \\

### 2021-07-06 paper/paper.tex
[paper] One more figure cleaned up

@@
 \usepackage{bookmark, titling, fontspec, xargs, multirow, polyglossia, luacode, fancyhdr, lastpage, amssymb}
-\usepackage{listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace}
+\usepackage{listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace, makecell}
 \usepackage[compact]{titlesec}
@@
 \newcommand{\imp}{\ensuremath{\rightarrow}}
+\newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
 
@@
 \NewDocumentEnvironment{eqntable}{m}{\table[h!]
-\tabularx{\textwidth}{@{} l X c X @{}}\toprule}
+\tabularx{\textwidth}{@{} l c c X @{}}\toprule}
 {\endtabularx\hrule\caption{#1}\endtable}
@@
   \\
-  \eqnline{\mylayer{l}{n,p,[p < n]}}{\shortstack{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}
-  \eqnline{\mylayer{l}{n,p}}{D~d}{\defeq}{\shortstack{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\ \times\; \mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))}}
+  \eqnline{\mylayer{l}{n,p,[p < n]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}
+
+  \eqnline{\mylayer{l}{n,p}}{D~d}{\defeq}{\makecell{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\ \times\; \mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))}}
+
   \\
-  \eqnline{\mycube{l}{n,p,[p \leq n]}}{\shortstack{(D:\partialcubset{l}{n}) \\(E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}
+
+  \eqnline{\mycube{l}{n,p,[p \leq n]}}{\makecell{(D:\partialcubset{l}{n}) \\(E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}
+
   \eqnline{\mycube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{E.\ensuremath{\mathsf{rel}}(d)}
+
   \eqnline{\mycube{l}{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma b:\mylayer{l}{n,p}(D)(d).\,\mycube{l}{n,p+1}(D)(E)(d,b)}
@@
 
-\begin{figure*}
-  \centerline{ \framebox{$
-        \begin{array}{llcl}
-          \downbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}   & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\end{array} & :      & \mybox{l}{n-1,p}(\hd(D))                                                              \\
-          \downbox{l,\epsilon,q}{n,0}                         & D~\unitpoint                    & \defeq & \unitpoint                                                                            \\
-          \downbox{l,\epsilon,q}{n,p'+1}                      & D~(d,b)                         & \defeq & (\downbox{l,\epsilon,q}{n,p'}(D)(d),\downlayer{l,\epsilon,q-1}{n,p'}(D)(d)(b))        \\
+\begin{eqntable}{Definition of a homogeneous bare cubical set ($q$-th projection)}
+  \eqnline{\downbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\mybox{l}{n-1,p}(\hd(D))}
+
+  \eqnline{\downbox{l,\epsilon,q}{n,p'+1}}{D~(d,b)}{\defeq}{(\downbox{l,\epsilon,q}{n,p'}(D)(d),\downlayer{l,\epsilon,q-1}{n,p'}(D)(d)(b))}
+
   \\
-          \downlayer{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\\(b:\mylayer{l}{n,p}(D)(d))\end{array} & :      & \mylayer{l}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))                       \\
-          \downlayer{l,\epsilon,q}{n,p}                       & D~d~c                           & \defeq & \!\!\begin{array}{l}(\overrightarrow{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L)),\\\;\overrightarrow{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R)))\end{array}                                                         \\
+
+  \eqnline{\downlayer{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D)) \\ (b:\mylayer{l}{n,p}(D)(d))}}{:}{\mylayer{l}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}
+
+  \eqnline{\downlayer{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))($c_L$)), \\ \;\overright{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))($c_R$)))}}
+
   \\
-          \downcube{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}{n,p}(D))\\(b:\mycube{l}{n,p}(D)(E)(d))\end{array} & :      & \mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))                \\
-          \downcube{l,\epsilon,q}{n,p,[p=q]}                  & D~E~d~(b,\_)                    & \defeq & b_{\epsilon}                                                                          \\
-          \downcube{l,\epsilon,q}{n,p,[p<q]}                  & D~E~d~(b,c)                     & \defeq & (\downlayer{l,\epsilon,q}{n,p}(D)(d)(b),\downcube{l,\epsilon,q}{n,p+1}(D)(E)(d,b)(c)) \\
-          \\
-        \end{array}
-      $}}
-  \caption{Definition of a homogeneous bare cubical set ($q$-th projection)}
-  \label{fig:barecubicalsetfaces}
-\end{figure*}
+
+  \eqnline{\downcube{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\partialcubset{l}{n}) \\ (E:\mycubsetcomp{l}{n}(D)) \\(d:\mybox{l}{n,p}(D)) \\ (b:\mycube{l}{n,p}(D)(E)(d))}}{:}{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}
+
+  \eqnline{\downcube{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{$b_\epsilon$}
+
+  \eqnline{\downcube{l,\epsilon,q}{n,p,[p<q]}}{D~E~d~(b,c)}{\defeq}{(\downlayer{l,\epsilon,q}{n,p}(D)(d)(b),\downcube{l,\epsilon,q}{n,p+1}(D)(E)(d,b)(c))}
+\end{eqntable}
 

### 2021-07-06 paper/paper.tex
[paper] Clean up two more figures

@@
 % Subbox, sublayer, and subcube
-\newcommand{\downbox}[2]{\ensuremath{\mathsf{subbox}_{#1}^{#2}}}
-\newcommand{\downlayer}[2]{\ensuremath{\mathsf{sublayer}_{#1}^{#2}}}
-\newcommand{\downcube}[2]{\ensuremath{\mathsf{subcube}_{#1}^{#2}}}
-\newcommand{\myfullbox}[2]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
+\newcommand{\downbox}[2][2=]{\ensuremath{\mathsf{subbox}_{#1}^{#2}}}
+\newcommand{\downlayer}[2][2=]{\ensuremath{\mathsf{sublayer}_{#1}^{#2}}}
+\newcommand{\downcube}[2][2=]{\ensuremath{\mathsf{subcube}_{#1}^{#2}}}
+\newcommand{\myfullbox}[2][2=]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
 
 % Coherence conditions
-\newcommand{\cohbox}[2]{\ensuremath{\mathsf{cohbox}_{{#1}}^{{#2}}}}
-\newcommand{\cohcube}[2]{\ensuremath{\mathsf{cohcube}_{#1,#2}}}
-\newcommand{\cohlayer}[2]{\ensuremath{\mathsf{cohlayer}_{#1}^{#2}}}
+\newcommand{\cohbox}[2][2=]{\ensuremath{\mathsf{cohbox}_{{#1}}^{{#2}}}}
+\newcommand{\cohcube}[2][2=]{\ensuremath{\mathsf{cohcube}_{#1,#2}}}
+\newcommand{\cohlayer}[2][2=]{\ensuremath{\mathsf{cohlayer}_{#1}^{#2}}}
+
+% Border
+\newcommand{\border}[1][1=]{\ensuremath{\mathsf{border}_{#1}}}
 
@@
 \NewDocumentEnvironment{eqntable}{m}{\table[h!]
-\tabularx{\textwidth}{@{} l c c X @{}}\toprule}
+\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
 {\endtabularx\hrule\caption{#1}\endtable}
@@
 % A block in the eqntable environment
-\newcommand{\eqnline}[4]{#1 & #2 & #3 & #4 \\}
+\newcommand{\eqnline}[4]{$#1$ & $#2$ & $#3$ & $#4$ \\}
 \newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}
@@
 \newcommand{\properheterocube}[2]{\mathsf{{\heteroname}filler}_{#1}^{#2}}
-\newcommand{\border}[1]{\mathsf{border}_{#1}}
 \newcommand{\bordertype}[1]{\mathsf{Boxofcube}_{#1}}
@@
 Note that such relational structure, cubes and boxes are relative to a universe.
-Note the presence of a coherence condition $\cohbox{l}{}$ to ensuring that both sides of the equality in $\downlayer{l}{}$ and $\downcube{l}{}$ are in the same type.
-The proof of $\cohbox{l}{}$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
+Note the presence of a coherence condition \cohbox{l} to ensuring that both sides of the equality in \downlayer{l} and \downcube{l} are in the same type.
+The proof of \cohbox{l} itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
 Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\downbox{l}{}$ nor $\cohbox{l}{}$ anymore.
+Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning \downbox{l} nor \cohbox{l} anymore.
 
@@
 
-  \eqnline{\mylayer{l}{n,p}}{D~d}{\defeq}{\makecell{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\ \times\; \mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))}}
+  \eqnline{\mylayer{l}{n,p}}{D~d}{\defeq}{\makecell{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\ \times\;\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))}}
 
@@
 
-  \eqnline{\mycube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{E.\ensuremath{\mathsf{rel}}(d)}
+  \eqnline{\mycube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{E.\mathsf{rel}(d)}
 
@@
 
-  \eqnline{\downlayer{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))($c_L$)), \\ \;\overright{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))($c_R$)))}}
+  \eqnline{\downlayer{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L)), \\ \;\overright{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R)))}}
 
@@
 
-  \eqnline{\downcube{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{$b_\epsilon$}
+  \eqnline{\downcube{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{b_\epsilon}
 
@@
 to partial cubes over the empty box.
-Figure~\ref{fig:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see $\border{}$).
+Figure~\ref{fig:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see \border).
 
@@
 
-\begin{figure*}
-  \centerline{ \framebox{$
-        \begin{array}{llcl}
-          \multicolumn{4}{c}{\mbox{Full (non-truncated) cubical sets with degeneracies}}                                         \\
+\begin{eqntable}{Definition of a bare cubical set (coinductive structure)}
+  \mc{Full (non-truncated) cubical sets with degeneracies}
+  \eqnline{\mycubset{l}}{}{:}{\sort{l+1}}
+  \eqnline{\mycubset{l}}{}{\defeq}{\mycubsetfrom{l}{0}(\star)}
   \\
-          \mycubset{l}        &                          & :      & \sort{l+1}                                                   \\
-          \mycubset{l}        &                          & \defeq & \mycubsetfrom{l}{0}(\star)                                   \\
-          \\
-          \mycubsetfrom{l}{n} & (D:\partialcubset{l}{n}) & :      & \sort{l+1}                                                   \\
-          \mycubsetfrom{l}{n} & D                        & \defeq & \Sigma R:\mycubsetcomp{l}{n}(D).\,\mycubsetfrom{l}{n+1}(D,R)
-        \end{array}
-      $
-    }}
-  \caption{Definition of a bare cubical set (coinductive structure)}
-  \label{fig:barecubicalset}
-\end{figure*}
+  \eqnline{\mycubsetfrom{l}{n}}{(D:\partialcubset{l}{n})}{:}{\sort{l+1}}
+  \eqnline{\mycubsetfrom{l}{n}}{D}{\defeq}{\Sigma R:\mycubsetcomp{l}{n}(D).\,\mycubsetfrom{l}{n+1}(D,R)}
+\end{eqntable}
 
-\begin{figure*}
-  \centerline{ \framebox{$
-        \begin{array}{llcl}
-          \multicolumn{4}{c}{\mbox{\textit{Type of full $n$-cubes}}}                                                                                                                         \\
-          \\
-          \myfullcube{l}^{n}     & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n+1})\end{array}                                                             & :      & \sort{l}                                          \\
-          \myfullcube{l}^{n}     & (D,E)                                                                                        & \defeq & \Sigma d:\myfullbox{l}{n}(D).\, E.\mathsf{rel}(d) \\
-          \\
-          \multicolumn{4}{c}{\mbox{\textit{Type of $n$-tubes}}}                                                                                                                              \\
-          \\
-          \tube{l}^{n}           & (D:\partialcubset{l}{n+1})                                                                   & :      & \sort{l}                                          \\
-          \tube{l}^{n}           & D                                                                                            & \defeq & \mybox{l}{n+1,n}(D)                               \\
-          \\
-          \multicolumn{4}{c}{\mbox{\textit{Type of grounded $n$-cubes}}}                                                                                                                     \\
-          \\
-          \mygroundedcube{l}^{n} & (D:\partialcubset{l}{n+1})                                                                   & :      & \sort{l}                                          \\
-          \mygroundedcube{l}^{n} & (D,E)                                                                                        & \defeq & \mycube{l}{n,0}(D)(E)(\star)                      \\
-          \\
-          \multicolumn{4}{c}{\mbox{\textit{Type of fillers of some $n$-box}}}                                                                                                                \\
-          \\
-          \propercube{l}^{n}     & (D:\partialcubset{l}{n+1})~(d:\myfullbox{l}{n}(\hd(D)))                                      & :      & \sort{l}                                          \\
-          \propercube{l}^{n}     & (D,E)~d                                                                                      & \defeq & E.\mathsf{rel}(d)                                 \\
-          \\
-          \multicolumn{4}{c}{\mbox{\textit{Border of a grounded $n$-cube}}}                                                                                                                  \\
-          \\
-          \border{l}^{n}         & (D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D))                                     & :      & \myfullbox{l}{n}(\hd(D))                          \\
-          \border{l}^{n}         & D~c                                                                                          & \defeq & \border{l}^{n,0}(D)(\star)(c)                     \\
-          \\
-          \multicolumn{4}{c}{\mbox{\textit{where the border of partial cubes is defined by}}}                                                                                                \\
-          \\
-          \border{l}^{n,p}       & (D:\partialcubset{l}{n+1})~(d:\mybox{l}{n,p}(\hd(D)))~(c:\mycube{l}{n,p}(\hd(D))(\tl(D))(d)) & :      & \myfullbox{l}{n}(\hd(D))                          \\
-          \border{l}^{n,p,[p=n]} & D~d~c                                                                                        & \defeq & d                                                 \\
-          \border{l}^{n,p,[p<n]} & D~d~(b,c)                                                                                    & \defeq & \border{l}^{n,p+1}(D)(d,b)(c)                     \\
-        \end{array}
-      $
-    }}
-  \caption{Standard derived notions}
-  \label{fig:macros}
-\end{figure*}
+\begin{eqntable}{Standard derived notions}
+  \mc{Type of full $n$-cubes}
+
+  \eqnline{\myfullcube{l}^{n}}{(D:\partialcubset{l}{n+1})}{:}{\sort{l}}
+
+  \eqnline{\myfullcube{l}^{n}}{(D,E)}{\defeq}{\Sigma d:\myfullbox{l}{n}(D).\, E.\mathsf{rel}(d)}
+
+  \\ \mc{Type of $n$-tubes}
+
+  \eqnline{\tube{l}^{n}}{(D:\partialcubset{l}{n+1})}{:}{\sort{l}}
+  \eqnline{\tube{l}^{n}}{D}{\defeq}{\mybox{l}{n+1,n}(D)}
+
+  \\ \mc{Type of grounded $n$-cubes}
+
+  \eqnline{\mygroundedcube{l}^{n}}{(D:\partialcubset{l}{n+1})}{:}{\sort{l}}
+  \eqnline{\mygroundedcube{l}^{n}}{(D,E)}{\defeq}{\mycube{l}{n,0}(D)(E)(\star)}
+
+  \\ \mc{Type of fillers of some $n$-box}
+
+  \eqnline{\propercube{l}^{n}}{(D:\partialcubset{l}{n+1})~(d:\myfullbox{l}{n}(\hd(D)))}{:}{\sort{l}}
+
+  \eqnline{\propercube{l}^{n}}{(D,E)~d}{\defeq}{E.\mathsf{rel}(d)}
+
+  \\ \mc{Border of a grounded $n$-cube}
+
+  \eqnline{\border{l}^{n}}{(D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D))}{:}{\myfullbox{l}{n}(\hd(D))}
+
+  \eqnline{\border{l}^{n}}{D~c}{\defeq}{\border{l}^{n,0}(D)(\star)(c)}
+
+  \\ \mc{where the border of partial cubes is defined by}
+
+  \eqnline{\border{l}^{n,p}}{(D:\partialcubset{l}{n+1})~(d:\mybox{l}{n,p}(\hd(D)))~(c:\mycube{l}{n,p}(\hd(D))(\tl(D))(d))}{:}{\myfullbox{l}{n}(\hd(D))}
+
+  \eqnline{\border{l}^{n,p,[p=n]}}{D~d~c}{\defeq}{d}
+
+  \eqnline{\border{l}^{n,p,[p<n]}}{D~d~(b,c)}{\defeq}{\border{l}^{n,p+1}(D)(d,b)(c)}
+\end{eqntable}
 

### 2021-07-09 paper/paper.tex
[paper] One figure left to clean up
[Cubical] Blow away first branch of cohbox with exfalso
The other branch looks manageable now. Lots of args specified
explicitly, to get rid of the annoying funs appearing everywhere.

@@
 
-\begin{figure*}
-  \centerline{ \framebox{$
-        \begin{array}{llcl}
-          \cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}   & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\end{array}  & :      & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))\end{array}                                                                              \\
-          \cohbox{l,\epsilon,\epsilon',q,r}{n,0}                               & D~\unitpoint                     & \defeq & \reflett(\unitpoint)                                                                                         \\
-          \cohbox{l,\epsilon,\epsilon',q,r}{n,p'+1}                            & D~(d,b)                          & \defeq & (\cohbox{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d)(b))           \\
+\begin{eqntable}{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}
+
+  \eqnline{\cohbox{l,\epsilon,\epsilon',q,r}{\multicell{n,p \\ [p \leq r \leq q \leq n - 2]}}}{\multicell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\multicell{\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}}
+
+  \eqnline{\cohbox{l,\epsilon,\epsilon',q,r}{n,0}}{D~\unitpoint}{\defeq}{\reflett}{(\unitpoint)}
+
+  \eqnline{\cohbox{l,\epsilon,\epsilon',q,r}{n,p'+1}}{D~(d,b)}{\defeq}{(\cohbox{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d)(b))}
+
   \\
+
   \cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p < r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\\(b:\mylayer{l}{n,p}(D)(d))\end{array}  & :      & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))\end{array}                                                                              \\
@@
   \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]}                        & D~E~d~(b,\_)                     & \defeq & \reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon})) \\
-          \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]}                        & D~E~d~(b,c)                      & \defeq & \!\!\begin{array}{l}(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))\end{array}                                                                               \\
-        \end{array}
-      $}}
-  \caption{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}
-  \label{fig:barecubicalsetcoherences}
-\end{figure*}
+  \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]}                        & D~E~d~(b,c)                      & \defeq & \!\!\begin{array}{l}(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))\end{array}
+\end{eqntable}
 
@@
 
-\begin{figure*}
-  \centerline{ \framebox{$
-        \begin{array}{llcl}
-          \multicolumn{4}{c}{\mbox{$q$-th projection of an $n$-box}}                                                                                                                            \\
-          \\
-          \fulldownbox{l,\epsilon,q}{n,[q < n]}   & (D:\partialcubset{l}{n})~(d:\myfullbox{l}{n}(D))     & :      & \myfullbox{l}{n-1}(\hd(D))                                                  \\
-          \fulldownbox{l,\epsilon,q}{n}           & D~(d,\_)                                             & \defeq & \downbox{l,\epsilon,q}{n,n-1}(D)(d)                                         \\
-          \\
-          \multicolumn{4}{c}{\mbox{$q$-th face of an $n$-cube}}                                                                                                                                 \\
-          \\
-          \fulldowncube{l,\epsilon,q}{n,[q < n]}  & (D:\partialcubset{l}{n+1})~(c:\myfullcube{l}^{n}(D)) & :      & \myfullcube{l}^{n-1}(\hd(D))                                                \\
-          \fulldowncube{l,\epsilon,q}{n}          & (D,E)~c                                              & \defeq & \downcube{l,\epsilon,q}{n,0}(D)(E)(\star)(c)                                \\
-          \\
-          \multicolumn{4}{c}{\mbox{\textit{where the extension of $\downbox{l}{}$ to $p>q$ is}}}                                                                                                \\
-          \\
-          \downbox{l,\epsilon,q}{n,p,[q < p < n]} & (D:\partialcubset{l}{n})~(d:\mybox{l}{n,p}(D))       & :      & \myfullbox{l}{n-1}(\hd(D))                                                  \\
-          \downbox{l,\epsilon,q}{n,q+1}           & D~(d,b)                                              & \defeq & \border{l}^{n-1,q}(\hd(D))(\downbox{l,\epsilon,q}{n,q}(D)(d))(b_{\epsilon}) \\
-          \downbox{l,\epsilon,q}{n,p,[q < p-1]}   & D~(d,b)                                              & \defeq & \downbox{l,\epsilon,q}{n,p-1}(D)(d)
-        \end{array}
-      $
-    }}
-  \caption{Standard derived notions (continued)}
-  \label{fig:macroscont}
-\end{figure*}
+\begin{eqntable}{Standard derived notions (continued)}
+  \mc{$q$-th projection of an $n$-box}
 
-\printbibliography
+  \eqnline{\fulldownbox{l,\epsilon,q}{n,[q < n]}}{(D:\partialcubset{l}{n})~(d:\myfullbox{l}{n}(D))}{:}{\myfullbox{l}{n-1}(\hd(D))}
+
+  \eqnline{\fulldownbox{l,\epsilon,q}{n}}{D~(d,\_)}{\defeq}{\downbox{l,\epsilon,q}{n,n-1}(D)(d)}
+
+  \\ \mc{$q$-th face of an $n$-cube}
+
+  \eqnline{\fulldowncube{l,\epsilon,q}{n,[q < n]}}{(D:\partialcubset{l}{n+1})~(c:\myfullcube{l}^{n}(D))}{:}{\myfullcube{l}^{n-1}(\hd(D))}
+
+  \eqnline{\fulldowncube{l,\epsilon,q}{n}}{(D,E)~c}{\defeq}{\downcube{l,\epsilon,q}{n,0}(D)(E)(\star)(c)}
+
+  \\ \mc{where the extension of \downbox{l} to $p>q$ is}
+
+  \eqnline{\downbox{l,\epsilon,q}{n,p,[q < p < n]}}{(D:\partialcubset{l}{n})~(d:\mybox{l}{n,p}(D))}{:}{\myfullbox{l}{n-1}(\hd(D))}
+
+  \eqnline{\downbox{l,\epsilon,q}{n,q+1}}{D~(d,b)}{\defeq}{\border{l}^{n-1,q}(\hd(D))(\downbox{l,\epsilon,q}{n,q}(D)(d))(b_{\epsilon})}
+
+  \eqnline{\downbox{l,\epsilon,q}{n,p,[q < p-1]}}{D~(d,b)}{\defeq}{\downbox{l,\epsilon,q}{n,p-1}(D)(d)}
+\end{eqntable}
 

### 2021-07-09 paper/paper.tex
[paper] Clean up final figure; fix all references

@@
 \usepackage[margin=0.5in]{geometry}
-
-\usepackage[backend=biber, style=apa, natbib=true, sorting=nyt, url=false,isbn=false, doi=false]{biblatex}
-
-% Add biblio-en.bib to the database
-\addbibresource{biblio-en.bib}
 
@@
 
-% Definitional equality
+% Definitional and extensional equality
 \newcommand{\defeq}{\ensuremath{\triangleq}}
+\newcommand{\eqett}{\equiv_{\mathit{ETT}}}
 
@@
 % Subbox, sublayer, and subcube
-\newcommand{\downbox}[2][2=]{\ensuremath{\mathsf{subbox}_{#1}^{#2}}}
-\newcommand{\downlayer}[2][2=]{\ensuremath{\mathsf{sublayer}_{#1}^{#2}}}
-\newcommand{\downcube}[2][2=]{\ensuremath{\mathsf{subcube}_{#1}^{#2}}}
-\newcommand{\myfullbox}[2][2=]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
+\newcommand{\downbox}[2]{\ensuremath{\mathsf{subbox}_{#1}^{#2}}}
+\newcommand{\downlayer}[2]{\ensuremath{\mathsf{sublayer}_{#1}^{#2}}}
+\newcommand{\downcube}[2]{\ensuremath{\mathsf{subcube}_{#1}^{#2}}}
+\newcommand{\myfullbox}[2]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
 
 % Coherence conditions
-\newcommand{\cohbox}[2][2=]{\ensuremath{\mathsf{cohbox}_{{#1}}^{{#2}}}}
-\newcommand{\cohcube}[2][2=]{\ensuremath{\mathsf{cohcube}_{#1,#2}}}
-\newcommand{\cohlayer}[2][2=]{\ensuremath{\mathsf{cohlayer}_{#1}^{#2}}}
+\newcommand{\cohbox}[2]{\ensuremath{\mathsf{cohbox}_{#1}^{#2}}}
+\newcommand{\cohlayer}[2]{\ensuremath{\mathsf{cohlayer}_{#1}^{#2}}}
+\newcommand{\cohcube}[2]{\ensuremath{\mathsf{cohcube}_{#1}^{#2}}}
 
 % Border
-\newcommand{\border}[1][1=]{\ensuremath{\mathsf{border}_{#1}}}
+\newcommand{\border}[1]{\ensuremath{\mathsf{border}_{#1}}}
 
+% Partials and fulls
 \newcommand{\partialcubset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
 \newcommand{\mycubsetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}
+\newcommand{\fulldownbox}[2]{\mathsf{subfullbox}_{#1}^{#2}}
+\newcommand{\fulldowncube}[2]{\mathsf{subfullcube}_{#1}^{#2}}
 
@@
 % The eqntable environment, displaying the various
-\NewDocumentEnvironment{eqntable}{m}{\table[h!]
+\NewDocumentEnvironment{eqntable}{m}{\table[!ht]
 \tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
@@
 
-\newcommand{\fulldownbox}[2]{\mathsf{subfullbox}_{#1}^{#2}}
-\newcommand{\fulldowncube}[2]{\mathsf{subfullcube}_{#1}^{#2}}
-
 \newcommand{\myheterobox}[2]{\mathsf{{\heteroname}box}_{#1}^{#2}}
@@
 \newcommand{\unitpoint}{\star}
-\newcommand{\eqett}{\equiv_{\mathit{ETT}}}
 \newcommand{\reflett}{\mathsf{refl}_{\mathit{ETT}}}
@@
 In this section, we give the core of the definition of semi-cubical
-sets as the coinductive limit (see Figure~\ref{fig:barecubicalset}) of a
+sets as the coinductive limit (see Figure~\ref{tab:barecubicalset}) of a
 construction of truncated semi-cubical sets.
@@
 
-The definition is dispatched over Figures~\ref{fig:barecubicalsetstructurecore}, \ref{fig:barecubicalsetstructure}, \ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences}.
+The definition is dispatched over Figures~\ref{tab:barecubicalsetstructurecore}, \ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}.
 It describes the structure of the underlying higher-dimensional relations on which cubes and boxes are built, together with the definition of homogeneous $n$-boxes, homogeneous $n$-cubes, together with face operations on boxes and cubes, together with commutation properties of the face operations.
@@
 
-\begin{eqntable}{Definition of a truncated cubical set (main part of the higher-dimensional relation structure)}
+\begin{eqntable}{\label{tab:barecubicalsetstructurecore} Definition of a truncated cubical set (main part of the higher-dimensional relation structure)}
   \mc{Type of truncated cubical sets} \\
@@
   \eqnline{\partialcubset{l}{n'+1}}{}{\defeq}{\ensuremath{\Sigma}D:\partialcubset{l}{n'}.\,\mycubsetcomp{l}{n'}(D)}
+
   \\
+
   \mc{Structure carried at each dimension}
@@
 
-\begin{eqntable}{Definition of a truncated cubical set (boxes)}
+\begin{eqntable}{\label{tab:barecubicalsetstructure} Definition of a truncated cubical set (boxes)}
   \mc{Full homogeneous $n$-boxes}
@@
   \eqnline{\myfullbox{l}{n}}{D}{\defeq}{\mybox{l}{n,n}(D)}
+
   \\
+
   \mc{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}
@@
   \eqnline{\mybox{l}{n,p'+1}}{D}{\defeq}{\Sigma d:\mybox{l}{n,p'}(D).\,\mylayer{l}{n,p'}(D)(d)}
+
   \\
+
   \eqnline{\mylayer{l}{n,p,[p < n]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}
@@
 
-\begin{eqntable}{Definition of a homogeneous bare cubical set ($q$-th projection)}
+\begin{eqntable}{\label{tab:barecubicalsetfaces} Definition of a homogeneous bare cubical set ($q$-th projection)}
+
   \eqnline{\downbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\mybox{l}{n-1,p}(\hd(D))}
@@
 
-\begin{eqntable}{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}
+\begin{eqntable}{\label{tab:barecubicalsetcoherences} Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}
 
-  \eqnline{\cohbox{l,\epsilon,\epsilon',q,r}{\multicell{n,p \\ [p \leq r \leq q \leq n - 2]}}}{\multicell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\multicell{\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}}
+  \eqnline{\cohbox{l,\epsilon,\epsilon',q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\makecell{\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}}
 
@@
 
-  \cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p < r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\\(b:\mylayer{l}{n,p}(D)(d))\end{array}  & :      & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))\end{array}                                                                              \\
-  \cohlayer{l,\epsilon,\epsilon',q,r}{n,p}                             & D~d~c                            & \defeq & \!\!\begin{array}{l}(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L),\\\;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))\end{array}                                                                               \\
+  \eqnline{\cohlayer{l,\epsilon,\epsilon',q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D)) \\(b:\mylayer{l}{n,p}(D)(d))}}{:}{\makecell{\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))}}
+
+  \eqnline{\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}}{D~d~c}{\defeq}{\makecell{(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L), \\ \;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))}}
+
   \\
-  \cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}{n,p}(D))\\(b:\mycube{l}{n,p}(D)(E)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))\end{array}                                                                             \\
-  \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]}                        & D~E~d~(b,\_)                     & \defeq & \reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon})) \\
-  \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]}                        & D~E~d~(b,c)                      & \defeq & \!\!\begin{array}{l}(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))\end{array}
+
+  \eqnline{\cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D)) \\ (b:\mycube{l}{n,p}(D)(E)(d))}}{:}{\makecell{\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))}}
+
+  \eqnline{\cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon}))}
+
+  \eqnline{\cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]}}{D~E~d~(b,c)}{\defeq}{(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))}
 \end{eqntable}
@@
 
-On top of the basic definitions on Figures~\ref{fig:barecubicalsetstructure}, \ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences}, we can define on Figures~\ref{fig:macros} and~\ref{fig:macroscont} a few other concepts at a more standard level of abstraction.
+On top of the basic definitions on Figures~\ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}, we can define on Figures~\ref{tab:macros} and~\ref{tab:macroscont} a few other concepts at a more standard level of abstraction.
 In particular, a homogeneous $n$-box in the above sense is defined to be an object of type $\myfullbox{l}{n}(D_{n})$ for $D_{n} \defeq (A,=_A,...,=^n_A)$ the initial segment of $n$-th first iterated equalities over $A$ (by convention, a homogeneous $0$-box shall be the canonical singleton type).
@@
 to partial cubes over the empty box.
-Figure~\ref{fig:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see \border).
+Figure~\ref{tab:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see \border).
 
-Figure~\ref{fig:macros} also shows how to compute the faces of a box or of a cube.
+Figure~\ref{tab:macros} also shows how to compute the faces of a box or of a cube.
 
-\begin{eqntable}{Definition of a bare cubical set (coinductive structure)}
+\begin{eqntable}{\label{tab:barecubicalset} Definition of a bare cubical set (coinductive structure)}
   \mc{Full (non-truncated) cubical sets with degeneracies}
@@
 
-\begin{eqntable}{Standard derived notions}
+\begin{eqntable}{\label{tab:macros} Standard derived notions}
   \mc{Type of full $n$-cubes}
-
   \eqnline{\myfullcube{l}^{n}}{(D:\partialcubset{l}{n+1})}{:}{\sort{l}}
@@
 
-\begin{eqntable}{Standard derived notions (continued)}
+\begin{eqntable}{\label{tab:macroscont} Standard derived notions (continued)}
   \mc{$q$-th projection of an $n$-box}
@@
 
+\begin{thebibliography}{10}
+  \bibitem{Herbelin15}
+  Herbelin, H. (2015). A dependently-typed construction of semi-simplicial types. \textit{Mathematical Structures in Computer Science, 25}(5), 1116-1131.
+\end{thebibliography}
+
 \end{document}

### 2021-07-09 paper/paper.tex
[paper] Switch to amsart; clean up junk macros

@@
-\documentclass{article}
+\documentclass[10pt]{amsart}
 
 \usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
-\usepackage{bookmark, titling, fontspec, xargs, multirow, polyglossia, luacode, fancyhdr, lastpage, amssymb}
-\usepackage{listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace, makecell}
-\usepackage[compact]{titlesec}
-\usepackage[margin=0.5in]{geometry}
+\usepackage{bookmark, titling, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace, makecell}
+\usepackage[margin=0.3in]{geometry}
 
 \newcommand{\highlight}[1]{\emph{#1}}
-
-\include{macros}
 
@@
 \newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
+\newcommand{\unitpoint}{\ensuremath{\star}}
 
@@
 \newcommand{\defeq}{\ensuremath{\triangleq}}
-\newcommand{\eqett}{\equiv_{\mathit{ETT}}}
+\newcommand{\eqett}{\ensuremath{\equiv_{\mathit{ETT}}}}
+\newcommand{\reflett}{\ensuremath{\mathsf{refl}_{\mathit{ETT}}}}
 
 % Box, layer, and cube
+\newcommand{\mycubset}[1]{\ensuremath{\mathsf{cubset}_{#1}}}
 \newcommand{\mybox}[2]{\ensuremath{\mathsf{box}_{#1}^{#2}}}
@@
 
-% Border
+% Partials and fulls, related to box, cube, and tube
 \newcommand{\border}[1]{\ensuremath{\mathsf{border}_{#1}}}
-
-% Partials and fulls
 \newcommand{\partialcubset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
 \newcommand{\mycubsetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}
-\newcommand{\fulldownbox}[2]{\mathsf{subfullbox}_{#1}^{#2}}
-\newcommand{\fulldowncube}[2]{\mathsf{subfullcube}_{#1}^{#2}}
+\newcommand{\fulldownbox}[2]{\ensuremath{\mathsf{subfullbox}_{#1}^{#2}}}
+\newcommand{\fulldowncube}[2]{\ensuremath{\mathsf{subfullcube}_{#1}^{#2}}}
+\newcommand{\propercube}[1]{\ensuremath{\mathsf{properfiller}_{#1}}}
+\newcommand{\mygroundedcube}[1]{\ensuremath{\mathsf{groundedcube}_{#1}}}
+\newcommand{\tube}[1]{\ensuremath{\mathsf{tube}_{#1}}}
+\newcommand{\mycubsetfrom}[2]{\ensuremath{\mathsf{cubset}_{#1}^{\geq#2}}}
+\newcommand{\myfullcube}[1]{\ensuremath{\mathsf{fullcube}_{#1}}}
 
@@
 
-% Junk follows
-
-\newcommand{\revimp}{\ensuremath{\leftarrow}}
-
-\newcommand{\Type}{\ensuremath{\mathsf{Type}}}
-\newcommand{\Set}{\ensuremath{\mathsf{Set}}}
-\newcommand{\Prop}{\ensuremath{\mathsf{Prop}}}
-\newcommand{\refl}[1]{\ensuremath{\mathsf{refl}\,{#1}}}
-\newcommand{\mkmlidtype}[3]{{#1} =^{\mathrm{id}}_{#2} {#3}}
-\newcommand{\mkmleqdep}[3]{{#1} =^{\mathrm{dep}}_{#2} {#3}}
-\newcommand{\hrefl}[1]{\ensuremath{\mathsf{refl^{\mathrm{dep}}}\,{#1}}}
-\newcommand{\mluniv}{\ensuremath{\mathsf{U}}}
-\newcommand{\Jdep}[2]{\ensuremath{\mathsf{J}\;{#1}\;{#2}}}
-
-\newcommand{\nth}[1]{{#1}^{\mbox{\scriptsize th}}}
-\newcommand{\binomial}[2]{\left(\begin{array}{c}#1\\#2\end{array}\right)}
-
-\newcommand{\wfctx}[1]{{#1}~\mathsf{ok}}
-
-\newcommand{\mkover}[1]{\widetilde{#1}}
-\newcommand{\mkoverdim}[2]{\widetilde{#2}^{#1}}
-\newcommand{\mkprod}[3]{\Pi {#2}.\,{#3}}
-\newcommand{\mkprodovereq}[3]{\mkover{\Pi} {#1}\!:\!{#2}.\,{#3}}
-\newcommand{\mkprodovereqopp}[3]{\opp{\mkover{\Pi}} {#1}\!:\!{#2}.\,{#3}}
-\newcommand{\mkboundedprod}[4]{\Pi {#3}\!:\!{#1}\leq{#2}.\,{#4}}
-\newcommand{\mklam}[3]{\lambda^{#2}.\,{#3}}
-\newcommand{\mkboundedlam}[4]{\lambda {#3}\!:\!{#1}\leq{#2}.\,{#4}}
-\newcommand{\mkapp}[2]{{#1}\,{#2}}
-\newcommand{\prodsort}[2]{\Pi ({#1},{#2})}
-
-% selecting kind of treatment of sorts
-\newcommand{\typeorsort}[2]{{#2}}
-
-\newcommand{\mksigma}[3]{\Sigma {#2}.\,{#3}}
-\newcommand{\mksigmaovereq}[3]{\mkover{\Sigma} {#1}\!:\!{#2}.\,{#3}}
-\newcommand{\mksigmaovereqopp}[3]{\opp{\mkover{\Sigma}} {#1}\!:\!{#2}.\,{#3}}
-\newcommand{\mkpair}[2]{\langle{#1},{#2}\rangle}
-\newcommand{\mkfst}[1]{{#1}.1}
-\newcommand{\mksnd}[1]{{#1}.2}
-\newcommand{\sigsort}[2]{\Sigma ({#1},{#2})}
-
-\newcommand{\sortsort}[1]{{\mathcal S}_{#1}}
-
-\newcommand{\Sone}{\mathbb{S}^1}
-\newcommand{\casesone}[5]
-  {\mathsf{case}\;{#1}\;\mathsf{of}\;{#2}\;\Rightarrow\;{#3}\;|\;{#4}\;\Rightarrow\;{#5}\;\mathsf{end}}
-\newcommand{\base}{\mathsf{base}}
-\newcommand{\loopsone}{\mathsf{loop}}
-\newcommand{\Sonesort}{l_{\mathbb{S}^1}}
-
-\newcommand{\emptyctx}{\boxbox}
-
-\newcommand{\univ}{\boxempty}
-\newcommand{\typeannot}{\mathsf{type}}
-\newcommand{\istype}{~\typeannot}
-
-\newcommand{\mkeq}[3]{{#1} =_{#2} {#3}}
-\newcommand{\mkhomeq}[3]{{#1} =_{#2} {#3}}
-\newcommand{\mkeqovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}}
-\newcommand{\mkeqovereqdim}[4]{{#2} \,\mkoverdim{#1}{=}_{#3}\, {#4}}
-\newcommand{\mkeqtype}[3]{{#1} =_{\typeannot} {#3}}
-\newcommand{\mkeqtypeovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}} % case where we can write either s or refl{s}
-\newcommand{\mkeqarray}[3]{\begin{array}{c}{#1}\\ =_{#2}\\ {#3}\end{array}}
-\newcommand{\mkfaces}[3]{\mkeq{#1}{#2}{#3}}
-\newcommand{\mkfacesarray}[3]{\mkeqarray{#1}{#2}{#3}}
-\newcommand{\mkfacesover}[3]{\mkeqovereq{#1}{#2}{#3}}
-\newcommand{\lameq}[2]{\lambda {#1}.{#2}}
-\newcommand{\reflterm}[1]{\widehat{#1}}
-\newcommand{\overreflterm}[1]{{\mkover{\reflterm{#1}}}}
-\newcommand{\refltermdim}[2]{{\widehat{#2}}^{#1}}
-\newcommand{\refltype}[1]{\reflterm{#1}}
-\newcommand{\purerewlr}[1]{\overrightarrow{#1}}
-\newcommand{\purerewrl}[1]{\overleftarrow{#1}}
-\newcommand{\rewlr}[2]{\overrightarrow{#1}(#2)}
-\newcommand{\rewrl}[2]{\overleftarrow{#1}(#2)}
-\newcommand{\deprewlr}[1]{\raisebox{0em}{$\ulcorner$}\!#1}
-\newcommand{\deprewrl}[1]{{#1}\raisebox{-0.2em}{$\!\lrcorner$}}
-\newcommand{\rewlrspec}[2]{{#1}^{\rightarrow}(#2)}
-\newcommand{\rewrlspec}[2]{{#1}^{\leftarrow}(#2)}
-\newcommand{\rewlrrevspec}[2]{{#1}_-^{\rightarrow}(#2)}
-\newcommand{\rewrlrevspec}[2]{{#1}_-^{\leftarrow}(#2)}
-\newcommand{\rewlrrevspecin}[2]{{#1}_+^{\rightarrow}(#2)}
-\newcommand{\rewrlrevspecin}[2]{{#1}_+^{\leftarrow}(#2)}
-\newcommand{\doublerewlr}[2]{\Overrightarrow{1.4ex}{#1}({#2})}
-\newcommand{\doublerewrl}[2]{\Overleftarrow{1.4ex}{#1}({#2})}
-\newcommand{\mktuple}[6]{\{#3; #4; #5; #6\}_{#1,#2}}
-\newcommand{\mktupleshort}[6]{\{#3; #4; #5; #6\}}
-\newcommand{\opp}[1]{{#1}^{-1}}
-\newcommand{\oppi}[2]{\appi{#1}{(\opp{#2}/{#2})}}
-
-\newcommand{\weakensquarelr}[2]{{#1}_L(#2)}
-\newcommand{\weakensquarerl}[2]{{#1}_R(#2)}
-
-\newcommand{\rewlrmkeq}[4]{\mkeq{\rewlr{#1}{#2}}{#3}{#4}}
-
-\newcommand{\appi}[2]{{#1}\;\!{#2}}
-\newcommand{\appidep}[2]{{#1}_{#2}}
-\newcommand{\bp}[1]{{#1}{\scriptstyle 0}}
-\newcommand{\ep}[1]{{#1}{\scriptstyle 1}}
-\newcommand{\bpoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{0}}}
-\newcommand{\epoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{1}}}
-\newcommand{\bpdep}[1]{{#1}_0}
-\newcommand{\epdep}[1]{{#1}_1}
-
-\newcommand{\bpsubstexpl}[2]{{#2}_{\{0/{#1}\}}}
-\newcommand{\epsubstexpl}[2]{{#2}_{\{1/{#1}\}}}
-\newcommand{\eqsubstexpl}[2]{{#2}_{\{\star/{#1}\}}}
-\newcommand{\bpsubstexplcons}[2]{{#2}\}\{0/{#1}}
-\newcommand{\epsubstexplcons}[2]{{#2}\}\{1/{#1}}
-\newcommand{\eqsubstexplcons}[2]{{#2}\}\{\star/{#1}}
-\newcommand{\bpsubst}[2]{{#2}{[0/{#1}]}}
-\newcommand{\epsubst}[2]{{#2}{[1/{#1}]}}
-\newcommand{\bpsubstctx}[3]{{#3}{[0/{#2}]}^{#1}}
-\newcommand{\epsubstctx}[3]{{#3}{[1/{#2}]}^{#1}}
-\newcommand{\takebpface}[2]{\partial^{#1}_0{#2}}
-\newcommand{\takeepface}[2]{\partial^{#1}_1{#2}}
-
-\newcommand{\dimvalid}[2]{{#1} \in {#2}}
-\newcommand{\dimdeclare}[1]{{#1}}
-\newcommand{\dimlength}[1]{|#1|_{\mathit{dim}}}
-\newcommand{\dimindex}[2]{\#_{#1}{#2}}
-
-\newcommand{\substminus}[2]{{#1}-{#2}}
-\newcommand{\substminusbernardymoulin}[2]{{#1}/{#2}}
-
-\newcommand{\N}{\mathbb{N}}
-\newcommand{\expand}[2]{\mathsf{expand}(#1,#2)}
-
-\newcommand{\metaequiv}{\cong}
-\newcommand{\metaletin}[3]{\mathit{let}\;{#1}\;\defeq\;{#2}\;\mathit{in}\;{#3}}
-\newcommand{\map}[2]{\mathsf{ap}\,{#1}\,{#2}}
-\newcommand{\depmap}[2]{\mathsf{apd}\,{#1}\,{#2}}
-\newcommand{\transport}[3]{\mathsf{transport}\,{#1}\,{#2}\,{#3}}
-\newcommand{\deptransport}[3]{\mathsf{transportd}\,{#1}\,{#2}\,{#3}}
-\newcommand{\swap}[1]{{#1}^{\circ}}
-\newcommand{\swapbracket}[1]{({#1})^{\circ}}
-\newcommand{\swaptype}[1]{{#1}^{\circ}}
-\newcommand{\swapoverdim}[2]{{#2}^{\mkoverdim{#1}{\circ}}}
-\newcommand{\homsquare}[1]{\mathsf{homsquare}(#1)}
-\newcommand{\permute}[2]{\mathsf{permute}_{#1}(#2)}
-\newcommand{\swapprodeq}[2]{\mathsf{swap}_{\Pi=}^{#1}(#2)}
-\newcommand{\swapeqprod}[2]{\mathsf{swap}_{=\Pi}^{#1}(#2)}
-\newcommand{\swapeqprodlr}[2]{\mathsf{swap}_{=\Pi}^{\rightarrow}({#1})(#2)}
-\newcommand{\swapeqprodrl}[2]{\mathsf{swap}_{=\Pi}^{\leftarrow}({#1})(#2)}
-\newcommand{\swapsigmaeq}[1]{\mathsf{swap}_{\Sigma=}(#1)}
-\newcommand{\swapeqsigma}[1]{\mathsf{swap}_{=\Sigma}(#1)}
-
-\newcommand{\bool}{\mathsf{bool}}
-\newcommand{\booldeux}{\bool^2}
-\newcommand{\boolexp}{\bool^{\bool}}
-
-\newcommand{\reduce}{\;\triangleright\;}
-
-\newcommand{\emptysubst}{\emptyctx}
-
-\newcommand{\sortrule}{\sort{}}
-\newcommand{\axrule}{\mathsf{Ax}}
-\newcommand{\ctxemptyrule}{\mathsf{Ctx}_{\emptyctx}}
-\newcommand{\ctxconsrule}{\mathsf{Ctx}_{\mathsf{cons}}}
-\newcommand{\convrule}{\mathsf{Conv}}
-\newcommand{\convconvrule}{\mathsf{Conv}-\mathsf{Conv}}
-\newcommand{\univrule}{\mathsf{\univ}}
-\newcommand{\convruleredright}{\reduce_R}
-\newcommand{\convruleredleft}{\reduce_L}
-\newcommand{\convrulerefl}{\equiv_{\mathsf{refl}}}
-\newcommand{\convruletrans}{\equiv_{\mathsf{trans}}}
-\newcommand{\convruleredtyperight}{\reduce_R^{\typeannot}}
-\newcommand{\convruleredtypeleft}{\reduce_L^{\typeannot}}
-\newcommand{\convruletyperefl}{\equiv_{\mathsf{refl}}^{\typeannot}}
-\newcommand{\convruletypetrans}{\equiv_{\mathsf{trans}}^{\typeannot}}
-
-\newcommand{\circovereq}{\;\mkover{\circ}\;}
-\newcommand{\circsigma}{\circ_{\Sigma}}
-
-\newcommand{\comprule}{R_{\mathsf{\circ}}}
-\newcommand{\opprule}{R_{\mathsf{\opp}}}
-
-\newcommand{\idleftredrule}{\mathsf{Id_L}}
-\newcommand{\idrightredrule}{\mathsf{Id_R}}
-\newcommand{\idoppredrule}{\mathsf{\opp{Id}}}
-\newcommand{\oppoppredrule}{\mathsf{\opp{(\opp{\_})}}}
-\newcommand{\assoccompredrule}{\mathsf{Assoc}}
-\newcommand{\distriboppcompredrule}{\mathsf{\opp{\circ}}}
-\newcommand{\squaredownredrule}{\circ_{=_{\mkover{=}}}}
-\newcommand{\exchangerule}{\mathsf{Exch}}
-\newcommand{\compeqovereqredrule}{\circ_{\mkover{=}}}
-\newcommand{\squareprodredrule}{\circ_{=_{\mkover{\Pi}}}}
-
-\newcommand{\depmapdef}{\mathsf{ApD}}
-\newcommand{\funextpuredef}{\mathsf{LiftDim}}
-\newcommand{\funextdeppuredef}{\mathsf{LiftDepDim}}
-\newcommand{\funextdepdeppuredef}{\mathsf{LiftDepDim}}
-\newcommand{\funextdef}{\mathsf{FunExt}}
-\newcommand{\funextdepdef}{\mathsf{FunDepExt}}
-\newcommand{\funext}[1]{\mathsf{funext}(#1)}
-\newcommand{\funextdep}[1]{\mathsf{fundepext}(#1)}
-\newcommand{\funextpure}[1]{\mathsf{liftdim}(#1)}
-\newcommand{\funextdeppure}[1]{\mathsf{liftdepdim}(#1)}
-
-\newcommand{\OMEGATT}{\omega\mathsf{TT}}
-
-\newcommand{\emptysigma}{\bullet}
-\newcommand{\itsemterm}[4]{\llbracket #4 \rrbracket^{#2;#3}_{#1}}
-\newcommand{\itsemtype}[4]{\llbracket #4 \rrbracket^{#2;#3}_{#1}}
-\newcommand{\semterm}[3]{\llbracket #3 \rrbracket^{#1;#2}}
-\newcommand{\semtype}[3]{\llbracket #3 \rrbracket^{#1;#2}}
-\newcommand{\incrstep}[3]{\mathsf{split}_{#1}{#3}(#2)}
-\newcommand{\distrstep}[3]{\mathsf{distr}_{#1}{#3}(#2)}
-\newcommand{\applytype}[4]{\mathsf{apptype}_{#1}^{#2}(#3,#4)}
-\newcommand{\shrink}[3]{\mathsf{shrink}_{#1}\,{#2}\,#3}
-\newcommand{\under}[3]{\mathsf{under}_{#1}\,{#2}\,#3}
-\newcommand{\undertau}[3]{\mathsf{under}_{#1}^{#2}\,#3}
-\newcommand{\proj}[3]{\pi_{#1}^{#2}\,#3}
-\newcommand{\elt}[2]{\mathsf{El}_{#1}\,#2}
-\newcommand{\semtypenew}[2]{| #2 |_{#1}}
-\newcommand{\semnew}[2]{\llbracket #2 \rrbracket_{#1}}
-\newcommand{\semctx}[2]{\llbracket #2 \rrbracket_{#1}}
-\newcommand{\semlam}[5]{\mathsf{lam}_{#1}^{#2}\,#4\,(#3)\,#5}
-\newcommand{\semlambis}[5]{\mathsf{lam'}_{#1}^{#2}\,#4\,(#3)\,#5}
-\newcommand{\semapp}[3]{\mathsf{app}_{#1}#2\,#3}
-\newcommand{\semprod}[5]{\mathsf{prod}_{#1}^{#2}\,#4\,(#3)\,#5}
-\newcommand{\access}[2]{\mathsf{get}_{#1}(#2)}
-\newcommand{\accesstyped}[3]{\mathsf{get}_{#1}^{#2}(#3)}
-\newcommand{\lift}[1]{\mathsf{lift}\, {#1}}
-\newcommand{\liftlr}[1]{\mathsf{lift}^\rightarrow\, {#1}}
-\newcommand{\liftrl}[1]{\mathsf{lift}^\leftarrow\, {#1}}
-\newcommand{\diag}[2]{\mathsf{diag}_{#1}(#2)}
-\newcommand{\semsort}[1]{\mathsf{sort}_{#1}}
-\newcommand{\reflsort}[1]{\mathsf{refl}^{\sort{}}_{#1}}
-\newcommand{\mktuplenew}[6]{\{#4\,|\begin{array}{l} #5 \\ #6 \end{array}\}_{#1,#2,#3}}
-\newcommand{\mktuplein}[4]{{#1}; {#2}; {#3}; {#4}}
-\newcommand{\nwconn}[2]{\deprewlr{#2}_{#1}}
-\newcommand{\seconn}[2]{\deprewrl{#2}_{#1}}
-\newcommand{\refltermn}[3]{\mathsf{reflterm}_{#1}(#3)}
-\newcommand{\refltypen}[2]{\mathsf{refltype}_{#1}(#2)}
-
-\newcommand{\restrict}{\mathsf{restrict}}
-\newcommand{\MofL}{\mathsf{underlying}}
-\newcommand{\defequiv}{\mathsf{\simeq}}
-\newcommand{\isequivalence}{\mathsf{isequiv}}
-\newcommand{\gpdlevel}{\mathsf{gpdlevel}}
-\newcommand{\regrefl}{\mathsf{regrefl}}
-
-\newcommand{\heteroname}{het}
-
-\newcommand{\informalcube}{\mathsf{cube}}
-\newcommand{\informalcubeover}{\mathsf{cube}}
-
-\newcommand{\pboxname}{box}
-\newcommand{\pBoxname}{Box}
-
-\newcommand{\myheterobox}[2]{\mathsf{{\heteroname}box}_{#1}^{#2}}
-\newcommand{\myheterolayer}[2]{\mathsf{{\heteroname}layer}_{#1}^{#2}}
-\newcommand{\myheterocube}[2]{\mathsf{{\heteroname}cube}_{#1}^{#2}}
-\newcommand{\myheteroboxtype}[2]{\mathsf{Box}_{#1}^{#2}}
-\newcommand{\myheterolayertype}[2]{\mathsf{Layer}_{#1}^{#2}}
-\newcommand{\myheterocubetype}[2]{\mathsf{Cube}_{#1}^{#2}}
-
-\newcommand{\myfulldepheterobox}[3]{\mathsf{fulldepBox}_{#1}^{#2,#3}}
-\newcommand{\mydepheterobox}[3]{\mathsf{depBox}_{#1}^{#2,#3}}
-\newcommand{\mydepheterolayer}[3]{\mathsf{depLayer}_{#1}^{#2,#3}}
-\newcommand{\mydepheterocube}[3]{\mathsf{depCube}_{#1}^{#2,#3}}
-\newcommand{\liftfulldepheterobox}[3]{\mathsf{liftfullBox}_{#1}^{#2,#3}}
-\newcommand{\liftdepheterobox}[3]{\mathsf{liftBox}_{#1}^{#2,#3}}
-\newcommand{\liftdepheterolayer}[3]{\mathsf{liftLayer}_{#1}^{#2,#3}}
-\newcommand{\liftdepheterocube}[3]{\mathsf{liftCube}_{#1}^{#2,#3}}
-
-\newcommand{\expandheterocube}[2]{\mathsf{expandCube}_{#1}^{#2}}
-\newcommand{\expandheterolayer}[2]{\mathsf{expandLayer}_{#1}^{#2}}
-\newcommand{\expanddownbox}[2]{\mathsf{expandsubbox}_{#1}^{#2}}
-\newcommand{\expanddownlayer}[2]{\mathsf{expandsublayer}_{#1}^{#2}}
-\newcommand{\expanddowncube}[2]{\mathsf{expandsubcube}_{#1}^{#2}}
-
-\newcommand{\depdownbox}[2]{\mathsf{depsubbox}_{#1}^{#2}}
-\newcommand{\depdownlayer}[2]{\mathsf{depsublayer}_{#1}^{#2}}
-\newcommand{\depdowncube}[2]{\mathsf{depsubcube}_{#1}^{#2}}
-\newcommand{\depdownboxbis}[2]{\mathsf{depsubliftbox}_{#1}^{#2}}
-\newcommand{\depdownlayerbis}[2]{\mathsf{depsubliftlayer}_{#1}^{#2}}
-\newcommand{\depdowncubebis}[2]{\mathsf{depsubliftcube}_{#1}^{#2}}
-\newcommand{\depdownboxter}[2]{\mathsf{depsubliftbox'}_{#1}^{#2}}
-\newcommand{\depdownlayerter}[2]{\mathsf{depsubliftlayer'}_{#1}^{#2}}
-\newcommand{\depdowncubeter}[2]{\mathsf{depsubliftcube'}_{#1}^{#2}}
-
-\newcommand{\depcohbox}[2]{\mathsf{depcohbox}_{#1}^{#2}}
-\newcommand{\depcohlayer}[2]{\mathsf{depcohlayer}_{#1}^{#2}}
-\newcommand{\depcohcube}[2]{\mathsf{depcohcube}_{#1}^{#2}}
-\newcommand{\depcohboxbis}[2]{\mathsf{depcohliftbox}_{#1}^{#2}}
-\newcommand{\depcohlayerbis}[2]{\mathsf{depcohliftlayer}_{#1}^{#2}}
-\newcommand{\depcohcubebis}[2]{\mathsf{depcohliftcube}_{#1}^{#2}}
-\newcommand{\depcohboxter}[2]{\mathsf{depcohliftbox'}_{#1}^{#2}}
-\newcommand{\depcohlayerter}[2]{\mathsf{depcohliftlayer'}_{#1}^{#2}}
-\newcommand{\depcohcubeter}[2]{\mathsf{depcohliftcube'}_{#1}^{#2}}
-
-\newcommand{\univfullcube}[2]{\mathsf{UnivfullCube}_{#1}^{#2}}
-\newcommand{\univfullbox}[2]{\mathsf{UnivfullBox}_{#1}^{#2}}
-\newcommand{\univbox}[2]{\mathsf{UnivBox}_{#1}^{#2}}
-\newcommand{\univlayer}[2]{\mathsf{UnivLayer}_{#1}^{#2}}
-\newcommand{\univcube}[2]{\mathsf{UnivCube}_{#1}^{#2}}
-\newcommand{\univfiller}[2]{\mathsf{UnivFiller}_{#1}^{#2}}
-\newcommand{\cubeofuniv}[2]{\mathsf{cubeofuniv}_{#1}^{#2}}
-\newcommand{\extend}[2]{\mathsf{extendcube}_{#1}^{#2}}
-
-\newcommand{\powersetfullcube}[2]{\mathsf{powersetfullCube}_{#1}^{#2}}
-
-\newcommand{\heterodownbox}[2]{\mathsf{sub{\heteroname}box}_{#1}^{#2}}
-\newcommand{\heterodownlayer}[2]{\mathsf{sub{\heteroname}layer}_{#1}^{#2}}
-\newcommand{\heterodowncube}[2]{\mathsf{sub{\heteroname}cube}_{#1}^{#2}}
-\newcommand{\depdownboxtype}[2]{\mathsf{Subdepbox}_{#1}^{#2}}
-\newcommand{\depdownlayertype}[2]{\mathsf{Subdeplayer}_{#1}^{#2}}
-\newcommand{\depdowncubetype}[2]{\mathsf{Subdepcube}_{#1}^{#2}}
-\newcommand{\downboxtype}[2]{\mathsf{Subbox}_{#1}^{#2}}
-\newcommand{\downlayertype}[2]{\mathsf{Sublayer}_{#1}^{#2}}
-\newcommand{\downcubetype}[2]{\mathsf{Subcube}_{#1}^{#2}}
-\newcommand{\cohreflbox}[1]{\mathsf{cohreflbox}_{#1}}
-\newcommand{\cohrefllayer}[1]{\mathsf{cohrefllayer}_{#1}}
-\newcommand{\cohreflcube}[1]{\mathsf{cohreflcube}_{#1}}
-\newcommand{\cohrefleqbox}[1]{\mathsf{cohrefleqbox}_{#1}}
-\newcommand{\cohrefleqlayer}[1]{\mathsf{cohrefleqlayer}_{#1}}
-\newcommand{\cohrefleqcube}[1]{\mathsf{cohrefleqcube}_{#1}}
-\newcommand{\cohboxtype}[2]{\mathsf{Cohbox}_{#1}^{#2}}
-\newcommand{\cohlayertype}[2]{\mathsf{Cohlayer}_{#1}^{#2}}
-\newcommand{\cohcubetype}[2]{\mathsf{Cohcube}_{#1}^{#2}}
-\newcommand{\heterocohbox}[2]{\mathsf{coh{\heteroname}box}_{#1}^{#2}}
-\newcommand{\heterocohlayer}[2]{\mathsf{coh{\heteroname}layer}_{#1}^{#2}}
-\newcommand{\heterocohcube}[2]{\mathsf{coh{\heteroname}cube}_{#1}^{#2}}
-\newcommand{\myappdepbox}[1]{\mathsf{homoappbox}_{#1}}
-\newcommand{\myappdeplayer}[1]{\mathsf{homoapplayer}_{#1}}
-\newcommand{\myappdepcube}[1]{\mathsf{homoappcube}_{#1}}
-\newcommand{\myappdepfullcube}[1]{\mathsf{homoappfullcube}_{#1}}
-\newcommand{\myappdepboxtype}[1]{\mathsf{homoappbox}_{#1}}
-\newcommand{\myappdepfullboxtype}[1]{\mathsf{homoappfullbox}_{#1}}
-\newcommand{\myappdeplayertype}[1]{\mathsf{homoapplayer}_{#1}}
-\newcommand{\myappdepcubetype}[1]{\mathsf{homoappcube}_{#1}}
-\newcommand{\myappdepfullcubetype}[1]{\mathsf{homoappfullcube}_{#1}}
-\newcommand{\myfullcube}[1]{\mathsf{fullcube}_{#1}}
-\newcommand{\myfullheteroboxtype}[2]{\mathsf{fullBox}_{#1}^{#2}}
-\newcommand{\myfullheterobox}[2]{\mathsf{full{\heteroname}box}_{#1}^{#2}}
-\newcommand{\reflfullcube}[1]{\mathsf{reflfullcube}_{#1}}
-\newcommand{\unitpoint}{\star}
-\newcommand{\reflett}{\mathsf{refl}_{\mathit{ETT}}}
-\newcommand{\mygpd}{\mathsf{gpd}}
-
-\newcommand{\mycubset}[1]{\mathsf{cubset}_{#1}}
-\newcommand{\mycubsetfrom}[2]{\mathsf{cubset}_{#1}^{\geq#2}}
-\newcommand{\mydepcubset}[1]{\mathsf{dephomocubset}_{#1}}
-\newcommand{\mydepcubsetfrom}[2]{\mathsf{dephomocubset}_{#1}^{\geq#2}}
-\newcommand{\mydepcubsetcomp}[2]{\mathsf{dephomocubset}_{#1}^{=#2}}
-\newcommand{\deppartialcubset}[2]{\mathsf{dephomocubset}_{#1}^{<#2}}
-\newcommand{\properheterocubetype}[2]{\mathsf{Filler}_{#1}^{#2}}
-
-\newcommand{\mydepheterocubset}[2]{\mathsf{depcubset}_{#1}^{#2}}
-\newcommand{\mydepheterocubsetfrom}[3]{\mathsf{depcubset}_{#1}^{#2,\geq#3}}
-\newcommand{\mydepheterocubsetcomp}[3]{\mathsf{depcubset}_{#1}^{#2,=#3}}
-\newcommand{\deppartialheterocubset}[3]{\mathsf{depcubset}_{#1}^{#2,<#3}}
-\newcommand{\myappheterodepbox}[1]{\mathsf{appbox}_{#1}}
-\newcommand{\myappheterodeplayer}[1]{\mathsf{applayer}_{#1}}
-\newcommand{\myappheterodepcube}[1]{\mathsf{appcube}_{#1}}
-\newcommand{\myappheterodepfullcube}[1]{\mathsf{appfullcube}_{#1}}
-\newcommand{\myappheterodepboxtype}[1]{\mathsf{appbox}_{#1}}
-\newcommand{\myappheterodepfullboxtype}[3]{\mathsf{appfullbox}_{#1}^{#2,#3}}
-\newcommand{\myappheterodeplayertype}[1]{\mathsf{applayer}_{#1}}
-\newcommand{\myappheterodepcubetype}[1]{\mathsf{appcube}_{#1}}
-\newcommand{\myappheterodepfullcubetype}[1]{\mathsf{appfullcube}_{#1}}
-
-\newcommand{\typecubset}{\mathsf{typecubset}}
-\newcommand{\mysymcubset}{\mathsf{symcubset}}
-\newcommand{\issymcubset}{\mathsf{issymcubset}}
-\newcommand{\partialsymcubset}{\mathsf{symcubset}}
-\newcommand{\mypermute}{\mathsf{permute}}
-\newcommand{\partialhascomp}{\mathsf{partialhascomp}}
-\newcommand{\hascomp}{\mathsf{hascomp}}
-\newcommand{\tube}[1]{\mathsf{tube}_{#1}}
-\newcommand{\propercube}[1]{\mathsf{properfiller}_{#1}}
-\newcommand{\properheterocube}[2]{\mathsf{{\heteroname}filler}_{#1}^{#2}}
-\newcommand{\bordertype}[1]{\mathsf{Boxofcube}_{#1}}
-\newcommand{\cohbordertype}[1]{\mathsf{Cohboxofcube}_{#1}}
-\newcommand{\myheteroborder}[1]{\mathsf{{\heteroname}border}_{#1}}
-\newcommand{\fullheterocubetype}[2]{\mathsf{fullCube}_{#1}^{#2}}
-\newcommand{\fullheterocube}[1]{\mathsf{full{\heteroname}cube}_{#1}}
-\newcommand{\heterotubetype}[1]{\mathsf{Tube}_{#1}}
-\newcommand{\heterotube}[1]{\mathsf{{\heteroname}tube}_{#1}}
-\newcommand{\mygroundedcube}[1]{\mathsf{groundedcube}_{#1}}
-\newcommand{\mygroundedheterocubetype}[1]{\mathsf{groundedCube}_{#1}}
-\newcommand{\mygroundedheterocube}[1]{\mathsf{grounded{\heteroname}cube}_{#1}}
-\newcommand{\reflexive}[1]{\mathsf{reflexive}_{#1}}
-\newcommand{\permutation}{\mathsf{permutation}}
-\newcommand{\diagonal}{\mathsf{diagonal}}
-\newcommand{\connection}{\mathsf{connection}}
-\newcommand{\diagprop}{\mathsf{diag}}
-\newcommand{\reglr}{\rightarrow-\mathsf{reg}}
-\newcommand{\regrl}{\leftarrow-\mathsf{reg}}
-\newcommand{\coercivelr}{\rightarrow-\mathsf{def}}
-\newcommand{\coerciverl}{\leftarrow-\mathsf{def}}
-\newcommand{\regularitylr}{\rightarrow-\mathsf{regularity}}
-\newcommand{\regularityrl}{\leftarrow-\mathsf{regularity}}
-\newcommand{\Reglr}{\Rightarrow-\mathsf{reg}}
-\newcommand{\Regrl}{\Leftarrow-\mathsf{reg}}
-\newcommand{\Coercivelr}{\Rightarrow-\mathsf{def}}
-\newcommand{\Coerciverl}{\Leftarrow-\mathsf{def}}
-\newcommand{\Regularitylr}{\Rightarrow-\mathsf{regularity}}
-\newcommand{\Regularityrl}{\Leftarrow-\mathsf{regularity}}
-\newcommand{\coebacklr}{\overrightarrow{\mathsf{coe}}}
-\newcommand{\coebackrl}{\overleftarrow{\mathsf{coe}}}
-\newcommand{\backcoercivelr}{\overrightarrow{\mathsf{coe}}-\mathsf{def}}
-\newcommand{\backcoerciverl}{\overleftarrow{\mathsf{coe}}-\mathsf{def}}
-\newcommand{\regbacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{reg}}
-\newcommand{\regbackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{reg}}
-\newcommand{\regularitybacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{regularity}}
-\newcommand{\regularitybackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{regularity}}
-\newcommand{\Coebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}}
-\newcommand{\Coebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}}
-\newcommand{\Coercivebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
-\newcommand{\Coercivebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
-\newcommand{\Regbacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
-\newcommand{\Regbackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
-\newcommand{\Regularitybacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}
-\newcommand{\Regularitybackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}
-
-\newcommand{\reflbox}[1]{\mathsf{reflbox}_{#1}}
-\newcommand{\refllayer}[1]{\mathsf{refllayer}_{#1}}
-\newcommand{\reflcube}[1]{\mathsf{reflcube}_{#1}}
-\newcommand{\permutebox}{\mathsf{permutebox}}
-\newcommand{\diagbox}{\mathsf{diagbox}}
-\newcommand{\connbox}{\mathsf{connbox}}
-\newcommand{\first}{\mathsf{first}}
-\newcommand{\groupoid}{\mathsf{groupoid}}
-\newcommand{\groupoidn}{\mathsf{groupoidn}}
-\newcommand{\letinsplit}[3]{\!\!\begin{array}{l}\mathbf{let}~{#1}=#2\;\mathbf{in}~\\#3\end{array}}
-
-\newcommand{\UIP}{\mathsf{UIP}}
-
 \title{An indexed construction of semi-cubical types}
@@
 \begin{document}
+\begin{abstract}
+  We present a dependently-typed construction of semi-cubical sets, along with an accompanying artifact in Coq.
+\end{abstract}
 \maketitle
-
 \tableofcontents

### 2021-07-10 paper/paper.tex
[paper] Fix table caption style

@@
 \usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
-\usepackage{bookmark, titling, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace, makecell}
+\usepackage{bookmark, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace, makecell, caption, floatrow}
 \usepackage[margin=0.3in]{geometry}
-
-\newcommand{\highlight}[1]{\emph{#1}}
 
@@
 \newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}
+
+% Table caption set up
+\DeclareCaptionFormat{hfillstart}{\hfill#1#2#3\par}
+\DeclareCaptionFont{mdit}{\mdseries\itshape}
+\captionsetup[table]{
+  justification=centering,
+  font=bf,
+  labelfont=mdit,
+}
+\floatsetup[table]{capposition=bottom}
 

### 2021-07-10 paper/paper.tex
[paper] Start an introductory section on SSet

@@
 \usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
-\usepackage{bookmark, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace, makecell, caption, floatrow}
+\usepackage{bookmark, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace, makecell, caption, floatrow, amsthm}
 \usepackage[margin=0.3in]{geometry}
@@
 
-% Simplicial set macros
-\newcommand{\BDelta}{\ensuremath{\boldsymbol{\Delta}}}
-\newcommand{\Simplex}[1][n]{\ensuremath{\boldsymbol{\Delta^{#1}}}}
-\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
-\newcommand{\SSet}{\ensuremath{\text{Set}_{\boldsymbol{\Delta}}}}
-
 % The eqntable environment, displaying the various
@@
 
+% Theorems
+\newtheorem{notation}{Notation}
+\newtheorem{definition}{Definition}
+\newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
+\newtheorem{theorem}{Theorem}
+\newtheorem{remark}{Remark}
+\newtheorem{example}{Example}
+
+% Simplicial sets
+\newcommand{\BDelta}{\ensuremath{\boldsymbol{\Delta}}}
+\newcommand{\Simplex}{\ensuremath{\boldsymbol{\Delta^n}}}
+\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
+\newcommand{\SSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\Delta}}}}
+\newcommand{\Set}{\ensuremath{\mathsf{Set}}}
+\newcommand{\sq}[1]{\ensuremath{\mathsf{[#1]}}}
+\newcommand{\sqsn}{\ensuremath{\mathsf{[1 \ldots n]}}}
+
+% Cubical sets
+\newcommand{\Cube}{\ensuremath{\boldsymbol{\square}}}
+
 \title{An indexed construction of semi-cubical types}
@@
 \tableofcontents
+
+\section{The intutution from \texorpdfstring{\SSet}{simplicial sets}}
+\subsection{Standard definitions}
+
+Let us first review a few standard definitions appearing in mathematical literature. We will refer the reader to \cite{Friedman08} and \cite{Riehl11} for more on the subject.
+
+\begin{notation}[\sq{n}]
+  The notation \sq{n} is used to denote the set of finite ordinals, with preorder structure.
+
+  \begin{equation*}
+    \sq{n} := 0 \rightarrow 1 \rightarrow \ldots \rightarrow n
+  \end{equation*}
+\end{notation}
+
+\begin{definition}[Informal definition of \Simplex]
+  The standard $n$-simplex is the prototypical example of a simplicial set,  can be informally defined as all ordered subsets of \sq{n}, also denoted \sqsn.
+\end{definition}
+
+We will now define the category of simplicial sets, and redefine $\Simplex$ formally.
+
+\begin{definition}[\BDelta]
+  The $\BDelta$ category can be defined in terms of its objects and morphisms:
+
+  \begin{align*}
+    obj(\BDelta) & := \sq{n}                                             \\
+    mor(\BDelta) & := \sq{m} \rightarrow \sq{n}, \text{order-preserving}
+  \end{align*}
+\end{definition}
+
+\begin{definition}[\SSet]
+  The category of simplicial sets is then defined as the functor category:
+
+  \begin{equation*}
+    \SSet := \Set^{\BDelta^{op}}
+  \end{equation*}
+\end{definition}
+
+\begin{definition}[\Simplex]
+  $\Simplex$ is the Yoneda embedding of \sq{n}.
+
+  \begin{equation*}
+    \Simplex := y(\sq{n})
+  \end{equation*}
+\end{definition}
+
+To concretely define simplicial sets in terms of objects and morphisms, they can be viewed from two different equivalent viewpoints.
+
+\begin{definition}[\SSet, from the first viewpoint]
+  \begin{align*}
+    obj(\SSet) & := \text{functors}, \BDelta \rightarrow \Set      \\
+    mor(\SSet) & := \text{natural transforms between the functors}
+  \end{align*}
+\end{definition}
+
+\begin{definition}[\SSet, from the second viewpoint]
+  \begin{align*}
+    obj(\SSet) & := \text{ordered n-simplices}, X_n \\
+    mor(\SSet) & :=
+    \begin{cases}
+      d_i : X_{n + 1} \rightarrow X_n & \text{face maps}       \\
+      s_i : X_n \rightarrow X_{n + 1} & \text{degeneracy maps}
+    \end{cases}
+  \end{align*}
+
+  where $X_n$ is defined as:
+  \begin{equation*}
+    X_n := \text{Hom}(\Simplex, X), \text{where X is the simplicial set}
+  \end{equation*}
+
+  and $d_i$, $s_i$ are constrained by the following ``gluing conditions'':
+
+  \begin{align*}
+    d_i d_j & = d_{j - 1} d_i, i < j \\
+    s_i s_j & = s_{j + 1} s_i, i < j \\
+    d_i s_j & =
+    \begin{cases}
+      s_{j - 1} d_i & i < j \\
+      id            & i = j \\
+      s_j d_{i - 1} & i > j
+    \end{cases}
+  \end{align*}
+\end{definition}
+
+\subsection{The motivation for \texorpdfstring{\DeltaHat}{delta sets}}
+
+The issue with mechanisation of \SSet, and the corresponding cubical sets, is the degeneracy maps - there are an infinite number of degenerate simplices in any simplicial set, and these degeneracies are not interesting from the point of view of cubical type theory.
+To remedy this problem, let us instead use \DeltaHat, and proceed towards building, what is called semi-cubical sets in literature.
+$\DeltaHat$ is identical to \BDelta, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are strictly order-preserving.
+The degeneracies then vanish, and we're left with the task of defining gluing conditions solely on the basis of face maps.
+In mathematical literature, there is little interest in studying \DeltaHat, since delta maps are not well-defined, and constructing a $\Set^{\DeltaHat^{op}}$ is inelegant.
+The objective of this paper is to first generalize delta-sets to the cubical setting, and provide a precise mechanically-checked formalization of the same.
+The formalization effort pushes the boundaries of dependently-typed programming and the tactic system in Coq.
+
+\subsection{Towards semi-cubical sets}
+
+Let us, on the outset, define \Cube, identically to \DeltaHat.
+
+\begin{definition}[\Cube]
+  \begin{align*}
+    \text{obj}(\Cube) & := \sq{n}                                                      \\
+    \text{mor}(\Cube) & := \sq{m} \rightarrow \sq{n}, \text{strictly order-preserving}
+  \end{align*}
+\end{definition}
 
@@
 Note that such relational structure, cubes and boxes are relative to a universe.
-Note the presence of a coherence condition \cohbox{l} to ensuring that both sides of the equality in \downlayer{l} and \downcube{l} are in the same type.
-The proof of \cohbox{l} itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
+Note the presence of a coherence condition $\cohbox{l}{}$ to ensuring that both sides of the equality in $\downlayer{l}{}$ and $\downcube{l}{}$ are in the same type.
+The proof of $\cohbox{l}{}$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
 Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning \downbox{l} nor \cohbox{l} anymore.
+Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\downbox{l}{}$ nor $\cohbox{l}{}$ anymore.
 
@@
 On top of the basic definitions on Figures~\ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}, we can define on Figures~\ref{tab:macros} and~\ref{tab:macroscont} a few other concepts at a more standard level of abstraction.
-In particular, a homogeneous $n$-box in the above sense is defined to be an object of type $\myfullbox{l}{n}(D_{n})$ for $D_{n} \defeq (A,=_A,...,=^n_A)$ the initial segment of $n$-th first iterated equalities over $A$ (by convention, a homogeneous $0$-box shall be the canonical singleton type).
+In particular, a homogeneous $n$-box in the above sense is defined to be an object of type $\myfullbox{l}{n}(D_{n})$ for $D_{n} \defeq (A, =_A, \ldots, =^n_A)$ the initial segment of $n$-th first iterated equalities over $A$ (by convention, a homogeneous $0$-box shall be the canonical singleton type).
 A $n$-tube is of type $\mybox{l}{n+1,n}(D_{n+1})$.
@@
 to partial cubes over the empty box.
-Figure~\ref{tab:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see \border).
+Figure~\ref{tab:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see $\border{}$).
 
@@
 \begin{thebibliography}{10}
+  \bibitem{Friedman08}
+  Friedman, G. (2008). An elementary illustrated introduction to simplicial sets. \textit{arXiv preprint arXiv:0809.4221}.
+
+  \bibitem{Riehl11}
+  Riehl, E.
+(2011).
+A leisurely introduction to simplicial sets.
+\textit{Unpublished expository article available online at \href{http://www.math.harvard.edu/~eriehl}{http://www.math.harvard.edu/~eriehl}}.
+
   \bibitem{Herbelin15}

### 2021-07-10 paper/paper.tex
[paper] Draft introduction

@@
 
+% Lettered footnotes
+\renewcommand{\thefootnote}{\alph{footnote}}
+
 % Theorems
@@
 \tableofcontents
+
+\section{Introduction}
+
+Cubical type theory is an extension of dependent type theory that provides a way to provide a computational interpretation of Voevodsky's Univalence Axiom.
+Several strides in the field have been made since \cite{Bezem14} in constructing a model of type theory for cubical sets, and we present another approach to the construction, with a rigorous mathematical foundation.
+Though motivated by homotopy type theory, construction of the path type and transport are beyond the scope of our work.
+Our secondary contribution is a formalization of semi-cubical sets in vanilla Coq~\footnote{\href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}}.
 
@@
 The objective of this paper is to first generalize delta-sets to the cubical setting, and provide a precise mechanically-checked formalization of the same.
-The formalization effort pushes the boundaries of dependently-typed programming and the tactic system in Coq.
 
@@
 \begin{thebibliography}{10}
+  \bibitem{Bezem14}
+  Bezem, M., Coquand, T., \& Huber, S.
+(2014, July).
+A model of type theory in cubical sets.
+\textit{In 19th International Conference on Types for Proofs and Programs (TYPES 2013)} (Vol.
+26, pp.
+107-128).
+Wadern, Germany: Schloss Dagstuhl–Leibniz Zentrum fuer Informatik.
+
   \bibitem{Friedman08}

### 2021-07-10 paper/paper.tex
[paper] Define CSet and get rid of all warnings

@@
-\documentclass[10pt]{amsart}
+\documentclass[10pt, titlepage]{amsart}
 
 \usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
-\usepackage{bookmark, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace, makecell, caption, floatrow, amsthm}
+\usepackage{bookmark, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, tikz-cd, booktabs, setspace, makecell, caption, floatrow, amsthm, lmodern}
 \usepackage[margin=0.3in]{geometry}
@@
 }
-\floatsetup[table]{capposition=bottom}
+\DeclareFloatFont{small}{\small}
+\floatsetup[table]{capposition=bottom, font=small}
 
@@
 % Simplicial sets
-\newcommand{\BDelta}{\ensuremath{\boldsymbol{\Delta}}}
-\newcommand{\Simplex}{\ensuremath{\boldsymbol{\Delta^n}}}
+\newcommand{\Simplex}[1]{\ensuremath{\boldsymbol{\Delta^{#1}}}}
 \newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
@@
 % Cubical sets
-\newcommand{\Cube}{\ensuremath{\boldsymbol{\square}}}
+\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
+\newcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
+\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
 
@@
 
-\begin{definition}[Informal definition of \Simplex]
+\begin{definition}[Informal definition of \Simplex{n}]
   The standard $n$-simplex is the prototypical example of a simplicial set,  can be informally defined as all ordered subsets of \sq{n}, also denoted \sqsn.
@@
 
-We will now define the category of simplicial sets, and redefine $\Simplex$ formally.
+We will now define the category of simplicial sets, and redefine $\Simplex{n}$ formally.
 
-\begin{definition}[\BDelta]
-  The $\BDelta$ category can be defined in terms of its objects and morphisms:
+\begin{definition}[\Simplex{}]
+  The $\Simplex{}$ category can be defined in terms of its objects and morphisms:
 
   \begin{align*}
-    obj(\BDelta) & := \sq{n}                                             \\
-    mor(\BDelta) & := \sq{m} \rightarrow \sq{n}, \text{order-preserving}
+    obj(\Simplex{}) & := \sq{n}                                             \\
+    mor(\Simplex{}) & := \sq{m} \rightarrow \sq{n}, \text{order-preserving}
   \end{align*}
@@
   \begin{equation*}
-    \SSet := \Set^{\BDelta^{op}}
+    \SSet := \Set^{\Simplex{}^{op}}
   \end{equation*}
@@
 
-\begin{definition}[\Simplex]
-  $\Simplex$ is the Yoneda embedding of \sq{n}.
+\begin{definition}[\Simplex{n}]
+  $\Simplex{n}$ is the Yoneda embedding of \sq{n}.
 
   \begin{equation*}
-    \Simplex := y(\sq{n})
+    \Simplex{n} := y(\sq{n})
   \end{equation*}
@@
   \begin{align*}
-    obj(\SSet) & := \text{functors}, \BDelta \rightarrow \Set      \\
+    obj(\SSet) & := \text{functors}, \Simplex{} \rightarrow \Set   \\
     mor(\SSet) & := \text{natural transforms between the functors}
@@
   \begin{equation*}
-    X_n := \text{Hom}(\Simplex, X), \text{where X is the simplicial set}
+    X_n := X(\sq{n}) = \text{Hom}(\Simplex{n}, X), \text{where X is the simplicial set}
   \end{equation*}
@@
 To remedy this problem, let us instead use \DeltaHat, and proceed towards building, what is called semi-cubical sets in literature.
-$\DeltaHat$ is identical to \BDelta, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are strictly order-preserving.
+$\DeltaHat$ is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are strictly order-preserving.
 The degeneracies then vanish, and we're left with the task of defining gluing conditions solely on the basis of face maps.
@@
 
-Let us, on the outset, define \Cube, identically to \DeltaHat.
+Let us first motivate the definition of semi-cubical sets, as defined in \cite{Antolini00}.
+On the outset, we might naively attempt to define $\Cube{}$ identically to \DeltaHat, but let us briefly explain why this wouldn't work.
+If there were morphisms from every $\sq{m}$ to $\sq{n}$, we would end up with:
 
-\begin{definition}[\Cube]
+$$
+  \begin{tikzcd}
+    \bullet \arrow[r] \arrow[dr] \arrow[d] & \bullet \arrow[dl] \arrow[d] \\
+    \bullet \arrow[r] & \bullet
+  \end{tikzcd}
+$$
+
+where the filling conditions are conflated with the cube itself.
+$\Simplex{n}$ can be defined quite simply as the convex hull of $n$ points, but even defining the standard $n$-cube becomes a problem if we start with with the point as $\Cube{0}$, but the situation becomes much more amenable if we define:
+
+\begin{definition}[\Cube{n}]
+  \begin{equation*}
+    \Cube{n} := \I{n} = \sq{0, 1}^n
+  \end{equation*}
+\end{definition}
+
+Here, $\I{n}$ serves the purpose of $\sq{n}$, but this change will cascade into other definitions. In view of defining a category \CSet, we will restrict the morphisms in \Cube{}.
+
+\begin{definition}[\Cube{}]
   \begin{align*}
-    \text{obj}(\Cube) & := \sq{n}                                                      \\
-    \text{mor}(\Cube) & := \sq{m} \rightarrow \sq{n}, \text{strictly order-preserving}
+    obj(\Cube{}) & := \I{n}                                           \\
+    mor(\Cube{}) & := \delta^\epsilon_i : \I{n + 1} \rightarrow \I{n}
+  \end{align*}
+
+  where $\delta^\epsilon_i$ must satisfy the corresponding face map condition:
+
+  \begin{equation*}
+    \delta^\epsilon_i \delta^\omega_j = \delta^\omega_{j - 1} \delta^\epsilon_i
+  \end{equation*}
+
+  where $\epsilon$ and $\omega$ correspond to opposite faces.
+\end{definition}
+
+\begin{definition}[\CSet]
+  Just as in \SSet, we define semi-cubical sets as the functor category:
+
+  \begin{equation*}
+    \CSet := \Set^{\Cube{}^{op}}
+  \end{equation*}
+\end{definition}
+
+Then, the first viewpoint corresponding to the one in simplicial sets is uninteresting for our purposes. Let us, instead, elaborate on the second viewpoint:
+
+\begin{definition}[$\CSet$ in terms of objects and morphisms]
+  \begin{align*}
+    obj(\CSet) & := X_n                                                   \\
+    mor(\CSet) & := X_\lambda, \text{where $\lambda$ is \Cube{}-morphism}
+  \end{align*}
+
+  where we term $X_n$ as the $n$-cubex, and $X_\lambda$ as the ``face map'', defined similarly:
+
+  \begin{align*}
+    X_n       & := X(\I{n}) = \text{Hom}(\I{n}, X), \text{where X is the semi-cubical set} \\
+    X_\lambda & := X(\lambda)
   \end{align*}
@@
 
-  \eqnline{\cohbox{l,\epsilon,\epsilon',q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\makecell{\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}}
+  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\makecell{\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\omega,r}{n,p}(D)(d)) \\ \eqett \downbox{l,\omega,r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}}
 
-  \eqnline{\cohbox{l,\epsilon,\epsilon',q,r}{n,0}}{D~\unitpoint}{\defeq}{\reflett}{(\unitpoint)}
+  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,0}}{D~\unitpoint}{\defeq}{\reflett}{(\unitpoint)}
 
-  \eqnline{\cohbox{l,\epsilon,\epsilon',q,r}{n,p'+1}}{D~(d,b)}{\defeq}{(\cohbox{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d)(b))}
+  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,p'+1}}{D~(d,b)}{\defeq}{(\cohbox{l,\epsilon,\omega,q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\omega,q,r}{n,p'}(D)(d)(b))}
 
@@
 
-  \eqnline{\cohlayer{l,\epsilon,\epsilon',q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D)) \\(b:\mylayer{l}{n,p}(D)(d))}}{:}{\makecell{\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))}}
+  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D)) \\(b:\mylayer{l}{n,p}(D)(d))}}{:}{\makecell{\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downlayer{l,\omega,r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\omega,r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))}}
 
-  \eqnline{\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}}{D~d~c}{\defeq}{\makecell{(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L), \\ \;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))}}
+  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p}}{D~d~c}{\defeq}{\makecell{(\cohcube{l,\epsilon,\omega,q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L), \\ \;\cohcube{l,\epsilon,\omega,q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))}}
 
@@
 
-  \eqnline{\cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D)) \\ (b:\mycube{l}{n,p}(D)(E)(d))}}{:}{\makecell{\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))}}
+  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D)) \\ (b:\mycube{l}{n,p}(D)(E)(d))}}{:}{\makecell{\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downcube{l,\omega,r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\omega,r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))}}
 
-  \eqnline{\cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon}))}
+  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\omega,p}{n,p}(D)(d))(b_{\epsilon}))}
 
-  \eqnline{\cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]}}{D~E~d~(b,c)}{\defeq}{(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))}
+  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p<r]}}{D~E~d~(b,c)}{\defeq}{(\cohlayer{l,\epsilon,\omega,q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\omega,q,r}{n,p+1}(D)(E)(d,b)(c))}
 \end{eqntable}
@@
 
+  \bibitem{Antolini00}
+  Antolini, R. (2000). Cubical structures, homotopy theory. \textit{Annali di Matematica pura ed applicata, 178}(1), 317-324.
+
   \bibitem{Herbelin15}

### 2021-07-10 paper/paper.tex
[paper] Some polish

@@
 
-% Partials and fulls, related to box, cube, and tube
+% Partials and fulls related to box, cube, and tube
 \newcommand{\border}[1]{\ensuremath{\mathsf{border}_{#1}}}
@@
 % Simplicial sets
+\newcommand{\Set}{\ensuremath{\mathsf{Set}}}
 \newcommand{\Simplex}[1]{\ensuremath{\boldsymbol{\Delta^{#1}}}}
@@
 \newcommand{\SSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\Delta}}}}
-\newcommand{\Set}{\ensuremath{\mathsf{Set}}}
 \newcommand{\sq}[1]{\ensuremath{\mathsf{[#1]}}}
@@
 
-Cubical type theory is an extension of dependent type theory that provides a way to provide a computational interpretation of Voevodsky's Univalence Axiom.
+Cubical type theory is an extension of dependent type theory that provides a computational interpretation of Voevodsky's Univalence Axiom.
 Several strides in the field have been made since \cite{Bezem14} in constructing a model of type theory for cubical sets, and we present another approach to the construction, with a rigorous mathematical foundation.
-Though motivated by homotopy type theory, construction of the path type and transport are beyond the scope of our work.
-Our secondary contribution is a formalization of semi-cubical sets in vanilla Coq~\footnote{\href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}}.
+Though motivated by homotopy type theory, construction of the path type and transport are beyond the scope of our work; we merely formalize semi-cubical sets.
+Our secondary contribution is a mechanically checked proof of our construction in vanilla Coq~\footnote{\href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}}.
 
@@
 
+\begin{theorem}[$\CSet$ does not admit degeneracies]
+  This is proved in \cite{Antolini00}.
+\end{theorem}
+
 \section{Semi-cubical sets}
@@
 In this section, we give the core of the definition of semi-cubical
-sets as the coinductive limit (see Figure~\ref{tab:barecubicalset}) of a
+sets as the coinductive limit (see table \ref{tab:barecubicalset}) of a
 construction of truncated semi-cubical sets.
@@
 
-The definition is dispatched over Figures~\ref{tab:barecubicalsetstructurecore}, \ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}.
+The definition is dispatched over tables \ref{tab:barecubicalsetstructurecore}, \ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}.
 It describes the structure of the underlying higher-dimensional relations on which cubes and boxes are built, together with the definition of homogeneous $n$-boxes, homogeneous $n$-cubes, together with face operations on boxes and cubes, together with commutation properties of the face operations.
@@
 
-When reflexivities are excepted, we call the structure thus defined \emph{bare truncated cubical sets}: \emph{bare} because it can be seen as defining a cubical equivalent to semi-simplicial sets with only faces as part of the structure (otherwise said, another terminology could have been ``semi-cubical'' sets); \emph{truncated} because we consider only such cubical sets up to some fixed dimension.
+When reflexivities are excepted, we call the structure thus defined \emph{bare truncated cubical sets}: \emph{bare} because it can be seen as defining semi-cubical sets corresponding to semi-simplicial sets with only faces as part of the structure; \emph{truncated} because we consider only such cubical sets up to some fixed dimension.
 
@@
 
-On top of the basic definitions on Figures~\ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}, we can define on Figures~\ref{tab:macros} and~\ref{tab:macroscont} a few other concepts at a more standard level of abstraction.
+On top of the basic definitions on tables \ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}, we can define on tables \ref{tab:macros} and \ref{tab:macroscont} a few other concepts at a more standard level of abstraction.
 In particular, a homogeneous $n$-box in the above sense is defined to be an object of type $\myfullbox{l}{n}(D_{n})$ for $D_{n} \defeq (A, =_A, \ldots, =^n_A)$ the initial segment of $n$-th first iterated equalities over $A$ (by convention, a homogeneous $0$-box shall be the canonical singleton type).
@@
 to partial cubes over the empty box.
-Figure~\ref{tab:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see $\border{}$).
+Table \ref{tab:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see $\border{}$).
 
-Figure~\ref{tab:macros} also shows how to compute the faces of a box or of a cube.
+Table \ref{tab:macros} also shows how to compute the faces of a box or of a cube.
 
@@
 
-  \\ \mc{where the extension of \downbox{l} to $p>q$ is}
+  \\ \mc{where the extension of $\downbox{l}{}$ to $p>q$ is}
 

### 2021-07-10 paper/paper.tex
[paper] Fix errors and supply examples

@@
 
+\begin{example}[\Simplex{0}, \Simplex{1}, and \Simplex{2}]
+  $\Simplex{0}$ can be drawn as:
+
+  $$
+    \begin{tikzcd}
+      0
+    \end{tikzcd}
+  $$
+
+  $\Simplex{1}$ can be drawn as:
+
+  $$
+    \begin{tikzcd}
+      0 \arrow[r] & 1
+    \end{tikzcd}
+  $$
+
+  and $\Simplex{2}$ can be drawn as:
+
+  $$
+    \begin{tikzcd}
+      & 1 \arrow[dr] & \\
+      0 \arrow[ur] \arrow[rr] & & 2
+    \end{tikzcd}
+  $$
+
+  Note that we only show non-degerate simplices in the figure.
+\end{example}
+
 We will now define the category of simplicial sets, and redefine $\Simplex{n}$ formally.
@@
   \begin{tikzcd}
-    \bullet \arrow[r] \arrow[dr] \arrow[d] & \bullet \arrow[dl] \arrow[d] \\
-    \bullet \arrow[r] & \bullet
+    \bullet \arrow[r] \arrow[dr] \arrow[d] & \bullet \arrow[d] \\
+    \bullet \arrow[r] \arrow[ur] & \bullet
   \end{tikzcd}
@@
 where the filling conditions are conflated with the cube itself.
-$\Simplex{n}$ can be defined quite simply as the convex hull of $n$ points, but even defining the standard $n$-cube becomes a problem if we start with with the point as $\Cube{0}$, but the situation becomes much more amenable if we define:
+$\Simplex{n}$ can be defined quite simply as the convex hull of $n$ points, but even defining the standard $n$-cube becomes a problem if we start with $\sq{n}$, but the situation becomes much more amenable if we define:
 
@@
 \end{definition}
+
+\begin{example}[$\Cube{0}$, $\Cube{1}$ and $\Cube{2}$]
+  $\Cube{0}$ can be drawn as:
+
+  $$
+    \begin{tikzcd}
+      0 \equiv 1
+    \end{tikzcd}
+  $$
+
+  $\Cube{1}$ can be drawn as:
+
+  $$
+    \begin{tikzcd}
+      0 \arrow[r, dash] & 1
+    \end{tikzcd}
+  $$
+
+  and $\Cube{2}$ can be drawn as:
+
+  $$
+    \begin{tikzcd}
+      1 \arrow[r, dash] & 1' \arrow[d, dash] \\
+      0 \arrow[u, dash] & 0' \arrow[l, dash]
+    \end{tikzcd}
+  $$
+\end{example}
 

### 2021-07-17 paper/paper.tex
[Cubical] Replace epsilon' with omega
[paper] Start writing Grothendieck construction

@@
 \usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
-\usepackage{bookmark, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, tikz-cd, booktabs, setspace, makecell, caption, floatrow, amsthm, lmodern}
+\usepackage{bookmark, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, tikz-cd, booktabs, setspace, makecell, caption, floatrow, amsthm, mathrsfs, lmodern}
 \usepackage[margin=0.3in]{geometry}
@@
 
-\title{An indexed construction of semi-cubical types}
+% Type theory
+\newcommand{\U}{\ensuremath{\mathscr{U}}}
+
+\title{An iterated Grothendieck construction of semi-cubical types}
 \author{Ramkumar Ramachandra}
@@
     \begin{tikzcd}
-      1 \arrow[r, dash] & 1' \arrow[d, dash] \\
-      0 \arrow[u, dash] & 0' \arrow[l, dash]
+      (0, 1) \arrow[r, dash] & (1, 1) \arrow[d, dash] \\
+      (0, 0) \arrow[u, dash] & (1, 0) \arrow[l, dash]
     \end{tikzcd}
@@
 
-Then, the first viewpoint corresponding to the one in simplicial sets is uninteresting for our purposes. Let us, instead, elaborate on the second viewpoint:
+Or, in terms of objects and morphisms:
 
@@
   \begin{align*}
-    X_n       & := X(\I{n}) = \text{Hom}(\I{n}, X), \text{where X is the semi-cubical set} \\
+    X_n       & := X(\I{n}), \text{where X is the semi-cubical set} \\
     X_\lambda & := X(\lambda)
@@
 \end{theorem}
+
+\section{Iterated Grothendieck construction}
+
+The Grothendieck construction provides a correspondence between a fibered representation, and an indexed representation.
+
+$$
+  \begin{tikzcd}
+    X_0 : \U & X_1 : \U \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \U \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
+  \end{tikzcd}
+$$
+
+\begin{align*}
+  X_0 & : \U                                                                                                      \\
+  X_1 & : X_0 \times X_0 \rightarrow \U                                                                           \\
+  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \U \\
+  \ldots
+\end{align*}
 
@@
 \begin{eqntable}{\label{tab:barecubicalsetstructurecore} Definition of a truncated cubical set (main part of the higher-dimensional relation structure)}
-  \mc{Type of truncated cubical sets} \\
+  \mc{Type of truncated cubical sets}
   \eqnline{\partialcubset{l}{n}}{}{:}{\sort{l+1}}
@@
 \begin{thebibliography}{10}
-  \bibitem{Bezem14}
+  \bibitem[Bez]{Bezem14}
   Bezem, M., Coquand, T., \& Huber, S.
@@
 
-  \bibitem{Friedman08}
+  \bibitem[Fri]{Friedman08}
   Friedman, G. (2008). An elementary illustrated introduction to simplicial sets. \textit{arXiv preprint arXiv:0809.4221}.
 
-  \bibitem{Riehl11}
+  \bibitem[Rie]{Riehl11}
   Riehl, E.
@@
 
-  \bibitem{Antolini00}
+  \bibitem[Ant]{Antolini00}
   Antolini, R. (2000). Cubical structures, homotopy theory. \textit{Annali di Matematica pura ed applicata, 178}(1), 317-324.
 
-  \bibitem{Herbelin15}
+  \bibitem[Her]{Herbelin15}
   Herbelin, H. (2015). A dependently-typed construction of semi-simplicial types. \textit{Mathematical Structures in Computer Science, 25}(5), 1116-1131.

### 2021-09-08 paper/paper.tex
Cubical: more progress; stuck on delicate rew unification
paper: rewrite SSet section; fancyhdr; write abstract

@@
-\documentclass[10pt, titlepage]{amsart}
+\documentclass[10pt]{amsart}
 
 \usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
-\usepackage{bookmark, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, tikz-cd, booktabs, setspace, makecell, caption, floatrow, amsthm, mathrsfs, lmodern}
-\usepackage[margin=0.3in]{geometry}
+\usepackage{amsthm, amssymb, amsaddr, fancyhdr, bookmark, fontspec, xargs, multirow, polyglossia, luacode, listings, color, soulutf8, tcolorbox, tabularx, tikz-cd, booktabs, setspace, makecell, caption, floatrow, mathrsfs, xpatch, lmodern}
+\usepackage[hmargin=0.4in, vmargin=0.8in, headheight=10pt]{geometry}
 
@@
 \newcommand{\Set}{\ensuremath{\mathsf{Set}}}
+\newcommand{\op}{\ensuremath{\mathsf{op}}}
 \newcommand{\Simplex}[1]{\ensuremath{\boldsymbol{\Delta^{#1}}}}
@@
 \newcommand{\sq}[1]{\ensuremath{\mathsf{[#1]}}}
-\newcommand{\sqsn}{\ensuremath{\mathsf{[1 \ldots n]}}}
 
@@
 
+% Roman numerals for chapters
+\renewcommand{\thesection}{\Roman{section}}
+
+% Fancy headers
+\pagestyle{fancy} % choose the "fancy" pagestyle
+\fancyhf{}        % clear all headers and footers
+% Now set the headers
+\fancyhead[LE,RO]{\footnotesize\thepage}
+\fancyhead[LO,RE]{\footnotesize\leftmark}
+\makeatletter
+\xapptocmd{\@sect}{\csname #1mark\endcsname{#7}}{}{}
+\makeatother
+
+% Subsection centering
+\makeatletter
+\def\subsection{\@startsection{subsection}{2}
+  \z@{.5\linespacing\@plus.7\linespacing}{.6\baselineskip}{\centering}}
+\makeatother
+
+% Nested numbering of sections and subsections
+\makeatletter
+\newif\ifsection
+\newif\ifsubsection
+\preto\section{\sectiontrue\subsectionfalse}
+\preto\subsection{\sectionfalse\subsectiontrue}
+\patchcmd{\@xsect}% <cmd>
+  {\ignorespaces}% <search>
+  {\ifsubsection
+   \numberwithin{definition}{subsection}
+   \else
+   \numberwithin{definition}{section}
+   \fi
+   \setcounter{definition}{0}\relax\ignorespaces}% <replace>
+  {}{}% <success><failure>
+\makeatother
+
 \title{An iterated Grothendieck construction of semi-cubical types}
 \author{Ramkumar Ramachandra}
+\address{Université de Paris}
 \author{Hugo Herbelin}
+\address{Institut de Recherche en Informatique Fondamentale}
 
@@
 \begin{abstract}
-  We present a dependently-typed construction of semi-cubical sets, along with an accompanying artifact in Coq.
+  A fresh approach to formalizing semi-cubical sets in dependent type theory with extensional equality.
+The approach could be described as a \emph{reverse iterated Grothendieck construction}, that is crisp and concise.
+The accompanying artifact is a Coq formalization that uses highly sophisticated rewriting techniques and pushes the boundary of proof assistant technology.
 \end{abstract}
@@
 \tableofcontents
+\newpage
 
 \section{Introduction}
-
-Cubical type theory is an extension of dependent type theory that provides a computational interpretation of Voevodsky's Univalence Axiom.
-Several strides in the field have been made since \cite{Bezem14} in constructing a model of type theory for cubical sets, and we present another approach to the construction, with a rigorous mathematical foundation.
-Though motivated by homotopy type theory, construction of the path type and transport are beyond the scope of our work; we merely formalize semi-cubical sets.
-Our secondary contribution is a mechanically checked proof of our construction in vanilla Coq~\footnote{\href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}}.
+Cubical type theory is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}.
+Several strides in the field have been made since \cite{Bezem14} in constructing a model of type theory for cubical sets, and we present another approach to the construction, with a sound motivation.
+Although our work is motivated by homotopy type theory, construction of the \emph{path type} and \emph{transport} are beyond the scope of our work; we merely formalize semi-cubical sets.
+Our secondary contribution is a mechanically checked proof of our construction in Coq~\footnote{\href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}}.
 
 \section{The intutution from \texorpdfstring{\SSet}{simplicial sets}}
-\subsection{Standard definitions}
+Simplicial sets are powerful mathematical objects, that form the basis of much of modern homotopy theory.
+Their power derives from the fact that their homotopy category is exceptionally well-behaved, and different model structures on them, as we will see in the following chapter.
+Unlike CW-complexes that rely on pure topological notions like spheres and disks to ``tame'' a topological space, the definition of simplicial sets is purely categorical, and exist independent of topological spaces.
+The geometric realization and singular complex functors facilitate travelling back-and-forth between simplicial sets and topological spaces, and these are non-trivial constructions.
+As such, simplicial sets exist purely in the imagination of the mathematician; each simplicial set has an infinite number of degenerate simplices, and they are not particularly well-suited to machine-based representation.
 
-Let us first review a few standard definitions appearing in mathematical literature. We will refer the reader to \cite{Friedman08} and \cite{Riehl11} for more on the subject.
+\subsection{The category of simplicial sets}
+There exists vast mathematical literature on the subject, and we refer the uninitiated reader to \cite{Friedman08} for a gentle introduction with excellent intutions.
+With these intuitions in place, we proceed with a purely categorical treatment.
+Emily Riehl's \cite{Riehl11} is a well-written manuscript on the subject.
 
-\begin{notation}[\sq{n}]
-  The notation \sq{n} is used to denote the set of finite ordinals, with preorder structure.
+\begin{definition}[\sq{n}]
+  $\sq{n}$ is used to denote a totally-ordered set of natural numbers less than or equal to $n$, ordered by magnitude.
+
+  \begin{equation*}
+    \sq{n} := \{0, 1, \ldots, n\}
+  \end{equation*}
+
+  We will regard the totally-ordered set as a category in certain contexts, and it should be clear which interpretation we're referring to from the context.
 
@@
   \end{equation*}
+\end{definition}
+
+\begin{definition}[\Simplex{}]
+  The category $\Simplex{}$ is defined in terms of its objects and morphisms:
+
+  \begin{align*}
+    obj(\Simplex{}) & := \sq{n}, \text{regarded as a totally-ordered set}   \\
+    mor(\Simplex{}) & := \sq{m} \rightarrow \sq{n}, \text{order-preserving}
+  \end{align*}
+\end{definition}
+
+\begin{definition}[\SSet]
+  The category of simplicial sets is defined as:
+
+  \begin{equation*}
+    \SSet := \Set^{\Simplex{}^\op}
+  \end{equation*}
+
+  It is a functor category, whose objects and morphisms are given by:
+
+  \begin{align*}
+    obj(\SSet)             & := \text{functors} \; \Simplex{}^\op \rightarrow \Set      \\
+    mor(\SSet)             & := \text{natural transforms between the functors}          \\
+    \text{composition law} & := \text{the usual composition of natural transformations} \\
+  \end{align*}
+\end{definition}
+
+\begin{definition}[\Simplex{n}]
+  The Yoneda embedding of $\sq{n}$ is referred to as the standard $n$-simplex.
+
+  \begin{equation*}
+    \Simplex{n} := y(\sq{n})
+  \end{equation*}
+\end{definition}
+
+\begin{notation}[$\sq{0, \ldots, n}$]
+  The notation $\sq{0, \ldots, n}$ denotes all ordered subsets of \sq{n}.
 \end{notation}
 
-\begin{definition}[Informal definition of \Simplex{n}]
-  The standard $n$-simplex is the prototypical example of a simplicial set,  can be informally defined as all ordered subsets of \sq{n}, also denoted \sqsn.
+With the definition of the category of simplicial sets firmly in place, we look inside a simplicial set to see the data it actually encodes concretely.
+
+\begin{definition}[The data of a simplicial set]
+  A simplicial set is equivalent to the data of a set of $n$-simplices, related to each other via face and degeneracy maps.
+
+  \begin{align*}
+    X_n                             & \;\;\text{a set of n-simplices} \\
+    d_i : X_{n + 1} \rightarrow X_n & \;\;\text{face maps}            \\
+    s_i : X_n \rightarrow X_{n + 1} & \;\;\text{degeneracy maps}      \\
+  \end{align*}
+
+  where $X_n$ is the set of $n$-simplices contained within the simplicial set $X$:
+
+  \begin{align*}
+    X_n & : \Set                                             \\
+    X_n & := X(\sq{n}), \text{where X is the simplicial set} \\
+  \end{align*}
+
+  and $d_i$ and $s_i$ operate on $X_n$ as follows (the hat on $i$ indicates that it is to be omitted):
+
+  \begin{align*}
+    d_i(\sq{0, \ldots, n}) & = \sq{0, \ldots, \hat{i}, \ldots, n} \\
+    s_i(\sq{0, \ldots, n}) & = \sq{0, \ldots, i, i, \ldots, n}    \\
+  \end{align*}
+
+  and $d_i$, $s_i$ are constrained by the following ``simplicial identities'':
+
+  \begin{align*}
+    d_i d_j & = d_{j - 1} d_i, i < j \\
+    s_i s_j & = s_{j + 1} s_i, i < j \\
+    d_i s_j & =
+    \begin{cases}
+      s_{j - 1} d_i & i < j \\
+      id            & i = j \\
+      s_j d_{i - 1} & i > j \\
+    \end{cases}
+  \end{align*}
 \end{definition}
+
+We mentioned degeneracies in the introduction to this section, and we define precisely what a degenerate simplex is now.
+
+\begin{definition}[Degenerate simplex]
+  A simplex is $x \in X_n$ is termed degenerate if it is the image of some degeneracy map $s_i$, and non-degenerate otherwise.
+\end{definition}
+
+\begin{example}[Non-degenerate simplices of \Simplex{n}]
+  The non-degenerate $k$-simplices of $\Simplex{n}$ are the injective maps $\sq{k} \rightarrow \sq{n}$ in $\Simplex{}$. In particular, $\Simplex{n}$ has a unique non-degenerate $n$-simplex.
+\end{example}
+
+As is clear from the above definitions, simplicial sets have an infinite number of degeneracies, and the first step towards drawing a simplicial set is to define a convention that omits these degeneracies in the drawing.
+
+\begin{notation}[Drawing of a simplicial set\label{not:drawsset}]
+  A diagram of the form
+
+  \begin{equation*}
+    \begin{tikzcd}
+      x \arrow[r, "f"] & y
+    \end{tikzcd}
+  \end{equation*}
+
+  in simplicial set $S$ will mean that $f$ is a non-degenerate $1$-simplex, and $x$ and $y$ are $0$-simplices.
+The simplices have a relationship to the simplicial set $S$ given by the following commutative diagram:
+
+  \begin{equation*}
+    \begin{tikzcd}
+      \Simplex{0} \arrow[dr] \arrow[drr, "x", bend left] & & \\
+      & \Simplex{1} \arrow[r, "f"] & S \\
+      \Simplex{0} \arrow[ur] \arrow[urr, "y"', bend right] & & \\
+    \end{tikzcd}
+  \end{equation*}
+
+  To attempting to draw simplices of dimension greater than $1$, we see that there is a potential ambiguity. Consider the following diagram:
+
+  \begin{equation*}
+    \begin{tikzcd}
+      & \bullet \arrow[ddr] & \\
+      \\
+      \bullet \arrow[uur] \arrow[rr] & & \bullet
+    \end{tikzcd}
+  \end{equation*}
+
+  In the above diagram, it is clear that there are three non-degenerate $1$-simplices, but it is unclear whether there is a non-degenerate $2$-simplex.
+By convention, when we draw such a diagram, we will assume that there is a non-degenerate $2$-simplex border by the three non-degenerate $1$-simplices.
+To generalize, we will always assume that there exists a non-degenerate $n$-simplex, when bounded by non-degenerate $(n - 1)$-simplices.
+\end{notation}
 
@@
     \begin{tikzcd}
-      & 1 \arrow[dr] & \\
-      0 \arrow[ur] \arrow[rr] & & 2
+      & 1 \arrow[ddr] & \\
+      \\
+      0 \arrow[uur] \arrow[rr] & & 2
     \end{tikzcd}
   $$
-
-  Note that we only show non-degerate simplices in the figure.
 \end{example}
-
-We will now define the category of simplicial sets, and redefine $\Simplex{n}$ formally.
-
-\begin{definition}[\Simplex{}]
-  The $\Simplex{}$ category can be defined in terms of its objects and morphisms:
-
-  \begin{align*}
-    obj(\Simplex{}) & := \sq{n}                                             \\
-    mor(\Simplex{}) & := \sq{m} \rightarrow \sq{n}, \text{order-preserving}
-  \end{align*}
-\end{definition}
-
-\begin{definition}[\SSet]
-  The category of simplicial sets is then defined as the functor category:
-
-  \begin{equation*}
-    \SSet := \Set^{\Simplex{}^{op}}
-  \end{equation*}
-\end{definition}
-
-\begin{definition}[\Simplex{n}]
-  $\Simplex{n}$ is the Yoneda embedding of \sq{n}.
-
-  \begin{equation*}
-    \Simplex{n} := y(\sq{n})
-  \end{equation*}
-\end{definition}
-
-To concretely define simplicial sets in terms of objects and morphisms, they can be viewed from two different equivalent viewpoints.
-
-\begin{definition}[\SSet, from the first viewpoint]
-  \begin{align*}
-    obj(\SSet) & := \text{functors}, \Simplex{} \rightarrow \Set   \\
-    mor(\SSet) & := \text{natural transforms between the functors}
-  \end{align*}
-\end{definition}
-
-\begin{definition}[\SSet, from the second viewpoint]
-  \begin{align*}
-    obj(\SSet) & := \text{ordered n-simplices}, X_n \\
-    mor(\SSet) & :=
-    \begin{cases}
-      d_i : X_{n + 1} \rightarrow X_n & \text{face maps}       \\
-      s_i : X_n \rightarrow X_{n + 1} & \text{degeneracy maps}
-    \end{cases}
-  \end{align*}
-
-  where $X_n$ is defined as:
-  \begin{equation*}
-    X_n := X(\sq{n}) = \text{Hom}(\Simplex{n}, X), \text{where X is the simplicial set}
-  \end{equation*}
-
-  and $d_i$, $s_i$ are constrained by the following ``gluing conditions'':
-
-  \begin{align*}
-    d_i d_j & = d_{j - 1} d_i, i < j \\
-    s_i s_j & = s_{j + 1} s_i, i < j \\
-    d_i s_j & =
-    \begin{cases}
-      s_{j - 1} d_i & i < j \\
-      id            & i = j \\
-      s_j d_{i - 1} & i > j
-    \end{cases}
-  \end{align*}
-\end{definition}
 
@@
 
-The issue with mechanisation of \SSet, and the corresponding cubical sets, is the degeneracy maps - there are an infinite number of degenerate simplices in any simplicial set, and these degeneracies are not interesting from the point of view of cubical type theory.
-To remedy this problem, let us instead use \DeltaHat, and proceed towards building, what is called semi-cubical sets in literature.
-$\DeltaHat$ is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are strictly order-preserving.
+As hinted earlier, simplicial sets are ill-suited for machine-based representation, due to the infinite number of degenerate simplices that are uninteresting from the point of view of cubical type theory.
+To remedy this problem, let us instead use \DeltaHat, and proceed towards building, what is called \emph{semi-cubical sets} in literature.
+$\DeltaHat$ is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are \emph{strictly} order-preserving.
 The degeneracies then vanish, and we're left with the task of defining gluing conditions solely on the basis of face maps.
 In mathematical literature, there is little interest in studying \DeltaHat, since delta maps are not well-defined, and constructing a $\Set^{\DeltaHat^{op}}$ is inelegant.
-The objective of this paper is to first generalize delta-sets to the cubical setting, and provide a precise mechanically-checked formalization of the same.
 
@@
 
-Let us first motivate the definition of semi-cubical sets, as defined in \cite{Antolini00}.
-On the outset, we might naively attempt to define $\Cube{}$ identically to \DeltaHat, but let us briefly explain why this wouldn't work.
-If there were morphisms from every $\sq{m}$ to $\sq{n}$, we would end up with:
+We might naively attempt to define $\Cube{}$ identically to \DeltaHat, but let us briefly explain why this wouldn't work, motivating the definition of semi-cubical sets as in \cite{Antolini00}.
+If there were morphisms from every $\sq{m}$ to \sq{n}, we would end up with:
 
@@
 
-Here, $\I{n}$ serves the purpose of $\sq{n}$, but this change will cascade into other definitions. In view of defining a category \CSet, we will restrict the morphisms in \Cube{}.
+Here, $\I{n}$ serves the purpose of \sq{n}, but this change will cascade into other definitions. In view of defining a category \CSet, we will restrict the morphisms in \Cube{}.
 
@@
 
-\begin{theorem}[$\CSet$ does not admit degeneracies]
-  This is proved in \cite{Antolini00}.
+\begin{theorem}
+  $\CSet$ does not admit degeneracies.
 \end{theorem}
 
+\begin{proof}
+  The reader is advised to refer to \cite{Antolini00} for the proof.
+\end{proof}
+
 \section{Iterated Grothendieck construction}
-
 The Grothendieck construction provides a correspondence between a fibered representation, and an indexed representation.
@@
 \section{Semi-cubical sets}
-
 In this section, we give the core of the definition of semi-cubical
@@
 \subsection{Truncated semi-cubical sets}
-
 The definition is dispatched over tables \ref{tab:barecubicalsetstructurecore}, \ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}.
@@
 
-\begin{eqntable}{\label{tab:barecubicalsetstructurecore} Definition of a truncated cubical set (main part of the higher-dimensional relation structure)}
+\begin{eqntable}{Definition of a truncated cubical set (main part of the higher-dimensional relation structure)\label{tab:barecubicalsetstructurecore}}
   \mc{Type of truncated cubical sets}
@@
 
-\begin{eqntable}{\label{tab:barecubicalsetstructure} Definition of a truncated cubical set (boxes)}
+\begin{eqntable}{Definition of a truncated cubical set (boxes)\label{tab:barecubicalsetstructure}}
   \mc{Full homogeneous $n$-boxes}
@@
 
-\begin{eqntable}{\label{tab:barecubicalsetfaces} Definition of a homogeneous bare cubical set ($q$-th projection)}
+\begin{eqntable}{Definition of a homogeneous bare cubical set ($q$-th projection)\label{tab:barecubicalsetfaces}}
 
@@
 
-\begin{eqntable}{\label{tab:barecubicalsetcoherences} Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}
+\begin{eqntable}{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)\label{tab:barecubicalsetcoherences}}
 
@@
 
-  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,0}}{D~\unitpoint}{\defeq}{\reflett}{(\unitpoint)}
+  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,0}}{D~\unitpoint}{\defeq}{\reflett(\unitpoint)}
 
@@
 
-\subsection{Derived notions}
-\label{sec:derived-notions}
-
+\subsection{Derived notions\label{sec:derived-notions}}
 On top of the basic definitions on tables \ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}, we can define on tables \ref{tab:macros} and \ref{tab:macroscont} a few other concepts at a more standard level of abstraction.
@@
 
-\begin{eqntable}{\label{tab:barecubicalset} Definition of a bare cubical set (coinductive structure)}
+\begin{eqntable}{Definition of a bare cubical set (coinductive structure)\label{tab:barecubicalset}}
   \mc{Full (non-truncated) cubical sets with degeneracies}
@@
 
-\begin{eqntable}{\label{tab:macros} Standard derived notions}
+\begin{eqntable}{Standard derived notions\label{tab:macros}}
   \mc{Type of full $n$-cubes}
@@
 
-\begin{eqntable}{\label{tab:macroscont} Standard derived notions (continued)}
+\begin{eqntable}{Standard derived notions (continued)\label{tab:macroscont}}
   \mc{$q$-th projection of an $n$-box}
@@
   \bibitem[Rie]{Riehl11}
-  Riehl, E.
-(2011).
-A leisurely introduction to simplicial sets.
-\textit{Unpublished expository article available online at \href{http://www.math.harvard.edu/~eriehl}{http://www.math.harvard.edu/~eriehl}}.
+  Riehl, E. (2011). A leisurely introduction to simplicial sets. \textit{Unpublished expository article available online from the author's web page}.
 

### 2021-09-08 paper/paper.tex
Cubical: mkBox is done! Celebrations!

@@
 \usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
-\usepackage{amsthm, amssymb, amsaddr, fancyhdr, bookmark, fontspec, xargs, multirow, polyglossia, luacode, listings, color, soulutf8, tcolorbox, tabularx, tikz-cd, booktabs, setspace, makecell, caption, floatrow, mathrsfs, xpatch, lmodern}
+\usepackage{amsthm, amssymb, amsaddr, fancyhdr, bookmark, fontspec, xargs, multirow, polyglossia, luacode, minted, color, soulutf8, tcolorbox, tabularx, tikz-cd, booktabs, setspace, makecell, caption, mathrsfs, xpatch, lmodern}
 \usepackage[hmargin=0.4in, vmargin=0.8in, headheight=10pt]{geometry}
@@
 }
-\DeclareFloatFont{small}{\small}
-\floatsetup[table]{capposition=bottom, font=small}
 
@@
 
+% Code listings
+\usemintedstyle{tango}
+
 \title{An iterated Grothendieck construction of semi-cubical types}
@@
 
-\section{Introduction}
-Cubical type theory is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}.
-Several strides in the field have been made since \cite{Bezem14} in constructing a model of type theory for cubical sets, and we present another approach to the construction, with a sound motivation.
-Although our work is motivated by homotopy type theory, construction of the \emph{path type} and \emph{transport} are beyond the scope of our work; we merely formalize semi-cubical sets.
-Our secondary contribution is a mechanically checked proof of our construction in Coq~\footnote{\href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}}.
+\section{Overture}
+Cubical type theory is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}.
+Cubical type theory has several attractive features, and people have been working on it since 2014~\cite{Bezem14}.
+Today, an experimental branch of Agda, known as \emph{Cubical Agda} is being worked on~\cite{Vezzosi21}.
 
-\section{The intutution from \texorpdfstring{\SSet}{simplicial sets}}
+However, there is no known formalization of cubical types in \emph{Coq}, which is a vastly more powerful proof assistant than Agda. Our work lays the foundation for a future Cubical Coq.
+
+\section{The intutution from simplicial sets}
 Simplicial sets are powerful mathematical objects, that form the basis of much of modern homotopy theory.
@@
 
-\subsection{The category of simplicial sets}
+\subsection{\texorpdfstring{\SSet}{The category of simplicial sets}}
 There exists vast mathematical literature on the subject, and we refer the uninitiated reader to \cite{Friedman08} for a gentle introduction with excellent intutions.
@@
 
-\subsection{The motivation for \texorpdfstring{\DeltaHat}{delta sets}}
-
+\subsection{Motivation for \texorpdfstring{\DeltaHat}{delta sets}}
 As hinted earlier, simplicial sets are ill-suited for machine-based representation, due to the infinite number of degenerate simplices that are uninteresting from the point of view of cubical type theory.
@@
 \subsection{Towards semi-cubical sets}
-
 We might naively attempt to define $\Cube{}$ identically to \DeltaHat, but let us briefly explain why this wouldn't work, motivating the definition of semi-cubical sets as in \cite{Antolini00}.
@@
 
-\section{Iterated Grothendieck construction}
+\section{Grothendieck construction}
 The Grothendieck construction provides a correspondence between a fibered representation, and an indexed representation.
@@
 
+\section{The formalization effort}
+\subsection{Converging on an approach}
+The core of our formalization effort demands proof irrelevance for inequalities.
+There were two approaches on the outset: one was HoTT, where we'd have proof relevance, but be able to transport one proof to another, and another was SProp, where we'd get proof irrelevance out-of-the-box.
+We initially experimented with HoTT, but there were serious limitations: HoTT drops the Coq standard library, and several tactics are (unfortunately) reliant on the standard library.
+As a result, several sophisticated tactics are infeasible in HoTT.
+
+SProp comes with a host of bugs and it took us some time to become comfortable with it, and realize its limitations.
+We did go back and forth with SProp a bit, but ended up using it in the final version.
+
+\subsection{Yoneda.v}
+\subsection{RewLemmas.v}
+\subsection{Notes on SProp}
+\subsection{Cubical.v}
+
+We'd tried to build the \texttt{Cubical} as a \texttt{Fixpoint} initially, but ran into unification problems with \texttt{le\_dec}.
+
+Type unification on the term \texttt{D} fails.
+
+\begin{minted}{coq}
+From Coq Require Import Arith.
+
+Theorem le_S_up {n m} (Hnm : n <= m) : n <= S m.
+Admitted.
+Theorem le_S_down {n m} (Hnm : S n <= m) : n <= m.
+Admitted.
+Theorem le_discr {n} : S n <= 0 -> forall {A}, A.
+Admitted.
+Theorem propagate_eq {m n} : m <= S n -> m = S n -> n <= n.
+Admitted.
+Theorem le_dec {n m} : n <= S m -> {n = S m} + {n <= m}.
+Admitted.
+Theorem le_dec' {n m} : n <= m -> {n = m} + {n <= pred m} + {m = O}.
+Admitted.
+Theorem lower_both {m n} : S m <= S n -> m <= n.
+Admitted.
+
+Notation "⇓ p" := (le_S_down p) (at level 40).
+Notation "↑ h" := (le_S_up h) (at level 40).
+Notation "l '.1'" := (projT1 l) (at level 40).
+Notation "l '.2'" := (projT2 l) (at level 40).
+
+Section Cubical.
+
+Universe l'.
+Universe l.
+
+Record Cubical {n : nat} :=
+{
+csp {n'} (Hn' : n' <= n) : Type@{l'} ;
+hd {n'} {Hn' : S n' <= n} : csp Hn' -> csp (⇓ Hn') ;
+box {n' p} {Hn' : n' <= n} (Hp : p <= n') : csp Hn' -> Type@{l} ;
+}.
+
+Fixpoint cubical {n : nat} : Cubical :=
+match n with
+| O => {| csp _ _ := unit;
+hd _ Hn' _ := ltac:(apply (le_discr Hn'));
+box _ _ _ _ _ := unit;
+|}
+| S n => let cn := cubical (n := n) in
+let cspn {n'} (Hn' : n' <= S n) :=
+match le_dec Hn' with
+| left Heq (* n' = S n *) => { D : cn.(csp) (propagate_eq Hn' Heq) &
+cn.(box) _ D -> Type@{l} }
+| right Hineq (* n' <= n *) => cn.(csp) Hineq
+end in
+let hdn {n'} (Hn' : S n' <= S n) :=
+match le_dec' (lower_both Hn') return cspn Hn' (* S n' <= S n *) ->
+cspn (⇓ Hn') (* n' <= S n *) with
+| inleft Hcmp =>
+match Hcmp with
+| left _ (* n' = n *) => fun D => D.1 (* n' = S n *)
+| right _ (* n' <= pred n *) => fun D => cn.(hd) D (* n' <= n *)
+end
+| inright _ (* n = O *) => fun D => cn.(hd) D
+end in
+  {|
+    csp _ Hn' := cspn Hn';
+    hd _ Hn' := hdn Hn';
+    |}
+end.
+
+End Section.
+\end{minted}
+
 \begin{thebibliography}{10}
@@
 
+  \bibitem[CubAgda]{Vezzosi21}
+  Vezzosi, A., Mörtberg, A., \& Abel, A. (2021). Cubical Agda: a dependently typed programming language with univalence and higher inductive types. \textit{Journal of Functional Programming, 31}.
+
   \bibitem[Fri]{Friedman08}
@@
 
-  \bibitem[Ant]{Antolini00}
+  \bibitem[CubSet]{Antolini00}
   Antolini, R. (2000). Cubical structures, homotopy theory. \textit{Annali di Matematica pura ed applicata, 178}(1), 317-324.
@@
 
+\appendix
+\section{Source code listing}
+
 \end{document}

### 2021-09-08 paper/paper.tex
paper: More notes on formalization; arrows not rendering in minted

@@
 % The eqntable environment, displaying the various
-\NewDocumentEnvironment{eqntable}{m}{\table[!ht]
+\NewDocumentEnvironment{eqntable}{m}{\table[!ht]\small
 \tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
-{\endtabularx\hrule\caption{#1}\endtable}
+{\endtabularx\vspace{0.3em}\hrule\vspace{0.5em}\caption{#1}\endtable}
 
@@
 \begin{abstract}
-  A fresh approach to formalizing semi-cubical sets in dependent type theory with extensional equality.
-The approach could be described as a \emph{reverse iterated Grothendieck construction}, that is crisp and concise.
+  A proposed model of \emph{homotopy type theory} built via a \emph{reverse iterated Grothendieck construction} process formalizing semi-cubical sets in dependent type theory with \emph{extensional equality}.
 The accompanying artifact is a Coq formalization that uses highly sophisticated rewriting techniques and pushes the boundary of proof assistant technology.
@@
 \section{Overture}
-Cubical type theory is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}.
+Cubical type theory is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT.
 Cubical type theory has several attractive features, and people have been working on it since 2014~\cite{Bezem14}.
@@
 
-However, there is no known formalization of cubical types in \emph{Coq}, which is a vastly more powerful proof assistant than Agda. Our work lays the foundation for a future Cubical Coq.
+Our contribution takes a different direction from traditional contributions to the field of HoTT: although it is a proposed model of HoTT, it uses \emph{unicity of identity proofs} (UIP) instead of univalence to finish off the final coherence condition; the two axoims are mutually incompatible.
 
-\section{The intutution from simplicial sets}
+\section{The intuition from simplicial sets}
 Simplicial sets are powerful mathematical objects, that form the basis of much of modern homotopy theory.
@@
 \section{The formalization effort}
-\subsection{Converging on an approach}
-The core of our formalization effort demands proof irrelevance for inequalities.
-There were two approaches on the outset: one was HoTT, where we'd have proof relevance, but be able to transport one proof to another, and another was SProp, where we'd get proof irrelevance out-of-the-box.
-We initially experimented with HoTT, but there were serious limitations: HoTT drops the Coq standard library, and several tactics are (unfortunately) reliant on the standard library.
-As a result, several sophisticated tactics are infeasible in HoTT.
+The core of our formalization effort demanded proof irrelevance for inequalities: \mintinline{coq}{SProp} was the natural choice.
 
-SProp comes with a host of bugs and it took us some time to become comfortable with it, and realize its limitations.
-We did go back and forth with SProp a bit, but ended up using it in the final version.
+\subsection{\texorpdfstring{\leq}{<=} in SProp}
+We start with one inequality primitive, namely $\leq$, and build up all our inequalities on the basis of that inequality.
+We tried three different approaches to defining $\leq$ in \mintinline{coq}{SProp}.
 
+\begin{enumerate}
+  \item[(a)] An inductive definition.
+    \begin{listing}[H]
+      \begin{minted}{coq}
+      Inductive le' (n : nat) : nat -> SProp :=
+      | le_refl : n <= n
+      | le_S_up : forall {m : nat}, n <= m -> n <= S m
+      where "n <= m" := (le' n m) : nat_scope.
+
+    Definition le := le'.
+    \end{minted}
+    \end{listing}
+  \item[(b)] A recursive definition.
+    \begin{listing}[H]
+      \begin{minted}{coq}
+      Inductive sFalse : SProp :=.
+      Inductive sTrue : SProp := sI.
+
+      Fixpoint le m n : SProp :=
+        match m with
+        | 0 => sTrue
+        | S m =>
+          match n with
+          | 0 => sFalse
+          | S n => le m n
+          end
+        end.
+     \end{minted}
+    \end{listing}
+  \item[(c)] An nested implication.
+    \begin{listing}[H]
+      \begin{minted}{coq}
+      Inductive le' (n : nat) : nat -> SProp :=
+        | le_refl' : n <= n
+        | le_S_up' : forall (m : nat), n <= m -> n <= S m
+        where "n <= m" := (le' n m) : nat_scope.
+
+      Definition le n m := forall p, p <= n -> p <= m.
+      \end{minted}
+    \end{listing}
+\end{enumerate}
+
+(b) was unworkable right from the start, and we tried approach (a) for a while, before settling on approach (c), because it made compositions of inequalities almost trivial to prove.
+Compare the following snippets defining transitivity of $\leq$:
+
+\begin{listing}[H]
+  \begin{minted}[linenos]{coq}
+    Theorem le_trans {p q n} : p <= q -> q <= n -> p <= n.
+    (* ... a non-trivial proof ... *)
+    Defined.
+  \end{minted}
+  \caption{↕ definition, when $\leq$ is defined using an inductive approach}
+\end{listing}
+
+\begin{listing}[H]
+  \begin{minted}[linenos]{coq}
+    Definition le_trans {n m p} (Hnm : n <= m) (Hmp : m <= p) : n <= p :=
+      fun q (Hqn : le' q n) => Hmp _ (Hnm _ Hqn).
+  \end{minted}
+  \caption{↕ definition, when $\leq$ is defined using a nested implication}
+\end{listing}
+
+Implications are naturally easier to work with, so the nested implication in \mintinline{coq}{SProp} was an easy choice. Many of the commutativity proofs were a simple \mintinline{coq}{reflexivity}:
+
+\begin{listing}[H]
+  \begin{minted}{coq}
+  Theorem le_trans_comm4 {n m p} (Hmn : S n <= S m) (Hmp : S m <= S p) :
+  ⇓ (Hmn ↕ Hmp) =S (⇓ Hmn) ↕ (⇓ Hmp).
+    reflexivity.
+  Defined.
+  \end{minted}
+\end{listing}
+
+\subsection{Raising and lowering operations on \texorpdfstring{\leq}{<=}}
+\mint{coq}/Notation "↕" := (Hnm : n <= m) (Hmp : m <= p) : n <= p/
+\mint{coq}/Notation "↑" := (Hnm : n <= m) : n <= S m/
+\mint{coq}/Notation "↓" := (Hnm : S n <= m) : n <= m/
+\mint{coq}/Notation "⇓" := (Hnm : S n <= S m) : n <= m/
+\mint{coq}/Notation "⇑" := (Hnm : n <= m) : S n <= S m/
 \subsection{Yoneda.v}
@@
 
-We'd tried to build the \texttt{Cubical} as a \texttt{Fixpoint} initially, but ran into unification problems with \texttt{le\_dec}.
+We'd tried to build the \mintinline{coq}{Cubical} as a \mintinline{coq}{Fixpoint} initially, but ran into unification problems with \mintinline{coq}{le_dec}.
 
-Type unification on the term \texttt{D} fails.
+Type unification on the term \mintinline{coq}{D} fails.
 
-\begin{minted}{coq}
-From Coq Require Import Arith.
-
-Theorem le_S_up {n m} (Hnm : n <= m) : n <= S m.
-Admitted.
-Theorem le_S_down {n m} (Hnm : S n <= m) : n <= m.
-Admitted.
-Theorem le_discr {n} : S n <= 0 -> forall {A}, A.
-Admitted.
-Theorem propagate_eq {m n} : m <= S n -> m = S n -> n <= n.
-Admitted.
+\begin{listing}[H]
+  \begin{minted}[linenos]{coq}
     Theorem le_dec {n m} : n <= S m -> {n = S m} + {n <= m}.
@@
     Admitted.
-Theorem lower_both {m n} : S m <= S n -> m <= n.
-Admitted.
-
-Notation "⇓ p" := (le_S_down p) (at level 40).
-Notation "↑ h" := (le_S_up h) (at level 40).
-Notation "l '.1'" := (projT1 l) (at level 40).
-Notation "l '.2'" := (projT2 l) (at level 40).
-
-Section Cubical.
-
-Universe l'.
-Universe l.
-
-Record Cubical {n : nat} :=
-{
-csp {n'} (Hn' : n' <= n) : Type@{l'} ;
-hd {n'} {Hn' : S n' <= n} : csp Hn' -> csp (⇓ Hn') ;
-box {n' p} {Hn' : n' <= n} (Hp : p <= n') : csp Hn' -> Type@{l} ;
-}.
-
-Fixpoint cubical {n : nat} : Cubical :=
-match n with
-| O => {| csp _ _ := unit;
-hd _ Hn' _ := ltac:(apply (le_discr Hn'));
-box _ _ _ _ _ := unit;
-|}
-| S n => let cn := cubical (n := n) in
-let cspn {n'} (Hn' : n' <= S n) :=
-match le_dec Hn' with
-| left Heq (* n' = S n *) => { D : cn.(csp) (propagate_eq Hn' Heq) &
-cn.(box) _ D -> Type@{l} }
-| right Hineq (* n' <= n *) => cn.(csp) Hineq
-end in
+    (* ... *)
     let hdn {n'} (Hn' : S n' <= S n) :=
@@
     end
-| inright _ (* n = O *) => fun D => cn.(hd) D
-end in
-  {|
-    csp _ Hn' := cspn Hn';
-    hd _ Hn' := hdn Hn';
-    |}
-end.
-
-End Section.
+    (* ... *)
     \end{minted}
+\end{listing}
 

### 2021-10-25 paper/paper.tex
[Cubical] Start with mkCube
[paper] Whiteboarding with Hugo

@@
 \usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
-\usepackage{amsthm, amssymb, amsaddr, fancyhdr, bookmark, fontspec, xargs, multirow, polyglossia, luacode, minted, color, soulutf8, tcolorbox, tabularx, tikz-cd, booktabs, setspace, makecell, caption, mathrsfs, xpatch, lmodern}
+\usepackage{amsthm, amssymb, amsmath, mathtools, amsaddr, fancyhdr, bookmark, fontspec, xargs, multirow, polyglossia, luacode, minted, color, soulutf8, tcolorbox, tabularx, tikz-cd, booktabs, setspace, makecell, caption, mathrsfs, xpatch, lmodern}
 \usepackage[hmargin=0.4in, vmargin=0.8in, headheight=10pt]{geometry}
@@
 
-% Universes
+% Universes, obj, mor
 \newcommand{\sort}[1]{\ensuremath{\mathsf{U}_{#1}}}
@@
 
+% Objects and morphisms
+\newcommand{\obj}{\ensuremath{\mathsf{obj}}}
+\newcommand{\mor}{\ensuremath{\mathsf{mor}}}
+
 % Simplicial sets
@@
 \usemintedstyle{tango}
+\setminted{escapeinside=~~}
+\setmintedinline{escapeinside=~~}
+
+% Fonts
+\setmainfont{Avenir Next}
+\setmonofont{Source Code Pro}
+\newfontfamily\mainfont{Avenir Next}
+\newfontfamily\caslon{Adobe Caslon Pro}
+\defaultfontfeatures{Ligatures=TeX, Scale=MatchUppercase}
 
 \title{An iterated Grothendieck construction of semi-cubical types}
+\author{Hugo Herbelin}
+\address{Institut de Recherche en Informatique Fondamentale}
 \author{Ramkumar Ramachandra}
 \address{Université de Paris}
-\author{Hugo Herbelin}
-\address{Institut de Recherche en Informatique Fondamentale}
 
@@
 
-Our contribution takes a different direction from traditional contributions to the field of HoTT: although it is a proposed model of HoTT, it uses \emph{unicity of identity proofs} (UIP) instead of univalence to finish off the final coherence condition; the two axoims are mutually incompatible.
+Our contribution uses the indexed approach to constructing semi-cubical types, as opposed to CCHM~\cite{Cohen16} in 2016, which takes a fibered approach.
+We will expound on this further in the Grothendieck construction section.
+We also use \emph{unicity of identity of proofs} (UIP) to finish off the last coherence condition, and we have dedicated a section to discussing it in various settings.
+
+\begin{table}[H]
+  \begin{tabularx}{\linewidth}{p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}}
+    \toprule
+            & Set theory & Type theory \\
+    \midrule
+    Fibered & CCHM       &             \\
+    \midrule
+    Indexed &            & Our work    \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
 
@@
   \begin{align*}
-    obj(\Simplex{}) & := \sq{n}, \text{regarded as a totally-ordered set}   \\
-    mor(\Simplex{}) & := \sq{m} \rightarrow \sq{n}, \text{order-preserving}
+    \obj(\Simplex{}) & := \sq{n}, \text{regarded as a totally-ordered set}   \\
+    \mor(\Simplex{}) & := \sq{m} \rightarrow \sq{n}, \text{order-preserving}
   \end{align*}
@@
   \begin{align*}
-    obj(\SSet)             & := \text{functors} \; \Simplex{}^\op \rightarrow \Set      \\
-    mor(\SSet)             & := \text{natural transforms between the functors}          \\
+    \obj(\SSet)            & := \text{functors} \; \Simplex{}^\op \rightarrow \Set      \\
+    \mor(\SSet)            & := \text{natural transforms between the functors}          \\
     \text{composition law} & := \text{the usual composition of natural transformations} \\
@@
   \begin{align*}
-    obj(\Cube{}) & := \I{n}                                           \\
-    mor(\Cube{}) & := \delta^\epsilon_i : \I{n + 1} \rightarrow \I{n}
+    \obj(\Cube{}) & := \I{n}                                           \\
+    \mor(\Cube{}) & := \delta^\epsilon_i : \I{n + 1} \rightarrow \I{n}
   \end{align*}
@@
   \begin{align*}
-    obj(\CSet) & := X_n                                                   \\
-    mor(\CSet) & := X_\lambda, \text{where $\lambda$ is \Cube{}-morphism}
+    \obj(\CSet) & := X_n                                                   \\
+    \mor(\CSet) & := X_\lambda, \text{where \lambda is \Cube{}-morphism}
   \end{align*}
@@
 \end{align*}
+
+\section{Unicity of identity proofs}
+We dedicate this section to discussing UIP in different settings, and supply intuitions into this notion.
+
+UIP is a flavor of proof-irrelevance:
+
+\begin{align*}
+  \forall x y, \forall p q : x = y, p = q
+\end{align*}
+
+which is to say that any two proofs of \emph{equality} of the same two types are \emph{equal}. In other words, the proofs cannot be distinguished from one another.
+
+Proof irrelevance is an inherent part of set theory and first-order logic, although the property cannot be stated in the language of natural deductions.
+Intuititively, what it means is that a tree of deductions converges to a result, with no memory of the proof route; the tree itself is forgotten once the final result is obtained.
+
+One way of formalising set theory in type theory is via Aczel sets [ref]. It can be written down as an inductive as follows:
+
+\begin{listing}[H]
+  \begin{minted}[mathescape]{coq}
+    Inductive SET : Type :=
+      node : \forall A : Type, (A -> SET) -> SET
+      ~$=_\textrm{SET}$~ : ...
+  \end{minted}
+\end{listing}
+
+[draw tree structure of set]
+
+Then, proof irrelevance can be stated as:
+
+\begin{align*}
+  \forall x y, \forall p q : x =_{\textrm{SET}} y, p = q
+\end{align*}
+
+We use UIP in the final coherence condition in \mintinline{coq}{cohbox} and \mintinline{coq}{cohcube}. If we weren't to use UIP in \mintinline{coq}{cohbox}, then we'd have something similar to:
+
+\begin{listing}[H]
+  \begin{minted}{coq}
+    cohbox : subbox ( subbox ... ) = subbox ( subbox ... )
+    coh2box : cohbox ... = cohbox ...
+    ...
+    cohNbox : cohPredNbox ... = cohPredNbox ...
+  \end{minted}
+\end{listing}
+
+In attempting to write the proof without UIP, we'd have a relation between \mintinline{coq}{cohNbox} and \mintinline{coq}{cohPredNbox}, which would be very difficult to prove.
 
@@
   \end{minted}
-  \caption{↕ definition, when $\leq$ is defined using an inductive approach}
+  \caption{when $\leq$ is defined using an inductive approach}
 \end{listing}
@@
   \end{minted}
-  \caption{↕ definition, when $\leq$ is defined using a nested implication}
+  \caption{when $\leq$ is defined using a nested implication}
 \end{listing}
@@
   Theorem le_trans_comm4 {n m p} (Hmn : S n <= S m) (Hmp : S m <= S p) :
-  ⇓ (Hmn ↕ Hmp) =S (⇓ Hmn) ↕ (⇓ Hmp).
+  ~⇓~ (Hmn ~↕~ Hmp) =S (~⇓~ Hmn) ~↕~ (~⇓~ Hmp).
     reflexivity.
@@
 \subsection{Raising and lowering operations on \texorpdfstring{\leq}{<=}}
-\mint{coq}/Notation "↕" := (Hnm : n <= m) (Hmp : m <= p) : n <= p/
-\mint{coq}/Notation "↑" := (Hnm : n <= m) : n <= S m/
-\mint{coq}/Notation "↓" := (Hnm : S n <= m) : n <= m/
-\mint{coq}/Notation "⇓" := (Hnm : S n <= S m) : n <= m/
-\mint{coq}/Notation "⇑" := (Hnm : n <= m) : S n <= S m/
+\mint{coq}/~↕~ := (Hnm : n <= m) (Hmp : m <= p) : n <= p/
+\mint{coq}/~↑~ := (Hnm : n <= m) : n <= S m/
+\mint{coq}/~↓~ := (Hnm : S n <= m) : n <= m/
+\mint{coq}/~⇓~ := (Hnm : S n <= S m) : n <= m/
+\mint{coq}/~⇑~ := (Hnm : n <= m) : S n <= S m/
 \subsection{Yoneda.v}
@@
 
+  \bibitem[CohCoq]{Cohen16}
+  Cohen, C., Coquand, T., Huber, S., \& Mörtberg, A. (2016). Cubical type theory: a constructive interpretation of the univalence axiom. arXiv preprint arXiv:1611.02108.
+
   \bibitem[Fri]{Friedman08}
@@
   Herbelin, H. (2015). A dependently-typed construction of semi-simplicial types. \textit{Mathematical Structures in Computer Science, 25}(5), 1116-1131.
+
+  \bibitem[CoqInCoq]{Barras97}
+  Barras, B., \& Werner, B. (1997). Coq in coq. \textit{Available on the WWW.}
 \end{thebibliography}

### 2021-10-26 paper/paper.tex
[paper] Overture

@@
 
-% The eqntable environment, displaying the various
-\NewDocumentEnvironment{eqntable}{m}{\table[!ht]\small
-\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
-{\endtabularx\vspace{0.3em}\hrule\vspace{0.5em}\caption{#1}\endtable}
-
-% A block in the eqntable environment
-\newcommand{\eqnline}[4]{$#1$ & $#2$ & $#3$ & $#4$ \\}
-\newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}
-
-% Table caption set up
-\DeclareCaptionFormat{hfillstart}{\hfill#1#2#3\par}
-\DeclareCaptionFont{mdit}{\mdseries\itshape}
-\captionsetup[table]{
-  justification=centering,
-  font=bf,
-  labelfont=mdit,
-}
-
-% Lettered footnotes
-\renewcommand{\thefootnote}{\alph{footnote}}
-
-% Theorems
-\newtheorem{notation}{Notation}
-\newtheorem{definition}{Definition}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{theorem}{Theorem}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
-
 % Objects and morphisms
@@
 
-% Roman numerals for chapters
-\renewcommand{\thesection}{\Roman{section}}
+% The eqntable environment, displaying the various
+\NewDocumentEnvironment{eqntable}{m}{\table[!ht]\small
+\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
+{\endtabularx\vspace{0.3em}\hrule\vspace{0.5em}\caption{#1}\endtable}
+
+% A block in the eqntable environment
+\newcommand{\eqnline}[4]{$#1$ & $#2$ & $#3$ & $#4$ \\}
+\newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}
+
+% Table caption set up
+\DeclareCaptionFormat{hfillstart}{\hfill#1#2#3\par}
+\DeclareCaptionFont{mdit}{\mdseries\itshape}
+\captionsetup[table]{
+  justification=centering,
+  font=bf,
+  labelfont=mdit,
+}
+
+% Use lettered footnotes
+\renewcommand{\thefootnote}{\alph{footnote}}
+
+% amsthm theorems
+\swapnumbers
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{terminology}[definition]{Terminology}
+\newtheorem{notation}[definition]{Notation}
+\newtheorem{proposition}[definition]{Proposition}
+\newtheorem{lemma}[definition]{Lemma}
+\newtheorem{theorem}[definition]{Theorem}
+\newtheorem{corollary}[definition]{Corollary}
+\newtheorem{remark}[definition]{Remark}
+\newtheorem{example}[definition]{Example}
+\newtheorem{caution}[definition]{Caution}
+\newtheorem{discussion}[definition]{Discussion}
+
+\usepackage{thmtools}
 
@@
 
+% Fancy headers
+\pagestyle{fancy} % choose the "fancy" pagestyle
+\fancyhf{}        % clear all headers and footers
+% Now set the headers
+\fancyhead[LE,RO]{\footnotesize\thepage}
+\fancyhead[LO,RE]{\footnotesize\leftmark}
+\makeatletter
+\xapptocmd{\@sect}{\csname #1mark\endcsname{#7}}{}{}
+\makeatother
+
+% Subsection centering
+\makeatletter
+\def\subsection{\@startsection{subsection}{2}
+  \z@{.5\linespacing\@plus.7\linespacing}{.6\baselineskip}{\centering}}
+\makeatother
+
 % Code listings
@@
 \newfontfamily\mainfont{Avenir Next}
-\newfontfamily\caslon{Adobe Caslon Pro}
 \defaultfontfeatures{Ligatures=TeX, Scale=MatchUppercase}
@@
 \section{Overture}
-Cubical type theory is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT.
-Cubical type theory has several attractive features, and people have been working on it since 2014~\cite{Bezem14}.
-Today, an experimental branch of Agda, known as \emph{Cubical Agda} is being worked on~\cite{Vezzosi21}.
+Cubical type theory~\cite{Bezem14}~\cite{Cohen16}~\cite{Angiuli17} is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT.
+Two real-world projects that implement cubical type theory are worthy of mention: an experimental branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}, and the Arend theorem prover~\footnote{\href{https://arend-lang.github.io}{arend-lang.github.io}}.
+Cubical type theory is usually modeled as cubical sets, in the set-theoretic setting.
+Efforts to model cubical type theory have been ongoing since 2014, and many of these efforts are in the set-theoretic setting.
 
-Our contribution uses the indexed approach to constructing semi-cubical types, as opposed to CCHM~\cite{Cohen16} in 2016, which takes a fibered approach.
-We will expound on this further in the Grothendieck construction section.
-We also use \emph{unicity of identity of proofs} (UIP) to finish off the last coherence condition, and we have dedicated a section to discussing it in various settings.
+Our contribution is to model the core of cubical types, semi-cubical sets, in type theory, using an indexed representation, in contrast to previous efforts that use a fibered representation.
+We use an \emph{iterated reverse-Grothendieck} construction as the basis of our formalization, which we expound on in \ref{sec:grothendieckconstr}.
+Another feature of our work is that, as we are in the type-theoretic setting, we use \emph{unicity of identity of proofs} (UIP), which would be an inherent property in the set-theoretic setting (see \ref{sec:uip}).
 
@@
     \obj(\CSet) & := X_n                                                   \\
-    \mor(\CSet) & := X_\lambda, \text{where \lambda is \Cube{}-morphism}
+    \mor(\CSet) & := X_\lambda, \text{where $\lambda$ is \Cube{}-morphism}
   \end{align*}
@@
 
-\section{Grothendieck construction}
+\section{Grothendieck construction\label{sec:grothendieckconstr}}
 The Grothendieck construction provides a correspondence between a fibered representation, and an indexed representation.
@@
 
-\section{Unicity of identity proofs}
+\section{Unicity of identity proofs\label{sec:uip}}
 We dedicate this section to discussing UIP in different settings, and supply intuitions into this notion.
@@
     Inductive SET : Type :=
-      node : \forall A : Type, (A -> SET) -> SET
+      node : ~$\forall$~A : Type, (A -> SET) -> SET
       ~$=_\textrm{SET}$~ : ...
@@
 
-[draw tree structure of set]
+The special case of \mintinline{coq}{(Bool -> SET) -> SET} can be drawn as:
+
+\begin{equation*}
+  \begin{tikzcd}
+    & & \{0, 1, 2\} \arrow[dr]\arrow[dl] & \\
+    & \{0, 1\} \arrow[dl]\arrow[dr] & & \{2\} \\
+    \{0\} & & \{1\} & \\
+  \end{tikzcd}
+\end{equation*}
+
+In general, \mintinline{coq}{SET} can have an $n$-ary branching structure, splitting out the various subsets until we get to the leaves.
 
@@
 
-In attempting to write the proof without UIP, we'd have a relation between \mintinline{coq}{cohNbox} and \mintinline{coq}{cohPredNbox}, which would be very difficult to prove.
+In attempting to write the proof without UIP, we'd have a relation between \mintinline{coq}{cohNbox} and \mintinline{coq}{cohPredNbox}, which, we expect to be tricky to prove.
 
@@
 
+  \bibitem[Angiuli]{Angiuli17}
+  Carlo Angiuli, Guillaume Brunerie, Thierry Coquand, Kuen-Bang Hou (Favonia),Robert Harper, \& Daniel R. Licata. arXiv preprint.
+
   \bibitem[Fri]{Friedman08}

### 2021-11-02 paper/paper.tex
[Cubical] Redo mkCube with different induction
[paper] Notes on the formalization

@@
 
-The special case of \mintinline{coq}{(Bool -> SET) -> SET} can be drawn as:
+\mintinline{coq}{(A -> SET) -> SET} can be drawn as:
 
 \begin{equation*}
+  \begin{tikzcd}
+    \{0\} \arrow[dr] & \\
+    & \{\} \\
+  \end{tikzcd}
+  \begin{tikzcd}
+    & \{0, 1\} \arrow[dr]\arrow[dl] & \\
+    \{0\} & & \{1\} \\
+  \end{tikzcd}
   \begin{tikzcd}
@@
 \end{align*}
-
-We use UIP in the final coherence condition in \mintinline{coq}{cohbox} and \mintinline{coq}{cohcube}. If we weren't to use UIP in \mintinline{coq}{cohbox}, then we'd have something similar to:
-
-\begin{listing}[H]
-  \begin{minted}{coq}
-    cohbox : subbox ( subbox ... ) = subbox ( subbox ... )
-    coh2box : cohbox ... = cohbox ...
-    ...
-    cohNbox : cohPredNbox ... = cohPredNbox ...
-  \end{minted}
-\end{listing}
-
-In attempting to write the proof without UIP, we'd have a relation between \mintinline{coq}{cohNbox} and \mintinline{coq}{cohPredNbox}, which, we expect to be tricky to prove.
 
@@
 
-  \eqnline{\mycube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{E.\mathsf{rel}(d)}
+  \eqnline{\mycube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{E(d)}
 
@@
 
-\section{The formalization effort}
-The core of our formalization effort demanded proof irrelevance for inequalities: \mintinline{coq}{SProp} was the natural choice.
+\section{Notes on the formalization}
+The core of our formalization effort consists of inequalities in \emph{Peano arithmetic}.
+We start with one inequality primitive, namely $\leq$, and build up all our inequalities on the basis of that inequality.
+Two different proofs of \mintinline{coq}{p <= q} must be the same: we chose to use \mintinline{coq}{SProp} for the proof irrelevance.
+
+\subsection{Notations in \texorpdfstring{\leq}{<=}}
+On the outset, we defined various \emph{raising}, \emph{lowering}, and \emph{composition} operations on $\leq$:
+
+\mint{coq}/~↑~ := (Hnm : n <= m) : n <= S m/
+\mint{coq}/~⇑~ := (Hnm : n <= m) : S n <= S m/
+\mint{coq}/~↓~ := (Hnm : S n <= m) : n <= m/
+\mint{coq}/~⇓~ := (Hnm : S n <= S m) : n <= m/
+\mint{coq}/~↕~ := (Hnm : n <= m) (Hmp : m <= p) : n <= p/
+
+\subsection{An SProp primer}
+\mintinline{coq}{SProp} is a replacement for standard propositions, or \mintinline{coq}{Prop}, that provides proof irrelevance.
+
+There are three inhabitants of \mintinline{coq}{SProp}: \mintinline{coq}{sUnit} corresponding to $\top$, \mintinline{coq}{sEmpty} corresponding to $\bot$, and \mintinline{coq}{sProposition} corresponding to a definitionally proof-irrelevant term.
+The way \mintinline{coq}{SProp} implements definitional proof-irrelevance is a simple engineering detail: there is hard-coding in Coq to render two inhabitants of \mintinline{coq}{sProposition} trivially inter-convertible.
+
+\begin{listing}[H]
+  \begin{minted}{coq}
+    Theorem SPropIrr (P : SProp) (x y : P) : x = y.
+    Proof.
+      by reflexivity.
+    Abort. (* Type-check fails at Qed.
+            * (=) : ∀ A, A -> A -> Prop, but we want to return an SProp.
+            *)
+  \end{minted}
+\end{listing}
+
+We can, however, define an \mintinline{coq}{=S} that returns an \mintinline{coq}{SProp}:
+
+\begin{listing}[H]
+  \begin{minted}{coq}
+    Inductive eqsprop {A : SProp} (x : A) : A -> Prop := eqsprop_refl : eqsprop x x.
+    Infix "=S" := eqsprop (at level 70) : type_scope.
+  \end{minted}
+\end{listing}
 
 \subsection{\texorpdfstring{\leq}{<=} in SProp}
-We start with one inequality primitive, namely $\leq$, and build up all our inequalities on the basis of that inequality.
 We tried three different approaches to defining $\leq$ in \mintinline{coq}{SProp}.
@@
 \begin{enumerate}
-  \item[(a)] An inductive definition.
-    \begin{listing}[H]
-      \begin{minted}{coq}
-      Inductive le' (n : nat) : nat -> SProp :=
-      | le_refl : n <= n
-      | le_S_up : forall {m : nat}, n <= m -> n <= S m
-      where "n <= m" := (le' n m) : nat_scope.
-
-    Definition le := le'.
-    \end{minted}
-    \end{listing}
-  \item[(b)] A recursive definition.
+  \item[(a)] A recursive definition.
     \begin{listing}[H]
@@
     \end{listing}
-  \item[(c)] An nested implication.
+  \item[(b)] An inductive definition.
     \begin{listing}[H]
@@
       Inductive le' (n : nat) : nat -> SProp :=
-        | le_refl' : n <= n
-        | le_S_up' : forall (m : nat), n <= m -> n <= S m
+      | le_refl : n <= n
+      | le_S_up : forall {m : nat}, n <= m -> n <= S m
       where "n <= m" := (le' n m) : nat_scope.
 
+    Definition le := le'.
+    \end{minted}
+    \end{listing}
+  \item[(c)] A refinement of the inductive definition; a nested implication.
+    \begin{listing}[H]
+      \begin{minted}{coq}
       Definition le n m := forall p, p <= n -> p <= m.
@@
 
-(b) was unworkable right from the start, and we tried approach (a) for a while, before settling on approach (c), because it made compositions of inequalities almost trivial to prove.
+(a) was unworkable right from the start, and we tried approach (b) for a while, before running into unification problems.
+We then settled on approach (c), because it made compositions of inequalities almost trivial to prove.
 Compare the following snippets defining transitivity of $\leq$:
@@
   \end{minted}
-  \caption{when $\leq$ is defined using an inductive approach}
+  \caption{\mintinline{coq}{le_trans} when $\leq$ is defined using an inductive approach}
 \end{listing}
@@
   \end{minted}
-  \caption{when $\leq$ is defined using a nested implication}
+  \caption{\mintinline{coq}{le_trans} when $\leq$ is defined using a nested implication}
 \end{listing}
 
-Implications are naturally easier to work with, so the nested implication in \mintinline{coq}{SProp} was an easy choice. Many of the commutativity proofs were a simple \mintinline{coq}{reflexivity}:
+Implications are naturally easier to work with, so the nested implication in \mintinline{coq}{SProp} was an easy choice.
+Many of the associtivity and commutativity proofs are then a simple \mintinline{coq}{reflexivity}:
 
@@
 
-\subsection{Raising and lowering operations on \texorpdfstring{\leq}{<=}}
-\mint{coq}/~↕~ := (Hnm : n <= m) (Hmp : m <= p) : n <= p/
-\mint{coq}/~↑~ := (Hnm : n <= m) : n <= S m/
-\mint{coq}/~↓~ := (Hnm : S n <= m) : n <= m/
-\mint{coq}/~⇓~ := (Hnm : S n <= S m) : n <= m/
-\mint{coq}/~⇑~ := (Hnm : n <= m) : S n <= S m/
-\subsection{Yoneda.v}
-\subsection{RewLemmas.v}
-\subsection{Notes on SProp}
-\subsection{Cubical.v}
+\subsection{The Fibonacci trick}
+We'd initially defined \mintinline{coq}{Cubical} in a monolithic manner, and attempted to use \emph{well-founded induction} to build it up in steps.
+Induction is the process of successively building up a type by reasoning on the result of the previous iteration, and well-founded induction remembers all the previous levels.
+A simple induction is clearly insufficient for our purposes, and as it turned out, well-founded induction was a non-starter too.
 
-We'd tried to build the \mintinline{coq}{Cubical} as a \mintinline{coq}{Fixpoint} initially, but ran into unification problems with \mintinline{coq}{le_dec}.
+Our initial \mintinline{coq}{Record} looked like:
 
-Type unification on the term \mintinline{coq}{D} fails.
+\begin{listing}[H]
+  \begin{minted}{coq}
+    Record Cubical {n : nat} :=
+    {
+    csp {n'} (Hn' : n' <= n) : Type@{l'} ;
+    hd {n'} {Hn' : S n' <= n} : csp Hn' -> csp (⇓ Hn') ;
+    box {n' p} {Hn' : n' <= n} (Hp : p <= n') : csp Hn' -> Type@{l} ;
+    tl {n'} {Hn' : S n' <= n} (D : csp Hn') :
+      box (le_refl n') (hd D) -> Type@{l} ;
+    (* ... *)
+    }.
+  \end{minted}
+\end{listing}
+
+To build it up in steps, we defined a \mintinline{coq}{Fixpoint} as follows, but ran into unification problems:
 
@@
   \begin{minted}[linenos]{coq}
-    Theorem le_dec {n m} : n <= S m -> {n = S m} + {n <= m}.
+    Theorem le_dec {n m} : n <= m -> {n = m} + {n <= pred m} + {m = O}.
     Admitted.
-    Theorem le_dec' {n m} : n <= m -> {n = m} + {n <= pred m} + {m = O}.
+    Theorem lower_both {m n} : S m <= S n -> m <= n.
     Admitted.
+
     (* ... *)
+
+    Fixpoint cubical {n : nat} : Cubical :=
+    match n with
+    | O => {|
+      csp _ _ := unit;
+      hd _ Hn' _ := ltac:(apply (le_discr Hn'));
+      box _ _ _ _ _ := unit;
+      tl _ Hn' _ _ := ltac:(apply (le_discr Hn'));
+      (* ... *)
+      |}
+    | S n => let cn := cubical (n := n) in
+
+    (* ... *)
+
     let hdn {n'} (Hn' : S n' <= S n) :=
-    match le_dec' (lower_both Hn') return cspn Hn' (* S n' <= S n *) ->
+    match le_dec (lower_both Hn') return cspn Hn' (* S n' <= S n *) ->
     cspn (⇓ Hn') (* n' <= S n *) with
@@
     end
-    (* ... *)
+    \end{minted}
+  \caption{Type unification on the term \mintinline{coq}{D} fails}
+\end{listing}
+
+We then settled on remembering the previous two levels of induction, a middle-ground between plain induction and well-founded recursion, which we refer to as the Fibonacci trick.
+Our final \mintinline{coq}{Record} for the box looks like:
+
+\begin{listing}[H]
+  \begin{minted}{coq}
+    (* PartialBox consists of an 0-cells, and fillers which are the 1-cells,
+    2-cells, and 3-cells relating the different 0-cells on the cube  *)
+    Record PartialBoxBase (n : nat) (csp : Type@{l'}) := {
+      box' {p} (Hp : p.+1 <= n) : csp -> Type@{l} ;
+      (* [box' n D] is [box (n-1) D.1] *)
+      box'' {p} (Hp : p.+2 <= n) : csp -> Type@{l} ;
+      subbox' {p q} {Hp : p.+2 <= q.+2} (Hq : q.+2 <= n) (ε : side) {D : csp} :
+        box' (↓ (Hp ↕ Hq)) D -> box'' (Hp ↕ Hq) D;
+    }.
+
+    Record PartialBox (n p : nat) (csp : Type@{l'})
+    (PB : PartialBoxBase n csp) := {
+      box (Hp : p <= n) : csp -> Type@{l} ;
+      subbox {q} {Hp : p.+1 <= q.+1} (Hq : q.+1 <= n) (ε : side) {D : csp} :
+      box (↓ (Hp ↕ Hq)) D -> PB.(box') (Hp ↕ Hq) D;
+      cohbox {q r} {Hpr : p.+2 <= r.+2} {Hr : r.+2 <= q.+2} {Hq : q.+2 <= n}
+      {ε : side} {ω : side} {D: csp} (d : box (↓ (⇓ Hpr ↕ (↓ (Hr ↕ Hq)))) D) :
+      PB.(subbox') (Hp := Hpr ↕ Hr) Hq ε (subbox (Hp := ⇓ Hpr) (↓ (Hr ↕ Hq)) ω d) =
+      (PB.(subbox') (Hp := Hpr) (Hr ↕ Hq) ω (subbox (Hp := ↓ (Hpr ↕ Hr)) Hq ε d));
+    }.
   \end{minted}
 \end{listing}
+
+To build up the box, we'd simply have to induction on \mintinline{coq}{p}:
+
+\begin{listing}[H]
+  \begin{minted}{coq}
+    Definition mkcsp {n : nat} {C : Cubical n} : Type@{l'} :=
+      { D : C.(csp) & C.(Box).(box) (le_refl n) D -> Type@{l} }.
+
+    Definition mkPB {n} {C : Cubical n} :
+      PartialBoxBase n.+1 mkcsp := {|
+      box' {p} {Hp : p.+1 <= n.+1} {D : mkcsp} := C.(Box).(box) (⇓ Hp) D.1 ;
+      box'' {p} {Hp : p.+2 <= n.+1} {D : mkcsp} := C.(PB).(box') (⇓ Hp) D.1 ;
+      subbox' {p q} {Hp : p.+2 <= q.+2} {Hq : q.+2 <= n.+1} {ε} {D : mkcsp} {d} :=
+        C.(Box).(subbox) (Hp := ⇓ Hp) (⇓ Hq) ε d ;
+    |}.
+
+    Definition mkBox {n} {C : Cubical n} p : PartialBox n.+1 p mkcsp mkPB.
+      induction p as [|p (boxSn, subboxSn, cohboxSn)].
+      + (* ... *)
+  \end{minted}
+\end{listing}
+
+\subsection{UIP}
+We use UIP in the final coherence condition in \mintinline{coq}{cohbox} and \mintinline{coq}{cohcube}. If we weren't to use UIP in \mintinline{coq}{cohbox}, then we'd have something similar to:
+
+\begin{listing}[H]
+  \begin{minted}{coq}
+    cohbox : subbox ( subbox ... ) = subbox ( subbox ... )
+    coh2box : cohbox ... = cohbox ...
+    ...
+    cohNbox : cohPredNbox ... = cohPredNbox ...
+  \end{minted}
+\end{listing}
+
+In attempting to write the proof without UIP, we'd have a relation between \mintinline{coq}{cohNbox} and \mintinline{coq}{cohPredNbox}, which, we expect to be tricky to prove.
 
@@
 
-\appendix
-\section{Source code listing}
-
 \end{document}

### 2022-02-18 paper/paper.tex
Correcting missing cohbox in cohlayer and cohcube
Proof of cohcube when p=r still to be checked.
Renaming \U into \UU (the former already exists and fails on my setup).

@@
 % Type theory
-\newcommand{\U}{\ensuremath{\mathscr{U}}}
+\newcommand{\UU}{\ensuremath{\mathscr{U}}}
 
@@
   \begin{tikzcd}
-    X_0 : \U & X_1 : \U \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \U \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
-  \end{tikzcd}
-$$
-
-\begin{align*}
-  X_0 & : \U                                                                                                      \\
-  X_1 & : X_0 \times X_0 \rightarrow \U                                                                           \\
-  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \U \\
+    X_0 : \UU & X_1 : \UU \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \UU \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
+  \end{tikzcd}
+$$
+
+\begin{align*}
+  X_0 & : \UU                                                                                                      \\
+  X_1 & : X_0 \times X_0 \rightarrow \UU                                                                           \\
+  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \UU \\
   \ldots
@@
 
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D)) \\(b:\mylayer{l}{n,p}(D)(d))}}{:}{\makecell{\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downlayer{l,\omega,r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\omega,r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))}}
+  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D)) \\(b:\mylayer{l}{n,p}(D)(d))}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p}(D)(d)}(\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downlayer{l,\omega,r}{n,p}(D)(d)(b))) \\ \eqett \downlayer{l,\omega,r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))}}
 
@@
 
-  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D)) \\ (b:\mycube{l}{n,p}(D)(E)(d))}}{:}{\makecell{\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downcube{l,\omega,r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\omega,r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))}}
+  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D)) \\ (b:\mycube{l}{n,p}(D)(E)(d))}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downcube{l,\omega,r}{n,p}(D)(E)(d)(b))) \\ \eqett \downcube{l,\omega,r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))}}
 

### 2022-02-19 paper/paper.tex
CubeInfinity: introduce something with a bombastic name ;)

@@
   \begin{minted}{coq}
-    (* PartialBox consists of an 0-cells, and fillers which are the 1-cells,
-    2-cells, and 3-cells relating the different 0-cells on the cube  *)
-    Record PartialBoxBase (n : nat) (csp : Type@{l'}) := {
+    Record PartialBoxPrev (n : nat) (csp : Type@{l'}) := {
       box' {p} (Hp : p.+1 <= n) : csp -> Type@{l} ;
@@
 
-    Definition mkPB {n} {C : Cubical n} :
+    Definition mkBoxPrev {n} {C : Cubical n} :
       PartialBoxBase n.+1 mkcsp := {|
@@
     Definition mkBox {n} {C : Cubical n} p : PartialBox n.+1 p mkcsp mkPB.
-      induction p as [|p (boxSn, subboxSn, cohboxSn)].
+      induction p.
       + (* ... *)

### 2022-02-23 paper/paper.tex
paper: major cleanup; removed derived notations
cohSheet is missing!

@@
 
-% Head and tail
-\newcommand{\hd}{\ensuremath{\mathsf{hd}}}
-\newcommand{\tl}{\ensuremath{\mathsf{tl}}}
-
-% Universes, obj, mor
+% Universes
 \newcommand{\sort}[1]{\ensuremath{\mathsf{U}_{#1}}}
@@
 
+% cubset
+\newcommand{\csp}[1]{\ensuremath{\mathsf{cubset}_{#1}}}
+\newcommand{\cubeset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
+\newcommand{\cubesetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}
+\newcommand{\cubesetfrom}[2]{\ensuremath{\mathsf{cubset}_{#1}^{\geq#2}}}
+
 % Box, layer, and cube
-\newcommand{\mycubset}[1]{\ensuremath{\mathsf{cubset}_{#1}}}
 \newcommand{\mybox}[2]{\ensuremath{\mathsf{box}_{#1}^{#2}}}
-\newcommand{\mylayer}[2]{\ensuremath{\mathsf{layer}_{#1}^{#2}}}
-\newcommand{\mycube}[2]{\ensuremath{\mathsf{cube}_{#1}^{#2}}}
+\newcommand{\layer}[2]{\ensuremath{\mathsf{layer}_{#1}^{#2}}}
+\newcommand{\cube}[2]{\ensuremath{\mathsf{cube}_{#1}^{#2}}}
 
 % Subbox, sublayer, and subcube
-\newcommand{\downbox}[2]{\ensuremath{\mathsf{subbox}_{#1}^{#2}}}
-\newcommand{\downlayer}[2]{\ensuremath{\mathsf{sublayer}_{#1}^{#2}}}
-\newcommand{\downcube}[2]{\ensuremath{\mathsf{subcube}_{#1}^{#2}}}
-\newcommand{\myfullbox}[2]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
+\newcommand{\subbox}[2]{\ensuremath{\mathsf{subbox}_{#1}^{#2}}}
+\newcommand{\sublayer}[2]{\ensuremath{\mathsf{sublayer}_{#1}^{#2}}}
+\newcommand{\subcube}[2]{\ensuremath{\mathsf{subcube}_{#1}^{#2}}}
+\newcommand{\fullbox}[2]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
 
@@
 \newcommand{\cohcube}[2]{\ensuremath{\mathsf{cohcube}_{#1}^{#2}}}
-
-% Partials and fulls related to box, cube, and tube
-\newcommand{\border}[1]{\ensuremath{\mathsf{border}_{#1}}}
-\newcommand{\partialcubset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
-\newcommand{\mycubsetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}
-\newcommand{\fulldownbox}[2]{\ensuremath{\mathsf{subfullbox}_{#1}^{#2}}}
-\newcommand{\fulldowncube}[2]{\ensuremath{\mathsf{subfullcube}_{#1}^{#2}}}
-\newcommand{\propercube}[1]{\ensuremath{\mathsf{properfiller}_{#1}}}
-\newcommand{\mygroundedcube}[1]{\ensuremath{\mathsf{groundedcube}_{#1}}}
-\newcommand{\tube}[1]{\ensuremath{\mathsf{tube}_{#1}}}
-\newcommand{\mycubsetfrom}[2]{\ensuremath{\mathsf{cubset}_{#1}^{\geq#2}}}
-\newcommand{\myfullcube}[1]{\ensuremath{\mathsf{fullcube}_{#1}}}
 
@@
 \newcommand{\UU}{\ensuremath{\mathscr{U}}}
+
+% Some abbreviations
+\newcommand{\D}{\ensuremath{(D)}}
+\newcommand{\hdD}{\ensuremath{(D.1)}}
+\newcommand{\tlD}{\ensuremath{(D.2)}}
+\renewcommand{\d}{\ensuremath{(d)}}
+\newcommand{\E}{\ensuremath{(E)}}
+\renewcommand{\l}{\ensuremath{(l)}}
+\renewcommand{\c}{\ensuremath{(c)}}
 
@@
 Note that such relational structure, cubes and boxes are relative to a universe.
-Note the presence of a coherence condition $\cohbox{l}{}$ to ensuring that both sides of the equality in $\downlayer{l}{}$ and $\downcube{l}{}$ are in the same type.
+Note the presence of a coherence condition $\cohbox{l}{}$ to ensuring that both sides of the equality in $\sublayer{l}{}$ and $\subcube{l}{}$ are in the same type.
 The proof of $\cohbox{l}{}$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
 Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\downbox{l}{}$ nor $\cohbox{l}{}$ anymore.
+Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\subbox{l}{}$ nor $\cohbox{l}{}$ anymore.
 
@@
   \mc{Type of truncated cubical sets}
-  \eqnline{\partialcubset{l}{n}}{}{:}{\sort{l+1}}
-  \eqnline{\partialcubset{l}{0}}{}{\defeq}{\unittype}
-  \eqnline{\partialcubset{l}{n'+1}}{}{\defeq}{\ensuremath{\Sigma}D:\partialcubset{l}{n'}.\,\mycubsetcomp{l}{n'}(D)}
+  \eqnline{\cubeset{l}{n}}{}{:}{\sort{l+1}}
+  \eqnline{\cubeset{l}{0}}{}{\defeq}{\unittype}
+  \eqnline{\cubeset{l}{n'+1}}{}{\defeq}{\ensuremath{\Sigma}D:\cubeset{l}{n'}.\,\cubesetcomp{l}{n'} \D}
 
@@
   \mc{Structure carried at each dimension}
-  \eqnline{\mycubsetcomp{l}{n}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
-  \eqnline{\mycubsetcomp{l}{n}}{D}{\defeq}{\myfullbox{l}{n}(D)\imp \sort{l}}
+  \eqnline{\cubesetcomp{l}{n}}{(D:\cubeset{l}{n})}{:}{\sort{l}}
+  \eqnline{\cubesetcomp{l}{n}}{D}{\defeq}{\fullbox{l}{n}\D\imp \sort{l}}
 \end{eqntable}
@@
   \mc{Full homogeneous $n$-boxes}
-  \eqnline{\myfullbox{l}{n}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
-  \eqnline{\myfullbox{l}{n}}{D}{\defeq}{\mybox{l}{n,n}(D)}
+  \eqnline{\fullbox{l}{n}}{(D:\cubeset{l}{n})}{:}{\sort{l}}
+  \eqnline{\fullbox{l}{n}}{D}{\defeq}{\mybox{l}{n,n}\D}
 
@@
   \mc{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}
-  \eqnline{\mybox{l}{n,p,[p \leq n]}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
+  \eqnline{\mybox{l}{n,p,[p \leq n]}}{(D:\cubeset{l}{n})}{:}{\sort{l}}
   \eqnline{\mybox{l}{n,0}}{D}{\defeq}{\unittype}
-  \eqnline{\mybox{l}{n,p'+1}}{D}{\defeq}{\Sigma d:\mybox{l}{n,p'}(D).\,\mylayer{l}{n,p'}(D)(d)}
+  \eqnline{\mybox{l}{n,p'+1}}{D}{\defeq}{\Sigma d:\mybox{l}{n,p'}\D.\,\layer{l}{n,p'} \D \d}
 
@@
 
-  \eqnline{\mylayer{l}{n,p,[p < n]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}
+  \eqnline{\layer{l}{n,p,[p < n]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D)}}{:}{\sort{l}}
 
-  \eqnline{\mylayer{l}{n,p}}{D~d}{\defeq}{\makecell{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\ \times\;\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))}}
+  \eqnline{\layer{l}{n,p}}{D~d}{\defeq}{\makecell{\cube{l}{n-1,p}\hdD\tlD(\subbox{l,L,p}{n,p} \D \d) \\ \times\;\cube{l}{n-1,p}\hdD\tlD(\subbox{l,R,p}{n,p} \D \d)}}
 
@@
 
-  \eqnline{\mycube{l}{n,p,[p \leq n]}}{\makecell{(D:\partialcubset{l}{n}) \\(E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}
+  \eqnline{\cube{l}{n,p,[p \leq n]}}{\makecell{(D:\cubeset{l}{n}) \\(E:\cubesetcomp{l}{n} \D) \\ (d:\mybox{l}{n,p} \D)}}{:}{\sort{l}}
 
-  \eqnline{\mycube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{E(d)}
+  \eqnline{\cube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{\E \d}
 
-  \eqnline{\mycube{l}{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma b:\mylayer{l}{n,p}(D)(d).\,\mycube{l}{n,p+1}(D)(E)(d,b)}
+  \eqnline{\cube{l}{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma l:\layer{l}{n,p} \D \d.\,\cube{l}{n,p+1} \E(d,l)}
 \end{eqntable}
@@
 
-  \eqnline{\downbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\mybox{l}{n-1,p}(\hd(D))}
+  \eqnline{\subbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D)}}{:}{\mybox{l}{n-1,p}\hdD}
 
-  \eqnline{\downbox{l,\epsilon,q}{n,p'+1}}{D~(d,b)}{\defeq}{(\downbox{l,\epsilon,q}{n,p'}(D)(d),\downlayer{l,\epsilon,q-1}{n,p'}(D)(d)(b))}
+  \eqnline{\subbox{l,\epsilon,q}{n,p'+1}}{D~(d,l)}{\defeq}{(\subbox{l,\epsilon,q}{n,p'} \D\d,\sublayer{l,\epsilon,q-1}{n,p'} \D \d\l)}
 
@@
 
-  \eqnline{\downlayer{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D)) \\ (b:\mylayer{l}{n,p}(D)(d))}}{:}{\mylayer{l}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}
+  \eqnline{\sublayer{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D) \\ (b:\layer{l}{n,p} \D \d)}}{:}{\layer{l}{n-1,p}\hdD(\subbox{l,\epsilon,q+1}{n,p} \D \d)}
 
-  \eqnline{\downlayer{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L)), \\ \;\overright{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R)))}}
+  \eqnline{\sublayer{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohbox{l,\epsilon,L,q,p}{n,p} \D \d}(\subcube{l,\epsilon,q}{n-1,p}\hdD\tlD(\subbox{l,L,p}{n,p} \D \d)(c_L)), \\ \;\overright{\cohbox{l,\epsilon,R,q,p}{n,p} \D \d}(\subcube{l,\epsilon,q}{n-1,p}\hdD\tlD(\subbox{l,R,p}{n,p}\D\d)(c_R)))}}
 
@@
 
-  \eqnline{\downcube{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\partialcubset{l}{n}) \\ (E:\mycubsetcomp{l}{n}(D)) \\(d:\mybox{l}{n,p}(D)) \\ (b:\mycube{l}{n,p}(D)(E)(d))}}{:}{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}
+  \eqnline{\subcube{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\cubeset{l}{n}) \\ (E:\cubesetcomp{l}{n} \D) \\(d:\mybox{l}{n,p} \D) \\ (b:\cube{l}{n,p} \D\E\d)}}{:}{\cube{l}{n-1,p}\hdD\tlD(\subbox{l,\epsilon,q+1}{n,p} \D \d)}
 
-  \eqnline{\downcube{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{b_\epsilon}
+  \eqnline{\subcube{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{b_\epsilon}
 
-  \eqnline{\downcube{l,\epsilon,q}{n,p,[p<q]}}{D~E~d~(b,c)}{\defeq}{(\downlayer{l,\epsilon,q}{n,p}(D)(d)(b),\downcube{l,\epsilon,q}{n,p+1}(D)(E)(d,b)(c))}
+  \eqnline{\subcube{l,\epsilon,q}{n,p,[p<q]}}{D~E~d~(b,c)}{\defeq}{(\sublayer{l,\epsilon,q}{n,p} \D \d(b),\subcube{l,\epsilon,q}{n,p+1} \D\E(d,b)\c)}
 \end{eqntable}
@@
 
-  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\makecell{\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\omega,r}{n,p}(D)(d)) \\ \eqett \downbox{l,\omega,r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}}
+  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D)}}{:}{\makecell{\subbox{l,\epsilon,q}{n-1,p}\hdD(\subbox{l,\omega,r}{n,p} \D \d) \\ \eqett \subbox{l,\omega,r}{n-1,p}\hdD(\subbox{l,\epsilon,q+1}{n,p} \D \d)}}
 
@@
 
-  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,p'+1}}{D~(d,b)}{\defeq}{(\cohbox{l,\epsilon,\omega,q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\omega,q,r}{n,p'}(D)(d)(b))}
+  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,p'+1}}{D~(d,c)}{\defeq}{(\cohbox{l,\epsilon,\omega,q,r}{n,p'} \D\d,\cohlayer{l,\epsilon,\omega,q,r}{n,p'} \D\d\c)}
 
@@
 
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D)) \\(b:\mylayer{l}{n,p}(D)(d))}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p}(D)(d)}(\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downlayer{l,\omega,r}{n,p}(D)(d)(b))) \\ \eqett \downlayer{l,\omega,r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))}}
+  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D) \\(b:\layer{l}{n,p} \D \d)}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\sublayer{l,\epsilon,q}{n-1,p}\hdD(\subbox{l,\omega,r}{n,p} \D \d)(\sublayer{l,\omega,r}{n,p} \D \d(b))) \\ \eqett \sublayer{l,\omega,r}{n-1,p}\hdD(\subbox{l,\epsilon,q+1}{n,p} \D \d)(\sublayer{l,\epsilon,q+1}{n,p} \D \d(b))}}
 
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p}}{D~d~c}{\defeq}{\makecell{(\cohcube{l,\epsilon,\omega,q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L), \\ \;\cohcube{l,\epsilon,\omega,q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))}}
+  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p}}{D~d~c}{\defeq}{\makecell{(\cohcube{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\subbox{l,L,p}{n,p} \D \d)(c_L), \\ \;\cohcube{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\subbox{l,R,p}{n,p} \D \d)(c_R))}}
 
@@
 
-  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D)) \\ (b:\mycube{l}{n,p}(D)(E)(d))}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\omega,r}{n,p}(D)(d))(\downcube{l,\omega,r}{n,p}(D)(E)(d)(b))) \\ \eqett \downcube{l,\omega,r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))}}
+  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (E:\cubesetcomp{l}{n} \D) \\ (d:\mybox{l}{n,p} \D) \\ (b:\cube{l}{n,p} \D\E \d)}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\subcube{l,\epsilon,q}{n-1,p}\hdD\tlD(\subbox{l,\omega,r}{n,p} \D \d)(\subcube{l,\omega,r}{n,p} \D\E \d(b))) \\ \eqett \subcube{l,\omega,r}{n-1,p}\hdD\tlD(\subbox{l,\epsilon,q+1}{n,p} \D \d)(\subcube{l,\epsilon,q+1}{n,p} \D\E \d(b))}}
 
-  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\omega,p}{n,p}(D)(d))(b_{\epsilon}))}
+  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\subcube{l,\epsilon,q-1}{n-1,p}\hdD\tlD(\subbox{l,\omega,p}{n,p} \D \d)(b_{\epsilon}))}
 
-  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p<r]}}{D~E~d~(b,c)}{\defeq}{(\cohlayer{l,\epsilon,\omega,q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\omega,q,r}{n,p+1}(D)(E)(d,b)(c))}
+  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p<r]}}{D~E~d~(b,c)}{\defeq}{(\cohlayer{l,\epsilon,\omega,q,r}{n,p} \D \d(b),\;\cohcube{l,\epsilon,\omega,q,r}{n,p+1} \D\E(d,b)\c)}
 \end{eqntable}
-
-\subsection{Derived notions\label{sec:derived-notions}}
-On top of the basic definitions on tables \ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}, we can define on tables \ref{tab:macros} and \ref{tab:macroscont} a few other concepts at a more standard level of abstraction.
-In particular, a homogeneous $n$-box in the above sense is defined to be an object of type $\myfullbox{l}{n}(D_{n})$ for $D_{n} \defeq (A, =_A, \ldots, =^n_A)$ the initial segment of $n$-th first iterated equalities over $A$ (by convention, a homogeneous $0$-box shall be the canonical singleton type).
-A $n$-tube is of type $\mybox{l}{n+1,n}(D_{n+1})$.
-An homogeneous (proper) $n$-cube in some $n$-box $d$ is of type $\mycube{l}{n+1,n}(\hd(D_{n+1}))(\tl(D_{n+1}))(d)$ and a full $n$-cube is of type $\mycube{l}{n+1,0}(\hd(D_{n+1}))(\tl(D_{n+1})))(\star)$.
-
-Note that the components of an $n$-box or $n$-tube are tuples associated to the left.
-For cubes, the components can be associated to the left, and we call this a full $n$-cube or to the right, which we call grounded $n$-cube, and which corresponds to ``complete'' partial cubes, i.e.
-to partial cubes over the empty box.
-Table \ref{tab:macros} show how to compute the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of iterated equalities (see $\border{}$).
-
-Table \ref{tab:macros} also shows how to compute the faces of a box or of a cube.
 
@@
   \mc{Full (non-truncated) cubical sets with degeneracies}
-  \eqnline{\mycubset{l}}{}{:}{\sort{l+1}}
-  \eqnline{\mycubset{l}}{}{\defeq}{\mycubsetfrom{l}{0}(\star)}
+  \eqnline{\csp{l}}{}{:}{\sort{l+1}}
+  \eqnline{\csp{l}}{}{\defeq}{\cubesetfrom{l}{0}(\star)}
   \\
-  \eqnline{\mycubsetfrom{l}{n}}{(D:\partialcubset{l}{n})}{:}{\sort{l+1}}
-  \eqnline{\mycubsetfrom{l}{n}}{D}{\defeq}{\Sigma R:\mycubsetcomp{l}{n}(D).\,\mycubsetfrom{l}{n+1}(D,R)}
-\end{eqntable}
-
-\begin{eqntable}{Standard derived notions\label{tab:macros}}
-  \mc{Type of full $n$-cubes}
-  \eqnline{\myfullcube{l}^{n}}{(D:\partialcubset{l}{n+1})}{:}{\sort{l}}
-
-  \eqnline{\myfullcube{l}^{n}}{(D,E)}{\defeq}{\Sigma d:\myfullbox{l}{n}(D).\, E.\mathsf{rel}(d)}
-
-  \\ \mc{Type of $n$-tubes}
-
-  \eqnline{\tube{l}^{n}}{(D:\partialcubset{l}{n+1})}{:}{\sort{l}}
-  \eqnline{\tube{l}^{n}}{D}{\defeq}{\mybox{l}{n+1,n}(D)}
-
-  \\ \mc{Type of grounded $n$-cubes}
-
-  \eqnline{\mygroundedcube{l}^{n}}{(D:\partialcubset{l}{n+1})}{:}{\sort{l}}
-  \eqnline{\mygroundedcube{l}^{n}}{(D,E)}{\defeq}{\mycube{l}{n,0}(D)(E)(\star)}
-
-  \\ \mc{Type of fillers of some $n$-box}
-
-  \eqnline{\propercube{l}^{n}}{(D:\partialcubset{l}{n+1})~(d:\myfullbox{l}{n}(\hd(D)))}{:}{\sort{l}}
-
-  \eqnline{\propercube{l}^{n}}{(D,E)~d}{\defeq}{E.\mathsf{rel}(d)}
-
-  \\ \mc{Border of a grounded $n$-cube}
-
-  \eqnline{\border{l}^{n}}{(D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D))}{:}{\myfullbox{l}{n}(\hd(D))}
-
-  \eqnline{\border{l}^{n}}{D~c}{\defeq}{\border{l}^{n,0}(D)(\star)(c)}
-
-  \\ \mc{where the border of partial cubes is defined by}
-
-  \eqnline{\border{l}^{n,p}}{(D:\partialcubset{l}{n+1})~(d:\mybox{l}{n,p}(\hd(D)))~(c:\mycube{l}{n,p}(\hd(D))(\tl(D))(d))}{:}{\myfullbox{l}{n}(\hd(D))}
-
-  \eqnline{\border{l}^{n,p,[p=n]}}{D~d~c}{\defeq}{d}
-
-  \eqnline{\border{l}^{n,p,[p<n]}}{D~d~(b,c)}{\defeq}{\border{l}^{n,p+1}(D)(d,b)(c)}
-\end{eqntable}
-
-\begin{eqntable}{Standard derived notions (continued)\label{tab:macroscont}}
-  \mc{$q$-th projection of an $n$-box}
-
-  \eqnline{\fulldownbox{l,\epsilon,q}{n,[q < n]}}{(D:\partialcubset{l}{n})~(d:\myfullbox{l}{n}(D))}{:}{\myfullbox{l}{n-1}(\hd(D))}
-
-  \eqnline{\fulldownbox{l,\epsilon,q}{n}}{D~(d,\_)}{\defeq}{\downbox{l,\epsilon,q}{n,n-1}(D)(d)}
-
-  \\ \mc{$q$-th face of an $n$-cube}
-
-  \eqnline{\fulldowncube{l,\epsilon,q}{n,[q < n]}}{(D:\partialcubset{l}{n+1})~(c:\myfullcube{l}^{n}(D))}{:}{\myfullcube{l}^{n-1}(\hd(D))}
-
-  \eqnline{\fulldowncube{l,\epsilon,q}{n}}{(D,E)~c}{\defeq}{\downcube{l,\epsilon,q}{n,0}(D)(E)(\star)(c)}
-
-  \\ \mc{where the extension of $\downbox{l}{}$ to $p>q$ is}
-
-  \eqnline{\downbox{l,\epsilon,q}{n,p,[q < p < n]}}{(D:\partialcubset{l}{n})~(d:\mybox{l}{n,p}(D))}{:}{\myfullbox{l}{n-1}(\hd(D))}
-
-  \eqnline{\downbox{l,\epsilon,q}{n,q+1}}{D~(d,b)}{\defeq}{\border{l}^{n-1,q}(\hd(D))(\downbox{l,\epsilon,q}{n,q}(D)(d))(b_{\epsilon})}
-
-  \eqnline{\downbox{l,\epsilon,q}{n,p,[q < p-1]}}{D~(d,b)}{\defeq}{\downbox{l,\epsilon,q}{n,p-1}(D)(d)}
+  \eqnline{\cubesetfrom{l}{n}}{(D:\cubeset{l}{n})}{:}{\sort{l+1}}
+  \eqnline{\cubesetfrom{l}{n}}{D}{\defeq}{\Sigma R:\cubesetcomp{l}{n} \D.\,\cubesetfrom{l}{n+1}(D,R)}
 \end{eqntable}
@@
     \end{listing}
-  \item[(c)] A refinement of the inductive definition; a nested implication.
+  \item[\c] A refinement of the inductive definition; a nested implication.
     \begin{listing}[H]
@@
 (a) was unworkable right from the start, and we tried approach (b) for a while, before running into unification problems.
-We then settled on approach (c), because it made compositions of inequalities almost trivial to prove.
+We then settled on approach \c, because it made compositions of inequalities almost trivial to prove.
 Compare the following snippets defining transitivity of $\leq$:

### 2022-02-23 paper/paper.tex
art.cls: switch to brand new art class

@@
-\documentclass[10pt]{amsart}
+\documentclass[10pt]{art}
 
-\usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
-\usepackage{amsthm, amssymb, amsmath, mathtools, amsaddr, fancyhdr, bookmark, fontspec, xargs, multirow, polyglossia, luacode, minted, color, soulutf8, tcolorbox, tabularx, tikz-cd, booktabs, setspace, makecell, caption, mathrsfs, xpatch, lmodern}
+\usepackage{multirow, minted, tabularx, booktabs, setspace, makecell, caption}
 \usepackage[hmargin=0.4in, vmargin=0.8in, headheight=10pt]{geometry}
+
+% Simplicial and Cubical sets
+\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
+\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
+\renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
+\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
 
@@
 
-% Objects and morphisms
-\newcommand{\obj}{\ensuremath{\mathsf{obj}}}
-\newcommand{\mor}{\ensuremath{\mathsf{mor}}}
-
-% Simplicial sets
-\newcommand{\Set}{\ensuremath{\mathsf{Set}}}
-\newcommand{\op}{\ensuremath{\mathsf{op}}}
-\newcommand{\Simplex}[1]{\ensuremath{\boldsymbol{\Delta^{#1}}}}
-\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
-\newcommand{\SSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\Delta}}}}
-\newcommand{\sq}[1]{\ensuremath{\mathsf{[#1]}}}
-
-% Cubical sets
-\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
-\newcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
-\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
-
 % Type theory
@@
 % Some abbreviations
-\newcommand{\D}{\ensuremath{(D)}}
+\renewcommand{\D}{\ensuremath{(D)}}
 \newcommand{\hdD}{\ensuremath{(D.1)}}
@@
 \renewcommand{\c}{\ensuremath{(c)}}
+
+% Fancy headers
+\pagestyle{fancy}
+\fancyhf{}
+\fancyhead[R]{\footnotesize\textcolor{gray80}{{\thepage / \pageref{LastPage}}}}
+\renewcommand{\sectionmark}[1]{\markboth{}{\thesection.\ #1}}
+\fancyhead[L]{\footnotesize\textcolor{gray80}{{\MakeUppercase{\rightmark}}}}
+
+% Section and subsection styles
+\renewcommand{\thesection}{\Roman{section}}
+\titleformat{\section}{\centering\scshape\Large\color{raspeberry}}{\thesection}{0.7em}{}
+\titleformat{\subsection}{\strongenv\large\color{gray80}}{\thesubsection}{0.7em}{}
+
+% Pack enumerate items and bibitems
+\setlist{nolistsep}
+\setlength{\bibitemsep}{.2\baselineskip plus .05\baselineskip minus .05\baselineskip}
 
@@
 
-% Use lettered footnotes
-\renewcommand{\thefootnote}{\alph{footnote}}
-
-% amsthm theorems
-\swapnumbers
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{terminology}[definition]{Terminology}
-\newtheorem{notation}[definition]{Notation}
-\newtheorem{proposition}[definition]{Proposition}
-\newtheorem{lemma}[definition]{Lemma}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{corollary}[definition]{Corollary}
-\newtheorem{remark}[definition]{Remark}
-\newtheorem{example}[definition]{Example}
-\newtheorem{caution}[definition]{Caution}
-\newtheorem{discussion}[definition]{Discussion}
-
-\usepackage{thmtools}
-
-% Fancy headers
-\pagestyle{fancy} % choose the "fancy" pagestyle
-\fancyhf{}        % clear all headers and footers
-% Now set the headers
-\fancyhead[LE,RO]{\footnotesize\thepage}
-\fancyhead[LO,RE]{\footnotesize\leftmark}
-\makeatletter
-\xapptocmd{\@sect}{\csname #1mark\endcsname{#7}}{}{}
-\makeatother
-
-% Subsection centering
-\makeatletter
-\def\subsection{\@startsection{subsection}{2}
-  \z@{.5\linespacing\@plus.7\linespacing}{.6\baselineskip}{\centering}}
-\makeatother
-
-% Nested numbering of sections and subsections
-\makeatletter
-\newif\ifsection
-\newif\ifsubsection
-\preto\section{\sectiontrue\subsectionfalse}
-\preto\subsection{\sectionfalse\subsectiontrue}
-\patchcmd{\@xsect}% <cmd>
-  {\ignorespaces}% <search>
-  {\ifsubsection
-   \numberwithin{definition}{subsection}
-   \else
-   \numberwithin{definition}{section}
-   \fi
-   \setcounter{definition}{0}\relax\ignorespaces}% <replace>
-  {}{}% <success><failure>
-\makeatother
-
-% Fancy headers
-\pagestyle{fancy} % choose the "fancy" pagestyle
-\fancyhf{}        % clear all headers and footers
-% Now set the headers
-\fancyhead[LE,RO]{\footnotesize\thepage}
-\fancyhead[LO,RE]{\footnotesize\leftmark}
-\makeatletter
-\xapptocmd{\@sect}{\csname #1mark\endcsname{#7}}{}{}
-\makeatother
-
-% Subsection centering
-\makeatletter
-\def\subsection{\@startsection{subsection}{2}
-  \z@{.5\linespacing\@plus.7\linespacing}{.6\baselineskip}{\centering}}
-\makeatother
-
 % Code listings
@@
 \setmonofont{Source Code Pro}
-\newfontfamily\mainfont{Avenir Next}
 \defaultfontfeatures{Ligatures=TeX, Scale=MatchUppercase}
@@
 \title{An iterated Grothendieck construction of semi-cubical types}
-\author{Hugo Herbelin}
-\address{Institut de Recherche en Informatique Fondamentale}
-\author{Ramkumar Ramachandra}
-\address{Université de Paris}
+\author{
+  \textcolor{gray80}{Hugo Herbelin} \\
+  \itshape \textcolor{gray80}{IRIF}
+  \and
+  \textcolor{gray80}{Ramkumar Ramachandra} \\
+  \itshape \textcolor{gray80}{Université de Paris}
+}
+\date{}
 
 \begin{document}
+\thispagestyle{empty}
+\maketitle
 \begin{abstract}
@@
 \end{abstract}
-\maketitle
 \tableofcontents
@@
   \begin{equation*}
-    \SSet := \Set^{\Simplex{}^\op}
+    \SSet := \Set^{\op{\Simplex{}}}
   \end{equation*}
@@
   \begin{align*}
-    \obj(\SSet)            & := \text{functors} \; \Simplex{}^\op \rightarrow \Set      \\
+    \obj(\SSet)            & := \text{functors} \; \op{\Simplex{}} \rightarrow \Set     \\
     \mor(\SSet)            & := \text{natural transforms between the functors}          \\
@@
 The degeneracies then vanish, and we're left with the task of defining gluing conditions solely on the basis of face maps.
-In mathematical literature, there is little interest in studying \DeltaHat, since delta maps are not well-defined, and constructing a $\Set^{\DeltaHat^{op}}$ is inelegant.
+In mathematical literature, there is little interest in studying \DeltaHat, since delta maps are not well-defined, and constructing a $\Set^{\op{\DeltaHat}}$ is inelegant.
 

### 2022-02-23 paper/paper.tex
paper: polish a bit

@@
 % The eqntable environment, displaying the various
-\NewDocumentEnvironment{eqntable}{m}{\table[!ht]\small
+\NewDocumentEnvironment{eqntable}{m}{\table[H]\small
 \tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
@@
 \date{}
+
+\color{gray65}
 
@@
     Abort. (* Type-check fails at Qed.
-            * (=) : ∀ A, A -> A -> Prop, but we want to return an SProp.
-            *)
+            * (=) : ∀ A, A -> A -> Prop, but we want to return an SProp. *)
   \end{minted}
@@
 \begin{listing}[H]
-  \begin{minted}[linenos]{coq}
+  \begin{minted}{coq}
     Theorem le_trans {p q n} : p <= q -> q <= n -> p <= n.
@@
 \begin{listing}[H]
-  \begin{minted}[linenos]{coq}
+  \begin{minted}{coq}
     Definition le_trans {n m p} (Hnm : n <= m) (Hmp : m <= p) : n <= p :=
@@
       box' {p} (Hp : p.+1 <= n) : csp -> Type@{l} ;
-      (* [box' n D] is [box (n-1) D.1] *)
       box'' {p} (Hp : p.+2 <= n) : csp -> Type@{l} ;
@@
 
+\newpage
+
 \begin{thebibliography}{10}
@@
   \bibitem[Angiuli]{Angiuli17}
-  Carlo Angiuli, Guillaume Brunerie, Thierry Coquand, Kuen-Bang Hou (Favonia),Robert Harper, \& Daniel R. Licata. arXiv preprint.
+  Carlo Angiuli, Guillaume Brunerie, Thierry Coquand, Kuen-Bang Hou (Favonia), Robert Harper, \& Daniel R. Licata. arXiv preprint.
 

### 2022-02-23 paper/paper.tex
_CoqProject: add a stub for VSCoq

@@
 \newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
-
-% Type theory
-\newcommand{\UU}{\ensuremath{\mathscr{U}}}
 
@@
 
-  \begin{align*}
-    d_i d_j & = d_{j - 1} d_i, i < j \\
-    s_i s_j & = s_{j + 1} s_i, i < j \\
-    d_i s_j & =
+  \begin{equation*}
+    \begin{matrix}
+      d_i d_j & = & d_{j - 1} d_i & i < j \\
+      s_i s_j & = & s_{j + 1} s_i & i < j \\
+      d_i s_j & = &
       \begin{cases}
@@
       \end{cases}
-  \end{align*}
+    \end{matrix}
+  \end{equation*}
 \end{definition}
@@
   \begin{tikzcd}
-    X_0 : \UU & X_1 : \UU \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \UU \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
+    X_0 : \sort{} & X_1 : \sort{} \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \sort{} \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
   \end{tikzcd}
@@
 \begin{align*}
-  X_0 & : \UU                                                                                                      \\
-  X_1 & : X_0 \times X_0 \rightarrow \UU                                                                           \\
-  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \UU \\
+  X_0 & : \sort{}                                                                                                      \\
+  X_1 & : X_0 \times X_0 \rightarrow \sort{}                                                                           \\
+  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \sort{} \\
   \ldots

### 2022-03-06 paper/notes.tex
paper: split out Notes on Formalization

--- 2022-02-23 paper/paper.tex
@@
 
-\usepackage{multirow, minted, tabularx, booktabs, setspace, makecell, caption}
-\usepackage[hmargin=0.4in, vmargin=0.8in, headheight=10pt]{geometry}
-
-% Simplicial and Cubical sets
-\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
-\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
-\renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
-\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
-
-% Universes
-\newcommand{\sort}[1]{\ensuremath{\mathsf{U}_{#1}}}
-
-% The unit type
-\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
-\newcommand{\unitpoint}{\ensuremath{\star}}
-
-% Definitional and extensional equality
-\newcommand{\defeq}{\ensuremath{\triangleq}}
-\newcommand{\eqett}{\ensuremath{\equiv_{\mathit{ETT}}}}
-\newcommand{\reflett}{\ensuremath{\mathsf{refl}_{\mathit{ETT}}}}
-
-% cubset
-\newcommand{\csp}[1]{\ensuremath{\mathsf{cubset}_{#1}}}
-\newcommand{\cubeset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
-\newcommand{\cubesetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}
-\newcommand{\cubesetfrom}[2]{\ensuremath{\mathsf{cubset}_{#1}^{\geq#2}}}
-
-% Box, layer, and cube
-\newcommand{\mybox}[2]{\ensuremath{\mathsf{box}_{#1}^{#2}}}
-\newcommand{\layer}[2]{\ensuremath{\mathsf{layer}_{#1}^{#2}}}
-\newcommand{\cube}[2]{\ensuremath{\mathsf{cube}_{#1}^{#2}}}
-
-% Subbox, sublayer, and subcube
-\newcommand{\subbox}[2]{\ensuremath{\mathsf{subbox}_{#1}^{#2}}}
-\newcommand{\sublayer}[2]{\ensuremath{\mathsf{sublayer}_{#1}^{#2}}}
-\newcommand{\subcube}[2]{\ensuremath{\mathsf{subcube}_{#1}^{#2}}}
-\newcommand{\fullbox}[2]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
-
-% Coherence conditions
-\newcommand{\cohbox}[2]{\ensuremath{\mathsf{cohbox}_{#1}^{#2}}}
-\newcommand{\cohlayer}[2]{\ensuremath{\mathsf{cohlayer}_{#1}^{#2}}}
-\newcommand{\cohcube}[2]{\ensuremath{\mathsf{cohcube}_{#1}^{#2}}}
-
-% Logical implication
-\newcommand{\imp}{\ensuremath{\rightarrow}}
-\newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
-
-% Some abbreviations
-\renewcommand{\D}{\ensuremath{(D)}}
-\newcommand{\hdD}{\ensuremath{(D.1)}}
-\newcommand{\tlD}{\ensuremath{(D.2)}}
-\renewcommand{\d}{\ensuremath{(d)}}
-\newcommand{\E}{\ensuremath{(E)}}
-\renewcommand{\l}{\ensuremath{(l)}}
-\renewcommand{\c}{\ensuremath{(c)}}
+\usepackage{minted, booktabs, setspace}
+\usepackage{geometry}
 
@@
 
-% Section and subsection styles
+% Section and section styles
 \renewcommand{\thesection}{\Roman{section}}
 \titleformat{\section}{\centering\scshape\Large\color{raspeberry}}{\thesection}{0.7em}{}
-\titleformat{\subsection}{\strongenv\large\color{gray80}}{\thesubsection}{0.7em}{}
+\titleformat{\section}{\strongenv\large\color{gray80}}{\thesection}{0.7em}{}
 
@@
 
-% The eqntable environment, displaying the various
-\NewDocumentEnvironment{eqntable}{m}{\table[H]\small
-\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
-{\endtabularx\vspace{0.3em}\hrule\vspace{0.5em}\caption{#1}\endtable}
-
-% A block in the eqntable environment
-\newcommand{\eqnline}[4]{$#1$ & $#2$ & $#3$ & $#4$ \\}
-\newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}
-
-% Table caption set up
-\DeclareCaptionFormat{hfillstart}{\hfill#1#2#3\par}
-\DeclareCaptionFont{mdit}{\mdseries\itshape}
-\captionsetup[table]{
-  justification=centering,
-  font=bf,
-  labelfont=mdit,
-}
-
 % Code listings
-\usemintedstyle{tango}
+\usemintedstyle{solarized-dark}
 \setminted{escapeinside=~~}
@@
 
-\title{An iterated Grothendieck construction of semi-cubical types}
-\author{
-  \textcolor{gray80}{Hugo Herbelin} \\
-  \itshape \textcolor{gray80}{IRIF}
-  \and
-  \textcolor{gray80}{Ramkumar Ramachandra} \\
-  \itshape \textcolor{gray80}{Université de Paris}
-}
+\title{Bonak: Notes on the formalization}
+\author{Ramkumar Ramachandra}
 \date{}
-
-\color{gray65}
 
@@
 \maketitle
-\begin{abstract}
-  A proposed model of \emph{homotopy type theory} built via a \emph{reverse iterated Grothendieck construction} process formalizing semi-cubical sets in dependent type theory with \emph{extensional equality}.
-The accompanying artifact is a Coq formalization that uses highly sophisticated rewriting techniques and pushes the boundary of proof assistant technology.
-\end{abstract}
-\tableofcontents
-\newpage
 
-\section{Overture}
-Cubical type theory~\cite{Bezem14}~\cite{Cohen16}~\cite{Angiuli17} is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT.
-Two real-world projects that implement cubical type theory are worthy of mention: an experimental branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}, and the Arend theorem prover~\footnote{\href{https://arend-lang.github.io}{arend-lang.github.io}}.
-Cubical type theory is usually modeled as cubical sets, in the set-theoretic setting.
-Efforts to model cubical type theory have been ongoing since 2014, and many of these efforts are in the set-theoretic setting.
-
-Our contribution is to model the core of cubical types, semi-cubical sets, in type theory, using an indexed representation, in contrast to previous efforts that use a fibered representation.
-We use an \emph{iterated reverse-Grothendieck} construction as the basis of our formalization, which we expound on in \ref{sec:grothendieckconstr}.
-Another feature of our work is that, as we are in the type-theoretic setting, we use \emph{unicity of identity of proofs} (UIP), which would be an inherent property in the set-theoretic setting (see \ref{sec:uip}).
-
-\begin{table}[H]
-  \begin{tabularx}{\linewidth}{p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}}
-    \toprule
-            & Set theory & Type theory \\
-    \midrule
-    Fibered & CCHM       &             \\
-    \midrule
-    Indexed &            & Our work    \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
-
-\section{The intuition from simplicial sets}
-Simplicial sets are powerful mathematical objects, that form the basis of much of modern homotopy theory.
-Their power derives from the fact that their homotopy category is exceptionally well-behaved, and different model structures on them, as we will see in the following chapter.
-Unlike CW-complexes that rely on pure topological notions like spheres and disks to ``tame'' a topological space, the definition of simplicial sets is purely categorical, and exist independent of topological spaces.
-The geometric realization and singular complex functors facilitate travelling back-and-forth between simplicial sets and topological spaces, and these are non-trivial constructions.
-As such, simplicial sets exist purely in the imagination of the mathematician; each simplicial set has an infinite number of degenerate simplices, and they are not particularly well-suited to machine-based representation.
-
-\subsection{\texorpdfstring{\SSet}{The category of simplicial sets}}
-There exists vast mathematical literature on the subject, and we refer the uninitiated reader to \cite{Friedman08} for a gentle introduction with excellent intutions.
-With these intuitions in place, we proceed with a purely categorical treatment.
-Emily Riehl's \cite{Riehl11} is a well-written manuscript on the subject.
-
-\begin{definition}[\sq{n}]
-  $\sq{n}$ is used to denote a totally-ordered set of natural numbers less than or equal to $n$, ordered by magnitude.
-
-  \begin{equation*}
-    \sq{n} := \{0, 1, \ldots, n\}
-  \end{equation*}
-
-  We will regard the totally-ordered set as a category in certain contexts, and it should be clear which interpretation we're referring to from the context.
-
-  \begin{equation*}
-    \sq{n} := 0 \rightarrow 1 \rightarrow \ldots \rightarrow n
-  \end{equation*}
-\end{definition}
-
-\begin{definition}[\Simplex{}]
-  The category $\Simplex{}$ is defined in terms of its objects and morphisms:
-
-  \begin{align*}
-    \obj(\Simplex{}) & := \sq{n}, \text{regarded as a totally-ordered set}   \\
-    \mor(\Simplex{}) & := \sq{m} \rightarrow \sq{n}, \text{order-preserving}
-  \end{align*}
-\end{definition}
-
-\begin{definition}[\SSet]
-  The category of simplicial sets is defined as:
-
-  \begin{equation*}
-    \SSet := \Set^{\op{\Simplex{}}}
-  \end{equation*}
-
-  It is a functor category, whose objects and morphisms are given by:
-
-  \begin{align*}
-    \obj(\SSet)            & := \text{functors} \; \op{\Simplex{}} \rightarrow \Set     \\
-    \mor(\SSet)            & := \text{natural transforms between the functors}          \\
-    \text{composition law} & := \text{the usual composition of natural transformations} \\
-  \end{align*}
-\end{definition}
-
-\begin{definition}[\Simplex{n}]
-  The Yoneda embedding of $\sq{n}$ is referred to as the standard $n$-simplex.
-
-  \begin{equation*}
-    \Simplex{n} := y(\sq{n})
-  \end{equation*}
-\end{definition}
-
-\begin{notation}[$\sq{0, \ldots, n}$]
-  The notation $\sq{0, \ldots, n}$ denotes all ordered subsets of \sq{n}.
-\end{notation}
-
-With the definition of the category of simplicial sets firmly in place, we look inside a simplicial set to see the data it actually encodes concretely.
-
-\begin{definition}[The data of a simplicial set]
-  A simplicial set is equivalent to the data of a set of $n$-simplices, related to each other via face and degeneracy maps.
-
-  \begin{align*}
-    X_n                             & \;\;\text{a set of n-simplices} \\
-    d_i : X_{n + 1} \rightarrow X_n & \;\;\text{face maps}            \\
-    s_i : X_n \rightarrow X_{n + 1} & \;\;\text{degeneracy maps}      \\
-  \end{align*}
-
-  where $X_n$ is the set of $n$-simplices contained within the simplicial set $X$:
-
-  \begin{align*}
-    X_n & : \Set                                             \\
-    X_n & := X(\sq{n}), \text{where X is the simplicial set} \\
-  \end{align*}
-
-  and $d_i$ and $s_i$ operate on $X_n$ as follows (the hat on $i$ indicates that it is to be omitted):
-
-  \begin{align*}
-    d_i(\sq{0, \ldots, n}) & = \sq{0, \ldots, \hat{i}, \ldots, n} \\
-    s_i(\sq{0, \ldots, n}) & = \sq{0, \ldots, i, i, \ldots, n}    \\
-  \end{align*}
-
-  and $d_i$, $s_i$ are constrained by the following ``simplicial identities'':
-
-  \begin{equation*}
-    \begin{matrix}
-      d_i d_j & = & d_{j - 1} d_i & i < j \\
-      s_i s_j & = & s_{j + 1} s_i & i < j \\
-      d_i s_j & = &
-      \begin{cases}
-        s_{j - 1} d_i & i < j \\
-        id            & i = j \\
-        s_j d_{i - 1} & i > j \\
-      \end{cases}
-    \end{matrix}
-  \end{equation*}
-\end{definition}
-
-We mentioned degeneracies in the introduction to this section, and we define precisely what a degenerate simplex is now.
-
-\begin{definition}[Degenerate simplex]
-  A simplex is $x \in X_n$ is termed degenerate if it is the image of some degeneracy map $s_i$, and non-degenerate otherwise.
-\end{definition}
-
-\begin{example}[Non-degenerate simplices of \Simplex{n}]
-  The non-degenerate $k$-simplices of $\Simplex{n}$ are the injective maps $\sq{k} \rightarrow \sq{n}$ in $\Simplex{}$. In particular, $\Simplex{n}$ has a unique non-degenerate $n$-simplex.
-\end{example}
-
-As is clear from the above definitions, simplicial sets have an infinite number of degeneracies, and the first step towards drawing a simplicial set is to define a convention that omits these degeneracies in the drawing.
-
-\begin{notation}[Drawing of a simplicial set\label{not:drawsset}]
-  A diagram of the form
-
-  \begin{equation*}
-    \begin{tikzcd}
-      x \arrow[r, "f"] & y
-    \end{tikzcd}
-  \end{equation*}
-
-  in simplicial set $S$ will mean that $f$ is a non-degenerate $1$-simplex, and $x$ and $y$ are $0$-simplices.
-The simplices have a relationship to the simplicial set $S$ given by the following commutative diagram:
-
-  \begin{equation*}
-    \begin{tikzcd}
-      \Simplex{0} \arrow[dr] \arrow[drr, "x", bend left] & & \\
-      & \Simplex{1} \arrow[r, "f"] & S \\
-      \Simplex{0} \arrow[ur] \arrow[urr, "y"', bend right] & & \\
-    \end{tikzcd}
-  \end{equation*}
-
-  To attempting to draw simplices of dimension greater than $1$, we see that there is a potential ambiguity. Consider the following diagram:
-
-  \begin{equation*}
-    \begin{tikzcd}
-      & \bullet \arrow[ddr] & \\
-      \\
-      \bullet \arrow[uur] \arrow[rr] & & \bullet
-    \end{tikzcd}
-  \end{equation*}
-
-  In the above diagram, it is clear that there are three non-degenerate $1$-simplices, but it is unclear whether there is a non-degenerate $2$-simplex.
-By convention, when we draw such a diagram, we will assume that there is a non-degenerate $2$-simplex border by the three non-degenerate $1$-simplices.
-To generalize, we will always assume that there exists a non-degenerate $n$-simplex, when bounded by non-degenerate $(n - 1)$-simplices.
-\end{notation}
-
-\begin{example}[\Simplex{0}, \Simplex{1}, and \Simplex{2}]
-  $\Simplex{0}$ can be drawn as:
-
-  $$
-    \begin{tikzcd}
-      0
-    \end{tikzcd}
-  $$
-
-  $\Simplex{1}$ can be drawn as:
-
-  $$
-    \begin{tikzcd}
-      0 \arrow[r] & 1
-    \end{tikzcd}
-  $$
-
-  and $\Simplex{2}$ can be drawn as:
-
-  $$
-    \begin{tikzcd}
-      & 1 \arrow[ddr] & \\
-      \\
-      0 \arrow[uur] \arrow[rr] & & 2
-    \end{tikzcd}
-  $$
-\end{example}
-
-\subsection{Motivation for \texorpdfstring{\DeltaHat}{delta sets}}
-As hinted earlier, simplicial sets are ill-suited for machine-based representation, due to the infinite number of degenerate simplices that are uninteresting from the point of view of cubical type theory.
-To remedy this problem, let us instead use \DeltaHat, and proceed towards building, what is called \emph{semi-cubical sets} in literature.
-$\DeltaHat$ is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are \emph{strictly} order-preserving.
-The degeneracies then vanish, and we're left with the task of defining gluing conditions solely on the basis of face maps.
-In mathematical literature, there is little interest in studying \DeltaHat, since delta maps are not well-defined, and constructing a $\Set^{\op{\DeltaHat}}$ is inelegant.
-
-\subsection{Towards semi-cubical sets}
-We might naively attempt to define $\Cube{}$ identically to \DeltaHat, but let us briefly explain why this wouldn't work, motivating the definition of semi-cubical sets as in \cite{Antolini00}.
-If there were morphisms from every $\sq{m}$ to \sq{n}, we would end up with:
-
-$$
-  \begin{tikzcd}
-    \bullet \arrow[r] \arrow[dr] \arrow[d] & \bullet \arrow[d] \\
-    \bullet \arrow[r] \arrow[ur] & \bullet
-  \end{tikzcd}
-$$
-
-where the filling conditions are conflated with the cube itself.
-$\Simplex{n}$ can be defined quite simply as the convex hull of $n$ points, but even defining the standard $n$-cube becomes a problem if we start with $\sq{n}$, but the situation becomes much more amenable if we define:
-
-\begin{definition}[\Cube{n}]
-  \begin{equation*}
-    \Cube{n} := \I{n} = \sq{0, 1}^n
-  \end{equation*}
-\end{definition}
-
-\begin{example}[$\Cube{0}$, $\Cube{1}$ and $\Cube{2}$]
-  $\Cube{0}$ can be drawn as:
-
-  $$
-    \begin{tikzcd}
-      0 \equiv 1
-    \end{tikzcd}
-  $$
-
-  $\Cube{1}$ can be drawn as:
-
-  $$
-    \begin{tikzcd}
-      0 \arrow[r, dash] & 1
-    \end{tikzcd}
-  $$
-
-  and $\Cube{2}$ can be drawn as:
-
-  $$
-    \begin{tikzcd}
-      (0, 1) \arrow[r, dash] & (1, 1) \arrow[d, dash] \\
-      (0, 0) \arrow[u, dash] & (1, 0) \arrow[l, dash]
-    \end{tikzcd}
-  $$
-\end{example}
-
-Here, $\I{n}$ serves the purpose of \sq{n}, but this change will cascade into other definitions. In view of defining a category \CSet, we will restrict the morphisms in \Cube{}.
-
-\begin{definition}[\Cube{}]
-  \begin{align*}
-    \obj(\Cube{}) & := \I{n}                                           \\
-    \mor(\Cube{}) & := \delta^\epsilon_i : \I{n + 1} \rightarrow \I{n}
-  \end{align*}
-
-  where $\delta^\epsilon_i$ must satisfy the corresponding face map condition:
-
-  \begin{equation*}
-    \delta^\epsilon_i \delta^\omega_j = \delta^\omega_{j - 1} \delta^\epsilon_i
-  \end{equation*}
-
-  where $\epsilon$ and $\omega$ correspond to opposite faces.
-\end{definition}
-
-\begin{definition}[\CSet]
-  Just as in \SSet, we define semi-cubical sets as the functor category:
-
-  \begin{equation*}
-    \CSet := \Set^{\Cube{}^{op}}
-  \end{equation*}
-\end{definition}
-
-Or, in terms of objects and morphisms:
-
-\begin{definition}[$\CSet$ in terms of objects and morphisms]
-  \begin{align*}
-    \obj(\CSet) & := X_n                                                   \\
-    \mor(\CSet) & := X_\lambda, \text{where $\lambda$ is \Cube{}-morphism}
-  \end{align*}
-
-  where we term $X_n$ as the $n$-cubex, and $X_\lambda$ as the ``face map'', defined similarly:
-
-  \begin{align*}
-    X_n       & := X(\I{n}), \text{where X is the semi-cubical set} \\
-    X_\lambda & := X(\lambda)
-  \end{align*}
-\end{definition}
-
-\begin{theorem}
-  $\CSet$ does not admit degeneracies.
-\end{theorem}
-
-\begin{proof}
-  The reader is advised to refer to \cite{Antolini00} for the proof.
-\end{proof}
-
-\section{Grothendieck construction\label{sec:grothendieckconstr}}
-The Grothendieck construction provides a correspondence between a fibered representation, and an indexed representation.
-
-$$
-  \begin{tikzcd}
-    X_0 : \sort{} & X_1 : \sort{} \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \sort{} \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
-  \end{tikzcd}
-$$
-
-\begin{align*}
-  X_0 & : \sort{}                                                                                                      \\
-  X_1 & : X_0 \times X_0 \rightarrow \sort{}                                                                           \\
-  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \sort{} \\
-  \ldots
-\end{align*}
-
-\section{Unicity of identity proofs\label{sec:uip}}
-We dedicate this section to discussing UIP in different settings, and supply intuitions into this notion.
-
-UIP is a flavor of proof-irrelevance:
-
-\begin{align*}
-  \forall x y, \forall p q : x = y, p = q
-\end{align*}
-
-which is to say that any two proofs of \emph{equality} of the same two types are \emph{equal}. In other words, the proofs cannot be distinguished from one another.
-
-Proof irrelevance is an inherent part of set theory and first-order logic, although the property cannot be stated in the language of natural deductions.
-Intuititively, what it means is that a tree of deductions converges to a result, with no memory of the proof route; the tree itself is forgotten once the final result is obtained.
-
-One way of formalising set theory in type theory is via Aczel sets [ref]. It can be written down as an inductive as follows:
-
-\begin{listing}[H]
-  \begin{minted}[mathescape]{coq}
-    Inductive SET : Type :=
-      node : ~$\forall$~A : Type, (A -> SET) -> SET
-      ~$=_\textrm{SET}$~ : ...
-  \end{minted}
-\end{listing}
-
-\mintinline{coq}{(A -> SET) -> SET} can be drawn as:
-
-\begin{equation*}
-  \begin{tikzcd}
-    \{0\} \arrow[dr] & \\
-    & \{\} \\
-  \end{tikzcd}
-  \begin{tikzcd}
-    & \{0, 1\} \arrow[dr]\arrow[dl] & \\
-    \{0\} & & \{1\} \\
-  \end{tikzcd}
-  \begin{tikzcd}
-    & & \{0, 1, 2\} \arrow[dr]\arrow[dl] & \\
-    & \{0, 1\} \arrow[dl]\arrow[dr] & & \{2\} \\
-    \{0\} & & \{1\} & \\
-  \end{tikzcd}
-\end{equation*}
-
-In general, \mintinline{coq}{SET} can have an $n$-ary branching structure, splitting out the various subsets until we get to the leaves.
-
-Then, proof irrelevance can be stated as:
-
-\begin{align*}
-  \forall x y, \forall p q : x =_{\textrm{SET}} y, p = q
-\end{align*}
-
-\section{Semi-cubical sets}
-In this section, we give the core of the definition of semi-cubical
-sets as the coinductive limit (see table \ref{tab:barecubicalset}) of a
-construction of truncated semi-cubical sets.
-
-\subsection{Truncated semi-cubical sets}
-The definition is dispatched over tables \ref{tab:barecubicalsetstructurecore}, \ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}.
-It describes the structure of the underlying higher-dimensional relations on which cubes and boxes are built, together with the definition of homogeneous $n$-boxes, homogeneous $n$-cubes, together with face operations on boxes and cubes, together with commutation properties of the face operations.
-All are mutually defined as types of the target language ETT.
-Note that such relational structure, cubes and boxes are relative to a universe.
-Note the presence of a coherence condition $\cohbox{l}{}$ to ensuring that both sides of the equality in $\sublayer{l}{}$ and $\subcube{l}{}$ are in the same type.
-The proof of $\cohbox{l}{}$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
-Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\subbox{l}{}$ nor $\cohbox{l}{}$ anymore.
-
-When reflexivities are excepted, we call the structure thus defined \emph{bare truncated cubical sets}: \emph{bare} because it can be seen as defining semi-cubical sets corresponding to semi-simplicial sets with only faces as part of the structure; \emph{truncated} because we consider only such cubical sets up to some fixed dimension.
-
-\begin{eqntable}{Definition of a truncated cubical set (main part of the higher-dimensional relation structure)\label{tab:barecubicalsetstructurecore}}
-  \mc{Type of truncated cubical sets}
-  \eqnline{\cubeset{l}{n}}{}{:}{\sort{l+1}}
-  \eqnline{\cubeset{l}{0}}{}{\defeq}{\unittype}
-  \eqnline{\cubeset{l}{n'+1}}{}{\defeq}{\ensuremath{\Sigma}D:\cubeset{l}{n'}.\,\cubesetcomp{l}{n'} \D}
-
-  \\
-
-  \mc{Structure carried at each dimension}
-  \eqnline{\cubesetcomp{l}{n}}{(D:\cubeset{l}{n})}{:}{\sort{l}}
-  \eqnline{\cubesetcomp{l}{n}}{D}{\defeq}{\fullbox{l}{n}\D\imp \sort{l}}
-\end{eqntable}
-
-\begin{eqntable}{Definition of a truncated cubical set (boxes)\label{tab:barecubicalsetstructure}}
-  \mc{Full homogeneous $n$-boxes}
-  \eqnline{\fullbox{l}{n}}{(D:\cubeset{l}{n})}{:}{\sort{l}}
-  \eqnline{\fullbox{l}{n}}{D}{\defeq}{\mybox{l}{n,n}\D}
-
-  \\
-
-  \mc{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}
-  \eqnline{\mybox{l}{n,p,[p \leq n]}}{(D:\cubeset{l}{n})}{:}{\sort{l}}
-  \eqnline{\mybox{l}{n,0}}{D}{\defeq}{\unittype}
-  \eqnline{\mybox{l}{n,p'+1}}{D}{\defeq}{\Sigma d:\mybox{l}{n,p'}\D.\,\layer{l}{n,p'} \D \d}
-
-  \\
-
-  \eqnline{\layer{l}{n,p,[p < n]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D)}}{:}{\sort{l}}
-
-  \eqnline{\layer{l}{n,p}}{D~d}{\defeq}{\makecell{\cube{l}{n-1,p}\hdD\tlD(\subbox{l,L,p}{n,p} \D \d) \\ \times\;\cube{l}{n-1,p}\hdD\tlD(\subbox{l,R,p}{n,p} \D \d)}}
-
-  \\
-
-  \eqnline{\cube{l}{n,p,[p \leq n]}}{\makecell{(D:\cubeset{l}{n}) \\(E:\cubesetcomp{l}{n} \D) \\ (d:\mybox{l}{n,p} \D)}}{:}{\sort{l}}
-
-  \eqnline{\cube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{\E \d}
-
-  \eqnline{\cube{l}{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma l:\layer{l}{n,p} \D \d.\,\cube{l}{n,p+1} \E(d,l)}
-\end{eqntable}
-
-\begin{eqntable}{Definition of a homogeneous bare cubical set ($q$-th projection)\label{tab:barecubicalsetfaces}}
-
-  \eqnline{\subbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D)}}{:}{\mybox{l}{n-1,p}\hdD}
-
-  \eqnline{\subbox{l,\epsilon,q}{n,p'+1}}{D~(d,l)}{\defeq}{(\subbox{l,\epsilon,q}{n,p'} \D\d,\sublayer{l,\epsilon,q-1}{n,p'} \D \d\l)}
-
-  \\
-
-  \eqnline{\sublayer{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D) \\ (b:\layer{l}{n,p} \D \d)}}{:}{\layer{l}{n-1,p}\hdD(\subbox{l,\epsilon,q+1}{n,p} \D \d)}
-
-  \eqnline{\sublayer{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohbox{l,\epsilon,L,q,p}{n,p} \D \d}(\subcube{l,\epsilon,q}{n-1,p}\hdD\tlD(\subbox{l,L,p}{n,p} \D \d)(c_L)), \\ \;\overright{\cohbox{l,\epsilon,R,q,p}{n,p} \D \d}(\subcube{l,\epsilon,q}{n-1,p}\hdD\tlD(\subbox{l,R,p}{n,p}\D\d)(c_R)))}}
-
-  \\
-
-  \eqnline{\subcube{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\cubeset{l}{n}) \\ (E:\cubesetcomp{l}{n} \D) \\(d:\mybox{l}{n,p} \D) \\ (b:\cube{l}{n,p} \D\E\d)}}{:}{\cube{l}{n-1,p}\hdD\tlD(\subbox{l,\epsilon,q+1}{n,p} \D \d)}
-
-  \eqnline{\subcube{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{b_\epsilon}
-
-  \eqnline{\subcube{l,\epsilon,q}{n,p,[p<q]}}{D~E~d~(b,c)}{\defeq}{(\sublayer{l,\epsilon,q}{n,p} \D \d(b),\subcube{l,\epsilon,q}{n,p+1} \D\E(d,b)\c)}
-\end{eqntable}
-
-\begin{eqntable}{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)\label{tab:barecubicalsetcoherences}}
-
-  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D)}}{:}{\makecell{\subbox{l,\epsilon,q}{n-1,p}\hdD(\subbox{l,\omega,r}{n,p} \D \d) \\ \eqett \subbox{l,\omega,r}{n-1,p}\hdD(\subbox{l,\epsilon,q+1}{n,p} \D \d)}}
-
-  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,0}}{D~\unitpoint}{\defeq}{\reflett(\unitpoint)}
-
-  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,p'+1}}{D~(d,c)}{\defeq}{(\cohbox{l,\epsilon,\omega,q,r}{n,p'} \D\d,\cohlayer{l,\epsilon,\omega,q,r}{n,p'} \D\d\c)}
-
-  \\
-
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D) \\(b:\layer{l}{n,p} \D \d)}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\sublayer{l,\epsilon,q}{n-1,p}\hdD(\subbox{l,\omega,r}{n,p} \D \d)(\sublayer{l,\omega,r}{n,p} \D \d(b))) \\ \eqett \sublayer{l,\omega,r}{n-1,p}\hdD(\subbox{l,\epsilon,q+1}{n,p} \D \d)(\sublayer{l,\epsilon,q+1}{n,p} \D \d(b))}}
-
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p}}{D~d~c}{\defeq}{\makecell{(\cohcube{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\subbox{l,L,p}{n,p} \D \d)(c_L), \\ \;\cohcube{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\subbox{l,R,p}{n,p} \D \d)(c_R))}}
-
-  \\
-
-  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (E:\cubesetcomp{l}{n} \D) \\ (d:\mybox{l}{n,p} \D) \\ (b:\cube{l}{n,p} \D\E \d)}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\subcube{l,\epsilon,q}{n-1,p}\hdD\tlD(\subbox{l,\omega,r}{n,p} \D \d)(\subcube{l,\omega,r}{n,p} \D\E \d(b))) \\ \eqett \subcube{l,\omega,r}{n-1,p}\hdD\tlD(\subbox{l,\epsilon,q+1}{n,p} \D \d)(\subcube{l,\epsilon,q+1}{n,p} \D\E \d(b))}}
-
-  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\subcube{l,\epsilon,q-1}{n-1,p}\hdD\tlD(\subbox{l,\omega,p}{n,p} \D \d)(b_{\epsilon}))}
-
-  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p<r]}}{D~E~d~(b,c)}{\defeq}{(\cohlayer{l,\epsilon,\omega,q,r}{n,p} \D \d(b),\;\cohcube{l,\epsilon,\omega,q,r}{n,p+1} \D\E(d,b)\c)}
-\end{eqntable}
-
-\begin{eqntable}{Definition of a bare cubical set (coinductive structure)\label{tab:barecubicalset}}
-  \mc{Full (non-truncated) cubical sets with degeneracies}
-  \eqnline{\csp{l}}{}{:}{\sort{l+1}}
-  \eqnline{\csp{l}}{}{\defeq}{\cubesetfrom{l}{0}(\star)}
-  \\
-  \eqnline{\cubesetfrom{l}{n}}{(D:\cubeset{l}{n})}{:}{\sort{l+1}}
-  \eqnline{\cubesetfrom{l}{n}}{D}{\defeq}{\Sigma R:\cubesetcomp{l}{n} \D.\,\cubesetfrom{l}{n+1}(D,R)}
-\end{eqntable}
-
-\section{Notes on the formalization}
 The core of our formalization effort consists of inequalities in \emph{Peano arithmetic}.
@@
 
-\subsection{Notations in \texorpdfstring{\leq}{<=}}
+\section{Notations in \texorpdfstring{\leq}{<=}}
 On the outset, we defined various \emph{raising}, \emph{lowering}, and \emph{composition} operations on $\leq$:
@@
 
-\subsection{An SProp primer}
+\section{An SProp primer}
 \mintinline{coq}{SProp} is a replacement for standard propositions, or \mintinline{coq}{Prop}, that provides proof irrelevance.
@@
   \begin{minted}{coq}
-    Inductive eqsprop {A : SProp} (x : A) : A -> Prop := eqsprop_refl : eqsprop x x.
+    Inductive eqsprop {A : SProp} (x : A) : A -> Prop :=
+      eqsprop_refl : eqsprop x x.
     Infix "=S" := eqsprop (at level 70) : type_scope.
@@
 
-\subsection{\texorpdfstring{\leq}{<=} in SProp}
+\section{\texorpdfstring{\leq}{<=} in SProp}
 We tried three different approaches to defining $\leq$ in \mintinline{coq}{SProp}.
@@
     \end{listing}
-  \item[\c] A refinement of the inductive definition; a nested implication.
+  \item[(c)] A refinement of the inductive definition; a nested implication.
     \begin{listing}[H]
@@
 
-\subsection{The Fibonacci trick}
+\section{The Fibonacci trick}
 We'd initially defined \mintinline{coq}{Cubical} in a monolithic manner, and attempted to use \emph{well-founded induction} to build it up in steps.
@@
 
-\subsection{UIP}
+\section{UIP}
 We use UIP in the final coherence condition in \mintinline{coq}{cohbox} and \mintinline{coq}{cohcube}. If we weren't to use UIP in \mintinline{coq}{cohbox}, then we'd have something similar to:
@@
 
-\newpage
-
-\begin{thebibliography}{10}
-  \bibitem[Bez]{Bezem14}
-  Bezem, M., Coquand, T., \& Huber, S.
-(2014, July).
-A model of type theory in cubical sets.
-\textit{In 19th International Conference on Types for Proofs and Programs (TYPES 2013)} (Vol.
-26, pp.
-107-128).
-Wadern, Germany: Schloss Dagstuhl–Leibniz Zentrum fuer Informatik.
-
-  \bibitem[CubAgda]{Vezzosi21}
-  Vezzosi, A., Mörtberg, A., \& Abel, A. (2021). Cubical Agda: a dependently typed programming language with univalence and higher inductive types. \textit{Journal of Functional Programming, 31}.
-
-  \bibitem[CohCoq]{Cohen16}
-  Cohen, C., Coquand, T., Huber, S., \& Mörtberg, A. (2016). Cubical type theory: a constructive interpretation of the univalence axiom. arXiv preprint arXiv:1611.02108.
-
-  \bibitem[Angiuli]{Angiuli17}
-  Carlo Angiuli, Guillaume Brunerie, Thierry Coquand, Kuen-Bang Hou (Favonia), Robert Harper, \& Daniel R. Licata. arXiv preprint.
-
-  \bibitem[Fri]{Friedman08}
-  Friedman, G. (2008). An elementary illustrated introduction to simplicial sets. \textit{arXiv preprint arXiv:0809.4221}.
-
-  \bibitem[Rie]{Riehl11}
-  Riehl, E. (2011). A leisurely introduction to simplicial sets. \textit{Unpublished expository article available online from the author's web page}.
-
-  \bibitem[CubSet]{Antolini00}
-  Antolini, R. (2000). Cubical structures, homotopy theory. \textit{Annali di Matematica pura ed applicata, 178}(1), 317-324.
-
-  \bibitem[Her]{Herbelin15}
-  Herbelin, H. (2015). A dependently-typed construction of semi-simplicial types. \textit{Mathematical Structures in Computer Science, 25}(5), 1116-1131.
-
-  \bibitem[CoqInCoq]{Barras97}
-  Barras, B., \& Werner, B. (1997). Coq in coq. \textit{Available on the WWW.}
-\end{thebibliography}
-
 \end{document}

### 2022-03-06 paper/paper.tex
paper: split out Notes on Formalization

@@
 % Code listings
-\usemintedstyle{tango}
+\usemintedstyle{solarized-dark}
 \setminted{escapeinside=~~}
@@
 
-\section{Notes on the formalization}
-The core of our formalization effort consists of inequalities in \emph{Peano arithmetic}.
-We start with one inequality primitive, namely $\leq$, and build up all our inequalities on the basis of that inequality.
-Two different proofs of \mintinline{coq}{p <= q} must be the same: we chose to use \mintinline{coq}{SProp} for the proof irrelevance.
-
-\subsection{Notations in \texorpdfstring{\leq}{<=}}
-On the outset, we defined various \emph{raising}, \emph{lowering}, and \emph{composition} operations on $\leq$:
-
-\mint{coq}/~↑~ := (Hnm : n <= m) : n <= S m/
-\mint{coq}/~⇑~ := (Hnm : n <= m) : S n <= S m/
-\mint{coq}/~↓~ := (Hnm : S n <= m) : n <= m/
-\mint{coq}/~⇓~ := (Hnm : S n <= S m) : n <= m/
-\mint{coq}/~↕~ := (Hnm : n <= m) (Hmp : m <= p) : n <= p/
-
-\subsection{An SProp primer}
-\mintinline{coq}{SProp} is a replacement for standard propositions, or \mintinline{coq}{Prop}, that provides proof irrelevance.
-
-There are three inhabitants of \mintinline{coq}{SProp}: \mintinline{coq}{sUnit} corresponding to $\top$, \mintinline{coq}{sEmpty} corresponding to $\bot$, and \mintinline{coq}{sProposition} corresponding to a definitionally proof-irrelevant term.
-The way \mintinline{coq}{SProp} implements definitional proof-irrelevance is a simple engineering detail: there is hard-coding in Coq to render two inhabitants of \mintinline{coq}{sProposition} trivially inter-convertible.
-
-\begin{listing}[H]
-  \begin{minted}{coq}
-    Theorem SPropIrr (P : SProp) (x y : P) : x = y.
-    Proof.
-      by reflexivity.
-    Abort. (* Type-check fails at Qed.
-            * (=) : ∀ A, A -> A -> Prop, but we want to return an SProp. *)
-  \end{minted}
-\end{listing}
-
-We can, however, define an \mintinline{coq}{=S} that returns an \mintinline{coq}{SProp}:
-
-\begin{listing}[H]
-  \begin{minted}{coq}
-    Inductive eqsprop {A : SProp} (x : A) : A -> Prop := eqsprop_refl : eqsprop x x.
-    Infix "=S" := eqsprop (at level 70) : type_scope.
-  \end{minted}
-\end{listing}
-
-\subsection{\texorpdfstring{\leq}{<=} in SProp}
-We tried three different approaches to defining $\leq$ in \mintinline{coq}{SProp}.
-
-\begin{enumerate}
-  \item[(a)] A recursive definition.
-    \begin{listing}[H]
-      \begin{minted}{coq}
-      Inductive sFalse : SProp :=.
-      Inductive sTrue : SProp := sI.
-
-      Fixpoint le m n : SProp :=
-        match m with
-        | 0 => sTrue
-        | S m =>
-          match n with
-          | 0 => sFalse
-          | S n => le m n
-          end
-        end.
-     \end{minted}
-    \end{listing}
-  \item[(b)] An inductive definition.
-    \begin{listing}[H]
-      \begin{minted}{coq}
-      Inductive le' (n : nat) : nat -> SProp :=
-      | le_refl : n <= n
-      | le_S_up : forall {m : nat}, n <= m -> n <= S m
-      where "n <= m" := (le' n m) : nat_scope.
-
-    Definition le := le'.
-    \end{minted}
-    \end{listing}
-  \item[\c] A refinement of the inductive definition; a nested implication.
-    \begin{listing}[H]
-      \begin{minted}{coq}
-      Definition le n m := forall p, p <= n -> p <= m.
-      \end{minted}
-    \end{listing}
-\end{enumerate}
-
-(a) was unworkable right from the start, and we tried approach (b) for a while, before running into unification problems.
-We then settled on approach \c, because it made compositions of inequalities almost trivial to prove.
-Compare the following snippets defining transitivity of $\leq$:
-
-\begin{listing}[H]
-  \begin{minted}{coq}
-    Theorem le_trans {p q n} : p <= q -> q <= n -> p <= n.
-    (* ... a non-trivial proof ... *)
-    Defined.
-  \end{minted}
-  \caption{\mintinline{coq}{le_trans} when $\leq$ is defined using an inductive approach}
-\end{listing}
-
-\begin{listing}[H]
-  \begin{minted}{coq}
-    Definition le_trans {n m p} (Hnm : n <= m) (Hmp : m <= p) : n <= p :=
-      fun q (Hqn : le' q n) => Hmp _ (Hnm _ Hqn).
-  \end{minted}
-  \caption{\mintinline{coq}{le_trans} when $\leq$ is defined using a nested implication}
-\end{listing}
-
-Implications are naturally easier to work with, so the nested implication in \mintinline{coq}{SProp} was an easy choice.
-Many of the associtivity and commutativity proofs are then a simple \mintinline{coq}{reflexivity}:
-
-\begin{listing}[H]
-  \begin{minted}{coq}
-  Theorem le_trans_comm4 {n m p} (Hmn : S n <= S m) (Hmp : S m <= S p) :
-  ~⇓~ (Hmn ~↕~ Hmp) =S (~⇓~ Hmn) ~↕~ (~⇓~ Hmp).
-    reflexivity.
-  Defined.
-  \end{minted}
-\end{listing}
-
-\subsection{The Fibonacci trick}
-We'd initially defined \mintinline{coq}{Cubical} in a monolithic manner, and attempted to use \emph{well-founded induction} to build it up in steps.
-Induction is the process of successively building up a type by reasoning on the result of the previous iteration, and well-founded induction remembers all the previous levels.
-A simple induction is clearly insufficient for our purposes, and as it turned out, well-founded induction was a non-starter too.
-
-Our initial \mintinline{coq}{Record} looked like:
-
-\begin{listing}[H]
-  \begin{minted}{coq}
-    Record Cubical {n : nat} :=
-    {
-    csp {n'} (Hn' : n' <= n) : Type@{l'} ;
-    hd {n'} {Hn' : S n' <= n} : csp Hn' -> csp (⇓ Hn') ;
-    box {n' p} {Hn' : n' <= n} (Hp : p <= n') : csp Hn' -> Type@{l} ;
-    tl {n'} {Hn' : S n' <= n} (D : csp Hn') :
-      box (le_refl n') (hd D) -> Type@{l} ;
-    (* ... *)
-    }.
-  \end{minted}
-\end{listing}
-
-To build it up in steps, we defined a \mintinline{coq}{Fixpoint} as follows, but ran into unification problems:
-
-\begin{listing}[H]
-  \begin{minted}[linenos]{coq}
-    Theorem le_dec {n m} : n <= m -> {n = m} + {n <= pred m} + {m = O}.
-    Admitted.
-    Theorem lower_both {m n} : S m <= S n -> m <= n.
-    Admitted.
-
-    (* ... *)
-
-    Fixpoint cubical {n : nat} : Cubical :=
-    match n with
-    | O => {|
-      csp _ _ := unit;
-      hd _ Hn' _ := ltac:(apply (le_discr Hn'));
-      box _ _ _ _ _ := unit;
-      tl _ Hn' _ _ := ltac:(apply (le_discr Hn'));
-      (* ... *)
-      |}
-    | S n => let cn := cubical (n := n) in
-
-    (* ... *)
-
-    let hdn {n'} (Hn' : S n' <= S n) :=
-    match le_dec (lower_both Hn') return cspn Hn' (* S n' <= S n *) ->
-    cspn (⇓ Hn') (* n' <= S n *) with
-    | inleft Hcmp =>
-    match Hcmp with
-    | left _ (* n' = n *) => fun D => D.1 (* n' = S n *)
-    | right _ (* n' <= pred n *) => fun D => cn.(hd) D (* n' <= n *)
-    end
-    \end{minted}
-  \caption{Type unification on the term \mintinline{coq}{D} fails}
-\end{listing}
-
-We then settled on remembering the previous two levels of induction, a middle-ground between plain induction and well-founded recursion, which we refer to as the Fibonacci trick.
-Our final \mintinline{coq}{Record} for the box looks like:
-
-\begin{listing}[H]
-  \begin{minted}{coq}
-    Record PartialBoxPrev (n : nat) (csp : Type@{l'}) := {
-      box' {p} (Hp : p.+1 <= n) : csp -> Type@{l} ;
-      box'' {p} (Hp : p.+2 <= n) : csp -> Type@{l} ;
-      subbox' {p q} {Hp : p.+2 <= q.+2} (Hq : q.+2 <= n) (ε : side) {D : csp} :
-        box' (↓ (Hp ↕ Hq)) D -> box'' (Hp ↕ Hq) D;
-    }.
-
-    Record PartialBox (n p : nat) (csp : Type@{l'})
-    (PB : PartialBoxBase n csp) := {
-      box (Hp : p <= n) : csp -> Type@{l} ;
-      subbox {q} {Hp : p.+1 <= q.+1} (Hq : q.+1 <= n) (ε : side) {D : csp} :
-      box (↓ (Hp ↕ Hq)) D -> PB.(box') (Hp ↕ Hq) D;
-      cohbox {q r} {Hpr : p.+2 <= r.+2} {Hr : r.+2 <= q.+2} {Hq : q.+2 <= n}
-      {ε : side} {ω : side} {D: csp} (d : box (↓ (⇓ Hpr ↕ (↓ (Hr ↕ Hq)))) D) :
-      PB.(subbox') (Hp := Hpr ↕ Hr) Hq ε (subbox (Hp := ⇓ Hpr) (↓ (Hr ↕ Hq)) ω d) =
-      (PB.(subbox') (Hp := Hpr) (Hr ↕ Hq) ω (subbox (Hp := ↓ (Hpr ↕ Hr)) Hq ε d));
-    }.
-  \end{minted}
-\end{listing}
-
-To build up the box, we'd simply have to induction on \mintinline{coq}{p}:
-
-\begin{listing}[H]
-  \begin{minted}{coq}
-    Definition mkcsp {n : nat} {C : Cubical n} : Type@{l'} :=
-      { D : C.(csp) & C.(Box).(box) (le_refl n) D -> Type@{l} }.
-
-    Definition mkBoxPrev {n} {C : Cubical n} :
-      PartialBoxBase n.+1 mkcsp := {|
-      box' {p} {Hp : p.+1 <= n.+1} {D : mkcsp} := C.(Box).(box) (⇓ Hp) D.1 ;
-      box'' {p} {Hp : p.+2 <= n.+1} {D : mkcsp} := C.(PB).(box') (⇓ Hp) D.1 ;
-      subbox' {p q} {Hp : p.+2 <= q.+2} {Hq : q.+2 <= n.+1} {ε} {D : mkcsp} {d} :=
-        C.(Box).(subbox) (Hp := ⇓ Hp) (⇓ Hq) ε d ;
-    |}.
-
-    Definition mkBox {n} {C : Cubical n} p : PartialBox n.+1 p mkcsp mkPB.
-      induction p.
-      + (* ... *)
-  \end{minted}
-\end{listing}
-
-\subsection{UIP}
-We use UIP in the final coherence condition in \mintinline{coq}{cohbox} and \mintinline{coq}{cohcube}. If we weren't to use UIP in \mintinline{coq}{cohbox}, then we'd have something similar to:
-
-\begin{listing}[H]
-  \begin{minted}{coq}
-    cohbox : subbox ( subbox ... ) = subbox ( subbox ... )
-    coh2box : cohbox ... = cohbox ...
-    ...
-    cohNbox : cohPredNbox ... = cohPredNbox ...
-  \end{minted}
-\end{listing}
-
-In attempting to write the proof without UIP, we'd have a relation between \mintinline{coq}{cohNbox} and \mintinline{coq}{cohPredNbox}, which, we expect to be tricky to prove.
-
 \newpage

### 2022-05-10 paper/paper.tex
paper: s/box/frame, s/cube/filler, s/sub-/restr_{}/

@@
 % cubset
-\newcommand{\csp}[1]{\ensuremath{\mathsf{cubset}_{#1}}}
-\newcommand{\cubeset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
-\newcommand{\cubesetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}
-\newcommand{\cubesetfrom}[2]{\ensuremath{\mathsf{cubset}_{#1}^{\geq#2}}}
+\newcommand{\Xp}[1]{\ensuremath{\mathsf{X}_{#1}}}
+\newcommand{\X}[2]{\ensuremath{\mathsf{X}_{#1}^{<#2}}}
+\newcommand{\Xcomp}[2]{\ensuremath{\mathsf{X}_{#1}^{=#2}}}
+\newcommand{\Xfrom}[2]{\ensuremath{\mathsf{X}_{#1}^{\geq#2}}}
 
-% Box, layer, and cube
-\newcommand{\mybox}[2]{\ensuremath{\mathsf{box}_{#1}^{#2}}}
+% Frame, layer, and filler
+\newcommand{\framep}[2]{\ensuremath{\mathsf{frame}_{#1}^{#2}}}
 \newcommand{\layer}[2]{\ensuremath{\mathsf{layer}_{#1}^{#2}}}
-\newcommand{\cube}[2]{\ensuremath{\mathsf{cube}_{#1}^{#2}}}
+\newcommand{\filler}[2]{\ensuremath{\mathsf{filler}_{#1}^{#2}}}
 
-% Subbox, sublayer, and subcube
-\newcommand{\subbox}[2]{\ensuremath{\mathsf{subbox}_{#1}^{#2}}}
-\newcommand{\sublayer}[2]{\ensuremath{\mathsf{sublayer}_{#1}^{#2}}}
-\newcommand{\subcube}[2]{\ensuremath{\mathsf{subcube}_{#1}^{#2}}}
-\newcommand{\fullbox}[2]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
+% Restriction for frame, layer, and filler
+\newcommand{\restrf}[2]{\ensuremath{\mathsf{restr}_{\mathsf{frame}, #1}^{#2}}}
+\newcommand{\restrl}[2]{\ensuremath{\mathsf{restr}_{\mathsf{layer}, #1}^{#2}}}
+\newcommand{\restrc}[2]{\ensuremath{\mathsf{restr}_{\mathsf{filler}, #1}^{#2}}}
+\newcommand{\fullframe}[2]{\ensuremath{\mathsf{fullframe}_{#1}^{#2}}}
 
-% Coherence conditions
-\newcommand{\cohbox}[2]{\ensuremath{\mathsf{cohbox}_{#1}^{#2}}}
+% Coherence conditions for frame, layer, and filler
+\newcommand{\cohframe}[2]{\ensuremath{\mathsf{cohframe}_{#1}^{#2}}}
 \newcommand{\cohlayer}[2]{\ensuremath{\mathsf{cohlayer}_{#1}^{#2}}}
-\newcommand{\cohcube}[2]{\ensuremath{\mathsf{cohcube}_{#1}^{#2}}}
+\newcommand{\cohfiller}[2]{\ensuremath{\mathsf{cohfiller}_{#1}^{#2}}}
 
@@
 
-\title{An iterated Grothendieck construction of semi-cubical types}
+\title{An indexed construction of semi-simplicial and semi-cubical types}
 \author{
@@
 \begin{abstract}
-  A proposed model of \emph{homotopy type theory} built via a \emph{reverse iterated Grothendieck construction} process formalizing semi-cubical sets in dependent type theory with \emph{extensional equality}.
+  A proposed model of \emph{homotopy type theory} built via a \emph{reverse iterated Grothendieck construction} process formalizing semi-simplicial and semi-cubical sets in dependent type theory with \emph{extensional equality}.
 The accompanying artifact is a Coq formalization that uses highly sophisticated rewriting techniques and pushes the boundary of proof assistant technology.
@@
 
-Our contribution is to model the core of cubical types, semi-cubical sets, in type theory, using an indexed representation, in contrast to previous efforts that use a fibered representation.
+Our contribution is to model the core of semi-simplicial and semi-cubical types, truncated sets, in type theory, using an indexed representation, in contrast to previous efforts that use a fibered representation.
 We use an \emph{iterated reverse-Grothendieck} construction as the basis of our formalization, which we expound on in \ref{sec:grothendieckconstr}.
-Another feature of our work is that, as we are in the type-theoretic setting, we use \emph{unicity of identity of proofs} (UIP), which would be an inherent property in the set-theoretic setting (see \ref{sec:uip}).
+Our work is, in principle axiom-free, although the accompanying artifact uses functional extensionality in order to generalize our work to $n$-truncated sets.
 
@@
 
-\section{The intuition from simplicial sets}
+\section{Simplicial sets}
 Simplicial sets are powerful mathematical objects, that form the basis of much of modern homotopy theory.
@@
 
-\subsection{Towards semi-cubical sets}
+\subsection{Semi-cubical sets}
 We might naively attempt to define $\Cube{}$ identically to \DeltaHat, but let us briefly explain why this wouldn't work, motivating the definition of semi-cubical sets as in \cite{Antolini00}.
@@
 In this section, we give the core of the definition of semi-cubical
-sets as the coinductive limit (see table \ref{tab:barecubicalset}) of a
+sets as the coinductive limit (see table \ref{tab:coind}) of a
 construction of truncated semi-cubical sets.
 
-\subsection{Truncated semi-cubical sets}
-The definition is dispatched over tables \ref{tab:barecubicalsetstructurecore}, \ref{tab:barecubicalsetstructure}, \ref{tab:barecubicalsetfaces} and \ref{tab:barecubicalsetcoherences}.
+\subsection{Truncated sets}
+The definition is dispatched over tables \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and \ref{tab:coh}.
 It describes the structure of the underlying higher-dimensional relations on which cubes and boxes are built, together with the definition of homogeneous $n$-boxes, homogeneous $n$-cubes, together with face operations on boxes and cubes, together with commutation properties of the face operations.
@@
 Note that such relational structure, cubes and boxes are relative to a universe.
-Note the presence of a coherence condition $\cohbox{l}{}$ to ensuring that both sides of the equality in $\sublayer{l}{}$ and $\subcube{l}{}$ are in the same type.
-The proof of $\cohbox{l}{}$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
+Note the presence of a coherence condition $\cohframe{l}{}$ to ensuring that both sides of the equality in $\restrl{l}{}$ and $\restrc{l}{}$ are in the same type.
+The proof of $\cohframe{l}{}$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
 Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\subbox{l}{}$ nor $\cohbox{l}{}$ anymore.
+Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf{l}{}$ nor $\cohframe{l}{}$ anymore.
 
-When reflexivities are excepted, we call the structure thus defined \emph{bare truncated cubical sets}: \emph{bare} because it can be seen as defining semi-cubical sets corresponding to semi-simplicial sets with only faces as part of the structure; \emph{truncated} because we consider only such cubical sets up to some fixed dimension.
+When reflexivities are excepted, we call the structure thus defined \emph{bare truncated sets}: \emph{bare} because it can be seen as defining semi-cubical sets corresponding to semi-simplicial sets with only faces as part of the structure; \emph{truncated} because we consider only such cubical sets up to some fixed dimension.
 
-\begin{eqntable}{Definition of a truncated cubical set (main part of the higher-dimensional relation structure)\label{tab:barecubicalsetstructurecore}}
-  \mc{Type of truncated cubical sets}
-  \eqnline{\cubeset{l}{n}}{}{:}{\sort{l+1}}
-  \eqnline{\cubeset{l}{0}}{}{\defeq}{\unittype}
-  \eqnline{\cubeset{l}{n'+1}}{}{\defeq}{\ensuremath{\Sigma}D:\cubeset{l}{n'}.\,\cubesetcomp{l}{n'} \D}
+\begin{eqntable}{Truncated sets, the core\label{tab:core}}
+  \mc{Type of truncated sets}
+  \eqnline{\X{l}{n}}{}{:}{\sort{l+1}}
+  \eqnline{\X{l}{0}}{}{\defeq}{\unittype}
+  \eqnline{\X{l}{n'+1}}{}{\defeq}{\ensuremath{\Sigma}D:\X{l}{n'}.\,\Xcomp{l}{n'} \D}
 
@@
   \mc{Structure carried at each dimension}
-  \eqnline{\cubesetcomp{l}{n}}{(D:\cubeset{l}{n})}{:}{\sort{l}}
-  \eqnline{\cubesetcomp{l}{n}}{D}{\defeq}{\fullbox{l}{n}\D\imp \sort{l}}
+  \eqnline{\Xcomp{l}{n}}{(D:\X{l}{n})}{:}{\sort{l}}
+  \eqnline{\Xcomp{l}{n}}{D}{\defeq}{\fullframe{l}{n}\D\imp \sort{l}}
 \end{eqntable}
 
-\begin{eqntable}{Definition of a truncated cubical set (boxes)\label{tab:barecubicalsetstructure}}
-  \mc{Full homogeneous $n$-boxes}
-  \eqnline{\fullbox{l}{n}}{(D:\cubeset{l}{n})}{:}{\sort{l}}
-  \eqnline{\fullbox{l}{n}}{D}{\defeq}{\mybox{l}{n,n}\D}
+\begin{eqntable}{$\mathsf{frame}, \mathsf{layer}, \mathsf{filler}$\label{tab:frames}}
+  \mc{Full $n$-frames}
+  \eqnline{\fullframe{l}{n}}{(D:\X{l}{n})}{:}{\sort{l}}
+  \eqnline{\fullframe{l}{n}}{D}{\defeq}{\framep{l}{n,n}\D}
 
@@
 
-  \mc{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}
-  \eqnline{\mybox{l}{n,p,[p \leq n]}}{(D:\cubeset{l}{n})}{:}{\sort{l}}
-  \eqnline{\mybox{l}{n,0}}{D}{\defeq}{\unittype}
-  \eqnline{\mybox{l}{n,p'+1}}{D}{\defeq}{\Sigma d:\mybox{l}{n,p'}\D.\,\layer{l}{n,p'} \D \d}
+  \mc{Partial $n$-frames, $n$-layers, and $n$-fillers}
+  \eqnline{\framep{l}{n,p,[p \leq n]}}{(D:\X{l}{n})}{:}{\sort{l}}
+  \eqnline{\framep{l}{n,0}}{D}{\defeq}{\unittype}
+  \eqnline{\framep{l}{n,p'+1}}{D}{\defeq}{\Sigma d:\framep{l}{n,p'}\D.\,\layer{l}{n,p'} \D \d}
 
@@
 
-  \eqnline{\layer{l}{n,p,[p < n]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D)}}{:}{\sort{l}}
+  \eqnline{\layer{l}{n,p,[p < n]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\sort{l}}
 
-  \eqnline{\layer{l}{n,p}}{D~d}{\defeq}{\makecell{\cube{l}{n-1,p}\hdD\tlD(\subbox{l,L,p}{n,p} \D \d) \\ \times\;\cube{l}{n-1,p}\hdD\tlD(\subbox{l,R,p}{n,p} \D \d)}}
+  \eqnline{\layer{l}{n,p}}{D~d}{\defeq}{\makecell{\filler{l}{n-1,p}\hdD\tlD(\restrf{l,L,p}{n,p} \D \d) \\ \times\;\filler{l}{n-1,p}\hdD\tlD(\restrf{l,R,p}{n,p} \D \d)}}
 
@@
 
-  \eqnline{\cube{l}{n,p,[p \leq n]}}{\makecell{(D:\cubeset{l}{n}) \\(E:\cubesetcomp{l}{n} \D) \\ (d:\mybox{l}{n,p} \D)}}{:}{\sort{l}}
+  \eqnline{\filler{l}{n,p,[p \leq n]}}{\makecell{(D:\X{l}{n}) \\(E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D)}}{:}{\sort{l}}
 
-  \eqnline{\cube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{\E \d}
+  \eqnline{\filler{l}{n,p,[p = n]}}{D~E~d}{\defeq}{\E \d}
 
-  \eqnline{\cube{l}{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma l:\layer{l}{n,p} \D \d.\,\cube{l}{n,p+1} \E(d,l)}
+  \eqnline{\filler{l}{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma l:\layer{l}{n,p} \D \d.\,\filler{l}{n,p+1} \E(d,l)}
 \end{eqntable}
 
-\begin{eqntable}{Definition of a homogeneous bare cubical set ($q$-th projection)\label{tab:barecubicalsetfaces}}
+\begin{eqntable}{$q$-th projection of $\mathsf{restr}$, or faces\label{tab:faces}}
+  \eqnline{\restrf{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\framep{l}{n-1,p}\hdD}
 
-  \eqnline{\subbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D)}}{:}{\mybox{l}{n-1,p}\hdD}
-
-  \eqnline{\subbox{l,\epsilon,q}{n,p'+1}}{D~(d,l)}{\defeq}{(\subbox{l,\epsilon,q}{n,p'} \D\d,\sublayer{l,\epsilon,q-1}{n,p'} \D \d\l)}
+  \eqnline{\restrf{l,\epsilon,q}{n,p'+1}}{D~(d,l)}{\defeq}{(\restrf{l,\epsilon,q}{n,p'} \D\d,\restrl{l,\epsilon,q-1}{n,p'} \D \d\l)}
 
@@
 
-  \eqnline{\sublayer{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D) \\ (b:\layer{l}{n,p} \D \d)}}{:}{\layer{l}{n-1,p}\hdD(\subbox{l,\epsilon,q+1}{n,p} \D \d)}
+  \eqnline{\restrl{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\ (b:\layer{l}{n,p} \D \d)}}{:}{\layer{l}{n-1,p}\hdD(\restrf{l,\epsilon,q+1}{n,p} \D \d)}
 
-  \eqnline{\sublayer{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohbox{l,\epsilon,L,q,p}{n,p} \D \d}(\subcube{l,\epsilon,q}{n-1,p}\hdD\tlD(\subbox{l,L,p}{n,p} \D \d)(c_L)), \\ \;\overright{\cohbox{l,\epsilon,R,q,p}{n,p} \D \d}(\subcube{l,\epsilon,q}{n-1,p}\hdD\tlD(\subbox{l,R,p}{n,p}\D\d)(c_R)))}}
+  \eqnline{\restrl{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohframe{l,\epsilon,L,q,p}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf{l,L,p}{n,p} \D \d)(c_L)), \\ \;\overright{\cohframe{l,\epsilon,R,q,p}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf{l,R,p}{n,p}\D\d)(c_R)))}}
 
@@
 
-  \eqnline{\subcube{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\cubeset{l}{n}) \\ (E:\cubesetcomp{l}{n} \D) \\(d:\mybox{l}{n,p} \D) \\ (b:\cube{l}{n,p} \D\E\d)}}{:}{\cube{l}{n-1,p}\hdD\tlD(\subbox{l,\epsilon,q+1}{n,p} \D \d)}
+  \eqnline{\restrc{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\(d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E\d)}}{:}{\filler{l}{n-1,p}\hdD\tlD(\restrf{l,\epsilon,q+1}{n,p} \D \d)}
 
-  \eqnline{\subcube{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{b_\epsilon}
+  \eqnline{\restrc{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{b_\epsilon}
 
-  \eqnline{\subcube{l,\epsilon,q}{n,p,[p<q]}}{D~E~d~(b,c)}{\defeq}{(\sublayer{l,\epsilon,q}{n,p} \D \d(b),\subcube{l,\epsilon,q}{n,p+1} \D\E(d,b)\c)}
+  \eqnline{\restrc{l,\epsilon,q}{n,p,[p<q]}}{D~E~d~(b,c)}{\defeq}{(\restrl{l,\epsilon,q}{n,p} \D \d(b),\restrc{l,\epsilon,q}{n,p+1} \D\E(d,b)\c)}
 \end{eqntable}
 
-\begin{eqntable}{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)\label{tab:barecubicalsetcoherences}}
+\begin{eqntable}{Commutation of $q$-th projection and $r$-th projection, or coherence conditions\label{tab:coh}}
 
-  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D)}}{:}{\makecell{\subbox{l,\epsilon,q}{n-1,p}\hdD(\subbox{l,\omega,r}{n,p} \D \d) \\ \eqett \subbox{l,\omega,r}{n-1,p}\hdD(\subbox{l,\epsilon,q+1}{n,p} \D \d)}}
+  \eqnline{\cohframe{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\makecell{\restrf{l,\epsilon,q}{n-1,p}\hdD(\restrf{l,\omega,r}{n,p} \D \d) \\ \eqett \restrf{l,\omega,r}{n-1,p}\hdD(\restrf{l,\epsilon,q+1}{n,p} \D \d)}}
 
-  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,0}}{D~\unitpoint}{\defeq}{\reflett(\unitpoint)}
+  \eqnline{\cohframe{l,\epsilon,\omega,q,r}{n,0}}{D~\unitpoint}{\defeq}{\reflett(\unitpoint)}
 
-  \eqnline{\cohbox{l,\epsilon,\omega,q,r}{n,p'+1}}{D~(d,c)}{\defeq}{(\cohbox{l,\epsilon,\omega,q,r}{n,p'} \D\d,\cohlayer{l,\epsilon,\omega,q,r}{n,p'} \D\d\c)}
+  \eqnline{\cohframe{l,\epsilon,\omega,q,r}{n,p'+1}}{D~(d,c)}{\defeq}{(\cohframe{l,\epsilon,\omega,q,r}{n,p'} \D\d,\cohlayer{l,\epsilon,\omega,q,r}{n,p'} \D\d\c)}
 
@@
 
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (d:\mybox{l}{n,p} \D) \\(b:\layer{l}{n,p} \D \d)}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\sublayer{l,\epsilon,q}{n-1,p}\hdD(\subbox{l,\omega,r}{n,p} \D \d)(\sublayer{l,\omega,r}{n,p} \D \d(b))) \\ \eqett \sublayer{l,\omega,r}{n-1,p}\hdD(\subbox{l,\epsilon,q+1}{n,p} \D \d)(\sublayer{l,\epsilon,q+1}{n,p} \D \d(b))}}
+  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\(b:\layer{l}{n,p} \D \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrl{l,\epsilon,q}{n-1,p}\hdD(\restrf{l,\omega,r}{n,p} \D \d)(\restrl{l,\omega,r}{n,p} \D \d(b))) \\ \eqett \restrl{l,\omega,r}{n-1,p}\hdD(\restrf{l,\epsilon,q+1}{n,p} \D \d)(\restrl{l,\epsilon,q+1}{n,p} \D \d(b))}}
 
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p}}{D~d~c}{\defeq}{\makecell{(\cohcube{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\subbox{l,L,p}{n,p} \D \d)(c_L), \\ \;\cohcube{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\subbox{l,R,p}{n,p} \D \d)(c_R))}}
+  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p}}{D~d~c}{\defeq}{\makecell{(\cohfiller{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\restrf{l,L,p}{n,p} \D \d)(c_L), \\ \;\cohfiller{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\restrf{l,R,p}{n,p} \D \d)(c_R))}}
 
@@
 
-  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\cubeset{l}{n}) \\ (E:\cubesetcomp{l}{n} \D) \\ (d:\mybox{l}{n,p} \D) \\ (b:\cube{l}{n,p} \D\E \d)}}{:}{\makecell{\overright{\cohbox{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\subcube{l,\epsilon,q}{n-1,p}\hdD\tlD(\subbox{l,\omega,r}{n,p} \D \d)(\subcube{l,\omega,r}{n,p} \D\E \d(b))) \\ \eqett \subcube{l,\omega,r}{n-1,p}\hdD\tlD(\subbox{l,\epsilon,q+1}{n,p} \D \d)(\subcube{l,\epsilon,q+1}{n,p} \D\E \d(b))}}
+  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf{l,\omega,r}{n,p} \D \d)(\restrc{l,\omega,r}{n,p} \D\E \d(b))) \\ \eqett \restrc{l,\omega,r}{n-1,p}\hdD\tlD(\restrf{l,\epsilon,q+1}{n,p} \D \d)(\restrc{l,\epsilon,q+1}{n,p} \D\E \d(b))}}
 
-  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\subcube{l,\epsilon,q-1}{n-1,p}\hdD\tlD(\subbox{l,\omega,p}{n,p} \D \d)(b_{\epsilon}))}
+  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\restrc{l,\epsilon,q-1}{n-1,p}\hdD\tlD(\restrf{l,\omega,p}{n,p} \D \d)(b_{\epsilon}))}
 
-  \eqnline{\cohcube{l,\epsilon,\omega,q,r}{n,p,[p<r]}}{D~E~d~(b,c)}{\defeq}{(\cohlayer{l,\epsilon,\omega,q,r}{n,p} \D \d(b),\;\cohcube{l,\epsilon,\omega,q,r}{n,p+1} \D\E(d,b)\c)}
+  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p<r]}}{D~E~d~(b,c)}{\defeq}{(\cohlayer{l,\epsilon,\omega,q,r}{n,p} \D \d(b),\;\cohfiller{l,\epsilon,\omega,q,r}{n,p+1} \D\E(d,b)\c)}
 \end{eqntable}
 
-\begin{eqntable}{Definition of a bare cubical set (coinductive structure)\label{tab:barecubicalset}}
-  \mc{Full (non-truncated) cubical sets with degeneracies}
-  \eqnline{\csp{l}}{}{:}{\sort{l+1}}
-  \eqnline{\csp{l}}{}{\defeq}{\cubesetfrom{l}{0}(\star)}
+\begin{eqntable}{Coinductive structure\label{tab:coind}}
+  \eqnline{\Xp{l}}{}{:}{\sort{l+1}}
+  \eqnline{\Xp{l}}{}{\defeq}{\Xfrom{l}{0}(\star)}
   \\
-  \eqnline{\cubesetfrom{l}{n}}{(D:\cubeset{l}{n})}{:}{\sort{l+1}}
-  \eqnline{\cubesetfrom{l}{n}}{D}{\defeq}{\Sigma R:\cubesetcomp{l}{n} \D.\,\cubesetfrom{l}{n+1}(D,R)}
+  \eqnline{\Xfrom{l}{n}}{(D:\X{l}{n})}{:}{\sort{l+1}}
+  \eqnline{\Xfrom{l}{n}}{D}{\defeq}{\Sigma R:\Xcomp{l}{n} \D.\,\Xfrom{l}{n+1}(D,R)}
 \end{eqntable}

### 2022-05-16 paper/paper.tex
README: update loc; it's ~800
paper: introduce magic joinargs lua code!

@@
 % Universes
-\newcommand{\sort}[1]{\ensuremath{\mathsf{U}_{#1}}}
+\newcommand{\U}[1]{\ensuremath{\mathsf{U}_{#1}}}
 
@@
 
+% Comma-separeated optional arguments
+\begin{luacode*}
+  function remove_empty(tbl)
+    for i, v in ipairs(tbl) do
+        if v == "" then
+          table.remove(tbl, i)
+          return remove_empty(tbl)
+        end
+    end
+    return tbl
+  end
+  function join_with_comma(tbl)
+    return table.concat(remove_empty(tbl), ",")
+  end
+\end{luacode*}
+
+\newcommandx{\joinargs}[4][1=,2=,3=,4=]{\directlua{tex.sprint(join_with_comma({"\luaescapestring{#1}";"\luaescapestring{#2}";"\luaescapestring{#3}";"\luaescapestring{#4}"}))}}
+
 % Restriction for frame, layer, and filler
-\newcommand{\restrf}[2]{\ensuremath{\mathsf{restr}_{\mathsf{frame}, #1}^{#2}}}
+\newcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\ensuremath{\mathsf{restr}_{\mathsf{frame}, \joinargs[#1][#2][#3]}^{\joinargs[#4][#5][#6]}}}
 \newcommand{\restrl}[2]{\ensuremath{\mathsf{restr}_{\mathsf{layer}, #1}^{#2}}}
@@
   \begin{tikzcd}
-    X_0 : \sort{} & X_1 : \sort{} \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \sort{} \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
+    X_0 : \U{} & X_1 : \U{} \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \U{} \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
   \end{tikzcd}
@@
 \begin{align*}
-  X_0 & : \sort{}                                                                                                      \\
-  X_1 & : X_0 \times X_0 \rightarrow \sort{}                                                                           \\
-  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \sort{} \\
+  X_0 & : \U{}                                                                                                      \\
+  X_1 & : X_0 \times X_0 \rightarrow \U{}                                                                           \\
+  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \U{} \\
   \ldots
@@
 Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf{l}{}$ nor $\cohframe{l}{}$ anymore.
+Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf[l]$ nor $\cohframe{l}{}$ anymore.
 
@@
   \mc{Type of truncated sets}
-  \eqnline{\X{l}{n}}{}{:}{\sort{l+1}}
+  \eqnline{\X{l}{n}}{}{:}{\U{l+1}}
   \eqnline{\X{l}{0}}{}{\defeq}{\unittype}
@@
   \mc{Structure carried at each dimension}
-  \eqnline{\Xcomp{l}{n}}{(D:\X{l}{n})}{:}{\sort{l}}
-  \eqnline{\Xcomp{l}{n}}{D}{\defeq}{\fullframe{l}{n}\D\imp \sort{l}}
+  \eqnline{\Xcomp{l}{n}}{(D:\X{l}{n})}{:}{\U{l}}
+  \eqnline{\Xcomp{l}{n}}{D}{\defeq}{\fullframe{l}{n}\D\imp \U{l}}
 \end{eqntable}
 
-\begin{eqntable}{$\mathsf{frame}, \mathsf{layer}, \mathsf{filler}$\label{tab:frames}}
+\begin{eqntable}{frame, layer, and filler\label{tab:frames}}
   \mc{Full $n$-frames}
-  \eqnline{\fullframe{l}{n}}{(D:\X{l}{n})}{:}{\sort{l}}
+  \eqnline{\fullframe{l}{n}}{(D:\X{l}{n})}{:}{\U{l}}
   \eqnline{\fullframe{l}{n}}{D}{\defeq}{\framep{l}{n,n}\D}
@@
   \mc{Partial $n$-frames, $n$-layers, and $n$-fillers}
-  \eqnline{\framep{l}{n,p,[p \leq n]}}{(D:\X{l}{n})}{:}{\sort{l}}
+  \eqnline{\framep{l}{n,p,[p \leq n]}}{(D:\X{l}{n})}{:}{\U{l}}
   \eqnline{\framep{l}{n,0}}{D}{\defeq}{\unittype}
@@
 
-  \eqnline{\layer{l}{n,p,[p < n]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\sort{l}}
+  \eqnline{\layer{l}{n,p,[p < n]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\U{l}}
 
-  \eqnline{\layer{l}{n,p}}{D~d}{\defeq}{\makecell{\filler{l}{n-1,p}\hdD\tlD(\restrf{l,L,p}{n,p} \D \d) \\ \times\;\filler{l}{n-1,p}\hdD\tlD(\restrf{l,R,p}{n,p} \D \d)}}
+  \eqnline{\layer{l}{n,p}}{D~d}{\defeq}{\makecell{\filler{l}{n-1,p}\hdD\tlD(\restrf[l][L][p][n][p] \D \d) \\ \times\;\filler{l}{n-1,p}\hdD\tlD(\restrf[l][R][p][n][p] \D \d)}}
 
@@
 
-  \eqnline{\filler{l}{n,p,[p \leq n]}}{\makecell{(D:\X{l}{n}) \\(E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D)}}{:}{\sort{l}}
+  \eqnline{\filler{l}{n,p,[p \leq n]}}{\makecell{(D:\X{l}{n}) \\(E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D)}}{:}{\U{l}}
 
@@
 \begin{eqntable}{$q$-th projection of $\mathsf{restr}$, or faces\label{tab:faces}}
-  \eqnline{\restrf{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\framep{l}{n-1,p}\hdD}
+  \eqnline{\restrf[l][\epsilon][q][n][p][p \leq q \leq n - 1]}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\framep{l}{n-1,p}\hdD}
 
-  \eqnline{\restrf{l,\epsilon,q}{n,p'+1}}{D~(d,l)}{\defeq}{(\restrf{l,\epsilon,q}{n,p'} \D\d,\restrl{l,\epsilon,q-1}{n,p'} \D \d\l)}
+  \eqnline{\restrf[l][\epsilon][q][n][p'+1]}{D~(d,l)}{\defeq}{(\restrf[l][\epsilon][q][n][p'] \D\d,\restrl{l,\epsilon,q-1}{n,p'} \D \d\l)}
 
@@
 
-  \eqnline{\restrl{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\ (b:\layer{l}{n,p} \D \d)}}{:}{\layer{l}{n-1,p}\hdD(\restrf{l,\epsilon,q+1}{n,p} \D \d)}
+  \eqnline{\restrl{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\ (b:\layer{l}{n,p} \D \d)}}{:}{\layer{l}{n-1,p}\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)}
 
-  \eqnline{\restrl{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohframe{l,\epsilon,L,q,p}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf{l,L,p}{n,p} \D \d)(c_L)), \\ \;\overright{\cohframe{l,\epsilon,R,q,p}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf{l,R,p}{n,p}\D\d)(c_R)))}}
+  \eqnline{\restrl{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohframe{l,\epsilon,L,q,p}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf[l][L][p][n][p] \D \d)(c_L)), \\ \;\overright{\cohframe{l,\epsilon,R,q,p}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf[l][R][p][n][p] \D\d)(c_R)))}}
 
@@
 
-  \eqnline{\restrc{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\(d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E\d)}}{:}{\filler{l}{n-1,p}\hdD\tlD(\restrf{l,\epsilon,q+1}{n,p} \D \d)}
+  \eqnline{\restrc{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\(d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E\d)}}{:}{\filler{l}{n-1,p}\hdD\tlD(\restrf[l][\epsilon][q+1][n][p] \D \d)}
 
@@
 
-  \eqnline{\cohframe{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\makecell{\restrf{l,\epsilon,q}{n-1,p}\hdD(\restrf{l,\omega,r}{n,p} \D \d) \\ \eqett \restrf{l,\omega,r}{n-1,p}\hdD(\restrf{l,\epsilon,q+1}{n,p} \D \d)}}
+  \eqnline{\cohframe{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\makecell{\restrf[l][\epsilon][q][n-1][p]\hdD(\restrf[l][\omega][r][n][p] \D \d) \\ \eqett \restrf{l,\omega,r}{n-1,p}\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)}}
 
@@
 
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\(b:\layer{l}{n,p} \D \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrl{l,\epsilon,q}{n-1,p}\hdD(\restrf{l,\omega,r}{n,p} \D \d)(\restrl{l,\omega,r}{n,p} \D \d(b))) \\ \eqett \restrl{l,\omega,r}{n-1,p}\hdD(\restrf{l,\epsilon,q+1}{n,p} \D \d)(\restrl{l,\epsilon,q+1}{n,p} \D \d(b))}}
+  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\(b:\layer{l}{n,p} \D \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrl{l,\epsilon,q}{n-1,p}\hdD(\restrf[l][\omega][r][n][p] \D \d)(\restrl{l,\omega,r}{n,p} \D \d(b))) \\ \eqett \restrl{l,\omega,r}{n-1,p}\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrl{l,\epsilon,q+1}{n,p} \D \d(b))}}
 
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p}}{D~d~c}{\defeq}{\makecell{(\cohfiller{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\restrf{l,L,p}{n,p} \D \d)(c_L), \\ \;\cohfiller{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\restrf{l,R,p}{n,p} \D \d)(c_R))}}
+  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p}}{D~d~c}{\defeq}{\makecell{(\cohfiller{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\restrf[l][L][p][n][p] \D \d)(c_L), \\ \;\cohfiller{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\restrf[l][R][p][n][p] \D \d)(c_R))}}
 
@@
 
-  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf{l,\omega,r}{n,p} \D \d)(\restrc{l,\omega,r}{n,p} \D\E \d(b))) \\ \eqett \restrc{l,\omega,r}{n-1,p}\hdD\tlD(\restrf{l,\epsilon,q+1}{n,p} \D \d)(\restrc{l,\epsilon,q+1}{n,p} \D\E \d(b))}}
+  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf[l][\omega][r][n][p] \D \d)(\restrc{l,\omega,r}{n,p} \D\E \d(b))) \\ \eqett \restrc{l,\omega,r}{n-1,p}\hdD\tlD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrc{l,\epsilon,q+1}{n,p} \D\E \d(b))}}
 
-  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\restrc{l,\epsilon,q-1}{n-1,p}\hdD\tlD(\restrf{l,\omega,p}{n,p} \D \d)(b_{\epsilon}))}
+  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\restrc{l,\epsilon,q-1}{n-1,p}\hdD\tlD(\restrf[l][\omega][p][n][p] \D \d)(b_{\epsilon}))}
 
@@
 \begin{eqntable}{Coinductive structure\label{tab:coind}}
-  \eqnline{\Xp{l}}{}{:}{\sort{l+1}}
+  \eqnline{\Xp{l}}{}{:}{\U{l+1}}
   \eqnline{\Xp{l}}{}{\defeq}{\Xfrom{l}{0}(\star)}
   \\
-  \eqnline{\Xfrom{l}{n}}{(D:\X{l}{n})}{:}{\sort{l+1}}
+  \eqnline{\Xfrom{l}{n}}{(D:\X{l}{n})}{:}{\U{l+1}}
   \eqnline{\Xfrom{l}{n}}{D}{\defeq}{\Sigma R:\Xcomp{l}{n} \D.\,\Xfrom{l}{n+1}(D,R)}

### 2022-05-16 paper/paper.tex
paper: convert all restr macros to rely on joinargs

@@
 \newcommand{\filler}[2]{\ensuremath{\mathsf{filler}_{#1}^{#2}}}
+\newcommand{\fullframe}[2]{\ensuremath{\mathsf{fullframe}_{#1}^{#2}}}
 
@@
 % Restriction for frame, layer, and filler
-\newcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\ensuremath{\mathsf{restr}_{\mathsf{frame}, \joinargs[#1][#2][#3]}^{\joinargs[#4][#5][#6]}}}
-\newcommand{\restrl}[2]{\ensuremath{\mathsf{restr}_{\mathsf{layer}, #1}^{#2}}}
-\newcommand{\restrc}[2]{\ensuremath{\mathsf{restr}_{\mathsf{filler}, #1}^{#2}}}
-\newcommand{\fullframe}[2]{\ensuremath{\mathsf{fullframe}_{#1}^{#2}}}
+\newcommandx{\restr}[7][2=,3=,4=,5=,6=,7=]{\ensuremath{\mathsf{restr}_{\mathsf{#1}, \joinargs[#2][#3][#4]}^{\joinargs[#5][#6][#7]}}}
+\newcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[#1][#2][#3][#4][#5][#6]}
+\newcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[#1][#2][#3][#4][#5][#6]}
+\newcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[#1][#2][#3][#4][#5][#6]}
 
@@
 Note that such relational structure, cubes and boxes are relative to a universe.
-Note the presence of a coherence condition $\cohframe{l}{}$ to ensuring that both sides of the equality in $\restrl{l}{}$ and $\restrc{l}{}$ are in the same type.
+Note the presence of a coherence condition $\cohframe{l}{}$ to ensuring that both sides of the equality in $\restrl[l]$ and $\restrc[l]$ are in the same type.
 The proof of $\cohframe{l}{}$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
@@
 
-  \eqnline{\restrf[l][\epsilon][q][n][p'+1]}{D~(d,l)}{\defeq}{(\restrf[l][\epsilon][q][n][p'] \D\d,\restrl{l,\epsilon,q-1}{n,p'} \D \d\l)}
+  \eqnline{\restrf[l][\epsilon][q][n][p'+1]}{D~(d,l)}{\defeq}{(\restrf[l][\epsilon][q][n][p'] \D\d,\restrl[l][\epsilon][q-1][n][p'] \D \d\l)}
 
@@
 
-  \eqnline{\restrl{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\ (b:\layer{l}{n,p} \D \d)}}{:}{\layer{l}{n-1,p}\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)}
+  \eqnline{\restrl[l][\epsilon][q][n][p][p \leq q \leq n - 2]}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\ (b:\layer{l}{n,p} \D \d)}}{:}{\layer{l}{n-1,p}\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)}
 
-  \eqnline{\restrl{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohframe{l,\epsilon,L,q,p}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf[l][L][p][n][p] \D \d)(c_L)), \\ \;\overright{\cohframe{l,\epsilon,R,q,p}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf[l][R][p][n][p] \D\d)(c_R)))}}
+  \eqnline{\restrl[l][\epsilon][q][n,p]}{D~d~c}{\defeq}{\makecell{(\overright{\cohframe{l,\epsilon,L,q,p}{n,p} \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][L][p][n][p] \D \d)(c_L)), \\ \;\overright{\cohframe{l,\epsilon,R,q,p}{n,p} \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][R][p][n][p] \D\d)(c_R)))}}
 
@@
 
-  \eqnline{\restrc{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\(d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E\d)}}{:}{\filler{l}{n-1,p}\hdD\tlD(\restrf[l][\epsilon][q+1][n][p] \D \d)}
+  \eqnline{\restrc[l][\epsilon][q][n][p][p \leq q \leq n - 1]}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\(d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E\d)}}{:}{\filler{l}{n-1,p}\hdD\tlD(\restrf[l][\epsilon][q+1][n][p] \D \d)}
 
-  \eqnline{\restrc{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{b_\epsilon}
+  \eqnline{\restrc[l][\epsilon][q][n][p][p=q]}{D~E~d~(b,\_)}{\defeq}{b_\epsilon}
 
-  \eqnline{\restrc{l,\epsilon,q}{n,p,[p<q]}}{D~E~d~(b,c)}{\defeq}{(\restrl{l,\epsilon,q}{n,p} \D \d(b),\restrc{l,\epsilon,q}{n,p+1} \D\E(d,b)\c)}
+  \eqnline{\restrc[l][\epsilon][q][n][p][p<q]}{D~E~d~(b,c)}{\defeq}{(\restrl[l][\epsilon][q][n][p] \D \d(b),\restrc[l][\epsilon][q][n][p+1] \D\E(d,b)\c)}
 \end{eqntable}
@@
 
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\(b:\layer{l}{n,p} \D \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrl{l,\epsilon,q}{n-1,p}\hdD(\restrf[l][\omega][r][n][p] \D \d)(\restrl{l,\omega,r}{n,p} \D \d(b))) \\ \eqett \restrl{l,\omega,r}{n-1,p}\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrl{l,\epsilon,q+1}{n,p} \D \d(b))}}
+  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\(b:\layer{l}{n,p} \D \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrl[l][\epsilon][q][n-1][p]\hdD(\restrf[l][\omega][r][n][p] \D \d)(\restrl[l][\omega][r][n][p] \D \d(b))) \\ \eqett \restrl[l][\omega][r][n-1][p]\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrl[l][\epsilon][q+1][n][p] \D \d(b))}}
 
@@
 
-  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrc{l,\epsilon,q}{n-1,p}\hdD\tlD(\restrf[l][\omega][r][n][p] \D \d)(\restrc{l,\omega,r}{n,p} \D\E \d(b))) \\ \eqett \restrc{l,\omega,r}{n-1,p}\hdD\tlD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrc{l,\epsilon,q+1}{n,p} \D\E \d(b))}}
+  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][\omega][r][n][p] \D \d)(\restrc[l][\omega][r][n][p] \D\E \d(b))) \\ \eqett \restrc[l][\omega][r][n-1][p]\hdD\tlD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrc[l][\epsilon][q+1][n][p] \D\E \d(b))}}
 
-  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\restrc{l,\epsilon,q-1}{n-1,p}\hdD\tlD(\restrf[l][\omega][p][n][p] \D \d)(b_{\epsilon}))}
+  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\restrc[l][\epsilon][q-1][n-1][p]\hdD\tlD(\restrf[l][\omega][p][n][p] \D \d)(b_{\epsilon}))}
 

### 2022-05-16 paper/paper.tex
paper: update all the coh macros to use joinargs

@@
 
-\newcommandx{\joinargs}[4][1=,2=,3=,4=]{\directlua{tex.sprint(join_with_comma({"\luaescapestring{#1}";"\luaescapestring{#2}";"\luaescapestring{#3}";"\luaescapestring{#4}"}))}}
+\newcommandx{\joinargs}[5][1=,2=,3=,4=,5=]{\directlua{tex.sprint(join_with_comma({"\luaescapestring{#1}";"\luaescapestring{#2}";"\luaescapestring{#3}";"\luaescapestring{#4}";"\luaescapestring{#5}"}))}}
 
@@
 % Coherence conditions for frame, layer, and filler
-\newcommand{\cohframe}[2]{\ensuremath{\mathsf{cohframe}_{#1}^{#2}}}
-\newcommand{\cohlayer}[2]{\ensuremath{\mathsf{cohlayer}_{#1}^{#2}}}
-\newcommand{\cohfiller}[2]{\ensuremath{\mathsf{cohfiller}_{#1}^{#2}}}
+\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{#1}_{\joinargs[#2][#3][#4][#5][#6]}^{\joinargs[#7][#8][#9]}}}
+\newcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6][#7][#8]}
+\newcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
+\newcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}
 
@@
 Note that such relational structure, cubes and boxes are relative to a universe.
-Note the presence of a coherence condition $\cohframe{l}{}$ to ensuring that both sides of the equality in $\restrl[l]$ and $\restrc[l]$ are in the same type.
-The proof of $\cohframe{l}{}$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
+Note the presence of a coherence condition $\cohframe[l]$ to ensuring that both sides of the equality in $\restrl[l]$ and $\restrc[l]$ are in the same type.
+The proof of $\cohframe[l]$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
 Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf[l]$ nor $\cohframe{l}{}$ anymore.
+Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf[l]$ nor $\cohframe[l]$ anymore.
 
@@
 
-  \eqnline{\restrl[l][\epsilon][q][n,p]}{D~d~c}{\defeq}{\makecell{(\overright{\cohframe{l,\epsilon,L,q,p}{n,p} \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][L][p][n][p] \D \d)(c_L)), \\ \;\overright{\cohframe{l,\epsilon,R,q,p}{n,p} \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][R][p][n][p] \D\d)(c_R)))}}
+  \eqnline{\restrl[l][\epsilon][q][n,p]}{D~d~c}{\defeq}{\makecell{(\overright{\cohframe[l][\epsilon][L][q][p][n][p] \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][L][p][n][p] \D \d)(c_L)), \\ \;\overright{\cohframe[l][\epsilon][R][q][p][n][p] \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][R][p][n][p] \D\d)(c_R)))}}
 
@@
 
-  \eqnline{\cohframe{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\makecell{\restrf[l][\epsilon][q][n-1][p]\hdD(\restrf[l][\omega][r][n][p] \D \d) \\ \eqett \restrf{l,\omega,r}{n-1,p}\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)}}
+  \eqnline{\cohframe[l][\epsilon][\omega][q][r][n][p][p \leq r \leq q \leq n - 2]}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\makecell{\restrf[l][\epsilon][q][n-1][p] \hdD(\restrf[l][\omega][r][n][p] \D \d) \\ \eqett \restrf[l][\omega][r][n-1][p] \hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)}}
 
-  \eqnline{\cohframe{l,\epsilon,\omega,q,r}{n,0}}{D~\unitpoint}{\defeq}{\reflett(\unitpoint)}
+  \eqnline{\cohframe[l][\epsilon][\omega][q][r][n][0]}{D~\unitpoint}{\defeq}{\reflett(\unitpoint)}
 
-  \eqnline{\cohframe{l,\epsilon,\omega,q,r}{n,p'+1}}{D~(d,c)}{\defeq}{(\cohframe{l,\epsilon,\omega,q,r}{n,p'} \D\d,\cohlayer{l,\epsilon,\omega,q,r}{n,p'} \D\d\c)}
+  \eqnline{\cohframe[l][\epsilon][\omega][q][r][n][p'+1]}{D~(d,c)}{\defeq}{(\cohframe[l][\epsilon][\omega][q][r][n][p'] \D\d,\cohlayer[l][\epsilon][\omega][q][r][n][p'] \D\d\c)}
 
@@
 
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p,[p < r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\(b:\layer{l}{n,p} \D \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrl[l][\epsilon][q][n-1][p]\hdD(\restrf[l][\omega][r][n][p] \D \d)(\restrl[l][\omega][r][n][p] \D \d(b))) \\ \eqett \restrl[l][\omega][r][n-1][p]\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrl[l][\epsilon][q+1][n][p] \D \d(b))}}
+  \eqnline{\cohlayer[l][\epsilon][\omega][q][r][n][p][p < r \leq q \leq n - 2]}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\(b:\layer{l}{n,p} \D \d)}}{:}{\makecell{\overright{\cohframe[l][\epsilon][\omega][q+1][r+1][n][p] \D \d}(\restrl[l][\epsilon][q][n-1][p]\hdD(\restrf[l][\omega][r][n][p] \D \d)(\restrl[l][\omega][r][n][p] \D \d(b))) \\ \eqett \restrl[l][\omega][r][n-1][p]\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrl[l][\epsilon][q+1][n][p] \D \d(b))}}
 
-  \eqnline{\cohlayer{l,\epsilon,\omega,q,r}{n,p}}{D~d~c}{\defeq}{\makecell{(\cohfiller{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\restrf[l][L][p][n][p] \D \d)(c_L), \\ \;\cohfiller{l,\epsilon,\omega,q-1,r-1}{n-1,p}\hdD\tlD(\restrf[l][R][p][n][p] \D \d)(c_R))}}
+  \eqnline{\cohlayer[l][\epsilon][\omega][q][r][n][p]}{D~d~c}{\defeq}{\makecell{(\cohfiller[l][\epsilon][\omega][q-1][r-1][n-1][p]\hdD\tlD(\restrf[l][L][p][n][p] \D \d)(c_L), \\ \;\cohfiller[l][\epsilon][\omega][q-1][r-1][n-1][p] \hdD\tlD(\restrf[l][R][p][n][p] \D \d)(c_R))}}
 
@@
 
-  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p \leq r \leq q \leq n - 2]}}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E \d)}}{:}{\makecell{\overright{\cohframe{l,\epsilon,\omega,q+1,r+1}{n,p} \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][\omega][r][n][p] \D \d)(\restrc[l][\omega][r][n][p] \D\E \d(b))) \\ \eqett \restrc[l][\omega][r][n-1][p]\hdD\tlD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrc[l][\epsilon][q+1][n][p] \D\E \d(b))}}
+  \eqnline{\cohfiller[l][\epsilon][\omega][q][r][n][p][p \leq r \leq q \leq n - 2]}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E \d)}}{:}{\makecell{\overright{\cohframe[l][\epsilon][\omega][q+1][r+1][n][p] \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][\omega][r][n][p] \D \d)(\restrc[l][\omega][r][n][p] \D\E \d(b))) \\ \eqett \restrc[l][\omega][r][n-1][p]\hdD\tlD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrc[l][\epsilon][q+1][n][p] \D\E \d(b))}}
 
-  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p=r]}}{D~E~d~(b,\_)}{\defeq}{\reflett(\restrc[l][\epsilon][q-1][n-1][p]\hdD\tlD(\restrf[l][\omega][p][n][p] \D \d)(b_{\epsilon}))}
+  \eqnline{\cohfiller[l][\epsilon][\omega][q][r][n][p][p=r]}{D~E~d~(b,\_)}{\defeq}{\reflett(\restrc[l][\epsilon][q-1][n-1][p]\hdD\tlD(\restrf[l][\omega][p][n][p] \D \d)(b_{\epsilon}))}
 
-  \eqnline{\cohfiller{l,\epsilon,\omega,q,r}{n,p,[p<r]}}{D~E~d~(b,c)}{\defeq}{(\cohlayer{l,\epsilon,\omega,q,r}{n,p} \D \d(b),\;\cohfiller{l,\epsilon,\omega,q,r}{n,p+1} \D\E(d,b)\c)}
+  \eqnline{\cohfiller[l][\epsilon][\omega][q][r][n][p][p<r]}{D~E~d~(b,c)}{\defeq}{(\cohlayer[l][\epsilon][\omega][q][r][n][p] \D \d(b),\;\cohfiller[l][\epsilon][\omega][q][r][n][p+1] \D\E(d,b)\c)}
 \end{eqntable}

### 2022-05-16 paper/paper.tex
paper: convert frame, layer, filler to use joinargs as well
tab-*.tex: split out tables; attempt abbreviated tables

@@
 
-% Simplicial and Cubical sets
-\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
-\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
-\renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
-\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
-
-% Universes
-\newcommand{\U}[1]{\ensuremath{\mathsf{U}_{#1}}}
-
-% The unit type
-\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
-\newcommand{\unitpoint}{\ensuremath{\star}}
-
-% Definitional and extensional equality
-\newcommand{\defeq}{\ensuremath{\triangleq}}
-\newcommand{\eqett}{\ensuremath{\equiv_{\mathit{ETT}}}}
-\newcommand{\reflett}{\ensuremath{\mathsf{refl}_{\mathit{ETT}}}}
-
-% cubset
-\newcommand{\Xp}[1]{\ensuremath{\mathsf{X}_{#1}}}
-\newcommand{\X}[2]{\ensuremath{\mathsf{X}_{#1}^{<#2}}}
-\newcommand{\Xcomp}[2]{\ensuremath{\mathsf{X}_{#1}^{=#2}}}
-\newcommand{\Xfrom}[2]{\ensuremath{\mathsf{X}_{#1}^{\geq#2}}}
-
-% Frame, layer, and filler
-\newcommand{\framep}[2]{\ensuremath{\mathsf{frame}_{#1}^{#2}}}
-\newcommand{\layer}[2]{\ensuremath{\mathsf{layer}_{#1}^{#2}}}
-\newcommand{\filler}[2]{\ensuremath{\mathsf{filler}_{#1}^{#2}}}
-\newcommand{\fullframe}[2]{\ensuremath{\mathsf{fullframe}_{#1}^{#2}}}
-
+% Some lua magic to join a variable number of arguments with commas
 % Comma-separeated optional arguments
@@
 
-% Restriction for frame, layer, and filler
+% Simplicial and Cubical sets
+\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
+\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
+\renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
+\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
+
+% Universe, referred to as U
+\newcommand{\U}[1]{\ensuremath{\mathsf{U}_{#1}}}
+
+% The unit type
+\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
+\newcommand{\unitpoint}{\ensuremath{\star}}
+
+% Definitional and extensional equality
+\newcommand{\defeq}{\ensuremath{\triangleq}}
+\newcommand{\eqett}{\ensuremath{\equiv_{\mathit{ETT}}}}
+\newcommand{\reflett}{\ensuremath{\mathsf{refl}_{\mathit{ETT}}}}
+
+% Truncated sets, otherwise referred to as X
+\newcommand{\Xp}[1]{\ensuremath{\mathsf{X}_{#1}}}
+\newcommand{\X}[2]{\ensuremath{\mathsf{X}_{#1}^{<#2}}}
+\newcommand{\Xcomp}[2]{\ensuremath{\mathsf{X}_{#1}^{=#2}}}
+\newcommand{\Xfrom}[2]{\ensuremath{\mathsf{X}_{#1}^{\geq#2}}}
+
+% Frame, layer, and filler: the general macro
+\newcommandx{\prim}[5][2=,3=,4=,5=]{\ensuremath{\mathsf{#1}_{#2}^{\joinargs[#3][#4][#5]}}}
+
+% Full frame
+\newcommand{\fullframe}[2]{\ensuremath{\mathsf{fullframe}_{#1}^{#2}}}
+
+% Restriction for frame, layer, and filler: the general macro
 \newcommandx{\restr}[7][2=,3=,4=,5=,6=,7=]{\ensuremath{\mathsf{restr}_{\mathsf{#1}, \joinargs[#2][#3][#4]}^{\joinargs[#5][#6][#7]}}}
-\newcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[#1][#2][#3][#4][#5][#6]}
-\newcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[#1][#2][#3][#4][#5][#6]}
-\newcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[#1][#2][#3][#4][#5][#6]}
 
-% Coherence conditions for frame, layer, and filler
+% Coherence conditions for frame, layer, and filler: the general macro
 \newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{#1}_{\joinargs[#2][#3][#4][#5][#6]}^{\joinargs[#7][#8][#9]}}}
-\newcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6][#7][#8]}
-\newcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
-\newcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}
 
@@
 \subsection{Truncated sets}
+% Now, we write the type theory bit, and input the abbreviated tables
+
+% Frame, layer, and filler
+\newcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[#1][#2][#3][#4]}
+\newcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[#1][#2][#3][#4]}
+\newcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[#1][#2][#3][#4]}
+
+% Restriction for frame, layer, and filler
+\newcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[][#2][][#4][#5][#6]}
+\newcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[][#2][][#4][#5][#6]}
+\newcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[][#2][][#4][#5][#6]}
+
+% Coherence conditions for frame, layer, and filler
+\newcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[][#2][#3][][][][][#8]}
+\newcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
+\newcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}
+
 The definition is dispatched over tables \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and \ref{tab:coh}.
@@
 
-\begin{eqntable}{Truncated sets, the core\label{tab:core}}
-  \mc{Type of truncated sets}
-  \eqnline{\X{l}{n}}{}{:}{\U{l+1}}
-  \eqnline{\X{l}{0}}{}{\defeq}{\unittype}
-  \eqnline{\X{l}{n'+1}}{}{\defeq}{\ensuremath{\Sigma}D:\X{l}{n'}.\,\Xcomp{l}{n'} \D}
+\input{tab-core.tex}
+\input{tab-frames.tex}
+\input{tab-faces.tex}
 
-  \\
+% Restriction for frame, layer, and filler
+\renewcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[#1][#2][#3][#4][#5][#6]}
+\renewcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[#1][#2][#3][#4][#5][#6]}
+\renewcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[#1][#2][#3][#4][#5][#6]}
 
-  \mc{Structure carried at each dimension}
-  \eqnline{\Xcomp{l}{n}}{(D:\X{l}{n})}{:}{\U{l}}
-  \eqnline{\Xcomp{l}{n}}{D}{\defeq}{\fullframe{l}{n}\D\imp \U{l}}
-\end{eqntable}
+% Coherence conditions for frame, layer, and filler
+\renewcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[][#2][#3][#4][#5][][#7][#8]}
+\renewcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[][#2][#3][#4][#5][][#7][#8]}
+\renewcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[][#2][#3][#4][#5][][#7][#8]}
 
-\begin{eqntable}{frame, layer, and filler\label{tab:frames}}
-  \mc{Full $n$-frames}
-  \eqnline{\fullframe{l}{n}}{(D:\X{l}{n})}{:}{\U{l}}
-  \eqnline{\fullframe{l}{n}}{D}{\defeq}{\framep{l}{n,n}\D}
-
-  \\
-
-  \mc{Partial $n$-frames, $n$-layers, and $n$-fillers}
-  \eqnline{\framep{l}{n,p,[p \leq n]}}{(D:\X{l}{n})}{:}{\U{l}}
-  \eqnline{\framep{l}{n,0}}{D}{\defeq}{\unittype}
-  \eqnline{\framep{l}{n,p'+1}}{D}{\defeq}{\Sigma d:\framep{l}{n,p'}\D.\,\layer{l}{n,p'} \D \d}
-
-  \\
-
-  \eqnline{\layer{l}{n,p,[p < n]}}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\U{l}}
-
-  \eqnline{\layer{l}{n,p}}{D~d}{\defeq}{\makecell{\filler{l}{n-1,p}\hdD\tlD(\restrf[l][L][p][n][p] \D \d) \\ \times\;\filler{l}{n-1,p}\hdD\tlD(\restrf[l][R][p][n][p] \D \d)}}
-
-  \\
-
-  \eqnline{\filler{l}{n,p,[p \leq n]}}{\makecell{(D:\X{l}{n}) \\(E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D)}}{:}{\U{l}}
-
-  \eqnline{\filler{l}{n,p,[p = n]}}{D~E~d}{\defeq}{\E \d}
-
-  \eqnline{\filler{l}{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma l:\layer{l}{n,p} \D \d.\,\filler{l}{n,p+1} \E(d,l)}
-\end{eqntable}
-
-\begin{eqntable}{$q$-th projection of $\mathsf{restr}$, or faces\label{tab:faces}}
-  \eqnline{\restrf[l][\epsilon][q][n][p][p \leq q \leq n - 1]}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\framep{l}{n-1,p}\hdD}
-
-  \eqnline{\restrf[l][\epsilon][q][n][p'+1]}{D~(d,l)}{\defeq}{(\restrf[l][\epsilon][q][n][p'] \D\d,\restrl[l][\epsilon][q-1][n][p'] \D \d\l)}
-
-  \\
-
-  \eqnline{\restrl[l][\epsilon][q][n][p][p \leq q \leq n - 2]}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\ (b:\layer{l}{n,p} \D \d)}}{:}{\layer{l}{n-1,p}\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)}
-
-  \eqnline{\restrl[l][\epsilon][q][n,p]}{D~d~c}{\defeq}{\makecell{(\overright{\cohframe[l][\epsilon][L][q][p][n][p] \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][L][p][n][p] \D \d)(c_L)), \\ \;\overright{\cohframe[l][\epsilon][R][q][p][n][p] \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][R][p][n][p] \D\d)(c_R)))}}
-
-  \\
-
-  \eqnline{\restrc[l][\epsilon][q][n][p][p \leq q \leq n - 1]}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\(d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E\d)}}{:}{\filler{l}{n-1,p}\hdD\tlD(\restrf[l][\epsilon][q+1][n][p] \D \d)}
-
-  \eqnline{\restrc[l][\epsilon][q][n][p][p=q]}{D~E~d~(b,\_)}{\defeq}{b_\epsilon}
-
-  \eqnline{\restrc[l][\epsilon][q][n][p][p<q]}{D~E~d~(b,c)}{\defeq}{(\restrl[l][\epsilon][q][n][p] \D \d(b),\restrc[l][\epsilon][q][n][p+1] \D\E(d,b)\c)}
-\end{eqntable}
-
-\begin{eqntable}{Commutation of $q$-th projection and $r$-th projection, or coherence conditions\label{tab:coh}}
-
-  \eqnline{\cohframe[l][\epsilon][\omega][q][r][n][p][p \leq r \leq q \leq n - 2]}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D)}}{:}{\makecell{\restrf[l][\epsilon][q][n-1][p] \hdD(\restrf[l][\omega][r][n][p] \D \d) \\ \eqett \restrf[l][\omega][r][n-1][p] \hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)}}
-
-  \eqnline{\cohframe[l][\epsilon][\omega][q][r][n][0]}{D~\unitpoint}{\defeq}{\reflett(\unitpoint)}
-
-  \eqnline{\cohframe[l][\epsilon][\omega][q][r][n][p'+1]}{D~(d,c)}{\defeq}{(\cohframe[l][\epsilon][\omega][q][r][n][p'] \D\d,\cohlayer[l][\epsilon][\omega][q][r][n][p'] \D\d\c)}
-
-  \\
-
-  \eqnline{\cohlayer[l][\epsilon][\omega][q][r][n][p][p < r \leq q \leq n - 2]}{\makecell{(D:\X{l}{n}) \\ (d:\framep{l}{n,p} \D) \\(b:\layer{l}{n,p} \D \d)}}{:}{\makecell{\overright{\cohframe[l][\epsilon][\omega][q+1][r+1][n][p] \D \d}(\restrl[l][\epsilon][q][n-1][p]\hdD(\restrf[l][\omega][r][n][p] \D \d)(\restrl[l][\omega][r][n][p] \D \d(b))) \\ \eqett \restrl[l][\omega][r][n-1][p]\hdD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrl[l][\epsilon][q+1][n][p] \D \d(b))}}
-
-  \eqnline{\cohlayer[l][\epsilon][\omega][q][r][n][p]}{D~d~c}{\defeq}{\makecell{(\cohfiller[l][\epsilon][\omega][q-1][r-1][n-1][p]\hdD\tlD(\restrf[l][L][p][n][p] \D \d)(c_L), \\ \;\cohfiller[l][\epsilon][\omega][q-1][r-1][n-1][p] \hdD\tlD(\restrf[l][R][p][n][p] \D \d)(c_R))}}
-
-  \\
-
-  \eqnline{\cohfiller[l][\epsilon][\omega][q][r][n][p][p \leq r \leq q \leq n - 2]}{\makecell{(D:\X{l}{n}) \\ (E:\Xcomp{l}{n} \D) \\ (d:\framep{l}{n,p} \D) \\ (b:\filler{l}{n,p} \D\E \d)}}{:}{\makecell{\overright{\cohframe[l][\epsilon][\omega][q+1][r+1][n][p] \D \d}(\restrc[l][\epsilon][q][n-1][p]\hdD\tlD(\restrf[l][\omega][r][n][p] \D \d)(\restrc[l][\omega][r][n][p] \D\E \d(b))) \\ \eqett \restrc[l][\omega][r][n-1][p]\hdD\tlD(\restrf[l][\epsilon][q+1][n][p] \D \d)(\restrc[l][\epsilon][q+1][n][p] \D\E \d(b))}}
-
-  \eqnline{\cohfiller[l][\epsilon][\omega][q][r][n][p][p=r]}{D~E~d~(b,\_)}{\defeq}{\reflett(\restrc[l][\epsilon][q-1][n-1][p]\hdD\tlD(\restrf[l][\omega][p][n][p] \D \d)(b_{\epsilon}))}
-
-  \eqnline{\cohfiller[l][\epsilon][\omega][q][r][n][p][p<r]}{D~E~d~(b,c)}{\defeq}{(\cohlayer[l][\epsilon][\omega][q][r][n][p] \D \d(b),\;\cohfiller[l][\epsilon][\omega][q][r][n][p+1] \D\E(d,b)\c)}
-\end{eqntable}
-
-\begin{eqntable}{Coinductive structure\label{tab:coind}}
-  \eqnline{\Xp{l}}{}{:}{\U{l+1}}
-  \eqnline{\Xp{l}}{}{\defeq}{\Xfrom{l}{0}(\star)}
-  \\
-  \eqnline{\Xfrom{l}{n}}{(D:\X{l}{n})}{:}{\U{l+1}}
-  \eqnline{\Xfrom{l}{n}}{D}{\defeq}{\Sigma R:\Xcomp{l}{n} \D.\,\Xfrom{l}{n+1}(D,R)}
-\end{eqntable}
+\input{tab-coh.tex}
+\input{tab-coind.tex}
 
 \newpage
+
+\appendix
+\section{Tables in full detail}
+% Frame, layer, and filler
+\renewcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[#1][#2][#3][#4]}
+\renewcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[#1][#2][#3][#4]}
+\renewcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[#1][#2][#3][#4]}
+
+% Coherence conditions for frame, layer, and filler
+\renewcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6][#7][#8]}
+\renewcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
+\renewcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}
+
+\input{tab-core.tex}
+\input{tab-frames.tex}
+\input{tab-faces.tex}
+\input{tab-coh.tex}
+\input{tab-coind.tex}
 

### 2022-05-16 paper/paper.tex
paper: refine abbreviated table
paper: colorize table!
paper: polish; make some corrections to tables

@@
 % Universe, referred to as U
-\newcommand{\U}[1]{\ensuremath{\mathsf{U}_{#1}}}
+\newcommand{\U}[1]{\ensuremath{\mathsf{\color{spanish-blue}{U}}_{#1}}}
 
@@
 % Truncated sets, otherwise referred to as X
-\newcommand{\Xp}[1]{\ensuremath{\mathsf{X}_{#1}}}
-\newcommand{\X}[2]{\ensuremath{\mathsf{X}_{#1}^{<#2}}}
-\newcommand{\Xcomp}[2]{\ensuremath{\mathsf{X}_{#1}^{=#2}}}
-\newcommand{\Xfrom}[2]{\ensuremath{\mathsf{X}_{#1}^{\geq#2}}}
+\newcommand{\Xp}[1]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}}}
+\newcommand{\X}[2]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{<#2}}}
+\newcommand{\Xcomp}[2]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{=#2}}}
+\newcommand{\Xfrom}[2]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{\geq#2}}}
 
 % Frame, layer, and filler: the general macro
-\newcommandx{\prim}[5][2=,3=,4=,5=]{\ensuremath{\mathsf{#1}_{#2}^{\joinargs[#3][#4][#5]}}}
+\newcommandx{\prim}[5][2=,3=,4=,5=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs[#3][#4][#5]}}}
 
 % Full frame
-\newcommand{\fullframe}[2]{\ensuremath{\mathsf{fullframe}_{#1}^{#2}}}
+\newcommandx{\fullframe}[2][1=,2=]{\ensuremath{\mathsf{\color{indian-yellow}{fullframe}}^{#2}}}
 
 % Restriction for frame, layer, and filler: the general macro
-\newcommandx{\restr}[7][2=,3=,4=,5=,6=,7=]{\ensuremath{\mathsf{restr}_{\mathsf{#1}, \joinargs[#2][#3][#4]}^{\joinargs[#5][#6][#7]}}}
+\newcommandx{\restr}[7][2=,3=,4=,5=,6=,7=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}, \joinargs[#2][#3][#4]}^{\joinargs[#5][#6][#7]}}}
 
 % Coherence conditions for frame, layer, and filler: the general macro
-\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{#1}_{\joinargs[#2][#3][#4][#5][#6]}^{\joinargs[#7][#8][#9]}}}
+\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{#1}}_{\joinargs[#2][#3][#4][#5][#6]}^{\joinargs[#7][#8][#9]}}}
 
@@
 \begin{abstract}
-  A proposed model of \emph{homotopy type theory} built via a \emph{reverse iterated Grothendieck construction} process formalizing semi-simplicial and semi-cubical sets in dependent type theory with \emph{extensional equality}.
-The accompanying artifact is a Coq formalization that uses highly sophisticated rewriting techniques and pushes the boundary of proof assistant technology.
+  A model of \emph{homotopy type theory}, that formalizes \emph{truncated} $n$-types in dependent type theory.
+The accompanying artifact is an axiomless Coq formalization~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to truncated $n$-types; if one were to instantiate our development for a particular type (say, augmented simplicial types), this requirement vanishes.} that uses sophisticated rewriting techniques and pushes the boundary of proof assistant technology.
 \end{abstract}
@@
 
-Our contribution is to model the core of semi-simplicial and semi-cubical types, truncated sets, in type theory, using an indexed representation, in contrast to previous efforts that use a fibered representation.
-We use an \emph{iterated reverse-Grothendieck} construction as the basis of our formalization, which we expound on in \ref{sec:grothendieckconstr}.
+Our contribution is to model the core of semi-cubical sets that naturally generalizes to augmented simplicial sets in type theory, and we call our generalization \emph{truncated $n$-sets}.
+In contrast to previous efforts that use a fibered representation, we use an indexed representation, that can be derived from the fibered one using a \emph{iterated reverse-Grothendieck} construction.
 Our work is, in principle axiom-free, although the accompanying artifact uses functional extensionality in order to generalize our work to $n$-truncated sets.
@@
 
+The outline of the paper is as follows.
+First, we take the opportunity to familize the reader with simplicial sets, as it appears in mathematical literature, along with a short section on semi-cubical sets.
+We then proceed to explain our construction, with the help of diagrams.
+Before spelling out the details of our formalization in type-theoretic language, we have a section on the unicity of identity proofs (UIP), since the use of \mintinline{coq}{SProp} has greatly eased our Coq formalization.
+
 \section{Simplicial sets}
 Simplicial sets are powerful mathematical objects, that form the basis of much of modern homotopy theory.
-Their power derives from the fact that their homotopy category is exceptionally well-behaved, and different model structures on them, as we will see in the following chapter.
+Their power derives from the fact that their homotopy category is exceptionally well-behaved, and that there are multiple model structures defined on them.
 Unlike CW-complexes that rely on pure topological notions like spheres and disks to ``tame'' a topological space, the definition of simplicial sets is purely categorical, and exist independent of topological spaces.
-The geometric realization and singular complex functors facilitate travelling back-and-forth between simplicial sets and topological spaces, and these are non-trivial constructions.
-As such, simplicial sets exist purely in the imagination of the mathematician; each simplicial set has an infinite number of degenerate simplices, and they are not particularly well-suited to machine-based representation.
+The \emph{geometric realization} and \emph{singular complex} functors facilitate travelling back-and-forth between simplicial sets and topological spaces, and these are non-trivial constructions.
+As such, simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
 
@@
 With these intuitions in place, we proceed with a purely categorical treatment.
-Emily Riehl's \cite{Riehl11} is a well-written manuscript on the subject.
+Emily Riehl's \cite{Riehl11} is an especially well-written manuscript on the subject.
 
@@
 
-\subsection{Motivation for \texorpdfstring{\DeltaHat}{delta sets}}
-As hinted earlier, simplicial sets are ill-suited for machine-based representation, due to the infinite number of degenerate simplices that are uninteresting from the point of view of cubical type theory.
-To remedy this problem, let us instead use \DeltaHat, and proceed towards building, what is called \emph{semi-cubical sets} in literature.
-$\DeltaHat$ is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are \emph{strictly} order-preserving.
+\subsection{\texorpdfstring{\DeltaHat}{Delta sets}}
+As a first step towards formalizing simplicial sets, we restrict outselves to representing \emph{augmented simplicial sets}, which are described roughly as delta-sets in mathematical literature, which forgets about the degeneracies.
+We now proceed to describe \DeltaHat, which is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are \emph{strictly} order-preserving.
 The degeneracies then vanish, and we're left with the task of defining gluing conditions solely on the basis of face maps.
-In mathematical literature, there is little interest in studying \DeltaHat, since delta maps are not well-defined, and constructing a $\Set^{\op{\DeltaHat}}$ is inelegant.
+In mathematical literature, there is little interest in studying \DeltaHat, since maps between delta sets are not well-defined, and it is therefore not possible to construct a category of delta sets.
 
@@
 
-\section{Semi-cubical sets}
-In this section, we give the core of the definition of semi-cubical
-sets as the coinductive limit (see table \ref{tab:coind}) of a
-construction of truncated semi-cubical sets.
+\section{Trunacated $n$-sets}
+In this section, we give the core of the definition of truncated $n$-sets
+as a coinductive limit.
 
-\subsection{Truncated sets}
 % Now, we write the type theory bit, and input the abbreviated tables
-
 % Frame, layer, and filler
-\newcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[#1][#2][#3][#4]}
-\newcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[#1][#2][#3][#4]}
-\newcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[#1][#2][#3][#4]}
+\newcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[][#2][#3][#4]}
+\newcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[][#2][#3][#4]}
+\newcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[][#2][#3][#4]}
 
@@
 The definition is dispatched over tables \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and \ref{tab:coh}.
-It describes the structure of the underlying higher-dimensional relations on which cubes and boxes are built, together with the definition of homogeneous $n$-boxes, homogeneous $n$-cubes, together with face operations on boxes and cubes, together with commutation properties of the face operations.
-All are mutually defined as types of the target language ETT.
-Note that such relational structure, cubes and boxes are relative to a universe.
+It describes the structure of the underlying higher-dimensional relations on which fillers are built.
 Note the presence of a coherence condition $\cohframe[l]$ to ensuring that both sides of the equality in $\restrl[l]$ and $\restrc[l]$ are in the same type.
-The proof of $\cohframe[l]$ itself requires an higher-dimensional coherence condition which we obtain by working here in ETT where all proofs of an equality are identified (principle of Unicity of Identity Proofs).
+The proof of $\cohframe[l]$ itself requires an higher-dimensional coherence condition which we obtain by working in \mintinline{coq}{HSet}.
 Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
@@
 
-When reflexivities are excepted, we call the structure thus defined \emph{bare truncated sets}: \emph{bare} because it can be seen as defining semi-cubical sets corresponding to semi-simplicial sets with only faces as part of the structure; \emph{truncated} because we consider only such cubical sets up to some fixed dimension.
+When reflexivities are excluded, we call the structure thus defined \emph{bare truncated sets}: \emph{bare} because it can be seen as defining truncated $n$-sets corresponding to simplical sets with only faces as part of the structure.
 
@@
 % Restriction for frame, layer, and filler
-\renewcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[#1][#2][#3][#4][#5][#6]}
-\renewcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[#1][#2][#3][#4][#5][#6]}
-\renewcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[#1][#2][#3][#4][#5][#6]}
+\renewcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[][#2][#3][#4][#5][#6]}
+\renewcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[][#2][#3][#4][#5][#6]}
+\renewcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[][#2][#3][#4][#5][#6]}
 
 % Coherence conditions for frame, layer, and filler
-\renewcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[][#2][#3][#4][#5][][#7][#8]}
-\renewcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[][#2][#3][#4][#5][][#7][#8]}
-\renewcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[][#2][#3][#4][#5][][#7][#8]}
+\renewcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[][][][#4][#5][][#7][#8]}
+\renewcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[][][][#4][#5][][#7][#8]}
+\renewcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[][][][#4][#5][][#7][#8]}
 
@@
 
+\section{Future work}
+
 \newpage
-
 \appendix
@@
 \renewcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[#1][#2][#3][#4]}
+
+\renewcommandx{\fullframe}[2][1=,2=]{\ensuremath{\mathsf{\color{indian-yellow}{fullframe}}_{#1}^{#2}}}
+
+% Restriction for frame, layer, and filler
+\renewcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[#1][#2][#3][#4][#5][#6]}
+\renewcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[#1][#2][#3][#4][#5][#6]}
+\renewcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[#1][#2][#3][#4][#5][#6]}
 
@@
 \input{tab-coind.tex}
+
+\newpage
 

### 2022-05-17 paper/paper.tex
paper: minor polish
paper: minor corrections; coh stuff needs work
paper: backend changes to macros for maint; NFC

@@
 
-% Full frame
-\newcommandx{\fullframe}[2][1=,2=]{\ensuremath{\mathsf{\color{indian-yellow}{fullframe}}^{#2}}}
-
 % Restriction for frame, layer, and filler: the general macro
@@
 % Coherence conditions for frame, layer, and filler: the general macro
-\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{#1}}_{\joinargs[#2][#3][#4][#5][#6]}^{\joinargs[#7][#8][#9]}}}
+\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}, \joinargs[#2][#3][#4][#5][#6]}^{\joinargs[#7][#8][#9]}}}
 
-% Logical implication
+% Some abbreviations
 \newcommand{\imp}{\ensuremath{\rightarrow}}
 \newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
-
-% Some abbreviations
 \renewcommand{\D}{\ensuremath{(D)}}
@@
 
-\section{Trunacated $n$-sets}
+\section{Trunacated \texorpdfstring{$n$}{n}-sets}
 In this section, we give the core of the definition of truncated $n$-sets
@@
 \newcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[][#2][#3][#4]}
-
+\newcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[][#2][][]}
 % Restriction for frame, layer, and filler
@@
 % Coherence conditions for frame, layer, and filler
-\newcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[][#2][#3][][][][][#8]}
-\newcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
-\newcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}
+\newcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][#2][#3][][][][][#8]}
+\newcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][#2][#3][][][][][#8]}
+\newcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][#2][#3][][][][][#8]}
 
@@
 It describes the structure of the underlying higher-dimensional relations on which fillers are built.
-Note the presence of a coherence condition $\cohframe[l]$ to ensuring that both sides of the equality in $\restrl[l]$ and $\restrc[l]$ are in the same type.
-The proof of $\cohframe[l]$ itself requires an higher-dimensional coherence condition which we obtain by working in \mintinline{coq}{HSet}.
+Note the presence of a coherence condition $\cohf[l]$ to ensuring that both sides of the equality in $\restrl[l]$ and $\restrc[l]$ are in the same type.
+The proof of $\cohf[l]$ itself requires an higher-dimensional coherence condition which we obtain by working in \mintinline{coq}{HSet}.
 Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf[l]$ nor $\cohframe[l]$ anymore.
+Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf[l]$ nor $\cohf[l]$ anymore.
 
@@
 % Coherence conditions for frame, layer, and filler
-\renewcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[][][][#4][#5][][#7][#8]}
-\renewcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[][][][#4][#5][][#7][#8]}
-\renewcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[][][][#4][#5][][#7][#8]}
+\renewcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][][][#4][#5][][#7][#8]}
+\renewcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][][][#4][#5][][#7][#8]}
+\renewcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][][][#4][#5][][#7][#8]}
 
@@
 \renewcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[#1][#2][#3][#4]}
-
-\renewcommandx{\fullframe}[2][1=,2=]{\ensuremath{\mathsf{\color{indian-yellow}{fullframe}}_{#1}^{#2}}}
+\renewcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[#1][#2][][]}
 
@@
 % Coherence conditions for frame, layer, and filler
-\renewcommandx{\cohframe}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6][#7][#8]}
-\renewcommandx{\cohlayer}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
-\renewcommandx{\cohfiller}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}
+\renewcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6][#7][#8]}
+\renewcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
+\renewcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}
 

### 2022-05-17 paper/paper.tex
paper: fix error in universe letter in U
paper: drop universe letter on X in abbrev-tabs 3,4
paper: many little corrections to abbrev-tabs
paper: s/ETT/HSet in tables
paper: remove trailing comma in restr/coh with no arg

@@
   end
-  function join_with_comma(tbl)
-    return table.concat(remove_empty(tbl), ",")
+  function join_with_comma(prefix, tbl)
+    str = table.concat(remove_empty(tbl), ",")
+    if str == "" then
+      return str
+    end
+    return prefix .. str
   end
@@
 
-\newcommandx{\joinargs}[5][1=,2=,3=,4=,5=]{\directlua{tex.sprint(join_with_comma({"\luaescapestring{#1}";"\luaescapestring{#2}";"\luaescapestring{#3}";"\luaescapestring{#4}";"\luaescapestring{#5}"}))}}
+\newcommandx{\joinargs}[6][2=,3=,4=,5=,6=]{\directlua{tex.sprint(join_with_comma("#1", {"\luaescapestring{#2}";"\luaescapestring{#3}";"\luaescapestring{#4}";"\luaescapestring{#5}";"\luaescapestring{#6}"}))}}
 
@@
 \newcommand{\defeq}{\ensuremath{\triangleq}}
-\newcommand{\eqett}{\ensuremath{\equiv_{\mathit{ETT}}}}
-\newcommand{\reflett}{\ensuremath{\mathsf{refl}_{\mathit{ETT}}}}
+\newcommand{\eqHSet}{\ensuremath{\equiv_{\mathit{HSet}}}}
+\newcommand{\reflHSet}{\ensuremath{\mathsf{refl}_{\mathit{HSet}}}}
 
-% Truncated sets, otherwise referred to as X
-\newcommand{\Xp}[1]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}}}
-\newcommand{\X}[2]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{<#2}}}
-\newcommand{\Xcomp}[2]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{=#2}}}
-\newcommand{\Xfrom}[2]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{\geq#2}}}
+% Truncated sets, otherwise referred to as X: the general macro
+\newcommandx{\X}[2][1=,2=]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{#2}}}
 
 % Frame, layer, and filler: the general macro
-\newcommandx{\prim}[5][2=,3=,4=,5=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs[#3][#4][#5]}}}
+\newcommandx{\prim}[5][2=,3=,4=,5=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}}}
 
 % Restriction for frame, layer, and filler: the general macro
-\newcommandx{\restr}[7][2=,3=,4=,5=,6=,7=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}, \joinargs[#2][#3][#4]}^{\joinargs[#5][#6][#7]}}}
+\newcommandx{\restr}[7][2=,3=,4=,5=,6=,7=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}}
 
 % Coherence conditions for frame, layer, and filler: the general macro
-\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}, \joinargs[#2][#3][#4][#5][#6]}^{\joinargs[#7][#8][#9]}}}
+\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8][#9]}}}
 
@@
   A model of \emph{homotopy type theory}, that formalizes \emph{truncated} $n$-types in dependent type theory.
-The accompanying artifact is an axiomless Coq formalization~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to truncated $n$-types; if one were to instantiate our development for a particular type (say, augmented simplicial types), this requirement vanishes.} that uses sophisticated rewriting techniques and pushes the boundary of proof assistant technology.
+The accompanying artifact is an axiomless Coq formalization~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to truncated $n$-types; if one were to instantiate our development for a particular type (say, semi-simplicial types), this requirement vanishes.} that uses sophisticated rewriting techniques and pushes the boundary of proof assistant technology.
 \end{abstract}
@@
 
-Our contribution is to model the core of semi-cubical sets that naturally generalizes to augmented simplicial sets in type theory, and we call our generalization \emph{truncated $n$-sets}.
+Our contribution is to model the core of semi-cubical sets that naturally generalizes to semi-simplicial sets in type theory, and we call our generalization \emph{truncated $n$-sets}.
 In contrast to previous efforts that use a fibered representation, we use an indexed representation, that can be derived from the fibered one using a \emph{iterated reverse-Grothendieck} construction.
@@
 \subsection{\texorpdfstring{\DeltaHat}{Delta sets}}
-As a first step towards formalizing simplicial sets, we restrict outselves to representing \emph{augmented simplicial sets}, which are described roughly as delta-sets in mathematical literature, which forgets about the degeneracies.
+The first step towards formalizing simplicial sets is to forget about the degeneracies, and we restrict ourselves to representing \emph{augmented simplicial sets}, otherwise known as delta-sets in mathematical literature.
 We now proceed to describe \DeltaHat, which is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are \emph{strictly} order-preserving.
@@
   $\CSet$ does not admit degeneracies.
-\end{theorem}
-
   \begin{proof}
@@
   \end{proof}
+\end{theorem}
 
@@
 % Now, we write the type theory bit, and input the abbreviated tables
+
+% Truncated sets, otherwise referred to as X
+% Keep all arguments
+\newcommandx{\Xp}[1]{\X[#1][]}
+\newcommandx{\Xto}[2]{\X[#1][<#2]}
+\newcommandx{\Xcomp}[2]{\X[#1][=#2]}
+\newcommandx{\Xfrom}[2]{\X[#1][\geq#2]}
+
 % Frame, layer, and filler
+% Drop the universe letter
 \newcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[][#2][#3][#4]}
@@
 \newcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[][#2][#3][#4]}
-\newcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[][#2][][]}
+
 % Restriction for frame, layer, and filler
+% Drop the unviverse letter and q
 \newcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[][#2][][#4][#5][#6]}
@@
 % Coherence conditions for frame, layer, and filler
-\newcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][#2][#3][][][][][#8]}
-\newcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][#2][#3][][][][][#8]}
-\newcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][#2][#3][][][][][#8]}
+% Keep only ε, ω; n, p; proposition on n and p
+\newcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][#2][#3][][][#6][#7][#8]}
+\newcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][#2][#3][][][#6][#7][#8]}
+\newcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][#2][#3][][][#6][#7][#8]}
 
@@
 
+% For just the first table, keep the universe letter in fullframe
+\newcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[#1][#2][][]}
 \input{tab-core.tex}
+
+% Drop the universe letter in fullframe for all remaining tables
+\renewcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[][#2][][]}
 \input{tab-frames.tex}
+
+% Truncated sets, otherwise referred to as X
+% Drop the universe letter for the third and fourth tables
+\renewcommandx{\Xto}[2]{\X[][<#2]}
+\renewcommandx{\Xcomp}[2]{\X[][=#2]}
+\renewcommandx{\Xfrom}[2]{\X[][\geq#2]}
 \input{tab-faces.tex}
@@
 % Restriction for frame, layer, and filler
+% Drop just the universe letter for the coh table
 \renewcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[][#2][#3][#4][#5][#6]}
@@
 
+% Frame, layer, and filler
+% Drop all arguments for coh table; they're not present in coind table.
+\renewcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[][][][]}
+\renewcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[][][][]}
+\renewcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[][][][]}
+
 % Coherence conditions for frame, layer, and filler
-\renewcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][][][#4][#5][][#7][#8]}
-\renewcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][][][#4][#5][][#7][#8]}
-\renewcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][][][#4][#5][][#7][#8]}
+% Drop universe letter, ε, and ω
+\renewcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][][][#4][#5][#6][#7][#8]}
+\renewcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][][][#4][#5][#6][#7][#8]}
+\renewcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][][][#4][#5][#6][#7][#8]}
+\input{tab-coh.tex}
 
-\input{tab-coh.tex}
+% Truncated sets, otherwise referred to as X
+% Keep universe letter for last table
+\renewcommandx{\Xto}[2]{\X[#1][<#2]}
+\renewcommandx{\Xcomp}[2]{\X[#1][=#2]}
+\renewcommandx{\Xfrom}[2]{\X[#1][\geq#2]}
+
 \input{tab-coind.tex}
@@
 \section{Tables in full detail}
+% Keep all arguments for all macros
 % Frame, layer, and filler
@@
 \newpage
-
 \begin{thebibliography}{10}

### 2022-05-18 paper/paper.tex
paper: get prepared to pass explicit arguments to xkeyval

@@
 
+% Magic with xkeyval to go over the 9-argument limit of LaTeX
+\makeatletter
+\define@key{Ex}{D}{#1}
+\define@key{Ex}{d}{#1}
+\define@key{Ex}{E}{#1}
+\define@key{Ex}{l}{#1}
+\define@key{Ex}{c}{#1}
+\makeatother
+
 % Frame, layer, and filler: the general macro
-\newcommandx{\prim}[5][2=,3=,4=,5=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}}}
+\makeatletter
+\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}\@ifstar{}{\setkeys*{Ex}{#6}}}}
+\makeatother
 
 % Restriction for frame, layer, and filler: the general macro
-\newcommandx{\restr}[7][2=,3=,4=,5=,6=,7=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}}
+\makeatletter
+\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}\@ifstar{}{\setkeys*{Ex}{#8}}}}
+\makeatother
 
 % Coherence conditions for frame, layer, and filler: the general macro
-\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8][#9]}}}
+
+% Hack: we'd like \coh to take 10 arguments, with the 10th being passed to
+% xkeyval, but this is not possible. The only possible compromise is to join
+% #7, and #8 by hand in usage of \coh, by hand.
+\makeatletter
+\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}\@ifstar{}{\setkeys*{Ex}{#9}}}}
+\makeatother
 
@@
 % Drop the universe letter
-\newcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[][#2][#3][#4]}
-\newcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[][#2][#3][#4]}
-\newcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[][#2][#3][#4]}
+\newcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][#2][#3][#4][#5]}
+\newcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][#2][#3][#4][#5]}
+\newcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][#2][#3][#4][#5]}
 
@@
 % Drop the unviverse letter and q
-\newcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[][#2][][#4][#5][#6]}
-\newcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[][#2][][#4][#5][#6]}
-\newcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[][#2][][#4][#5][#6]}
+\newcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[][#2][][#4][#5][#6][#7]}
+\newcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[][#2][][#4][#5][#6][#7]}
+\newcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[][#2][][#4][#5][#6][#7]}
 
@@
 % Keep only ε, ω; n, p; proposition on n and p
-\newcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][#2][#3][][][#6][#7][#8]}
-\newcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][#2][#3][][][#6][#7][#8]}
-\newcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][#2][#3][][][#6][#7][#8]}
+\newcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][#2][#3][][][][][#9]}
+\newcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[][#2][#3][][][][][#9]}
+\newcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[][#2][#3][][][][][#9]}
 
@@
 \renewcommandx{\Xfrom}[2]{\X[][\geq#2]}
+
+% The third table mentions cohframe; keep ε, ω in this instance
+\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
 \input{tab-faces.tex}
@@
 % Drop just the universe letter for the coh table
-\renewcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[][#2][#3][#4][#5][#6]}
-\renewcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[][#2][#3][#4][#5][#6]}
-\renewcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[][#2][#3][#4][#5][#6]}
+\renewcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}
 
@@
 % Drop all arguments for coh table; they're not present in coind table.
-\renewcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[][][][]}
-\renewcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[][][][]}
-\renewcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[][][][]}
+\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][][][][]}
+\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][][][][]}
+\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][][][][]}
 
@@
 % Drop universe letter, ε, and ω
-\renewcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][][][#4][#5][#6][#7][#8]}
-\renewcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][][][#4][#5][#6][#7][#8]}
-\renewcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][][][#4][#5][#6][#7][#8]}
+\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][][][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[][][][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[][][][#4][#5][#6,#7][#8][#9]}
 \input{tab-coh.tex}
@@
 % Frame, layer, and filler
-\renewcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[#1][#2][#3][#4]}
-\renewcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[#1][#2][#3][#4]}
-\renewcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[#1][#2][#3][#4]}
+\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[#1][#2][#3][#4][#5]}
+\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[#1][#2][#3][#4][#5]}
+\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[#1][#2][#3][#4][#5]}
 \renewcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[#1][#2][][]}
@@
 % Restriction for frame, layer, and filler
-\renewcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[#1][#2][#3][#4][#5][#6]}
-\renewcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[#1][#2][#3][#4][#5][#6]}
-\renewcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[#1][#2][#3][#4][#5][#6]}
+\renewcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[#1][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[#1][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[#1][#2][#3][#4][#5][#6][#7]}
 
 % Coherence conditions for frame, layer, and filler
-\renewcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6][#7][#8]}
-\renewcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
-\renewcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}
+\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
 

### 2022-05-18 paper/paper.tex
paper: proof-of-concept xkeyval on tab-frames

@@
 \makeatletter
-\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}\@ifstar{}{\setkeys*{Ex}{#6}}}}
+\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}}\@ifstar{}{\setkeys*{Ex}{#6}}}
 \makeatother
@@
 \makeatletter
-\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}\@ifstar{}{\setkeys*{Ex}{#8}}}}
+\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}\@ifstar{}{\setkeys*{Ex}{#8}}}
 \makeatother
@@
 \makeatletter
-\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}\@ifstar{}{\setkeys*{Ex}{#9}}}}
+\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}\@ifstar{}{\setkeys*{Ex}{#9}}}
 \makeatother
@@
 \renewcommand{\c}{\ensuremath{(c)}}
+\newcommand{\pair}[2]{\ensuremath{(#1, #2)}}
 

### 2022-05-18 paper/paper.tex
paper, tab-faces: create more key fams; roadblock at nested

@@
 \makeatletter
-\define@key{Ex}{D}{#1}
-\define@key{Ex}{d}{#1}
-\define@key{Ex}{E}{#1}
-\define@key{Ex}{l}{#1}
-\define@key{Ex}{c}{#1}
+\define@cmdkey{prim-frame}{D}{#1}
+\define@cmdkey{prim-layer}{D}{#1}
+\define@cmdkey{prim-layer}{d}{#1}
+\define@cmdkey{prim-filler}{D}{#1}
+\define@cmdkey{prim-filler}{E}{#1}
+\define@cmdkey{prim-filler}{d}{#1}
+
+\define@cmdkey{restr-frame}{D}{#1}
+\define@cmdkey{restr-frame}{d}{#1}
+\define@cmdkey{restr-layer}{D}{#1}
+\define@cmdkey{restr-layer}{d}{#1}
+\define@cmdkey{restr-layer}{l}{#1}
+\define@cmdkey{restr-filler}{D}{#1}
+\define@cmdkey{restr-filler}{E}{#1}
+\define@cmdkey{restr-filler}{d}{#1}
+\define@cmdkey{restr-filler}{c}{#1}
+
+\define@cmdkey{coh-frame}{D}{#1}
+\define@cmdkey{coh-frame}{d}{#1}
+\define@cmdkey{coh-layer}{D}{#1}
+\define@cmdkey{coh-layer}{d}{#1}
+\define@cmdkey{coh-layer}{l}{#1}
+\define@cmdkey{coh-filler}{D}{#1}
+\define@cmdkey{coh-filler}{E}{#1}
+\define@cmdkey{coh-filler}{d}{#1}
+\define@cmdkey{coh-filler}{c}{#1}
 \makeatother
@@
 \makeatletter
-\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}}\@ifstar{}{\setkeys*{Ex}{#6}}}
+\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}}\@ifstar{}{\setkeys*{prim-#1}{#6}}}
 \makeatother
@@
 \makeatletter
-\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}\@ifstar{}{\setkeys*{Ex}{#8}}}
+\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}\@ifstar{}{\setkeys*{restr-#1}{#8}}}
 \makeatother
@@
 \makeatletter
-\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}\@ifstar{}{\setkeys*{Ex}{#9}}}
+\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}\@ifstar{}{\setkeys*{coh-#1}{#9}}}
 \makeatother
@@
 % Coherence conditions for frame, layer, and filler
-\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
 

### 2022-05-18 paper/paper.tex
paper: finish off the easy part of the xkeyval conversion

--- 2022-05-18 paper/paper.tex
@@
 
-% Truncated sets, otherwise referred to as X: the general macro
-\newcommandx{\X}[2][1=,2=]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{#2}}}
-
 % Magic with xkeyval to go over the 9-argument limit of LaTeX
 \makeatletter
-\define@key{Ex}{D}{#1}
-\define@key{Ex}{d}{#1}
-\define@key{Ex}{E}{#1}
-\define@key{Ex}{l}{#1}
-\define@key{Ex}{c}{#1}
+\define@cmdkey{X}{D}{(#1)}
+
+\define@cmdkey[prim]{frame}{D}{(#1)}
+\define@cmdkey[prim]{layer}{D}{(#1)}
+\define@cmdkey[prim]{layer}{d}{(#1)}
+\define@cmdkey[prim]{filler}{D}{(#1)}
+\define@cmdkey[prim]{filler}{E}{(#1)}
+\define@cmdkey[prim]{filler}{d}{(#1)}
+\define@cmdkey[prim]{fullframe}{D}{(#1)}
+
+\define@cmdkey[restr]{frame}{D}{(#1)}
+\define@cmdkey[restr]{frame}{d}{(#1)}
+\define@cmdkey[restr]{layer}{D}{(#1)}
+\define@cmdkey[restr]{layer}{d}{(#1)}
+\define@cmdkey[restr]{layer}{l}{(#1)}
+\define@cmdkey[restr]{filler}{D}{(#1)}
+\define@cmdkey[restr]{filler}{E}{(#1)}
+\define@cmdkey[restr]{filler}{d}{(#1)}
+\define@cmdkey[restr]{filler}{c}{(#1)}
+
+\define@cmdkey[coh]{frame}{D}{(#1)}
+\define@cmdkey[coh]{frame}{d}{(#1)}
+\define@cmdkey[coh]{layer}{D}{(#1)}
+\define@cmdkey[coh]{layer}{d}{(#1)}
+\define@cmdkey[coh]{layer}{l}{(#1)}
+\define@cmdkey[coh]{filler}{D}{(#1)}
+\define@cmdkey[coh]{filler}{E}{(#1)}
+\define@cmdkey[coh]{filler}{d}{(#1)}
+\define@cmdkey[coh]{filler}{c}{(#1)}
 \makeatother
 
+% Truncated sets, otherwise referred to as X: the general macro
+\newcommandx{\X}[3][1=,2=,3=]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{#2}{\setkeys*{X}{#3}}}}
+
 % Frame, layer, and filler: the general macro
-\makeatletter
-\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}\@ifstar{}{\setkeys*{Ex}{#6}}}}
-\makeatother
+\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}{\setkeys*[prim]{#1}{#6}}}}
 
 % Restriction for frame, layer, and filler: the general macro
-\makeatletter
-\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}\@ifstar{}{\setkeys*{Ex}{#8}}}}
-\makeatother
+\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}{\setkeys*[restr]{#1}{#8}}}}
 
@@
 % xkeyval, but this is not possible. The only possible compromise is to join
-% #7, and #8 by hand in usage of \coh, by hand.
-\makeatletter
-\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}\@ifstar{}{\setkeys*{Ex}{#9}}}}
-\makeatother
+% #7 and #8 by hand in usage of \coh: it's now #7 or '#6,#7' in \cohfoo commands
+\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}{\setkeys*[coh]{#1}{#9}}}}
 
@@
 \newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
-\renewcommand{\D}{\ensuremath{(D)}}
-\newcommand{\hdD}{\ensuremath{(D.1)}}
-\newcommand{\tlD}{\ensuremath{(D.2)}}
-\renewcommand{\d}{\ensuremath{(d)}}
-\newcommand{\E}{\ensuremath{(E)}}
-\renewcommand{\l}{\ensuremath{(l)}}
-\renewcommand{\c}{\ensuremath{(c)}}
+\renewcommand{\D}{\ensuremath{D}}
+\newcommand{\hdD}{\ensuremath{D.1}}
+\newcommand{\tlD}{\ensuremath{D.2}}
+\renewcommand{\d}{\ensuremath{d}}
+\newcommand{\E}{\ensuremath{E}}
+\renewcommand{\l}{\ensuremath{l}}
+\renewcommand{\c}{\ensuremath{c}}
+\newcommand{\pair}[2]{\ensuremath{#1, #2}}
 
@@
 % For just the first table, keep the universe letter in fullframe
-\newcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[#1][#2][][]}
+\newcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[#1][#2][][][#3]}
 \input{tab-core.tex}
@@
 % Drop the universe letter in fullframe for all remaining tables
-\renewcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[][#2][][]}
+\renewcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[][#2][][][#3]}
 \input{tab-frames.tex}
@@
 % Drop all arguments for coh table; they're not present in coind table.
-\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][][][][]}
-\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][][][][]}
-\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][][][][]}
+\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][][][][#5]}
+\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][][][][#5]}
+\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][][][][#5]}
 
@@
 \renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[#1][#2][#3][#4][#5]}
-\renewcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[#1][#2][][]}
+\renewcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[#1][#2][][][#3]}
 

### 2022-05-19 paper/paper.tex
paper: minor backend changes; grouping commands
paper: figured out syntax for grouping; ready to merge into master
paper: roadblock in patching xkv; doesn't match original def

@@
 
-\usepackage{multirow, minted, tabularx, booktabs, setspace, makecell, caption}
-\usepackage[hmargin=0.4in, vmargin=0.8in, headheight=10pt]{geometry}
+\usepackage{multirow, minted, tabularx, booktabs, setspace, makecell, caption, xstring, pdflscape}
+\usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}
 
@@
 
+% More magic: we extend xkeyval with a \appendmask macro to pass to \setkeys
+\makeatletter
+\edef\bonak@mask{}
+
+\def\bonak@appendmask[#1]{
+  \XKV@addtolist@n\bonak@mask{\g@addto@macro{\XKV@prefix\XKV@tfam}{@}#1}
+}
+\def\appendmask{\XKV@testopta{\XKV@testoptc\bonak@appendmask}}
+\makeatother
+
+% Now we patch XKV@setkeys
+\makeatletter
+\let\XKV@setkeys@alt\XKV@setkeys
+\long\def\XKV@setkeys[#1]#2{
+  \edef\bonak@pfx{\g@addto@macro{\XKV@prefix\XKV@tfam}{@}}
+  \edef\bonak@tempa\@empty
+  \edef\bonak@keys{}
+  \XKV@for@n{\bonak@mask}\bonak@tempa{
+    \IfBeginWith{\bonak@tempa}{\bonak@pfx}{
+      \XKV@addtolist@n\bonak@keys{\StrBehind{\bonak@tempa}{\bonak@pfx}}}{}
+  }
+  % Finally, call the real function
+  \XKV@setkeys@alt[\bonak@keys]{#2}
+}
+\makeatother
+
 % Truncated sets, otherwise referred to as X: the general macro
-\newcommandx{\X}[3][1=,2=,3=]{\ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{#2}{\setkeys*{X}{#3}}}}
+\newcommandx*{\X}[3][1=,2=,3=]{
+  \ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{#2}}
+  \setkeys*{X}{#3}
+}
 
 % Frame, layer, and filler: the general macro
-\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}{\setkeys*[prim]{#1}{#6}}}}
+\newcommandx*{\prim}[6][2=,3=,4=,5=,6=]{
+  \ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{
+    \joinargs{}[#3][#4][#5]}}
+  \setkeys*[prim]{#1}{#6}
+}
 
 % Restriction for frame, layer, and filler: the general macro
-\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}{\setkeys*[restr]{#1}{#8}}}}
+\newcommandx*{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{
+  \ensuremath{\mathsf{\color{russian-green}{restr}}_{
+    \mathsf{\color{indian-yellow}{#1}}
+    \joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}
+  \setkeys*[restr]{#1}{#8}
+}
 
@@
 % #7 and #8 by hand in usage of \coh: it's now #7 or '#6,#7' in \cohfoo commands
-\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}{\setkeys*[coh]{#1}{#9}}}}
+\newcommandx*{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{
+  \ensuremath{\mathsf{\color{chestnut}{coh}}_{
+    \mathsf{\color{indian-yellow}{#1}}
+    \joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}
+  \setkeys*[coh]{#1}{#9}
+}
 
@@
 % The eqntable environment, displaying the various
-\NewDocumentEnvironment{eqntable}{m}{\table[H]\small
-\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
+\NewDocumentEnvironment{eqntable}{m}{\table[H]\small\hrule\vspace{0.5em}
+\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}}
 {\endtabularx\vspace{0.3em}\hrule\vspace{0.5em}\caption{#1}\endtable}
@@
 \author{
+  \textcolor{gray80}{Ramkumar Ramachandra} \\
+  \itshape \textcolor{gray80}{Université Paris-Cité}
+  \and
   \textcolor{gray80}{Hugo Herbelin} \\
-  \itshape \textcolor{gray80}{IRIF}
-  \and
-  \textcolor{gray80}{Ramkumar Ramachandra} \\
-  \itshape \textcolor{gray80}{Université de Paris}
+  \itshape \textcolor{gray80}{Instit de Recherche en Informatique Fondamentale}
 }
@@
 \begin{abstract}
-  A model of \emph{homotopy type theory}, that formalizes \emph{truncated} $n$-types in dependent type theory.
-The accompanying artifact is an axiomless Coq formalization~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to truncated $n$-types; if one were to instantiate our development for a particular type (say, semi-simplicial types), this requirement vanishes.} that uses sophisticated rewriting techniques and pushes the boundary of proof assistant technology.
+  A model of homotopy type theory, that formalizes augmented semi-simplicial sets that naturally generalizes to semi-cubical sets as well, in dependent type theory.
+The accompanying artifact is an axiomless~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to $\nu$-types; if $\nu$ is finite (say, unit type corresponding to augmented semi-simplicial types), this requirement vanishes.} Coq formalization that uses sophisticated rewriting techniques and pushes the boundaries of proof assistant technology.
 \end{abstract}
@@
 
-\section{Simplicial sets}
+\section{\texorpdfstring{$\nu$}{nu}-sets}
 Simplicial sets are powerful mathematical objects, that form the basis of much of modern homotopy theory.
@@
 
-\subsection{\texorpdfstring{\SSet}{The category of simplicial sets}}
-There exists vast mathematical literature on the subject, and we refer the uninitiated reader to \cite{Friedman08} for a gentle introduction with excellent intutions.
-With these intuitions in place, we proceed with a purely categorical treatment.
-Emily Riehl's \cite{Riehl11} is an especially well-written manuscript on the subject.
-
-\begin{definition}[\sq{n}]
-  $\sq{n}$ is used to denote a totally-ordered set of natural numbers less than or equal to $n$, ordered by magnitude.
-
-  \begin{equation*}
-    \sq{n} := \{0, 1, \ldots, n\}
-  \end{equation*}
-
-  We will regard the totally-ordered set as a category in certain contexts, and it should be clear which interpretation we're referring to from the context.
-
-  \begin{equation*}
-    \sq{n} := 0 \rightarrow 1 \rightarrow \ldots \rightarrow n
-  \end{equation*}
-\end{definition}
-
-\begin{definition}[\Simplex{}]
-  The category $\Simplex{}$ is defined in terms of its objects and morphisms:
-
-  \begin{align*}
-    \obj(\Simplex{}) & := \sq{n}, \text{regarded as a totally-ordered set}   \\
-    \mor(\Simplex{}) & := \sq{m} \rightarrow \sq{n}, \text{order-preserving}
-  \end{align*}
-\end{definition}
-
-\begin{definition}[\SSet]
-  The category of simplicial sets is defined as:
-
-  \begin{equation*}
-    \SSet := \Set^{\op{\Simplex{}}}
-  \end{equation*}
-
-  It is a functor category, whose objects and morphisms are given by:
-
-  \begin{align*}
-    \obj(\SSet)            & := \text{functors} \; \op{\Simplex{}} \rightarrow \Set     \\
-    \mor(\SSet)            & := \text{natural transforms between the functors}          \\
-    \text{composition law} & := \text{the usual composition of natural transformations} \\
-  \end{align*}
-\end{definition}
-
-\begin{definition}[\Simplex{n}]
-  The Yoneda embedding of $\sq{n}$ is referred to as the standard $n$-simplex.
-
-  \begin{equation*}
-    \Simplex{n} := y(\sq{n})
-  \end{equation*}
-\end{definition}
-
-\begin{notation}[$\sq{0, \ldots, n}$]
-  The notation $\sq{0, \ldots, n}$ denotes all ordered subsets of \sq{n}.
-\end{notation}
-
-With the definition of the category of simplicial sets firmly in place, we look inside a simplicial set to see the data it actually encodes concretely.
-
-\begin{definition}[The data of a simplicial set]
-  A simplicial set is equivalent to the data of a set of $n$-simplices, related to each other via face and degeneracy maps.
-
-  \begin{align*}
-    X_n                             & \;\;\text{a set of n-simplices} \\
-    d_i : X_{n + 1} \rightarrow X_n & \;\;\text{face maps}            \\
-    s_i : X_n \rightarrow X_{n + 1} & \;\;\text{degeneracy maps}      \\
-  \end{align*}
-
-  where $X_n$ is the set of $n$-simplices contained within the simplicial set $X$:
-
-  \begin{align*}
-    X_n & : \Set                                             \\
-    X_n & := X(\sq{n}), \text{where X is the simplicial set} \\
-  \end{align*}
-
-  and $d_i$ and $s_i$ operate on $X_n$ as follows (the hat on $i$ indicates that it is to be omitted):
-
-  \begin{align*}
-    d_i(\sq{0, \ldots, n}) & = \sq{0, \ldots, \hat{i}, \ldots, n} \\
-    s_i(\sq{0, \ldots, n}) & = \sq{0, \ldots, i, i, \ldots, n}    \\
-  \end{align*}
-
-  and $d_i$, $s_i$ are constrained by the following ``simplicial identities'':
-
-  \begin{equation*}
-    \begin{matrix}
-      d_i d_j & = & d_{j - 1} d_i & i < j \\
-      s_i s_j & = & s_{j + 1} s_i & i < j \\
-      d_i s_j & = &
-      \begin{cases}
-        s_{j - 1} d_i & i < j \\
-        id            & i = j \\
-        s_j d_{i - 1} & i > j \\
-      \end{cases}
-    \end{matrix}
-  \end{equation*}
-\end{definition}
-
-We mentioned degeneracies in the introduction to this section, and we define precisely what a degenerate simplex is now.
-
-\begin{definition}[Degenerate simplex]
-  A simplex is $x \in X_n$ is termed degenerate if it is the image of some degeneracy map $s_i$, and non-degenerate otherwise.
-\end{definition}
-
-\begin{example}[Non-degenerate simplices of \Simplex{n}]
-  The non-degenerate $k$-simplices of $\Simplex{n}$ are the injective maps $\sq{k} \rightarrow \sq{n}$ in $\Simplex{}$. In particular, $\Simplex{n}$ has a unique non-degenerate $n$-simplex.
-\end{example}
-
-As is clear from the above definitions, simplicial sets have an infinite number of degeneracies, and the first step towards drawing a simplicial set is to define a convention that omits these degeneracies in the drawing.
-
-\begin{notation}[Drawing of a simplicial set\label{not:drawsset}]
-  A diagram of the form
-
-  \begin{equation*}
-    \begin{tikzcd}
-      x \arrow[r, "f"] & y
-    \end{tikzcd}
-  \end{equation*}
-
-  in simplicial set $S$ will mean that $f$ is a non-degenerate $1$-simplex, and $x$ and $y$ are $0$-simplices.
-The simplices have a relationship to the simplicial set $S$ given by the following commutative diagram:
-
-  \begin{equation*}
-    \begin{tikzcd}
-      \Simplex{0} \arrow[dr] \arrow[drr, "x", bend left] & & \\
-      & \Simplex{1} \arrow[r, "f"] & S \\
-      \Simplex{0} \arrow[ur] \arrow[urr, "y"', bend right] & & \\
-    \end{tikzcd}
-  \end{equation*}
-
-  To attempting to draw simplices of dimension greater than $1$, we see that there is a potential ambiguity. Consider the following diagram:
-
-  \begin{equation*}
-    \begin{tikzcd}
-      & \bullet \arrow[ddr] & \\
-      \\
-      \bullet \arrow[uur] \arrow[rr] & & \bullet
-    \end{tikzcd}
-  \end{equation*}
-
-  In the above diagram, it is clear that there are three non-degenerate $1$-simplices, but it is unclear whether there is a non-degenerate $2$-simplex.
-By convention, when we draw such a diagram, we will assume that there is a non-degenerate $2$-simplex border by the three non-degenerate $1$-simplices.
-To generalize, we will always assume that there exists a non-degenerate $n$-simplex, when bounded by non-degenerate $(n - 1)$-simplices.
-\end{notation}
-
-\begin{example}[\Simplex{0}, \Simplex{1}, and \Simplex{2}]
-  $\Simplex{0}$ can be drawn as:
-
-  $$
-    \begin{tikzcd}
-      0
-    \end{tikzcd}
-  $$
-
-  $\Simplex{1}$ can be drawn as:
-
-  $$
-    \begin{tikzcd}
-      0 \arrow[r] & 1
-    \end{tikzcd}
-  $$
-
-  and $\Simplex{2}$ can be drawn as:
-
-  $$
-    \begin{tikzcd}
-      & 1 \arrow[ddr] & \\
-      \\
-      0 \arrow[uur] \arrow[rr] & & 2
-    \end{tikzcd}
-  $$
-\end{example}
-
-\subsection{\texorpdfstring{\DeltaHat}{Delta sets}}
+\subsection{Augmented semi-simplicial sets}
 The first step towards formalizing simplicial sets is to forget about the degeneracies, and we restrict ourselves to representing \emph{augmented simplicial sets}, otherwise known as delta-sets in mathematical literature.
@@
 
-\section{Grothendieck construction\label{sec:grothendieckconstr}}
+\section{Our construction}
 The Grothendieck construction provides a correspondence between a fibered representation, and an indexed representation.
@@
 
-\section{Unicity of identity proofs\label{sec:uip}}
+\section{Reasoning about sets in type theory}
 We dedicate this section to discussing UIP in different settings, and supply intuitions into this notion.
@@
 
-\section{Trunacated \texorpdfstring{$n$}{n}-sets}
-In this section, we give the core of the definition of truncated $n$-sets
+\section{Type-theoretic construction of \texorpdfstring{$\nu$}{nu}-sets}
+In this section, we give the core of the definition of truncated $\nu$-sets
 as a coinductive limit.
@@
 
-% For just the first table, keep the universe letter in fullframe
+\input{tab-coind.tex}
+
+% For just the second table, keep the universe letter in fullframe
 \newcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[#1][#2][][][#3]}
@@
 \input{tab-frames.tex}
+
+% From the third table onwards, make the {D, E} arguments of prims implicit
+\appendmask[prim]{frame}[D]
+\appendmask[prim]{layer}[D]
+\appendmask[prim]{filler}[D, E]
 
@@
 
-% Truncated sets, otherwise referred to as X
-% Keep universe letter for last table
-\renewcommandx{\Xto}[2]{\X[#1][<#2]}
-\renewcommandx{\Xcomp}[2]{\X[#1][=#2]}
-\renewcommandx{\Xfrom}[2]{\X[#1][\geq#2]}
-
-\input{tab-coind.tex}
-
 \section{Future work}
@@
 
+\input{tab-coind.tex}
 \input{tab-core.tex}
 \input{tab-frames.tex}
+
+\begin{landscape}
   \input{tab-faces.tex}
   \input{tab-coh.tex}
-\input{tab-coind.tex}
+\end{landscape}
 

### 2022-05-20 paper/paper.tex
Efforts still in vain
xpatch ftw!
paper: compile works, but no-visible-change
paper: there's probably some issue with appendmask
paper: possible false progress; components working
Drop subsection SSet

@@
 
-\usepackage{multirow, minted, tabularx, booktabs, setspace, makecell, caption, xstring, pdflscape}
-\usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}
+\usepackage{multirow, minted, tabularx, booktabs, setspace, makecell, caption}
+\usepackage[hmargin=0.4in, vmargin=0.8in, headheight=10pt]{geometry}
 
@@
 
-% More magic: we extend xkeyval with a \appendmask macro to pass to \setkeys
-\makeatletter
-\edef\bonak@mask{}
-
-\def\bonak@appendmask[#1]{
-  \XKV@addtolist@n\bonak@mask{\g@addto@macro{\XKV@prefix\XKV@tfam}{@}#1}
-}
-\def\appendmask{\XKV@testopta{\XKV@testoptc\bonak@appendmask}}
-\makeatother
-
-% Now we patch XKV@setkeys
-\makeatletter
-\let\XKV@setkeys@alt\XKV@setkeys
-\long\def\XKV@setkeys[#1]#2{
-  \edef\bonak@pfx{\g@addto@macro{\XKV@prefix\XKV@tfam}{@}}
-  \edef\bonak@tempa\@empty
-  \edef\bonak@keys{}
-  \XKV@for@n{\bonak@mask}\bonak@tempa{
-    \IfBeginWith{\bonak@tempa}{\bonak@pfx}{
-      \XKV@addtolist@n\bonak@keys{\StrBehind{\bonak@tempa}{\bonak@pfx}}}{}
-  }
-  % Finally, call the real function
-  \XKV@setkeys@alt[\bonak@keys]{#2}
-}
-\makeatother
-
 % Truncated sets, otherwise referred to as X: the general macro
@@
 % The eqntable environment, displaying the various
-\NewDocumentEnvironment{eqntable}{m}{\table[H]\small\hrule\vspace{0.5em}
-\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}}
+\NewDocumentEnvironment{eqntable}{m}{\table[H]\small
+\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}\toprule}
 {\endtabularx\vspace{0.3em}\hrule\vspace{0.5em}\caption{#1}\endtable}
@@
 \author{
+  \textcolor{gray80}{Hugo Herbelin} \\
+  \itshape \textcolor{gray80}{IRIF}
+  \and
   \textcolor{gray80}{Ramkumar Ramachandra} \\
-  \itshape \textcolor{gray80}{Université Paris-Cité}
-  \and
-  \textcolor{gray80}{Hugo Herbelin} \\
-  \itshape \textcolor{gray80}{Instit de Recherche en Informatique Fondamentale}
+  \itshape \textcolor{gray80}{Université de Paris}
 }
@@
 \begin{abstract}
-  A model of homotopy type theory, that formalizes augmented semi-simplicial sets that naturally generalizes to semi-cubical sets as well, in dependent type theory.
-The accompanying artifact is an axiomless~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to $\nu$-types; if $\nu$ is finite (say, unit type corresponding to augmented semi-simplicial types), this requirement vanishes.} Coq formalization that uses sophisticated rewriting techniques and pushes the boundaries of proof assistant technology.
+  A model of \emph{homotopy type theory}, that formalizes \emph{truncated} $n$-types in dependent type theory.
+The accompanying artifact is an axiomless Coq formalization~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to truncated $n$-types; if one were to instantiate our development for a particular type (say, semi-simplicial types), this requirement vanishes.} that uses sophisticated rewriting techniques and pushes the boundary of proof assistant technology.
 \end{abstract}
@@
 
-\section{\texorpdfstring{$\nu$}{nu}-sets}
+\section{Simplicial sets}
 Simplicial sets are powerful mathematical objects, that form the basis of much of modern homotopy theory.
@@
 
-\subsection{Augmented semi-simplicial sets}
+\subsection{\texorpdfstring{\DeltaHat}{Delta sets}}
 The first step towards formalizing simplicial sets is to forget about the degeneracies, and we restrict ourselves to representing \emph{augmented simplicial sets}, otherwise known as delta-sets in mathematical literature.
@@
 
-\section{Our construction}
+\section{Grothendieck construction\label{sec:grothendieckconstr}}
 The Grothendieck construction provides a correspondence between a fibered representation, and an indexed representation.
@@
 
-\section{Reasoning about sets in type theory}
+\section{Unicity of identity proofs\label{sec:uip}}
 We dedicate this section to discussing UIP in different settings, and supply intuitions into this notion.
@@
 
-\section{Type-theoretic construction of \texorpdfstring{$\nu$}{nu}-sets}
-In this section, we give the core of the definition of truncated $\nu$-sets
+\section{Trunacated \texorpdfstring{$n$}{n}-sets}
+In this section, we give the core of the definition of truncated $n$-sets
 as a coinductive limit.
@@
 
-\input{tab-coind.tex}
-
-% For just the second table, keep the universe letter in fullframe
+% For just the first table, keep the universe letter in fullframe
 \newcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[#1][#2][][][#3]}
@@
 \input{tab-frames.tex}
-
-% From the third table onwards, make the {D, E} arguments of prims implicit
-\appendmask[prim]{frame}[D]
-\appendmask[prim]{layer}[D]
-\appendmask[prim]{filler}[D, E]
 
@@
 
+% Truncated sets, otherwise referred to as X
+% Keep universe letter for last table
+\renewcommandx{\Xto}[2]{\X[#1][<#2]}
+\renewcommandx{\Xcomp}[2]{\X[#1][=#2]}
+\renewcommandx{\Xfrom}[2]{\X[#1][\geq#2]}
+
+\input{tab-coind.tex}
+
 \section{Future work}
@@
 
-\input{tab-coind.tex}
 \input{tab-core.tex}
 \input{tab-frames.tex}
-
-\begin{landscape}
 \input{tab-faces.tex}
 \input{tab-coh.tex}
-\end{landscape}
+\input{tab-coind.tex}
 

### 2022-05-20 paper/paper.tex
paper: reorder tables; tab:coind first

@@
 
-\section{Trunacated \texorpdfstring{$n$}{n}-sets}
-In this section, we give the core of the definition of truncated $n$-sets
+\section{Reasoning on \texorpdfstring{$\nu$}{nu}-sets}
+In this section, we give the core of the definition of truncated $\nu$-sets
 as a coinductive limit.
@@
 
+\input{tab-coind.tex}
 \input{tab-core.tex}
@@
 \input{tab-coh.tex}
-\input{tab-coind.tex}
 

### 2022-05-23 paper/paper.tex
paper: adjust margins, lscape two tables, polish abstract
paper: minor polish

--- 2022-05-19 paper/paper.tex
@@
 
-\usepackage{multirow, minted, tabularx, booktabs, setspace, makecell, caption, xstring, pdflscape}
+\usepackage{multirow, minted, tabularx, booktabs, setspace, makecell, caption, xkeyval, xstring, xpatch, pdflscape}
 \usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}
@@
 
-% More magic: we extend xkeyval with a \appendmask macro to pass to \setkeys
+% More magic: we patch xkeyval's \setkeys to use a mask to ignore keys
 \makeatletter
-\edef\bonak@mask{}
+% Our global mask
+\def\bonak@mask{}
+\def\bonak@na{}
 
-\def\bonak@appendmask[#1]{
-  \XKV@addtolist@n\bonak@mask{\g@addto@macro{\XKV@prefix\XKV@tfam}{@}#1}
+% First we define \appendmask
+\long\def\bonak@appendmask[#1]{
+  \XKV@for@eo\XKV@fams\XKV@tfam{
+    \def\bonak@hdr{\XKV@prefix\XKV@tfam @}
+    \XKV@for@o{#1}\XKV@tempa{
+      \XKV@addtolist@x\bonak@mask{\bonak@hdr\XKV@tempa}
+    }
+  }
 }
 \def\appendmask{\XKV@testopta{\XKV@testoptc\bonak@appendmask}}
-\makeatother
 
-% Now we patch XKV@setkeys
-\makeatletter
-\let\XKV@setkeys@alt\XKV@setkeys
-\long\def\XKV@setkeys[#1]#2{
-  \edef\bonak@pfx{\g@addto@macro{\XKV@prefix\XKV@tfam}{@}}
-  \edef\bonak@tempa\@empty
-  \edef\bonak@keys{}
-  \XKV@for@n{\bonak@mask}\bonak@tempa{
-    \IfBeginWith{\bonak@tempa}{\bonak@pfx}{
-      \XKV@addtolist@n\bonak@keys{\StrBehind{\bonak@tempa}{\bonak@pfx}}}{}
+% Now we patch \XKV@setkeys
+\xpretocmd{\XKV@setkeys}{
+  \XKV@for@eo\XKV@fams\XKV@tfam{
+    \def\bonak@hdr{\XKV@prefix\XKV@tfam @}
+    \XKV@for@eo{\bonak@mask}\XKV@tempa{
+      \IfBeginWith{\XKV@tempa}{\bonak@hdr}{
+        \def\XKV@tempb{\StrBehind{\XKV@tempa}{\bonak@hdr}}
+        \XKV@addtolist@o\bonak@na{\XKV@tempb}}{}
     }
-  % Finally, call the real function
-  \XKV@setkeys@alt[\bonak@keys]{#2}
   }
+}{\tracingpatches}{\tracingpatches}
+\xpatchcmd{\XKV@setkeys}{#1}{\bonak@na}{\tracingpatches}{\tracingpatches}
 \makeatother
@@
 \newcommand{\eqnline}[4]{$#1$ & $#2$ & $#3$ & $#4$ \\}
-\newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}
+\newcommand{\mc}[1]{\multicolumn{4}{c}{\emph{#1}} \\\\}
 
@@
 \begin{abstract}
-  A model of homotopy type theory, that formalizes augmented semi-simplicial sets that naturally generalizes to semi-cubical sets as well, in dependent type theory.
-The accompanying artifact is an axiomless~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to $\nu$-types; if $\nu$ is finite (say, unit type corresponding to augmented semi-simplicial types), this requirement vanishes.} Coq formalization that uses sophisticated rewriting techniques and pushes the boundaries of proof assistant technology.
+  A model of homotopy type theory, formalizing augmented semi-simplicial sets, that naturally generalizes to semi-cubical sets as well, in dependent type theory.
+The accompanying artifact is an axiom-less~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to $\nu$-types; if $\nu$ is finite (say, unit type corresponding to augmented semi-simplicial types), this requirement vanishes.} Coq formalization that uses sophisticated rewriting techniques and pushes the boundaries of proof assistant technology.
 \end{abstract}
@@
 We then proceed to explain our construction, with the help of diagrams.
-Before spelling out the details of our formalization in type-theoretic language, we have a section on the unicity of identity proofs (UIP), since the use of \mintinline{coq}{SProp} has greatly eased our Coq formalization.
+Before spelling out the details of our formalization in type-theoretic language, we have a section on reasoning in sets, in which we spell out \texttt{HSet}.
 
@@
 \section{Our construction}
-The Grothendieck construction provides a correspondence between a fibered representation, and an indexed representation.
+The fibered representation:
 
-$$
+\begin{equation*}
   \begin{tikzcd}
@@
   \end{tikzcd}
-$$
+\end{equation*}
 
+The indexed representation:
 \begin{align*}
@@
 Intuititively, what it means is that a tree of deductions converges to a result, with no memory of the proof route; the tree itself is forgotten once the final result is obtained.
-
-One way of formalising set theory in type theory is via Aczel sets [ref]. It can be written down as an inductive as follows:
-
-\begin{listing}[H]
-  \begin{minted}[mathescape]{coq}
-    Inductive SET : Type :=
-      node : ~$\forall$~A : Type, (A -> SET) -> SET
-      ~$=_\textrm{SET}$~ : ...
-  \end{minted}
-\end{listing}
-
-\mintinline{coq}{(A -> SET) -> SET} can be drawn as:
-
-\begin{equation*}
-  \begin{tikzcd}
-    \{0\} \arrow[dr] & \\
-    & \{\} \\
-  \end{tikzcd}
-  \begin{tikzcd}
-    & \{0, 1\} \arrow[dr]\arrow[dl] & \\
-    \{0\} & & \{1\} \\
-  \end{tikzcd}
-  \begin{tikzcd}
-    & & \{0, 1, 2\} \arrow[dr]\arrow[dl] & \\
-    & \{0, 1\} \arrow[dl]\arrow[dr] & & \{2\} \\
-    \{0\} & & \{1\} & \\
-  \end{tikzcd}
-\end{equation*}
-
-In general, \mintinline{coq}{SET} can have an $n$-ary branching structure, splitting out the various subsets until we get to the leaves.
-
-Then, proof irrelevance can be stated as:
-
-\begin{align*}
-  \forall x y, \forall p q : x =_{\textrm{SET}} y, p = q
-\end{align*}
 
@@
 It describes the structure of the underlying higher-dimensional relations on which fillers are built.
-Note the presence of a coherence condition $\cohf[l]$ to ensuring that both sides of the equality in $\restrl[l]$ and $\restrc[l]$ are in the same type.
-The proof of $\cohf[l]$ itself requires an higher-dimensional coherence condition which we obtain by working in \mintinline{coq}{HSet}.
+Note the presence of a coherence condition $\cohf$ to ensuring that both sides of the equality in $\restrl$ and $\restrc$ are in the same type.
+The proof of $\cohf$ itself requires an higher-dimensional coherence condition which we obtain by working in HSet.
 Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf[l]$ nor $\cohf[l]$ anymore.
+Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
 
-When reflexivities are excluded, we call the structure thus defined \emph{bare truncated sets}: \emph{bare} because it can be seen as defining truncated $n$-sets corresponding to simplical sets with only faces as part of the structure.
+We call the structure thus defined \emph{bare truncated sets}: \emph{bare} because it can be seen as defining truncated $\nu$-sets corresponding to simplical sets with only faces as part of the structure.
 
@@
 \appendmask[prim]{layer}[D]
-\appendmask[prim]{filler}[D, E]
+\appendmask[prim]{filler}[D,E]
 
@@
 A model of type theory in cubical sets.
-\textit{In 19th International Conference on Types for Proofs and Programs (TYPES 2013)} (Vol.
+\emph{In 19th International Conference on Types for Proofs and Programs (TYPES 2013)} (Vol.
 26, pp.
@@
   \bibitem[CubAgda]{Vezzosi21}
-  Vezzosi, A., Mörtberg, A., \& Abel, A. (2021). Cubical Agda: a dependently typed programming language with univalence and higher inductive types. \textit{Journal of Functional Programming, 31}.
+  Vezzosi, A., Mörtberg, A., \& Abel, A. (2021). Cubical Agda: a dependently typed programming language with univalence and higher inductive types. \emph{Journal of Functional Programming, 31}.
 
   \bibitem[CohCoq]{Cohen16}
-  Cohen, C., Coquand, T., Huber, S., \& Mörtberg, A. (2016). Cubical type theory: a constructive interpretation of the univalence axiom. arXiv preprint arXiv:1611.02108.
+  Cohen, C., Coquand, T., Huber, S., \& Mörtberg, A. (2016). Cubical type theory: a constructive interpretation of the univalence axiom. \emph{arXiv preprint arXiv:1611.02108}.
 
@@
   \bibitem[Fri]{Friedman08}
-  Friedman, G. (2008). An elementary illustrated introduction to simplicial sets. \textit{arXiv preprint arXiv:0809.4221}.
+  Friedman, G. (2008). An elementary illustrated introduction to simplicial sets. \emph{arXiv preprint arXiv:0809.4221}.
 
   \bibitem[Rie]{Riehl11}
-  Riehl, E. (2011). A leisurely introduction to simplicial sets. \textit{Unpublished expository article available online from the author's web page}.
+  Riehl, E. (2011). A leisurely introduction to simplicial sets. \emph{Unpublished expository article available online from the author's web page}.
 
   \bibitem[CubSet]{Antolini00}
-  Antolini, R. (2000). Cubical structures, homotopy theory. \textit{Annali di Matematica pura ed applicata, 178}(1), 317-324.
+  Antolini, R. (2000). Cubical structures, homotopy theory. \emph{Annali di Matematica pura ed applicata, 178}(1), 317-324.
 
   \bibitem[Her]{Herbelin15}
-  Herbelin, H. (2015). A dependently-typed construction of semi-simplicial types. \textit{Mathematical Structures in Computer Science, 25}(5), 1116-1131.
+  Herbelin, H. (2015). A dependently-typed construction of semi-simplicial types. \emph{Mathematical Structures in Computer Science, 25}(5), 1116-1131.
 
   \bibitem[CoqInCoq]{Barras97}
-  Barras, B., \& Werner, B. (1997). Coq in coq. \textit{Available on the WWW.}
+  Barras, B., \& Werner, B. (1997). Coq in coq. \emph{Available on the WWW.}
 \end{thebibliography}

### 2022-06-01 paper/paper.tex
paper: eliminate use of patchcmd; still doesn't work
paper: inching closer and closer to xkv-patching
paper: some guesswork progress in xkv-patch
paper: XKV@delete doesn't seem to work; debugging
paper: major debugging in progress
xkv patch: debugging draws to an end!
paper: #2 is inaccessible in patched command
paper: down to very minor issues of specifying optarg
paper: Some syntax error from expansion?
paper: table beautification; mask disabled
paper: minor polish without breakage
paper: switch to xpatchcmd without breakage
paper: namespace within bonak family
paper: some more progress; ift

@@
 
-\usepackage{multirow, minted, tabularx, booktabs, setspace, makecell, caption, xkeyval, xstring, xpatch, pdflscape}
+\usepackage{multirow, minted, tabularx, environ, booktabs, setspace, makecell, caption, xkeymask, joinargs, colortbl, pdflscape, ct, sset}
 \usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}
-
-% Some lua magic to join a variable number of arguments with commas
-% Comma-separeated optional arguments
-\begin{luacode*}
-  function remove_empty(tbl)
-    for i, v in ipairs(tbl) do
-        if v == "" then
-          table.remove(tbl, i)
-          return remove_empty(tbl)
-        end
-    end
-    return tbl
-  end
-  function join_with_comma(prefix, tbl)
-    str = table.concat(remove_empty(tbl), ",")
-    if str == "" then
-      return str
-    end
-    return prefix .. str
-  end
-\end{luacode*}
-
-\newcommandx{\joinargs}[6][2=,3=,4=,5=,6=]{\directlua{tex.sprint(join_with_comma("#1", {"\luaescapestring{#2}";"\luaescapestring{#3}";"\luaescapestring{#4}";"\luaescapestring{#5}";"\luaescapestring{#6}"}))}}
 
@@
 
-% Universe, referred to as U
-\newcommand{\U}[1]{\ensuremath{\mathsf{\color{spanish-blue}{U}}_{#1}}}
-
-% The unit type
-\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
-\newcommand{\unitpoint}{\ensuremath{\star}}
-
-% Definitional and extensional equality
-\newcommand{\defeq}{\ensuremath{\triangleq}}
-\newcommand{\eqHSet}{\ensuremath{\equiv_{\mathit{HSet}}}}
-\newcommand{\reflHSet}{\ensuremath{\mathsf{refl}_{\mathit{HSet}}}}
-
 % Magic with xkeyval to go over the 9-argument limit of LaTeX
 \makeatletter
-\define@cmdkey{X}{D}{(#1)}
+\define@cmdkey[bonak]{X}{D}{(#1)}
 
-\define@cmdkey[prim]{frame}{D}{(#1)}
-\define@cmdkey[prim]{layer}{D}{(#1)}
-\define@cmdkey[prim]{layer}{d}{(#1)}
-\define@cmdkey[prim]{filler}{D}{(#1)}
-\define@cmdkey[prim]{filler}{E}{(#1)}
-\define@cmdkey[prim]{filler}{d}{(#1)}
-\define@cmdkey[prim]{fullframe}{D}{(#1)}
+\define@cmdkey[bonak]{frame}{D}{(#1)}
+\define@cmdkey[bonak]{layer}{D}{(#1)}
+\define@cmdkey[bonak]{layer}{d}{(#1)}
+\define@cmdkey[bonak]{filler}{D}{(#1)}
+\define@cmdkey[bonak]{filler}{E}{(#1)}
+\define@cmdkey[bonak]{filler}{d}{(#1)}
+\define@cmdkey[bonak]{fullframe}{D}{(#1)}
 
-\define@cmdkey[restr]{frame}{D}{(#1)}
-\define@cmdkey[restr]{frame}{d}{(#1)}
-\define@cmdkey[restr]{layer}{D}{(#1)}
-\define@cmdkey[restr]{layer}{d}{(#1)}
-\define@cmdkey[restr]{layer}{l}{(#1)}
-\define@cmdkey[restr]{filler}{D}{(#1)}
-\define@cmdkey[restr]{filler}{E}{(#1)}
-\define@cmdkey[restr]{filler}{d}{(#1)}
-\define@cmdkey[restr]{filler}{c}{(#1)}
+\define@cmdkey[bonak]{restrframe}{D}{(#1)}
+\define@cmdkey[bonak]{restrframe}{d}{(#1)}
+\define@cmdkey[bonak]{restrlayer}{D}{(#1)}
+\define@cmdkey[bonak]{restrlayer}{d}{(#1)}
+\define@cmdkey[bonak]{restrlayer}{l}{(#1)}
+\define@cmdkey[bonak]{restrfiller}{D}{(#1)}
+\define@cmdkey[bonak]{restrfiller}{E}{(#1)}
+\define@cmdkey[bonak]{restrfiller}{d}{(#1)}
+\define@cmdkey[bonak]{restrfiller}{c}{(#1)}
 
-\define@cmdkey[coh]{frame}{D}{(#1)}
-\define@cmdkey[coh]{frame}{d}{(#1)}
-\define@cmdkey[coh]{layer}{D}{(#1)}
-\define@cmdkey[coh]{layer}{d}{(#1)}
-\define@cmdkey[coh]{layer}{l}{(#1)}
-\define@cmdkey[coh]{filler}{D}{(#1)}
-\define@cmdkey[coh]{filler}{E}{(#1)}
-\define@cmdkey[coh]{filler}{d}{(#1)}
-\define@cmdkey[coh]{filler}{c}{(#1)}
-\makeatother
-
-% More magic: we patch xkeyval's \setkeys to use a mask to ignore keys
-\makeatletter
-% Our global mask
-\def\bonak@mask{}
-\def\bonak@na{}
-
-% First we define \appendmask
-\long\def\bonak@appendmask[#1]{
-  \XKV@for@eo\XKV@fams\XKV@tfam{
-    \def\bonak@hdr{\XKV@prefix\XKV@tfam @}
-    \XKV@for@o{#1}\XKV@tempa{
-      \XKV@addtolist@x\bonak@mask{\bonak@hdr\XKV@tempa}
-    }
-  }
-}
-\def\appendmask{\XKV@testopta{\XKV@testoptc\bonak@appendmask}}
-
-% Now we patch \XKV@setkeys
-\xpretocmd{\XKV@setkeys}{
-  \XKV@for@eo\XKV@fams\XKV@tfam{
-    \def\bonak@hdr{\XKV@prefix\XKV@tfam @}
-    \XKV@for@eo{\bonak@mask}\XKV@tempa{
-      \IfBeginWith{\XKV@tempa}{\bonak@hdr}{
-        \def\XKV@tempb{\StrBehind{\XKV@tempa}{\bonak@hdr}}
-        \XKV@addtolist@o\bonak@na{\XKV@tempb}}{}
-    }
-  }
-}{\tracingpatches}{\tracingpatches}
-\xpatchcmd{\XKV@setkeys}{#1}{\bonak@na}{\tracingpatches}{\tracingpatches}
+\define@cmdkey[bonak]{cohframe}{D}{(#1)}
+\define@cmdkey[bonak]{cohframe}{d}{(#1)}
+\define@cmdkey[bonak]{cohlayer}{D}{(#1)}
+\define@cmdkey[bonak]{cohlayer}{d}{(#1)}
+\define@cmdkey[bonak]{cohlayer}{l}{(#1)}
+\define@cmdkey[bonak]{cohfiller}{D}{(#1)}
+\define@cmdkey[bonak]{cohfiller}{E}{(#1)}
+\define@cmdkey[bonak]{cohfiller}{d}{(#1)}
+\define@cmdkey[bonak]{cohfiller}{c}{(#1)}
 \makeatother
@@
 % Truncated sets, otherwise referred to as X: the general macro
-\newcommandx*{\X}[3][1=,2=,3=]{
-  \ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{#2}}
-  \setkeys*{X}{#3}
+\newcommandx{\X}[3][1,2,3]{
+  \mathsf{\color{carolina}{X}}_{#1}^{#2}
+  \setkeys*[bonak]{X}{#3}
 }
@@
 % Frame, layer, and filler: the general macro
-\newcommandx*{\prim}[6][2=,3=,4=,5=,6=]{
+\newcommandx{\prim}[6][2,3,4,5,6]{
   \ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{
     \joinargs{}[#3][#4][#5]}}
-  \setkeys*[prim]{#1}{#6}
+  \setkeys*[bonak]{#1}{#6}
 }
@@
 % Restriction for frame, layer, and filler: the general macro
-\newcommandx*{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{
+\newcommandx{\restr}[8][2,3,4,5,6,7,8]{
   \ensuremath{\mathsf{\color{russian-green}{restr}}_{
@@
     \joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}
-  \setkeys*[restr]{#1}{#8}
+  \setkeys*[bonak]{restr#1}{#8}
 }
@@
 % #7 and #8 by hand in usage of \coh: it's now #7 or '#6,#7' in \cohfoo commands
-\newcommandx*{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{
+\newcommandx{\coh}[9][2,3,4,5,6,7,8,9]{
   \ensuremath{\mathsf{\color{chestnut}{coh}}_{
@@
     \joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}
-  \setkeys*[coh]{#1}{#9}
+  \setkeys*[bonak]{coh#1}{#9}
 }
 
+% Universe, referred to as U
+\newcommand{\U}[1]{\mathsf{\color{spanish-blue}{U}}_{#1}}
+
+% The unit type
+\newcommand{\unittype}{\mathsf{unit}}
+\newcommand{\unitpoint}{\star}
+
+% Definitional and extensional equality
+\newcommand{\defeq}{\triangleq}
+\newcommand{\eqHSet}{\ensuremath{\equiv_{\mathit{HSet}}}}
+\newcommand{\reflHSet}{\ensuremath{\mathsf{refl}_{\mathit{HSet}}}}
+
 % Some abbreviations
-\newcommand{\imp}{\ensuremath{\rightarrow}}
-\newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
-\renewcommand{\D}{\ensuremath{D}}
-\newcommand{\hdD}{\ensuremath{D.1}}
-\newcommand{\tlD}{\ensuremath{D.2}}
-\renewcommand{\d}{\ensuremath{d}}
-\newcommand{\E}{\ensuremath{E}}
-\renewcommand{\l}{\ensuremath{l}}
-\renewcommand{\c}{\ensuremath{c}}
-\newcommand{\pair}[2]{\ensuremath{#1, #2}}
+\newcommand{\imp}{\rightarrow}
+\newcommand{\overright}[1]{\overrightarrow{#1}}
+\renewcommand{\D}{D}
+\newcommand{\hdD}{D.1}
+\newcommand{\tlD}{D.2}
+\renewcommand{\d}{d}
+\newcommand{\E}{E}
+\renewcommand{\l}{l}
+\renewcommand{\c}{c}
+\newcommand{\pair}[2]{#1, #2}
 
@@
 % The eqntable environment, displaying the various
-\NewDocumentEnvironment{eqntable}{m}{\table[H]\small\hrule\vspace{0.5em}
-\tabularx{\textwidth}{@{} l c c >{\centering\arraybackslash}X @{}}}
-{\endtabularx\vspace{0.3em}\hrule\vspace{0.5em}\caption{#1}\endtable}
+\newcolumntype{Y}{>{\centering\arraybackslash}X}
+\NewEnviron{eqntable}[1]{
+  \begin{table}[H]
+    \small
+    \begin{tabularx}{\linewidth}{@{}>{$}l<{$} >{$}c<{$} >{$}c<{$} >{$}Y<{$} @{}}
+      \toprule
+      \BODY
+      \bottomrule
+    \end{tabularx}
+    \caption{#1}
+  \end{table}
+}
+
+% The label, since we're including twice
+\newcommand*{\lab}{}
+
+% \midrule color
+\def\graymidrule{\arrayrulecolor{gray30}\midrule\arrayrulecolor{gray65}}
 
 % A block in the eqntable environment
-\newcommand{\eqnline}[4]{$#1$ & $#2$ & $#3$ & $#4$ \\}
-\newcommand{\mc}[1]{\multicolumn{4}{c}{\emph{#1}} \\\\}
+\NewDocumentCommand{\eqnline}{m m m m}{#1 & #2 & #3 & #4 \\}
+\newcommandx*{\mc}[1]{\multicolumn{4}{c}{\emph{#1}} \\\\}
 
@@
             & Set theory & Type theory \\
-    \midrule
+    \graymidrule
     Fibered & CCHM       &             \\
-    \midrule
+    \graymidrule
     Indexed &            & Our work    \\
@@
 % Keep all arguments
-\newcommandx{\Xp}[1]{\X[#1][]}
-\newcommandx{\Xto}[2]{\X[#1][<#2]}
-\newcommandx{\Xcomp}[2]{\X[#1][=#2]}
-\newcommandx{\Xfrom}[2]{\X[#1][\geq#2]}
+\newcommandx{\Xp}[1]{\X[#1][][]}
+\newcommandx{\Xto}[3][3=]{\X[#1][<#2][#3]}
+\newcommandx{\Xcomp}[3][3=]{\X[#1][=#2][#3]}
+\newcommandx{\Xfrom}[3][3=]{\X[#1][\geq#2][#3]}
 
@@
 % Drop the universe letter
-\newcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][#2][#3][#4][#5]}
-\newcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][#2][#3][#4][#5]}
-\newcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][#2][#3][#4][#5]}
+\newcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
+\newcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
+\newcommandx{\filler}[5][1,2,3,4,5]{\prim{filler}[][#2][#3][#4][#5]}
 
@@
 % Drop the unviverse letter and q
-\newcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[][#2][][#4][#5][#6][#7]}
-\newcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[][#2][][#4][#5][#6][#7]}
-\newcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[][#2][][#4][#5][#6][#7]}
+\newcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][][#4][#5][#6][#7]}
+\newcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][][#4][#5][#6][#7]}
+\newcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][][#4][#5][#6][#7]}
 
@@
 % Keep only ε, ω; n, p; proposition on n and p
-\newcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][#2][#3][][][][][#9]}
-\newcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[][#2][#3][][][][][#9]}
-\newcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[][#2][#3][][][][][#9]}
+\newcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
+\newcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
+\newcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][][][][][#9]}
 
@@
 
+\renewcommand*{\lab}{tab:coind}
 \input{tab-coind.tex}
@@
 % For just the second table, keep the universe letter in fullframe
-\newcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[#1][#2][][][#3]}
+\newcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
+\renewcommand*{\lab}{tab:core}
 \input{tab-core.tex}
@@
 % Drop the universe letter in fullframe for all remaining tables
-\renewcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[][#2][][][#3]}
+\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
+\renewcommand*{\lab}{tab:frames}
 \input{tab-frames.tex}
 
-% From the third table onwards, make the {D, E} arguments of prims implicit
-\appendmask[prim]{frame}[D]
-\appendmask[prim]{layer}[D]
-\appendmask[prim]{filler}[D,E]
+% For the last two tables
+\appendmask[bonak]{frame}[D]
+\appendmask[bonak]{layer}[D]
+\appendmask[bonak]{filler}[D, E]
+\appendmask[bonak]{restrframe}[D]
+\appendmask[bonak]{restrlayer}[D, d]
+\appendmask[bonak]{restrfiller}[D, d]
 
@@
 % Drop the universe letter for the third and fourth tables
-\renewcommandx{\Xto}[2]{\X[][<#2]}
-\renewcommandx{\Xcomp}[2]{\X[][=#2]}
-\renewcommandx{\Xfrom}[2]{\X[][\geq#2]}
+\renewcommandx{\Xto}[3][3]{\X[][<#2][#3]}
+\renewcommandx{\Xcomp}[3][3]{\X[][=#2][#3]}
+\renewcommandx{\Xfrom}[3][3]{\X[][\geq#2][#3]}
 
 % The third table mentions cohframe; keep ε, ω in this instance
-\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
+\renewcommand*{\lab}{tab:faces}
 \input{tab-faces.tex}
+
+% For the last table,
+% (1) make the {d} arguments of restr implicit
+% (2) make the {D, E} arguments of coh implicit
+\appendmask[bonak]{cohframe}[D]
+\appendmask[bonak]{cohlayer}[D]
+\appendmask[bonak]{cohfiller}[D, E]
 
@@
 % Drop just the universe letter for the coh table
-\renewcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}
 
@@
 % Drop all arguments for coh table; they're not present in coind table.
-\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][][][][#5]}
-\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][][][][#5]}
-\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][][][][#5]}
+\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][][][][#5]}
+\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][][][][#5]}
+\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{filler}[][][][][#5]}
 
@@
 % Drop universe letter, ε, and ω
-\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][][][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[][][][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[][][][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][][][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][][][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][][][#4][#5][#6,#7][#8][#9]}
+\renewcommand*{\lab}{tab:coh}
 \input{tab-coh.tex}
@@
 \section{Tables in full detail}
+% Clear the mask and label
+\clearmask
+
 % Keep all arguments for all macros
 % Frame, layer, and filler
-\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[#1][#2][#3][#4][#5]}
-\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[#1][#2][#3][#4][#5]}
-\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[#1][#2][#3][#4][#5]}
-\renewcommandx{\fullframe}[3][1=,2=,3=]{\prim{fullframe}[#1][#2][][][#3]}
+\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[#1][#2][#3][#4][#5]}
+\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[#1][#2][#3][#4][#5]}
+\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{filler}[#1][#2][#3][#4][#5]}
+\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
 
 % Restriction for frame, layer, and filler
-\renewcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[#1][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[#1][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[#1][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[#1][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[#1][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[#1][#2][#3][#4][#5][#6][#7]}
 
 % Coherence conditions for frame, layer, and filler
-\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
 
+\renewcommand*{\lab}{fulltab:coind}
 \input{tab-coind.tex}
+\renewcommand*{\lab}{fulltab:core}
 \input{tab-core.tex}
+\renewcommand*{\lab}{fulltab:frames}
 \input{tab-frames.tex}
@@
 \begin{landscape}
+  \renewcommand*{\lab}{fulltab:faces}
   \input{tab-faces.tex}
+  \renewcommand*{\lab}{fulltab:coh}
   \input{tab-coh.tex}

### 2022-06-07 paper/paper.tex
xkeymask.sty: get ready to package with option-parsing
paper: MAJ; polish

@@
 
-\usepackage{multirow, minted, tabularx, environ, booktabs, setspace, makecell, caption, xkeymask, joinargs, colortbl, pdflscape, ct, sset}
+\usepackage{multirow, minted, tabularx, environ, booktabs, setspace, makecell, caption, joinargs, colortbl, pdflscape, ct, sset}
+\usepackage[prefix=bonak]{xkeymask}
 \usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}
@@
 
-Our contribution is to model the core of semi-cubical sets that naturally generalizes to semi-simplicial sets in type theory, and we call our generalization \emph{truncated $n$-sets}.
-In contrast to previous efforts that use a fibered representation, we use an indexed representation, that can be derived from the fibered one using a \emph{iterated reverse-Grothendieck} construction.
-Our work is, in principle axiom-free, although the accompanying artifact uses functional extensionality in order to generalize our work to $n$-truncated sets.
+Our contribution is the following.
+We have modelled the core of semi-cubical sets in a way that naturally generalizes to semi-simplicial sets in type theory, and we call our generalization \emph{$\nu$-sets}.
+In contrast to previous efforts that use a fibered representation, we use an indexed representation.
+Our work is, in principle axiom-free, although the accompanying artifact uses functional extensionality, and this requires disappears if $\nu$ is finite.
 
@@
 The outline of the paper is as follows.
-First, we take the opportunity to familize the reader with simplicial sets, as it appears in mathematical literature, along with a short section on semi-cubical sets.
+First, we briefly describe semi-simplicial and semi-cubical sets, as it appears in mathematical literature.
 We then proceed to explain our construction, with the help of diagrams.
@@
 Unlike CW-complexes that rely on pure topological notions like spheres and disks to ``tame'' a topological space, the definition of simplicial sets is purely categorical, and exist independent of topological spaces.
-The \emph{geometric realization} and \emph{singular complex} functors facilitate travelling back-and-forth between simplicial sets and topological spaces, and these are non-trivial constructions.
 As such, simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
+What we have formalized is \emph{augmented} semi-simplicial sets, and semi-cubical sets, which is to say that they are the usual simplicial sets and cubical sets, minus the degeneracies.
 
 \subsection{Augmented semi-simplicial sets}
-The first step towards formalizing simplicial sets is to forget about the degeneracies, and we restrict ourselves to representing \emph{augmented simplicial sets}, otherwise known as delta-sets in mathematical literature.
-We now proceed to describe \DeltaHat, which is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are \emph{strictly} order-preserving.
+Semi-simplicial sets are otherwise known as \emph{delta-sets} in mathematical literature.
+Since they are of little interest to the mathematician, we briefly describe \DeltaHat, which is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are \emph{strictly} order-preserving.
 The degeneracies then vanish, and we're left with the task of defining gluing conditions solely on the basis of face maps.
-In mathematical literature, there is little interest in studying \DeltaHat, since maps between delta sets are not well-defined, and it is therefore not possible to construct a category of delta sets.
+There is little interest in studying \DeltaHat, since maps between delta sets are not well-defined, and it is therefore not possible to construct a category of delta sets.
 
@@
 \section{Our construction}
-The fibered representation:
-
+The fibered representation can be drawn as:
 \begin{equation*}
@@
 
-The indexed representation:
+The indexed representation can be drawn as:
 \begin{align*}

### 2022-06-08 paper/paper.tex
paper: uniform appendmask without bugs
xkeymask: introduce ifinmask to query mask; show implicits in { ... }
paper: major polish

@@
 
+% \eqnarg is slightly more involved: output ( ... ) if not in mask,
+% and { ... } if in mask
+\newcommandx*{\eqnarg}[3]{\ifinmask[bonak]{#1}[#2]{\{#2:#3\}}{(#2:#3)}}
+
 % Table caption set up
@@
   \textcolor{gray80}{Hugo Herbelin} \\
-  \itshape \textcolor{gray80}{Instit de Recherche en Informatique Fondamentale}
+  \itshape \textcolor{gray80}{Institut de Recherche en Informatique Fondamentale}
 }
@@
 Cubical type theory~\cite{Bezem14}~\cite{Cohen16}~\cite{Angiuli17} is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT.
-Two real-world projects that implement cubical type theory are worthy of mention: an experimental branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}, and the Arend theorem prover~\footnote{\href{https://arend-lang.github.io}{arend-lang.github.io}}.
+The most significant implementation of cubical type theory in the real world is an experimental branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}.
 Cubical type theory is usually modeled as cubical sets, in the set-theoretic setting.
-Efforts to model cubical type theory have been ongoing since 2014, and many of these efforts are in the set-theoretic setting.
 
 Our contribution is the following.
-We have modelled the core of semi-cubical sets in a way that naturally generalizes to semi-simplicial sets in type theory, and we call our generalization \emph{$\nu$-sets}.
+We have modelled the core of semi-cubical sets in a way that naturally generalizes to augmented semi-simplicial sets in type theory, and we call our generalization \emph{$\nu$-sets}.
 In contrast to previous efforts that use a fibered representation, we use an indexed representation.
@@
 The outline of the paper is as follows.
-First, we briefly describe semi-simplicial and semi-cubical sets, as it appears in mathematical literature.
+First, we briefly describe augmented semi-simplicial and semi-cubical sets, as it appears in mathematical literature, and our generalization to $\nu$-sets.
 We then proceed to explain our construction, with the help of diagrams.
-Before spelling out the details of our formalization in type-theoretic language, we have a section on reasoning in sets, in which we spell out \texttt{HSet}.
+Before spelling out the details of our formalization in type-theoretic language, we have a section on reasoning in sets.
 
-\section{\texorpdfstring{$\nu$}{nu}-sets}
-Simplicial sets are powerful mathematical objects, that form the basis of much of modern homotopy theory.
-Their power derives from the fact that their homotopy category is exceptionally well-behaved, and that there are multiple model structures defined on them.
-Unlike CW-complexes that rely on pure topological notions like spheres and disks to ``tame'' a topological space, the definition of simplicial sets is purely categorical, and exist independent of topological spaces.
-As such, simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
+\section{Mathematical treatment of \texorpdfstring{$\nu$}{nu}-sets}
+It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
 What we have formalized is \emph{augmented} semi-simplicial sets, and semi-cubical sets, which is to say that they are the usual simplicial sets and cubical sets, minus the degeneracies.
+Since they're not of particular interest, and indeed, we plan to extend our work to do degeneracies in the future, we briefly explain the mathematical objects we have formalized.
 
@@
 
+\subsection{Generalization to \texorpdfstring{$\nu$}{nu}}
+
+\begin{table}[H]
+  \begin{tabularx}{\linewidth}{p{.2\linewidth}|p{.4\linewidth}|p{.3\linewidth}}
+    \toprule
+    Value of $\nu$ & 1                              & 2                  \\
+    \graymidrule
+    Interpretation & Augmented semi-simplical types & Semi-cubical types \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
+
 \section{Our construction}
-The fibered representation can be drawn as:
+In this section, we briefly explain the difference between the fibered and indexed representations, and illustrate our approach to the construction, with the help of some figures.
+
+The fibered representation can be illustrated as:
 \begin{equation*}
@@
 
-The indexed representation can be drawn as:
+The indexed representation can be illustrated as:
 \begin{align*}
@@
 
+One way to obtain one construction from the other is via the \emph{Grothendieck construction}, although this is not relvant to our work.
+
+\subsection{Iterated parameteriticity}
+
 \section{Reasoning about sets in type theory}
-We dedicate this section to discussing UIP in different settings, and supply intuitions into this notion.
+Since proof irrelevance is an inherent part of set theory and first-order logic, and proof irrelevance is \emph{extensional} in type theory, we work in a universe known as \texttt{HSet}, which we describe shortly.
 
+\subsection{Unicity of identity proofs}
 UIP is a flavor of proof-irrelevance:
@@
 
-Proof irrelevance is an inherent part of set theory and first-order logic, although the property cannot be stated in the language of natural deductions.
-Intuititively, what it means is that a tree of deductions converges to a result, with no memory of the proof route; the tree itself is forgotten once the final result is obtained.
+In type theory, UIP can be proved on the unit type:
+
+\begin{align*}
+  \mathsf{eq\_refl}        & : \forall x, x = x                               \\
+  \mathsf{UIP\_refl\_unit} & : \forall x : \top = \top, x = \mathsf{eq\_refl}
+\end{align*}
+
+\subsection{HSet}
+\texttt{HSet} provides us a restricted setting of UIP, and our implementation of \texttt{HSet} is a straightforward packaging of two fields:
+
+\begin{align*}
+  \mathsf{Dom} & : \mathsf{Type}                                          \\
+  \mathsf{UIP} & : \forall x y : \mathsf{Dom}, \forall p q : x = y, p = q
+\end{align*}
+
+In the \texttt{HSet} universe, three properties hold:
+
+\begin{enumerate}
+  \item[(i)] UIP holds on the unit type.
+  \item[(ii)] UIP propogates to $\Sigma$-types.
+  \item[(iii)] UIP propogates to $\Pi$-types, with some additional functional extensionality axioms.
+\end{enumerate}
 
 \section{Type-theoretic construction of \texorpdfstring{$\nu$}{nu}-sets}
-In this section, we give the core of the definition of truncated $\nu$-sets
-as a coinductive limit.
+% Abbreviated tables in this section
+%
+% The rule for implicit arguments for each table:
+% show 1 explicit in first two parts
+% show E + 1 explicit in the third part
+\appendmask[bonak]{layer}[D]
+\appendmask[bonak]{filler}[D]
+\appendmask[bonak]{restrframe}[D]
+\appendmask[bonak]{restrlayer}[D, d]
+\appendmask[bonak]{restrfiller}[D, d]
+\appendmask[bonak]{cohframe}[D]
+\appendmask[bonak]{cohlayer}[D, d]
+\appendmask[bonak]{cohfiller}[D, d]
 
@@
 
-The definition is dispatched over tables \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and \ref{tab:coh}.
-It describes the structure of the underlying higher-dimensional relations on which fillers are built.
-Note the presence of a coherence condition $\cohf$ to ensuring that both sides of the equality in $\restrl$ and $\restrc$ are in the same type.
-The proof of $\cohf$ itself requires an higher-dimensional coherence condition which we obtain by working in HSet.
-Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-Note also that for a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
-
-We call the structure thus defined \emph{bare truncated sets}: \emph{bare} because it can be seen as defining truncated $\nu$-sets corresponding to simplical sets with only faces as part of the structure.
+The definition in \ref{tab:coind}, the coinductive limit, is dispatched over tables \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and \ref{tab:coh}.
+They describe the structure of the underlying higher-dimensional relations on which fillers are built.
 
@@
 \newcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
+
+We now describe \emph{bare truncated sets}: \emph{bare} because it can be seen as defining truncated $\nu$-sets without face maps, and \emph{truncated} because it is $n$-truncated.
+
 \renewcommand*{\lab}{tab:core}
@@
 
-% For the last two tables
-\appendmask[bonak]{frame}[D]
-\appendmask[bonak]{layer}[D]
-\appendmask[bonak]{filler}[D, E]
-\appendmask[bonak]{restrframe}[D]
-\appendmask[bonak]{restrlayer}[D, d]
-\appendmask[bonak]{restrfiller}[D, d]
-
 % Truncated sets, otherwise referred to as X
@@
 
+% Hack to remove , in \cohf
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
+
+In the way we have chosen to formlate these tables, there is, for instance, coherence condition $\cohf$ both sides of the equality in $\restrl$ and $\restrc$, to ensure that they are the same type.
+
+For a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
+
 % The third table mentions cohframe; keep ε, ω in this instance
 \renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
+
 \renewcommand*{\lab}{tab:faces}
 \input{tab-faces.tex}
-
-% For the last table,
-% (1) make the {d} arguments of restr implicit
-% (2) make the {D, E} arguments of coh implicit
-\appendmask[bonak]{cohframe}[D]
-\appendmask[bonak]{cohlayer}[D]
-\appendmask[bonak]{cohfiller}[D, E]
 
@@
 
+% Hack to remove , in \cohf
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
+
+The proof of $\cohf$ require an higher-dimensional coherence condition which we obtain by working in \texttt{HSet}.
+If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
+
 % Coherence conditions for frame, layer, and filler
@@
 \renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][][][#4][#5][#6,#7][#8][#9]}
+
 \renewcommand*{\lab}{tab:coh}
@@
 \section{Tables in full detail}
+% Full tables in this section
+%
 % Clear the mask and label

### 2022-06-18 paper/param2.tex
Adding 2019 version of the paper description of the construction

%\documentclass[sigplan]{acmart}
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage{t1enc}

\usepackage{hyperref}
%\usepackage{proof}
\usepackage{fullpage}
\usepackage{amssymb}
\usepackage{stmaryrd}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{color}
%\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{yfonts}
\usepackage[all]{xy}
\xyoption{2cell}
\UseAllTwocells

\makeatletter
\newcommand{\Overrightarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#2}$}}{}$}}
\newcommand{\Overleftarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Leftarrowfill@{\mbox{${#2}$}}{}$}}
%\newcommand{\Overrightarrow}[1]{\raisebox{1.4ex}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#1}$}}{}$}}
\makeatother

\newcommand{\highlight}[1]{{\em #1}}

\include{macros}
\newcommand{\Type}{\mathsf{Type}}
\newcommand{\Set}{\mathsf{Set}}
\newcommand{\Prop}{\mathsf{Prop}}
\newcommand{\refl}[1]{\mathsf{refl}\,{#1}}
\newcommand{\mkmlidtype}[3]{{#1} =^{\mathrm{id}}_{#2} {#3}}
\newcommand{\mkmleqdep}[3]{{#1} =^{\mathrm{dep}}_{#2} {#3}}
\newcommand{\hrefl}[1]{\mathsf{refl^{\mathrm{dep}}}\,{#1}}
\newcommand{\mluniv}{\mathsf{U}}
\newcommand{\Jdep}[2]{\mathsf{J}\;{#1}\;{#2}}

\newcommand{\nth}[1]{{#1}^{\mbox{\scriptsize th}}}
\newcommand{\binomial}[2]{\left(\begin{array}{c}#1\\#2\end{array}\right)}

\newcommand{\wfctx}[1]{{#1}~\mathsf{ok}}

\newcommand{\mkover}[1]{\widetilde{#1}}
\newcommand{\mkoverdim}[2]{\widetilde{#2}^{#1}}
%\newcommand{\mkover}[1]{\dot{#1}}
\newcommand{\mkprod}[3]{\Pi {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkprodovereq}[3]{\mkover{\Pi} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkprodovereqopp}[3]{\opp{\mkover{\Pi}} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkboundedprod}[4]{\Pi {#3}\!:\!{#1}\leq{#2}.\,{#4}}
\newcommand{\mklam}[3]{\lambda {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkboundedlam}[4]{\lambda {#3}\!:\!{#1}\leq{#2}.\,{#4}}
\newcommand{\mkapp}[2]{{#1}\,{#2}}
\newcommand{\prodsort}[2]{\Pi ({#1},{#2})}

% selecting kind of treatment of sorts
\newcommand{\typeorsort}[2]{{#2}}

\newcommand{\mksigma}[3]{\Sigma {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mksigmaovereq}[3]{\mkover{\Sigma} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mksigmaovereqopp}[3]{\opp{\mkover{\Sigma}} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkpair}[2]{\langle{#1},{#2}\rangle}
\newcommand{\mkfst}[1]{{#1}.1}
\newcommand{\mksnd}[1]{{#1}.2}
\newcommand{\sigsort}[2]{\Sigma ({#1},{#2})}

\newcommand{\sortsort}[1]{{\mathcal S}_{#1}}

\newcommand{\Sone}{\mathbb{S}^1}
\newcommand{\casesone}[5]
  {\mathsf{case}\;{#1}\;\mathsf{of}\;{#2}\;\Rightarrow\;{#3}\;|\;{#4}\;\Rightarrow\;{#5}\;\mathsf{end}}
\newcommand{\base}{\mathsf{base}}
\newcommand{\loopsone}{\mathsf{loop}}
\newcommand{\Sonesort}{l_{\mathbb{S}^1}}

\newcommand{\emptyctx}{\boxbox}

\newcommand{\sort}[1]{\mathsf{U}_{#1}}
\newcommand{\univ}{\boxempty}
%\newcommand{\istype}{~:~S}
\newcommand{\typeannot}{\mathsf{type}}
\newcommand{\istype}{~\typeannot}

\newcommand{\mkeq}[3]{{#1} =_{#2} {#3}}
\newcommand{\mkhomeq}[3]{{#1} =_{#2} {#3}}
\newcommand{\mkeqovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}}
\newcommand{\mkeqovereqdim}[4]{{#2} \,\mkoverdim{#1}{=}_{#3}\, {#4}}
%\newcommand{\mkeqtype}[3]{{#1} =_{#2} {#3}} % case where we can write either s or refl{s}
\newcommand{\mkeqtype}[3]{{#1} =_{\typeannot} {#3}}
\newcommand{\mkeqtypeovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}} % case where we can write either s or refl{s}
\newcommand{\mkeqarray}[3]{\begin{array}{c}{#1}\\ =_{#2}\\ {#3}\end{array}}
\newcommand{\mkfaces}[3]{\mkeq{#1}{#2}{#3}}
\newcommand{\mkfacesarray}[3]{\mkeqarray{#1}{#2}{#3}}
\newcommand{\mkfacesover}[3]{\mkeqovereq{#1}{#2}{#3}}
\newcommand{\lameq}[2]{\lambda {#1}.{#2}}
%\newcommand{\reflterm}[1]{\textsf{refl}{#1}}
\newcommand{\reflterm}[1]{\widehat{#1}}
\newcommand{\overreflterm}[1]{{\mkover{\reflterm{#1}}}}
\newcommand{\refltermdim}[2]{{\widehat{#2}}^{#1}}
%\newcommand{\reflterm}[1]{\lambda{#1}}
%\newcommand{\refltype}[1]{\lambda{#1}}
\newcommand{\refltype}[1]{\reflterm{#1}}
\newcommand{\purerewlr}[1]{\overrightarrow{#1}}
\newcommand{\purerewrl}[1]{\overleftarrow{#1}}
%\newcommand{\rewlr}[2]{\mathsf{rew}^\rightarrow\;{#1}\;\mathsf{in}\;{#2}}
%\newcommand{\rewrl}[2]{\mathsf{rew}^\leftarrow\;{#1}\;\mathsf{in}\;{#2}}
\newcommand{\rewlr}[2]{\overrightarrow{#1}(#2)}
\newcommand{\rewrl}[2]{\overleftarrow{#1}(#2)}
\newcommand{\deprewlr}[1]{\raisebox{0em}{$\ulcorner$}\!#1}
\newcommand{\deprewrl}[1]{{#1}\raisebox{-0.2em}{$\!\lrcorner$}}
\newcommand{\rewlrspec}[2]{{#1}^{\rightarrow}(#2)}
\newcommand{\rewrlspec}[2]{{#1}^{\leftarrow}(#2)}
\newcommand{\rewlrrevspec}[2]{{#1}_-^{\rightarrow}(#2)}
\newcommand{\rewrlrevspec}[2]{{#1}_-^{\leftarrow}(#2)}
\newcommand{\rewlrrevspecin}[2]{{#1}_+^{\rightarrow}(#2)}
\newcommand{\rewrlrevspecin}[2]{{#1}_+^{\leftarrow}(#2)}
\newcommand{\doublerewlr}[2]{\Overrightarrow{1.4ex}{#1}({#2})}
\newcommand{\doublerewrl}[2]{\Overleftarrow{1.4ex}{#1}({#2})}
%\newcommand{\mktuple}[6]{\{#1\mapsto #3(#1); #2\mapsto #4(#2); #1\mapsto #5(#1); #2\mapsto #6(#2)\}}
\newcommand{\mktuple}[6]{\{#3; #4; #5; #6\}_{#1,#2}}
\newcommand{\mktupleshort}[6]{\{#3; #4; #5; #6\}}
\newcommand{\opp}[1]{{#1}^{-1}}
\newcommand{\oppi}[2]{\appi{#1}{(\opp{#2}/{#2})}}

\newcommand{\weakensquarelr}[2]{{#1}_L(#2)}
\newcommand{\weakensquarerl}[2]{{#1}_R(#2)}

\newcommand{\rewlrmkeq}[4]{\mkeq{\rewlr{#1}{#2}}{#3}{#4}}

% Version basse
%% \newcommand{\appi}[2]{{#1}_{#2}}
%% \newcommand{\appidep}[2]{{#1}_{({#2})}}
%% \newcommand{\bp}[1]{{#1}_0}
%% \newcommand{\ep}[1]{{#1}_1}
%% \newcommand{\bpdep}[1]{{#1}_{(0)}}
%% \newcommand{\epdep}[1]{{#1}_{(1}}}
% Version haute
% \newcommand{\metaappi}[2]{{#1}_{[{#2}]}}
\newcommand{\appi}[2]{{#1}\;\!{#2}}
\newcommand{\appidep}[2]{{#1}_{#2}}
\newcommand{\bp}[1]{{#1}{\scriptstyle 0}}
\newcommand{\ep}[1]{{#1}{\scriptstyle 1}}
\newcommand{\bpoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{0}}}
\newcommand{\epoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{1}}}
\newcommand{\bpdep}[1]{{#1}_0}
\newcommand{\epdep}[1]{{#1}_1}

\newcommand{\bpsubstexpl}[2]{{#2}_{\{0/{#1}\}}}
\newcommand{\epsubstexpl}[2]{{#2}_{\{1/{#1}\}}}
\newcommand{\eqsubstexpl}[2]{{#2}_{\{\star/{#1}\}}}
\newcommand{\bpsubstexplcons}[2]{{#2}\}\{0/{#1}}
\newcommand{\epsubstexplcons}[2]{{#2}\}\{1/{#1}}
\newcommand{\eqsubstexplcons}[2]{{#2}\}\{\star/{#1}}
\newcommand{\bpsubst}[2]{{#2}{[0/{#1}]}}
\newcommand{\epsubst}[2]{{#2}{[1/{#1}]}}
\newcommand{\bpsubstctx}[3]{{#3}{[0/{#2}]}^{#1}}
\newcommand{\epsubstctx}[3]{{#3}{[1/{#2}]}^{#1}}
\newcommand{\takebpface}[2]{\partial^{#1}_0{#2}}
\newcommand{\takeepface}[2]{\partial^{#1}_1{#2}}

\newcommand{\dimvalid}[2]{{#1} \in {#2}}
\newcommand{\dimdeclare}[1]{{#1}}
\newcommand{\dimlength}[1]{|#1|_{\mathit{dim}}}
\newcommand{\dimindex}[2]{\#_{#1}{#2}}

\newcommand{\substminus}[2]{{#1}-{#2}}
\newcommand{\substminusbernardymoulin}[2]{{#1}/{#2}}

\newcommand{\N}{\mathbb{N}}
\newcommand{\expand}[2]{\mathsf{expand}(#1,#2)}

\newcommand{\defeq}{\triangleq}
%\newcommand{\metaequiv}{=\!\!\!=}
\newcommand{\metaequiv}{\cong}
\newcommand{\metaletin}[3]{\mathit{let}\;{#1}\;\defeq\;{#2}\;\mathit{in}\;{#3}}
\newcommand{\map}[2]{\mathsf{ap}\,{#1}\,{#2}}
\newcommand{\depmap}[2]{\mathsf{apd}\,{#1}\,{#2}}
\newcommand{\transport}[3]{\mathsf{transport}\,{#1}\,{#2}\,{#3}}
\newcommand{\deptransport}[3]{\mathsf{transportd}\,{#1}\,{#2}\,{#3}}
%\newcommand{\swap}[1]{\mathsf{swap}(#1)}
%\newcommand{\swapbracket}[1]{\mathsf{swap}(#1)}
%\newcommand{\swaptype}[1]{\mathsf{swap}(#1)}
\newcommand{\swap}[1]{{#1}^{\circ}}
\newcommand{\swapbracket}[1]{({#1})^{\circ}}
\newcommand{\swaptype}[1]{{#1}^{\circ}}
\newcommand{\swapoverdim}[2]{{#2}^{\mkoverdim{#1}{\circ}}}
\newcommand{\homsquare}[1]{\mathsf{homsquare}(#1)}
\newcommand{\permute}[2]{\mathsf{permute}_{#1}(#2)}
\newcommand{\swapprodeq}[2]{\mathsf{swap}_{\Pi=}^{#1}(#2)}
\newcommand{\swapeqprod}[2]{\mathsf{swap}_{=\Pi}^{#1}(#2)}
\newcommand{\swapeqprodlr}[2]{\mathsf{swap}_{=\Pi}^{\rightarrow}({#1})(#2)}
\newcommand{\swapeqprodrl}[2]{\mathsf{swap}_{=\Pi}^{\leftarrow}({#1})(#2)}
\newcommand{\swapsigmaeq}[1]{\mathsf{swap}_{\Sigma=}(#1)}
\newcommand{\swapeqsigma}[1]{\mathsf{swap}_{=\Sigma}(#1)}

\newcommand{\bool}{\mathsf{bool}}
\newcommand{\booldeux}{\bool^2}
\newcommand{\boolexp}{\bool^{\bool}}

\newcommand{\reduce}{\;\triangleright\;}

\newcommand{\emptysubst}{\emptyctx}

\newcommand{\sortrule}{\sort{}}
\newcommand{\axrule}{\mathsf{Ax}}
\newcommand{\ctxemptyrule}{\mathsf{Ctx}_{\emptyctx}}
\newcommand{\ctxconsrule}{\mathsf{Ctx}_{\mathsf{cons}}}
\newcommand{\convrule}{\mathsf{Conv}}
\newcommand{\convconvrule}{\mathsf{Conv}-\mathsf{Conv}}
\newcommand{\univrule}{\mathsf{\univ}}
\newcommand{\convruleredright}{\reduce_R}
\newcommand{\convruleredleft}{\reduce_L}
\newcommand{\convrulerefl}{\equiv_{\mathsf{refl}}}
\newcommand{\convruletrans}{\equiv_{\mathsf{trans}}}
\newcommand{\convruleredtyperight}{\reduce_R^{\typeannot}}
\newcommand{\convruleredtypeleft}{\reduce_L^{\typeannot}}
\newcommand{\convruletyperefl}{\equiv_{\mathsf{refl}}^{\typeannot}}
\newcommand{\convruletypetrans}{\equiv_{\mathsf{trans}}^{\typeannot}}

\newcommand{\circovereq}{\;\mkover{\circ}\;}
\newcommand{\circsigma}{\circ_{\Sigma}}

\newcommand{\comprule}{R_{\mathsf{\circ}}}
\newcommand{\opprule}{R_{\mathsf{\opp}}}

\newcommand{\idleftredrule}{\mathsf{Id_L}}
\newcommand{\idrightredrule}{\mathsf{Id_R}}
\newcommand{\idoppredrule}{\mathsf{\opp{Id}}}
\newcommand{\oppoppredrule}{\mathsf{\opp{(\opp{\_})}}}
\newcommand{\assoccompredrule}{\mathsf{Assoc}}
\newcommand{\distriboppcompredrule}{\mathsf{\opp{\circ}}}
\newcommand{\squaredownredrule}{\circ_{=_{\mkover{=}}}}
\newcommand{\exchangerule}{\mathsf{Exch}}
\newcommand{\compeqovereqredrule}{\circ_{\mkover{=}}}
\newcommand{\squareprodredrule}{\circ_{=_{\mkover{\Pi}}}}

\newcommand{\depmapdef}{\mathsf{ApD}}
\newcommand{\funextpuredef}{\mathsf{LiftDim}}
\newcommand{\funextdeppuredef}{\mathsf{LiftDepDim}}
\newcommand{\funextdepdeppuredef}{\mathsf{LiftDepDim}}
\newcommand{\funextdef}{\mathsf{FunExt}}
\newcommand{\funextdepdef}{\mathsf{FunDepExt}}
\newcommand{\funext}[1]{\mathsf{funext}(#1)}
\newcommand{\funextdep}[1]{\mathsf{fundepext}(#1)}
\newcommand{\funextpure}[1]{\mathsf{liftdim}(#1)}
\newcommand{\funextdeppure}[1]{\mathsf{liftdepdim}(#1)}

\newcommand{\OMEGATT}{\omega\mathsf{TT}}

\begin{document}

\title{Iterated syntactic parametricity translation}

\maketitle

\newcommand{\emptysigma}{\bullet}
\newcommand{\itsemterm}[4]{\llbracket #4 \rrbracket^{#2;#3}_{#1}}
\newcommand{\itsemtype}[4]{\llbracket #4 \rrbracket^{#2;#3}_{#1}}
\newcommand{\semterm}[3]{\llbracket #3 \rrbracket^{#1;#2}}
\newcommand{\semtype}[3]{\llbracket #3 \rrbracket^{#1;#2}}
\newcommand{\incrstep}[3]{\mathsf{split}_{#1}{#3}(#2)}
\newcommand{\distrstep}[3]{\mathsf{distr}_{#1}{#3}(#2)}
\newcommand{\applytype}[4]{\mathsf{apptype}_{#1}^{#2}(#3,#4)}
\newcommand{\shrink}[3]{\mathsf{shrink}_{#1}\,{#2}\,#3}
\newcommand{\under}[3]{\mathsf{under}_{#1}\,{#2}\,#3}
\newcommand{\undertau}[3]{\mathsf{under}_{#1}^{#2}\,#3}
\newcommand{\proj}[3]{\pi_{#1}^{#2}\,#3}
\newcommand{\elt}[2]{\mathsf{El}_{#1}\,#2}
\newcommand{\semtypenew}[2]{| #2 |_{#1}}
\newcommand{\semnew}[2]{\llbracket #2 \rrbracket_{#1}}
\newcommand{\semctx}[2]{\llbracket #2 \rrbracket_{#1}}
\newcommand{\semlam}[5]{\mathsf{lam}_{#1}^{#2}\,#4\,(#3)\,#5}
\newcommand{\semlambis}[5]{\mathsf{lam'}_{#1}^{#2}\,#4\,(#3)\,#5}
\newcommand{\semapp}[3]{\mathsf{app}_{#1}#2\,#3}
\newcommand{\semprod}[5]{\mathsf{prod}_{#1}^{#2}\,#4\,(#3)\,#5}
\newcommand{\access}[2]{\mathsf{get}_{#1}(#2)}
\newcommand{\accesstyped}[3]{\mathsf{get}_{#1}^{#2}(#3)}
\newcommand{\lift}[1]{\mathsf{lift}\, {#1}}
\newcommand{\liftlr}[1]{\mathsf{lift}^\rightarrow\, {#1}}
\newcommand{\liftrl}[1]{\mathsf{lift}^\leftarrow\, {#1}}
\newcommand{\diag}[2]{\mathsf{diag}_{#1}(#2)}
\newcommand{\semsort}[1]{\mathsf{sort}_{#1}}
\newcommand{\reflsort}[1]{\mathsf{refl}^{\sort{}}_{#1}}
\newcommand{\mktuplenew}[6]{\{#4\,|\begin{array}{l} #5 \\ #6 \end{array}\}_{#1,#2,#3}}
\newcommand{\mktuplein}[4]{{#1}; {#2}; {#3}; {#4}}
\newcommand{\nwconn}[2]{\deprewlr{#2}_{#1}}
\newcommand{\seconn}[2]{\deprewrl{#2}_{#1}}
\newcommand{\refltermn}[3]{\mathsf{reflterm}_{#1}(#3)}
\newcommand{\refltypen}[2]{\mathsf{refltype}_{#1}(#2)}

\newcommand{\restrict}{\mathsf{restrict}}
\newcommand{\MofL}{\mathsf{underlying}}
\newcommand{\defequiv}{\mathsf{\simeq}}
\newcommand{\isequivalence}{\mathsf{isequiv}}
\newcommand{\gpdlevel}{\mathsf{gpdlevel}}
\newcommand{\regrefl}{\mathsf{regrefl}}
\newcommand{\mybox}[1]{\mathsf{r\mbox{-}box}_{#1}}
\newcommand{\mylayer}[1]{\mathsf{r\mbox{-}layer}_{#1}}
\newcommand{\mycube}[1]{\mathsf{r\mbox{-}cube}_{#1}}
\newcommand{\myheterobox}[1]{\mathsf{box}_{#1}}
\newcommand{\myheterolayer}[1]{\mathsf{layer}_{#1}}
\newcommand{\myheterocube}[1]{\mathsf{cube}_{#1}}
\newcommand{\myheteroboxtype}[1]{\mathsf{Box}_{#1}}
\newcommand{\myheterolayertype}[1]{\mathsf{Layer}_{#1}}
\newcommand{\myheterocubetype}[1]{\mathsf{Cube}_{#1}}
\newcommand{\myheterodepbox}[1]{\mathsf{d\mbox{-}box}_{#1}}
\newcommand{\myheterodeplayer}[1]{\mathsf{d\mbox{-}layer}_{#1}}
\newcommand{\myheterodepcube}[1]{\mathsf{d\mbox{-}cube}_{#1}}
\newcommand{\myheterodepboxtype}[1]{\mathsf{d\mbox{-}Box}_{#1}}
\newcommand{\myheterodeplayertype}[1]{\mathsf{d\mbox{-}Layer}_{#1}}
\newcommand{\myheterodepcubetype}[1]{\mathsf{d\mbox{-}Cube}_{#1}}
\newcommand{\downbox}[2]{\mathsf{r\mbox{-}subbox}_{#1,#2}}
\newcommand{\downlayer}[2]{\mathsf{r\mbox{-}sublayer}_{#1,#2}}
\newcommand{\downcube}[2]{\mathsf{r\mbox{-}subcube}_{#1,#2}}
%\newcommand{\downboxleft}{\mathsf{subbox}^L}
%\newcommand{\downboxright}{\mathsf{subbox}^R}
%\newcommand{\downlayerleft}{\mathsf{sublayer}^L}
%\newcommand{\downlayerright}{\mathsf{sublayer}^R}
%\newcommand{\downcubeleft}{\mathsf{subcube}^L}
%\newcommand{\downcuberight}{\mathsf{subcube}^R}
%% \newcommand{\downboxleft}{\downarrow^{\mathsf{box},L}}
%% \newcommand{\downboxright}{\downarrow^{\mathsf{box},R}}
%% \newcommand{\downlayerleft}{\downarrow^{\mathsf{layer},L}}
%% \newcommand{\downlayerright}{\downarrow^{\mathsf{layer},R}}
%% \newcommand{\downcubeleft}{\downarrow^{\mathsf{cube},L}}
%% \newcommand{\downcuberight}{\downarrow^{\mathsf{cube},R}}
\newcommand{\heterodownbox}[2]{\mathsf{subbox}_{#1,#2}}
\newcommand{\heterodownlayer}[2]{\mathsf{sublayer}_{#1,#2}}
\newcommand{\heterodowncube}[2]{\mathsf{subcube}_{#1,#2}}
\newcommand{\heterodepdownbox}[1]{\mathsf{d\mbox{-}subbox}_{#1}}
\newcommand{\heterodepdownlayer}[1]{\mathsf{d\mbox{-}sublayer}_{#1}}
\newcommand{\heterodepdowncube}[1]{\mathsf{d\mbox{-}subcube}_{#1}}
\newcommand{\heterodepdownboxtype}[1]{\mathsf{d\mbox{-}Subbox}_{#1}}
\newcommand{\heterodepdownlayertype}[1]{\mathsf{d\mbox{-}Sublayer}_{#1}}
\newcommand{\heterodepdowncubetype}[1]{\mathsf{d\mbox{-}Subcube}_{#1}}
\newcommand{\downboxtype}[2]{\mathsf{Subbox}_{#1,#2}}
\newcommand{\downlayertype}[2]{\mathsf{Sublayer}_{#1,#2}}
\newcommand{\downcubetype}[2]{\mathsf{Subcube}_{#1,#2}}
\newcommand{\cohbox}[2]{\mathsf{r\mbox{-}cohbox}_{#1,#2}}
\newcommand{\cohlayer}[2]{\mathsf{r\mbox{-}cohlayer}_{#1,#2}}
\newcommand{\cohcube}[2]{\mathsf{r\mbox{-}cohcube}_{#1,#2}}
\newcommand{\cohreflbox}[1]{\mathsf{r\mbox{-}cohreflbox}_{#1}}
\newcommand{\cohrefllayer}[1]{\mathsf{r\mbox{-}cohrefllayer}_{#1}}
\newcommand{\cohreflcube}[1]{\mathsf{r\mbox{-}cohreflcube}_{#1}}
\newcommand{\cohrefleqbox}[1]{\mathsf{cohrefleqbox}_{#1}}
\newcommand{\cohrefleqlayer}[1]{\mathsf{cohrefleqlayer}_{#1}}
\newcommand{\cohrefleqcube}[1]{\mathsf{cohrefleqcube}_{#1}}
\newcommand{\cohboxtype}[2]{\mathsf{Cohbox}_{#1,#2}}
\newcommand{\cohlayertype}[2]{\mathsf{Cohlayer}_{#1,#2}}
\newcommand{\cohcubetype}[2]{\mathsf{Cohcube}_{#1,#2}}
\newcommand{\heterocohbox}[2]{\mathsf{cohbox}_{#1,#2}}
\newcommand{\heterocohlayer}[2]{\mathsf{cohlayer}_{#1,#2}}
\newcommand{\heterocohcube}[2]{\mathsf{cohcube}_{#1,#2}}
\newcommand{\myappdepbox}[1]{\mathsf{appbox}_{#1}}
\newcommand{\myappdeplayer}[1]{\mathsf{applayer}_{#1}}
\newcommand{\myappdepcube}[1]{\mathsf{appcube}_{#1}}
\newcommand{\myappdepboxtype}[1]{\mathsf{Appbox}_{#1}}
\newcommand{\myappdeplayertype}[1]{\mathsf{Applayer}_{#1}}
\newcommand{\myappdepcubetype}[1]{\mathsf{Appcube}_{#1}}
\newcommand{\unitpoint}{\star}
\newcommand{\unittype}{\mathsf{unit}}
\newcommand{\eqett}{\equiv_{\mathit{ETT}}}
\newcommand{\reflett}{\mathsf{refl}_{\mathit{ETT}}}
\newcommand{\mygpd}{\mathsf{gpd}}
\newcommand{\mycubset}{\mathsf{cubset}}
\newcommand{\partialcubset}[1]{\mathsf{cubsetprefix}_{#1}}
\newcommand{\typecubset}{\mathsf{typecubset}}
\newcommand{\mysymcubset}{\mathsf{symcubset}}
\newcommand{\issymcubset}{\mathsf{issymcubset}}
\newcommand{\partialsymcubset}{\mathsf{symcubset}}
\newcommand{\mypermute}{\mathsf{permute}}
\newcommand{\partialhascomp}{\mathsf{partialhascomp}}
\newcommand{\hascomp}{\mathsf{hascomp}}
\newcommand{\tube}[1]{\mathsf{r\mbox{-}tube}_{#1}}
\newcommand{\propercube}[1]{\mathsf{r\mbox{-}propercube}_{#1}}
\newcommand{\border}[1]{\mathsf{r\mbox{-}border}_{#1}}
\newcommand{\myheteroborder}[1]{\mathsf{border}_{#1}}
\newcommand{\reflexive}{\mathsf{refl}}
\newcommand{\permutation}{\mathsf{permutation}}
\newcommand{\diagonal}{\mathsf{diagonal}}
\newcommand{\connection}{\mathsf{connection}}
\newcommand{\diagprop}{\mathsf{diag}}
\newcommand{\reglr}{\rightarrow-\mathsf{reg}}
\newcommand{\regrl}{\leftarrow-\mathsf{reg}}
\newcommand{\coercivelr}{\rightarrow-\mathsf{def}}
\newcommand{\coerciverl}{\leftarrow-\mathsf{def}}
\newcommand{\regularitylr}{\rightarrow-\mathsf{regularity}}
\newcommand{\regularityrl}{\leftarrow-\mathsf{regularity}}
\newcommand{\Reglr}{\Rightarrow-\mathsf{reg}}
\newcommand{\Regrl}{\Leftarrow-\mathsf{reg}}
\newcommand{\Coercivelr}{\Rightarrow-\mathsf{def}}
\newcommand{\Coerciverl}{\Leftarrow-\mathsf{def}}
\newcommand{\Regularitylr}{\Rightarrow-\mathsf{regularity}}
\newcommand{\Regularityrl}{\Leftarrow-\mathsf{regularity}}
\newcommand{\coebacklr}{\overrightarrow{\mathsf{coe}}}
\newcommand{\coebackrl}{\overleftarrow{\mathsf{coe}}}
\newcommand{\backcoercivelr}{\overrightarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\backcoerciverl}{\overleftarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\regbacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regbackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regularitybacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\regularitybackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Coebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coercivebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Coercivebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Regbacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regbackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regularitybacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Regularitybackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}

\newcommand{\reflbox}{\mathsf{reflbox}}
\newcommand{\refllayer}{\mathsf{refllayer}}
\newcommand{\reflcube}{\mathsf{reflcube}}
\newcommand{\permutebox}{\mathsf{permutebox}}
\newcommand{\diagbox}{\mathsf{diagbox}}
\newcommand{\connbox}{\mathsf{connbox}}
%% \newcommand{\cohbox}{\mathsf{coh}^{\mathsf{box}}}
%% \newcommand{\cohlayer}{\mathsf{coh}^{\mathsf{layer}}}
\newcommand{\hd}{\mathsf{hd}}
\newcommand{\tl}{\mathsf{tl}}
\newcommand{\first}{\mathsf{first}}
\newcommand{\groupoid}{\mathsf{groupoid}}
\newcommand{\groupoidn}{\mathsf{groupoidn}}
\newcommand{\letinsplit}[3]{\!\!\begin{array}{l}\mathbf{let}~{#1}=#2\;\mathbf{in}~\\#3\end{array}}

\tableofcontents

\section{Introduction}

This note aims at interpreting the cubical type theory described in
Moeneclaey's master thesis (called the ``source'') through a delimited iterated
``univalent'' parametricity translation into Extensional Type Theory
(called the ``target'').

We call our parametricity translation univalent in that it interprets
type not only as relations (as in usual parametricity) but as
relations equipped with a transport structure in such a way that types
are related under parametricity when they are equivalent. We call our
parametricity iterated in that it iterates the usual parametricity
translation $n$ times for a sequent of dimension with $n$ declarations
of an axis. We call it delimited in that the declaration of a
dimension in the source delimits a new iteration of the translation.

This translation can be seen as a delimited variant in unbounded
dimensions of previous (non-delimited) syntactic translations by:
\begin{itemize}
\item Gandy~\cite{Gandy56} and Takeuti~\cite{Takeuti57}: setoid
  translation, capturing function extensionality and propositional
  extensionality\footnote{The corresponding translation applies to Church's
  simple type theory, which, as a type system, can be seen as System
  $F_{\omega}$ with an impredicative ``universe'' $\mathsf{Prop}$ and
  a ``universe'' $\mathsf{Type}$ of simple types based on
  $\mathsf{Prop}$. Equality in $\mathsf{Prop}$ is over elements typed
  in types of $\mathsf{Type}$. The proof level is not dependent, so
  there is no equality of proofs to consider. The translation thus
  applies only to the simply-typed $\lambda$-calculus built from the
  arrow type and the impredicative sort $\mathsf{Prop}$. (actually, as
  a consequence of satisfying propositional extensional types in
  $\mathsf{Prop}$ are provably-irrelevant. Technically, the
  translation only requires to show that the existence of maps back
  and forth a proposition extends from propositional atoms to
  implication and universal quantification over types of the
  $\mathsf{Type}$ level.}
\item Section 5 of Barras, Coquand and
  Huber~\cite{BarrasCoquandHuber15} modifies the setoid translation so
  that it supports dependent types and a proof-relevant
  (non-impredicative) universe up to isomorphism (i.e. equality
  between types is the existence of an isomorphism). The translation
  is formulated as a translation to semi-simplicial sets truncated half
  way between dimension~1 and~2.
  The
  translation is to intentional type theory (ITT) and it does not
  validate the reduction rules for $J$ nor validate substitution under a
  $\lambda$-abstraction.

  In comparison, our translation uses cubes rather than simplices (see
  Shulman and Riehl~\cite{} for an interpretation of simplices on top
  of cubes using declaration of variables in the interval of the form
  $j \leq i$ where $i$ is the name of the previous variable declared,
  and 1 if $j$ is the first variable declared) but mutatis mutandis,
  both use Kan composition rather than ordinary composition and
  inverses. The main differences are that: 1) our translation is
  incremental and iterated, locally extending the dimension when a new
  interval variable is declared 2) our composition is required to be
  regular (in the sense of~\cite[Section 10]{CohCoqHubMor16}) so that
  the reduction rules for Martin-Löf's eliminator $J$ are validated.

  TODO: why Barras, Coquand and Huber's translation does not validate
  substitution under a $\lambda$-abstraction?

\item Sozeau and Tabareau~\cite{SozeauTabareau14}: this also extends
  Gandy and Takeuti translations but using a definition of 1-groupoid
  with composition and inverses rather than a semi-simplicial sets
  with a Kan composition.

\item Altenkirch, Boulier, Kaposi and
  Tabareau~\cite{AltenkirchBoulierKaposiTabareau19} gives a
  machine-checked setoid translation in ITT extended with a
  definitionally proof-irrelevant universe of proposition. The
  translation derives from previous work of the first author in the
  context of Observational Type Theory~\cite{}. This is similar to
  Gandy et Takeuti's translation but for a different source language
  (ITT rather than Church's simple theory of types). In particular, it
  supports dependent product.
\end{itemize}

Our translation can alternatively be seen as a (delimited, arbitrarily
highly $n$-truncated) syntactic formulation of (undelimited,
untruncated) presheaves semantics in set theory (or in any other
metalanguage featuring a notion of sets, e.g. type theory with
h-sets):
\begin{itemize}
\item Sections 7 and 8 of Barras, Coquand and
  Huber~\cite{BarrasCoquandHuber15} presents an interpretation of ITT
  with univalence within Kan semi-simplicial set in all dimensions.
\item Cohen, Coquand, Huber and M\"ortberg~\cite{CohCoqHubMor16}
  presents an interpretation of a variant of ITT with cubical equality
  within Kan cubical sets in all dimensions. The source language being
  interpreted differs in the following:
  \begin{itemize}
  \item Composition in our approach is only for ``tubes'' while it
    supports arbitrary systems of faces in \cite{CohCoqHubMor16}.
  \item Univalence, which connects equivalence of types and equality
    of types is obtained via a ``Glue'' operator while it is by
    definition in our case.
  \end{itemize}
 Regarding the interpretation, besides the fact that
 \cite{CohCoqHubMor16} gives an interpretation within the metalanguage
 while our interpretation is in another object language, we see the
 following differences:
 \begin{itemize}
 \item We interpret a judgement with $n$ axis variables in the typing
   context by a cubical set truncated to dimension $n$ while
   \cite{CohCoqHubMor16} interprets all judgements by a non-truncated
   cubical set independently of the number of axis variables in the
   context.
 \item The authors of \cite{CohCoqHubMor16} reason at a level of
   abstraction which circumscribes the combinatoric and equational
   structure of cubical sets in the definition of the site category of
   the presheaf. In our case, the equational structure of cubical sets
   is enforced using type dependencies rather than equations. As a
   consequence, the combinatorics of cubical sets become intertwined
   with the definition of cubical sets.

   For instance, as a comparison, a cube in a semi-cubical
   set\footnote{meaning here a cubical set with only face maps}
   presented as a presheaf is an object $a$ together with, for each
   iteration of faces $\tau$ considered modulo the equational theory
   on faces, another object $a_{\tau}$ which itself comes equipped for
   each face map $\tau'$ of a subobject $(a_{\tau})_{\tau'}$ such that
   $(a_{\tau})_{\tau'} = a_{(\tau\tau')}$ holds. In our definition of
   cubical sets, the later equality holds by construction using type
   dependencies. Otherwise said, while the presheaf construction
   represents a cube $a$ by a flat collection of all objects of the
   form $(...(a_{\tau_1})...)_{\tau_n}$ together with all equations
   asserting all necessary equations between these objects, our
   construction adds objects incrementally using instead type
   dependencies to enforce that the necessary equations hold.

   Also, while \cite{CohCoqHubMor16} treats faces, degeneracies,
   symmetries, diagonals, reversal and connections at the level of the
   site of the presheaf, we start from a semi-cubical basis (i.e. with
   only faces) and introduce reflexivity/degeneracies, symmetries and
   diagonals as axtra structure (we do not have reversal - TODO:
   connections?).

   We believe that, in any case, the combinatorics of cubical sets
   cannot be avoided and the level of details we present is anyway
   necessary for a full syntactic translation. Alternative syntactic
   translations closer to the structure of presheaves (i.e. building
   objects coming together with their collection of cubical maps and
   their associated equations) are certainly possible and they would
   eventually require to also characterize the combinatorical and
   equational structure of cubical sets. Whatever way the
   information is structured, there are irreductible bits of
   information to consider.
 \end{itemize}
\end{itemize}

It relies on an adaptation of the dependent construction of
semi-simplicial sets in type theory~\cite{Herbelin14} to a semi-strict
(regular) cubical form of $\omega$-groupoids.

\section{Delimited iterated parametricity translation}

One step of parametricity can be seen as interpreting a point by a
line. Iterating parametricity shall lead to map terms typed in a
context with $n$ declarations of an axis as $n$-cubes. We shall
interpret a
typing derivation with $n$ axis declarations as an $n$-cube of typing
derivations in the target. For instance, a typing derivation with
exactly one declaration of an axis will be interpreted by 3 typing
derivations in the target, two of them typing points and the third one
typing a proof, seen as a line, together with the fact that these two points are related (as
in ordinary parametricity), while a typing derivation with $n$
declarations of an axis shall be interpreted as a $3^n$ derivations,
split into $2^n$ derivations of points, 
$2^{n-1}\times\left(\begin{array}{c}1\\n\end{array}\right)$ derivations of lines
between those points, $2^{n-2}\times\left(\begin{array}{c}2\\n\end{array}\right)$
derivations of squares between those lines, etc. until having a single
(i.e. $2^{n-n}\times \left(\begin{array}{c}n\\n\end{array}\right)$)
$n$-cube connecting the whole. Note that the points are not typed in
the same context as the lines which connect them: a variable of some
type in the source context is interpreted as a variable of the same
type in the derivation of a point but as a variable of line over
points in this type for the derivation of the line. This difference of
typing context in each component of the so-obtained $n$-cube 
gives to parametricity a semantic flavor. In the presence of transport, we
suspect that a more purely syntactic form of parametricity where all components of
the $n$-cube are typed in the same context is possible. Then, an
$n$-cube of derivations in the same context is isomorphic to the
single derivation of the tupling of all components of the $n$-cubes as
an inhabitant of a $\Sigma$-type iterated $n$ times.

Each operation of the source language relative to a connective shall
be interpreted as an operation applied in parallel on each derivation
of the $n$-cube of derivations. Abstraction over a variable of axis
shall be interpreted as turning an $n$-cube of derivation over some
type $A$ into an $(n-1)$-cube of derivations over lines over $A$.
Application of a variable of axis to a proof of an equality shall be
interpreted as taking a diagonal of the square defined by this axis
and by the line which this equality denotes.

Abstraction over an ordinary variable shall require some
care. Interpreting abstraction of an $n$-cube as an $n$-cube of
abstractions such that a face of dimension $p$ of the $n$-cube takes a
$p$-cube as arguments shall drop too much information for the
diagonals to be definable in dependent products. Thus, abstraction
shall instead be interpreted as the abstraction together with a
precomputation of the diagonals in all the axes of the $n$-cube. On
the other side, dependent pairing of $n$-cubes will compositionally be
defined as $n$-cubes of dependent pairs.

Types shall be interpreted as $n$-cubes of equivalent types. More
concretely, a $0$-cube shall be a type, a $1$-cube shall be two types
$A$ and $B$, both equipped with a proper homogeneous relation,
together with a form of Galois connection structure over the two
types made of an ``oblique'' heterogeneous relation over $A$ and $B$
and of coercions back and forth between $A$ and $B$ that agree on the
oblique relation. Additionally, this Galois connection is supposed to
be regular, meaning here that if the two types are identical, the
coercions are the identity. A $2$-cube shall be four types forming a
square, four proofs that nearby pairs are equivalences and a proof
that the four equivalences are consistent, i.e., in fine, that the square
commutes. The later itself shall consist of a relation over the four
types and four equivalences and 2-dimensional coherent coercions back
and forth between the four equivalences. Note in particular that such
a relation is defined over the border of a square, i.e. the $3^2 - 1$
objects made from the four types and four equivalences between those
types. In the general case, an $n$-cube of types will be characterized
by an $n$-dimensional heterogeneous relation over $n$-boxes, i.e. of
the border of an $n$-cube, i.e. an $n$-cube without a filler inside,
plus $n$-dimensional coercions back and forth.

Each $n$-cube of derivations (i.e. again, $3^n$ components) can thus
be decomposed into an $n$-dimensional filler (one component) of its
border which is an $n$-box made from the faces (and iterated faces) of
the $n$-cube.

A typing judgement $t:A$ shall be interpreted as follows: if one sees
each $p$-dimensional face $t'$ of the interpretation of $t$ as an
$n$-cube as the pair of a filler and of a $p$-box, then, $t'$ shall be
an inhabitant of the relation underlying the corresponding face of $A$
applied to the aforementioned $p$-box.

The interpretation of the universe shall be a delicate
part. Since a type $A$ has type $\sort{l}$ for some universe level $l$
in the source, the interpretation of $\sort{l}$ as an $n$-cube has to
characterize what it means for a type to be interpreted as an $n$-cube.

In the following, we are interpreting cubical type theory in ETT and
thus use a ``type-theoretic'' terminology, such as $t$ is a term of
type $A$. The reader used to set theory can in petto reformulate such
a statement as $t$ is a element of the set $A$.

\subsection{Structure of cubes}

The notion of {\em cube} goes together with the notions of {\em box} and of {\em tube}.
A $n$-cube {\em fills} an $n$-box and, conversely, the border of an $n$-cube
is an $n$-box. A $(n+1)$-box whose two opposite faces are missing is
called an $n$-tube. The data of an $n$-cube together with the $n$-box
that it inhabits shall be called a full $n$-cube. A
$0$-cube is called a {\em point}. A $1$-cube connects two points and is
called a {\em line} with the two points forming the bordering $1$-box of the
line. A $2$-cube is a filled {\em square}. The unfilled square is a $2$-box
which can be seen as a $1$-tube made of two parallel lines together
with two extra lines closing the tube.  A $3$-cube is a filled
3-dimensional cube. The unfilled cube is a $3$-box which can be seen
as a $2$-tube made of an unfilled square stretched in one direction so
that it looks like a squared hollow cylinder together with two extra squares
closing the tube.

Cubes, boxes and tubes are relative to a type of points and to a
{\em relational structure} in all dimensions telling when a cube inhabits
(or fills) a box. There are {\em homogeneous} and {\em heterogeneous} cubes and
boxes. By a homogeneous cube or box, we mean a (full) cube or box in
which all points are in the same type and all relations in all
dimensions are homogeneous. In an heterogeneous cube or box, each
point might be in a different type and the higher-dimensional
relational structure over these types is itself
heterogeneous. However, in the latter case, even though the types and
higher-dimensional relations is heterogeneous, they can in turn be
themselves organized as a full cube or box, which, this time, is
homogeneous (i.e. a higher-dimensional relational structure can be
seen as a cube over another higher-dimensional relational structure in
a upper level, the same way as a type is itself a term in some
universe, and this universe itself a term in some upper universe, and
so on).

In the syntax of cubical type theory, the cubical structure can be
seen in two forms. A judgement in a context with $n$ axis variables
denotes an $n$-cube and this is the ``metalevel'' use of $n$-cubes. In
particular, in a judgement $\Gamma \vdash t:A$ with $n$ axis variables
declared in $\Gamma$, the type $A$ denotes an $n$-cube of relations up to dimension
$n$ (with types as points) and $t$ is a full heterogeneous $n$-cube
over the homogeneous $n$-cube of relations denoted by~$A$.

In the syntax of cubical type theory, there is also an internalizing
of the metalevel language in the object language by means of the
equality symbol. The equality over some type denotes a relation and,
when iterated, it denotes a higher-dimensional relation. Such equality
in dimension $n$ expects an $n$-box as argument, and, altogether, they
express the type of fillers of the $n$-box. For instance, in a
judgement of the form $\Gamma \vdash \alpha:p =_{\lambda i.(r i =_A s
  i)} q$ can be seen as a (non full) $2$-cube $\alpha$ inhabiting the
$2$-box built from $p$, $q$, $r$ and~$s$. More generally, if the
context $\Gamma$ itself declares $m$ variables of axis, a judgement
about an equality nested $n$ times denotes a full heterogeneous $m$-cube whose
points are themselves (non full) heterogeneous $n$-cubes.

As for an $n$-tube, it can be seen as the chain of the $2n$ $n$-cubes
forming the tube.

\iffalse
Types of the source language are eventually interpreted as
$\omega$-groupoids. We use a non-standard cubical definition of
(semi-strict) $\omega$-groupoid suitable for our needs. Relating it to
other definitions of $\omega$-groupoid is an open question.

An $\omega$-groupoid is given by a cubical type structure and a
transport structure. The cubical type structure is given by a type $A$
and a collection of higher-dimensional equalities over this type. The
inhabitants of $A$ are written $t$, $u$, $v$, $w$, ... and called
points or $0$-cubes. The equality over points, written $t =_A u$, have
lines written $p$, $q$, $r$, $s$, ... and also called $1$-cubes as
inhabitants. The equality over lines, written $p =_{r \hat{=}_A s} q$
or $[p,r] =^2_A [q,s]$, have squares, written $\alpha$, $\beta$,
$\gamma$, ... and also called $2$-cubes as inhabitants.  The equality
over squares $\alpha =_{\gamma \hat{=}_{\eta \widehat{\hat{=}}_A
    \theta} \delta} \beta$, also shortened $[\alpha,\gamma,\eta] =^3_A
[\beta,\delta,\theta]$ have proper cubes, also called $3$-cubes as
inhabitants, etc.

The transport structure is obtained by saying that any $n$-tube gives
rise to an equivalence of the $n$-boxes characterizing the missing
opposite faces of the $n$-tube, i.e. that any $n$-tube gives rise to a
mean to ``transport'' a face filling one of the hole of the $n$-tube
into a face filling the opposite hole of the $n$-tube, together with a
filler of this ``open box'' completion.
\fi

The characterization of homogeneous $n$-boxes and full $n$-cubes can
be obtained by a recursive definition reminiscent from parametricity:
a full $(n+1)$-cube is obtained by taking two full $n$-cubes plus a
third full $n$-cube connecting the two full $n$-cubes. Since it
connects full $n$-cubes, the third full $n$-cube is actually a full
$n$-cube over lines, so it is shifted by one relatively to the
underlying relational structure. Let us write $\mycube{}^{n,p}$ for a
full $(n-p)$-cube over points which are full $p$-cubes. Working
informally, we thus have the equation:
$$
\mycube{}^{n+1,0} \defeq (\mycube{}^{n,0} \times \mycube{}^{n,0}) \times \mycube{}^{n+1,1}
$$
and, iterating and generalizing the process, we have actually:
$$
\mycube{}^{n+1,p} \defeq (\mycube{}^{n,p} \times \mycube{}^{n,p}) \times \mycube{}^{n+1,p+1}
$$ 
Now, the third cube (of dimension $((n+1)-(p+1))$, i.e. $n-p$) connects the first two
$(n-p)$-cubes, so it has to depend on them. So, the equation is rather
something of the form:
$$
\mycube{}^{n+1,p} \defeq \Sigma a:(\mycube{}^{n,p} \times \mycube{}^{n,p}).\, \mycube{}^{n+1,p+1}(a)
$$
Then, by iterating, we obtain:
$$ 
\mycube{}^{n+1,p} \defeq \Sigma a:(\mycube{}^{n,p} \times \mycube{}^{n,p}).\,
 \Sigma b:(\mycube{}^{n,p+1}(a) \times \mycube{}^{n,p+1}(a)). \, \mycube{}^{n+1,p+2}(a,b)
$$
and so on. Thus, we need first to make the definition of
$\mycube{}^{n,p}$ dependent over the part of the full cube built up to
this point and secondly to accumulate this information. At the end of
the accumulation of the process, i.e. at the time of building
$\mycube{}^{n+1,n}$, a complete $n$-box will have been built. So, let us
call $\mybox{}^{n,p}$ the partial $n$-box built up to the stage $p$
of the construction. Thus, we refine our definition into something like:
$$
\begin{array}{lll}
\mybox{}^{n,0} &\defeq& \unittype\\
\mybox{}^{n,p+1} &\defeq& \Sigma d:\mybox{}^{n,p}.\,(\mycube{}^{n,p}(d) \times \mycube{}^{n,p}(d))\\
\\
\mycube{}^{n+1,p}(d:\mybox{}^{n,p}) &\defeq& \Sigma a:(\mycube{}^{n,p}(d) \times \mycube{}^{n,p}(d)).\,\mycube{}^{n+1,p+1}(d,a)
\end{array}
$$
where $\unittype$ is a canonical singleton type used to initiate the
construction of a list of pairs of $n$-cubes.

Now, the two cubes $\mycube{}^{n,p}(d)$ and $\mycube{}^{n,p}(d)$ cannot be
any cubes. They have to represent two opposite cubes and we need a way
to express this. The answer is simple. The partial box has two faces
and these two cubes have to respectively fill the left face and the
right face of the partial box. We thus have to rely on operations
$\downbox{l}{L}$ and $\downbox{l}{R}$ which extract the sides of a box,
leading to the refined definition:
$$
\begin{array}{lll}
\mycube{}^{n+1,p}(d:\mybox{}^{n,p}) &\defeq& \Sigma a:(\mycube{}^{n,p}(\downbox{l}{L}(d)) \times \mycube{}^{n,p}(\downbox{l}{R}(d))).\,\mycube{}^{n+1,p+1}(d,a)
\end{array}
$$

The full explicit definition shall be given in the next sections but,
to give an idea, let us show the structure of an $n$-cube for the
first three dimensions.

A full $0$-cube is made of just one point:
$$
\begin{array}{lll}
\mbox{\textit{points}}\\
\end{array}
\begin{array}{lll}
  \framebox{$a$}\\
\end{array}
$$

A full $1$-cube is made of two points connected by a line:
$$
\begin{array}{lll}
\mbox{\textit{lines}}\\
[1mm]\mbox{\textit{points}}\\
\end{array}
\begin{array}{lll}
\framebox{$
\begin{array}{ll}
  & \framebox{$a_{\star}$}\\
\framebox{$a_0$}~\framebox{$a_1$}\\
\end{array}
$}
\end{array}
$$

A full $2$-cube is made of two full $1$-cubes connected by a lifted
$1$-cube made of two lines connecting the former points and a square
connecting the former lines:
$$
\begin{array}{lll}
\mbox{\textit{squares}}\\
[1mm]\mbox{\textit{lines}}\\
[1mm]\mbox{\textit{points}}\\
[1mm]\end{array}
\framebox{$\begin{array}{lll}
\framebox{$
\begin{array}{ll}
  & \framebox{$a_{0\star}$}\\
\framebox{$a_{00}$}~\framebox{$a_{01}$}\\
\end{array}
$}~
\framebox{$
\begin{array}{ll}
 & \framebox{$a_{1\star}$}\\
\framebox{$a_{10}$}~\framebox{$a_{11}$}\\
\end{array}
$}~
\raisebox{4.8mm}{$\framebox{$
\begin{array}{ll}
 & \framebox{$a_{\star\star}$}\\
\framebox{$a_{\star 0}$}~\framebox{$a_{\star 1}$}\\
\end{array}
$}$}
\end{array}$}
$$

In the next sections, we define homogeneous cubes, what allows to
define a structure of cubical set and, later, of cubical
$\omega$-groupoid. From that, we can define heterogeneous cubes over
$\omega$-groupoid at leaves. This heterogeneous cubes will be the
basis for interpreting judgements of cubical type theory.

%This is what leads to the definition on
%Figures~\ref{fig:barecubicalset}, \ref{fig:barecubicalsetstructure},
%\ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences}.

\subsection{Homogeneous cubes}

In this section, we formally define in
Figures~\ref{fig:barecubicalsetstructure},
\ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences}
the structure of the underlying higher-dimensional relations on which
cubes and boxes are built, together with the definition of homogeneous
$n$-boxes, homogeneous $n$-cubes, together with face operations on
boxes and cubes, together with commutation properties of the face
operations. All are mutually defined as types of the target language
ETT. Such relational structure, cubes and boxes are relative to a
universe, so let us fix $\sort{l}$ to be a given universe and
$\sort{l+1}$ to be its type. Let also $\unittype$ be the canonical
type with a single distinguished inhabitant $\unitpoint$. This type
lives in the first universe and, by cumulativity, also in all other
universes. We write $\hd(l)$ for the first component of a
$\Sigma$-type. We write $\times$ for the non-dependent case of a 
$\Sigma$-type and may sometimes also use the notation $p_0$ and $p_1$
for the two projections from a non-dependent $\Sigma$-types. We write
$\overrightarrow{p}$ for the rewriting operator along an equality
proof $p$ of the target language. Regarding equality in the
metalanguage, we will implicitly consider equality of a dependent pair
as equivalent to a dependent pair of component-wise equalities.

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\partialcubset{l}^n && : & \sort{l+1}\\
\partialcubset{l}^0 && \defeq & \unittype\\
\partialcubset{l}^{n'+1} && \defeq & \Sigma D:\partialcubset{l}^{n'}.\,(\mybox{l}^{n',n'}(D) \imp \sort{l})\\
\\
\mybox{l}^{n,p,[p \leq n]} & (D:\partialcubset{l}^n) & : & \sort{l}\\
\mybox{l}^{n,0} & D & \defeq & \unittype\\
\mybox{l}^{n,p'+1} & D & \defeq & \Sigma d:\mybox{l}^{n,p'}(D).\,\mylayer{l}^{n,p'}(D)(d)\\
\\
\mylayer{l}^{n,p,[p < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n})\\(d:\mybox{l}^{n,p}(D))\end{array}& : & \sort{l}\\
\mylayer{l}^{n,p} & D~d & \defeq & \!\!\begin{array}{l}\mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l}{L}^{n,p,p}(D)(d)) \\\times\; \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l}{R}^{n,p,p}(D)(d))\end{array}\\
\\
\mycube{l}^{n,p,[p \leq n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n})\\(E:\mybox{l}^{n,n}(D) \imp \sort{l})\\(d:\mybox{l}^{n,p}(D))\end{array} & : & \sort{l}\\
\mycube{l}^{n,p,[p = n]} & D~E~d & \defeq & E(d)\\
\mycube{l}^{n,p,[p < n]} & D~E~d & \defeq & \Sigma b:\mylayer{l}^{n,p}(D)(d).\,\mycube{l}^{n,p+1}(D)(E)(d,b)\\
\\
\end{array}
$
}}
\caption{Definition of a bare truncated cubical set (higher-dimensional relation structure and homogeneous cubes)}
\label{fig:barecubicalsetstructure}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{small}
\begin{array}{llcl}
\downbox{l}{\epsilon}^{n,q,p,[p \leq q < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n})\\(d:\mybox{l}^{n,p}(D))\end{array}& : & \mybox{l}^{n-1,p}(\hd(D))\\
\downbox{l}{\epsilon}^{n,q,0} & D~\unitpoint & \defeq & \unitpoint\\
\downbox{l}{\epsilon}^{n,q,p'+1} & D~(d,b) & \defeq & (\downbox{l}{\epsilon}^{n,q,p'}(D)(d),\downlayer{l}{\epsilon}^{n,q,p'}(D)(d)(b))\\
\\
\downlayer{l}{\epsilon}^{n,q,p,[p < q < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array}& : & \mylayer{l}^{n-1,p}(\hd(D))(\downbox{l}{\epsilon}^{n,q,p}(D)(d))\\
\downlayer{l}{\epsilon}^{n,q,p} & D~d~c & \defeq & \!\!\begin{array}{l}(\overrightarrow{\cohbox{l}{\epsilon,L}^{n,p,q,p}(D)(d)}(\downcube{l}{\epsilon}^{n-1,q-1,p}(\hd(D))(\tl(D))(\downbox{l}{L}^{n,p,p}(D)(d))(c_L)),\\\;\overrightarrow{\cohbox{l}{\epsilon,R}^{n,p,q,p}(D)(d)}(\downcube{l}{\epsilon}^{n-1,q-1,p}(\hd(D))(\tl(D))(\downbox{l}{bR}^{n,p,p}(D)(d))(c_R)))\end{array}\\
\\
\downcube{l}{\epsilon}^{n,q,p,[p \leq q < n]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n})\\(E:\mybox{l}^{n,n}(D) \imp \sort{l})\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array}& : & \mycube{l}^{n-1,p}(\hd(D))(\tl(D))(\downbox{l}{\epsilon}^{n,q,p}(D)(d))\\
\downcube{l}{\epsilon}^{n,q,p,[p=q]} & D~E~d~(b,\_) & \defeq & b_{\epsilon}\\
\downcube{l}{\epsilon}^{n,q,p,[p<q]} & D~E~d~(b,c) & \defeq & \letinsplit{b'}{\downlayer{l}{\epsilon}^{n,q,p}(D)(d)(b)}{(b',\downcube{l}{\epsilon}^{n,q,p+1}(D)(E)(d,b')(c))}\\
\\
\end{array}
\end{small}
$
}}
\caption{Definition of a homogeneous bare cubical set ($q$-th projection)}
\label{fig:barecubicalsetfaces}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{small}
\begin{array}{llcl}
\cohbox{l}{\epsilon,\epsilon'}^{\!\!\!\tiny\begin{array}{l}n,q,r,p\\\mbox{}[p \leq r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n})\\(d:\mybox{l}^{n,p}(D))\end{array}& : & \!\!\!\begin{array}{ll}\downbox{l}{\epsilon}^{n-1,q,p}(\hd(D))(\downbox{l}{\epsilon'}^{n,r,p}(D)(d)) \\ \eqett \downbox{l}{\epsilon'}^{n-1,r,p}(\hd(D))(\downbox{l}{\epsilon}^{n,q,p}(D)(d))\end{array}\\
\cohbox{l}{\epsilon,\epsilon'}^{n,q,r,0} & D~\unitpoint & \defeq & \reflett(\unitpoint)\\
\cohbox{l}{\epsilon,\epsilon'}^{n,q,r,p'+1} & D~(d,b) & \defeq & (\cohbox{l}{\epsilon,\epsilon'}^{n,q,r,p'}(D)(d),\cohlayer{l}{\epsilon,\epsilon'}^{n,q,r,p'}(D)(d)(b))\\
\\
\cohlayer{l}{\epsilon,\epsilon'}^{\!\!\!\tiny\begin{array}{l}n,q,r,p\\\mbox{}[p < r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array}& : & \!\!\!\begin{array}{ll}\downlayer{l}{\epsilon}^{n-1,q,p}(\hd(D))(\downbox{l}{\epsilon'}^{n,r,p}(D)(d))(\downlayer{l}{\epsilon'}^{n,r,p}(D)(d)(b)) \\ \eqett \downlayer{l}{\epsilon'}^{n-1,r,p}(\hd(D))(\downbox{l}{\epsilon}^{n,q,p}(D)(d))(\downlayer{l}{\epsilon}^{n,q,p}(D)(d)(b))\end{array}\\
\cohlayer{l}{\epsilon,\epsilon'}^{n,q,r,p} & D~d~c & \defeq & \!\!\begin{array}{l}(\cohcube{l}{\epsilon,\epsilon'}^{n-1,q-1,r-1,p}(\hd(D))(\tl(D))(\downbox{l}{L}^{n,p,p}(D)(d))(c_L),\\\;\cohcube{l}{\epsilon,\epsilon'}^{n-1,q-1,r-1,p}(\hd(D))(\tl(E))(\downbox{l}{R}^{n,p,p}(D)(d))(c_R))\end{array}\\
\\
\cohcube{l}{\epsilon,\epsilon'}^{\!\!\!\tiny\begin{array}{l}n,q,r,p\\\mbox{}[p \leq r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n})\\(E:\mybox{l}^{n,n}(D) \imp \sort{l})\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array}& : & \!\!\!\begin{array}{ll}\downcube{l}{\epsilon}^{n-1,q-1,p}(\hd(D))(\tl(D))(\downbox{l}{\epsilon'}^{n,r,p}(D)(d))(\downcube{l}{\epsilon'}^{n,r,p}(D)(E)(d)(b)) \\ \eqett \downcube{l}{\epsilon'}^{n-1,r-1,p}(\hd(D))(\tl(D))(\downbox{l}{\epsilon}^{n,q,p}(D)(d))(\downcube{l}{\epsilon}^{n,q,p}(D)(E)(d)(b))\end{array}\\
\cohcube{l}{\epsilon,\epsilon'}^{n,q,r,p,[p=r]} & D~E~d~(b,\_) & \defeq & \reflett(\downcube{l}{\epsilon}^{n-1,q-1,p}(\hd(D))(\tl(E))(\downbox{l}{\epsilon'}^{n,p,p}(D)(d))(b_{\epsilon}))\\
\cohcube{l}{\epsilon,\epsilon'}^{n,q,r,p,[p<r]} & D~E~d~(b,c) & \defeq & \!\!\begin{array}{l}(\cohlayer{l}{\epsilon,\epsilon'}^{n,q,r,p}(D)(d)(b),\\\;\cohcube{l}{\epsilon,\epsilon'}^{n,q,r,p+1}(D)(E)(d,\downlayer{l}{\epsilon}^{n,q,p}(D)(d)(b))(c))\end{array}\\
\end{array}
\end{small}
$
}}
\caption{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}
\label{fig:barecubicalsetcoherences}
\end{figure*}

Note the presence of a coherence condition $\cohbox{l}{}$ to
ensuring that both sides of the equality in $\downlayer{l}{}$ and $\downcube{l}{}$
are in the same type. The proof of $\cohbox{l}{}$ itself requires
an higher-dimensional coherence condition which we obtain by
working here in ETT where all proofs of an
equality are identified (principle of Unicity of Identity Proofs). Note that if the proofs of the same equality were not equated, there would be a need for arbitrary many 
higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a
discussion on the de facto need for recursive higher-dimensional
coherence conditions in formulating higher-dimensional structures in
type theory). Note also that for a given
$n$, the coherence conditions evaluate to a reflexivity proof, so that
the construction evaluates to an effective sequence of types of
iterated relations not mentioning $\downbox{l}{}$ nor $\cohbox{l}{}$ anymore.

We call the structure thus defined {\em bare truncated cubical sets}:
{\em bare} because it can be seen as defining a cubical equivalent to
semi-simplicial sets with only faces as part of the structure
(otherwise said, another terminology could have been ``semi-cubical''
sets); {\em truncated} because we consider only such cubical sets up
to some fixed dimension.

On top of the basic definitions on
Figures~\ref{fig:barecubicalsetstructure},
\ref{fig:barecubicalsetfaces} and \ref{fig:barecubicalsetcoherences},
we can define on Figure~\ref{fig:macros} and~\ref{fig:macroscont} a few other concepts at a
more standard level of abstraction. In particular, a homogeneous
$n$-box in the above sense is defined to be an object of type
$\mybox{l}^{n,n}(D_{n})$ for $D_{n} \defeq (A,=_A,...,=^n_A)$ the initial
segment of $n$-th first iterated equalities over $A$ (by convention, a
homogeneous $0$-box shall be the canonical singleton type). A $n$-tube
is of type $\mybox{l}^{n+1,n}(D_{n+1})$. An homogeneous (proper) $n$-cube
in some $n$-box $d$ is of type $\mycube{l}^{n+1,n}(\hd(D_{n+1}))(\tl(D_{n+1}))(d)$ and a
full $n$-cube is of type $\mycube{l}^{n+1,0}(\hd(D_{n+1}))(\tl(D_{n+1})))(\star)$.

Note that the components of an $n$-box or $n$-tube are tuples
associated to the left while the components of an $n$-cube are tuples
associated to the right. Figure~\ref{fig:macros} show how to compute
the $n$-box surrounding a full $n$-cube over a prefix $D_{n+1}$ of
iterated equalities (see $\border{}$).

Figure~\ref{fig:macros} also shows how to compute the faces of a box or of a cube.

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\multicolumn{4}{c}{\mbox{\it Type of full $n$-boxes}}\\
\\
\mybox{l}^{n} & (D:\partialcubset{l}^{n}) & : & \sort{l}\\
\mybox{l}^{n} & D & \defeq & \mybox{l}^{n,n}(D)\\
\\
\multicolumn{4}{c}{\mbox{\it Type of $n$-tubes}}\\
\\
\tube{l}^{n} & (D:\partialcubset{l}^{n+1}) & : & \sort{l}\\
\tube{l}^{n} & D & \defeq & \mybox{l}^{n+1,n}(D)\\
\\
\multicolumn{4}{c}{\mbox{\it Type of full $n$-cubes}}\\
\\
\mycube{l}^{n} & (D:\partialcubset{l}^{n+1}) & : & \sort{l}\\
\mycube{l}^{n} & (D,E) & \defeq & \mycube{l}^{n,0}(D)(E)(\star)\\
\\
\multicolumn{4}{c}{\mbox{\it Type of a proper $n$-cube over some $n$-box}}\\
\\
\propercube{l}^{n} & (D:\partialcubset{l}^{n+1})~(d:\mybox{l}^{n}(\hd(D))) & : & \sort{l}\\
\propercube{l}^{n} & (D,E)~d & \defeq & E(d)\\
\\
\multicolumn{4}{c}{\mbox{\it Border of a full $n$-cube}}\\
\\
\border{l}^{n} & (D:\partialcubset{l}^{n+1})~(c:\mycube{l}^{n}(D)) & : & \mybox{l}^{n}(\hd(D))\\
\border{l}^{n} & D~c & \defeq & \border{l}^{n,0}(D)(\star)(c)\\
\\
\multicolumn{4}{c}{\mbox{\it where the border of partial cubes is defined by}}\\
\\
\border{l}^{n,p} & (D:\partialcubset{l}^{n+1})~(d:\mybox{l}^{n,p}(\hd(D)))~(c:\mycube{l}^{n,p}(\hd(D))(\tl(E))(d)) & : & \mybox{l}^{n}(\hd(D))\\
\border{l}^{n,p,[p=n]} & D~d~c & \defeq & d\\
\border{l}^{n,p,[p<n]} & D~d~(b,c) & \defeq & \border{l}^{n,p+1}(D)(d,b)(c)\\
\end{array}
$
}}
\caption{Standard notions}
\label{fig:macros}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\multicolumn{4}{c}{\mbox{$q$-th projection of an $n$-box}}\\
\\
\downbox{l}{\epsilon}^{n,q,[q < n]} & (D:\partialcubset{l}^{n})~(d:\mybox{l}^{n}(D)) &:& \mybox{l}^{n-1}(\hd(D))\\
\downbox{l}{\epsilon}^{n,q} & D~(d,\_) &\defeq& \downbox{l}{\epsilon}^{n,q,n-1}(D)(d)\\
\\
\multicolumn{4}{c}{\mbox{$q$-th face of an $n$-cube}}\\
\\
\downcube{l}{\epsilon}^{n,q,[q < n]} & (D:\partialcubset{l}^{n+1})~(c:\mycube{l}^{n}(D)) &:& \mycube{l}^{n-1}(\hd(D))\\
\downcube{l}{\epsilon}^{n,q} & (D,E)~c &\defeq& \downcube{l}{\epsilon}^{n,q,0}(D)(E)(\star)(c)\\
\\
\multicolumn{4}{c}{\mbox{\it where the extension of $\downbox{l}{}$ to $p>q$ is}}\\
\\
\downbox{l}{\epsilon}^{n,q,p,[q < p < n]} & (D:\partialcubset{l}^{n})~(d:\mybox{l}^{n,p}(D))& : & \mybox{l}^{n-1}(\hd(D))\\
\downbox{l}{\epsilon}^{n,q,q+1} & D~(d,b) & \defeq & \border{l}^{n-1,q}(\hd(D))(\downbox{l}{\epsilon}^{n,q,q}(D)(d))(b_{\epsilon})\\
\downbox{l}{\epsilon}^{n,q,p,[q < p-1]} & D~(d,b) & \defeq & \downbox{l}{\epsilon}^{n,q,p-1}(D)(d)
\end{array}
$
}}
\caption{Standard notions (continued)}
\label{fig:macroscont}
\end{figure*}

\subsection{Types as cubical sets}

We shall interpret types as cubical sets, themselves obtained as the
coinductive limit of truncated cubical sets, see Figure~\ref{fig:barecubicalset}.

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\multicolumn{4}{c}{\mbox{Full (non-truncated) bare cubical sets}}\\
\\
\mycubset_l && \defeq & \mycubset_l^0(\star)\\
\\
\mycubset_l^n & (D:\partialcubset{l}^n) & : & \sort{l+1}\\
\mycubset_l^n & D & \defeq & \Sigma R:(\mybox{l}^{n,n}(D) \imp \sort{l}).\,\mycubset_l^{n+1}(D,R)
\end{array}
$
}}
\caption{Definition of a bare cubical set (coinductive structure)}
\label{fig:barecubicalset}
\end{figure*}

\subsection{Cubes of types}

\subsection{Heterogeneous $n$-cubes}

While homogeneous $n$-boxes and $n$-cubes are useful to interpret
types as cubical $\omega$-groupoids, we need to define heterogeneous
$n$-cubes over $n$-cubes of types to interpret both judgements and
iterated equalities.

The structure of heterogeneous cubes is similar to the one of
homogeneous cubes but with two levels, one level of heterogeneous
types and another heterogeneous level for fillers.
%% We make it parameterized over two functors:
%% $$
%% \begin{array}{llll}
%% \phi_n & (D:\myheterocubetype{l}^{n,n}) &:& \sort{l+1}\\
%% \psi_n & (D:\myheterocubetype{l}^{n,n})~(P:F(D))~(d:\myheterocube{l}^{n,n}(D)) & : &\sort{l}\\
%% \end{array}
%% $$
%% which, in the basic case of iterated parametricity, as in Bernardy, Coquand and
%% Moulin~\cite{BernardyCoquandMoulin15}, shall be instantiated by
%% $$
%% \begin{array}{llll}
%% \phi_n & D & \defeq & \myheterobox{l}^{n,n}(D) \imp \sort{l}\\
%% \psi_n & D~P~d & \defeq & P\,d\\
%% \end{array}
%% $$

The construction is a large mutual definition dispatched on
Figures~\ref{fig:heterobarecubicalsettype},
\ref{fig:heterobarecubicalset},
\ref{fig:heterobarecubicalsetfacestype},
\ref{fig:heterobarecubicalsetfaces},
\ref{fig:heterobarecubicalsetcoherencestype} and
\ref{fig:heterobarecubicalsetcoherences}.

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\myheteroboxtype{l}^{n,p,[p \leq n]} & & : & \sort{l+1}\\
\myheteroboxtype{l}^{n,0} & & \defeq & \unittype\\
\myheteroboxtype{l}^{n,p'+1} & & \defeq & \Sigma D:\myheteroboxtype{l}^{n,p'}.\,\myheterolayertype{l}^{n,p'}(D)\\
\\
\myheterolayertype{l}^{n,p,[p < n]} & (D:\myheteroboxtype{l}^{n,p}) & : & \sort{l+1}\\
\myheterolayertype{l}^{n,p} & D & \defeq & \!\!\begin{array}{l}\myheterocubetype{l}^{n-1,p}(\downboxtype{l}{L}^{n,p,p}(D)) \\\times\; \myheterocubetype{l}^{n-1,p}(\downboxtype{l}{R}^{n,p,p}(D))\end{array}\\
\\
\myheterocubetype{l}^{n,p,[p \leq n]} & (D:\myheteroboxtype{l}^{n,p}) & : & \sort{l+1}\\
\myheterocubetype{l}^{n,p,[p = n]} & D & \defeq & \myheterobox{l}^{n,n}(D) \imp \sort{l}\\
\myheterocubetype{l}^{n,p,[p < n]} & D & \defeq & \Sigma B:\myheterolayertype{l}^{n,p}(D).\,\myheterocubetype{l}^{n,p+1}(D,B)\\
\end{array}
$
}}
\caption{Definition of a heterogeneous cube (cube of higher-order relations)}
\label{fig:heterobarecubicalsettype}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\myheterobox{l}^{n,p,[p \leq n]} & (D:\myheteroboxtype{l}^{n,n}) & : & \sort{l}\\
\myheterobox{l}^{n,0} & D & \defeq & \unittype\\
\myheterobox{l}^{n,p'+1,[p' < n]} & D & \defeq & \Sigma d:\myheterobox{l}^{n,p'}(D).\,\myheterolayer{l}^{n,p'}(D)(d)\\
\\
\myheterolayer{l}^{n,p,[p < n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(d:\myheterobox{l}^{n,p}(D))\end{array}& : & \sort{l}\\
\myheterolayer{l}^{n,p} & D ~d & \defeq & \!\!\begin{array}{l}\myheterocube{l}^{n-1,p}(\downboxtype{l}{L}^{n,p,n-1}(\hd(D)))(\tl(D)_L)(\heterodownbox{l}{L}^{n,p,p}(D)(d)) \\\times\; \myheterocube{l}^{n-1,p}(\downboxtype{l}{R}^{n,p,n-1}(\hd(D)))(\tl(D)_R)(\heterodownbox{l}{R}^{n,p,p}(D)(d))\end{array}\\
\\
\myheterocube{l}^{n,p,[p \leq n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(E:\myheterocubetype{l}^{n,n}(D))\\(d:\myheterobox{l}^{n,p}(D))\end{array}& : & \sort{l}\\
\myheterocube{l}^{n,p,[p = n]} & D~E~d & \defeq & E(d)\\
\myheterocube{l}^{n,p,[p < n]} & D~E~d & \defeq & \Sigma b:\myheterolayer{l}^{n,p}(D)(d).\,\myheterocube{l}^{n,p+1}(D)(E)(d,b)\\
\\
\end{array}
$
}}
\caption{Definition of a heterogeneous cube (cube of terms)}
\label{fig:heterobarecubicalset}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{small}
\begin{array}{llcl}
\downboxtype{l}{\epsilon}^{n,q,p,[p \leq q < n]} & (D:\myheteroboxtype{l}^{n,p}) & : & \myheteroboxtype{l}^{n-1,p}\\
\downboxtype{l}{\epsilon}^{n,q,0} & \unitpoint & \defeq & \unitpoint\\
\downboxtype{l}{\epsilon}^{n,q,p'+1} & (D,B) & \defeq & (\downboxtype{l}{\epsilon}^{n,q,p'}(D),\downlayertype{l}{\epsilon}^{n,q,p'}(D)(B))\\
\\
\downlayertype{l}{\epsilon}^{n,q,p,[p < q < n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,p})\\(B:\myheterolayertype{l}^{n,p}(D))\end{array}& : & \myheterolayertype{l}^{n-1,p}(\downboxtype{l}{\epsilon}^{n,q,p}(D))\\
\downlayertype{l}{\epsilon}^{n,q,p} & D~(C_0,C_1) & \defeq & \!\!\begin{array}{l}(\overrightarrow{\cohboxtype{l}{\epsilon,L}^{n,q,p,p}(D)}(\downcubetype{l}{\epsilon}^{n-1,q-1,p}(\downboxtype{l}{L}^{n,p,p}(D))(C_0)),\\\;\overrightarrow{\cohboxtype{l}{\epsilon,R}^{n,q,p,p}(D)}(\downcubetype{l}{\epsilon}^{n-1,q-1,p}(\downboxtype{l}{R}^{n,p,p}(D))(C_1)))\end{array}\\
\\
\downcubetype{l}{\epsilon}^{n,p,q,[p \leq q < n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,p})\\(C:\myheterocubetype{l}^{n,p}(D))\end{array}& : & \myheterocubetype{l}^{n-1,p}(\downboxtype{l}{\epsilon}^{n,q,p}(D))\\
\downcubetype{l}{\epsilon}^{n,q,p,[p=q]} & D~(B,\_) & \defeq & B_{\epsilon}\\
\downcubetype{l}{\epsilon}^{n,q,p,[p<q]} & D~(B,C) & \defeq & \letinsplit{B'}{\downlayertype{l}{\epsilon}^{n,q,p}(D)(B)}{(B',\downcubetype{l}{\epsilon}^{n,q,p+1}(D,B')(C))}\\
\\
\multicolumn{4}{c}{\mbox{TODO: add $\downboxtype{}{}$ for $p>q$}}
\end{array}
\end{small}
$
}}
\caption{Definition of a heterogeneous cube (faces of higher-order relations)}
\label{fig:heterobarecubicalsetfacestype}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{small}
\begin{array}{llcl}
\heterodownbox{l}{\epsilon}^{n,q,p,[p \leq q < n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(d:\myheterobox{l}^{n,p}(D))\end{array}& : & \myheterobox{l}^{n-1,p}(\downboxtype{l}{\epsilon}^{n,q,n-1}(\hd(D)))\\
\heterodownbox{l}{\epsilon}^{n,q,0} & D~\unitpoint & \defeq & \unitpoint\\
\heterodownbox{l}{\epsilon}^{n,q,p'+1} & D~(d,b) & \defeq & (\heterodownbox{l}{\epsilon}^{n,q,p'}(D)(d),\heterodownlayer{l}{\epsilon}^{n,q,p'}(D)(d)(b))\\
\\
\heterodownlayer{l}{\epsilon}^{n,q,p,[p < q < n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(d:\myheterobox{l}^{n,p}(D))\\(b:\myheterolayer{l}^{n,p}(D)(d))\end{array}& : & \myheterolayer{l}^{n-1,p}(\downboxtype{l}{\epsilon}^{n,q,n-1}(\hd(D)))(\heterodownbox{l}{\epsilon}^{n,q,p}(D)(d))\\
\heterodownlayer{l}{\epsilon}^{n,q,p} & D~d~c & \defeq & \!\!\begin{array}{l}(\!\!\!\begin{array}{l}(\overrightarrow{\cohboxtype{l}{\epsilon,L}^{n,q,p,p}(D)(d)},\\\overrightarrow{\heterocohbox{l}{\epsilon,L}^{n,q,p,p}(D)(d)})\end{array}(\heterodowncube{l}{\epsilon}^{n-1,q-1,p}\left(\!\!\!\begin{array}{l}\downboxtype{l}{L}^{n,p,n-1}(D)\\\tl(D)_L\\\heterodownbox{l}{L}^{n,p,p}(D)(d)\\c_L\end{array}\right)),\\\;\!\!\!\begin{array}{l}(\overrightarrow{\cohboxtype{l}{\epsilon,R}^{n,q,p,p}(D)(d)},\\\overrightarrow{\heterocohbox{l}{\epsilon,R}^{n,q,p,p}(D)(d)})\end{array}(\heterodowncube{l}{\epsilon}^{n-1,q-1,p}\left(\!\!\!\begin{array}{l}\downboxtype{l}{R}^{n,p,n-1}(D)\\\tl(D)_R\\\heterodownbox{l}{R}^{n,p,p}(D)(d)\\c_R\end{array}\right)))\end{array}\\
\\
\heterodowncube{l}{\epsilon}^{n,q,p,[p \leq q < n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(E:\myheterocubetype{l}^{n,n}(D))\\(d:\myheterobox{l}^{n,p}(D))\\(c:\myheterocube{l}^{n,p}(D)(E)(d))\end{array}& : & \myheterocube{l}^{n-1,p}(\downboxtype{l}{\epsilon}^{n,q,n-1}(D))(\tl(D)_{\epsilon})(\heterodownbox{l}{\epsilon}^{n,q,p}(D)(d))\\
\heterodowncube{l}{\epsilon}^{n,q,p,[p=q]} & D~E~d~(b,\_) & \defeq & b_{\epsilon}\\
\heterodowncube{l}{\epsilon}^{n,q,p,[p<q]} & D~E~d~(b,c) & \defeq & \letinsplit{b'}{\heterodownlayer{l}{\epsilon}^{n,q,p}(D)(d)(b)}{(b',\heterodowncube{l}{\epsilon}^{n,q,p+1}(D)(E)(d,b')(c))}\\
%\\
%\multicolumn{4}{c}{\mbox{TODO: add $\heterodownbox{}{}$ for $n>q$}}
\end{array}
\end{small}
$
}}
\caption{Definition of a heterogeneous cube (faces of terms)}
\label{fig:heterobarecubicalsetfaces}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{small}
\begin{array}{llcl}
\cohboxtype{l}{\epsilon,\epsilon'}^{\!\!\!\tiny\begin{array}{l}n,q,p,r\\\mbox{}[p \leq r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,p})\end{array}& : & \!\!\!\begin{array}{ll}\downboxtype{l}{\epsilon}^{n-1,q,p}(\downboxtype{l}{\epsilon'}^{n,r,p}(D)) \\ \eqett \downboxtype{l}{\epsilon'}^{n-1,r,p}(\downboxtype{l}{\epsilon}^{n,q,p}(D))\end{array}\\
\cohboxtype{l}{\epsilon,\epsilon'}^{n,q,r,0} & D~\unitpoint & \defeq & \reflett(\unitpoint)\\
\cohboxtype{l}{\epsilon,\epsilon'}^{n,q,r,p'+1} & D~(d,b) & \defeq & (\cohboxtype{l}{\epsilon,\epsilon'}^{n,q,p,r,p'}(D)(d),\cohlayertype{l}{\epsilon,\epsilon'}^{n,q,r,p'}(D)(d)(b))\\
\\
\cohlayertype{l}{\epsilon,\epsilon'}^{\!\!\!\tiny\begin{array}{l}n,q,r,p\\\mbox{}[p < r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,p})\\(B:\myheterolayertype{l}^{n,p}(D)\end{array}& : & \!\!\!\begin{array}{ll}\downlayertype{l}{\epsilon}^{n-1,q-1,p}(\downboxtype{l}{\epsilon'}^{n,r,p}(D))(\downlayertype{l}{\epsilon'}^{n,r,p}(D)(B)) \\ \eqett \downlayertype{l}{\epsilon'}^{n-1,r-1,p}(\downboxtype{l}{\epsilon}^{n,q,p}(D))(\downlayertype{l}{\epsilon}^{n,q,p}(D)(B))\end{array}\\
\cohlayertype{l}{\epsilon,\epsilon'}^{n,q,r,p} & D~C & \defeq & \!\!\begin{array}{l}(\cohcubetype{l}{\epsilon,\epsilon'}^{n-1,q-1,r-1,p}(\downboxtype{l}{L}^{n,p,p}(D))(C_L),\\\;\cohcubetype{l}{\epsilon,\epsilon'}^{n-1,q-1,r-1,p}(\downboxtype{l}{R}^{n,p,p}(D))(C_R))\end{array}\\
\\
\cohcubetype{l}{\epsilon,\epsilon'}^{\!\!\!\tiny\begin{array}{l}n,q,r,p\\\mbox{}[p \leq r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,p})\\(C:\myheterocubetype{l}^{n,p}(D))\end{array}& : & \!\!\!\begin{array}{ll}\downcubetype{l}{\epsilon}^{n-1,q-1,p}(\downboxtype{l}{\epsilon'}^{n,q,p}(D))(\downcubetype{l}{\epsilon'}^{n,r,p}(D)(C)) \\ \eqett \downcubetype{l}{\epsilon'}^{n-1,r-1,p}(\downboxtype{l}{\epsilon}^{n,q,p}(D))(\downcubetype{l}{\epsilon}^{n,q,p}(D)(C))\end{array}\\
\cohcubetype{l}{\epsilon,\epsilon'}^{n,q,r,p,[p=r]} & D~(B,\_) & \defeq & \reflett(\downcubetype{l}{\epsilon}^{n-1,q-1,p}(\downboxtype{l}{\epsilon'}^{n,q,p}(D))(B_{\epsilon}))\\
\cohcubetype{l}{\epsilon,\epsilon'}^{n,q,r,p,[p<r)} & D~(B,C) & \defeq & \!\!\begin{array}{l}(\cohlayertype{l}{\epsilon,\epsilon'}^{n,q,r,p}(D)(B),\\\;\cohcubetype{l}{\epsilon,\epsilon'}^{n,q,r,p+1}(D,\downlayertype{l}{\epsilon}^{n,q,p}(D)(B))(C))\end{array}\\
\\
\multicolumn{4}{c}{\mbox{TODO: add ${\cohboxtype{}{}}$ for $p>q$}}
\end{array}
\end{small}
$
}}
\caption{Definition of a heterogeneous cube (compatibility of faces of higher-order relations)}
\label{fig:heterobarecubicalsetcoherencestype}
\end{figure*}

\begin{figure*}
\centerline{\framebox{$
\begin{small}
\begin{array}{llcl}
\heterocohbox{l}{\epsilon,\epsilon'}^{\!\!\!\tiny\begin{array}{l}n,q,r,p\\\mbox{}[p \leq r < q < n]\end{array}} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(d:\myheterobox{l}^{n,p}(D))\end{array}& : & \!\!\!\begin{array}{ll}\heterodownbox{l}{\epsilon}^{n-1,q-1,p}(\downboxtype{l}{\epsilon'}^{n,r,p}(\hd(D)))(\heterodownbox{l}{\epsilon'}^{n,r,p}(D)(d)) \\ \eqett \heterodownbox{l}{\epsilon'}^{n-1,r-1,p}(\downboxtype{l}{\epsilon}^{n,q,p}(\hd(D)))(\heterodownbox{l}{\epsilon}^{n,q,p}(D)(d))\end{array}\\
\heterocohbox{l}{\epsilon,\epsilon'}^{n,q,r,0} & D~\unitpoint & \defeq & \reflett(\unitpoint)\\
\heterocohbox{l}{\epsilon,\epsilon'}^{n,q,r,p'+1} & D~(d,b) & \defeq & (\heterocohbox{l}{\epsilon,\epsilon'}^{n,q,r,p'}(D)(d),\heterocohlayer{l}{\epsilon,\epsilon'}^{n,q,r,p'}(D)(d)(b))\\
\\
\heterocohlayer{l}{\epsilon,\epsilon'}^{\!\!\!\tiny\begin{array}{l}n,q,r,p\\\mbox{}[p < r < q < n]\end{array}} & \!\!\!\tiny\begin{array}{l}(D:\myheteroboxtype{l}^{n,p})\\(d:\myheterobox{l}^{n,p}(D))\\(b:\myheterolayer{l}^{n,p}(D)(d))\end{array}& : & \!\!\!\begin{array}{ll}\heterodownlayer{l}{\epsilon}^{n-1,q-1,p}(\downboxtype{l}{\epsilon'}^n(D))(\heterodownbox{l}{\epsilon'}^{n,r,p}(D)(d))(\heterodownlayer{l}{\epsilon'}^{n,r,p}(D)(d)(b)) \\ \eqett \heterodownlayer{l}{\epsilon'}^{n-1,r-1,p}(\downboxtype{l}{\epsilon}^n(D))(\heterodownbox{l}{\epsilon}^{n,r,p}(D)(d))(\heterodownlayer{l}{\epsilon}^{n,r,p}(D)(d)(b))\end{array}\\
\heterocohlayer{l}{\epsilon,\epsilon'}^{n,q,r,p} & D~d~c & \defeq & \!\!\begin{array}{l}(\heterocohcube{l}{\epsilon,\epsilon'}^{n,q,r,p}(D)(\heterodownbox{l}{L}^{n,p,p}(D)(d))(c_L),\\\;\heterocohcube{l}{\epsilon,\epsilon'}^{n,q,r,p}(D)(\heterodownbox{l}{R}^{n,p,p}(D)(d))(c_R))\end{array}\\
\\
\heterocohcube{l}{\epsilon,\epsilon'}^{\!\!\!\tiny\begin{array}{l}n,q,r,p\\\mbox{}[p \leq r < q < n]\end{array}} & \!\!\!\tiny\begin{array}{l}(D:\myheteroboxtype{l}^{n,p})\\(d:\myheterobox{l}^{n,p}(D))\\(b:\myheterocube{l}{??}^{n,p}(D)(d))\end{array}& : & \!\!\!\begin{array}{ll}\heterodowncube{l}{\epsilon}^{n-1,q-1,p}(\downboxtype{l}{\epsilon'}^{n,q,p}(D))(\heterodownbox{l}{\epsilon'}^{n,r,p}(D)(d))(\heterodowncube{l}{\epsilon'}^{n,r,p}(D)(d)(b)) \\ \eqett \heterodowncube{l}{\epsilon'}^{n-1,r-1,p}(\downboxtype{l}{\epsilon}^{n,q,p}(D))(\heterodownbox{l}{\epsilon}^{n,q,p}(D)(d))(\heterodowncube{l}{\epsilon}^{n,q,p}(D)(d)(b))\end{array}\\
\heterocohcube{l}{\epsilon,\epsilon'}^{n,q,r,p,[p=r]} & D~d~(b,\_) & \defeq & \reflett(\heterodowncube{l}{\epsilon}^{n-1,q-1,p}(\downboxtype{l}{\epsilon'}^n(D))(\heterodownbox{l}{\epsilon'}^{n,q,p}(D)(d))(b_{\epsilon}))\\
\heterocohcube{l}{\epsilon,\epsilon'}^{n,q,r,p,[p<r)} & D~d~(b,c) & \defeq & \!\!\begin{array}{l}(\heterocohlayer{l}{\epsilon,\epsilon'}^{n,q,r,p}(\downboxtype{l}{\epsilon}^n(D))(d)(b),\\\;\heterocohcube{l}{\epsilon,\epsilon'}^{n,q,r,p+1}(D)(d,\heterodownlayer{l}{\epsilon}^{n,q,p}(\downboxtype{l}{\epsilon?}^n(D))(d)(b))(c))\end{array}\\
\end{array}
\end{small}
$
}}
\caption{Definition of a heterogeneous cube (compatibility of faces of terms)}
\label{fig:heterobarecubicalsetcoherences}
\end{figure*}

TODO: Unify the different variants of $\Sigma$-types: $\times$,
records, names of the projections.

\subsection{Dependent cubes}

See Figure~\ref{fig:heterobaredepcube}.

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\myheterodepboxtype{l}^{n,p,[p \leq n]} & (D:\myheteroboxtype{l}^{n,n}) & : & U_{l+1}\\
\myheterodepboxtype{l}^{n,0} & D & \defeq & \unittype\\
\myheterodepboxtype{l}^{n,p'+1} & D & \defeq & \Sigma d:\myheterodepboxtype{l}^{n,p'}(D).\,\myheterolayertype{l}^{n,p'}(D)(d)\\
\\
\myheterodeplayertype{l}^{n,p,[p < n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(d:\myheterodepboxtype{l}^{n,p}(D))\end{array}& : & \sort{l+1}\\
\myheterodeplayertype{l}^{n,p} & D~d & \defeq & \!\!\!\begin{array}{l}\myheterodepcubetype{l}^{n-1,p}(\downboxtype{l}{L}^{n,n-1}(\hd(D)))(\tl(D)_L)(\heterodepdownboxtype{L}^{n,p,p}(D)(d)) \\\times\; \myheterodepcubetype{l}^{n-1,p}(\downboxtype{l}{L}^{n,n-1}(\hd(D)))(\tl(D)_R)(\heterodepdownboxtype{R}^{n,p,p}(D)(d))\end{array}\\
\\
\multicolumn{4}{c}{\mbox{+ definition of $\heterodepdownboxtype{\epsilon}$}}\\
\\
\myheterodepcubetype{l}^{n,p,[p < n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(E:\myheterocubetype{l}^{n,n}(D))\\(d:\myheterodepboxtype{l}^{n,p}(D))\end{array}& : & \sort{l+1}\\
\myheterodepcubetype{l}^{n,p,[p = n]} & D~E~d & \defeq & \Pi d':\myheterobox{l}^{n,n}(D). \Pi c:\myheterocube{l}^{n,n}(D)(E)(d'). \myheterobox{l}^{n,n}(\myappdepboxtype{l}^{n,n}(D)(d)(d')) \imp \sort{l}\\
\myheterodepcubetype{l}^{n,p,[p < n]} & D~E~d & \defeq & \Sigma b:\myheterodeplayertype{l}^{n,p}(D)(d).\,\myheterodepcubetype{l}^{n,p+1}(D)(d,b)\\
\end{array}
$
}}
\caption{Definition of a heterogeneous dependent cube of higher-order relations}
\label{fig:heterobaredepcube}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\myappdepboxtype{l}^{n,p,[p \leq n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(d:\myheterodepboxtype{l}^{n,p}(D))\\(d':\myheterobox{l}^{n,p}(D))\end{array}& : & \myheteroboxtype{l}^{n,p}\\
\myappdepboxtype{l}^{n,0} & D~\star~\star & \defeq & \star\\
\myappdepboxtype{l}^{n,p'+1} & D~(d,b)~(d',b') & \defeq & (\myappdepboxtype{l}^{n,p'}(D)(d)(d'),\myappdeplayertype{l}^{n,p'}(D)(d)(d')(b)(b'))\\
\\
\myappdeplayertype{l}^{n,p,[p \leq n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(d:\myheterodepboxtype{l}^{n,p}(D))\\(d':\myheterobox{l}^{n,p}(D))\\(b:\myheterodeplayertype{l}^{n,p}(D)(d))\\(b':\myheterolayer{l}^{n,p}(D)(d'))\end{array} & : & \myheterolayertype{l}^{n,p}(\myappdepboxtype{l}^{n,p'}(D)(d)(d'))\\
\myappdeplayertype{l}^{n,p} & D~d~d'~c~c' & \defeq & \!\!\!\begin{array}{l}(\myappdepcubetype{l}^{n-1,p}\!\!\!\begin{array}{l}(\downboxtype{l}{L}^{n,n-1,n-1}(\hd(D)))\\(\heterodepdownbox{L}^{n,n-1,n-1}(d))\\(\heterodownbox{l}{L}^{n,n-1,n-1}(d'))\end{array}(c_L)(c_L'), \\~\myappdepcubetype{l}^{n-1,p}\!\!\!\begin{array}{l}(\downboxtype{l}{R}^{n,n-1,n-1}(\hd(D)))\\(\heterodepdownbox{R}^{n,n-1,n-1}(d))\\(\heterodownbox{l}{R}^{n,n-1,n-1}(d'))\end{array}(c_R)(c_R'))\end{array}\\
\\
\multicolumn{4}{c}{\mbox{+ proofs of commutations $\downboxtype{l}{}$/$\myappdepboxtype{}$}}\\
\\
\myappdepcubetype{l}^{n,p,[p \leq n]} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(d:\myheterodepboxtype{l}^{n,p}(D))\\(d':\myheterobox{l}^{n,p}(D))\\(c:\myheterodepcubetype{l}^{n,p}(D)(d))\\(c':\myheterocube{l}^{n,p}(D)(d'))\end{array} & : & \myheterocubetype{l}^{n,p}(\myappdepboxtype{l}^{n,p'}(D)(d)(d'))\\
\myappdepcubetype{l}^{n,p,[p = n]} & D~d~d'~c~c' & \defeq & (c\,d'\,c')\\
\myappdepcubetype{l}^{n,p,[p < n]} & D~d~d'~(b,c)~(b',c') & \defeq & (\myappdeplayertype{l}^{n,p}(D)(d)(d')(b)(b'),\myappdepcubetype{l}^{n,p+1}(D)(d)(d')(c)(c'))\\
\end{array}
$
}}
\caption{Definition of a heterogeneous dependent cube of higher-order relations (application)}
\label{fig:heterobaredepcubemap}
\end{figure*}
\iffalse %%%
\subsection{Symmetric cartesian structure of cubes}

In order to interpret abstraction and application over a variable of
the interval we need to equip the bare structure of cubical sets with
arbitrary maps from a finite set of variables of the interval to
another finite set of variables of the interval of same or larger
cardinality (if we want the application of the same variable to be
allowed several times, we also to allow maps to a finite set of
smaller cardinality).

There are different ways to canonically represent such maps. One of
these ways is to factorize the maps using reflexivities
(i.e. degeneracies in the language of cubical sets, or identities in
the language of category theory) and permutations (called symmetries
in the context of cubical sets).

The additional structure defining a symmetric cubical set with
degeneracies is given on Figure~\ref{fig:symcubicalset},
\ref{fig:reflexivity} and \ref{fig:permutation}. To allow maps to a
finite set of smaller cardinality, we also need diagonals which are
additionally presented on Figure~\ref{fig:diagonals}. Also,
connections shall be needed to support dependent composition. These
are on Figure~\ref{fig:connections}.

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\partialsymcubset^n & (D:\partialcubset{l}^n) & : & \sort{l+1}\\
\partialsymcubset^0 & \star & \defeq & \unittype\\
\partialsymcubset^{n+1} & (D,R) & \defeq & \Sigma S:\partialsymcubset^n(D).\,\issymcubset^n(D)(R)(S)\\
\\
\issymcubset^n & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n})\\(R:\mybox{l}^{n,n}(D) \imp \sort{l})\\(S:\partialsymcubset^n(D))\end{array}& \defeq & \{\\
&&& \mathsf{reflexive} ~:~ \reflexive^n(D)(R)(S);\\
&&& \mypermute ~:~ \permutation^n(D)(R)(S);\\
&&& \diagprop ~:~ \diagprop^n(D)(R)(S);\\
&&& \}\\
\end{array}
$
}}
\caption{Definition of a truncated symmetric cartesian cubical set}
\label{fig:symcubicalset}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{small}
\begin{array}{llcl}
\reflexive_l^n & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n})\\(R:\mybox{l}^{n,n}(D)\imp \sort{l})\end{array}& : & \sort{l}\\
\reflexive^0 & \unitpoint~A & \defeq & \unittype\\
\reflexive^{n+1} & (D,R_n)~(R^{n+1}) & \defeq & \!\!\!\begin{array}{l}\Pi d:\mybox{l}^{n,n}(\hd(D)).\, \Pi c:R_n\,d.\,\\ R^{n+1}(\reflbox^{n+1,n}(D)(d),(\overrightarrow{\cohrefleqbox{R}^{n+1,n}(D)(d)}(c),\overrightarrow{\cohrefleqbox{L}^{n+1,n}(D)(d)}(c)))\end{array}\\
\\
\reflbox^{n+1,p,[p \leq n]} & \!\!\!\begin{array}{l}(D : \partialcubset{l}^{n+1})\\(d:\mybox{l}^{n,p}(\hd(D)))\end{array}& : & \mybox{l}^{n+1,p}(D)\\
\reflbox^{n+1,0} & D~\unitpoint & \defeq & \unitpoint\\
\reflbox^{n+1,p+1} & D~(d,b) & \defeq & (\reflbox^{n+1,p}(D)(d),\refllayer^{n+1,p}(D)(d)(b))\\
\\
\refllayer^{n+2,p,[p \leq n]} & \!\!\!\begin{array}{l}(D : \partialcubset{l}^{n+2})\\(d:\mybox{l}^{n+1,p}(\hd(D)))\\(b:\mylayer{l}^{n+1,p}(\hd(D))(d)\end{array}& : & \mylayer{l}^{n+2,p}(D)(\reflbox^{n+2,p}(D)(d))\\
\refllayer^{n+2,p} & D~d~c & \defeq & \!\!\!\begin{array}{l}(\overrightarrow{\cohreflbox{L}^{n+2,p,p}(D)(d)}(\reflcube^{n+2,p}(D)(\downbox{l}{L}^{n+1,p,p}(\hd(D))(d))(c_L)),\\\;\overrightarrow{\cohreflbox{R}^{n+2,p,p}(D)(d)}(\reflcube^{n+2,p}(D)(\downbox{l}{R}^{n+1,p,p}(\hd(D))(d))(c_R)))\end{array}\\
\\
\reflcube^{n+2,p,[p \leq n]} & \!\!\!\begin{array}{l}(D : \partialcubset{l}^{n+2})\\(d:\mybox{l}^{n,p}(\hd(\hd(D))))\\(c:\mycube{l}^{n+1,p}(\hd(D))(d))\end{array}& : & \mycube{l}^{n+2,p}(D)(\reflbox^{n+1,p}(\hd(D))(d))\\
\reflcube^{n+2,p,[p = n]} & (D,R)~d~c & \defeq & ((\overrightarrow{\cohrefleqbox{L}^{n+2}(D)(d)}(c),\overrightarrow{\cohrefleqbox{R}^{n+2}(D)(d)}(c)),\reflexive^{n+1}(D)(R)(d)(c))\\
\reflcube^{n+3,p,[p < n]} & D~d~(b,c) & \defeq & (\refllayer^{n+2,p}(D)(d)(b),\reflcube^{n+3,p+1}(D)(d)(c))\\
\\
\cohrefleqbox{\epsilon}^{\!\!\!\tiny\begin{array}{l}n,p\\\mbox{}[p \leq n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n+2})\\(d:\mybox{l}^{n+1,p+1}(\hd(D)))\end{array}& : & \!\!\!\begin{array}{ll}\downbox{l}{\epsilon}^{n+2,p+1,n+1}(D)(\reflbox^{n+2,p+1}(D)(d)) \\ \eqett d\end{array}\\
\cohrefleqbox{\epsilon}^{n,0} & D~\unitpoint & \defeq & \reflett(\unitpoint)\\
\cohrefleqbox{\epsilon}^{n+1,p+1} & D~(d,b) & \defeq & (\cohrefleqbox{\epsilon}^{n+1,p}(D)(d),\cohrefleqlayer{\epsilon}^{n+1,p}(D)(d)(b))\\
\\
\cohrefleqlayer{\epsilon}^{\!\!\!\tiny\begin{array}{l}n+1,p\\\mbox{}[p \leq n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n+3})\\(d:\mybox{l}^{n+2,p+1}(\hd(D)))\\(b:\mylayer{l}^{n+2,p+1}(\hd(D))(d))\end{array}& : & \!\!\!\begin{array}{ll}\downlayer{l}{\epsilon}^{n+3,p+1,n+2}(D)(\reflbox^{n+3,p+1}(D)(d))(\refllayer^{n+3,p+1}(D)(d)(b)) \\ \eqett b\end{array}\\
\cohrefleqlayer{\epsilon}^{n+1,p} & D~d~(c_L,c_R) & \defeq & \!\!\!\begin{array}{l}(\cohrefleqcube{\epsilon}^{n+1,p}(D)(\downbox{l}{L}^{n+3,p+1,p+1}(D)(d))(c_L),\\\;\cohrefleqcube{\epsilon}^{n+1,p}(D)(\downbox{l}{R}^{n+3,p+1,p+1}(D)(d))(c_R))\end{array}\\
\\
\cohrefleqcube{\epsilon}^{\!\!\!\tiny\begin{array}{l}n+1,p\\\mbox{}[p \leq n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n+3})\\(d:\mybox{l}^{n+1,p+1}(\hd(\hd(D))))\\(c:\mycube{l}^{n+2,p+1}(\hd(D))(d))\end{array}& : & \!\!\!\begin{array}{ll}\downcube{l}{\epsilon}^{n+3,p+1,n+2}(D)(\reflbox^{n+3,p+1}(D)(d))(\reflcube^{n+3,p+1}(D)(d)(c)) \\ \eqett c\end{array}\\
\cohrefleqcube{\epsilon}^{n+1,p,[n=p]} & D~d~c & \defeq & \reflett(c)\\
\cohrefleqcube{\epsilon}^{n+2,p,[n>p)} & D~d~(b,c) & \defeq & \!\!\!\begin{array}{l}(\cohrefleqlayer{\epsilon}^{n+2,p}(\hd(D))(d)(b),\\\;\cohrefleqcube{\epsilon}^{n+2,p+1}(D)(d,\downlayer{l}{\epsilon}^{n+2,p+1,n+1}(\hd(D))(d)(b))(c))\end{array}\\
\\
\cohreflbox{\epsilon}^{\!\!\!\tiny\begin{array}{l}n+2,p,q\\\mbox{}[p \leq q \leq n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n+2})\\(d:\mybox{l}^{n+1,p}(\hd(D)))\end{array}& : & \!\!\!\begin{array}{ll}\downbox{l}{\epsilon}^{n+2,p,q}(D)(\reflbox^{n+2,p}(D)(d)) \\ \eqett \reflbox^{n+1,p}(\hd(D))(\downbox{l}{\epsilon}^{n+1,p,q}(\hd(D))(d))\end{array}\\
\cohreflbox{\epsilon}^{n+2,0,q} & D~\unitpoint & \defeq & \reflett(\unitpoint)\\
\cohreflbox{\epsilon}^{n+3,p+1,q+1} & D~(d,b) & \defeq & (\cohreflbox{\epsilon}^{n+3,p,q+1}(D)(d),\cohrefllayer{\epsilon}^{n+3,p,q+1}(D)(d)(b))\\
\\
\cohrefllayer{\epsilon}^{\!\!\!\tiny\begin{array}{l}n+3,p,q+1\\\mbox{}[p \leq q \leq n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n+3})\\(d:\mybox{l}^{n+2,p}(\hd(D)))\\(b:\mylayer{l}^{n+2,p}(\hd(D))(d))\end{array}& : & \!\!\!\begin{array}{ll}\downlayer{l}{\epsilon}^{n+3,p,q+1}(D)(\reflbox^{n+3,p}(D)(d))(\refllayer^{n+3,p}(D)(d)(b)) \\ \eqett \refllayer^{n+2,p}(\hd(D))(\downbox{l}{\epsilon}^{n+2,p,q+1}(\hd(D))(d))(\downlayer{l}{\epsilon}^{n+3,p,q+1}(\hd(D))(d)(b))\end{array}\\
\cohrefllayer{\epsilon}^{n+3,p,q+1} & D~d~c & \defeq & \!\!\!\begin{array}{l}(\cohreflcube{\epsilon}^{n+3,p,q+1}(D)(\downbox{l}{L}^{n+3,p,p}(D)(d))(c_R),\\\;\cohreflcube{\epsilon}^{n+3,p,q+1}(D)(\downbox{l}{R}^{n+3,p,p}(D)(d))(c_R))\end{array}\\
\\
\cohreflcube{\epsilon}^{\!\!\!\tiny\begin{array}{l}n+3,p,q+1\\\mbox{}[p \leq q \leq n]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n+3})\\(d:\mybox{l}^{n+1,p}(D))\\(b:\mycube{l}^{n+2,p}(D)(d))\end{array}& : & \!\!\!\begin{array}{ll}\downcube{l}{\epsilon}^{n+3,p,q+1}(D)(\reflbox^{n+3,p}(D)(d))(\reflcube^{n+3,p}(D)(d)(b)) \\ \eqett \reflcube^{n+2,p}(\hd(D))(\downbox{l}{\epsilon}^{n+2,p,q+1}(D)(d))(\downcube{l}{\epsilon}^{n+2,p,q+1}(D)(d)(b))\end{array}\\
\cohreflcube{\epsilon}^{n+3,p,q+1,[p=q]} & D~d~(b,\_) & \defeq & \reflett(\reflcube^{n+2,p}(\hd(D))(\downbox{l}{\epsilon'}^{n+3,p,q+2}(D)(d))(b_{\epsilon}))\\
\cohreflcube{\epsilon}^{n+4,p,q+1,[p<q)} & D~d~(b,c) & \defeq & \!\!\!\begin{array}{l}(\cohrefllayer{\epsilon}^{n+3,p,q+1}(\hd(D))(d)(b),\\\;\cohreflcube{\epsilon}^{n+4,p+1,q+1}(D)(d,\downlayer{l}{\epsilon}^{n+3,p,q+1}(\hd(D))(d)(b))(c))\end{array}\\
\end{array}
\end{small}
$
}}
\caption{Specification of reflexivity in a cubical set (TODO: check the cohreflcube part; check whether it is normal that we don't need reflexivity in directions other than the top one; point out where UIP is used)}
\label{fig:reflexivity}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\permutation_{\sigma}^n & (D:\partialcubset{l}^{n}) & : & \sort{}\\
\permutation_{\sigma}^0 & D & \defeq & \unittype\\
\permutation_{\sigma}^{n+1} & (D,R) & \defeq & \Pi d:\mybox{l}^{n,n}(D).\, R(d) \imp R(\permutebox_{\sigma}^{n,n}(D)(d))\\
\\
\permutebox_{\sigma}^{n,p} & (D : \partialcubset{l}^{n})~(d:\mybox{l}^{n,n}(D)) & : & \mybox{l}^{n,p}(D)\\
\permutebox_{k,\sigma}^{n,p} & D~d & : & ...
\end{array}
$
}}
\caption{Specification of permutations in a cubical set}
\label{fig:permutation}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\diagonal^n & (D:\partialcubset{l}^{n}) & : & \sort{}\\
\diagonal^0 & D & \defeq & \unittype\\
\diagonal^{n+1} & ((D,R),R') & \defeq & \Pi d:\mybox{l}^{n+1,n+1}(D,R).\, R'(d) \imp R(\diagbox^{n}(D,R)(d))\\
\\
\diagbox^{n} & (D : \partialcubset{l}^{n+1})~(d:\mybox{l}^{n+1,n+1}(D) & : & \mybox{l}^{n,n}(\hd(D))\\
...
\end{array}
$
}}
\caption{Specification of diagonals in a cubical set}
\label{fig:diagonals}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\connection^n & (D:\partialcubset{l}^{n+2}) & : & \sort{}\\
\connection^0 & D & \defeq & \unittype\\
\connection^{n+1} & ((D,R),R') & \defeq & \Pi d:\mybox{l}^{n+1,n+1}(D,R).\, R'(d) \imp R(\connbox^{n}(D,R)(d))\\
\\
\connbox^{n} & (D : \partialcubset{l}^{n+2})~(d:\mybox{l}^{n+1,n+1}(\hd(D)) & : & \mybox{l}^{n+2,n+2}(D)\\
...
\end{array}
$
}}
\caption{Specification of connections in a cubical set}
\label{fig:connections}
\end{figure*}

We shall not need it, but the definition of a full non-truncated symmetric cubical set is shown on Figure~\ref{fig:fullsymcubicalset}.

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\mysymcubset_l && \defeq & \mysymcubset_l^0(\star)(\star)\\
\\
\mysymcubset_l^n & \!\!\!\begin{array}{l}(D:\partialcubset{l}^n)\\(S:\partialsymcubset^n(D))\end{array}& : & \sort{l+1}\\
\mysymcubset_l^n & D~S & \defeq & \Sigma R:(\mybox{l}^{n,n}(D) \imp \sort{l}).\,\Sigma E:\issymcubset^n(D)(R)(S).\,\mycubset_l^{n+1}(D,R)(S,E)\\
\end{array}
$
}}
\caption{Full (non-truncated) symmetric cartesian cubical set}
\label{fig:fullsymcubicalset}
\end{figure*}

\subsection{Cubical $\omega$-groupoids}

The truncated bare cubical set structure is inherent to iterated
parametricity. The requirement of the relations to be reflexive and
stable by permutation is inherent to abstraction over an axis variable
and to (linear) application to an axis variable. In particular, in a
(non-cartesian) framework of pure parametricity, such as Bernardy,
Coquand and Moulin~\cite{BernardyCoquandMoulin15}, these are the
minimal requirements to interpret a type. For instance, to interpret
the cubical type theory from~\cite{BernardyCoquandMoulin15}, a type
variable of the source language can simply be interpreted as a type of
the target language, canonically interpreting each higher-dimensional
relation by iterations of the identity type of the target language.
This interpretation would be compatible with any type for which the
equality assigned to this type in the translation coincides with
identity. This is case for $\Sigma$-types and also for $\Pi$-types
since ETT satisfies functional extensionality. Since identity is
truncated by virtue of the uniqueness of identity proofs in ETT, this
would mean interpreting each type by a degenerated higher-dimensional
structure. Thus, it would not support the interpretation of
non-trivial types such as the circle, or more generally $n$-spheres,
or more generally higher-inductive types.

Thus, to support the interpretation of types with non degenerated
higher-dimensional structure, and in particular to support
higher-inductive types, it is required to interpret types by means of
cubical sets with a non-trivial higher-dimensional structure as high
as required to interpret such type. In particular, to interpret types
with unbounded homotopy levels, one need to interpret types of the
source language by means of untruncated cubical sets as defined in
Figure~\ref{fig:barecubicalset}. This would be the case
of~\cite{BernardyCoquandMoulin15} but we need more to interpret
transport.

To support transport, we need each higher-dimensional relation over an
$n$-box to be equipped with a composition operator. If, additionally,
we want that composition is coherent, i.e. that it transports to equal
elements (this is needed to define transport over dependent types), we
shall need to enforce this as a requirement. If we additionally expect
the composition to to be ``regular'' meaning that composition along a
degenerated tube is the identity and the map from a degenerated filler
to a homogeneous equality to be the identity too. Note that we require
composition only in the direction of the main faces of an
$n$-cube. This is because our homogeneous $n$-cubes are required to be
stable by permutation, so compositions in all other directions can be
derived from the composition in the main direction.

All this is described in Figures~\ref{fig:compositionstructure}
and~\ref{fig:compositionproperties} and we conjecture that the
resulting definition provides with a definition of semi-strict
$\omega$-groupoid based on cubical sets. For that reason, we call it
cubical $\omega$-groupoid.

Note that the diagonal structure could a priori be derived from the
composition structure.

Note that if $G$ is a cubical $\omega$-groupoid and
$a_0:\hd(G).R\star$ and $a_1:\hd(G)(\star)$ (i.e. $a_0$ and $a_1$ are
two points of the groupoid, then $\tl(\tl(G))$ can be seen as a
cubical $\omega$-groupoid by specializing all its $n$-cubes to
$(n-1)$-cubes completed with degeneracies of $a_0$ and
$a_1$. Otherwise said, there is a map from $G_1:\mygpd^{1}(A)(E)$ to
$G':\mygpd_0(\star)(\star)$ such that $\hd(G')$ is
$\hd(G_1)(\star,(a_1,a_2))$ (A FAIRE PRÉCISÉMENT).

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\mygpd_l && \defeq & \mygpd_l^0(\star)(\star)\\
\\
\mygpd_l^0 & \!\!\!\begin{array}{l}(D:\partialcubset{l}^n)\\(S:\partialhascomp^n(D))\end{array}& : & \sort{l+1}\\
\mygpd_l^n & D~S & \defeq & \Sigma R:(\mybox{l}^{n,n}(D) \imp \sort{l}).\Sigma E:\hascomp^n(D)(R)(S).\,\mygpd_l^{n+1}(D,R)(S,E)\\
\\
\partialhascomp^n & (D:\partialcubset{l}^n) & : & \sort{l+1}\\
\partialhascomp^0 & \star & \defeq & \unittype\\
\partialhascomp^{n+1} & (D,R) & \defeq & \Sigma S:\partialhascomp^n(D).\,\hascomp^n(D)(R)(S)\\
\\
\hascomp^n & \!\!\!\begin{array}{l}(D:\partialcubset{l}^{n})\\(R:\mybox{l}^{n,n}(D) \imp \sort{l})\\(S:\partialhascomp^n(D))\end{array}& \defeq & \{\\
&&& \mathsf{hassymcubset} ~:~ \issymcubset^n(D)(R);\\
&&& \overrightarrow{\cdot} ~:~ \coercivelr^n(D)(R);\\
&&& \overleftarrow{\cdot} ~:~ \coerciverl^n(D)(R);\\
%&&& \overleftarrow{\cdot} : 
% \Pi a:\left(\begin{array}{c}
%          \Sigma a_0:\left(\begin{array}{c}\mybox{l}^{n,n-1}(D)\\ \times\\ \mybox{l}^{n,n-1}(D)\end{array}\right).a^{00}=a^{01}\\
%          \times\\
%          \Sigma a_1:\left(\begin{array}{c}\mybox{l}^{n,n-1}(D)\\ \times\\ \mybox{l}^{n,n-1}(D)\end{array}\right).a^{10}=a^{11}\\
%          \end{array}\right). a^{01} = a^{11} \imp a^{00} = a^{10};\\
&&& \reglr ~:~ \regularitylr^n(D)(R)(S);\\
&&& \regrl ~:~ \regularityrl^n(D)(R)(S);\\
%\Pi a:\left(\begin{array}{c}\mybox{l}^{n,n-1}(D)\\ \times\\ \mybox{l}^{n,n-1}(D)\end{array}\right).\Pi a_{\star}:a_0 = a_1.\overrightarrow{\cdot}(((a_0,a_0),\refl(a_0)),((a_1,a_1),\refl(a_1)),a_{\star}) \equiv a\\
&&& \Overrightarrow{1ex}{\cdot} ~:~ \Coercivelr^n(D)(R);\\
&&& \Overleftarrow{1ex}{\cdot} ~:~ \Coerciverl^n(D)(R);\\
&&& \Reglr{\cdot} ~:~ \Regularitylr^n(D)(R)(S);\\
&&& \Regrl{\cdot} ~:~ \Regularityrl^n(D)(R)(S);\\
&&& \coebacklr{\cdot} ~:~ \backcoercivelr^n(D)(R);\\
&&& \coebackrl{\cdot} ~:~ \backcoerciverl^n(D)(R);\\
&&& \regbacklr{\cdot} ~:~ \regularitybacklr^n(D)(R)(S);\\
&&& \regbackrl{\cdot} ~:~ \regularitybackrl^n(D)(R)(S);\\
&&& \Coebacklr{\cdot} ~:~ \Coercivebacklr^n(D)(R);\\
&&& \Coebackrl{\cdot} ~:~ \Coercivebackrl^n(D)(R);\\
&&& \Regbacklr{\cdot} ~:~ \Regularitybacklr^n(D)(R)(S);\\
&&& \Regbackrl{\cdot} ~:~ \Regularitybackrl^n(D)(R)(S);\\
&&& \}\\
\end{array}
$
}}
\caption{Definition of a cubical groupoid}
\label{fig:compositionstructure}
\end{figure*}

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\coercivelr^0 & D~R & \defeq & \unittype\\
\coercivelr^{n+1} & D~R & \defeq & \Pi d:\mybox{l}^{n+1,n}(D,R).\, R(\downbox{l}{L}^{n+1,n,n}(D)(d)) \imp R(\downbox{l}{R}^{n+1,n,n}(D)(d))\\
\\
\coerciverl^0 & D~R & \defeq & \unittype\\
\coerciverl^{n+1} & D~R & \defeq & \Pi d:\mybox{l}^{n+1,n}(D,R).\, R(\downbox{l}{R}^{n+1,n,n}(D)(d)) \imp R(\downbox{l}{L}^{n+1,n,n}(D)(d))\\
\\
\regularitylr^0 & D~R~S & \defeq & \unittype\\
\regularitylr^{n+1} & D~R~S & \defeq & \Pi d:\mybox{l}^{n,n}(D).\, \overrightarrow{\cdot}(\reflbox^{n+1}(D)(d))(a) \equiv_{ETT} a\\
\\
\regularityrl^0 & D~R~S & \defeq & \unittype\\
\regularityrl^{n+1} & D~R~S & \defeq & \Pi d:\mybox{l}^{n,n}(D).\, \overleftarrow{\cdot}(\reflbox^{n+1}(D)(d))(a) \equiv_{ETT} a\\
\\
...
\end{array}
$
}}
\caption{Definition of a groupoid (properties of a groupoid)}
\label{fig:compositionproperties}
\end{figure*}

\subsection{Types as $n$-cubes of equivalences}

To support transport, or dependent transport, or univalence, extra
structure is needed to relate types. We obtain this extra structure by
taking the instance for $\phi_n$ and $\psi_n$ given on
Figure~\ref{fig:equivalence}.  Instead of just returning a relation to
$\sort{}$, we return a relation $R$ which first returns an
$\omega$-groupoid rather than just a type and, second, returns the
property that the relation is an equivalence.

MANY REMAINING QUESTIONS...

\begin{figure*}
\centerline{ \framebox{$
\begin{array}{llcl}
\phi_n & D & \defeq & \{\\
&&& R ~:~ \myheterobox{l}^{n,n}(D) \imp \mygpd_l\\
&&& E ~:~ \isequivalence^{n}(D)(R)\\
%&&& E' ~:~\isequivalence'^{n}(D)(R)(E)\\
%&&& E'' ~:~\isequivalence''^{n}(D)(R)(E)(E')\\
&&& \}\\
\psi_n & D~P~d & \defeq & P.R\,d\\
\\
\isequivalence^{n} & \!\!\!\begin{array}{l}(D:\myheteroboxtype{l}^{n,n})\\(R:\myheterobox{l}^{n,n}(D) \imp \mygpd_l)\end{array}& : & \sort{}\\
\isequivalence^{n} & D~R & \defeq &\\
 \{\\
\multicolumn{4}{c}{\begin{array}{llll}
&&&\rightarrow^{n+1} ~:~ \Pi d:\myheterobox{l}^{n+1,n}(D).\,\heterodownbox{l}{L}^{n+1,n,n}(D)(d) \imp \heterodownbox{l}{R}^{n+1,n,n}(D)(d)\\
&&&\leftarrow^{n+1} ~:~ \Pi d:\myheterobox{l}^{n+1,n}(D).\heterodownbox{l}{R}^{n+1,n,n}(D)(d) \imp \heterodownbox{l}{L}^{n+1,n,n}(D)(d)\\
&&&\Rightarrow^{n+1} ~:~ \Pi d:\myheterobox{l}^{n+1,n}(D).\,\Pi a:\heterodownbox{l}{L}^{n+1,n,n}(D)(d).\, R(d,(a,\rightarrow^{n+1}(d)(a)))\\
&&&\Leftarrow^{n+1} ~:~ \Pi d:\myheterobox{l}^{n+1,n}(D).\,\Pi a:\heterodownbox{l}{R}^{n+1,p,p}(D).\, R(d,(\leftarrow^{n+1}(d)(a),a))\\
&&&\overrightarrow{\mathsf{coe}}^{n+1} ~:~ \Pi (d,(a_0,a_1)):\myheterobox{l}^{n+1,n+1}(D).\, \tl(D)_1.R(d,(\rightarrow^{n+1}(d)(a_0),a_1))\\
&&&\overleftarrow{\mathsf{coe}}^{n+1} ~:~ \Pi (d,(a_0,a_1)):\myheterobox{l}^{n+1,n+1}(D).\, \tl(D)_0.R(d,(a_0,\leftarrow^{n+1}(d)(a_1)))\\
&&&\Overrightarrow{1ex}{\mathsf{coe}}^{n+3} ~:~ \Pi (d,(a_0,a_1)):\myheterobox{l}^{n+1,n+1}(D).\, R(D,(a,\rightarrow(p)(a)))\\
&&&\Overleftarrow{1ex}{\mathsf{coe}}^{n+3} ~:~ \Pi d:\myheterobox{l}^{n+1,n}(D).\,\Pi (a_0,a_1):(\heterodownbox{l}{L}^{n,p,p}(D) \times \heterodownbox{l}{R}^{n,p,p}(D)).\, \Pi a_{\star}:R(D,a).\, (D).\, R(D,(a,\rightarrow(p)(a)))\\
  \end{array}}\\
\}\\
\end{array}
$
}}
\caption{Specializing heterogeneous cubes to heterogeneous cubes over cubes of equivalences}
\label{fig:equivalence}
\end{figure*}

\fi %%%
\iffalse
$$
\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
\begin{array}{lll}
\semsort{l}^{0,0} & \defeq & \sort{l} \\
\semsort{l}^{0,1} & \defeq & \Sigma A:\sort{l}.\,(A\imp A \imp \sort{l})\\
\semsort{l}^{0,2} & \defeq & \Sigma (A,=_A):(\Sigma A:\sort{l}.\,A\imp A \imp \sort{l}).\,\Pi a_{00}.\,\Pi a_{01}:A.\, a_{00} =_A a_{01} \imp \Pi a_{00}:A.\,\Pi a_{11}:A.\, a_{10} =_A a_{11} \imp a_{00} =_A a_{10} \imp a_{01} =_A a_{11} \imp \sort\
{l};\\
\semsort{l}^{1,0} & \defeq & \{\\
& & 
\begin{array}{lll}
(A_0,=_{0}) &:& \semsort{l}^{0,1};\\
(A_1,=_{1}) &:& \semsort{l}^{0,1};\\
=_{\star} &:& A_0 \imp A_1 \imp \sort{l};\\
\rightarrow &:& A_0 \imp A_1;\\
\leftarrow &:& A_1 \imp A_0;\\
\Rightarrow &:& \Pi a_0:A_0.\, a_0 =_{\star} \rightarrow(a_0)\\
\Leftarrow &:& \Pi a_1:A_1.\, \leftarrow(a_1) =_{\star} a_1\\
%\mbox{reg} &:& A_0 =_{ETT} A_1 \imp \Pi a:A_0.\,(\rightarrow(a)=_{ETT} a \times \leftarrow(a)=_{ETT} a \times \Rightarrow(a) =_{ETT} \Leftarrow(a))\\
\end{array}\\
&&\}\\
\semsort{l}^{2,0} & \defeq & \{\\
& & 
\begin{array}{l}
(((A_{00},=_{00},=_{=_{00}}),(A_{01},=_{01},=_{=_{01}})),(=_{0\star},\leftrightarrow_{0\star},\Leftrightarrow_{0\star})) : \semsort{l}^{1,1};\\
(((A_{10},=_{10},=_{=_{10}}),(A_{11},=_{11},=_{=_{11}})),(=_{1\star},\leftrightarrow_{1\star},\Leftrightarrow_{1\star})) : \semsort{l}^{1,1};\\
(=_{\star 0},\leftrightarrow_{\star 0},\Leftrightarrow_{\star 0});\\
(=_{\star 1},\leftrightarrow_{\star 1},\Leftrightarrow_{\star 1});\\
=_{=_{\star\star}} : \Pi a_{00}:A_{00}.\,\Pi a_{01}:A_{01}.\, a_{00} =_{0\star} a_{01} \imp \Pi a_{00}:A_{00}.\,\Pi a_{11}:A_{11}.\, a_{10} =_{1\star} a_{11} \imp a_{00} =_{\star 0} a_{10} \imp a_{01} =_{\star 1} a_{11} \imp \sort{l};\\
\rightarrow_{\star\diamond} : \Pi a_{00}:A_{00}.\,\Pi a_{01}:A_{01}.\, a_{00} =_{0\star} a_{01} \imp (\rightarrow_{\star 0}(a_{00}) =_{1\star} \rightarrow_{\star 1}(a_{01}))\\
\rightarrow_{\diamond\star} : \Pi a_{00}:A_{00}.\,\Pi a_{10}:A_{10}.\, a_{00} =_{\star 0} a_{10} \imp (\rightarrow_{0\star}(a_{00}) =_{\star 1} \rightarrow_{1 \star}(a_{10}))\\
\leftarrow_{\star\diamond} ...\\
\leftarrow_{\diamond\star} ...\\
\Rightarrow ... \mbox{referring to $=_{00}$ etc}\\
\Leftarrow ...\\
%\mbox{reg} &:& A_0 =_{ETT} A_1 \imp \Pi a:A_0.(\rightarrow(a)=_{ETT} a \times \leftarrow(a)=_{ETT} a \times \Rightarrow(a) =_{ETT} \Leftarrow(a))\\
\end{array}\\
&&\}\\
\end{array}
$$

Such construction will typically be a refinement of the previous
construction of $\partialcubset{l}^n$.
\fi

\iffalse
Thanks to the definition of $\partialcubset{l}^n$, we can define an $\omega$-groupoid
as a stream of equalities in all dimensions together with a property
of transportation between parallel such equalities (i.e. between
equalities connected by a tube).

$$
\begin{array}{llcl}
\groupoid & & \defeq & \Sigma A:\sort{i}.\,\mathsf{isgroupoid}(A)\\
\\
\mathsf{isGroupoid} & A & \defeq & \Sigma =_A:A \imp A \imp \sort{i}.\,\\
& & & \Sigma \mathsf{reflexive} : \Pi a:A.\, a =_A a.\,\\
& & & \groupoidn(0)((\star,A),=_A)\\
\\
\groupoidn & (n:\mathbb{N})~(D:\partialcubset{l}^{n+2}) & : & \sort{i+1}\\
\groupoidn & n~(D,E) & \defeq & \exists \epsilon : (\Pi d_0 : \mybox{l}^{n,n}(D).\,\Pi d_1 : \mybox{l}^{n,n}(D).\, E(d_0) \simeq E(d_1)).\,\groupoidn(n+1)(...\\
A \simeq_{\sort{i}} B & & \defeq &
 \Sigma \{=_{\_}\, : A \rightarrow B \rightarrow \sort{i}.\,\\
& & & \Pi a_0:A.\, \Pi a_1:A.\, \Pi a_\star: a_0 =_A a_1.\, \Pi b_0:B.\, \Pi b_1:B.\, \Pi b_\star:b_0 =_B b_1.\, isGroupoid (a = b)\\
& & & (\Sigma \overrightarrow{\_} : A \rightarrow B.\,\\
& & & \Sigma \Overrightarrow{1ex}{\_} : \Pi a:A.\, a =_{\_} \overrightarrow{\_}(a).\,\\
& & & \Sigma \overrightarrow{\mathsf{coe}} : \Pi a:A.\,\Pi b:B.\,\, a =_{\_} b \rightarrow \overrightarrow{\_}(a) =_B b.\,\\
& & & \Pi a:A.\,\Pi b:B.\,\, a =_{\_} b \rightarrow \overrightarrow{\_}(a) =_ b.\,\\
& & & \Sigma \overleftarrow{\_} : B \rightarrow A.\,\\
& & & \Sigma \Overleftarrow{1ex}{\_} : \Pi b:B.\, \overleftarrow{\_}(b) =_{\_} b; \\
& & & \Sigma \overleftarrow{\mathsf{coe}} : \Pi a:A.\,\Pi b:B.\, a =_{\_} b \rightarrow a =_B \overleftarrow{\_}(a).\,\\
& & \Sigma \overrightarrow{\mathsf{coe}} : \Pi a:A.\,\Pi b:B.\, a =_{\_} b \rightarrow \overrightarrow{\_}(a) =_B b.\\
\\
\end{array}
$$

\fi

\iffalse
To each type $A$ is associated a structure of $\omega$-groupoid which
we define as follows:

Each type $A$ comes with:
\begin{itemize}
\item an equality $=^n_A$ between $n$-cubes of this type
\item a reflexity proof $\reflterm{n}{a} : a =^n_A a$ for any $n$-cube
  $a$ in $A$
\item a connection $\nwconn{n}{p} : [p,p] =^{n+1}_A [\refltermn{n}{A}{a_1},\refltermn{n}{A}{a_1}]$ for any $n+1$-cube $p:a_0 =^n_A a_1$ over $A$
\item a connection $\seconn{n}{p} : [\refltermn{n}{A}{a_0},\refltermn{n}{A}{a_0}] =^{n+1}_A [p,p]$ for any $n+1$-cube $p:a_0 =^n_A a_1$ over $A$
\item ...
\end{itemize}

We define the following ``record'' type:
$$
\begin{array}{lcl}
  A \simeq B & \defeq & \{=_{\_}\, : A \rightarrow B \rightarrow \sort;\\
& & \overrightarrow{\_} : A \rightarrow B; \overleftarrow{\_} : B \rightarrow A; \\
& & \Overrightarrow{1ex}{\_} : \Pi a:A.\, a =_{\_} \overrightarrow{\_}(a); \Overleftarrow{1ex}{\_} : \Pi b:B.\, \overleftarrow{\_}(b) =_{\_} b; \\
& &  : \Pi a:A.\,\Pi b:B.\, a =_{\_} b \rightarrow \overrightarrow{\_}(a) =_B b;\\
& & ...\}
\end{array}
$$
\fi
\iffalse %%%
\subsection{Reflexivities}

We need to provide reflexivities to turn $n$-cubes into
$(n+1)$-cubes. For $n$-cubes of types and equivalences, this means
being able to prove the equivalence $A \simeq A$ from $A$ being a
cubical $\omega$-groupoid, to prove the equality $\epsilon = \epsilon$
for $\epsilon$ an arbitrary general equivalence of level $n$.

For the former, this shall come by taking the identity for
$\rightarrow$, $\leftarrow$, $\overrightarrow{\mathsf{coe}}$ and
$\overleftarrow{\mathsf{coe}}$ and by taking the reflexivity and
connections coming with the definition of cubical $\omega$-groupoid.

For the latter, we shall probably need an extra property to
$\rightarrow$, $\leftarrow$, $\overrightarrow{\mathsf{coe}}$ and
$\overleftarrow{\mathsf{coe}}$, namely that they respect equality.

For an heterogeneous $n$-cubes over some $n$-cube of types and
relations, this shall come from the property that the relations are
themselves cubical $\omega$-groupoid and thus have reflexivities.

For the latter, this shall come from the structure of types.  For type
variables, it shall come from the requirement that such type variable
are cubical groupoids in the definition of $n$-cubes. It shall then be
proved also that the type constructors ($\Pi$, $\Sigma$, $\mathbb{N}$,
...) preserve the property of being a cubical $\omega$-groupoid and
the property of being equivalent.

\subsection{Dependent sums}

\subsection{Dependent products}

We believe that it is enough to interpret a dependent product in
dimension $n$ as its usual interpretation as an $n$-cube of dependent
products over $n$-cubes, together, in each of the $3^n$ $p$-subcube of
this cube, of a copy of the precomputation of the $p$ possible
diagonals in this subcube.

For dependent products to propagate reflexivities, the assumption that
functions preserve equality shall have to be enforced.

\subsection{Structure of the cubes of derivations in the target}

For $\Gamma$ a typing context with $n$ declarations of axes, the $3^n$
derivations in the target constituting the interpretation of a source
derivation shall be indexed by a substitution where each variable of
axis can take three values: $0$ for the left point, $1$ for the right
point, and $\star$ for the connecting line (i.e., these three values
are the defining components of an interval over connected endpoints
$0$ and $1$).

In this very same substitution, ordinary variables will be interpreted
as internal $p$-cubes if the variable has $p$ variables of axes before
it at the time it is declared.

Substitutions of typing contexts of the source can thus be described
by the following grammar (we use $\sigma$ to range over such
substitution):
$$
\begin{array}{lcl}
r & ::= & 0 ~|~ 1 ~|~ \star\\
\sigma, \tau & ::= & \emptysigma ~|~ \sigma, a:=t:A ~|~ \sigma, i:=r\\
\end{array}
$$

We define a notion of valid substitution $\sigma$ of source type
$\Gamma$ in a well-formed ETT typing context $\Delta$ as follows:
$$
\seq{}
    {\Delta \vDash \emptysigma : \emptyctx}
\qquad
\seq{\Delta \vDash \sigma : \Gamma
\qquad \Gamma \vdash A : \sort{l} \qquad \Delta \vdash_{ECC} t : \semnew{\sigma}{A}
}
    {\Delta \vDash (\sigma,a:=t:A) : (\Gamma,a:A)}
\qquad
\seq{\Delta \vDash \sigma : \Gamma}
    {\Delta \vDash (\sigma,i:=r) : (\Gamma,i)}
$$

%TODO: deal with the need for the translation to know the type (in
%practice, the translation has to be done on derivations rather than on
%terms).

Then, writing $\semnew{\sigma}{t}$ for the ETT derivation component
over $\sigma$ of a derivation of $\Gamma \vdash t : A$ such that
$\Delta \vDash \Gamma$, we expect the following invariant:

\begin{lemma}
$\Gamma \vdash t : A$ and $\Delta \vDash \sigma : \Gamma$ implies
$\Delta \vdash_{ECC} \semnew{\sigma}{t} : \applytype{\sigma}{\emptysigma}{\semnew{\sigma}{A}}{t}$
\end{lemma}
where $\applytype{\sigma}{\emptysigma}{\semnew{\sigma}{B}}{t}$ builds
the equality type representing in ETT the border of the
$\sigma$-component of the interpretation of a proof $b$ of type $B$ (TODO: rewrite $\applytype{}{}{}{}$ in terms of $\myheteroboxtype{l}$ and $\myheterobox{l}$):

$$
\begin{array}{lcll}
\applytype{\emptysigma}{\tau}{B}{b} & \defeq & B\\
\applytype{\sigma,a:=t:A}{\tau}{B}{b} & \defeq & \applytype{\sigma}{a:=tA,\tau}{B}{b}\\
\applytype{\sigma,i:=0}{\tau}{B}{b} & \defeq & \applytype{\sigma}{i:=0,\tau}{B}{b}\\
\applytype{\sigma,i:=1}{\tau}{B}{b} & \defeq & \applytype{\sigma}{i:=1,\tau}{B}{b}\\
%\applytype{\sigma,i:=j}{\tau}{B}{b} & \defeq & \applytype{\sigma}{i:=j,\tau}{B}{b}\\
\applytype{\sigma,i:=\star}{\tau}{B}{b} & \defeq & \applytype{\sigma}{i:=\star,\tau}{(\undertau{\sigma,i=0}{\shrink{0}{(t\mapsto t.0)}{\tau}}{b}) =_B (\undertau{\sigma,i=1}{\shrink{0}{(t\mapsto t.1)}{\tau}}{b})}{b}
\end{array}
$$
where, for $\sigma,i:=r,\tau$ an initial substitution, and $r$ being
$0$ or $1$, $\undertau{\sigma,i:=r}{\tau}{b}$ computes the internal
representation of the face $r$ of the interpretation of the component
$\sigma,i:=\star,\tau$ of $b$.

$$
\begin{array}{lcll}
\undertau{\sigma}{\emptysigma}{b} & \defeq & \semnew{\sigma}{b} \\
\undertau{\sigma}{a:=t,\tau}{b} & \defeq & \undertau{\sigma,a:=t}{\tau}{b}\\
\undertau{\sigma}{i:=0,\tau}{b} & \defeq & \undertau{\sigma,i:=0}{\tau}{b} \\
\undertau{\sigma}{i:=1,\tau}{b} & \defeq & \undertau{\sigma,i:=1}{\tau}{b} \\
%\undertau{\sigma}{i:=j,\tau}{b} & \defeq & \undertau{\sigma,i:=j}{\tau}{b} \\
\undertau{\sigma}{i:=\star,\tau}{b} & \defeq & (\undertau{\sigma,i:=0}{\tau}{b},\undertau{\sigma,i:=1}{\tau}{b},\undertau{\sigma,i:=\star}{\tau}{b})\\
\end{array}
$$

$$
\begin{array}{lcll}
\shrink{k}{f}{\emptysigma} & \defeq & \emptysigma\\
\shrink{k}{f}{a:=t:A,\sigma} & \defeq & (a:=\under{k}{f}{a}:A),\shrink{k}{f}{\sigma}\\
\shrink{k}{f}{i:=\star,\sigma} & \defeq & i:=\star,\shrink{k+1}{f}{\sigma}\\
\end{array}
$$

For instance, if $i,j,k,a:A \vdash b(a):B$ of dimension 3 and $\sigma$ is
$i:=\star,j:=0,k:=\star,a:=t:A$ which denotes the 2-dimensional face numbered
$0$ in axis $j$ of the expected $3$-cube, then
$\applytype{\sigma}{\emptysigma}{B}{b}$ builds (dropping the names of
axes and listing their value in sequence):
$$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!(\semnew{000a_{00}}{b},\semnew{001a_{01}}{b},\semnew{00\star (a_{00},a_{01},a_{0\star})}{b})
 =_{(\semnew{000 a_{00}}{b},\semnew{i:=100a_{10}}{b},\semnew{\star00a_{0}}{b})
  =_{\semnew{\star0\star a}{B}} (\semnew{001a_{01}}{b},\semnew{101}{b},\semnew{\star01a_{1}}{b})}
(\semnew{100a_{10}}{b},\semnew{101a_{11}}{b},\semnew{10\star (a_{10},a_{11},a_{1\star})}{b})$$
\fi %%%
\iffalse
\subsection{A ranger}

$$
\begin{array}{lcll}
\reflsort{0} & \defeq & \sort{}\\
\reflsort{n+1} & \defeq & (\lambda A_0:\semsort{n}.\lambda A_1:\semsort{n}.A_0 \simeq A_1,\lambda A:\semsort{n}.A,\lambda A:\semsort{n}.\reflsort{n},...,...,...,...,...,...))\\
\\
%\simeq_0 & \defeq & \simeq\\
%\simeq_{n+1} & \defeq & \sort{}\\
%\\
\refltypen{n}{(A:\sort{})} & : & A \simeq A\\
\refltypen{n}{A} & \defeq & (\lambda a_0:A.\lambda a_1:A.a_0 =_A a_1,\lambda a_0:A.a_0,\lambda a_0:A.\refltermn{n}{A}{a_0},...,...,...,...,...,...))\\
\\
\# \emptysigma & \defeq & 0\\
\# (\sigma,a:A) & \defeq & \#\sigma\\
\# (\sigma,i:=0) & \defeq & (\#\sigma)\\
\# (\sigma,i:=1) & \defeq & (\#\sigma)\\
\# (\sigma,i:=\star) & \defeq & (\#\sigma) + 1\\
\\
\semctx{\sigma}{i, \Delta} & \defeq &
  \semctx{\sigma, i}{\Delta} \\
\semctx{\sigma}{a:A, \Delta} & \defeq &
  a : \semnew{\sigma}{A}, \semctx{\sigma, a:A}{\Delta} \\
\\
\elt{0}{B} & \defeq & B\\
\elt{n+1}{(B_0,B_1,B_\star)} & \defeq &
  \Sigma b_0:\elt{n}{B_0}.
  \Sigma b_1:\elt{n}{B_1}.
  b_0 =_{B_\star} b_1\\
\end{array}
$$
\fi
\iffalse %%%
\subsection{Core of the translation}

Translation of types (TODO: $\elt{}{}$ should just be the $\myheterobox{l}$ function).

$$
\begin{array}{lcll}
\semtypenew{\sigma}{A} & \defeq & \elt{\#\sigma}{\semnew{\sigma}{A}}\\
\elt{0}{B} & \defeq & B\\
\elt{n+1}{(B_0,B_1,B_\star)} & \defeq & 
  \Sigma b_0:\elt{n}{B_0}.
  \Sigma b_1:\elt{n}{B_1}.
  b_0 =_{B_\star} b_1\\
\\
\# \emptysigma & \defeq & 0\\
\# (\sigma,a:A) & \defeq & \#\sigma\\
\# (\sigma,i:=0) & \defeq & (\#\sigma)\\
\# (\sigma,i:=1) & \defeq & (\#\sigma)\\
\# (\sigma,i:=\star) & \defeq & (\#\sigma) + 1\\
\end{array}
$$

\noindent Translation of terms (sketch):

$$
\begin{array}{lcll}
\semnew{\sigma}{a} & \defeq & \access{\sigma}{a}\\
\semnew{\sigma}{\lambda i.t} & \defeq & \semnew{\sigma,i:=\star}{t}\\
\semnew{\sigma}{t \, i} & \defeq & \diag{i}{\semnew{\sigma}{t}}\\
\semnew{\sigma}{t =_\epsilon u} & \defeq & \semnew{\sigma}{t} =_{\semnew{\sigma}{\epsilon}} \semnew{\sigma}{u}\\
%\semnew{\sigma}{\mktuplenew{a_0:A_0}{a_1:A_1}{\textgoth{c}}{R}{\mktuplein{f^\rightarrow}{p^\rightarrow}{r^\rightarrow}{\alpha^\rightarrow}}{\mktuplein{f^\leftarrow}{p^\leftarrow}{r^\leftarrow}{\alpha^\leftarrow}}} & \defeq & (\semnew{\sigma,a_0:A_0,a_1:A_1}{R},\semnew{\sigma,a_0:A_0}{f^\rightarrow},...,...,...,\semnew{\sigma,a_1:A_1}{f^\leftarrow},...,...,...)\\
\semnew{\sigma}{\sort{l}} & \defeq & \semsort{l}^{\#\sigma,0}\\
\semnew{\sigma}{(t,u)} & \defeq & (\semnew{\sigma}{t},\semnew{\sigma}{u})\\
\semnew{\sigma}{\pi_1(t)} & \defeq & \pi_1(\semnew{\sigma}{t})\\
\semnew{\sigma}{\pi_2(t)} & \defeq & \pi_2(\semnew{\sigma}{t})\\
\semnew{\sigma}{\Sigma a:A.B} & \defeq & \Sigma a:\semtypenew{\sigma}{A}.\semtypenew{\sigma,a:=a:A}{B}\\
\semnew{\sigma}{\lambda a:A.t} & \defeq & \\%\semlam{\#\sigma,0}{\sigma}{a \mapsto a}{\semnew{\sigma}{A}}{t} \\
\semnew{\sigma}{t\,u} & \defeq & \\%\semapp{\#\sigma,0}{\semnew{\sigma}{t}}{\semnew{\sigma}{u}} \\
\semnew{\sigma}{\Pi a:A.B} & \defeq & \\%\semprod{\#\sigma,0}{\sigma}{a \mapsto a}{\semnew{\sigma}{A}}{B}\\
\\
\access{\sigma, i:=0}{a} & \defeq & \access{\sigma}{a} \\
\access{\sigma, i:=1}{a} & \defeq & \access{\sigma}{a} \\
%\access{\sigma, i:=j}{a} & \defeq & \access{\sigma}{a} \\
\access{\sigma, i:=\star}{a} & \defeq & (\refltermn{}{A}{t}:A) \qquad & \mbox{if $\access{\sigma}{a}$ is $t:A$}\\
\access{\sigma, a:=t:A}{a} & \defeq & (t:A) \\
\access{\sigma, b:=u:B}{a} & \defeq & \access{\sigma}{a} & a \neq b\\
\end{array}
$$

Note that the interpretation of an explicit proof of equivalence
derives from its definition as a combination of $\Sigma$ and $\Pi$
types. Similarly, the clause for $t =_\epsilon u$ is actually derivable
as a projection from the $\Sigma$-type used to define an equivalence.

The reflexivity $\refltermn{}{}{t}$ remains to be made more precise.

\subsection{``Syntactic'' version of the translation}

We believe that it would be possible to define a variant of the
translation which maps a source derivation into a single derivation in
the target by combining the $3^n$ judgements constituting the
interpretation into an iterated $\Sigma$-type collecting all
judgements into ones. This time, each $n$-cube shall have to
destructed and constructed so that each constructor and eliminator of
the source language can be applied to each component of the tuple.
\fi %%%
\iffalse
$$
\begin{array}{lcl}
\sigma & ::= & \emptysigma ~|~ \sigma, i ~|~ \sigma, a:=t\\
\end{array}
$$

$$
\begin{array}{lcl}
A \simeq B & \defeq & \Sigma =\, : A \rightarrow B \rightarrow \sort. \Sigma ...\\
\end{array}
$$

A few expected invariants:

$$
\seq{\semctx{\emptysigma}{\Gamma} \vdash' B : \semnew{|\Gamma|}{\sort{}}}
    {\semctx{\emptysigma}{\Gamma} \vdash' \elt{|\Gamma|}{B} : \sort{}}
$$

$$
\seq{\Gamma \vdash t : A}
    {\semctx{\emptysigma}{\Gamma} \vdash' \semnew{|\Gamma|}{t} : \elt{|\Gamma|}{\semnew{|\Gamma|}{A}}}
$$

$$
\begin{array}{lcll}
\under{0}{f}{t} & \defeq & f\,t\\
\under{n+1}{f}{t} & \defeq & (\under{n}{f}{\pi_0\,t}, \under{n}{f}{\pi_1\,t}, \under{n}{f}{\pi_\star\,t})\\
\\
|\emptyctx|  & \defeq & \emptysigma\\
|\Gamma, i|  & \defeq & |\Gamma|, i\\
|\Gamma, a|  & \defeq & |\Gamma|, a:=a\\
\\
\# \emptysigma & \defeq & 0\\
\# (\sigma,a:=t) & \defeq & \#\sigma\\
\# (\sigma,i) & \defeq & (\#\sigma) + 1\\
\\
\semctx{\sigma}{i, \Delta} & \defeq &
  \semctx{\sigma, i}{\Delta} \\
\semctx{\sigma}{a:A, \Delta} & \defeq &
  a : \semnew{\sigma}{A}, \semctx{\sigma, a:A}{\Delta} \\
\\
\semtypenew{\sigma}{A} & \defeq & \elt{\#\sigma}{\semnew{\sigma}{A}}\\
\\
\semnew{\sigma}{a} & \defeq & \access{\sigma}{a}\\
\semnew{\sigma}{\lambda i.t} & \defeq & \semnew{\sigma,i}{t}\\
\semnew{\sigma}{t \, i} & \defeq & \diag{i}{\semnew{\sigma}{t}}\\
\semnew{\sigma}{t =_\epsilon u} & \defeq & \semnew{\sigma}{t} =_{\semnew{\sigma}{\epsilon}} \semnew{\sigma}{u}\\
\semnew{\sigma}{\mktuplenew{a_0:A_0}{a_1:A_1}{\textgoth{c}}{R}{\mktuplein{f^\rightarrow}{p^\rightarrow}{r^\rightarrow}{\alpha^\rightarrow}}{\mktuplein{f^\leftarrow}{p^\leftarrow}{r^\leftarrow}{\alpha^\leftarrow}}} & \defeq & (\semnew{\sigma,a_0:A_0,a_1:A_1}{R},\semnew{\sigma,a_0:A_0}{f^\rightarrow},...,...,...,\semnew{\sigma,a_1:A_1}{f^\leftarrow},...,...,...)\\
\semnew{\sigma}{\sort{l}} & \defeq & \semsort{l}^{\#\sigma,0}\\
%\semnew{\sigma}{\lambda a:A.t} & \defeq & \semlam{\#\sigma,0}{\sigma}{a \mapsto a}{\semnew{\sigma}{A}}{t} \\
%\semnew{\sigma}{t\,u} & \defeq & \semapp{\#\sigma,0}{\semnew{\sigma}{t}}{\semnew{\sigma}{u}} \\
%\semnew{\sigma}{\Pi a:A.B} & \defeq & \semprod{\#\sigma,0}{\sigma}{a \mapsto a}{\semnew{\sigma}{A}}{B}\\
\\
\access{\sigma, i}{a} & \defeq & \lift{(\access{\sigma}{a})} \\
\access{\sigma, a:=t}{a} & \defeq & t \\
\access{\sigma, b:=t}{a} & \defeq &
  \access{\sigma}{a} & a \neq b\\
\end{array}
$$
$$
\begin{array}{lcll}
\semsort{0} & \defeq & \sort{}\\
\semsort{n+1} & \defeq & (\semsort{n},\semsort{n},(...,...,...,...,...,...,...,...))\\
\\
\multicolumn{4}{l}{\mbox{Insert the ``coe'' between lifted and non-lifted expressions, check...}}\\
\semlam{0,k}{\sigma}{f}{A}{t} & \defeq & \lambda a:\elt{k}{A}.\semnew{\sigma,(a:=f a)}{t}\\
\semlam{n+1,k}{\sigma}{f}{A}{t} & \defeq & \left(
  \begin{array}{l}
  \semlam{n,k}{\sigma}{(\under{k}{\liftlr{}}{})\circ f}{(\under{k}{\pi_0}{A})}{t}\\
  \semlam{n,k}{\sigma}{(\under{k}{\liftrl{}}{})\circ f}{(\under{k}{\pi_1}{A})}{t}\\
  \semlam{n,k+1}{\sigma}{f}{A}{t}\\
  \end{array}\right)\\
\\
\semapp{0,k}{t}{u} & \defeq & t\,u\\
\semapp{n+1,k}{t}{u} & \defeq & \left(
  \begin{array}{l}
  \semapp{n,k}{(\pi_0\,t)}{(\under{k}{\pi_0}{u})}\\
  \semapp{n,k}{(\pi_1\,t)}{(\under{k}{\pi_1}{u})}\\
  \semapp{n,k+1}{(\pi_\star\,t)}{u}\\
  \end{array}\right)\\
\\
\multicolumn{4}{l}{\mbox{First approximation}}\\
\semprod{0,k}{\sigma}{f}{A}{B} & \defeq & \Pi a:\elt{k}{A}.\semnew{\sigma,(a:=f a)}{B}\\
\semprod{n+1,k}{\sigma}{f}{A}{B} & \defeq & \left(
  \begin{array}{l}
  \semprod{n,k}{\sigma}{(\under{k}{\liftlr{}}{})\circ f}{(\under{k}{\pi_0}{A})}{t}\\
  \semprod{n,k}{\sigma}{(\under{k}{\liftrl{}}{})\circ f}{(\under{k}{\pi_1}{A})}{t}\\
  (\lambda f_0:\semprod{n,k}{\sigma}{(\under{k}{\liftlr{}}{})\circ f}{(\under{k}{\pi_0}{A})}{t}.\\
   ~\lambda f_1:\semprod{n,k}{\sigma}{(\under{k}{\liftlr{}}{})\circ f}{(\under{k}{\pi_1}{A})}{t}.\\
   ~\Pi a:\semnew{\sigma}{A}.f_0\,(\pi_0\, a) =_{\semnew{\sigma,(a:=a)}{B}} f_1\, (\pi_1\, a),\\
   ~...,...,...,...,...,...,...,...)
  \end{array}\right)\\
\\
\lift{t} & \defeq & (t,t,\refl{t})\\
\liftlr{t} & \defeq & 
     (t,
      \overrightarrow{\elt{\sigma}{\pi_\star \semnew{\sigma}{A}}}(t),
      \overrightarrow{\overrightarrow{\elt{\sigma}{\pi_\star \semnew{\sigma}{A}}}}(t))\\
\liftrl{t} & \defeq & 
     (\overleftarrow{\elt{\sigma}{\pi_\star \semnew{\sigma}{A}}}(t),
      t,
      \overleftarrow{\overleftarrow{\elt{\sigma}{\pi_\star \semnew{\sigma}{A}}}}(t))\\
\end{array}
$$

Variante sans projection de variables

$$
\begin{array}{lcl}
\semlambis{n+1,k}{A}{t} & \defeq & \left(
  \begin{array}{l}
  \semlambis{n,k}{(\under{k}{\liftlr{}}{})\circ f}{(\under{k}{\pi_0}{A})}{t}\\
  \semlambis{n,k}{(\under{k}{\liftrl{}}{})\circ f}{(\under{k}{\pi_1}{A})}{t}\\
  \semlambis{n,k+1}{A}{\pi_\star\, t}\\
  \end{array}\right)\\
\\
\semapp{0,k}{t}{u} & \defeq & t\,u\\
\semapp{n+1,k}{t}{u} & \defeq & \left(
  \begin{array}{l}
  \semapp{n,k}{(\pi_0\,t)}{(\under{k}{\pi_0}{u})}\\
  \semapp{n,k}{(\pi_1\,t)}{(\under{k}{\pi_1}{u})}\\
  \semapp{n,k+1}{(\pi_\star\,t)}{u}\\
  \end{array}\right)\\
\\
\semprod{0,k}{\sigma}{f}{A}{B} & \defeq & \Pi a:\elt{k}{A}.\semnew{\sigma,(a:=f a)}{B}\\
\semprod{n+1,k}{\sigma}{f}{A}{B} & \defeq & \left(
  \begin{array}{l}
  \semprod{n,k}{\sigma}{(\under{k}{\liftlr{}}{})\circ f}{(\under{k}{\pi_0}{A})}{t}\\
  \semprod{n,k}{\sigma}{(\under{k}{\liftrl{}}{})\circ f}{(\under{k}{\pi_1}{A})}{t}\\
  (\lambda f_0:\semprod{n,k}{\sigma}{(\under{k}{\liftlr{}}{})\circ f}{(\under{k}{\pi_0}{A})}{t}.\\
   ~\lambda f_1:\semprod{n,k}{\sigma}{(\under{k}{\liftlr{}}{})\circ f}{(\under{k}{\pi_1}{A})}{t}.\\
   ~\Pi a:\semnew{\sigma}{A}.f_0\,(\pi_0\, a) =_{\semnew{\sigma,(a:=a)}{B}} f_1\, (\pi_1\, a),\\
   ~...,...,...,...,...,...,...,...)
  \end{array}\right)\\
\end{array}
$$

OBSOLÈTE

$$
\begin{array}{lcl}
k & ::= & 0 ~|~ 1 ~|~ \star \\
\tau & ::= & \emptyctx ~|~ \tau, i:=k ~|~ \tau, a\\
\end{array}
$$

$$
\begin{array}{lcl}
\incrstep{i}{\tau}{F} & \defeq &
  (F{((i:=0,\tau)},F{(i:=1,\tau)},F{(i:=\star,\tau)})\\
\\
\distrstep{i}{\tau}{F} & \defeq &
  (F{(i:=0)\tau},F{(i:=1)\tau},F{(i:=\star)\tau})\\
\\
  \incrstep{i}{\tau}{(\tau \mapsto \itsemtype{\Gamma}{\uparrow\sigma}{\tau}{A})}\\
\itsemtype{\Gamma,a:A}{\sigma}{\tau}{A} & \defeq &
  \itsemtype{\Gamma}{a:=a,\sigma}{\tau}{A}\\
\itsemtype{\emptyctx}{\sigma}{\tau}{A} & \defeq &
  \semtype{\sigma}{\tau}{A}\\
\\
\itsemtype{\Gamma,i}{\sigma}{\tau}{A} & \defeq &
  \incrstep{i}{\tau}{(\tau \mapsto \itsemtype{\Gamma}{\uparrow\sigma}{\tau}{A})}\\
\itsemtype{\Gamma,a:A}{\sigma}{\tau}{A} & \defeq &
  \itsemtype{\Gamma}{a:=a,\sigma}{\tau}{A}\\
\itsemtype{\emptyctx}{\sigma}{\tau}{A} & \defeq &
  \semtype{\sigma}{\tau}{A}\\
\\
\itsemterm{\Gamma,i}{\sigma}{\tau}{t:A} & \defeq &
  \incrstep{i}{\tau}{(\tau \mapsto \itsemterm{\Gamma}{\uparrow\sigma}{\tau}{t:A})}\\
\itsemterm{\Gamma,a:A}{\sigma}{\tau}{t:A} & \defeq &
  \itsemterm{\Gamma}{a:=a,\sigma}{\tau}{t:A}\\
\itsemterm{\emptyctx}{\sigma}{\tau}{A} & \defeq &
  \semterm{\sigma}{\tau}{A}\\
\\
\semtype{\sigma}{\emptyctx}{\sort{}} & \defeq &
  \sort{}\\
\\
\semtype{\sigma}{\tau,i=0}{\sort{}} & \defeq &
  \sort{}\\
\semtype{\sigma}{\tau,i=1}{\sort{}} & \defeq &
  \sort{}\\
\semtype{\sigma}{\tau,i=\star}{\sort{}} & \defeq &
  (\lambda A_0:\sort{}.\lambda A_1:\sort{}.A_0 \simeq A_1, ..., ..., ..., ..., ..., ..., ..., ...)\\
\\
\semtype{\sigma}{\emptyctx}{\Pi a:A.B} & \defeq &
  \Pi a:\semtype{\sigma}{\emptyctx}{A}.\semtype{\sigma,a:=a}{\emptyctx}{B}\\
\\
\semtype{\sigma}{\tau,i:=0}{\Pi a:A.B} & \defeq &
  \Pi a_0:\semtype{\sigma}{\tau,i:=0}{A}.
  \semtype{\sigma,a:=
     (a_0,
      \overrightarrow{\semtype{\sigma}{\tau,i=\star}{A}}(a_0),
      \overrightarrow{\overrightarrow{\semtype{\sigma}{\tau,i=\star}{A}}}(a_0))}
     {\tau,i:=0}{B}\\
\semtype{\sigma}{\tau,i:=1}{\Pi a:A.B} & \defeq &
  \Pi a_1:\semtype{\sigma}{\tau,i:=1}{A}.
  \semtype{\sigma,a:=
     (\overleftarrow{\semtype{\sigma}{\tau,i=\star}{A}}(a_1),
      a_1,
      \overleftarrow{\overleftarrow{\semtype{\sigma}{\tau,i=\star}{A}}}(a_1))}
     {\tau,i:=1}{B}\\
\semtype{\sigma}{\tau,i:=\star}{\Pi a:A.B} & \defeq &
  (\lambda f_0:\Pi a_0:\semtype{\sigma}{\tau,i:=0}{A}.
  \semtype{\sigma,a:=
     (a_0,
      \overrightarrow{\semtype{\sigma}{\tau,i=\star}{A}}(a_0),
      \overrightarrow{\overrightarrow{\semtype{\sigma}{\tau,i=\star}{A}}}(a_0))}
     {\tau,i:=0}{B}.\\
& &  \lambda f_1:\Pi a_1:\semtype{\sigma}{\tau,i:=1}{A}.\semtype{\sigma,a:=
     (\overleftarrow{\semtype{\sigma}{\tau,i=\star}{A}}(a_1),
      a_1,
      \overleftarrow{\overleftarrow{\semtype{\sigma}{\tau,i=\star}{A}}}(a_1))}
     {\tau,i:=1}{B}.\\
& &  \Pi a_0:\phi(\incrstep{i}{\tau}{(\tau \mapsto \semtype{\sigma}{\tau}{A})}).
  \Pi a_1:\phi(\incrstep{i}{\tau}{(\tau \mapsto \semtype{\sigma}{\tau}{A})}).
  f_0\, a_0 =_{\semtype{\sigma,a:=a}{\tau,i:=\star}{B}} f_1\, a_1,\\
& &
  ..., ...,   ..., ...,   ..., ...,   ..., ...)\\
\\
\semterm{\sigma}{\tau,i:=0}{\lambda a:A.t} & \defeq &
  \lambda a_0:\semtype{\sigma}{\tau,i:=0}{A}.
  \semterm{\sigma,a:=
     (a_0,
      \overrightarrow{\semtype{\sigma}{\tau,i=\star}{A}}(a_0),
      \overrightarrow{\overrightarrow{\semtype{\sigma}{\tau,i=\star}{A}}}(a_0))}
     {\tau,i:=0}{t}\\
\semterm{\sigma}{\tau,i:=1}{\lambda a:A.t} & \defeq &
  \lambda a_1:\semtype{\sigma}{\tau,i:=1}{A}.
  \semterm{\sigma,a:=
     (a_1,
      \overleftarrow{\semtype{\sigma}{\tau,i=\star}{A}}(a_1),
      \overleftarrow{\overleftarrow{\semtype{\sigma}{\tau,i=\star}{A}}}(a_1))}
     {\tau,i:=1}{t}\\
\semterm{\sigma}{\tau,i:=\star}{\lambda a:A.t} & \defeq &
  \lambda a:\phi(\incrstep{i}{\tau}{(\tau \mapsto \semtype{\sigma}{\tau}{A})}).
  \semterm{\sigma,a:=a}{\tau,i:=\star}{t}\\
\\
\semterm{\sigma}{\tau,i:=0}{t\,u} & \defeq &
  \semterm{\sigma}{\tau,i:=0}{t}\,\semterm{\sigma}{\tau,i:=0}{u}\\
\semterm{\sigma}{\tau,i:=1}{t\,u} & \defeq &
  \semterm{\sigma}{\tau,i:=1}{t}\,\semterm{\sigma}{\tau,i:=1}{u}\\
\semterm{\sigma}{\tau,i:=\star}{t\,u} & \defeq &
  \semterm{\sigma}{\tau,i:=\star}{t}\,\incrstep{i}{\tau}{\tau \mapsto \semterm{\sigma}{\tau}{u}}\\
\\
%\semtype{\sigma}{\tau}{X} & \defeq &
%  \proj{\tau}{\sigma(X)} \\
%\\
%\semterm{\sigma}{\tau}{a} & \defeq &
%  \proj{\tau}{\sigma(a)} \\
%\\
\end{array}
$$
\fi

\bibliographystyle{plain}
\bibliography{biblio-en,extra}

\end{document}

((=₀⋆, ...) ≃₂ (=₁⋆, ...)) ≜ λ(=⋆₀, ...).λ(=⋆₁, ...).
∀a₀₀a₀₁a₁₀a₁₁.... -> Type

((Type,Type,(≃,λx.x,...)),(Type,Type,(≃,λx.x,...)),((≃,λx.x,...),(≃,λx.x,...),(≃_2,λx.x,...))

((Πa:A₀₀.B₀₀),(Πa:A₀₁.B₀₁),(≃,λx.x,...)),(Type,Type,(≃,λx.x,...)),((≃,λx.x,...),(≃,λx.x,...),(≃_2,λx.x,...))

(Πa:A₀₀.B₀₀),(Πa:A₀₁.B₀₁),(≃,λx.x,...)),(Type,Type,(≃,λx.x,...)),((≃,λx.x,...),(≃,λx.x,...),(≃_2,λx.x,...))

          A₀                    A₁                              A⋆
/ A₀₀               \ / A₁₀               \ / =_A⋆₀ : A₀.₀→A₁.₀→U                     \
| A₀₁               | | A₁₁               | | =_A⋆₁ : A₀.₁→A₁.₁→U                     |
\ =_A₀⋆ : A₀₀→A₀₁→U / \ =_A₁⋆ : A₁₀→A₁₁→U / \ =_A⋆⋆ : Πa₀:ϕ(A₀).Πa₁:ϕ(A₁)             /
                                              a₀.₀ =_A⋆₀ a₁.₀ → a₀.₁ =_A⋆₁ a₁.₁ → U

Structure d'un carré de type A (qui lui-même est un carré) :

Les indices sur les variables font partie du nom. Les indices sur les
termes ou types sont des suites de projection.

t  ≜ (t₀,t₁,t⋆) : {a₀ : {a₀₀ : A₀₀;           a₀₁ : A₀₁;           a₀⋆ : a₀₀ =_A₀⋆ a₀₁};
                   a₁ : {a₁₀ : A₁₀;           a₁₁ : A₁₁;           a₁⋆ : a₁₀ =_A₁⋆ a₁₁};
                   a⋆ : {a⋆₀ : t₀₀ =_A⋆₀ t₁₀; a⋆₁ : t₁₀ =_A⋆₁ t₁₁; a⋆⋆ : a⋆₀ =_A⋆⋆ a⋆₁}}
t₀ ≜ (t₀₀,t₀₁,t₀⋆) : {a₀₀ : A₀₀;           a₀₁ : A₀₁;           a₀⋆ : a₀₀ =_A₀⋆ a₀₁}
t₁ ≜ (t₁₀,t₁₁,t₁⋆) : {a₁₀ : A₁₀;           a₁₁ : A₁₁;           a₁⋆ : a₁₀ =_A₁⋆ a₁₁}
t⋆ ≜ (t⋆₀,t⋆₁,t⋆⋆) : {a⋆₀ : t₀₀ =_A⋆₀ t₁₀; a⋆₁ : t₁₀ =_A⋆₁ t₁₁; a⋆⋆ : a⋆₀ =_A⋆⋆ a⋆₁}
                     ≡ t₀ =_ {a⋆₀:A⋆₀; a⋆₁:A⋆₁; a⋆⋆:a⋆₀ =_A⋆⋆ a⋆₁} t₁

                                 t : A
    /---------------------------------------------------------------------\
        t₀ : A₀                 t₁ : A₁                 t⋆ : t₀ =_A⋆ t₁
/ t₀₀ : A₀₀           \ / t₁₀ : A₁₀           \ / t⋆₀ : t₀₀ =_A⋆₀ t₁₀        \
| t₀₁ : A₀₁           | | t₁₁ : A₁₁           | | t⋆₁ : t₀₁ =_A⋆₁ t₁₁        |
\ t₀⋆ : t₀₀ =_A₀⋆ t₀₁ / \ t₁⋆ : t₁₀ =_A₁⋆ t₁₁ / \ t⋆⋆ : t⋆₀ =_A⋆⋆(t₀,t₁) t⋆₁ /

       t₀⋆
   t₀₀ ---> t₀₁
    |        |
t⋆₀ |  t⋆⋆   | t⋆₁
    V        V
   t₁₀ ---> t₁₁
       t₁⋆

Dans le type Πa:A.B

t₀⋆ : (t₀₀ =_(Πa₀⋆:A₀⋆.B₀⋆) t₀₁) ≡ Πa₀:{a₀₀;a₀₁;a₀⋆:a₀₀ =_A₀⋆ a₀₁}.(t₀₀ a₀₀ =_B₀⋆(a₀₀ a₀₁ a₀⋆) t₀₁ a₀₁)
t⋆⋆ : (t₀⋆ =_(Πa⋆⋆:A⋆⋆.B⋆⋆) t₁⋆) ≡
          Πa:{a₀:{a₀₀;a₀₁;a₀⋆:a₀₀ =_A₀⋆ a₀₁};
              a₁:{a₁₀;a₁₁;a₁⋆:a₁₀ =_A₁⋆ a₁₁};
              a⋆:{a⋆₀;a⋆₁;a⋆⋆:a⋆₀ =_A⋆⋆ a⋆₁}}.
          (t₀⋆ a₀ =_B⋆⋆[a⋆⋆] t₁⋆ a₁)

/ λa₀₀:A₀₀.t₀₀{a:=...} : A₀₀           \ / λa₁₀:A₁₀.t₁₀{a:=...} : A₁₀           \ / λa₀:Σ(A₀₀,A₁₀,A⋆₀).t⋆₀ :            \
|                                      | |                                      | |   λa₀₀.t₀₀ =_(Πa⋆₀:A⋆₀.B⋆₀) λa₁₀.t₁₀ |
| λa₀₁:A₀₁.t₀₁{a:=...} : A₀₁           | | λa₁₁:A₁₁.t₁₁{a:=...} : A₁₁           | | λa₁:Σ(A₀₁,A₁₁,A⋆₁).t⋆₁ :             |
|                                      | |                                      | |   λa₀₁.t₀₁ =_(Πa⋆₁:A⋆₁.B⋆₁) λa₁₁.t₁₁ |
| λa₀:A₀.t₀⋆{a:=...} :                 | | λa₀:A₀.t₁⋆{a:=...} :                 | | λa:A.t⋆⋆ :                           |
\   λa₀₀.t₀₀ =_(Πa₀⋆:A₀⋆.B₀⋆) λa₀₁.t₀₁ / \   λa₁₀.t₁₀ =_(Πa₁⋆:A₁⋆.B₁⋆) λa₁₁:t₁₁ / \   λa₀.t⋆₀ =_(Πa⋆⋆:A⋆⋆.B⋆⋆) λa₁.t⋆₁  /

                                                   app(t,u)
   /-------------------------------------------------------------------------------------------------------------------------------------------------\
         app(t₀,u₀)                               app(t₁,u₁)                                        app(t⋆,u⋆)
/ t₀₀ u₀₀ : B₀₀[u₀₀]                   \ / t₁₀ u₁₀ : B₁₀[u₁₀]                  \ / t⋆₀ (u₀₀,u₁₀,u⋆₀) : t₀₀ u₀₀ =_B⋆₀[u⋆₀] t₁₀ u₁₀                       \
| t₀₁ u₀₁ : B₀₁[u₀₁]                   | | t₁₁ u₁₁ : B₁₁[u₁₁]                  | | t⋆₁ (u₀₁,u₁₁,u⋆₁) : t₀₁ u₀₁ =_B⋆₁[u⋆₁] t₁₁ u₁₁                       |
\ t₀⋆ u₀  : t₀₀ u₀₀ =_B₀⋆[u₀⋆] t₀₁ u₀₁ / \ t₁⋆ u₁ : t₁₀ u₁₀ =_B₁⋆[u₁⋆] t₁₁ u₁₁ / \ t⋆⋆ u             : t⋆₀ (u₀₀,u₁₀,u⋆₀) =_B⋆⋆[u⋆⋆] t⋆.₁ (u₀₁,u₁₁,u⋆₁) /

= = = = = = =

Mq π...π(t) π...π(u) :

((λa:A₀₀.t₀₀),(λa:A₀₁.t₀₁),(λa:A₀₀.λa:A₀₁.λa⋆:a₀₀=a₀₁.t₀⋆.)),(...,...,(≃,λx.x,...)),((≃,λx.x,...),(≃,λx.x,...),(≃_2,λx.x,...))

  ⇑σ Type     ≜ (Type,Type,(≃,λx.x,...))
  ⇑σ (Πc:C.D) ≜ (Πc₀:ϕ(⇑σC)₀.(ϕ(⇑(σ,c:=((#₀(ϕ(⇑(σ)C))⋆)c₀))D))₀,
                 Πc₁:ϕ(⇑σC)₁.(ϕ(⇑(σ,c:=((#₀(ϕ(⇑(σ)C))⋆)c₁))D))₁,
                 (λf₀.λf₁.Πc:ϕ(⇑σC).f₀ c.0 =_(ϕ(⇑(σ,c:=c)D)⋆) f₁ c.1,
                  ...))   (9 com
  ⇑σ (Σc:C.D) ≜ (Σc₀:ϕ(⇑σC)₀.(ϕ(⇑(σ,c:=((#₀(ϕ(⇑(σ)C))⋆)c₀))D))₀,
                 Σc₁:ϕ(⇑σC)₁.(ϕ(⇑(σ,c:=((#₁(ϕ(⇑(σ)C))⋆)c₁))D))₁,
                 (λq₀.λq₁.Σp:(q₀.1 =_(ϕ(⇑σC)⋆) q₁.1).(q₀.2 =_(ϕ(⇑(σ,c:=c)D)⋆) q₁.2))
  ⇑σ (t u)    ≜ ((⇑σt)₀ (⇑σu)₀,
                 (⇑σt)₁ (⇑σu)₁,
                 (⇑σt)⋆ (⇑σu))  on va avoir besoin de coe ici ??
  ⇑σ (λc:C.t) ≜ (λc₀:ϕ(⇑σC)₀.(⇑(σ,c:=((#₀(ϕ(⇑(σ)C))⋆)c₀))t)₀,
                 λc₁:ϕ(⇑σC)₁.(⇑(σ,c:=((#₁(ϕ(⇑(σ)C))⋆)c₁))t)₁,
                 λc:ϕ(⇑σC).(⇑(σ,c:=c)t)⋆)
  ⇑σ (t,u)    ≜ (((⇑σt)₀,(⇑σu)₀),
                 ((⇑σt)₁,(⇑σu)₁),
                 ((⇑σt)⋆,(⇑σu)⋆))  on va avoir besoin de coe ici ??
  ⇑σ (t.1)    ≜ ((⇑σt)₀.1,
                 (⇑σt)₁.1,
                 (⇑σt)⋆.1)  on va avoir besoin de coe ici ??
  ⇑σ (t.2)    ≜ ((⇑σt)₀.2,
                 (⇑σt)₁.2,
                 (⇑σt)⋆.2)  on va avoir besoin de coe ici ??
  ⇑σ c        ≜ σ(c)   (où chaque traversée d'un i dans σ avant de trouver c induit un a↦(a,a,⇑σ'a)
                        avec σ' préfixe de σ avant i)
  ⇑σ =ⁿ_Ν     ≜ (=ⁿ_Ν,=ⁿ_N,(=ⁿ⁺¹_,λx.x,...))   (9 composantes dans la 3e composante)
  ⇑σ 0ⁿ       ≜ (0ⁿ,0ⁿ,0ⁿ⁺¹)             (où 0ⁿ⁺¹ prouve Γ ⊢ 0ⁿ =ⁿ⁺¹_N 0ⁿ)
  ⇑σ (Sⁿ t)   ≜ (Sⁿ (⇑σt)₀,Sⁿ (⇑σt)₁,Sⁿ⁺¹ (⇑σt)⋆) 
                    (où Sⁿ⁺¹ prouve Γ ⊢ (Sⁿ n) =ⁿ⁺¹_N (Sⁿ m) à partir de Γ ⊢ n =ⁿ_N m)
  ⇑σ (λi.t)   ≜ (⇑(σ,i)t)⋆
  ⇑σ (t i)    ≜ ⇑(σ\i) t ???
  ⇑σ ([α₁,...,α_n] =ⁿ_X [β₁,...,β_n]) prédéfini en fonction
      des ⇑σαᵢ et ⇑σβᵢ pour chaque n-cube de X (y compris pour n=0)

### 2022-06-24 paper/paper.tex
paper: minor polish
paper: partial spell-check

@@
     \graymidrule
-    Interpretation & Augmented semi-simplical types & Semi-cubical types \\
+    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
     \bottomrule
@@
 
+\subsection{Fibered versus indexed representation}
 The fibered representation can be illustrated as:
+
 \begin{equation*}
@@
 The indexed representation can be illustrated as:
+
 \begin{align*}
@@
 
-One way to obtain one construction from the other is via the \emph{Grothendieck construction}, although this is not relvant to our work.
+One way to obtain one construction from the other is via the \emph{Grothendieck construction}, although this is not relevant to our work.
 
-\subsection{Iterated parameteriticity}
+\subsection{Iterated parametricity}
 
@@
   \item[(i)] UIP holds on the unit type.
-  \item[(ii)] UIP propogates to $\Sigma$-types.
-  \item[(iii)] UIP propogates to $\Pi$-types, with some additional functional extensionality axioms.
+  \item[(ii)] UIP propagates to $\Sigma$-types.
+  \item[(iii)] UIP propagates to $\Pi$-types, with some additional functional extensionality axioms.
 \end{enumerate}
@@
 
+\newpage
 \section{Future work}
@@
   \bibitem[Angiuli]{Angiuli17}
-  Carlo Angiuli, Guillaume Brunerie, Thierry Coquand, Kuen-Bang Hou (Favonia), Robert Harper, \& Daniel R. Licata. arXiv preprint.
+  Carlo Angiuli, Guillaume Brunerie, Thierry Coquand, Kuen-Bang Hou (Favonia), Robert Harper, \& Daniel R. Licata. \emph{arXiv preprint}.
 

### 2022-08-16 paper/paper.tex
paper: MAJ title

@@
 
-\title{An indexed construction of semi-simplicial and semi-cubical types}
+\title{A mechanization of Kan complexes in the calculus of inductive constructions}
 \author{
@@
 
-The proof of $\cohf$ require an higher-dimensional coherence condition which we obtain by working in \texttt{HSet}.
+The proof of $\cohf$ require a higher-dimensional coherence condition which we obtain by working in \texttt{HSet}.
 If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
@@
 
-  \bibitem[CohCoq]{Cohen16}
+  \bibitem[Takeuti–Gandy]{Barras15}
+  Barras, B., Coquand, T., \& Huber, S. (2015). A generalization of the Takeuti–Gandy interpretation. \emph{Mathematical structures in computer science}, 25(5), 1071-1099.
+
+  \bibitem[CCHM]{Cohen16}
   Cohen, C., Coquand, T., Huber, S., \& Mörtberg, A. (2016). Cubical type theory: a constructive interpretation of the univalence axiom. \emph{arXiv preprint arXiv:1611.02108}.

### 2022-08-20 paper/paper.tex
paper, NType: MAJ

@@
   \ensuremath{\mathsf{\color{chestnut}{coh}}_{
+    \mathsf{\color{indian-yellow}{#1}}
+    \joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}
+  \setkeys*[bonak]{coh#1}{#9}
+}
+
+\newcommandx{\cohtwo}[9][2,3,4,5,6,7,8,9]{
+  \ensuremath{\mathsf{\color{chestnut}{coh2}}_{
     \mathsf{\color{indian-yellow}{#1}}
@@
 
-\title{A mechanization of Kan complexes in the calculus of inductive constructions}
+\title{A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions}
 \author{
@@
   \textcolor{gray80}{Hugo Herbelin} \\
-  \itshape \textcolor{gray80}{Institut de Recherche en Informatique Fondamentale}
+  \itshape \textcolor{gray80}{IRIF/Inria/Université Paris-Cité}
 }
@@
 \begin{abstract}
-  A model of homotopy type theory, formalizing augmented semi-simplicial sets, that naturally generalizes to semi-cubical sets as well, in dependent type theory.
+  We present a parametricity-based construction of semi-simplicial sets, that naturally generalizes to semi-cubical sets as well, in the calculus of inductive constructions.
 The accompanying artifact is an axiom-less~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to $\nu$-types; if $\nu$ is finite (say, unit type corresponding to augmented semi-simplicial types), this requirement vanishes.} Coq formalization that uses sophisticated rewriting techniques and pushes the boundaries of proof assistant technology.
@@
 \section{Overture}
-Cubical type theory~\cite{Bezem14}~\cite{Cohen16}~\cite{Angiuli17} is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT.
-The most significant implementation of cubical type theory in the real world is an experimental branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}.
-Cubical type theory is usually modeled as cubical sets, in the set-theoretic setting.
-
 Our contribution is the following.
-We have modelled the core of semi-cubical sets in a way that naturally generalizes to augmented semi-simplicial sets in type theory, and we call our generalization \emph{$\nu$-sets}.
+We have modelled the core of semi-simplicial sets in a way that naturally generalizes to semi-cubical sets in type theory, and we call our generalization \emph{$\nu$-sets}.
 In contrast to previous efforts that use a fibered representation, we use an indexed representation.
@@
 
+Cubical type theory~\cite{Bezem14}~\cite{Cohen16}~\cite{Angiuli17} is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT.
+The most significant implementation of cubical type theory in the real world is an branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}.
+Cubical type theory is usually modeled as cubical sets, in the set-theoretic setting.
+
 The outline of the paper is as follows.
-First, we briefly describe augmented semi-simplicial and semi-cubical sets, as it appears in mathematical literature, and our generalization to $\nu$-sets.
+First, we briefly describe semi-simplicial and semi-cubical sets, as it appears in mathematical literature, and our generalization to $\nu$-sets.
 We then proceed to explain our construction, with the help of diagrams.
@@
 It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
-What we have formalized is \emph{augmented} semi-simplicial sets, and semi-cubical sets, which is to say that they are the usual simplicial sets and cubical sets, minus the degeneracies.
+What we have formalized is \emph{semi-simplicial} sets, and semi-cubical sets, which is to say that they are the usual simplicial sets and cubical sets, minus the degeneracies.
 Since they're not of particular interest, and indeed, we plan to extend our work to do degeneracies in the future, we briefly explain the mathematical objects we have formalized.
 
-\subsection{Augmented semi-simplicial sets}
+\subsection{Semi-simplicial sets}
 Semi-simplicial sets are otherwise known as \emph{delta-sets} in mathematical literature.
-Since they are of little interest to the mathematician, we briefly describe \DeltaHat, which is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are \emph{strictly} order-preserving.
+We briefly describe \DeltaHat, which is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are \emph{strictly} order-preserving.
 The degeneracies then vanish, and we're left with the task of defining gluing conditions solely on the basis of face maps.
-There is little interest in studying \DeltaHat, since maps between delta sets are not well-defined, and it is therefore not possible to construct a category of delta sets.
+The core of the definition of $\SSet$ is precisely what we have constructed.
 
@@
     \graymidrule
-    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
+    Interpretation & Semi-simplicial types & Semi-cubical types \\
     \bottomrule
@@
 % Coherence conditions for frame, layer, and filler
-% Drop universe letter, ε, and ω
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][][][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][][][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][][][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\newcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
 
@@
 \renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
 

### 2022-08-22 paper/paper.tex
paper: some diagrams for DeltaHat
tab-coh: fix the proof term of coh_layer
tab-coh: MAJ
paper: put the q back into restr
tab-coh: add brackets around ap

@@
     \mathsf{\color{indian-yellow}{#1}}
-    \joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}
+    \joinargs{,}[#2][#3][#4][#5][#6][#7]}^{\joinargs{}[#8]}}
   \setkeys*[bonak]{coh#1}{#9}
@@
 \newcommand{\E}{E}
+\newcommand{\ap}{\mathsf{ap}}
 \renewcommand{\l}{l}
@@
 Cubical type theory~\cite{Bezem14}~\cite{Cohen16}~\cite{Angiuli17} is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT.
-The most significant implementation of cubical type theory in the real world is an branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}.
+The most significant implementation of cubical type theory in the real world is a branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}.
 Cubical type theory is usually modeled as cubical sets, in the set-theoretic setting.
@@
 
-\section{Mathematical treatment of \texorpdfstring{$\nu$}{nu}-sets}
+\section{Mathematical treatment of \texorpdfstring{$\nu$}{𝜈}-sets}
 It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
@@
 The core of the definition of $\SSet$ is precisely what we have constructed.
+
+\begin{example}[$\DeltaHat^0$, $\DeltaHat^1$, $\DeltaHat^2$]
+  $\DeltaHat^0$ can be drawn as:
+  \begin{equation*}
+    \begin{tikzcd}
+      \bullet
+    \end{tikzcd}
+  \end{equation*}
+
+  $\DeltaHat^1$ can be drawn as:
+  \begin{equation*}
+    \begin{tikzcd}
+      \bullet \arrow[r, dash] & \bullet
+    \end{tikzcd}
+  \end{equation*}
+
+  $\DeltaHat^2$ can be drawn as:
+  \begin{equation*}
+    \begin{tikzcd}
+      & \bullet\arrow[dr, dash] & \\
+      \bullet\arrow[rr, dash]\arrow[ur, dash] && \bullet
+    \end{tikzcd}
+  \end{equation*}
+\end{example}
 
@@
 
-  $$
+  \begin{equation*}
     \begin{tikzcd}
@@
     \end{tikzcd}
-  $$
+  \end{equation*}
 
@@
     \end{tikzcd}
-  $$
+  \end{equation*}
 \end{example}
@@
 % Restriction for frame, layer, and filler
-% Drop the unviverse letter and q
-\newcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][][#4][#5][#6][#7]}
-\newcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][][#4][#5][#6][#7]}
-\newcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][][#4][#5][#6][#7]}
+% Drop the unviverse letter
+\newcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\newcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
+\newcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}
 
@@
 \renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\newcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\newcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
 

### 2022-08-26 paper/paper.tex
paper: MAJ
paper: s/U/HSet/
paper: include art.cls as submodule

@@
-\documentclass[10pt]{art}
+\documentclass[10pt]{art.cls/art}
 
-\usepackage{multirow, minted, tabularx, environ, booktabs, setspace, makecell, caption, joinargs, colortbl, pdflscape, ct, sset}
-\usepackage[prefix=bonak]{xkeymask}
+\usepackage{multirow, minted, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape}
+\usepackage[prefix=bonak]{art.cls/xkeymask}
 \usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}
@@
 % Universe, referred to as U
-\newcommand{\U}[1]{\mathsf{\color{spanish-blue}{U}}_{#1}}
+\newcommand{\U}[1]{\mathsf{\color{spanish-blue}{HSet}}_{#1}}
 
@@
 % Definitional and extensional equality
-\newcommand{\defeq}{\triangleq}
+\newcommand{\defeq}{\ensuremath{\triangleq}}
 \newcommand{\eqHSet}{\ensuremath{\equiv_{\mathit{HSet}}}}
@@
 \renewcommand{\d}{d}
-\newcommand{\E}{E}
+\renewcommand{\E}{E}
 \newcommand{\ap}{\mathsf{ap}}
@@
   \textcolor{gray80}{Hugo Herbelin} \\
-  \itshape \textcolor{gray80}{IRIF/Inria/Université Paris-Cité}
+  \itshape \textcolor{gray80}{IRIF/Inria Paris/Université Paris-Cité}
 }
@@
   \mathsf{eq\_refl}        & : \forall x, x = x                                           \\
-  \mathsf{UIP\_refl\_unit} & : \forall x : \top = \top, x = \mathsf{eq\_refl}
+  \mathsf{UIP\_refl\_unit} & : \forall x : \unitpoint = \unitpoint, x = \mathsf{eq\_refl}
 \end{align*}
@@
 \renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[#1][#2][#3][#4][#5][#6][#7,#8][#9]}
 

### 2022-08-28 paper/paper.tex
paper: typeset an array for iter param
paper: strip some useless minted stuff
paper: usepackage float for [H] specifier; not minted

@@
 
-\usepackage{multirow, minted, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape}
+\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape}
 \usepackage[prefix=bonak]{art.cls/xkeymask}
@@
 }
-
-% Code listings
-\usemintedstyle{solarized-dark}
-\setminted{escapeinside=~~}
-\setmintedinline{escapeinside=~~}
 
@@
 \subsection{Iterated parametricity}
+A full 2-cube is made of two full 1-cubes connected by a lifted 1-cube made of two lines connecting the former points and a square connecting the former lines:
+\begin{equation*}
+  \begin{array}{lll}
+    \mbox{\textit{squares}}     \\
+    [1mm]\mbox{\textit{lines}}  \\
+    [1mm]\mbox{\textit{points}} \\
+    [1mm]\end{array}
+  \framebox{$\begin{array}{lll}
+        \framebox{$
+            \begin{array}{ll}
+               & \framebox{$a_{0\star}$}              \\
+              \framebox{$a_{00}$}~\framebox{$a_{01}$} \\
+            \end{array}
+          $}~
+        \framebox{$
+            \begin{array}{ll}
+               & \framebox{$a_{1\unitpoint}$}         \\
+              \framebox{$a_{10}$}~\framebox{$a_{11}$} \\
+            \end{array}
+          $}~
+        \raisebox{4.8mm}{$\framebox{$
+                \begin{array}{ll}
+                   & \framebox{$a_{\unitpoint\unitpoint}$}                    \\
+                  \framebox{$a_{\unitpoint 0}$}~\framebox{$a_{\unitpoint 1}$} \\
+                \end{array}
+              $}$}
+      \end{array}$}
+\end{equation*}
 

### 2022-08-29 paper/paper.tex
art.cls, paper: MAJ
art.cls: MAJ
paper: better typesetting for iterated-param

@@
 \usepackage[prefix=bonak]{art.cls/xkeymask}
-\usepackage[a4paper, inner=25mm, outer=25mm, top=25mm, bottom=25mm]{geometry}
-
-% Simplicial and Cubical sets
-\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
-\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
-\renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
-\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
 
@@
 
+% Simplicial and Cubical sets
+\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
+\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
+\renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
+\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
+
 % Universe, referred to as U
@@
 \newcommand{\pair}[2]{#1, #2}
-
-% Fancy headers
-\pagestyle{fancy}
-\fancyhf{}
-\fancyhead[R]{\footnotesize\textcolor{gray80}{{\thepage / \pageref{LastPage}}}}
-\renewcommand{\sectionmark}[1]{\markboth{}{\thesection.\ #1}}
-\fancyhead[L]{\footnotesize\textcolor{gray80}{{\MakeUppercase{\rightmark}}}}
-
-% Section and subsection styles
-\renewcommand{\thesection}{\Roman{section}}
-\titleformat{\section}{\centering\scshape\Large\color{raspeberry}}{\thesection}{0.7em}{}
-\titleformat{\subsection}{\strongenv\large\color{gray80}}{\thesubsection}{0.7em}{}
-
-% Pack enumerate items and bibitems
-\setlist{nolistsep}
-\setlength{\bibitemsep}{.2\baselineskip plus .05\baselineskip minus .05\baselineskip}
+\newcommandx{\myframe}[2][1,2]{\prim{frame}[][#1][#2][#2][]}
+\newcommandx{\mylayer}[2][1,2]{\prim{layer}[][#1][#2][][]}
+\newcommandx{\myfiller}[2][1,2]{\prim{filler}[][#1][#2][][]}
 
@@
 % Table caption set up
-\DeclareCaptionFormat{hfillstart}{\hfill#1#2#3\par}
+\DeclareCaptionFormat{hfillunittypet}{\hfill#1#2#3\par}
 \DeclareCaptionFont{mdit}{\mdseries\itshape}
@@
 }
-
-% Fonts
-\setmainfont{Avenir Next}
-\setmonofont{Source Code Pro}
-\defaultfontfeatures{Ligatures=TeX, Scale=MatchUppercase}
 
@@
 where the filling conditions are conflated with the cube itself.
-$\Simplex{n}$ can be defined quite simply as the convex hull of $n$ points, but even defining the standard $n$-cube becomes a problem if we start with $\sq{n}$, but the situation becomes much more amenable if we define:
+$\Simplex{n}$ can be defined quite simply as the convex hull of $n$ points, but even defining the standard $n$-cube becomes a problem if we unittypet with $\sq{n}$, but the situation becomes much more amenable if we define:
 
@@
   X_1 & : X_0 \times X_0 \rightarrow \U{}                                                                                   \\
-  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \U{} \\
+  X_2 & : \forall a b c d, X_1 (a, b) \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \rightarrow X_1 (c, d) \rightarrow \U{} \\
   \ldots
@@
 \begin{equation*}
+  \begin{array}{l}
     \begin{array}{lll}
       \mbox{\textit{squares}}     \\
-    [1mm]\mbox{\textit{lines}}  \\
-    [1mm]\mbox{\textit{points}} \\
+      [3mm]\mbox{\textit{lines}}  \\
+      [3mm]\mbox{\textit{points}} \\
       [1mm]\end{array}
     \framebox{$\begin{array}{lll}
-        \framebox{$
+                     \overbrace{\raisebox{0.05cm}{\framebox{$
                            \begin{array}{ll}
-               & \framebox{$a_{0\star}$}              \\
-              \framebox{$a_{00}$}~\framebox{$a_{01}$} \\
+                  \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[1][0]$}} & \framebox{$a_{0\unitpoint}$} \\
+                  [1mm]\overbrace{\framebox{$a_{00}$}~\framebox{$a_{01}$}}   &
+                  \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[1][0]\!\!\!\!\!\!\!\!$}}
+                  \\
                 \end{array}
-          $}~
-        \framebox{$
+                         $}}~
+                     {\raisebox{0.05cm}{\framebox{$
                            \begin{array}{ll}
-               & \framebox{$a_{1\unitpoint}$}         \\
-              \framebox{$a_{10}$}~\framebox{$a_{11}$} \\
+                  \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[1][0]$}} & \framebox{$a_{1\unitpoint}$} \\
+                  [1mm]\overbrace{\framebox{$a_{10}$}~\framebox{$a_{11}$}}   &
+                  \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[1][0]\!\!\!\!\!\!\!\!$}}
                 \end{array}
-          $}~
-        \raisebox{4.8mm}{$\framebox{$
+                         $}}}}^{\mylayer[2][0]}~\stackrel{\raisebox{9.5mm}{$\framebox{$
                                \begin{array}{ll}
-                   & \framebox{$a_{\unitpoint\unitpoint}$}                    \\
-                  \framebox{$a_{\unitpoint 0}$}~\framebox{$a_{\unitpoint 1}$} \\
+                      \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[2][1]$}}                   & \framebox{$a_{\unitpoint\unitpoint}$} \\
+                      [1mm]\overbrace{\framebox{$a_{\unitpoint 0}$}~\framebox{$a_{\unitpoint 1}$}} &
+                      \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[2][1]\!\!\!\!\!\!\!\!$}}
+                    \end{array}$}$}}
+                     {\raisebox{-0.4cm}{{\scriptsize \hspace{2.5cm}$\myfiller[2][0]\!\!\!\!\!\!\!$}}}
+                   \end{array}$}
+    ~~~\parbox{3.5cm}{{\it additionally, each atomic component at dimension $n$ is a $\myfiller[n][n]$}} \\
+    [-1mm]\qquad\qquad~~
+    \begin{tikzcd}
+      \bullet\arrow[r, leftrightarrow] & \bullet\\
+    \end{tikzcd}
+    \mbox{\normalsize $\myframe[1][1]$}
+    \quad~~
+    \begin{tikzcd}
+      \bullet\arrow[r, leftrightarrow] & \bullet \\
+    \end{tikzcd}
+    \mbox{\normalsize $\myframe[1][1]$}                                                                  \\
+    [-2mm]\qquad\qquad
+    \begin{tikzcd}
+     \bullet\arrow[r, leftrightarrow] & \bullet\\
+    \end{tikzcd}
+    \mbox{\normalsize$\myframe[2][1]$}                                                                   \\
+    [-2mm]\qquad\qquad
+    \begin{tikzcd}
+      \bullet\arrow[r, leftrightarrow] & \bullet\\
+    \end{tikzcd}
+    \mbox{\normalsize$\myframe[2][2]$}                                                                   \\
   \end{array}
-              $}$}
-      \end{array}$}
 \end{equation*}

### 2022-08-29 paper/paper.tex
paper: MAJ

@@
 \newcommand{\pair}[2]{#1, #2}
-\newcommandx{\myframe}[2][1,2]{\prim{frame}[][#1][#2][#2][]}
+\newcommandx{\myframe}[2][1,2]{\prim{frame}[][#1][#2][][]}
 \newcommandx{\mylayer}[2][1,2]{\prim{layer}[][#1][#2][][]}
@@
 \subsection{Iterated parametricity}
+One step of parametricity can be seen as interpreting a point by a line.
+Iterating parametricity shall lead to map terms typed in a context with $n$ declarations of an axis as $n$-cubes.
+We shall interpret a
+typing derivation with $n$ axis declarations as an $n$-cube of typing derivations in the target.
+For instance, a typing derivation with exactly one declaration of an axis will be interpreted by 3 typing derivations in the target, two of them typing points and the third one typing a proof, seen as a line, together with the fact that these two points are related (as in ordinary parametricity), while a typing derivation with $n$ declarations of an axis shall be interpreted as a $3^n$ derivations, split into $2^n$ derivations of points.
+
 A full 2-cube is made of two full 1-cubes connected by a lifted 1-cube made of two lines connecting the former points and a square connecting the former lines:
@@
   \mathsf{eq\_refl}        & : \forall x, x = x                                                    \\
-  \mathsf{UIP\_refl\_unit} & : \forall x : \unitpoint = \unitpoint, x = \mathsf{eq\_refl}
+  \mathsf{UIP\_refl\_unit} & : \forall x : \unitpoint = \unitpoint, x = \mathsf{eq\_refl}          \\
+  \mathsf{UIP\_refl\_bool} & : \forall b : \mathsf{bool}, \forall x : b = b, x = \mathsf{eq\_refl} \\
 \end{align*}

### 2022-08-29 paper/paper.tex
paper: fix alignmented of iter-param diagram

@@
 A full 2-cube is made of two full 1-cubes connected by a lifted 1-cube made of two lines connecting the former points and a square connecting the former lines:
+{\scriptsize
 \begin{equation*}
@@
                            \begin{array}{ll}
-                  \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[1][0]$}} & \framebox{$a_{0\unitpoint}$} \\
+                  \raisebox{0cm}{\hspace{.5cm}{\mylayer[1][0]}} & \framebox{$a_{0\unitpoint}$} \\
                   [1mm]\overbrace{\framebox{$a_{00}$}~\framebox{$a_{01}$}}   &
-                  \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[1][0]\!\!\!\!\!\!\!\!$}}
+                  \raisebox{-0.1cm}{\hspace{0.1cm}\myfiller[1][0]\!\!\!\!\!\!\!\!}
                   \\
@@
                            \begin{array}{ll}
-                  \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[1][0]$}} & \framebox{$a_{1\unitpoint}$} \\
+                  \raisebox{0cm}{\hspace{.5cm}{\mylayer[1][0]}} & \framebox{$a_{1\unitpoint}$} \\
                   [1mm]\overbrace{\framebox{$a_{10}$}~\framebox{$a_{11}$}}   &
-                  \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[1][0]\!\!\!\!\!\!\!\!$}}
+                  \raisebox{-0.1cm}{\myfiller[1][0]\!\!\!\!\!\!\!\!}
                 \end{array}
@@
                                \begin{array}{ll}
-                      \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[2][1]$}}                   & \framebox{$a_{\unitpoint\unitpoint}$} \\
+                      \raisebox{0cm}{\hspace{.5cm}{$\mylayer[2][1]$}}                   & \framebox{$a_{\unitpoint\unitpoint}$} \\
                       [1mm]\overbrace{\framebox{$a_{\unitpoint 0}$}~\framebox{$a_{\unitpoint 1}$}} &
-                      \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[2][1]\!\!\!\!\!\!\!\!$}}
+                      \raisebox{-0.1cm}{ \hspace{0.1cm}\myfiller[2][1]\!\!\!\!\!\!\!\!}
                     \end{array}$}$}}
-                     {\raisebox{-0.4cm}{{\scriptsize \hspace{2.5cm}$\myfiller[2][0]\!\!\!\!\!\!\!$}}}
+                     {\raisebox{-0.4cm}{\hspace{2.5cm}\myfiller[2][0]\!\!\!\!\!\!\!}}
                    \end{array}$}
-    ~~~\parbox{3.5cm}{{\it additionally, each atomic component at dimension $n$ is a $\myfiller[n][n]$}} \\
-    [-1mm]\qquad\qquad~~
-    \begin{tikzcd}
-      \bullet\arrow[r, leftrightarrow] & \bullet\\
+    ~~~\parbox{2cm}{{\it additionally, each atomic component at dimension $n$ is a \myfiller[n][n]}} \\\\
+    [-1mm]\qquad\qquad\quad~~
+    \begin{tikzcd}[column sep=5.2em, row sep=1em]
+      \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
     \end{tikzcd}
-    \mbox{\normalsize $\myframe[1][1]$}
-    \quad~~
-    \begin{tikzcd}
-      \bullet\arrow[r, leftrightarrow] & \bullet \\
+    \mbox{\myframe[1][1]}
+    \qquad
+    \begin{tikzcd}[column sep=5.2em, row sep=1em]
+      \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
     \end{tikzcd}
-    \mbox{\normalsize $\myframe[1][1]$}                                                                  \\
-    [-2mm]\qquad\qquad
-    \begin{tikzcd}
-      \bullet\arrow[r, leftrightarrow] & \bullet\\
+    \mbox{\myframe[1][1]} \\
+    \qquad\qquad~~
+    \begin{tikzcd}[column sep=32em, row sep=1em]
+      \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
     \end{tikzcd}
-    \mbox{\normalsize$\myframe[2][1]$}                                                                   \\
-    [-2mm]\qquad\qquad
-    \begin{tikzcd}
-      \bullet\arrow[r, leftrightarrow] & \bullet\\
+    \mbox{\myframe[2][1]} \\
+    \qquad\qquad~~
+    \begin{tikzcd}[column sep=39em, row sep=1em]
+      \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
     \end{tikzcd}
-    \mbox{\normalsize$\myframe[2][2]$}                                                                   \\
+    \mbox{\myframe[2][2]} \\
   \end{array}
 \end{equation*}
+}
 

### 2022-08-29 paper/paper.tex
Proposal for beginning of overture.

@@
 \begin{abstract}
-  We present a parametricity-based construction of semi-simplicial sets, that naturally generalizes to semi-cubical sets as well, in the calculus of inductive constructions.
+  We present a parametricity-based construction of semi-simplicial sets and semi-cubical sets in indexed form, in the calculus of inductive constructions.
 The accompanying artifact is an axiom-less~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to $\nu$-types; if $\nu$ is finite (say, unit type corresponding to augmented semi-simplicial types), this requirement vanishes.} Coq formalization that uses sophisticated rewriting techniques and pushes the boundaries of proof assistant technology.
@@
 \section{Overture}
+
+In the context of typed functional programming, Reynolds'
+parametricity~\cite{Reynolds72} interprets types as relations
+characterizing the observational equality of programs of this type.
+Parametricity can be iterated and it has been noted that iterated
+Reynolds' parametricity has a cubical
+flavor~\cite{AltenkirchKaposi15,JohannSojakova17,Moulin16,...}. We obtain a
+\emph{unary} variant of Reynolds' \emph{binary} parametricity by using
+predicates instead of relations, in which case we obtain a form of
+(Kreisel) realizability~\cite{Moulin16,BernardyMoulin12}. It has then be
+noted that iterated unary parametricity has an augmented simplicial
+flavor\footnote{Observation from Hugo Moeneclaey}.
+
+We exploit the connection between iterated unary parametricity and
+augmented simplicial sets and between binary parametricity and cubical
+sets to present a uniform construction of both semi-simplicial
+semi-cubical sets obtained by applying simple rules iterating
+parametricity.  In contrast to the presheaf presentation of
+semi-simplicial and semi-cubical sets, our uniform construction, which
+we call \emph{$\nu$-sets}, is \emph{indexed}. That is, instead of
+having the set of semi-simplices or semi-cubes in dimension $n+1$
+\emph{fibered} over the set of semi-simplices or semi-cubes in
+dimension $n$, we consider families of semi-simplices and semi-cubes
+indexed over their faces.
+
+\iffalse
 Our contribution is the following.
 We have modelled the core of semi-simplicial sets in a way that naturally generalizes to semi-cubical sets in type theory, and we call our generalization \emph{$\nu$-sets}.
-In contrast to previous efforts that use a fibered representation, we use an indexed representation.
+In contrast to the presheaf presentation of semi-cubical -based where the set of  that use a fibered representation, we use an indexed representation.
 Our work is, in principle axiom-free, although the accompanying artifact uses functional extensionality, and this requires disappears if $\nu$ is finite.
@@
 Cubical type theory is usually modeled as cubical sets, in the set-theoretic setting.
+\fi
 

### 2022-08-29 paper/paper.tex
paper: wrap Hugo's contrib-para

@@
 
-In the context of typed functional programming, Reynolds'
-parametricity~\cite{Reynolds72} interprets types as relations
-characterizing the observational equality of programs of this type.
-Parametricity can be iterated and it has been noted that iterated
-Reynolds' parametricity has a cubical
-flavor~\cite{AltenkirchKaposi15,JohannSojakova17,Moulin16,...}. We obtain a
-\emph{unary} variant of Reynolds' \emph{binary} parametricity by using
-predicates instead of relations, in which case we obtain a form of
-(Kreisel) realizability~\cite{Moulin16,BernardyMoulin12}. It has then be
-noted that iterated unary parametricity has an augmented simplicial
-flavor\footnote{Observation from Hugo Moeneclaey}.
+In the context of typed functional programming, Reynolds' parametricity~\cite{} interprets types as relations characterizing the observational equality of programs of this type.
+Parametricity can be iterated and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{}.
+We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{}.
+It has then be noted that iterated unary parametricity has an augmented simplicial flavor\footnote{Observation from Hugo Moeneclaey}.
 
-We exploit the connection between iterated unary parametricity and
-augmented simplicial sets and between binary parametricity and cubical
-sets to present a uniform construction of both semi-simplicial
-semi-cubical sets obtained by applying simple rules iterating
-parametricity.  In contrast to the presheaf presentation of
-semi-simplicial and semi-cubical sets, our uniform construction, which
-we call \emph{$\nu$-sets}, is \emph{indexed}. That is, instead of
-having the set of semi-simplices or semi-cubes in dimension $n+1$
-\emph{fibered} over the set of semi-simplices or semi-cubes in
-dimension $n$, we consider families of semi-simplices and semi-cubes
-indexed over their faces.
+We exploit the connection between iterated unary parametricity and augmented simplicial sets and between binary parametricity and cubical sets to present a uniform construction of both semi-simplicial semi-cubical sets obtained by applying simple rules iterating parametricity.
+In contrast to the presheaf presentation of semi-simplicial and semi-cubical sets, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
+That is, instead of having the set of semi-simplices or semi-cubes in dimension $n+1$
+\emph{fibered} over the set of semi-simplices or semi-cubes in dimension $n$, we consider families of semi-simplices and semi-cubes indexed over their faces.
 

### 2022-08-29 paper/paper.tex
paper: ws changes

@@
 \newcommand{\pair}[2]{#1, #2}
-\newcommandx{\myframe}[2][1,2]{\prim{frame}[][#1][#2][][]}
-\newcommandx{\mylayer}[2][1,2]{\prim{layer}[][#1][#2][][]}
-\newcommandx{\myfiller}[2][1,2]{\prim{filler}[][#1][#2][][]}
+\newcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
+\newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
+\newcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
 
@@
 We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{}.
-It has then be noted that iterated unary parametricity has an augmented simplicial flavor\footnote{Observation from Hugo Moeneclaey}.
+It has then be noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation from Hugo Moeneclaey}.
 
@@
 It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
-What we have formalized is \emph{semi-simplicial} sets, and semi-cubical sets, which is to say that they are the usual simplicial sets and cubical sets, minus the degeneracies.
-Since they're not of particular interest, and indeed, we plan to extend our work to do degeneracies in the future, we briefly explain the mathematical objects we have formalized.
+What we have formalized is \emph{semi-simplicial} sets, and \emph{semi-cubical} sets, which is to say that they are the usual simplicial sets and cubical sets, minus the degeneracies.
+Indeed, we plan to extend our work to do degeneracies in the future, but let us briefly explain the mathematical objects we have formalized.
 
@@
                 \begin{array}{ll}
-                  \raisebox{0cm}{\hspace{.5cm}{\mylayer[1][0]}} & \framebox{$a_{0\unitpoint}$} \\
+                  \raisebox{0cm}{\hspace{.5cm}{\layer[1][0]}} & \framebox{$a_{0\unitpoint}$} \\
                   [1mm]\overbrace{\framebox{$a_{00}$}~\framebox{$a_{01}$}}   &
-                  \raisebox{-0.1cm}{\hspace{0.1cm}\myfiller[1][0]\!\!\!\!\!\!\!\!}
+                  \raisebox{-0.1cm}{\hspace{0.1cm}\filler[1][0]\!\!\!\!\!\!\!\!}
                   \\
@@
                 \begin{array}{ll}
-                  \raisebox{0cm}{\hspace{.5cm}{\mylayer[1][0]}} & \framebox{$a_{1\unitpoint}$} \\
+                  \raisebox{0cm}{\hspace{.5cm}{\layer[1][0]}} & \framebox{$a_{1\unitpoint}$} \\
                   [1mm]\overbrace{\framebox{$a_{10}$}~\framebox{$a_{11}$}}   &
-                  \raisebox{-0.1cm}{\myfiller[1][0]\!\!\!\!\!\!\!\!}
+                  \raisebox{-0.1cm}{\filler[1][0]\!\!\!\!\!\!\!\!}
                 \end{array}
-                         $}}}}^{\mylayer[2][0]}~\stackrel{\raisebox{9.5mm}{$\framebox{$
+                         $}}}}^{\layer[2][0]}~\stackrel{\raisebox{9.5mm}{$\framebox{$
                     \begin{array}{ll}
-                      \raisebox{0cm}{\hspace{.5cm}{$\mylayer[2][1]$}}                   & \framebox{$a_{\unitpoint\unitpoint}$} \\
+                      \raisebox{0cm}{\hspace{.5cm}{$\layer[2][1]$}}                   & \framebox{$a_{\unitpoint\unitpoint}$} \\
                       [1mm]\overbrace{\framebox{$a_{\unitpoint 0}$}~\framebox{$a_{\unitpoint 1}$}} &
-                      \raisebox{-0.1cm}{ \hspace{0.1cm}\myfiller[2][1]\!\!\!\!\!\!\!\!}
+                      \raisebox{-0.1cm}{ \hspace{0.1cm}\filler[2][1]\!\!\!\!\!\!\!\!}
                     \end{array}$}$}}
-                     {\raisebox{-0.4cm}{\hspace{2.5cm}\myfiller[2][0]\!\!\!\!\!\!\!}}
+                     {\raisebox{-0.4cm}{\hspace{2.5cm}\filler[2][0]\!\!\!\!\!\!\!}}
           \end{array}$}
-    ~~~\parbox{2cm}{{\it additionally, each atomic component at dimension $n$ is a \myfiller[n][n]}} \\\\
+    ~~~\parbox{2cm}{{\it additionally, each atomic component at dimension $n$ is a \filler[n][n]}} \\\\
     [-1mm]\qquad\qquad\quad~~
@@
     \end{tikzcd}
-    \mbox{\myframe[1][1]}
+    \mbox{\framep[1][1]}
     \qquad
@@
     \end{tikzcd}
-    \mbox{\myframe[1][1]} \\
+    \mbox{\framep[1][1]} \\
     \qquad\qquad~~
@@
     \end{tikzcd}
-    \mbox{\myframe[2][1]} \\
+    \mbox{\framep[2][1]} \\
     \qquad\qquad~~
@@
     \end{tikzcd}
-    \mbox{\myframe[2][2]} \\
+    \mbox{\framep[2][2]} \\
   \end{array}
@@
 % Drop the universe letter
-\newcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
-\newcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
-\newcommandx{\filler}[5][1,2,3,4,5]{\prim{filler}[][#2][#3][#4][#5]}
+\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
+\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
+\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{filler}[][#2][#3][#4][#5]}
 

### 2022-08-30 paper/paper.tex
paper: fix some citations

@@
 
-In the context of typed functional programming, Reynolds' parametricity~\cite{} interprets types as relations characterizing the observational equality of programs of this type.
-Parametricity can be iterated and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{}.
-We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{}.
-It has then be noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation from Hugo Moeneclaey}.
+In the context of typed functional programming, Reynolds' parametricity~\cite{Reynolds72} interprets types as relations characterizing the observational equality of programs of this type.
+Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{Johann17,Altenkirch15,Moulin16}.
+We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{Bernardy12,Moulin16}.
+It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation from Hugo Moeneclaey}.
 
@@
 \begin{thebibliography}{10}
+  \bibitem[Reynolds72]{Reynolds72}
+  Reynolds, J. C. (1972, August). Definitional interpreters for higher-order programming languages. \emph{In Proceedings of the ACM annual conference-Volume 2} (pp. 717-740).
+
+  \bibitem[Johann17]{Johann17}
+  Johann, P., \& Sojakova, K. (2017). Cubical categories for higher-dimensional parametricity. \emph{arXiv preprint arXiv:1701.06244}.
+
+  \bibitem[BernardyMoulin]{Bernardy12}
+  Bernardy, J. P., \& Moulin, G. (2012, June). A computational interpretation of parametricity. \emph{In 2012 27th Annual IEEE Symposium on Logic in Computer Science} (pp. 135-144). IEEE.
+
+  \bibitem[AltenkirchKaposi]{Altenkirch15}
+  Altenkirch, Thorsten, and Ambrus Kaposi. "A nominal syntax for internal parametricity." \emph{TYPES 2015} (2015): 21.
+
+  \bibitem[Moulin16]{Moulin16}
+  Moulin, G. (2016). \emph{Internalizing parametricity.} Department of Computer Science and Engineering, Chalmers University of Technology.
+
   \bibitem[Bez]{Bezem14}

### 2022-08-30 paper/paper.tex
paper: include table in Overture

@@
 Our work is, in principle axiom-free, although the accompanying artifact uses functional extensionality, and this requires disappears if $\nu$ is finite.
+\fi
 
@@
     \graymidrule
-      Fibered & CCHM       &             \\
+    Fibered & \cite{Cohen16} &             \\
     \graymidrule
@@
 \end{table}
-
-  Cubical type theory~\cite{Bezem14}~\cite{Cohen16}~\cite{Angiuli17} is an extension of dependent type theory that provides a computational interpretation of Voevodsky's \emph{univalence axiom}, in a field known as \emph{homotopy type theory}, or HoTT.
-The most significant implementation of cubical type theory in the real world is a branch of Agda, known as \emph{Cubical Agda}~\cite{Vezzosi21}.
-Cubical type theory is usually modeled as cubical sets, in the set-theoretic setting.
-\fi
 

### 2022-09-09 paper/paper.tex
paper: typeset definition of coh2

@@
 \subsection{Semi-cubical sets}
-We might naively attempt to define $\Cube{}$ identically to \DeltaHat, but let us briefly explain why this wouldn't work, motivating the definition of semi-cubical sets as in \cite{Antolini00}.
-If there were morphisms from every $\sq{m}$ to \sq{n}, we would end up with:
-
-$$
-  \begin{tikzcd}
-    \bullet \arrow[r] \arrow[dr] \arrow[d] & \bullet \arrow[d] \\
-    \bullet \arrow[r] \arrow[ur] & \bullet
-  \end{tikzcd}
-$$
-
-where the filling conditions are conflated with the cube itself.
-$\Simplex{n}$ can be defined quite simply as the convex hull of $n$ points, but even defining the standard $n$-cube becomes a problem if we unittypet with $\sq{n}$, but the situation becomes much more amenable if we define:
-
 \begin{definition}[\Cube{n}]
@@
 
+where $\cohtwo{frame}$ is:
+
+\begin{align*}
+  \cohf[m][\omega][\theta][r][p][n][p][][d = {\restrf[m][\epsilon][q+2][n][p][][d = \d, D = \D]}, D = \D]\;\bullet         \\
+  \ap (\restrf[m][\omega][r][n][p][][d = {\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d, D = \D]}, D = \D]\;\bullet    \\
+  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d, D = \D]}, D = \D] =                  \\
+  \ap (\restrf[m][\theta][p][n][p][][d = {\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d, D = \D]}, D = \D])\;\bullet \\
+  \cohf[m][\epsilon][\theta][q][p][n][p][][d = {\restrf[m][\omega][r+1][n][p][][d = \d, D = \D]}, D = \D]\;\bullet         \\
+  \ap (\restrf[m][\epsilon][q][n][p][][d = {\cohf[m][\omega][\theta][r][p][n][p][][d = \d, D = \D]}, D = \D])
+\end{align*}
+
 \newpage

### 2022-09-10 paper/paper.tex
paper: define semi-{simplicial, cubical} sets combinatorially

@@
 % Simplicial and Cubical sets
-\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
+\newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
 \newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
@@
 
-\subsection{Semi-simplicial sets}
-Semi-simplicial sets are otherwise known as \emph{delta-sets} in mathematical literature.
-We briefly describe \DeltaHat, which is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are \emph{strictly} order-preserving.
-The degeneracies then vanish, and we're left with the task of defining gluing conditions solely on the basis of face maps.
-The core of the definition of $\SSet$ is precisely what we have constructed.
+\subsection{Augmented semi-simplicial sets}
+We consider the category of augmented semi-simplices, which can be written in different ways, up to equivalence. We proceed to describe to combinatorial definition.
+\begin{definition}[\DeltaPlus]
+  The category of augmented semi-simplices is defined in terms of objects and morphisms:
 
-\begin{example}[$\DeltaHat^0$, $\DeltaHat^1$, $\DeltaHat^2$]
-  $\DeltaHat^0$ can be drawn as:
+  \begin{align*}
+    \obj(\DeltaPlus) & := \Nat                                                                            \\
+    \hom(p, n)       & := \{i_{p + 1}, \ldots, i_n \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\} \\
+    f \circ g        & := \text{concatenation of the sequences $f$ and $g$}
+  \end{align*}
+\end{definition}
+
+\begin{example}[$\DeltaPlus^0$, $\DeltaPlus^1$]
+  $\DeltaPlus^0$ can be drawn as:
+
   \begin{equation*}
     \begin{tikzcd}
-      \bullet
+      0 \arrow[r, dash] & 1
     \end{tikzcd}
@@
 
-  $\DeltaHat^1$ can be drawn as:
+  $\DeltaPlus^1$ can be drawn as a filled triangle:
+
   \begin{equation*}
     \begin{tikzcd}
-      \bullet \arrow[r, dash] & \bullet
-    \end{tikzcd}
-  \end{equation*}
-
-  $\DeltaHat^2$ can be drawn as:
-  \begin{equation*}
-    \begin{tikzcd}
-      & \bullet\arrow[dr, dash] & \\
-      \bullet\arrow[rr, dash]\arrow[ur, dash] && \bullet
+      & 2 \arrow[dr, dash] & \\
+      0 \arrow[rr, dash]\arrow[ur, dash] && 1
     \end{tikzcd}
@@
 \subsection{Semi-cubical sets}
-\begin{definition}[\Cube{n}]
-  \begin{equation*}
-    \Cube{n} := \I{n} = \sq{0, 1}^n
-  \end{equation*}
+\begin{definition}[\Cube{}]
+  \begin{align*}
+    \obj(\Cube{}) & := \Nat                                                                                                             \\
+    \hom(p, n)    & := \{(i_{p + 1}, \epsilon_{p + 1}) \ldots, (i_n, \epsilon_n) \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\}
+  \end{align*}
 \end{definition}
@@
 
-  and $\Cube{2}$ can be drawn as:
+  and $\Cube{2}$ can be drawn as a filled square:
 

### 2022-09-10 paper/paper.tex
paper: MAJ semi-{simplicial, cubical} sets

@@
 \newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
-\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
+\newcommand{\Cube}{\ensuremath{\boldsymbol{\square}}}
 \renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
@@
 
+\begin{definition}[$\Set_{\DeltaPlus}$]
+  We define the category of augmented semi-simplicial sets as the functor category:
+
+  \begin{equation*}
+    \Set_{\DeltaPlus} := \Set^{\op{\DeltaPlus}}
+  \end{equation*}
+\end{definition}
+
 \begin{example}[$\DeltaPlus^0$, $\DeltaPlus^1$]
@@
 \subsection{Semi-cubical sets}
-\begin{definition}[\Cube{}]
+\begin{definition}[\Cube]
   \begin{align*}
-    \obj(\Cube{}) & := \Nat                                                                                                             \\
-    \hom(p, n)    & := \{(i_{p + 1}, \epsilon_{p + 1}) \ldots, (i_n, \epsilon_n) \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\}
+    \obj(\Cube) & := \Nat                                                                                                             \\
+    \hom(p, n)  & := \{(i_{p + 1}, \epsilon_{p + 1}) \ldots, (i_n, \epsilon_n) \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\} \\
+    f \circ g   & := \text{concatenation of the sequences $f$ and $g$}
   \end{align*}
@@
 
-\begin{example}[$\Cube{0}$, $\Cube{1}$ and $\Cube{2}$]
-  $\Cube{0}$ can be drawn as:
+\begin{definition}[\CSet]
+  We define the category of semi-cubical sets as the functor category:
+
+  \begin{equation*}
+    \CSet := \Set^{\op{\Cube}}
+  \end{equation*}
+\end{definition}
+
+\begin{example}[$\Cube^0$, $\Cube^1$ and $\Cube^2$]
+  $\Cube^0$ can be drawn as:
 
@@
 
-  $\Cube{1}$ can be drawn as:
+  $\Cube^1$ can be drawn as:
 
@@
 
-  and $\Cube{2}$ can be drawn as a filled square:
+  and $\Cube^2$ can be drawn as a filled square:
 
@@
 
-Here, $\I{n}$ serves the purpose of \sq{n}, but this change will cascade into other definitions. In view of defining a category \CSet, we will restrict the morphisms in \Cube{}.
-
-\begin{definition}[\Cube{}]
-  \begin{align*}
-    \obj(\Cube{}) & := \I{n}                                           \\
-    \mor(\Cube{}) & := \delta^\epsilon_i : \I{n + 1} \rightarrow \I{n}
-  \end{align*}
-
-  where $\delta^\epsilon_i$ must satisfy the corresponding face map condition:
-
-  \begin{equation*}
-    \delta^\epsilon_i \delta^\omega_j = \delta^\omega_{j - 1} \delta^\epsilon_i
-  \end{equation*}
-
-  where $\epsilon$ and $\omega$ correspond to opposite faces.
-\end{definition}
-
-\begin{definition}[\CSet]
-  Just as in \SSet, we define semi-cubical sets as the functor category:
-
-  \begin{equation*}
-    \CSet := \Set^{\Cube{}^{op}}
-  \end{equation*}
-\end{definition}
+Here, $\I{n}$ serves the purpose of \sq{n}, but this change will cascade into other definitions. In view of defining a category \CSet, we will restrict the morphisms in \Cube.
 
 Or, in terms of objects and morphisms:
-
-\begin{definition}[$\CSet$ in terms of objects and morphisms]
-  \begin{align*}
-    \obj(\CSet) & := X_n                                                   \\
-    \mor(\CSet) & := X_\lambda, \text{where $\lambda$ is \Cube{}-morphism}
-  \end{align*}
-
-  where we term $X_n$ as the $n$-cubex, and $X_\lambda$ as the ``face map'', defined similarly:
-
-  \begin{align*}
-    X_n       & := X(\I{n}), \text{where X is the semi-cubical set} \\
-    X_\lambda & := X(\lambda)
-  \end{align*}
-\end{definition}
 

### 2022-09-15 paper/paper.tex
paper: polish
paper: MAJ

@@
 \subsection{Augmented semi-simplicial sets}
-We consider the category of augmented semi-simplices, which can be written in different ways, up to equivalence. We proceed to describe to combinatorial definition.
+We consider the category of augmented semi-simplices, which can be written in different ways, up to equivalence. Here, we describe the combinatorial definition.
+
+\begin{notation}[Sequences of integers]
+  We write $\{i_1, \ldots i_n\}$ for (ordered) sequences of integers. In particular, the empty sequence is written $\{\}$.
+\end{notation}
+
 \begin{definition}[\DeltaPlus]
@@
     \obj(\DeltaPlus)   & := \Nat                                                                                    \\
-    \hom(p, n)       & := \{i_{p + 1}, \ldots, i_n \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\} \\
-    f \circ g        & := \text{concatenation of the sequences $f$ and $g$}
+    \hom(p, n)         & := \{i_{p + 1}, \ldots, i_n \mid 0 < i_{p + 1} < \ldots < i_n \leq n\}                     \\
+    g \circ f          & := \{i_{j_{p + 1}}, \ldots, i_{j_n} \mid j_0 < i_{j_{p + 1}} < \ldots < i_{j_n} \leq j_n\} \\
+    \id \in \hom(n, n) & := \{\}                                                                                    \\
   \end{align*}
@@
 \subsection{Semi-cubical sets}
+\begin{notation}[Faces of cube]
+  We use $\epsilon$ to indicate opposite faces of a cube; it takes values $+$ or $-$.
+\end{notation}
+
 \begin{definition}[\Cube]
@@
     \hom(p, n)         & := \{(i_{p + 1}, \epsilon_{p + 1}) \ldots, (i_n, \epsilon_n) \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\} \\
-    f \circ g   & := \text{concatenation of the sequences $f$ and $g$}
+    g \circ f          & :=                                                                                                                  \\
+    \id \in \hom(n, n) & := \{\}                                                                                                             \\
   \end{align*}
@@
 
-Here, $\I{n}$ serves the purpose of \sq{n}, but this change will cascade into other definitions. In view of defining a category \CSet, we will restrict the morphisms in \Cube.
-
-Or, in terms of objects and morphisms:
-
 \begin{theorem}
@@
 \subsection{Generalization to \texorpdfstring{$\nu$}{nu}}
-
 \begin{table}[H]

### 2022-09-15 paper/paper.tex
paper: Borrow a couple of paras from param2

@@
 \newcommandx{\X}[3][1,2,3]{
-  \mathsf{\color{carolina}{X}}_{#1}^{#2}
+  \ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{#2}}
   \setkeys*[bonak]{X}{#3}
@@
 % Universe, referred to as U
-\newcommand{\U}[1]{\mathsf{\color{spanish-blue}{HSet}}_{#1}}
+\newcommand{\U}[1]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
 
 % The unit type
-\newcommand{\unittype}{\mathsf{unit}}
-\newcommand{\unitpoint}{\star}
+\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
+\newcommand{\unitpoint}{\ensuremath{\star}}
 
@@
 \newcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
+\newcommandx{\restrf}[1][1]{\restr{frame}[][#1][][][][][]}
 
@@
 
+The characterization of homogeneous $n$-boxes and full $n$-cubes can be obtained by a recursive definition reminiscent from parametricity: a full $(n+1)$-cube is obtained by taking two full $n$-cubes plus a third full $n$-cube connecting the two full $n$-cubes.
+Since it connects full $n$-cubes, the third full $n$-cube is actually a full $n$-cube over lines, so it is shifted by one relatively to the underlying relational structure.
+Let us write $\filler[n][p]$ for a full $(n-p)$-cube over points which are full $p$-cubes.
+Working informally, we thus have the equation:
+
+\begin{equation*}
+  \filler[n+1][0] \defeq (\filler[n][0] \times \filler[n][0]) \times \filler[n+1][1]
+\end{equation*}
+
+and, iterating and generalizing the process, we have actually:
+
+\begin{equation*}
+  \filler[n+1][p] \defeq (\filler[n][p] \times \filler[n][p]) \times \filler[n+1][p+1]
+\end{equation*}
+
+Now, the third cube (of dimension $((n+1)-(p+1))$, i.e. $n-p$) connects the first two $(n-p)$-cubes, so it has to depend on them. So, the equation is rather something of the form:
+
+\begin{equation*}
+  \filler[n+1][p] \defeq \Sigma a:(\filler[n][p] \times \filler[n][p]).\, \filler[n+1][p+1](a)
+\end{equation*}
+
+Then, by iterating, we obtain:
+
+\begin{equation*}
+  \filler[n+1][p] \defeq \Sigma a:(\filler[n][p] \times \filler[n][p]).\,
+  \Sigma b:(\filler[n][p+1](a) \times \filler[n][p+1](a)). \, \filler[n+1][p+2](a,b)
+\end{equation*}
+
+and so on.
+Thus, we need first to make the definition of $\filler[n][p]$ dependent over the part of the full cube built up to this point and secondly to accumulate this information.
+At the end of the accumulation of the process, i.e.
+at the time of building $\filler[n+1][n]$, a complete $n$-box will have been built.
+So, let us call $\filler[n][p]$ the partial $n$-box built up to the stage $p$ of the construction.
+Thus, we refine our definition into something like:
+
+\begin{equation*}
+  \begin{array}{lll}
+    \framep[n][0]                    & \defeq & \unittype                                                                       \\
+    \framep[n][p+1]                  & \defeq & \Sigma d:\framep[n][p] .\,(\filler[n][p](d) \times \filler[n][p](d))            \\
+    \\
+    \filler[n+1][p](d:\framep[n][p]) & \defeq & $\Sigma$ a:(\filler[n][p](d) \times \filler[n][p](d)) .\,\filler[n+1][p+1](d,a)
+  \end{array}
+\end{equation*}
+
+where $\unittype$ is a canonical singleton type used to initiate the
+construction of a list of pairs of $n$-cubes.
+
+Now, the two cubes $\filler[n][p](d)$ and $\filler[n][p](d)$ cannot be any cubes.
+They have to represent two opposite cubes, and we need a way to express this.
+The answer is simple.
+The partial box has two faces and these two cubes have to respectively fill the left face and the right face of the partial box.
+We thus have to rely on operations $\restrf[L]$ and $\restrf[R]$ which extract the sides of a box, leading to the refined definition:
+
+\begin{equation*}
+  \begin{array}{lll}
+    \filler[n+1][p](d:\framep[n][p]) & \defeq & \Sigma a:(\filler[n][p](\restrf[L](d)) \times \filler[n][p](\restrf[R](d))) .\, \filler[n+1][p+1](d,a)
+  \end{array}
+\end{equation*}
+
+The full explicit definition shall be given in the next sections but, to give an idea, let us show the structure of an $n$-cube for the first three dimensions.
+
 A full 2-cube is made of two full 1-cubes connected by a lifted 1-cube made of two lines connecting the former points and a square connecting the former lines:
+
 {\scriptsize
@@
 % Drop the unviverse letter
-\newcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
 \newcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}

### 2022-09-15 paper/paper.tex
paper: MAJ

--- 2022-09-15 paper/paper.tex
@@
 One step of parametricity can be seen as interpreting a point by a line.
-Iterating parametricity shall lead to map terms typed in a context with $n$ declarations of an axis as $n$-cubes.
+Iterating parametricity shall lead to map terms typed in a context with $n$ declarations of an axis as $n$-fillers.
 We shall interpret a
-typing derivation with $n$ axis declarations as an $n$-cube of typing derivations in the target.
+typing derivation with $n$ axis declarations as an $n$-filler of typing derivations in the target.
 For instance, a typing derivation with exactly one declaration of an axis will be interpreted by 3 typing derivations in the target, two of them typing points and the third one typing a proof, seen as a line, together with the fact that these two points are related (as in ordinary parametricity), while a typing derivation with $n$ declarations of an axis shall be interpreted as a $3^n$ derivations, split into $2^n$ derivations of points.
 
-A full 2-cube is made of two full 1-cubes connected by a lifted 1-cube made of two lines connecting the former points and a square connecting the former lines:
+The characterization of homogeneous $n$-frame and full $n$-fillers can be obtained by a recursive definition reminiscent from parametricity: a full $(n+1)$-filler is obtained by taking two full $n$-fillers plus a third full $n$-filler connecting the two full $n$-fillers.
+Since it connects full $n$-fillers, the third full $n$-filler is actually a full $n$-filler over lines, so it is shifted by one relatively to the underlying relational structure.
+Let us write $\filler[n][p]$ for a full $(n-p)$-filler over points which are full $p$-fillers.
+Working informally, we thus have the equation:
+
+\begin{equation*}
+  \filler[n+1][0] \defeq (\filler[n][0] \times \filler[n][0]) \times \filler[n+1][1]
+\end{equation*}
+
+and, iterating and generalizing the process, we have actually:
+
+\begin{equation*}
+  \filler[n+1][p] \defeq (\filler[n][p] \times \filler[n][p]) \times \filler[n+1][p+1]
+\end{equation*}
+
+Now, the third filler (of dimension $n - p$) connects the first two $(n - p)$-fillers, so it has to depend on them. So, the equation is rather something of the form:
+
+\begin{equation*}
+  \filler[n+1][p] \defeq \Sigma a:(\filler[n][p] \times \filler[n][p]).\, \filler[n+1][p+1](a)
+\end{equation*}
+
+Then, by iterating, we obtain:
+
+\begin{equation*}
+  \filler[n+1][p] \defeq \Sigma a:(\filler[n][p] \times \filler[n][p]).\,
+  \Sigma b:(\filler[n][p+1](a) \times \filler[n][p+1](a)). \, \filler[n+1][p+2](a,b)
+\end{equation*}
+
+and so on.
+Thus, we need first to make the definition of $\filler[n][p]$ dependent over the part of the full filler built up to this point and secondly to accumulate this information.
+At the end of the accumulation of the process, i.e.
+at the time of building $\filler[n+1][n]$, a complete $n$-frame will have been built.
+So, let us call $\filler[n][p]$ the partial $n$-frame built up to the stage $p$ of the construction.
+Thus, we refine our definition into something like:
+
+\begin{equation*}
+  \begin{array}{lll}
+    \framep[n][0]                    & \defeq & \unittype                                                                       \\
+    \framep[n][p+1]                  & \defeq & \Sigma d:\framep[n][p] .\,(\filler[n][p](d) \times \filler[n][p](d))            \\
+    \\
+    \filler[n+1][p](d:\framep[n][p]) & \defeq & $\Sigma$ a:(\filler[n][p](d) \times \filler[n][p](d)) .\,\filler[n+1][p+1](d,a)
+  \end{array}
+\end{equation*}
+
+where $\unittype$ is a canonical singleton type used to initiate the
+construction of a list of pairs of $n$-fillers.
+
+Now, the two fillers $\filler[n][p](d)$ and $\filler[n][p](d)$ cannot be any fillers.
+They have to represent two opposite fillers, and we need a way to express this.
+The answer is simple.
+The partial frame has two faces and these two fillers have to respectively fill the left face and the right face of the partial frame.
+We thus have to rely on operations $\restrf[L]$ and $\restrf[R]$ which extract the sides of a frame, leading to the refined definition:
+
+\begin{equation*}
+  \begin{array}{lll}
+    \filler[n+1][p](d:\framep[n][p]) & \defeq & \Sigma a:(\filler[n][p](\restrf[L](d)) \times \filler[n][p](\restrf[R](d))) .\, \filler[n+1][p+1](d,a)
+  \end{array}
+\end{equation*}
+
+The full explicit definition shall be given in the next sections but, to give an idea, let us show the structure of an $n$-filler for the first three dimensions.
+
+A full $2$-filler is made of two full $1$-fillers connected by a lifted $1$-filler made of two lines connecting the former points and a square connecting the former lines:
+
 {\scriptsize

### 2022-09-23 paper/paper.tex
paper: update diagrams; include UIP_refl

@@
 \usepackage[prefix=bonak]{art.cls/xkeymask}
+\usepackage[skip=0.4em]{parskip}
 
@@
 
-\iffalse
-  Our contribution is the following.
-We have modelled the core of semi-simplicial sets in a way that naturally generalizes to semi-cubical sets in type theory, and we call our generalization \emph{$\nu$-sets}.
-In contrast to the presheaf presentation of semi-cubical -based where the set of  that use a fibered representation, we use an indexed representation.
-Our work is, in principle axiom-free, although the accompanying artifact uses functional extensionality, and this requires disappears if $\nu$ is finite.
-\fi
-
 \begin{table}[H]
@@
 
-\begin{example}[$\DeltaPlus^0$, $\DeltaPlus^1$]
-  $\DeltaPlus^0$ can be drawn as:
+\begin{definition}[$\DeltaPlus^n$]
+  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as:
+\end{definition}
+
+We now illustrate the standard augmented $n$-semi-simplices for dimensions $1$, $2$, and $3$.
+
+\begin{example}[$\DeltaPlus^1$]
+  In dimension $1$, the standard augmented semi-simplex is simply the unit type:
 
@@
     \begin{tikzcd}
-      0 \arrow[r, dash] & 1
+      0
     \end{tikzcd}
   \end{equation*}
+\end{example}
 
-  $\DeltaPlus^1$ can be drawn as a filled triangle:
-
+\begin{example}[$\DeltaPlus^2$]
   \begin{equation*}
     \begin{tikzcd}
-      & 2 \arrow[dr, dash] & \\
-      0 \arrow[rr, dash]\arrow[ur, dash] && 1
+      \star0 \arrow[r, dash, "\star\star"] & 0\star
+    \end{tikzcd}
+  \end{equation*}
+\end{example}
+
+\begin{example}[$\DeltaPlus^3$]
+  \begin{equation*}
+    \begin{tikzcd}
+      & 00\star \arrow[dr, dash, "0\star\star"] & \\
+      \star00 \arrow[rr, dash, "\star\star0"]\arrow[ur, dash, "\star0\star"] && 0\star0
     \end{tikzcd}
@@
 
-\begin{example}[$\Cube^0$, $\Cube^1$ and $\Cube^2$]
+\begin{definition}[$\Cube^n$]
+  The standard semi-cube $\Cube^n$ is defined as:
+\end{definition}
+
+We now illustrate the standard $n$-semi-cubes for dimensions $0$, $1$, and $2$.
+
+\begin{example}[$\Cube^0$]
   $\Cube^0$ can be drawn as:
@@
     \begin{tikzcd}
-      0 \equiv 1
+      \{\}
     \end{tikzcd}
   \end{equation*}
+\end{example}
 
-  $\Cube^1$ can be drawn as:
-
+\begin{example}[$\Cube^1$]
   \begin{equation*}
     \begin{tikzcd}
-      0 \arrow[r, dash] & 1
+      0 \arrow[r, "\star", dash] & 1
     \end{tikzcd}
   \end{equation*}
+\end{example}
 
-  and $\Cube^2$ can be drawn as a filled square:
-
+\begin{example}[$\Cube^2$]
   \begin{equation*}
@@
 
-\begin{theorem}
+\begin{remark}
   $\CSet$ does not admit degeneracies.
-  \begin{proof}
-    The reader is advised to refer to \cite{Antolini00} for the proof.
-  \end{proof}
-\end{theorem}
+\end{remark}
 
@@
 
-In type theory, UIP can be proved on the unit type:
+An equivalent defintion of UIP is given by \textsf{UIP\_refl}:
 
 \begin{align*}
-  \mathsf{eq\_refl}        & : \forall x, x = x                                                    \\
-  \mathsf{UIP\_refl\_unit} & : \forall x : \unitpoint = \unitpoint, x = \mathsf{eq\_refl}          \\
-  \mathsf{UIP\_refl\_bool} & : \forall b : \mathsf{bool}, \forall x : b = b, x = \mathsf{eq\_refl} \\
+  \textsf{UIP\_refl} & : \forall x, \forall p : x = x, p = \textsf{eq\_refl } x
+\end{align*}
+
+In type theory, UIP can be proved on the unit type and bool type:
+
+\begin{align*}
+  \textsf{eq\_refl}        & : \forall x, x = x                                                    \\
+  \textsf{UIP\_refl\_unit} & : \forall u : \textsf{unit}, \forall x : u = u, x = \textsf{eq\_refl} \\
+  \textsf{UIP\_refl\_bool} & : \forall b : \textsf{bool}, \forall x : b = b, x = \textsf{eq\_refl} \\
 \end{align*}
@@
 
-  \bibitem[CubSet]{Antolini00}
-  Antolini, R. (2000). Cubical structures, homotopy theory. \emph{Annali di Matematica pura ed applicata, 178}(1), 317-324.
-
   \bibitem[Her]{Herbelin15}

### 2022-09-24 paper/paper.tex
paper: label diagrams; kerning problem with 0\star0
paper: fix kerning for \star
paper: fix simplicial dia

@@
 
+% Kerning for star
+\newcommand{\kstar}{{\star}}
+
 % The eqntable environment, displaying the various
@@
 
-We exploit the connection between iterated unary parametricity and augmented simplicial sets and between binary parametricity and cubical sets to present a uniform construction of both semi-simplicial semi-cubical sets obtained by applying simple rules iterating parametricity.
+We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both semi-simplicial semi-cubical sets obtained by applying simple rules iterating parametricity.
 In contrast to the presheaf presentation of semi-simplicial and semi-cubical sets, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
@@
     \begin{tikzcd}
-      \star0 \arrow[r, dash, "\star\star"] & 0\star
+      \kstar0 \arrow[r, dash, "\kstar\kstar"] & 0\kstar
     \end{tikzcd}
@@
     \begin{tikzcd}
-      & 00\star \arrow[dr, dash, "0\star\star"] & \\
-      \star00 \arrow[rr, dash, "\star\star0"]\arrow[ur, dash, "\star0\star"] && 0\star0
+      & |[alias=F]|00\kstar \arrow[ddr, dash, "0\kstar\kstar"] & \\\\
+      \kstar00 \arrow[rr, dash, "\kstar\kstar0"{name=T, below}]\arrow[uur, dash, "\kstar0\kstar"] && 0\kstar0 \\
+      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar\kstar" description]
     \end{tikzcd}
@@
     \begin{tikzcd}
-      0 \arrow[r, "\star", dash] & 1
+      0 \arrow[r, "\kstar", dash] & 1
     \end{tikzcd}
@@
     \begin{tikzcd}
-      (0, 1) \arrow[r, dash] & (1, 1) \arrow[d, dash] \\
-      (0, 0) \arrow[u, dash] & (1, 0) \arrow[l, dash]
+      (0, 1) \arrow[r, dash, "\kstar1"{name=F}] \arrow[d, dash, "0\kstar" left] & (1, 1) \arrow[d, dash, "1\kstar"] \\
+      (0, 0) \arrow[r, dash, "\kstar0"{name=T, below}] & (1, 0) \\
+      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar" description]
     \end{tikzcd}

### 2022-09-24 paper/paper.tex
paper: port over to using bibtex

@@
 
-In the context of typed functional programming, Reynolds' parametricity~\cite{Reynolds72} interprets types as relations characterizing the observational equality of programs of this type.
-Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{Johann17,Altenkirch15,Moulin16}.
-We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{Bernardy12,Moulin16}.
+In the context of typed functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational equality of programs of this type.
+Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{johann17,altenkirch14,moulin16}.
+We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{bernardy12,moulin16}.
 It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation from Hugo Moeneclaey}.
@@
     \graymidrule
-    Fibered & \cite{Cohen16} &             \\
+    Fibered & \cite{cchm} &             \\
     \graymidrule
@@
 
+\begin{remark}
+  $\CSet$ does not admit degeneracies.
+\end{remark}
+
 \begin{definition}[$\Cube^n$]
@@
 \end{example}
-
-\begin{remark}
-  $\CSet$ does not admit degeneracies.
-\end{remark}
 
@@
                    \end{array}$}
-    ~~~\parbox{2cm}{{\it additionally, each atomic component at dimension $n$ is a \filler[n][n]}} \\\\
+    ~~~\parbox{2cm}{additionally, each atomic component at dimension $n$ is a \filler[n][n]} \\\\
     [-1mm]\qquad\qquad\quad~~
@@
 The proof of $\cohf$ require a higher-dimensional coherence condition which we obtain by working in \texttt{HSet}.
-If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{Herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
+If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
 
@@
 
-\newpage
-\begin{thebibliography}{10}
-  \bibitem[Reynolds72]{Reynolds72}
-  Reynolds, J. C. (1972, August). Definitional interpreters for higher-order programming languages. \emph{In Proceedings of the ACM annual conference-Volume 2} (pp. 717-740).
-
-  \bibitem[Johann17]{Johann17}
-  Johann, P., \& Sojakova, K. (2017). Cubical categories for higher-dimensional parametricity. \emph{arXiv preprint arXiv:1701.06244}.
-
-  \bibitem[BernardyMoulin]{Bernardy12}
-  Bernardy, J. P., \& Moulin, G. (2012, June). A computational interpretation of parametricity. \emph{In 2012 27th Annual IEEE Symposium on Logic in Computer Science} (pp. 135-144). IEEE.
-
-  \bibitem[AltenkirchKaposi]{Altenkirch15}
-  Altenkirch, Thorsten, and Ambrus Kaposi. "A nominal syntax for internal parametricity." \emph{TYPES 2015} (2015): 21.
-
-  \bibitem[Moulin16]{Moulin16}
-  Moulin, G. (2016). \emph{Internalizing parametricity.} Department of Computer Science and Engineering, Chalmers University of Technology.
-
-  \bibitem[Bez]{Bezem14}
-  Bezem, M., Coquand, T., \& Huber, S.
-(2014, July).
-A model of type theory in cubical sets.
-\emph{In 19th International Conference on Types for Proofs and Programs (TYPES 2013)} (Vol.
-26, pp.
-107-128).
-Wadern, Germany: Schloss Dagstuhl–Leibniz Zentrum fuer Informatik.
-
-  \bibitem[CubAgda]{Vezzosi21}
-  Vezzosi, A., Mörtberg, A., \& Abel, A. (2021). Cubical Agda: a dependently typed programming language with univalence and higher inductive types. \emph{Journal of Functional Programming, 31}.
-
-  \bibitem[Takeuti–Gandy]{Barras15}
-  Barras, B., Coquand, T., \& Huber, S. (2015). A generalization of the Takeuti–Gandy interpretation. \emph{Mathematical structures in computer science}, 25(5), 1071-1099.
-
-  \bibitem[CCHM]{Cohen16}
-  Cohen, C., Coquand, T., Huber, S., \& Mörtberg, A. (2016). Cubical type theory: a constructive interpretation of the univalence axiom. \emph{arXiv preprint arXiv:1611.02108}.
-
-  \bibitem[Angiuli]{Angiuli17}
-  Carlo Angiuli, Guillaume Brunerie, Thierry Coquand, Kuen-Bang Hou (Favonia), Robert Harper, \& Daniel R. Licata. \emph{arXiv preprint}.
-
-  \bibitem[Fri]{Friedman08}
-  Friedman, G. (2008). An elementary illustrated introduction to simplicial sets. \emph{arXiv preprint arXiv:0809.4221}.
-
-  \bibitem[Rie]{Riehl11}
-  Riehl, E. (2011). A leisurely introduction to simplicial sets. \emph{Unpublished expository article available online from the author's web page}.
-
-  \bibitem[Her]{Herbelin15}
-  Herbelin, H. (2015). A dependently-typed construction of semi-simplicial types. \emph{Mathematical Structures in Computer Science, 25}(5), 1116-1131.
-
-  \bibitem[CoqInCoq]{Barras97}
-  Barras, B., \& Werner, B. (1997). Coq in coq. \emph{Available on the WWW.}
-\end{thebibliography}
+\bibliographystyle{alpha}
+\bibliography{paper}
 

### 2022-09-27 paper/paper.tex
paper: minor polish

@@
 \newcommand{\Cube}{\ensuremath{\boldsymbol{\square}}}
-\renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
 \newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
@@
 \newcommand{\pair}[2]{#1, #2}
+
+% These are renewed in tables, but let's define them now for in-document
+% typesetting
 \newcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
@@
 \begin{document}
-\thispagestyle{empty}
 \maketitle
@@
 \section{Overture}
-
 In the context of typed functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational equality of programs of this type.
@@
 Indeed, we plan to extend our work to do degeneracies in the future, but let us briefly explain the mathematical objects we have formalized.
+
+\begin{table}[H]
+  \begin{tabularx}{\linewidth}{p{.2\linewidth}|p{.4\linewidth}|p{.3\linewidth}}
+    \toprule
+    Value of $\nu$ & 1                               & 2                  \\
+    \graymidrule
+    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
 
@@
 
-\subsection{Generalization to \texorpdfstring{$\nu$}{nu}}
-\begin{table}[H]
-  \begin{tabularx}{\linewidth}{p{.2\linewidth}|p{.4\linewidth}|p{.3\linewidth}}
-    \toprule
-    Value of $\nu$ & 1                     & 2                  \\
-    \graymidrule
-    Interpretation & Semi-simplicial types & Semi-cubical types \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
-
 \section{Our construction}
@@
 Iterating parametricity shall lead to map terms typed in a context with $n$ declarations of an axis as $n$-fillers.
-We shall interpret a
-typing derivation with $n$ axis declarations as an $n$-filler of typing derivations in the target.
+We shall interpret a typing derivation with $n$ axis declarations as an $n$-filler of typing derivations in the target.
 For instance, a typing derivation with exactly one declaration of an axis will be interpreted by 3 typing derivations in the target, two of them typing points and the third one typing a proof, seen as a line, together with the fact that these two points are related (as in ordinary parametricity), while a typing derivation with $n$ declarations of an axis shall be interpreted as a $3^n$ derivations, split into $2^n$ derivations of points.
@@
 \begin{align*}
-  \mathsf{Dom} & : \mathsf{Type}                                          \\
-  \mathsf{UIP} & : \forall x y : \mathsf{Dom}, \forall p q : x = y, p = q
+  \textsf{Dom} & : \textsf{Type}                                          \\
+  \textsf{UIP} & : \forall x y : \textsf{Dom}, \forall p q : x = y, p = q
 \end{align*}

### 2022-09-27 paper/paper.tex
paper: MAJ

@@
 In the context of typed functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational equality of programs of this type.
-Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{johann17,altenkirch14,moulin16}.
+Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{johann17,altenkirch15,moulin16}.
 We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{bernardy12,moulin16}.
@@
 \subsection{Augmented semi-simplicial sets}
-We consider the category of augmented semi-simplices, which can be written in different ways, up to equivalence. Here, we describe the combinatorial definition.
+Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the points are additionally dependent on a ``color''.
+Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over a singleton set of colors.
+
+Let us associate dimension $0$ to colors; then, points are dimension $1$, lines are dimension $2$, and so on.
+There is hence a shift by one when compared to semi-simplicial sets.
+We can then draw augmented semi-simplicial sets like semi-simplicial sets, except for this shift by one.
+
+While semi-simplicial sets are presheaves over the semi-simplex category $\hat{\Delta}$, augmented semi-simplicial sets are presheaves over, what we will define as $\DeltaPlus$.
+There are different ways to define $\DeltaPlus$, upto equivalence, and we use a combinatorial definition; the reason for our choice is that this definition has a straightforward extension to semi-cubical sets.
 
 \begin{notation}[Sequences of integers]
-  We write $\{i_1, \ldots i_n\}$ for (ordered) sequences of integers. In particular, the empty sequence is written $\{\}$.
+  We write $\{i_1, \ldots i_n\}$ for sequences of integers. In particular, the empty sequence is written $\{\}$.
+
+  Additionally, we define $i :: \{j_1, \ldots, j_n\}$ to be $\{i, j_1, \ldots, j_n\}$, and $\uparrow \{i_1, \ldots, i_n\}$ to be $\{i_1 + 1, \ldots, i_n + 1\}$.
 \end{notation}
@@
 \begin{definition}[\DeltaPlus]
-  The category of augmented semi-simplices is defined in terms of objects and morphisms:
+  The category of augmented semi-simplices is defined in terms of objects, morphisms, composition, and identity.
 
@@
     \obj(\DeltaPlus) & := \Nat                                                                    \\
-    \hom(p, n)         & := \{i_{p + 1}, \ldots, i_n \mid 0 < i_{p + 1} < \ldots < i_n \leq n\}                     \\
-    g \circ f          & := \{i_{j_{p + 1}}, \ldots, i_{j_n} \mid j_0 < i_{j_{p + 1}} < \ldots < i_{j_n} \leq j_n\} \\
-    \id \in \hom(n, n) & := \{\}                                                                                    \\
+    \hom(p, n)       & := \{\{i_{p + 1}, \ldots, i_n\} \mid 0 < i_{p + 1} < \ldots < i_n \leq n\} \\
+    g \circ f        & :=
+    \begin{cases}
+      g                          & \text{if f = \{\}}                                    \\
+      f                          & \text{if g = \{\}}                                    \\
+      b :: (g \circ f')          & \text{if g = (a :: g'), f = (b :: f'), with b < a}    \\
+      a :: (g' \circ \uparrow f) & \text{if g = (a :: g'), f = (b :: f'), with b \geq a} \\
+    \end{cases}            \\
+    \id              & := \{\}
   \end{align*}
+
+  Composition can be shown to be associative.
 \end{definition}
@@
   \begin{equation*}
-    \Set_{\DeltaPlus} := \Set^{\op{\DeltaPlus}}
+    \Set_{\DeltaPlus} := \Set^{\DeltaPlus^{\mathsf{op}}}
   \end{equation*}
@@
   The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as:
+
+  \begin{align*}
+    \DeltaPlus^n    & : \Set_{\DeltaPlus}      \\
+    \DeltaPlus^n(p) & := \Hom(p, n)            \\
+    \DeltaPlus^n(f) & := \lambda g . g \circ f
+  \end{align*}
 \end{definition}
 
-We now illustrate the standard augmented $n$-semi-simplices for dimensions $1$, $2$, and $3$.
+The standard $0$-semi-simplex is just the set of colors. Standard augmented $n$-semi-simplices have a geometric interpretation for dimensions $1$, $2$, and $3$, and we illustrate them now.
 
@@
     \begin{tikzcd}
-      0
+      \star
     \end{tikzcd}
@@
 \begin{example}[$\DeltaPlus^2$]
+  In dimension $2$, it is
   \begin{equation*}
@@
   The standard semi-cube $\Cube^n$ is defined as:
+
+  \begin{align*}
+    \Cube^n    & : \CSet                  \\
+    \Cube^n(p) & := \Hom(p, n)            \\
+    \Cube^n(f) & := \lambda g . g \circ f
+  \end{align*}
 \end{definition}
 
-We now illustrate the standard $n$-semi-cubes for dimensions $0$, $1$, and $2$.
+Standard $n$-semi-cubes have a geometric interpreation, for dimensions $0$, $1$, and $2$, and we illustrate them now.
 
 \begin{example}[$\Cube^0$]
-  $\Cube^0$ can be drawn as:
+  $\Cube^0$ is the empty set:
 

### 2022-09-27 paper/paper.tex
paper: MAJ

@@
       f                          & \text{if g = \{\}}                                          \\
-      b :: (g \circ f')          & \text{if g = (a :: g'), f = (b :: f'), with b < a}    \\
-      a :: (g' \circ \uparrow f) & \text{if g = (a :: g'), f = (b :: f'), with b \geq a} \\
+      b :: (g \circ f')          & \text{if $g = (a :: g')$, $f = (b :: f')$, with $b < a$}    \\
+      a :: (g' \circ \uparrow f) & \text{if $g = (a :: g')$, $f = (b :: f')$, with $b \geq a$} \\
     \end{cases}      \\
@@
 
-  Composition can be shown to be associative.
+  Evidently, $\id$ is neutral. Further, composition can be shown to be associative.
+\end{definition}
+
+\begin{definition}[Alternative definition of $\DeltaPlus$]
+  \begin{align*}
+    \obj(\DeltaPlus) & := \Nat                                                                     \\
+    \hom(p, n)       & := \{l \in \{0, \kstar\}^n \mid \text{number of $\kstar$ in l = p}\}        \\
+    g \circ f        & :=
+    \begin{cases}
+      f                  & \text{if $g = \{\}$}                                                      \\
+      0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
+      a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
+    \end{cases} \\
+    \id              & := \{\kstar, \ldots, \kstar\} \text{ $n$ times}
+  \end{align*}
+
+  Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
 \end{definition}
@@
 \begin{example}[$\DeltaPlus^1$]
-  In dimension $1$, the standard augmented semi-simplex is simply the unit type:
+  In dimension $1$, the standard augmented semi-simplex can be pictured as a point, where the color is kept implicit.
+This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$:
 
@@
     \begin{tikzcd}
-      \star
+      \kstar
     \end{tikzcd}
@@
 \begin{example}[$\DeltaPlus^2$]
-  In dimension $2$, it is
+  In dimension $2$,
   \begin{equation*}
@@
 \subsection{Semi-cubical sets}
-\begin{notation}[Faces of cube]
-  We use $\epsilon$ to indicate opposite faces of a cube; it takes values $+$ or $-$.
-\end{notation}
+\begin{definition}[\Cube]
+  $\Cube$ is defined similarly to $\DeltaPlus$, except that we take $0$, $1$ and $\star$, instead of $0$ and $\kstar$. We use $0$ and $1$ to indicate opposite faces of a cube.
 
-\begin{definition}[\Cube]
   \begin{align*}
-    \obj(\Cube)        & := \Nat                                                                                                             \\
-    \hom(p, n)         & := \{(i_{p + 1}, \epsilon_{p + 1}) \ldots, (i_n, \epsilon_n) \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\} \\
-    g \circ f          & :=                                                                                                                  \\
-    \id \in \hom(n, n) & := \{\}                                                                                                             \\
+    \obj(\DeltaPlus) & := \Nat                                                                     \\
+    \hom(p, n)       & := \{l \in \{0, 1, \kstar\}^n \mid \text{number of $\kstar$ in l = p}\}     \\
+    g \circ f        & :=
+    \begin{cases}
+      f                  & \text{if $g = \{\}$}                                                      \\
+      0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
+      a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
+    \end{cases} \\
+    \id              & := \{\kstar, \ldots, \kstar\} \text{ $n$ times}
   \end{align*}
@@
 \begin{example}[$\Cube^0$]
-  $\Cube^0$ is the empty set:
+  $\Cube^0$ is $\Hom(0, 0)$, or the empty set:
 
@@
 \begin{example}[$\Cube^1$]
+  $\Cube^1$ is two points and a line:
   \begin{equation*}

### 2022-10-03 paper/paper.tex
paper: MAJ

@@
 It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
-What we have formalized is \emph{semi-simplicial} sets, and \emph{semi-cubical} sets, which is to say that they are the usual simplicial sets and cubical sets, minus the degeneracies.
-Indeed, we plan to extend our work to do degeneracies in the future, but let us briefly explain the mathematical objects we have formalized.
+What we have formalized is \emph{augmented semi-simplicial} sets, and \emph{semi-cubical} sets.
+We will proceed to explain the mathematical objects we have formalized.
 
@@
 
-While semi-simplicial sets are presheaves over the semi-simplex category $\hat{\Delta}$, augmented semi-simplicial sets are presheaves over, what we will define as $\DeltaPlus$.
+While ordinary semi-simplicial sets are presheaves over the semi-simplex category $\hat{\Delta}$, augmented semi-simplicial sets are presheaves over, what we will define as $\DeltaPlus$.
 There are different ways to define $\DeltaPlus$, upto equivalence, and we use a combinatorial definition; the reason for our choice is that this definition has a straightforward extension to semi-cubical sets.
@@
   We write $\{i_1, \ldots i_n\}$ for sequences of integers. In particular, the empty sequence is written $\{\}$.
+\end{notation}
 
-  Additionally, we define $i :: \{j_1, \ldots, j_n\}$ to be $\{i, j_1, \ldots, j_n\}$, and $\uparrow \{i_1, \ldots, i_n\}$ to be $\{i_1 + 1, \ldots, i_n + 1\}$.
+We introduce two additional notations for working with sequences of integers.
+
+\begin{notation}[::]
+  We define $i :: \{j_1, \ldots, j_n\}$ to be $\{i, j_1, \ldots, j_n\}$.
+\end{notation}
+
+\begin{notation}[$\uparrow$]
+  Let us write $\uparrow \{i_1, \ldots, i_n\}$ to denote $\{i_1 + 1, \ldots, i_n + 1\}$.
 \end{notation}
@@
 
-The standard $0$-semi-simplex is just the set of colors. Standard augmented $n$-semi-simplices have a geometric interpretation for dimensions $1$, $2$, and $3$, and we illustrate them now.
+The standard augmented $0$-semi-simplex is a singleton of one color. Standard augmented $n$-semi-simplices have a geometric interpretation, and we illustrate them for dimensions $1$, $2$, and $3$.
 
 \begin{example}[$\DeltaPlus^1$]
-  In dimension $1$, the standard augmented semi-simplex can be pictured as a point, where the color is kept implicit.
+  In dimension $1$, the standard augmented semi-simplex can be pictured as a point, where the unique color is kept implicit; the unique morphism in $\Hom(0, 1)$ is not pictured.
 This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$:
@@
 \begin{example}[$\DeltaPlus^2$]
-  In dimension $2$,
+  In dimension $2$, the standard augmented semi-simplex is drawn as two points, given by $\Hom(1, 2)$, along with a line connecting them, given by $\Hom(2, 2)$.
+Again, the unique morphim in $\Hom(0, 2)$ is not pictured.
+
   \begin{equation*}
@@
 \begin{example}[$\DeltaPlus^3$]
+  $\DeltaPlus^3$ is drawn as three points, given by $\Hom(1, 3)$, three lines connecting them, given by $\Hom(2, 3)$, and a filler given by $\Hom(3, 3)$.
+
   \begin{equation*}
@@
 \begin{definition}[\Cube]
-  $\Cube$ is defined similarly to $\DeltaPlus$, except that we take $0$, $1$ and $\star$, instead of $0$ and $\kstar$. We use $0$ and $1$ to indicate opposite faces of a cube.
+  $\Cube$ is defined similarly to $\DeltaPlus$, except that we take sequences of $0$, $1$ and $\star$, instead of sequences of $0$ and $\kstar$.
+We use $0$ and $1$ to indicate opposite faces of a cube.
 
   \begin{align*}
-    \obj(\DeltaPlus) & := \Nat                                                                     \\
-    \hom(p, n)       & := \{l \in \{0, 1, \kstar\}^n \mid \text{number of $\kstar$ in l = p}\}     \\
+    \obj(\Cube) & := \Nat                                                                                \\
+    \hom(p, n)  & := \{l \in \{0, 1, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}              \\
     g \circ f   & :=
@@
       f                  & \text{if $g = \{\}$}                                                            \\
-      0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
-      a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
+      a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a = 0$ or $1$}                          \\
+      a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$, $1$, or $\kstar$} \\
     \end{cases} \\
@@
   \end{align*}
+
+  Again, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
 \end{definition}
@@
 \end{definition}
-
-\begin{remark}
-  $\CSet$ does not admit degeneracies.
-\end{remark}
 
@@
 
-Standard $n$-semi-cubes have a geometric interpreation, for dimensions $0$, $1$, and $2$, and we illustrate them now.
+Standard $n$-semi-cubes have a geometric interpretion, which we illustrate for dimensions $0$, $1$, and $2$.
 
 \begin{example}[$\Cube^0$]
-  $\Cube^0$ is $\Hom(0, 0)$, or the empty set:
+  $\Cube^0$ is $\Hom(0, 0)$, or the singleton set of the empty sequence:
 
@@
 \begin{example}[$\Cube^1$]
-  $\Cube^1$ is two points and a line:
+  $\Cube^1$ is two points, given by $\Hom(0, 1)$ and a line, given by $\Hom(1, 1)$:
+
   \begin{equation*}
@@
 \begin{example}[$\Cube^2$]
+  $\Cube^2$ is four points, given by $\Hom(0, 2)$, four lines connecting the four points, given by $\Hom(1, 2)$, and a filler, given by $\Hom(2, 2)$:
+
   \begin{equation*}
     \begin{tikzcd}
-      (0, 1) \arrow[r, dash, "\kstar1"{name=F}] \arrow[d, dash, "0\kstar" left] & (1, 1) \arrow[d, dash, "1\kstar"] \\
-      (0, 0) \arrow[r, dash, "\kstar0"{name=T, below}] & (1, 0) \\
+      01 \arrow[r, dash, "\kstar1"{name=F}] \arrow[d, dash, "0\kstar" left] & 11 \arrow[d, dash, "1\kstar"] \\
+      00 \arrow[r, dash, "\kstar0"{name=T, below}] & 10 \\
       \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar" description]

### 2022-10-03 paper/paper.tex
paper: MAJ

@@
 
-\begin{table}[H]
-  \begin{tabularx}{\linewidth}{p{.2\linewidth}|p{.4\linewidth}|p{.3\linewidth}}
-    \toprule
-    Value of $\nu$ & 1                               & 2                  \\
-    \graymidrule
-    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
-
 \subsection{Augmented semi-simplicial sets}
@@
 
+\subsection{Generalization to \texorpdfstring{$\nu$}{ν}-sets}
+Let us call $\nu$-sets, the straightforward generalization of augmented semi-simplicial sets and semi-cubical sets to an arbirary arity, where morphisms are sequences of elements of an arbirary set $\nu$, extended with $\kstar$.
+Then, we observe:
+
+\begin{table}[H]
+  \begin{tabularx}{\linewidth}{p{.2\linewidth}|p{.4\linewidth}|p{.3\linewidth}}
+    \toprule
+    Value of $\nu$ & 1                               & 2                  \\
+    \graymidrule
+    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
+
 \section{Our construction}
@@
 
+\subsection{Homotopy type theory}
+Homotopy type theory (HoTT) is a logical foundation based on Martin-Löf type theory and the univalence axiom~\cite{hottbook}.
+HoTT is based on the notion of a basic \textsf{Type}, and the notion of sets can be recovered as \textsf{HSet}, where \texttt{HSet} is a straightforward packaging of two fields:
+
+\begin{align*}
+  \textsf{Dom} & : \textsf{Type}                                          \\
+  \textsf{UIP} & : \forall x y : \textsf{Dom}, \forall p q : x = y, p = q
+\end{align*}
+
+In the \texttt{HSet} universe, three properties hold:
+
+\begin{enumerate}
+  \item[(i)] UIP holds on the unit type.
+  \item[(ii)] UIP propagates to $\Sigma$-types.
+  \item[(iii)] UIP propagates to $\Pi$-types, with some additional functional extensionality axioms.
+\end{enumerate}
+
+\textsf{HSet} provides us a form of unicity of identity of proofs (UIP), which is a form of proof irrelevance:
+
+\begin{align*}
+  \forall x y, \forall p q : x = y, p = q
+\end{align*}
+
+which is to say that any two proofs of \emph{equality} of the same two types are \emph{equal}. In other words, the proofs cannot be distinguished from one another.
+
+An equivalent defintion of UIP is given by \textsf{UIP\_refl}:
+
+\begin{align*}
+  \textsf{UIP\_refl} & : \forall x, \forall p : x = x, p = \textsf{eq\_refl } x
+\end{align*}
+
+In type theory, UIP can be proved on the unit type and bool type:
+
+\begin{align*}
+  \textsf{eq\_refl}        & : \forall x, x = x                                                    \\
+  \textsf{UIP\_refl\_unit} & : \forall u : \textsf{unit}, \forall x : u = u, x = \textsf{eq\_refl} \\
+  \textsf{UIP\_refl\_bool} & : \forall b : \textsf{bool}, \forall x : b = b, x = \textsf{eq\_refl} \\
+\end{align*}
+
 \subsection{Fibered versus indexed representation}
-The fibered representation can be illustrated as:
+It is well-known in set theory, that families of small sets can be represented in a fibered or indexed way.
+In the fibered way, a family over $T$ is represented a pair of a set $S$, and a function $S \rightarrow T$.
+The function classifies the original set into fibers.
+In contrast, in the indexed way, a family over $T$ is represented as a functional relation with domain $T$, which itself, by replacement axiom, is a set.
+
+In category theory, the correspondence between fibered and indexed way, manifests as the correspondence between Grothendieck fibrations and pseudofunctors, of which a particular instance is the correspondence between discrete fibrations and presheaves, or even between discrete fibrations over sets and families of sets.
+
+In HoTT, the latter correspondence can be expressed, for $T: \textsf{Type}$, as an equivalence between $\Sigma S: \textsf{Type}\;.\;S \rightarrow T$ and $T \rightarrow \textsf{Type}$, which can be proved using univalence.
+This correspondence also holds on \textsf{HSet}, for $T: \textsf{HSet}$:
+
+\begin{equation*}
+  \Sigma S: \textsf{HSet}\;.\;S\rightarrow T \simeq T \rightarrow \textsf{HSet}
+\end{equation*}
+
+Let us now come back to cubical sets. A cubical set can be represented as a sequence of fibrations, together with appropriate coherence conditions:
 
@@
 
-The indexed representation can be illustrated as:
+We can iteratively apply the above correspondence to obtain an indexed representation of cubical sets:
 
@@
 
-One way to obtain one construction from the other is via the \emph{Grothendieck construction}, although this is not relevant to our work.
+The focus of our work has been to formally define such an indexed presentation of not just semi-cubical, but more generally, $\nu$-sets.
 
@@
 
-\section{Reasoning about sets in type theory}
-Since proof irrelevance is an inherent part of set theory and first-order logic, and proof irrelevance is \emph{extensional} in type theory, we work in a universe known as \texttt{HSet}, which we describe shortly.
-
-\subsection{Unicity of identity proofs}
-UIP is a flavor of proof-irrelevance:
-
-\begin{align*}
-  \forall x y, \forall p q : x = y, p = q
-\end{align*}
-
-which is to say that any two proofs of \emph{equality} of the same two types are \emph{equal}. In other words, the proofs cannot be distinguished from one another.
-
-An equivalent defintion of UIP is given by \textsf{UIP\_refl}:
-
-\begin{align*}
-  \textsf{UIP\_refl} & : \forall x, \forall p : x = x, p = \textsf{eq\_refl } x
-\end{align*}
-
-In type theory, UIP can be proved on the unit type and bool type:
-
-\begin{align*}
-  \textsf{eq\_refl}        & : \forall x, x = x                                                    \\
-  \textsf{UIP\_refl\_unit} & : \forall u : \textsf{unit}, \forall x : u = u, x = \textsf{eq\_refl} \\
-  \textsf{UIP\_refl\_bool} & : \forall b : \textsf{bool}, \forall x : b = b, x = \textsf{eq\_refl} \\
-\end{align*}
-
-\subsection{HSet}
-\texttt{HSet} provides us a restricted setting of UIP, and our implementation of \texttt{HSet} is a straightforward packaging of two fields:
-
-\begin{align*}
-  \textsf{Dom} & : \textsf{Type}                                          \\
-  \textsf{UIP} & : \forall x y : \textsf{Dom}, \forall p q : x = y, p = q
-\end{align*}
-
-In the \texttt{HSet} universe, three properties hold:
-
-\begin{enumerate}
-  \item[(i)] UIP holds on the unit type.
-  \item[(ii)] UIP propagates to $\Sigma$-types.
-  \item[(iii)] UIP propagates to $\Pi$-types, with some additional functional extensionality axioms.
-\end{enumerate}
-
 \section{Type-theoretic construction of \texorpdfstring{$\nu$}{nu}-sets}
@@
 \renewcommand*{\lab}{tab:faces}
-\input{tab-faces.tex}
+\input{tab-faces-ett.tex}
 
@@
 \renewcommand*{\lab}{tab:coh}
-\input{tab-coh.tex}
+\input{tab-coh-ett.tex}
 

### 2022-10-04 paper/paper.tex
paper: hottbook bib

@@
 Homotopy type theory (HoTT) is a logical foundation based on Martin-Löf type theory and the univalence axiom~\cite{hottbook}.
-HoTT is based on the notion of a basic \textsf{Type}, and the notion of sets can be recovered as \textsf{HSet}, where \texttt{HSet} is a straightforward packaging of two fields:
+HoTT is based on the notion of a basic \textsf{Type}, and the notion of sets can be recovered as \textsf{HSet}, where \textsf{HSet} is a straightforward packaging of two fields:
 
@@
 
-In the \texttt{HSet} universe, three properties hold:
+In the \textsf{HSet} universe, three properties hold:
 
@@
 
-In HoTT, the latter correspondence can be expressed, for $T: \textsf{Type}$, as an equivalence between $\Sigma S: \textsf{Type}\;.\;S \rightarrow T$ and $T \rightarrow \textsf{Type}$, which can be proved using univalence.
+The latter correspondence can be expressed in HoTT, for $T: \textsf{Type}$, as an equivalence between $\Sigma S: \textsf{Type}\;.\;S \rightarrow T$ and $T \rightarrow \textsf{Type}$, which can be proved using univalence.
 This correspondence also holds on \textsf{HSet}, for $T: \textsf{HSet}$:

### 2022-10-10 paper/paper.tex
paper: macros; minor polish

@@
 % Universe, referred to as U
-\newcommand{\U}[1]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
+\newcommand{\U}[1][]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
 
@@
 \newcommand{\pair}[2]{#1, #2}
+\newcommand{\Type}{\textsf{Type}}
+\newcommand{\Dom}{\textsf{Dom}}
+\newcommand{\UIP}{\textsf{UIP}}
 
@@
 Homotopy type theory (HoTT) is a logical foundation based on Martin-Löf type theory and the univalence axiom~\cite{hottbook}.
-HoTT is based on the notion of a basic \textsf{Type}, and the notion of sets can be recovered as \textsf{HSet}, where \textsf{HSet} is a straightforward packaging of two fields:
+HoTT is based on the notion of a basic Type, and the notion of sets can be recovered as \U, where $\U$ is a straightforward packaging of two fields:
 
 \begin{align*}
-  \textsf{Dom} & : \textsf{Type}                                          \\
-  \textsf{UIP} & : \forall x y : \textsf{Dom}, \forall p q : x = y, p = q
+  \Dom & : \Type                                          \\
+  \UIP & : \forall x y : \Dom, \forall p q : x = y, p = q
 \end{align*}
 
-In the \textsf{HSet} universe, three properties hold:
+In the $\U$ universe, three properties hold:
 
@@
 
-\textsf{HSet} provides us a form of unicity of identity of proofs (UIP), which is a form of proof irrelevance:
+$\U$ provides us a form of unicity of identity of proofs (UIP), which is a form of proof irrelevance:
 
@@
 
-The latter correspondence can be expressed in HoTT, for $T: \textsf{Type}$, as an equivalence between $\Sigma S: \textsf{Type}\;.\;S \rightarrow T$ and $T \rightarrow \textsf{Type}$, which can be proved using univalence.
-This correspondence also holds on \textsf{HSet}, for $T: \textsf{HSet}$:
+The latter correspondence can be expressed in HoTT, for $T: \Type$, as an equivalence between $\Sigma S: \Type\;.\;S \rightarrow T$ and $T \rightarrow \Type$, which can be proved using univalence.
+This correspondence also holds on \U, for $T: \U$:
 
 \begin{equation*}
-  \Sigma S: \textsf{HSet}\;.\;S\rightarrow T \simeq T \rightarrow \textsf{HSet}
+  \Sigma S: \U\;.\;S\rightarrow T \simeq T \rightarrow \U
 \end{equation*}
 
-Let us now come back to cubical sets. A cubical set can be represented as a sequence of fibrations, together with appropriate coherence conditions:
+Let us now come back to cubical sets. A cubical set can be represented as a sequence of fibrations, together with appropriate coherence conditions.
 
@@
   \begin{tikzcd}
-    X_0 : \U{} & X_1 : \U{} \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \U{} \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
+    X_0 : \U & X_1 : \U \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \U \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
   \end{tikzcd}
@@
 
-We can iteratively apply the above correspondence to obtain an indexed representation of cubical sets:
+We can iteratively apply the above correspondence to obtain an indexed representation of cubical sets.
 
 \begin{align*}
-  X_0 & : \U{}                                                                                                              \\
-  X_1 & : X_0 \times X_0 \rightarrow \U{}                                                                                   \\
-  X_2 & : \forall a b c d, X_1 (a, b) \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \rightarrow X_1 (c, d) \rightarrow \U{} \\
+  X_0 & : \U                                                                                                              \\
+  X_1 & : X_0 \times X_0 \rightarrow \U                                                                                   \\
+  X_2 & : \forall a b c d, X_1 (a, b) \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \rightarrow X_1 (c, d) \rightarrow \U \\
   \ldots
@@
 
-The proof of $\cohf$ require a higher-dimensional coherence condition which we obtain by working in \texttt{HSet}.
+The proof of $\cohf$ require a higher-dimensional coherence condition which we obtain by working in \U.
 If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).

### 2022-10-10 paper/paper.tex
paper: MAJ

@@
 \newcommandx{\X}[3][1,2,3]{
-  \ensuremath{\mathsf{\color{carolina}{X}}_{#1}^{#2}}
+  \ensuremath{{\color{carolina}{\nu\textsf{Set}}}_{#1}^{#2}}
   \setkeys*[bonak]{X}{#3}
@@
 % Universe, referred to as U
-\newcommand{\U}[1][]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
+\newcommandx{\U}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
 
@@
 \newcommandx{\restrf}[1][1]{\restr{frame}[][#1][][][][][]}
+\newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}
 
@@
 The outline of the paper is as follows.
-First, we briefly describe semi-simplicial and semi-cubical sets, as it appears in mathematical literature, and our generalization to $\nu$-sets.
+First, we briefly describe semi-simplicial and semi-cubical sets, and our generalization to $\nu$-sets.
 We then proceed to explain our construction, with the help of diagrams.
@@
 \subsection{Augmented semi-simplicial sets}
-Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the points are additionally dependent on a ``color''.
+Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``color''.
 Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over a singleton set of colors.
@@
 \begin{example}[$\DeltaPlus^1$]
-  In dimension $1$, the standard augmented semi-simplex can be pictured as a point, where the unique color is kept implicit; the unique morphism in $\Hom(0, 1)$ is not pictured.
+  In dimension $1$, the standard augmented semi-simplex can be pictured as a point, colored black, corresponding to the unique morphism in $\Hom(0, 1)$.
 This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$:
@@
   In dimension $2$, the standard augmented semi-simplex is drawn as two points, given by $\Hom(1, 2)$, along with a line connecting them, given by $\Hom(2, 2)$.
-Again, the unique morphim in $\Hom(0, 2)$ is not pictured.
+We use the color black to denote the unique morphims in $\Hom(0, 1)$ and $\Hom(0, 2)$.
 
@@
 
-\subsection{Iterated parametricity}
-One step of parametricity can be seen as interpreting a point by a line.
-Iterating parametricity shall lead to map terms typed in a context with $n$ declarations of an axis as $n$-fillers.
-We shall interpret a typing derivation with $n$ axis declarations as an $n$-filler of typing derivations in the target.
-For instance, a typing derivation with exactly one declaration of an axis will be interpreted by 3 typing derivations in the target, two of them typing points and the third one typing a proof, seen as a line, together with the fact that these two points are related (as in ordinary parametricity), while a typing derivation with $n$ declarations of an axis shall be interpreted as a $3^n$ derivations, split into $2^n$ derivations of points.
+\subsection{Intuition for our formal construction}
+To assign $X_0$, $X_1$, $X_2$, $\ldots$ in the above indexed representation types, we need to exhibit a recursive definition over our building blocks, which we will call $\framep$, $\layer$, and $\filler$.
+As a first step, we assign every $X_n$ the type $\fullframe[n] \rightarrow \U$, which is a form of uncurrification (i.e.
+the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$).
+The question is then to find the recursive recipe defining $\fullframe[n]$.
+First, $\fullframe[n]$ depends on all $X_i$ upto $n - 1$.
+So, we need to package up $X_i$, for $i < n$, into a type, which we call $\X[][<n][]$.
+This allows us to give the type $\X[][<n][] \rightarrow \U$ to $\fullframe[n]$.
+For $D: \X[][<n][]$, the initial prefix of $\X[][0][]$ to $\X[][n - 1][]$, $\X[][n][]$ has type $\fullframe[n](D) \rightarrow \U$.
+We shall give the full definition of $\fullframe[n]$ shortly, but first assuming $\fullframe[n]$ is defined, we are able to take the coinductive limit of the $\X[][<n][]$, as shown in \ref{tab:coind}, therefore fully characterizing the indexed definition of $\nu$-sets.
 
@@
 at the time of building $\filler[n+1][n]$, a complete $n$-frame will have been built.
-So, let us call $\filler[n][p]$ the partial $n$-frame built up to the stage $p$ of the construction.
+So, let us call $\framep[n][p]$ the partial $n$-frame built up to the stage $p$ of the construction.
 Thus, we refine our definition into something like:
@@
 
-\section{Type-theoretic construction of \texorpdfstring{$\nu$}{nu}-sets}
+\subsection{Formal construction of \texorpdfstring{$\nu$}{nu}-sets}
 % Abbreviated tables in this section
@@
 % For just the second table, keep the universe letter in fullframe
-\newcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
+\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
 

### 2022-10-10 paper/paper.tex
paper: polish

@@
 \subsection{Intuition for our formal construction}
-To assign $X_0$, $X_1$, $X_2$, $\ldots$ in the above indexed representation types, we need to exhibit a recursive definition over our building blocks, which we will call $\framep$, $\layer$, and $\filler$.
-As a first step, we assign every $X_n$ the type $\fullframe[n] \rightarrow \U$, which is a form of uncurrification (i.e.
-the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$).
+To assign $X_0, X_1, X_2, \ldots$ in the above indexed representation types, we need to exhibit a recursive definition over our building blocks, which we will call $\framep$, $\layer$, and $\filler$.
+A $\framep$ is a boundary of a standard form (simplex, cube, etc.), a $\filler$ is a filled $\framep$; both of them can be decomposed into $\layer$.
+
+As a first step, we assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a : A, (B a \rightarrow C)$ and $(\Sigma a : A, B a) \rightarrow C$.
 The question is then to find the recursive recipe defining $\fullframe[n]$.
@@
 This allows us to give the type $\X[][<n][] \rightarrow \U$ to $\fullframe[n]$.
-For $D: \X[][<n][]$, the initial prefix of $\X[][0][]$ to $\X[][n - 1][]$, $\X[][n][]$ has type $\fullframe[n](D) \rightarrow \U$.
-We shall give the full definition of $\fullframe[n]$ shortly, but first assuming $\fullframe[n]$ is defined, we are able to take the coinductive limit of the $\X[][<n][]$, as shown in \ref{tab:coind}, therefore fully characterizing the indexed definition of $\nu$-sets.
+Then, for $D: \X[][<n][]$, representing an initial prefix of $X_0, X_1, \ldots X_{n - 1}$, the indexed set $X_n$ has type $\fullframe[n](D) \rightarrow \U$.
+We shall give the full definition of $\fullframe[n]$ shortly, but first, assuming $\fullframe[n]$ is defined, we are able to take the coinductive limit of the $\X[][<n][]$, as shown in \ref{tab:coind}, therefore fully characterizing the indexed definition of $\nu$-sets.
 
-The characterization of homogeneous $n$-frame and full $n$-fillers can be obtained by a recursive definition reminiscent from parametricity: a full $(n+1)$-filler is obtained by taking two full $n$-fillers plus a third full $n$-filler connecting the two full $n$-fillers.
-Since it connects full $n$-fillers, the third full $n$-filler is actually a full $n$-filler over lines, so it is shifted by one relatively to the underlying relational structure.
-Let us write $\filler[n][p]$ for a full $(n-p)$-filler over points which are full $p$-fillers.
+The characterization of $\framep[n]$ and $\filler[n]$ can be obtained by a recursive definition reminiscent from parametricity translation \cite{reynolds72}: a $\filler[n+1]$ is obtained by taking two $\filler[n]$ plus a third $\filler[n]$ connecting the two full $\filler[n]$.
+Since it connects $\filler[n]$, the third $\filler[n]$ is actually a $\filler[n]$ over lines, so it is shifted by one relatively to the underlying relational structure.
+Let us write $\filler[n][p]$ for a $\filler[n - p]$ over points which are $\filler[p]$.
 Working informally, we thus have the equation:
-
-\begin{equation*}
-  \filler[n+1][0] \defeq (\filler[n][0] \times \filler[n][0]) \times \filler[n+1][1]
-\end{equation*}
-
-and, iterating and generalizing the process, we have actually:
 
@@
 
-Now, the third filler (of dimension $n - p$) connects the first two $(n - p)$-fillers, so it has to depend on them. So, the equation is rather something of the form:
+Now, the third filler (of dimension $n - p$) connects the first two $\filler[n-p]$, so it has to depend on them. So, the equation is rather something of the form:
 
@@
 and so on.
-Thus, we need first to make the definition of $\filler[n][p]$ dependent over the part of the full filler built up to this point and secondly to accumulate this information.
+Thus, we need first to make the definition of $\filler[n][p]$ dependent over the part of the filler built up to this point and secondly to accumulate this information.
 At the end of the accumulation of the process, i.e.
-at the time of building $\filler[n+1][n]$, a complete $n$-frame will have been built.
-So, let us call $\framep[n][p]$ the partial $n$-frame built up to the stage $p$ of the construction.
+at the time of building $\filler[n+1][n]$, a complete $\framep[n]$ will have been built.
+So, let us call $\framep[n][p]$ the partial $\framep[n]$ built up to the stage $p$ of the construction.
 Thus, we refine our definition into something like:

### 2022-10-11 paper/paper.tex
paper: minor polish

@@
 
-The characterization of $\framep[n]$ and $\filler[n]$ can be obtained by a recursive definition reminiscent from parametricity translation \cite{reynolds72}: a $\filler[n+1]$ is obtained by taking two $\filler[n]$ plus a third $\filler[n]$ connecting the two full $\filler[n]$.
+The characterization of $\framep[n]$ and $\filler[n]$ can be obtained by a recursive definition reminiscent from parametricity translation \cite{reynolds72}: a $\filler[n+1]$ is obtained by taking two $\filler[n]$ plus a third $\filler[n]$ connecting the two $\filler[n]$.
 Since it connects $\filler[n]$, the third $\filler[n]$ is actually a $\filler[n]$ over lines, so it is shifted by one relatively to the underlying relational structure.
@@
 
-The full explicit definition shall be given in the next sections but, to give an idea, let us show the structure of an $n$-filler for the first three dimensions.
+The full explicit definition shall be given in the next sections but, to give an idea, let us show the structure of a $\filler[n]$ for the first three dimensions.
 
-A full $2$-filler is made of two full $1$-fillers connected by a lifted $1$-filler made of two lines connecting the former points and a square connecting the former lines:
+A $\filler[2]$ is made of two $\filler[1]$ connected by a lifted $\filler[1]$ made of two lines connecting the former points and a square connecting the former lines.
 

### 2022-10-18 paper/paper.tex
paper: provide nice pic for intuition; X_0, X_1, ...

@@
 % Some abbreviations
+\newcommand{\tl}{\ensuremath{\mathsf{tl}}}
+\newcommand{\hd}{\ensuremath{\mathsf{hd}}}
 \newcommand{\imp}{\rightarrow}
@@
 \subsection{Intuition for our formal construction}
+\begin{notation}[\Sigma]
+  In the prose that follows, we assume the existence of $\Sigma$-types with projections $\hd$ and $\tl$.
+\end{notation}
+
 To assign $X_0, X_1, X_2, \ldots$ in the above indexed representation types, we need to exhibit a recursive definition over our building blocks, which we will call $\framep$, $\layer$, and $\filler$.
@@
 We shall give the full definition of $\fullframe[n]$ shortly, but first, assuming $\fullframe[n]$ is defined, we are able to take the coinductive limit of the $\X[][<n][]$, as shown in \ref{tab:coind}, therefore fully characterizing the indexed definition of $\nu$-sets.
+Let us illustrate how we will build $\fullframe[n]$ by refining types of $X_0, X_1, \ldots, X_{n - 1}$ so that they have the form $\fullframe[n] \rightarrow \U$.
+To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ of $X_0$ can be equivalently formulated as $\unittype \rightarrow \U$.
+The rest of the construction follows.
+
+\begin{equation*}
+  \begin{array}{llll}
+    X_0                & :              & \unittype                                   & \rightarrow \U \\
+    X_1                & :              & \Sigma \kstar: \unittype. \left(
+    \begin{array}{c}
+        X_0 \kstar
+        \\ \times \\
+        X_0 \kstar
+      \end{array}\right) & \rightarrow \U                                                                \\
+    X_2                & :              & \Sigma a: (\Sigma \kstar: \unittype. \left(
+    \begin{array}{c}
+        \Sigma c: \left(
+        \begin{array}{c}X_0 \kstar
+            \\ \times \\
+            X_0 \kstar
+          \end{array}
+        \right). (X_1 (\kstar, c)
+        \\ \times \\
+        \Sigma c: \left(
+        \begin{array}{l}
+            X_0 \kstar
+            \\ \times \\
+            X_0 \kstar
+          \end{array}
+        \right). (X_1 (\kstar, c)
+      \end{array}
+    \right).\left(
+    \begin{array}{c}
+        X_1 \left(\kstar, \left(
+          \begin{array}{c}
+              a.\tl.0.\hd.0, \\
+              a.\tl.1.\hd.0
+            \end{array}
+          \right)\right)
+        \\ \times \\
+        X_1 \left(\kstar, \left(
+          \begin{array}{c}
+              a.\tl.0.\hd.1, \\
+              a.\tl.1.\hd.1
+            \end{array}
+          \right)\right)
+      \end{array}
+    \right)
+                       & \rightarrow \U                                                                \\
+    \ldots
+  \end{array}
+\end{equation*}
 

### 2022-10-18 paper/paper.tex
paper: reorg intuition a bit

@@
 To assign $X_0, X_1, X_2, \ldots$ in the above indexed representation types, we need to exhibit a recursive definition over our building blocks, which we will call $\framep$, $\layer$, and $\filler$.
-A $\framep$ is a boundary of a standard form (simplex, cube, etc.), a $\filler$ is a filled $\framep$; both of them can be decomposed into $\layer$.
+A $\framep$ is a boundary of a standard form (simplex, cube, etc.), a $\filler$ is a filled $\framep$.
 
 As a first step, we assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a : A, (B a \rightarrow C)$ and $(\Sigma a : A, B a) \rightarrow C$.
-The question is then to find the recursive recipe defining $\fullframe[n]$.
-First, $\fullframe[n]$ depends on all $X_i$ upto $n - 1$.
-So, we need to package up $X_i$, for $i < n$, into a type, which we call $\X[][<n][]$.
-This allows us to give the type $\X[][<n][] \rightarrow \U$ to $\fullframe[n]$.
-Then, for $D: \X[][<n][]$, representing an initial prefix of $X_0, X_1, \ldots X_{n - 1}$, the indexed set $X_n$ has type $\fullframe[n](D) \rightarrow \U$.
-We shall give the full definition of $\fullframe[n]$ shortly, but first, assuming $\fullframe[n]$ is defined, we are able to take the coinductive limit of the $\X[][<n][]$, as shown in \ref{tab:coind}, therefore fully characterizing the indexed definition of $\nu$-sets.
 Let us illustrate how we will build $\fullframe[n]$ by refining types of $X_0, X_1, \ldots, X_{n - 1}$ so that they have the form $\fullframe[n] \rightarrow \U$.
@@
     X_0                                & :              & \unittype                                               & \rightarrow \U \\
-    X_1                & :              & \Sigma \kstar: \unittype. \left(
+    X_1                                & :              & \Sigma \kstar: \unittype. \underbrace{\left(
     \begin{array}{c}
@@
         X_0 \kstar
-      \end{array}\right) & \rightarrow \U                                                                \\
-    X_2                & :              & \Sigma a: (\Sigma \kstar: \unittype. \left(
+      \end{array}\right)}_{\layer[1][1]} & \rightarrow \U                                                                            \\
+    X_2                                & :              & \Sigma a: (\Sigma \kstar: \unittype. \underbrace{\left(
       \begin{array}{c}
@@
       \end{array}
-    \right).\left(
+      \right)}_{\layer[2][1]}.\underbrace{\left(
       \begin{array}{c}
@@
       \end{array}
-    \right)
+      \right)}_{\layer[2][2]}
                                        & \rightarrow \U                                                                            \\
@@
 \end{equation*}
+
+Then, $\fullframe[n]$ is a nesting of $n$ $\Sigma$-types, of which each component is called a $\layer[n]$.
+
+The question is then to find the recursive recipe defining $\fullframe[n]$.
+First, $\fullframe[n]$ depends on all $X_i$ upto $n - 1$.
+So, we need to package up $X_i$, for $i < n$, into a type, which we call $\X[][<n][]$.
+This allows us to give the type $\X[][<n][] \rightarrow \U$ to $\fullframe[n]$.
+Then, for $D: \X[][<n][]$, representing an initial prefix of $X_0, X_1, \ldots X_{n - 1}$, the indexed set $X_n$ has type $\fullframe[n](D) \rightarrow \U$.
+We shall give the full definition of $\fullframe[n]$ shortly, but first, assuming $\fullframe[n]$ is defined, we are able to take the coinductive limit of the $\X[][<n][]$, as shown in \ref{tab:coind}, therefore fully characterizing the indexed definition of $\nu$-sets.
 

### 2022-11-01 paper/paper.tex
paper: polish
paper: squelch a warning about overfull hbox
paper: more detail in diagram

@@
 \newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
-\newcommand{\unitpoint}{\ensuremath{\star}}
+\newcommand{\unitpoint}{\ensuremath{\ast}}
 
@@
 \newcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
-\newcommandx{\restrf}[1][1]{\restr{frame}[][#1][][][][][]}
+\newcommandx{\restrf}[3][1,2,3]{\restr{frame}[][#3][][#1][#2][][]}
 \newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}
@@
 \begin{definition}[\Cube]
-  $\Cube$ is defined similarly to $\DeltaPlus$, except that we take sequences of $0$, $1$ and $\star$, instead of sequences of $0$ and $\kstar$.
-We use $0$ and $1$ to indicate opposite faces of a cube.
+  $\Cube$ is defined similarly to $\DeltaPlus$, except that we take sequences of $L$, $R$ and $\star$, instead of sequences of $0$ and $\kstar$.
+We use $L$ and $R$ to indicate opposite faces of a cube.
 
@@
     \obj(\Cube) & := \Nat                                                                                \\
-    \hom(p, n)  & := \{l \in \{0, 1, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}              \\
+    \hom(p, n)  & := \{l \in \{L, R, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}              \\
     g \circ f   & :=
@@
       f                  & \text{if $g = \{\}$}                                                            \\
-      a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a = 0$ or $1$}                          \\
-      a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$, $1$, or $\kstar$} \\
+      a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a = L$ or $R$}                          \\
+      a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = L$, $R$, or $\kstar$} \\
     \end{cases} \\
@@
 \subsection{Generalization to \texorpdfstring{$\nu$}{ν}-sets}
-Let us call $\nu$-sets, the straightforward generalization of augmented semi-simplicial sets and semi-cubical sets to an arbirary arity, where morphisms are sequences of elements of an arbirary set $\nu$, extended with $\kstar$.
+Let us call $\nu$-sets, the straightforward generalization of augmented semi-simplicial sets and semi-cubical sets to an arbitrary cardinal, where morphisms are sequences of elements of an arbitrary set $\nu$, extended with $\kstar$.
 Then, we observe:
@@
   \begin{array}{llll}
-    X_0                                & :              & \unittype                                               & \rightarrow \U \\
-    X_1                                & :              & \Sigma \kstar: \unittype. \underbrace{\left(
+    X_0                                :                & \underbrace{\unittype}_{\framep[0][0]}                                                   & \rightarrow \U \\
+    X_1                                :                & \underbrace{\Sigma \unitpoint: \unittype. \underbrace{\left(
     \begin{array}{c}
-        X_0 \kstar
+        \underbrace{X_0(\unitpoint)}_{\filler[0][0]}
         \\ \times \\
-        X_0 \kstar
-      \end{array}\right)}_{\layer[1][1]} & \rightarrow \U                                                                            \\
-    X_2                                & :              & \Sigma a: (\Sigma \kstar: \unittype. \underbrace{\left(
+        \underbrace{X_0(\unitpoint)}_{\filler[0][0]}
+      \end{array}\right)}_{\layer[1][0]}}_{\framep[1][1]} & \rightarrow \U                                                                                            \\
+    X_2                                :                & \underbrace{\Sigma a: \underbrace{\left(\Sigma \unitpoint: \unittype. \underbrace{\left(
         \begin{array}{c}
-        \Sigma c: \left(
-        \begin{array}{c}X_0 \kstar
+          \underbrace{\Sigma b: \left(
+          \begin{array}{c}
+              X_0(\unitpoint)
               \\ \times \\
-            X_0 \kstar
+              X_0(\unitpoint)
             \end{array}
-        \right). (X_1 (\kstar, c)
+          \right).\; \underbrace{X_1 (\unitpoint, b)}_{\filler[1][1]}}_{\filler[1][0]}
           \\ \times \\
-        \Sigma c: \left(
-        \begin{array}{l}
-            X_0 \kstar
+          \underbrace{\Sigma b: \left(
+          \begin{array}{c}
+              X_0(\unitpoint)
               \\ \times \\
-            X_0 \kstar
+              X_0(\unitpoint)
             \end{array}
-        \right). (X_1 (\kstar, c)
+          \right).\; \underbrace{X_1 (\unitpoint, b)}_{\filler[1][1]}}_{\filler[1][0]}
         \end{array}
-      \right)}_{\layer[2][1]}.\underbrace{\left(
+        \right)}_{\layer[2][0]}\right)}_{\framep[2][1]}.\underbrace{\left(
       \begin{array}{c}
-        X_1 \left(\kstar, \left(
+        \underbrace{X_1 \underbrace{\left(a.\hd, \left(
           \begin{array}{c}
-              a.\tl.0.\hd.0, \\
-              a.\tl.1.\hd.0
+            a.\tl.L.\hd.L, \\
+            a.\tl.R.\hd.L
           \end{array}
-          \right)\right)
+          \right)\right)}_{\restrf[2][1][L]}}_{\filler[1][1]}
         \\ \times \\
-        X_1 \left(\kstar, \left(
+        \underbrace{X_1 \underbrace{\left(a.\hd, \left(
           \begin{array}{c}
-              a.\tl.0.\hd.1, \\
-              a.\tl.1.\hd.1
+            a.\tl.L.\hd.R, \\
+            a.\tl.R.\hd.R
           \end{array}
-          \right)\right)
+          \right)\right)}_{\restrf[2][1][R]}}_{\filler[1][1]}
       \end{array}
-      \right)}_{\layer[2][2]}
+      \right)}_{\layer[2][1]}}_{\framep[2][2]}
                                                         & \rightarrow \U                                                                                            \\
@@
 
-Then, $\fullframe[n]$ is a nesting of $n$ $\Sigma$-types, of which each component is called a $\layer[n]$.
+$\fullframe[n]$ is a nesting of $n$ $\Sigma$-types, of which each component is called a $\layer[n]$.
 
@@
 The partial frame has two faces and these two fillers have to respectively fill the left face and the right face of the partial frame.
-We thus have to rely on operations $\restrf[L]$ and $\restrf[R]$ which extract the sides of a frame, leading to the refined definition:
+We thus have to rely on operations $\restrf[n][p][L]$ and $\restrf[n][p][R]$ which extract the sides of a frame, leading to the refined definition:
 
@@
   \begin{array}{lll}
-    \filler[n+1][p](d:\framep[n][p]) & \defeq & \Sigma a:(\filler[n][p](\restrf[L](d)) \times \filler[n][p](\restrf[R](d))) .\, \filler[n+1][p+1](d,a)
+    \filler[n+1][p](d:\framep[n][p]) & \defeq & \Sigma a:(\filler[n][p](\restrf[n][p][L](d)) \times \filler[n][p](\restrf[n][p][R](d))) .\, \filler[n+1][p+1](d,a)
   \end{array}
@@
 A $\filler[2]$ is made of two $\filler[1]$ connected by a lifted $\filler[1]$ made of two lines connecting the former points and a square connecting the former lines.
-
-  {\scriptsize
-    \begin{equation*}
-      \begin{array}{l}
-        \begin{array}{lll}
-          \mbox{\textit{squares}}     \\
-          [3mm]\mbox{\textit{lines}}  \\
-          [3mm]\mbox{\textit{points}} \\
-          [1mm]\end{array}
-        \framebox{$\begin{array}{lll}
-                         \overbrace{\raisebox{0.05cm}{\framebox{$
-                               \begin{array}{ll}
-                      \raisebox{0cm}{\hspace{.5cm}{\layer[1][0]}}              & \framebox{$a_{0\unitpoint}$} \\
-                      [1mm]\overbrace{\framebox{$a_{00}$}~\framebox{$a_{01}$}} &
-                      \raisebox{-0.1cm}{\hspace{0.1cm}\filler[1][0]\!\!\!\!\!\!\!\!}
-                      \\
-                    \end{array}
-                             $}}~
-                         {\raisebox{0.05cm}{\framebox{$
-                               \begin{array}{ll}
-                      \raisebox{0cm}{\hspace{.5cm}{\layer[1][0]}}              & \framebox{$a_{1\unitpoint}$} \\
-                      [1mm]\overbrace{\framebox{$a_{10}$}~\framebox{$a_{11}$}} &
-                      \raisebox{-0.1cm}{\filler[1][0]\!\!\!\!\!\!\!\!}
-                    \end{array}
-                             $}}}}^{\layer[2][0]}~\stackrel{\raisebox{9.5mm}{$\framebox{$
-                                   \begin{array}{ll}
-                          \raisebox{0cm}{\hspace{.5cm}{$\layer[2][1]$}}                                & \framebox{$a_{\unitpoint\unitpoint}$} \\
-                          [1mm]\overbrace{\framebox{$a_{\unitpoint 0}$}~\framebox{$a_{\unitpoint 1}$}} &
-                          \raisebox{-0.1cm}{ \hspace{0.1cm}\filler[2][1]\!\!\!\!\!\!\!\!}
-                        \end{array}$}$}}
-                         {\raisebox{-0.4cm}{\hspace{2.5cm}\filler[2][0]\!\!\!\!\!\!\!}}
-                       \end{array}$}
-        ~~~\parbox{2cm}{additionally, each atomic component at dimension $n$ is a \filler[n][n]} \\\\
-        [-1mm]\qquad\qquad\quad~~
-        \begin{tikzcd}[column sep=5.2em, row sep=1em]
-          \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
-        \end{tikzcd}
-        \mbox{\framep[1][1]}
-        \qquad
-        \begin{tikzcd}[column sep=5.2em, row sep=1em]
-          \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
-        \end{tikzcd}
-        \mbox{\framep[1][1]}                                                                     \\
-        \qquad\qquad~~
-        \begin{tikzcd}[column sep=32em, row sep=1em]
-          \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
-        \end{tikzcd}
-        \mbox{\framep[2][1]}                                                                     \\
-        \qquad\qquad~~
-        \begin{tikzcd}[column sep=39em, row sep=1em]
-          \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
-        \end{tikzcd}
-        \mbox{\framep[2][2]}                                                                     \\
-      \end{array}
-    \end{equation*}
-  }
 

### 2022-11-01 paper/paper.tex
paper: mark two more restrf
paper: 01 to LR change

@@
     \begin{tikzcd}
-      0 \arrow[r, "\kstar", dash] & 1
+      L \arrow[r, "\kstar", dash] & R
     \end{tikzcd}
@@
     \begin{tikzcd}
-      01 \arrow[r, dash, "\kstar1"{name=F}] \arrow[d, dash, "0\kstar" left] & 11 \arrow[d, dash, "1\kstar"] \\
-      00 \arrow[r, dash, "\kstar0"{name=T, below}] & 10 \\
+      LR \arrow[r, dash, "\kstar R"{name=F}] \arrow[d, dash, "L\kstar" left] & RR \arrow[d, dash, "R\kstar"] \\
+      LL \arrow[r, dash, "\kstar L"{name=T, below}] & RL \\
       \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar" description]
@@
             \end{array}
-          \right).\; \underbrace{X_1 (\unitpoint, b)}_{\filler[1][1]}}_{\filler[1][0]}
+          \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][L]}}_{\filler[1][1]}}_{\filler[1][0]}
           \\ \times \\
@@
             \end{array}
-          \right).\; \underbrace{X_1 (\unitpoint, b)}_{\filler[1][1]}}_{\filler[1][0]}
+          \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][R]}}_{\filler[1][1]}}_{\filler[1][0]}
         \end{array}

### 2022-11-09 paper/paper.tex
paper: minor polish

@@
 To assign $X_0, X_1, X_2, \ldots$ in the above indexed representation types, we need to exhibit a recursive definition over our building blocks, which we will call $\framep$, $\layer$, and $\filler$.
-A $\framep$ is a boundary of a standard form (simplex, cube, etc.), a $\filler$ is a filled $\framep$.
+A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$, and a $\filler$ is a filled $\framep$.
 
-As a first step, we assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a : A, (B a \rightarrow C)$ and $(\Sigma a : A, B a) \rightarrow C$.
-Let us illustrate how we will build $\fullframe[n]$ by refining types of $X_0, X_1, \ldots, X_{n - 1}$ so that they have the form $\fullframe[n] \rightarrow \U$.
+We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a : A, (B a \rightarrow C)$ and $(\Sigma a : A, B a) \rightarrow C$.
+Let us illustrate how we build $\fullframe[n]$ by refining types of $X_0, X_1, \ldots, X_{n - 1}$ so that they have the form $\fullframe[n] \rightarrow \U$.
 To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ of $X_0$ can be equivalently formulated as $\unittype \rightarrow \U$.
+Each $\fullframe[n]$ is made of $n$-layers, written $\layer[n][p]$ with $p < n$, initalized with the $\unittype$ type.
+Then, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$.
 The rest of the construction follows.
@@
 \begin{equation*}
-  \begin{array}{llll}
-    X_0                                :                & \underbrace{\unittype}_{\framep[0][0]}                                                   & \rightarrow \U \\
-    X_1                                :                & \underbrace{\Sigma \unitpoint: \unittype. \underbrace{\left(
+  \begin{array}{ll}
+    X_0                                : \underbrace{\unittype}_{\framep[0][0]}                                                    \rightarrow \U \\
+    X_1                                : \underbrace{\Sigma \unitpoint: \unittype. \underbrace{\left(
     \begin{array}{c}
@@
         \underbrace{X_0(\unitpoint)}_{\filler[0][0]}
-      \end{array}\right)}_{\layer[1][0]}}_{\framep[1][1]} & \rightarrow \U                                                                                            \\
-    X_2                                :                & \underbrace{\Sigma a: \underbrace{\left(\Sigma \unitpoint: \unittype. \underbrace{\left(
+      \end{array}\right)}_{\layer[1][0]}}_{\framep[1][1]} \rightarrow \U                                                                            \\
+    X_2                                : \underbrace{\Sigma a: \underbrace{\left(\Sigma \unitpoint: \unittype. \underbrace{\left(
         \begin{array}{c}
           \underbrace{\Sigma b: \left(
-          \begin{array}{c}
+          \hspace{-0.4em}\begin{array}{c}
                            X_0(\unitpoint)
@@
                            X_0(\unitpoint)
-            \end{array}
+                         \end{array}\hspace{-0.4em}
           \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][L]}}_{\filler[1][1]}}_{\filler[1][0]}
@@
           \underbrace{\Sigma b: \left(
-          \begin{array}{c}
+          \hspace{-0.4em}\begin{array}{c}
                            X_0(\unitpoint)
@@
                            X_0(\unitpoint)
-            \end{array}
+                         \end{array}\hspace{-0.4em}
           \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][R]}}_{\filler[1][1]}}_{\filler[1][0]}
@@
         \underbrace{X_1 \underbrace{\left(a.\hd, \left(
-          \begin{array}{c}
+            \hspace{-0.4em}\begin{array}{c}
                              a.\tl.L.\hd.L, \\
                              a.\tl.R.\hd.L
-          \end{array}
+                           \end{array}\hspace{-0.4em}
             \right)\right)}_{\restrf[2][1][L]}}_{\filler[1][1]}
@@
         \underbrace{X_1 \underbrace{\left(a.\hd, \left(
-          \begin{array}{c}
+            \hspace{-0.4em}\begin{array}{c}
                              a.\tl.L.\hd.R, \\
                              a.\tl.R.\hd.R
-          \end{array}
+                           \end{array}\hspace{-0.4em}
             \right)\right)}_{\restrf[2][1][R]}}_{\filler[1][1]}
@@
       \right)}_{\layer[2][1]}}_{\framep[2][2]}
-                                                        & \rightarrow \U                                                                                            \\
+    \rightarrow \U                                                                                                                                \\
     \ldots
@@
 
-$\fullframe[n]$ is a nesting of $n$ $\Sigma$-types, of which each component is called a $\layer[n]$.
-
-The question is then to find the recursive recipe defining $\fullframe[n]$.
+Let us then make explicit the recursive recipe defining $\fullframe[n]$.
 First, $\fullframe[n]$ depends on all $X_i$ upto $n - 1$.

### 2022-11-09 paper/paper.tex
paper: new tikzpicture!

@@
 \usepackage[skip=0.4em]{parskip}
+\usetikzlibrary{patterns}
 
@@
 
-The characterization of $\framep[n]$ and $\filler[n]$ can be obtained by a recursive definition reminiscent from parametricity translation \cite{reynolds72}: a $\filler[n+1]$ is obtained by taking two $\filler[n]$ plus a third $\filler[n]$ connecting the two $\filler[n]$.
+A $\fullframe[n]$ is a sequence of $\layer[n][p]$, and we write $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is a $\framep[n][n]$.
+If $\nu = 2$, a $\layer[n][p]$ is a product of two $\filler[n - 1][p]$.
+Let us illustrate the construction of frames in dimension $3$, and $\nu = 2$:
+
+\begin{figure}[H]
+  \centering
+  \begin{tikzpicture}[scale=2]
+    \draw[spanish-blue, fill=spanish-blue] (0, 0) -- (1, 0) -- (1, 1) -- (0, 1) -- (0, 0);
+    \draw[spanish-blue, fill=spanish-blue, nearly transparent] (0.6, 1) -- (0.6, 1.6) -- (1.6, 1.6) -- (1.6, 0.6) -- (1, 0.6);
+  \end{tikzpicture}
+  \;\;
+  \begin{tikzpicture}[scale=2]
+    \draw[spanish-blue, fill=spanish-blue] (0, 0) -- (1, 0) -- (1, 1) -- (0, 1) -- (0, 0);
+    \draw[spanish-blue, fill=spanish-blue, nearly transparent] (0.6, 1) -- (0.6, 1.6) -- (1.6, 1.6) -- (1.6, 0.6) -- (1.0, 0.6);
+    \draw[raspeberry, pattern=dots] (1.1, 1.1) -- (1.5, 1.5) -- (1.5, 0.5) -- (1.1, 0.1) -- (1.1, 1.1);
+    \draw[raspeberry] (1.3, 1.3) -- (1.3, 0.3);
+    \draw[raspeberry, pattern=dots] (0.1, 1.1) -- (0.5, 1.5) -- (0.5, 1.1);
+  \end{tikzpicture}
+  \;\;
+  \begin{tikzpicture}[scale=2]
+    \draw[spanish-blue, fill=spanish-blue] (0, 0) -- (1, 0) -- (1, 1) -- (0, 1) -- (0, 0);
+    \draw[spanish-blue, fill=spanish-blue, nearly transparent] (0.6, 1) -- (0.6, 1.6) -- (1.6, 1.6) -- (1.6, 0.6) -- (1.0, 0.6);
+    \draw[raspeberry, pattern=dots] (1.1, 1.1) -- (1.5, 1.5) -- (1.5, 0.5) -- (1.1, 0.1) -- (1.1, 1.1);
+    \draw[raspeberry] (1.3, 1.3) -- (1.3, 0.3);
+    \draw[raspeberry] (0.1, 1.1) -- (0.5, 1.5);
+    \draw[russian-green, pattern=dots] (0.2, 1.1) -- (1.0, 1.1) -- (1.4, 1.5) -- (0.6, 1.5) -- (0.2, 1.1);
+    \filldraw[russian-green] (0.8, 1.3) circle (0.6pt);
+  \end{tikzpicture}
+\end{figure}
+
 Since it connects $\filler[n]$, the third $\filler[n]$ is actually a $\filler[n]$ over lines, so it is shifted by one relatively to the underlying relational structure.

### 2022-11-09 paper/paper.tex
paper: more intuition

@@
 
-Let us then make explicit the recursive recipe defining $\fullframe[n]$.
-First, $\fullframe[n]$ depends on all $X_i$ upto $n - 1$.
-So, we need to package up $X_i$, for $i < n$, into a type, which we call $\X[][<n][]$.
-This allows us to give the type $\X[][<n][] \rightarrow \U$ to $\fullframe[n]$.
-Then, for $D: \X[][<n][]$, representing an initial prefix of $X_0, X_1, \ldots X_{n - 1}$, the indexed set $X_n$ has type $\fullframe[n](D) \rightarrow \U$.
-We shall give the full definition of $\fullframe[n]$ shortly, but first, assuming $\fullframe[n]$ is defined, we are able to take the coinductive limit of the $\X[][<n][]$, as shown in \ref{tab:coind}, therefore fully characterizing the indexed definition of $\nu$-sets.
-
 A $\fullframe[n]$ is a sequence of $\layer[n][p]$, and we write $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is a $\framep[n][n]$.
-If $\nu = 2$, a $\layer[n][p]$ is a product of two $\filler[n - 1][p]$.
 Let us illustrate the construction of frames in dimension $3$, and $\nu = 2$:
@@
     \draw[raspeberry, pattern=dots] (0.1, 1.1) -- (0.5, 1.5) -- (0.5, 1.1);
+    \draw[raspeberry] (0.3, 1.3) -- (0.3, 1.1);
   \end{tikzpicture}
@@
 \end{figure}
+
+The figure on the left is $\framep[3][1]$, in the middle is $\framep[3][2]$, and on the right is $\framep[3][3]$.
+Further, $\layer[3][0]$ is shown in blue, $\layer[3][1]$ is shown in red, $\layer[3][2]$ is shown in green.
+In general, a $\layer[n][p]$ is a product of $\nu$ $\filler[n - 1][p]$.
+Then, a $\filler[n][p]$ is an $n$-dimensional object obtained by stretching a $(n - p)$-dimensional frame in $p$ directions.
+For instance, each of the two $\filler[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\filler[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a square, and each of the two $\filler[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a square.
+Note that a filler, which extends a frame with an element depending on it, shown as an element of $X_n$ below.
+As filler extends a frame, it also has layer components, but the layers are associated on the right that is opposite to the way they're associated in frames.
+
+\begin{align*}
+  \framep[n][p] & = \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0]) \ldots) .\; \layer[n][p] \\
+  \filler[n][p] & = \Sigma l_p : \layer[n][p] . (\ldots (\Sigma l_n : \layer[n][n - 1] .\; X_n) \ldots)
+\end{align*}
+
+Up to now, we haven't paid attention to the fact that we have a dependent type, shown as a $\Sigma$.
+Let us be more precise about this requirement.
+First, $\fullframe[n]$ depends on all $X_i$ upto $n - 1$.
+So, we need to package up $X_i$, for $i < n$, into a type, which we call $\X[][<n][]$.
+This allows us to give the type $\X[][<n][] \rightarrow \U$ to $\fullframe[n]$.
+Then, for $D: \X[][<n][]$, representing an initial prefix of $X_0, X_1, \ldots X_{n - 1}$, the indexed set $X_n$ has type $\fullframe[n](D) \rightarrow \U$.
+Thus, $\framep[n][p]$, $\layer[n][p]$ and $\filler[n][p]$ also depend on $D$.
+We can then refine the previous equation by showing the dependencies on $D$.
+In particular, $X_n$ is just $D.\tl$.
+
+\begin{align*}
+  \framep[n][p](D) & = \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0]) \ldots) .\; \layer[n][p](D) \\
+  \filler[n][p](D) & = \Sigma l_p : \layer[n][p] . (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\; D.\tl) \ldots)
+\end{align*}
+
+So far, we haven't paid attention to the fact that each addition of a layer has to be glued onto the border of the previous layer.
+So, each $\layer[n][p]$ has to depend on $\layer[n][p - 1]$.
+We also need a way to characterize the border of a filler of a layer, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$.
+For instance, the left $\filler[2][1]$ needs to glue onto the left borders of the two blue boxes $c_{\textsf{front}}$ and $c_{\textsf{back}}$, extracted as $\restrf[2][1][L](D)(d_\textsf{front})$ and $\restrf[2][1][L](D)(d_\textsf{back})$, where $d_\textsf{front}$ and $d_\textsf{back}$ are the underlying fullframes in $c_\textsf{front}$ $c_\textsf{back}$.
+
+We shall give the full definition of $\fullframe[n]$ shortly, but first, assuming $\fullframe[n]$ is defined, we are able to take the coinductive limit of the $\X[][<n][]$, as shown in \ref{tab:coind}, therefore fully characterizing the indexed definition of $\nu$-sets.
 

### 2022-11-09 paper/paper.tex
paper: minor additions

@@
 We also need a way to characterize the border of a filler of a layer, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$.
-For instance, the left $\filler[2][1]$ needs to glue onto the left borders of the two blue boxes $c_{\textsf{front}}$ and $c_{\textsf{back}}$, extracted as $\restrf[2][1][L](D)(d_\textsf{front})$ and $\restrf[2][1][L](D)(d_\textsf{back})$, where $d_\textsf{front}$ and $d_\textsf{back}$ are the underlying fullframes in $c_\textsf{front}$ $c_\textsf{back}$.
+For instance, the left $\filler[2][1]$ needs to glue onto the left borders of the two blue boxes, and hence needs to depend on some $\framep[2][1]$.
+The borders of the two blue boxes are extracted as $\restrf[2][1][L](D)(d_\textsf{front})$ and $\restrf[2][1][L](D)(d_\textsf{back})$, where $d_\textsf{front}$ and $d_\textsf{back}$ are the inhabitants of $\framep[2][1](D)$.
 

### 2022-11-16 paper/paper.tex
paper: MAJ

--- 2022-11-09 paper/paper.tex
@@
 \newcommandx{\restrf}[3][1,2,3]{\restr{frame}[][#3][][#1][#2][][]}
+\newcommandx{\restrl}[3][1,2,3]{\restr{layer}[][#3][][#1][#2][][]}
+\newcommandx{\restrc}[3][1,2,3]{\restr{filler}[][#3][][#1][#2][][]}
 \newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}
@@
 The figure on the left is $\framep[3][1]$, in the middle is $\framep[3][2]$, and on the right is $\framep[3][3]$.
-Further, $\layer[3][0]$ is shown in blue, $\layer[3][1]$ is shown in red, $\layer[3][2]$ is shown in green.
+Further, $\framep[3][1]$ is made of one layer, $\layer[3][0]$, shown in blue, $\framep[3][2]$ is made of one additional layer, $\layer[3][1]$, shown in red, $\framep[3][3]$ is made of one more layer, $\layer[3][2]$, shown in green.
 In general, a $\layer[n][p]$ is a product of $\nu$ $\filler[n - 1][p]$.
@@
 \begin{align*}
-  \framep[n][p] & = \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0]) \ldots) .\; \layer[n][p] \\
-  \filler[n][p] & = \Sigma l_p : \layer[n][p] . (\ldots (\Sigma l_n : \layer[n][n - 1] .\; X_n) \ldots)
+  \framep[n][p] & \defeq \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0]) \ldots) .\; \layer[n][p] \\
+  \filler[n][p] & \defeq \Sigma l_p : \layer[n][p] . (\ldots (\Sigma l_n : \layer[n][n - 1] .\; X_n) \ldots)
 \end{align*}
@@
 \begin{align*}
-  \framep[n][p](D) & = \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0]) \ldots) .\; \layer[n][p](D) \\
-  \filler[n][p](D) & = \Sigma l_p : \layer[n][p] . (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\; D.\tl) \ldots)
+  \framep[n][p](D) & \defeq \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)) \ldots) .\; \layer[n][p](D) \\
+  \filler[n][p](D) & \defeq \Sigma l_p : \layer[n][p](D) . (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\; D.\tl) \ldots)
 \end{align*}
@@
 We also need a way to characterize the border of a filler of a layer, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$.
-For instance, the left $\filler[2][1]$ needs to glue onto the left borders of the two blue boxes $c_{\textsf{front}}$ and $c_{\textsf{back}}$, extracted as $\restrf[2][1][L](D)(d_\textsf{front})$ and $\restrf[2][1][L](D)(d_\textsf{back})$, where $d_\textsf{front}$ and $d_\textsf{back}$ are the underlying fullframes in $c_\textsf{front}$ $c_\textsf{back}$.
+For instance, each of the $\filler[2][1]$, shown as the red boxes, is laid on the borders of the blue boxes, and hence needs to depend on $\framep[3][1]$.
+The left and right borders of the two blue boxes are extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$.
+We can then refine the previous equation by showing the dependencies on $d$.
+
+\begin{align*}
+  \framep[n][p](D)    & \defeq \Sigma d : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)(\unitpoint)) \ldots) .\; \layer[n][p](D)(d)                              \\
+  \filler[n][p](D)(d) & \defeq \Sigma l_p : \layer[n][p](D)(d) . (\ldots (\Sigma l_n : \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}) .\; D.\tl(d, l_p, \ldots, l_n)) \ldots) \\
+  \text{where}\;      & (d, l_p, \ldots, l_q) \text{ abbreviates } ((\ldots(d, l_p), \ldots), l_q)
+\end{align*}
+
+Let us recall that a layer is made of two fillers. This can now be made precise as illustrated below.
+
+\begin{align*}
+  \layer[n][p](D)(d) & \defeq \filler[n-1][p](D.\hd)(\restrf[n][p][L](d)) \times \filler[n-1][p](D.\hd)(\restrf[n][p][R](d))
+\end{align*}
+
+We now define $\restrf[n][p][\epsilon]$ by recursion on the structure of a frame, which necessitates definitions of $\restrl[n][p][\epsilon]$ and $\restrc[n][p][\epsilon]$.
 
@@
 
-\begin{equation*}
-  \filler[n+1][p] \defeq (\filler[n][p] \times \filler[n][p]) \times \filler[n+1][p+1]
-\end{equation*}
+\begin{align*}
+  \filler[n+1][p] & \defeq (\filler[n][p] \times \filler[n][p]) \times \filler[n+1][p+1]
+\end{align*}
 
@@
 \renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
-\newcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\newcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}
 

### 2022-11-16 paper/paper.tex
paper: first draft at explaining coh*

@@
 \newcommandx{\restrc}[3][1,2,3]{\restr{filler}[][#3][][#1][#2][][]}
+\newcommandx{\cohf}{\coh{frame}[][][][][][][][]}
+\newcommandx{\cohl}{\coh{layer}[][][][][][][][]}
+\newcommandx{\cohc}{\coh{filler}[][][][][][][][]}
 \newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}
@@
 
-We now define $\restrf[n][p][\epsilon]$ by recursion on the structure of a frame, which necessitates definitions of $\restrl[n][p][\epsilon]$ and $\restrc[n][p][\epsilon]$.
+We now define $\restrf[n][p][\epsilon](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon](d)(l)$ and $\restrc[n][p][\epsilon](d)(c)$, for $l$ a layer and $c$ a filler.
+The key case is $\restrc[n][n-1][\epsilon](d)(c)$, where $c$, a $\filler[n][n-1]$, has necessarily the form of $((c_L, c_R), \_)$: $\restrc[n][n-1][L]$ picks out $c_L$, a $\filler[n][n]$, $\restrc[n][n-1][R]$ picks out the $c_R$, also a $\filler[n][n]$, and $\_$ is discarded.
+There is one more difficulty, which we illustrate by writing down expected and actual types.
 
-We shall give the full definition of $\fullframe[n]$ shortly, but first, assuming $\fullframe[n]$ is defined, we are able to take the coinductive limit of the $\X[][<n][]$, as shown in \ref{tab:coind}, therefore fully characterizing the indexed definition of $\nu$-sets.
-
-Since it connects $\filler[n]$, the third $\filler[n]$ is actually a $\filler[n]$ over lines, so it is shifted by one relatively to the underlying relational structure.
-Let us write $\filler[n][p]$ for a $\filler[n - p]$ over points which are $\filler[p]$.
-Working informally, we thus have the equation:
+Given $c_\omega$ of type
 
 \begin{align*}
-  \filler[n+1][p] & \defeq (\filler[n][p] \times \filler[n][p]) \times \filler[n+1][p+1]
+  c_\omega & : \filler[n-1][p](D.\hd)(\restrf[n-1][p][\omega](d))
 \end{align*}
 
-Now, the third filler (of dimension $n - p$) connects the first two $\filler[n-p]$, so it has to depend on them. So, the equation is rather something of the form:
+$\restrl[n][p][\epsilon](d)(c_L, c_R)$ produces a layer, of which $\omega$-component has the type
 
 \begin{equation*}
-  \filler[n+1][p] \defeq \Sigma a:(\filler[n][p] \times \filler[n][p]).\, \filler[n+1][p+1](a)
+  \filler[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\epsilon](\restrf[n][p][\omega](d)))
 \end{equation*}
 
-Then, by iterating, we obtain:
+while we expect a term of type
 
 \begin{equation*}
-  \filler[n+1][p] \defeq \Sigma a:(\filler[n][p] \times \filler[n][p]).\,
-  \Sigma b:(\filler[n][p+1](a) \times \filler[n][p+1](a)). \, \filler[n+1][p+2](a,b)
+  \filler[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\omega](\restrf[n][p][\epsilon](d)))
 \end{equation*}
 
-and so on.
-Thus, we need first to make the definition of $\filler[n][p]$ dependent over the part of the filler built up to this point and secondly to accumulate this information.
-At the end of the accumulation of the process, i.e.
-at the time of building $\filler[n+1][n]$, a complete $\framep[n]$ will have been built.
-So, let us call $\framep[n][p]$ the partial $\framep[n]$ built up to the stage $p$ of the construction.
-Thus, we refine our definition into something like:
-
-\begin{equation*}
-  \begin{array}{lll}
-    \framep[n][0]                    & \defeq & \unittype                                                                       \\
-    \framep[n][p+1]                  & \defeq & \Sigma d:\framep[n][p] .\,(\filler[n][p](d) \times \filler[n][p](d))            \\
-    \\
-    \filler[n+1][p](d:\framep[n][p]) & \defeq & $\Sigma$ a:(\filler[n][p](d) \times \filler[n][p](d)) .\,\filler[n+1][p+1](d,a)
-  \end{array}
-\end{equation*}
-
-where $\unittype$ is a canonical singleton type used to initiate the
-construction of a list of pairs of $n$-fillers.
-
-Now, the two fillers $\filler[n][p](d)$ and $\filler[n][p](d)$ cannot be any fillers.
-They have to represent two opposite fillers, and we need a way to express this.
-The answer is simple.
-The partial frame has two faces and these two fillers have to respectively fill the left face and the right face of the partial frame.
-We thus have to rely on operations $\restrf[n][p][L]$ and $\restrf[n][p][R]$ which extract the sides of a frame, leading to the refined definition:
-
-\begin{equation*}
-  \begin{array}{lll}
-    \filler[n+1][p](d:\framep[n][p]) & \defeq & \Sigma a:(\filler[n][p](\restrf[n][p][L](d)) \times \filler[n][p](\restrf[n][p][R](d))) .\, \filler[n+1][p+1](d,a)
-  \end{array}
-\end{equation*}
-
-The full explicit definition shall be given in the next sections but, to give an idea, let us show the structure of a $\filler[n]$ for the first three dimensions.
-
-A $\filler[2]$ is made of two $\filler[1]$ connected by a lifted $\filler[1]$ made of two lines connecting the former points and a square connecting the former lines.
+Hence, we need a coherence condition to commute the $\restrf[n][p][\epsilon]$ and $\restrf[n][p][\omega]$.
+Coherence conditions similar to this necessitate, what are shown as, $\cohf$, $\cohl$ and $\cohc$ in tables in the next section.
 
@@
 % Keep only ε, ω; n, p; proposition on n and p
-\newcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
-\newcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
-\newcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][][][][][#9]}
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][][][][][#9]}
 

### 2022-11-25 paper/paper.tex
paper: finish intuitive explanation

@@
 \renewcommand{\E}{E}
-\newcommand{\ap}{\mathsf{ap}}
+\newcommand{\ap}{\mathsf{ap}\;}
 \renewcommand{\l}{l}
@@
 \newcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
-\newcommandx{\restrf}[3][1,2,3]{\restr{frame}[][#3][][#1][#2][][]}
-\newcommandx{\restrl}[3][1,2,3]{\restr{layer}[][#3][][#1][#2][][]}
-\newcommandx{\restrc}[3][1,2,3]{\restr{filler}[][#3][][#1][#2][][]}
+\newcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
+\newcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
+\newcommandx{\restrc}[4][1,2,3,4]{\restr{filler}[][#3][#4][#1][#2][][]}
 \newcommandx{\cohf}{\coh{frame}[][][][][][][][]}
@@
 \newcommandx{\cohc}{\coh{filler}[][][][][][][][]}
+\newcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
 \newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}
@@
 \begin{align*}
-  \layer[n][p](D)(d) & \defeq \filler[n-1][p](D.\hd)(\restrf[n][p][L](d)) \times \filler[n-1][p](D.\hd)(\restrf[n][p][R](d))
+  \layer[n][p](D)(d) & \defeq \filler[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) \times \filler[n-1][p](D.\hd)(\restrf[n][p][R][p](d))
 \end{align*}
 
-We now define $\restrf[n][p][\epsilon](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon](d)(l)$ and $\restrc[n][p][\epsilon](d)(c)$, for $l$ a layer and $c$ a filler.
-The key case is $\restrc[n][n-1][\epsilon](d)(c)$, where $c$, a $\filler[n][n-1]$, has necessarily the form of $((c_L, c_R), \_)$: $\restrc[n][n-1][L]$ picks out $c_L$, a $\filler[n][n]$, $\restrc[n][n-1][R]$ picks out the $c_R$, also a $\filler[n][n]$, and $\_$ is discarded.
+$\restrf[n][p][\epsilon][q]$ indicates restriction on $q$ layers of a frame, and the induction is on $p$, going from $0$ to $q$.
+In particular, $\restrf[n][p][\epsilon][p]$ is a ``full restriction''.
+We define $\restrf[n][p][\epsilon][p](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a layer and $c$ a filler.
+The key case is $\restrc[n][p][\epsilon][p](d)(c)$, where $c$, a $\filler[n][p]$, has necessarily the form of $((c_L, c_R), \_)$: $\restrc[n][p][L][p]$ picks out $c_L$, a $\filler[n-1][p]$, $\restrc[n][p][R][p]$ picks out the $c_R$, also a $\filler[n-1][p]$, and $\_$, a $\filler[n][p+1]$, is discarded.
 There is one more difficulty, which we illustrate by writing down expected and actual types.
@@
 \begin{align*}
-  c_\omega & : \filler[n-1][p](D.\hd)(\restrf[n-1][p][\omega](d))
+  c_\omega & : \filler[n-1][p](D.\hd)(\restrf[n-1][p][\omega][q](d))
 \end{align*}
@@
 \begin{equation*}
-  \filler[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\epsilon](\restrf[n][p][\omega](d)))
+  \filler[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\epsilon][q](\restrf[n][p][\omega][p](d)))
 \end{equation*}
@@
 \begin{equation*}
-  \filler[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\omega](\restrf[n][p][\epsilon](d)))
+  \filler[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\omega][p](\restrf[n][p][\epsilon][q+1](d)))
 \end{equation*}
 
-Hence, we need a coherence condition to commute the $\restrf[n][p][\epsilon]$ and $\restrf[n][p][\omega]$.
+Hence, we need a coherence condition to commute the terms.
 Coherence conditions similar to this necessitate, what are shown as, $\cohf$, $\cohl$ and $\cohc$ in tables in the next section.
+These are by induction on the structure of $\framep$, $\layer$ and $\filler$.
+In particular, for $\cohl$, we need a $2$-dimensional coherence condition called $\coht$.
+
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
+
+\begin{align*}
+  \cohf[m][\omega][\theta][r][p][n][p][][d = {\restrf[m][\epsilon][q+2][n][p][][d = \d]}]\;\bullet     \\
+  \ap \restrf[m][\omega][r][n][p][][]\;(\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d])\;\bullet   \\
+  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =              \\
+  \ap \restrf[m][\theta][p][n][p][][]\;(\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d])\;\bullet \\
+  \cohf[m][\epsilon][\theta][q][p][n][p][][d = {\restrf[m][\omega][r+1][n][p][][d = \d]}]\;\bullet     \\
+  \ap \restrf[m][\epsilon][q][n][p][]\;(\cohf[m][\omega][\theta][r][p][n][p][][d = \d])
+\end{align*}
+
+where $\mathsf{ap}$ applies a function on two sides of an equality, and $\bullet$ is transitivity of equality. This property of equality proofs holds in \U.
 
@@
 \renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\newcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
+\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
 
@@
 
-where $\cohtwo{frame}$ is:
+\section{Details on the mechanization}
+\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
+\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
+\renewcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
+\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
+\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
+\renewcommandx{\restrc}[4][1,2,3,4]{\restr{filler}[][#3][#4][#1][#2][][]}
+\renewcommandx{\cohf}[1][1]{\coh{frame}[][][][][][][#1][]}
+\renewcommandx{\cohl}[1][1]{\coh{layer}[][][][][][][#1][]}
+\renewcommandx{\cohc}[1][1]{\coh{filler}[][][][][][][#1][]}
 
-\begin{align*}
-  \cohf[m][\omega][\theta][r][p][n][p][][d = {\restrf[m][\epsilon][q+2][n][p][][d = \d, D = \D]}, D = \D]\;\bullet         \\
-  \ap (\restrf[m][\omega][r][n][p][][d = {\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d, D = \D]}, D = \D]\;\bullet    \\
-  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d, D = \D]}, D = \D] =                  \\
-  \ap (\restrf[m][\theta][p][n][p][][d = {\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d, D = \D]}, D = \D])\;\bullet \\
-  \cohf[m][\epsilon][\theta][q][p][n][p][][d = {\restrf[m][\omega][r+1][n][p][][d = \d, D = \D]}, D = \D]\;\bullet         \\
-  \ap (\restrf[m][\epsilon][q][n][p][][d = {\cohf[m][\omega][\theta][r][p][n][p][][d = \d, D = \D]}, D = \D])
-\end{align*}
-
-\newpage
-\section{Future work}
+The construction is obviously on induction on $n$, but $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$.
+A priori, this necessitates well-founded induction.
+Due to technical difficulties experienced with Coq, we chose a different route; in practice, since we only need to keep track of three levels, we built separate data structures for the levels, with dependencies.
 

### 2022-11-30 paper/paper.tex
paper: adapt to new simplified \joinargs
tab-coh-ett: update
paper: write formal construction in ett/itt

@@
   \ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{
-    \joinargs{}[#3][#4][#5]}}
+    \joinargs[#3][#4][#5]}}
   \setkeys*[bonak]{#1}{#6}
@@
   \ensuremath{\mathsf{\color{russian-green}{restr}}_{
-    \mathsf{\color{indian-yellow}{#1}}
-    \joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}
+    \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4]}^{\joinargs[#5][#6][#7]}}
   \setkeys*[bonak]{restr#1}{#8}
@@
   \ensuremath{\mathsf{\color{chestnut}{coh}}_{
-    \mathsf{\color{indian-yellow}{#1}}
-    \joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}
+    \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4][#5][#6]}^{\joinargs[#7][#8]}}
   \setkeys*[bonak]{coh#1}{#9}
@@
   \ensuremath{\mathsf{\color{chestnut}{coh2}}_{
-    \mathsf{\color{indian-yellow}{#1}}
-    \joinargs{,}[#2][#3][#4][#5][#6][#7]}^{\joinargs{}[#8]}}
+    \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4][#5][#6][#7]}^{\joinargs[#8]}}
   \setkeys*[bonak]{coh#1}{#9}
@@
 \newcommand{\defeq}{\ensuremath{\triangleq}}
-\newcommand{\eqHSet}{\ensuremath{\equiv_{\mathit{HSet}}}}
+\newcommand{\eqHSet}{\ensuremath{{=}_{\mathit{HSet}\;}}}
 \newcommand{\reflHSet}{\ensuremath{\mathsf{refl}_{\mathit{HSet}}}}
@@
 \newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}
+
+% For typesetting type theory rules
+\newcommand \seqr[3]
+  {\shortstack{$#2$ \\ \mbox{}\\
+                   \mbox{}\hrulefill\mbox{}\\ \mbox{}\\ $#3$} \raisebox{2ex}{$\;\;\mbox{$#1$}$}}
 
@@
 \author{
+  \textcolor{gray80}{Hugo Herbelin} \\
+  \itshape \textcolor{gray80}{IRIF/Inria Paris/Université Paris-Cité}
+  \and
   \textcolor{gray80}{Ramkumar Ramachandra} \\
   \itshape \textcolor{gray80}{Université Paris-Cité}
-  \and
-  \textcolor{gray80}{Hugo Herbelin} \\
-  \itshape \textcolor{gray80}{IRIF/Inria Paris/Université Paris-Cité}
 }
@@
 
-The definition in \ref{tab:coind}, the coinductive limit, is dispatched over tables \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and \ref{tab:coh}.
-They describe the structure of the underlying higher-dimensional relations on which fillers are built.
+We now formally present the construction in \emph{extensional} type theory; i.e.
+in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality:
+
+\begin{equation*}
+  \seqr{}{\Gamma \vdash p : t = u}{\Gamma \vdash t \equiv u}
+\end{equation*}
+
+For the presentation corresponding to the formalization in \emph{intensional} type theory, see \ref{appendix:A}.
+
+The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and \ref{tab:coh}.
+Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a coinductive limit of $n$-truncated $\nu$-sets.
+$n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.
+The $n$th component is a family over a $\fullframe$.
+$\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\filler$.
+$\layer$ and $\filler$ are dependent over $\restrf$, and these restrictions are defined on \ref{tab:faces}.
+These restrictions are defined using auxiliary definitions of $\restrl$ and $\restrc$.
+
+Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$.
+This is apriori undecidable, and we have to prove the commutation propositionally before using the reflection rule.
+Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\filler$.
+This is what $\cohf$ proves, as shown in the table \ref{tab:coh}.
+Even though it looks independent of the other tables, it has to proved mutually with the definitions of $\framep$, $\layer$, $\filler$, and their corresponding restrictions.
+
+Remark: For a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
 
@@
 \renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
-
-We now describe \emph{bare truncated sets}: \emph{bare} because it can be seen as defining truncated $\nu$-sets without face maps, and \emph{truncated} because it is $n$-truncated.
 
@@
 \renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
-
-In the way we have chosen to formlate these tables, there is, for instance, coherence condition $\cohf$ both sides of the equality in $\restrl$ and $\restrc$, to ensure that they are the same type.
-
-For a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
 
@@
 
-The proof of $\cohf$ require a higher-dimensional coherence condition which we obtain by working in \U.
-If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-
 % Coherence conditions for frame, layer, and filler
@@
 \renewcommandx{\restrc}[4][1,2,3,4]{\restr{filler}[][#3][#4][#1][#2][][]}
-\renewcommandx{\cohf}[1][1]{\coh{frame}[][][][][][][#1][]}
-\renewcommandx{\cohl}[1][1]{\coh{layer}[][][][][][][#1][]}
-\renewcommandx{\cohc}[1][1]{\coh{filler}[][][][][][][#1][]}
+\renewcommandx{\cohf}[1][1]{\coh{frame}[][][][][][#1][][]}
+\renewcommandx{\cohl}[1][1]{\coh{layer}[][][][][][#1][][]}
+\renewcommandx{\cohc}[1][1]{\coh{filler}[][][][][][#1][][]}
 
@@
 \appendix
-\section{Tables in full detail}
+\section{Tables in full detail\label{appendix:A}}
 % Full tables in this section
@@
   \input{tab-faces.tex}
+
+  The proof of $\cohf$ requires a higher-dimensional coherence condition which we obtain by working in \U.
+If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
+
   \renewcommand*{\lab}{fulltab:coh}

### 2022-11-30 paper/paper.tex
paper: move stuff around

@@
 
-\section{Mathematical treatment of \texorpdfstring{$\nu$}{𝜈}-sets}
+\section{Semi-simplicial and semi-cubical sets}
 It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
@@
 These are by induction on the structure of $\framep$, $\layer$ and $\filler$.
-In particular, for $\cohl$, we need a $2$-dimensional coherence condition called $\coht$.
+Note that, for the construction in \ref{sec:itt}, we further need a $2$-dimensional coherence condition, $\coht$, for $\cohl$.
 
-\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
-
-\begin{align*}
-  \cohf[m][\omega][\theta][r][p][n][p][][d = {\restrf[m][\epsilon][q+2][n][p][][d = \d]}]\;\bullet     \\
-  \ap \restrf[m][\omega][r][n][p][][]\;(\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d])\;\bullet   \\
-  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =              \\
-  \ap \restrf[m][\theta][p][n][p][][]\;(\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d])\;\bullet \\
-  \cohf[m][\epsilon][\theta][q][p][n][p][][d = {\restrf[m][\omega][r+1][n][p][][d = \d]}]\;\bullet     \\
-  \ap \restrf[m][\epsilon][q][n][p][]\;(\cohf[m][\omega][\theta][r][p][n][p][][d = \d])
-\end{align*}
-
-where $\mathsf{ap}$ applies a function on two sides of an equality, and $\bullet$ is transitivity of equality. This property of equality proofs holds in \U.
-
-\subsection{Formal construction of \texorpdfstring{$\nu$}{nu}-sets}
+\subsection{Formal construction in extensional type theory}
 % Abbreviated tables in this section
@@
 
-For the presentation corresponding to the formalization in \emph{intensional} type theory, see \ref{appendix:A}.
+For the presentation corresponding to the formalization in \emph{intensional} type theory, see \ref{sec:itt}.
 
@@
 Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\filler$.
-This is what $\cohf$ proves, as shown in the table \ref{tab:coh}.
+This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$.
 Even though it looks independent of the other tables, it has to proved mutually with the definitions of $\framep$, $\layer$, $\filler$, and their corresponding restrictions.
+
+Note that in $\cohf$ and $\cohc$, we use the reflection rule to identify equalities of pairs with a conjuction of two equalities.
+Note also that in $\cohl$, we use the reflection rule to identify equality of functions with pointwise equality.
 
@@
 
-\section{Details on the mechanization}
-\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
-\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
-\renewcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
-\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
-\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
-\renewcommandx{\restrc}[4][1,2,3,4]{\restr{filler}[][#3][#4][#1][#2][][]}
-\renewcommandx{\cohf}[1][1]{\coh{frame}[][][][][][#1][][]}
-\renewcommandx{\cohl}[1][1]{\coh{layer}[][][][][][#1][][]}
-\renewcommandx{\cohc}[1][1]{\coh{filler}[][][][][][#1][][]}
+\subsection{Formal construction in intensional type theory\label{sec:itt}}
+We now present the tables in \emph{intensional} type theory, leaving implict some details, which we will soon explain.
 
-The construction is obviously on induction on $n$, but $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$.
-A priori, this necessitates well-founded induction.
-Due to technical difficulties experienced with Coq, we chose a different route; in practice, since we only need to keep track of three levels, we built separate data structures for the levels, with dependencies.
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
 
-\newpage
-\appendix
-\section{Tables in full detail\label{appendix:A}}
+\begin{align*}
+  \cohf[m][\omega][\theta][r][p][n][p][][d = {\restrf[m][\epsilon][q+2][n][p][][d = \d]}]\;\bullet     \\
+  \ap \restrf[m][\omega][r][n][p][][]\;(\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d])\;\bullet   \\
+  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =              \\
+  \ap \restrf[m][\theta][p][n][p][][]\;(\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d])\;\bullet \\
+  \cohf[m][\epsilon][\theta][q][p][n][p][][d = {\restrf[m][\omega][r+1][n][p][][d = \d]}]\;\bullet     \\
+  \ap \restrf[m][\epsilon][q][n][p][]\;(\cohf[m][\omega][\theta][r][p][n][p][][d = \d])
+\end{align*}
+
+where $\mathsf{ap}$ applies a function on two sides of an equality, and $\bullet$ is transitivity of equality. This property of equality proofs holds in \U.
+
 % Full tables in this section
@@
 
+\subsection{Details on the mechanization}
+\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
+\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
+\renewcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
+\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
+\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
+\renewcommandx{\restrc}[4][1,2,3,4]{\restr{filler}[][#3][#4][#1][#2][][]}
+\renewcommandx{\cohf}[1][1]{\coh{frame}[][][][][][#1][][]}
+\renewcommandx{\cohl}[1][1]{\coh{layer}[][][][][][#1][][]}
+\renewcommandx{\cohc}[1][1]{\coh{filler}[][][][][][#1][][]}
+
+Our formalization is done in the intensional type theory flavor of the calculus of inductive constructions.
+Working in intensional type theory necessitates explicitly supplying a number of type equalities, which hold definitionally in extensional type theory.
+
+The construction is obviously on induction on $n$, but $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$.
+A priori, this necessitates well-founded induction.
+Due to technical difficulties experienced with Coq, we chose a different route; in practice, since we only need to keep track of three levels, we built separate data structures for the levels, with dependencies.
+
 \bibliographystyle{alpha}

### 2022-12-05 paper/paper.tex
paper: minor polish

@@
 \subsection{Formal construction in intensional type theory\label{sec:itt}}
-We now present the tables in \emph{intensional} type theory, leaving implict some details, which we will soon explain.
+\renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
+
+We now present the tables in \emph{intensional} type theory, leaving implict some details, which we will explain shortly.
+
+The proof of $\cohf$ requires a higher-dimensional coherence condition which we obtain by working in \U.
+If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
 
@@
 
-  The proof of $\cohf$ requires a higher-dimensional coherence condition which we obtain by working in \U.
-If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
-
   \renewcommand*{\lab}{fulltab:coh}
@@
 
+\newpage
 \bibliographystyle{alpha}

### 2022-12-08 paper/paper.tex
paper: finish itt section

@@
 \newcommandx{\U}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
+\newcommandx{\HGpd}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HGpd}}_{#1}}}
+\newcommand{\Type}{\ensuremath{\mathsf{\color{spanish-blue}{Type}}}}
 
@@
 \newcommand{\pair}[2]{#1, #2}
-\newcommand{\Type}{\textsf{Type}}
 \newcommand{\Dom}{\textsf{Dom}}
@@
 
-Note that in $\cohf$ and $\cohc$, we use the reflection rule to identify equalities of pairs with a conjuction of two equalities.
-Note also that in $\cohl$, we use the reflection rule to identify equality of functions with pointwise equality.
-
 Remark: For a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
@@
 
-We now present the tables in \emph{intensional} type theory, leaving implict some details, which we will explain shortly.
+Since we have formalized the proof in the Coq proof assistant, which works in intensional type theory, we now present the tables in \emph{intensional} type theory, leaving implicit some details, which we will explain shortly.
 
-The proof of $\cohf$ requires a higher-dimensional coherence condition which we obtain by working in \U.
-If the proofs of the same equality were not equated, there would be a need for arbitrary many higher-dimensional coherences (see e.g.~\cite{herbelin15} for a discussion on the de facto need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory).
+Tables \ref{fulltab:coind}, \ref{fulltab:core}, and \ref{fulltab:frames} are unchanged, except that we make explicit all arguments, including those that can be inferred from the context.
+The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit as shown in table \ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
+The proof of $\cohf$ is described on \ref{fulltab:coh}, and it requires explication of several equalities which were implicit in extensional type theory.
+The commutation of $\restrl$ lives in a type referring to $\cohf$, so we need a transport along the commutation of $\restrf$ in the statement of $\cohl$.
+The proof of $\cohl$ is the most involved proof in the construction.
+This is where the higher-dimensional coherence condition is needed.
+The exact formulation of this coherence condition is as follows.
 
@@
 \renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
 
@@
   \ap \restrf[m][\omega][r][n][p][][]\;(\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d])\;\bullet   \\
-  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =              \\
+  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =_{HProp}      \\
   \ap \restrf[m][\theta][p][n][p][][]\;(\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d])\;\bullet \\
@@
 
-where $\mathsf{ap}$ applies a function on two sides of an equality, and $\bullet$ is transitivity of equality. This property of equality proofs holds in \U.
+\renewcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
+\renewcommandx{\restrf}{\restr{frame}[][][][][][][]}
+\renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
+\renewcommandx{\cohl}{\coh{layer}[][][][][][][][]}
+\renewcommandx{\cohc}{\coh{filler}[][][][][][][][]}
+
+where $\mathsf{ap}$ applies a function on two sides of an equality, and $\bullet$ is transitivity of equality.
+This property of equality proofs holds in \U, and since our formalization is done in \U, the term is trivially discharged.
+
+Notice that each $\restrl$ in the type of $\cohl$ is hiding a $\cohf$ rewrite: this makes a sum total of three $\cohf$ rewrites on the left-hand side, and two $\cohf$ rewrites on the right-hand side.
+In the proof term of $\cohl$, $\cohc$ has one $\cohf$ rewrite on its left-hand side and zero on the right-hand side.
+This combined with the two terms of the form $\ap \cohf$ matches our expectation of three $\cohf$ on the left-hand side and two $\cohf$ on the right-hand side.
+$\coht$ can roughly be seen as a commutation of these $\cohf$ terms.
+
+Finally, let us explain $\cohc$.
+The base case $p = r$ is the key case of the commutation of $\restrf$, when one of the $\restrc$ collapses, and the remaining equation holds trivially.
+The case of $p < r$ follows the structure of $\restrc$ by induction.
+
+There are a few more subtleties.
+In $\cohf$ and $\cohc$, we use the reflection rule to identify equalities of pairs with a conjunction of two equalities.
+In $\cohl$, we use the reflection rule to identify equality of functions with pointwise equality.
+We additionally rely heavily on basic properties of the groupoid transport, which we don't detail.
+
+Remark: If we weren't working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitarily many higher-dimensional coherences.
+For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x =_{HGpd} y$ is in \U.
+See \cite{herbelin15} for a discussion on the need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory.
 

### 2022-12-08 paper/paper.tex
paper: start detailing mechanization

@@
 
-\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape}
+\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape, minted}
 \usepackage[prefix=bonak]{art.cls/xkeymask}
@@
 
+For a fixed $n$, $\framep$, $\restrf$, and $\cohf$ have to be mutually defined by induction on $p$.
+Each of them rely on $\filler$, $\restrf$, and $\cohc$ at lower $n$, so they are well-founded.
+Finally, each of $\filler$, $\restrf$, and $\cohf$ are by induction from $p$ to $n$.
+
 Remark: If we weren't working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitarily many higher-dimensional coherences.
-For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x =_{HGpd} y$ is in \U.
+For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x =_{\mathit{HGpd}} y$ is in \U.
 See \cite{herbelin15} for a discussion on the need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory.
@@
 
-Our formalization is done in the intensional type theory flavor of the calculus of inductive constructions.
-Working in intensional type theory necessitates explicitly supplying a number of type equalities, which hold definitionally in extensional type theory.
-
-The construction is obviously on induction on $n$, but $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$.
-A priori, this necessitates well-founded induction.
-Due to technical difficulties experienced with Coq, we chose a different route; in practice, since we only need to keep track of three levels, we built separate data structures for the levels, with dependencies.
+Since the construction shown in the previous sections are by induction on $n$, and dependencies are on lower $n$ and $p < n$, one would imagine formalizing this using well-founded induction in the calculus of inductive constructions.
+We initially tried this approach: we had terms dependent on the proofs of the case distinction of $n' \leq n$ implies $n' < n$ or $n' = n$, and these proofs were didn't have definitional computational rule; it was necessary to reason proposionally on the computational property of the case distinction, and it even turned out to be unmanageable.
+Hence, we chose a different route: in practice, since $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$, we only need to keep track of three ``levels'', and we built separate data structures for the levels, with dependencies.
+More concretely, we build the ten definitions shown in the tables by induction, and this is part of the definition of a larger record.
+Other fields in the record are necessary because we need copies of $\framep$, $\layer$, $\filler$ at levels $n - 1$ and $n - 2$, $\restrf$, $\restrl$, and $\restrc$ at level $n - 1$, and equations to recall the definitions of these objects at lower levels.
+We hence have what looks like the following.
 

### 2022-12-17 paper/paper.tex
paper: finish writing about three flavors of le

@@
 Other fields in the record are necessary because we need copies of $\framep$, $\layer$, $\filler$ at levels $n - 1$ and $n - 2$, $\restrf$, $\restrl$, and $\restrc$ at level $n - 1$, and equations to recall the definitions of these objects at lower levels.
-We hence have what looks like the following.
+
+The entire construction relies on inequalities over natural numbers, and we have three different definitions of $\leq$ addressing different concerns, and conversions betwen them.
+First, we have what we call the ``recusive variant'', phrased as:
+
+\begin{minted}{coq}
+  Fixpoint leR (n m : nat) : SProp :=
+  match n, m with
+  | O, _ => STrue
+  | S n, O => SFalse
+  | S n, S m => leR n m
+  end.
+\end{minted}
+
+The upside of this definition is that all inequalities of the form $m \leq n$ are equivalent, definitionally.
+By placing the definition in \texttt{SProp}, we have definitional equality of inequality proofs.
+For the purpose of unification, however, this definition doesn't go far enough.
+Consider the unification problems:
+
+\begin{minted}{coq}
+  le_trans ?p le_refl = ?p
+  le_trans le_refl ?p = ?p
+\end{minted}
+
+where \texttt{le\_trans} is transitivity, \texttt{le\_refl} is reflexivity, and \texttt{?p} is an existential variable.
+These two problems definitionally hold in \texttt{SProp}, but equalizing them does not solve the existential.
+For unification to be useful in inferring existentials, we present our next definition, which we dub as the ``Yoneda variant'':
+
+\begin{minted}{coq}
+  Definition leY n m := forall p, leR p n -> leR p m.
+\end{minted}
+
+\texttt{leY} is an improvement over \texttt{leR} since reflexivity is now definitionally the neutral elemement of transitivity, and associativity of transitivity also holds definitionally.
+Although it significantly eases our proof, there are some instances where unification is unable to solve for the existentials, and we have to provide them explicitly.
+
+Finally, we have the ``inductive variant'', phrased as:
+
+\begin{minted}{coq}
+  Inductive leI : nat -> nat -> Type :=
+  | leI_refl n : n <~ n
+  | leI_down {n p} : p.+1 <~ n -> p <~ n
+  where "n <~ m" := (leI n m) : nat_scope.
+\end{minted}
+
+Compared to \texttt{leY}, \texttt{leI} has no proof-irrelevance properties.
+This definition is specially crafted for $\filler$, where we have to reason inductively from $p \leq n$ to $n$.
+In our usage, we have lemmas \texttt{leY\_of\_leI} and \texttt{leI\_of\_leY} in order to equip \texttt{leY} with the induction scheme of \texttt{leI}.
+Then, together with computational rules stated propositionally, we reason about $\beta$-reduction of induction.
 

### 2022-12-17 paper/paper.tex
paper: spell-check document

@@
   In dimension $2$, the standard augmented semi-simplex is drawn as two points, given by $\Hom(1, 2)$, along with a line connecting them, given by $\Hom(2, 2)$.
-We use the color black to denote the unique morphims in $\Hom(0, 1)$ and $\Hom(0, 2)$.
+We use the color black to denote the unique morphisms in $\Hom(0, 1)$ and $\Hom(0, 2)$.
 
@@
 To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ of $X_0$ can be equivalently formulated as $\unittype \rightarrow \U$.
-Each $\fullframe[n]$ is made of $n$-layers, written $\layer[n][p]$ with $p < n$, initalized with the $\unittype$ type.
+Each $\fullframe[n]$ is made of $n$-layers, written $\layer[n][p]$ with $p < n$, initialized with the $\unittype$ type.
 Then, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$.
@@
 Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$.
-This is apriori undecidable, and we have to prove the commutation propositionally before using the reflection rule.
+This is a priori undecidable, and we have to prove the commutation propositionally before using the reflection rule.
 Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\filler$.
@@
 In $\cohf$ and $\cohc$, we use the reflection rule to identify equalities of pairs with a conjunction of two equalities.
-In $\cohl$, we use the reflection rule to identify equality of functions with pointwise equality.
+In $\cohl$, we use the reflection rule to identify equality of functions with point-wise equality.
 We additionally rely heavily on basic properties of the groupoid transport, which we don't detail.
@@
 
-Remark: If we weren't working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitarily many higher-dimensional coherences.
+Remark: If we weren't working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences.
 For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x =_{\mathit{HGpd}} y$ is in \U.
@@
 Since the construction shown in the previous sections are by induction on $n$, and dependencies are on lower $n$ and $p < n$, one would imagine formalizing this using well-founded induction in the calculus of inductive constructions.
-We initially tried this approach: we had terms dependent on the proofs of the case distinction of $n' \leq n$ implies $n' < n$ or $n' = n$, and these proofs were didn't have definitional computational rule; it was necessary to reason proposionally on the computational property of the case distinction, and it even turned out to be unmanageable.
+We initially tried this approach: we had terms dependent on the proofs of the case distinction of $n' \leq n$ implies $n' < n$ or $n' = n$, and these proofs were didn't have definitional computational rule; it was necessary to reason propositionally on the computational property of the case distinction, and it even turned out to be unmanageable.
 Hence, we chose a different route: in practice, since $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$, we only need to keep track of three ``levels'', and we built separate data structures for the levels, with dependencies.
@@
 
-The entire construction relies on inequalities over natural numbers, and we have three different definitions of $\leq$ addressing different concerns, and conversions betwen them.
-First, we have what we call the ``recusive variant'', phrased as:
+The entire construction relies on inequalities over natural numbers, and we have three different definitions of $\leq$ addressing different concerns, and conversions between them.
+First, we have what we call the ``recursive variant'', phrased as:
 
@@
 
-\texttt{leY} is an improvement over \texttt{leR} since reflexivity is now definitionally the neutral elemement of transitivity, and associativity of transitivity also holds definitionally.
+\texttt{leY} is an improvement over \texttt{leR} since reflexivity is now definitionally the neutral element of transitivity, and associativity of transitivity also holds definitionally.
 Although it significantly eases our proof, there are some instances where unification is unable to solve for the existentials, and we have to provide them explicitly.

### 2023-01-06 paper/paper.tex
paper: minor polish

@@
   \textcolor{gray80}{Hugo Herbelin} \\
-  \itshape \textcolor{gray80}{IRIF/Inria Paris/Université Paris-Cité}
+  \itshape \textcolor{gray80}{Université Paris-Cité, Inria, CNRS, IRIF, Paris}
   \and
   \textcolor{gray80}{Ramkumar Ramachandra} \\
-  \itshape \textcolor{gray80}{Université Paris-Cité}
+  \itshape \textcolor{gray80}{Université Paris-Cité, Inria, CNRS, IRIF, Paris}
 }
@@
 
-We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both semi-simplicial semi-cubical sets obtained by applying simple rules iterating parametricity.
+We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both semi-simplicial and semi-cubical sets obtained by applying simple rules iterating parametricity.
 In contrast to the presheaf presentation of semi-simplicial and semi-cubical sets, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
@@
 Since the construction shown in the previous sections are by induction on $n$, and dependencies are on lower $n$ and $p < n$, one would imagine formalizing this using well-founded induction in the calculus of inductive constructions.
-We initially tried this approach: we had terms dependent on the proofs of the case distinction of $n' \leq n$ implies $n' < n$ or $n' = n$, and these proofs were didn't have definitional computational rule; it was necessary to reason propositionally on the computational property of the case distinction, and it even turned out to be unmanageable.
+We initially tried this approach: we had terms dependent on the proofs of the case distinction of $n' \leq n$ implies $n' < n$ or $n' = n$, and these proofs didn't have definitional computational rule; it started to be necessary to reason propositionally on the computational property of the case distinction, and it eventually turned out to be unmanageable.
 Hence, we chose a different route: in practice, since $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$, we only need to keep track of three ``levels'', and we built separate data structures for the levels, with dependencies.
@@
 
-The entire construction relies on inequalities over natural numbers, and we have three different definitions of $\leq$ addressing different concerns, and conversions between them.
+The entire construction relies on inequalities over natural numbers, and we have three different definitions of $\leq$ addressing two different concerns, and conversions between them.
 First, we have what we call the ``recursive variant'', phrased as:

### 2023-01-06 paper/paper.tex
paper: more polish

@@
 
-\title{A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions}
+\title{A formalization of semi-simplicial and semi-cubical sets}
 \author{
@@
 \begin{abstract}
-  We present a parametricity-based construction of semi-simplicial sets and semi-cubical sets in indexed form, in the calculus of inductive constructions.
+  We present a parametricity-based construction of semi-simplicial sets and semi-cubical sets in indexed form, formulated in dependent type theory.
 The accompanying artifact is an axiom-less~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to $\nu$-types; if $\nu$ is finite (say, unit type corresponding to augmented semi-simplicial types), this requirement vanishes.} Coq formalization that uses sophisticated rewriting techniques and pushes the boundaries of proof assistant technology.
@@
 Before spelling out the details of our formalization in type-theoretic language, we have a section on reasoning in sets.
+We end with some of the finer details of our mechanization.
+
+Our precise mechanization in Coq is available at \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}.
 
@@
 
-An equivalent defintion of UIP is given by \textsf{UIP\_refl}:
+An equivalent definition of UIP is given by \textsf{UIP\_refl}:
 
@@
 % Restriction for frame, layer, and filler
-% Drop the unviverse letter
+% Drop the universe letter
 \renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
@@
 
-We now formally present the construction in \emph{extensional} type theory; i.e.
+We now present the construction in \emph{extensional} type theory; i.e.
 in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality:
@@
 Even though it looks independent of the other tables, it has to proved mutually with the definitions of $\framep$, $\layer$, $\filler$, and their corresponding restrictions.
+
+Most components of the construction takes inequality constraints as parameters, and we have left implicit that they are satisfied in the table.
+Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, and assume that we can pick a definition for which inequality proofs are definitionally equal.
 
@@
 
-Since we have formalized the proof in the Coq proof assistant, which works in intensional type theory, we now present the tables in \emph{intensional} type theory, leaving implicit some details, which we will explain shortly.
+Since we have formalized the proof in the Coq proof assistant, which works in intensional type theory, we now present the tables in \emph{intensional} type theory, leaving implicit some details, which we will explain here, and other details, which we will explain in \ref{sec:mech}.
 
@@
 
-\subsection{Details on the mechanization}
+\subsection{Details on the mechanization\label{sec:mech}}
 \renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}

### 2023-01-06 paper/paper.tex
paper: minor polish

@@
   \textcolor{gray80}{Hugo Herbelin} \\
-  \itshape \textcolor{gray80}{Université Paris-Cité, Inria, CNRS, IRIF, Paris}
+  \itshape \textcolor{gray80}{Université Paris Cité, Inria, CNRS, IRIF, Paris}
   \and
   \textcolor{gray80}{Ramkumar Ramachandra} \\
-  \itshape \textcolor{gray80}{Université Paris-Cité, Inria, CNRS, IRIF, Paris}
+  \itshape \textcolor{gray80}{Université Paris Cité, Inria, CNRS, IRIF, Paris}
 }
@@
 Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{johann17,altenkirch15,moulin16}.
-We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{bernardy12,moulin16}.
+We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of realizability~\cite{bernardy12,moulin16}.
 It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation from Hugo Moeneclaey}.
@@
 \emph{fibered} over the set of semi-simplices or semi-cubes in dimension $n$, we consider families of semi-simplices and semi-cubes indexed over their faces.
-
-\begin{table}[H]
-  \begin{tabularx}{\linewidth}{p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}}
-    \toprule
-            & Set theory  & Type theory \\
-    \graymidrule
-    Fibered & \cite{cchm} &             \\
-    \graymidrule
-    Indexed &             & Our work    \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
 

### 2023-01-06 paper/paper.tex
.gitmodules: fix submodule url
paper: remove one def of \DeltaPlus

@@
 
-\begin{notation}[$\uparrow$]
-  Let us write $\uparrow \{i_1, \ldots, i_n\}$ to denote $\{i_1 + 1, \ldots, i_n + 1\}$.
-\end{notation}
-
-\begin{definition}[\DeltaPlus]
-  The category of augmented semi-simplices is defined in terms of objects, morphisms, composition, and identity.
-
-  \begin{align*}
-    \obj(\DeltaPlus) & := \Nat                                                                    \\
-    \hom(p, n)       & := \{\{i_{p + 1}, \ldots, i_n\} \mid 0 < i_{p + 1} < \ldots < i_n \leq n\} \\
-    g \circ f        & :=
-    \begin{cases}
-      g                          & \text{if f = \{\}}                                          \\
-      f                          & \text{if g = \{\}}                                          \\
-      b :: (g \circ f')          & \text{if $g = (a :: g')$, $f = (b :: f')$, with $b < a$}    \\
-      a :: (g' \circ \uparrow f) & \text{if $g = (a :: g')$, $f = (b :: f')$, with $b \geq a$} \\
-    \end{cases}      \\
-    \id              & := \{\}
-  \end{align*}
-
-  Evidently, $\id$ is neutral. Further, composition can be shown to be associative.
-\end{definition}
-
-\begin{definition}[Alternative definition of $\DeltaPlus$]
+\begin{definition}[$\DeltaPlus$]
   \begin{align*}
@@
 
-Standard $n$-semi-cubes have a geometric interpretion, which we illustrate for dimensions $0$, $1$, and $2$.
+Standard $n$-semi-cubes have a geometric interpretation, which we illustrate for dimensions $0$, $1$, and $2$.
 

### 2023-01-06 paper/paper.tex
paper: beef up bib a bit

@@
 It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
-What we have formalized is \emph{augmented semi-simplicial} sets, and \emph{semi-cubical} sets.
+What we have formalized is \emph{augmented semi-simplicial} sets~\cite{fri08,riehl11}, and \emph{semi-cubical} sets~\cite{grandis03,buchholtz17}.
 We will proceed to explain the mathematical objects we have formalized.
@@
 We now present the construction in \emph{extensional} type theory; i.e.
-in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality:
+in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
 

### 2023-01-07 paper/paper.tex
paper: trim riehl from bib

@@
 We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of realizability~\cite{bernardy12,moulin16}.
-It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation from Hugo Moeneclaey}.
+It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation by Hugo Moeneclaey}.
 
@@
 It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
-What we have formalized is \emph{augmented semi-simplicial} sets~\cite{fri08,riehl11}, and \emph{semi-cubical} sets~\cite{grandis03,buchholtz17}.
+What we have formalized is \emph{augmented semi-simplicial} sets~\cite{fri08}, and \emph{semi-cubical} sets~\cite{grandis03,buchholtz17}.
 We will proceed to explain the mathematical objects we have formalized.

### 2023-01-09 paper/paper.tex
paper: start preparing for LICS submission
The last table in landscape mode isn't properly formatted.

@@
 
-\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape, minted}
+\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, multicol, pdflscape, minted}
 \usepackage[prefix=bonak]{art.cls/xkeymask}
@@
 \newcolumntype{Y}{>{\centering\arraybackslash}X}
-\NewEnviron{eqntable}[1]{
+\NewEnviron{onecoltbl}[1]{
   \begin{table}[H]
@@
   \end{table}
+}
+
+\NewEnviron{eqntable}[1]{
+  \begin{table*}[t!]
+    \small
+    \begin{tabularx}{\linewidth}{@{}>{$}l<{$} >{$}c<{$} >{$}c<{$} >{$}Y<{$} @{}}
+      \toprule
+      \BODY
+      \bottomrule
+    \end{tabularx}
+    \caption{#1}
+  \end{table*}
 }
@@
 \author{
-  \textcolor{gray80}{Hugo Herbelin} \\
-  \itshape \textcolor{gray80}{Université Paris Cité, Inria, CNRS, IRIF, Paris}
+  Hugo Herbelin \\
+  Université Paris Cité, Inria, CNRS, IRIF, Paris \\
   \and
-  \textcolor{gray80}{Ramkumar Ramachandra} \\
-  \itshape \textcolor{gray80}{Université Paris Cité, Inria, CNRS, IRIF, Paris}
+  Ramkumar Ramachandra \\
+  Université Paris Cité, Inria, CNRS, IRIF, Paris
 }
@@
 \end{abstract}
-\tableofcontents
-\newpage
 
@@
 \begin{definition}[$\DeltaPlus$]
+  \begin{figure*}[!t]
     \begin{align*}
@@
     \end{align*}
+    \caption{Definition of \DeltaPlus}\label{fig:deltaplus}
+  \end{figure*}
 
-  Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
+  The definition of $\DeltaPlus$ is shown in Fig.
+\ref{fig:deltaplus}.
+Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$.
+It can be shown that composition is associative and that $\id$ is neutral.
 \end{definition}
@@
 We use $L$ and $R$ to indicate opposite faces of a cube.
+The definition is shown in Fig.
+\ref{fig:cube}.
 
+  \begin{figure*}[!t]
     \begin{align*}
@@
     \end{align*}
+    \caption{Definition of \Cube}\label{fig:cube}
+  \end{figure*}
 
@@
   X_1 & : X_0 \times X_0 \rightarrow \U                                             \\
-  X_2 & : \forall a b c d, X_1 (a, b) \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \rightarrow X_1 (c, d) \rightarrow \U \\
+  X_2 & : \forall a b c d, X_1 (a, b) \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \\
+      & \rightarrow X_1 (c, d) \rightarrow \U                                       \\
   \ldots
@@
 Then, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$.
-The rest of the construction follows.
+The rest of the construction is shown in Fig.
+\ref{fig:intuition}
 
+\begin{figure*}[!t]
   \begin{equation*}
@@
   \end{equation*}
+  \caption{Intuition for formal construction}\label{fig:intuition}
+\end{figure*}
 
@@
   \end{tikzpicture}
-  \;\;
+  \newline\newline
   \begin{tikzpicture}[scale=2]
@@
 \begin{align*}
-  \framep[n][p](D) & \defeq \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)) \ldots) .\; \layer[n][p](D) \\
-  \filler[n][p](D) & \defeq \Sigma l_p : \layer[n][p](D) . (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\; D.\tl) \ldots)
+  \framep[n][p](D) & \defeq & \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .        \\
+                   &        & \layer[n][0](D)) \ldots) .\; \layer[n][p](D)                 \\
+  \filler[n][p](D) & \defeq & \Sigma l_p : \layer[n][p](D) .                               \\
+                   &        & (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\; D.\tl) \ldots)
 \end{align*}
@@
 \begin{align*}
-  \framep[n][p](D)    & \defeq \Sigma d : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)(\unitpoint)) \ldots) .\; \layer[n][p](D)(d)                              \\
-  \filler[n][p](D)(d) & \defeq \Sigma l_p : \layer[n][p](D)(d) . (\ldots (\Sigma l_n : \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}) .\; D.\tl(d, l_p, \ldots, l_n)) \ldots) \\
-  \text{where}\;      & (d, l_p, \ldots, l_q) \text{ abbreviates } ((\ldots(d, l_p), \ldots), l_q)
+  \framep[n][p](D)    & \defeq & \Sigma d : (\ldots (\Sigma \unitpoint: \unittype .\; \layer[n][0](D)(\unitpoint)) \ldots) . \\
+                      &        & \layer[n][p](D)(d)                                                                          \\
+  \filler[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d) .                                                            \\
+                      &        & (\ldots (\Sigma l_n : \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}) .                      \\
+                      &        & D.\tl(d, l_p, \ldots, l_n)) \ldots)                                                         \\
+  \text{where}\;      &        & (d, l_p, \ldots, l_q) \text{ abbreviates }                                                  \\
+                      &        & ((\ldots(d, l_p), \ldots), l_q)
 \end{align*}
@@
 \begin{align*}
-  \layer[n][p](D)(d) & \defeq \filler[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) \times \filler[n-1][p](D.\hd)(\restrf[n][p][R][p](d))
+  \layer[n][p](D)(d) & \defeq & \filler[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) \times \\
+                     &        & \filler[n-1][p](D.\hd)(\restrf[n][p][R][p](d))
 \end{align*}
@@
 
-\begin{landscape}
 \renewcommand*{\lab}{fulltab:faces}
@@
 
+\begin{landscape}
   \renewcommand*{\lab}{fulltab:coh}
@@
 \begin{minted}{coq}
-  Definition leY n m := forall p, leR p n -> leR p m.
+  Definition leY n m :=
+    forall p, leR p n -> leR p m.
 \end{minted}

### 2023-01-10 paper/paper.tex
paper, tab-coh: use rotating to fix last table
paper: fix some underfull hboxes

@@
 
-\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, multicol, pdflscape, minted}
+\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, multicol, minted, rotating}
 \usepackage[prefix=bonak]{art.cls/xkeymask}
@@
 \section{Overture}
-In the context of typed functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational equality of programs of this type.
+In the context of functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational equality of programs of this type.
 Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{johann17,altenkirch15,moulin16}.
@@
 
-Our precise mechanization in Coq is available at \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}.
+Our precise mechanization in Coq is available on Github, at \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}.
 
@@
 
-While ordinary semi-simplicial sets are presheaves over the semi-simplex category $\hat{\Delta}$, augmented semi-simplicial sets are presheaves over, what we will define as $\DeltaPlus$.
-There are different ways to define $\DeltaPlus$, upto equivalence, and we use a combinatorial definition; the reason for our choice is that this definition has a straightforward extension to semi-cubical sets.
+While ordinary semi-simplicial sets are presheaves over the semi-simplex category $\hat{\Delta}$, augmented semi-simplicial sets are presheaves over, what we will define as, $\DeltaPlus$.
+There are different ways to define $\DeltaPlus$, upto equivalence, and we use a combinatorial definition.
+The reason for our choice is that this definition has a straightforward extension to semi-cubical sets.
 
 \begin{notation}[Sequences of integers]
-  We write $\{i_1, \ldots i_n\}$ for sequences of integers. In particular, the empty sequence is written $\{\}$.
+  We denote sequences of integers by $\{i_1, \ldots i_n\}$. In particular, the empty sequence is written $\{\}$.
 \end{notation}
@@
 \begin{example}[$\Cube^1$]
-  $\Cube^1$ is two points, given by $\Hom(0, 1)$ and a line, given by $\Hom(1, 1)$:
+  $\Cube^1$ consists of two points, given by $\Hom(0, 1)$ and a line, given by $\Hom(1, 1)$:
 
@@
 \begin{example}[$\Cube^2$]
-  $\Cube^2$ is four points, given by $\Hom(0, 2)$, four lines connecting the four points, given by $\Hom(1, 2)$, and a filler, given by $\Hom(2, 2)$:
+  $\Cube^2$ consists of four points, given by $\Hom(0, 2)$, four lines connecting the four points, given by $\Hom(1, 2)$, and a filler, given by $\Hom(2, 2)$:
 
@@
 \begin{table}[H]
-  \begin{tabularx}{\linewidth}{p{.2\linewidth}|p{.4\linewidth}|p{.3\linewidth}}
+  \centering
+  \begin{tabularx}{0.95\linewidth}{X|X|X}
     \toprule
@@
 
-In category theory, the correspondence between fibered and indexed way, manifests as the correspondence between Grothendieck fibrations and pseudofunctors, of which a particular instance is the correspondence between discrete fibrations and presheaves, or even between discrete fibrations over sets and families of sets.
+In category theory, the correspondence between the fibered and indexed way manifests as the correspondence between Grothendieck fibrations and pseudofunctors, of which a particular instance is the correspondence between discrete fibrations and presheaves, or even between discrete fibrations over sets and families of sets.
 
@@
 
-$\restrl[n][p][\epsilon](d)(c_L, c_R)$ produces a layer, of which $\omega$-component has the type
+$\restrl[n][p][\epsilon](d)(c_L, c_R)$ produces a layer, in which the $\omega$-component has the type
 
@@
 
-\subsection{Formal construction in extensional type theory}
+\subsection{Formal construction in ETT}
 % Abbreviated tables in this section
@@
 
-\subsection{Formal construction in intensional type theory\label{sec:itt}}
+\subsection{Formal construction in ITT\label{sec:itt}}
 \renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
@@
 
-\begin{landscape}
 \renewcommand*{\lab}{fulltab:coh}
 \input{tab-coh.tex}
-\end{landscape}
 

### 2023-01-10 paper/paper.tex
paper, art.cls: use conference mode, use IEEEtran bib
paper: minor polish

@@
 \usepackage[prefix=bonak]{art.cls/xkeymask}
-\usepackage[skip=0.4em]{parskip}
 \usetikzlibrary{patterns}
@@
 \newcommand{\Type}{\ensuremath{\mathsf{\color{spanish-blue}{Type}}}}
+\newcommand{\SProp}{\ensuremath{\mathsf{\color{spanish-blue}{SProp}}}}
 
@@
 \NewEnviron{eqntable}[1]{
-  \begin{table*}[t!]
+  \begin{table*}[!t]
     \small
@@
 
-\title{A formalization of semi-simplicial and semi-cubical sets}
-\author{
-  Hugo Herbelin \\
-  Université Paris Cité, Inria, CNRS, IRIF, Paris \\
-  \and
-  Ramkumar Ramachandra \\
-  Université Paris Cité, Inria, CNRS, IRIF, Paris
-}
-\date{}
-
-\color{gray65}
+\title{A formalization of semi-simplicial and semi-cubical sets in dependent type theory}
+\author{\IEEEauthorblockN{Hugo Herbelin \\ and Ramkumar Ramachandra} \IEEEauthorblockA{Université Paris Cité, Inria, CNRS, IRIF, Paris}}
 
@@
 \begin{align*}
-  \layer[n][p](D)(d) & \defeq & \filler[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) \times \\
-                     &        & \filler[n-1][p](D.\hd)(\restrf[n][p][R][p](d))
+  \layer[n][p](D)(d) & \defeq & \filler[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) & \times \\
+                     &        & \filler[n-1][p](D.\hd)(\restrf[n][p][R][p](d)) &
 \end{align*}
@@
   \ap \restrf[m][\omega][r][n][p][][]\;(\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d])\;\bullet     \\
-  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =_{HProp}      \\
+  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =_\mathit{HProp} \\
   \ap \restrf[m][\theta][p][n][p][][]\;(\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d])\;\bullet   \\
@@
 The upside of this definition is that all inequalities of the form $m \leq n$ are equivalent, definitionally.
-By placing the definition in \texttt{SProp}, we have definitional equality of inequality proofs.
+By placing the definition in \SProp, we have definitional equality of inequality proofs.
 For the purpose of unification, however, this definition doesn't go far enough.
@@
 where \texttt{le\_trans} is transitivity, \texttt{le\_refl} is reflexivity, and \texttt{?p} is an existential variable.
-These two problems definitionally hold in \texttt{SProp}, but equalizing them does not solve the existential.
+These two problems definitionally hold in \SProp, but equalizing them does not solve the existential.
 For unification to be useful in inferring existentials, we present our next definition, which we dub as the ``Yoneda variant'':
@@
 
-\newpage
-\bibliographystyle{alpha}
+\bibliographystyle{IEEEtran}
 \bibliography{paper}

### 2023-01-10 paper/paper.tex
paper: more polish

@@
 Homotopy type theory (HoTT) is a logical foundation based on Martin-Löf type theory and the univalence axiom~\cite{hottbook}.
-HoTT is based on the notion of a basic Type, and the notion of sets can be recovered as \U, where $\U$ is a straightforward packaging of two fields:
+HoTT is based on the notion of a basic \Type, and the notion of sets can be recovered as \U, where $\U$ is a straightforward packaging of two fields:
 
@@
 \subsection{Fibered versus indexed representation}
-It is well-known in set theory, that families of small sets can be represented in a fibered or indexed way.
+It is well-known in set theory that families of small sets can be represented in a fibered or indexed way.
 In the fibered way, a family over $T$ is represented a pair of a set $S$, and a function $S \rightarrow T$.
@@
 \begin{align*}
-  X_0 & : \U                                                                        \\
-  X_1 & : X_0 \times X_0 \rightarrow \U                                             \\
-  X_2 & : \forall a b c d, X_1 (a, b) \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \\
-      & \rightarrow X_1 (c, d) \rightarrow \U                                       \\
+  X_0 & :                             & \U                                            \\
+  X_1 & :                             & X_0 \times X_0 \rightarrow \U                 \\
+  X_2 & : \forall a b c d, X_1 (a, b) & \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \\
+      &                               & \rightarrow X_1 (c, d) \rightarrow \U         \\
   \ldots
@@
 \begin{align*}
-  \framep[n][p](D) & \defeq & \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .        \\
-                   &        & \layer[n][0](D)) \ldots) .\; \layer[n][p](D)                 \\
+  \framep[n][p](D) & \defeq & \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)) \ldots) . \\
+                   &        & \layer[n][p](D)                                                                    \\
   \filler[n][p](D) & \defeq & \Sigma l_p : \layer[n][p](D) .                                                     \\
@@
 \renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
+\renewcommandx{\cohl}{\coh{layer}[][][][][][][][]}
 

### 2023-01-11 paper/paper.tex
paper: more polish; fix references to fig

@@
   X_1 & :                  & X_0 \times X_0 \rightarrow \U                            \\
-  X_2 & : \forall a b c d, X_1 (a, b) & \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \\
+  X_2 & : \forall a b c d, & X_1 (a, b) \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \\
       &                    & \rightarrow X_1 (c, d) \rightarrow \U                    \\
@@
 
-The figure on the left is $\framep[3][1]$, in the middle is $\framep[3][2]$, and on the right is $\framep[3][3]$.
+The figure on the left is $\framep[3][1]$, on the right is $\framep[3][2]$, and on the bottom is $\framep[3][3]$.
 Further, $\framep[3][1]$ is made of one layer, $\layer[3][0]$, shown in blue, $\framep[3][2]$ is made of one additional layer, $\layer[3][1]$, shown in red, $\framep[3][3]$ is made of one more layer, $\layer[3][2]$, shown in green.
@@
 
-Up to now, we haven't paid attention to the fact that we have a dependent type, shown as a $\Sigma$.
+So far, we haven't paid attention to the fact that we have a dependent type, shown as a $\Sigma$.
 Let us be more precise about this requirement.
@@
 
-So far, we haven't paid attention to the fact that each addition of a layer has to be glued onto the border of the previous layer.
+An additional refinement arises from the fact that each addition of a layer has to be glued onto the border of the previous layer.
 So, each $\layer[n][p]$ has to depend on $\layer[n][p - 1]$.

### 2023-01-11 paper/paper.tex
paper: repharse a few things for fewer underflows

@@
 
-\section{Overture}
+\section{Introduction}
 In the context of functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational equality of programs of this type.
@@
 We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both semi-simplicial and semi-cubical sets obtained by applying simple rules iterating parametricity.
-In contrast to the presheaf presentation of semi-simplicial and semi-cubical sets, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
+In contrast to the presheaf presentation of semi-simplicial and semi-cubical sets~\cite{cchm}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
 That is, instead of having the set of semi-simplices or semi-cubes in dimension $n+1$
@@
 \end{notation}
-
-We introduce two additional notations for working with sequences of integers.
 
@@
 \section{Our construction}
-In this section, we briefly explain the difference between the fibered and indexed representations, and illustrate our approach to the construction, with the help of some figures.
+In this section, we gradually build up an intuition for our construction, followed by the full details of our construction.
 
@@
 \subsection{Intuition for our formal construction}
-\begin{notation}[\Sigma]
+\begin{notation}[$\Sigma$]
   In the prose that follows, we assume the existence of $\Sigma$-types with projections $\hd$ and $\tl$.
@@
 We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a : A, (B a \rightarrow C)$ and $(\Sigma a : A, B a) \rightarrow C$.
-Let us illustrate how we build $\fullframe[n]$ by refining types of $X_0, X_1, \ldots, X_{n - 1}$ so that they have the form $\fullframe[n] \rightarrow \U$.
+Let us now illustrate how we build $\fullframe[n]$ by refining types of $X_0, X_1, \ldots, X_{n - 1}$ so that they have the form $\fullframe[n] \rightarrow \U$.
 To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ of $X_0$ can be equivalently formulated as $\unittype \rightarrow \U$.

### 2023-01-11 paper/paper.tex
A polishing step

@@
 \begin{abstract}
-  We present a parametricity-based construction of semi-simplicial sets and semi-cubical sets in indexed form, formulated in dependent type theory.
-The accompanying artifact is an axiom-less~\footnote{Technically speaking, we use some axioms related to functional extensionality, but the requirement arises only from our generalization to $\nu$-types; if $\nu$ is finite (say, unit type corresponding to augmented semi-simplicial types), this requirement vanishes.} Coq formalization that uses sophisticated rewriting techniques and pushes the boundaries of proof assistant technology.
+Constructions such as semi-simplicial and semi-cubical sets can be defined in the ``usual way'' as presheaves over respectively the semi-simplex or semi-cube category, which we shall call ``fibered'' definitions, but also, as done e.g.
+in Voevodsky~\cite{} and in previous work~\cite{} as an ``dependently-typed'', or, say, ``indexed'' construction.
+
+This paper describes an alternative indexed construction of both augmented semi-simplicial and semi-cubical sets based on the property that augmented semi-simplicial and semi-cubical sets naturally arise as respectively unary and binary iterated parametricity-based constructions.
+
+Additionally, the axiom-free construction has been fully formalized in Coq's dependent type theory, which turned out not to be so straightforward.
 \end{abstract}
@@
 In the context of functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational equality of programs of this type.
-Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{johann17,altenkirch15,moulin16}.
+Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
 We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of realizability~\cite{bernardy12,moulin16}.
-It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation by Hugo Moeneclaey}.
+It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication by Thorsten Altenkirch and Hugo Moeneclaey}.
 
 We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both semi-simplicial and semi-cubical sets obtained by applying simple rules iterating parametricity.
-In contrast to the presheaf presentation of semi-simplicial and semi-cubical sets~\cite{cchm}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
+In contrast to the standard presheaf presentation of semi-simplicial and semi-cubical sets~\cite{fri08,grandis03,buchholtz1}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
 That is, instead of having the set of semi-simplices or semi-cubes in dimension $n+1$
@@
 The outline of the paper is as follows.
-First, we briefly describe semi-simplicial and semi-cubical sets, and our generalization to $\nu$-sets.
-We then proceed to explain our construction, with the help of diagrams.
-Before spelling out the details of our formalization in type-theoretic language, we have a section on reasoning in sets.
+First, we briefly describe a free-monoid-style (?) in the fibered presentation of semi-simplicial and semi-cubical sets, and our generalization to $\nu$-sets.
+We then proceed to explain our indexed construction, with the help of diagrams.
+Before spelling out the details of our formalization in type-theoretic language, we have a section on reasoning with sets inside type theory.
 We end with some of the finer details of our mechanization.
@@
 
-\begin{notation}[Sequences of integers]
-  We denote sequences of integers by $\{i_1, \ldots i_n\}$. In particular, the empty sequence is written $\{\}$.
+\begin{notation}[Finite sequences]
+  We denote finite sequences by $\{i_1, \ldots i_n\}$ for $i_j$ ranging over some domain. In particular, the empty sequence is written $\{\}$.
 \end{notation}
@@
     \begin{align*}
-      \obj(\DeltaPlus) & := \Nat                                                                     \\
-      \hom(p, n)       & := \{l \in \{0, \kstar\}^n \mid \text{number of $\kstar$ in l = p}\}        \\
+      \Obj(\DeltaPlus) & := \Nat                                                                     \\
+      \Hom(p, n)       & := \{l \in \{0, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}        \\
       g \circ f        & :=
@@
 
+To provide examples, we define the standard augmented $n$-semi-simplex.
+
 \begin{definition}[$\DeltaPlus^n$]
@@
     \DeltaPlus^n(p) & := \Hom(p, n)            \\
-    \DeltaPlus^n(f) & := \lambda g . g \circ f
+    \DeltaPlus^n(f) & := \lambda g .\, g \circ f
   \end{align*}
@@
 \subsection{Semi-cubical sets}
+
+Semi-cubical sets are defined like augmented semi-simplicial sets except that $\DeltaPlus$ is replaced by $\Cube$ in which we take sequences of $L$, $R$ and $\star$, instead of sequences of $0$ and $\kstar$.
+
 \begin{definition}[\Cube]
-  $\Cube$ is defined similarly to $\DeltaPlus$, except that we take sequences of $L$, $R$ and $\star$, instead of sequences of $0$ and $\kstar$.
-We use $L$ and $R$ to indicate opposite faces of a cube.
-The definition is shown in Fig.
-\ref{fig:cube}.
-
+  The definition of $\Cube$ is shown in Fig.~\ref{fig:cube}.
+  The symbols $L$ and $R$ indicate opposite faces of a cube.
   \begin{figure*}[!t]
     \begin{align*}
-      \obj(\Cube) & := \Nat                                                                                \\
-      \hom(p, n)  & := \{l \in \{L, R, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}              \\
+      \Obj(\Cube) & := \Nat                                                                                \\
+      \Hom(p, n)  & := \{l \in \{L, R, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}              \\
       g \circ f   & :=
@@
     \Cube^n(p) & := \Hom(p, n)            \\
-    \Cube^n(f) & := \lambda g . g \circ f
+    \Cube^n(f) & := \lambda g .\, g \circ f
   \end{align*}
@@
 Let us call $\nu$-sets, the straightforward generalization of augmented semi-simplicial sets and semi-cubical sets to an arbitrary cardinal, where morphisms are sequences of elements of an arbitrary set $\nu$, extended with $\kstar$.
-Then, we observe:
+That is:
 
@@
 
-\section{Our construction}
-In this section, we gradually build up an intuition for our construction, followed by the full details of our construction.
+\section{Our setting}
 
-\subsection{Homotopy type theory}
-Homotopy type theory (HoTT) is a logical foundation based on Martin-Löf type theory and the univalence axiom~\cite{hottbook}.
-HoTT is based on the notion of a basic \Type, and the notion of sets can be recovered as \U, where $\U$ is a straightforward packaging of two fields:
+In this
+
+\subsection{Working with sets in type theory}
+Martin-L\"of's Type theory~\cite{martinlof84,?} is a logical formalism based on the notion of $\Type$ rather than \Set.
+It is the core of several tools for the formalization of mathematics such as Coq~\cite{} or Lean~\cite{}.
+Type Theory is a flexible formalism supporting different models.
+One of this model interprets types as topological spaces, where equality is interpreted as path, and substitutivity of equality as transport, leading to the development of Homotopy Type Theory~\cite{hottbook}, a foundation of mathematics alternative to set theory.
+Conversely, a notion of sets can be recovered within Type Theory as \U, denoting the subtype of $\Type$ for which paths are degenerated, what can be expressed by the property of Uniqueness of Identity Proofs (UIP).
+Technically, this is expressed as a structure equipping a domain $\Dom$ with the property $\UIP$:
 
@@
 
-In the $\U$ universe, three properties hold:
+In the $\U$ universe, the following properties hold:
 
 \begin{enumerate}
-  \item[(i)] UIP holds on the unit type.
-  \item[(ii)] UIP propagates to $\Sigma$-types.
-  \item[(iii)] UIP propagates to $\Pi$-types, with some additional functional extensionality axioms.
-\end{enumerate}
-
-$\U$ provides us a form of unicity of identity of proofs (UIP), which is a form of proof irrelevance:
-
-\begin{align*}
-  \forall x y, \forall p q : x = y, p = q
-\end{align*}
-
-which is to say that any two proofs of \emph{equality} of the same two types are \emph{equal}. In other words, the proofs cannot be distinguished from one another.
-
-An equivalent definition of UIP is given by \textsf{UIP\_refl}:
-
-\begin{align*}
-  \textsf{UIP\_refl} & : \forall x, \forall p : x = x, p = \textsf{eq\_refl } x
-\end{align*}
-
-In type theory, UIP can be proved on the unit type and bool type:
-
+  \item[(i)] UIP holds on the unit and bool type:
 \begin{align*}
@@
 \end{align*}
+  \item[(ii)] UIP propagates to $\Sigma$-types.
+  \item[(iii)] UIP propagates to $\Pi$-types, with some additional functional extensionality axioms.
+\end{enumerate}
+
+Note that an equivalent definition of UIP is given by \textsf{UIP\_refl}:
+
+\begin{align*}
+  \textsf{UIP\_refl} & : \forall x:\Dom, \forall p : x = x, p = \textsf{eq\_refl } x
+\end{align*}
 
@@
 It is well-known in set theory that families of small sets can be represented in a fibered or indexed way.
-In the fibered way, a family over $T$ is represented a pair of a set $S$, and a function $S \rightarrow T$.
+In the fibered way, a family over $T$ is represented a pair of a set $S$, and a function from $S$ to $T$.
 The function classifies the original set into fibers.
-In contrast, in the indexed way, a family over $T$ is represented as a functional relation with domain $T$, which itself, by replacement axiom, is a set.
+In contrast, in the indexed way, a family over $T$ is represented as a functional relation with domain $T$, which itself, by the replacement axiom, is a set.
 
@@
 
-The latter correspondence can be expressed in HoTT, for $T: \Type$, as an equivalence between $\Sigma S: \Type\;.\;S \rightarrow T$ and $T \rightarrow \Type$, which can be proved using univalence.
+The latter correspondence can be expressed in Homotopy Type Theory, for $T: \Type$, as an equivalence between $\Sigma S: \Type\;.\;S \rightarrow T$ and $T \rightarrow \Type$, which can be proved using univalence.
 This correspondence also holds on \U, for $T: \U$:
@@
 
-Let us now come back to cubical sets. A cubical set can be represented as a sequence of fibrations, together with appropriate coherence conditions.
+Let us now come back to semi-cubical sets. A semi-cubical set can be represented as a sequence of fibrations, together with appropriate coherence conditions.
 
@@
   \begin{tikzcd}
-    X_0 : \U & X_1 : \U \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \U \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
+    X_0 : \U & X_1 : \U \arrow[l, "\delta^L" description, shift left=2] \arrow[l, "\delta^R" description, shift right=2] & X_2 : \U \arrow[l, "\delta^{L\kstar}" description, shift left=6] \arrow[l, "\delta^{R\kstar}" description, shift left=2] \arrow[l, "\delta^{\kstar R}" description, shift right=2] \arrow[l, "\delta^{\kstar L}" description, shift right=6] & \ldots
   \end{tikzcd}
@@
 
+\section{Our construction}
+
+In this section, we gradually build up an intuition for our construction, followed by the full details.
+
 \subsection{Intuition for our formal construction}
+
 \begin{notation}[$\Sigma$]

### 2023-01-11 paper/paper.tex
art.cls, paper: mostly whitespace changes, update submodule

@@
 
-This paper describes an alternative indexed construction of both augmented semi-simplicial and semi-cubical sets based on the property that augmented semi-simplicial and semi-cubical sets naturally arise as respectively unary and binary iterated parametricity-based constructions.
+  This paper describes an alternative indexed construction of both augmented semi-simplicial and semi-cubical sets based on the property that they naturally arise as respectively unary and binary iterated parametricity-based constructions.
 
@@
 We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of realizability~\cite{bernardy12,moulin16}.
-It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication by Thorsten Altenkirch and Hugo Moeneclaey}.
+It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication with Thorsten Altenkirch and Hugo Moeneclaey}.
 
 We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both semi-simplicial and semi-cubical sets obtained by applying simple rules iterating parametricity.
-In contrast to the standard presheaf presentation of semi-simplicial and semi-cubical sets~\cite{fri08,grandis03,buchholtz1}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
-That is, instead of having the set of semi-simplices or semi-cubes in dimension $n+1$
-\emph{fibered} over the set of semi-simplices or semi-cubes in dimension $n$, we consider families of semi-simplices and semi-cubes indexed over their faces.
+In contrast to the standard presheaf presentation of semi-simplicial and semi-cubical sets~\cite{fri08,grandis03,buchholtz17}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
+That is, instead of having the set of semi-simplices or semi-cubes in dimension $n+1$ \emph{fibered} over the set of semi-simplices or semi-cubes in dimension $n$, we consider families of semi-simplices and semi-cubes indexed over their faces.
 
@@
 \subsection{Semi-cubical sets}
-
 Semi-cubical sets are defined like augmented semi-simplicial sets except that $\DeltaPlus$ is replaced by $\Cube$ in which we take sequences of $L$, $R$ and $\star$, instead of sequences of $0$ and $\kstar$.
@@
 \begin{definition}[\Cube]
-  The definition of $\Cube$ is shown in Fig.~\ref{fig:cube}.
-  The symbols $L$ and $R$ indicate opposite faces of a cube.
+  The definition of $\Cube$ is shown in Fig.~\ref{fig:cube}. The symbols $L$ and $R$ indicate opposite faces of a cube.
   \begin{figure*}[!t]
@@
 \section{Our setting}
-
-In this
+In this section,
 
 \subsection{Working with sets in type theory}
-Martin-L\"of's Type theory~\cite{martinlof84,?} is a logical formalism based on the notion of $\Type$ rather than \Set.
+Martin-Löf's Type theory~\cite{martinlof84,?} is a logical formalism based on the notion of $\Type$ rather than \Set.
 It is the core of several tools for the formalization of mathematics such as Coq~\cite{} or Lean~\cite{}.
@@
   \item[(i)] UIP holds on the unit and bool type:
+
     \begin{align*}
@@
     \end{align*}
+
   \item[(ii)] UIP propagates to $\Sigma$-types.
@@
 \section{Our construction}
-
 In this section, we gradually build up an intuition for our construction, followed by the full details.
@@
 \subsection{Intuition for our formal construction}
-
 \begin{notation}[$\Sigma$]

### 2023-01-13 paper/paper.tex
Update

@@
 \begin{abstract}
-  Constructions such as semi-simplicial and semi-cubical sets can be defined in the ``usual way'' as presheaves over respectively the semi-simplex or semi-cube category, which we shall call ``fibered'' definitions, but also, as done e.g.
-in Voevodsky~\cite{} and in previous work~\cite{} as an ``dependently-typed'', or, say, ``indexed'' construction.
+  Constructions such as semi-simplicial and semi-cubical sets can be defined in the ``usual way'' as presheaves over respectively the semi-simplex or semi-cube category, which we shall call \emph{fibered} definitions, but also, as done e.g.
+in Voevodsky~\cite{voevodsky12} and in previous work~\cite{herbelin15} as a dependently-typed, or, say, \emph{indexed} construction.
 
@@
 \subsection{Working with sets in type theory}
-Martin-Löf's Type theory~\cite{martinlof84,?} is a logical formalism based on the notion of $\Type$ rather than \Set.
-It is the core of several tools for the formalization of mathematics such as Coq~\cite{} or Lean~\cite{}.
-Type Theory is a flexible formalism supporting different models.
-One of this model interprets types as topological spaces, where equality is interpreted as path, and substitutivity of equality as transport, leading to the development of Homotopy Type Theory~\cite{hottbook}, a foundation of mathematics alternative to set theory.
-Conversely, a notion of sets can be recovered within Type Theory as \U, denoting the subtype of $\Type$ for which paths are degenerated, what can be expressed by the property of Uniqueness of Identity Proofs (UIP).
+Martin-Löf's Type theory~\cite{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
+It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Coq~\cite{coq22} or Lean~\cite{lean15}.
+Type theory is a flexible formalism supporting different models.
+One of this model interprets types as topological spaces, where equality is interpreted as path and substitutivity of equality as transport.
+This model supports the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\cite{hottbook}.
+In type theory, types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number.
+Typical types in type theory are the types of dependent pairs, called $\Sigma$-types, with projections $\hd$ and $\tl$, the types of dependent functions, called $\Pi$-types, a distinguished singleton type called $\textsf{unit}$ type, the type of Boolean values, called $\textsf{bool}$, the type of natural numbers.
+
+A notion of sets can be recovered in each universe as $\U[m]$, denoting the subtype of $\Type_m$ for which paths are degenerated, what can be expressed by the property of Uniqueness of Identity Proofs (UIP).
 Technically, this is expressed as a structure equipping a domain $\Dom$ with the property $\UIP$:
@@
 \begin{align*}
-  \Dom & : \Type                                          \\
+  \Dom & : \Type_m                                          \\
   \UIP & : \forall x y : \Dom, \forall p q : x = y, p = q
@@
 
-In the $\U$ universe, the following properties hold:
+In $\U[m]$, the following properties hold:
 
@@
 
+Unless otherwise specified, we fix a universe level $m$ and abbreviate
+$\Type_m$ as $\Type$ and $\U[m]$ as $\U$.
+
 \subsection{Fibered versus indexed representation}
@@
 \begin{equation*}
-  \Sigma S: \U\;.\;S\rightarrow T \simeq T \rightarrow \U
+  \Sigma S: \U\;.\;S\rightarrow T ~\simeq~ T \rightarrow \U
 \end{equation*}
@@
 
-We can iteratively apply the above correspondence to obtain an indexed representation of cubical sets.
+We can iteratively apply the above correspondence to obtain an indexed representation of semi-cubical sets.
 

### 2023-01-15 paper/paper.tex
paper, paper.bib: polish, fix bib

@@
 \section{Our setting}
-In this section,
+In this section, we explain how we recover the notion of sets in type theory, and briefly explain the difference between the fibered and indexed representations.
 
@@
 In type theory, types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number.
-Typical types in type theory are the types of dependent pairs, called $\Sigma$-types, with projections $\hd$ and $\tl$, the types of dependent functions, called $\Pi$-types, a distinguished singleton type called $\textsf{unit}$ type, the type of Boolean values, called $\textsf{bool}$, the type of natural numbers.
+Typical types in type theory are the types of dependent pairs, called $\Sigma$-types, with projections $\hd$ and $\tl$, the types of dependent functions, called $\Pi$-types, a distinguished singleton type called $\textsf{unit}$ type, the type of boolean values, called $\textsf{bool}$, and the type of natural numbers.
 
@@
   \item[(i)] UIP holds on the unit and bool type:
-
     \begin{align*}
@@
       \textsf{UIP\_refl\_unit} & : \forall u : \textsf{unit}, \forall x : u = u, x = \textsf{eq\_refl} \\
-      \textsf{UIP\_refl\_bool} & : \forall b : \textsf{bool}, \forall x : b = b, x = \textsf{eq\_refl} \\
+      \textsf{UIP\_refl\_bool} & : \forall b : \textsf{bool}, \forall x : b = b, x = \textsf{eq\_refl}
     \end{align*}
-
   \item[(ii)] UIP propagates to $\Sigma$-types.
@@
 \subsection{Intuition for our formal construction}
-\begin{notation}[$\Sigma$]
-  In the prose that follows, we assume the existence of $\Sigma$-types with projections $\hd$ and $\tl$.
-\end{notation}
-
 To assign $X_0, X_1, X_2, \ldots$ in the above indexed representation types, we need to exhibit a recursive definition over our building blocks, which we will call $\framep$, $\layer$, and $\filler$.

### 2023-01-17 paper/paper.tex
paper: add \booltype

@@
 
-% The unit type
+% The unit and bool types
 \newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
+\newcommand{\booltype}{\ensuremath{\mathsf{bool}}}
 \newcommand{\unitpoint}{\ensuremath{\ast}}
@@
 The outline of the paper is as follows.
-First, we briefly describe a free-monoid-style (?) in the fibered presentation of semi-simplicial and semi-cubical sets, and our generalization to $\nu$-sets.
+First, we recall the definition of the augmented semi-simplicial and semi-cubical categories using a combinatorial presentation, that directly leads to our generalization to $\nu$-sets.
 We then proceed to explain our indexed construction, with the help of diagrams.
@@
 \subsection{Generalization to \texorpdfstring{$\nu$}{ν}-sets}
-Let us call $\nu$-sets, the straightforward generalization of augmented semi-simplicial sets and semi-cubical sets to an arbitrary cardinal, where morphisms are sequences of elements of an arbitrary set $\nu$, extended with $\kstar$.
+Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets.
+To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner by taking sequences of elements of a set $\nu$ of arbitrary cardinal, extended with $\kstar$.
 That is:
@@
 \subsection{Working with sets in type theory}
-Martin-Löf's Type theory~\cite{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
+Martin-Löf's Type theory~\cite{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a\emph{set}.
 It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Coq~\cite{coq22} or Lean~\cite{lean15}.
@@
 In type theory, types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number.
-Typical types in type theory are the types of dependent pairs, called $\Sigma$-types, with projections $\hd$ and $\tl$, the types of dependent functions, called $\Pi$-types, a distinguished singleton type called $\textsf{unit}$ type, the type of boolean values, called $\textsf{bool}$, and the type of natural numbers.
+Main types in type theory are the types of dependent pairs, written $\Sigma a : A.\,B(a)$, and the types of dependent functions, written $\Pi a:A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$.
+We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, called $\textsf{bool}$, and the type of natural numbers.
+We also write $\hd$ and $\tl$ the projections of dependent pairs.
+In type theory, logical propositions are types themselves and we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification.
 
@@
   \Dom & : \Type_m                                        \\
-  \UIP & : \forall x y : \Dom, \forall p q : x = y, p = q
+  \UIP & : \Pi x y : \Dom, \Pi p q : x = y, p = q
 \end{align*}
@@
     \begin{align*}
-      \textsf{eq\_refl}        & : \forall x, x = x                                                    \\
-      \textsf{UIP\_refl\_unit} & : \forall u : \textsf{unit}, \forall x : u = u, x = \textsf{eq\_refl} \\
-      \textsf{UIP\_refl\_bool} & : \forall b : \textsf{bool}, \forall x : b = b, x = \textsf{eq\_refl}
+      \textsf{eq\_refl}        & : \Pi x, x = x                                                    \\
+      \textsf{UIP\_refl\_unit} & : \Pi u : \textsf{unit}, \Pi x : u = u, x = \textsf{eq\_refl} \\
+      \textsf{UIP\_refl\_bool} & : \Pi b : \textsf{bool}, \Pi x : b = b, x = \textsf{eq\_refl}
     \end{align*}
@@
 \begin{align*}
-  \textsf{UIP\_refl} & : \forall x:\Dom, \forall p : x = x, p = \textsf{eq\_refl } x
+  \textsf{UIP\_refl} & : \Pi x:\Dom, \Pi p : x = x, p = \textsf{eq\_refl } x
 \end{align*}
@@
 
-We can iteratively apply the above correspondence to obtain an indexed representation of semi-cubical sets.
+If we think of $X_1$ fibered over two copies of $X_0$ in an indexed way, we get $X_1$ of type $X_0 \times X_0 \rightarrow \U$.
+Continuing the process, we can think of $X_2$ fibered over four copies of $X_1$ themselves fibered over two copies of $X_0$ as a dependent type.
+We have a priori a dependency over eight copies of $X_0$ but these are actually four due to the coherence conditions.
+Based on these coherence conditions, the type of $X_2$ happens to have the form $\Pi a b c d, X_1 (a, b) \times X_1 (a, c) \times X_1 (b, d) \times X_1 (c, d) \rightarrow \U$, recovering the square structure of $X_2$.
+In summary,
 
@@
   X_1 & :                  & X_0 \times X_0 \rightarrow \U                            \\
-  X_2 & : \forall a b c d, & X_1 (a, b) \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \\
-      &                    & \rightarrow X_1 (c, d) \rightarrow \U                    \\
+  X_2 & : \Pi a b c d, & X_1 (a, b) \times X_1 (a, c)  \times X_1 (b, d) \times X_1 (c, d) \\
+ & &  \rightarrow \U                    \\
   \ldots

### 2023-01-17 paper/paper.tex
Progress
paper: introduce \DeltaHat

@@
 % Simplicial and Cubical sets
+\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
 \newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
@@
 
-While ordinary semi-simplicial sets are presheaves over the semi-simplex category $\hat{\Delta}$, augmented semi-simplicial sets are presheaves over, what we will define as, $\DeltaPlus$.
-There are different ways to define $\DeltaPlus$, upto equivalence, and we use a combinatorial definition.
+While ordinary semi-simplicial sets are presheaves over the semi-simplex category \DeltaHat, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus.
+There are different ways to define \DeltaPlus, upto equivalence, and we use a combinatorial definition.
 The reason for our choice is that this definition has a straightforward extension to semi-cubical sets.

### 2023-01-18 paper/paper.tex
More progress
progress

@@
 
-\title{A formalization of semi-simplicial and semi-cubical sets in dependent type theory}
+\title{A parametricity-based formalization of semi-simplicial and semi-cubical sets}
 \author{\IEEEauthorblockN{Hugo Herbelin \\ and Ramkumar Ramachandra} \IEEEauthorblockA{Université Paris Cité, Inria, CNRS, IRIF, Paris}}
@@
 \begin{abstract}
-  Constructions such as semi-simplicial and semi-cubical sets can be defined in the ``usual way'' as presheaves over respectively the semi-simplex or semi-cube category, which we shall call \emph{fibered} definitions, but also, as done e.g.
-in Voevodsky~\cite{voevodsky12} and in previous work~\cite{herbelin15} as a dependently-typed, or, say, \emph{indexed} construction.
+  Constructions such as semi-simplicial and semi-cubical sets can be defined in the ``usual way'' as presheaves over respectively, the semi-simplex or semi-cube category, which we call \emph{fibered} definitions, but also defined like in e.g.
+Voevodsky~\cite{voevodsky12} or in previous work~\cite{herbelin15}, as a dependently-typed construction, which we call \emph{indexed}.
 
-  This paper describes an alternative indexed construction of both augmented semi-simplicial and semi-cubical sets based on the property that they naturally arise as respectively unary and binary iterated parametricity-based constructions.
+  This paper describes an alternative indexed characterization of both augmented semi-simplicial and semi-cubical sets arising respectively as unary and binary iterated parametricity-based constructions.
 
-  Additionally, the axiom-free construction has been fully formalized in Coq's dependent type theory, which turned out not to be so straightforward.
+  Additionally, our construction is fully formalized in Coq's dependent type theory.
 \end{abstract}
@@
 Our precise mechanization in Coq is available on Github, at \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}.
+The construction was conceived in Summer 2019 and the mechanization began in late 2019.
+A sketch of the construction was presented at the 2020 HoTT-UF workshop and the completion of the mechanization was reported at the TYPES 2022 conference.
 
@@
 \end{align*}
+
+Now, let's observe that the process of construction of the type of
+$X_1$ from that of $X_0$ and from that of $X_2$ to that of $X_1$ is
+similar to applying a binary parametricity translation on contexts that
+is: to triplicate each declaration $x_L:X_0$ and $x_R:X_0$ into two
+copies of $x$ and a line connecting these copies, that is into two
+triples of declarations $x_{LL}:X_0, x_{LR}:X_0,
+x_{L\kstar}:X_1(x_{LL},x_{LR})$ and $x_{RL}:X_0, x_{RL}:X_0,
+x_{R\kstar}:X_1(x_{RL},x_{RR})$, and to expand $\U$ into the type of a
+relation over these two copies, that is, into $x_{\kstar
+  L}:X_1(x_{LL},x_{RL}) \times x_{\kstar R}:X_1(x_{LR},x_{RR})
+\rightarrow \U$.
 
@@
 
+\section{Perspectives}
+
+In the cubical case, we expect the construction to eventually provide
+a model of (some version of) parametric type theory~\cite{} by adding
+degeneracies, a hierarchy of universes (as sketched e.g. in a talk by
+Herbelin at the HoTT-UF workshop for the bridge
+case~\cite{herbelin-hott-uf}) as well as reasoning modulo
+permutations~\cite{grandis03}.
+
+By equipping the universe construction with a structure of
+equivalences (as suggested along the lines of Altenkirch and
+Kaposi~\cite{}), as well as connections~\cite{}, we expect the
+parametric model to extend into a model of cubical type
+theory~\cite{}. A key point in this approach, is that, thanks to the
+indexed construction, we expect univalence to hold by definition in
+the model, without requiring any kind of Reedy fibrancy as it would a
+priori be needed in the fibered case. If these intuitions are correct,
+this would definitively root cubical type theory on top of iterated
+parametricity translation.
+
 \bibliographystyle{IEEEtran}

### 2023-01-20 paper/paper.tex
progress

@@
 Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
-We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of realizability~\cite{bernardy12,moulin16}.
+We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case, we obtain a form of realizability~\cite{bernardy12,moulin16}.
 It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication with Thorsten Altenkirch and Hugo Moeneclaey}.
@@
 
-If we think of $X_1$ fibered over two copies of $X_0$ in an indexed way, we get $X_1$ of type $X_0 \times X_0 \rightarrow \U$.
+If we think of $X_1$ fibered over two copies of $X_0$ in an indexed way, we get $X_1$ of type $X_0 \rightarrow X_0 \rightarrow \U$.
 Continuing the process, we can think of $X_2$ fibered over four copies of $X_1$ themselves fibered over two copies of $X_0$ as a dependent type.
 We have a priori a dependency over eight copies of $X_0$ but these are actually four due to the coherence conditions.
-Based on these coherence conditions, the type of $X_2$ happens to have the form $\Pi a b c d, X_1 (a, b) \times X_1 (a, c) \times X_1 (b, d) \times X_1 (c, d) \rightarrow \U$, recovering the square structure of $X_2$.
+Based on these coherence conditions, the type of $X_2$ happens to have the form $\Pi a b c d, X_1 (a)(b) \rightarrow X_1 (a)(c) \rightarrow X_1 (b)(d) \rightarrow X_1 (c)(d) \rightarrow \U$, recovering the square structure of $X_2$.
 In summary,
@@
   X_0 & :                  & \U                                                       \\
-  X_1 & :                  & X_0 \times X_0 \rightarrow \U                            \\
-  X_2 & : \Pi a b c d, & X_1 (a, b) \times X_1 (a, c)  \times X_1 (b, d) \times X_1 (c, d) \\
- & &  \rightarrow \U                    \\
+  X_1 & :                  & X_0 \rightarrow X_0 \rightarrow \U                            \\
+  X_2 & : \Pi a b c d, & X_1(a)(b) \rightarrow X_1(a)(c) \rightarrow X_1 (b)(d) \\
+  & & \rightarrow X_1 (c)(d) \rightarrow \U                    \\
   \ldots
@@
 
-Now, let's observe that the process of construction of the type of
-$X_1$ from that of $X_0$ and from that of $X_2$ to that of $X_1$ is
-similar to applying a binary parametricity translation on contexts that
-is: to triplicate each declaration $x_L:X_0$ and $x_R:X_0$ into two
-copies of $x$ and a line connecting these copies, that is into two
-triples of declarations $x_{LL}:X_0, x_{LR}:X_0,
-x_{L\kstar}:X_1(x_{LL},x_{LR})$ and $x_{RL}:X_0, x_{RL}:X_0,
-x_{R\kstar}:X_1(x_{RL},x_{RR})$, and to expand $\U$ into the type of a
-relation over these two copies, that is, into $x_{\kstar
-  L}:X_1(x_{LL},x_{RL}) \times x_{\kstar R}:X_1(x_{LR},x_{RR})
-\rightarrow \U$.
+We observe that the process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$, is similar to applying a binary parametricity translation and expecting the resulting translation to be inhabited.
+Indeed, parametricity interprets a type $A$ by a relation $A_\kstar$ over this type, and a term $t: A$ as an evidence that $A_\kstar(t)(t)$ is inhabited.
+Technically, $\U$ is interpreted as the relation ${\U}_\kstar$, which takes two types $A_L$ and $A_R$ and returns the type $A_L \rightarrow A_R \rightarrow \U$, while a dependent function type $\Pi a: A.\, B$ is interpreted as the relation $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and returns the $\Pi$ type taking as arguments two copies of $a: A$ together with a line between the two copies.
+That is,
 
-The focus of our work has been to formally define such an indexed presentation of not just semi-cubical, but more generally, $\nu$-sets.
+\begin{align*}
+  & (\Pi a: A.\, B)_\kstar(f_L)(f_R) \defeq \\
+  & \Pi a_L: A.\, \Pi a_R: A.\, A_\kstar(a_L)(a_R) \rightarrow B_\kstar(f_L(a_L))(f_R(a_R))
+\end{align*}
+
+In particular, for $X: \U$, applying the parametricity translation is about exhibiting a relation $X_\kstar$ which inhabits ${\U}_\kstar(X)(X)$ i.e.
+$X \rightarrow X \rightarrow \U$.
+In turn, the parametricity translation of $X_\kstar: X \rightarrow X \rightarrow \U$ is about finding an inhabitant $X_{\kstar\kstar}$ of $(X \rightarrow X \rightarrow \U)\_\kstar(X_\kstar)(X_\kstar)$ i.e.
+of:
+%.
+Let us equivalently write the type of $X_1$ as $\Pi x_L: X_0.\, \Pi x_R: X_0.\, \U$.
+To define its translation, we need to triplicate each of $x_L: X_0$ and $x_R: X_0$ into two copies and a line connecting these copies, leading to the sequences of premises $x_{LL}: X_0$, $x_{LR}: X_0$, $x_{L\kstar}: X_1(x_{LL}$, $x_{LR})$ and $x_{RL}: X_0$, $x_{RL}: X_0$, $x_{R\kstar}: X_1(x_{RL})(x_{RR})$.
+Then, in the context of $x_L$ and $x_R$, interpreting $X_1(x_L)(x_R): \U$ itself leads to exhibiting an inhabitant of $X_1(x_{LL})(x_{LR}) \rightarrow X_1(x_{RL})(x_{RR}) \rightarrow \U$, therefore leading to exhibiting an inhabitant of:
+
+\begin{align*}
+  \Pi x_{LL}: X.\, \Pi x_{LR}: X\, X_\kstar(x_{LL})(x_{LR}) \\
+  \rightarrow \Pi x_{RL}: X.\, \Pi x_{RR}: X.\, X_\kstar(x_{RL})(x_{RR}) \\ \rightarrow X_\kstar(x_{LL}, x_{RL}) \rightarrow X_\kstar(x_{LR})(x_{RR}) \\
+  \rightarrow \U
+\end{align*}
+
+which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration $X_0 \defeq X$, $X_1 \defeq X_\kstar$, $X_2 \defeq X_{\kstar\kstar}$ of parametricity applied to an initial $X: \U$.
+This tells us how the previous (informal) type given to $X_2$ could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.
+
+The focus of our work has then been to formally define such an indexed presentation of not just semi-cubical, but more generally, $\nu$-sets.
 
@@
 The rest of the construction is shown in Fig.
-\ref{fig:intuition}
+\ref{fig:intuition}.
 
@@
 
-In the cubical case, we expect the construction to eventually provide
-a model of (some version of) parametric type theory~\cite{} by adding
-degeneracies, a hierarchy of universes (as sketched e.g. in a talk by
-Herbelin at the HoTT-UF workshop for the bridge
-case~\cite{herbelin-hott-uf}) as well as reasoning modulo
-permutations~\cite{grandis03}.
+In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\cite{} by adding degeneracies, a hierarchy of universes (as sketched e.g.
+in a talk by Herbelin at the HoTT-UF workshop for the bridge case~\cite{herbelin-hott-uf}) as well as reasoning modulo permutations~\cite{grandis03}.
 
-By equipping the universe construction with a structure of
-equivalences (as suggested along the lines of Altenkirch and
-Kaposi~\cite{}), as well as connections~\cite{}, we expect the
-parametric model to extend into a model of cubical type
-theory~\cite{}. A key point in this approach, is that, thanks to the
-indexed construction, we expect univalence to hold by definition in
-the model, without requiring any kind of Reedy fibrancy as it would a
-priori be needed in the fibered case. If these intuitions are correct,
-this would definitively root cubical type theory on top of iterated
-parametricity translation.
+By equipping the universe construction with a structure of equivalences (as suggested along the lines of Altenkirch and Kaposi~\cite{}), as well as connections~\cite{}, we expect the parametric model to extend into a model of cubical type theory~\cite{}.
+A key point in this approach, is that, thanks to the indexed construction, we expect univalence to hold by definition in the model, without requiring any kind of Reedy fibrancy as it would a priori be needed in the fibered case.
+If these intuitions are correct, this would definitively root cubical type theory on top of iterated parametricity translation.
 

### 2023-01-20 paper/paper.tex
progress

@@
 Indeed, parametricity interprets a type $A$ by a relation $A_\kstar$ over this type, and a term $t: A$ as an evidence that $A_\kstar(t)(t)$ is inhabited.
-Technically, $\U$ is interpreted as the relation ${\U}_\kstar$, which takes two types $A_L$ and $A_R$ and returns the type $A_L \rightarrow A_R \rightarrow \U$, while a dependent function type $\Pi a: A.\, B$ is interpreted as the relation $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and returns the $\Pi$ type taking as arguments two copies of $a: A$ together with a line between the two copies.
-That is,
+Technically, $\U$ is interpreted as the relation ${\U}_\kstar$, which takes two types $A_L$ and $A_R$ and returns the type $A_L \rightarrow A_R \rightarrow \U$, while a dependent function type $\Pi a: A.\, B$ is interpreted as the relation $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
 
@@
 $X \rightarrow X \rightarrow \U$.
-In turn, the parametricity translation of $X_\kstar: X \rightarrow X \rightarrow \U$ is about finding an inhabitant $X_{\kstar\kstar}$ of $(X \rightarrow X \rightarrow \U)\_\kstar(X_\kstar)(X_\kstar)$ i.e.
+In turn, the parametricity translation of $X_\kstar: X \rightarrow X \rightarrow \U$ is about finding an inhabitant $X_{\kstar\kstar}$ of $(X \rightarrow X \rightarrow \U)_\kstar(X_\kstar)(X_\kstar)$ i.e.
 of:
-%.
-Let us equivalently write the type of $X_1$ as $\Pi x_L: X_0.\, \Pi x_R: X_0.\, \U$.
-To define its translation, we need to triplicate each of $x_L: X_0$ and $x_R: X_0$ into two copies and a line connecting these copies, leading to the sequences of premises $x_{LL}: X_0$, $x_{LR}: X_0$, $x_{L\kstar}: X_1(x_{LL}$, $x_{LR})$ and $x_{RL}: X_0$, $x_{RL}: X_0$, $x_{R\kstar}: X_1(x_{RL})(x_{RR})$.
-Then, in the context of $x_L$ and $x_R$, interpreting $X_1(x_L)(x_R): \U$ itself leads to exhibiting an inhabitant of $X_1(x_{LL})(x_{LR}) \rightarrow X_1(x_{RL})(x_{RR}) \rightarrow \U$, therefore leading to exhibiting an inhabitant of:
 
@@
   \Pi x_{LL}: X.\, \Pi x_{LR}: X\, X_\kstar(x_{LL})(x_{LR}) \\
-  \rightarrow \Pi x_{RL}: X.\, \Pi x_{RR}: X.\, X_\kstar(x_{RL})(x_{RR}) \\ \rightarrow X_\kstar(x_{LL}, x_{RL}) \rightarrow X_\kstar(x_{LR})(x_{RR}) \\
-  \rightarrow \U
-\end{align*}
-
-which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration $X_0 \defeq X$, $X_1 \defeq X_\kstar$, $X_2 \defeq X_{\kstar\kstar}$ of parametricity applied to an initial $X: \U$.
+  \rightarrow \Pi x_{RL}: X.\, \Pi x_{RR}: X.\, X_\kstar(x_{RL})(x_{RR}) \\ \rightarrow X_\kstar(x_{LL}, x_{RL}) \rightarrow X_\kstar(x_{LR})(x_{RR})  \rightarrow \U
+\end{align*}
+which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration
+
+\begin{align*}
+  X_0 &\defeq X:& \U \\
+  X_1 &\defeq X_\kstar:& {\U}_\kstar(X)(X) \\
+  X_2 &\defeq X_{\kstar\kstar}:& ({\U}_\kstar(X)(X))_{\kstar}(X_\kstar)(X_\kstar)
+\end{align*}
+of parametricity applied to an initial $X: \U$.
 This tells us how the previous (informal) type given to $X_2$ could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.

### 2023-01-20 paper/paper.tex
paper: minor fixes after LiveShare session with Hugo

@@
   \Dom & : \Type_m                                  \\
-  \UIP & : \Pi x y : \Dom, \Pi p q : x = y, p = q
+  \UIP & : \Pi x y: \Dom.\, \Pi p q: x = y.\, p = q
 \end{align*}
@@
     \begin{align*}
-      \textsf{eq\_refl}        & : \Pi x, x = x                                                    \\
-      \textsf{UIP\_refl\_unit} & : \Pi u : \textsf{unit}, \Pi x : u = u, x = \textsf{eq\_refl} \\
-      \textsf{UIP\_refl\_bool} & : \Pi b : \textsf{bool}, \Pi x : b = b, x = \textsf{eq\_refl}
+      \textsf{eq\_refl}        & : \Pi x.\, x = x                                             \\
+      \textsf{UIP\_refl\_unit} & : \Pi u: \unittype.\, \Pi x : u = u.\, x = \textsf{eq\_refl} \\
+      \textsf{UIP\_refl\_bool} & : \Pi b: \booltype.\, \Pi x : b = b.\, x = \textsf{eq\_refl}
     \end{align*}
@@
 \begin{align*}
-  \textsf{UIP\_refl} & : \Pi x:\Dom, \Pi p : x = x, p = \textsf{eq\_refl } x
+  \textsf{UIP\_refl} & : \Pi x: \Dom.\, \Pi p: x = x.\, p = \textsf{eq\_refl } x
 \end{align*}
@@
 \begin{align*}
-  X_0 &\defeq X:& \U \\
-  X_1 &\defeq X_\kstar:& {\U}_\kstar(X)(X) \\
-  X_2 &\defeq X_{\kstar\kstar}:& ({\U}_\kstar(X)(X))_{\kstar}(X_\kstar)(X_\kstar)
+  X_0 & \defeq X                & :\, & \U                                               \\
+  X_1 & \defeq X_\kstar         & :\, & {\U}_\kstar(X)(X)                                \\
+  X_2 & \defeq X_{\kstar\kstar} & :\, & ({\U}_\kstar(X)(X))_{\kstar}(X_\kstar)(X_\kstar)
 \end{align*}
@@
 
-\section{Perspectives}
+\section{Future work}
 
@@
 
-By equipping the universe construction with a structure of equivalences (as suggested along the lines of Altenkirch and Kaposi~\cite{}), as well as connections~\cite{}, we expect the parametric model to extend into a model of cubical type theory~\cite{}.
+By equipping the universe construction with a structure of equivalences , as suggested along the lines of Altenkirch and Kaposi~\cite{}, as well as connections~\cite{}, we expect the parametric model to extend into a model of cubical type theory~\cite{}.
 A key point in this approach, is that, thanks to the indexed construction, we expect univalence to hold by definition in the model, without requiring any kind of Reedy fibrancy as it would a priori be needed in the fibered case.

### 2023-01-21 paper/paper.tex
progress

@@
   X_1 & :              & X_0 \rightarrow X_0 \rightarrow \U                     \\
-  X_2 & : \Pi a b c d, & X_1(a)(b) \rightarrow X_1(a)(c) \rightarrow X_1 (b)(d) \\
+  X_2 & : \Pi a b c d. & X_1(a)(b) \rightarrow X_1(a)(c) \rightarrow X_1 (b)(d) \\
       &                & \rightarrow X_1 (c)(d) \rightarrow \U                  \\
@@
 Indeed, parametricity interprets a type $A$ by a relation $A_\kstar$ over this type, and a term $t: A$ as an evidence that $A_\kstar(t)(t)$ is inhabited.
-Technically, $\U$ is interpreted as the relation ${\U}_\kstar$, which takes two types $A_L$ and $A_R$ and returns the type $A_L \rightarrow A_R \rightarrow \U$, while a dependent function type $\Pi a: A.\, B$ is interpreted as the relation $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
+In particular, $\U$ is interpreted as the relation ${\U}_\kstar$, which takes two types $A_L$ and $A_R$ and returns the type $A_L \rightarrow A_R \rightarrow \U$, while, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the relation $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
 
@@
 
-In particular, for $X: \U$, applying the parametricity translation is about exhibiting a relation $X_\kstar$ which inhabits ${\U}_\kstar(X)(X)$ i.e.
-$X \rightarrow X \rightarrow \U$.
-In turn, the parametricity translation of $X_\kstar: X \rightarrow X \rightarrow \U$ is about finding an inhabitant $X_{\kstar\kstar}$ of $(X \rightarrow X \rightarrow \U)_\kstar(X_\kstar)(X_\kstar)$ i.e.
+In particular, for $X: \U$, applying the parametricity translation is about canonically associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X)(X)$ i.e.
+of $X \rightarrow X \rightarrow \U$.
+In turn, applying the parametricity translation to $X_\kstar: X \rightarrow X \rightarrow \U$ is about canonically associating to $X_\kstar$ an inhabitant $X_{\kstar\kstar}$ of $(X \rightarrow X \rightarrow \U)_\kstar(X_\kstar)(X_\kstar)$ i.e.
 of:
@@
 \end{align*}
-which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration
-
-\begin{align*}
-  X_0 & \defeq X                & :\, & \U                                               \\
-  X_1 & \defeq X_\kstar         & :\, & {\U}_\kstar(X)(X)                                \\
-  X_2 & \defeq X_{\kstar\kstar} & :\, & ({\U}_\kstar(X)(X))_{\kstar}(X_\kstar)(X_\kstar)
-\end{align*}
-of parametricity applied to an initial $X: \U$.
+which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of parametricity
+
+\begin{equation*}
+\begin{array}{llllr}
+  X_0 & \defeq & X                & : & \U                                               \\
+  X_1 & \defeq & X_\kstar         & : & {\U}_\kstar(X)(X)                                \\
+  X_2 & \defeq & X_{\kstar\kstar} & : & ({\U}_\kstar(X)(X))_{\kstar}(X_\kstar)(X_\kstar) \\
+  \ldots
+\end{array}
+\end{equation*}
+applied to an initial $X: \U$.
 This tells us how the previous (informal) type given to $X_2$ could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.
 
-The focus of our work has then been to formally define such an indexed presentation of not just semi-cubical, but more generally, $\nu$-sets.
+Notice, however, that the recipe obtained so far, $X_{n + 1}: ({S_n})_\kstar(X_n)(X_n)$ for $X_n: S_n$, applies parametricity on the \emph{syntax} of the type of $X_n$.
+It does not directly yield a characterization of $S_n$ as a function from $n$, as one would need for that to work on the syntax of types, with an ultimate step of interpretation of the syntax of types as a type, rather than on types directly.
+Reformulating the recipe as an explicit type construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and the generalization to $\nu$-sets.
 
@@
 More concretely, we build the ten definitions shown in the tables by induction, and this is part of the definition of a larger record.
-Other fields in the record are necessary because we need copies of $\framep$, $\layer$, $\filler$ at levels $n - 1$ and $n - 2$, $\restrf$, $\restrl$, and $\restrc$ at level $n - 1$, and equations to recall the definitions of these objects at lower levels.
-
-The entire construction relies on inequalities over natural numbers, and we have three different definitions of $\leq$ addressing two different concerns, and conversions between them.
-First, we have what we call the ``recursive variant'', phrased as:
+The other fields of the record aref $\framep$, $\layer$, $\filler$ at levels $n - 1$ and $n - 2$, $\restrf$, $\restrl$, and $\restrc$ at level $n - 1$, and equations to recall the definitions of these objects at lower levels.
+
+The entire construction relies on inequalities over natural numbers, and we use two different definitions of $\leq$ addressing different concerns in our formalization.
+In order to build our first variant, we present an intermediate ``recursive definition'', phrased as:
 
@@
 
-The upside of this definition is that all inequalities of the form $m \leq n$ are equivalent, definitionally.
-By placing the definition in \SProp, we have definitional equality of inequality proofs.
-For the purpose of unification, however, this definition doesn't go far enough.
+By placing the definition in \SProp, we have definitional equality of all inequality proofs.
+For the purpose of unification, however, this definition does not go far enough.
 Consider the unification problems:
@@
 \end{minted}
-
 where \texttt{le\_trans} is transitivity, \texttt{le\_refl} is reflexivity, and \texttt{?p} is an existential variable.
 These two problems definitionally hold in \SProp, but equalizing them does not solve the existential.
-For unification to be useful in inferring existentials, we present our next definition, which we dub as the ``Yoneda variant'':
+For unification to be useful in inferring existentials, we present our first variant of $\leq$, which we dub as the ``Yoneda variant'':
 
@@
 
-Finally, we have the ``inductive variant'', phrased as:
+The second variant of $\leq$, the ``inductive variant'', is phrased as:
 
@@
 
+- Equality lemmas (rew_app, assoc, ...)
+
 \section{Future work}

### 2023-01-21 paper/paper.tex
theories/νType: some renames

@@
 In our usage, we have lemmas \texttt{leY\_of\_leI} and \texttt{leI\_of\_leY} in order to equip \texttt{leY} with the induction scheme of \texttt{leI}.
-Then, together with computational rules stated propositionally, we reason about $\beta$-reduction of induction.
-
-- Equality lemmas (rew_app, assoc, ...)
+The resulting induction scheme has computational rules holding propositionally.
 
 \section{Future work}
-
 In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\cite{} by adding degeneracies, a hierarchy of universes (as sketched e.g.

### 2023-01-21 paper/paper.tex
paper.bib: beef up

@@
 \section{Future work}
-In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\cite{} by adding degeneracies, a hierarchy of universes (as sketched e.g.
+In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\cite{nuyts17,cavallo19} by adding degeneracies, a hierarchy of universes (as sketched e.g.
 in a talk by Herbelin at the HoTT-UF workshop for the bridge case~\cite{herbelin-hott-uf}) as well as reasoning modulo permutations~\cite{grandis03}.
 
-By equipping the universe construction with a structure of equivalences , as suggested along the lines of Altenkirch and Kaposi~\cite{}, as well as connections~\cite{}, we expect the parametric model to extend into a model of cubical type theory~\cite{}.
+By equipping the universe construction with a structure of equivalences , as suggested along the lines of Altenkirch and Kaposi~\cite{altenkirch15}, as well as a structure of connections, we expect the parametric model to extend into a model of cubical type theory~\cite{bezem13}.
 A key point in this approach, is that, thanks to the indexed construction, we expect univalence to hold by definition in the model, without requiring any kind of Reedy fibrancy as it would a priori be needed in the fibered case.

### 2023-01-21 paper/paper.tex
rewording here and there

@@
 
-\section{Semi-simplicial and semi-cubical sets}
+\section{Semi-simplicial sets, semi-cubical sets and a generalization}
 It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
@@
 While ordinary semi-simplicial sets are presheaves over the semi-simplex category \DeltaHat, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus.
-There are different ways to define \DeltaPlus, upto equivalence, and we use a combinatorial definition.
-The reason for our choice is that this definition has a straightforward extension to semi-cubical sets.
+There are different ways to define \DeltaPlus, upto equivalence, and we use a definition that will later straightforwardly extend to semi-cubical sets.
 
 \begin{notation}[Finite sequences]
-  We denote finite sequences by $\{i_1, \ldots i_n\}$ for $i_j$ ranging over some domain. In particular, the empty sequence is written $\{\}$.
-\end{notation}
-
-\begin{notation}[::]
-  We define $i :: \{j_1, \ldots, j_n\}$ to be $\{i, j_1, \ldots, j_n\}$.
+  We denote finite sequences by $\{i_1, \ldots i_n\}$ for $i_j$ ranging over some domain.
+In particular, the empty sequence is written $\{\}$ and we define $i :: \{j_1, \ldots, j_n\}$ to be $\{i, j_1, \ldots, j_n\}$.
 \end{notation}
@@
       \end{cases} \\
-      \id              & := \{\kstar, \ldots, \kstar\} \text{ $n$ times}
+      \id              & := \{\kstar, \ldots, \kstar\} \text{ $n$ times} % TODO: n not bound on the left
     \end{align*}
@@
 \end{align*}
-which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of parametricity
+which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of parametricity applied to an initial $X: \U$:
 
@@
 \end{equation*}
-applied to an initial $X: \U$.
 This tells us how the previous (informal) type given to $X_2$ could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.
@@
 Notice, however, that the recipe obtained so far, $X_{n + 1}: ({S_n})_\kstar(X_n)(X_n)$ for $X_n: S_n$, applies parametricity on the \emph{syntax} of the type of $X_n$.
-It does not directly yield a characterization of $S_n$ as a function from $n$, as one would need for that to work on the syntax of types, with an ultimate step of interpretation of the syntax of types as a type, rather than on types directly.
-Reformulating the recipe as an explicit type construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and the generalization to $\nu$-sets.
+It does not directly yield a characterization of $S_n$ as a function from $n$.
+Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and its uniform treatment of augmented semi-simplial and semi-cubical sets by means of the generalization to $\nu$-sets.
 

### 2023-01-21 paper/paper.tex
referring to Yoneda embedding since this seems very standard terminology

@@
 \begin{definition}[$\DeltaPlus^n$]
-  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as:
+  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as what is called the Yoneda embedding of $n\in\Obj(\DeltaPlus)$:
 
@@
 \begin{definition}[$\Cube^n$]
-  The standard semi-cube $\Cube^n$ is defined as:
+  The standard semi-cube $\Cube^n$ is defined as the Yoneda embedding of $n\in\Obj(\Cube)$:
 

### 2023-01-21 paper/paper.tex
hinting about how building the n+1-semi-(simplex/cube) is a parametricity translation

@@
 
+In particular, the standard augmented $(n+1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as the base and glueing on top of it another copy of it lifted by one dimension.
+In the latter, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.
+
 \subsection{Semi-cubical sets}
@@
 \end{example}
+
+In particular, the standard $(n+1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them by a tube obtained as an other copy of the standard $n$-semi-cube stretched in the new dimension.
 

### 2023-01-21 paper/paper.tex
more definitions about nu-sets and making explicit the link with parametricity

@@
 Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets.
-To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner by taking sequences of elements of a set $\nu$ of arbitrary cardinal, extended with $\kstar$.
-That is:
+To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\nu$-semi-shape category.
+The morphisms of the $\nu$-semi-shape category are sequences of elements of a set $\nu$ of arbitrary cardinal, extended with $\kstar$, so that the following holds:
 
@@
 \end{table}
+
+A $\nu$-set is thus a functor $\phi$ from the $\nu$-semi-shape category to $\Set$ and we call $n$-$\nu$-semi-shape an element of $\phi(n)$.
+As in the augmented semi-simplicial and semi-cubical cases, the standard $(n+1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in a new dimension.
+We clarify in the next sections how this process of construction is similar to the parametricity translation considered in the context of typed programming languages~\cite{reynolds72, bernardy10, bernardy11, atkey14, bernardy15}.
 

### 2023-01-21 paper/paper.tex
moving the observation of indexed = parametricity to section "our construction"

@@
 
-We observe that the process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$, is similar to applying a binary parametricity translation and expecting the resulting translation to be inhabited.
+\section{Our construction}
+In this section, we gradually build up an intuition for our construction, followed by the full details.
+
+\subsection{Relating the indexed representation to parametricity}
+
+We observe that the process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$ in the last section, is similar to applying a binary parametricity translation and expecting the resulting translation to be inhabited.
 Indeed, parametricity interprets a type $A$ by a relation $A_\kstar$ over this type, and a term $t: A$ as an evidence that $A_\kstar(t)(t)$ is inhabited.
@@
 \end{equation*}
-This tells us how the previous (informal) type given to $X_2$ could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.
+This tells us how the informal type given to $X_2$ in the previous section could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.
 
@@
 Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and its uniform treatment of augmented semi-simplial and semi-cubical sets by means of the generalization to $\nu$-sets.
-
-\section{Our construction}
-In this section, we gradually build up an intuition for our construction, followed by the full details.
 

### 2023-01-21 paper/paper.tex
typo
full reading up to page 5

@@
 Voevodsky~\cite{voevodsky12} or in previous work~\cite{herbelin15}, as a dependently-typed construction, which we call \emph{indexed}.
-
-  This paper describes an alternative indexed characterization of both augmented semi-simplicial and semi-cubical sets arising respectively as unary and binary iterated parametricity-based constructions.
+%TODO anonymize
+
+  This paper describes an uniform indexed characterization of both augmented semi-simplicial and semi-cubical sets arising respectively as unary and binary iterated parametricity-based constructions.
 
@@
 \section{Introduction}
-In the context of functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational equality of programs of this type.
-Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
-We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case, we obtain a form of realizability~\cite{bernardy12,moulin16}.
+In the context of functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational behavior of programs of this type.
+Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity, when using more generally graphs than relations, has a cubical flavor (see e.g.~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}).
+We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or graphs, in which case, we obtain a form of realizability (see e.g.~\cite{bernardy12,lasson12,moulin16}).
 It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication with Thorsten Altenkirch and Hugo Moeneclaey}.
-
-We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both semi-simplicial and semi-cubical sets obtained by applying simple rules iterating parametricity.
-In contrast to the standard presheaf presentation of semi-simplicial and semi-cubical sets~\cite{fri08,grandis03,buchholtz17}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
-That is, instead of having the set of semi-simplices or semi-cubes in dimension $n+1$ \emph{fibered} over the set of semi-simplices or semi-cubes in dimension $n$, we consider families of semi-simplices and semi-cubes indexed over their faces.
+% TODO anonymize??
+
+We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets obtained by applying simple rules characterizing iterated parametricity.
+In contrast to the standard presheaf presentation of augmented semi-simplicial and semi-cubical sets (see e.g.~\cite{fri08,grandis03,buchholtz17}), our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
+That is, instead of having the set of augmented semi-simplices or semi-cubes in dimension $n+1$ \emph{fibered} over the set of augmented semi-simplices or semi-cubes in dimension $n$, we consider families of augmented semi-simplices and semi-cubes indexed over their faces.
 
@@
 We end with some of the finer details of our mechanization.
+% TODO polish
 
@@
 We will proceed to explain the mathematical objects we have formalized.
+% TODO: well-known: can we find a reference?
 
@@
 
+%TODO check in other places if it makes sense to use the notation and definition LaTeX environment
 \begin{definition}[$\DeltaPlus$]
@@
 \begin{example}[$\DeltaPlus^3$]
-  $\DeltaPlus^3$ is drawn as three points, given by $\Hom(1, 3)$, three lines connecting them, given by $\Hom(2, 3)$, and a filler given by $\Hom(3, 3)$.
+  $\DeltaPlus^3$ is drawn as three points, given by $\Hom(1, 3)$, three lines connecting them, given by $\Hom(2, 3)$, and a triangular filler given by $\Hom(3, 3)$.
 
@@
 
-In particular, the standard augmented $(n+1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as the base and glueing on top of it another copy of it lifted by one dimension.
+More generally, the standard augmented $(n+1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as the base and glueing on top of it another copy of it lifted by one dimension.
 In the latter, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.
+In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by 0 while the components of the lifted copy are postfixed by $\kstar$.
 
@@
 
-In particular, the standard $(n+1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them by a tube obtained as an other copy of the standard $n$-semi-cube stretched in the new dimension.
+More generally, the standard $(n+1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them by a tube obtained as a third copy stretched in the new dimension.
+The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the tube is obtained by postfixing with~$\kstar$.
 
@@
 A $\nu$-set is thus a functor $\phi$ from the $\nu$-semi-shape category to $\Set$ and we call $n$-$\nu$-semi-shape an element of $\phi(n)$.
-As in the augmented semi-simplicial and semi-cubical cases, the standard $(n+1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in a new dimension.
-We clarify in the next sections how this process of construction is similar to the parametricity translation considered in the context of typed programming languages~\cite{reynolds72, bernardy10, bernardy11, atkey14, bernardy15}.
+As in the augmented semi-simplicial and semi-cubical cases, the standard $(n+1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
+We clarify in the next sections how this process of construction is similar to the parametricity translation developed for functional programming~\cite{reynolds72} and more generally for type theory~\cite{bernardy10, bernardy11, atkey14, bernardy15}.
 
@@
 
+\subsection{Example: indexed semi-cubical sets}
+
 Let us now come back to semi-cubical sets. A semi-cubical set can be represented as a sequence of fibrations, together with appropriate coherence conditions.
@@
 
+Now, one may wonder how to express the type of $X_i$ uniformly as a function of $n$? Connecting semi-cubical sets to binary parametricity
+%, later, thanks to the generalization to $\nu$-sets, augmented semi-simplicial sets to unary parametricity
+will give us a solution which we describe in the next section.
+
 \section{Our construction}
@@
 
-We observe that the process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$ in the last section, is similar to applying a binary parametricity translation and expecting the resulting translation to be inhabited.
-Indeed, parametricity interprets a type $A$ by a relation $A_\kstar$ over this type, and a term $t: A$ as an evidence that $A_\kstar(t)(t)$ is inhabited.
-In particular, $\U$ is interpreted as the relation ${\U}_\kstar$, which takes two types $A_L$ and $A_R$ and returns the type $A_L \rightarrow A_R \rightarrow \U$, while, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the relation $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
+The process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$ in the last section, is similar to applying a binary parametricity translation and expecting the resulting translation to be inhabited.
+The parametricity which we consider interprets a type $A$ by a graph $A_\kstar$ over this type, and a term $t: A$ as an edge in $A_\kstar(t)(t)$.
+In particular, $\U$ is interpreted as the graph ${\U}_\kstar$, which takes two types $A_L$ and $A_R$ and returns the type $A_L \rightarrow A_R \rightarrow \U$ of graphs over $A_L$ and $A_R$.
+Also, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the graph $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$: %TODO be explicit that HSet and HSet* are in the next universe??
 
@@
    & (\Pi a: A.\, B)_\kstar(f_L)(f_R) \defeq                                                 \\
-   & \Pi a_L: A.\, \Pi a_R: A.\, A_\kstar(a_L)(a_R) \rightarrow B_\kstar(f_L(a_L))(f_R(a_R))
+   & \Pi a_L: A.\, \Pi a_R: A.\, \Pi a_\kstar: A_\kstar(a_L)(a_R).\, B_\kstar(f_L(a_L))(f_R(a_R))
 \end{align*}
@@
 \begin{align*}
-  \Pi x_{LL}: X.\, \Pi x_{LR}: X\, X_\kstar(x_{LL})(x_{LR})              \\
+  \Pi x_{LL}: X.\, \Pi x_{LR}: X.\, X_\kstar(x_{LL})(x_{LR})              \\
   \rightarrow \Pi x_{RL}: X.\, \Pi x_{RR}: X.\, X_\kstar(x_{RL})(x_{RR}) \\ \rightarrow X_\kstar(x_{LL}, x_{RL}) \rightarrow X_\kstar(x_{LR})(x_{RR})  \rightarrow \U
 \end{align*}
-which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of parametricity applied to an initial $X: \U$:
+which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of binary parametricity applied to an initial $X: \U$:
 
@@
 It does not directly yield a characterization of $S_n$ as a function from $n$.
-Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and its uniform treatment of augmented semi-simplial and semi-cubical sets by means of the generalization to $\nu$-sets.
+Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and the uniform treatment of augmented semi-simplial and semi-cubical sets by means of the generalization to $\nu$-sets.
 
 \subsection{Intuition for our formal construction}
-To assign $X_0, X_1, X_2, \ldots$ in the above indexed representation types, we need to exhibit a recursive definition over our building blocks, which we will call $\framep$, $\layer$, and $\filler$.
-A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$, and a $\filler$ is a filled $\framep$.
-
-We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a : A, (B a \rightarrow C)$ and $(\Sigma a : A, B a) \rightarrow C$.
-Let us now illustrate how we build $\fullframe[n]$ by refining types of $X_0, X_1, \ldots, X_{n - 1}$ so that they have the form $\fullframe[n] \rightarrow \U$.
+To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\filler$.
+A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$s, and a $\filler$ is a filled $\framep$.
+
+We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying to the description above the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a : A, (B a \rightarrow C)$ and $(\Sigma a : A, B a) \rightarrow C$.
+Let us now illustrate how we build $\fullframe[n]$.
 To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ of $X_0$ can be equivalently formulated as $\unittype \rightarrow \U$.
-Each $\fullframe[n]$ is made of $n$-layers, written $\layer[n][p]$ with $p < n$, initialized with the $\unittype$ type.
-Then, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$.
-The rest of the construction is shown in Fig.
+Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type.
+For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$.
+The next steps of the construction are shown in Fig.
 \ref{fig:intuition}.
@@
 
-The figure on the left is $\framep[3][1]$, on the right is $\framep[3][2]$, and on the bottom is $\framep[3][3]$.
+The figure on the left is $\framep[3][1]$, on the right is $\framep[3][2]$, and on the bottom is $\framep[3][3]$, which is full.
 Further, $\framep[3][1]$ is made of one layer, $\layer[3][0]$, shown in blue, $\framep[3][2]$ is made of one additional layer, $\layer[3][1]$, shown in red, $\framep[3][3]$ is made of one more layer, $\layer[3][2]$, shown in green.
-In general, a $\layer[n][p]$ is a product of $\nu$ $\filler[n - 1][p]$.
-Then, a $\filler[n][p]$ is an $n$-dimensional object obtained by stretching a $(n - p)$-dimensional frame in $p$ directions.
-For instance, each of the two $\filler[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\filler[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a square, and each of the two $\filler[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a square.
+
+We illustrated here the cubical case, that is $\nu=2$, but, in general, a $\layer[n][p]$ is a product of $\nu$ $\filler[n - 1][p]$.
+A $\filler[n][p]$ is an $n$-dimensional object obtained by stretching a $(n - p)$-dimensional frame in $p$ directions.
+For instance, in the picture, each of the two $\filler[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\filler[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a square, and each of the two $\filler[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a square.
 Note that a filler, which extends a frame with an element depending on it, shown as an element of $X_n$ below.
-As filler extends a frame, it also has layer components, but the layers are associated on the right that is opposite to the way they're associated in frames.
-
+As a filler extends a frame, it also has layer components, but note that the layers of a filler are associated on the right that is opposite to the way they are associated in frames:
 \begin{align*}
@@
 
-So far, we haven't paid attention to the fact that we have a dependent type, shown as a $\Sigma$.
+So far, we have not paid attention to the fact that we have a dependent type, shown as a $\Sigma$.
 Let us be more precise about this requirement.

### 2023-01-22 paper/paper.tex
paper: minor nits

@@
 
-\section{Semi-simplicial sets, semi-cubical sets and a generalization}
+\section{Semi-simplicial and semi-cubical sets}
 It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
@@
 In the latter, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.
-In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by 0 while the components of the lifted copy are postfixed by $\kstar$.
+In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by $\kstar$.
 

### 2023-01-22 paper/paper.tex
paper: minor nits

@@
       \end{cases} \\
-      \id              & := \{\kstar, \ldots, \kstar\} \text{ $n$ times}                             % TODO: n not bound on the left
+      \id              & := \{\kstar, \ldots, \kstar\} \text{ $n$ times for $\id \in \Hom(n, n)$}
     \end{align*}
@@
 \begin{definition}[$\DeltaPlus^n$]
-  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as what is called the Yoneda embedding of $n\in\Obj(\DeltaPlus)$:
+  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as what is called the Yoneda embedding of $n \in \Obj(\DeltaPlus)$:
 
@@
 More generally, the standard augmented $(n+1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as the base and glueing on top of it another copy of it lifted by one dimension.
-In the latter, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.
+In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.
 In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by $\kstar$.
@@
 \begin{definition}[$\Cube^n$]
-  The standard semi-cube $\Cube^n$ is defined as the Yoneda embedding of $n\in\Obj(\Cube)$:
+  The standard semi-cube $\Cube^n$ is defined as the Yoneda embedding of $n \in \Obj(\Cube)$:
 
@@
 
-More generally, the standard $(n+1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them by a tube obtained as a third copy stretched in the new dimension.
-The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the tube is obtained by postfixing with~$\kstar$.
+More generally, the standard $(n+1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them by a cylinder obtained as a third copy stretched in the new dimension.
+The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with \kstar.
 
@@
 
-Now, one may wonder how to express the type of $X_i$ uniformly as a function of $n$? Connecting semi-cubical sets to binary parametricity
-%, later, thanks to the generalization to $\nu$-sets, augmented semi-simplicial sets to unary parametricity
-will give us a solution which we describe in the next section.
+Now, one may wonder how to express the type of $X_i$ uniformly as a function of $n$. Connecting semi-cubical sets to binary parametricity will give us a solution which we describe in the next section.
 
@@
 \subsection{Relating the indexed representation to parametricity}
-
 The process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$ in the last section, is similar to applying a binary parametricity translation and expecting the resulting translation to be inhabited.
 The parametricity which we consider interprets a type $A$ by a graph $A_\kstar$ over this type, and a term $t: A$ as an edge in $A_\kstar(t)(t)$.
-In particular, $\U$ is interpreted as the graph ${\U}_\kstar$, which takes two types $A_L$ and $A_R$ and returns the type $A_L \rightarrow A_R \rightarrow \U$ of graphs over $A_L$ and $A_R$.
-Also, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the graph $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$: %TODO be explicit that HSet and HSet* are in the next universe??
+In particular, $\U$ is interpreted as the graph ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \rightarrow A_R \rightarrow \U$ of graphs over $A_L$ and $A_R$.
+Also, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the graph $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
 
@@
 \end{equation*}
+
 This tells us how the informal type given to $X_2$ in the previous section could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.
@@
 
-We illustrated here the cubical case, that is $\nu=2$, but, in general, a $\layer[n][p]$ is a product of $\nu$ $\filler[n - 1][p]$.
+We illustrated here the cubical case, that is $\nu = 2$, but, in general, a $\layer[n][p]$ is a product of $\nu$ $\filler[n - 1][p]$.
 A $\filler[n][p]$ is an $n$-dimensional object obtained by stretching a $(n - p)$-dimensional frame in $p$ directions.
@@
 As a filler extends a frame, it also has layer components, but note that the layers of a filler are associated on the right that is opposite to the way they are associated in frames:
+
 \begin{align*}

### 2023-01-22 paper/paper.tex
paper: use painting instead of filler
paper: fix one compile error

@@
 \define@cmdkey[bonak]{layer}{d}{(#1)}
-\define@cmdkey[bonak]{filler}{D}{(#1)}
-\define@cmdkey[bonak]{filler}{E}{(#1)}
-\define@cmdkey[bonak]{filler}{d}{(#1)}
+\define@cmdkey[bonak]{painting}{D}{(#1)}
+\define@cmdkey[bonak]{painting}{E}{(#1)}
+\define@cmdkey[bonak]{painting}{d}{(#1)}
 \define@cmdkey[bonak]{fullframe}{D}{(#1)}
@@
 \define@cmdkey[bonak]{restrlayer}{l}{(#1)}
-\define@cmdkey[bonak]{restrfiller}{D}{(#1)}
-\define@cmdkey[bonak]{restrfiller}{E}{(#1)}
-\define@cmdkey[bonak]{restrfiller}{d}{(#1)}
-\define@cmdkey[bonak]{restrfiller}{c}{(#1)}
+\define@cmdkey[bonak]{restrpainting}{D}{(#1)}
+\define@cmdkey[bonak]{restrpainting}{E}{(#1)}
+\define@cmdkey[bonak]{restrpainting}{d}{(#1)}
+\define@cmdkey[bonak]{restrpainting}{c}{(#1)}
 
@@
 \define@cmdkey[bonak]{cohlayer}{l}{(#1)}
-\define@cmdkey[bonak]{cohfiller}{D}{(#1)}
-\define@cmdkey[bonak]{cohfiller}{E}{(#1)}
-\define@cmdkey[bonak]{cohfiller}{d}{(#1)}
-\define@cmdkey[bonak]{cohfiller}{c}{(#1)}
+\define@cmdkey[bonak]{cohpainting}{D}{(#1)}
+\define@cmdkey[bonak]{cohpainting}{E}{(#1)}
+\define@cmdkey[bonak]{cohpainting}{d}{(#1)}
+\define@cmdkey[bonak]{cohpainting}{c}{(#1)}
 \makeatother
@@
 
-% Frame, layer, and filler: the general macro
+% Frame, layer, and painting: the general macro
 \newcommandx{\prim}[6][2,3,4,5,6]{
@@
 
-% Restriction for frame, layer, and filler: the general macro
+% Restriction for frame, layer, and painting: the general macro
 \newcommandx{\restr}[8][2,3,4,5,6,7,8]{
@@
 
-% Coherence conditions for frame, layer, and filler: the general macro
+% Coherence conditions for frame, layer, and painting: the general macro
 
@@
 \newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
-\newcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
+\newcommandx{\filler}[2][1,2]{\prim{painting}[][#1][#2][][]}
 \newcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
 \newcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
-\newcommandx{\restrc}[4][1,2,3,4]{\restr{filler}[][#3][#4][#1][#2][][]}
+\newcommandx{\restrc}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
 \newcommandx{\cohf}{\coh{frame}[][][][][][][][]}
 \newcommandx{\cohl}{\coh{layer}[][][][][][][][]}
-\newcommandx{\cohc}{\coh{filler}[][][][][][][][]}
+\newcommandx{\cohc}{\coh{painting}[][][][][][][][]}
 \newcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
@@
 More generally, the standard $(n+1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them by a cylinder obtained as a third copy stretched in the new dimension.
-The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with \kstar.
+The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$.
 
@@
 \appendmask[bonak]{layer}[D]
-\appendmask[bonak]{filler}[D]
+\appendmask[bonak]{painting}[D]
 \appendmask[bonak]{restrframe}[D]
 \appendmask[bonak]{restrlayer}[D, d]
-\appendmask[bonak]{restrfiller}[D, d]
+\appendmask[bonak]{restrpainting}[D, d]
 \appendmask[bonak]{cohframe}[D]
 \appendmask[bonak]{cohlayer}[D, d]
-\appendmask[bonak]{cohfiller}[D, d]
+\appendmask[bonak]{cohpainting}[D, d]
 
@@
 
-% Frame, layer, and filler
+% Frame, layer, and painting
 % Drop the universe letter
@@
 \renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
-\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{filler}[][#2][#3][#4][#5]}
-
-% Restriction for frame, layer, and filler
+\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
+
+% Restriction for frame, layer, and painting
 % Drop the universe letter
@@
 \renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}
-
-% Coherence conditions for frame, layer, and filler
+\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
+
+% Coherence conditions for frame, layer, and painting
 % Keep only ε, ω; n, p; proposition on n and p
@@
 \renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][][][][][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][][][][][#9]}
 
@@
 
-% Restriction for frame, layer, and filler
+% Restriction for frame, layer, and painting
 % Drop just the universe letter for the coh table
@@
 \renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}
-
-% Frame, layer, and filler
+\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
+
+% Frame, layer, and painting
 % Drop all arguments for coh table; they're not present in coind table.
@@
 \renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][][][][#5]}
-\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{filler}[][][][][#5]}
+\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{painting}[][][][][#5]}
 
@@
 
-% Coherence conditions for frame, layer, and filler
+% Coherence conditions for frame, layer, and painting
 \renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
 \renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
 \renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
@@
 \renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
 
@@
 \renewcommandx{\cohl}{\coh{layer}[][][][][][][][]}
-\renewcommandx{\cohc}{\coh{filler}[][][][][][][][]}
+\renewcommandx{\cohc}{\coh{painting}[][][][][][][][]}
 
@@
 % Keep all arguments for all macros
-% Frame, layer, and filler
+% Frame, layer, and painting
 \renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[#1][#2][#3][#4][#5]}
 \renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[#1][#2][#3][#4][#5]}
-\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{filler}[#1][#2][#3][#4][#5]}
+\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{painting}[#1][#2][#3][#4][#5]}
 \renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
 
-% Restriction for frame, layer, and filler
+% Restriction for frame, layer, and painting
 \renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[#1][#2][#3][#4][#5][#6][#7]}
 \renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[#1][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{filler}[#1][#2][#3][#4][#5][#6][#7]}
-
-% Coherence conditions for frame, layer, and filler
+\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[#1][#2][#3][#4][#5][#6][#7]}
+
+% Coherence conditions for frame, layer, and painting
 \renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
 \renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{filler}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
 \renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[#1][#2][#3][#4][#5][#6][#7,#8][#9]}
@@
 \renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
-\renewcommandx{\filler}[2][1,2]{\prim{filler}[][#1][#2][][]}
+\renewcommandx{\filler}[2][1,2]{\prim{painting}[][#1][#2][][]}
 \renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
 \renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
-\renewcommandx{\restrc}[4][1,2,3,4]{\restr{filler}[][#3][#4][#1][#2][][]}
+\renewcommandx{\restrc}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
 \renewcommandx{\cohf}[1][1]{\coh{frame}[][][][][][#1][][]}
 \renewcommandx{\cohl}[1][1]{\coh{layer}[][][][][][#1][][]}
-\renewcommandx{\cohc}[1][1]{\coh{filler}[][][][][][#1][][]}
+\renewcommandx{\cohc}[1][1]{\coh{painting}[][][][][][#1][][]}
 

### 2023-01-22 paper/paper.tex
paper: fix an overflow on page 6, polish eqns a bit
paper: make Table IX a sidewaystable as well
reading up to page 7

@@
 While ordinary semi-simplicial sets are presheaves over the semi-simplex category \DeltaHat, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus.
-There are different ways to define \DeltaPlus, upto equivalence, and we use a definition that will later straightforwardly extend to semi-cubical sets.
+There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that will later straightforwardly extend to semi-cubical sets.
 
@@
 To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\filler$.
-A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$s, and a $\filler$ is a filled $\framep$.
+A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$s, and a $\filler$ corresponds to a filled $\framep$.
+Some $\framep$ are full and we call them $\fullframe$.
 
@@
 To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ of $X_0$ can be equivalently formulated as $\unittype \rightarrow \U$.
-Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type.
-For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$.
-The next steps of the construction are shown in Fig.
-\ref{fig:intuition}.
+Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
+For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown in Fig.
+\ref{fig:intuition} for $\nu = 2$ which also mentions how the type of $X_2$ is structured.
 
@@
   \end{equation*}
-  \caption{Intuition for formal construction}\label{fig:intuition}
+  \caption{Intuition for formal construction ($\nu = 2$)}\label{fig:intuition}
 \end{figure*}
 
-A $\fullframe[n]$ is a sequence of $\layer[n][p]$, and we write $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is a $\framep[n][n]$.
-Let us illustrate the construction of frames in dimension $3$, and $\nu = 2$:
+Let us now illustrate the construction of $\fullframe[3]$, necessary to build the type of $X_3$.
 
@@
 We illustrated here the cubical case, that is $\nu = 2$, but, in general, a $\layer[n][p]$ is a product of $\nu$ $\filler[n - 1][p]$.
-A $\filler[n][p]$ is an $n$-dimensional object obtained by stretching a $(n - p)$-dimensional frame in $p$ directions.
-For instance, in the picture, each of the two $\filler[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\filler[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a square, and each of the two $\filler[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a square.
-Note that a filler, which extends a frame with an element depending on it, shown as an element of $X_n$ below.
-As a filler extends a frame, it also has layer components, but note that the layers of a filler are associated on the right that is opposite to the way they are associated in frames:
+A $\filler[n][0]$ is a $n$-dimensional object corresponding to a filled $\fullframe[n]$.
+More generally, a $\filler[n][p]$ is an $n$-dimensional object which has the form of a $\filler[n-p][0]$, thus of $(n-p)$-dimensional form, but shifted and living in dimensions $p$ to $n$.
+Such $\filler[n][p]$ fills a space framed by a partial $\framep[n][p]$ so that, together, they form a filled $\fullframe[n]$.
+For instance, in the picture, each of the two $\filler[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\filler[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a partial square filling the partial frames made of respectively the left and right border of the blue square, and each of the two $\filler[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a partial square filling the full frames made respectively of the upper and lower borders of the blue and red squares.
+A $\filler[n][p]$ adds to a $\framep[n][p]$ the layers needed to form a $\fullframe[n]$.
+They are added from dimension $n$ to dimension $p$ that is opposite to the order from $0$ to $p$ the $\framep[n][p]$ are built.
+A $\filler[n][p]$ complementing a given $\framep[n][p]$ fills the resulting $\fullframe[n]$.
+Thus, on the contrary of frames, it includes a filler, which lives in $X_n$ as shown below:
 
@@
 Let us be more precise about this requirement.
-First, $\fullframe[n]$ depends on all $X_i$ upto $n - 1$.
+First, $\fullframe[n]$ depends on all $X_i$ up to $n - 1$.
 So, we need to package up $X_i$, for $i < n$, into a type, which we call $\X[][<n][]$.
@@
 \begin{align*}
-  \framep[n][p](D) & \defeq & \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)) \ldots) . \\
-                   &        & \layer[n][p](D)                                                                    \\
-  \filler[n][p](D) & \defeq & \Sigma l_p : \layer[n][p](D) .                                                     \\
-                   &        & (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\; D.\tl) \ldots)
-\end{align*}
-
-An additional refinement arises from the fact that each addition of a layer has to be glued onto the border of the previous layer.
-So, each $\layer[n][p]$ has to depend on $\layer[n][p - 1]$.
-We also need a way to characterize the border of a filler of a layer, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$.
-For instance, each of the $\filler[2][1]$, shown as the red boxes, is laid on the borders of the blue boxes, and hence needs to depend on $\framep[3][1]$.
+   & \framep[n][p](D) \defeq                                                                                     \\
+   & \;\;\;\;\Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)) \ldots) .\,\layer[n][p](D) \\
+   & \filler[n][p](D) \defeq                                                                                     \\
+   & \;\;\;\;\Sigma l_p : \layer[n][p](D).\, (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\, D.\tl) \ldots)
+\end{align*}
+
+An extra refinement arises from the fact that each addition of a layer to a frame has to be glued onto the border of the partial frame built so far.
+So, each $\layer[n][p]$ has to depend on $\framep[n][p]$.
+We also need a way to characterize the border of the $\nu$ $\filler[n-1][p]$ that compose a $\layer[n][p]$, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$.
+For instance, on the picture, each of the $\filler[2][1]$, shown as the red boxes, is laid on the borders of the blue boxes, and hence needs to depend on $\framep[3][1]$.
 The left and right borders of the two blue boxes are extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$.
-We can then refine the previous equation by showing the dependencies on $d$.
-
-\begin{align*}
-  \framep[n][p](D)    & \defeq & \Sigma d : (\ldots (\Sigma \unitpoint: \unittype .\; \layer[n][0](D)(\unitpoint)) \ldots) . \\
-                      &        & \layer[n][p](D)(d)                                                                          \\
-  \filler[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d) .                                                            \\
-                      &        & (\ldots (\Sigma l_n : \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}) .                      \\
-                      &        & D.\tl(d, l_p, \ldots, l_n)) \ldots)                                                         \\
-  \text{where}\;      &        & (d, l_p, \ldots, l_q) \text{ abbreviates }                                                  \\
-                      &        & ((\ldots(d, l_p), \ldots), l_q)
-\end{align*}
-
-Let us recall that a layer is made of two fillers. This can now be made precise as illustrated below.
+We can then refine the previous equation by showing the dependencies on $d$, as shown in Figure~\ref{fig:refinement}.
+
+\begin{figure*}[!t]
+  \begin{align*}
+    \framep[n][p](D)    & \defeq & \Sigma d : (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)(\unitpoint)) \ldots).\, \layer[n][p](D)(d)                                \\
+    \filler[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d).\, (\ldots (\Sigma l_n : \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}).\, D.\tl(d, l_p, \ldots, l_n)) \ldots) \\
+                        &        & \text{where } (d, l_p, \ldots, l_q) \text{ abbreviates } ((\ldots(d, l_p), \ldots), l_q)
+  \end{align*}
+  \caption{Refinement of definition of $\framep$ and $\filler$\label{fig:refinement}}
+\end{figure*}
+
+Let us recall that a layer is made of $\nu$ paintings. When $\nu=2$, this amounts to:
 
@@
 In particular, $\restrf[n][p][\epsilon][p]$ is a ``full restriction''.
-We define $\restrf[n][p][\epsilon][p](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a layer and $c$ a filler.
+We define $\restrf[n][p][\epsilon][p](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$ and $c$ a $\filler$.
 The key case is $\restrc[n][p][\epsilon][p](d)(c)$, where $c$, a $\filler[n][p]$, has necessarily the form of $((c_L, c_R), \_)$: $\restrc[n][p][L][p]$ picks out $c_L$, a $\filler[n-1][p]$, $\restrc[n][p][R][p]$ picks out the $c_R$, also a $\filler[n-1][p]$, and $\_$, a $\filler[n][p+1]$, is discarded.
@@
 \end{align*}
-
 $\restrl[n][p][\epsilon](d)(c_L, c_R)$ produces a layer, in which the $\omega$-component has the type
@@
 \end{equation*}
-
 while we expect a term of type
@@
 
-Hence, we need a coherence condition to commute the terms.
+Hence, we need a coherence condition to commute the restrictions.
 Coherence conditions similar to this necessitate, what are shown as, $\cohf$, $\cohl$ and $\cohc$ in tables in the next section.
@@
 Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a coinductive limit of $n$-truncated $\nu$-sets.
-$n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.
+The $n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.
 The $n$th component is a family over a $\fullframe$.
-$\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\filler$.
-$\layer$ and $\filler$ are dependent over $\restrf$, and these restrictions are defined on \ref{tab:faces}.
+The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\filler$.
+The type $\layer$ and $\filler$ are dependent over $\restrf$, and these restrictions are defined on \ref{tab:faces}.
 These restrictions are defined using auxiliary definitions of $\restrl$ and $\restrc$.
@@
 Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$.
-This is a priori undecidable, and we have to prove the commutation propositionally before using the reflection rule.
+This commutation is not provable by computation so we have to prove it propositionally before using the reflection rule.
 Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\filler$.
@@
 
-Most components of the construction takes inequality constraints as parameters, and we have left implicit that they are satisfied in the table.
-Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, and assume that we can pick a definition for which inequality proofs are definitionally equal.
-
-Remark: For a given $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
+Most components of the construction takes inequality constraints as parameters, and we have left implicit that they are satisfied in the tables.
+Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, and assume that we can pick a definition for which proofs of $m \leq n$ are provably unique and thus definitionally equal by the reflection rule.
+
+%TODO add a word on the definition of eq on sig and pi, about eq_trans, etc.
+
+Remark: For a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
 
@@
 
+\begin{sidewaystable*}
   \renewcommand*{\lab}{fulltab:faces}
   \input{tab-faces.tex}
-
+  \vspace{5em}
   \renewcommand*{\lab}{fulltab:coh}
   \input{tab-coh.tex}
+\end{sidewaystable*}
 

### 2023-01-23 paper/paper.tex
paper: \filler -> \painting

@@
 \newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
-\newcommandx{\filler}[2][1,2]{\prim{painting}[][#1][#2][][]}
+\newcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
 \newcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
@@
 
-Our precise mechanization in Coq is available on Github, at \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}.
+Our precise mechanization in Coq is available at \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}.
 The construction was conceived in Summer 2019 and the mechanization began in late 2019.
@@
 
-  The definition of $\DeltaPlus$ is shown in Fig.
-\ref{fig:deltaplus}.
+  The definition of $\DeltaPlus$ is shown in Fig.~\ref{fig:deltaplus}.
 Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$.
@@
 \subsection{Intuition for our formal construction}
-To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\filler$.
-A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$s, and a $\filler$ corresponds to a filled $\framep$.
+To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\painting$.
+A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$s, and a $\painting$ corresponds to a filled $\framep$.
 Some $\framep$ are full and we call them $\fullframe$.
@@
 Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
-For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown in Fig.
-\ref{fig:intuition} for $\nu = 2$ which also mentions how the type of $X_2$ is structured.
+For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown in Fig.~\ref{fig:intuition} for $\nu = 2$ which also mentions how the type of $X_2$ is structured.
 
@@
       \begin{array}{c}
-          \underbrace{X_0(\unitpoint)}_{\filler[0][0]}
+          \underbrace{X_0(\unitpoint)}_{\painting[0][0]}
           \\ \times \\
-          \underbrace{X_0(\unitpoint)}_{\filler[0][0]}
+          \underbrace{X_0(\unitpoint)}_{\painting[0][0]}
         \end{array}\right)}_{\layer[1][0]}}_{\framep[1][1]} \rightarrow \U                                                                            \\
@@
                            \end{array}\hspace{-0.4em}
-            \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][L]}}_{\filler[1][1]}}_{\filler[1][0]}
+            \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][L]}}_{\painting[1][1]}}_{\painting[1][0]}
             \\ \times \\
@@
                            \end{array}\hspace{-0.4em}
-            \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][R]}}_{\filler[1][1]}}_{\filler[1][0]}
+            \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][R]}}_{\painting[1][1]}}_{\painting[1][0]}
           \end{array}
@@
                              \end{array}\hspace{-0.4em}
-              \right)\right)}_{\restrf[2][1][L]}}_{\filler[1][1]}
+              \right)\right)}_{\restrf[2][1][L]}}_{\painting[1][1]}
           \\ \times \\
@@
                              \end{array}\hspace{-0.4em}
-              \right)\right)}_{\restrf[2][1][R]}}_{\filler[1][1]}
+              \right)\right)}_{\restrf[2][1][R]}}_{\painting[1][1]}
         \end{array}
@@
 
-We illustrated here the cubical case, that is $\nu = 2$, but, in general, a $\layer[n][p]$ is a product of $\nu$ $\filler[n - 1][p]$.
-A $\filler[n][0]$ is a $n$-dimensional object corresponding to a filled $\fullframe[n]$.
-More generally, a $\filler[n][p]$ is an $n$-dimensional object which has the form of a $\filler[n-p][0]$, thus of $(n-p)$-dimensional form, but shifted and living in dimensions $p$ to $n$.
-Such $\filler[n][p]$ fills a space framed by a partial $\framep[n][p]$ so that, together, they form a filled $\fullframe[n]$.
-For instance, in the picture, each of the two $\filler[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\filler[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a partial square filling the partial frames made of respectively the left and right border of the blue square, and each of the two $\filler[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a partial square filling the full frames made respectively of the upper and lower borders of the blue and red squares.
-A $\filler[n][p]$ adds to a $\framep[n][p]$ the layers needed to form a $\fullframe[n]$.
+We illustrated here the cubical case, that is $\nu = 2$, but, in general, a $\layer[n][p]$ is a product of $\nu$ $\painting[n - 1][p]$.
+A $\painting[n][0]$ is a $n$-dimensional object corresponding to a filled $\fullframe[n]$.
+More generally, a $\painting[n][p]$ is an $n$-dimensional object which has the form of a $\painting[n-p][0]$, thus of $(n-p)$-dimensional form, but shifted and living in dimensions $p$ to $n$.
+Such $\painting[n][p]$ fills a space framed by a partial $\framep[n][p]$ so that, together, they form a filled $\fullframe[n]$.
+For instance, in the picture, each of the two $\painting[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\painting[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a partial square filling the partial frames made of respectively the left and right border of the blue square, and each of the two $\painting[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a partial square filling the full frames made respectively of the upper and lower borders of the blue and red squares.
+A $\painting[n][p]$ adds to a $\framep[n][p]$ the layers needed to form a $\fullframe[n]$.
 They are added from dimension $n$ to dimension $p$ that is opposite to the order from $0$ to $p$ the $\framep[n][p]$ are built.
-A $\filler[n][p]$ complementing a given $\framep[n][p]$ fills the resulting $\fullframe[n]$.
+A $\painting[n][p]$ complementing a given $\framep[n][p]$ fills the resulting $\fullframe[n]$.
 Thus, on the contrary of frames, it includes a filler, which lives in $X_n$ as shown below:
@@
   \framep[n][p]   & \defeq \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0]) \ldots) .\; \layer[n][p] \\
-  \filler[n][p] & \defeq \Sigma l_p : \layer[n][p] . (\ldots (\Sigma l_n : \layer[n][n - 1] .\; X_n) \ldots)
+  \painting[n][p] & \defeq \Sigma l_p : \layer[n][p] . (\ldots (\Sigma l_n : \layer[n][n - 1] .\; X_n) \ldots)
 \end{align*}
@@
 Then, for $D: \X[][<n][]$, representing an initial prefix of $X_0, X_1, \ldots X_{n - 1}$, the indexed set $X_n$ has type $\fullframe[n](D) \rightarrow \U$.
-Thus, $\framep[n][p]$, $\layer[n][p]$ and $\filler[n][p]$ also depend on $D$.
+Thus, $\framep[n][p]$, $\layer[n][p]$ and $\painting[n][p]$ also depend on $D$.
 We can then refine the previous equation by showing the dependencies on $D$.
@@
    & \;\;\;\;\Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)) \ldots) .\,\layer[n][p](D) \\
-   & \filler[n][p](D) \defeq                                                                                     \\
+   & \painting[n][p](D) \defeq                                                                                   \\
    & \;\;\;\;\Sigma l_p : \layer[n][p](D).\, (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\, D.\tl) \ldots)
@@
 So, each $\layer[n][p]$ has to depend on $\framep[n][p]$.
-We also need a way to characterize the border of the $\nu$ $\filler[n-1][p]$ that compose a $\layer[n][p]$, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$.
-For instance, on the picture, each of the $\filler[2][1]$, shown as the red boxes, is laid on the borders of the blue boxes, and hence needs to depend on $\framep[3][1]$.
+We also need a way to characterize the border of the $\nu$ $\painting[n-1][p]$ that compose a $\layer[n][p]$, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$.
+For instance, on the picture, each of the $\painting[2][1]$, shown as the red boxes, is laid on the borders of the blue boxes, and hence needs to depend on $\framep[3][1]$.
 The left and right borders of the two blue boxes are extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$.
-We can then refine the previous equation by showing the dependencies on $d$, as shown in Figure~\ref{fig:refinement}.
+We can then refine the previous equation by showing the dependencies on $d$, as shown in Fig.~\ref{fig:refinement}.
 
@@
     \framep[n][p](D)      & \defeq & \Sigma d : (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)(\unitpoint)) \ldots).\, \layer[n][p](D)(d)                                \\
-    \filler[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d).\, (\ldots (\Sigma l_n : \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}).\, D.\tl(d, l_p, \ldots, l_n)) \ldots) \\
+    \painting[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d).\, (\ldots (\Sigma l_n : \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}).\, D.\tl(d, l_p, \ldots, l_n)) \ldots) \\
                           &        & \text{where } (d, l_p, \ldots, l_q) \text{ abbreviates } ((\ldots(d, l_p), \ldots), l_q)
   \end{align*}
-  \caption{Refinement of definition of $\framep$ and $\filler$\label{fig:refinement}}
+  \caption{Refinement of definition of $\framep$ and $\painting$\label{fig:refinement}}
 \end{figure*}
 
-Let us recall that a layer is made of $\nu$ paintings. When $\nu=2$, this amounts to:
-
-\begin{align*}
-  \layer[n][p](D)(d) & \defeq & \filler[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) & \times \\
-                     &        & \filler[n-1][p](D.\hd)(\restrf[n][p][R][p](d)) &
+Let us recall that a layer is made of $\nu$ paintings. When $\nu = 2$, this amounts to:
+
+\begin{align*}
+  \layer[n][p](D)(d) & \defeq & \painting[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) & \times \\
+                     &        & \painting[n-1][p](D.\hd)(\restrf[n][p][R][p](d)) &
 \end{align*}
@@
 In particular, $\restrf[n][p][\epsilon][p]$ is a ``full restriction''.
-We define $\restrf[n][p][\epsilon][p](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$ and $c$ a $\filler$.
-The key case is $\restrc[n][p][\epsilon][p](d)(c)$, where $c$, a $\filler[n][p]$, has necessarily the form of $((c_L, c_R), \_)$: $\restrc[n][p][L][p]$ picks out $c_L$, a $\filler[n-1][p]$, $\restrc[n][p][R][p]$ picks out the $c_R$, also a $\filler[n-1][p]$, and $\_$, a $\filler[n][p+1]$, is discarded.
+We define $\restrf[n][p][\epsilon][p](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$ and $c$ a $\painting$.
+The key case is $\restrc[n][p][\epsilon][p](d)(c)$, where $c$, a $\painting[n][p]$, has necessarily the form of $((c_L, c_R), \_)$: $\restrc[n][p][L][p]$ picks out $c_L$, a $\painting[n-1][p]$, $\restrc[n][p][R][p]$ picks out the $c_R$, also a $\painting[n-1][p]$, and $\_$, a $\painting[n][p+1]$, is discarded.
 There is one more difficulty, which we illustrate by writing down expected and actual types.
@@
 \begin{align*}
-  c_\omega & : \filler[n-1][p](D.\hd)(\restrf[n-1][p][\omega][q](d))
+  c_\omega & : \painting[n-1][p](D.\hd)(\restrf[n-1][p][\omega][q](d))
 \end{align*}
@@
 \begin{equation*}
-  \filler[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\epsilon][q](\restrf[n][p][\omega][p](d)))
+  \painting[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\epsilon][q](\restrf[n][p][\omega][p](d)))
 \end{equation*}
@@
 \begin{equation*}
-  \filler[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\omega][p](\restrf[n][p][\epsilon][q+1](d)))
+  \painting[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\omega][p](\restrf[n][p][\epsilon][q+1](d)))
 \end{equation*}
@@
 Coherence conditions similar to this necessitate, what are shown as, $\cohf$, $\cohl$ and $\cohc$ in tables in the next section.
-These are by induction on the structure of $\framep$, $\layer$ and $\filler$.
+These are by induction on the structure of $\framep$, $\layer$ and $\painting$.
 Note that, for the construction in \ref{sec:itt}, we further need a $2$-dimensional coherence condition, $\coht$, for $\cohl$.
@@
 \renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
-\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
+\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
 
@@
 The $n$th component is a family over a $\fullframe$.
-The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\filler$.
-The type $\layer$ and $\filler$ are dependent over $\restrf$, and these restrictions are defined on \ref{tab:faces}.
+The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\painting$.
+The type $\layer$ and $\painting$ are dependent over $\restrf$, and these restrictions are defined on \ref{tab:faces}.
 These restrictions are defined using auxiliary definitions of $\restrl$ and $\restrc$.
@@
 This commutation is not provable by computation so we have to prove it propositionally before using the reflection rule.
-Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\filler$.
+Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\painting$.
 This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$.
-Even though it looks independent of the other tables, it has to proved mutually with the definitions of $\framep$, $\layer$, $\filler$, and their corresponding restrictions.
+Even though it looks independent of the other tables, it has to proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
 
@@
 \renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][][][][#5]}
-\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{painting}[][][][][#5]}
+\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][][][][#5]}
 
@@
 For a fixed $n$, $\framep$, $\restrf$, and $\cohf$ have to be mutually defined by induction on $p$.
-Each of them rely on $\filler$, $\restrf$, and $\cohc$ at lower $n$, so they are well-founded.
-Finally, each of $\filler$, $\restrf$, and $\cohf$ are by induction from $p$ to $n$.
+Each of them rely on $\painting$, $\restrf$, and $\cohc$ at lower $n$, so they are well-founded.
+Finally, each of $\painting$, $\restrf$, and $\cohf$ are by induction from $p$ to $n$.
 
@@
 \renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[#1][#2][#3][#4][#5]}
-\renewcommandx{\filler}[5][1,2,3,4,5]{\prim{painting}[#1][#2][#3][#4][#5]}
+\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[#1][#2][#3][#4][#5]}
 \renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
@@
 \renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
-\renewcommandx{\filler}[2][1,2]{\prim{painting}[][#1][#2][][]}
+\renewcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
 \renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
@@
 More concretely, we build the ten definitions shown in the tables by induction, and this is part of the definition of a larger record.
-The other fields of the record aref $\framep$, $\layer$, $\filler$ at levels $n - 1$ and $n - 2$, $\restrf$, $\restrl$, and $\restrc$ at level $n - 1$, and equations to recall the definitions of these objects at lower levels.
+The other fields of the record aref $\framep$, $\layer$, $\painting$ at levels $n - 1$ and $n - 2$, $\restrf$, $\restrl$, and $\restrc$ at level $n - 1$, and equations to recall the definitions of these objects at lower levels.
 
@@
 Compared to \texttt{leY}, \texttt{leI} has no proof-irrelevance properties.
-This definition is specially crafted for $\filler$, where we have to reason inductively from $p \leq n$ to $n$.
+This definition is specially crafted for $\painting$, where we have to reason inductively from $p \leq n$ to $n$.
 In our usage, we have lemmas \texttt{leY\_of\_leI} and \texttt{leI\_of\_leY} in order to equip \texttt{leY} with the induction scheme of \texttt{leI}.

### 2023-01-23 paper/paper.tex
some clarification

@@
 \subsection{Working with sets in type theory}
-Martin-Löf's Type theory~\cite{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a\emph{set}.
+Martin-Löf's Type theory~\cite{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
 It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Coq~\cite{coq22} or Lean~\cite{lean15}.
+In type theory, propositions are types and proofs are programs.
+A particularity of type theory is also that types and programs, henceforth propositions and proofs also, are considered modulo an equational theory called definitional equality.
+
 Type theory is a flexible formalism supporting different models.
@@
 In type theory, types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number.
-Main types in type theory are the types of dependent pairs, written $\Sigma a : A.\,B(a)$, and the types of dependent functions, written $\Pi a:A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$.
+Main types in type theory are the types of dependent pairs, written $\Sigma a : A.\,B(a)$, the types of dependent functions, written $\Pi a:A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$, and the type of propositional equality, written $t = u$.
 We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, called $\textsf{bool}$, and the type of natural numbers.
@@
 Most components of the construction takes inequality constraints as parameters, and we have left implicit that they are satisfied in the tables.
-Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, and assume that we can pick a definition for which proofs of $m \leq n$ are provably unique and thus definitionally equal by the reflection rule.
-
-%TODO add a word on the definition of eq on sig and pi, about eq_trans, etc.
-
-Remark: For a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
+Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, only assuming that we can pick a definition for which proofs of $m \leq n$ are provably unique and thus definitionally equal by the reflection rule.
+
+The construction takes benefit of various provable equalities over proofs of equality being definitional by the reflection rule.
+This includes in particular the groupoid properties of equality.
+Notably, unicity of identity proofs holds in extensional type theory, so that any type is automatically an $\U$.
+Also, we left implicit in table~\ref{tab:coh} the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
+(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type.
+In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a:A.f(a) = g(a)$ for $f$ and $g$ in $\Pi a:A.\, B$, where it should be recalled that the right-to-left map, that is function extensionality, holds by default in extensional type theory.
+
+% TODO explain the role of the subscript HSet on =
+
+As a side remark, note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
 
@@
 
-Since we have formalized the proof in the Coq proof assistant, which works in intensional type theory, we now present the tables in \emph{intensional} type theory, leaving implicit some details, which we will explain here, and other details, which we will explain in \ref{sec:mech}.
+Since we have formalized the proof in the Coq proof assistant, which implements an intensional type theory, we now present the tables in \emph{intensional} type theory~\cite{martin-lof...,Coq}, leaving implicit some details, which we will explain here, and other details, which we will explain in \ref{sec:mech}.
 
@@
 The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit as shown in table \ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
-The proof of $\cohf$ is described on \ref{fulltab:coh}, and it requires explication of several equalities which were implicit in extensional type theory.
+The proof of $\cohf$ is described on \ref{fulltab:coh}, and it requires explicitation of several equalities which were definitional in extensional type theory.
 The commutation of $\restrl$ lives in a type referring to $\cohf$, so we need a transport along the commutation of $\restrf$ in the statement of $\cohl$.

### 2023-01-23 paper/paper.tex
paper: fix some underfull hboxes, rephrase "see eg."

@@
 
-  This paper describes an uniform indexed characterization of both augmented semi-simplicial and semi-cubical sets arising respectively as unary and binary iterated parametricity-based constructions.
+  This paper describes a uniform indexed characterization of both augmented semi-simplicial and semi-cubical sets arising respectively as unary and binary iterated parametricity-based constructions.
 
@@
 In the context of functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational behavior of programs of this type.
-Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity, when using more generally graphs than relations, has a cubical flavor (see e.g.~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}).
-We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or graphs, in which case, we obtain a form of realizability (see e.g.~\cite{bernardy12,lasson12,moulin16}).
-It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication with Thorsten Altenkirch and Hugo Moeneclaey}.
+Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity, when using more generally graphs than relations, has a cubical flavor~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
+We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or graphs, in which case, we obtain a form of realizability~\cite{bernardy12,lasson12,moulin16}.
+It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch}.
 % TODO anonymize??
@@
 We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets obtained by applying simple rules characterizing iterated parametricity.
-In contrast to the standard presheaf presentation of augmented semi-simplicial and semi-cubical sets (see e.g.~\cite{fri08,grandis03,buchholtz17}), our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
+In contrast to the standard presheaf presentation of augmented semi-simplicial and semi-cubical sets~\cite{fri08,grandis03,buchholtz17}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
 That is, instead of having the set of augmented semi-simplices or semi-cubes in dimension $n+1$ \emph{fibered} over the set of augmented semi-simplices or semi-cubes in dimension $n$, we consider families of augmented semi-simplices and semi-cubes indexed over their faces.
@@
 
-Since we have formalized the proof in the Coq proof assistant, which implements an intensional type theory, we now present the tables in \emph{intensional} type theory~\cite{martin-lof...,Coq}, leaving implicit some details, which we will explain here, and other details, which we will explain in \ref{sec:mech}.
+Since we have formalized the proof in the Coq proof assistant, which implements an intensional type theory, we now present the tables in \emph{intensional} type theory~\cite{martinlof75,martinlof84,coq22}, leaving implicit some details, which we will explain here, and other details, which we will explain in \ref{sec:mech}.
 

### 2023-01-23 paper/paper.tex
paper: fix line breaks before align*
paper: clip whitespace around equation*

@@
 Our precise mechanization in Coq is available at \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}.
-The construction was conceived in Summer 2019 and the mechanization began in late 2019.
+The construction was conceived in Summer 2019, and the mechanization began in late 2019.
 A sketch of the construction was presented at the 2020 HoTT-UF workshop and the completion of the mechanization was reported at the TYPES 2022 conference.
@@
 What we have formalized is \emph{augmented semi-simplicial} sets~\cite{fri08}, and \emph{semi-cubical} sets~\cite{grandis03,buchholtz17}.
-We will proceed to explain the mathematical objects we have formalized.
+We will proceed to explain the mathematical objects we have formalized, the connection with parametricity, and our generalization to $\nu$-sets.
 % TODO: well-known: can we find a reference?
@@
   We define the category of augmented semi-simplicial sets as the functor category:
-
   \begin{equation*}
@@
   The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as what is called the Yoneda embedding of $n \in \Obj(\DeltaPlus)$:
-
   \begin{align*}
@@
 This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$:
-
   \begin{equation*}
@@
 We use the color black to denote the unique morphisms in $\Hom(0, 1)$ and $\Hom(0, 2)$.
-
   \begin{equation*}
@@
   $\DeltaPlus^3$ is drawn as three points, given by $\Hom(1, 3)$, three lines connecting them, given by $\Hom(2, 3)$, and a triangular filler given by $\Hom(3, 3)$.
-
   \begin{equation*}
@@
   We define the category of semi-cubical sets as the functor category:
-
   \begin{equation*}
@@
   The standard semi-cube $\Cube^n$ is defined as the Yoneda embedding of $n \in \Obj(\Cube)$:
-
   \begin{align*}
@@
   $\Cube^0$ is $\Hom(0, 0)$, or the singleton set of the empty sequence:
-
   \begin{equation*}
@@
   $\Cube^1$ consists of two points, given by $\Hom(0, 1)$ and a line, given by $\Hom(1, 1)$:
-
   \begin{equation*}
@@
   $\Cube^2$ consists of four points, given by $\Hom(0, 2)$, four lines connecting the four points, given by $\Hom(1, 2)$, and a filler, given by $\Hom(2, 2)$:
-
   \begin{equation*}
@@
 To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\nu$-semi-shape category.
-The morphisms of the $\nu$-semi-shape category are sequences of elements of a set $\nu$ of arbitrary cardinal, extended with $\kstar$, so that the following holds:
+The morphisms of the $\nu$-semi-shape category are sequences of elements of a set $\nu$ of arbitrary cardinal, extended with $\kstar$, so that the following holds.
 
@@
 \section{Our setting}
-In this section, we explain how we recover the notion of sets in type theory, and briefly explain the difference between the fibered and indexed representations.
+We now explain how we recover the notion of sets in type theory, explain the difference between the fibered and indexed representations, and supply an example of indexed semi-cubical sets.
 
@@
 Technically, this is expressed as a structure equipping a domain $\Dom$ with the property $\UIP$:
-
 \begin{align*}
@@
 Note that an equivalent definition of UIP is given by \textsf{UIP\_refl}:
-
 \begin{align*}
@@
 This correspondence also holds on \U, for $T: \U$:
-
 \begin{equation*}
@@
 \subsection{Example: indexed semi-cubical sets}
-
 Let us now come back to semi-cubical sets. A semi-cubical set can be represented as a sequence of fibrations, together with appropriate coherence conditions.
-
 \begin{equation*}
@@
 In summary,
-
 \begin{align*}
@@
 Also, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the graph $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
-
 \begin{align*}
@@
 of:
-
 \begin{align*}
@@
 which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of binary parametricity applied to an initial $X: \U$:
-
 \begin{equation*}
@@
 To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\painting$.
-A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$s, and a $\painting$ corresponds to a filled $\framep$.
+A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$, and a $\painting$ corresponds to a filled $\framep$.
 Some $\framep$ are full and we call them $\fullframe$.
@@
 A $\painting[n][p]$ complementing a given $\framep[n][p]$ fills the resulting $\fullframe[n]$.
-Thus, on the contrary of frames, it includes a filler, which lives in $X_n$ as shown below:
-
+Thus, on the contrary of frames, it includes a filler, which lives in $X_n$ as shown below.
 \begin{align*}
@@
 In particular, $X_n$ is just $D.\tl$.
-
 \begin{align*}
@@
 \end{align*}
+
+\begin{figure*}[!t]
+  \begin{align*}
+    \framep[n][p](D)      & \defeq & \Sigma d : (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)(\unitpoint)) \ldots).\, \layer[n][p](D)(d)                                \\
+    \painting[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d).\, (\ldots (\Sigma l_n : \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}).\, D.\tl(d, l_p, \ldots, l_n)) \ldots) \\
+                          &        & \text{where } (d, l_p, \ldots, l_q) \text{ abbreviates } ((\ldots(d, l_p), \ldots), l_q)
+  \end{align*}
+  \caption{Refinement of definition of $\framep$ and $\painting$\label{fig:refinement}}
+\end{figure*}
 
@@
 
-\begin{figure*}[!t]
-  \begin{align*}
-    \framep[n][p](D)      & \defeq & \Sigma d : (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)(\unitpoint)) \ldots).\, \layer[n][p](D)(d)                                \\
-    \painting[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d).\, (\ldots (\Sigma l_n : \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}).\, D.\tl(d, l_p, \ldots, l_n)) \ldots) \\
-                          &        & \text{where } (d, l_p, \ldots, l_q) \text{ abbreviates } ((\ldots(d, l_p), \ldots), l_q)
-  \end{align*}
-  \caption{Refinement of definition of $\framep$ and $\painting$\label{fig:refinement}}
-\end{figure*}
-
 Let us recall that a layer is made of $\nu$ paintings. When $\nu = 2$, this amounts to:
-
 \begin{align*}
@@
 Given $c_\omega$ of type
-
 \begin{align*}
@@
 $\restrl[n][p][\epsilon](d)(c_L, c_R)$ produces a layer, in which the $\omega$-component has the type
-
 \begin{equation*}
@@
 while we expect a term of type
-
 \begin{equation*}
@@
 in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
-
 \begin{equation*}
@@
 The exact formulation of this coherence condition is as follows.
-
 \renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
@@
 \renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-
 \begin{align*}
@@
 \end{align*}
+where $\mathsf{ap}$ applies a function on two sides of an equality, and $\bullet$ is transitivity of equality.
+This property of equality proofs holds in \U, and since our formalization is done in \U, the term is trivially discharged.
 
@@
 \renewcommandx{\cohc}{\coh{painting}[][][][][][][][]}
-
-where $\mathsf{ap}$ applies a function on two sides of an equality, and $\bullet$ is transitivity of equality.
-This property of equality proofs holds in \U, and since our formalization is done in \U, the term is trivially discharged.
 

### 2023-01-23 paper/paper.tex
paper: fix minor whitespace issues in Sigma types

@@
       \textsf{eq\_refl}        & : \Pi x.\, x = x                                            \\
-      \textsf{UIP\_refl\_unit} & : \Pi u: \unittype.\, \Pi x : u = u.\, x = \textsf{eq\_refl} \\
-      \textsf{UIP\_refl\_bool} & : \Pi b: \booltype.\, \Pi x : b = b.\, x = \textsf{eq\_refl}
+      \textsf{UIP\_refl\_unit} & : \Pi u: \unittype.\, \Pi x: u = u.\, x = \textsf{eq\_refl} \\
+      \textsf{UIP\_refl\_bool} & : \Pi b: \booltype.\, \Pi x: b = b.\, x = \textsf{eq\_refl}
     \end{align*}
@@
 
-The latter correspondence can be expressed in Homotopy Type Theory, for $T: \Type$, as an equivalence between $\Sigma S: \Type\;.\;S \rightarrow T$ and $T \rightarrow \Type$, which can be proved using univalence.
+The latter correspondence can be expressed in Homotopy Type Theory, for $T: \Type$, as an equivalence between $\Sigma S: \Type.\, S \rightarrow T$ and $T \rightarrow \Type$, which can be proved using univalence.
 This correspondence also holds on \U, for $T: \U$:
 \begin{equation*}
-  \Sigma S: \U\;.\;S\rightarrow T ~\simeq~ T \rightarrow \U
+  \Sigma S: \U.\, S\rightarrow T ~\simeq~ T \rightarrow \U
 \end{equation*}
@@
   \begin{tikzcd}
-    X_0 : \U & X_1 : \U \arrow[l, "\delta^L" description, shift left=2] \arrow[l, "\delta^R" description, shift right=2] & X_2 : \U \arrow[l, "\delta^{L\kstar}" description, shift left=6] \arrow[l, "\delta^{R\kstar}" description, shift left=2] \arrow[l, "\delta^{\kstar R}" description, shift right=2] \arrow[l, "\delta^{\kstar L}" description, shift right=6] & \ldots
+    X_0: \U & X_1: \U \arrow[l, "\delta^L" description, shift left=2] \arrow[l, "\delta^R" description, shift right=2] & X_2: \U \arrow[l, "\delta^{L\kstar}" description, shift left=6] \arrow[l, "\delta^{R\kstar}" description, shift left=2] \arrow[l, "\delta^{\kstar R}" description, shift right=2] \arrow[l, "\delta^{\kstar L}" description, shift right=6] & \ldots
   \end{tikzcd}
@@
 
-We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying to the description above the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a : A, (B a \rightarrow C)$ and $(\Sigma a : A, B a) \rightarrow C$.
+We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying to the description above the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A, (B a \rightarrow C)$ and $(\Sigma a: A, B a) \rightarrow C$.
 Let us now illustrate how we build $\fullframe[n]$.
@@
                            \end{array}\hspace{-0.4em}
-            \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][L]}}_{\painting[1][1]}}_{\painting[1][0]}
+            \right).\, \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][L]}}_{\painting[1][1]}}_{\painting[1][0]}
             \\ \times \\
@@
                            \end{array}\hspace{-0.4em}
-            \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][R]}}_{\painting[1][1]}}_{\painting[1][0]}
+            \right).\, \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][R]}}_{\painting[1][1]}}_{\painting[1][0]}
           \end{array}
@@
 \begin{align*}
-  \framep[n][p]   & \defeq \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0]) \ldots) .\; \layer[n][p] \\
-  \painting[n][p] & \defeq \Sigma l_p : \layer[n][p] . (\ldots (\Sigma l_n : \layer[n][n - 1] .\; X_n) \ldots)
+  \framep[n][p]   & \defeq \Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype .\, \layer[n][0]) \ldots) .\, \layer[n][p] \\
+  \painting[n][p] & \defeq \Sigma l_p: \layer[n][p] . (\ldots (\Sigma l_n: \layer[n][n - 1] .\, X_n) \ldots)
 \end{align*}
@@
    & \framep[n][p](D) \defeq                                                                                  \\
-   & \;\;\;\;\Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)) \ldots) .\,\layer[n][p](D) \\
+   & \;\;\;\;\Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)) \ldots) .\,\layer[n][p](D) \\
    & \painting[n][p](D) \defeq                                                                                \\
-   & \;\;\;\;\Sigma l_p : \layer[n][p](D).\, (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\, D.\tl) \ldots)
+   & \;\;\;\;\Sigma l_p: \layer[n][p](D).\, (\ldots (\Sigma l_n: \layer[n][n - 1](D) .\, D.\tl) \ldots)
 \end{align*}
@@
   \begin{align*}
-    \framep[n][p](D)      & \defeq & \Sigma d : (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)(\unitpoint)) \ldots).\, \layer[n][p](D)(d)                                \\
-    \painting[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d).\, (\ldots (\Sigma l_n : \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}).\, D.\tl(d, l_p, \ldots, l_n)) \ldots) \\
+    \framep[n][p](D)      & \defeq & \Sigma d: (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)(\unitpoint)) \ldots).\, \layer[n][p](D)(d)                                \\
+    \painting[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d).\, (\ldots (\Sigma l_n: \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}).\, D.\tl(d, l_p, \ldots, l_n)) \ldots) \\
                           &        & \text{where } (d, l_p, \ldots, l_q) \text{ abbreviates } ((\ldots(d, l_p), \ldots), l_q)
@@
 \begin{equation*}
-  \seqr{}{\Gamma \vdash p : t = u}{\Gamma \vdash t \equiv u}
+  \seqr{}{\Gamma \vdash p: t = u}{\Gamma \vdash t \equiv u}
 \end{equation*}
@@
 (u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type.
-In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a:A.f(a) = g(a)$ for $f$ and $g$ in $\Pi a:A.\, B$, where it should be recalled that the right-to-left map, that is function extensionality, holds by default in extensional type theory.
+In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is function extensionality, holds by default in extensional type theory.
 

### 2023-01-23 paper/paper.tex
paper: consistent typing of Sigma types and Pi types

@@
 
-The latter correspondence can be expressed in Homotopy Type Theory, for $T: \Type$, as an equivalence between $\Sigma S: \Type.\, S \rightarrow T$ and $T \rightarrow \Type$, which can be proved using univalence.
+The latter correspondence can be expressed in Homotopy Type Theory, for $T: \Type$, as an equivalence between $\Sigma S: \Type.\; S \rightarrow T$ and $T \rightarrow \Type$, which can be proved using univalence.
 This correspondence also holds on \U, for $T: \U$:
@@
 
-We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying to the description above the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A, (B a \rightarrow C)$ and $(\Sigma a: A, B a) \rightarrow C$.
+We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying to the description above the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$.
 Let us now illustrate how we build $\fullframe[n]$.

### 2023-01-23 paper/paper.tex
paper: reorg to trim whitespace

@@
 \section{Semi-simplicial and semi-cubical sets}
-It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices.
-What we have formalized is \emph{augmented semi-simplicial} sets~\cite{fri08}, and \emph{semi-cubical} sets~\cite{grandis03,buchholtz17}.
-We will proceed to explain the mathematical objects we have formalized, the connection with parametricity, and our generalization to $\nu$-sets.
-% TODO: well-known: can we find a reference?
-
 \subsection{Augmented semi-simplicial sets}
@@
 
-More generally, the standard augmented $(n+1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as the base and glueing on top of it another copy of it lifted by one dimension.
+More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as the base and glueing on top of it another copy of it lifted by one dimension.
 In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.
@@
 
-More generally, the standard $(n+1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them by a cylinder obtained as a third copy stretched in the new dimension.
+More generally, the standard $(n + 1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them by a cylinder obtained as a third copy stretched in the new dimension.
 The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$.
@@
 A $\nu$-set is thus a functor $\phi$ from the $\nu$-semi-shape category to $\Set$ and we call $n$-$\nu$-semi-shape an element of $\phi(n)$.
-As in the augmented semi-simplicial and semi-cubical cases, the standard $(n+1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
+As in the augmented semi-simplicial and semi-cubical cases, the standard $(n + 1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
 We clarify in the next sections how this process of construction is similar to the parametricity translation developed for functional programming~\cite{reynolds72} and more generally for type theory~\cite{bernardy10, bernardy11, atkey14, bernardy15}.
@@
 Type theory is a flexible formalism supporting different models.
-One of this model interprets types as topological spaces, where equality is interpreted as path and substitutivity of equality as transport.
+Some models are based on topological spaces, where equality is interpreted as path, and substitutivity of equality as transport.
 This model supports the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\cite{hottbook}.
@@
 \end{align*}
-
-In particular, for $X: \U$, applying the parametricity translation is about canonically associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X)(X)$ i.e.
-of $X \rightarrow X \rightarrow \U$.
-In turn, applying the parametricity translation to $X_\kstar: X \rightarrow X \rightarrow \U$ is about canonically associating to $X_\kstar$ an inhabitant $X_{\kstar\kstar}$ of $(X \rightarrow X \rightarrow \U)_\kstar(X_\kstar)(X_\kstar)$ i.e.
-of:
-\begin{align*}
-  \Pi x_{LL}: X.\, \Pi x_{LR}: X.\, X_\kstar(x_{LL})(x_{LR})             \\
-  \rightarrow \Pi x_{RL}: X.\, \Pi x_{RR}: X.\, X_\kstar(x_{RL})(x_{RR}) \\ \rightarrow X_\kstar(x_{LL}, x_{RL}) \rightarrow X_\kstar(x_{LR})(x_{RR})  \rightarrow \U
-\end{align*}
-which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of binary parametricity applied to an initial $X: \U$:
-\begin{equation*}
-  \begin{array}{llllr}
-    X_0 & \defeq & X                & : & \U                                               \\
-    X_1 & \defeq & X_\kstar         & : & {\U}_\kstar(X)(X)                                \\
-    X_2 & \defeq & X_{\kstar\kstar} & : & ({\U}_\kstar(X)(X))_{\kstar}(X_\kstar)(X_\kstar) \\
-    \ldots
-  \end{array}
-\end{equation*}
-
-This tells us how the informal type given to $X_2$ in the previous section could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.
-
-Notice, however, that the recipe obtained so far, $X_{n + 1}: ({S_n})_\kstar(X_n)(X_n)$ for $X_n: S_n$, applies parametricity on the \emph{syntax} of the type of $X_n$.
-It does not directly yield a characterization of $S_n$ as a function from $n$.
-Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and the uniform treatment of augmented semi-simplial and semi-cubical sets by means of the generalization to $\nu$-sets.
-
-\subsection{Intuition for our formal construction}
-To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\painting$.
-A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$, and a $\painting$ corresponds to a filled $\framep$.
-Some $\framep$ are full and we call them $\fullframe$.
-
-We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying to the description above the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$.
-Let us now illustrate how we build $\fullframe[n]$.
-To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ of $X_0$ can be equivalently formulated as $\unittype \rightarrow \U$.
-Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
-For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown in Fig.~\ref{fig:intuition} for $\nu = 2$ which also mentions how the type of $X_2$ is structured.
 
@@
 
+In particular, for $X: \U$, applying the parametricity translation is about canonically associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X)(X)$ i.e.
+of $X \rightarrow X \rightarrow \U$.
+In turn, applying the parametricity translation to $X_\kstar: X \rightarrow X \rightarrow \U$ is about canonically associating to $X_\kstar$ an inhabitant $X_{\kstar\kstar}$ of $(X \rightarrow X \rightarrow \U)_\kstar(X_\kstar)(X_\kstar)$ i.e.
+of:
+\begin{align*}
+  \Pi x_{LL}: X.\, \Pi x_{LR}: X.\, X_\kstar(x_{LL})(x_{LR})             \\
+  \rightarrow \Pi x_{RL}: X.\, \Pi x_{RR}: X.\, X_\kstar(x_{RL})(x_{RR}) \\ \rightarrow X_\kstar(x_{LL}, x_{RL}) \rightarrow X_\kstar(x_{LR})(x_{RR})  \rightarrow \U
+\end{align*}
+which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of binary parametricity applied to an initial $X: \U$:
+\begin{equation*}
+  \begin{array}{llllr}
+    X_0 & \defeq & X                & : & \U                                               \\
+    X_1 & \defeq & X_\kstar         & : & {\U}_\kstar(X)(X)                                \\
+    X_2 & \defeq & X_{\kstar\kstar} & : & ({\U}_\kstar(X)(X))_{\kstar}(X_\kstar)(X_\kstar) \\
+    \ldots
+  \end{array}
+\end{equation*}
+
+This tells us how the informal type given to $X_2$ in the previous section could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.
+
+Notice, however, that the recipe obtained so far, $X_{n + 1}: ({S_n})_\kstar(X_n)(X_n)$ for $X_n: S_n$, applies parametricity on the \emph{syntax} of the type of $X_n$.
+It does not directly yield a characterization of $S_n$ as a function from $n$.
+Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and the uniform treatment of augmented semi-simplial and semi-cubical sets by means of the generalization to $\nu$-sets.
+
+\subsection{Intuition for our formal construction}
+To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\painting$.
+A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$, and a $\painting$ corresponds to a filled $\framep$.
+Some $\framep$ are full and we call them $\fullframe$.
+
+We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying to the description above the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$.
+Let us now illustrate how we build $\fullframe[n]$.
+To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ of $X_0$ can be equivalently formulated as $\unittype \rightarrow \U$.
+Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
+For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown in Fig.~\ref{fig:intuition} for $\nu = 2$ which also mentions how the type of $X_2$ is structured.
+
 Let us now illustrate the construction of $\fullframe[3]$, necessary to build the type of $X_3$.
@@
 For instance, in the picture, each of the two $\painting[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\painting[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a partial square filling the partial frames made of respectively the left and right border of the blue square, and each of the two $\painting[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a partial square filling the full frames made respectively of the upper and lower borders of the blue and red squares.
-A $\painting[n][p]$ adds to a $\framep[n][p]$ the layers needed to form a $\fullframe[n]$.
+A $\painting[n][p]$ complements a $\framep[n][p]$ by adding layers needed to form a $\fullframe[n]$.
 They are added from dimension $n$ to dimension $p$ that is opposite to the order from $0$ to $p$ the $\framep[n][p]$ are built.
-A $\painting[n][p]$ complementing a given $\framep[n][p]$ fills the resulting $\fullframe[n]$.
 Thus, on the contrary of frames, it includes a filler, which lives in $X_n$ as shown below.
@@
   \framep[n][p]   & \defeq \Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype .\, \layer[n][0]) \ldots) .\, \layer[n][p] \\
-  \painting[n][p] & \defeq \Sigma l_p: \layer[n][p] . (\ldots (\Sigma l_n: \layer[n][n - 1] .\, X_n) \ldots)
+  \painting[n][p] & \defeq \Sigma l_p: \layer[n][p]. (\ldots (\Sigma l_n: \layer[n][n - 1] .\, X_n) \ldots)
 \end{align*}
@@
 More concretely, we build the ten definitions shown in the tables by induction, and this is part of the definition of a larger record.
-The other fields of the record aref $\framep$, $\layer$, $\painting$ at levels $n - 1$ and $n - 2$, $\restrf$, $\restrl$, and $\restrc$ at level $n - 1$, and equations to recall the definitions of these objects at lower levels.
+The other fields of the record are $\framep$, $\layer$, $\painting$ at levels $n - 1$ and $n - 2$, $\restrf$, $\restrl$, and $\restrc$ at level $n - 1$, and equations to recall the definitions of these objects at lower levels.
 

### 2023-01-23 paper/paper.tex
paper: drop subscripts on =

@@
 \newcommand{\defeq}{\ensuremath{\triangleq}}
-\newcommand{\eqHSet}{\ensuremath{{=}_{\mathit{HSet}\;}}}
-\newcommand{\reflHSet}{\ensuremath{\mathsf{refl}_{\mathit{HSet}}}}
+\newcommand{\refl}{\ensuremath{\mathsf{refl}}}
 
@@
 It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch}.
-% TODO anonymize??
+% TODO anonymize
 
@@
 We end with some of the finer details of our mechanization.
-% TODO polish
 
@@
 
-%TODO check in other places if it makes sense to use the notation and definition LaTeX environment
 \begin{definition}[$\DeltaPlus$]
@@
 We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, called $\textsf{bool}$, and the type of natural numbers.
-We also write $\hd$ and $\tl$ the projections of dependent pairs.
+We also write $\hd$ and $\tl$ the projections of dependent pairs, and $\refl$ for reflexivity.
 In type theory, logical propositions are types themselves and we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification.
@@
 \begin{enumerate}
-  \item[(i)] UIP holds on the unit and bool type:
-    \begin{align*}
-      \textsf{eq\_refl}        & : \Pi x.\, x = x                                            \\
-      \textsf{UIP\_refl\_unit} & : \Pi u: \unittype.\, \Pi x: u = u.\, x = \textsf{eq\_refl} \\
-      \textsf{UIP\_refl\_bool} & : \Pi b: \booltype.\, \Pi x: b = b.\, x = \textsf{eq\_refl}
-    \end{align*}
+  \item[(i)] UIP holds on the unit type, bool type, as well as all types of finite cardinal $\nu$.
   \item[(ii)] UIP propagates to $\Sigma$-types.
@@
 \end{enumerate}
-
-Note that an equivalent definition of UIP is given by \textsf{UIP\_refl}:
-\begin{align*}
-  \textsf{UIP\_refl} & : \Pi x: \Dom.\, \Pi p: x = x.\, p = \textsf{eq\_refl } x
-\end{align*}
 
@@
 
-% TODO explain the role of the subscript HSet on =
-
 As a side remark, note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
@@
 
-Since we have formalized the proof in the Coq proof assistant, which implements an intensional type theory, we now present the tables in \emph{intensional} type theory~\cite{martinlof75,martinlof84,coq22}, leaving implicit some details, which we will explain here, and other details, which we will explain in \ref{sec:mech}.
+Since we have formalized the proof in the Coq proof assistant, which implements an intensional type theory, we now present the tables in \emph{intensional} type theory~\cite{martinlof84,coq22}, leaving implicit some details, which we will explain here, and other details, which we will explain in \ref{sec:mech}.
 
@@
 Remark: If we weren't working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences.
-For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x =_{\mathit{HGpd}} y$ is in \U.
+For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x = y$ is in \U.
 See \cite{herbelin15} for a discussion on the need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory.

### 2023-01-23 paper/paper.tex
paper: fix one pending instance of subscript on =
refs

@@
   \ap \restrf[m][\omega][r][n][p][][]\;(\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d])\;\bullet   \\
-  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =_\mathit{HProp} \\
+  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =              \\
   \ap \restrf[m][\theta][p][n][p][][]\;(\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d])\;\bullet \\
@@
 Remark: If we weren't working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences.
-For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x = y$ is in \U.
-See \cite{herbelin15} for a discussion on the need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory.
+For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x =} y$ is in \U.
+See \cite{herbelin15,altenkirch16,kraus21} for a discussion on the need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory.
 

### 2023-01-23 paper/paper.tex
paper: fix compile, minor nits

@@
 This combined with the two terms of the form $\ap \cohf$ matches our expectation of three $\cohf$ on the left-hand side and two $\cohf$ on the right-hand side.
-$\coht$ can roughly be seen as a commutation of these $\cohf$ terms.
+Then, $\coht$ can roughly be seen as a commutation of these $\cohf$ terms.
 
@@
 For a fixed $n$, $\framep$, $\restrf$, and $\cohf$ have to be mutually defined by induction on $p$.
-Each of them rely on $\painting$, $\restrf$, and $\cohc$ at lower $n$, so they are well-founded.
-Finally, each of $\painting$, $\restrf$, and $\cohf$ are by induction from $p$ to $n$.
+Each of them rely on $\painting$, $\restrc$, and $\cohc$ at lower $n$, so they are well-founded.
+Finally, each of $\painting$, $\restrc$, and $\cohc$ are by induction from $p$ to $n$.
 
 Remark: If we weren't working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences.
-For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x =} y$ is in \U.
+For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x = y$ is in \U.
 See \cite{herbelin15,altenkirch16,kraus21} for a discussion on the need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory.
@@
 
-Since the construction shown in the previous sections are by induction on $n$, and dependencies are on lower $n$ and $p < n$, one would imagine formalizing this using well-founded induction in the calculus of inductive constructions.
-We initially tried this approach: we had terms dependent on the proofs of the case distinction of $n' \leq n$ implies $n' < n$ or $n' = n$, and these proofs didn't have definitional computational rule; it started to be necessary to reason propositionally on the computational property of the case distinction, and it eventually turned out to be unmanageable.
+Since the construction shown in the previous sections is by induction on $n$, and dependencies are on lower $n$ and $p < n$, one would imagine formalizing this using well-founded induction in dependent type theory.
+We initially tried this approach: we had terms dependent on the proofs of the case distinction of $n' \leq n$ implies $n' < n$ or $n' = n$, and these proofs did not have definitional computational rule; it started to be necessary to reason propositionally on the computational property of the case distinction, and it eventually turned out to be unmanageable.
 Hence, we chose a different route: in practice, since $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$, we only need to keep track of three ``levels'', and we built separate data structures for the levels, with dependencies.

### 2023-01-23 paper/paper.tex
paper: fix one paragraph

@@
 
-There are a few more subtleties.
-In $\cohf$ and $\cohc$, we use the reflection rule to identify equalities of pairs with a conjunction of two equalities.
-In $\cohl$, we use the reflection rule to identify equality of functions with point-wise equality.
-We additionally rely heavily on basic properties of the groupoid transport, which we don't detail.
+Like in \ref{tab:coh}, we leave implicit in \ref{fulltab:coh}, the use of the isomorphism between the type of equalities of dependent pairs in a $\Sigma$-type with the $\Sigma$-type of equalities of the components of the pair, as well as the isomorphism between equality of functions with point-wise equality.
+Contrary to the ETT case, functional extensionality does not hold, so we assume it.
+However, the requirement of functional extensionality disappears if $\nu$ is finite.
+As for basic groupoid properties of equalities, which no longer hold definitionally, we do not mention them for simplicity.
 
@@
 
-Remark: If we weren't working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences.
+Remark: If we were not working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences.
 For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x = y$ is in \U.
@@
 
+Here \SProp is a definitionally proof-irrelevant impredicative universe at the bottom of the universe hierarchy~\cite{gilbert19}.
 By placing the definition in \SProp, we have definitional equality of all inequality proofs.
@@
 \begin{minted}{coq}
-  le_trans ?p le_refl = ?p
-  le_trans le_refl ?p = ?p
+  leR_trans ?p leR_refl = ?p
+  leR_trans leR_refl ?p = ?p
 \end{minted}
-where \texttt{le\_trans} is transitivity, \texttt{le\_refl} is reflexivity, and \texttt{?p} is an existential variable.
+where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable.
 These two problems definitionally hold in \SProp, but equalizing them does not solve the existential.
@@
 
-\texttt{leY} is an improvement over \texttt{leR} since reflexivity is now definitionally the neutral element of transitivity, and associativity of transitivity also holds definitionally.
-Although it significantly eases our proof, there are some instances where unification is unable to solve for the existentials, and we have to provide them explicitly.
+This definition is an improvement over \texttt{leR} since reflexivity is now definitionally the neutral element of transitivity, and associativity of transitivity also holds definitionally.
+Although it significantly eases our proof, there are some instances where unification is unable to solve the existentials, and we have to provide them explicitly.
 

### 2023-01-23 paper/paper.tex
New reading up to before the formal construction in ETT

@@
   In dimension $1$, the standard augmented semi-simplex can be pictured as a point, colored black, corresponding to the unique morphism in $\Hom(0, 1)$.
-This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$:
+This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$.
   \begin{equation*}
@@
 
-More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as the base and glueing on top of it another copy of it lifted by one dimension.
+More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base and glueing on top of it another copy lifted by one dimension.
 In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.
-In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by $\kstar$.
+In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by~$\kstar$.
 
@@
 \begin{example}[$\Cube^1$]
-  $\Cube^1$ consists of two points, given by $\Hom(0, 1)$ and a line, given by $\Hom(1, 1)$:
+  $\Cube^1$ consists of two points, given by $\Hom(0, 1)$ and a line, given by $\Hom(1, 1)$.
   \begin{equation*}
@@
 
-More generally, the standard $(n + 1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them by a cylinder obtained as a third copy stretched in the new dimension.
+More generally, the standard $(n + 1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them on their border by a cylinder obtained as a third copy stretched in the new dimension.
 The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$.
@@
 Martin-Löf's Type theory~\cite{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
-It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Coq~\cite{coq22} or Lean~\cite{lean15}.
+It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda~\cite{agda23}, Coq~\cite{coq22} or Lean~\cite{lean15}.
 In type theory, propositions are types and proofs are programs.
@@
 We also write $\hd$ and $\tl$ the projections of dependent pairs, and $\refl$ for reflexivity.
-In type theory, logical propositions are types themselves and we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification.
+Logical propositions being types themselves, we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification.
 
@@
 It is well-known in set theory that families of small sets can be represented in a fibered or indexed way.
-In the fibered way, a family over $T$ is represented a pair of a set $S$, and a function from $S$ to $T$.
+In the fibered way, a family over $T$ is represented as a pair of a set $S$, and a function from $S$ to $T$.
 The function classifies the original set into fibers.
@@
 We have a priori a dependency over eight copies of $X_0$ but these are actually four due to the coherence conditions.
-Based on these coherence conditions, the type of $X_2$ happens to have the form $\Pi a b c d, X_1 (a)(b) \rightarrow X_1 (a)(c) \rightarrow X_1 (b)(d) \rightarrow X_1 (c)(d) \rightarrow \U$, recovering the square structure of $X_2$.
-In summary,
+Based on these coherence conditions, the types of $X_0, X_1, X_2$ happen to have the form:
 \begin{align*}
@@
 
-Now, one may wonder how to express the type of $X_i$ uniformly as a function of $n$. Connecting semi-cubical sets to binary parametricity will give us a solution which we describe in the next section.
+Now, one may wonder how to express the type of $X_n$ uniformly as a function of $n$. Connecting semi-cubical sets to binary parametricity will give us a solution which we describe in the next section.
 
 \section{Our construction}
-In this section, we gradually build up an intuition for our construction, followed by the full details.
+In this section, we gradually build up an intuition for our construction, followed by the details.
 
@@
 Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
-For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown in Fig.~\ref{fig:intuition} for $\nu = 2$ which also mentions how the type of $X_2$ is structured.
+For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown in Fig.~\ref{fig:intuition}.
+Fig.~\ref{fig:intuition} also mentions how the type of $X_2$ is structured.
 
@@
 For instance, in the picture, each of the two $\painting[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\painting[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a partial square filling the partial frames made of respectively the left and right border of the blue square, and each of the two $\painting[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a partial square filling the full frames made respectively of the upper and lower borders of the blue and red squares.
-A $\painting[n][p]$ complements a $\framep[n][p]$ by adding layers needed to form a $\fullframe[n]$.
-They are added from dimension $n$ to dimension $p$ that is opposite to the order from $0$ to $p$ the $\framep[n][p]$ are built.
-Thus, on the contrary of frames, it includes a filler, which lives in $X_n$ as shown below.
+A $\painting[n][p]$ complements a $\framep[n][p]$ by adding layers needed to form a $\fullframe[n]$ and by filling the resulting $\fullframe[n]$ with an inhabitant of $X_n$.
+Layers are added from dimension $n$ to dimension $p$ that is opposite to the order from $0$ to $p$ the $\framep[n][p]$ are built, as shown below.
 \begin{align*}
@@
 So, each $\layer[n][p]$ has to depend on $\framep[n][p]$.
-We also need a way to characterize the border of the $\nu$ $\painting[n-1][p]$ that compose a $\layer[n][p]$, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$.
-For instance, on the picture, each of the $\painting[2][1]$, shown as the red boxes, is laid on the borders of the blue boxes, and hence needs to depend on $\framep[3][1]$.
+We also need a way to characterize the border of the $\nu$ $\painting[n-1][p]$ that compose a $\layer[n][p]$, and this is $\restrf[n][p][\epsilon][p]$, for all $\epsilon < \nu$.
+For instance, on the picture, the left and right $\painting[2][1]$, shown in red, are laid on respectively the left and right borders of the blue boxes, and hence needs to depend on $\framep[3][1]$.
 The left and right borders of the two blue boxes are extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$.
@@
 
-Let us recall that a layer is made of $\nu$ paintings. When $\nu = 2$, this amounts to:
+When $\nu = 2$, the formation of layers from paintings amounts to:
 \begin{align*}
@@
 
-$\restrf[n][p][\epsilon][q]$ indicates restriction on $q$ layers of a frame, and the induction is on $p$, going from $0$ to $q$.
+The operation $\restrf[n][p][\epsilon][q]$ indicates restriction on $q$ layers of a frame, and the induction is on $p$, going from $0$ to $q$.
 In particular, $\restrf[n][p][\epsilon][p]$ is a ``full restriction''.

### 2023-01-23 paper/paper.tex
spell checking

@@
 
-More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base and glueing on top of it another copy lifted by one dimension.
+More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base and gluing on top of it another copy lifted by one dimension.
 In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.
@@
 
-The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and \ref{tab:coh}.
+The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and~\ref{tab:coh}.
 Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a coinductive limit of $n$-truncated $\nu$-sets.
@@
 This includes in particular the groupoid properties of equality.
-Notably, unicity of identity proofs holds in extensional type theory, so that any type is automatically an $\U$.
+Notably, uniqueness of identity proofs holds in extensional type theory, so that any type is automatically an $\U$.
 Also, we left implicit in table~\ref{tab:coh} the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
@@
 The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit as shown in table \ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
-The proof of $\cohf$ is described on \ref{fulltab:coh}, and it requires explicitation of several equalities which were definitional in extensional type theory.
+The proof of $\cohf$ is described on \ref{fulltab:coh}, and it requires making explicit several equalities which were definitional in extensional type theory.
 The commutation of $\restrl$ lives in a type referring to $\cohf$, so we need a transport along the commutation of $\restrf$ in the statement of $\cohl$.

### 2023-01-23 paper/paper.tex
misc

@@
 Tables \ref{fulltab:coind}, \ref{fulltab:core}, and \ref{fulltab:frames} are unchanged, except that we make explicit all arguments, including those that can be inferred from the context.
-The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit as shown in table \ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
-The proof of $\cohf$ is described on \ref{fulltab:coh}, and it requires making explicit several equalities which were definitional in extensional type theory.
+The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit as shown in table~\ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
+The proof of $\cohf$ is described on~\ref{fulltab:coh}, and it requires making explicit several rewritings which were invisible in extensional type theory.
 The commutation of $\restrl$ lives in a type referring to $\cohf$, so we need a transport along the commutation of $\restrf$ in the statement of $\cohl$.
@@
 Each of them rely on $\painting$, $\restrc$, and $\cohc$ at lower $n$, so they are well-founded.
-Finally, each of $\painting$, $\restrc$, and $\cohc$ are by induction from $p$ to $n$.
+Finally, each of $\painting$, $\restrc$, and $\cohc$ are built by induction from $p$ to $n$.
 
 Remark: If we were not working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences.
-For the unfamiliar reader, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x = y$ is in \U.
+Here, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x = y$ is in \U.
 See \cite{herbelin15,altenkirch16,kraus21} for a discussion on the need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory.

### 2023-01-23 paper/paper.tex
about inequality in ITT version
perspectives

@@
 
+Depending on how inequality on natural numbers is defined, different equalities may hold or not definitionally, such as transitivity of inequality or the computational properties of induction over inequality proofs.
+We do not address these details in this section, see instead~\ref{sec:mech}.
+
 Remark: If we were not working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences.
@@
 In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\cite{nuyts17,cavallo19} by adding degeneracies, a hierarchy of universes (as sketched e.g.
-in a talk by Herbelin at the HoTT-UF workshop for the bridge case~\cite{herbelin-hott-uf}) as well as reasoning modulo permutations~\cite{grandis03}.
+in a talk by Herbelin at the HoTT-UF workshop for the bridge case~\cite{herbelin-hott-uf}), as well as reasoning modulo permutations~\cite{grandis03}.
 
-By equipping the universe construction with a structure of equivalences , as suggested along the lines of Altenkirch and Kaposi~\cite{altenkirch15}, as well as a structure of connections, we expect the parametric model to extend into a model of cubical type theory~\cite{bezem13}.
-A key point in this approach, is that, thanks to the indexed construction, we expect univalence to hold by definition in the model, without requiring any kind of Reedy fibrancy as it would a priori be needed in the fibered case.
+By equipping the universe construction with a structure of equivalences, as suggested along the lines of Altenkirch and Kaposi~\cite{altenkirch15}, we expect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\cite{bezem13,cohen16,angiuli21}.
+A key point is that, thanks to the indexed approach, we expect univalence to hold by definition.
 If these intuitions are correct, this would definitively root cubical type theory on top of iterated parametricity translation.

### 2023-01-24 paper/paper.tex
a rewording

@@
 It does not directly yield a characterization of $S_n$ as a function from $n$.
-Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and the uniform treatment of augmented semi-simplial and semi-cubical sets by means of the generalization to $\nu$-sets.
+Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and the uniform treatment of augmented semi-simplicial and semi-cubical sets by means of the generalization to $\nu$-sets.
 
@@
 Depending on how inequality on natural numbers is defined, different equalities may hold or not definitionally, such as transitivity of inequality or the computational properties of induction over inequality proofs.
-We do not address these details in this section, see instead~\ref{sec:mech}.
+Details are given in~\ref{sec:mech}.
 
@@
 
+\begin{figure}[H]
   \begin{minted}{coq}
@@
   \end{minted}
+\end{figure}
 
-Here \SProp is a definitionally proof-irrelevant impredicative universe at the bottom of the universe hierarchy~\cite{gilbert19}.
+Here $\SProp$ is a definitionally proof-irrelevant impredicative universe at the bottom of the universe hierarchy~\cite{gilbert19}.
 By placing the definition in \SProp, we have definitional equality of all inequality proofs.
@@
   \end{minted}
+\end{figure}
 where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable.
@@
   \end{minted}
+\end{figure}
 

### 2023-01-24 paper/paper.tex
paper: fix a typo
explaining the recursion argument already in itt

--- 2023-01-24 paper/paper.tex
@@
 This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$.
-Even though it looks independent of the other tables, it has to proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
+Even though it looks independent of the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
+More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be mutually defined by induction on $p$.
+Similarly, the block made of $\painting$, $\restrc$, and $\cohc$ is built by induction from $p$ to $n$.
+The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but, conversely, the dependency is only on lower $n$, so this is well-founded.
+Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
+We leave however here implicit the exact way this mutual recursion can be formalized.
 
@@
 
-For a fixed $n$, $\framep$, $\restrf$, and $\cohf$ have to be mutually defined by induction on $p$.
-Each of them rely on $\painting$, $\restrc$, and $\cohc$ at lower $n$, so they are well-founded.
-Finally, each of $\painting$, $\restrc$, and $\cohc$ are built by induction from $p$ to $n$.
+The way recursion is implemented is still left implicit at this stage. See \ref{sec:mech} for the details.
 

### 2023-01-24 paper/paper.tex
referring to fig 3 for examples

@@
 
-As a side remark, note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning $\restrf$ nor $\cohf$ anymore.
+Note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning them anymore.
+For instance, it produces figure \ref{fig:intuition} for $n=2$ and $\nu=2$.
 

### 2023-01-24 paper/paper.tex
more

@@
 More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be mutually defined by induction on $p$.
-Similarly, the block made of $\painting$, $\restrc$, and $\cohc$ is built by induction from $p$ to $n$.
-The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but, conversely, the dependency is only on lower $n$, so this is well-founded.
+Also, each of $\painting$, $\restrc$, and $\cohc$ is built by induction from $p$ to $n$.
+The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but, the converse dependency is only on lower $n$, so this is well-founded.
 Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
-We leave however here implicit the exact way this mutual recursion can be formalized.
+We leave however implicit the exact way this mutual recursion can be formalized as this stage.
 

### 2023-01-25 paper/paper.tex
paper: equalize columns on last page
paper: fix an underfull hbox

@@
 
-\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, multicol, minted, rotating}
+\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, multicol, rotating, flushend}
+
+\makeatletter
+\@namedef{ver@lineno.sty}{9999/12/31}
+\@namedef{opt@lineno.sty}{}
+\makeatother
+\usepackage{minted}
+
 \usepackage[prefix=bonak]{art.cls/xkeymask}
@@
 
-The operation $\restrf[n][p][\epsilon][q]$ indicates restriction on $q$ layers of a frame, and the induction is on $p$, going from $0$ to $q$.
+The operation $\restrf[n][p][\epsilon][q]$ indicates restriction on $q$ layers of a frame, and the induction is on $p$, from $0$ to $q$.
 In particular, $\restrf[n][p][\epsilon][p]$ is a ``full restriction''.

### 2023-01-30 paper/paper.tex
paper: add author emails

@@
 \title{A parametricity-based formalization of semi-simplicial and semi-cubical sets}
-\author{\IEEEauthorblockN{Hugo Herbelin \\ and Ramkumar Ramachandra} \IEEEauthorblockA{Université Paris Cité, Inria, CNRS, IRIF, Paris}}
+\author{\IEEEauthorblockN{Hugo Herbelin \texttt{<Hugo.Herbelin@inria.fr>} \\ and Ramkumar Ramachandra \texttt{<r@artagnon.com>}}\IEEEauthorblockA{Université Paris Cité, Inria, CNRS, IRIF, Paris}}
 

### 2023-01-30 paper/paper.tex
Email in paper

--- 2023-01-25 paper/paper.tex
@@
 \title{A parametricity-based formalization of semi-simplicial and semi-cubical sets}
-\author{\IEEEauthorblockN{Hugo Herbelin \\ and Ramkumar Ramachandra} \IEEEauthorblockA{Université Paris Cité, Inria, CNRS, IRIF, Paris}}
+\author{\IEEEauthorblockN{Hugo Herbelin \\ and Ramkumar Ramachandra}\\\IEEEauthorblockA{Université Paris Cité, Inria, CNRS, IRIF, Paris\\\texttt{Hugo.Herbelin@inria.fr} and \texttt{r@artagnon.com}}}
 

### 2023-03-16 paper/paper.tex
Adding magic compilation incantation for hal/arxiv
paper: fix some problems pointed out by reviewers

@@
+%% -*- latex-command: pdflatex -shell-escape -*-
 \documentclass[10pt]{art.cls/art}
@@
 Voevodsky~\cite{voevodsky12} or in previous work~\cite{herbelin15}, as a dependently-typed construction, which we call \emph{indexed}.
-%TODO anonymize
 
@@
 In the context of functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational behavior of programs of this type.
-Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity, when using more generally graphs than relations, has a cubical flavor~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
+Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity can be interpreted in various various cubical sets~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
 We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or graphs, in which case, we obtain a form of realizability~\cite{bernardy12,lasson12,moulin16}.
 It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch}.
-% TODO anonymize
 
-We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets obtained by applying simple rules characterizing iterated parametricity.
+We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets obtained by applying rules inspired from iterated parametricity.
 In contrast to the standard presheaf presentation of augmented semi-simplicial and semi-cubical sets~\cite{fri08,grandis03,buchholtz17}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
@@
 The outline of the paper is as follows.
-First, we recall the definition of the augmented semi-simplicial and semi-cubical categories using a combinatorial presentation, that directly leads to our generalization to $\nu$-sets.
-We then proceed to explain our indexed construction, with the help of diagrams.
-Before spelling out the details of our formalization in type-theoretic language, we have a section on reasoning with sets inside type theory.
-We end with some of the finer details of our mechanization.
+We recall the definition of the augmented semi-simplicial and semi-cubical categories using a combinatorial presentation, that directly leads to our generalization to $\nu$-sets, in \ref{sec:nu}.
+We then proceed to explain our setting in \ref{sec:setting}.
+Before spelling out the details of our formalization in type-theoretic language in \ref{sec:itt}, we explain the connection between the indexed representation and parametricity in \ref{sec:indexed-param}, and build up intuitions in \ref{sec:intuition}.
+We end with some of the finer details of our mechanization in \ref{sec:mech}.
 
-Our precise mechanization in Coq is available at \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}.
+See \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak} for our mechanization.
 The construction was conceived in Summer 2019, and the mechanization began in late 2019.
@@
 
-\section{Semi-simplicial and semi-cubical sets}
+\section{Semi-simplicial and semi-cubical sets\label{sec:nu}}
 \subsection{Augmented semi-simplicial sets}
@@
 \begin{notation}[Finite sequences]
-  We denote finite sequences by $\{i_1, \ldots i_n\}$ for $i_j$ ranging over some domain.
-In particular, the empty sequence is written $\{\}$ and we define $i :: \{j_1, \ldots, j_n\}$ to be $\{i, j_1, \ldots, j_n\}$.
+  We denote finite sequences by $[i_1, \ldots i_n]$ for $i_j$ ranging over some domain.
+In particular, the empty sequence is written $[]$ and we define $i :: [j_1, \ldots, j_n]$ to be $[i, j_1, \ldots, j_n]$.
 \end{notation}
@@
       \Obj(\DeltaPlus) & := \Nat                                                                     \\
-      \Hom(p, n)       & := \{l \in \{0, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}      \\
+      \Hom(p, n)       & := \{l \in [0, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}        \\
       g \circ f        & :=
       \begin{cases}
-        f                  & \text{if $g = \{\}$}                                                      \\
+        f                  & \text{if $g = []$}                                                        \\
         0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
@@
       \end{cases} \\
-      \id              & := \{\kstar, \ldots, \kstar\} \text{ $n$ times for $\id \in \Hom(n, n)$}
+      \id              & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom(n, n)$}
     \end{align*}
@@
 \begin{example}[$\DeltaPlus^2$]
-  In dimension $2$, the standard augmented semi-simplex is drawn as two points, given by $\Hom(1, 2)$, along with a line connecting them, given by $\Hom(2, 2)$.
+  The standard augmented $2$-semi-simplex is drawn as two points, given by $\Hom(1, 2)$, along with a line connecting them, given by $\Hom(2, 2)$.
 We use the color black to denote the unique morphisms in $\Hom(0, 1)$ and $\Hom(0, 2)$.
@@
       \Obj(\Cube) & := \Nat                                                                                \\
-      \Hom(p, n)  & := \{l \in \{L, R, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}              \\
+      \Hom(p, n)  & := \{l \in [L, R, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}                \\
       g \circ f   & :=
       \begin{cases}
-        f                  & \text{if $g = \{\}$}                                                            \\
+        f                  & \text{if $g = []$}                                                              \\
         a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a = L$ or $R$}                          \\
@@
       \end{cases} \\
-      \id         & := \{\kstar, \ldots, \kstar\} \text{ $n$ times}
+      \id         & := [\kstar, \ldots, \kstar] \text{ $n$ times}
     \end{align*}
@@
 
-A $\nu$-set is thus a functor $\phi$ from the $\nu$-semi-shape category to $\Set$ and we call $n$-$\nu$-semi-shape an element of $\phi(n)$.
+A $\nu$-set is thus a contravariant functor $\phi$ from the $\nu$-semi-shape category to $\Set$ and we call $n$-$\nu$-semi-shape an element of $\phi(n)$.
 As in the augmented semi-simplicial and semi-cubical cases, the standard $(n + 1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
@@
 
-\section{Our setting}
+\section{Our setting\label{sec:setting}}
 We now explain how we recover the notion of sets in type theory, explain the difference between the fibered and indexed representations, and supply an example of indexed semi-cubical sets.
@@
 In type theory, propositions are types and proofs are programs.
-A particularity of type theory is also that types and programs, henceforth propositions and proofs also, are considered modulo an equational theory called definitional equality.
+A particularity of type theory is also that types and programs, hence propositions and proofs also, are considered modulo an equational theory called definitional equality.
 
@@
 Some models are based on topological spaces, where equality is interpreted as path, and substitutivity of equality as transport.
-This model supports the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\cite{hottbook}.
+These models support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\cite{hottbook}.
 In type theory, types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number.
@@
 
-\subsection{Fibered versus indexed representation}
-It is well-known in set theory that families of small sets can be represented in a fibered or indexed way.
-In the fibered way, a family over $T$ is represented as a pair of a set $S$, and a function from $S$ to $T$.
-The function classifies the original set into fibers.
-In contrast, in the indexed way, a family over $T$ is represented as a functional relation with domain $T$, which itself, by the replacement axiom, is a set.
+\subsection{Relating the indexed representation to parametricity\label{sec:indexed-param}}
+% \begin{equation*}
+%   \Sigma S: \U.\, S\rightarrow T ~\simeq~ T \rightarrow \U
+% \end{equation*}
 
-In category theory, the correspondence between the fibered and indexed way manifests as the correspondence between Grothendieck fibrations and pseudofunctors, of which a particular instance is the correspondence between discrete fibrations and presheaves, or even between discrete fibrations over sets and families of sets.
-
-The latter correspondence can be expressed in Homotopy Type Theory, for $T: \Type$, as an equivalence between $\Sigma S: \Type.\; S \rightarrow T$ and $T \rightarrow \Type$, which can be proved using univalence.
-This correspondence also holds on \U, for $T: \U$:
-\begin{equation*}
-  \Sigma S: \U.\, S\rightarrow T ~\simeq~ T \rightarrow \U
-\end{equation*}
-
-\subsection{Example: indexed semi-cubical sets}
 Let us now come back to semi-cubical sets. A semi-cubical set can be represented as a sequence of fibrations, together with appropriate coherence conditions.
@@
 
-Now, one may wonder how to express the type of $X_n$ uniformly as a function of $n$. Connecting semi-cubical sets to binary parametricity will give us a solution which we describe in the next section.
-
-\section{Our construction}
-In this section, we gradually build up an intuition for our construction, followed by the details.
-
-\subsection{Relating the indexed representation to parametricity}
 The process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$ in the last section, is similar to applying a binary parametricity translation and expecting the resulting translation to be inhabited.
@@
 
-\subsection{Intuition for our formal construction}
+\section{Our construction}
+In this section, we gradually build up an intuition for our construction, followed by the details.
+
+\subsection{Intuition for our formal construction\label{sec:intuition}}
 To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\painting$.

### 2023-03-17 paper/paper.tex
lics23: write some more responses

@@
 In the context of functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational behavior of programs of this type.
-Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity can be interpreted in various various cubical sets~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
+Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity can be interpreted in various cubical sets~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
 We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or graphs, in which case, we obtain a form of realizability~\cite{bernardy12,lasson12,moulin16}.

### 2023-03-17 paper/paper.tex
paper: update a couple of refs

@@
 \section{Introduction}
-In the context of functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational behavior of programs of this type.
+In the context of functional programming, Reynolds' parametricity~\cite{reynolds83} interprets types as relations characterizing the observational behavior of programs of this type.
 Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity can be interpreted in various cubical sets~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
@@
 As in the augmented semi-simplicial and semi-cubical cases, the standard $(n + 1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
-We clarify in the next sections how this process of construction is similar to the parametricity translation developed for functional programming~\cite{reynolds72} and more generally for type theory~\cite{bernardy10, bernardy11, atkey14, bernardy15}.
+We clarify in the next sections how this process of construction is similar to the parametricity translation developed for functional programming~\cite{reynolds83} and more generally for type theory~\cite{bernardy10, bernardy11, atkey14, bernardy15}.
 
@@
 Type theory is a flexible formalism supporting different models.
-Some models are based on topological spaces, where equality is interpreted as path, and substitutivity of equality as transport.
+Some models are based on topological spaces, where equality is interpreted as path, and substitutivity of equality as transport~\cite{kapulkin21}.
 These models support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\cite{hottbook}.

### 2023-03-17 paper/paper.tex
lics23, paper: minor changes

@@
 \subsection{Relating the indexed representation to parametricity\label{sec:indexed-param}}
-% \begin{equation*}
-%   \Sigma S: \U.\, S\rightarrow T ~\simeq~ T \rightarrow \U
-% \end{equation*}
+The correspondence between fibered and indexed representation is a particular case of the Grothendieck construction, and can be written as:
+\begin{equation*}
+  (\Sigma S: \U. (S \rightarrow T)) \simeq (T \rightarrow \U)
+\end{equation*}
 

### 2023-03-18 paper/paper.tex
paper: fix typo in framep defn
paper: polish 3B

@@
 We recall the definition of the augmented semi-simplicial and semi-cubical categories using a combinatorial presentation, that directly leads to our generalization to $\nu$-sets, in \ref{sec:nu}.
-We then proceed to explain our setting in \ref{sec:setting}.
-Before spelling out the details of our formalization in type-theoretic language in \ref{sec:itt}, we explain the connection between the indexed representation and parametricity in \ref{sec:indexed-param}, and build up intuitions in \ref{sec:intuition}.
+We then proceed to explain the connection between the indexed representation and parametricity in \ref{sec:indexed-param}.
+Before spelling out the details of our formalization in type-theoretic language in \ref{sec:itt}, we build up intuitions in \ref{sec:intuition}.
 We end with some of the finer details of our mechanization in \ref{sec:mech}.
@@
 
-\section{Our setting\label{sec:setting}}
-We now explain how we recover the notion of sets in type theory, explain the difference between the fibered and indexed representations, and supply an example of indexed semi-cubical sets.
+\section{Indexed representation and parametricity\label{sec:indexed-param}}
+In this section, we introduce some preliminaries on interpreting sets in type theory, followed by a small section on the indexed presentation, before relating it to parametricity in \ref{sec:rel-param}.
 
-\subsection{Working with sets in type theory}
+\subsection{Preliminaries}
 Martin-Löf's Type theory~\cite{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
@@
 
-\subsection{Relating the indexed representation to parametricity\label{sec:indexed-param}}
-The correspondence between fibered and indexed representation is a particular case of the Grothendieck construction, and can be written as:
+\subsection{Fibered versus indexed representation}
+There are different ways to represent a family of sets, commonly known as the fibered and indexed representations. In type theory, they are equivalent, and this equivalence can be formulated as:
 \begin{equation*}
@@
 
-Let us now come back to semi-cubical sets. A semi-cubical set can be represented as a sequence of fibrations, together with appropriate coherence conditions.
+Let us apply this correspondence to the case of semi-cubical sets. A semi-cubical set can be represented as a sequence of fibrations, together with appropriate coherence conditions.
 \begin{equation*}
@@
 
+\subsection{Relating to parametricity\label{sec:rel-param}}
 The process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$ in the last section, is similar to applying a binary parametricity translation and expecting the resulting translation to be inhabited.
@@
 \begin{align*}
-  \framep[n][p]   & \defeq \Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype .\, \layer[n][0]) \ldots) .\, \layer[n][p] \\
+  \framep[n][p]   & \defeq \Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype .\, \layer[n][0]) \ldots) .\, \layer[n][p - 1] \\
   \painting[n][p] & \defeq \Sigma l_p: \layer[n][p]. (\ldots (\Sigma l_n: \layer[n][n - 1] .\, X_n) \ldots)
@@
    & \framep[n][p](D) \defeq                                                                                      \\
-   & \;\;\;\;\Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)) \ldots) .\,\layer[n][p](D) \\
+   & \;\;\;\;\Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)) \ldots) .\,\layer[n][p - 1](D) \\
    & \painting[n][p](D) \defeq                                                                                    \\

### 2023-03-19 paper/paper.tex
paper: minor polish
reformulating conclusion

@@
 Note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning them anymore.
-For instance, it produces figure \ref{fig:intuition} for $n=2$ and $\nu=2$.
+For instance, it produces Fig.~\ref{fig:intuition} for $n=2$ and $\nu=2$.
 
@@
 
-By equipping the universe construction with a structure of equivalences, as suggested along the lines of Altenkirch and Kaposi~\cite{altenkirch15}, we expect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\cite{bezem13,cohen16,angiuli21}.
-A key point is that, thanks to the indexed approach, we expect univalence to hold by definition.
-If these intuitions are correct, this would definitively root cubical type theory on top of iterated parametricity translation.
+By equipping the universe construction with a structure of equivalences, as suggested along the lines of Altenkirch and Kaposi~\cite{altenkirch15}, we expect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\cite{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models.
+This would a priori preserve definitional properties which may be lost when detouring via presheaves.
+In particular, we conjecture being able to justify univalence holding definitionally.
+Our approach would also definitively ground cubical type theory in iterated parametricity.
 

### 2023-03-19 paper/paper.tex
adding indication on how to orient

@@
 In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by~$\kstar$.
+Note that the components may be oriented by letting each $n$-dimensional component point to the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ of the $n$-dimensional component with $0$.
 
@@
 The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$.
+Note that the components can this time be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$ to the one obtained by replacing the leftmost $\kstar$ with $R$.
 

### 2023-03-19 paper/paper.tex
Removing confusing terminology \hat{Delta}

@@
 
-While ordinary semi-simplicial sets are presheaves over the semi-simplex category \DeltaHat, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus.
+While ordinary semi-simplicial sets are presheaves over the semi-simplex category, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus.
 There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that will later straightforwardly extend to semi-cubical sets.
+
+%% Notations
+% simplicial, augmented, where
+% Γ           Γ+         Augmented Simplicial Combinatorics through Category Theory
+%                        José Manuel García-Calcines, María Teresa Rivas-Rodríguez, Luis Javier Hernández-Paricio, 2022
+
+% semi-augmented, where
+% ∆_s        HOMOLOGY IN RELATIVE SEMI-ABELIAN CATEGORIES, JULIA GOEDECKE, 2011
+
+% simplicial, semi-simplicial, where
+% Δ           Δ_inj            SEMI-SIMPLICIAL SPACES, JOHANNES EBERT AND OSCAR RANDAL-WILLIAMS, 2018
+% Δ           Δ_inj            PhD, Josep Esquirol Esteve, 2019
+% Δ           Δ'               Strict n-categories and augmented directed complexes model homotopy types, Andrea Gagna, 2018
+% Δ           Δ_inj, Δ_{inj,aug} Ms Th. Jonas Dallend ̈orfer, 2019
 

### 2023-03-19 paper/paper.tex
Smoothing a formulation

@@
 
-We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets obtained by applying rules inspired from iterated parametricity.
+We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets generated by iterating parametricity.
 In contrast to the standard presheaf presentation of augmented semi-simplicial and semi-cubical sets~\cite{fri08,grandis03,buchholtz17}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.

### 2023-03-19 paper/paper.tex
Addressing the question of the contribution of the paper and of the stepwise explanation of the construction

@@
 
-We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets generated by iterating parametricity.
+We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets, generated by iterating the parametricity translation for type judgements.
 In contrast to the standard presheaf presentation of augmented semi-simplicial and semi-cubical sets~\cite{fri08,grandis03,buchholtz17}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
 That is, instead of having the set of augmented semi-simplices or semi-cubes in dimension $n+1$ \emph{fibered} over the set of augmented semi-simplices or semi-cubes in dimension $n$, we consider families of augmented semi-simplices and semi-cubes indexed over their faces.
+
+As a result, our work can be seen as contributing the following: it characterizes, will full details, how to technically define parametricity iterated in arbitrary dimensions; %Second, it makes fully formal the relation between semi-simplicial and semi-cubical sets and parametricity.
+it provides with an alternative case study in the realm of indexed constructions of semi-simplicial and semi-cubical sets~\cite{voevodsky12,herbelin15,part15}, especially in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\cite{part15,shulman14,altenkirch16,kraus2017space}, as well as of better understanding the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}); it makes a step in the direction of the program initiated in~\cite{altenkirch15} to develop parametricity-based models of parametric type theory~\cite{bernardy15,nuyts17,cavallo19} and cubical type theory~\cite{bezem13,cohen16,angiuli21} which are closer from the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do (compare e.g.
+to the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally closed cartesian categories~\cite{curien14}).
 
@@
 \section{Semi-simplicial and semi-cubical sets\label{sec:nu}}
+
+We give in this section a uniform definition of semi-simplicial and semi-cubical sets which we believe is folklore.
+The uniformity allows the definition of a notion of $\nu$-sets that subsumes semi-simplicial and semi-cubical sets.
+
 \subsection{Augmented semi-simplicial sets}
@@
 \section{Our construction}
-In this section, we gradually build up an intuition for our construction, followed by the details.
+
+Our construction involves several details, some of them being visible only in the Coq formalization.
+A description at an informal level which we estimate to be however mathematically precise enough can be found in Sections~\ref{sec:ett} and~\ref{sec:itt}, while technical issues with the mechanization are explained in~\ref{sec:mech}.
+
+The whole definition is highly dependent, with dependencies in
+inequality proofs and in coherence conditions. In Section~\ref{sec:ett} and Tables~\ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces}, \ref{tab:coh}, we
+give a definition in Extensional Type Theory, which roughly
+corresponds to a level of reasoning ``à la set theory'' where coherence
+conditions are thought as ``holding on the nose'' without having to
+mention them explicitly once they are justified. In Section~\ref{sec:itt} and Tables~\ref{fulltab:coind}, \ref{fulltab:core}, \ref{fulltab:frames}, \ref{fulltab:faces}, \ref{fulltab:coh}, we
+give a definition in Intentional Type Theory, where transporting along
+the coherence conditions is made explicit. This makes the definition
+more involved, but at the same time helps to understand the
+specificities of coherence conditions.
+
+But first, we start with a section gradually and informally explaining the intuition of the construction.
 
@@
 
-\subsection{Formal construction in ETT}
+\subsection{Formal construction in ETT\label{sec:ett}}
 % Abbreviated tables in this section

### 2023-03-19 paper/paper.tex
Preparing a response, answering several points, but not all yet

@@
 In the context of functional programming, Reynolds' parametricity~\cite{reynolds83} interprets types as relations characterizing the observational behavior of programs of this type.
-Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity can be interpreted in various cubical sets~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
+Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has the structure of a cubical set~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
 We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or graphs, in which case, we obtain a form of realizability~\cite{bernardy12,lasson12,moulin16}.
-It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch}.
+It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch}.
 
@@
 We then proceed to explain the connection between the indexed representation and parametricity in \ref{sec:indexed-param}.
-Before spelling out the details of our formalization in type-theoretic language in \ref{sec:itt}, we build up intuitions in \ref{sec:intuition}.
+Before spelling out the details of our formalization in type-theoretic language in \ref{sec:ett} and \ref{sec:itt}, we build up intuitions in \ref{sec:intuition}.
 We end with some of the finer details of our mechanization in \ref{sec:mech}.
@@
 
-The standard augmented $0$-semi-simplex is a singleton of one color. Standard augmented $n$-semi-simplices have a geometric interpretation, and we illustrate them for dimensions $1$, $2$, and $3$.
+The standard augmented $0$-semi-simplex is a singleton made of one color (in our case black).
+Standard augmented $n$-semi-simplices for $n\geq 1$ have a geometric interpretation, and we illustrate them for dimensions $1$, $2$, and $3$.
 
 \begin{example}[$\DeltaPlus^1$]
-  In dimension $1$, the standard augmented semi-simplex can be pictured as a point, colored black, corresponding to the unique morphism in $\Hom(0, 1)$.
+  The standard augmented $1$-semi-simplex can be pictured as a point, colored black, corresponding to the unique morphism in $\Hom(0, 1)$.
 This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$.
@@
 Semi-cubical sets are defined like augmented semi-simplicial sets except that $\DeltaPlus$ is replaced by $\Cube$ in which we take sequences of $L$, $R$ and $\star$, instead of sequences of $0$ and $\kstar$.
+They represent ordinary semi-cubical sets, with faces (and no augmentation).
 
@@
   \begin{tikzcd}
-    X_0: \U & X_1: \U \arrow[l, "\delta^L" description, shift left=2] \arrow[l, "\delta^R" description, shift right=2] & X_2: \U \arrow[l, "\delta^{L\kstar}" description, shift left=6] \arrow[l, "\delta^{R\kstar}" description, shift left=2] \arrow[l, "\delta^{\kstar R}" description, shift right=2] \arrow[l, "\delta^{\kstar L}" description, shift right=6] & \ldots
+    X_0: \U & X_1: \U \arrow[l, "\delta^L" description, shift left=2] \arrow[l, "\delta^R" description, shift right=2] & X_2: \U \arrow[l, "\delta^{L\kstar}" description, shift left=6] \arrow[l, "\delta^{R\kstar}" description, shift left=2] \arrow[l, "\delta^{\kstar L}" description, shift right=2] \arrow[l, "\delta^{\kstar R}" description, shift right=6] & \ldots
   \end{tikzcd}
@@
 Continuing the process, we can think of $X_2$ fibered over four copies of $X_1$ themselves fibered over two copies of $X_0$ as a dependent type.
-We have a priori a dependency over eight copies of $X_0$ but these are actually four due to the coherence conditions.
+We have a priori a dependency over eight copies of $X_0$ but these are actually four due to the coherence conditions on the functor (e.g.
+that $\delta^R \circ \delta^{R\kstar} = \delta^{(R\kstar)\circ(R)} = \delta^{RR} = \delta^{(\kstar R)\circ(R)} = \delta^R \circ \delta^{\kstar R}$, etc.).
 Based on these coherence conditions, the types of $X_0, X_1, X_2$ happen to have the form:
@@
 
-But first, we start with a section gradually and informally explaining the intuition of the construction.
+But first, we start with a section gradually and informally explaining
+the intuition of the construction. It can be read in parallel with the
+tables if wished.
 
@@
 We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying to the description above the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$.
+In particular, $\fullframe[n]$ is a ``telescope'', i.e.
+a nesting of $\Sigma$-type.
 Let us now illustrate how we build $\fullframe[n]$.
@@
 First, $\fullframe[n]$ depends on all $X_i$ up to $n - 1$.
-So, we need to package up $X_i$, for $i < n$, into a type, which we call $\X[][<n][]$.
+So, we need to package up $X_i$, for $i < n$, into a nesting of $\Sigma$-type, which we abbreviate as $\X[][<n][]$.
 This allows us to give the type $\X[][<n][] \rightarrow \U$ to $\fullframe[n]$.
@@
 The $n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.
-The $n$th component is a family over a $\fullframe$.
+This is a nested $\Sigma$-type of which the $n$th component is a family over a $\fullframe$.
 The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\painting$.
@@
 Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
-We leave however implicit the exact way this mutual recursion can be formalized as this stage.
+We leave however implicit the exact way this mutual recursion can be formalized at this stage of the paper.
 

### 2023-03-20 paper/paper.tex
More comments

@@
 
-Our construction involves several details, some of them being visible only in the Coq formalization.
-A description at an informal level which we estimate to be however mathematically precise enough can be found in Sections~\ref{sec:ett} and~\ref{sec:itt}, while technical issues with the mechanization are explained in~\ref{sec:mech}.
-
-The whole definition is highly dependent, with dependencies in
-inequality proofs and in coherence conditions. In Section~\ref{sec:ett} and Tables~\ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces}, \ref{tab:coh}, we
-give a definition in Extensional Type Theory, which roughly
-corresponds to a level of reasoning ``à la set theory'' where coherence
-conditions are thought as ``holding on the nose'' without having to
-mention them explicitly once they are justified. In Section~\ref{sec:itt} and Tables~\ref{fulltab:coind}, \ref{fulltab:core}, \ref{fulltab:frames}, \ref{fulltab:faces}, \ref{fulltab:coh}, we
-give a definition in Intentional Type Theory, where transporting along
-the coherence conditions is made explicit. This makes the definition
-more involved, but at the same time helps to understand the
-specificities of coherence conditions.
+Our construction is highly dependent, with dependencies in inequality
+and equality proofs. It involves several involved details, some of
+them being visible only in the Coq formalization.
+
+In Section~\ref{sec:ett} and Tables~\ref{tab:coind}, \ref{tab:core},
+\ref{tab:frames}, \ref{tab:faces}, \ref{tab:coh}, we give an informal,
+mathematical definition in Extensional Type Theory, which roughly
+corresponds to a level of reasoning ``à la set theory'' where
+equalities are thought as ``holding on the nose'' without having to
+mention them explicitly once they are justified. In
+Section~\ref{sec:itt} and Tables~\ref{fulltab:coind},
+\ref{fulltab:core}, \ref{fulltab:frames}, \ref{fulltab:faces},
+\ref{fulltab:coh}, we give the same mathematical definition in
+Intensional Type Theory, where transporting along coherence conditions
+is now made explicit. Adding this level of details helps to understand
+the specificities of coherence conditions.
 

### 2023-03-20 paper/paper.tex
Almost finished, let's read it again

@@
 First, $\fullframe[n]$ depends on all $X_i$ up to $n - 1$.
-So, we need to package up $X_i$, for $i < n$, into a nesting of $\Sigma$-type, which we abbreviate as $\X[][<n][]$.
+So, we need to package up $X_i$, for $i < n$, into a nesting of $\Sigma$-types, which we abbreviate as $\X[][<n][]$.
 This allows us to give the type $\X[][<n][] \rightarrow \U$ to $\fullframe[n]$.
@@
 The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and~\ref{tab:coh}.
-Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a coinductive limit of $n$-truncated $\nu$-sets.
+Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a stream representing the (coinductive) limit of $n$-truncated $\nu$-sets.
 The $n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.
-This is a nested $\Sigma$-type of which the $n$th component is a family over a $\fullframe$.
+In such stream, the $n$th component is a type dependent over a $\fullframe$.
 The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\painting$.
@@
 
-Since we have formalized the proof in the Coq proof assistant, which implements an intensional type theory, we now present the tables in \emph{intensional} type theory~\cite{martinlof84,coq22}, leaving implicit some details, which we will explain here, and other details, which we will explain in \ref{sec:mech}.
-
-Tables \ref{fulltab:coind}, \ref{fulltab:core}, and \ref{fulltab:frames} are unchanged, except that we make explicit all arguments, including those that can be inferred from the context.
+We now present the definition in \emph{intensional} type theory~\cite{martinlof84,coq22}, making explicit the need for transport along coherence proofs.
+
+Tables \ref{fulltab:coind}, \ref{fulltab:core}, and \ref{fulltab:frames} are the same as tables \ref{tab:coind}, \ref{tab:core}, and \ref{tab:frames}, except that, in function applications, so as to be more informative, we make explicit all arguments, including those that can be inferred from the context.
+
 The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit as shown in table~\ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.

### 2023-03-20 paper/paper.tex
Version of the response sent

@@
 As a result, our work can be seen as contributing the following: it characterizes, will full details, how to technically define parametricity iterated in arbitrary dimensions; %Second, it makes fully formal the relation between semi-simplicial and semi-cubical sets and parametricity.
-it provides with an alternative case study in the realm of indexed constructions of semi-simplicial and semi-cubical sets~\cite{voevodsky12,herbelin15,part15}, especially in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\cite{part15,shulman14,altenkirch16,kraus2017space}, as well as of better understanding the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}); it makes a step in the direction of the program initiated in~\cite{altenkirch15} to develop parametricity-based models of parametric type theory~\cite{bernardy15,nuyts17,cavallo19} and cubical type theory~\cite{bezem13,cohen16,angiuli21} which are closer from the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do (compare e.g.
-to the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally closed cartesian categories~\cite{curien14}).
+it provides a new example of indexed constructions of semi-simplicial and semi-cubical sets~\cite{voevodsky12,herbelin15,part15}, useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\cite{part15,shulman14,altenkirch16,kraus2017space}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}); it makes a step in the direction of the program initiated in~\cite{altenkirch15} to develop parametricity-based models of parametric type theory~\cite{bernardy15,nuyts17,cavallo19} and cubical type theory~\cite{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do (compare e.g.
+to the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\cite{curien14}).
 
@@
 We then proceed to explain the connection between the indexed representation and parametricity in \ref{sec:indexed-param}.
-Before spelling out the details of our formalization in type-theoretic language in \ref{sec:ett} and \ref{sec:itt}, we build up intuitions in \ref{sec:intuition}.
+Before spelling out the details of our formalization in type-theoretic language in \ref{sec:ett} and \ref{sec:itt}, we give intuitions in \ref{sec:intuition}.
 We end with some of the finer details of our mechanization in \ref{sec:mech}.
@@
 
-We give in this section a uniform definition of semi-simplicial and semi-cubical sets which we believe is folklore.
+In this section, we give a uniform definition of semi-simplicial and semi-cubical sets which we believe is folklore.
 The uniformity allows the definition of a notion of $\nu$-sets that subsumes semi-simplicial and semi-cubical sets.
@@
 The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and~\ref{tab:coh}.
-Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a stream representing the (coinductive) limit of $n$-truncated $\nu$-sets.
+Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a stream, coinductively representing the limit of $n$-truncated $\nu$-sets.
 The $n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.

### 2023-05-01 paper/paper.tex
paper: major restructuring

@@
 \section{Introduction}
+% - semisimplicial/semicubical sets in indexed form
+%   - clarify indexed/fibered, justify advantages of the respective choice
+%     - the presentation matters when expressed in indexed way!
+%   - compare to indexed VV, previous indexed HH, indexed Pang-Luo
+% - iterated unary/binary parametricity has a semi-simplicial/semi-cubical structure
+% - nu-types as a uniform definition of semi-simplicial/semi-cubical
+%   iterated parametricity gives an alternative presentation of indexed semi-simplicial/semi-cubical
+%   this is what we described in the paper
+% - perspective: models of cubical type theory using indexed cubical sets, hence preserving more definitial rules
+% - mention also the semi-simplicial types problem
+
 In the context of functional programming, Reynolds' parametricity~\cite{reynolds83} interprets types as relations characterizing the observational behavior of programs of this type.
@@
 \section{Semi-simplicial and semi-cubical sets\label{sec:nu}}
-
-In this section, we give a uniform definition of semi-simplicial and semi-cubical sets which we believe is folklore.
-The uniformity allows the definition of a notion of $\nu$-sets that subsumes semi-simplicial and semi-cubical sets.
-
-\subsection{Augmented semi-simplicial sets}
-Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``color''.
-Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over a singleton set of colors.
-
-Let us associate dimension $0$ to colors; then, points are dimension $1$, lines are dimension $2$, and so on.
-There is hence a shift by one when compared to semi-simplicial sets.
-We can then draw augmented semi-simplicial sets like semi-simplicial sets, except for this shift by one.
-
-While ordinary semi-simplicial sets are presheaves over the semi-simplex category, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus.
-There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that will later straightforwardly extend to semi-cubical sets.
-
-%% Notations
-% simplicial, augmented, where
-% Γ           Γ+         Augmented Simplicial Combinatorics through Category Theory
-%                        José Manuel García-Calcines, María Teresa Rivas-Rodríguez, Luis Javier Hernández-Paricio, 2022
-
-% semi-augmented, where
-% ∆_s        HOMOLOGY IN RELATIVE SEMI-ABELIAN CATEGORIES, JULIA GOEDECKE, 2011
-
-% simplicial, semi-simplicial, where
-% Δ           Δ_inj            SEMI-SIMPLICIAL SPACES, JOHANNES EBERT AND OSCAR RANDAL-WILLIAMS, 2018
-% Δ           Δ_inj            PhD, Josep Esquirol Esteve, 2019
-% Δ           Δ'               Strict n-categories and augmented directed complexes model homotopy types, Andrea Gagna, 2018
-% Δ           Δ_inj, Δ_{inj,aug} Ms Th. Jonas Dallend ̈orfer, 2019
-
-\begin{notation}[Finite sequences]
-  We denote finite sequences by $[i_1, \ldots i_n]$ for $i_j$ ranging over some domain.
-In particular, the empty sequence is written $[]$ and we define $i :: [j_1, \ldots, j_n]$ to be $[i, j_1, \ldots, j_n]$.
-\end{notation}
-
-\begin{definition}[$\DeltaPlus$]
-  \begin{figure*}[!t]
-    \begin{align*}
-      \Obj(\DeltaPlus) & := \Nat                                                                     \\
-      \Hom(p, n)       & := \{l \in [0, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}        \\
-      g \circ f        & :=
-      \begin{cases}
-        f                  & \text{if $g = []$}                                                        \\
-        0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
-        a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
-      \end{cases} \\
-      \id              & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom(n, n)$}
-    \end{align*}
-    \caption{Definition of \DeltaPlus}\label{fig:deltaplus}
-  \end{figure*}
-
-  The definition of $\DeltaPlus$ is shown in Fig.~\ref{fig:deltaplus}.
-Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$.
-It can be shown that composition is associative and that $\id$ is neutral.
-\end{definition}
-
-\begin{definition}[$\Set_{\DeltaPlus}$]
-  We define the category of augmented semi-simplicial sets as the functor category:
-  \begin{equation*}
-    \Set_{\DeltaPlus} := \Set^{\DeltaPlus^{\mathsf{op}}}
-  \end{equation*}
-\end{definition}
-
-To provide examples, we define the standard augmented $n$-semi-simplex.
-
-\begin{definition}[$\DeltaPlus^n$]
-  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as what is called the Yoneda embedding of $n \in \Obj(\DeltaPlus)$:
-  \begin{align*}
-    \DeltaPlus^n    & : \Set_{\DeltaPlus}        \\
-    \DeltaPlus^n(p) & := \Hom(p, n)              \\
-    \DeltaPlus^n(f) & := \lambda g .\, g \circ f
-  \end{align*}
-\end{definition}
-
-The standard augmented $0$-semi-simplex is a singleton made of one color (in our case black).
-Standard augmented $n$-semi-simplices for $n\geq 1$ have a geometric interpretation, and we illustrate them for dimensions $1$, $2$, and $3$.
-
-\begin{example}[$\DeltaPlus^1$]
-  The standard augmented $1$-semi-simplex can be pictured as a point, colored black, corresponding to the unique morphism in $\Hom(0, 1)$.
-This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$.
-  \begin{equation*}
-    \begin{tikzcd}
-      \kstar
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-\begin{example}[$\DeltaPlus^2$]
-  The standard augmented $2$-semi-simplex is drawn as two points, given by $\Hom(1, 2)$, along with a line connecting them, given by $\Hom(2, 2)$.
-We use the color black to denote the unique morphisms in $\Hom(0, 1)$ and $\Hom(0, 2)$.
-  \begin{equation*}
-    \begin{tikzcd}
-      \kstar0 \arrow[r, dash, "\kstar\kstar"] & 0\kstar
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-\begin{example}[$\DeltaPlus^3$]
-  $\DeltaPlus^3$ is drawn as three points, given by $\Hom(1, 3)$, three lines connecting them, given by $\Hom(2, 3)$, and a triangular filler given by $\Hom(3, 3)$.
-  \begin{equation*}
-    \begin{tikzcd}
-      & |[alias=F]|00\kstar \arrow[ddr, dash, "0\kstar\kstar"] & \\\\
-      \kstar00 \arrow[rr, dash, "\kstar\kstar0"{name=T, below}]\arrow[uur, dash, "\kstar0\kstar"] && 0\kstar0 \\
-      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar\kstar" description]
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base and gluing on top of it another copy lifted by one dimension.
-In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.
-In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by~$\kstar$.
-Note that the components may be oriented by letting each $n$-dimensional component point to the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ of the $n$-dimensional component with $0$.
-
-\subsection{Semi-cubical sets}
-Semi-cubical sets are defined like augmented semi-simplicial sets except that $\DeltaPlus$ is replaced by $\Cube$ in which we take sequences of $L$, $R$ and $\star$, instead of sequences of $0$ and $\kstar$.
-They represent ordinary semi-cubical sets, with faces (and no augmentation).
-
-\begin{definition}[\Cube]
-  The definition of $\Cube$ is shown in Fig.~\ref{fig:cube}. The symbols $L$ and $R$ indicate opposite faces of a cube.
-  \begin{figure*}[!t]
-    \begin{align*}
-      \Obj(\Cube) & := \Nat                                                                                \\
-      \Hom(p, n)  & := \{l \in [L, R, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}                \\
-      g \circ f   & :=
-      \begin{cases}
-        f                  & \text{if $g = []$}                                                              \\
-        a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a = L$ or $R$}                          \\
-        a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = L$, $R$, or $\kstar$} \\
-      \end{cases} \\
-      \id         & := [\kstar, \ldots, \kstar] \text{ $n$ times}
-    \end{align*}
-    \caption{Definition of \Cube}\label{fig:cube}
-  \end{figure*}
-
-  Again, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
-\end{definition}
-
-\begin{definition}[\CSet]
-  We define the category of semi-cubical sets as the functor category:
-  \begin{equation*}
-    \CSet := \Set^{\op{\Cube}}
-  \end{equation*}
-\end{definition}
-
-\begin{definition}[$\Cube^n$]
-  The standard semi-cube $\Cube^n$ is defined as the Yoneda embedding of $n \in \Obj(\Cube)$:
-  \begin{align*}
-    \Cube^n    & : \CSet                    \\
-    \Cube^n(p) & := \Hom(p, n)              \\
-    \Cube^n(f) & := \lambda g .\, g \circ f
-  \end{align*}
-\end{definition}
-
-Standard $n$-semi-cubes have a geometric interpretation, which we illustrate for dimensions $0$, $1$, and $2$.
-
-\begin{example}[$\Cube^0$]
-  $\Cube^0$ is $\Hom(0, 0)$, or the singleton set of the empty sequence:
-  \begin{equation*}
-    \begin{tikzcd}
-      \{\}
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-\begin{example}[$\Cube^1$]
-  $\Cube^1$ consists of two points, given by $\Hom(0, 1)$ and a line, given by $\Hom(1, 1)$.
-  \begin{equation*}
-    \begin{tikzcd}
-      L \arrow[r, "\kstar", dash] & R
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-\begin{example}[$\Cube^2$]
-  $\Cube^2$ consists of four points, given by $\Hom(0, 2)$, four lines connecting the four points, given by $\Hom(1, 2)$, and a filler, given by $\Hom(2, 2)$:
-  \begin{equation*}
-    \begin{tikzcd}
-      LR \arrow[r, dash, "\kstar R"{name=F}] \arrow[d, dash, "L\kstar" left] & RR \arrow[d, dash, "R\kstar"] \\
-      LL \arrow[r, dash, "\kstar L"{name=T, below}] & RL \\
-      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar" description]
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-More generally, the standard $(n + 1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them on their border by a cylinder obtained as a third copy stretched in the new dimension.
-The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$.
-Note that the components can this time be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$ to the one obtained by replacing the leftmost $\kstar$ with $R$.
-
-\subsection{Generalization to \texorpdfstring{$\nu$}{ν}-sets}
+In this section, we generalize semi-simplicial and semi-cubical sets to, what we call, $\nu$-sets, subsuming the earlier defintions.
+However, we also explicitly work out the cases of semi-simplical and semi-cubical sets, in a way that is similar to a previous art~\cite{aitchison86}.
+
+\subsection{\texorpdfstring{$\nu$}{ν}-sets}
 Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets.
@@
 
-\section{Indexed representation and parametricity\label{sec:indexed-param}}
-In this section, we introduce some preliminaries on interpreting sets in type theory, followed by a small section on the indexed presentation, before relating it to parametricity in \ref{sec:rel-param}.
-
-\subsection{Preliminaries}
+\subsection{Augmented semi-simplicial sets}
+Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``color''.
+Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over a singleton set of colors.
+
+Let us associate dimension $0$ to colors; then, points are dimension $1$, lines are dimension $2$, and so on.
+There is hence a shift by one when compared to semi-simplicial sets.
+We can then draw augmented semi-simplicial sets like semi-simplicial sets, except for this shift by one.
+
+While ordinary semi-simplicial sets are presheaves over the semi-simplex category, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus.
+There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that will later straightforwardly extend to semi-cubical sets.
+
+%% Notations
+% simplicial, augmented, where
+% Γ           Γ+         Augmented Simplicial Combinatorics through Category Theory
+%                        José Manuel García-Calcines, María Teresa Rivas-Rodríguez, Luis Javier Hernández-Paricio, 2022
+
+% semi-augmented, where
+% ∆_s        HOMOLOGY IN RELATIVE SEMI-ABELIAN CATEGORIES, JULIA GOEDECKE, 2011
+
+% simplicial, semi-simplicial, where
+% Δ           Δ_inj            SEMI-SIMPLICIAL SPACES, JOHANNES EBERT AND OSCAR RANDAL-WILLIAMS, 2018
+% Δ           Δ_inj            PhD, Josep Esquirol Esteve, 2019
+% Δ           Δ'               Strict n-categories and augmented directed complexes model homotopy types, Andrea Gagna, 2018
+% Δ           Δ_inj, Δ_{inj,aug} Ms Th. Jonas Dallend ̈orfer, 2019
+
+\begin{notation}[Finite sequences]
+  We denote finite sequences by $[i_1, \ldots i_n]$ for $i_j$ ranging over some domain.
+In particular, the empty sequence is written $[]$ and we define $i :: [j_1, \ldots, j_n]$ to be $[i, j_1, \ldots, j_n]$.
+\end{notation}
+
+\begin{definition}[$\DeltaPlus$]
+  \begin{figure*}[!t]
+    \begin{align*}
+      \Obj(\DeltaPlus) & := \Nat                                                                     \\
+      \Hom(p, n)       & := \{l \in [0, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}        \\
+      g \circ f        & :=
+      \begin{cases}
+        f                  & \text{if $g = []$}                                                        \\
+        0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
+        a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
+      \end{cases} \\
+      \id              & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom(n, n)$}
+    \end{align*}
+    \caption{Definition of \DeltaPlus}\label{fig:deltaplus}
+  \end{figure*}
+
+  The definition of $\DeltaPlus$ is shown in Fig.~\ref{fig:deltaplus}.
+Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$.
+It can be shown that composition is associative and that $\id$ is neutral.
+\end{definition}
+
+\begin{definition}[$\Set_{\DeltaPlus}$]
+  We define the category of augmented semi-simplicial sets as the functor category:
+  \begin{equation*}
+    \Set_{\DeltaPlus} := \Set^{\DeltaPlus^{\mathsf{op}}}
+  \end{equation*}
+\end{definition}
+
+To provide examples, we define the standard augmented $n$-semi-simplex.
+
+\begin{definition}[$\DeltaPlus^n$]
+  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as what is called the Yoneda embedding of $n \in \Obj(\DeltaPlus)$:
+  \begin{align*}
+    \DeltaPlus^n    & : \Set_{\DeltaPlus}        \\
+    \DeltaPlus^n(p) & := \Hom(p, n)              \\
+    \DeltaPlus^n(f) & := \lambda g .\, g \circ f
+  \end{align*}
+\end{definition}
+
+The standard augmented $0$-semi-simplex is a singleton made of one color (in our case black).
+Standard augmented $n$-semi-simplices for $n\geq 1$ have a geometric interpretation, and we illustrate them for dimensions $1$, $2$, and $3$.
+
+\begin{example}[$\DeltaPlus^1$]
+  The standard augmented $1$-semi-simplex can be pictured as a point, colored black, corresponding to the unique morphism in $\Hom(0, 1)$.
+This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$.
+  \begin{equation*}
+    \begin{tikzcd}
+      \kstar
+    \end{tikzcd}
+  \end{equation*}
+\end{example}
+
+\begin{example}[$\DeltaPlus^2$]
+  The standard augmented $2$-semi-simplex is drawn as two points, given by $\Hom(1, 2)$, along with a line connecting them, given by $\Hom(2, 2)$.
+We use the color black to denote the unique morphisms in $\Hom(0, 1)$ and $\Hom(0, 2)$.
+  \begin{equation*}
+    \begin{tikzcd}
+      \kstar0 \arrow[r, dash, "\kstar\kstar"] & 0\kstar
+    \end{tikzcd}
+  \end{equation*}
+\end{example}
+
+\begin{example}[$\DeltaPlus^3$]
+  $\DeltaPlus^3$ is drawn as three points, given by $\Hom(1, 3)$, three lines connecting them, given by $\Hom(2, 3)$, and a triangular filler given by $\Hom(3, 3)$.
+  \begin{equation*}
+    \begin{tikzcd}
+      & |[alias=F]|00\kstar \arrow[ddr, dash, "0\kstar\kstar"] & \\\\
+      \kstar00 \arrow[rr, dash, "\kstar\kstar0"{name=T, below}]\arrow[uur, dash, "\kstar0\kstar"] && 0\kstar0 \\
+      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar\kstar" description]
+    \end{tikzcd}
+  \end{equation*}
+\end{example}
+
+More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base and gluing on top of it another copy lifted by one dimension.
+In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.
+In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by~$\kstar$.
+Note that the components may be oriented by letting each $n$-dimensional component point to the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ of the $n$-dimensional component with $0$.
+
+\subsection{Semi-cubical sets}
+Semi-cubical sets are defined like augmented semi-simplicial sets except that $\DeltaPlus$ is replaced by $\Cube$ in which we take sequences of $L$, $R$ and $\star$, instead of sequences of $0$ and $\kstar$.
+They represent ordinary semi-cubical sets, with faces (and no augmentation).
+
+\begin{definition}[\Cube]
+  The definition of $\Cube$ is shown in Fig.~\ref{fig:cube}. The symbols $L$ and $R$ indicate opposite faces of a cube.
+  \begin{figure*}[!t]
+    \begin{align*}
+      \Obj(\Cube) & := \Nat                                                                                \\
+      \Hom(p, n)  & := \{l \in [L, R, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}                \\
+      g \circ f   & :=
+      \begin{cases}
+        f                  & \text{if $g = []$}                                                              \\
+        a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a = L$ or $R$}                          \\
+        a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = L$, $R$, or $\kstar$} \\
+      \end{cases} \\
+      \id         & := [\kstar, \ldots, \kstar] \text{ $n$ times}
+    \end{align*}
+    \caption{Definition of \Cube}\label{fig:cube}
+  \end{figure*}
+
+  Again, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
+\end{definition}
+
+\begin{definition}[\CSet]
+  We define the category of semi-cubical sets as the functor category:
+  \begin{equation*}
+    \CSet := \Set^{\op{\Cube}}
+  \end{equation*}
+\end{definition}
+
+\begin{definition}[$\Cube^n$]
+  The standard semi-cube $\Cube^n$ is defined as the Yoneda embedding of $n \in \Obj(\Cube)$:
+  \begin{align*}
+    \Cube^n    & : \CSet                    \\
+    \Cube^n(p) & := \Hom(p, n)              \\
+    \Cube^n(f) & := \lambda g .\, g \circ f
+  \end{align*}
+\end{definition}
+
+Standard $n$-semi-cubes have a geometric interpretation, which we illustrate for dimensions $0$, $1$, and $2$.
+
+\begin{example}[$\Cube^0$]
+  $\Cube^0$ is $\Hom(0, 0)$, or the singleton set of the empty sequence:
+  \begin{equation*}
+    \begin{tikzcd}
+      \{\}
+    \end{tikzcd}
+  \end{equation*}
+\end{example}
+
+\begin{example}[$\Cube^1$]
+  $\Cube^1$ consists of two points, given by $\Hom(0, 1)$ and a line, given by $\Hom(1, 1)$.
+  \begin{equation*}
+    \begin{tikzcd}
+      L \arrow[r, "\kstar", dash] & R
+    \end{tikzcd}
+  \end{equation*}
+\end{example}
+
+\begin{example}[$\Cube^2$]
+  $\Cube^2$ consists of four points, given by $\Hom(0, 2)$, four lines connecting the four points, given by $\Hom(1, 2)$, and a filler, given by $\Hom(2, 2)$:
+  \begin{equation*}
+    \begin{tikzcd}
+      LR \arrow[r, dash, "\kstar R"{name=F}] \arrow[d, dash, "L\kstar" left] & RR \arrow[d, dash, "R\kstar"] \\
+      LL \arrow[r, dash, "\kstar L"{name=T, below}] & RL \\
+      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar" description]
+    \end{tikzcd}
+  \end{equation*}
+\end{example}
+
+More generally, the standard $(n + 1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them on their border by a cylinder obtained as a third copy stretched in the new dimension.
+The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$.
+Note that the components can this time be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$ to the one obtained by replacing the leftmost $\kstar$ with $R$.
+
+\section{Preliminaries}
 Martin-Löf's Type theory~\cite{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
@@
 
-\subsection{Fibered versus indexed representation}
+\section{Comparison of fibered and indexed presentations}
+%     - standard augmented triangle:
+%       Inductive points := A | B | C.
+%       Inductive lines := AB | BC | AC.
+%       Inductive surface := ABC.
+
+%       {X n := match n with 0 => unit | 1 => points | 2 => lines | 4 => surface | n => empty_set;
+%        d {n} i (Hi:i<n) (x:X n) := match n, i, x with
+%        | 0, _, _ => assert false
+%        | 1, _, _ => tt
+%        | 2, 0, AB => B
+%        | 2, 1, AB => A
+%        | 2, 0, BC => C
+%        | 2, 1, BC => B
+%        | 2, 0, AC => C
+%        | 2, 1, AC => A
+%        | 3, 0, ABC => BC
+%        | 3, 1, ABC => AC
+%        | 3, 2, ABC => AB
+%        | n.+4, i, _ => assert false
+%        end;
+%        alpha n i j (Hi:i<n) (Hj:j<i) (x : X n) : d i Hi (d j _ x) = d (j-1) _ (d i _ x)
+%        := match n, i, j, x with
+%        | 0, _, _, _ => assert false
+%        | 1, _, _, _ => assert false
+%        | 2, _, _, _ => proof_irrelevance_of_unit : tt = tt
+%        | 3, 1, 0, ABC => proof_irrelevance_in_points : C = C
+%        | 3, 2, 0, ABC => proof_irrelevance_in_points : B = B
+%        | 3, 2, 1, ABC => proof_irrelevance_in_points : A = A
+%        | n.+4, i, _ => assert false
+%        end
+%        }
+%        {hd tt := unit;
+%         tl := {hd _ (* (tt;tt) *) := points; (* 3 points *)
+%                tl := {hd _ (* ((tt;(tt;a));b) *) := unit; (* unique line over any a and any b *)
+%                       tl := {hd _ (* ((tt;(tt;(a;(b;tt))));((c;tt);tt)) *) := unit; (* unique triangle over ab, bc, and ac *)
+%                              tl := cofix s := {hd _ := empty_set; tl := s}}}}}
+%        {hd _ := unit; tl :=
+%        {hd _ := points; tl :=
+%        {hd _ := unit; tl :=
+%        {hd _ := unit; tl := cofix s := {hd _ := empty_set; tl := s}}}}} : AugmentedSemiSimplicial
+
+%        standard n : AugmentedSemiSimplicial
+%        := {hd _ := unit; tl :=
+%           {hd _ := [0;n]; tl :=
+%            unit unit unit ... n times ... unit; empty_set; ... }}
 There are different ways to represent a family of sets, commonly known as the fibered and indexed representations. In type theory, they are equivalent, and this equivalence can be formulated as:
@@
 \end{align*}
-
-\subsection{Relating to parametricity\label{sec:rel-param}}
+\section{Relating to parametricity\label{sec:rel-param}}
 The process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$ in the last section, is similar to applying a binary parametricity translation and expecting the resulting translation to be inhabited.
@@
 
+\subsection{Formal construction in ETT\label{sec:ett}}
+% Abbreviated tables in this section
+%
+% The rule for implicit arguments for each table:
+% show 1 explicit in first two parts
+% show E + 1 explicit in the third part
+\appendmask[bonak]{layer}[D]
+\appendmask[bonak]{painting}[D]
+\appendmask[bonak]{restrframe}[D]
+\appendmask[bonak]{restrlayer}[D, d]
+\appendmask[bonak]{restrpainting}[D, d]
+\appendmask[bonak]{cohframe}[D]
+\appendmask[bonak]{cohlayer}[D, d]
+\appendmask[bonak]{cohpainting}[D, d]
+
+% Now, we write the type theory bit, and input the abbreviated tables
+
+% Truncated sets, otherwise referred to as X
+% Keep all arguments
+\newcommandx{\Xp}[1]{\X[#1][][]}
+\newcommandx{\Xto}[3][3=]{\X[#1][<#2][#3]}
+\newcommandx{\Xcomp}[3][3=]{\X[#1][=#2][#3]}
+\newcommandx{\Xfrom}[3][3=]{\X[#1][\geq#2][#3]}
+
+% Frame, layer, and painting
+% Drop the universe letter
+\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
+\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
+\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
+
+% Restriction for frame, layer, and painting
+% Drop the universe letter
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
+
+% Coherence conditions for frame, layer, and painting
+% Keep only ε, ω; n, p; proposition on n and p
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][][][][][#9]}
+
+We now present the construction in \emph{extensional} type theory; i.e.
+in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
+\begin{equation*}
+  \seqr{}{\Gamma \vdash p: t = u}{\Gamma \vdash t \equiv u}
+\end{equation*}
+
+For the presentation corresponding to the formalization in \emph{intensional} type theory, see \ref{sec:itt}.
+
+The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and~\ref{tab:coh}.
+Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a stream, coinductively representing the limit of $n$-truncated $\nu$-sets.
+The $n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.
+In such stream, the $n$th component is a type dependent over a $\fullframe$.
+The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\painting$.
+The type $\layer$ and $\painting$ are dependent over $\restrf$, and these restrictions are defined on \ref{tab:faces}.
+These restrictions are defined using auxiliary definitions of $\restrl$ and $\restrc$.
+
+Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$.
+This commutation is not provable by computation so we have to prove it propositionally before using the reflection rule.
+Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\painting$.
+This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$.
+Even though it looks independent of the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
+More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be mutually defined by induction on $p$.
+Also, each of $\painting$, $\restrc$, and $\cohc$ is built by induction from $p$ to $n$.
+The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but, the converse dependency is only on lower $n$, so this is well-founded.
+Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
+We leave however implicit the exact way this mutual recursion can be formalized at this stage of the paper.
+
+Most components of the construction takes inequality constraints as parameters, and we have left implicit that they are satisfied in the tables.
+Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, only assuming that we can pick a definition for which proofs of $m \leq n$ are provably unique and thus definitionally equal by the reflection rule.
+
+The construction takes benefit of various provable equalities over proofs of equality being definitional by the reflection rule.
+This includes in particular the groupoid properties of equality.
+Notably, uniqueness of identity proofs holds in extensional type theory, so that any type is automatically an $\U$.
+Also, we left implicit in table~\ref{tab:coh} the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
+(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type.
+In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is function extensionality, holds by default in extensional type theory.
+
+Note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning them anymore.
+For instance, it produces Fig.~\ref{fig:intuition} for $n=2$ and $\nu=2$.
+
+\renewcommand*{\lab}{tab:coind}
+\input{tab-coind.tex}
+
+% For just the second table, keep the universe letter in fullframe
+\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
+
+\renewcommand*{\lab}{tab:core}
+\input{tab-core.tex}
+
+% Drop the universe letter in fullframe for all remaining tables
+\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
+\renewcommand*{\lab}{tab:frames}
+\input{tab-frames.tex}
+
+% Truncated sets, otherwise referred to as X
+% Drop the universe letter for the third and fourth tables
+\renewcommandx{\Xto}[3][3]{\X[][<#2][#3]}
+\renewcommandx{\Xcomp}[3][3]{\X[][=#2][#3]}
+\renewcommandx{\Xfrom}[3][3]{\X[][\geq#2][#3]}
+
+% Hack to remove , in \cohf
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
+
+% The third table mentions cohframe; keep ε, ω in this instance
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
+
+\renewcommand*{\lab}{tab:faces}
+\input{tab-faces-ett.tex}
+
+% Restriction for frame, layer, and painting
+% Drop just the universe letter for the coh table
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
+
+% Frame, layer, and painting
+% Drop all arguments for coh table; they're not present in coind table.
+\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][][][][#5]}
+\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][][][][#5]}
+\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][][][][#5]}
+
+% Hack to remove , in \cohf
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
+
+% Coherence conditions for frame, layer, and painting
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
+
+\renewcommand*{\lab}{tab:coh}
+\input{tab-coh-ett.tex}
+
 \subsection{Intuition for our formal construction\label{sec:intuition}}
@@
 
-\subsection{Formal construction in ETT\label{sec:ett}}
-% Abbreviated tables in this section
-%
-% The rule for implicit arguments for each table:
-% show 1 explicit in first two parts
-% show E + 1 explicit in the third part
-\appendmask[bonak]{layer}[D]
-\appendmask[bonak]{painting}[D]
-\appendmask[bonak]{restrframe}[D]
-\appendmask[bonak]{restrlayer}[D, d]
-\appendmask[bonak]{restrpainting}[D, d]
-\appendmask[bonak]{cohframe}[D]
-\appendmask[bonak]{cohlayer}[D, d]
-\appendmask[bonak]{cohpainting}[D, d]
-
-% Now, we write the type theory bit, and input the abbreviated tables
-
-% Truncated sets, otherwise referred to as X
-% Keep all arguments
-\newcommandx{\Xp}[1]{\X[#1][][]}
-\newcommandx{\Xto}[3][3=]{\X[#1][<#2][#3]}
-\newcommandx{\Xcomp}[3][3=]{\X[#1][=#2][#3]}
-\newcommandx{\Xfrom}[3][3=]{\X[#1][\geq#2][#3]}
-
-% Frame, layer, and painting
-% Drop the universe letter
-\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
-\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
-\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
-
-% Restriction for frame, layer, and painting
-% Drop the universe letter
-\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
-
-% Coherence conditions for frame, layer, and painting
-% Keep only ε, ω; n, p; proposition on n and p
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
-\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][][][][][#9]}
-
-We now present the construction in \emph{extensional} type theory; i.e.
-in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
-\begin{equation*}
-  \seqr{}{\Gamma \vdash p: t = u}{\Gamma \vdash t \equiv u}
-\end{equation*}
-
-For the presentation corresponding to the formalization in \emph{intensional} type theory, see \ref{sec:itt}.
-
-The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and~\ref{tab:coh}.
-Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a stream, coinductively representing the limit of $n$-truncated $\nu$-sets.
-The $n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.
-In such stream, the $n$th component is a type dependent over a $\fullframe$.
-The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\painting$.
-The type $\layer$ and $\painting$ are dependent over $\restrf$, and these restrictions are defined on \ref{tab:faces}.
-These restrictions are defined using auxiliary definitions of $\restrl$ and $\restrc$.
-
-Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$.
-This commutation is not provable by computation so we have to prove it propositionally before using the reflection rule.
-Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\painting$.
-This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$.
-Even though it looks independent of the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
-More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be mutually defined by induction on $p$.
-Also, each of $\painting$, $\restrc$, and $\cohc$ is built by induction from $p$ to $n$.
-The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but, the converse dependency is only on lower $n$, so this is well-founded.
-Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
-We leave however implicit the exact way this mutual recursion can be formalized at this stage of the paper.
-
-Most components of the construction takes inequality constraints as parameters, and we have left implicit that they are satisfied in the tables.
-Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, only assuming that we can pick a definition for which proofs of $m \leq n$ are provably unique and thus definitionally equal by the reflection rule.
-
-The construction takes benefit of various provable equalities over proofs of equality being definitional by the reflection rule.
-This includes in particular the groupoid properties of equality.
-Notably, uniqueness of identity proofs holds in extensional type theory, so that any type is automatically an $\U$.
-Also, we left implicit in table~\ref{tab:coh} the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
-(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type.
-In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is function extensionality, holds by default in extensional type theory.
-
-Note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning them anymore.
-For instance, it produces Fig.~\ref{fig:intuition} for $n=2$ and $\nu=2$.
-
-\renewcommand*{\lab}{tab:coind}
-\input{tab-coind.tex}
-
-% For just the second table, keep the universe letter in fullframe
-\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
-
-\renewcommand*{\lab}{tab:core}
-\input{tab-core.tex}
-
-% Drop the universe letter in fullframe for all remaining tables
-\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
-\renewcommand*{\lab}{tab:frames}
-\input{tab-frames.tex}
-
-% Truncated sets, otherwise referred to as X
-% Drop the universe letter for the third and fourth tables
-\renewcommandx{\Xto}[3][3]{\X[][<#2][#3]}
-\renewcommandx{\Xcomp}[3][3]{\X[][=#2][#3]}
-\renewcommandx{\Xfrom}[3][3]{\X[][\geq#2][#3]}
-
-% Hack to remove , in \cohf
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
-
-% The third table mentions cohframe; keep ε, ω in this instance
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
-
-\renewcommand*{\lab}{tab:faces}
-\input{tab-faces-ett.tex}
-
-% Restriction for frame, layer, and painting
-% Drop just the universe letter for the coh table
-\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
-
-% Frame, layer, and painting
-% Drop all arguments for coh table; they're not present in coind table.
-\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][][][][#5]}
-\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][][][][#5]}
-\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][][][][#5]}
-
-% Hack to remove , in \cohf
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
-
-% Coherence conditions for frame, layer, and painting
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
-
-\renewcommand*{\lab}{tab:coh}
-\input{tab-coh-ett.tex}
-
+\section{Details on the mechanization\label{sec:mech}}
 \subsection{Formal construction in ITT\label{sec:itt}}
@@
 
-\subsection{Details on the mechanization\label{sec:mech}}
+\subsection{Finer details}
 \renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}

### 2023-05-07 paper/paper.tex
paper: change to MSCS class; rewrite introduction

@@
-%% -*- latex-command: pdflatex -shell-escape -*-
-\documentclass[10pt]{art.cls/art}
-
-\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, multicol, rotating, flushend}
-
-\makeatletter
-\@namedef{ver@lineno.sty}{9999/12/31}
-\@namedef{opt@lineno.sty}{}
-\makeatother
-\usepackage{minted}
+\documentclass{msc}
+
+\usepackage{amsmath, amssymb, mathrsfs, url, bookmark, tikz, tikz-cd, mathpazo, enumitem, xargs, multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, colortbl, pdflscape, flushend, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
 
@@
 \newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
-\newcommand{\Cube}{\ensuremath{\boldsymbol{\square}}}
-\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
+\newcommand{\Cube}{\ensuremath{\boldsymbol{{\Box}}}}
+\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\Box}}}}
 
@@
 \newcommand{\SProp}{\ensuremath{\mathsf{\color{spanish-blue}{SProp}}}}
+
+% Examples
+\newtheorem{example}[therm]{Example}
 
@@
 
-% The eqntable environment, displaying the various
+% The eqntable environment
 \newcolumntype{Y}{>{\centering\arraybackslash}X}
-\NewEnviron{onecoltbl}[1]{
+\NewEnviron{eqntable}[1]{
   \begin{table}[H]
     \small
-    \begin{tabularx}{\linewidth}{@{}>{$}l<{$} >{$}c<{$} >{$}c<{$} >{$}Y<{$} @{}}
+    \begin{tabularx}{\linewidth}{
+      @{}
+      >{$}l<{$}
+      >{$}c<{$}
+      >{$}c<{$}
+      >{$}Y<{$}
+      @{}}
       \toprule
@@
   \end{table}
-}
-
-\NewEnviron{eqntable}[1]{
-  \begin{table*}[!t]
-    \small
-    \begin{tabularx}{\linewidth}{@{}>{$}l<{$} >{$}c<{$} >{$}c<{$} >{$}Y<{$} @{}}
-      \toprule
-      \BODY
-      \bottomrule
-    \end{tabularx}
-    \caption{#1}
-  \end{table*}
 }
@@
 
+% Use lettered footnotes
+\renewcommand{\thefootnote}{\alph{footnote}}
+
+\begin{document}
 \title{A parametricity-based formalization of semi-simplicial and semi-cubical sets}
-\author{\IEEEauthorblockN{Hugo Herbelin \\ and Ramkumar Ramachandra}\\\IEEEauthorblockA{Université Paris Cité, Inria, CNRS, IRIF, Paris\\\texttt{Hugo.Herbelin@inria.fr} and \texttt{r@artagnon.com}}}
-
-\begin{document}
-\maketitle
+\begin{authgrp}
+  \author{Hugo Herbelin}
+  \affiliation{Université Paris Cité, Inria, CNRS, IRIF, Paris
+    \email{Hugo.Herbelin@inria.fr}}
+\end{authgrp}
 \begin{abstract}
@@
 
-  This paper describes a uniform indexed characterization of both augmented semi-simplicial and semi-cubical sets arising respectively as unary and binary iterated parametricity-based constructions.
-
-  Additionally, our construction is fully formalized in Coq's dependent type theory.
+  On another side, it is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds's parametricity, respectively in its unary and binary variants\dots
+
+  We exploit this correspondence to develop a uniform indexed definition of both augmented semi-simplicial and semi-cubical sets, which is additionally fully formalized in Coq's dependent type theory.
+Beside the interest in the construction itself, we expect it to eventually serve as models of type theory preserving more definitional equalities than presheaf models do.
 \end{abstract}
@@
 
+\subsection{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
+
+A dependent set can be represented in two ways: as a family indexed over a set or as a set together with a map telling for each element on which index it depends on.
+In the latter case, the set associated to a given index is the fiber (i.e.
+the inverse image) of this index under the map.
+The two presentations are equivalent, what can be formally stated as what we call the fibered/indexed correspondence\footnote{At a discussion on the Zulip discussion channel for the HoTT community, alternative names fibration/family and unbundled/bundled were proposed, among others.
+In our experience, the opposition fibered/indexed is intuitively understood by many speakers.
+In particular, it echoes to the Grothendieck construction of fibered categories from indexed categories, so that some people also calls this correspondence the Grothendieck construction for dummies}:
+$$(\Sigma S: \U. (S \rightarrow T)) \simeq (T \rightarrow \U)$$
+
+While a presheaf, i.e.
+a family of sets with maps between them according to an index category, can be seen as living on the indexed side of the correspondence, with discrete fibration on the other side of the correspondence, there are situations where the presheaf can be seen as living on the fibered side of the correspondence.
+Indeed, when the index category of the presheaf is direct, i.e.
+with a well-founded collection of morphisms, as is the case of semi-simplicial and semi-cubical sets, each set serving as domain of a map can be turned into a family dependent, i.e.
+indexed, on the codomain of the map, and, since the collection of maps is well-founded, this can be iterated, eventually producing a collection of families which we call the indexed presentation of the presheaf over a direct category\dots
+
+For instance, in the case of a semi-cubical set, presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes, the presheaf approach corresponds to a family of sets fibered the ones over the others as follows (up to some coherence conditions):
+
+\begin{equation*}
+  \begin{tikzcd}
+    X_0: \U & X_1: \U \arrow[l, "\delta^L" description, shift left=2] \arrow[l, "\delta^R" description, shift right=2] & X_2: \U \arrow[l, "\delta^{L\kstar}" description, shift left=6] \arrow[l, "\delta^{R\kstar}" description, shift left=2] \arrow[l, "\delta^{\kstar L}" description, shift right=2] \arrow[l, "\delta^{\kstar R}" description, shift right=6] & \ldots
+  \end{tikzcd}
+\end{equation*}
+
+On the other side, the indexed presentation of the same presheaf is a stratified sequence of families recursively indexed on elements of families of lower rank, taking into account the coherence conditions to prevent duplications:
+\begin{align*}
+  X_0                                                                                      & \mbox{ a set of points}                                       \\
+  (X_1)_{a,b\in X_0}                                                                       & \mbox{ a set of lines between any two points}                 \\
+  (X_2)_{a,b,c,d\in X_0,p\in (X_1)_{ab},q\in (X_1)_{bc},r \in (X_1)_{ac}, s\in (X_1)_{cd}} & \mbox{ a set of squares over any 4 lines lying over 4 points} \\
+  \ldots
+\end{align*}
+
+The idea for such indexed presentation of presheaves over a direct category was introduced at the Univalent Foundations year in the context of defining semi-simplicial types~\cite{...}.
+A couple of constructions were proposed since then.
+One, by Voevodsky, relies on the presentation of semi-simplicial sets as a presheaf over injective monotone finite maps (see \cite[Section]{Herbelin14} for a presentation).
+Another, by the first author, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps~\cite{Herbelin14}.
+Another one by Park and Luo, and formalized in Plastic, works generically for any Reedy category with only upwards maps~\cite{ParkLuo}.
+
+The indexed definition of a presheaf over a direct category is technically more involvedthanthepresheafdefinition as it requires hard-wiringinthestructurethe dependencies betweenelements of the sets of the presheaf, including the coherence condition between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex is the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
+On the other side, defining a concrete presheaf in indexedform only requires to provide the family since the burden of defining maps and showing the coherence conditions over them is has already been integrate what is not the case in the presheaf presentation.
+
+\subsection{Reynolds' parametricity and its unary and binary variants}
+
 In the context of functional programming, Reynolds' parametricity~\cite{reynolds83} interprets types as relations characterizing the observational behavior of programs of this type.
@@
 It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch}.
+
+\subsection{Iterated-parametricity-based constructio}
 
@@
 \begin{definition}[$\DeltaPlus$]
-  \begin{figure*}[!t]
+  \begin{figure}[H]
     \begin{align*}
@@
     \caption{Definition of \DeltaPlus}\label{fig:deltaplus}
-  \end{figure*}
+  \end{figure}
 
@@
   The definition of $\Cube$ is shown in Fig.~\ref{fig:cube}. The symbols $L$ and $R$ indicate opposite faces of a cube.
-  \begin{figure*}[!t]
+  \begin{figure}[H]
     \begin{align*}
@@
     \caption{Definition of \Cube}\label{fig:cube}
-  \end{figure*}
+  \end{figure}
 
@@
 
-\begin{figure*}[!t]
+\begin{figure}[H]
   \begin{equation*}
@@
   \caption{Intuition for formal construction ($\nu = 2$)}\label{fig:intuition}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[!t]
+\begin{figure}[H]
   \begin{align*}
@@
   \caption{Refinement of definition of $\framep$ and $\painting$\label{fig:refinement}}
-\end{figure*}
+\end{figure}
 
@@
 \input{tab-frames.tex}
-
-\begin{sidewaystable*}
 \renewcommand*{\lab}{fulltab:faces}
 \input{tab-faces.tex}
-  \vspace{5em}
+
+\begin{landscape}
   \renewcommand*{\lab}{fulltab:coh}
   \input{tab-coh.tex}
-\end{sidewaystable*}
+\end{landscape}
 
@@
 
-\bibliographystyle{IEEEtran}
+Another direction for future work would also be to generically construct the indexed form of any presentation of presheaves over a direct category and to show the equivalence between the two presentations.
+\bibliographystyle{msclike}
 \bibliography{paper}

### 2023-05-07 paper/paper.tex
Intro, continued

--- 2023-05-01 paper/paper.tex
@@
 
+\subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
+
+A family of sets can commonly be represented in two ways: as a family indexed over a set properly speaking or as a set together with a map telling for each element of the set on which index it depends on.
+In the latter case, the set associated to a given index is the fiber, i.e.
+inverse image, of the index under the map.
+The two presentations are equivalent, what can be formally stated in a type-theoretic language as a fibered/indexed correspondence\footnote{At a discussion on the Zulip channel for the HoTT community, alternative names fibration/family correspondence and unbundled/bundled correspondence were proposed, among others.
+In our experience, the opposition fibered/indexed is spontaneously understood by many listeners.
+In particular, it echoes to the Grothendieck construction of fibered categories from indexed categories.
+Some people actually calls this correspondence ``the Grothendieck construction for dummies''.
+Its proof requires univalence (see~\cite{hottbook}).}:
+$$(\Sigma S: \U. (S \rightarrow T)) \simeq (T \rightarrow \U)$$
+where $\U$ represents the type of sets.
+
+While a presheaf over an index category, i.e.
+a family of sets with maps between them according to the morphisms of the category, can be seen as living on the indexed side of the correspondence, with discrete Grothendieck fibrations on the other side of the correspondence, there are situations where the presheaf can also be seen as living on the fibered side of the correspondence.
+Indeed, when the index category is direct, i.e.
+with a downwards-well-founded collection of morphisms, as is the case of semi-simplicial and semi-cubical sets, each set serving as domain of a map can be turned into a family indexed on the codomain of the map, and, since the collection of maps is well-founded, this can be iterated, eventually producing a collection of families which we call an indexed presentation of the presheaf over the direct category.
+
+For instance, in the case of a semi-cubical set, presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes, the presheaf approach corresponds to a family of sets fibered the ones over the others (up to coherence conditions such).
+Formulated in type theory, it corresponds to:
+
+\begin{equation*}
+  \begin{tikzcd}
+    X_0: \U & X_1: \U \arrow[l, "\partial^L" description, shift left=2] \arrow[l, "\partial^R" description, shift right=2] & X_2: \U \arrow[l, "\partial^{L\kstar}" description, shift left=6] \arrow[l, "\partial^{R\kstar}" description, shift left=2] \arrow[l, "\partial^{\kstar L}" description, shift right=2] \arrow[l, "\partial^{\kstar R}" description, shift right=6] & \ldots
+  \end{tikzcd}
+\end{equation*}
+
+On the other side, the indexed presentation of the same presheaf is a stratified sequence of families indexed on elements of families of lower rank, taking into account the coherence conditions to prevent duplications.
+Formulated in type theory, it corresponds to:
+\begin{align*}
+  X_0 & :              & \U                                                     \\
+  X_1 & :              & X_0 \rightarrow X_0 \rightarrow \U                     \\
+  X_2 & : \Pi a b c d. & X_1(a)(b) \rightarrow X_1(a)(c) \rightarrow X_1 (b)(d) \\
+      &                & \rightarrow X_1 (c)(d) \rightarrow \U                  \\
+  \ldots
+\end{align*}
+%% \begin{align*}
+%%   X_0                                                                                      & \mbox{ a set of points}                                       \\
+%%   (X_1)_{a,b\in X_0}                                                                       & \mbox{ a set of lines between any two points}                 \\
+%%   (X_2)_{a,b,c,d\in X_0,p\in (X_1)_{ab},q\in (X_1)_{bc},r \in (X_1)_{ac}, s\in (X_1)_{cd}} & \mbox{ a set of squares over any 4 lines lying over 4 points} \\
+%%   \ldots
+%% \end{align*}
+
+The idea for such indexed presentation of presheaves over a direct category was introduced at the Univalent Foundations year in the context of defining semi-simplicial types~\cite{}.
+A couple of constructions were proposed since then.
+One, by Voevodsky~\cite{Voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over injective monotone maps between finite ordinals.
+Another, by the first author, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps~\cite{herbelin15}.
+Another one by Part and Luo, and formalized in the Plastic proof assistant, works generically for any Reedy category with only upwards maps~\cite{part15}.
+
+The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence condition between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex is the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
+On the other side, defining a concrete presheaf in indexed form only requires to provide the family since the burden of defining maps and showing the coherence conditions has already been integrated in the definition what is not the case in the presheaf presentation.
+
+\subsection*{Reynolds' parametricity and its unary and binary variants}
+
 In the context of functional programming, Reynolds' parametricity~\cite{reynolds83} interprets types as relations characterizing the observational behavior of programs of this type.
@@
 
+\subsection*{Iterated-parametricity-based construction}
+
 We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets, generated by iterating the parametricity translation for type judgements.
@@
 
+\subsection*{Contribution}
+
 As a result, our work can be seen as contributing the following: it characterizes, will full details, how to technically define parametricity iterated in arbitrary dimensions; %Second, it makes fully formal the relation between semi-simplicial and semi-cubical sets and parametricity.
@@
 to the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\cite{curien14}).
+
+\subsection*{Outline}
 
@@
   \begin{tikzcd}
-    X_0: \U & X_1: \U \arrow[l, "\delta^L" description, shift left=2] \arrow[l, "\delta^R" description, shift right=2] & X_2: \U \arrow[l, "\delta^{L\kstar}" description, shift left=6] \arrow[l, "\delta^{R\kstar}" description, shift left=2] \arrow[l, "\delta^{\kstar L}" description, shift right=2] \arrow[l, "\delta^{\kstar R}" description, shift right=6] & \ldots
+    X_0: \U & X_1: \U \arrow[l, "\partial^L" description, shift left=2] \arrow[l, "\partial^R" description, shift right=2] & X_2: \U \arrow[l, "\partial^{L\kstar}" description, shift left=6] \arrow[l, "\partial^{R\kstar}" description, shift left=2] \arrow[l, "\partial^{\kstar L}" description, shift right=2] \arrow[l, "\partial^{\kstar R}" description, shift right=6] & \ldots
   \end{tikzcd}
@@
 We have a priori a dependency over eight copies of $X_0$ but these are actually four due to the coherence conditions on the functor (e.g.
-that $\delta^R \circ \delta^{R\kstar} = \delta^{(R\kstar)\circ(R)} = \delta^{RR} = \delta^{(\kstar R)\circ(R)} = \delta^R \circ \delta^{\kstar R}$, etc.).
+that $\partial^R \circ \partial^{R\kstar} = \partial^{(R\kstar)\circ(R)} = \partial^{RR} = \partial^{(\kstar R)\circ(R)} = \partial^R \circ \partial^{\kstar R}$, etc.).
 Based on these coherence conditions, the types of $X_0, X_1, X_2$ happen to have the form:

### 2023-05-07 paper/paper.tex
fix

@@
 A couple of constructions were proposed since then.
-One, by Voevodsky~\cite{Voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over injective monotone maps between finite ordinals.
+One, by Voevodsky~\cite{Voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
 Another, by the first author, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps~\cite{herbelin15}.

### 2023-05-08 paper/paper.tex
paper: minor formatting fixes

--- 2023-05-07 paper/paper.tex
@@
 \newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
-\newcommand{\Cube}{\ensuremath{\boldsymbol{{\Box}}}}
-\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\Box}}}}
+\newcommand{\Cube}{\ensuremath{\boldsymbol{{\square}}}}
+\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
 
@@
 A couple of constructions were proposed since then.
-One, by Voevodsky~\cite{Voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over injective monotone maps between finite ordinals.
+One, by Voevodsky~\cite{voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
 Another, by the first author, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps~\cite{herbelin15}.
@@
 
-\subsection{\texorpdfstring{$\nu$}{ν}-sets}
+\subsection*{\texorpdfstring{$\nu$}{ν}-sets}
 Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets.
@@
   \centering
-  \begin{tabularx}{0.95\linewidth}{X|X|X}
+  \begin{tabularx}{0.7\linewidth}{X|X|X}
     \toprule
@@
 
-\subsection{Augmented semi-simplicial sets}
+\subsection*{Augmented semi-simplicial sets}
 Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``color''.
@@
 
-\subsection{Semi-cubical sets}
+\subsection*{Semi-cubical sets}
 Semi-cubical sets are defined like augmented semi-simplicial sets except that $\DeltaPlus$ is replaced by $\Cube$ in which we take sequences of $L$, $R$ and $\star$, instead of sequences of $0$ and $\kstar$.
@@
 
-\section{Comparison of fibered and indexed presentations}
+\section*{Comparison of fibered and indexed presentations}
 %     - standard augmented triangle:
@@
 \end{align*}
+
+In particular, for $X: \U$, applying the parametricity translation is about canonically associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X)(X)$ i.e.
+of $X \rightarrow X \rightarrow \U$.
+In turn, applying the parametricity translation to $X_\kstar: X \rightarrow X \rightarrow \U$ is about canonically associating to $X_\kstar$ an inhabitant $X_{\kstar\kstar}$ of $(X \rightarrow X \rightarrow \U)_\kstar(X_\kstar)(X_\kstar)$ i.e.
+of:
+\begin{align*}
+  \Pi x_{LL}: X.\, \Pi x_{LR}: X.\, X_\kstar(x_{LL})(x_{LR})             \\
+  \rightarrow \Pi x_{RL}: X.\, \Pi x_{RR}: X.\, X_\kstar(x_{RL})(x_{RR}) \\ \rightarrow X_\kstar(x_{LL}, x_{RL}) \rightarrow X_\kstar(x_{LR})(x_{RR})  \rightarrow \U
+\end{align*}
+which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of binary parametricity applied to an initial $X: \U$:
+\begin{equation*}
+  \begin{array}{llllr}
+    X_0 & \defeq & X                & : & \U                                               \\
+    X_1 & \defeq & X_\kstar         & : & {\U}_\kstar(X)(X)                                \\
+    X_2 & \defeq & X_{\kstar\kstar} & : & ({\U}_\kstar(X)(X))_{\kstar}(X_\kstar)(X_\kstar) \\
+    \ldots
+  \end{array}
+\end{equation*}
+
+This tells us how the informal type given to $X_2$ in the previous section could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.
+
+Notice, however, that the recipe obtained so far, $X_{n + 1}: ({S_n})_\kstar(X_n)(X_n)$ for $X_n: S_n$, applies parametricity on the \emph{syntax} of the type of $X_n$.
+It does not directly yield a characterization of $S_n$ as a function from $n$.
+Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and the uniform treatment of augmented semi-simplicial and semi-cubical sets by means of the generalization to $\nu$-sets.
+
+\section{Our construction}
+Our construction is highly dependent, with dependencies in inequality and equality proofs. It involves several involved details, some of them being visible only in the Coq formalization.
+
+In Section~\ref{sec:ett} and Tables~\ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces}, \ref{tab:coh}, we give an informal, mathematical definition in Extensional Type Theory, which roughly corresponds to a level of reasoning ``à la set theory'' where equalities are thought as ``holding on the nose'' without having to mention them explicitly once they are justified.
+In Section~\ref{sec:itt} and Tables~\ref{fulltab:coind}, \ref{fulltab:core}, \ref{fulltab:frames}, \ref{fulltab:faces}, \ref{fulltab:coh}, we give the same mathematical definition in Intensional Type Theory, where transporting along coherence conditions is now made explicit.
+Adding this level of details helps to understand the specificities of coherence conditions.
+
+But first, we start with a section gradually and informally explaining the intuition of the construction. It can be read in parallel with the tables if wished.
+
+\subsection*{Formal construction in ETT\label{sec:ett}}
+% Abbreviated tables in this section
+%
+% The rule for implicit arguments for each table:
+% show 1 explicit in first two parts
+% show E + 1 explicit in the third part
+\appendmask[bonak]{layer}[D]
+\appendmask[bonak]{painting}[D]
+\appendmask[bonak]{restrframe}[D]
+\appendmask[bonak]{restrlayer}[D, d]
+\appendmask[bonak]{restrpainting}[D, d]
+\appendmask[bonak]{cohframe}[D]
+\appendmask[bonak]{cohlayer}[D, d]
+\appendmask[bonak]{cohpainting}[D, d]
+
+% Now, we write the type theory bit, and input the abbreviated tables
+
+% Truncated sets, otherwise referred to as X
+% Keep all arguments
+\newcommandx{\Xp}[1]{\X[#1][][]}
+\newcommandx{\Xto}[3][3=]{\X[#1][<#2][#3]}
+\newcommandx{\Xcomp}[3][3=]{\X[#1][=#2][#3]}
+\newcommandx{\Xfrom}[3][3=]{\X[#1][\geq#2][#3]}
+
+% Frame, layer, and painting
+% Drop the universe letter
+\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
+\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
+\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
+
+% Restriction for frame, layer, and painting
+% Drop the universe letter
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
+
+% Coherence conditions for frame, layer, and painting
+% Keep only ε, ω; n, p; proposition on n and p
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][][][][][#9]}
+
+We now present the construction in \emph{extensional} type theory; i.e.
+in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
+\begin{equation*}
+  \seqr{}{\Gamma \vdash p: t = u}{\Gamma \vdash t \equiv u}
+\end{equation*}
+
+For the presentation corresponding to the formalization in \emph{intensional} type theory, see \ref{sec:itt}.
+
+The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and~\ref{tab:coh}.
+Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a stream, coinductively representing the limit of $n$-truncated $\nu$-sets.
+The $n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.
+In such stream, the $n$th component is a type dependent over a $\fullframe$.
+The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\painting$.
+The type $\layer$ and $\painting$ are dependent over $\restrf$, and these restrictions are defined on \ref{tab:faces}.
+These restrictions are defined using auxiliary definitions of $\restrl$ and $\restrc$.
+
+Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$.
+This commutation is not provable by computation so we have to prove it propositionally before using the reflection rule.
+Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\painting$.
+This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$.
+Even though it looks independent of the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
+More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be mutually defined by induction on $p$.
+Also, each of $\painting$, $\restrc$, and $\cohc$ is built by induction from $p$ to $n$.
+The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but, the converse dependency is only on lower $n$, so this is well-founded.
+Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
+We leave however implicit the exact way this mutual recursion can be formalized at this stage of the paper.
+
+Most components of the construction takes inequality constraints as parameters, and we have left implicit that they are satisfied in the tables.
+Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, only assuming that we can pick a definition for which proofs of $m \leq n$ are provably unique and thus definitionally equal by the reflection rule.
+
+The construction takes benefit of various provable equalities over proofs of equality being definitional by the reflection rule.
+This includes in particular the groupoid properties of equality.
+Notably, uniqueness of identity proofs holds in extensional type theory, so that any type is automatically an $\U$.
+Also, we left implicit in table~\ref{tab:coh} the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
+(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type.
+In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is function extensionality, holds by default in extensional type theory.
+
+Note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning them anymore.
+For instance, it produces Fig.~\ref{fig:intuition} for $n=2$ and $\nu=2$.
+
+\renewcommand*{\lab}{tab:coind}
+\input{tab-coind.tex}
+
+% For just the second table, keep the universe letter in fullframe
+\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
+
+\renewcommand*{\lab}{tab:core}
+\input{tab-core.tex}
+
+% Drop the universe letter in fullframe for all remaining tables
+\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
+\renewcommand*{\lab}{tab:frames}
+\input{tab-frames.tex}
+
+% Truncated sets, otherwise referred to as X
+% Drop the universe letter for the third and fourth tables
+\renewcommandx{\Xto}[3][3]{\X[][<#2][#3]}
+\renewcommandx{\Xcomp}[3][3]{\X[][=#2][#3]}
+\renewcommandx{\Xfrom}[3][3]{\X[][\geq#2][#3]}
+
+% Hack to remove , in \cohf
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
+
+% The third table mentions cohframe; keep ε, ω in this instance
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
+
+\renewcommand*{\lab}{tab:faces}
+\input{tab-faces-ett.tex}
+
+% Restriction for frame, layer, and painting
+% Drop just the universe letter for the coh table
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
+
+% Frame, layer, and painting
+% Drop all arguments for coh table; they're not present in coind table.
+\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][][][][#5]}
+\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][][][][#5]}
+\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][][][][#5]}
+
+% Hack to remove , in \cohf
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
+
+% Coherence conditions for frame, layer, and painting
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
+
+\renewcommand*{\lab}{tab:coh}
+\input{tab-coh-ett.tex}
+
+\subsection*{Intuition for our formal construction\label{sec:intuition}}
+To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\painting$.
+A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$, and a $\painting$ corresponds to a filled $\framep$.
+Some $\framep$ are full and we call them $\fullframe$.
+
+We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying to the description above the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$.
+In particular, $\fullframe[n]$ is a ``telescope'', i.e.
+a nesting of $\Sigma$-type.
+Let us now illustrate how we build $\fullframe[n]$.
+To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ of $X_0$ can be equivalently formulated as $\unittype \rightarrow \U$.
+Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
+For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown in Fig.~\ref{fig:intuition}.
+Fig.~\ref{fig:intuition} also mentions how the type of $X_2$ is structured.
 
@@
 
-In particular, for $X: \U$, applying the parametricity translation is about canonically associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X)(X)$ i.e.
-of $X \rightarrow X \rightarrow \U$.
-In turn, applying the parametricity translation to $X_\kstar: X \rightarrow X \rightarrow \U$ is about canonically associating to $X_\kstar$ an inhabitant $X_{\kstar\kstar}$ of $(X \rightarrow X \rightarrow \U)_\kstar(X_\kstar)(X_\kstar)$ i.e.
-of:
-\begin{align*}
-  \Pi x_{LL}: X.\, \Pi x_{LR}: X.\, X_\kstar(x_{LL})(x_{LR})             \\
-  \rightarrow \Pi x_{RL}: X.\, \Pi x_{RR}: X.\, X_\kstar(x_{RL})(x_{RR}) \\ \rightarrow X_\kstar(x_{LL}, x_{RL}) \rightarrow X_\kstar(x_{LR})(x_{RR})  \rightarrow \U
-\end{align*}
-which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of binary parametricity applied to an initial $X: \U$:
-\begin{equation*}
-  \begin{array}{llllr}
-    X_0 & \defeq & X                & : & \U                                               \\
-    X_1 & \defeq & X_\kstar         & : & {\U}_\kstar(X)(X)                                \\
-    X_2 & \defeq & X_{\kstar\kstar} & : & ({\U}_\kstar(X)(X))_{\kstar}(X_\kstar)(X_\kstar) \\
-    \ldots
-  \end{array}
-\end{equation*}
-
-This tells us how the informal type given to $X_2$ in the previous section could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.
-
-Notice, however, that the recipe obtained so far, $X_{n + 1}: ({S_n})_\kstar(X_n)(X_n)$ for $X_n: S_n$, applies parametricity on the \emph{syntax} of the type of $X_n$.
-It does not directly yield a characterization of $S_n$ as a function from $n$.
-Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and the uniform treatment of augmented semi-simplicial and semi-cubical sets by means of the generalization to $\nu$-sets.
-
-\section{Our construction}
-
-Our construction is highly dependent, with dependencies in inequality
-and equality proofs. It involves several involved details, some of
-them being visible only in the Coq formalization.
-
-In Section~\ref{sec:ett} and Tables~\ref{tab:coind}, \ref{tab:core},
-\ref{tab:frames}, \ref{tab:faces}, \ref{tab:coh}, we give an informal,
-mathematical definition in Extensional Type Theory, which roughly
-corresponds to a level of reasoning ``à la set theory'' where
-equalities are thought as ``holding on the nose'' without having to
-mention them explicitly once they are justified. In
-Section~\ref{sec:itt} and Tables~\ref{fulltab:coind},
-\ref{fulltab:core}, \ref{fulltab:frames}, \ref{fulltab:faces},
-\ref{fulltab:coh}, we give the same mathematical definition in
-Intensional Type Theory, where transporting along coherence conditions
-is now made explicit. Adding this level of details helps to understand
-the specificities of coherence conditions.
-
-But first, we start with a section gradually and informally explaining
-the intuition of the construction. It can be read in parallel with the
-tables if wished.
-
-\subsection{Formal construction in ETT\label{sec:ett}}
-% Abbreviated tables in this section
-%
-% The rule for implicit arguments for each table:
-% show 1 explicit in first two parts
-% show E + 1 explicit in the third part
-\appendmask[bonak]{layer}[D]
-\appendmask[bonak]{painting}[D]
-\appendmask[bonak]{restrframe}[D]
-\appendmask[bonak]{restrlayer}[D, d]
-\appendmask[bonak]{restrpainting}[D, d]
-\appendmask[bonak]{cohframe}[D]
-\appendmask[bonak]{cohlayer}[D, d]
-\appendmask[bonak]{cohpainting}[D, d]
-
-% Now, we write the type theory bit, and input the abbreviated tables
-
-% Truncated sets, otherwise referred to as X
-% Keep all arguments
-\newcommandx{\Xp}[1]{\X[#1][][]}
-\newcommandx{\Xto}[3][3=]{\X[#1][<#2][#3]}
-\newcommandx{\Xcomp}[3][3=]{\X[#1][=#2][#3]}
-\newcommandx{\Xfrom}[3][3=]{\X[#1][\geq#2][#3]}
-
-% Frame, layer, and painting
-% Drop the universe letter
-\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
-\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
-\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
-
-% Restriction for frame, layer, and painting
-% Drop the universe letter
-\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
-
-% Coherence conditions for frame, layer, and painting
-% Keep only ε, ω; n, p; proposition on n and p
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
-\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][][][][][#9]}
-
-We now present the construction in \emph{extensional} type theory; i.e.
-in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
-\begin{equation*}
-  \seqr{}{\Gamma \vdash p: t = u}{\Gamma \vdash t \equiv u}
-\end{equation*}
-
-For the presentation corresponding to the formalization in \emph{intensional} type theory, see \ref{sec:itt}.
-
-The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and~\ref{tab:coh}.
-Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a stream, coinductively representing the limit of $n$-truncated $\nu$-sets.
-The $n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.
-In such stream, the $n$th component is a type dependent over a $\fullframe$.
-The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\painting$.
-The type $\layer$ and $\painting$ are dependent over $\restrf$, and these restrictions are defined on \ref{tab:faces}.
-These restrictions are defined using auxiliary definitions of $\restrl$ and $\restrc$.
-
-Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$.
-This commutation is not provable by computation so we have to prove it propositionally before using the reflection rule.
-Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\painting$.
-This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$.
-Even though it looks independent of the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
-More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be mutually defined by induction on $p$.
-Also, each of $\painting$, $\restrc$, and $\cohc$ is built by induction from $p$ to $n$.
-The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but, the converse dependency is only on lower $n$, so this is well-founded.
-Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
-We leave however implicit the exact way this mutual recursion can be formalized at this stage of the paper.
-
-Most components of the construction takes inequality constraints as parameters, and we have left implicit that they are satisfied in the tables.
-Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, only assuming that we can pick a definition for which proofs of $m \leq n$ are provably unique and thus definitionally equal by the reflection rule.
-
-The construction takes benefit of various provable equalities over proofs of equality being definitional by the reflection rule.
-This includes in particular the groupoid properties of equality.
-Notably, uniqueness of identity proofs holds in extensional type theory, so that any type is automatically an $\U$.
-Also, we left implicit in table~\ref{tab:coh} the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
-(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type.
-In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is function extensionality, holds by default in extensional type theory.
-
-Note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning them anymore.
-For instance, it produces Fig.~\ref{fig:intuition} for $n=2$ and $\nu=2$.
-
-\renewcommand*{\lab}{tab:coind}
-\input{tab-coind.tex}
-
-% For just the second table, keep the universe letter in fullframe
-\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
-
-\renewcommand*{\lab}{tab:core}
-\input{tab-core.tex}
-
-% Drop the universe letter in fullframe for all remaining tables
-\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
-\renewcommand*{\lab}{tab:frames}
-\input{tab-frames.tex}
-
-% Truncated sets, otherwise referred to as X
-% Drop the universe letter for the third and fourth tables
-\renewcommandx{\Xto}[3][3]{\X[][<#2][#3]}
-\renewcommandx{\Xcomp}[3][3]{\X[][=#2][#3]}
-\renewcommandx{\Xfrom}[3][3]{\X[][\geq#2][#3]}
-
-% Hack to remove , in \cohf
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
-
-% The third table mentions cohframe; keep ε, ω in this instance
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
-
-\renewcommand*{\lab}{tab:faces}
-\input{tab-faces-ett.tex}
-
-% Restriction for frame, layer, and painting
-% Drop just the universe letter for the coh table
-\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
-
-% Frame, layer, and painting
-% Drop all arguments for coh table; they're not present in coind table.
-\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][][][][#5]}
-\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][][][][#5]}
-\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][][][][#5]}
-
-% Hack to remove , in \cohf
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
-
-% Coherence conditions for frame, layer, and painting
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
-
-\renewcommand*{\lab}{tab:coh}
-\input{tab-coh-ett.tex}
-
-\subsection{Intuition for our formal construction\label{sec:intuition}}
-To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\painting$.
-A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$, and a $\painting$ corresponds to a filled $\framep$.
-Some $\framep$ are full and we call them $\fullframe$.
-
-We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying to the description above the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$.
-In particular, $\fullframe[n]$ is a ``telescope'', i.e.
-a nesting of $\Sigma$-type.
-Let us now illustrate how we build $\fullframe[n]$.
-To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ of $X_0$ can be equivalently formulated as $\unittype \rightarrow \U$.
-Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
-For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown in Fig.~\ref{fig:intuition}.
-Fig.~\ref{fig:intuition} also mentions how the type of $X_2$ is structured.
-
 Let us now illustrate the construction of $\fullframe[3]$, necessary to build the type of $X_3$.
@@
 \section{Details on the mechanization\label{sec:mech}}
-\subsection{Formal construction in ITT\label{sec:itt}}
+\subsection*{Formal construction in ITT\label{sec:itt}}
 \renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
@@
 
-\subsection{Finer details}
+\subsection*{Finer details}
 \renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
@@
 Another direction for future work would also be to generically construct the indexed form of any presentation of presheaves over a direct category and to show the equivalence between the two presentations.
+
 \bibliographystyle{msclike}

### 2023-05-08 paper/paper.tex
paper: more formatting fixes; show right args in sec:intuition

@@
 
-\usepackage{amsmath, amssymb, mathrsfs, url, bookmark, tikz, tikz-cd, mathpazo, enumitem, xargs, multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, colortbl, pdflscape, flushend, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
+\usepackage{amsmath, amssymb, mathrsfs, url, bookmark, tikz, tikz-cd, mathpazo, enumitem, xargs, multirow, float, tabularx, environ, booktabs, setspace, makecell, colortbl, pdflscape, flushend, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
 
@@
 
-% Table caption set up
-\DeclareCaptionFormat{hfillunittypet}{\hfill#1#2#3\par}
-\DeclareCaptionFont{mdit}{\mdseries\itshape}
-\captionsetup[table]{
-  justification=centering,
-  font=bf,
-  labelfont=mdit,
-}
-
 % Use lettered footnotes
@@
     \email{Hugo.Herbelin@inria.fr}}
+  \author{Ramkumar Ramachandra}
+  \affiliation{Unaffiliated \email{r@artagnon.com}}
 \end{authgrp}
@@
 Formulated in type theory, it corresponds to:
+
 \begin{align*}
@@
 \subsection*{Reynolds' parametricity and its unary and binary variants}
-
 In the context of functional programming, Reynolds' parametricity~\cite{reynolds83} interprets types as relations characterizing the observational behavior of programs of this type.
@@
 \subsection*{Iterated-parametricity-based construction}
-
 We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets, generated by iterating the parametricity translation for type judgements.
@@
 \subsection*{Contribution}
-
-As a result, our work can be seen as contributing the following: it characterizes, will full details, how to technically define parametricity iterated in arbitrary dimensions; %Second, it makes fully formal the relation between semi-simplicial and semi-cubical sets and parametricity.
-it provides a new example of indexed constructions of semi-simplicial and semi-cubical sets~\cite{voevodsky12,herbelin15,part15}, useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\cite{part15,shulman14,altenkirch16,kraus2017space}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}); it makes a step in the direction of the program initiated in~\cite{altenkirch15} to develop parametricity-based models of parametric type theory~\cite{bernardy15,nuyts17,cavallo19} and cubical type theory~\cite{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do (compare e.g.
+As a result, our work can be seen as contributing the following: it characterizes, will full details, how to technically define parametricity iterated in arbitrary dimensions; it provides a new example of indexed constructions of semi-simplicial and semi-cubical sets~\cite{voevodsky12,herbelin15,part15}, useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\cite{part15,shulman14,altenkirch16,kraus2017space}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}); it makes a step in the direction of the program initiated in~\cite{altenkirch15} to develop parametricity-based models of parametric type theory~\cite{bernardy15,nuyts17,cavallo19} and cubical type theory~\cite{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do (compare e.g.
 to the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\cite{curien14}).
@@
 \begin{definition}[$\DeltaPlus$]
+  The definition of $\DeltaPlus$ is shown below.
+Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$.
+It can be shown that composition is associative and that $\id$ is neutral.
+
   \begin{figure}[H]
+    \centering
     \begin{align*}
@@
     \end{align*}
-    \caption{Definition of \DeltaPlus}\label{fig:deltaplus}
   \end{figure}
-
-  The definition of $\DeltaPlus$ is shown in Fig.~\ref{fig:deltaplus}.
-Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$.
-It can be shown that composition is associative and that $\id$ is neutral.
 \end{definition}
@@
 \begin{definition}[\Cube]
-  The definition of $\Cube$ is shown in Fig.~\ref{fig:cube}. The symbols $L$ and $R$ indicate opposite faces of a cube.
+  The definition of $\Cube$ is shown below. The symbols $L$ and $R$ indicate opposite faces of a cube.
+
   \begin{figure}[H]
+    \centering
     \begin{align*}
@@
     \end{align*}
-    \caption{Definition of \Cube}\label{fig:cube}
   \end{figure}
@@
 \end{align*}
+
 \section{Relating to parametricity\label{sec:rel-param}}
@@
 \subsection*{Intuition for our formal construction\label{sec:intuition}}
+\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
+\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
+\renewcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
+\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
+\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
+\renewcommandx{\restrc}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
+\renewcommandx{\cohf}[1][1]{\coh{frame}[][][][][][#1][][]}
+\renewcommandx{\cohl}[1][1]{\coh{layer}[][][][][][#1][][]}
+\renewcommandx{\cohc}[1][1]{\coh{painting}[][][][][][#1][][]}
+\renewcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
+
 To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\painting$.
@@
 Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
-For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown in Fig.~\ref{fig:intuition}.
-Fig.~\ref{fig:intuition} also mentions how the type of $X_2$ is structured.
+For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown below.
+The figure also mentions how the type of $X_2$ is structured.
 
 \begin{figure}[H]
+  \centering
   \begin{equation*}
@@
   \end{equation*}
-  \caption{Intuition for formal construction ($\nu = 2$)}\label{fig:intuition}
 \end{figure}
@@
   \end{tikzpicture}
-  \newline\newline
+  \;\;
   \begin{tikzpicture}[scale=2]
@@
 Layers are added from dimension $n$ to dimension $p$ that is opposite to the order from $0$ to $p$ the $\framep[n][p]$ are built, as shown below.
-\begin{align*}
-  \framep[n][p]   & \defeq \Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype .\, \layer[n][0]) \ldots) .\, \layer[n][p - 1] \\
-  \painting[n][p] & \defeq \Sigma l_p: \layer[n][p]. (\ldots (\Sigma l_n: \layer[n][n - 1] .\, X_n) \ldots)
-\end{align*}
+\begin{equation*}
+  \begin{array}{lll}
+    \framep[n][p]   & \defeq & \Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype .\, \layer[n][0]) \ldots) .\, \layer[n][p - 1] \\
+    \painting[n][p] & \defeq & \Sigma l_p: \layer[n][p]. (\ldots (\Sigma l_n: \layer[n][n - 1] .\, X_n) \ldots)
+  \end{array}
+\end{equation*}
 
@@
 In particular, $X_n$ is just $D.\tl$.
-\begin{align*}
-   & \framep[n][p](D) \defeq                                                                                      \\
-   & \;\;\;\;\Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)) \ldots) .\,\layer[n][p - 1](D) \\
-   & \painting[n][p](D) \defeq                                                                                    \\
-   & \;\;\;\;\Sigma l_p: \layer[n][p](D).\, (\ldots (\Sigma l_n: \layer[n][n - 1](D) .\, D.\tl) \ldots)
-\end{align*}
-
-\begin{figure}[H]
-  \begin{align*}
-    \framep[n][p](D)      & \defeq & \Sigma d: (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)(\unitpoint)) \ldots).\, \layer[n][p](D)(d)                                \\
-    \painting[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d).\, (\ldots (\Sigma l_n: \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}).\, D.\tl(d, l_p, \ldots, l_n)) \ldots) \\
-                          &        & \text{where } (d, l_p, \ldots, l_q) \text{ abbreviates } ((\ldots(d, l_p), \ldots), l_q)
-  \end{align*}
-  \caption{Refinement of definition of $\framep$ and $\painting$\label{fig:refinement}}
-\end{figure}
+\begin{equation*}
+  \begin{array}{lll}
+    \framep[n][p](D)   & \defeq & \Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)) \ldots) .\,\layer[n][p - 1](D) \\
+    \painting[n][p](D) & \defeq & \Sigma l_p: \layer[n][p](D).\, (\ldots (\Sigma l_n: \layer[n][n - 1](D) .\, D.\tl) \ldots)
+  \end{array}
+\end{equation*}
 
@@
 The left and right borders of the two blue boxes are extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$.
-We can then refine the previous equation by showing the dependencies on $d$, as shown in Fig.~\ref{fig:refinement}.
+We can then refine the previous equation by showing the dependencies on $d$, as shown below.
+
+\begin{equation*}
+  \begin{array}{llr}
+    \framep[n][p](D)      & \defeq & \Sigma d: (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)(\unitpoint)) \ldots).\, \layer[n][p](D)(d) \\
+    \painting[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d).\, (\ldots (\Sigma l_n: \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}).        \\
+                          &        & D.\tl(d, l_p, \ldots, l_n)) \ldots)                                                                           \\
+                          &        & \text{where } (d, l_p, \ldots, l_q) \text{ abbreviates } ((\ldots(d, l_p), \ldots), l_q)
+  \end{array}
+\end{equation*}
 
 When $\nu = 2$, the formation of layers from paintings amounts to:
-\begin{align*}
-  \layer[n][p](D)(d) & \defeq & \painting[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) & \times \\
-                     &        & \painting[n-1][p](D.\hd)(\restrf[n][p][R][p](d)) &
-\end{align*}
+\begin{equation*}
+  \begin{array}{llc}
+    \layer[n][p](D)(d) & \defeq & \painting[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) \\
+                       &        & \times                                           \\
+                       &        & \painting[n-1][p](D.\hd)(\restrf[n][p][R][p](d))
+  \end{array}
+\end{equation*}
 

### 2023-05-21 paper/paper.tex
introduction: ongoing

@@
 
-A family of sets can commonly be represented in two ways: as a family indexed over a set properly speaking or as a set together with a map telling for each element of the set on which index it depends on.
+A family of sets can commonly be represented in two ways: as a family indexed over a set properly speaking or as a set together with a map telling for each element of the set on which index it depends.
 In the latter case, the set associated to a given index is the fiber, i.e.
@@
 $$(\Sigma S: \U. (S \rightarrow T)) \simeq (T \rightarrow \U)$$
-where $\U$ represents the type of sets.
+where $\U$ represents the subset of types with proof-irrelevant equality.
 
@@
 Indeed, when the index category is direct, i.e.
-with a downwards-well-founded collection of morphisms, as is the case of semi-simplicial and semi-cubical sets, each set serving as domain of a map can be turned into a family indexed on the codomain of the map, and, since the collection of maps is well-founded, this can be iterated, eventually producing a collection of families which we call an indexed presentation of the presheaf over the direct category.
+with a downwards-well-founded collection of morphisms, as is the case of semi-simplicial and semi-cubical sets, each $F(X)$ serving as source of a map $F(X) \stackrel{F(f)}{\rightarrow} F(Y)$ can be turned into a family $F(X)$ indexed on $F(Y)$, and, since the collection of maps is well-founded, this can be iterated, eventually producing a collection of families which we call an indexed presentation of the presheaf over the direct category.
 
@@
 One, by Voevodsky~\cite{voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
-Another, by the first author, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps~\cite{herbelin15}.
+Another, by the first author, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps~\cite{herbelin15}\footnote{The title of the paper ``A dependently-typed construction of semi-simplicial types'' is confusing: it was part of a project at defining semi-simplicial types, but, in practice, the definition is done in a type theory with Unicity of Identity Proofs (UIP), meaning in a type theory where types (intended to represent arbitrary $\infty$-groupoids) are actually sets ($0$-truncated $\infty$-groupoids, that is, morally, $0$-groupoids).}.
 Another one by Part and Luo, and formalized in the Plastic proof assistant, works generically for any Reedy category with only upwards maps~\cite{part15}.

### 2023-05-21 paper/paper.tex
paper: more on introduction; remove IIT tables

--- 2023-05-08 paper/paper.tex
@@
 
-% Use lettered footnotes
-\renewcommand{\thefootnote}{\alph{footnote}}
-
 \begin{document}
@@
   Constructions such as semi-simplicial and semi-cubical sets can be defined in the ``usual way'' as presheaves over respectively, the semi-simplex or semi-cube category, which we call \emph{fibered} definitions, but also defined like in e.g.
-Voevodsky~\cite{voevodsky12} or in previous work~\cite{herbelin15}, as a dependently-typed construction, which we call \emph{indexed}.
+\cite{voevodsky12} or in \cite{herbelin15}, as a dependently-typed construction, which we call \emph{indexed}.
 
@@
 \end{abstract}
+\begin{keywords}
+  simplicial set, cubical set, coq, formalization, HoTT
+\end{keywords}
+% \maketitle
 
@@
 
-A family of sets can commonly be represented in two ways: as a family indexed over a set properly speaking or as a set together with a map telling for each element of the set on which index it depends on.
+A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a set or as a set together with a map specifying for each element of the set on which index it depends.
 In the latter case, the set associated to a given index is the fiber, i.e.
 inverse image, of the index under the map.
-The two presentations are equivalent, what can be formally stated in a type-theoretic language as a fibered/indexed correspondence\footnote{At a discussion on the Zulip channel for the HoTT community, alternative names fibration/family correspondence and unbundled/bundled correspondence were proposed, among others.
+The two presentations are equivalent, what can be formally stated in a type-theoretic language as a fibered/indexed correspondence~\footnote{At a discussion on the Zulip channel for the HoTT community, alternative names fibration/family correspondence and unbundled/bundled correspondence were proposed, among others.
 In our experience, the opposition fibered/indexed is spontaneously understood by many listeners.
 In particular, it echoes to the Grothendieck construction of fibered categories from indexed categories.
-Some people actually calls this correspondence ``the Grothendieck construction for dummies''.
-Its proof requires univalence (see~\cite{hottbook}).}:
-$$(\Sigma S: \U. (S \rightarrow T)) \simeq (T \rightarrow \U)$$
-where $\U$ represents the type of sets.
+The most elementary instance of the correspondence, with $\Type$ instead of $\U$, that is $(\Sigma S: \Type.
+(S \rightarrow T)) \simeq (T \rightarrow \Type)$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see~\cite{hottbook}).}:
+\begin{equation*}
+  \mbox{(fibered)}\qquad(\Sigma S: \U. (S \rightarrow T)) \simeq (T \rightarrow \U)\qquad \mbox{(indexed)}
+\end{equation*}
+where $\U$ represents the subset of types with a unique proof of equality, that is the type-theoretic counterpart of the category of sets (within some universe).
 
 While a presheaf over an index category, i.e.
-a family of sets with maps between them according to the morphisms of the category, can be seen as living on the indexed side of the correspondence, with discrete Grothendieck fibrations on the other side of the correspondence, there are situations where the presheaf can also be seen as living on the fibered side of the correspondence.
+a family of sets connected with maps according to the morphisms of the index category, can be seen as living on the indexed side of the correspondence, opposing to discrete Grothendieck fibrations on the fibered side, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the correspondence.
 Indeed, when the index category is direct, i.e.
-with a downwards-well-founded collection of morphisms, as is the case of semi-simplicial and semi-cubical sets, each set serving as domain of a map can be turned into a family indexed on the codomain of the map, and, since the collection of maps is well-founded, this can be iterated, eventually producing a collection of families which we call an indexed presentation of the presheaf over the direct category.
-
-For instance, in the case of a semi-cubical set, presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes, the presheaf approach corresponds to a family of sets fibered the ones over the others (up to coherence conditions such).
+with a downwards-well-founded collection of non-identity morphisms, as is the case of semi-simplicial and semi-cubical sets, each $F(X)$ serving as source of a map $F(X) \stackrel{F(f)}{\rightarrow} F(Y)$ can be turned into a family $F(X)$ indexed on $F(Y)$, and, since the maps are well-founded downward, this can be iterated from below, eventually producing a collection of families which we call an \emph{indexed presentation} of the presheaf over the direct category.
+
+For instance, in the case of a semi-cubical set, presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes, the standard presheaf approach prescribes a family of sets fibered the ones over the others (up to coherence conditions such).
 Formulated in type theory, it corresponds to:
@@
 A couple of constructions were proposed since then.
-One, by Voevodsky~\cite{voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
-Another, by the first author, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps~\cite{herbelin15}.
-Another one by Part and Luo, and formalized in the Plastic proof assistant, works generically for any Reedy category with only upwards maps~\cite{part15}.
-
-The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence condition between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex is the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
+One, by \cite{voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
+Another, by \cite{herbelin15}\footnote{The title of the paper ``A dependently-typed construction of semi-simplicial types'' is confusing: it was part of a project at defining semi-simplicial types, but, in practice, the definition is done in a type theory with Unicity of Identity Proofs (UIP), meaning in a type theory where types (intended to represent arbitrary $\infty$-groupoids) are actually sets ($0$-truncated $\infty$-groupoids, that is, morally, $0$-groupoids).}, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
+Two other ones by~\cite{part15}, formalized in (an emulation of logic-enriched homotopoty type theory in) the Plastic proof assistant, and by \cite{annenkovCK17}, formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\url{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, also rely on the presentation of the semi-simplicial category from increasing injective func†ions over finite ordinals.
+
+The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence conditions between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex is the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
 On the other side, defining a concrete presheaf in indexed form only requires to provide the family since the burden of defining maps and showing the coherence conditions has already been integrated in the definition what is not the case in the presheaf presentation.
@@
 \section{Semi-simplicial and semi-cubical sets\label{sec:nu}}
-In this section, we generalize semi-simplicial and semi-cubical sets to, what we call, $\nu$-sets, subsuming the earlier defintions.
-However, we also explicitly work out the cases of semi-simplical and semi-cubical sets, in a way that is similar to a previous art~\cite{aitchison86}.
+In this section, we generalize semi-simplicial and semi-cubical sets to, what we call, $\nu$-sets, subsuming the earlier definitions.
+However, we also explicitly work out the cases of semi-simplicial and semi-cubical sets, in a way that is similar to a previous art~\cite{aitchison86}.
 
@@
 
-% Full tables in this section
-%
-% Clear the mask and label
-\clearmask
-
-% Keep all arguments for all macros
-% Frame, layer, and painting
-\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[#1][#2][#3][#4][#5]}
-\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[#1][#2][#3][#4][#5]}
-\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[#1][#2][#3][#4][#5]}
-\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
-
-% Restriction for frame, layer, and painting
-\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[#1][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[#1][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[#1][#2][#3][#4][#5][#6][#7]}
-
-% Coherence conditions for frame, layer, and painting
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[#1][#2][#3][#4][#5][#6][#7,#8][#9]}
-
-\renewcommand*{\lab}{fulltab:coind}
-\input{tab-coind.tex}
-\renewcommand*{\lab}{fulltab:core}
-\input{tab-core.tex}
-\renewcommand*{\lab}{fulltab:frames}
-\input{tab-frames.tex}
-\renewcommand*{\lab}{fulltab:faces}
-\input{tab-faces.tex}
-
-\begin{landscape}
-  \renewcommand*{\lab}{fulltab:coh}
-  \input{tab-coh.tex}
-\end{landscape}
-
 \subsection*{Finer details}

### 2023-05-28 paper/paper.tex
paper: polish first few sections; removed some undef refs

@@
 \subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
-
 A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a set or as a set together with a map specifying for each element of the set on which index it depends.
@@
 \end{align*}
-%% \begin{align*}
-%%   X_0                                                                                      & \mbox{ a set of points}                                       \\
-%%   (X_1)_{a,b\in X_0}                                                                       & \mbox{ a set of lines between any two points}                 \\
-%%   (X_2)_{a,b,c,d\in X_0,p\in (X_1)_{ab},q\in (X_1)_{bc},r \in (X_1)_{ac}, s\in (X_1)_{cd}} & \mbox{ a set of squares over any 4 lines lying over 4 points} \\
-%%   \ldots
-%% \end{align*}
-
-The idea for such indexed presentation of presheaves over a direct category was introduced at the Univalent Foundations year in the context of defining semi-simplicial types~\cite{}.
+
+The idea for such indexed presentation of presheaves over a direct category was mentioned at the Univalent Foundations year in the context of defining semi-simplicial types~\footnote{See e.g.
+\url{https://ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}.}.
 A couple of constructions were proposed since then.
@@
 Another, by \cite{herbelin15}\footnote{The title of the paper ``A dependently-typed construction of semi-simplicial types'' is confusing: it was part of a project at defining semi-simplicial types, but, in practice, the definition is done in a type theory with Unicity of Identity Proofs (UIP), meaning in a type theory where types (intended to represent arbitrary $\infty$-groupoids) are actually sets ($0$-truncated $\infty$-groupoids, that is, morally, $0$-groupoids).}, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
-Two other ones by~\cite{part15}, formalized in (an emulation of logic-enriched homotopoty type theory in) the Plastic proof assistant, and by \cite{annenkovCK17}, formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\url{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, also rely on the presentation of the semi-simplicial category from increasing injective func†ions over finite ordinals.
+Another by~\cite{part15}, formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17}, formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\url{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, also rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
 
 The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence conditions between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex is the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
-On the other side, defining a concrete presheaf in indexed form only requires to provide the family since the burden of defining maps and showing the coherence conditions has already been integrated in the definition what is not the case in the presheaf presentation.
+On the other side, defining a concrete presheaf in indexed form only requires to provide the family since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition, what is not the case in the presheaf presentation.
 
 \subsection*{Reynolds' parametricity and its unary and binary variants}
-In the context of functional programming, Reynolds' parametricity~\cite{reynolds83} interprets types as relations characterizing the observational behavior of programs of this type.
-Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has the structure of a cubical set~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
-We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or graphs, in which case, we obtain a form of realizability~\cite{bernardy12,lasson12,moulin16}.
+In the context of functional programming, Reynolds' parametricity~(\citeyear{reynolds83}) interprets types as relations characterizing the observational behavior of programs of this type.
+More generally, correspondences, in the sense of ``relevant'' relation, that is of a family over a product of types, ca Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has the structure of a cubical set~\citep{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
+We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using families instead of relations or graphs, in which case, we obtain a form of realizability~\citep{bernardy12,lasson12,moulin16}.
 It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch}.
@@
 We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets, generated by iterating the parametricity translation for type judgements.
-In contrast to the standard presheaf presentation of augmented semi-simplicial and semi-cubical sets~\cite{fri08,grandis03,buchholtz17}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
+In contrast to the standard presheaf presentation of augmented semi-simplicial and semi-cubical sets~\citep{fri08,grandis03,buchholtz17}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
 That is, instead of having the set of augmented semi-simplices or semi-cubes in dimension $n+1$ \emph{fibered} over the set of augmented semi-simplices or semi-cubes in dimension $n$, we consider families of augmented semi-simplices and semi-cubes indexed over their faces.
@@
 \subsection*{Contribution}
-As a result, our work can be seen as contributing the following: it characterizes, will full details, how to technically define parametricity iterated in arbitrary dimensions; it provides a new example of indexed constructions of semi-simplicial and semi-cubical sets~\cite{voevodsky12,herbelin15,part15}, useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\cite{part15,shulman14,altenkirch16,kraus2017space}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}); it makes a step in the direction of the program initiated in~\cite{altenkirch15} to develop parametricity-based models of parametric type theory~\cite{bernardy15,nuyts17,cavallo19} and cubical type theory~\cite{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do (compare e.g.
-to the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\cite{curien14}).
-
+Our work:
+\begin{itemize}
+  \item characterizes, will full details, how to technically define parametricity iterated in arbitrary dimensions
+  \item provides a new example of indexed constructions of semi-simplicial and semi-cubical sets~\citep{voevodsky12,herbelin15,part15}, useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\citep{part15,shulman14,altenkirch16,kraus2017space}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett})
+  \item makes a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do; compare, for example, the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~(\citeyear{curien14}).
+\end{itemize}
 \subsection*{Outline}
-
 The outline of the paper is as follows.
 We recall the definition of the augmented semi-simplicial and semi-cubical categories using a combinatorial presentation, that directly leads to our generalization to $\nu$-sets, in \ref{sec:nu}.
-We then proceed to explain the connection between the indexed representation and parametricity in \ref{sec:indexed-param}.
 Before spelling out the details of our formalization in type-theoretic language in \ref{sec:ett} and \ref{sec:itt}, we give intuitions in \ref{sec:intuition}.
@@
 In this section, we generalize semi-simplicial and semi-cubical sets to, what we call, $\nu$-sets, subsuming the earlier definitions.
-However, we also explicitly work out the cases of semi-simplicial and semi-cubical sets, in a way that is similar to a previous art~\cite{aitchison86}.
+However, we also explicitly work out the cases of semi-simplicial and semi-cubical sets, in a way that is similar to a previous art~(\citeyear{aitchison86}).
 
@@
 \section{Preliminaries}
-Martin-Löf's Type theory~\cite{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
+Martin-Löf's Type theory~[\cite{martinlof75,martinlof84}] is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
 It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda~\cite{agda23}, Coq~\cite{coq22} or Lean~\cite{lean15}.
@@
 
-Tables \ref{fulltab:coind}, \ref{fulltab:core}, and \ref{fulltab:frames} are the same as tables \ref{tab:coind}, \ref{tab:core}, and \ref{tab:frames}, except that, in function applications, so as to be more informative, we make explicit all arguments, including those that can be inferred from the context.
-
-The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit as shown in table~\ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
-The proof of $\cohf$ is described on~\ref{fulltab:coh}, and it requires making explicit several rewritings which were invisible in extensional type theory.
+The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit, where the arrow over $\cohf$ indicates the direction of rewrite.
+The proof of $\cohf$ requires making explicit several rewritings which were invisible in extensional type theory.
 The commutation of $\restrl$ lives in a type referring to $\cohf$, so we need a transport along the commutation of $\restrf$ in the statement of $\cohl$.

### 2023-05-28 paper/paper.tex
paper/introduction: more polish, more content

@@
 
-For instance, in the case of a semi-cubical set, presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes, the standard presheaf approach prescribes a family of sets fibered the ones over the others (up to coherence conditions such).
+For instance, in the case of a semi-cubical set~\citep{grandis03,buchholtz17}, presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes, the standard presheaf approach prescribes a family of sets fibered the ones over the others (up to coherence conditions such).
 Formulated in type theory, it corresponds to:
@@
 One, by \cite{voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
-Another, by \cite{herbelin15}\footnote{The title of the paper ``A dependently-typed construction of semi-simplicial types'' is confusing: it was part of a project at defining semi-simplicial types, but, in practice, the definition is done in a type theory with Unicity of Identity Proofs (UIP), meaning in a type theory where types (intended to represent arbitrary $\infty$-groupoids) are actually sets ($0$-truncated $\infty$-groupoids, that is, morally, $0$-groupoids).}, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
+Another, by \cite{herbelin15}\footnote{With hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somehow confusing: it was part of a project at defining semi-simplicial types, but, in practice, the definition is done in a type theory with Unicity of Identity Proofs (UIP), meaning in a type theory where types (intended to represent arbitrary $\infty$-groupoids) are actually sets ($0$-truncated $\infty$-groupoids, that is, morally, $0$-groupoids).
+The confusion was however common at that time.}, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
 Another by~\cite{part15}, formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17}, formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\url{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, also rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
@@
 The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence conditions between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex is the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
-On the other side, defining a concrete presheaf in indexed form only requires to provide the family since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition, what is not the case in the presheaf presentation.
+On the other side, defining a concrete presheaf in indexed form only requires to provide the family since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition, what is not the case by default in the presheaf presentation.
+In category-theoretic terms, the indexation set of the family $X_n$ in the indexed presentation is called a \emph{matching object}.
+The indexed presentation of presheaves over a direct category can then be identified with a subclass of ordinary presheaves known as Reedy fibrant where Reedy fibrancy precisely expresses that the set $X_n$ in the fibered presentation is a $\Sigma$-type over an instance up to isomorphism of the matching object at level $n$~\citep{shulman14,kraus17}.
 
@@
 In the context of functional programming, Reynolds' parametricity~(\citeyear{reynolds83}) interprets types as relations characterizing the observational behavior of programs of this type.
-More generally, correspondences, in the sense of ``relevant'' relation, that is of a family over a product of types, ca Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has the structure of a cubical set~\citep{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
-We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using families instead of relations or graphs, in which case, we obtain a form of realizability~\citep{bernardy12,lasson12,moulin16}.
-It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch}.
-
-\subsection*{Iterated-parametricity-based construction}
-We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both augmented semi-simplicial and semi-cubical sets, generated by iterating the parametricity translation for type judgements.
-In contrast to the standard presheaf presentation of augmented semi-simplicial and semi-cubical sets~\citep{fri08,grandis03,buchholtz17}, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}.
-That is, instead of having the set of augmented semi-simplices or semi-cubes in dimension $n+1$ \emph{fibered} over the set of augmented semi-simplices or semi-cubes in dimension $n$, we consider families of augmented semi-simplices and semi-cubes indexed over their faces.
+More generally, correspondences, in the sense of ``relevant'' relation, that is of a family over a product of sets, can be used in place of relations.
+Parametricity can then be iterated, and, relying on the fibered representation of correspondences as spans, it has been noted that iterated Reynolds' parametricity has the structure of a cubical set~\citep{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
+We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or correspondences, in which case, we obtain a form of realizability~\citep{bernardy12,lasson12,moulin16}.
+It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
+This similarity suggests to join the definition of augmented semi-simplicial sets and cubical sets and to see both of them as instances of a more general construction which we call $\nu$-sets of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu$+1, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
+
+\subsection*{An iterated parametricity-based indexed construction}
+The main contribution of the paper is to describe in full details a recipe uniformly characterizing unary and binary iterated parametricity in indexed form and to derive from it a new indexed presentation, called indexed \emph{$\nu$-sets}, uniformly of augmented semi-simplicial and semi-cubical sets.
+Alternatively, from a category-theory perspective, we are characterizing, among the class of matching objects up to isomorphism for augmented semi-simplicial and cubical sets, a particular instance that reflects the structure of iterated parametricity.
 
@@
 \begin{itemize}
-  \item characterizes, will full details, how to technically define parametricity iterated in arbitrary dimensions
-  \item provides a new example of indexed constructions of semi-simplicial and semi-cubical sets~\citep{voevodsky12,herbelin15,part15}, useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\citep{part15,shulman14,altenkirch16,kraus2017space}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett})
-  \item makes a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do; compare, for example, the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~(\citeyear{curien14}).
+  \item Characterizes, will full details, how to technically define parametricity iterated in arbitrary dimensions.
+  \item Provides a new example of indexed constructions of semi-simplicial and semi-cubical sets~\citep{voevodsky12,herbelin15,part15}, useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\citep{part15,shulman14,altenkirch16,kraus17}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}).
+  \item Makes a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do; compare, for example, the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~(\citeyear{curien14}).
 \end{itemize}
@@
 \section{Preliminaries}
-Martin-Löf's Type theory~[\cite{martinlof75,martinlof84}] is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
-It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda~\cite{agda23}, Coq~\cite{coq22} or Lean~\cite{lean15}.
+Martin-Löf's Type theory~\citep{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
+It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda~(\citeyear{agda23}), Coq~(\citeyear{coq22}) or Lean~(\citeyear{lean15}).
 In type theory, propositions are types and proofs are programs.
@@
 In Section~\ref{sec:ett} and Tables~\ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces}, \ref{tab:coh}, we give an informal, mathematical definition in Extensional Type Theory, which roughly corresponds to a level of reasoning ``à la set theory'' where equalities are thought as ``holding on the nose'' without having to mention them explicitly once they are justified.
-In Section~\ref{sec:itt} and Tables~\ref{fulltab:coind}, \ref{fulltab:core}, \ref{fulltab:frames}, \ref{fulltab:faces}, \ref{fulltab:coh}, we give the same mathematical definition in Intensional Type Theory, where transporting along coherence conditions is now made explicit.
+In Section~\ref{sec:itt}, we give the same mathematical definition in Intensional Type Theory, where transporting along coherence conditions is now made explicit.
 Adding this level of details helps to understand the specificities of coherence conditions.

### 2023-05-28 paper/paper.tex
paper/contribution: polish

@@
 
-\subsection*{An iterated parametricity-based indexed construction}
+\subsection*{Contribution}
 The main contribution of the paper is to describe in full details a recipe uniformly characterizing unary and binary iterated parametricity in indexed form and to derive from it a new indexed presentation, called indexed \emph{$\nu$-sets}, uniformly of augmented semi-simplicial and semi-cubical sets.
 Alternatively, from a category-theory perspective, we are characterizing, among the class of matching objects up to isomorphism for augmented semi-simplicial and cubical sets, a particular instance that reflects the structure of iterated parametricity.
-
-\subsection*{Contribution}
-Our work:
+Additionally,
+
 \begin{itemize}
-  \item Characterizes, will full details, how to technically define parametricity iterated in arbitrary dimensions.
-  \item Provides a new example of indexed constructions of semi-simplicial and semi-cubical sets~\citep{voevodsky12,herbelin15,part15}, useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\citep{part15,shulman14,altenkirch16,kraus17}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}).
-  \item Makes a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do; compare, for example, the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~(\citeyear{curien14}).
+  \item This new construction is useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\citep{part15,shulman14,altenkirch16,kraus17}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}).
+  \item Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do; compare, for example, the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\citep{curien14}.
 \end{itemize}
+
 \subsection*{Outline}

### 2023-07-02 paper/paper.tex
paper: more progress

@@
 \subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
-A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a set or as a set together with a map specifying for each element of the set on which index it depends.
+A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a set $S$, or as a set $T$ together with a map specifying for each element of the set $T$ on which index it depends in $S$.
+In the first case, we call it an \emph{indexed} presentation.
 In the latter case, the set associated to a given index is the fiber, i.e.
-inverse image, of the index under the map.
-The two presentations are equivalent, what can be formally stated in a type-theoretic language as a fibered/indexed correspondence~\footnote{At a discussion on the Zulip channel for the HoTT community, alternative names fibration/family correspondence and unbundled/bundled correspondence were proposed, among others.
+inverse image, of the index under the map, so we call it a \emph{fibered} presentation.
+The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\cite{hottbook} as a fibered/indexed correspondence\footnote{At a discussion on the Zulip channel for the HoTT community, alternative names fibration/family correspondence and unbundled/bundled correspondence were proposed, among others.
 In our experience, the opposition fibered/indexed is spontaneously understood by many listeners.
@@
 The most elementary instance of the correspondence, with $\Type$ instead of $\U$, that is $(\Sigma S: \Type.
-(S \rightarrow T)) \simeq (T \rightarrow \Type)$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see~\cite{hottbook}).}:
-\begin{equation*}
-  \mbox{(fibered)}\qquad(\Sigma S: \U. (S \rightarrow T)) \simeq (T \rightarrow \U)\qquad \mbox{(indexed)}
-\end{equation*}
-where $\U$ represents the subset of types with a unique proof of equality, that is the type-theoretic counterpart of the category of sets (within some universe).
-
-While a presheaf over an index category, i.e.
-a family of sets connected with maps according to the morphisms of the index category, can be seen as living on the indexed side of the correspondence, opposing to discrete Grothendieck fibrations on the fibered side, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the correspondence.
-Indeed, when the index category is direct, i.e.
+(S \rightarrow T)) \simeq (T \rightarrow \Type)$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see~\cite{hottbook}).}
+\begin{equation*}
+  \mbox{(fibered)}\qquad(\Sigma S: \U. (S \rightarrow T)) ~\simeq~ (T \rightarrow \U)\qquad \mbox{(indexed)}
+\end{equation*}
+where $\U$ represents sets in homotopy type theory as the subset of types with a unique proof of equality (within some universe).
+
+A \emph{presheaf} on an category is a family of sets connected with maps according to the morphisms of the category.
+As such, it lives on the indexed side of the correspondence, opposing on the fibered side to what is called \emph{discrete Grothendieck fibrations}.
+However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the correspondence.
+Indeed, when the indexing category is direct, i.e.
 with a downwards-well-founded collection of non-identity morphisms, as is the case of semi-simplicial and semi-cubical sets, each $F(X)$ serving as source of a map $F(X) \stackrel{F(f)}{\rightarrow} F(Y)$ can be turned into a family $F(X)$ indexed on $F(Y)$, and, since the maps are well-founded downward, this can be iterated from below, eventually producing a collection of families which we call an \emph{indexed presentation} of the presheaf over the direct category.
 
-For instance, in the case of a semi-cubical set~\citep{grandis03,buchholtz17}, presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes, the standard presheaf approach prescribes a family of sets fibered the ones over the others (up to coherence conditions such).
+For instance, in the case of a semi-cubical set~\citep{grandis03,buchholtz17}, presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes, the standard presheaf approach prescribes a family of sets fibered the ones over the others (up to cubical faces identities).
 Formulated in type theory, it corresponds to:
@@
 On the other side, the indexed presentation of the same presheaf is a stratified sequence of families indexed on elements of families of lower rank, taking into account the coherence conditions to prevent duplications.
-Formulated in type theory, it corresponds to:
+Formulated in type theory, it takes the form:
 
@@
 The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence conditions between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex is the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
-On the other side, defining a concrete presheaf in indexed form only requires to provide the family since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition, what is not the case by default in the presheaf presentation.
-In category-theoretic terms, the indexation set of the family $X_n$ in the indexed presentation is called a \emph{matching object}.
+On the other side, defining a concrete presheaf in indexed form only requires to provide the family since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition, what is not the case by default in the (ordinary) presheaf presentation.
+
+In category-theoretic terms, the indexi set of the family $X_n$ in the indexed presentation is called a \emph{matching object}.
 The indexed presentation of presheaves over a direct category can then be identified with a subclass of ordinary presheaves known as Reedy fibrant where Reedy fibrancy precisely expresses that the set $X_n$ in the fibered presentation is a $\Sigma$-type over an instance up to isomorphism of the matching object at level $n$~\citep{shulman14,kraus17}.
@@
 However, we also explicitly work out the cases of semi-simplicial and semi-cubical sets, in a way that is similar to a previous art~(\citeyear{aitchison86}).
-
-\subsection*{\texorpdfstring{$\nu$}{ν}-sets}
-Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets.
-To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\nu$-semi-shape category.
-The morphisms of the $\nu$-semi-shape category are sequences of elements of a set $\nu$ of arbitrary cardinal, extended with $\kstar$, so that the following holds.
-
-\begin{table}[H]
-  \centering
-  \begin{tabularx}{0.7\linewidth}{X|X|X}
-    \toprule
-    Value of $\nu$ & 1                               & 2                  \\
-    \graymidrule
-    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
-
-A $\nu$-set is thus a contravariant functor $\phi$ from the $\nu$-semi-shape category to $\Set$ and we call $n$-$\nu$-semi-shape an element of $\phi(n)$.
-As in the augmented semi-simplicial and semi-cubical cases, the standard $(n + 1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
-We clarify in the next sections how this process of construction is similar to the parametricity translation developed for functional programming~\cite{reynolds83} and more generally for type theory~\cite{bernardy10, bernardy11, atkey14, bernardy15}.
 
@@
         a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a = L$ or $R$}                           \\
-        a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = L$, $R$, or $\kstar$} \\
+        a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a = L$, $R$, or $\kstar$} \\
       \end{cases} \\
@@
 Note that the components can this time be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$ to the one obtained by replacing the leftmost $\kstar$ with $R$.
+
+\subsection*{\texorpdfstring{$\nu$}{ν}-sets}
+Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets.
+To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\nu$-semi-shape category.
+
+\begin{definition}[$\nu$-semi-shape categroy]
+  The definition of $\nu$-semi-shape category is shown below.
+Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$.
+It can be shown that composition is associative and that $\id$ is neutral.
+
+  \begin{figure}[H]
+    \centering
+    \begin{align*}
+      \Obj       & := \Nat                                                                            \\
+      \Hom(p, n) & := \{l \in (\nu \cup \kstar) \mid \text{number of $\kstar$ in $l = p$}\}           \\
+      g \circ f  & :=
+      \begin{cases}
+        f                  & \text{if $g = []$}                                                         \\
+        a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $R \in \nu$}                        \\
+        a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
+      \end{cases} \\
+      \id        & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom(n, n)$}
+    \end{align*}
+  \end{figure}
+\end{definition}
+
+The morphisms of the $\nu$-semi-shape category are sequences of elements of a set $\nu$ of arbitrary cardinal, extended with $\kstar$:
+
+so that the following holds.
+
+\begin{table}[H]
+  \centering
+  \begin{tabularx}{0.7\linewidth}{X|X|X}
+    \toprule
+    Value of $\nu$ & 1                               & 2                  \\
+    \graymidrule
+    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
+
+A $\nu$-set is thus a contravariant functor $\phi$ from the $\nu$-semi-shape category to $\Set$ and we call $n$-$\nu$-semi-shape an element of $\phi(n)$.
+As in the augmented semi-simplicial and semi-cubical cases, the standard $(n + 1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
+We clarify in the next sections how this process of construction is similar to the parametricity translation developed for functional programming~\cite{reynolds83} and more generally for type theory~\cite{bernardy10, bernardy11, atkey14, bernardy15}.
 

### 2023-07-16 paper/paper.tex
Minor change

@@
 
-\usepackage{amsmath, amssymb, mathrsfs, url, bookmark, tikz, tikz-cd, mathpazo, enumitem, xargs, multirow, float, tabularx, environ, booktabs, setspace, makecell, colortbl, pdflscape, flushend, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
+\usepackage{amsmath, amssymb, mathrsfs, wasysym, url, bookmark, tikz, tikz-cd, mathpazo, enumitem, xargs, multirow, float, tabularx, environ, booktabs, setspace, makecell, colortbl, pdflscape, flushend, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
 
@@
 \subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
-A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a set $S$, or as a set $T$ together with a map specifying for each element of the set $T$ on which index it depends in $S$.
+A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a given set $S$ or as a set $T$ together with a map specifying for each element of the set $T$ on which index in $S$ it depends.
 In the first case, we call it an \emph{indexed} presentation.
@@
 
-In category-theoretic terms, the indexi set of the family $X_n$ in the indexed presentation is called a \emph{matching object}.
+In category-theoretic terms, the indexing set of the family $X_n$ in the indexed presentation is called a \emph{matching object}.
 The indexed presentation of presheaves over a direct category can then be identified with a subclass of ordinary presheaves known as Reedy fibrant where Reedy fibrancy precisely expresses that the set $X_n$ in the fibered presentation is a $\Sigma$-type over an instance up to isomorphism of the matching object at level $n$~\citep{shulman14,kraus17}.
@@
 
-%% Notations
-% simplicial, augmented, where
-% Γ           Γ+         Augmented Simplicial Combinatorics through Category Theory
-%                        José Manuel García-Calcines, María Teresa Rivas-Rodríguez, Luis Javier Hernández-Paricio, 2022
-
-% semi-augmented, where
-% ∆_s        HOMOLOGY IN RELATIVE SEMI-ABELIAN CATEGORIES, JULIA GOEDECKE, 2011
-
-% simplicial, semi-simplicial, where
-% Δ           Δ_inj            SEMI-SIMPLICIAL SPACES, JOHANNES EBERT AND OSCAR RANDAL-WILLIAMS, 2018
-% Δ           Δ_inj            PhD, Josep Esquirol Esteve, 2019
-% Δ           Δ'               Strict n-categories and augmented directed complexes model homotopy types, Andrea Gagna, 2018
-% Δ           Δ_inj, Δ_{inj,aug} Ms Th. Jonas Dallend ̈orfer, 2019
-
 \begin{notation}[Finite sequences]
@@
     \begin{align*}
-      \Obj(\DeltaPlus) & := \Nat                                                                     \\
-      \Hom(p, n)       & := \{l \in [0, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}        \\
+      \Obj_{\DeltaPlus}       & := \Nat                                                                             \\
+      \Hom_{\DeltaPlus}(p, n) & := \{l \in \{0, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}              \\
       g \circ f               & :=
@@
       \end{cases}                \\
-      \id              & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom(n, n)$}
+      \id                     & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom_{\DeltaPlus}(n, n)$}
     \end{align*}
@@
 \begin{definition}[$\DeltaPlus^n$]
-  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as what is called the Yoneda embedding of $n \in \Obj(\DeltaPlus)$:
+  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as the Yoneda embedding of $n \in \Obj(\DeltaPlus)$:
   \begin{align*}
@@
     \begin{align*}
-      \Obj(\Cube) & := \Nat                                                                                 \\
-      \Hom(p, n)  & := \{l \in [L, R, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}                 \\
+      \Obj_{\Cube}       & := \Nat                                                                          \\
+      \Hom_{\Cube}(p, n) & := \{l \in \{L, R, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}        \\
       g \circ f          & :=
@@
 \begin{example}[$\Cube^1$]
-  $\Cube^1$ consists of two points, given by $\Hom(0, 1)$ and a line, given by $\Hom(1, 1)$.
+  $\Cube^1$ consists of two points, given by $\Hom(0, 1)$, and a line, given by $\Hom(1, 1)$.
   \begin{equation*}
@@
 Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets.
-To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\nu$-semi-shape category.
-
-\begin{definition}[$\nu$-semi-shape categroy]
+To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\hexagon$.
+
+\begin{definition}[$\hexagon$]
   The definition of $\nu$-semi-shape category is shown below.
@@
     \begin{align*}
-      \Obj       & := \Nat                                                                            \\
-      \Hom(p, n) & := \{l \in (\nu \cup \kstar) \mid \text{number of $\kstar$ in $l = p$}\}           \\
+      \Obj_{\hexagon}       & := \Nat                                                                           \\
+      \Hom_{\hexagon}(p, n) & := \{l \in (\nu \cup \{\kstar\})^n \mid \text{number of $\kstar$ in $l = p$}\}    \\
       g \circ f             & :=
@@
         f                  & \text{if $g = []$}                                                                 \\
-        a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $R \in \nu$}                        \\
-        a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
+        a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a \in \nu$}                                \\
+        a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a \in \nu$ or $a = \kstar$} \\
       \end{cases}   \\
-      \id        & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom(n, n)$}
+      \id                   & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom_{\hexagon}(n, n)$}
     \end{align*}
@@
 \end{definition}
-
-The morphisms of the $\nu$-semi-shape category are sequences of elements of a set $\nu$ of arbitrary cardinal, extended with $\kstar$:
 
@@
 As in the augmented semi-simplicial and semi-cubical cases, the standard $(n + 1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
-We clarify in the next sections how this process of construction is similar to the parametricity translation developed for functional programming~\cite{reynolds83} and more generally for type theory~\cite{bernardy10, bernardy11, atkey14, bernardy15}.
-
-\section{Preliminaries}
+We clarify in the next sections how this process of construction is similar to the parametricity translation developed for functional programming~\citep{reynolds83} and more generally for type theory~\citep{bernardy10, bernardy11, atkey14, bernardy15}.
+
+\section{Type theory}
 Martin-Löf's Type theory~\citep{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
@@
 Type theory is a flexible formalism supporting different models.
-Some models are based on topological spaces, where equality is interpreted as path, and substitutivity of equality as transport~\cite{kapulkin21}.
-These models support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\cite{hottbook}.
+Some models are based on topological spaces, where equality is interpreted as path, and substitutivity of equality as transport~\citep{kapulkin21}.
+These models support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\citep{hottbook}.
 In type theory, types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number.
@@
 
-A notion of sets can be recovered in each universe as $\U[m]$, denoting the subtype of $\Type_m$ for which paths are degenerated, what can be expressed by the property of Uniqueness of Identity Proofs (UIP).
+A type-theoretic notion of sets can be recovered in each universe as $\U[m]$, denoting the subtype of $\Type_m$ for which paths are degenerated, what can be expressed by the property of Uniqueness of Identity Proofs (UIP).
 Technically, this is expressed as a structure equipping a domain $\Dom$ with the property $\UIP$:
@@
 $\Type_m$ as $\Type$ and $\U[m]$ as $\U$.
-
-\section*{Comparison of fibered and indexed presentations}
-%     - standard augmented triangle:
-%       Inductive points := A | B | C.
-%       Inductive lines := AB | BC | AC.
-%       Inductive surface := ABC.
-
-%       {X n := match n with 0 => unit | 1 => points | 2 => lines | 4 => surface | n => empty_set;
-%        d {n} i (Hi:i<n) (x:X n) := match n, i, x with
-%        | 0, _, _ => assert false
-%        | 1, _, _ => tt
-%        | 2, 0, AB => B
-%        | 2, 1, AB => A
-%        | 2, 0, BC => C
-%        | 2, 1, BC => B
-%        | 2, 0, AC => C
-%        | 2, 1, AC => A
-%        | 3, 0, ABC => BC
-%        | 3, 1, ABC => AC
-%        | 3, 2, ABC => AB
-%        | n.+4, i, _ => assert false
-%        end;
-%        alpha n i j (Hi:i<n) (Hj:j<i) (x : X n) : d i Hi (d j _ x) = d (j-1) _ (d i _ x)
-%        := match n, i, j, x with
-%        | 0, _, _, _ => assert false
-%        | 1, _, _, _ => assert false
-%        | 2, _, _, _ => proof_irrelevance_of_unit : tt = tt
-%        | 3, 1, 0, ABC => proof_irrelevance_in_points : C = C
-%        | 3, 2, 0, ABC => proof_irrelevance_in_points : B = B
-%        | 3, 2, 1, ABC => proof_irrelevance_in_points : A = A
-%        | n.+4, i, _ => assert false
-%        end
-%        }
-%        {hd tt := unit;
-%         tl := {hd _ (* (tt;tt) *) := points; (* 3 points *)
-%                tl := {hd _ (* ((tt;(tt;a));b) *) := unit; (* unique line over any a and any b *)
-%                       tl := {hd _ (* ((tt;(tt;(a;(b;tt))));((c;tt);tt)) *) := unit; (* unique triangle over ab, bc, and ac *)
-%                              tl := cofix s := {hd _ := empty_set; tl := s}}}}}
-%        {hd _ := unit; tl :=
-%        {hd _ := points; tl :=
-%        {hd _ := unit; tl :=
-%        {hd _ := unit; tl := cofix s := {hd _ := empty_set; tl := s}}}}} : AugmentedSemiSimplicial
-
-%        standard n : AugmentedSemiSimplicial
-%        := {hd _ := unit; tl :=
-%           {hd _ := [0;n]; tl :=
-%            unit unit unit ... n times ... unit; empty_set; ... }}
-There are different ways to represent a family of sets, commonly known as the fibered and indexed representations. In type theory, they are equivalent, and this equivalence can be formulated as:
-\begin{equation*}
-  (\Sigma S: \U. (S \rightarrow T)) \simeq (T \rightarrow \U)
-\end{equation*}
-
-Let us apply this correspondence to the case of semi-cubical sets. A semi-cubical set can be represented as a sequence of fibrations, together with appropriate coherence conditions.
-\begin{equation*}
-  \begin{tikzcd}
-    X_0: \U & X_1: \U \arrow[l, "\partial^L" description, shift left=2] \arrow[l, "\partial^R" description, shift right=2] & X_2: \U \arrow[l, "\partial^{L\kstar}" description, shift left=6] \arrow[l, "\partial^{R\kstar}" description, shift left=2] \arrow[l, "\partial^{\kstar L}" description, shift right=2] \arrow[l, "\partial^{\kstar R}" description, shift right=6] & \ldots
-  \end{tikzcd}
-\end{equation*}
-
-If we think of $X_1$ fibered over two copies of $X_0$ in an indexed way, we get $X_1$ of type $X_0 \rightarrow X_0 \rightarrow \U$.
-Continuing the process, we can think of $X_2$ fibered over four copies of $X_1$ themselves fibered over two copies of $X_0$ as a dependent type.
-We have a priori a dependency over eight copies of $X_0$ but these are actually four due to the coherence conditions on the functor (e.g.
-that $\partial^R \circ \partial^{R\kstar} = \partial^{(R\kstar)\circ(R)} = \partial^{RR} = \partial^{(\kstar R)\circ(R)} = \partial^R \circ \partial^{\kstar R}$, etc.).
-Based on these coherence conditions, the types of $X_0, X_1, X_2$ happen to have the form:
-\begin{align*}
-  X_0 & :              & \U                                                     \\
-  X_1 & :              & X_0 \rightarrow X_0 \rightarrow \U                     \\
-  X_2 & : \Pi a b c d. & X_1(a)(b) \rightarrow X_1(a)(c) \rightarrow X_1 (b)(d) \\
-      &                & \rightarrow X_1 (c)(d) \rightarrow \U                  \\
-  \ldots
-\end{align*}
 

### 2023-07-16 paper/paper.tex
Some rewording

@@
 In this section, we generalize semi-simplicial and semi-cubical sets to, what we call, $\nu$-sets, subsuming the earlier definitions.
-However, we also explicitly work out the cases of semi-simplicial and semi-cubical sets, in a way that is similar to a previous art~(\citeyear{aitchison86}).
+We start by first explicitly working out the cases of semi-simplicial and semi-cubical sets.
+%, in a way that is similar to a previous art~(\citeyear{aitchison86}).
 
@@
 Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``color''.
-Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over a singleton set of colors.
+Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over the singleton set of one fixed color.
 

### 2023-07-16 paper/paper.tex
paper: MAJ

--- 2023-07-02 paper/paper.tex
@@
     \begin{align*}
-      \Obj(\DeltaPlus) & := \Nat                                                                     \\
-      \Hom(p, n)       & := \{l \in [0, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}        \\
+      \Obj_{\DeltaPlus}       & := \Nat                                                                             \\
+      \Hom_{\DeltaPlus}(p, n) & := \{l \in [0, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}                \\
       g \circ f               & :=
@@
     \begin{align*}
-      \Obj(\Cube) & := \Nat                                                                                 \\
-      \Hom(p, n)  & := \{l \in [L, R, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}                 \\
+      \Obj_{\Cube}       & := \Nat                                                                          \\
+      \Hom_{\Cube}(p, n) & := \{l \in [L, R, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}          \\
       g \circ f          & :=
@@
     \begin{align*}
-      \Obj       & := \Nat                                                                            \\
-      \Hom(p, n) & := \{l \in (\nu \cup \kstar) \mid \text{number of $\kstar$ in $l = p$}\}           \\
+      \Obj_{\hexagon}        & := \Nat                                                                           \\
+      \Hom_{\hexagon}(p, n) & := \{l \in (\nu \cup \kstar) \mid \text{number of $\kstar$ in $l = p$}\}          \\
       g \circ f              & :=
@@
         a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $R \in \nu$}                     \\
-        a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
+        a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a $ or $\kstar$} \\
       \end{cases}               \\
-      \id        & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom(n, n)$}
+      \id                    & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom_{\hexagon}(n, n)$}
     \end{align*}

### 2023-07-16 paper/paper.tex
paper: remove extraneous content

--- 2023-07-16 paper/paper.tex
@@
 \subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
-A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a given set $S$ or as a set $T$ together with a map specifying for each element of the set $T$ on which index in $S$ it depends.
+A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a set $S$, or as a set $T$ together with a map specifying for each element of the set $T$ on which index it depends in $S$.
 In the first case, we call it an \emph{indexed} presentation.

### 2023-07-16 paper/paper.tex
Moving table nu-sets above

--- 2023-07-16 paper/paper.tex
@@
 \subsection*{\texorpdfstring{$\nu$}{ν}-sets}
-Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets.
+Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets obtained by building on an arbitrary alphabet $\nu$, so that the following holds:
+
+\begin{table}[H]
+  \centering
+  \begin{tabularx}{0.7\linewidth}{X|X|X}
+    \toprule
+    Cardinal of $\nu$ & 1                               & 2                  \\
+    \graymidrule
+    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
+
 To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\hexagon$.
@@
 \end{definition}
-
-so that the following holds.
-
-\begin{table}[H]
-  \centering
-  \begin{tabularx}{0.7\linewidth}{X|X|X}
-    \toprule
-    Value of $\nu$ & 1                               & 2                  \\
-    \graymidrule
-    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
 

### 2023-07-16 paper/paper.tex
paper: fix some obvious issues in last few sections

@@
 \section{Introduction}
-% - semisimplicial/semicubical sets in indexed form
-%   - clarify indexed/fibered, justify advantages of the respective choice
-%     - the presentation matters when expressed in indexed way!
-%   - compare to indexed VV, previous indexed HH, indexed Pang-Luo
-% - iterated unary/binary parametricity has a semi-simplicial/semi-cubical structure
-% - nu-types as a uniform definition of semi-simplicial/semi-cubical
-%   iterated parametricity gives an alternative presentation of indexed semi-simplicial/semi-cubical
-%   this is what we described in the paper
-% - perspective: models of cubical type theory using indexed cubical sets, hence preserving more definitial rules
-% - mention also the semi-simplicial types problem
-
 \subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
@@
 \end{equation*}
-where $\U$ represents sets in homotopy type theory as the subset of types with a unique proof of equality (within some universe).
+where $\U$ represents in homotopy type theory the subset of types with a unique proof of equality (within some universe).
 
@@
   X_1 & :              & X_0 \rightarrow X_0 \rightarrow \U                                                           \\
-  X_2 & : \Pi a b c d. & X_1(a)(b) \rightarrow X_1(a)(c) \rightarrow X_1 (b)(d) \\
-      &                & \rightarrow X_1 (c)(d) \rightarrow \U                  \\
+  X_2 & : \Pi a b c d. & X_1(a)(b) \rightarrow X_1(a)(c) \rightarrow X_1 (b)(d) \rightarrow X_1 (c)(d) \rightarrow \U \\
   \ldots
@@
 One, by \cite{voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
-Another, by \cite{herbelin15}\footnote{With hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somehow confusing: it was part of a project at defining semi-simplicial types, but, in practice, the definition is done in a type theory with Unicity of Identity Proofs (UIP), meaning in a type theory where types (intended to represent arbitrary $\infty$-groupoids) are actually sets ($0$-truncated $\infty$-groupoids, that is, morally, $0$-groupoids).
-The confusion was however common at that time.}, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
+Another, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it was part of a project for defining semi-simplicial types, but, in practice, the definition is done in a type theory with Unicity of Identity Proofs (UIP), meaning in a type theory where types (intended to represent arbitrary $\infty$-groupoids) are actually sets ($0$-truncated $\infty$-groupoids, that is, morally, $0$-groupoids).
+The confusion was however common at the time.}, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
 Another by~\cite{part15}, formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17}, formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\url{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, also rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
@@
 
-In category-theoretic terms, the indexing set of the family $X_n$ in the indexed presentation is called a \emph{matching object}.
+In category-theoretic terms, the indexing set of the family $X_n$ in the indexed presentation is the \emph{matching object} of the presheaf at $n$.
 The indexed presentation of presheaves over a direct category can then be identified with a subclass of ordinary presheaves known as Reedy fibrant where Reedy fibrancy precisely expresses that the set $X_n$ in the fibered presentation is a $\Sigma$-type over an instance up to isomorphism of the matching object at level $n$~\citep{shulman14,kraus17}.
@@
 We start by first explicitly working out the cases of semi-simplicial and semi-cubical sets.
-%, in a way that is similar to a previous art~(\citeyear{aitchison86}).
 
@@
 \section{Relating to parametricity\label{sec:rel-param}}
-The process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$ in the last section, is similar to applying a binary parametricity translation and expecting the resulting translation to be inhabited.
+Let us recall from the introduction, the form taken by the indexed presentation of a semi-cubical set:
+\begin{align*}
+  X_0 & :              & \U                                                                                           \\
+  X_1 & :              & X_0 \rightarrow X_0 \rightarrow \U                                                           \\
+  X_2 & : \Pi a b c d. & X_1(a)(b) \rightarrow X_1(a)(c) \rightarrow X_1 (b)(d) \rightarrow X_1 (c)(d) \rightarrow \U \\
+  \ldots
+\end{align*}
+
+In there, the process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$, and so on, is similar to iteratively applying a binary parametricity translation.
 The parametricity which we consider interprets a type $A$ by a graph $A_\kstar$ over this type, and a term $t: A$ as an edge in $A_\kstar(t)(t)$.
@@
 
-In Section~\ref{sec:ett} and Tables~\ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces}, \ref{tab:coh}, we give an informal, mathematical definition in Extensional Type Theory, which roughly corresponds to a level of reasoning ``à la set theory'' where equalities are thought as ``holding on the nose'' without having to mention them explicitly once they are justified.
-In Section~\ref{sec:itt}, we give the same mathematical definition in Intensional Type Theory, where transporting along coherence conditions is now made explicit.
+In tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces}, \ref{tab:coh}, we give an informal, mathematical definition in Extensional Type Theory, which roughly corresponds to a level of reasoning ``à la set theory'' where equalities are thought as ``holding on the nose'' without having to mention them explicitly once they are justified.
+In section \ref{sec:itt}, we give the same mathematical definition in Intensional Type Theory, where transporting along coherence conditions is now made explicit.
 Adding this level of details helps to understand the specificities of coherence conditions.
-
-But first, we start with a section gradually and informally explaining the intuition of the construction. It can be read in parallel with the tables if wished.
 
@@
 
-For the presentation corresponding to the formalization in \emph{intensional} type theory, see \ref{sec:itt}.
-
 The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and~\ref{tab:coh}.
@@
 Note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning them anymore.
-For instance, it produces Fig.~\ref{fig:intuition} for $n=2$ and $\nu=2$.
 
@@
 
-We now present the definition in \emph{intensional} type theory~\cite{martinlof84,coq22}, making explicit the need for transport along coherence proofs.
+We now present the definition in \emph{intensional} type theory~\citep{martinlof84,coq22}, making explicit the need for transport along coherence proofs.
 
@@
 
-The way recursion is implemented is still left implicit at this stage. See \ref{sec:mech} for the details.
-
-Depending on how inequality on natural numbers is defined, different equalities may hold or not definitionally, such as transitivity of inequality or the computational properties of induction over inequality proofs.
-Details are given in~\ref{sec:mech}.
+The way recursion is implemented is still left implicit at this stage.
+Also, depending on how inequality on natural numbers is defined, different equalities may hold or not definitionally, such as transitivity of inequality or the computational properties of induction over inequality proofs.
+Details are given in \ref{sec:mech}.
 
@@
 
-Here $\SProp$ is a definitionally proof-irrelevant impredicative universe at the bottom of the universe hierarchy~\cite{gilbert19}.
+Here $\SProp$ is a definitionally proof-irrelevant impredicative universe at the bottom of the universe hierarchy~\citep{gilbert19}.
 By placing the definition in \SProp, we have definitional equality of all inequality proofs.
@@
 \section{Future work}
-In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\cite{nuyts17,cavallo19} by adding degeneracies, a hierarchy of universes (as sketched e.g.
-in a talk by Herbelin at the HoTT-UF workshop for the bridge case~\cite{herbelin-hott-uf}), as well as reasoning modulo permutations~\cite{grandis03}.
-
-By equipping the universe construction with a structure of equivalences, as suggested along the lines of Altenkirch and Kaposi~\cite{altenkirch15}, we expect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\cite{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models.
+In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\citep{nuyts17,cavallo19} by adding degeneracies, a hierarchy of universes (as sketched e.g.
+in a talk by Herbelin at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf})), as well as reasoning modulo permutations~\citep{grandis03}.
+
+By equipping the universe construction with a structure of equivalences, as suggested along the lines of Altenkirch and Kaposi~(\citeyear{altenkirch15}), we expect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models.
 This would a priori preserve definitional properties which may be lost when detouring via presheaves.

### 2023-07-22 paper/paper.tex
paper: cooking some plans for restructuring

@@
 We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, called $\textsf{bool}$, and the type of natural numbers.
+We also assume that our type theory includes the coinductive type of infinite tuples.
 We also write $\hd$ and $\tl$ the projections of dependent pairs, and $\refl$ for reflexivity.
@@
 Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and the uniform treatment of augmented semi-simplicial and semi-cubical sets by means of the generalization to $\nu$-sets.
+
+% 5. The "mathematical" construction (and its intuition)
+%   leaving equality and inequality side conditions implicit
+%   in particular, this means:
+%   - assuming equality reflection
+%   - equality as in observational type theory
+%   - assuming termination of recursive constructions
+% 6. Formal details
+% - making substitution of equals by equals explicit
+% - observational properties of equality
+% - the theory of inequality proofs
+% - the well-foundedness
+% - the formalization tricks
+%   - implicit arguments
+%   - refine-style vs tactic-style
 
@@
 \renewcommandx{\Xfrom}[3][3]{\X[][\geq#2][#3]}
-
-% Hack to remove , in \cohf
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
 
@@
 
-Like in \ref{tab:coh}, we leave implicit in \ref{fulltab:coh}, the use of the isomorphism between the type of equalities of dependent pairs in a $\Sigma$-type with the $\Sigma$-type of equalities of the components of the pair, as well as the isomorphism between equality of functions with point-wise equality.
 Contrary to the ETT case, functional extensionality does not hold, so we assume it.

### 2023-07-30 paper/paper.tex
paper: lots of progress on Our Construction; restructure

@@
 
+We are also interested in \emph{extensional} type theory; i.e.
+in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
+\begin{equation*}
+  \seqr{}{\Gamma \vdash p: t = u}{\Gamma \vdash t \equiv u}
+\end{equation*}
+
 \section{Relating to parametricity\label{sec:rel-param}}
@@
 \section{Our construction}
-Our construction is highly dependent, with dependencies in inequality and equality proofs. It involves several involved details, some of them being visible only in the Coq formalization.
-
-In tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces}, \ref{tab:coh}, we give an informal, mathematical definition in Extensional Type Theory, which roughly corresponds to a level of reasoning ``à la set theory'' where equalities are thought as ``holding on the nose'' without having to mention them explicitly once they are justified.
-In section \ref{sec:itt}, we give the same mathematical definition in Intensional Type Theory, where transporting along coherence conditions is now made explicit.
-Adding this level of details helps to understand the specificities of coherence conditions.
-
-\subsection*{Formal construction in ETT\label{sec:ett}}
+
+From now on, we assume reasoning in type theory, first informally, then, stepwise, in fully formal type theory.
+
+In informal type theory, which would roughly correspond to an extensional type theory leaving implicit trivial steps, our inductive construction is described by tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames} and \ref{tab:faces}.
+However, we went to the point of fully formalizing it in the intentional type theory of the Coq proof assistant.
+Going to such level of details requires to address the following points:
+\begin{itemize}
+  \item Verification that the construction is well-typed: for instance, the typing of $\restrl$, given in Table \ref{tab:faces}, requires a non-trivial coherence condition, given on \ref{tab:coh}, which has to be proved simultaneously with the rest of the construction.
+This proof also relies on type isomorphisms which have to be made explicit.
+All this is discussed in Section ...
+  \item The well-foundedness of the induction requires a special termination evidence which will be discussed in Section ...
+  \item Technically, even if trivial from the mathematical, the components of the construction have side conditions on the range of parameters of the constructions.
+In type theory, this typically corresponds to be dependent on proofs of inequalities on natural numbers.
+We discuss how we deal with such dependencies in Section ...
+  \item The simulation of extensional type theory in intensional type theory requires to make explicit equality reasoning, leading to types of the construction becoming dependent on proofs of equalities.
+This will be discussed in Section ...
+  \item Technically, a number of groupoid properties of equality are also used which will be discussed in Section ...
+\end{itemize}
+
+But first, let us give details and intuition on the informal construction.
+
+\subsection*{The informal construction\label{sec:ett}}
 % Abbreviated tables in this section
@@
 
-We now present the construction in \emph{extensional} type theory; i.e.
-in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
-\begin{equation*}
-  \seqr{}{\Gamma \vdash p: t = u}{\Gamma \vdash t \equiv u}
-\end{equation*}
-
-The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames}, \ref{tab:faces} and~\ref{tab:coh}.
+The definition is thus dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames} and \ref{tab:faces} with~\ref{tab:coh} showing the proof of a needed coherence condition.
 Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a stream, coinductively representing the limit of $n$-truncated $\nu$-sets.
 The $n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.
-In such stream, the $n$th component is a type dependent over a $\fullframe$.
+In such stream, the $n$-th component is a type dependent over a $\fullframe$.
 The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\painting$.
@@
 
-\section{Details on the mechanization\label{sec:mech}}
-\subsection*{Formal construction in ITT\label{sec:itt}}
+\subsection*{From extensional to intentional type theory: explicitation of the equality proofs\label{sec:itt}}
 \renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
 \renewcommandx{\cohl}{\coh{layer}[][][][][][][][]}
-
-We now present the definition in \emph{intensional} type theory~\citep{martinlof84,coq22}, making explicit the need for transport along coherence proofs.
 

### 2023-07-30 paper/paper.tex
paper: more work on Our Construction

@@
   \item Verification that the construction is well-typed: for instance, the typing of $\restrl$, given in Table \ref{tab:faces}, requires a non-trivial coherence condition, given on \ref{tab:coh}, which has to be proved simultaneously with the rest of the construction.
-This proof also relies on type isomorphisms which have to be made explicit.
-All this is discussed in Section ...
-  \item The well-foundedness of the induction requires a special termination evidence which will be discussed in Section ...
+Since this coherence condition is part of the general inductive argument, we will integrate to our discussion on the basic ideas of the construction, in section~\ref{sec:ett}.
+  \item The well-foundedness of the induction requires a special termination evidence which will be discussed in section~\ref{sec:wf}.
   \item Technically, even if trivial from the mathematical, the components of the construction have side conditions on the range of parameters of the constructions.
 In type theory, this typically corresponds to be dependent on proofs of inequalities on natural numbers.
-We discuss how we deal with such dependencies in Section ...
+We discuss how we deal with such dependencies in section~\ref{sec:wf}.
   \item The simulation of extensional type theory in intensional type theory requires to make explicit equality reasoning, leading to types of the construction becoming dependent on proofs of equalities.
-This will be discussed in Section ...
-  \item Technically, a number of groupoid properties of equality are also used which will be discussed in Section ...
+This will be discussed in Section~\ref{sec:itt}.
+  \item Technically, a number of groupoid properties of equality as well as type isomorphisms need to be made explicit. This will be discussed in section~\ref{sec:eqproperties}.
 \end{itemize}
@@
 
-\subsection*{The informal construction\label{sec:ett}}
+\subsection{The construction in informal type theory\label{sec:ett}}
 % Abbreviated tables in this section
@@
 Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, only assuming that we can pick a definition for which proofs of $m \leq n$ are provably unique and thus definitionally equal by the reflection rule.
-
-The construction takes benefit of various provable equalities over proofs of equality being definitional by the reflection rule.
-This includes in particular the groupoid properties of equality.
-Notably, uniqueness of identity proofs holds in extensional type theory, so that any type is automatically an $\U$.
-Also, we left implicit in table~\ref{tab:coh} the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
-(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type.
-In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is function extensionality, holds by default in extensional type theory.
 
@@
 
-\subsection*{From extensional to intentional type theory: explicitation of the equality proofs\label{sec:itt}}
+\subsection{From extensional to intentional type theory: explicitation of the equality proofs\label{sec:itt}}
 \renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
@@
 
-The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit, where the arrow over $\cohf$ indicates the direction of rewrite.
+The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit as follows, where the arrow over $\cohf$ indicates the direction of rewrite:
+
+% insert the fulltab faces table... \input{fulltab:faces}
+
 The proof of $\cohf$ requires making explicit several rewritings which were invisible in extensional type theory.
@@
 
-\subsection*{Finer details}
+\subsection{Well-foundedness of the construction\label{sec:wf}}
 \renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
@@
 
+\subsection{Dependencies in inequality proofs\label{sec:le}}
 The entire construction relies on inequalities over natural numbers, and we use two different definitions of $\leq$ addressing different concerns in our formalization.
@@
 
+\subsection{Groupoid properties of equality and basic type isomorphisms\ref{sec:eqproperties}}
+
+The construction takes benefit of various provable equalities over proofs of equality being definitional by the reflection rule.
+This includes in particular the groupoid properties of equality.
+Notably, uniqueness of identity proofs holds in extensional type theory, so that any type is automatically an $\U$.
+Also, we left implicit in table~\ref{tab:coh} the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
+(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type.
+In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is function extensionality, holds by default in extensional type theory.
+
 \section{Future work}

### 2023-09-17 paper/paper.tex
paper: insert fulltab:faces; improve writing

@@
 
-From now on, we assume reasoning in type theory, first informally, then, stepwise, in fully formal type theory.
+From now on, we assume reasoning in type theory, first informally, then, stepwise, in afully formal type theory implements.u.
 
@@
 \begin{itemize}
-  \item Verification that the construction is well-typed: for instance, the typing of $\restrl$, given in Table \ref{tab:faces}, requires a non-trivial coherence condition, given on \ref{tab:coh}, which has to be proved simultaneously with the rest of the construction.
-Since this coherence condition is part of the general inductive argument, we will integrate to our discussion on the basic ideas of the construction, in section~\ref{sec:ett}.
+  \item Verification that the construction is well-typed: for instance, the typing of $\restrl$, given in table \ref{tab:faces}, requires a non-trivial coherence condition, given on~\ref{tab:coh}, which has to be proved simultaneously with the rest of the construction.
+The informal description of the whole construction, including the coherence condition, is explained in section~\ref{sec:ett}.
   \item The well-foundedness of the induction requires a special termination evidence which will be discussed in section~\ref{sec:wf}.
-  \item Technically, even if trivial from the mathematical, the components of the construction have side conditions on the range of parameters of the constructions.
-In type theory, this typically corresponds to be dependent on proofs of inequalities on natural numbers.
-We discuss how we deal with such dependencies in section~\ref{sec:wf}.
-  \item The simulation of extensional type theory in intensional type theory requires to make explicit equality reasoning, leading to types of the construction becoming dependent on proofs of equalities.
-This will be discussed in Section~\ref{sec:itt}.
-  \item Technically, a number of groupoid properties of equality as well as type isomorphisms need to be made explicit. This will be discussed in section~\ref{sec:eqproperties}.
+  \item The construction is indexed by integers and holds under some constraints on the range of these integers.
+There is a standard formalization dilemma in this kind of situation: either the constraints on the range are embedded in the construction so that the construction makes sense only on the corresponding range, or the construction is made first on a more general domain than needed but restricted to a smaller domain only at the time of use.
+We adopted the first approach, requiring however to let the construction be dependent on proofs of inequalities on natural numbers.
+We discuss how we deal with such dependencies in section~\ref{sec:le}.
+  \item The interpretation of extensional type theory in intensional type theory requires to make explicit equality reasoning, leading to types of the construction becoming dependent on proofs of equalities.
+Our constructions also relies on a few standard type isomorphisms.
+Both issues will be discussed in Section~\ref{sec:itt}.
+  \item Among those equalities, a number of groupoid properties of equality as well as type isomorphisms need to be made explicit. This will be discussed in section~\ref{sec:eqproperties}.
 \end{itemize}
@@
 
-The definition is thus dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames} and \ref{tab:faces} with~\ref{tab:coh} showing the proof of a needed coherence condition.
+The definition is thus dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames} and \ref{tab:faces}.
+The extra table~\ref{tab:coh} shows the proof of a coherence condition use in \ref{tab:faces}.
 Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a stream, coinductively representing the limit of $n$-truncated $\nu$-sets.
@@
 \renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
+
+The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit as follows, where the arrow over $\cohf$ indicates the direction of rewrite:
+
+\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
+\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
+\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommand*{\lab}{fulltab:faces}
+\input{tab-faces.tex}
+
+\renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
 \renewcommandx{\cohl}{\coh{layer}[][][][][][][][]}
-
-The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit as follows, where the arrow over $\cohf$ indicates the direction of rewrite:
-
-% insert the fulltab faces table... \input{fulltab:faces}
-
 The proof of $\cohf$ requires making explicit several rewritings which were invisible in extensional type theory.
@@
 The exact formulation of this coherence condition is as follows.
-\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
 \renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
@@
 
-\subsection{Groupoid properties of equality and basic type isomorphisms\ref{sec:eqproperties}}
+\subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
 

### 2023-09-24 paper/paper.tex
paper: insert fulltab:coh too
paper: rewrite Our construction; other minor prose fixes

@@
 \subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
-A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a given set $S$ or as a set $T$ together with a map specifying for each element of the set $T$ on which index in $S$ it depends.
+A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a given set $S$, or as a set $T$ together with a map specifying for each element of the set $T$ on which index in $S$ it depends.
 In the first case, we call it an \emph{indexed} presentation.
@@
 inverse image, of the index under the map, so we call it a \emph{fibered} presentation.
-The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\cite{hottbook} as a fibered/indexed correspondence\footnote{At a discussion on the Zulip channel for the HoTT community, alternative names fibration/family correspondence and unbundled/bundled correspondence were proposed, among others.
+The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\citep{hottbook} as a fibered/indexed correspondence\footnote{At a discussion on the Zulip channel for the HoTT community, alternative names fibration/family correspondence and unbundled/bundled correspondence were proposed, among others.
 In our experience, the opposition fibered/indexed is spontaneously understood by many listeners.
@@
 The most elementary instance of the correspondence, with $\Type$ instead of $\U$, that is $(\Sigma S: \Type.
-(S \rightarrow T)) \simeq (T \rightarrow \Type)$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see~\cite{hottbook}).}
+(S \rightarrow T)) \simeq (T \rightarrow \Type)$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see \cite{hottbook}).}
 \begin{equation*}
@@
 
-A \emph{presheaf} on an category is a family of sets connected with maps according to the morphisms of the category.
-As such, it lives on the indexed side of the correspondence, opposing on the fibered side to what is called \emph{discrete Grothendieck fibrations}.
+A \emph{presheaf} on an category is a family of sets connected with maps indexed over the morphisms of the category.
+As such, it lives on the indexed side of the correspondence, opposing on the fibered side to \emph{discrete Grothendieck fibrations}~\cite{FIND-A-CITATION}.
 However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the correspondence.
-Indeed, when the indexing category is direct, i.e.
+Indeed, when the indexing category is \emph{direct}, i.e.
 with a downwards-well-founded collection of non-identity morphisms, as is the case of semi-simplicial and semi-cubical sets, each $F(X)$ serving as source of a map $F(X) \stackrel{F(f)}{\rightarrow} F(Y)$ can be turned into a family $F(X)$ indexed on $F(Y)$, and, since the maps are well-founded downward, this can be iterated from below, eventually producing a collection of families which we call an \emph{indexed presentation} of the presheaf over the direct category.
@@
 Another, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it was part of a project for defining semi-simplicial types, but, in practice, the definition is done in a type theory with Unicity of Identity Proofs (UIP), meaning in a type theory where types (intended to represent arbitrary $\infty$-groupoids) are actually sets ($0$-truncated $\infty$-groupoids, that is, morally, $0$-groupoids).
-The confusion was however common at the time.}, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
-Another by~\cite{part15}, formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17}, formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\url{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, also rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
-
-The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence conditions between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex is the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
+The confusion between the question of moving from semi-simplicial sets to semi-simplicial types and the question of moving from a presheaf to an indexed presentation of it was however common at the time.}, and fully formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
+Another by \cite{part15}, formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17}, formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\url{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, also rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
+
+The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence conditions between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex being the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
 On the other side, defining a concrete presheaf in indexed form only requires to provide the family since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition, what is not the case by default in the (ordinary) presheaf presentation.
 
-In category-theoretic terms, the indexing set of the family $X_n$ in the indexed presentation is the \emph{matching object} of the presheaf at $n$.
-The indexed presentation of presheaves over a direct category can then be identified with a subclass of ordinary presheaves known as Reedy fibrant where Reedy fibrancy precisely expresses that the set $X_n$ in the fibered presentation is a $\Sigma$-type over an instance up to isomorphism of the matching object at level $n$~\citep{shulman14,kraus17}.
+In category-theoretic terms, the indexing set of the family $X_n$ in the indexed presentation is a \emph{matching object} of the presheaf at $n$.
+The indexed presentation of presheaves over a direct category can then be identified with a subclass of ordinary presheaves known as Reedy fibrant where Reedy fibrancy precisely expresses that the set $X_n$ in the fibered presentation is a $\Sigma$-type over a representative of the class of equivalence of matching objects at level $n$~\citep{shulman14,kraus17}.
 
@@
 While ordinary semi-simplicial sets are presheaves over the semi-simplex category, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus.
-There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that will later straightforwardly extend to semi-cubical sets.
+There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that can be extended to semi-cubical sets in a straightforward manner.
 
@@
 \section{Our construction}
-
-From now on, we assume reasoning in type theory, first informally, then, stepwise, in afully formal type theory implements.u.
-
-In informal type theory, which would roughly correspond to an extensional type theory leaving implicit trivial steps, our inductive construction is described by tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames} and \ref{tab:faces}.
-However, we went to the point of fully formalizing it in the intentional type theory of the Coq proof assistant.
-Going to such level of details requires to address the following points:
+In this section, we describe our parametricity-based construction of $\nu$-sets in indexed form at different levels of formality:
+
 \begin{itemize}
-  \item Verification that the construction is well-typed: for instance, the typing of $\restrl$, given in table \ref{tab:faces}, requires a non-trivial coherence condition, given on~\ref{tab:coh}, which has to be proved simultaneously with the rest of the construction.
-The informal description of the whole construction, including the coherence condition, is explained in section~\ref{sec:ett}.
+  \item Sections~\ref{sec:ett} and~\ref{sec:itt} describe the construction at an informal level of discourse:
+        \begin{itemize}
+          \item In \ref{sec:ett}, we present it in informal extensional type theory where equational reasoning is left implicit.
+          \item While reasoning in extensional type theory is similar to reasoning in set theory regarding how equality is implicitly handled, extensional type theory has two limitations.
+The first limitation is that it enforces the principle of Uniqueness of Identity Proofs and this is inconsistent with the Univalence principle.
+The second limitation is that we formalized the construction in the Coq proof assistant whose underlying type theory is intensional.
+Section~\ref{sec:itt} thus rephrases the construction in (informal) intensional type theory.
+        \end{itemize}
+  \item Sections~\ref{sec:wf}, \ref{sec:le} and \ref{sec:eqproperties} describe issues to be addressed in order to get a fully formal construction:
+        \begin{itemize}
           \item The well-foundedness of the induction requires a special termination evidence which will be discussed in section~\ref{sec:wf}.
-  \item The construction is indexed by integers and holds under some constraints on the range of these integers.
+          \item The construction is indexed over integers and holds under some constraints on the range of these integers.
 There is a standard formalization dilemma in this kind of situation: either the constraints on the range are embedded in the construction so that the construction makes sense only on the corresponding range, or the construction is made first on a more general domain than needed but restricted to a smaller domain only at the time of use.
@@
 We discuss how we deal with such dependencies in section~\ref{sec:le}.
-  \item The interpretation of extensional type theory in intensional type theory requires to make explicit equality reasoning, leading to types of the construction becoming dependent on proofs of equalities.
-Our constructions also relies on a few standard type isomorphisms.
-Both issues will be discussed in Section~\ref{sec:itt}.
-  \item Among those equalities, a number of groupoid properties of equality as well as type isomorphisms need to be made explicit. This will be discussed in section~\ref{sec:eqproperties}.
+          \item A number of obvious groupoid properties of equality as well as type isomorphisms have been left implicit in the informal definition.
+This is discussed in section~\ref{sec:eqproperties}.
         \end{itemize}
-
-But first, let us give details and intuition on the informal construction.
+\end{itemize}
 
@@
 
-The definition is thus dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames} and \ref{tab:faces}.
+The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames} and \ref{tab:faces}.
 The extra table~\ref{tab:coh} shows the proof of a coherence condition use in \ref{tab:faces}.
-Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a stream, coinductively representing the limit of $n$-truncated $\nu$-sets.
-The $n$-truncated $\nu$-sets are themselves described in \ref{tab:core}.
-In such stream, the $n$-th component is a type dependent over a $\fullframe$.
+Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a coinductively-defined infinite sequence of types representing the limit over $n$ of a $n$-truncated $\nu$-set.
+The definition of a $n$-truncated $\nu$-set is in turn described in \ref{tab:core}.
+In the infinite sequence of types representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$.
 The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\painting$.
@@
 
+% Insert fulltab:faces and fulltab:coh, after overriding macros to make
+% everything but the universe letter explicit.
 \renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
@@
 \renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
 \renewcommand*{\lab}{fulltab:faces}
 \input{tab-faces.tex}
+\renewcommand*{\lab}{fulltab:coh}
+\input{tab-coh.tex}
 

### 2023-09-24 paper/paper.tex
paper: remove Outline

@@
 
-\subsection*{Outline}
-The outline of the paper is as follows.
-We recall the definition of the augmented semi-simplicial and semi-cubical categories using a combinatorial presentation, that directly leads to our generalization to $\nu$-sets, in \ref{sec:nu}.
-Before spelling out the details of our formalization in type-theoretic language in \ref{sec:ett} and \ref{sec:itt}, we give intuitions in \ref{sec:intuition}.
-We end with some of the finer details of our mechanization in \ref{sec:mech}.
-
 See \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak} for our mechanization.
@@
           \item While reasoning in extensional type theory is similar to reasoning in set theory regarding how equality is implicitly handled, extensional type theory has two limitations.
-The first limitation is that it enforces the principle of Uniqueness of Identity Proofs and this is inconsistent with the Univalence principle.
-The second limitation is that we formalized the construction in the Coq proof assistant whose underlying type theory is intensional.
+The first limitation is that it enforces the principle of Uniqueness of Identity Proofs and this is inconsistent with the Univalence principle, thus making it inexpressible in Homotopy Type Theory.
+The second limitation is that we want the construction to be formalizable in the Coq proof assistant whose underlying type theory is intensional.
 Section~\ref{sec:itt} thus rephrases the construction in (informal) intensional type theory.
         \end{itemize}
-  \item Sections~\ref{sec:wf}, \ref{sec:le} and \ref{sec:eqproperties} describe issues to be addressed in order to get a fully formal construction:
+  \item Sections~\ref{sec:wf}, \ref{sec:le}, and \ref{sec:eqproperties} describe issues to be addressed in order to get a fully formal construction:
         \begin{itemize}
@@
 The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames} and \ref{tab:faces}.
-The extra table~\ref{tab:coh} shows the proof of a coherence condition use in \ref{tab:faces}.
-Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a coinductively-defined infinite sequence of types representing the limit over $n$ of a $n$-truncated $\nu$-set.
+The extra table~\ref{tab:coh} shows the proof of a coherence condition used in \ref{tab:faces}.
+Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a coinductively-defined infinite sequence of types representing the limit of $n$-truncated $\nu$-sets.
 The definition of a $n$-truncated $\nu$-set is in turn described in \ref{tab:core}.

### 2023-09-24 paper/paper.tex
paper: polish sec:ett a bit

@@
 In the infinite sequence of types representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$.
-The type $\fullframe$ is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\layer$ and $\painting$.
-The type $\layer$ and $\painting$ are dependent over $\restrf$, and these restrictions are defined on \ref{tab:faces}.
-These restrictions are defined using auxiliary definitions of $\restrl$ and $\restrc$.
-
-Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$.
+The type $\fullframe$ represents a matching object.
+It is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
+The type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in \ref{tab:faces}.
+This restriction operator is defined using the auxiliary definitions of $\restrl$ and $\restrc$.
+
+Notably, the definition of $\restrl$ relies on an equality expressing the commutation of the composition of $\restrf$.
 This commutation is not provable by computation so we have to prove it propositionally before using the reflection rule.
@@
 This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$.
-Even though it looks independent of the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
+Even though it looks independent of the definitions from the the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
 More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be mutually defined by induction on $p$.
@@
 Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
-We leave however implicit the exact way this mutual recursion can be formalized at this stage of the paper.
+The exact way this mutual recursion is eventually formalized is explained in section~\ref{sec:wf}.
 
 Most components of the construction takes inequality constraints as parameters, and we have left implicit that they are satisfied in the tables.
-Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, only assuming that we can pick a definition for which proofs of $m \leq n$ are provably unique and thus definitionally equal by the reflection rule.
-
-Note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning them anymore.
+Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, only assuming that we can pick a definition for which proofs of $m \leq n$ are provably unique and thus definitionally equal by the reflection rule (formal details are given in section~\ref{sec:le}).
+
+Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that the construction builds an effective sequence of types not mentioning coherences anymore.
 
@@
 
-\subsection{From extensional to intentional type theory: explicitation of the equality proofs\label{sec:itt}}
+\subsection{From extensional to intentional type theory: explication of the equality proofs\label{sec:itt}}
 \renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
@@
 Also, depending on how inequality on natural numbers is defined, different equalities may hold or not definitionally, such as transitivity of inequality or the computational properties of induction over inequality proofs.
-Details are given in \ref{sec:mech}.
 

### 2023-10-01 paper/paper.tex
Micro-changes

@@
 There is a standard formalization dilemma in this kind of situation: either the constraints on the range are embedded in the construction so that the construction makes sense only on the corresponding range, or the construction is made first on a more general domain than needed but restricted to a smaller domain only at the time of use.
-We adopted the first approach, requiring however to let the construction be dependent on proofs of inequalities on natural numbers.
+We adopted the first approach, requiring however the construction to be dependent on proofs of inequalities on natural numbers.
 We discuss how we deal with such dependencies in section~\ref{sec:le}.
-          \item A number of obvious groupoid properties of equality as well as type isomorphisms have been left implicit in the informal definition.
+          \item A number of standard groupoid properties of equality as well as type isomorphisms have been left implicit in the informal definition.
 This is discussed in section~\ref{sec:eqproperties}.
@@
 The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames} and \ref{tab:faces}.
-The extra table~\ref{tab:coh} shows the proof of a coherence condition used in \ref{tab:faces}.
+The extra table~\ref{tab:coh} shows the proof of a coherence condition used implicitly in \ref{tab:faces}.
 Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a coinductively-defined infinite sequence of types representing the limit of $n$-truncated $\nu$-sets.

### 2023-10-01 paper/paper.tex
paper: changes to Our Construction

@@
 In there, the process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$, and so on, is similar to iteratively applying a binary parametricity translation.
-The parametricity which we consider interprets a type $A$ by a graph $A_\kstar$ over this type, and a term $t: A$ as an edge in $A_\kstar(t)(t)$.
-In particular, $\U$ is interpreted as the graph ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \rightarrow A_R \rightarrow \U$ of graphs over $A_L$ and $A_R$.
+The parametricity which we consider interprets a type $A$ by a family $A_\kstar$ of edges in a graph over $A$, and a term $t: A$ as an edge in $A_\kstar(t)(t)$.
+To each type constructor is then associated the construction of a graph.
+In particular, the type of types $\U$ is interpreted as the family of families ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \rightarrow A_R \rightarrow \U$ of families of edges over $A_L$ and $A_R$.
 Also, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the graph $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
 \begin{align*}
-   & (\Pi a: A.\, B)_\kstar(f_L)(f_R) \defeq                                                      \\
-   & \Pi a_L: A.\, \Pi a_R: A.\, \Pi a_\kstar: A_\kstar(a_L)(a_R).\, B_\kstar(f_L(a_L))(f_R(a_R))
+  (\Pi a: A.\, B)_\kstar(f_L)(f_R) \; \defeq \; \Pi a_L: A.\, \Pi a_R: A.\, \Pi a_\kstar: A_\kstar(a_L)(a_R).\, B_\kstar(f_L(a_L))(f_R(a_R))
 \end{align*}
@@
         \end{itemize}
-  \item Sections~\ref{sec:wf}, \ref{sec:le}, and \ref{sec:eqproperties} describe issues to be addressed in order to get a fully formal construction:
+  \item Sections~\ref{sec:wf}, \ref{sec:le}, and \ref{sec:eqproperties} describe additional issues to be addressed in order to get a fully formal construction:
         \begin{itemize}
@@
 
-The definition is dispatched over tables \ref{tab:coind}, \ref{tab:core}, \ref{tab:frames} and \ref{tab:faces}.
-The extra table~\ref{tab:coh} shows the proof of a coherence condition used implicitly in \ref{tab:faces}.
-Table \ref{tab:coind} describes a $\nu$-set in indexed form, as a coinductively-defined infinite sequence of types representing the limit of $n$-truncated $\nu$-sets.
+We use the type $\U$ to represent $\nu$-sets in type theory and fix for that purpose a universe level $m$, that is, we define $\nu$-sets at level $m$ living in $\U[m+1]$.
+
+Table \ref{tab:coind} describes a $\nu$-set at level $m$ in indexed form, as a coinductively-defined infinite sequence of types representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set $\Xto{m}{n}$ so that, when $m$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
+This is made possible because the $0$-truncated $\nu$-set $\Xto{m}{n}$ is degenerated: it is defined to be the unit type and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
+
 The definition of a $n$-truncated $\nu$-set is in turn described in \ref{tab:core}.
@@
 It is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
-The type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in \ref{tab:faces}.
-This restriction operator is defined using the auxiliary definitions of $\restrl$ and $\restrc$.
+The rationale behind $\framep$, $\layer$ and $\painting$ will be explained later but it should already be noticed that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in \ref{tab:faces}, and this restriction operator is in turn defined using the auxiliary definitions of $\restrl$ and $\restrc$.
 
 Notably, the definition of $\restrl$ relies on an equality expressing the commutation of the composition of $\restrf$.
-This commutation is not provable by computation so we have to prove it propositionally before using the reflection rule.
-Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\painting$.
-This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$.
+The proof of this commutation is worth being made explicit, which we do in table \ref{tab:coh} using proof-term notations.
+The proof requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\painting$.
+This is what $\cohf$ does using auxiliary proofs $\cohl$ and $\cohc$.
 Even though it looks independent of the definitions from the the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
@@
 Also, each of $\painting$, $\restrc$, and $\cohc$ is built by induction from $p$ to $n$.
-The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but, the converse dependency is only on lower $n$, so this is well-founded.
+The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but the converse dependency is only on lower $n$, so this is well-founded.
 Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
 The exact way this mutual recursion is eventually formalized is explained in section~\ref{sec:wf}.
-
-Most components of the construction takes inequality constraints as parameters, and we have left implicit that they are satisfied in the tables.
-Comparison of inequality proofs depends on the definition of inequality, which we leave implicit, only assuming that we can pick a definition for which proofs of $m \leq n$ are provably unique and thus definitionally equal by the reflection rule (formal details are given in section~\ref{sec:le}).
 

### 2023-10-08 paper/paper.tex
paper: lots of minor corrections

@@
 
-Unless otherwise specified, we fix a universe level $m$ and abbreviate
-$\Type_m$ as $\Type$ and $\U[m]$ as $\U$.
+By the notations $\Type$ and $\U$ will be meant $\Type_m$ or $\U[m]$ at some unspecified universe level $m$.
 
 We are also interested in \emph{extensional} type theory; i.e.
-in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
+in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\citep{martinlof84}:
 \begin{equation*}
@@
 
-We use the type $\U$ to represent $\nu$-sets in type theory and fix for that purpose a universe level $m$, that is, we define $\nu$-sets at level $m$ living in $\U[m+1]$.
-
-Table \ref{tab:coind} describes a $\nu$-set at level $m$ in indexed form, as a coinductively-defined infinite sequence of types representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set $\Xto{m}{n}$ so that, when $m$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
-This is made possible because the $0$-truncated $\nu$-set $\Xto{m}{n}$ is degenerated: it is defined to be the unit type and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
-
-The definition of a $n$-truncated $\nu$-set is in turn described in \ref{tab:core}.
-In the infinite sequence of types representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$.
+A $\nu$-set is a sequence of families of $\U$, that is $\U[m]$ for some universe level $m$. We call such sequence a $\nu$-set at level $m$, whose type thus lives in $\U[m+1]$.
+
+Table \ref{tab:coind} describes the type of a $\nu$-set at level $m$ in indexed form, as the type of a coinductively-defined infinite sequence of type families representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $m$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
+This is made possible because the $0$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, defined to be the unit type, and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
+
+The definition of the type of a $n$-truncated $\nu$-set is in turn described in \ref{tab:core}.
+In the infinite sequence of type families representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$.
 The type $\fullframe$ represents a matching object.
@@
 \subsection*{Intuition for our formal construction\label{sec:intuition}}
+\renewcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}
 \renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
@@
 
-To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on building blocks, which we call $\framep$, $\layer$, and $\painting$.
+To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on the building blocks which we call $\framep$, $\layer$, and $\painting$.
 A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$, and a $\painting$ corresponds to a filled $\framep$.
-Some $\framep$ are full and we call them $\fullframe$.
-
-We assign every $X_n$ the type $\fullframe[n] \rightarrow \U$ uniformly, applying to the description above the isomorphism between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$.
+Some $\framep$ are full and we call them $\fullframe$: they represent matching objects.
+
+To every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
+Compared to the informal description given in section~\ref{sec:rel-param}, e.g.
+$X_1 : X_0 \rightarrow X_0 \rightarrow \U$, this amounts to apply the isomorphisms between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$ so as to get the expected form $\fullframe[n] \rightarrow \U$..
 In particular, $\fullframe[n]$ is a ``telescope'', i.e.
-a nesting of $\Sigma$-type.
-Let us now illustrate how we build $\fullframe[n]$.
-To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ of $X_0$ can be equivalently formulated as $\unittype \rightarrow \U$.
+a nesting of $\Sigma$-types.
+
+Let us now illustrate how we recursively build $\fullframe[n]$.
+To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ given to $X_0$ in section~\ref{sec:rel-param} can be equivalently formulated as $\unittype \rightarrow \U$.
 Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
@@
 
-The figure on the left is $\framep[3][1]$, on the right is $\framep[3][2]$, and on the bottom is $\framep[3][3]$, which is full.
+The figure on the left is $\framep[3][1]$, in the middle is $\framep[3][2]$, and on the right is $\framep[3][3]$, which is full.
 Further, $\framep[3][1]$ is made of one layer, $\layer[3][0]$, shown in blue, $\framep[3][2]$ is made of one additional layer, $\layer[3][1]$, shown in red, $\framep[3][3]$ is made of one more layer, $\layer[3][2]$, shown in green.
@@
 
-So far, we have not paid attention to the fact that we have a dependent type, shown as a $\Sigma$.
+So far, we have not paid attention to the fact that we have a dependent type, shown as a $\Sigma$-type.
 Let us be more precise about this requirement.
 First, $\fullframe[n]$ depends on all $X_i$ up to $n - 1$.
-So, we need to package up $X_i$, for $i < n$, into a nesting of $\Sigma$-types, which we abbreviate as $\X[][<n][]$.
+So, we need to package up $X_i$, for $i < n$, into a nesting of $\Sigma$-types, constituting the type of a $n$-truncated $\nu$-set, which we wrote $\X[][<n][]$.
 This allows us to give the type $\X[][<n][] \rightarrow \U$ to $\fullframe[n]$.
@@
 Thus, $\framep[n][p]$, $\layer[n][p]$ and $\painting[n][p]$ also depend on $D$.
-We can then refine the previous equation by showing the dependencies on $D$.
-In particular, $X_n$ is just $D.\tl$.
+We can then reformulate the previous equation with its dependency on $D$.
+In particular, $X_n$ is just the last component of $D$, that is $D.\tl$.
 \begin{equation*}
@@
 
-An extra refinement arises from the fact that each addition of a layer to a frame has to be glued onto the border of the partial frame built so far.
+An extra refinement arises from the fact that each new layer of a frame has to be glued onto the border of the partial frame built so far.
 So, each $\layer[n][p]$ has to depend on $\framep[n][p]$.
-We also need a way to characterize the border of the $\nu$ $\painting[n-1][p]$ that compose a $\layer[n][p]$, and this is $\restrf[n][p][\epsilon][p]$, for all $\epsilon < \nu$.
+We also need a way to characterize the border of the $\nu$ $\painting[n-1][p]$ that compose a $\layer[n][p]$, and this is where the restriction $\restrf[n][p][\epsilon][p]$ is involved, for each $\epsilon < \nu$.
 For instance, on the picture, the left and right $\painting[2][1]$, shown in red, are laid on respectively the left and right borders of the blue boxes, and hence needs to depend on $\framep[3][1]$.
 The left and right borders of the two blue boxes are extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$.
-We can then refine the previous equation by showing the dependencies on $d$, as shown below.
+We can then refine again the previous equation by showing the dependencies on $d$, as shown below.
 
@@
 
-The operation $\restrf[n][p][\epsilon][q]$ indicates restriction on $q$ layers of a frame, and the induction is on $p$, from $0$ to $q$.
+The operation $\restrf[n][p][\epsilon][q]$ restricts the $p$ first layers of a frame, and the induction is on $p$, from $0$ to $q$.
 In particular, $\restrf[n][p][\epsilon][p]$ is a ``full restriction''.
-We define $\restrf[n][p][\epsilon][p](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$ and $c$ a $\painting$.
+We define $\restrf[n][p][\epsilon][q](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$ and $c$ a $\painting$.
 The key case is $\restrc[n][p][\epsilon][p](d)(c)$, where $c$, a $\painting[n][p]$, has necessarily the form of $((c_L, c_R), \_)$: $\restrc[n][p][L][p]$ picks out $c_L$, a $\painting[n-1][p]$, $\restrc[n][p][R][p]$ picks out the $c_R$, also a $\painting[n-1][p]$, and $\_$, a $\painting[n][p+1]$, is discarded.
@@
 \subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
-
 The construction takes benefit of various provable equalities over proofs of equality being definitional by the reflection rule.

### 2023-10-08 paper/paper.tex
paper: changes to sec:itt mainly

@@
 \end{equation*}
+
+Note that the reflection rule implies UIP so that $\U$ and $\Type$ ae equivalent in extensional type theory.
+The reflection rules also implies functional extensionality, and, actually, extensional type theory is logically equivalent to intentional type theory extended with UIP and functional extensionality~\citep{HofmannPhd}.
 
@@
 
-\subsection*{Intuition for our formal construction\label{sec:intuition}}
+\subsection{Intuition for our formal construction\label{sec:intuition}}
 \renewcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}
@@
 So, each $\layer[n][p]$ has to depend on $\framep[n][p]$.
-We also need a way to characterize the border of the $\nu$ $\painting[n-1][p]$ that compose a $\layer[n][p]$, and this is where the restriction $\restrf[n][p][\epsilon][p]$ is involved, for each $\epsilon < \nu$.
+We also need a way to characterize the $\nu$ borders of each $\painting[n-1][p]$ that composes a $\layer[n][p]$, and this is where the restriction $\restrf[n][p][\epsilon][p]$ arrives, for each $\epsilon < \nu$.
 For instance, on the picture, the left and right $\painting[2][1]$, shown in red, are laid on respectively the left and right borders of the blue boxes, and hence needs to depend on $\framep[3][1]$.
@@
 
-The operation $\restrf[n][p][\epsilon][q]$ restricts the $p$ first layers of a frame, and the induction is on $p$, from $0$ to $q$.
-In particular, $\restrf[n][p][\epsilon][p]$ is a ``full restriction''.
-We define $\restrf[n][p][\epsilon][q](d)$ by recursion on the structure of a frame $d$, which necessitates definitions of $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$ and $c$ a $\painting$.
+The operation $\restrf[n][p][\epsilon][q]$ restricts the $p$ first layers of a frame, and the construction is by recursion on the structure of a frame $d$.
+This necessitates the definitions $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$ and $c$ a $\painting$.
 The key case is $\restrc[n][p][\epsilon][p](d)(c)$, where $c$, a $\painting[n][p]$, has necessarily the form of $((c_L, c_R), \_)$: $\restrc[n][p][L][p]$ picks out $c_L$, a $\painting[n-1][p]$, $\restrc[n][p][R][p]$ picks out the $c_R$, also a $\painting[n-1][p]$, and $\_$, a $\painting[n][p+1]$, is discarded.
-There is one more difficulty, which we illustrate by writing down expected and actual types.
+There is one last difficulty, which we illustrate by writing down expected and actual types.
 
@@
 \end{align*}
-$\restrl[n][p][\epsilon](d)(c_L, c_R)$ produces a layer, in which the $\omega$-component has the type
+$\restrl[n][p][\epsilon](d)(c_L, c_R)$ produces a layer in which the $\omega$-component has the type
 \begin{equation*}
@@
 \end{equation*}
-while we expect a term of type
+while we expect a component of type
 \begin{equation*}
@@
 Hence, we need a coherence condition to commute the restrictions.
-Coherence conditions similar to this necessitate, what are shown as, $\cohf$, $\cohl$ and $\cohc$ in tables in the next section.
+Coherence conditions similar to this necessitate what are shown as, $\cohf$, $\cohl$ and $\cohc$ in table~\ref{tab:coh}.
 These are by induction on the structure of $\framep$, $\layer$ and $\painting$.
-Note that, for the construction in \ref{sec:itt}, we further need a $2$-dimensional coherence condition, $\coht$, for $\cohl$.
+Note that, for the construction in intentional type theory, we further need a $2$-dimensional coherence condition, $\coht$, for $\cohl$.
+This is explained in the next section.
 
@@
 
-The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit as follows, where the arrow over $\cohf$ indicates the direction of rewrite:
+In this section, we intend to get rid of the reflection rule and make explicit what is needed to rephrase the construction from extensional type theory to intentional type theory.
+For readability purpose, we however make explicit only the key coherence conditions of the construction.
+Other form of equality reasoning would have to be made explicit to obtain a construction fully in intentional type theory but these other steps are standard enough to be omitted at this stage.
+See section~\ref{sec:eqproperties} for the details.
+
+The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit in table~\ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
 
@@
 \renewcommandx{\cohl}{\coh{layer}[][][][][][][][]}
-The proof of $\cohf$ requires making explicit several rewritings which were invisible in extensional type theory.
+\renewcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
+The proof of $\cohf$ itself requires making explicit several rewritings which were invisible in extensional type theory.
 The commutation of $\restrl$ lives in a type referring to $\cohf$, so we need a transport along the commutation of $\restrf$ in the statement of $\cohl$.
-The proof of $\cohl$ is the most involved proof in the construction.
-This is where the higher-dimensional coherence condition is needed.
-The exact formulation of this coherence condition is as follows.
+The proof of $\cohl$ is the most involved proof of the construction.
+It requires a higher-dimensional coherence condition, $\coht$, whose exact formulation is as follows.
 \renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
@@
 \renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
 \begin{align*}
@@
 \end{align*}
-where $\mathsf{ap}$ applies a function on two sides of an equality, and $\bullet$ is transitivity of equality.
+where $\ap$ applies a function on two sides of an equality, and $\bullet$ is transitivity of equality.
 This property of equality proofs holds in \U, and since our formalization is done in \U, the term is trivially discharged.
@@
 In the proof term of $\cohl$, $\cohc$ has one $\cohf$ rewrite on its left-hand side and zero on the right-hand side.
-This combined with the two terms of the form $\ap \cohf$ matches our expectation of three $\cohf$ on the left-hand side and two $\cohf$ on the right-hand side.
+This, combined with the two terms of the form $\ap \cohf$, matches our expectation of three $\cohf$ on the left-hand side and two $\cohf$ on the right-hand side.
 Then, $\coht$ can roughly be seen as a commutation of these $\cohf$ terms.
@@
 
-Contrary to the ETT case, functional extensionality does not hold, so we assume it.
-However, the requirement of functional extensionality disappears if $\nu$ is finite.
-As for basic groupoid properties of equalities, which no longer hold definitionally, we do not mention them for simplicity.
-
-The way recursion is implemented is still left implicit at this stage.
-Also, depending on how inequality on natural numbers is defined, different equalities may hold or not definitionally, such as transitivity of inequality or the computational properties of induction over inequality proofs.
-
-Remark: If we were not working in \U, but in \HGpd, we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences.
+If we were not working in \U, but in $\HGpd$ we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences.
 Here, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x = y$ is in \U.
@@
 (u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type.
-In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is function extensionality, holds by default in extensional type theory.
+In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is functional extensionality, holds by default in extensional type theory.
 

### 2023-10-08 paper/paper.tex
paper/sec:eqproperties: polish

@@
 In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is functional extensionality, holds by default in extensional type theory.
+As a final remark, note, as a consequence of $\eta$-conversion for finite enumerated types, that the requirement of functional extensionality disappears when $\nu$ is finite.
+However, this is a conversion which Coq does not implement, so, in Coq, the alternative would be to replace $\Pi a: \nu.\, B$ by a ``flat'' iterated product $B(1) \times B(2) \times \ldots \times B(\nu)$.
 

### 2023-11-05 paper/paper.tex
Citation discrete fibrations

@@
 A \emph{presheaf} on an category is a family of sets connected with maps indexed over the morphisms of the category.
-As such, it lives on the indexed side of the correspondence, opposing on the fibered side to \emph{discrete Grothendieck fibrations}~\cite{FIND-A-CITATION}.
+As such, it lives on the indexed side of the correspondence, opposing on the fibered side to \emph{discrete Grothendieck fibrations}~\cite{LoregianRiehl20}.
 However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the correspondence.

### 2023-11-05 paper/paper.tex
paper: polish first few paragraphs

@@
 \subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
-A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a given set $S$, or as a set $T$ together with a map specifying for each element of the set $T$ on which index in $S$ it depends.
-In the first case, we call it an \emph{indexed} presentation.
-In the latter case, the set associated to a given index is the fiber, i.e.
-inverse image, of the index under the map, so we call it a \emph{fibered} presentation.
-The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\citep{hottbook} as a fibered/indexed correspondence\footnote{At a discussion on the Zulip channel for the HoTT community, alternative names fibration/family correspondence and unbundled/bundled correspondence were proposed, among others.
-In our experience, the opposition fibered/indexed is spontaneously understood by many listeners.
-In particular, it echoes to the Grothendieck construction of fibered categories from indexed categories.
-The most elementary instance of the correspondence, with $\Type$ instead of $\U$, that is $(\Sigma S: \Type.
-(S \rightarrow T)) \simeq (T \rightarrow \Type)$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see \cite{hottbook}).}
-\begin{equation*}
-  \mbox{(fibered)}\qquad(\Sigma S: \U. (S \rightarrow T)) ~\simeq~ (T \rightarrow \U)\qquad \mbox{(indexed)}
-\end{equation*}
-where $\U$ represents in homotopy type theory the subset of types with a unique proof of equality (within some universe).
+A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over the elements of a given set $S$, or as a set $T$ together with a map from $T$ to $S$, which specifies for each element of set $T$ its dependency on $S$.
+In the former case, we call it an \emph{indexed} presentation.
+In the latter case, the set associated to a given element of $S$ is the fiber of this element, so we call it a \emph{fibered} presentation.
+The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\citep{hottbook} as the fibered/indexed correspondence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family correspondence and unbundled/bundled correspondence.
+The fibered/indexed nomenclature echoes the Grothendieck construction of fibered categories from indexed categories.
+The most elementary instance of the correspondence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see \cite{hottbook}).}.
+\begin{equation*}
+  \mbox{(fibered)}\qquad(\Sigma T: \U. (T \rightarrow S)) ~\simeq~ (S \rightarrow \U)\qquad \mbox{(indexed)}
+\end{equation*}
+where $\U$ represents in homotopy type theory the subset of types within a given universe where equality of any two elements has at most one proof.
 
 A \emph{presheaf} on an category is a family of sets connected with maps indexed over the morphisms of the category.
-As such, it lives on the indexed side of the correspondence, opposing on the fibered side to \emph{discrete Grothendieck fibrations}~\cite{LoregianRiehl20}.
+As such, it lives on the indexed side of the correspondence, contrasting with the fibered side, where we have \emph{discrete Grothendieck fibrations}~\cite{LoregianRiehl20}.
 However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the correspondence.
-Indeed, when the indexing category is \emph{direct}, i.e.
-with a downwards-well-founded collection of non-identity morphisms, as is the case of semi-simplicial and semi-cubical sets, each $F(X)$ serving as source of a map $F(X) \stackrel{F(f)}{\rightarrow} F(Y)$ can be turned into a family $F(X)$ indexed on $F(Y)$, and, since the maps are well-founded downward, this can be iterated from below, eventually producing a collection of families which we call an \emph{indexed presentation} of the presheaf over the direct category.
-
-For instance, in the case of a semi-cubical set~\citep{grandis03,buchholtz17}, presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes, the standard presheaf approach prescribes a family of sets fibered the ones over the others (up to cubical faces identities).
+This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.
+This is the case in semi-simplicial and semi-cubical sets, where each $F(X)$ serving as source of a map $F(X) \stackrel{F(f)}{\rightarrow} F(Y)$ can be turned into a family $F(X)$ indexed on $F(Y)$.
+Since the maps are well-founded downward, this can be iterated from below, eventually producing a collection of families which we call an indexed presentation of the presheaf over the direct category.
+
+For instance, in the case of a semi-cubical set~\citep{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes, the standard presheaf approach prescribes a family of sets fibered the ones over the others (up to cubical faces identities).
 Formulated in type theory, it corresponds to:

### 2023-11-05 paper/paper.tex
paper: major polish; remove some ugly itemize

@@
 A \emph{presheaf} on an category is a family of sets connected with maps indexed over the morphisms of the category.
-As such, it lives on the indexed side of the correspondence, contrasting with the fibered side, where we have \emph{discrete Grothendieck fibrations}~\cite{LoregianRiehl20}.
+As such, it lives on the indexed side of the correspondence, contrasting with the fibered side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
 However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the correspondence.
@@
 
-For instance, in the case of a semi-cubical set~\citep{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes, the standard presheaf approach prescribes a family of sets fibered the ones over the others (up to cubical faces identities).
-Formulated in type theory, it corresponds to:
+Let us consider, for instance, the case of a semi-cubical set~\citep{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
+Formulated in type theory, the corresponding presheaf definition of a semi-cubical set prescribes a family of sets and face
+maps between them as follows:
 
@@
 \end{equation*}
-
-On the other side, the indexed presentation of the same presheaf is a stratified sequence of families indexed on elements of families of lower rank, taking into account the coherence conditions to prevent duplications.
+up to cubical faces identities.
+In it, $X_1$ can be seen as a family over $X_0 \times X_0$ presented in a fibered form, $X_2$ can be seen as a family of $X_1 \times X_1 \times X_1 \times X_1$, and so on.
+This suggests an alternative indexed presentation of the same presheaf as a stratified sequence of families indexed on elements of families of lower rank, taking into account the coherence conditions to prevent duplications.
 Formulated in type theory, it takes the form:
@@
   X_0 & :              & \U                                                                                           \\
-  X_1 & :              & X_0 \rightarrow X_0 \rightarrow \U                                                           \\
-  X_2 & : \Pi a b c d. & X_1(a)(b) \rightarrow X_1(a)(c) \rightarrow X_1 (b)(d) \rightarrow X_1 (c)(d) \rightarrow \U \\
+  X_1 & :              & X_0 \times X_0 \rightarrow \U                                                           \\
+  X_2 & : \Pi a b c d. & X_1(a)(b) \times X_1(a)(c) \times X_1 (b)(d) \times X_1 (c)(d) \rightarrow \U \\
   \ldots
@@
 
-The idea for such indexed presentation of presheaves over a direct category was mentioned at the Univalent Foundations year in the context of defining semi-simplicial types~\footnote{See e.g.
+The idea for such an indexed presentation of presheaves over a direct category was mentioned at the Univalent Foundations year in the context of defining semi-simplicial types~\footnote{See e.g.
 \url{https://ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}.}.
@@
 One, by \cite{voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
-Another, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it was part of a project for defining semi-simplicial types, but, in practice, the definition is done in a type theory with Unicity of Identity Proofs (UIP), meaning in a type theory where types (intended to represent arbitrary $\infty$-groupoids) are actually sets ($0$-truncated $\infty$-groupoids, that is, morally, $0$-groupoids).
-The confusion between the question of moving from semi-simplicial sets to semi-simplicial types and the question of moving from a presheaf to an indexed presentation of it was however common at the time.}, and fully formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
+Another, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it was part of a project for defining semi-simplicial types, but, in practice, the definition is done in a type theory with Unicity of Identity Proofs, meaning, in a type theory where types (intended to represent arbitrary $\infty$-groupoids) are actually sets ($0$-truncated $\infty$-groupoids or $0$-groupoids).
+The confusion between the question of moving from semi-simplicial sets to semi-simplicial types, and moving from a presheaf to an indexed presentation was, however, common at the time.}, and fully formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
 Another by \cite{part15}, formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17}, formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\url{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, also rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
 
-The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence conditions between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex being the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
-On the other side, defining a concrete presheaf in indexed form only requires to provide the family since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition, what is not the case by default in the (ordinary) presheaf presentation.
+The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition, as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence conditions between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex being the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
+However, defining a concrete presheaf in indexed form only requires providing the family, since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition.
 
 In category-theoretic terms, the indexing set of the family $X_n$ in the indexed presentation is a \emph{matching object} of the presheaf at $n$.
-The indexed presentation of presheaves over a direct category can then be identified with a subclass of ordinary presheaves known as Reedy fibrant where Reedy fibrancy precisely expresses that the set $X_n$ in the fibered presentation is a $\Sigma$-type over a representative of the class of equivalence of matching objects at level $n$~\citep{shulman14,kraus17}.
+The indexed presentation of presheaves over a direct category can then be identified with a subclass of ordinary presheaves known as Reedy fibrant, where Reedy fibrancy precisely expresses that the set $X_n$ in the fibered presentation is a $\Sigma$-type over a representative of the class of equivalence of matching objects at level $n$~\citep{shulman14,kraus17}.
 
@@
 More generally, correspondences, in the sense of ``relevant'' relation, that is of a family over a product of sets, can be used in place of relations.
-Parametricity can then be iterated, and, relying on the fibered representation of correspondences as spans, it has been noted that iterated Reynolds' parametricity has the structure of a cubical set~\citep{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
+Parametricity can then be iterated, and relying on the fibered representation of correspondences as spans, it has been noted that iterated Reynolds' parametricity has the structure of a cubical set~\citep{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
 We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or correspondences, in which case, we obtain a form of realizability~\citep{bernardy12,lasson12,moulin16}.
 It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
-This similarity suggests to join the definition of augmented semi-simplicial sets and cubical sets and to see both of them as instances of a more general construction which we call $\nu$-sets of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu$+1, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
+This similarity suggests that the definition of augmented semi-simplicial sets and semi-cubical sets can both be seen as instances of a more general construction which we call $\nu$-sets of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu$+1, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
 
 \subsection*{Contribution}
-The main contribution of the paper is to describe in full details a recipe uniformly characterizing unary and binary iterated parametricity in indexed form and to derive from it a new indexed presentation, called indexed \emph{$\nu$-sets}, uniformly of augmented semi-simplicial and semi-cubical sets.
+The main contribution of the paper is to describe in full, the details of a recipe that uniformly characterizes unary and binary iterated parametricity in indexed form, and to derive from it a new indexed presentation, called indexed \emph{$\nu$-sets}, of augmented semi-simplicial and semi-cubical sets.
 Alternatively, from a category-theory perspective, we are characterizing, among the class of matching objects up to isomorphism for augmented semi-simplicial and cubical sets, a particular instance that reflects the structure of iterated parametricity.
-Additionally,
-
-\begin{itemize}
-  \item This new construction is useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\citep{part15,shulman14,altenkirch16,kraus17}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}).
-  \item Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory and thus more liable to reflect definitional properties of type theory than presheaf-based cubical sets would do; compare, for example, the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\citep{curien14}.
-\end{itemize}
-
-See \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak} for our mechanization.
+
+This new construction is useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\citep{part15,shulman14,altenkirch16,kraus17}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}).
+
+Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory, and is likely to better reflect the definitional properties of type theory than presheaf-based cubical sets would do.
+Compare, for example, the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\citep{curien14}.
+
+Our mechanization can be found at \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}.
 The construction was conceived in Summer 2019, and the mechanization began in late 2019.
@@
 \section{Semi-simplicial and semi-cubical sets\label{sec:nu}}
-In this section, we generalize semi-simplicial and semi-cubical sets to, what we call, $\nu$-sets, subsuming the earlier definitions.
-We start by first explicitly working out the cases of semi-simplicial and semi-cubical sets.
+In this section, we generalize semi-simplicial and semi-cubical sets to $\nu$-sets, subsuming the earlier definitions.
+We start with some introductory material on semi-simplicial and semi-cubical sets.
 
@@
 The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$.
-Note that the components can this time be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$ to the one obtained by replacing the leftmost $\kstar$ with $R$.
+Note that the components can
+
+time be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$ to the one obtained by replacing the leftmost $\kstar$ with $R$.
 
@@
 \section{Our construction}
-In this section, we describe our parametricity-based construction of $\nu$-sets in indexed form at different levels of formality:
-
-\begin{itemize}
-  \item Sections~\ref{sec:ett} and~\ref{sec:itt} describe the construction at an informal level of discourse:
-        \begin{itemize}
+In this section, we describe our parametricity-based construction of $\nu$-sets in indexed form at two levels of formality:
+
+Sections~\ref{sec:ett} and~\ref{sec:itt} describe the construction at an informal level of discourse:
+\begin{enumerate}
   \item In \ref{sec:ett}, we present it in informal extensional type theory where equational reasoning is left implicit.
@@
 Section~\ref{sec:itt} thus rephrases the construction in (informal) intensional type theory.
-        \end{itemize}
-  \item Sections~\ref{sec:wf}, \ref{sec:le}, and \ref{sec:eqproperties} describe additional issues to be addressed in order to get a fully formal construction:
-        \begin{itemize}
+\end{enumerate}
+
+Sections~\ref{sec:wf}, \ref{sec:le}, and \ref{sec:eqproperties} describe additional issues to be addressed in order to get a fully formal construction:
+\begin{enumerate}
   \item The well-foundedness of the induction requires a special termination evidence which will be discussed in section~\ref{sec:wf}.
@@
 We discuss how we deal with such dependencies in section~\ref{sec:le}.
-          \item A number of standard groupoid properties of equality as well as type isomorphisms have been left implicit in the informal definition.
-This is discussed in section~\ref{sec:eqproperties}.
-        \end{itemize}
-\end{itemize}
+  \item A number of standard groupoid properties of equality as well as type isomorphisms have been left implicit in the informal definition. This is discussed in section~\ref{sec:eqproperties}.
+\end{enumerate}
 

### 2023-11-05 paper/paper.tex
paper: minor consistency update; polish

@@
 In the context of functional programming, Reynolds' parametricity~(\citeyear{reynolds83}) interprets types as relations characterizing the observational behavior of programs of this type.
-More generally, correspondences, in the sense of ``relevant'' relation, that is of a family over a product of sets, can be used in place of relations.
+More generally, \emph{correspondences}, in the sense of ``relevant'' relation, that is of a family over a product of sets, can be used in place of relations.
 Parametricity can then be iterated, and relying on the fibered representation of correspondences as spans, it has been noted that iterated Reynolds' parametricity has the structure of a cubical set~\citep{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
@@
 It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
-This similarity suggests that the definition of augmented semi-simplicial sets and semi-cubical sets can both be seen as instances of a more general construction which we call $\nu$-sets of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu$+1, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
+This similarity suggests that the definition of augmented semi-simplicial sets and semi-cubical sets can both be seen as instances of a more general construction, which we call $\nu$-sets, of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu$+1, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
 

### 2023-11-05 paper/paper.tex
paper: fix bugs in msc, get title/author/abstract in paper

@@
 
-  On another side, it is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds's parametricity, respectively in its unary and binary variants\dots
+  It is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds's parametricity, respectively in its unary and binary variants\dots
 
@@
 \end{keywords}
-% \maketitle
+\maketitle
 

### 2023-11-12 paper/paper.tex
paper: fix abstract

@@
   \author{Ramkumar Ramachandra}
-  \affiliation{Unaffiliated \email{r@artagnon.com}}
+  \affiliation{Université Paris Cité (2020-2022) \email{r@artagnon.com}}
 \end{authgrp}
 \begin{abstract}
-  Constructions such as semi-simplicial and semi-cubical sets can be defined in the ``usual way'' as presheaves over respectively, the semi-simplex or semi-cube category, which we call \emph{fibered} definitions, but also defined like in e.g.
-\cite{voevodsky12} or in \cite{herbelin15}, as a dependently-typed construction, which we call \emph{indexed}.
-
-  It is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds's parametricity, respectively in its unary and binary variants\dots
-
-  We exploit this correspondence to develop a uniform indexed definition of both augmented semi-simplicial and semi-cubical sets, which is additionally fully formalized in Coq's dependent type theory.
-Beside the interest in the construction itself, we expect it to eventually serve as models of type theory preserving more definitional equalities than presheaf models do.
+  Semi-simplicial and semi-cubical sets are commonly defined as presheaves over respectively, the semi-simplex or semi-cube category.
+Homotopy Type Theory then popularized an alternative definition, where the set of $n$-simplices or $n$-cubes are instead regrouped into the families of the fibers over their faces, leading to a characterization we call \emph{indexed}.
+
+  Moreover, it is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds's parametricity, respectively in its unary and binary variants.
+
+  We exploit this correspondence to develop an original uniform indexed definition of both augmented semi-simplicial and semi-cubical sets, and fully formalize it in Coq.
 \end{abstract}
@@
 \appendmask[bonak]{cohpainting}[D, d]
-
-% Now, we write the type theory bit, and input the abbreviated tables
 

### 2023-11-12 paper/paper.tex
paper: minor polish

@@
 In the latter case, the set associated to a given element of $S$ is the fiber of this element, so we call it a \emph{fibered} presentation.
-The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\citep{hottbook} as the fibered/indexed correspondence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family correspondence and unbundled/bundled correspondence.
+The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\citep{hottbook} as the fibered/indexed equivalence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family equivalence and unbundled/bundled equivalence.
 The fibered/indexed nomenclature echoes the Grothendieck construction of fibered categories from indexed categories.
-The most elementary instance of the correspondence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see \cite{hottbook}).}.
+The most elementary instance of the equivalence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see \cite{hottbook}).}.
 \begin{equation*}
@@
 A \emph{presheaf} on an category is a family of sets connected with maps indexed over the morphisms of the category.
-As such, it lives on the indexed side of the correspondence, contrasting with the fibered side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
-However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the correspondence.
+As such, it lives on the indexed side of the equivalence, contrasting with the fibered side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
+However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the equivalance.
 This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.
@@
 The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$.
-Note that the components can
-
-time be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$ to the one obtained by replacing the leftmost $\kstar$ with $R$.
+Note that the components can be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$ to the one obtained by replacing the leftmost $\kstar$ with $R$.
 

### 2023-11-12 paper/paper.tex
paper: fix inconsistencies (WIP)

@@
 In there, the process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$, and so on, is similar to iteratively applying a binary parametricity translation.
-The parametricity which we consider interprets a type $A$ by a family $A_\kstar$ of edges in a graph over $A$, and a term $t: A$ as an edge in $A_\kstar(t)(t)$.
-To each type constructor is then associated the construction of a graph.
-In particular, the type of types $\U$ is interpreted as the family of families ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \rightarrow A_R \rightarrow \U$ of families of edges over $A_L$ and $A_R$.
+The parametricity which we consider interprets a type $A$ by a family $A_\kstar$ over $A \times A$, what can be seen as a graph whose vertices are in $A$.
+To each type constructor is thus associated the construction of a graph.
+In particular, the type of types $\U$ is interpreted as the family of families ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \rightarrow A_R \rightarrow \U$ of families over $A_L$ and $A_R$.
 Also, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the graph $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
 \begin{align*}
-  (\Pi a: A.\, B)_\kstar(f_L)(f_R) \; \defeq \; \Pi a_L: A.\, \Pi a_R: A.\, \Pi a_\kstar: A_\kstar(a_L)(a_R).\, B_\kstar(f_L(a_L))(f_R(a_R))
-\end{align*}
-
-In particular, for $X: \U$, applying the parametricity translation is about canonically associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X)(X)$ i.e.
-of $X \rightarrow X \rightarrow \U$.
-In turn, applying the parametricity translation to $X_\kstar: X \rightarrow X \rightarrow \U$ is about canonically associating to $X_\kstar$ an inhabitant $X_{\kstar\kstar}$ of $(X \rightarrow X \rightarrow \U)_\kstar(X_\kstar)(X_\kstar)$ i.e.
+  (\Pi a: A.\, B)_\kstar(f_L)(f_R) \; \defeq \; \Pi a_L: A.\, \Pi a_R: A.\, \Pi a_\kstar: A_\kstar(a_L,a_R).\, B_\kstar(f_L(a_L),f_R(a_R))
+\end{align*}
+
+In particular, for $X: \U$, applying the parametricity translation is about canonically associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X,X)$ i.e.
+of $X \times X \rightarrow \U$.
+In turn, applying the parametricity translation to $X_\kstar: X \times X \rightarrow \U$ is about canonically associating to $X_\kstar$ an inhabitant $X_{\kstar\kstar}$ of $(X \times X \rightarrow \U)_\kstar(X_\kstar,X_\kstar)$ i.e.
 of:
 \begin{align*}
-  \Pi x_{LL}: X.\, \Pi x_{LR}: X.\, X_\kstar(x_{LL})(x_{LR})             \\
-  \rightarrow \Pi x_{RL}: X.\, \Pi x_{RR}: X.\, X_\kstar(x_{RL})(x_{RR}) \\ \rightarrow X_\kstar(x_{LL}, x_{RL}) \rightarrow X_\kstar(x_{LR})(x_{RR})  \rightarrow \U
+  \Pi x_{LL}: X.\, \Pi x_{LR}: X.\, X_\kstar(x_{LL},x_{LR})              \\
+  \rightarrow \Pi x_{RL}: X.\, \Pi x_{RR}: X.\, X_\kstar(x_{RL})(x_{RR}) \\ \rightarrow X_\kstar(x_{LL}, x_{RL}) \times X_\kstar(x_{LR},x_{RR})  \rightarrow \U
 \end{align*}

### 2023-11-12 paper/paper.tex
Using \times in parametricity.

@@
 Main types in type theory are the types of dependent pairs, written $\Sigma a : A.\,B(a)$, the types of dependent functions, written $\Pi a:A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$, and the type of propositional equality, written $t = u$.
+As a notation, the type of dependent pairs when $B$ is actually not dependent on $A$ is shortened into $A \times B$ and the type of dependent functions when $B$ is not dependent on $A$ is written $A \rightarrow B$.
 We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, called $\textsf{bool}$, and the type of natural numbers.
@@
 To each type constructor is thus associated the construction of a graph.
-In particular, the type of types $\U$ is interpreted as the family of families ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \rightarrow A_R \rightarrow \U$ of families over $A_L$ and $A_R$.
+In particular, the type of types $\U$ is interpreted as the family of families ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \times A_R \rightarrow \U$ of families over $A_L$ and $A_R$.
 Also, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the graph $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
 \begin{align*}
-  (\Pi a: A.\, B)_\kstar(f_L)(f_R) \; \defeq \; \Pi a_L: A.\, \Pi a_R: A.\, \Pi a_\kstar: A_\kstar(a_L,a_R).\, B_\kstar(f_L(a_L),f_R(a_R))
+  (\Pi a: A.\, B)_\kstar(f_L)(f_R) \; \defeq \; \Pi (a_L,a_R): (A \times A).\, (A_\kstar(a_L,a_R)\,\rightarrow B_\kstar(f_L(a_L),f_R(a_R)))
+\end{align*}
+
+Similarly, a product type $A \times B$ is interpreted as the graph $(A \times B)_\kstar$ that relates two tuples $(a_L,b_L)$ and $(a_R,b_R)$ in $A \times B$ as follows:
+\begin{align*}
+  (A \times B)_\kstar((a_L,b_L),(a_R,b_R)) \; \defeq \; A_\kstar(a_L,a_R) \times B_\kstar(b_L,b_R)
 \end{align*}
@@
 \begin{align*}
-  \Pi x_{LL}: X.\, \Pi x_{LR}: X.\, X_\kstar(x_{LL},x_{LR})              \\
-  \rightarrow \Pi x_{RL}: X.\, \Pi x_{RR}: X.\, X_\kstar(x_{RL})(x_{RR}) \\ \rightarrow X_\kstar(x_{LL}, x_{RL}) \times X_\kstar(x_{LR},x_{RR})  \rightarrow \U
+  \Pi ((x_{LL},x_{lR}),(x_{RL},x_{RR})): ((X \times X) \times (X \times X)).\,\\
+  (X_\kstar(x_{LL},x_{LR}) \times X_\kstar(x_{RL},x_{RR})
+  \rightarrow X_\kstar(x_{LL}, x_{RL}) \times X_\kstar(x_{LR},x_{RR})  \rightarrow \U)
 \end{align*}
@@
     X_0 & \defeq & X                & : & \U                                               \\
-    X_1 & \defeq & X_\kstar         & : & {\U}_\kstar(X)(X)                                \\
-    X_2 & \defeq & X_{\kstar\kstar} & : & ({\U}_\kstar(X)(X))_{\kstar}(X_\kstar)(X_\kstar) \\
+    X_1 & \defeq & X_\kstar         & : & {\U}_\kstar(X,X)                                \\
+    X_2 & \defeq & X_{\kstar\kstar} & : & ({\U}_\kstar(X,X))_{\kstar}(X_\kstar,X_\kstar) \\
     \ldots
@@
 
-Notice, however, that the recipe obtained so far, $X_{n + 1}: ({S_n})_\kstar(X_n)(X_n)$ for $X_n: S_n$, applies parametricity on the \emph{syntax} of the type of $X_n$.
+Notice, however, that the recipe obtained so far, $X_{n + 1}: ({S_n})_\kstar(X_n,X_n)$ for $X_n: S_n$, applies parametricity on the \emph{syntax} of the type of $X_n$.
 It does not directly yield a characterization of $S_n$ as a function from $n$.

### 2023-11-19 paper/paper.tex
paper: minor polish, cleanup

@@
 
-\usepackage{amsmath, amssymb, mathrsfs, wasysym, url, bookmark, tikz, tikz-cd, mathpazo, enumitem, xargs, multirow, float, tabularx, environ, booktabs, setspace, makecell, colortbl, pdflscape, flushend, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
+\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, mathpazo, xargs, environ, multirow, float, tabularx, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
 
@@
   \author{Ramkumar Ramachandra}
-  \affiliation{Université Paris Cité (2020-2022) \email{r@artagnon.com}}
+  \affiliation{Université Paris Cité (2020-2022), Unaffiliated
+    \email{r@artagnon.com}}
 \end{authgrp}
@@
 As such, it lives on the indexed side of the equivalence, contrasting with the fibered side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
-However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the equivalance.
+However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the equivalence.
 This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.
@@
   X_1 & :              & X_0 \times X_0 \rightarrow \U                                                 \\
-  X_2 & : \Pi a b c d. & X_1(a)(b) \times X_1(a)(c) \times X_1 (b)(d) \times X_1 (c)(d) \rightarrow \U \\
+  X_2 & : \Pi a b c d. & X_1(a)(b) \times X_1 (c)(d) \times X_1(a)(c) \times X_1 (b)(d) \rightarrow \U \\
   \ldots
@@
 The idea for such an indexed presentation of presheaves over a direct category was mentioned at the Univalent Foundations year in the context of defining semi-simplicial types~\footnote{See e.g.
-\url{https://ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}.}.
+\href{https://ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}{ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}.}.
 A couple of constructions were proposed since then.
@@
 The confusion between the question of moving from semi-simplicial sets to semi-simplicial types, and moving from a presheaf to an indexed presentation was, however, common at the time.}, and fully formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
-Another by \cite{part15}, formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17}, formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\url{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, also rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
+Another by \cite{part15}, formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17}, formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, also rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
 
@@
 To each type constructor is thus associated the construction of a graph.
-In particular, the type of types $\U$ is interpreted as the family of families ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \times A_R \rightarrow \U$ of families over $A_L$ and $A_R$.
+To start with, the type of types $\U$ is interpreted as the family of type of families ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \times A_R \rightarrow \U$ of families over $A_L$ and $A_R$.
 Also, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the graph $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
 \begin{align*}
-  (\Pi a: A.\, B)_\kstar(f_L)(f_R) \; \defeq \; \Pi (a_L,a_R): (A \times A).\, (A_\kstar(a_L,a_R)\,\rightarrow B_\kstar(f_L(a_L),f_R(a_R)))
+  (\Pi a: A.\, B)_\kstar(f_L,f_R) \; \defeq \; \Pi (a_L,a_R): (A \times A).\, (A_\kstar(a_L,a_R)\,\rightarrow B_\kstar(f_L(a_L),f_R(a_R)))
 \end{align*}
@@
 
-In particular, for $X: \U$, applying the parametricity translation is about canonically associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X,X)$ i.e.
+In particular, for $X: \U$, applying the parametricity construction is about canonically associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X,X)$ i.e.
 of $X \times X \rightarrow \U$.
@@
 \begin{align*}
-  \Pi ((x_{LL},x_{lR}),(x_{RL},x_{RR})): ((X \times X) \times (X \times X)).\,\\
+  \Pi ((x_{LL},x_{lR}),(x_{RL},x_{RR})): ((X \times X) \times (X \times X)). \\
   (X_\kstar(x_{LL},x_{LR}) \times X_\kstar(x_{RL},x_{RR})
@@
 \section{Our construction}
-In this section, we describe our parametricity-based construction of $\nu$-sets in indexed form at two levels of formality:
+In this section, we describe our parametricity-based construction of $\nu$-sets in indexed form at two levels of formality.
 

### 2023-11-19 paper/paper.tex
paper: formatting; kill overflows, unnecessary float

@@
 
-\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, mathpazo, xargs, environ, multirow, float, tabularx, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
+\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, mathpazo, xargs, environ, multirow, float, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
 
@@
 
+% Caption setup
+\DeclareCaptionFormat{plain}{#1#3}
+\captionsetup{font=scriptsize,labelfont=bf}
+
 % The eqntable environment
@@
 \NewEnviron{eqntable}[1]{
-  \begin{table}[H]
-    \small
-    \begin{tabularx}{\linewidth}{
+  \scriptsize
+  \begin{tabularx}{0.9\linewidth}{
     @{}
@@
   \end{tabularx}
-    \caption{#1}
-  \end{table}
+  \captionof{table}{#1}
 }
@@
 \end{abstract}
-\begin{keywords}
-  simplicial set, cubical set, coq, formalization, HoTT
-\end{keywords}
 \maketitle
@@
 \begin{enumerate}
-  \item[(i)] UIP holds on the unit type, bool type, as well as all types of finite cardinal $\nu$.
-  \item[(ii)] UIP propagates to $\Sigma$-types.
-  \item[(iii)] UIP propagates to $\Pi$-types, with some additional functional extensionality axioms.
+  \item UIP holds on the unit type, bool type, as well as all types of finite cardinal $\nu$.
+  \item UIP propagates to $\Sigma$-types.
+  \item UIP propagates to $\Pi$-types, with some additional functional extensionality axioms.
 \end{enumerate}
@@
 Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that the construction builds an effective sequence of types not mentioning coherences anymore.
+\\
 
@@
   \centering
+  \small
   \begin{equation*}
@@
 The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit in table~\ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
+\\
 
@@
 \renewcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
+\vspace{1em}
 The proof of $\cohf$ itself requires making explicit several rewritings which were invisible in extensional type theory.
@@
 
-\begin{figure}[H]
 \begin{minted}{coq}
@@
 \end{minted}
-\end{figure}
 
@@
 \end{minted}
-\end{figure}
+
 where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable.

### 2023-11-19 paper/paper.tex
paper: tweak table numbering
About parametricity

@@
   \scriptsize
-  \begin{tabularx}{0.9\linewidth}{
+  \begin{tabularx}{0.93\linewidth}{
     @{}
@@
 In there, the process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$, and so on, is similar to iteratively applying a binary parametricity translation.
-The parametricity which we consider interprets a type $A$ by a family $A_\kstar$ over $A \times A$, what can be seen as a graph whose vertices are in $A$.
+The binary parametricity which we consider is composed with the diagonal on types and interprets a type $A$ by a family $A_\kstar$ over $A \times A$, what can be seen as a graph whose vertices are in $A$.
 To each type constructor is thus associated the construction of a graph.
@@
 
-In particular, for $X: \U$, applying the parametricity construction is about canonically associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X,X)$ i.e.
+In particular, for $X: \U$, applying our parametricity translation is about associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X,X)$ i.e.
 of $X \times X \rightarrow \U$.
-In turn, applying the parametricity translation to $X_\kstar: X \times X \rightarrow \U$ is about canonically associating to $X_\kstar$ an inhabitant $X_{\kstar\kstar}$ of $(X \times X \rightarrow \U)_\kstar(X_\kstar,X_\kstar)$ i.e.
+In turn, applying the translation again to $X_\kstar: X \times X \rightarrow \U$ is about associating to $X_\kstar$ an inhabitant $X_{\kstar\kstar}$ of $(X \times X \rightarrow \U)_\kstar(X_\kstar,X_\kstar)$ i.e.
 of:
@@
 \end{align*}
-which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of binary parametricity applied to an initial $X: \U$:
+which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of the composition of binary parametricity with the diagonal on types and type families, applied to an initial $X: \U$:
 \begin{equation*}
@@
 \renewcommand*{\lab}{fulltab:faces}
+\renewcommand{\thetable}{4'}
 \input{tab-faces.tex}
 \renewcommand*{\lab}{fulltab:coh}
+\renewcommand{\thetable}{5'}
 \input{tab-coh.tex}

### 2023-11-19 paper/paper.tex
paper: tweak font sizes harder using anyfont; lmodern

@@
 
-\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, mathpazo, xargs, environ, multirow, float, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
-
+\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, lmodern, mathpazo, t1enc, anyfontsize, xargs, environ, multirow, float, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
 \usepackage[prefix=bonak]{art.cls/xkeymask}
+
+% Use the patterns library to draw the cubes figure
 \usetikzlibrary{patterns}
@@
 \NewEnviron{eqntable}[1]{
-  \scriptsize
-  \begin{tabularx}{0.93\linewidth}{
+  \fontsize{7.2}{9}\selectfont
+  \begin{tabularx}{0.94\linewidth}{
     @{}
@@
 In there, the process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$, and so on, is similar to iteratively applying a binary parametricity translation.
-The binary parametricity which we consider is composed with the diagonal on types and interprets a type $A$ by a family $A_\kstar$ over $A \times A$, what can be seen as a graph whose vertices are in $A$.
+The binary parametricity which we consider interprets a type $A$ by a family $A_\kstar$ over $A \times A$, what can be seen as a graph whose vertices are in $A$.
 To each type constructor is thus associated the construction of a graph.

### 2023-11-19 paper/paper.tex
Improving text

@@
 To every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
-Compared to the informal description given in section~\ref{sec:rel-param}, e.g.
-$X_1 : X_0 \rightarrow X_0 \rightarrow \U$, this amounts to apply the isomorphisms between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$ so as to get the expected form $\fullframe[n] \rightarrow \U$..
+Compared to the informal description given in section~\ref{sec:rel-param}, this amounts to applying the isomorphisms between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$ so as to get the expected form $\fullframe[n] \rightarrow \U$.
 In particular, $\fullframe[n]$ is a ``telescope'', i.e.

### 2023-11-19 paper/paper.tex
paper: kill some floats, adjust whitespace

@@
 \maketitle
+\vspace{-2em} % Remove space after abstract
 
@@
 Formulated in type theory, it takes the form:
-
 \begin{align*}
@@
 It can be shown that composition is associative and that $\id$ is neutral.
-
-  \begin{figure}[H]
-    \centering
   \begin{align*}
@@
   \end{align*}
-  \end{figure}
 \end{definition}
@@
 
-  \begin{figure}[H]
-    \centering
   \begin{align*}
@@
   \end{align*}
-  \end{figure}
 
@@
 
-\begin{table}[H]
-  \centering
+\begin{center}
   \begin{tabularx}{0.7\linewidth}{X|X|X}
@@
   \end{tabularx}
-\end{table}
+\end{center}
 
@@
 In $\U[m]$, the following properties hold:
-
 \begin{enumerate}
@@
 
-To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on the building blocks which we call $\framep$, $\layer$, and $\painting$.
-A $\framep$ is a boundary of a standard form (simplex, cube, etc.), which we decompose into $\layer$, and a $\painting$ corresponds to a filled $\framep$.
+To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on the building blocks called $\framep$, $\layer$, and $\painting$.
+A $\framep$ is a boundary of a standard form (simplex, cube), which we decompose into $\layer$, and a $\painting$ corresponds to a filled $\framep$.
 Some $\framep$ are full and we call them $\fullframe$: they represent matching objects.
 
-To every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
-Compared to the informal description given in section~\ref{sec:rel-param}, this amounts to applying the isomorphisms between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$ so as to get the expected form $\fullframe[n] \rightarrow \U$.
-In particular, $\fullframe[n]$ is a ``telescope'', i.e.
-a nesting of $\Sigma$-types.
+Every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
+Compared to the informal description given in section~\ref{sec:rel-param}, this amounts to applying the isomorphisms between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$ to get the expected form $\fullframe[n] \rightarrow \U$.
+In particular, $\fullframe[n]$ is a ``telescope'', or a nesting of $\Sigma$-types.
 
@@
 To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ given to $X_0$ in section~\ref{sec:rel-param} can be equivalently formulated as $\unittype \rightarrow \U$.
-Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from the $\unittype$ type and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
-For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of the $\unittype$ and $\layer[1][0]$, as shown below.
+Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from $\unittype$, and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
+For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of $\unittype$ and $\layer[1][0]$, as shown below.
 The figure also mentions how the type of $X_2$ is structured.
-
-\begin{figure}[H]
-  \centering
-  \small
+\begin{small}
   \begin{equation*}
@@
   \end{equation*}
-\end{figure}
+\end{small}
 

### 2023-11-19 paper/paper.tex
paper: tweak caption fontsize
paper, msc, art.cls: squelch some warnings; switch to master

@@
 
-\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, lmodern, mathpazo, t1enc, anyfontsize, xargs, environ, multirow, float, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
+\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, lmodern, mathpazo, anyfontsize, xargs, environ, multirow, float, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
 \usepackage[prefix=bonak]{art.cls/xkeymask}
@@
 \DeclareCaptionFormat{plain}{#1#3}
-\captionsetup{font=scriptsize,labelfont=bf}
+\captionsetup{font=footnotesize,labelfont=bf}
 

### 2023-11-19 paper/paper.tex
paper: macro cleanup, NFC

@@
 
-% The label, since we're including twice
-\newcommand*{\lab}{}
-
 % \midrule color
@@
 
-The definition of the type of a $n$-truncated $\nu$-set is in turn described in \ref{tab:core}.
+The definition of the type of a $n$-truncated $\nu$-set is in turn described in table \ref{tab:core}.
 In the infinite sequence of type families representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$.
 The type $\fullframe$ represents a matching object.
-It is recursively defined in \ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
-The rationale behind $\framep$, $\layer$ and $\painting$ will be explained later but it should already be noticed that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in \ref{tab:faces}, and this restriction operator is in turn defined using the auxiliary definitions of $\restrl$ and $\restrc$.
+It is recursively defined in table \ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
+The rationale behind $\framep$, $\layer$ and $\painting$ will be explained later but it should already be noticed that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table \ref{tab:faces}, and this restriction operator is in turn defined using the auxiliary definitions of $\restrl$ and $\restrc$.
 
@@
 
-\renewcommand*{\lab}{tab:coind}
+\def\lab{tab:coind}
 \input{tab-coind.tex}
@@
 
-\renewcommand*{\lab}{tab:core}
+\def\lab{tab:core}
 \input{tab-core.tex}
@@
 \renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
-\renewcommand*{\lab}{tab:frames}
+\def\lab{tab:frames}
 \input{tab-frames.tex}
@@
 
-\renewcommand*{\lab}{tab:faces}
+\def\lab{tab:faces}
 \input{tab-faces-ett.tex}
@@
 
-\renewcommand*{\lab}{tab:coh}
+\def\lab{tab:coh}
 \input{tab-coh-ett.tex}
@@
 \renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
-\renewcommand*{\lab}{fulltab:faces}
+\def\lab{fulltab:faces}
 \renewcommand{\thetable}{4'}
 \input{tab-faces.tex}
-\renewcommand*{\lab}{fulltab:coh}
+\def\lab{fulltab:coh}
 \renewcommand{\thetable}{5'}

### 2023-11-26 paper/paper.tex
paper: minor polish

@@
 Homotopy Type Theory then popularized an alternative definition, where the set of $n$-simplices or $n$-cubes are instead regrouped into the families of the fibers over their faces, leading to a characterization we call \emph{indexed}.
-
 Moreover, it is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds's parametricity, respectively in its unary and binary variants.
-
 We exploit this correspondence to develop an original uniform indexed definition of both augmented semi-simplicial and semi-cubical sets, and fully formalize it in Coq.
@@
 \section{Type theory}
-Martin-Löf's Type theory~\citep{martinlof75,martinlof84} is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
+Martin-Löf's Type theory~(\citeyear{martinlof75,martinlof84}) is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
 It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda~(\citeyear{agda23}), Coq~(\citeyear{coq22}) or Lean~(\citeyear{lean15}).
@@
 In there, the process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$, and so on, is similar to iteratively applying a binary parametricity translation.
-The binary parametricity which we consider interprets a type $A$ by a family $A_\kstar$ over $A \times A$, what can be seen as a graph whose vertices are in $A$.
+The binary parametricity which we consider interprets a closed type $A$ by a family $A_\kstar$ over $A \times A$, what can be seen as a graph whose vertices are in $A$.
 To each type constructor is thus associated the construction of a graph.
@@
   \item In \ref{sec:ett}, we present it in informal extensional type theory where equational reasoning is left implicit.
-  \item While reasoning in extensional type theory is similar to reasoning in set theory regarding how equality is implicitly handled, extensional type theory has two limitations.
+  \item While reasoning in extensional type theory is similar to reasoning in set theory regarding how equality is handled, extensional type theory has two limitations.
 The first limitation is that it enforces the principle of Uniqueness of Identity Proofs and this is inconsistent with the Univalence principle, thus making it inexpressible in Homotopy Type Theory.
@@
   \item The construction is indexed over integers and holds under some constraints on the range of these integers.
-There is a standard formalization dilemma in this kind of situation: either the constraints on the range are embedded in the construction so that the construction makes sense only on the corresponding range, or the construction is made first on a more general domain than needed but restricted to a smaller domain only at the time of use.
+There is a standard formalization dilemma in this kind of situation: either the constraints on the range are embedded in the construction so that the construction makes sense only on the corresponding range, or the construction is made first on a more general domain than needed but restricted to a smaller domain at the time of use.
 We adopted the first approach, requiring however the construction to be dependent on proofs of inequalities on natural numbers.
@@
 In the infinite sequence of type families representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$.
-The type $\fullframe$ represents a matching object.
+The type $\fullframe$ defines a matching object.
 It is recursively defined in table \ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
-The rationale behind $\framep$, $\layer$ and $\painting$ will be explained later but it should already be noticed that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table \ref{tab:faces}, and this restriction operator is in turn defined using the auxiliary definitions of $\restrl$ and $\restrc$.
+The rationale behind $\framep$, $\layer$ and $\painting$ will be explained later but it should already be noticed that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table \ref{tab:faces}, and this restriction operator is in turn defined using auxiliary definitions $\restrl$ and $\restrc$.
 
@@
 The proof of this commutation is worth being made explicit, which we do in table \ref{tab:coh} using proof-term notations.
-The proof requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\painting$.
+The proof requires an induction on the dimension and on the structure of $\framep$, $\layer$, and $\painting$.
 This is what $\cohf$ does using auxiliary proofs $\cohl$ and $\cohc$.
 Even though it looks independent of the definitions from the the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
-More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be mutually defined by induction on $p$.
+More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be defined in one go by induction on $p$.
 Also, each of $\painting$, $\restrc$, and $\cohc$ is built by induction from $p$ to $n$.
@@
 
-To assign types to $X_0, X_1, X_2, \ldots$ in the above indexed representation, we give a recursive definition relying on the building blocks called $\framep$, $\layer$, and $\painting$.
+To assign types to $X_0, X_1, X_2, \ldots$ in the indexed representation, we give a recursive definition relying on the building blocks called $\framep$, $\layer$, and $\painting$.
 A $\framep$ is a boundary of a standard form (simplex, cube), which we decompose into $\layer$, and a $\painting$ corresponds to a filled $\framep$.
@@
 Every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
-Compared to the informal description given in section~\ref{sec:rel-param}, this amounts to applying the isomorphisms between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$ to get the expected form $\fullframe[n] \rightarrow \U$.
+Compared to the informal description given in section~\ref{sec:rel-param}, this amounts to applying isomorphisms such as $(A \rightarrow B \rightarrow C) \simeq (A \times B \rightarrow C)$, or $()\Pi a: A.\, (B a \rightarrow C)) \simeq ((\Sigma a: A.\, B a) \rightarrow C)$, or associativity of $\times$, etc.
 In particular, $\fullframe[n]$ is a ``telescope'', or a nesting of $\Sigma$-types.
 
-Let us now illustrate how we recursively build $\fullframe[n]$.
+We now illustrate how to recursively build $\fullframe[n]$.
 To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ given to $X_0$ in section~\ref{sec:rel-param} can be equivalently formulated as $\unittype \rightarrow \U$.
-Then, more generally, we let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from $\unittype$, and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
+Then, more generally, let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from $\unittype$, and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
 For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of $\unittype$ and $\layer[1][0]$, as shown below.

### 2023-11-26 paper/paper.tex
Upgrading version of Coq

@@
 Martin-Löf's Type theory~(\citeyear{martinlof75,martinlof84}) is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
-It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda~(\citeyear{agda23}), Coq~(\citeyear{coq22}) or Lean~(\citeyear{lean15}).
+It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda~(\citeyear{agda23}), Coq~(\citeyear{coq23}) or Lean~(\citeyear{lean15}).
 In type theory, propositions are types and proofs are programs.

### 2023-11-26 paper/paper.tex
paper: some additions; remove useless float

@@
 
-\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, lmodern, mathpazo, anyfontsize, xargs, environ, multirow, float, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
+\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, lmodern, mathpazo, anyfontsize, xargs, environ, multirow, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
 \usepackage[utf8]{inputenc}
@@
 Note that the reflection rule implies UIP so that $\U$ and $\Type$ ae equivalent in extensional type theory.
-The reflection rules also implies functional extensionality, and, actually, extensional type theory is logically equivalent to intentional type theory extended with UIP and functional extensionality~\citep{HofmannPhd}.
+The reflection rules also implies functional extensionality, and, actually, extensional type theory is logically equivalent to intensional type theory extended with UIP and functional extensionality~\citep{HofmannPhd}.
 
@@
 Every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
-Compared to the informal description given in section~\ref{sec:rel-param}, this amounts to applying isomorphisms such as $(A \rightarrow B \rightarrow C) \simeq (A \times B \rightarrow C)$, or $()\Pi a: A.\, (B a \rightarrow C)) \simeq ((\Sigma a: A.\, B a) \rightarrow C)$, or associativity of $\times$, etc.
+Compared to the informal description given in section~\ref{sec:rel-param}, this amounts to applying isomorphisms such as $(A \rightarrow B \rightarrow C) \simeq (A \times B \rightarrow C)$ or $(\Pi a: A.\, (B a \rightarrow C)) \simeq ((\Sigma a: A.\, B a) \rightarrow C)$.
 In particular, $\fullframe[n]$ is a ``telescope'', or a nesting of $\Sigma$-types.
@@
 
-\begin{figure}[H]
-  \centering
+\begin{center}
   \begin{tikzpicture}[scale=2]
@@
   \end{tikzpicture}
-\end{figure}
+\end{center}
 
@@
 
-When $\nu = 2$, the formation of layers from paintings amounts to:
+When $\nu = 2$, using $L$ and $R$ to represent the sides, the formation of layers from paintings amounts to:
 \begin{equation*}
@@
 These are by induction on the structure of $\framep$, $\layer$ and $\painting$.
-Note that, for the construction in intentional type theory, we further need a $2$-dimensional coherence condition, $\coht$, for $\cohl$.
+Note that, for the construction in intensional type theory, we further need a $2$-dimensional coherence condition, $\coht$, for $\cohl$.
 This is explained in the next section.
 
-\subsection{From extensional to intentional type theory: explication of the equality proofs\label{sec:itt}}
+\subsection{From extensional to intensional type theory: making explicit the equality proofs\label{sec:itt}}
 \renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
-
-In this section, we intend to get rid of the reflection rule and make explicit what is needed to rephrase the construction from extensional type theory to intentional type theory.
+In this section, we intend to get rid of the reflection rule and make explicit what is needed to rephrase the construction in intensional type theory.
 For readability purpose, we however make explicit only the key coherence conditions of the construction.
-Other form of equality reasoning would have to be made explicit to obtain a construction fully in intentional type theory but these other steps are standard enough to be omitted at this stage.
+Other cases of equality reasoning would have to be made explicit to fully obtain a construction in intensional type theory but these other steps are standard enough to be omitted at this stage.
 See section~\ref{sec:eqproperties} for the details.
@@
 This, combined with the two terms of the form $\ap \cohf$, matches our expectation of three $\cohf$ on the left-hand side and two $\cohf$ on the right-hand side.
-Then, $\coht$ can roughly be seen as a commutation of these $\cohf$ terms.
+Then, $\coht$ can be seen as expressing the commutation of these $\cohf$ terms.
 
@@
 Since the construction shown in the previous sections is by induction on $n$, and dependencies are on lower $n$ and $p < n$, one would imagine formalizing this using well-founded induction in dependent type theory.
-We initially tried this approach: we had terms dependent on the proofs of the case distinction of $n' \leq n$ implies $n' < n$ or $n' = n$, and these proofs did not have definitional computational rule; it started to be necessary to reason propositionally on the computational property of the case distinction, and it eventually turned out to be unmanageable.
+We initially tried this approach: we had terms dependent on the proofs of the case distinction that $n' \leq n$ implies $n' < n$ or $n' = n$, but these proofs did not come with enough definitional properties to be usable in practice.
 Hence, we chose a different route: in practice, since $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$, we only need to keep track of three ``levels'', and we built separate data structures for the levels, with dependencies.
@@
 
-Here $\SProp$ is a definitionally proof-irrelevant impredicative universe at the bottom of the universe hierarchy~\citep{gilbert19}.
+Here $\SProp$ is a definitionally proof-irrelevant impredicative universe morally\footnote{In Coq~(\citeyear{coq23}), it is however a stand-alone universe unrelated to the universe hierarchy.} living at the bottom of the universe hierarchy~\citep{gilbert19}.
 By placing the definition in \SProp, we have definitional equality of all inequality proofs.
@@
 \end{minted}
-
+%
 where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable.
-These two problems definitionally hold in \SProp, but equalizing them does not solve the existential.
+These two problems definitionally hold in \SProp, but equating them does not solve the existential.
 For unification to be useful in inferring existentials, we present our first variant of $\leq$, which we dub as the ``Yoneda variant'':
@@
 
+\newpage
 \bibliographystyle{msclike}

### 2023-11-26 paper/paper.tex
paper: major work on last two sections

@@
 \subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
-The construction takes benefit of various provable equalities over proofs of equality being definitional by the reflection rule.
-This includes in particular the groupoid properties of equality.
-Notably, uniqueness of identity proofs holds in extensional type theory, so that any type is automatically an $\U$.
-Also, we left implicit in table~\ref{tab:coh} the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
-(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type.
-In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is functional extensionality, holds by default in extensional type theory.
-As a final remark, note, as a consequence of $\eta$-conversion for finite enumerated types, that the requirement of functional extensionality disappears when $\nu$ is finite.
-However, this is a conversion which Coq does not implement, so, in Coq, the alternative would be to replace $\Pi a: \nu.\, B$ by a ``flat'' iterated product $B(1) \times B(2) \times \ldots \times B(\nu)$.
+The construction relies on the groupoid properties of equality in some places, which have to be made explicit in the formalization.
+
+Notice that in table~\ref{fulltab:coh}, the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
+(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type is left implicit.
+Also implicit is the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, or functional extensionality, holds by default in extensional type theory.
+
+As a final remark, note that as a consequence of $\eta$-conversion for finite enumerated types, the requirement of functional extensionality disappears when $\nu$ is finite.
+However, this is a conversion which Coq does not implement, and the alternative would be to replace $\Pi a: \nu.\, B$ by a ``flat'' iterated product $B(1) \times B(2) \times \ldots \times B(\nu)$.
 
 \section{Future work}
-In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\citep{nuyts17,cavallo19} by adding degeneracies, a hierarchy of universes (as sketched e.g.
-in a talk by Herbelin at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf})), as well as reasoning modulo permutations~\citep{grandis03}.
-
-By equipping the universe construction with a structure of equivalences, as suggested along the lines of Altenkirch and Kaposi~(\citeyear{altenkirch15}), we expect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models.
-This would a priori preserve definitional properties which may be lost when detouring via presheaves.
+The construction could be extended with degeneracies as well as with permutations~\citep{grandis03}.
+Dependent $\nu$-sets could also be defined, opening the way to construct $\Pi$-types and $\Sigma$-types of $\nu$-sets.
+A $\nu$-set of $\nu$-set representing a universe could also be defined (as sketched e.g.
+in a talk by Herbelin at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf})).
+More generally, we believe these lines of work to eventually provide alternative models to parametric type theories~\citep{nuyts17,cavallo19}.
+
+By equipping the universe construction with a structure of equivalences, as suggested along the lines of Altenkirch and Kaposi~(\citeyear{altenkirch15}), we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models.
+In particular, we wonder whether the indexed approach might provide definitional properties which are otherwise lost when detouring via presheaves.
 In particular, we conjecture being able to justify univalence holding definitionally.

### 2023-11-26 paper/paper.tex
paper: minor polish

@@
 \subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
-The construction relies on the groupoid properties of equality in some places, which have to be made explicit in the formalization.
-
-Notice that in table~\ref{fulltab:coh}, the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
-(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type is left implicit.
-Also implicit is the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, or functional extensionality, holds by default in extensional type theory.
+The construction relies on the groupoid properties of equality which are left implicit in table~\ref{fulltab:coh}.
+The use of the equivalence between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
+(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type is left implicit in the same table.
+Also implicit is the use of the equivalence between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, or functional extensionality, holds by default in extensional type theory.
+These have to be made explicit in the formalization.
 
@@
 
-By equipping the universe construction with a structure of equivalences, as suggested along the lines of Altenkirch and Kaposi~(\citeyear{altenkirch15}), we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models.
+By equipping the universe construction with a structure of equivalences, as suggested along the lines of \cite{altenkirch15}, we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models.
 In particular, we wonder whether the indexed approach might provide definitional properties which are otherwise lost when detouring via presheaves.

### 2023-11-26 paper/paper.tex
paper: minor pluralization
paper: minor polish

@@
 
-This new construction is useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\citep{part15,shulman14,altenkirch16,kraus17}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory (as will be discussed in Section~\ref{sec:ett}).
+This new construction is useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\citep{part15,shulman14,altenkirch16,kraus17}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory.
 
@@
 
-% 5. The "mathematical" construction (and its intuition)
-%   leaving equality and inequality side conditions implicit
-%   in particular, this means:
-%   - assuming equality reflection
-%   - equality as in observational type theory
-%   - assuming termination of recursive constructions
-% 6. Formal details
-% - making substitution of equals by equals explicit
-% - observational properties of equality
-% - the theory of inequality proofs
-% - the well-foundedness
-% - the formalization tricks
-%   - implicit arguments
-%   - refine-style vs tactic-style
-
 \section{Our construction}
@@
 There is a standard formalization dilemma in this kind of situation: either the constraints on the range are embedded in the construction so that the construction makes sense only on the corresponding range, or the construction is made first on a more general domain than needed but restricted to a smaller domain at the time of use.
-We adopted the first approach, requiring however the construction to be dependent on proofs of inequalities on natural numbers.
+We adopted the former approach, requiring the construction to be dependent on proofs of inequalities on natural numbers.
 We discuss how we deal with such dependencies in section~\ref{sec:le}.
@@
 Dependent $\nu$-sets could also be defined, opening the way to construct $\Pi$-types and $\Sigma$-types of $\nu$-sets.
-A $\nu$-set of $\nu$-set representing a universe could also be defined (as sketched e.g.
+A $\nu$-set of $\nu$-sets representing a universe could also be defined (as sketched e.g.
 in a talk by Herbelin at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf})).

### 2023-11-26 paper/paper.tex
paper: minor polish of footnote

@@
 The fibered/indexed nomenclature echoes the Grothendieck construction of fibered categories from indexed categories.
-The most elementary instance of the equivalence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see \cite{hottbook}).}.
+The most elementary instance of the equivalence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'', and its proof requires univalence~\citep{hottbook}.}.
 \begin{equation*}

### 2023-12-03 paper/paper.tex
paper: polish Future Work

@@
 \end{minted}
-%
+
 where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable.
@@
 A $\nu$-set of $\nu$-sets representing a universe could also be defined (as sketched e.g.
-in a talk by Herbelin at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf})).
-More generally, we believe these lines of work to eventually provide alternative models to parametric type theories~\citep{nuyts17,cavallo19}.
+in a talk at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf})).
+More generally, we believe these lines of work to eventually provide alternative models to parametric type theories~\citep{nuyts17,cavallo19} where equality of types, now a family rather than the total space of a fibration, is not only definitionally isomorphic to bridges~\cite{bernardy15} but definitionally the same as bridges.
 
@@
 
-Another direction for future work would also be to generically construct the indexed form of any presentation of presheaves over a direct category and to show the equivalence between the two presentations.
+Another direction for future work is to give a general definition of presheaf in indexed form over a direct category and to show the equivalence with the standard definition of presheaf.
 

### 2023-12-17 paper/paper.tex
paper: major polish

@@
 Homotopy Type Theory then popularized an alternative definition, where the set of $n$-simplices or $n$-cubes are instead regrouped into the families of the fibers over their faces, leading to a characterization we call \emph{indexed}.
-Moreover, it is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds's parametricity, respectively in its unary and binary variants.
+Moreover, it is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds parametricity, respectively in its unary and binary variants.
 We exploit this correspondence to develop an original uniform indexed definition of both augmented semi-simplicial and semi-cubical sets, and fully formalize it in Coq.
@@
 \subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
-A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over the elements of a given set $S$, or as a set $T$ together with a map from $T$ to $S$, which specifies for each element of set $T$ its dependency on $S$.
+A family of sets can commonly be represented in two ways: as a family properly speaking, indexed by the elements of a given set $S$, or as a set $T$ together with a map from $T$ to $S$, which specifies for each element of set $T$ its dependency on $S$.
 In the former case, we call it an \emph{indexed} presentation.
@@
 \end{equation*}
-where $\U$ represents in homotopy type theory the subset of types within a given universe where equality of any two elements has at most one proof.
-
-A \emph{presheaf} on an category is a family of sets connected with maps indexed over the morphisms of the category.
+Here, $\U$ represents in homotopy type theory the subset of types within a given universe where equality of any two elements has at most one proof.
+
+A \emph{presheaf} on an category is a family of sets indexed by the object of the category with maps indexed by the morphisms.
 As such, it lives on the indexed side of the equivalence, contrasting with the fibered side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
 However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the equivalence.
-This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.
-This is the case in semi-simplicial and semi-cubical sets, where each $F(X)$ serving as source of a map $F(X) \stackrel{F(f)}{\rightarrow} F(Y)$ can be turned into a family $F(X)$ indexed on $F(Y)$.
-Since the maps are well-founded downward, this can be iterated from below, eventually producing a collection of families which we call an indexed presentation of the presheaf over the direct category.
-
-Let us consider, for instance, the case of a semi-cubical set~\citep{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
-Formulated in type theory, the corresponding presheaf definition of a semi-cubical set prescribes a family of sets and face
-maps between them as follows:
+This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.Let us consider, for instance, the case of a semi-cubical set~\citep{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
+Formulated in type theory, the corresponding presheaf definition of a semi-cubical set prescribes a family of sets and face maps between them as follows.
 
@@
 up to cubical faces identities.
-In it, $X_1$ can be seen as a family over $X_0 \times X_0$ presented in a fibered form, $X_2$ can be seen as a family of $X_1 \times X_1 \times X_1 \times X_1$, and so on.
-This suggests an alternative indexed presentation of the same presheaf as a stratified sequence of families indexed on elements of families of lower rank, taking into account the coherence conditions to prevent duplications.
+Here, $X_1$ can be seen as a family over $X_0 \times X_0$ presented in a fibered form, $X_2$ can be seen as a family over $X_1 \times X_1 \times X_1 \times X_1$.
+This suggests an alternative indexed presentation of the presheaf as a stratified sequence of families indexed by families of lower rank, taking into account the coherence conditions to prevent duplications.
 Formulated in type theory, it takes the form:
@@
 \href{https://ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}{ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}.}.
-A couple of constructions were proposed since then.
-One, by \cite{voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
-Another, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it was part of a project for defining semi-simplicial types, but, in practice, the definition is done in a type theory with Unicity of Identity Proofs, meaning, in a type theory where types (intended to represent arbitrary $\infty$-groupoids) are actually sets ($0$-truncated $\infty$-groupoids or $0$-groupoids).
-The confusion between the question of moving from semi-simplicial sets to semi-simplicial types, and moving from a presheaf to an indexed presentation was, however, common at the time.}, and fully formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
-Another by \cite{part15}, formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17}, formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, also rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
+A few constructions have been proposed since then.
+The first construction by \cite{voevodsky12} relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
+The second, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it claimed to construct semi-simplicial types, but the construction was done in a type theory with Unicity of Identity Proofs.
+Consequentially, what was really obtained was an indexed presentation of semi-simplicial sets.
+The confusion was however, common at the time.} formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
+Another by \cite{part15} formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17} formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
 
 The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition, as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence conditions between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex being the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
-However, defining a concrete presheaf in indexed form only requires providing the family, since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition.
+However, exhibiting a concrete instance of a presheaf in indexed form only requires providing the families, since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition of the structure.
 
@@
 \subsection*{Reynolds' parametricity and its unary and binary variants}
-In the context of functional programming, Reynolds' parametricity~(\citeyear{reynolds83}) interprets types as relations characterizing the observational behavior of programs of this type.
-More generally, \emph{correspondences}, in the sense of ``relevant'' relation, that is of a family over a product of sets, can be used in place of relations.
-Parametricity can then be iterated, and relying on the fibered representation of correspondences as spans, it has been noted that iterated Reynolds' parametricity has the structure of a cubical set~\citep{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
-We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or correspondences, in which case, we obtain a form of realizability~\citep{bernardy12,lasson12,moulin16}.
+In the context of functional programming, Reynolds parametricity~(\citeyear{reynolds83}) interprets types as relations characterizing the observational behavior of programs of this type.
+More generally, families over a product of sets, or \emph{correspondences}, can be used in place of relations.
+Parametricity can then be iterated, and relying on the fibered presentation of correspondences as spans, it has been noted that iterated Reynolds parametricity has the structure of a cubical set~\citep{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
+We obtain a \emph{unary} variant of Reynolds \emph{binary} parametricity by using predicates or families instead of relations or correspondences, and this is a form of realizability~\citep{bernardy12,lasson12,moulin16}.
 It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
-This similarity suggests that the definition of augmented semi-simplicial sets and semi-cubical sets can both be seen as instances of a more general construction, which we call $\nu$-sets, of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu$+1, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
+This suggests that the definition of augmented semi-simplicial sets and semi-cubical sets can both be seen as instances of a more general construction, which we call $\nu$-sets, of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu+1$, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
 
 \subsection*{Contribution}
-The main contribution of the paper is to describe in full, the details of a recipe that uniformly characterizes unary and binary iterated parametricity in indexed form, and to derive from it a new indexed presentation, called indexed \emph{$\nu$-sets}, of augmented semi-simplicial and semi-cubical sets.
-Alternatively, from a category-theory perspective, we are characterizing, among the class of matching objects up to isomorphism for augmented semi-simplicial and cubical sets, a particular instance that reflects the structure of iterated parametricity.
-
-This new construction is useful in the direction of better understanding the technicality of coherence issues in defining ``semi-simplicial types''~\citep{part15,shulman14,altenkirch16,kraus17}, as well as the dialectic between reasoning in Extensional Type Theory and Intensional Type Theory.
-
-Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory, and is likely to better reflect the definitional properties of type theory than presheaf-based cubical sets would do.
-Compare, for example, the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\citep{curien14}.
+The main contribution of the paper is to describe the details of a recipe that uniformly characterizes unary and binary iterated parametricity in indexed form, and to derive from it a new indexed presentation, called indexed \emph{$\nu$-sets}, of augmented semi-simplicial and semi-cubical sets.
+Alternatively, from a category-theory perspective, we are characterizing, among the class of matching objects up to isomorphism for augmented semi-simplicial and semi-cubical sets, a particular instance that reflects the structure of iterated parametricity.
+
+Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory, and is likely to better reflect the definitional properties of type theory than presheaf-based cubical sets would.
+For example, consider the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\citep{curien14}.
 
@@
 The construction was conceived in Summer 2019, and the mechanization began in late 2019.
-A sketch of the construction was presented at the 2020 HoTT-UF workshop and the completion of the mechanization was reported at the TYPES 2022 conference.
+A sketch of the construction was presented at the 2020 HoTT-UF workshop, and the completion of the mechanization was reported at the TYPES 2022 conference.
 
@@
 Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``color''.
-Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over the singleton set of one fixed color.
-
+Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over the singleton set of a fixed color.
 Let us associate dimension $0$ to colors; then, points are dimension $1$, lines are dimension $2$, and so on.
 There is hence a shift by one when compared to semi-simplicial sets.
-We can then draw augmented semi-simplicial sets like semi-simplicial sets, except for this shift by one.
-
-While ordinary semi-simplicial sets are presheaves over the semi-simplex category, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus.
+
+While ordinary semi-simplicial sets are presheaves over the semi-simplex category, augmented semi-simplicial sets are presheaves over \DeltaPlus.
 There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that can be extended to semi-cubical sets in a straightforward manner.
@@
 \begin{notation}[Finite sequences]
-  We denote finite sequences by $[i_1, \ldots i_n]$ for $i_j$ ranging over some domain.
-In particular, the empty sequence is written $[]$ and we define $i :: [j_1, \ldots, j_n]$ to be $[i, j_1, \ldots, j_n]$.
+  We denote finite sequences by $i_1 \ldots i_n$ for $i_j$ ranging over some domain. The empty sequence is written $\epsilon$.
 \end{notation}
@@
     \begin{cases}
-      f                  & \text{if $g = []$}                                                        \\
-      0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
-      a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
+      f                  & \text{if $g = \epsilon$}                                                        \\
+      0\,(g' \circ f)  & \text{if $g = (0\,g')$}                                                 \\
+      a\,(g' \circ f') & \text{if $g = (\kstar\,g')$, $f = (a\,f')$, where $a = 0$ or $\kstar$} \\
     \end{cases}                \\
-    \id                     & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom_{\DeltaPlus}(n, n)$}
+    \id                     & := \kstar \ldots \kstar \text{ $n$ times for $\id \in \Hom_{\DeltaPlus}(n, n)$}
   \end{align*}
@@
 
-The standard augmented $0$-semi-simplex is a singleton made of one color (in our case black).
-Standard augmented $n$-semi-simplices for $n\geq 1$ have a geometric interpretation, and we illustrate them for dimensions $1$, $2$, and $3$.
+The standard augmented $0$-semi-simplex is a singleton made of one color (in this case, black).
+Standard augmented $n$-semi-simplices for $n \geq 1$ have a geometric interpretation, and we illustrate them for dimensions $1$, $2$, and $3$.
 
@@
   The standard augmented $2$-semi-simplex is drawn as two points, given by $\Hom(1, 2)$, along with a line connecting them, given by $\Hom(2, 2)$.
-We use the color black to denote the unique morphisms in $\Hom(0, 1)$ and $\Hom(0, 2)$.
+We use black to denote the unique morphisms in $\Hom(0, 1)$ and $\Hom(0, 2)$.
   \begin{equation*}
@@
 More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base and gluing on top of it another copy lifted by one dimension.
-In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.
-In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by~$\kstar$.
+In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point, and so on.
+In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by $\kstar$.
 Note that the components may be oriented by letting each $n$-dimensional component point to the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ of the $n$-dimensional component with $0$.
@@
 \subsection*{Semi-cubical sets}
-Semi-cubical sets are defined like augmented semi-simplicial sets except that $\DeltaPlus$ is replaced by $\Cube$ in which we take sequences of $L$, $R$ and $\star$, instead of sequences of $0$ and $\kstar$.
-They represent ordinary semi-cubical sets, with faces (and no augmentation).
+Semi-cubical sets are defined like augmented semi-simplicial sets except that $\DeltaPlus$ is replaced by $\Cube$ in which we take sequences of $L$, $R$ and $\kstar$, instead of sequences of $0$ and $\kstar$.
 
@@
     \begin{cases}
-      f                  & \text{if $g = []$}                                                               \\
-      a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a = L$ or $R$}                           \\
-      a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a = L$, $R$, or $\kstar$} \\
+      f                  & \text{if $g = \epsilon$}                                                               \\
+      a\,(g' \circ f)  & \text{if $g = (a\,g')$}, \text{where $a = L$ or $R$}                           \\
+      a\,(g' \circ f') & \text{if $g = (\kstar\,g')$, $f = (a\,f')$, where $a = L$, $R$, or $\kstar$} \\
     \end{cases} \\
-    \id                & := [\kstar, \ldots, \kstar] \text{ $n$ times}
+    \id                & := \kstar \ldots \kstar \text{ $n$ times}
   \end{align*}
@@
     \begin{tikzcd}
-      \{\}
+      \epsilon
     \end{tikzcd}
@@
 The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$.
-Note that the components can be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$ to the one obtained by replacing the leftmost $\kstar$ with $R$.
+Note that the components can be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$, to the one obtained by replacing the leftmost $\kstar$ with $R$.
 
@@
     \Obj_{\hexagon}       & := \Nat                                                                           \\
-    \Hom_{\hexagon}(p, n) & := \{l \in (\nu \cup \{\kstar\})^n \mid \text{number of $\kstar$ in $l = p$}\}    \\
+    \Hom_{\hexagon}(p, n) & := \{l \in (\nu \sqcup \{\kstar\})^n \mid \text{number of $\kstar$ in $l = p$}\}    \\
     g \circ f             & :=
     \begin{cases}
-      f                  & \text{if $g = []$}                                                                 \\
-      a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a \in \nu$}                                \\
-      a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a \in \nu$ or $a = \kstar$} \\
+      f                  & \text{if $g = \epsilon$}                                                                 \\
+      a\,(g' \circ f)  & \text{if $g = (a\,g')$}, \text{where $a \in \nu$}                                \\
+      a\,(g' \circ f') & \text{if $g = (\kstar\,g')$, $f = (a\,f')$, where $a \in \nu$ or $a = \kstar$} \\
     \end{cases}   \\
-    \id                   & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom_{\hexagon}(n, n)$}
+    \id                   & := \kstar \ldots \kstar \text{ $n$ times for $\id \in \Hom_{\hexagon}(n, n)$}
   \end{align*}
@@
 As in the augmented semi-simplicial and semi-cubical cases, the standard $(n + 1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
-We clarify in the next sections how this process of construction is similar to the parametricity translation developed for functional programming~\citep{reynolds83} and more generally for type theory~\citep{bernardy10, bernardy11, atkey14, bernardy15}.
+We clarify in the next sections, how this process of construction is similar to the parametricity translation developed for functional programming~\citep{reynolds83} and more generally for type theory~\citep{bernardy10,bernardy11,atkey14,bernardy15}.
 
@@
 Martin-Löf's Type theory~(\citeyear{martinlof75,martinlof84}) is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
-It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda~(\citeyear{agda23}), Coq~(\citeyear{coq23}) or Lean~(\citeyear{lean15}).
+It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda~(\citeyear{agda23}), Coq~(\citeyear{coq23}) and Lean~(\citeyear{lean15}).
 In type theory, propositions are types and proofs are programs.
-A particularity of type theory is also that types and programs, hence propositions and proofs also, are considered modulo an equational theory called definitional equality.
+Type theory includes \emph{definitional equality}, by which all propositions and proofs are quotiented.
 
@@
 These models support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\citep{hottbook}.
-In type theory, types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number.
-Main types in type theory are the types of dependent pairs, written $\Sigma a : A.\,B(a)$, the types of dependent functions, written $\Pi a:A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$, and the type of propositional equality, written $t = u$.
-As a notation, the type of dependent pairs when $B$ is actually not dependent on $A$ is shortened into $A \times B$ and the type of dependent functions when $B$ is not dependent on $A$ is written $A \rightarrow B$.
+
+Types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number.
+The main types in type theory are the types of dependent pairs, written $\Sigma a : A.\,B(a)$, the types of dependent functions, written $\Pi a : A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$, and the type of propositional equality, written $t = u$.
+As a notation, the type of dependent pairs when $B$ is not dependent on $A$ is shortened into $A \times B$ and the type of dependent functions when $B$ is not dependent on $A$ is written $A \rightarrow B$.
 We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, called $\textsf{bool}$, and the type of natural numbers.
 We also assume that our type theory includes the coinductive type of infinite tuples.
-We also write $\hd$ and $\tl$ the projections of dependent pairs, and $\refl$ for reflexivity.
+We write $\hd$ and $\tl$ the projections of dependent pairs, and $\refl$ for reflexivity.
 Logical propositions being types themselves, we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification.
 
-A type-theoretic notion of sets can be recovered in each universe as $\U[m]$, denoting the subtype of $\Type_m$ for which paths are degenerated, what can be expressed by the property of Uniqueness of Identity Proofs (UIP).
+A type-theoretic notion of sets can be recovered in each universe as $\U[m]$, denoting the subtype of $\Type_m$ for which paths are degenerated, using Uniqueness of Identity Proofs (UIP).
 Technically, this is expressed as a structure equipping a domain $\Dom$ with the property $\UIP$:
@@
 
-By the notations $\Type$ and $\U$ will be meant $\Type_m$ or $\U[m]$ at some unspecified universe level $m$.
-
-We are also interested in \emph{extensional} type theory; i.e.
-in a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\citep{martinlof84}:
+By notation, $\Type$ and $\U$ mean $\Type_m$ and $\U[m]$ at some unspecified universe level $m$.
+
+We are also interested in \emph{extensional} type theory, a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\citep{martinlof84}:
 \begin{equation*}
@@
 
-Note that the reflection rule implies UIP so that $\U$ and $\Type$ ae equivalent in extensional type theory.
-The reflection rules also implies functional extensionality, and, actually, extensional type theory is logically equivalent to intensional type theory extended with UIP and functional extensionality~\citep{HofmannPhd}.
+Note that the reflection rule implies UIP so that $\U$ and $\Type$ are equivalent in extensional type theory.
+The reflection rules also implies functional extensionality.
+Extensional type theory is logically equivalent to intensional type theory extended with UIP and functional extensionality~\citep{HofmannPhd}.
 
 \section{Relating to parametricity\label{sec:rel-param}}
-Let us recall from the introduction, the form taken by the indexed presentation of a semi-cubical set:
+Recall from the introduction, the form taken by the indexed presentation of a semi-cubical set:
 \begin{align*}
@@
 
-In there, the process of construction of the type of $X_1$ from that of $X_0$, and from the type of $X_2$ to that of $X_1$, and so on, is similar to iteratively applying a binary parametricity translation.
-The binary parametricity which we consider interprets a closed type $A$ by a family $A_\kstar$ over $A \times A$, what can be seen as a graph whose vertices are in $A$.
-To each type constructor is thus associated the construction of a graph.
+Here, the process of construction of the type of $X_1$ from that of $X_0$, and of the type of $X_2$ from that of $X_1$, is similar to iteratively applying a binary parametricity translation.
+The binary parametricity which we consider interprets a closed type $A$ by a family $A_\kstar$ over $A \times A$, and this can be seen as a graph whose vertices are in $A$.
+Each type constructor is associated with the construction of a graph.
 To start with, the type of types $\U$ is interpreted as the family of type of families ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \times A_R \rightarrow \U$ of families over $A_L$ and $A_R$.

### 2023-12-17 paper/paper.tex
paper: some more polish

@@
       f                  & \text{if $g = \epsilon$}                                                        \\
-      0\,(g' \circ f)  & \text{if $g = (0\,g')$}                                                 \\
-      a\,(g' \circ f') & \text{if $g = (\kstar\,g')$, $f = (a\,f')$, where $a = 0$ or $\kstar$} \\
+      0\,(g' \circ f)  & \text{if $g = 0\,g'$}                                                 \\
+      a\,(g' \circ f') & \text{if $g = \kstar\,g'$, $f = a\,f'$, where $a = 0$ or $\kstar$} \\
     \end{cases}                \\
@@
       f                  & \text{if $g = \epsilon$}                                                               \\
-      a\,(g' \circ f)  & \text{if $g = (a\,g')$}, \text{where $a = L$ or $R$}                           \\
-      a\,(g' \circ f') & \text{if $g = (\kstar\,g')$, $f = (a\,f')$, where $a = L$, $R$, or $\kstar$} \\
+      a\,(g' \circ f)  & \text{if $g = a\,g'$}, \text{where $a = L$ or $R$}                           \\
+      a\,(g' \circ f') & \text{if $g = \kstar\,g'$, $f = a\,f'$, where $a = L$, $R$, or $\kstar$} \\
     \end{cases} \\
@@
       f                  & \text{if $g = \epsilon$}                                                                 \\
-      a\,(g' \circ f)  & \text{if $g = (a\,g')$}, \text{where $a \in \nu$}                                \\
-      a\,(g' \circ f') & \text{if $g = (\kstar\,g')$, $f = (a\,f')$, where $a \in \nu$ or $a = \kstar$} \\
+      a\,(g' \circ f)  & \text{if $g = a\,g'$}, \text{where $a \in \nu$}                                \\
+      a\,(g' \circ f') & \text{if $g = \kstar\,g'$, $f = a\,f'$, where $a \in \nu$ or $a = \kstar$} \\
     \end{cases}   \\

### 2023-12-24 paper/paper.tex
paper: major polish

@@
 
-The idea for such an indexed presentation of presheaves over a direct category was mentioned at the Univalent Foundations year in the context of defining semi-simplicial types~\footnote{See e.g.
+The idea for such an indexed presentation of presheaves over a direct category was mentioned at the Univalent Foundations year in the context of defining semi-simplicial types\footnote{See e.g.
 \href{https://ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}{ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}.}.
@@
 The confusion was however, common at the time.} formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
-Another by \cite{part15} formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17} formalized in (an emulation of a two-level type theory in) the Agda proof assistant~\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
+Another by \cite{part15} formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17} formalized in (an emulation of a two-level type theory in) the Agda proof assistant\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
 
@@
 However, exhibiting a concrete instance of a presheaf in indexed form only requires providing the families, since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition of the structure.
-
-In category-theoretic terms, the indexing set of the family $X_n$ in the indexed presentation is a \emph{matching object} of the presheaf at $n$.
-The indexed presentation of presheaves over a direct category can then be identified with a subclass of ordinary presheaves known as Reedy fibrant, where Reedy fibrancy precisely expresses that the set $X_n$ in the fibered presentation is a $\Sigma$-type over a representative of the class of equivalence of matching objects at level $n$~\citep{shulman14,kraus17}.
 
@@
 We obtain a \emph{unary} variant of Reynolds \emph{binary} parametricity by using predicates or families instead of relations or correspondences, and this is a form of realizability~\citep{bernardy12,lasson12,moulin16}.
-It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
+It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
 This suggests that the definition of augmented semi-simplicial sets and semi-cubical sets can both be seen as instances of a more general construction, which we call $\nu$-sets, of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu+1$, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
@@
 The main contribution of the paper is to describe the details of a recipe that uniformly characterizes unary and binary iterated parametricity in indexed form, and to derive from it a new indexed presentation, called indexed \emph{$\nu$-sets}, of augmented semi-simplicial and semi-cubical sets.
-Alternatively, from a category-theory perspective, we are characterizing, among the class of matching objects up to isomorphism for augmented semi-simplicial and semi-cubical sets, a particular instance that reflects the structure of iterated parametricity.
 
@@
 
-Sections~\ref{sec:ett} and~\ref{sec:itt} describe the construction at an informal level of discourse:
+Sections \ref{sec:ett} and \ref{sec:itt} describe the construction at an informal level of discourse:
 \begin{enumerate}
@@
 The second limitation is that we want the construction to be formalizable in the Coq proof assistant whose underlying type theory is intensional.
-Section~\ref{sec:itt} thus rephrases the construction in (informal) intensional type theory.
+Section \ref{sec:itt} thus rephrases the construction in (informal) intensional type theory.
 \end{enumerate}
 
-Sections~\ref{sec:wf}, \ref{sec:le}, and \ref{sec:eqproperties} describe additional issues to be addressed in order to get a fully formal construction:
+Sections \ref{sec:wf}, \ref{sec:le}, and \ref{sec:eqproperties} describe additional issues to be addressed in order to get a fully formal construction:
 \begin{enumerate}
-  \item The well-foundedness of the induction requires a special termination evidence which will be discussed in section~\ref{sec:wf}.
+  \item The well-foundedness of the induction requires a special termination evidence which will be discussed in section \ref{sec:wf}.
   \item The construction is indexed over integers and holds under some constraints on the range of these integers.
@@
 We adopted the former approach, requiring the construction to be dependent on proofs of inequalities on natural numbers.
-We discuss how we deal with such dependencies in section~\ref{sec:le}.
-  \item A number of standard groupoid properties of equality as well as type isomorphisms have been left implicit in the informal definition. This is discussed in section~\ref{sec:eqproperties}.
+We discuss how we deal with such dependencies in section \ref{sec:le}.
+  \item A number of standard groupoid properties of equality as well as type isomorphisms have been left implicit in the informal definition. This is discussed in section \ref{sec:eqproperties}.
 \end{enumerate}
@@
 
-Table \ref{tab:coind} describes the type of a $\nu$-set at level $m$ in indexed form, as the type of a coinductively-defined infinite sequence of type families representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $m$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
-This is made possible because the $0$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, defined to be the unit type, and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
+Table \ref{tab:coind} describes the type of a $\nu$-set at level $m$ in indexed form, as the type of a coinductively-defined infinite sequence of type families representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
+This is made possible because the $0$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, defined to be in the unit type, and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
 
@@
 In the infinite sequence of type families representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$.
-The type $\fullframe$ defines a matching object.
 It is recursively defined in table \ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
-The rationale behind $\framep$, $\layer$ and $\painting$ will be explained later but it should already be noticed that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table \ref{tab:faces}, and this restriction operator is in turn defined using auxiliary definitions $\restrl$ and $\restrc$.
-
-Notably, the definition of $\restrl$ relies on an equality expressing the commutation of the composition of $\restrf$.
+A $\fullframe$ describes a boundary of a standard form (simplex, cube), which we decompose into $\layer$, and a $\painting$ corresponds to a filled frame.
+Notice that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table \ref{tab:faces}, and this restriction operator is in turn defined using auxiliary definitions $\restrl$ and $\restrc$.
+
+Notably, the definition of $\restrl$ relies on an equality expressing the commutation of the composition of two $\restrf$.
 The proof of this commutation is worth being made explicit, which we do in table \ref{tab:coh} using proof-term notations.
@@
 Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
-The exact way this mutual recursion is eventually formalized is explained in section~\ref{sec:wf}.
-
-Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that the construction builds an effective sequence of types not mentioning coherences anymore.
+The exact way this mutual recursion is eventually formalized is explained in section \ref{sec:wf}.
+
+Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that in this case the construction builds an effective sequence of types not mentioning coherences anymore.
 \\
@@
 
-To assign types to $X_0, X_1, X_2, \ldots$ in the indexed representation, we give a recursive definition relying on the building blocks called $\framep$, $\layer$, and $\painting$.
-A $\framep$ is a boundary of a standard form (simplex, cube), which we decompose into $\layer$, and a $\painting$ corresponds to a filled $\framep$.
-Some $\framep$ are full and we call them $\fullframe$: they represent matching objects.
-
-Every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
-Compared to the informal description given in section~\ref{sec:rel-param}, this amounts to applying isomorphisms such as $(A \rightarrow B \rightarrow C) \simeq (A \times B \rightarrow C)$ or $(\Pi a: A.\, (B a \rightarrow C)) \simeq ((\Sigma a: A.\, B a) \rightarrow C)$.
+There is a $\fullframe$ for each level $n$, written $\fullframe[n]$, and
+every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
+Compared to the informal description given in section \ref{sec:rel-param}, this amounts to applying isomorphisms such as $(A \rightarrow B \rightarrow C) \simeq (A \times B \rightarrow C)$ or $(\Pi a: A.\, (B a \rightarrow C)) \simeq ((\Sigma a: A.\, B a) \rightarrow C)$.
 In particular, $\fullframe[n]$ is a ``telescope'', or a nesting of $\Sigma$-types.
 
-We now illustrate how to recursively build $\fullframe[n]$.
-To begin, let us set $\fullframe[0] = \unittype$, so that the type $\U$ given to $X_0$ in section~\ref{sec:rel-param} can be equivalently formulated as $\unittype \rightarrow \U$.
+To illustrate how to recursively build $\fullframe[n]$, let us begin by setting $\fullframe[0] \defeq \unittype$, so that the type $\U$ given to $X_0$ in section \ref{sec:rel-param} can be equivalently formulated as $\unittype \rightarrow \U$.
 Then, more generally, let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from $\unittype$, and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
@@
 Such $\painting[n][p]$ fills a space framed by a partial $\framep[n][p]$ so that, together, they form a filled $\fullframe[n]$.
-For instance, in the picture, each of the two $\painting[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\painting[2][1]$ of $\layer[3][1]$ is the line shown in red, stretched into a partial square filling the partial frames made of respectively the left and right border of the blue square, and each of the two $\painting[2][2]$ of $\layer[3][2]$ is a point shown in green, stretched into a partial square filling the full frames made respectively of the upper and lower borders of the blue and red squares.
+For instance, in the picture, each of the two $\painting[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\painting[2][1]$ of $\layer[3][1]$ is a line, shown in red, stretched into a partial square filling the partial frames made of respectively, the left and right border of the blue square, and each of the two $\painting[2][2]$ of $\layer[3][2]$ is the point shown in green, stretched into a partial square filling the full frames made respectively of the upper and lower borders of the blue and red squares.
 A $\painting[n][p]$ complements a $\framep[n][p]$ by adding layers needed to form a $\fullframe[n]$ and by filling the resulting $\fullframe[n]$ with an inhabitant of $X_n$.
-Layers are added from dimension $n$ to dimension $p$ that is opposite to the order from $0$ to $p$ the $\framep[n][p]$ are built, as shown below.
+Layers are added from dimension $n$ to dimension $p$, opposite to the order from $0$ to $p$ the $\framep[n][p]$ are built, as shown below.
 \begin{equation*}
@@
 
-So far, we have not paid attention to the fact that we have a dependent type, shown as a $\Sigma$-type.
-Let us be more precise about this requirement.
-First, $\fullframe[n]$ depends on all $X_i$ up to $n - 1$.
+So far, we have not paid attention to the fact that we have a dependent type, shown as $\Sigma$.
+To be more precise, note that $\fullframe[n]$ depends on all $X_i$ up to $n - 1$.
 So, we need to package up $X_i$, for $i < n$, into a nesting of $\Sigma$-types, constituting the type of a $n$-truncated $\nu$-set, which we wrote $\X[][<n][]$.
@@
 We also need a way to characterize the $\nu$ borders of each $\painting[n-1][p]$ that composes a $\layer[n][p]$, and this is where the restriction $\restrf[n][p][\epsilon][p]$ arrives, for each $\epsilon < \nu$.
-For instance, on the picture, the left and right $\painting[2][1]$, shown in red, are laid on respectively the left and right borders of the blue boxes, and hence needs to depend on $\framep[3][1]$.
-The left and right borders of the two blue boxes are extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$.
+For instance, in the picture, the left and right $\painting[2][1]$, shown in red, are laid on respectively the left and right borders of the blue boxes, and hence need to depend on $\framep[3][1]$.
+The left and right borders of the two blue boxes are then extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$.
 We can then refine again the previous equation by showing the dependencies on $d$, as shown below.
-
 \begin{equation*}
@@
 The operation $\restrf[n][p][\epsilon][q]$ restricts the $p$ first layers of a frame, and the construction is by recursion on the structure of a frame $d$.
-This necessitates the definitions $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$ and $c$ a $\painting$.
-The key case is $\restrc[n][p][\epsilon][p](d)(c)$, where $c$, a $\painting[n][p]$, has necessarily the form of $((c_L, c_R), \_)$: $\restrc[n][p][L][p]$ picks out $c_L$, a $\painting[n-1][p]$, $\restrc[n][p][R][p]$ picks out the $c_R$, also a $\painting[n-1][p]$, and $\_$, a $\painting[n][p+1]$, is discarded.
+This necessitates the definitions $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$, and $c$ a $\painting$.
+The key case is $\restrc[n][p][\epsilon][p](d)(c)$, where $c$, a $\painting[n][p]$, necessarily has the form of $((c_L, c_R), \_)$.
+Here, $\restrc[n][p][L][p]$ picks out $c_L$, a $\painting[n-1][p]$, $\restrc[n][p][R][p]$ picks out the $c_R$, also a $\painting[n-1][p]$, and the last component, shown as $\_$, a $\painting[n][p+1]$, is discarded.
 There is one last difficulty, which we illustrate by writing down expected and actual types.
@@
 Hence, we need a coherence condition to commute the restrictions.
-Coherence conditions similar to this necessitate what are shown as, $\cohf$, $\cohl$ and $\cohc$ in table~\ref{tab:coh}.
+Coherence conditions similar to this necessitate what are shown as, $\cohf$, $\cohl$ and $\cohc$ in table \ref{tab:coh}.
 These are by induction on the structure of $\framep$, $\layer$ and $\painting$.
-Note that, for the construction in intensional type theory, we further need a $2$-dimensional coherence condition, $\coht$, for $\cohl$.
-This is explained in the next section.
+Note that, for the construction in intensional type theory, we further need a $2$-dimensional coherence condition, $\coht$, for $\cohl$, which is explained in the next section.
 
@@
 For readability purpose, we however make explicit only the key coherence conditions of the construction.
-Other cases of equality reasoning would have to be made explicit to fully obtain a construction in intensional type theory but these other steps are standard enough to be omitted at this stage.
-See section~\ref{sec:eqproperties} for the details.
-
-The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit in table~\ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
+Other cases of equality reasoning would have to be made explicit to fully obtain a construction in intensional type theory, but these steps are standard enough to be omitted at this stage.
+See section \ref{sec:eqproperties} for the details.
+
+The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit in table \ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
 \\
@@
 \vspace{1em}
-The proof of $\cohf$ itself requires making explicit several rewritings which were invisible in extensional type theory.
+The proof of $\cohf$ itself requires making explicit several rewrites which were invisible in extensional type theory.
 The commutation of $\restrl$ lives in a type referring to $\cohf$, so we need a transport along the commutation of $\restrf$ in the statement of $\cohl$.
-The proof of $\cohl$ is the most involved proof of the construction.
-It requires a higher-dimensional coherence condition, $\coht$, whose exact formulation is as follows.
+The proof of $\cohl$ is the most involved proof of the construction, as it requires a higher-dimensional coherence condition, $\coht$, whose exact formulation is as follows.
 \renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
@@
 where $\ap$ applies a function on two sides of an equality, and $\bullet$ is transitivity of equality.
-This property of equality proofs holds in \U, and since our formalization is done in \U, the term is trivially discharged.
+This property of equality proofs holds in \U, and since our construction is done in \U, the term is trivially discharged.
 
@@
 Notice that each $\restrl$ in the type of $\cohl$ is hiding a $\cohf$ rewrite: this makes a sum total of three $\cohf$ rewrites on the left-hand side, and two $\cohf$ rewrites on the right-hand side.
-In the proof term of $\cohl$, $\cohc$ has one $\cohf$ rewrite on its left-hand side and zero on the right-hand side.
-This, combined with the two terms of the form $\ap \cohf$, matches our expectation of three $\cohf$ on the left-hand side and two $\cohf$ on the right-hand side.
+In the proof term of $\cohl$, $\cohc$ has one $\cohf$ rewrite on its left-hand side.
+This, combined with the two terms of the form $\ap \cohf$, matches our expectation of three $\cohf$ on the left-hand side, and two $\cohf$ on the right-hand side.
 Then, $\coht$ can be seen as expressing the commutation of these $\cohf$ terms.
@@
 Since the construction shown in the previous sections is by induction on $n$, and dependencies are on lower $n$ and $p < n$, one would imagine formalizing this using well-founded induction in dependent type theory.
-We initially tried this approach: we had terms dependent on the proofs of the case distinction that $n' \leq n$ implies $n' < n$ or $n' = n$, but these proofs did not come with enough definitional properties to be usable in practice.
-Hence, we chose a different route: in practice, since $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$, we only need to keep track of three ``levels'', and we built separate data structures for the levels, with dependencies.
+We initially tried this approach, and had terms dependent on the proofs of the case distinction that $n' \leq n$ implies $n' < n$ or $n' = n$, but these proofs did not come with enough definitional properties to be usable in practice.
+Hence, we chose a different route: in practice, since $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$, we only need to keep track of three ``levels''; hence, we built separate data structures for the levels, with dependencies.
 More concretely, we build the ten definitions shown in the tables by induction, and this is part of the definition of a larger record.
@@
 The entire construction relies on inequalities over natural numbers, and we use two different definitions of $\leq$ addressing different concerns in our formalization.
-In order to build our first variant, we present an intermediate ``recursive definition'', phrased as:
+In order to build our first variant, we use an intermediate ``recursive definition'' phrased as:
 
@@
 Here $\SProp$ is a definitionally proof-irrelevant impredicative universe morally\footnote{In Coq~(\citeyear{coq23}), it is however a stand-alone universe unrelated to the universe hierarchy.} living at the bottom of the universe hierarchy~\citep{gilbert19}.
-By placing the definition in \SProp, we have definitional equality of all inequality proofs.
-For the purpose of unification, however, this definition does not go far enough.
+By placing the definition in \SProp, we have definitional equality of inequality proofs.
+However, for the purpose of unification, this definition does not go far enough.
 Consider the unification problems:
@@
 \subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
-The construction relies on the groupoid properties of equality which are left implicit in table~\ref{fulltab:coh}.
+The construction relies on the groupoid properties of equality which are left implicit in table \ref{fulltab:coh}.
 The use of the equivalence between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
@@
 in a talk at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf})).
-More generally, we believe these lines of work to eventually provide alternative models to parametric type theories~\citep{nuyts17,cavallo19} where equality of types, now a family rather than the total space of a fibration, is not only definitionally isomorphic to bridges~\cite{bernardy15} but definitionally the same as bridges.
+More generally, we believe these lines of work would eventually provide alternative models to parametric type theories~\citep{nuyts17,cavallo19} where equality of types, now a family rather than the total space of a fibration, is not only definitionally isomorphic to bridges~\citep{bernardy15}, but definitionally the same as bridges.
 
 By equipping the universe construction with a structure of equivalences, as suggested along the lines of \cite{altenkirch15}, we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models.
-In particular, we wonder whether the indexed approach might provide definitional properties which are otherwise lost when detouring via presheaves.
 In particular, we conjecture being able to justify univalence holding definitionally.
@@
 
-Another direction for future work is to give a general definition of presheaf in indexed form over a direct category and to show the equivalence with the standard definition of presheaf.
+Another direction for future work is to give a general definition of presheaf in indexed form over a direct category, and to show the equivalence with the standard definition of presheaf.
 

### 2023-12-24 paper/paper.tex
paper: minor polish

@@
 However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the equivalence.
-This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.Let us consider, for instance, the case of a semi-cubical set~\citep{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
+This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.
+Let us consider, for instance, the case of a semi-cubical set~\citep{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
 Formulated in type theory, the corresponding presheaf definition of a semi-cubical set prescribes a family of sets and face maps between them as follows.
@@
 up to cubical faces identities.
-Here, $X_1$ can be seen as a family over $X_0 \times X_0$ presented in a fibered form, $X_2$ can be seen as a family over $X_1 \times X_1 \times X_1 \times X_1$.
+Here, $X_1$ can be seen as a family over $X_0 \times X_0$, and $X_2$ can be seen as a family over $X_1 \times X_1 \times X_1 \times X_1$, in the fibered presentation.
 This suggests an alternative indexed presentation of the presheaf as a stratified sequence of families indexed by families of lower rank, taking into account the coherence conditions to prevent duplications.
@@
 
-The idea for such an indexed presentation of presheaves over a direct category was mentioned at the Univalent Foundations year in the context of defining semi-simplicial types\footnote{See e.g.
-\href{https://ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}{ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}.}.
+The idea for such an indexed presentation of presheaves over a direct category was mentioned at the Univalent Foundations year in the context of defining semi-simplicial types\footnote{\href{https://ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}{ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}}.
 A few constructions have been proposed since then.
@@
 The confusion was however, common at the time.} formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
-Another by \cite{part15} formalized in (an emulation of logic-enriched homotopy type theory in) the Plastic proof assistant, and yet another by \cite{annenkovCK17} formalized in (an emulation of a two-level type theory in) the Agda proof assistant\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
+Another by \cite{part15} formalized in an emulation of logic-enriched homotopy type theory in the Plastic proof assistant, and yet another by \cite{annenkovCK17} formalized in an emulation of a two-level type theory in the Agda proof assistant\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
 
@@
 
-Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21} which are closer to the syntax of type theory, and is likely to better reflect the definitional properties of type theory than presheaf-based cubical sets would.
+Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21}, which are closer to the syntax of type theory, and are likely to better reflect the definitional properties of type theory than presheaf-based cubical sets would.
 For example, consider the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\citep{curien14}.
@@
 
-More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base and gluing on top of it another copy lifted by one dimension.
+More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base, and gluing on top of it another copy lifted by one dimension.
 In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point, and so on.
@@
 Dependent $\nu$-sets could also be defined, opening the way to construct $\Pi$-types and $\Sigma$-types of $\nu$-sets.
-A $\nu$-set of $\nu$-sets representing a universe could also be defined (as sketched e.g.
-in a talk at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf})).
+A $\nu$-set of $\nu$-sets representing a universe could also be defined as sketched in a talk at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf}).
 More generally, we believe these lines of work would eventually provide alternative models to parametric type theories~\citep{nuyts17,cavallo19} where equality of types, now a family rather than the total space of a fibration, is not only definitionally isomorphic to bridges~\citep{bernardy15}, but definitionally the same as bridges.

### 2023-12-25 paper/paper.tex
paper: misc

@@
 
-\subsection*{Reynolds' parametricity and its unary and binary variants}
+\subsection*{Reynolds parametricity and its unary and binary variants}
 In the context of functional programming, Reynolds parametricity~(\citeyear{reynolds83}) interprets types as relations characterizing the observational behavior of programs of this type.
@@
 In particular, we conjecture being able to justify univalence holding definitionally.
-Our approach would also definitively ground cubical type theory in iterated parametricity.
+Our approach would also firmly ground cubical type theory in iterated parametricity.
 

### 2023-12-25 paper/paper.tex
paper: final polish

@@
 
-Sections \ref{sec:ett} and \ref{sec:itt} describe the construction at an informal level of discourse:
+Sections~\ref{sec:ett} and~\ref{sec:itt} describe the construction at an informal level of discourse:
 \begin{enumerate}
-  \item In \ref{sec:ett}, we present it in informal extensional type theory where equational reasoning is left implicit.
+  \item In~\ref{sec:ett}, we present it in informal extensional type theory where equational reasoning is left implicit.
   \item While reasoning in extensional type theory is similar to reasoning in set theory regarding how equality is handled, extensional type theory has two limitations.
@@
 The second limitation is that we want the construction to be formalizable in the Coq proof assistant whose underlying type theory is intensional.
-Section \ref{sec:itt} thus rephrases the construction in (informal) intensional type theory.
+Section~\ref{sec:itt} thus rephrases the construction in (informal) intensional type theory.
 \end{enumerate}
 
-Sections \ref{sec:wf}, \ref{sec:le}, and \ref{sec:eqproperties} describe additional issues to be addressed in order to get a fully formal construction:
+Sections~\ref{sec:wf},~\ref{sec:le}, and~\ref{sec:eqproperties} describe additional issues to be addressed in order to get a fully formal construction:
 \begin{enumerate}
-  \item The well-foundedness of the induction requires a special termination evidence which will be discussed in section \ref{sec:wf}.
+  \item The well-foundedness of the induction requires a special termination evidence which will be discussed in section~\ref{sec:wf}.
   \item The construction is indexed over integers and holds under some constraints on the range of these integers.
@@
 We adopted the former approach, requiring the construction to be dependent on proofs of inequalities on natural numbers.
-We discuss how we deal with such dependencies in section \ref{sec:le}.
-  \item A number of standard groupoid properties of equality as well as type isomorphisms have been left implicit in the informal definition. This is discussed in section \ref{sec:eqproperties}.
+We discuss how we deal with such dependencies in section~\ref{sec:le}.
+  \item A number of standard groupoid properties of equality as well as type isomorphisms have been left implicit in the informal definition. This is discussed in section~\ref{sec:eqproperties}.
 \end{enumerate}
@@
 
-Table \ref{tab:coind} describes the type of a $\nu$-set at level $m$ in indexed form, as the type of a coinductively-defined infinite sequence of type families representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
+Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ in indexed form, as the type of a coinductively-defined infinite sequence of type families representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
 This is made possible because the $0$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, defined to be in the unit type, and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
 
-The definition of the type of a $n$-truncated $\nu$-set is in turn described in table \ref{tab:core}.
+The definition of the type of a $n$-truncated $\nu$-set is in turn described in table~\ref{tab:core}.
 In the infinite sequence of type families representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$.
-It is recursively defined in table \ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
+It is recursively defined in table~\ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
 A $\fullframe$ describes a boundary of a standard form (simplex, cube), which we decompose into $\layer$, and a $\painting$ corresponds to a filled frame.
-Notice that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table \ref{tab:faces}, and this restriction operator is in turn defined using auxiliary definitions $\restrl$ and $\restrc$.
+Notice that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table~\ref{tab:faces}, and this restriction operator is in turn defined using auxiliary definitions $\restrl$ and $\restrc$.
 
 Notably, the definition of $\restrl$ relies on an equality expressing the commutation of the composition of two $\restrf$.
-The proof of this commutation is worth being made explicit, which we do in table \ref{tab:coh} using proof-term notations.
+The proof of this commutation is worth being made explicit, which we do in table~\ref{tab:coh} using proof-term notations.
 The proof requires an induction on the dimension and on the structure of $\framep$, $\layer$, and $\painting$.
@@
 Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
-The exact way this mutual recursion is eventually formalized is explained in section \ref{sec:wf}.
+The exact way this mutual recursion is eventually formalized is explained in section~\ref{sec:wf}.
 
@@
 every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
-Compared to the informal description given in section \ref{sec:rel-param}, this amounts to applying isomorphisms such as $(A \rightarrow B \rightarrow C) \simeq (A \times B \rightarrow C)$ or $(\Pi a: A.\, (B a \rightarrow C)) \simeq ((\Sigma a: A.\, B a) \rightarrow C)$.
-In particular, $\fullframe[n]$ is a ``telescope'', or a nesting of $\Sigma$-types.
-
-To illustrate how to recursively build $\fullframe[n]$, let us begin by setting $\fullframe[0] \defeq \unittype$, so that the type $\U$ given to $X_0$ in section \ref{sec:rel-param} can be equivalently formulated as $\unittype \rightarrow \U$.
+Here, $\fullframe[n]$ is thus a ``telescope'' collecting all arguments of the type of $X_i$ in section~\ref{sec:rel-param} as a nesting of $\Sigma$-types.
+
+To illustrate how to recursively build $\fullframe[n]$, let us begin by setting $\fullframe[0] \defeq \unittype$, so that the type $\U$ given to $X_0$ in section~\ref{sec:rel-param} can be equivalently formulated as $\unittype \rightarrow \U$.
 Then, more generally, let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from $\unittype$, and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
-For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of $\unittype$ and $\layer[1][0]$, as shown below.
-The figure also mentions how the type of $X_2$ is structured.
+For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of $\unittype$ and $\layer[1][0]$.
+Then, $X_2$ is similarly made of two layers.
+
 \begin{small}
@@
 Hence, we need a coherence condition to commute the restrictions.
-Coherence conditions similar to this necessitate what are shown as, $\cohf$, $\cohl$ and $\cohc$ in table \ref{tab:coh}.
+Coherence conditions similar to this necessitate what are shown as, $\cohf$, $\cohl$ and $\cohc$ in table~\ref{tab:coh}.
 These are by induction on the structure of $\framep$, $\layer$ and $\painting$.
@@
 Other cases of equality reasoning would have to be made explicit to fully obtain a construction in intensional type theory, but these steps are standard enough to be omitted at this stage.
-See section \ref{sec:eqproperties} for the details.
-
-The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit in table \ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
+See section~\ref{sec:eqproperties} for the details.
+
+The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit in table~\ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
 \\
@@
 \subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
-The construction relies on the groupoid properties of equality which are left implicit in table \ref{fulltab:coh}.
+The construction relies on the groupoid properties of equality which are left implicit in table~\ref{fulltab:coh}.
 The use of the equivalence between $u = v$ and $\Sigma (p:u.\hd = v.\hd).

### 2023-12-25 paper/paper.tex
paper, art.cls: draft for arxiv submission

@@
-\documentclass{msc}
+\documentclass{art.cls/art}
 
 \usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, lmodern, mathpazo, anyfontsize, xargs, environ, multirow, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
 \usepackage[prefix=bonak]{art.cls/xkeymask}
@@
 \newcommand{\SProp}{\ensuremath{\mathsf{\color{spanish-blue}{SProp}}}}
-
-% Examples
-\newtheorem{example}[therm]{Example}
 
@@
 
+% Set the entire document to gray65, and pick certain colors
+\color{gray65}
+
 \begin{document}
 \title{A parametricity-based formalization of semi-simplicial and semi-cubical sets}
-\begin{authgrp}
-  \author{Hugo Herbelin}
-  \affiliation{Université Paris Cité, Inria, CNRS, IRIF, Paris
-    \email{Hugo.Herbelin@inria.fr}}
-  \author{Ramkumar Ramachandra}
-  \affiliation{Université Paris Cité (2020-2022), Unaffiliated
-    \email{r@artagnon.com}}
-\end{authgrp}
+\date{}
+\author{
+  \textcolor{gray80}{Hugo Herbelin} \\
+  \itshape \textcolor{gray80}{Université Paris-Cité, Inria, CNRS, IRIF, Paris} \\
+  \ttfamily \textcolor{gray80}{Hugo.Herbelin@inria.fr}
+  \and
+  \textcolor{gray80}{Ramkumar Ramachandra} \\
+  \itshape \textcolor{gray80}{Université Paris-Cité (2020-2022), Unaffiliated} \\
+  \ttfamily \textcolor{gray80}{r@artagnon.com}
+}
+\maketitle
 \begin{abstract}
   Semi-simplicial and semi-cubical sets are commonly defined as presheaves over respectively, the semi-simplex or semi-cube category.
-Homotopy Type Theory then popularized an alternative definition, where the set of $n$-simplices or $n$-cubes are instead regrouped into the families of the fibers over their faces, leading to a characterization we call \emph{indexed}.
+Homotopy Type Theory then popularized an alternative definition, where the set of $n$-simplices or $n$-cubes are instead regrouped into the families of the fibres over their faces, leading to a characterization we call \emph{indexed}.
 Moreover, it is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds parametricity, respectively in its unary and binary variants.
@@
 \end{abstract}
-\maketitle
-\vspace{-2em} % Remove space after abstract
 
 \section{Introduction}
-\subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
-A family of sets can commonly be represented in two ways: as a family properly speaking, indexed by the elements of a given set $S$, or as a set $T$ together with a map from $T$ to $S$, which specifies for each element of set $T$ its dependency on $S$.
+\subsection*{Fibred vs indexed presentation of semi-simplicial and semi-cubical sets}
+A family of sets can commonly be represented in two ways: as a family properly speaking, indexed by the elements of a given set $S$, or as a set $T$ together with a map from $T$ to $S$, which specifies for each element of $T$ its dependency on $S$.
 In the former case, we call it an \emph{indexed} presentation.
-In the latter case, the set associated to a given element of $S$ is the fiber of this element, so we call it a \emph{fibered} presentation.
-The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\citep{hottbook} as the fibered/indexed equivalence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family equivalence and unbundled/bundled equivalence.
-The fibered/indexed nomenclature echoes the Grothendieck construction of fibered categories from indexed categories.
-The most elementary instance of the equivalence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'', and its proof requires univalence~\citep{hottbook}.}.
-\begin{equation*}
-  \mbox{(fibered)}\qquad(\Sigma T: \U. (T \rightarrow S)) ~\simeq~ (S \rightarrow \U)\qquad \mbox{(indexed)}
+In the latter case, the set associated to a given element of $S$ is the fibre of this element, so we call it a \emph{fibred} presentation.
+The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\cite{hottbook} as the fibred/indexed equivalence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family equivalence and unbundled/bundled equivalence.
+The fibred/indexed nomenclature echoes the Grothendieck construction of fibred categories from indexed categories.
+The most elementary instance of the equivalence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'', and its proof requires univalence~\cite{hottbook}.}.
+\begin{equation*}
+  \mbox{(fibred)}\qquad(\Sigma T: \U. (T \rightarrow S)) ~\simeq~ (S \rightarrow \U)\qquad \mbox{(indexed)}
 \end{equation*}
@@
 A \emph{presheaf} on an category is a family of sets indexed by the object of the category with maps indexed by the morphisms.
-As such, it lives on the indexed side of the equivalence, contrasting with the fibered side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
-However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the equivalence.
+As such, it lives on the indexed side of the equivalence, contrasting with the fibred side, where we have \emph{discrete Grothendieck fibrations}~\cite{LoregianRiehl20}.
+However, there are situations where a presheaf can also be seen as living on the fibred side of the equivalence.
 This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.
-Let us consider, for instance, the case of a semi-cubical set~\citep{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
+Let us consider, for instance, the case of a semi-cubical set~\cite{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
 Formulated in type theory, the corresponding presheaf definition of a semi-cubical set prescribes a family of sets and face maps between them as follows.
@@
 up to cubical faces identities.
-Here, $X_1$ can be seen as a family over $X_0 \times X_0$, and $X_2$ can be seen as a family over $X_1 \times X_1 \times X_1 \times X_1$, in the fibered presentation.
-This suggests an alternative indexed presentation of the presheaf as a stratified sequence of families indexed by families of lower rank, taking into account the coherence conditions to prevent duplications.
+Here, $X_1$ can be seen as a family over $X_0 \times X_0$, and $X_2$ can be seen as a family over $X_1 \times X_1 \times X_1 \times X_1$, in the fibred presentation, together with coherence conditions between the $X_1$ seen as families over $X_0 \times X_0$.
+This suggests an alternative indexed presentation of the presheaf as a stratified sequence of families indexed by families of lower rank, taking into account those coherence conditions to prevent duplications.
 Formulated in type theory, it takes the form:
-\begin{align*}
-  X_0 & :              & \U                                                                            \\
-  X_1 & :              & X_0 \times X_0 \rightarrow \U                                                 \\
-  X_2 & : \Pi a b c d. & X_1(a)(b) \times X_1 (c)(d) \times X_1(a)(c) \times X_1 (b)(d) \rightarrow \U \\
+\begin{equation*}
+  \begin{array}{lll}
+    X_0 & :               \U                                                                          \\
+    X_1 & :               X_0 \times X_0 \rightarrow  \U                                              \\
+    X_2 & : \Pi a b c d.\,  X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
     \ldots
-\end{align*}
+  \end{array}
+\end{equation*}
 
@@
 The first construction by \cite{voevodsky12} relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
-The second, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it claimed to construct semi-simplicial types, but the construction was done in a type theory with Unicity of Identity Proofs.
-Consequentially, what was really obtained was an indexed presentation of semi-simplicial sets.
+The second, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it implicitly claimed to construct semi-simplicial types, but the construction was done in a type theory with Uniqueness of Identity Proofs.
+Consequently, what was really obtained was an indexed presentation of semi-simplicial sets.
 The confusion was however, common at the time.} formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
-Another by \cite{part15} formalized in an emulation of logic-enriched homotopy type theory in the Plastic proof assistant, and yet another by \cite{annenkovCK17} formalized in an emulation of a two-level type theory in the Agda proof assistant\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
+Another by \cite{part15} formalized in an emulation of logic-enriched homotopy type theory in the Plastic proof assistant, and yet another by \cite{altenkirch16} formalized in an emulation of a two-level type theory in the Agda proof assistant\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, rely, like in Voevodsky, on the presentation of the semi-simplicial category from increasing injective maps between finite ordinals.
+The latter constructions, besides being stated as providing semi-simplicial types (thanks to an extension of the type theory), are particularly concise, taking advantage of a definition of increasing injective maps between finite ordinals as type-theoretic functions to inherit the associativity of composition directly from it holding in type theory.
+This contrasts with the combinatorial construction in \cite{herbelin15} where equations over face maps have to be proved by induction.
+
+By taking the sum of each component of an indexed presentation over the indexing set of this component, one obtains back a presheaf in the ordinary sense that has a property of \emph{Reedy fibrancy}, that is whose morphisms are projections in the set-theoretic sense.
+Such Reedy fibrant presheaves over a direct category have been studied in e.g.
+\cite{shulman15}, \cite{kraus17} and \cite{annenkovCK17,AnnenkovCKS2023}, presenting generic constructions over such presheaves.
 
@@
 \subsection*{Reynolds parametricity and its unary and binary variants}
-In the context of functional programming, Reynolds parametricity~(\citeyear{reynolds83}) interprets types as relations characterizing the observational behavior of programs of this type.
+In the context of functional programming, Reynolds parametricity~\cite{reynolds83} interprets types as relations characterizing the observational behaviour of programs of this type.
 More generally, families over a product of sets, or \emph{correspondences}, can be used in place of relations.
-Parametricity can then be iterated, and relying on the fibered presentation of correspondences as spans, it has been noted that iterated Reynolds parametricity has the structure of a cubical set~\citep{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
-We obtain a \emph{unary} variant of Reynolds \emph{binary} parametricity by using predicates or families instead of relations or correspondences, and this is a form of realizability~\citep{bernardy12,lasson12,moulin16}.
-It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
-This suggests that the definition of augmented semi-simplicial sets and semi-cubical sets can both be seen as instances of a more general construction, which we call $\nu$-sets, of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu+1$, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
+Parametricity can then be iterated, and relying on the fibred presentation of correspondences as spans, it has been noted that iterated Reynolds parametricity has the structure of a cubical set~\cite{altenkirch15,moulin16,johann17,moeneclaey21,moeneclaey22phd}.
+We obtain a \emph{unary} variant of Reynolds \emph{binary} parametricity by using predicates or families instead of relations or correspondences, and this is a form of realizability~\cite{bernardy12,lasson12,moulin16}.
+Cubical set models which differ only by the arity one~\cite{bernardy15} or two~\cite{bezem13} were introduced, and this led to a general notion of affine $\nu$-ary cubes in \cite{nuytsdevriese24}.
+In parallel, it has been noted that iterated unary parametricity has the structure of an augmented simplicial set\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
+This suggests that the definition of augmented semi-simplicial sets and semi-cubical sets can in turn be seen as particular instances of the restriction of Nuyts-Devriese's $\nu$-ary cubes to only faces, which we call $\nu$-sets, of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu+1$, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
 
@@
 
-Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21}, which are closer to the syntax of type theory, and are likely to better reflect the definitional properties of type theory than presheaf-based cubical sets would.
-For example, consider the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\citep{curien14}.
+Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\cite{bernardy15,nuyts17,cavallo19} and cubical type theory~\cite{bezem13,cohen16,angiuli21}, which are closer to the syntax of type theory, and are likely to better reflect the definitional properties of type theory than presheaf-based cubical sets would.
+For example, consider the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\cite{curien14}.
+
+Our construction has the unique property of reflecting the structure of parametricity and of yielding both augmented semi-simplicial and semi-cubical sets from the same construction.
+The approach taken in \cite{part15} and \cite{altenkirch16} takes benefit of the definitional compositionality of increasing injective maps, but we do not see how they could be generalized to yield semi-cubical sets.
 
@@
 \subsection*{Augmented semi-simplicial sets}
-Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``color''.
-Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over the singleton set of a fixed color.
-Let us associate dimension $0$ to colors; then, points are dimension $1$, lines are dimension $2$, and so on.
-There is hence a shift by one when compared to semi-simplicial sets.
+Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``colour''.
+Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over the singleton set of a fixed colour.
+Let us associate dimension $-1$ to colours; then, points are dimension $0$, lines are dimension $1$, and so on.
 
@@
 There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that can be extended to semi-cubical sets in a straightforward manner.
+In particular, we start numbering objects from $0$ instead of $-1$ so that there is a shift by one compared to the standard numbering of augmented semi-simplicial sets.
 
@@
   The definition of $\DeltaPlus$ is shown below.
-Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$.
+Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than or equal to that of $g$.
 It can be shown that composition is associative and that $\id$ is neutral.
@@
 
-To provide examples, we define the standard augmented $n$-semi-simplex.
+To provide examples, we define the standard augmented $n$-semi-simplex, taking into account the shift by one in the numbering.
 
 \begin{definition}[$\DeltaPlus^n$]
-  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as the Yoneda embedding of $n \in \Obj(\DeltaPlus)$:
+  The standard augmented $(n-1)$-semi-simplex $\DeltaPlus^{n-1}$ is defined as the Yoneda embedding of $n \in \Obj(\DeltaPlus)$:
   \begin{align*}
-    \DeltaPlus^n    & : \Set_{\DeltaPlus}        \\
-    \DeltaPlus^n(p) & := \Hom(p, n)              \\
-    \DeltaPlus^n(f) & := \lambda g .\, g \circ f
+    \DeltaPlus^{n-1}    & : \Set_{\DeltaPlus}        \\
+    \DeltaPlus^{n-1}(p) & := \Hom(p, n)              \\
+    \DeltaPlus^{n-1}(f) & := \lambda g .\, g \circ f
   \end{align*}
@@
 
-The standard augmented $0$-semi-simplex is a singleton made of one color (in this case, black).
-Standard augmented $n$-semi-simplices for $n \geq 1$ have a geometric interpretation, and we illustrate them for dimensions $1$, $2$, and $3$.
-
-\begin{example}[$\DeltaPlus^1$]
-  The standard augmented $1$-semi-simplex can be pictured as a point, colored black, corresponding to the unique morphism in $\Hom(0, 1)$.
+The standard augmented $(-1)$-semi-simplex is a singleton made of one colour (in this case, black).
+Standard augmented $n$-semi-simplices for $n \geq 0$ have a geometric interpretation, and we illustrate them for dimensions $0$, $1$, and $2$.
+
+\begin{example}[$\DeltaPlus^0$]
+  The standard augmented $0$-semi-simplex can be pictured as a point, coloured black, corresponding to the unique morphism in $\Hom(0, 1)$.
 This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$.
@@
 
-\begin{example}[$\DeltaPlus^2$]
-  The standard augmented $2$-semi-simplex is drawn as two points, given by $\Hom(1, 2)$, along with a line connecting them, given by $\Hom(2, 2)$.
+\begin{example}[$\DeltaPlus^1$]
+  The standard augmented $1$-semi-simplex is drawn as two points, given by $\Hom(1, 2)$, along with a line connecting them, given by $\Hom(2, 2)$.
 We use black to denote the unique morphisms in $\Hom(0, 1)$ and $\Hom(0, 2)$.
@@
 
-\begin{example}[$\DeltaPlus^3$]
-  $\DeltaPlus^3$ is drawn as three points, given by $\Hom(1, 3)$, three lines connecting them, given by $\Hom(2, 3)$, and a triangular filler given by $\Hom(3, 3)$.
+\begin{example}[$\DeltaPlus^2$]
+  $\DeltaPlus^2$ is drawn as three points, given by $\Hom(1, 3)$, three lines connecting them, given by $\Hom(2, 3)$, and a triangular filler given by $\Hom(3, 3)$.
   \begin{equation*}
@@
 More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base, and gluing on top of it another copy lifted by one dimension.
-In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point, and so on.
+In the second copy, the colour becomes an extra point, the points become lines connecting the points of the base to the extra point, and so on.
 In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by $\kstar$.
@@
 
-  Again, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
+  Again, if $g \circ f$ is well-defined, then the length of $f$ is less than or equal to that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
 \end{definition}
@@
 
-More generally, the standard $(n + 1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them on their border by a cylinder obtained as a third copy stretched in the new dimension.
-The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$.
+More generally, the standard $(n + 1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them on their border by a prism obtained as a third copy stretched in the new dimension.
+The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the prism is obtained by postfixing with $\kstar$.
 Note that the components can be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$, to the one obtained by replacing the leftmost $\kstar$ with $R$.
@@
     \graymidrule
-    Interpretation    & Augmented semi-simplicial types & Semi-cubical types \\
+    Interpretation    & Augmented semi-simplicial sets & Semi-cubical sets \\
     \bottomrule
@@
   The definition of $\nu$-semi-shape category is shown below.
-Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$.
+Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than or equal to that of $g$.
 It can be shown that composition is associative and that $\id$ is neutral.
@@
 As in the augmented semi-simplicial and semi-cubical cases, the standard $(n + 1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
-We clarify in the next sections, how this process of construction is similar to the parametricity translation developed for functional programming~\citep{reynolds83} and more generally for type theory~\citep{bernardy10,bernardy11,atkey14,bernardy15}.
-
-\section{Type theory}
-Martin-Löf's Type theory~(\citeyear{martinlof75,martinlof84}) is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
-It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda~(\citeyear{agda23}), Coq~(\citeyear{coq23}) and Lean~(\citeyear{lean15}).
+We clarify in the next sections, how this process of construction is similar to the parametricity translation developed for functional programming~\cite{reynolds83} and more generally for type theory~\cite{bernardy10,bernardy11,atkey14,bernardy15}.
+
+\section{Type theory\label{sec:tt}}
+Martin-Löf's Type theory~(\cite{martinlof75,martinlof84}) is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
+It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda, Coq and Lean.
 In type theory, propositions are types and proofs are programs.
@@
 Type theory is a flexible formalism supporting different models.
-Some models are based on topological spaces, where equality is interpreted as path, and substitutivity of equality as transport~\citep{kapulkin21}.
-These models support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\citep{hottbook}.
+Some models come from homotopy theory, and are based on simplicial sets or related structures~\cite{HofmannStreicher94,kapulkin21,BezemCoquandHuber13,cchm}: in these models, equality is interpreted as paths, and they support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\cite{hottbook}.
 
 Types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number.
-The main types in type theory are the types of dependent pairs, written $\Sigma a : A.\,B(a)$, the types of dependent functions, written $\Pi a : A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$, and the type of propositional equality, written $t = u$.
+The main types in type theory are the type of dependent pairs, written $\Sigma a : A.\,B(a)$, the type of dependent functions, written $\Pi a : A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$, and the type of propositional equalities, written $t = u$.
 As a notation, the type of dependent pairs when $B$ is not dependent on $A$ is shortened into $A \times B$ and the type of dependent functions when $B$ is not dependent on $A$ is written $A \rightarrow B$.
-We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, called $\textsf{bool}$, and the type of natural numbers.
-We also assume that our type theory includes the coinductive type of infinite tuples.
+We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, and the type of natural numbers.
 We write $\hd$ and $\tl$ the projections of dependent pairs, and $\refl$ for reflexivity.
 Logical propositions being types themselves, we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification.
+We also assume that our type theory includes a coinductively-defined notion of dependent streams described in Appendix \ref{app:depstream}.
 
@@
 
-We are also interested in \emph{extensional} type theory, a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\citep{martinlof84}:
+We are also interested in \emph{extensional} type theory, a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
 \begin{equation*}
@@
 Note that the reflection rule implies UIP so that $\U$ and $\Type$ are equivalent in extensional type theory.
-The reflection rules also implies functional extensionality.
-Extensional type theory is logically equivalent to intensional type theory extended with UIP and functional extensionality~\citep{HofmannPhd}.
+The rule also implies functional extensionality.
+Extensional type theory is logically equivalent to intensional type theory extended with UIP and functional extensionality~\cite{HofmannPhd}.
 
@@
 Recall from the introduction, the form taken by the indexed presentation of a semi-cubical set:
-\begin{align*}
-  X_0 & :              & \U                                                                            \\
-  X_1 & :              & X_0 \times X_0 \rightarrow \U                                                 \\
-  X_2 & : \Pi a b c d. & X_1(a)(b) \times X_1 (c)(d) \times X_1(a)(c) \times X_1 (b)(d) \rightarrow \U \\
+\begin{equation*}
+  \begin{array}{lll}
+    X_0 & :               \U                                                                         \\
+    X_1 & :               X_0 \times X_0 \rightarrow \U                                              \\
+    X_2 & : \Pi a b c d.\, X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
     \ldots
-\end{align*}
+  \end{array}
+\end{equation*}
 
@@
 To start with, the type of types $\U$ is interpreted as the family of type of families ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \times A_R \rightarrow \U$ of families over $A_L$ and $A_R$.
-Also, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the graph $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
-\begin{align*}
-  (\Pi a: A.\, B)_\kstar(f_L,f_R) \; \defeq \; \Pi (a_L,a_R): (A \times A).\, (A_\kstar(a_L,a_R)\,\rightarrow B_\kstar(f_L(a_L),f_R(a_R)))
-\end{align*}
+Also, for $A$ interpreted by $A_\kstar$ and $B(a)$, for $a:A$, interpreted by $B_\kstar((a_L,a_R),a_\kstar)$ with $a_\kstar:A_\kstar(a_L,a_R)$, a dependent function type $\Pi a: A.\, B(a)$ is interpreted as the graph $(\Pi a: A.\, B(a))_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B(a)$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
+\begin{equation*}
+  \begin{array}{l}
+    (\Pi a: A.\, B(a))_\kstar(f_L,f_R) \; \defeq \\
+    \multicolumn{1}{r}{\qquad\Pi (a_L,a_R): (A \times A).\, \Pi a_\kstar: (A_\kstar(a_L,a_R)\, B_\kstar((a_L,a_R),a_\kstar)(f_L(a_L),f_R(a_R)))}
+  \end{array}
+\end{equation*}
 
@@
 \begin{align*}
-  \Pi ((x_{LL},x_{lR}),(x_{RL},x_{RR})): ((X \times X) \times (X \times X)). \\
+  \Pi ((x_{LL},x_{LR}),(x_{RL},x_{RR})): ((X \times X) \times (X \times X)). \\
   (X_\kstar(x_{LL},x_{LR}) \times X_\kstar(x_{RL},x_{RR})
@@
 \begin{equation*}
-  \begin{array}{llllr}
+  \begin{array}{lllll}
     X_0 & \defeq & X                & : & \U                                             \\
@@
 \begin{enumerate}
-  \item In~\ref{sec:ett}, we present it in informal extensional type theory where equational reasoning is left implicit.
+  \item In~\ref{sec:ett}, we present it in informal extensional type theory where equational reasoning is left implicit, and we give an intuition for the construction in~\ref{sec:intuition}.
   \item While reasoning in extensional type theory is similar to reasoning in set theory regarding how equality is handled, extensional type theory has two limitations.
@@
 Section~\ref{sec:itt} thus rephrases the construction in (informal) intensional type theory.
+Since $\nu$-sets are $0$-truncated types, we compensate for the absence of UIP by assuming a ``local UIP'', requiring types to be \U.
 \end{enumerate}
@@
 
-A $\nu$-set is a sequence of families of $\U$, that is $\U[m]$ for some universe level $m$. We call such sequence a $\nu$-set at level $m$, whose type thus lives in $\U[m+1]$.
-
-Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ in indexed form, as the type of a coinductively-defined infinite sequence of type families representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
-This is made possible because the $0$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, defined to be in the unit type, and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
+A $\nu$-set in indexed form is a sequence of families of $\U$, that is $\U[m]$ for some universe level $m$. We call such sequence a $\nu$-set at level $m$, whose type thus lives in $\U[m+1]$.
+
+Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets: using the notations of Section~\ref{sec:tt}, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
+Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
+This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
 
@@
 This is what $\cohf$ does using auxiliary proofs $\cohl$ and $\cohc$.
-Even though it looks independent of the definitions from the the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
+Even though it looks independent of the definitions from the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
 More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be defined in one go by induction on $p$.
@@
 
-Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that in this case the construction builds an effective sequence of types not mentioning coherences anymore.
+Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that the construction builds an effective sequence of types not mentioning coherences anymore.
 \\
@@
 
-There is a $\fullframe$ for each level $n$, written $\fullframe[n]$, and
-every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
-Here, $\fullframe[n]$ is thus a ``telescope'' collecting all arguments of the type of $X_i$ in section~\ref{sec:rel-param} as a nesting of $\Sigma$-types.
+There is a $\fullframe$ for each dimension $n$, written $\fullframe[n]$, and every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
+Here, $\fullframe[n]$ is a ``telescope'' collecting all arguments of the type of $X_i$ in section~\ref{sec:rel-param} as a nesting of $\Sigma$-types.
 
@@
                            \end{array}\hspace{-0.4em}
-            \right).\, \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][L]}}_{\painting[1][1]}}_{\painting[1][0]}
+            \right).\, \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][L][0]}}_{\painting[1][1]}}_{\painting[1][0]}
             \\ \times \\
@@
                            \end{array}\hspace{-0.4em}
-            \right).\, \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][R]}}_{\painting[1][1]}}_{\painting[1][0]}
+            \right).\, \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][R][0]}}_{\painting[1][1]}}_{\painting[1][0]}
           \end{array}
@@
                              \end{array}\hspace{-0.4em}
-              \right)\right)}_{\restrf[2][1][L]}}_{\painting[1][1]}
+              \right)\right)}_{\restrf[2][1][L][1]}}_{\painting[1][1]}
           \\ \times \\
@@
                              \end{array}\hspace{-0.4em}
-              \right)\right)}_{\restrf[2][1][R]}}_{\painting[1][1]}
+              \right)\right)}_{\restrf[2][1][R][1]}}_{\painting[1][1]}
         \end{array}
@@
 The figure on the left is $\framep[3][1]$, in the middle is $\framep[3][2]$, and on the right is $\framep[3][3]$, which is full.
-Further, $\framep[3][1]$ is made of one layer, $\layer[3][0]$, shown in blue, $\framep[3][2]$ is made of one additional layer, $\layer[3][1]$, shown in red, $\framep[3][3]$ is made of one more layer, $\layer[3][2]$, shown in green.
+Further, $\framep[3][1]$ is made of one layer, $\layer[3][0]$, shown as the front and back faces (blue boxes), $\framep[3][2]$ is made of one additional layer, $\layer[3][1]$, shown as the left and right faces (red boxes), $\framep[3][3]$ is made of one more layer, $\layer[3][2]$, shown as the top face (green box).
 
@@
 Such $\painting[n][p]$ fills a space framed by a partial $\framep[n][p]$ so that, together, they form a filled $\fullframe[n]$.
-For instance, in the picture, each of the two $\painting[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\painting[2][1]$ of $\layer[3][1]$ is a line, shown in red, stretched into a partial square filling the partial frames made of respectively, the left and right border of the blue square, and each of the two $\painting[2][2]$ of $\layer[3][2]$ is the point shown in green, stretched into a partial square filling the full frames made respectively of the upper and lower borders of the blue and red squares.
+For instance, in the picture, each of the two $\painting[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\painting[2][1]$ of $\layer[3][1]$ is a line, shown as lines across the left and right faces (red lines), stretched into a partial square filling the partial frames made of respectively, the left and right border of the front-back faces (blue), and each of the two $\painting[2][2]$ of $\layer[3][2]$ is the point shown on the top face (green point), stretched into a partial square filling the full frames made respectively of the upper and lower borders of the front-back and left-right faces (blue and red squares).
 A $\painting[n][p]$ complements a $\framep[n][p]$ by adding layers needed to form a $\fullframe[n]$ and by filling the resulting $\fullframe[n]$ with an inhabitant of $X_n$.
@@
 We also need a way to characterize the $\nu$ borders of each $\painting[n-1][p]$ that composes a $\layer[n][p]$, and this is where the restriction $\restrf[n][p][\epsilon][p]$ arrives, for each $\epsilon < \nu$.
-For instance, in the picture, the left and right $\painting[2][1]$, shown in red, are laid on respectively the left and right borders of the blue boxes, and hence need to depend on $\framep[3][1]$.
-The left and right borders of the two blue boxes are then extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$.
+For instance, in the picture, the left and right faces (red), $\painting[2][1]$, are laid on respectively the left and right borders of the front and back faces (blue), and hence need to depend on $\framep[3][1]$.
+The left and right borders of the front and back faces are then extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$.
 We can then refine again the previous equation by showing the dependencies on $d$, as shown below.
@@
 \begin{align*}
-  c_\omega & : \painting[n-1][p](D.\hd)(\restrf[n-1][p][\omega][q](d))
+  c_\omega & : \painting[n-1][p](D.\hd)(\restrf[n][p][\omega][p](d))
 \end{align*}
-$\restrl[n][p][\epsilon](d)(c_L, c_R)$ produces a layer in which the $\omega$-component has the type
+$\restrl[n][p][\epsilon][q](d)(c_L, c_R)$ produces a layer in which the $\omega$-component has the type
 \begin{equation*}
@@
 
-\subsection{From extensional to intensional type theory: making explicit the equality proofs\label{sec:itt}}
+\subsection{From extensional to intensional type theory\label{sec:itt}}
 \renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
-In this section, we intend to get rid of the reflection rule and make explicit what is needed to rephrase the construction in intensional type theory.
-For readability purpose, we however make explicit only the key coherence conditions of the construction.
+In this section, we intend to get rid of the reflection rule and make explicit the equational reasoning step needed to rephrase the construction in intensional type theory.
+For readability purposes, we make only explicit in this section the key coherence conditions of the construction.
 Other cases of equality reasoning would have to be made explicit to fully obtain a construction in intensional type theory, but these steps are standard enough to be omitted at this stage.
@@
 \begin{align*}
-  \cohf[m][\omega][\theta][r][p][n][p][][d = {\restrf[m][\epsilon][q+2][n][p][][d = \d]}]\;\bullet     \\
-  \ap \restrf[m][\omega][r][n][p][][]\;(\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d])\;\bullet   \\
-  \cohf[m][\epsilon][\omega][q][r][n][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =              \\
-  \ap \restrf[m][\theta][p][n][p][][]\;(\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d])\;\bullet \\
-  \cohf[m][\epsilon][\theta][q][p][n][p][][d = {\restrf[m][\omega][r+1][n][p][][d = \d]}]\;\bullet     \\
-  \ap \restrf[m][\epsilon][q][n][p][]\;(\cohf[m][\omega][\theta][r][p][n][p][][d = \d])
+  \cohf[m][\omega][\theta][r][p][n-1][p][][d = {\restrf[m][\epsilon][q+2][n][p][][d = \d]}]\;\bullet     \\
+  \ap \restrf[m][\omega][r][n-2][p][][]\;(\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d])\;\bullet   \\
+  \cohf[m][\epsilon][\omega][q][r][n-1][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =              \\
+  \ap \restrf[m][\theta][p][n-2][p][][]\;(\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d])\;\bullet \\
+  \cohf[m][\epsilon][\theta][q][p][n-1][p][][d = {\restrf[m][\omega][r+1][n][p][][d = \d]}]\;\bullet     \\
+  \ap \restrf[m][\epsilon][q][n-2][p][]\;(\cohf[m][\omega][\theta][r][p][n][p][][d = \d])
 \end{align*}
@@
 We initially tried this approach, and had terms dependent on the proofs of the case distinction that $n' \leq n$ implies $n' < n$ or $n' = n$, but these proofs did not come with enough definitional properties to be usable in practice.
-Hence, we chose a different route: in practice, since $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$, we only need to keep track of three ``levels''; hence, we built separate data structures for the levels, with dependencies.
-More concretely, we build the ten definitions shown in the tables by induction, and this is part of the definition of a larger record.
-The other fields of the record are $\framep$, $\layer$, $\painting$ at levels $n - 1$ and $n - 2$, $\restrf$, $\restrl$, and $\restrc$ at level $n - 1$, and equations to recall the definitions of these objects at lower levels.
+Hence, we chose a different route: in practice, since $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$, we only need to keep track of three consecutive dimensions.
+Hence, what we build by induction at level $n$, is a structure made not only of the definitions shown in the tables~\ref{tab:frames},~\ref{fulltab:faces}, and~\ref{fulltab:coh}, but also of $\framep$, $\layer$, $\painting$ at levels $n - 1$ and $n - 2$, as well as $\restrf$, $\restrl$, and $\restrc$ at level $n - 1$, together with helper equations.
 
@@
 
-Here $\SProp$ is a definitionally proof-irrelevant impredicative universe morally\footnote{In Coq~(\citeyear{coq23}), it is however a stand-alone universe unrelated to the universe hierarchy.} living at the bottom of the universe hierarchy~\citep{gilbert19}.
+Here, $\SProp$ is a definitionally proof-irrelevant impredicative universe morally\footnote{In Coq, it is however a stand-alone universe unrelated to the universe hierarchy.} living at the bottom of the universe hierarchy~\cite{gilbert19}.
 By placing the definition in \SProp, we have definitional equality of inequality proofs.
@@
 \end{minted}
-
 where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable.
-These two problems definitionally hold in \SProp, but equating them does not solve the existential.
-For unification to be useful in inferring existentials, we present our first variant of $\leq$, which we dub as the ``Yoneda variant'':
+These two problems definitionally hold in \SProp, but equating them does not solve the existential variable.
+For unification to be useful in solving existential variables, we present our first variant of $\leq$, which we dub as the ``Yoneda variant'':
 
@@
 This definition is an improvement over \texttt{leR} since reflexivity is now definitionally the neutral element of transitivity, and associativity of transitivity also holds definitionally.
-Although it significantly eases our proof, there are some instances where unification is unable to solve the existentials, and we have to provide them explicitly.
+Although it significantly eases our proof, there are some instances where unification is unable to solve the existential variables, and we have to provide them explicitly.
 
@@
 \subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
-The construction relies on the groupoid properties of equality which are left implicit in table~\ref{fulltab:coh}.
+The construction relies on groupoid properties of equality which are left implicit in table~\ref{fulltab:coh}.
 The use of the equivalence between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
@@
 \section{Future work}
-The construction could be extended with degeneracies as well as with permutations~\citep{grandis03}.
+The construction could be extended with degeneracies as well as with permutations~\cite{grandis03}.
 Dependent $\nu$-sets could also be defined, opening the way to construct $\Pi$-types and $\Sigma$-types of $\nu$-sets.
-A $\nu$-set of $\nu$-sets representing a universe could also be defined as sketched in a talk at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf}).
-More generally, we believe these lines of work would eventually provide alternative models to parametric type theories~\citep{nuyts17,cavallo19} where equality of types, now a family rather than the total space of a fibration, is not only definitionally isomorphic to bridges~\citep{bernardy15}, but definitionally the same as bridges.
-
-By equipping the universe construction with a structure of equivalences, as suggested along the lines of \cite{altenkirch15}, we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models.
+A $\nu$-set of $\nu$-sets representing a universe could also be defined as sketched in a talk at the HoTT-UF workshop for the bridge case~(\cite{herbelin-hott-uf}).
+More generally, we believe these lines of work would eventually provide alternative models to parametric type theories~\cite{nuyts17,cavallo19} where equality of types, now a family rather than the total space of a fibration, is not only definitionally isomorphic to bridges~\cite{bernardy15}, but definitionally the same as bridges.
+
+By equipping the universe construction with a structure of equivalences, as suggested along the lines of \cite{altenkirch15}, we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\cite{bezem13,cohen16,angiuli21}, saving the detour via the fibred approach inherent to usual presheaf models.
 In particular, we conjecture being able to justify univalence holding definitionally.
@@
 
-Another direction for future work is to give a general definition of presheaf in indexed form over a direct category, and to show the equivalence with the standard definition of presheaf.
-
-\newpage
-\bibliographystyle{msclike}
+Although prior approaches to constructing the indexed presentation of a presheaf over a direct category rely on it being evident by inspection that the fibred and indexed presentations are equivalent, no formal proof has been given, and this is a direction for future work.
+In our construction, we can check by computation of the first levels that it indeed computes the expected sets.
+
+\bibliographystyle{alpha}
 \bibliography{paper}
 
+\appendix
+\fancyhead[L]{\footnotesize\textcolor{gray80}{{\MakeUppercase{Appendix}}}}
+\section*{Appendix: Definition of dependent stream\label{app:depstream}}
+
+\begin{align*}
+  \mbox{\emph{type formation}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\
+  \seqr{}{\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u:A}
+  {\Gamma \vdash Stream_{A,B,f}\, u : \Type_m}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\
+  \mbox{\emph{introduction and eliminations}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     \\
+  \seqr{}{\!\!\!\begin{array}{l}\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u : A \\ \Gamma, a:A \vdash D(a) : \Type_m \qquad \Gamma \vdash w : D(u) \\ \Gamma, a:A, d:D(a) \vdash v(a,d) : B(a) \qquad \Gamma, a:A, d:D(a) \vdash s(a,d) : D(f(a,v(a,d))) \end{array}}{\Gamma \vdash \textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\} : Stream_{A,B,f}\, u}                                                                                                                                                      \\
+  \seqr{}{\Gamma \vdash t : Stream_{A,B,f}\, u}{\Gamma \vdash t.this : B(u)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      \\
+  \seqr{}{\Gamma \vdash t : Stream_{A,B,f}\, u}{\Gamma \vdash t.next : Stream_{A,B,f}\, f(u,t.this)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\
+  \mbox{\emph{computation}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       \\
+  \seqr{}{\!\!\!\begin{array}{l}\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u : A \\ \Gamma, a:A \vdash D(a) : \Type_m \qquad \Gamma \vdash w : D(u) \\ \Gamma, a:A, d:D(a) \vdash v(a,d) : B(a) \qquad \Gamma, a:A, d:D(a) \vdash s(a,d) : D(f(a,v(a,d))) \end{array}}{\Gamma \vdash \textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\}.this \equiv v(u,w) : B(u)}                                                                                                                                                 \\
+  \seqr{}{\!\!\!\begin{array}{l}\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u : A \\ \Gamma, a:A \vdash D(a) : \Type_m \qquad \Gamma \vdash w : D(u) \\ \Gamma, a:A, d:D(a) \vdash v(a,d) : B(a) \qquad \Gamma, a:A, d:D(a) \vdash s(a,d) : D(f(a,v(a,d)))\end{array}}{\!\!\!\begin{array}{r}\Gamma \vdash \textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\}.next \equiv \\ \textsf{cofix}_{a,d,g}^{f(u,v(u,w)),s(u,w))}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\} \\ : Stream_{A,B,f}\,f(u,v(u,w))\end{array}} \\
+\end{align*}
+where $\textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\}$ is a notation for the instantiation on parameter $u$ and internal value $w$ of the corecursive definition of a stream over an arbitrary $a$ generated by a recipe dependent on an arbitrary internal value $d:D(a)$ with first component given by $v(a,d)$ and second component given by $g(f(a,v(a,d)),s(a,d))$ where $g$, typed as $\Gamma, a:A, d:D(a) \vdash g(a,d): Stream_{A,B,f}\, (f(a,d))$, formally represents the recursive call, and where $s(a,d)$ tells how the internal value evolves.
 \end{document}

### 2023-12-31 paper/paper.tex
paper: paper-specific spacing fixes for art.cls
paper: final polish

--- 2023-12-25 paper/paper.tex
@@
 \subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
-A family of sets can commonly be represented in two ways: as a family properly speaking, indexed by the elements of a given set $S$, or as a set $T$ together with a map from $T$ to $S$, which specifies for each element of set $T$ its dependency on $S$.
+A family of sets can commonly be represented in two ways: as a family properly speaking, indexed by the elements of a given set $S$, or as a set $T$ together with a map from $T$ to $S$, which specifies for each element of $T$ its dependency on $S$.
 In the former case, we call it an \emph{indexed} presentation.
@@
 As such, it lives on the indexed side of the equivalence, contrasting with the fibered side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
-However, there are situations where a presheaf $F$ can also be seen as living on the fibered side of the equivalence.
+However, there are situations where a presheaf can also be seen as living on the fibered side of the equivalence.
 This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.
@@
 Formulated in type theory, it takes the form:
-\begin{align*}
+\begin{equation*}
+  \begin{array}{llr}
     X_0 & :              & \U                                                                            \\
     X_1 & :              & X_0 \times X_0 \rightarrow  \U                                                 \\
-  X_2 & : \Pi a b c d. & X_1(a)(b) \times X_1 (c)(d) \times X_1(a)(c) \times X_1 (b)(d) \rightarrow \U \\
+    X_2 & : \Pi a b c d. & X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
     \ldots
-\end{align*}
+  \end{array}
+\end{equation*}
 
@@
 The first construction by \cite{voevodsky12} relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
-The second, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it claimed to construct semi-simplicial types, but the construction was done in a type theory with Unicity of Identity Proofs.
+The second, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it implicitly claimed to construct semi-simplicial types, but the construction was done in a type theory with Unicity of Identity Proofs.
 Consequentially, what was really obtained was an indexed presentation of semi-simplicial sets.
@@
 More generally, families over a product of sets, or \emph{correspondences}, can be used in place of relations.
-Parametricity can then be iterated, and relying on the fibered presentation of correspondences as spans, it has been noted that iterated Reynolds parametricity has the structure of a cubical set~\citep{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}.
+Parametricity can then be iterated, and relying on the fibered presentation of correspondences as spans, it has been noted that iterated Reynolds parametricity has the structure of a cubical set~\citep{altenkirch15,moulin16,johann17,moeneclaey21,moeneclaey22phd}.
 We obtain a \emph{unary} variant of Reynolds \emph{binary} parametricity by using predicates or families instead of relations or correspondences, and this is a form of realizability~\citep{bernardy12,lasson12,moulin16}.
@@
 Types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number.
-The main types in type theory are the types of dependent pairs, written $\Sigma a : A.\,B(a)$, the types of dependent functions, written $\Pi a : A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$, and the type of propositional equality, written $t = u$.
+The main types in type theory are the type of dependent pairs, written $\Sigma a : A.\,B(a)$, the type of dependent functions, written $\Pi a : A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$, and the type of propositional equalities, written $t = u$.
 As a notation, the type of dependent pairs when $B$ is not dependent on $A$ is shortened into $A \times B$ and the type of dependent functions when $B$ is not dependent on $A$ is written $A \rightarrow B$.
-We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, called $\textsf{bool}$, and the type of natural numbers.
-We also assume that our type theory includes the coinductive type of infinite tuples.
+We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, and the type of natural numbers.
+We also assume that our type theory includes the coinductive type of infinite dependent tuples.
 We write $\hd$ and $\tl$ the projections of dependent pairs, and $\refl$ for reflexivity.
@@
 Recall from the introduction, the form taken by the indexed presentation of a semi-cubical set:
-\begin{align*}
+\begin{equation*}
+  \begin{array}{llr}
     X_0 & :              & \U                                                                            \\
     X_1 & :              & X_0 \times X_0 \rightarrow \U                                                 \\
-  X_2 & : \Pi a b c d. & X_1(a)(b) \times X_1 (c)(d) \times X_1(a)(c) \times X_1 (b)(d) \rightarrow \U \\
+    X_2 & : \Pi a b c d. & X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
     \ldots
-\end{align*}
+  \end{array}
+\end{equation*}
 
@@
 
-A $\nu$-set is a sequence of families of $\U$, that is $\U[m]$ for some universe level $m$. We call such sequence a $\nu$-set at level $m$, whose type thus lives in $\U[m+1]$.
+A $\nu$-set in indexed form is a sequence of families of $\U$, that is $\U[m]$ for some universe level $m$. We call such sequence a $\nu$-set at level $m$, whose type thus lives in $\U[m+1]$.
 
@@
 
-Here $\SProp$ is a definitionally proof-irrelevant impredicative universe morally\footnote{In Coq~(\citeyear{coq23}), it is however a stand-alone universe unrelated to the universe hierarchy.} living at the bottom of the universe hierarchy~\citep{gilbert19}.
+Here, $\SProp$ is a definitionally proof-irrelevant impredicative universe morally\footnote{In Coq~(\citeyear{coq23}), it is however a stand-alone universe unrelated to the universe hierarchy.} living at the bottom of the universe hierarchy~\citep{gilbert19}.
 By placing the definition in \SProp, we have definitional equality of inequality proofs.
@@
 \end{minted}
-
 where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable.

### 2023-12-31 paper/paper.tex
paper: arxiv-specific tweak to prose

@@
 Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ in indexed form, as the type of a coinductively-defined infinite sequence of type families representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
-This is made possible because the $0$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, defined to be in the unit type, and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
+This is made possible because the $0$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
 

### 2023-12-31 paper/paper.tex
Spell-checking

@@
 The first construction by \cite{voevodsky12} relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
-The second, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it implicitly claimed to construct semi-simplicial types, but the construction was done in a type theory with Unicity of Identity Proofs.
+The second, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it implicitly claimed to construct semi-simplicial types, but the construction was done in a type theory with Uniqueness of Identity Proofs.
 Consequentially, what was really obtained was an indexed presentation of semi-simplicial sets.
@@
 where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable.
-These two problems definitionally hold in \SProp, but equating them does not solve the existential.
-For unification to be useful in inferring existentials, we present our first variant of $\leq$, which we dub as the ``Yoneda variant'':
+These two problems definitionally hold in \SProp, but equating them does not solve the existential variable.
+For unification to be useful in solving existential variables, we present our first variant of $\leq$, which we dub as the ``Yoneda variant'':
 

### 2024-10-12 paper/paper.tex
paper: double-spacing, declare competing interests
Typos in paper (restr on picture page 22)
paper: update after mscs review

@@
 
+% Double-spacing
+\linespread{2}
+
 \begin{document}
@@
 \end{abstract}
+\footnotetext{Competing interests: The authors declare none}
 \maketitle
@@
 up to cubical faces identities.
-Here, $X_1$ can be seen as a family over $X_0 \times X_0$, and $X_2$ can be seen as a family over $X_1 \times X_1 \times X_1 \times X_1$, in the fibered presentation.
-This suggests an alternative indexed presentation of the presheaf as a stratified sequence of families indexed by families of lower rank, taking into account the coherence conditions to prevent duplications.
+Here, $X_1$ can be seen as a family over $X_0 \times X_0$, and $X_2$ can be seen as a family over $X_1 \times X_1 \times X_1 \times X_1$, in the fibered presentation, together with coherence conditions between the $X_1$ seen as families over $X_0 \times X_0$.
+This suggests an alternative indexed presentation of the presheaf as a stratified sequence of families indexed by families of lower rank, taking into account those coherence conditions to prevent duplications.
 Formulated in type theory, it takes the form:
@@
 The confusion was however, common at the time.} formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
-Another by \cite{part15} formalized in an emulation of logic-enriched homotopy type theory in the Plastic proof assistant, and yet another by \cite{annenkovCK17} formalized in an emulation of a two-level type theory in the Agda proof assistant\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, rely on the presentation of the semi-simplicial category from increasing injective functions over finite ordinals.
+Another by \cite{part15} formalized in an emulation of logic-enriched homotopy type theory in the Plastic proof assistant, and yet another by \cite{altenkirch16} formalized in an emulation of a two-level type theory in the Agda proof assistant\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, rely, like in Voevodsky, on the presentation of the semi-simplicial category from increasing injective maps between finite ordinals.
+The latter constructions are particularly concise, taking advantage of a definition of increasing injective maps between finite ordinals as type-theoretic functions to inherit the associativity of composition directly from it holding in type theory.
+This contrasts with the combinatorial construction in \cite{herbelin15} where equations over face maps have to be proved by induction.
+
+By taking the sum of each component of an indexed presentation over the indexing set of this component, one obtains back a presheaf in the ordinary sense that has a property of \emph{Reedy fibrancy}, that is whose morphisms are projections in the set-theoretic sense.
+Such Reedy fibrant presheaves over a direct category have been studied in e.g.
+\cite{shulman15}, \cite{kraus17} and \cite{annenkovCK17,AnnenkovCKS2023}, presenting generic constructions over such presheaves.
 
@@
 We obtain a \emph{unary} variant of Reynolds \emph{binary} parametricity by using predicates or families instead of relations or correspondences, and this is a form of realizability~\citep{bernardy12,lasson12,moulin16}.
-It has then been noted that iterated unary parametricity has the structure of an augmented simplicial set\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
-This suggests that the definition of augmented semi-simplicial sets and semi-cubical sets can both be seen as instances of a more general construction, which we call $\nu$-sets, of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu+1$, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
+Cubical set models which differ only by the arity one~\citep{bernardy15} or two~\citep{bezem13} were introduced, and this led to a general notion of affine $\nu$-ary cubes in \cite{nuytsdevriese24}.
+In parallel, it has been noted that iterated unary parametricity has the structure of an augmented simplicial set\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
+This suggests that the definition of augmented semi-simplicial sets and semi-cubical sets can in turn be seen as particular instances of the restriction of Nuyts-Devriese's $\nu$-ary cubes to only faces, which we call $\nu$-sets, of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu+1$, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
 
@@
 For example, consider the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\citep{curien14}.
+
+Our construction has the unique property of reflecting the structure of parametricity and of yielding both augmented semi-simplicial and semi-cubical sets from the same construction.
+The approach taken in \cite{part15} and \cite{altenkirch16} takes benefit of the definitional compositionality of increasing injective maps, but we do not see how they could be generalized to yield semi-cubical sets.
 
@@
 Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over the singleton set of a fixed color.
-Let us associate dimension $0$ to colors; then, points are dimension $1$, lines are dimension $2$, and so on.
+Let us associate dimension $-1$ to colors; then, points are dimension $0$, lines are dimension $1$, and so on.
 There is hence a shift by one when compared to semi-simplicial sets.
@@
 
-The standard augmented $0$-semi-simplex is a singleton made of one color (in this case, black).
-Standard augmented $n$-semi-simplices for $n \geq 1$ have a geometric interpretation, and we illustrate them for dimensions $1$, $2$, and $3$.
-
-\begin{example}[$\DeltaPlus^1$]
-  The standard augmented $1$-semi-simplex can be pictured as a point, colored black, corresponding to the unique morphism in $\Hom(0, 1)$.
+The standard augmented $(-1)$-semi-simplex is a singleton made of one color (in this case, black).
+Standard augmented $n$-semi-simplices for $n \geq 0$ have a geometric interpretation, and we illustrate them for dimensions $0$, $1$, and $2$.
+
+\begin{example}[$\DeltaPlus^0$]
+  The standard augmented $0$-semi-simplex can be pictured as a point, colored black, corresponding to the unique morphism in $\Hom(0, 1)$.
 This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$.
@@
 
-\section{Type theory}
+\section{Type theory\label{sec:tt}}
 Martin-Löf's Type theory~(\citeyear{martinlof75,martinlof84}) is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
-It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda~(\citeyear{agda23}), Coq~(\citeyear{coq23}) and Lean~(\citeyear{lean15}).
+It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda, Coq and Lean.
 In type theory, propositions are types and proofs are programs.
@@
 Type theory is a flexible formalism supporting different models.
-Some models are based on topological spaces, where equality is interpreted as path, and substitutivity of equality as transport~\citep{kapulkin21}.
-These models support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\citep{hottbook}.
+Some models come from homotopy theory, and are based on simplicial sets or related structures~\citep{HofmannStreicher94,kapulkin21,BezemCoquandHuber13,cchm}: in these models, equality is interpreted as paths, and they support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\citep{hottbook}.
 
@@
 We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, and the type of natural numbers.
-We also assume that our type theory includes the coinductive type of infinite dependent tuples.
 We write $\hd$ and $\tl$ the projections of dependent pairs, and $\refl$ for reflexivity.
 Logical propositions being types themselves, we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification.
+We also assume that our type theory includes a coinductively-defined notion of dependent streams described in \ref{app:depstream}.
 
@@
 Note that the reflection rule implies UIP so that $\U$ and $\Type$ are equivalent in extensional type theory.
-The reflection rules also implies functional extensionality.
+The rule also implies functional extensionality.
 Extensional type theory is logically equivalent to intensional type theory extended with UIP and functional extensionality~\citep{HofmannPhd}.
@@
 To start with, the type of types $\U$ is interpreted as the family of type of families ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \times A_R \rightarrow \U$ of families over $A_L$ and $A_R$.
-Also, for $A$ interpreted by $A_\kstar$ and $B$ interpreted by $B_\kstar$, a dependent function type $\Pi a: A.\, B$ is interpreted as the graph $(\Pi a: A.\, B)_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
-\begin{align*}
-  (\Pi a: A.\, B)_\kstar(f_L,f_R) \; \defeq \; \Pi (a_L,a_R): (A \times A).\, (A_\kstar(a_L,a_R)\,\rightarrow B_\kstar(f_L(a_L),f_R(a_R)))
+Also, for $A$ interpreted by $A_\kstar$ and $B(a)$, for $a:A$, interpreted by $B_\kstar((a_L,a_R),a_\kstar)$ with $a_\kstar:A_\kstar(a_L,a_R)$, a dependent function type $\Pi a: A.\, B(a)$ is interpreted as the graph $(\Pi a: A.\, B(a))_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B(a)$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
+\begin{align*}
+  (\Pi a: A.\, B(a))_\kstar(f_L,f_R) \; \defeq \; \Pi (a_L,a_R): (A \times A).\, \Pi a_\kstar: (A_\kstar(a_L,a_R)\, B_\kstar((a_L,a_R),a_\kstar)(f_L(a_L),f_R(a_R)))
 \end{align*}
@@
 
-Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ in indexed form, as the type of a coinductively-defined infinite sequence of type families representing the limit of $n$-truncated $\nu$-sets: $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n+1}, X_{n+2}, \ldots$ dependent on a $n$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
-This is made possible because the $0$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $0$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
+Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets: using the notations of Section~\ref{sec:tt}, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
+Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
+This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
 
@@
 
-Here, $\SProp$ is a definitionally proof-irrelevant impredicative universe morally\footnote{In Coq~(\citeyear{coq23}), it is however a stand-alone universe unrelated to the universe hierarchy.} living at the bottom of the universe hierarchy~\citep{gilbert19}.
+Here, $\SProp$ is a definitionally proof-irrelevant impredicative universe morally\footnote{In Coq, it is however a stand-alone universe unrelated to the universe hierarchy.} living at the bottom of the universe hierarchy~\citep{gilbert19}.
 By placing the definition in \SProp, we have definitional equality of inequality proofs.
@@
 
-Another direction for future work is to give a general definition of presheaf in indexed form over a direct category, and to show the equivalence with the standard definition of presheaf.
+Although prior approaches to constructing the indexed presentation of a presheaf over a direct category rely on it being evident by inspection that the fibered and indexed presentations are equivalent, no formal proof has been given, and this is a direction for future work.
+In our construction, we can check by computation of the first levels that it indeed computes the expected sets.
 
@@
 
+\appendix
+\section{Definition of dependent stream\label{app:depstream}}
+
+\begin{align*}
+  \mbox{\emph{type formation}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\
+  \seqr{}{\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u:A}
+  {\Gamma \vdash Stream_{A,B,f}\, u : \Type_m}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\
+  \mbox{\emph{introduction and eliminations}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     \\
+  \seqr{}{\!\!\!\begin{array}{l}\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u : A \\ \Gamma, a:A \vdash D(a) : \Type_m \qquad \Gamma \vdash w : D(u) \\ \Gamma, a:A, d:D(a) \vdash v(a,d) : B(a) \qquad \Gamma, a:A, d:D(a) \vdash s(a,d) : D(f(a,v(a,d))) \end{array}}{\Gamma \vdash \textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\} : Stream_{A,B,f}\, u}                                                                                                                                                      \\
+  \seqr{}{\Gamma \vdash t : Stream_{A,B,f}\, u}{\Gamma \vdash t.this : B(u)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      \\
+  \seqr{}{\Gamma \vdash t : Stream_{A,B,f}\, u}{\Gamma \vdash t.next : Stream_{A,B,f}\, f(u,t.this)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\
+  \mbox{\emph{computation}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       \\
+  \seqr{}{\!\!\!\begin{array}{l}\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u : A \\ \Gamma, a:A \vdash D(a) : \Type_m \qquad \Gamma \vdash w : D(u) \\ \Gamma, a:A, d:D(a) \vdash v(a,d) : B(a) \qquad \Gamma, a:A, d:D(a) \vdash s(a,d) : D(f(a,v(a,d))) \end{array}}{\Gamma \vdash \textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\}.this \equiv v(u,w) : B(u)}                                                                                                                                                 \\
+  \seqr{}{\!\!\!\begin{array}{l}\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u : A \\ \Gamma, a:A \vdash D(a) : \Type_m \qquad \Gamma \vdash w : D(u) \\ \Gamma, a:A, d:D(a) \vdash v(a,d) : B(a) \qquad \Gamma, a:A, d:D(a) \vdash s(a,d) : D(f(a,v(a,d)))\end{array}}{\!\!\!\begin{array}{r}\Gamma \vdash \textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\}.next \equiv \\ \textsf{cofix}_{a,d,g}^{f(u,v(u,w)),s(u,w))}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\} \\ : Stream_{A,B,f}\,f(u,v(u,w))\end{array}} \\
+\end{align*}
+where $\textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\}$ is a notation for the instantiation on parameter $u$ and internal value $w$ of the corecursive definition of a stream over an arbitrary $a$ generated by a recipe dependent on an arbitrary internal value $d:D(a)$ with first component given by $v(a,d)$ and second component given by $g(f(a,v(a,d)),s(a,d))$ where $g$, typed as $\Gamma, a:A, d:D(a) \vdash g(a,d): Stream_{A,B,f}\, (f(a,d))$, formally represents the recursive call, and where $s(a,d)$ tells how the internal value evolves.
 \end{document}

### 2024-10-12 gendoc.sh
gendoc.sh: add small coqdoc helper

@@ -1,0 +1,3 @@
+#!/usr/bin/env sh
+
+coqdoc -t Bonak --no-lib-name --parse-comments --utf8 -d docs -Q _build/default/theories Bonak _build/default/theories/νType/*.v

### 2025-06-23 paper/paper.tex
paper, vType: changes from final version

@@
 % Double-spacing
-\linespread{2}
+% \linespread{2}
 
@@
   Semi-simplicial and semi-cubical sets are commonly defined as presheaves over respectively, the semi-simplex or semi-cube category.
-Homotopy Type Theory then popularized an alternative definition, where the set of $n$-simplices or $n$-cubes are instead regrouped into the families of the fibers over their faces, leading to a characterization we call \emph{indexed}.
+Homotopy Type Theory then popularized an alternative definition, where the set of $n$-simplices or $n$-cubes are instead regrouped into the families of the fibres over their faces, leading to a characterization we call \emph{indexed}.
 Moreover, it is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds parametricity, respectively in its unary and binary variants.
@@
 \section{Introduction}
-\subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
+\subsection*{Fibred vs indexed presentation of semi-simplicial and semi-cubical sets}
 A family of sets can commonly be represented in two ways: as a family properly speaking, indexed by the elements of a given set $S$, or as a set $T$ together with a map from $T$ to $S$, which specifies for each element of $T$ its dependency on $S$.
 In the former case, we call it an \emph{indexed} presentation.
-In the latter case, the set associated to a given element of $S$ is the fiber of this element, so we call it a \emph{fibered} presentation.
-The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\citep{hottbook} as the fibered/indexed equivalence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family equivalence and unbundled/bundled equivalence.
-The fibered/indexed nomenclature echoes the Grothendieck construction of fibered categories from indexed categories.
+In the latter case, the set associated to a given element of $S$ is the fibre of this element, so we call it a \emph{fibred} presentation.
+The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\citep{hottbook} as the fibred/indexed equivalence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family equivalence and unbundled/bundled equivalence.
+The fibred/indexed nomenclature echoes the Grothendieck construction of fibred categories from indexed categories.
 The most elementary instance of the equivalence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'', and its proof requires univalence~\citep{hottbook}.}.
 \begin{equation*}
-  \mbox{(fibered)}\qquad(\Sigma T: \U. (T \rightarrow S)) ~\simeq~ (S \rightarrow \U)\qquad \mbox{(indexed)}
+  \mbox{(fibred)}\qquad(\Sigma T: \U. (T \rightarrow S)) ~\simeq~ (S \rightarrow \U)\qquad \mbox{(indexed)}
 \end{equation*}
@@
 A \emph{presheaf} on an category is a family of sets indexed by the object of the category with maps indexed by the morphisms.
-As such, it lives on the indexed side of the equivalence, contrasting with the fibered side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
-However, there are situations where a presheaf can also be seen as living on the fibered side of the equivalence.
+As such, it lives on the indexed side of the equivalence, contrasting with the fibred side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
+However, there are situations where a presheaf can also be seen as living on the fibred side of the equivalence.
 This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.
@@
 up to cubical faces identities.
-Here, $X_1$ can be seen as a family over $X_0 \times X_0$, and $X_2$ can be seen as a family over $X_1 \times X_1 \times X_1 \times X_1$, in the fibered presentation, together with coherence conditions between the $X_1$ seen as families over $X_0 \times X_0$.
+Here, $X_1$ can be seen as a family over $X_0 \times X_0$, and $X_2$ can be seen as a family over $X_1 \times X_1 \times X_1 \times X_1$, in the fibred presentation, together with coherence conditions between the $X_1$ seen as families over $X_0 \times X_0$.
 This suggests an alternative indexed presentation of the presheaf as a stratified sequence of families indexed by families of lower rank, taking into account those coherence conditions to prevent duplications.
@@
 \begin{equation*}
-  \begin{array}{llr}
-    X_0 & :              & \U                                                                        \\
-    X_1 & :              & X_0 \times X_0 \rightarrow  \U                                            \\
-    X_2 & : \Pi a b c d. & X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
+  \begin{array}{lll}
+    X_0 & :               \U                                                                        \\
+    X_1 & :               X_0 \times X_0 \rightarrow  \U                                            \\
+    X_2 & : \Pi a b c d.\,  X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
     \ldots
@@
 The second, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it implicitly claimed to construct semi-simplicial types, but the construction was done in a type theory with Uniqueness of Identity Proofs.
-Consequentially, what was really obtained was an indexed presentation of semi-simplicial sets.
+Consequently, what was really obtained was an indexed presentation of semi-simplicial sets.
 The confusion was however, common at the time.} formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
 Another by \cite{part15} formalized in an emulation of logic-enriched homotopy type theory in the Plastic proof assistant, and yet another by \cite{altenkirch16} formalized in an emulation of a two-level type theory in the Agda proof assistant\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, rely, like in Voevodsky, on the presentation of the semi-simplicial category from increasing injective maps between finite ordinals.
-The latter constructions are particularly concise, taking advantage of a definition of increasing injective maps between finite ordinals as type-theoretic functions to inherit the associativity of composition directly from it holding in type theory.
+The latter constructions, besides being stated as providing semi-simplicial types (thanks to an extension of the type theory), are particularly concise, taking advantage of a definition of increasing injective maps between finite ordinals as type-theoretic functions to inherit the associativity of composition directly from it holding in type theory.
 This contrasts with the combinatorial construction in \cite{herbelin15} where equations over face maps have to be proved by induction.
@@
 \subsection*{Reynolds parametricity and its unary and binary variants}
-In the context of functional programming, Reynolds parametricity~(\citeyear{reynolds83}) interprets types as relations characterizing the observational behavior of programs of this type.
+In the context of functional programming, Reynolds parametricity~(\citeyear{reynolds83}) interprets types as relations characterizing the observational behaviour of programs of this type.
 More generally, families over a product of sets, or \emph{correspondences}, can be used in place of relations.
-Parametricity can then be iterated, and relying on the fibered presentation of correspondences as spans, it has been noted that iterated Reynolds parametricity has the structure of a cubical set~\citep{altenkirch15,moulin16,johann17,moeneclaey21,moeneclaey22phd}.
+Parametricity can then be iterated, and relying on the fibred presentation of correspondences as spans, it has been noted that iterated Reynolds parametricity has the structure of a cubical set~\citep{altenkirch15,moulin16,johann17,moeneclaey21,moeneclaey22phd}.
 We obtain a \emph{unary} variant of Reynolds \emph{binary} parametricity by using predicates or families instead of relations or correspondences, and this is a form of realizability~\citep{bernardy12,lasson12,moulin16}.
@@
 \subsection*{Augmented semi-simplicial sets}
-Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``color''.
-Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over the singleton set of a fixed color.
-Let us associate dimension $-1$ to colors; then, points are dimension $0$, lines are dimension $1$, and so on.
-There is hence a shift by one when compared to semi-simplicial sets.
+Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``colour''.
+Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over the singleton set of a fixed colour.
+Let us associate dimension $-1$ to colours; then, points are dimension $0$, lines are dimension $1$, and so on.
 
@@
 
-The standard augmented $(-1)$-semi-simplex is a singleton made of one color (in this case, black).
+The standard augmented $(-1)$-semi-simplex is a singleton made of one colour (in this case, black).
 Standard augmented $n$-semi-simplices for $n \geq 0$ have a geometric interpretation, and we illustrate them for dimensions $0$, $1$, and $2$.
@@
 \begin{example}[$\DeltaPlus^0$]
-  The standard augmented $0$-semi-simplex can be pictured as a point, colored black, corresponding to the unique morphism in $\Hom(0, 1)$.
+  The standard augmented $0$-semi-simplex can be pictured as a point, coloured black, corresponding to the unique morphism in $\Hom(0, 1)$.
 This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$.
@@
 Logical propositions being types themselves, we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification.
-We also assume that our type theory includes a coinductively-defined notion of dependent streams described in \ref{app:depstream}.
+We also assume that our type theory includes a coinductively-defined notion of dependent streams described in Appendix \ref{app:depstream}.
 
@@
 \begin{equation*}
-  \begin{array}{llr}
-    X_0 & :              & \U                                                                        \\
-    X_1 & :              & X_0 \times X_0 \rightarrow \U                                             \\
-    X_2 & : \Pi a b c d. & X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
+  \begin{array}{lll}
+    X_0 & :               \U                                                                        \\
+    X_1 & :               X_0 \times X_0 \rightarrow \U                                             \\
+    X_2 & : \Pi a b c d.\, X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
     \ldots
@@
 Also, for $A$ interpreted by $A_\kstar$ and $B(a)$, for $a:A$, interpreted by $B_\kstar((a_L,a_R),a_\kstar)$ with $a_\kstar:A_\kstar(a_L,a_R)$, a dependent function type $\Pi a: A.\, B(a)$ is interpreted as the graph $(\Pi a: A.\, B(a))_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B(a)$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
-\begin{align*}
-  (\Pi a: A.\, B(a))_\kstar(f_L,f_R) \; \defeq \; \Pi (a_L,a_R): (A \times A).\, \Pi a_\kstar: (A_\kstar(a_L,a_R)\, B_\kstar((a_L,a_R),a_\kstar)(f_L(a_L),f_R(a_R)))
-\end{align*}
+\begin{equation*}
+  \begin{array}{l}
+  (\Pi a: A.\, B(a))_\kstar(f_L,f_R) \; \defeq \\
+  \multicolumn{1}{r}{\qquad\Pi (a_L,a_R): (A \times A).\, \Pi a_\kstar: (A_\kstar(a_L,a_R)\, B_\kstar((a_L,a_R),a_\kstar)(f_L(a_L),f_R(a_R)))}
+  \end{array}
+\end{equation*}
 
@@
 
-By equipping the universe construction with a structure of equivalences, as suggested along the lines of \cite{altenkirch15}, we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models.
+By equipping the universe construction with a structure of equivalences, as suggested along the lines of \cite{altenkirch15}, we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibred approach inherent to usual presheaf models.
 In particular, we conjecture being able to justify univalence holding definitionally.
@@
 
-Although prior approaches to constructing the indexed presentation of a presheaf over a direct category rely on it being evident by inspection that the fibered and indexed presentations are equivalent, no formal proof has been given, and this is a direction for future work.
+Although prior approaches to constructing the indexed presentation of a presheaf over a direct category rely on it being evident by inspection that the fibred and indexed presentations are equivalent, no formal proof has been given, and this is a direction for future work.
 In our construction, we can check by computation of the first levels that it indeed computes the expected sets.

### 2025-06-23 paper/paper.tex
paper: NFC formatting fix
paper: some fixes

@@
-\documentclass{msc}
-
-\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, lmodern, mathpazo, anyfontsize, xargs, environ, multirow, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
+\documentclass{art.cls/art}
+
+\usepackage{environ, multirow, tabularx, caption, booktabs, makecell, colortbl, minted, art.cls/joinargs}
+\setminted[]{fontfamily=lmtt}
 \usepackage[prefix=bonak]{art.cls/xkeymask}
@@
 % Universe, referred to as U
-\newcommandx{\U}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
+\renewcommandx{\U}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
 \newcommandx{\HGpd}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HGpd}}_{#1}}}
@@
 % Caption setup
-\DeclareCaptionFormat{plain}{#1#3}
+\DeclareCaptionFormat{plain}{#1: #3}
 \captionsetup{font=footnotesize,labelfont=bf}
@@
 \NewEnviron{eqntable}[1]{
-  \fontsize{7.2}{9}\selectfont
+  \small
   \begin{tabularx}{0.94\linewidth}{
@@
 
-% Double-spacing
-% \linespread{2}
+% Set the entire document to gray65, and pick certain colors
+\color{gray65}
 
@@
 \title{A parametricity-based formalization of semi-simplicial and semi-cubical sets}
-\begin{authgrp}
-  \author{Hugo Herbelin}
-  \affiliation{Université Paris Cité, Inria, CNRS, IRIF, Paris
-    \email{Hugo.Herbelin@inria.fr}}
-  \author{Ramkumar Ramachandra}
-  \affiliation{Université Paris Cité (2020-2022), Unaffiliated
-    \email{r@artagnon.com}}
-\end{authgrp}
+\date{}
+\author{
+  \textcolor{gray80}{Hugo Herbelin} \\
+  \itshape \textcolor{gray80}{Université Paris-Cité, Inria, CNRS, IRIF, Paris} \\
+  \ttfamily \textcolor{gray80}{Hugo.Herbelin@inria.fr}
+  \and
+  \textcolor{gray80}{Ramkumar Ramachandra} \\
+  \itshape \textcolor{gray80}{Université Paris-Cité (2020-2022), Unaffiliated} \\
+  \ttfamily \textcolor{gray80}{r@artagnon.com}
+}
+\maketitle
 \begin{abstract}
@@
 \end{abstract}
-\footnotetext{Competing interests: The authors declare none}
-\maketitle
-\vspace{-2em} % Remove space after abstract
 
@@
 In the latter case, the set associated to a given element of $S$ is the fibre of this element, so we call it a \emph{fibred} presentation.
-The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\citep{hottbook} as the fibred/indexed equivalence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family equivalence and unbundled/bundled equivalence.
+The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\cite{hottbook} as the fibred/indexed equivalence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family equivalence and unbundled/bundled equivalence.
 The fibred/indexed nomenclature echoes the Grothendieck construction of fibred categories from indexed categories.
-The most elementary instance of the equivalence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'', and its proof requires univalence~\citep{hottbook}.}.
+The most elementary instance of the equivalence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'', and its proof requires univalence~\cite{hottbook}.}.
 \begin{equation*}
@@
 A \emph{presheaf} on an category is a family of sets indexed by the object of the category with maps indexed by the morphisms.
-As such, it lives on the indexed side of the equivalence, contrasting with the fibred side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
+As such, it lives on the indexed side of the equivalence, contrasting with the fibred side, where we have \emph{discrete Grothendieck fibrations}~\cite{LoregianRiehl20}.
 However, there are situations where a presheaf can also be seen as living on the fibred side of the equivalence.
 This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.
-Let us consider, for instance, the case of a semi-cubical set~\citep{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
+Let us consider, for instance, the case of a semi-cubical set~\cite{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
 Formulated in type theory, the corresponding presheaf definition of a semi-cubical set prescribes a family of sets and face maps between them as follows.
@@
 \subsection*{Reynolds parametricity and its unary and binary variants}
-In the context of functional programming, Reynolds parametricity~(\citeyear{reynolds83}) interprets types as relations characterizing the observational behaviour of programs of this type.
+In the context of functional programming, Reynolds parametricity~\cite{reynolds83} interprets types as relations characterizing the observational behaviour of programs of this type.
 More generally, families over a product of sets, or \emph{correspondences}, can be used in place of relations.
-Parametricity can then be iterated, and relying on the fibred presentation of correspondences as spans, it has been noted that iterated Reynolds parametricity has the structure of a cubical set~\citep{altenkirch15,moulin16,johann17,moeneclaey21,moeneclaey22phd}.
-We obtain a \emph{unary} variant of Reynolds \emph{binary} parametricity by using predicates or families instead of relations or correspondences, and this is a form of realizability~\citep{bernardy12,lasson12,moulin16}.
-Cubical set models which differ only by the arity one~\citep{bernardy15} or two~\citep{bezem13} were introduced, and this led to a general notion of affine $\nu$-ary cubes in \cite{nuytsdevriese24}.
+Parametricity can then be iterated, and relying on the fibred presentation of correspondences as spans, it has been noted that iterated Reynolds parametricity has the structure of a cubical set~\cite{altenkirch15,moulin16,johann17,moeneclaey21,moeneclaey22phd}.
+We obtain a \emph{unary} variant of Reynolds \emph{binary} parametricity by using predicates or families instead of relations or correspondences, and this is a form of realizability~\cite{bernardy12,lasson12,moulin16}.
+Cubical set models which differ only by the arity one~\cite{bernardy15} or two~\cite{bezem13} were introduced, and this led to a general notion of affine $\nu$-ary cubes in \cite{nuytsdevriese24}.
 In parallel, it has been noted that iterated unary parametricity has the structure of an augmented simplicial set\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
@@
 
-Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\citep{bernardy15,nuyts17,cavallo19} and cubical type theory~\citep{bezem13,cohen16,angiuli21}, which are closer to the syntax of type theory, and are likely to better reflect the definitional properties of type theory than presheaf-based cubical sets would.
-For example, consider the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\citep{curien14}.
+Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\cite{bernardy15,nuyts17,cavallo19} and cubical type theory~\cite{bezem13,cohen16,angiuli21}, which are closer to the syntax of type theory, and are likely to better reflect the definitional properties of type theory than presheaf-based cubical sets would.
+For example, consider the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\cite{curien14}.
 
@@
 
-While ordinary semi-simplicial sets are presheaves over the semi-simplex category, augmented semi-simplicial sets are presheaves over \DeltaPlus.
+Ordinary semi-simplicial sets are presheaves over the semi-simplex category.
+Augmented semi-simplicial sets are presheaves over \DeltaPlus.
 There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that can be extended to semi-cubical sets in a straightforward manner.
@@
 \begin{center}
-  \begin{tabularx}{0.7\linewidth}{X|X|X}
+  \begin{tabularx}{\linewidth}{X|X|X}
     \toprule
@@
 As in the augmented semi-simplicial and semi-cubical cases, the standard $(n + 1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
-We clarify in the next sections, how this process of construction is similar to the parametricity translation developed for functional programming~\citep{reynolds83} and more generally for type theory~\citep{bernardy10,bernardy11,atkey14,bernardy15}.
+We clarify in the next sections, how this process of construction is similar to the parametricity translation developed for functional programming~\cite{reynolds83} and more generally for type theory~\cite{bernardy10,bernardy11,atkey14,bernardy15}.
 
 \section{Type theory\label{sec:tt}}
-Martin-Löf's Type theory~(\citeyear{martinlof75,martinlof84}) is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
+Martin-Löf's Type theory~(\cite{martinlof75,martinlof84}) is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
 It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda, Coq and Lean.
@@
 Type theory is a flexible formalism supporting different models.
-Some models come from homotopy theory, and are based on simplicial sets or related structures~\citep{HofmannStreicher94,kapulkin21,BezemCoquandHuber13,cchm}: in these models, equality is interpreted as paths, and they support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\citep{hottbook}.
+Some models come from homotopy theory, and are based on simplicial sets or related structures~\cite{HofmannStreicher94,kapulkin21,BezemCoquandHuber13,cchm}: in these models, equality is interpreted as paths, and they support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\cite{hottbook}.
 
@@
 The rule also implies functional extensionality.
-Extensional type theory is logically equivalent to intensional type theory extended with UIP and functional extensionality~\citep{HofmannPhd}.
+Extensional type theory is logically equivalent to intensional type theory extended with UIP and functional extensionality~\cite{HofmannPhd}.
 
@@
 
-Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets: using the notations of Section~\ref{sec:tt}, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
+Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets.
+
+Using the notations of Section~\ref{sec:tt}, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
 Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
@@
 Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that the construction builds an effective sequence of types not mentioning coherences anymore.
-\\
-
+
+\vspace{1em}
 \def\lab{tab:coind}
@@
 
+\vspace{1em}
 \def\lab{tab:core}
@@
 \renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
+\vspace{1em}
 \def\lab{tab:frames}
@@
 
+\vspace{1em}
 \def\lab{tab:faces}
@@
 
+\vspace{1em}
 \def\lab{tab:coh}
@@
   \begin{array}{llc}
-    \layer[n][p](D)(d) & \defeq & \painting[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) \\
-                       &        & \times                                           \\
-                       &        & \painting[n-1][p](D.\hd)(\restrf[n][p][R][p](d))
+    \layer[n][p](D)(d) & \defeq & \painting[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) \times \painting[n-1][p](D.\hd)(\restrf[n][p][R][p](d))
   \end{array}
@@
 The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit in table~\ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
-\\
+\vspace{1em}
 
@@
 \def\lab{fulltab:faces}
+\vspace{1em}
 \renewcommand{\thetable}{4'}
 \input{tab-faces.tex}
+\vspace{1em}
 \def\lab{fulltab:coh}
@@
 
-Here, $\SProp$ is a definitionally proof-irrelevant impredicative universe morally\footnote{In Coq, it is however a stand-alone universe unrelated to the universe hierarchy.} living at the bottom of the universe hierarchy~\citep{gilbert19}.
+Here, $\SProp$ is a definitionally proof-irrelevant impredicative universe morally\footnote{In Coq, it is however a stand-alone universe unrelated to the universe hierarchy.} living at the bottom of the universe hierarchy~\cite{gilbert19}.
 By placing the definition in \SProp, we have definitional equality of inequality proofs.
@@
 \section{Future work}
-The construction could be extended with degeneracies as well as with permutations~\citep{grandis03}.
+The construction could be extended with degeneracies as well as with permutations~\cite{grandis03}.
 Dependent $\nu$-sets could also be defined, opening the way to construct $\Pi$-types and $\Sigma$-types of $\nu$-sets.
-A $\nu$-set of $\nu$-sets representing a universe could also be defined as sketched in a talk at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf}).
-More generally, we believe these lines of work would eventually provide alternative models to parametric type theories~\citep{nuyts17,cavallo19} where equality of types, now a family rather than the total space of a fibration, is not only definitionally isomorphic to bridges~\citep{bernardy15}, but definitionally the same as bridges.
-
-By equipping the universe construction with a structure of equivalences, as suggested along the lines of \cite{altenkirch15}, we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\citep{bezem13,cohen16,angiuli21}, saving the detour via the fibred approach inherent to usual presheaf models.
+A $\nu$-set of $\nu$-sets representing a universe could also be defined as sketched in a talk at the HoTT-UF workshop for the bridge case~(\cite{herbelin-hott-uf}).
+More generally, we believe these lines of work would eventually provide alternative models to parametric type theories~\cite{nuyts17,cavallo19} where equality of types, now a family rather than the total space of a fibration, is not only definitionally isomorphic to bridges~\cite{bernardy15}, but definitionally the same as bridges.
+
+By equipping the universe construction with a structure of equivalences, as suggested along the lines of \cite{altenkirch15}, we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\cite{bezem13,cohen16,angiuli21}, saving the detour via the fibred approach inherent to usual presheaf models.
 In particular, we conjecture being able to justify univalence holding definitionally.
@@
 
+\bibliographystyle{alpha}
+\bibliography{paper}
+
 \newpage
-\bibliographystyle{msclike}
-\bibliography{paper}
-
 \appendix
-\section{Definition of dependent stream\label{app:depstream}}
+\fancyhead[L]{\footnotesize\textcolor{gray80}{{\MakeUppercase{Appendix}}}}
+\section*{Appendix: Definition of dependent stream\label{app:depstream}}
 

### 2025-07-20 paper/restruct-new.tex
New

\documentclass[a4paper,english,cleveref,autoref,thm-restate]{article}

\usepackage[utf8x]{inputenc}
\usepackage{t1enc}

\usepackage{hyperref}
%\usepackage{proof}
\usepackage{fullpage}
\usepackage{amssymb}
\usepackage{stmaryrd}
%\usepackage{txfonts}
\usepackage{url}

\usepackage{xcolor}
%\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{yfonts}
\usepackage{tikz}
\usetikzlibrary{cd, arrows}

\newcommand{\Overrightarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#2}$}}{}$}}
\newcommand{\Overleftarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Leftarrowfill@{\mbox{${#2}$}}{}$}}
%\newcommand{\Overrightarrow}[1]{\raisebox{1.4ex}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#1}$}}{}$}}
\makeatother

\newcommand{\rocq}[1]{(\mbox{\texttt{#1}})}
\newcommand{\highlight}[1]{\emph{#1}}

\newcommand{\imp}{\rightarrow}
\newcommand{\Type}{\mathsf{Type}}
\newcommand{\Set}{\mathsf{Set}}
\newcommand{\Prop}{\mathsf{Prop}}
\newcommand{\refl}[1]{\mathsf{refl}\,{#1}}
\newcommand{\mkmlidtype}[3]{{#1} =^{\mathrm{id}}_{#2} {#3}}
\newcommand{\mkmleqdep}[3]{{#1} =^{\mathrm{dep}}_{#2} {#3}}
\newcommand{\hrefl}[1]{\mathsf{refl^{\mathrm{dep}}}\,{#1}}
\newcommand{\mluniv}{\mathsf{U}}
\newcommand{\Jdep}[2]{\mathsf{J}\;{#1}\;{#2}}
\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
\newcommand{\unitpoint}{\ensuremath{\ast}}

\newcommand{\nth}[1]{{#1}^{\mbox{\scriptsize th}}}
\newcommand{\defeq}{\triangleq}

\newcommand{\U}{\ensuremath{\mathsf{{HSet}}}}

\begin{document}

\section{The recursive structure of iterated parametricity}

Iterated parametricity (in indexed form) produces a family of type
families of the following form:
\begin{equation*}
  \begin{array}{llr}
    X_0 & :              & \U                                                                        \\
    X_1 & :              & X_0 \times X_0 \rightarrow  \U                                            \\
    X_2 & : \Pi a b c d. & X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
    \ldots
  \end{array}
\end{equation*}

Such family can be recursively described by the equations given on Table \ref{}.

The well-foundedness of the construction can be justified by the observation that:
\begin{enumerate}
\item Defining frame$^{n,p}$ for $p\leq n$ requires the definition of
  painting$^{n-1,k}$, thus also frame$^{n-1,k}$ by typing dependency,
  as well as restrframe$^{n,k}$, for $k < p$, where restrframe$^{n,k}$
  in turn depends in frame$^{n,k}$ for its typing. Schematically,
  using dotted arrows for dependency in the type and plain arrows for
  dependency in the definition, this gives the following dependencies:
\begin{center}
\begin{tikzcd}
frame^{n,p} \arrow[d] \arrow[ddr]\\
painting^{n-1,k<p} \arrow[d, dotted] \\
frame^{n-1,k<p} & restrframe^{n,k<p} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{center}

In particular, the mutual dependency of frame$^{n,p}$ in the type of
restrframe$^{n,p}$ and of restrframe$^{n,p}$ in the definition of
requires to mutually defining the type of restrframe$^{n,p}$
and frame$^{n,p}$ as a function from all restrframe$^{n,k}$ for
$k < p$.

\item The same dependencies for frame$^{n-1,p}$ for $p \leq n-1$ gives:
\begin{center}
\begin{tikzcd}
frame^{n-1,p} \arrow[d] \arrow[ddr, shift right=1mm]\\
painting^{n-2,k<p} \arrow[d, dotted] \\
frame^{n-2,k<p} & restrframe^{n-1,k<p} \arrow[l, dotted] \arrow[uul, dotted, shift right=1mm]\\
\end{tikzcd}
\end{center}

Similarly, restrframe$^{n-1,p}$ and frame$^{n-1,p}$ as a function from
all restrframe$^{n-1,k}$ for $k < p$ have to be mutually defined.

\item Defining painting$^{n-1,p}$ for $p\leq n-1$, in addition to the
  type dependency in frame$^{n-1,p}$, requires the definition of
  painting$^{n-2,k}$, thus also frame$^{n-2,k}$ by typing dependency,
  as well as restrframe$^{n,k}$, this time for $k \geq p$, and the
  assumption of an inhabitant $X_{n-2}$ of $\nu$Set$^{=n-2}$
\begin{center}
\begin{tikzcd}
   & & painting^{n-1,p} \arrow[ddll] \arrow[dddl] \arrow[d, dotted]\\
   & & frame^{n-1,p} \\
painting^{n-2,k\geq p} \arrow[d, dotted] \\
frame^{n-2,k\geq p} & restrframe^{n-1,k\geq p},X_{n-2} \arrow[l, dotted]\\
\end{tikzcd}
\end{center}

\item Defining restrframe$^{n,p}$ for $p\leq n-1$, in addition to the
  type dependency in frame$^{n+1,p}$ and frame$^{n,p}$, requires
  defining restrpainting$^{n-1,k}$, thus also restrframe$^{n-1,k}$,
  frame$^{n-2,k}$ by typing dependency, as well as cohframe$^{n,k}$,
  for $k < p$, where cohframes$^{n,k}$ in turn depends in
  restrframe$^{n,k}$ for its typing:
\begin{center}
\begin{tikzcd}
frame^{n,p} \\
 \\
frame^{n-1,p} & restrframe^{n,p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted]\\
  & restrpainting^{n-1,k<p} \arrow[d, dotted] \\
frame^{n-2,p} & restrframe^{n-1,k<p} \arrow[l, dotted] \arrow[uul, dotted] & cohframe^{n,k<p} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{center}

In particular, the mutual dependency of restrframe$^{n,p}$ in the type
of cohframe$^{n,p}$ and of cohframe$^{n,p}$ in the definition of
restrframe$^{n,p}$ requires to mutually defining the type of
cohframe$^{n,p}$ and restrframe$^{n,p}$ as a function from all
cohframe$^{n,k}$ for $k\leq p$.

\item Defining cohframe$^{n+1,p}$ for $p\leq n-1$, in addition to the
  type dependency in restrframe$^{n+1,p}$, restrframe$^{n,p}$,
  frame$^{n+1,p}$, frame$^{n,p}$ and frame$^{n-1,p}$, requires defining
  cohpainting$^{n,k}$, thus also cohframe$^{n,k}$ by typing
  dependency, for $k < p$. By reasoning in sets, no higher-dimensional
  coherence frame is needed:
\begin{center}
\begin{tikzcd}
frame^{n+1,p} \\
\\
frame^{n,p} & restrframe^{n+1,p} \arrow[l, dotted] \arrow[uul, dotted] \\
\\
frame^{n-1,p} & restrframe^{n,p} \arrow[l, dotted] \arrow[uul, dotted] & cohframe^{n+1,p} \arrow[d] \arrow[uul, dotted] \arrow[l, dotted]\\
& & cohpainting^{n,k<p} \arrow[d, dotted] \\
frame^{n-2,p} & restrframe^{n-1,p} \arrow[l, dotted] \arrow[uul, dotted] & cohframe^{n,k<p} \arrow[uul, dotted] \arrow[l, dotted]\\
\end{tikzcd}
\end{center}
\item Defining restrpainting$^{n,p}$ for $p\leq n-1$, in addition to
  the type dependency in painting$^{n,p}$, painting$^{n-1,p}$, restrframe$^{n,p}$, frame$^{n,p}$ and
  frame$^{n-1,p}$, requires the definition of restrpainting$^{n-1,k}$,
  thus also restrframe$^{n-1,k}$ and frame$^{n-2,p}$ by typing
  dependency, as well as cohframe$^{n,k}$ for $p \geq k$ and the
  assumption of an inhabitant $X_{n-1}$ of nuSet$^{=n-1}$:
\begin{center}
\begin{tikzcd}
   & & painting^{n,p} \arrow[d, dotted] \\
   & & frame^{n,p} \\
   & & painting^{n-1,p} \arrow[d, dotted] & restrpainting^{n,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \arrow[uul, dotted] \arrow[ul, dotted] \arrow[l, dotted] \\
   & & frame^{n-1,p} & restrframe^{n,p} \arrow[uul, dotted] \arrow[l, dotted]\\
restrpainting^{n-1,k\geq p} \arrow[d, dotted] \\
restrframe^{n-1,k\geq p} & cohframe^{n,k\geq p},X_{n-1} \arrow[l, dotted]\\
\end{tikzcd}
\end{center}

\item Defining cohpainting$^{n+1,p}$ for $p\leq n-1$, in addition to
  the type dependency in restrpainting$^{n+1,p}$,
  restrpainting$^{n,p}$, painting$^{n+1,p}$, painting$^{n,p}$,
  painting$^{n-1,p}$, restrframe$^{n+1,p}$, restrframe$^{n,p}$,
  frame$^{n+1,p}$, frame$^{n,p}$ and frame$^{n-1,p}$ requires the
  definition of cohpainting$^{n,k}$, thus also cohframe$^{n,k}$ by
  typing dependency, for also $p \geq k$. By reasoning in sets, no
  higher-dimensional coherence frame is needed:
\begin{center}
\begin{tikzcd}
   & & painting^{n+1,p} \arrow[d, dotted] \\
   & & frame^{n+1,p} \\
   & & painting^{n,p} \arrow[d, dotted] & restrpainting^{n+1,p} \arrow[d, dotted] \arrow[uul, dotted] \arrow[ul, dotted] \arrow[l, dotted] \\
   & & frame^{n,p} & restrframe^{n+1,p} \arrow[uul, dotted] \arrow[l, dotted] \\
   & & painting^{n-1,p} \arrow[d, dotted] & restrpainting^{n,p} \arrow[d, dotted] \arrow[uul, dotted] \arrow[ul, dotted] \arrow[l, dotted] & cohpainting^{n+1,p} \arrow[ddllll] \arrow[l, dotted] \arrow[uul, dotted] \arrow[d, dotted]\\
   & & frame^{n-1,p} & restrframe^{n,p} \arrow[l, dotted] & cohframe^{n+1,p} \arrow[l, dotted] \arrow[uul, dotted]\\
cohpainting^{n,k\geq p} \arrow[d, dotted] \\
cohframe^{n,k\geq p} \\
\end{tikzcd}
\end{center}
\end{enumerate}

Looking at the dependencies in the reverse order, it is thus enough:
\begin{enumerate}
\item To assume frame$^{n-2,k}$ and painting$^{n-2,k}$ for all $k\leq
  p$ in order to mutually define, for all $p\leq n$, the type of
  restrframe$^{n-1,p}$ and frame$^{n-1,p}$ as a function from all
  restrframe$^{n-1,k}$ for $k\leq p$. Using red for assumptions, this
  can be pictured as:
\begin{center}
\begin{tikzcd}
frame^{n-1,p}(\textcolor{red}{restrframe^{n-1,k<p}}) \arrow[d] \\
\textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k<p}} \\
\end{tikzcd}
\end{center}
\item To further assume restrframe$^{n-1,k}$ for all $k\leq p$ to get
  frame$^{n-2,p}$ for all $p<n$:
\begin{center}
\begin{tikzcd}
frame^{n-1,p} \arrow[d] \arrow[ddr]\\
\textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{center}

\item To rely on frame$^{n-2,k}$, painting$^{n-2,k}$ and
  restrframe$^{n-1,k}$ now for all $k > p$, as well as an inhabitant
  of $X_{n-2}$ of nuSet$^{=n-2}$ to define painting$^{n-1,p}$ for all
  $p \leq n$:
\begin{center}
\begin{tikzcd}
& & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
& & & frame^{n-1,p} \arrow[d] \arrow[ddr]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{center}

\item To rely on frame$^{n-1,k}$ and painting$^{n-1,k}$ for all $k <
  p$ to now construct the frame$^{n,p}$ for $p \leq n-1$ as a function
  from all restrframe$^{n,k}$ for $k\leq p$:

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{tikzcd}
& & & frame^{n,p}(\textcolor{red}{restrframe^{n,k<p}}) \arrow[d] \\
& & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
& & & frame^{n-1,p} \arrow[d] \\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}

\item To additionally assume restrpainting$^{n-1,k}$ for $k < p$ to
  mutually define for $p \leq n-1$ the type of cohframe$^{n,p}$ and
  restrframe$^{n,p}$ as a function from all cohframe$^{n,k}$ for
  $k\leq p$, as well as, consequently, frame$^{n,p}$ for all $p\leq n$

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{tikzcd}
& & & frame^{n,p} \arrow[d] \arrow[ddr] \\
& & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
& & & frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p}(\textcolor{red}{cohframe^{n,k<p}}) \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}

\item To additionally assume cohframe$^{n,k}$ for $k \leq p$ to get
  all restrframe$^{n,k}$ for all $k \leq p$:

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{small}
\begin{tikzcd}
& & & frame^{n,p} \arrow[d] \arrow[ddr]\\
& & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
& & & frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] & \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{small}

\item To rely on frame$^{n-2,k\geq p}$, painting$^{n-1,k\geq p}$ and
  restrframe$^{n,k\geq p}$ to build frame$^{n,k\geq p}$ and
  painting$^{n,k\geq p}$ for $p \leq n$:

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{small}
\begin{tikzcd}
& & & frame^{n,p} \arrow[d] \arrow[ddr]\\
painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & & & frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] & \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{small}

Note that this can be done in parallel with the steps building frame$^{n,p}$.

\item To assume restrpainting$^{n-1,k}$ and cohframe$^{n,k}$ for $k >
  p$ to build restrframe$^{n,k\geq p}$:

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{small}
\begin{tikzcd}
& & & frame^{n,p} \arrow[d] \arrow[ddr]\\
painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & & frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] & &
   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
   \textcolor{red}{frame^{n-2,k<p}} &
   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
\end{tikzcd}
\end{small}

\item To rely on painting$^{n-1,k\geq p}$ and restrframe$^{n,p\leq n-1}$ to build painting$^{n,p}$ for $p \leq n$:

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{small}
\begin{tikzcd}
& & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
& & & frame^{n,p} \arrow[d] \arrow[ddr]\\
painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & & frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] & &
   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
   \textcolor{red}{frame^{n-2,k<p}} &
   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
\end{tikzcd}
\end{small}

\item To rely on restrpainting$^{n-1,k}$ and cohframe$^{n,k}$ for $k >
  p$ to also get restrpainting$^{n,p}$ for all $p \leq n$:

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{small}
\begin{tikzcd}
& & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
& & & frame^{n,p} \arrow[d] \arrow[ddr]\\
painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70]  & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
  frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[d, dotted] & &
   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
   \textcolor{red}{frame^{n-2,k<p}} &
   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
\end{tikzcd}
\end{small}

\item To rely on frame$^{n,k}$ and painting$^{n,k}$ for all $k < p$ to
  now construct frame$^{n+1,p}$ for $p \leq n+1$ as a function from
  all restrframe$^{n+1,k}$ for $k \leq p$:

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{scriptsize}
\begin{tikzcd}
& & & frame^{n+1,p}(\textcolor{red}{restrframe^{n+1,k<p}}) \arrow[d]\\
& & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
& & & frame^{n,p} \arrow[d] \arrow[ddr]\\
painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70]  & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
  frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[d, dotted] & &
   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
   \textcolor{red}{frame^{n-2,k<p}} &
   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
\end{tikzcd}
\end{scriptsize}

\item To rely on restrframe$^{n,k}$ and restrpainting$^{n,k}$ for all
  $k < p$ to now construct restrframe$^{n+1,p}$ for $p \leq n$ as a
  function from all cohframe$^{n+1,k}$ for $k \leq p$. This also
  allows to instantiate the dependency of frame$^{n+1,p}$ on
  restrframe$^{n+1,p}$:

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{scriptsize}
\begin{tikzcd}
& & & frame^{n+1,p} \arrow[d] \arrow[ddr] \\
& & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
& & & frame^{n,p} \arrow[d] \arrow[ddr] & restrframe^{n+1,k<p}(\textcolor{red}{cohframe^{n+1,k<p}}) \arrow[d] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
   painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
  frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[d, dotted] & &
   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
   \textcolor{red}{frame^{n-2,k<p}} &
   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
\end{tikzcd}
\end{scriptsize}

\item To additionally assume cohpainting$^{n,k}$ for $k < p$ to get
  cohframe$^{n+1,p}$ for all $p \leq n-1$. This also allows to
  instantiate the dependency of restrframe$^{n+1,p}$ on
  cohframe$^{n+1,p}$:

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{scriptsize}
\begin{tikzcd}
& & & frame^{n+1,p} \arrow[d] \arrow[ddr] \\
& & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
& & & frame^{n,p} \arrow[d] \arrow[ddr] & restrframe^{n+1,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
  painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
 frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   cohframe^{n+1,p} \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[d, dotted] & &
   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted] &
   \textcolor{red}{cohpainting^{n,k<p}} \arrow[l, dotted] \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
   \textcolor{red}{frame^{n-2,k<p}} &
   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
\end{tikzcd}
\end{scriptsize}

\item To finally assume cohpainting$^{n,k}$ for $k \geq p$
to get cohpainting$^{n+1,p}$ for $p \leq n-1$:

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{scriptsize}
\begin{tikzcd}
& & & frame^{n+1,p} \arrow[d] \arrow[ddr] \\
& & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
& & & frame^{n,p} \arrow[d] \arrow[ddr] & restrframe^{n+1,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
 painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] &
   cohpainting^{n+1,p} \arrow[ddlll] \arrow[d, dotted] \arrow[l, dotted] \\
frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
  frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   cohframe^{n+1,p} \arrow[d] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] & \textcolor{red}{cohpainting^{n,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] &
   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted] &
   \textcolor{red}{cohpainting^{n,k<p}} \arrow[l, dotted] \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
   \textcolor{red}{frame^{n-2,k<p}} &
   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
\end{tikzcd}
\end{scriptsize}
\end{enumerate}

Thus, shortly, assuming frame$^{n-2,p}$, painting$^{n-2,p}$,
restrframe$^{n-1,p}$, restrpainting$^{n-1,p}$, cohframe$^{n,p}$ and
cohpainting$^{n,p}$ for all $p \leq n-2$ allows to define
frame$^{n-1,p}$, painting$^{n-1,p}$, restrframe$^{n,p}$,
restrpainting$^{n,p}$, cohframe$^{n+1,p}$ and cohpainting$^{n+1,p}$
for all $p \leq n-1$, so the construction can be recursively
continued.

\end{document}

### 2025-07-20 paper/restruct-new.tex
update

@@
 \begin{enumerate}
-\item To assume frame$^{n-2,k}$ and painting$^{n-2,k}$ for all $k\leq
-  p$ in order to mutually define, for all $p\leq n$, the type of
+\item To assume frame$^{n-2,k}$ and painting$^{n-2,k}$ for all $k< p$
+  in order to mutually define, for all $p\leq n$, the type of
   restrframe$^{n-1,p}$ and frame$^{n-1,p}$ as a function from all
-  restrframe$^{n-1,k}$ for $k\leq p$. Using red for assumptions, this
+  restrframe$^{n-1,k}$ for $k< p$. Using red for assumptions, this
   can be pictured as:
@@
 \end{center}
-\item To further assume restrframe$^{n-1,k}$ for all $k\leq p$ to get
-  frame$^{n-2,p}$ for all $p<n$:
+
+\item To further assume restrframe$^{n-1,k}$ for all $k<p$ to get
+  frame$^{n-1,p}$ for all $p\leq n-1$:
 \begin{center}
@@
 \item To rely on frame$^{n-2,k}$, painting$^{n-2,k}$ and
-  restrframe$^{n-1,k}$ now for all $k > p$, as well as an inhabitant
-  of $X_{n-2}$ of nuSet$^{=n-2}$ to define painting$^{n-1,p}$ for all
-  $p \leq n$:
+  restrframe$^{n-1,k}$, jointly with frame$^{n-1,k}$, and now for all
+  $k \geq p$, as well as an inhabitant $X_{n-2}$ of $\nu$Set$^{=n-2}$
+  to define painting$^{n-1,p}$ for all $p \leq n-1$:
 \begin{center}
@@
 & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
-& & & frame^{n-1,p} \arrow[d] \arrow[ddr]\\
+frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & & & frame^{n-1,p} \arrow[d] \arrow[ddr]\\
 \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
@@
 
-\item To rely on frame$^{n-2,k\geq p}$, painting$^{n-1,k\geq p}$ and
-  restrframe$^{n,k\geq p}$ to build frame$^{n,k\geq p}$ and
-  painting$^{n,k\geq p}$ for $p \leq n$:
+\item To rely on frame$^{n-2,k\geq p}$, painting$^{n-2,k\geq p}$ and
+  restrframe$^{n-1,k\geq p}$ to build frame$^{n-1,k\geq p}$ and
+  painting$^{n-1,k\geq p}$ for $p \leq n$:
 
@@
 \item To rely on restrpainting$^{n-1,k}$ and cohframe$^{n,k}$ for $k >
-  p$ to also get restrpainting$^{n,p}$ for all $p \leq n$:
+  p$ to also get restrpainting$^{n,p}$ for all $p \leq n-1$:
 
@@
 
-\item To finally assume cohpainting$^{n,k}$ for $k \geq p$
-to get cohpainting$^{n+1,p}$ for $p \leq n-1$:
+\item To assume cohpainting$^{n+1,k}$ for $k \geq p$ to build
+  cohframe$^{n+1,k\geq p}$:
+
+$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
+\begin{scriptsize}
+\begin{tikzcd}
+& & & frame^{n+1,p} \arrow[d] \arrow[ddr] \\
+& & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
+& & & frame^{n,p} \arrow[d] \arrow[ddr] & restrframe^{n+1,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
+painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
+  painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
+frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
+ frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
+   cohframe^{n+1,p} \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
+\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[d, dotted] & &
+   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
+   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted] &
+   \textcolor{red}{cohpainting^{n,k<p}} \arrow[l, dotted] \arrow[d, dotted] \\
+\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
+   \textcolor{red}{frame^{n-2,k<p}} &
+   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
+   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
+\end{tikzcd}
+\end{scriptsize}
+
+\item To rely on restrpainting$^{n,k}$ and cohframe$^{n+1,k}$ for $k \geq
+  p$ to also get restrpainting$^{n+1,p}$ for all $p \leq n$:
+
+$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
+\begin{scriptsize}
+\begin{tikzcd}
+& & & frame^{n+1,p} \arrow[d] \arrow[ddr] \\
+& & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
+& & & frame^{n,p} \arrow[d] \arrow[ddr] & restrframe^{n+1,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
+painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
+  painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
+frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
+ frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
+   cohframe^{n+1,p} \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
+\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] &
+   \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] &
+   \textcolor{red}{cohpainting^{n,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] &
+   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
+   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted] &
+   \textcolor{red}{cohpainting^{n,k<p}} \arrow[l, dotted] \arrow[d, dotted] \\
+\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
+   \textcolor{red}{frame^{n-2,k<p}} &
+   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
+   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
+\end{tikzcd}
+\end{scriptsize}
+
+\item To finally rely on cohpainting$^{n,k}$ for $k \geq p$
+to also get cohpainting$^{n+1,p}$ for $p \leq n-1$:
 
@@
    cohframe^{n+1,p} \arrow[d] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
-\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] & \textcolor{red}{cohpainting^{n,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] &
+\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] &
+   \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] &
+   \textcolor{red}{cohpainting^{n,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] &
    \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
@@
    \textcolor{red}{cohpainting^{n,k<p}} \arrow[l, dotted] \arrow[d, dotted] \\
-\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
+\textcolor{red}{frame^{n-2,k\geq p}} &
+   \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] &
+   \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
    \textcolor{red}{frame^{n-2,k<p}} &

### 2025-07-20 paper/paper.tex
paper: add the \SSSet macro
paper: make tables float, stripping ugly ws

@@
 \newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
+\newcommand{\SSSet}{\ensuremath{\Set_{\DeltaPlus}}}
 \newcommand{\Cube}{\ensuremath{\boldsymbol{{\square}}}}
-\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
+\newcommand{\CSet}{\ensuremath{\Set_{\Cube}}}
 
@@
 \NewEnviron{eqntable}[1]{
+  \begin{table}[h]
   \small
@@
     \end{tabularx}
-  \captionof{table}{#1}
+    \caption{#1}
+  \end{table}
 }
@@
 
-\begin{definition}[$\Set_{\DeltaPlus}$]
+\begin{definition}[$\SSSet$]
   We define the category of augmented semi-simplicial sets as the functor category:
   \begin{equation*}
-    \Set_{\DeltaPlus} := \Set^{\DeltaPlus^{\mathsf{op}}}
+    \SSSet := \Set^{\DeltaPlus^{\mathsf{op}}}
   \end{equation*}
@@
   \begin{align*}
-    \DeltaPlus^{n-1}    & : \Set_{\DeltaPlus}        \\
+    \DeltaPlus^{n-1}    & : \SSSet                   \\
     \DeltaPlus^{n-1}(p) & := \Hom(p, n)              \\
@@
 
-\vspace{1em}
 \def\lab{tab:coind}
@@
 
-\vspace{1em}
 \def\lab{tab:core}
@@
 \renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
-\vspace{1em}
 \def\lab{tab:frames}
@@
 
-\vspace{1em}
 \def\lab{tab:faces}
@@
 
-\vspace{1em}
 \def\lab{tab:coh}
@@
 The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit in table~\ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
-\vspace{1em}
 
@@
 \def\lab{fulltab:faces}
-\vspace{1em}
 \renewcommand{\thetable}{4'}
 \input{tab-faces.tex}
-\vspace{1em}
 \def\lab{fulltab:coh}
@@
 \renewcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
-\vspace{1em}
 The proof of $\cohf$ itself requires making explicit several rewrites which were invisible in extensional type theory.

### 2025-07-20 paper/paper.tex
No more numbering of Appendix

@@
 Logical propositions being types themselves, we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification.
-We also assume that our type theory includes a coinductively-defined notion of dependent streams described in Appendix \ref{app:depstream}.
+We also assume that our type theory includes a coinductively-defined notion of dependent streams described in the Appendix.
 
@@
 \fancyhead[L]{\footnotesize\textcolor{gray80}{{\MakeUppercase{Appendix}}}}
-\section*{Appendix: Definition of dependent stream\label{app:depstream}}
+\section*{Appendix: Definition of dependent stream}
 

### 2025-07-20 paper/paper.tex
Rewording to preserve a paragraph

@@
 Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets.
-
-Using the notations of Section~\ref{sec:tt}, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
+Using the notations of Section~\ref{sec:tt} and of the Appendix, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the dependent stream given by $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
 Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.

### 2025-08-02 paper/restruct-new.tex
Update: - attempt to define in full details the construction of frame(n)   from frame(n-1) and painting(n-1) - attempt to picture in full details the construction of painting with   dependency in extradeps - attempt to picture in full details the construction of restrframe   but avoiding dependency in extradeps

@@
 
+\newcommand{\myframe}{\mathit{frame}}
+\newcommand{\myframetype}{\mathit{frametype}}
+\newcommand{\painting}{\mathit{painting}}
+\newcommand{\paintingtype}{\mathit{paintingtype}}
+\newcommand{\restrframe}{\mathit{restrframe}}
+\newcommand{\restrframetype}{\mathit{restrframetype}}
+\newcommand{\restrpainting}{\mathit{restrpainting}}
+\newcommand{\cohframe}{\mathit{cohframe}}
+\newcommand{\cohpainting}{\mathit{cohpainting}}
+
+\newcommand{\udensdash}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {$#1$};
+        \draw[densely dashed] (todotted.south west) -- (todotted.south east);
+    }%
+}%
+
 \begin{document}
@@
 \begin{enumerate}
-\item Defining frame$^{n,p}$ for $p\leq n$ requires the definition of
-  painting$^{n-1,k}$, thus also frame$^{n-1,k}$ by typing dependency,
-  as well as restrframe$^{n,k}$, for $k < p$, where restrframe$^{n,k}$
-  in turn depends in frame$^{n,k}$ for its typing. Schematically,
-  using dotted arrows for dependency in the type and plain arrows for
-  dependency in the definition, this gives the following dependencies:
+\item Defining $\myframe^{n,p}$ for $p \leq n$ requires the definition
+  of $\painting^{n-1,p-1}$, thus also $\myframe^{n-1,p-1}$ by typing
+  dependency, as well as $\restrframe^{n,p-1}$, where
+  $\restrframe^{n,p-1}$ in turn depends in $\myframe^{n,p-1}$ for its
+  typing.
+
+  Moreover, $\myframe^{n,p}$ depends on $\myframe^{n,p-1}$, so these
+  dependencies are between the blocks of $\myframe^{n,k}$ for all
+  $k\leq p$, as well as $\myframe^{n-1,k}$, $\painting^{n-1,k}$ and
+  $\restrframe^{n,k}$ for all $k\leq p-1$, which we respectively
+  abbreviate as $\myframe^{n,[0,...,p]}$,
+  $\myframe^{n-1,[0,...,p-1]}$, $\painting^{n-1,[0,...,p-1]}$ and
+  $\restrframe^{n,[0,...,p-1]}$.
+
+  Also, $\restrframe^{n,p-1}$ depends on $n$.
+
+  Schematically, using dotted arrows for dependencies in
+  the type and plain arrows for dependencies in the definition, this
+  gives the following dependencies for $p\leq n$ fixed:
 \begin{center}
 \begin{tikzcd}
-frame^{n,p} \arrow[d] \arrow[ddr]\\
-painting^{n-1,k<p} \arrow[d, dotted] \\
-frame^{n-1,k<p} & restrframe^{n,k<p} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
+\myframe^{n,[0,...,p]} \arrow[d] \arrow[ddr]\\
+\painting^{n-1,[0,...,p-1]} \arrow[d, dotted] \\
+\myframe^{n-1,[0,...,p-1]} &
+   \restrframe^{n,[0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[0,...,p-1]$}"', near start, shift right=2mm, hook']\\
 \end{tikzcd}
@@
 
-In particular, the mutual dependency of frame$^{n,p}$ in the type of
-restrframe$^{n,p}$ and of restrframe$^{n,p}$ in the definition of
-requires to mutually defining the type of restrframe$^{n,p}$
-and frame$^{n,p}$ as a function from all restrframe$^{n,k}$ for
-$k < p$.
+In particular, the mutual dependency on one side of
+$\myframe^{n,[0,...,p-1]}$ within the type of
+$\restrframe^{n,[0,...,p-1]}$ and on the other side of
+$\restrframe^{n,[0,...,p-1]}$ within the definition of
+$\myframe^{n,[0,...,p]}$ requires to mutually define the type of
+$\restrframe^{n,[0,...,p-1]}$ together with $\myframe^{n,p}$ (or
+$\myframe^{n,[0,...,p]}$) as a function from
+$\restrframe^{n,[0,...,p-1]}$.
 
-\item The same dependencies for frame$^{n-1,p}$ for $p \leq n-1$ gives:
+To talk about sequences of $\myframe$, $\painting$ or $\restrframe$,
+we need to specify their types. The type of $\restrframe$ will be
+defined mutually with $\myframe$ of the same level, but the type of
+$\myframe$, $\painting$ can be defined in advance, the second one
+being however dependent on the first one. In general, components of
+such sequences will have a type dependent on the previous components
+of the sequence, as it is the case for $\restrframe$. So, the type of
+a sequence of length $p$ will be expressed as a $n$-iterated
+$\Sigma$-type. In the case of $\myframe$ and $\painting$, there will
+be however no dependency, so an ordinary product can be used. If
+$\myframe^{n,[0,...,p]}$ is such a sequence of length $p+1$, we write
+$\myframe^{n,[0,...,p-1]}$ for its immediate subsequence of length $p$
+and $\myframe^{n,p}$ for its last component. We can now define the
+types of sequences of $\myframe$ and $\painting$ as follows:
+
+$$
+\begin{array}{llcl}
+\myframetype^{n,[0,...,p]} & & : & Type_{l+1} \\
+\myframetype^{n,[]} & & \defeq & unit \\
+\myframetype^{n,[0,...,p]} & & \defeq & \myframetype^{n,[0,...,p-1]} \times Type_l\\
+\\
+\paintingtype^{n,[0,...,p]} & (\myframe^{n,[0,...,p]}:\myframetype^{n,[0,...,p]}) & : & Type_{l+1} \\
+\paintingtype^{n,[]} & \star & \defeq & unit \\
+\paintingtype^{n,[0,...,p]} & (\myframe^{n,[0,...,p]}) & \defeq & \paintingtype^{n,[0,...,p-1]} \times (\myframe^{n,p} \rightarrow Type_l)\\
+\end{array}
+$$
+
+Formally, this can be described as:
+$$
+\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
+\begin{array}{llcl}
+\myframe^{n,[0,...,p]} &
+  \multicolumn{3}{l}{
+  \left(\begin{array}{l}
+     \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}\\
+     \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]})\\
+     \restrframe^{n,[0,...,p-1]}:\restrframetype^{n,[0,...,p-1]}\\
+  \end{array}\right) : \myframetype^{n-1,[0,...,p]}
+  }\\
+\myframe^{n,[0]} &
+   \left(\begin{array}{l}
+      \star\\
+      \star\\
+      \star\\
+   \end{array}\right) & \defeq & (\star,unit)\\
+\myframe^{n,[0,...,p+1]} &
+   \left(\begin{array}{l}
+      \myframe^{n-1,[0,...,p]}\\
+      \painting^{n-1,[0,...,p]}\\
+     \restrframe^{n,[0,...,p]}\\
+   \end{array}\right) & \defeq &
+   \left(\begin{array}{l}
+     \myframe^{n,[0,...,p]}
+             \left(\begin{array}{l}
+               \myframe^{n-1,[0,...,p-1]}\\
+               \painting^{n-1,[0,...,p-1]}\\
+               \restrframe^{n,[0,...,p-1]}\\
+             \end{array}\right)     ,\\
+     \Sigma d:\myframe^{n,[0,...,p]}
+             \left(\begin{array}{l}
+               \myframe^{n-1,[0,...,p-1]}\\
+               \painting^{n-1,[0,...,p-1]}\\
+               \restrframe^{n,[0,...,p-1]}\\
+             \end{array}\right).\,\\
+     \quad \Pi\omega.\,\painting^{n-1,p}(\restrframe^{n,p}(d))\\
+   \end{array}\right)\\
+\restrframetype^{n,[0,...,p-1]} &
+   \multicolumn{3}{l}{
+   \left(\begin{array}{l}
+      \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}\\
+      \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]})\\
+   \end{array}\right) : Type_{l}
+   }\\
+\restrframetype^{n,[]} &
+   \left(\begin{array}{l}
+      \star\\
+      \star\\
+   \end{array}\right) & \defeq &
+   unit\\
+\restrframetype^{n,[0,...,p]} &
+   \left(\begin{array}{l}
+      \myframe^{n-1,[0,...,p]}\\
+      \painting^{n-1,[0,...,p]}\\
+   \end{array}\right) & \defeq &
+   \begin{array}{l}
+     \Sigma \restrframe^{n,[0,...,p-1]}\\
+     \quad:\restrframetype^{n,[0,...,p-1]}
+                \left(\begin{array}{l}
+                  \myframe^{n-1,[0,...,p-1]}\\
+                  \painting^{n-1,[0,...,p-1]}\\
+                \end{array}\right)
+                .\,\\
+     \Pi q\leq n.\,\Pi \omega.\,\myframe^{n,[0,...,p]}
+       \left(\begin{array}{l}
+         \myframe^{n-1,[0,...,p-1]}\\
+         \painting^{n-1,[0,...,p-1]}\\
+         \restrframe^{n,[0,...,p-1]}\\
+       \end{array}\right)\\
+   \end{array}\\
+\end{array}
+$$
+
+TODO: discuss $p\leq q \leq n$ vs $0 \leq q \leq n-p$.
+
+TODO: remark that we abuse terminology for frame, since, informally, a
+frame is an inhabitant of the type frame, while formally, it is the
+type of (an informal) frame which we call frame. (See same abuse of
+terminology when talking about a list, and using the term list to
+refer to the type of a list.)
+
+TODO: when to talk about the ``prefix'' $X_0, ..., X_{n-1}$?
+
+%% \item By induction on $p$, we deduce this for all $p\leq n$:
+%% \begin{center}
+%% \begin{tikzcd}
+%% frame^{n,[0,...,p...n]} \arrow[d] \arrow[ddr]\\
+%% painting^{n-1,[0,...,p-1...n-1]} \arrow[d, dotted] \\
+%% frame^{n-1,[0,...,p-1...n-1]} &
+%%    \restrframe^{n,[0,...,p-1...n-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
+%% \end{tikzcd}
+%% \end{center}
+
+%% \item The same dependencies for $\myframe^{n-1,p}$ for $p \leq n-1$ gives:
+%% \begin{center}
+%% \begin{tikzcd}
+%% frame^{n-1,p} \arrow[d] \arrow[ddr, shift right=1mm]\\
+%% painting^{n-2,k<p} \arrow[d, dotted] \\
+%% frame^{n-2,k<p} & \restrframe^{n-1,k<p} \arrow[l, dotted] \arrow[uul, dotted, shift right=1mm]\\
+%% \end{tikzcd}
+%% \end{center}
+
+%% Similarly, $\restrframe^{n-1,p}$ and $\myframe^{n-1,p}$ as a function from
+%% all $\restrframe^{n-1,k}$ for $k < p$ have to be mutually defined.
+
+\item Defining $\painting^{n,p}$, in addition to the type dependency
+  in $\myframe^{n,p}$, requires the definition of
+  $\painting^{n-1,p-1}$, thus also $\myframe^{n-1,p-1}$ by typing
+  dependency, as well as $\restrframe^{n,p-1}$. Since
+  $\painting^{n,p}$ also depends on $\painting^{n,p+1}$ when $p<n$,
+  these dependencies are actually between $\painting^{n,[p,...,n]}$,
+  $\painting^{n-1,[p,...,n-1]}$, $\myframe^{n,[p,...,n]}$,
+  $\myframe^{n-1,[p,...,n-1]}$ and $\restrframe^{n,[p,...,n]}$. Also,
+  for the case $p=n$, this also requires the assumption of an
+  inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally,
+  $\myframe^{n,[p,...,n]}$, $\myframe^{n-1,[p,...,n-1]}$ and
+  $\restrframe^{n,[p,...,n-1]}$ respectively depend on the earlier
+  values $\myframe^{n,[0,...,p-1]}$, $\myframe^{n-1,[0,...,p-1]}$ and
+  $\restrframe^{n,[0,...,p-1]}$.  Below, we use dashed underline and
+  dashed arrows for dependencies in subconstructions, here in the
+  construction of $\myframe$ at level $n-1$ and $\restrframetype$ at
+  level $n$:
 \begin{center}
 \begin{tikzcd}
-frame^{n-1,p} \arrow[d] \arrow[ddr, shift right=1mm]\\
-painting^{n-2,k<p} \arrow[d, dotted] \\
-frame^{n-2,k<p} & restrframe^{n-1,k<p} \arrow[l, dotted] \arrow[uul, dotted, shift right=1mm]\\
+& & \painting^{n,[p,...,n]} \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
+\udensdash{\myframe}^{n,[0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
+  \udensdash{\myframe}^{n,[p,...,n]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
+\painting^{n-1,[0,...,p-1]} \arrow[d, dotted] & &
+  \painting^{n-1,[p,...,n-1]} \arrow[ll, dotted] \arrow[d, dotted] \\
+\myframe^{n-1,[0,...,p-1]} &
+  \udensdash{\restrframe}^{n,[0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
+  \myframe^{n-1,[p,...,n-1]} \arrow[ll, dotted, bend left=15] &
+  \udensdash{\restrframe}^{n,[p,...,n-1]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
 \end{tikzcd}
@@
 
-Similarly, restrframe$^{n-1,p}$ and frame$^{n-1,p}$ as a function from
-all restrframe$^{n-1,k}$ for $k < p$ have to be mutually defined.
+\item Defining $\restrframe^{n,p}$ for $p\leq n-1$, in addition to the
+  mutual type dependency in $\myframe^{n,p}$ and the dependency in
+  $\myframe^{n-1,p}$, requires $\restrpainting^{n-1,p-1}$, thus also
+  $\restrframe^{n-1,p-1}$ and $\myframe^{n-1,p-1}$ mutually, as well
+  as $\myframe^{n-2,p-2}$, $painting^{n-2,p-1}$ and
+  $\painting^{n-2,p-1}$ by typing dependency, as well as
+  $\cohframe^{n,p-1}$. Since $\restrframe^{n,p}$ also depends on
+  $\restrframe^{n,p-1}$, these dependencies are between the blocks
+  $\myframe^{n,[0..p]}$, $\myframe^{n-1,[0..p]}$,
+  $\myframe^{n-2,[0..p]}$, $\painting^{n-1,[0..p-1]}$ and
+  $\restrframe^{n,[0..p-1]}$, where cohframes$^{n,k}$ in turn depends
+  in $\restrframe^{n,k}$ for its typing. Below, we use again dashed
+  underline and dashed arrows for dependencies in subconstructions,
+  here in the construction of $\myframe$ at level $n-1$ and $n-2$ and $\restrframetype$ at level $n$ and $n-1$ :
 
-\item Defining painting$^{n-1,p}$ for $p\leq n-1$, in addition to the
-  type dependency in frame$^{n-1,p}$, requires the definition of
-  painting$^{n-2,k}$, thus also frame$^{n-2,k}$ by typing dependency,
-  as well as restrframe$^{n,k}$, this time for $k \geq p$, and the
-  assumption of an inhabitant $X_{n-2}$ of $\nu$Set$^{=n-2}$
 \begin{center}
 \begin{tikzcd}
-   & & painting^{n-1,p} \arrow[ddll] \arrow[dddl] \arrow[d, dotted]\\
-   & & frame^{n-1,p} \\
-painting^{n-2,k\geq p} \arrow[d, dotted] \\
-frame^{n-2,k\geq p} & restrframe^{n-1,k\geq p},X_{n-2} \arrow[l, dotted]\\
+\udensdash{\myframe}^{n,[0..p]} \arrow[d, dashed] \arrow[ddr, dashed] \\
+\painting^{n-1,[0..p-1]} \arrow[d, dotted]\\
+\udensdash{\myframe}^{n-1,[0..p-1]} \arrow[d, dashed] \arrow[ddr, dashed] &
+  \restrframe^{n,[0..p-1]} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook']\\
+\painting^{n-2,[0..p-2]} \arrow[d, dotted] &
+  \restrpainting^{n-1,[0..p-2]} \arrow[d, dotted] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
+\myframe^{n-2,[0..p-2]} &
+  \restrframe^{n-1,[0..p-2]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
+  \cohframe^{n,[0..p-2]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook']\\
 \end{tikzcd}
@@
 
-\item Defining restrframe$^{n,p}$ for $p\leq n-1$, in addition to the
-  type dependency in frame$^{n+1,p}$ and frame$^{n,p}$, requires
-  defining restrpainting$^{n-1,k}$, thus also restrframe$^{n-1,k}$,
-  frame$^{n-2,k}$ by typing dependency, as well as cohframe$^{n,k}$,
-  for $k < p$, where cohframes$^{n,k}$ in turn depends in
-  restrframe$^{n,k}$ for its typing:
-\begin{center}
-\begin{tikzcd}
-frame^{n,p} \\
- \\
-frame^{n-1,p} & restrframe^{n,p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted]\\
-  & restrpainting^{n-1,k<p} \arrow[d, dotted] \\
-frame^{n-2,p} & restrframe^{n-1,k<p} \arrow[l, dotted] \arrow[uul, dotted] & cohframe^{n,k<p} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
-\end{tikzcd}
-\end{center}
+In particular, the mutual dependency of $\restrframe^{n,[0,...,p-1]}$
+in the type of $\cohframe^{n,[0,...,p-2]}$ and of
+$\cohframe^{n,[0,..,p-2]}$ in the definition of
+$\restrframe^{n,[0,...,p-1]}$ requires to mutually define the type of
+$\cohframe^{n,[0,...,p-2]}$ and $\restrframe^{n,p}$
+($\restrframe^{n,[0,...,p-1]}$) as a function from
+  $\cohframe^{n,[0,...,p-2]}$.
 
-In particular, the mutual dependency of restrframe$^{n,p}$ in the type
-of cohframe$^{n,p}$ and of cohframe$^{n,p}$ in the definition of
-restrframe$^{n,p}$ requires to mutually defining the type of
-cohframe$^{n,p}$ and restrframe$^{n,p}$ as a function from all
-cohframe$^{n,k}$ for $k\leq p$.
-
-\item Defining cohframe$^{n+1,p}$ for $p\leq n-1$, in addition to the
-  type dependency in restrframe$^{n+1,p}$, restrframe$^{n,p}$,
-  frame$^{n+1,p}$, frame$^{n,p}$ and frame$^{n-1,p}$, requires defining
-  cohpainting$^{n,k}$, thus also cohframe$^{n,k}$ by typing
-  dependency, for $k < p$. By reasoning in sets, no higher-dimensional
-  coherence frame is needed:
-\begin{center}
-\begin{tikzcd}
-frame^{n+1,p} \\
-\\
-frame^{n,p} & restrframe^{n+1,p} \arrow[l, dotted] \arrow[uul, dotted] \\
-\\
-frame^{n-1,p} & restrframe^{n,p} \arrow[l, dotted] \arrow[uul, dotted] & cohframe^{n+1,p} \arrow[d] \arrow[uul, dotted] \arrow[l, dotted]\\
-& & cohpainting^{n,k<p} \arrow[d, dotted] \\
-frame^{n-2,p} & restrframe^{n-1,p} \arrow[l, dotted] \arrow[uul, dotted] & cohframe^{n,k<p} \arrow[uul, dotted] \arrow[l, dotted]\\
-\end{tikzcd}
-\end{center}
-\item Defining restrpainting$^{n,p}$ for $p\leq n-1$, in addition to
-  the type dependency in painting$^{n,p}$, painting$^{n-1,p}$, restrframe$^{n,p}$, frame$^{n,p}$ and
-  frame$^{n-1,p}$, requires the definition of restrpainting$^{n-1,k}$,
-  thus also restrframe$^{n-1,k}$ and frame$^{n-2,p}$ by typing
-  dependency, as well as cohframe$^{n,k}$ for $p \geq k$ and the
+\item Defining $\restrpainting^{n,p}$ for $p\leq n-1$, in addition to
+  the type dependency in $\painting^{n,p}$, $\painting^{n-1,p}$, $\restrframe^{n,p}$, $\myframe^{n,p}$ and
+  $\myframe^{n-1,p}$, requires the definition of $\restrpainting^{n-1,k}$,
+  thus also $\restrframe^{n-1,k}$ and $\myframe^{n-2,p}$ by typing
+  dependency, as well as $\cohframe^{n,k}$ for $p \geq k$ and the
   assumption of an inhabitant $X_{n-1}$ of nuSet$^{=n-1}$:
@@
    & & frame^{n,p} \\
-   & & painting^{n-1,p} \arrow[d, dotted] & restrpainting^{n,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \arrow[uul, dotted] \arrow[ul, dotted] \arrow[l, dotted] \\
-   & & frame^{n-1,p} & restrframe^{n,p} \arrow[uul, dotted] \arrow[l, dotted]\\
-restrpainting^{n-1,k\geq p} \arrow[d, dotted] \\
-restrframe^{n-1,k\geq p} & cohframe^{n,k\geq p},X_{n-1} \arrow[l, dotted]\\
+   & & painting^{n-1,p} \arrow[d, dotted] & \restrpainting^{n,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \arrow[uul, dotted] \arrow[ul, dotted] \arrow[l, dotted] \\
+   & & frame^{n-1,p} & \restrframe^{n,p} \arrow[uul, dotted] \arrow[l, dotted]\\
+restrpainting^{n-1,[p,...,n]} \arrow[d, dotted] \\
+restrframe^{n-1,[p,...,n]} & \cohframe^{n,[p,...,n]},X_{n-1} \arrow[l, dotted]\\
 \end{tikzcd}
@@
 
-\item Defining cohpainting$^{n+1,p}$ for $p\leq n-1$, in addition to
-  the type dependency in restrpainting$^{n+1,p}$,
-  restrpainting$^{n,p}$, painting$^{n+1,p}$, painting$^{n,p}$,
-  painting$^{n-1,p}$, restrframe$^{n+1,p}$, restrframe$^{n,p}$,
-  frame$^{n+1,p}$, frame$^{n,p}$ and frame$^{n-1,p}$ requires the
-  definition of cohpainting$^{n,k}$, thus also cohframe$^{n,k}$ by
+\item Defining $\cohframe^{n+1,p}$ for $p\leq n-1$, in addition to the
+  type dependency in $\restrframe^{n+1,p}$, $\restrframe^{n,p}$,
+  $\myframe^{n+1,p}$, $\myframe^{n,p}$ and $\myframe^{n-1,p}$, requires defining
+  $\cohpainting^{n,k}$, thus also $\cohframe^{n,k}$, $\restrpainting^{n,k}$, $\restrpainting^{n-1,k}$, $\painting^{n,k}$, $\painting^{n-1,k}$ and $\painting^{n-2,k}$ by typing
+  dependency, for $k < p$. By reasoning in sets, no higher-dimensional
+  coherence frame is needed:
+\begin{center}
+\begin{tikzcd}
+\myframe^{n+1,p} \\
+\painting^{n,p} \arrow[d, dotted] \\
+\myframe^{n,p} & \restrframe^{n+1,p} \arrow[l, dotted] \arrow[uul, dotted, hook'] \\
+\painting^{n-1,p} \arrow[d, dotted] &
+  \restrpainting^{n-1,p} \arrow[d, dotted] \arrow[l, dotted] \arrow[uul, dotted, hook'] \\
+\myframe^{n-1,p} &
+  \restrframe^{n,p} \arrow[l, dotted] \arrow[uul, dotted, hook'] &
+  \cohframe^{n+1,p} \arrow[d] \arrow[l, dotted] \arrow[uul, dotted, hook'] \\
+\painting^{n-2,p} \arrow[d, dotted] &
+  \restrpainting^{n-1,p} \arrow[d, dotted] \arrow[l, dotted] \arrow[uul, dotted, hook'] &
+  \cohpainting^{n,k<p} \arrow[d, dotted] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
+\myframe^{n-2,p} &
+  \restrframe^{n-1,p} \arrow[l, dotted] \arrow[uul, dotted, hook'] &
+  \cohframe^{n,k<p} \arrow[l, dotted] \arrow[uul, dotted, hook']\\
+\end{tikzcd}
+\end{center}
+
+\item Defining $\cohpainting^{n+1,p}$ for $p\leq n-1$, in addition to
+  the type dependency in $\restrpainting^{n+1,p}$,
+  $\restrpainting^{n,p}$, $\painting^{n+1,p}$, $\painting^{n,p}$,
+  $\painting^{n-1,p}$, $\restrframe^{n+1,p}$, $\restrframe^{n,p}$,
+  $\myframe^{n+1,p}$, $\myframe^{n,p}$ and $\myframe^{n-1,p}$ requires the
+  definition of $\cohpainting^{n,k}$, thus also $\cohframe^{n,k}$ by
   typing dependency, for also $p \geq k$. By reasoning in sets, no
@@
    & & frame^{n+1,p} \\
-   & & painting^{n,p} \arrow[d, dotted] & restrpainting^{n+1,p} \arrow[d, dotted] \arrow[uul, dotted] \arrow[ul, dotted] \arrow[l, dotted] \\
-   & & frame^{n,p} & restrframe^{n+1,p} \arrow[uul, dotted] \arrow[l, dotted] \\
-   & & painting^{n-1,p} \arrow[d, dotted] & restrpainting^{n,p} \arrow[d, dotted] \arrow[uul, dotted] \arrow[ul, dotted] \arrow[l, dotted] & cohpainting^{n+1,p} \arrow[ddllll] \arrow[l, dotted] \arrow[uul, dotted] \arrow[d, dotted]\\
-   & & frame^{n-1,p} & restrframe^{n,p} \arrow[l, dotted] & cohframe^{n+1,p} \arrow[l, dotted] \arrow[uul, dotted]\\
+   & & painting^{n,p} \arrow[d, dotted] & \restrpainting^{n+1,p} \arrow[d, dotted] \arrow[uul, dotted] \arrow[ul, dotted] \arrow[l, dotted] \\
+   & & frame^{n,p} & \restrframe^{n+1,p} \arrow[uul, dotted] \arrow[l, dotted] \\
+   & & painting^{n-1,p} \arrow[d, dotted] & \restrpainting^{n,p} \arrow[d, dotted] \arrow[uul, dotted] \arrow[ul, dotted] \arrow[l, dotted] & \cohpainting^{n+1,p} \arrow[ddllll] \arrow[l, dotted] \arrow[uul, dotted] \arrow[d, dotted]\\
+   & & frame^{n-1,p} & \restrframe^{n,p} \arrow[l, dotted] & \cohframe^{n+1,p} \arrow[l, dotted] \arrow[uul, dotted]\\
 cohpainting^{n,k\geq p} \arrow[d, dotted] \\
@@
 \begin{enumerate}
-\item To assume frame$^{n-2,k}$ and painting$^{n-2,k}$ for all $k< p$
+\item To assume $\myframe^{n-2,k}$ and $\painting^{n-2,k}$ for all $k< p$
   in order to mutually define, for all $p\leq n$, the type of
-  restrframe$^{n-1,p}$ and frame$^{n-1,p}$ as a function from all
-  restrframe$^{n-1,k}$ for $k< p$. Using red for assumptions, this
+  $\restrframe^{n-1,p}$ and $\myframe^{n-1,p}$ as a function from all
+  $\restrframe^{n-1,k}$ for $k< p$. Using red for assumptions, this
   can be pictured as:
@@
 \begin{tikzcd}
-frame^{n-1,p}(\textcolor{red}{restrframe^{n-1,k<p}}) \arrow[d] \\
+\myframe^{n-1,p}(\textcolor{red}{restrframe^{n-1,k<p}}) \arrow[d] \\
 \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
@@
 
-\item To further assume restrframe$^{n-1,k}$ for all $k<p$ to get
-  frame$^{n-1,p}$ for all $p\leq n-1$:
+\item To further assume $\restrframe^{n-1,k}$ for all $k<p$ to get
+  $\myframe^{n-1,p}$ for all $p\leq n-1$:
 \begin{center}
 \begin{tikzcd}
-frame^{n-1,p} \arrow[d] \arrow[ddr]\\
+\myframe^{n-1,p} \arrow[d] \arrow[ddr]\\
 \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
@@
 
-\item To rely on frame$^{n-2,k}$, painting$^{n-2,k}$ and
-  restrframe$^{n-1,k}$, jointly with frame$^{n-1,k}$, and now for all
+\item To rely on $\myframe^{n-2,k}$, $\painting^{n-2,k}$ and
+  $\restrframe^{n-1,k}$, jointly with $\myframe^{n-1,k}$, and now for all
   $k \geq p$, as well as an inhabitant $X_{n-2}$ of $\nu$Set$^{=n-2}$
-  to define painting$^{n-1,p}$ for all $p \leq n-1$:
+  to define $\painting^{n-1,p}$ for all $p \leq n-1$:
 \begin{center}
@@
 & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
-frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & & & frame^{n-1,p} \arrow[d] \arrow[ddr]\\
+\myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & & & frame^{n-1,p} \arrow[d] \arrow[ddr]\\
 \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
@@
 
-\item To rely on frame$^{n-1,k}$ and painting$^{n-1,k}$ for all $k <
-  p$ to now construct the frame$^{n,p}$ for $p \leq n-1$ as a function
-  from all restrframe$^{n,k}$ for $k\leq p$:
+\item To rely on $\myframe^{n-1,k}$ and $\painting^{n-1,k}$ for all $k <
+  p$ to now construct the $\myframe^{n,p}$ for $p \leq n-1$ as a function
+  from all $\restrframe^{n,k}$ for $k\leq p$:
 
@@
 
-\item To additionally assume restrpainting$^{n-1,k}$ for $k < p$ to
-  mutually define for $p \leq n-1$ the type of cohframe$^{n,p}$ and
-  restrframe$^{n,p}$ as a function from all cohframe$^{n,k}$ for
-  $k\leq p$, as well as, consequently, frame$^{n,p}$ for all $p\leq n$
+\item To additionally assume $\restrpainting^{n-1,k}$ for $k < p$ to
+  mutually define for $p \leq n-1$ the type of $\cohframe^{n,p}$ and
+  $\restrframe^{n,p}$ as a function from all $\cohframe^{n,k}$ for
+  $k\leq p$, as well as, consequently, $\myframe^{n,p}$ for all $p\leq n$
 
@@
 & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
-& & & frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p}(\textcolor{red}{cohframe^{n,k<p}}) \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
+& & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p}(\textcolor{red}{cohframe^{n,k<p}}) \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
 \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[d, dotted]\\
@@
 
-\item To additionally assume cohframe$^{n,k}$ for $k \leq p$ to get
-  all restrframe$^{n,k}$ for all $k \leq p$:
+\item To additionally assume $\cohframe^{n,k}$ for $k \leq p$ to get
+  all $\restrframe^{n,k}$ for all $k \leq p$:
 
@@
 & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
-& & & frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
+& & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
 \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
@@
 
-\item To rely on frame$^{n-2,k\geq p}$, painting$^{n-2,k\geq p}$ and
-  restrframe$^{n-1,k\geq p}$ to build frame$^{n-1,k\geq p}$ and
-  painting$^{n-1,k\geq p}$ for $p \leq n$:
+\item To rely on $\myframe^{n-2,k\geq p}$, $\painting^{n-2,k\geq p}$ and
+  $\restrframe^{n-1,k\geq p}$ to build $\myframe^{n-1,k\geq p}$ and
+  $\painting^{n-1,k\geq p}$ for $p \leq n$:
 
@@
 & & & frame^{n,p} \arrow[d] \arrow[ddr]\\
-painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
-frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & & & frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
+\painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
+\myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
 \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
@@
 
-Note that this can be done in parallel with the steps building frame$^{n,p}$.
+Note that this can be done in parallel with the steps building $\myframe^{n,p}$.
 
-\item To assume restrpainting$^{n-1,k}$ and cohframe$^{n,k}$ for $k >
-  p$ to build restrframe$^{n,k\geq p}$:
+\item To assume $\restrpainting^{n-1,k}$ and $\cohframe^{n,k}$ for $k >
+  p$ to build $\restrframe^{n,k\geq p}$:
 
@@
 & & & frame^{n,p} \arrow[d] \arrow[ddr]\\
-painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
-frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & & frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
+\painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
+\myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & \restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
 \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] & &
@@
 
-\item To rely on painting$^{n-1,k\geq p}$ and restrframe$^{n,p\leq n-1}$ to build painting$^{n,p}$ for $p \leq n$:
+\item To rely on $\painting^{n-1,k\geq p}$ and $\restrframe^{n,p\leq n-1}$ to build $\painting^{n,p}$ for $p \leq n$:
 
@@
 
-\item To rely on restrpainting$^{n-1,k}$ and cohframe$^{n,k}$ for $k >
-  p$ to also get restrpainting$^{n,p}$ for all $p \leq n-1$:
+\item To rely on $\restrpainting^{n-1,k}$ and $\cohframe^{n,k}$ for $k >
+  p$ to also get $\restrpainting^{n,p}$ for all $p \leq n-1$:
 
@@
 & & & frame^{n,p} \arrow[d] \arrow[ddr]\\
-painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70]  & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
-frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
-  frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
+\painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70]  & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & \restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
+\myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & \restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
+  frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
 \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[d, dotted] & &
@@
 
-\item To rely on frame$^{n,k}$ and painting$^{n,k}$ for all $k < p$ to
-  now construct frame$^{n+1,p}$ for $p \leq n+1$ as a function from
-  all restrframe$^{n+1,k}$ for $k \leq p$:
+\item To rely on $\myframe^{n,k}$ and $\painting^{n,k}$ for all $k < p$ to
+  now construct $\myframe^{n+1,p}$ for $p \leq n+1$ as a function from
+  all $\restrframe^{n+1,k}$ for $k \leq p$:
 
@@
 
-\item To rely on restrframe$^{n,k}$ and restrpainting$^{n,k}$ for all
-  $k < p$ to now construct restrframe$^{n+1,p}$ for $p \leq n$ as a
-  function from all cohframe$^{n+1,k}$ for $k \leq p$. This also
-  allows to instantiate the dependency of frame$^{n+1,p}$ on
-  restrframe$^{n+1,p}$:
+\item To rely on $\restrframe^{n,k}$ and $\restrpainting^{n,k}$ for all
+  $k < p$ to now construct $\restrframe^{n+1,p}$ for $p \leq n$ as a
+  function from all $\cohframe^{n+1,k}$ for $k \leq p$. This also
+  allows to instantiate the dependency of $\myframe^{n+1,p}$ on
+  $\restrframe^{n+1,p}$:
 
@@
 & & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
-& & & frame^{n,p} \arrow[d] \arrow[ddr] & restrframe^{n+1,k<p}(\textcolor{red}{cohframe^{n+1,k<p}}) \arrow[d] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
-painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
-   painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
-frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
-  frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
+& & & frame^{n,p} \arrow[d] \arrow[ddr] & \restrframe^{n+1,k<p}(\textcolor{red}{cohframe^{n+1,k<p}}) \arrow[d] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
+\painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
+   painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & \restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
+\myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & \restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
+  frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
 \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[d, dotted] & &
@@
 
-\item To additionally assume cohpainting$^{n,k}$ for $k < p$ to get
-  cohframe$^{n+1,p}$ for all $p \leq n-1$. This also allows to
-  instantiate the dependency of restrframe$^{n+1,p}$ on
-  cohframe$^{n+1,p}$:
+\item To additionally assume $\cohpainting^{n,k}$ for $k < p$ to get
+  $\cohframe^{n+1,p}$ for all $p \leq n-1$. This also allows to
+  instantiate the dependency of $\restrframe^{n+1,p}$ on
+  $\cohframe^{n+1,p}$:
 
@@
 & & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
-& & & frame^{n,p} \arrow[d] \arrow[ddr] & restrframe^{n+1,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
-painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
-  painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
-frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
- frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
-   cohframe^{n+1,p} \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
+& & & frame^{n,p} \arrow[d] \arrow[ddr] & \restrframe^{n+1,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
+\painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
+  painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & \restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
+\myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & \restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
+ frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
+   \cohframe^{n+1,p} \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
 \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[d, dotted] & &
@@
 
-\item To assume cohpainting$^{n+1,k}$ for $k \geq p$ to build
-  cohframe$^{n+1,k\geq p}$:
+\item To assume $\cohpainting^{n+1,k}$ for $k \geq p$ to build
+  $\cohframe^{n+1,k\geq p}$:
 
@@
 
-\item To rely on restrpainting$^{n,k}$ and cohframe$^{n+1,k}$ for $k \geq
-  p$ to also get restrpainting$^{n+1,p}$ for all $p \leq n$:
+\item To rely on $\restrpainting^{n,k}$ and $\cohframe^{n+1,k}$ for $k \geq
+  p$ to also get $\restrpainting^{n+1,p}$ for all $p \leq n$:
 
@@
 & & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
-& & & frame^{n,p} \arrow[d] \arrow[ddr] & restrframe^{n+1,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
-painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
-  painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
-frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
- frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
-   cohframe^{n+1,p} \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
+& & & frame^{n,p} \arrow[d] \arrow[ddr] & \restrframe^{n+1,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
+\painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
+  painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & \restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
+\myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & \restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
+ frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
+   \cohframe^{n+1,p} \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
 \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] &
@@
 
-\item To finally rely on cohpainting$^{n,k}$ for $k \geq p$
-to also get cohpainting$^{n+1,p}$ for $p \leq n-1$:
+\item To finally rely on $\cohpainting^{n,k}$ for $k \geq p$
+to also get $\cohpainting^{n+1,p}$ for $p \leq n-1$:
 
@@
 & & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
-& & & frame^{n,p} \arrow[d] \arrow[ddr] & restrframe^{n+1,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
-painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
- painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] &
-   cohpainting^{n+1,p} \arrow[ddlll] \arrow[d, dotted] \arrow[l, dotted] \\
-frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
-  frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
-   cohframe^{n+1,p} \arrow[d] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
+& & & frame^{n,p} \arrow[d] \arrow[ddr] & \restrframe^{n+1,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
+\painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
+ painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & \restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] &
+   \cohpainting^{n+1,p} \arrow[ddlll] \arrow[d, dotted] \arrow[l, dotted] \\
+\myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & \restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
+  frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
+   \cohframe^{n+1,p} \arrow[d] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
 \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] &
@@
 
-Thus, shortly, assuming frame$^{n-2,p}$, painting$^{n-2,p}$,
-restrframe$^{n-1,p}$, restrpainting$^{n-1,p}$, cohframe$^{n,p}$ and
-cohpainting$^{n,p}$ for all $p \leq n-2$ allows to define
-frame$^{n-1,p}$, painting$^{n-1,p}$, restrframe$^{n,p}$,
-restrpainting$^{n,p}$, cohframe$^{n+1,p}$ and cohpainting$^{n+1,p}$
+Thus, shortly, assuming $\myframe^{n-2,p}$, $\painting^{n-2,p}$,
+$\restrframe^{n-1,p}$, $\restrpainting^{n-1,p}$, $\cohframe^{n,p}$ and
+$\cohpainting^{n,p}$ for all $p \leq n-2$ allows to define
+$\myframe^{n-1,p}$, $\painting^{n-1,p}$, $\restrframe^{n,p}$,
+$\restrpainting^{n,p}$, $\cohframe^{n+1,p}$ and $\cohpainting^{n+1,p}$
 for all $p \leq n-1$, so the construction can be recursively

### 2025-08-02 paper/restruct-new.tex
restruct-new: NFC style changes

@@
-\documentclass[a4paper,english,cleveref,autoref,thm-restate]{article}
+\documentclass{article}
+\usepackage[a4paper, margin=2em]{geometry}
 
-\usepackage[utf8x]{inputenc}
-\usepackage{t1enc}
+\usepackage{hyperref, amssymb, stmaryrd, url, xcolor, amsmath, graphicx, yfonts, tikz, enumitem}
+\usetikzlibrary{cd, arrows}
+\setlist[enumerate]{left=0pt,nosep}
 
-\usepackage{hyperref}
-%\usepackage{proof}
-\usepackage{fullpage}
-\usepackage{amssymb}
-\usepackage{stmaryrd}
-%\usepackage{txfonts}
-\usepackage{url}
-
-\usepackage{xcolor}
-%\usepackage{textcomp}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{yfonts}
-\usepackage{tikz}
-\usetikzlibrary{cd, arrows}
-
-\newcommand{\Overrightarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#2}$}}{}$}}
-\newcommand{\Overleftarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Leftarrowfill@{\mbox{${#2}$}}{}$}}
-%\newcommand{\Overrightarrow}[1]{\raisebox{1.4ex}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#1}$}}{}$}}
-\makeatother
-
-\newcommand{\rocq}[1]{(\mbox{\texttt{#1}})}
-\newcommand{\highlight}[1]{\emph{#1}}
-
-\newcommand{\imp}{\rightarrow}
-\newcommand{\Type}{\mathsf{Type}}
-\newcommand{\Set}{\mathsf{Set}}
-\newcommand{\Prop}{\mathsf{Prop}}
-\newcommand{\refl}[1]{\mathsf{refl}\,{#1}}
-\newcommand{\mkmlidtype}[3]{{#1} =^{\mathrm{id}}_{#2} {#3}}
-\newcommand{\mkmleqdep}[3]{{#1} =^{\mathrm{dep}}_{#2} {#3}}
-\newcommand{\hrefl}[1]{\mathsf{refl^{\mathrm{dep}}}\,{#1}}
-\newcommand{\mluniv}{\mathsf{U}}
-\newcommand{\Jdep}[2]{\mathsf{J}\;{#1}\;{#2}}
-\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
-\newcommand{\unitpoint}{\ensuremath{\ast}}
-
-\newcommand{\nth}[1]{{#1}^{\mbox{\scriptsize th}}}
 \newcommand{\defeq}{\triangleq}
-
 \newcommand{\U}{\ensuremath{\mathsf{{HSet}}}}
-
 \newcommand{\myframe}{\mathit{frame}}
@@
 \section{The recursive structure of iterated parametricity}
-
 Iterated parametricity (in indexed form) produces a family of type
@@
 
-Such family can be recursively described by the equations given on Table \ref{}.
+Such family can be recursively described by the equations given on Table ?.
 
@@
             \myframetype^{n,[]}         &                                                     & \defeq & unit                                                                     \\
-\myframetype^{n,[0,...,p]} & & \defeq & \myframetype^{n,[0,...,p-1]} \times Type_l\\
+            \myframetype^{n,[0,...,p]}  &                                                     & \defeq & \myframetype^{n,[0,...,p-1]} \times Type_l                               \\
             \\
@@
             \paintingtype^{n,[]}        & \star                                               & \defeq & unit                                                                     \\
-\paintingtype^{n,[0,...,p]} & (\myframe^{n,[0,...,p]}) & \defeq & \paintingtype^{n,[0,...,p-1]} \times (\myframe^{n,p} \rightarrow Type_l)\\
+            \paintingtype^{n,[0,...,p]} & (\myframe^{n,[0,...,p]})                            & \defeq & \paintingtype^{n,[0,...,p-1]} \times (\myframe^{n,p} \rightarrow Type_l) \\
           \end{array}
@@
         $$
-\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
           \begin{array}{llcl}
@@
               \left(\begin{array}{l}
-     \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}\\
-     \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]})\\
-     \restrframe^{n,[0,...,p-1]}:\restrframetype^{n,[0,...,p-1]}\\
+                        \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}                               \\
+                        \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]}) \\
+                        \restrframe^{n,[0,...,p-1]}:\restrframetype^{n,[0,...,p-1]}                             \\
                       \end{array}\right) : \myframetype^{n-1,[0,...,p]}
-  }\\
+            }                                                                                         \\
             \myframe^{n,[0]}                                           &
             \left(\begin{array}{l}
-      \star\\
-      \star\\
-      \star\\
-   \end{array}\right) & \defeq & (\star,unit)\\
+                      \star \\
+                      \star \\
+                      \star \\
+                    \end{array}\right)                                     & \defeq & (\star,unit)      \\
             \myframe^{n,[0,...,p+1]}                                   &
             \left(\begin{array}{l}
-      \myframe^{n-1,[0,...,p]}\\
-      \painting^{n-1,[0,...,p]}\\
-     \restrframe^{n,[0,...,p]}\\
+                      \myframe^{n-1,[0,...,p]}  \\
+                      \painting^{n-1,[0,...,p]} \\
+                      \restrframe^{n,[0,...,p]} \\
                     \end{array}\right) & \defeq &
@@
                       \left(\begin{array}{l}
-               \myframe^{n-1,[0,...,p-1]}\\
-               \painting^{n-1,[0,...,p-1]}\\
-               \restrframe^{n,[0,...,p-1]}\\
-             \end{array}\right)     ,\\
+                          \myframe^{n-1,[0,...,p-1]}  \\
+                          \painting^{n-1,[0,...,p-1]} \\
+                          \restrframe^{n,[0,...,p-1]} \\
+                        \end{array}\right)     , \\
                       \Sigma d:\myframe^{n,[0,...,p]}
                       \left(\begin{array}{l}
-               \myframe^{n-1,[0,...,p-1]}\\
-               \painting^{n-1,[0,...,p-1]}\\
-               \restrframe^{n,[0,...,p-1]}\\
-             \end{array}\right).\,\\
-     \quad \Pi\omega.\,\painting^{n-1,p}(\restrframe^{n,p}(d))\\
-   \end{array}\right)\\
+                          \myframe^{n-1,[0,...,p-1]}  \\
+                          \painting^{n-1,[0,...,p-1]} \\
+                          \restrframe^{n,[0,...,p-1]} \\
+                        \end{array}\right).\, \\
+                      \quad \Pi\omega.\,\painting^{n-1,p}(\restrframe^{n,p}(d))     \\
+                    \end{array}\right)                    \\
             \restrframetype^{n,[0,...,p-1]}                            &
@@
               \left(\begin{array}{l}
-      \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}\\
-      \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]})\\
+                        \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}                               \\
+                        \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]}) \\
                       \end{array}\right) : Type_{l}
-   }\\
+            }                                                                                         \\
             \restrframetype^{n,[]}                                     &
             \left(\begin{array}{l}
-      \star\\
-      \star\\
+                      \star \\
+                      \star \\
                     \end{array}\right)                                     & \defeq &
-   unit\\
+            unit                                                                                      \\
             \restrframetype^{n,[0,...,p]}                              &
             \left(\begin{array}{l}
-      \myframe^{n-1,[0,...,p]}\\
-      \painting^{n-1,[0,...,p]}\\
+                      \myframe^{n-1,[0,...,p]}  \\
+                      \painting^{n-1,[0,...,p]} \\
                     \end{array}\right) & \defeq &
             \begin{array}{l}
-     \Sigma \restrframe^{n,[0,...,p-1]}\\
+              \Sigma \restrframe^{n,[0,...,p-1]}                            \\
               \quad:\restrframetype^{n,[0,...,p-1]}
               \left(\begin{array}{l}
-                  \myframe^{n-1,[0,...,p-1]}\\
-                  \painting^{n-1,[0,...,p-1]}\\
+                        \myframe^{n-1,[0,...,p-1]}  \\
+                        \painting^{n-1,[0,...,p-1]} \\
                       \end{array}\right)
-                .\,\\
+              .\,                                                           \\
               \Pi q\leq n.\,\Pi \omega.\,\myframe^{n,[0,...,p]}
               \left(\begin{array}{l}
-         \myframe^{n-1,[0,...,p-1]}\\
-         \painting^{n-1,[0,...,p-1]}\\
-         \restrframe^{n,[0,...,p-1]}\\
-       \end{array}\right)\\
-   \end{array}\\
+                        \myframe^{n-1,[0,...,p-1]}  \\
+                        \painting^{n-1,[0,...,p-1]} \\
+                        \restrframe^{n,[0,...,p-1]} \\
+                      \end{array}\right) \\
+            \end{array} \\
           \end{array}
@@
 
-$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
         \begin{tikzcd}
@@
 
-$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
-\begin{small}
+        \begin{tiny}
           \begin{tikzcd}
@@
           \end{tikzcd}
-\end{small}
+        \end{tiny}
 
@@
 
-$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
-\begin{scriptsize}
+        \begin{tiny}
           \begin{tikzcd}
@@
           \end{tikzcd}
-\end{scriptsize}
+        \end{tiny}
 
@@
           \end{tikzcd}
-\end{scriptsize}
+        \end{tiny}
 \end{enumerate}

### 2025-09-21 paper/restruct-new.tex
Update

@@
 
+\title{On the specific recursive structure of iterated parametricity}
+
+\maketitle
+
+\begin{abstract}
+  In a previous paper, we gave equations describing the construction
+  of semi-simplicial and semi-cubical sets via iterated parametricity.
+  The construction was formalised in the Rocq (ex-Coq) proof assistant
+  building $n$-truncated sets using an induction on a large structure
+  embedding equational reasoning.
+
+  The current paper describes a new and lighter presentation of the
+  construction where equational reasoning is replaced by
+  definition. Being lighter, it can now be described in full details,
+  closely following the corresponding new machine-checked
+  formalisation.
+\end{abstract}
+
 \section{The recursive structure of iterated parametricity}
@@
 The well-foundedness of the construction can be justified by the observation that:
-\begin{enumerate}
+\begin{itemize}
   \item Defining $\myframe^{n,p}$ for $p \leq n$ requires the definition
@@
             \paintingtype^{n,[]}        & \star                                               & \defeq & unit                                                                     \\
-            \paintingtype^{n,[0,...,p]} & (\myframe^{n,[0,...,p]})                            & \defeq & \paintingtype^{n,[0,...,p-1]} \times (\myframe^{n,p} \rightarrow Type_l) \\
+            \paintingtype^{n,[0,...,p]} & (\myframe^{n,[0,...,p]})                            & \defeq & \paintingtype^{n,[0,...,p-1]}(\myframe^{n,[0,...,p-1]}) \times (\myframe^{n,p} \rightarrow Type_l) \\
           \end{array}
@@
                         \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]}) \\
-                        \restrframe^{n,[0,...,p-1]}:\restrframetype^{n,[0,...,p-1]}                             \\
+                        \restrframe^{n,[0,...,p-1]}:\restrframetype^{n,[0,...,p-1]}
+                                \left(\begin{array}{l}
+                                    \myframe^{n-1,[0,...,p-1]}  \\
+                                    \painting^{n-1,[0,...,p-1]} \\
+                                  \end{array}\right)                             \\
                       \end{array}\right) : \myframetype^{n-1,[0,...,p]}
@@
 
+        Or, alternatively, as:
+        $$\!\!\!\!\!\!\!\!\!\!\!\!
+          \begin{array}{llcl}
+            \restrframetype^{n,[0,...,p-1]}                            &
+            \multicolumn{3}{l}{
+              \left(\begin{array}{l}
+                        \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}                               \\
+                        \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]}) \\
+                      \end{array}\right) : Type_{l}
+            }                                                                                         \\
+            \restrframetype^{n,[]}                                     &
+            \left(\begin{array}{l}
+                      \star \\
+                      \star \\
+                    \end{array}\right)                                     & \defeq &
+            unit                                                                                      \\
+            \restrframetype^{n,[0,...,p]}                              &
+            \left(\begin{array}{l}
+                      \myframe^{n-1,[0,...,p]}  \\
+                      \painting^{n-1,[0,...,p]} \\
+                    \end{array}\right) & \defeq &
+            \begin{array}{l}
+              \Sigma \restrframe^{n,[0,...,p-1]}                            \\
+              \quad:\restrframetype^{n,[0,...,p-1]}
+              \left(\begin{array}{l}
+                        \myframe^{n-1,[0,...,p-1]}  \\
+                        \painting^{n-1,[0,...,p-1]} \\
+                      \end{array}\right)
+              .\,                                                           \\
+              \Pi q\leq n.\,\Pi \omega.\,\myframe^{n,[0,...,p]}
+              \left(\begin{array}{l}
+                        \myframe^{n-1,[0,...,p-1]}  \\
+                        \painting^{n-1,[0,...,p-1]} \\
+                      \end{array}\right)(\restrframe^{n,[0,...,p-1]}) \\
+            \end{array} \\
+            \myframe^{n,[0,...,p]}                                     &
+            \multicolumn{3}{l}{
+              \left(\begin{array}{l}
+                        \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}                               \\
+                        \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]}) \\
+                      \end{array}\right) : \restrframetype^{n,[0,...,p-1]}
+                        \left(\begin{array}{l}
+                          \myframe^{n-1,[0,...,p-1]}  \\
+                          \painting^{n-1,[0,...,p-1]} \\
+                        \end{array}\right) \rightarrow \myframetype^{n-1,[0,...,p]}
+            }                                                                                         \\
+            \myframe^{n,[0]}                                           &
+            \left(\begin{array}{l}
+                      \star \\
+                      \star \\
+                    \end{array}\right)                                     & \defeq & \star \mapsto (\star,unit)      \\
+            \myframe^{n,[0,...,p+1]}                                   &
+            \left(\begin{array}{l}
+                      \myframe^{n-1,[0,...,p]}  \\
+                      \painting^{n-1,[0,...,p]} \\
+                    \end{array}\right) & \defeq &
+            \restrframe^{n,[0,...,p]} \mapsto
+            \left(\begin{array}{l}
+                      \myframe^{n,[0,...,p]}
+                      \left(\begin{array}{l}
+                          \myframe^{n-1,[0,...,p-1]}  \\
+                          \painting^{n-1,[0,...,p-1]} \\
+                        \end{array}\right)(\restrframe^{n,[0,...,p-1]}), \\
+                      \Sigma d:\myframe^{n,[0,...,p]}
+                      \left(\begin{array}{l}
+                          \myframe^{n-1,[0,...,p-1]}  \\
+                          \painting^{n-1,[0,...,p-1]} \\
+                        \end{array}\right)(\restrframe^{n,[0,...,p-1]}).\, \\
+                      \quad \Pi\omega.\,\painting^{n-1,p}(\restrframe^{n,p}(d))     \\
+                    \end{array}\right)                    \\
+          \end{array}
+        $$
+
+        Or, even, using an alternative notation, as:
+        $$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
+          \begin{array}{llcl}
+            \restrframetype^{n,<p}                            &
+            \multicolumn{3}{l}{
+              \left(\begin{array}{l}
+                        \myframe^{n-1,<p}:\myframetype^{n-1,<p}                               \\
+                        \painting^{n-1,<p}:\paintingtype^{n-1,<p}(\myframe^{n-1,<p}) \\
+                      \end{array}\right) : Type_{l}
+            }                                                                                         \\
+            \restrframetype^{n,<0}                                     &
+            \left(\begin{array}{l}
+                      \star \\
+                      \star \\
+                    \end{array}\right)                                     & \defeq &
+            unit                                                                                      \\
+            \restrframetype^{n,\leq p}                              &
+            \left(\begin{array}{l}
+                      \myframe^{n-1,\leq p}  \\
+                      \painting^{n-1,\leq p} \\
+                    \end{array}\right) & \defeq &
+            \begin{array}{l}
+              \Sigma \restrframe^{n,<p}                            \\
+              \quad:\restrframetype^{n,<p}
+              \left(\begin{array}{l}
+                        \myframe^{n-1,<p}  \\
+                        \painting^{n-1,<p} \\
+                      \end{array}\right)
+              .\,                                                           \\
+              \Pi q\leq n.\,\Pi \omega.\,\myframe^{n,\leq p}
+              \left(\begin{array}{l}
+                        \myframe^{n-1,<p}  \\
+                        \painting^{n-1,<p} \\
+                      \end{array}\right)(\restrframe^{n,<p}) \\
+            \end{array} \\
+            \myframe^{n,\leq p}                                     &
+            \multicolumn{3}{l}{
+              \left(\begin{array}{l}
+                        \myframe^{n-1,<p}:\myframetype^{n-1,<p}                               \\
+                        \painting^{n-1,<p}:\paintingtype^{n-1,<p}(\myframe^{n-1,<p}) \\
+                      \end{array}\right) : \restrframetype^{n,<p}
+                        \left(\begin{array}{l}
+                          \myframe^{n-1,<p}  \\
+                          \painting^{n-1,<p} \\
+                        \end{array}\right) \rightarrow \myframetype^{n-1,\leq p}
+            }                                                                                         \\
+            \myframe^{n,\leq 0}                                           &
+            \left(\begin{array}{l}
+                      \star \\
+                      \star \\
+                    \end{array}\right)                                     & \defeq & \star \mapsto (\star,unit)      \\
+            \myframe^{n,\leq p+1}                                   &
+            \left(\begin{array}{l}
+                      \myframe^{n-1,\leq p}  \\
+                      \painting^{n-1,\leq p} \\
+                    \end{array}\right) & \defeq &
+            \restrframe^{n,\leq p} \mapsto
+            \left(\begin{array}{l}
+                      \myframe^{n,\leq p}
+                      \left(\begin{array}{l}
+                          \myframe^{n-1,<p}  \\
+                          \painting^{n-1,<p} \\
+                        \end{array}\right)(\restrframe^{n,<p}), \\
+                      \Sigma d:\myframe^{n,\leq p}
+                      \left(\begin{array}{l}
+                          \myframe^{n-1,<p}  \\
+                          \painting^{n-1,<p} \\
+                        \end{array}\right)(\restrframe^{n,<p}).\, \\
+                      \quad \Pi\omega.\,\painting^{n-1,p}(\restrframe^{n,p}(d))     \\
+                    \end{array}\right)                    \\
+          \end{array}
+        $$
+
         TODO: discuss $p\leq q \leq n$ vs $0 \leq q \leq n-p$.
@@
         \end{center}
+
+To define $\painting$ formally, we need to define $\myframe^{n,[p,...,n]}$, $\painting^{n,[p,...,n]}$ and $\restrframe^{n,[p,...,n]}$:
+
+        $$
+\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
+          \begin{array}{llcl}
+            \myframetype^{n,[p,...,n]}  &                                                     & :      & Type_{l+1}                                                               \\
+            \myframetype^{n,[]}         &                                                     & \defeq & unit                                                                     \\
+            \myframetype^{n,[p,...,n]}  &                                                     & \defeq & Type_l \times \myframetype^{n,[p+1,...,n-1]}                               \\
+            \\
+            \paintingtype^{n,[p,...,n]} & (\myframe^{n,[p,...,n]}:\myframetype^{n,[p,...,n]}) & :      & Type_{l+1}                                                               \\
+            \paintingtype^{n,[]}        & \star                                               & \defeq & unit                                                                     \\
+            \paintingtype^{n,[p,...,n]}_{p<n} & (\myframe^{n,[p,...,n]})                            & \defeq & (\myframe^{n,p} \rightarrow Type_l) \times \paintingtype^{n,[p+1,...,n]}(\myframe^{n,[p+1,...,n]}) \\
+            \\
+            \restrframetype^{n,[p,...,n]} &
+            \multicolumn{3}{l}{
+              \left(\begin{array}{l}
+                        \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}                               \\
+                        \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]}) \\
+                        \myframe^{n-1,[p,...,n-1]}:\myframetype^{n-1,[p,...,n-1]}                                     \\
+                        \painting^{n-1,[p,...,n-1]}:\paintingtype^{n-1,[p,...,n-1]}(\myframe^{n-1,[p,...,n-1]})           \\
+                        \restrframe^{n,[0,...,p-1]}:\restrframetype^{n,[0,...,p-1]}
+                                \left(\begin{array}{l}
+                                    \myframe^{n-1,[0,...,p-1]}  \\
+                                    \painting^{n-1,[0,...,p-1]} \\
+                                  \end{array}\right) \\
+                      \end{array}\right) : Type_{l}
+            }    \\
+            \restrframetype^{n,[]}        &
+            \left(\begin{array}{l}
+                      \myframe^{n-1,[0,...,n-1]} \\
+                      \painting^{n-1,[0,...,n-1]} \\
+                      \star \\
+                      \star \\
+                      \restrpainting^{n,[0,...,n-1]} \\
+                    \end{array}\right)                                     & \defeq & unit \\
+            \restrframetype^{n,[p,...,n-1]} &
+                                \left(\begin{array}{l}
+                                    \myframe^{n-1,[0,...,p-1]}  \\
+                                    \painting^{n-1,[0,...,p-1]} \\
+                                    \myframe^{n-1,[p,...,n-1]}  \\
+                                    \painting^{n-1,[p,...,n-1]} \\
+                                    \restrframe^{n,[0,...,p-1]} \\
+                                  \end{array}\right)
+            & \defeq & 
+                                \begin{array}{l}
+                                  \myframe^{n,p}
+                                  \left(\begin{array}{l}
+                                    \myframe^{n-1,[0,...,p-1]}  \\
+                                    \painting^{n-1,[0,...,p-1]} \\
+                                    \restrframe^{n,[0,...,p-1]} \\
+                                  \end{array}\right)
+                                \rightarrow \myframe^{n-1,p}\\
+                                \times \\
+                                \restrframetype^{n,[p+1,...,n]}
+                                \left(\begin{array}{l}
+                                    \myframe^{n-1,[0,...,p]}  \\
+                                    \painting^{n-1,[0,...,p]} \\
+                                    \myframe^{n-1,[p+1,...,n-1]}  \\
+                                    \painting^{n-1,[p+1,...,n-1]} \\
+                                    \restrframe^{n,[0,...,p]} \\
+                                  \end{array}\right)
+                                \end{array}
+          \end{array}
+        $$
+
+        This allows to define $\painting^{n,p}$ formally:
+        $$
+          \begin{array}{llcl}
+            \painting^{n,p}                                     &
+            \multicolumn{3}{l}{
+              \left(\begin{array}{l}
+                        \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}                               \\
+                        \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]}) \\
+                        \myframe^{n-1,[p,...,n-1]}:\myframetype^{n-1,[p,...,n-1]}                                     \\
+                        \painting^{n-1,[p,...,n-1]}:\paintingtype^{n-1,[p,...,n-1]}(\myframe^{n-1,[p,...,n-1]})           \\
+                        \restrframe^{n,[0,...,p-1]}:\restrframetype^{n,[0,...,p-1]}
+                                \left(\begin{array}{l}
+                                    \myframe^{n-1,[0,...,p-1]}  \\
+                                    \painting^{n-1,[0,...,p-1]} \\
+                                  \end{array}\right) \\
+                        \restrframe^{n,[p,...,n-1]}:\restrframetype^{n,[p,...,n-1]}
+                                \left(\begin{array}{l}
+                                    \myframe^{n-1,[0,...,p-1]}  \\
+                                    \painting^{n-1,[0,...,p-1]} \\
+                                    \myframe^{n-1,[p,...,n-2]}  \\
+                                    \painting^{n-1,[p,...,n-2]} \\
+                                    \restrframe^{n,[0,...,p-1]} \\
+                                  \end{array}\right) \\
+                        E:\myframe^{n-1,n-1}\rightarrow Type_l\\
+                      \end{array}\right) : \myframe^{n-1,n-1}\rightarrow Type_l
+            }    \\
+            \painting^{n,n}                                           &
+            \left(\begin{array}{l}
+                      \myframe^{n-1,[0,...,n-1]} \\
+                      \painting^{n-1,[0,...,n-1]} \\
+                      \star \\
+                      \star \\
+                      \restrpainting^{n,[0,...,n-1]} \\
+                      \star \\
+                      E \\
+                    \end{array}\right)                                     & \defeq & E \\
+            \painting^{n,p}_{p<n}                                   &
+                                \left(\begin{array}{l}
+                                    \myframe^{n-1,[0,...,p-1]}  \\
+                                    \painting^{n-1,[0,...,p-1]} \\
+                                    \myframe^{n-1,[p,...,n-1]}  \\
+                                    \painting^{n-1,[p,...,n-1]} \\
+                                    \restrframe^{n,[0,...,p-1]} \\
+                                    \restrframe^{n,[p,...,n-1]} \\
+                                    E \\
+                                  \end{array}\right) & \defeq & d \mapsto
+            \left(\begin{array}{l}
+              \Sigma l:(\Pi q\leq n.\,\Pi \omega.\
+                      \painting^{n-1,[0,...,p]}(\restrframe^{n,p}(d))). \\
+                      \painting^{n,[p+1,...,n-1]}
+                      \left(\begin{array}{l}
+                                    \myframe^{n-1,[0,...,p]}  \\
+                                    \painting^{n-1,[0,...,p]} \\
+                                    \myframe^{n-1,[p+1,...,n-1]}  \\
+                                    \painting^{n-1,[p+1,...,n-1]} \\
+                                    \restrframe^{n,[0,...,p]} \\
+                                    \restrframe^{n,[p+1,...,n-1]} \\
+                                    E \\
+                        \end{array}\right)(d,l) \\
+                    \end{array}\right)                    \\
+          \end{array}
+          $$
+
+          From which we can deduce $\painting^{n,[0,...,p]}$ by recursion on $p$.
 
@@
         \end{center}
-\end{enumerate}
+\end{itemize}
 
 Looking at the dependencies in the reverse order, it is thus enough:
-\begin{enumerate}
+\begin{itemize}
   \item To assume $\myframe^{n-2,k}$ and $\painting^{n-2,k}$ for all $k< p$
@@
         \end{tiny}
-\end{enumerate}
+\end{itemize}
 

### 2025-09-28 paper/paper.tex
Moving a paragraph to prevent a big overflow (even if still a small underflow)
paper: start new paper

--- 2025-07-20 paper/paper.tex
@@
-\documentclass{art.cls/art}
+\documentclass{msc}
 
-\usepackage{environ, multirow, tabularx, caption, booktabs, makecell, colortbl, minted, art.cls/joinargs}
-\setminted[]{fontfamily=lmtt}
+\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, lmodern, mathpazo, anyfontsize, xargs, environ, multirow, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
 \usepackage[prefix=bonak]{art.cls/xkeymask}
@@
 \newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
-\newcommand{\SSSet}{\ensuremath{\Set_{\DeltaPlus}}}
 \newcommand{\Cube}{\ensuremath{\boldsymbol{{\square}}}}
-\newcommand{\CSet}{\ensuremath{\Set_{\Cube}}}
+\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}
 
 % Universe, referred to as U
-\renewcommandx{\U}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
+\newcommandx{\U}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HSet}}_{#1}}}
 \newcommandx{\HGpd}[1][1=]{\ensuremath{\mathsf{\color{spanish-blue}{HGpd}}_{#1}}}
@@
 
+\newcommand{\frametype}{\ensuremath{\mathsf{frametype}}}
+\newcommand{\paintingtype}{\ensuremath{\mathsf{paintingtype}}}
+\newcommand{\restrftype}{\ensuremath{\mathsf{restrftype}}}
+
+\newcommand{\udensdash}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {$#1$};
+        \draw[densely dashed] (todotted.south west) -- (todotted.south east);
+    }%
+}%
+
 % These are renewed in tables, but let's define them now for in-document
@@
 \newcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
-\newcommandx{\restrc}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
+\newcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
 \newcommandx{\cohf}{\coh{frame}[][][][][][][][]}
@@
 % Caption setup
-\DeclareCaptionFormat{plain}{#1: #3}
+\DeclareCaptionFormat{plain}{#1#3}
 \captionsetup{font=footnotesize,labelfont=bf}
@@
 \NewEnviron{eqntable}[1]{
-  \begin{table}[h]
-  \small
+  \fontsize{7.2}{9}\selectfont
   \begin{tabularx}{0.94\linewidth}{
@@
 
-% Set the entire document to gray65, and pick certain colors
-\color{gray65}
+% Double-spacing
+% \linespread{2}
 
 \begin{document}
-\title{A parametricity-based formalization of semi-simplicial and semi-cubical sets}
-\date{}
-\author{
-  \textcolor{gray80}{Hugo Herbelin} \\
-  \itshape \textcolor{gray80}{Université Paris-Cité, Inria, CNRS, IRIF, Paris} \\
-  \ttfamily \textcolor{gray80}{Hugo.Herbelin@inria.fr}
-  \and
-  \textcolor{gray80}{Ramkumar Ramachandra} \\
-  \itshape \textcolor{gray80}{Université Paris-Cité (2020-2022), Unaffiliated} \\
-  \ttfamily \textcolor{gray80}{r@artagnon.com}
-}
+\title{On the specific recursive structure of iterated parametricity}
+\begin{authgrp}
+  \author{Hugo Herbelin}
+  \affiliation{Université Paris Cité, Inria, CNRS, IRIF, Paris
+    \email{Hugo.Herbelin@inria.fr}}
+  \author{Ramkumar Ramachandra}
+  \affiliation{Unaffiliated \email{r@artagnon.com}}
+\end{authgrp}
+\begin{abstract}
+  In a previous paper, we gave equations describing the construction of semi-simplicial and semi-cubical sets via iterated parametricity.
+The construction was formalised in the Rocq (formerly known as Coq) proof assistant building $n$-truncated sets using an induction on a large structure embedding equational reasoning.
+
+  The current paper describes a new and lighter presentation of the construction where equational reasoning is replaced by definition.
+Being lighter, it can now be described in full details, closely following the corresponding new machine-checked formalisation.
+\end{abstract}
 \maketitle
-\begin{abstract}
-  Semi-simplicial and semi-cubical sets are commonly defined as presheaves over respectively, the semi-simplex or semi-cube category.
-Homotopy Type Theory then popularized an alternative definition, where the set of $n$-simplices or $n$-cubes are instead regrouped into the families of the fibres over their faces, leading to a characterization we call \emph{indexed}.
-Moreover, it is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds parametricity, respectively in its unary and binary variants.
-We exploit this correspondence to develop an original uniform indexed definition of both augmented semi-simplicial and semi-cubical sets, and fully formalize it in Coq.
-\end{abstract}
+\vspace{-2em} % Remove space after abstract
 
 \section{Introduction}
-\subsection*{Fibred vs indexed presentation of semi-simplicial and semi-cubical sets}
 A family of sets can commonly be represented in two ways: as a family properly speaking, indexed by the elements of a given set $S$, or as a set $T$ together with a map from $T$ to $S$, which specifies for each element of $T$ its dependency on $S$.
@@
 In the latter case, the set associated to a given element of $S$ is the fibre of this element, so we call it a \emph{fibred} presentation.
-The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\cite{hottbook} as the fibred/indexed equivalence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family equivalence and unbundled/bundled equivalence.
+The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\citep{hottbook} as the fibred/indexed equivalence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family equivalence and unbundled/bundled equivalence.
 The fibred/indexed nomenclature echoes the Grothendieck construction of fibred categories from indexed categories.
-The most elementary instance of the equivalence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'', and its proof requires univalence~\cite{hottbook}.}.
+The most elementary instance of the equivalence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'', and its proof requires univalence~\citep{hottbook}.}.
 \begin{equation*}
@@
 A \emph{presheaf} on an category is a family of sets indexed by the object of the category with maps indexed by the morphisms.
-As such, it lives on the indexed side of the equivalence, contrasting with the fibred side, where we have \emph{discrete Grothendieck fibrations}~\cite{LoregianRiehl20}.
+As such, it lives on the indexed side of the equivalence, contrasting with the fibred side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
 However, there are situations where a presheaf can also be seen as living on the fibred side of the equivalence.
 This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.
-Let us consider, for instance, the case of a semi-cubical set~\cite{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
+Let us consider, for instance, the case of a semi-cubical set~\citep{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
 Formulated in type theory, the corresponding presheaf definition of a semi-cubical set prescribes a family of sets and face maps between them as follows.
@@
 
-\subsection*{Reynolds parametricity and its unary and binary variants}
-In the context of functional programming, Reynolds parametricity~\cite{reynolds83} interprets types as relations characterizing the observational behaviour of programs of this type.
-More generally, families over a product of sets, or \emph{correspondences}, can be used in place of relations.
-Parametricity can then be iterated, and relying on the fibred presentation of correspondences as spans, it has been noted that iterated Reynolds parametricity has the structure of a cubical set~\cite{altenkirch15,moulin16,johann17,moeneclaey21,moeneclaey22phd}.
-We obtain a \emph{unary} variant of Reynolds \emph{binary} parametricity by using predicates or families instead of relations or correspondences, and this is a form of realizability~\cite{bernardy12,lasson12,moulin16}.
-Cubical set models which differ only by the arity one~\cite{bernardy15} or two~\cite{bezem13} were introduced, and this led to a general notion of affine $\nu$-ary cubes in \cite{nuytsdevriese24}.
-In parallel, it has been noted that iterated unary parametricity has the structure of an augmented simplicial set\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch.}.
-This suggests that the definition of augmented semi-simplicial sets and semi-cubical sets can in turn be seen as particular instances of the restriction of Nuyts-Devriese's $\nu$-ary cubes to only faces, which we call $\nu$-sets, of presheaves over a $\nu$-semi-shape category made of words of some cardinal $\nu+1$, where $\nu=1$ gives augmented semi-simplicial sets and $\nu=2$ gives semi-cubical sets.
-
-\subsection*{Contribution}
-The main contribution of the paper is to describe the details of a recipe that uniformly characterizes unary and binary iterated parametricity in indexed form, and to derive from it a new indexed presentation, called indexed \emph{$\nu$-sets}, of augmented semi-simplicial and semi-cubical sets.
-
-Our work is a step in the direction of the program initiated in \cite{altenkirch15} to develop parametricity-based models of parametric type theory~\cite{bernardy15,nuyts17,cavallo19} and cubical type theory~\cite{bezem13,cohen16,angiuli21}, which are closer to the syntax of type theory, and are likely to better reflect the definitional properties of type theory than presheaf-based cubical sets would.
-For example, consider the loss of definitional properties when interpreting ``indexed'' dependent types of type theory as ``fibrations'' in models such as locally cartesian closed categories~\cite{curien14}.
-
-Our construction has the unique property of reflecting the structure of parametricity and of yielding both augmented semi-simplicial and semi-cubical sets from the same construction.
-The approach taken in \cite{part15} and \cite{altenkirch16} takes benefit of the definitional compositionality of increasing injective maps, but we do not see how they could be generalized to yield semi-cubical sets.
-
-Our mechanization can be found at \href{https://github.com/artagnon/bonak}{github.com/artagnon/bonak}.
-The construction was conceived in Summer 2019, and the mechanization began in late 2019.
-A sketch of the construction was presented at the 2020 HoTT-UF workshop, and the completion of the mechanization was reported at the TYPES 2022 conference.
-
-\section{Semi-simplicial and semi-cubical sets\label{sec:nu}}
-In this section, we generalize semi-simplicial and semi-cubical sets to $\nu$-sets, subsuming the earlier definitions.
-We start with some introductory material on semi-simplicial and semi-cubical sets.
-
-\subsection*{Augmented semi-simplicial sets}
-Augmented semi-simplicial sets are defined similarly to semi-simplicial sets, except that the connected components are additionally dependent on a ``colour''.
-Conversely, semi-simplicial sets can be seen as augmented semi-simplicial sets over the singleton set of a fixed colour.
-Let us associate dimension $-1$ to colours; then, points are dimension $0$, lines are dimension $1$, and so on.
-
-Ordinary semi-simplicial sets are presheaves over the semi-simplex category.
-Augmented semi-simplicial sets are presheaves over \DeltaPlus.
-There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that can be extended to semi-cubical sets in a straightforward manner.
-In particular, we start numbering objects from $0$ instead of $-1$ so that there is a shift by one compared to the standard numbering of augmented semi-simplicial sets.
-
-\begin{notation}[Finite sequences]
-  We denote finite sequences by $i_1 \ldots i_n$ for $i_j$ ranging over some domain. The empty sequence is written $\epsilon$.
-\end{notation}
-
-\begin{definition}[$\DeltaPlus$]
-  The definition of $\DeltaPlus$ is shown below.
-Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than or equal to that of $g$.
-It can be shown that composition is associative and that $\id$ is neutral.
-  \begin{align*}
-    \Obj_{\DeltaPlus}       & := \Nat                                                                         \\
-    \Hom_{\DeltaPlus}(p, n) & := \{l \in \{0, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\}          \\
-    g \circ f               & :=
-    \begin{cases}
-      f                & \text{if $g = \epsilon$}                                           \\
-      0\,(g' \circ f)  & \text{if $g = 0\,g'$}                                              \\
-      a\,(g' \circ f') & \text{if $g = \kstar\,g'$, $f = a\,f'$, where $a = 0$ or $\kstar$} \\
-    \end{cases}                     \\
-    \id                     & := \kstar \ldots \kstar \text{ $n$ times for $\id \in \Hom_{\DeltaPlus}(n, n)$}
-  \end{align*}
-\end{definition}
-
-\begin{definition}[$\SSSet$]
-  We define the category of augmented semi-simplicial sets as the functor category:
+\section{The recursive structure of iterated parametricity}
+Iterated parametricity (in indexed form) produces a family of type
+families of the following form:
 \begin{equation*}
-    \SSSet := \Set^{\DeltaPlus^{\mathsf{op}}}
-  \end{equation*}
-\end{definition}
-
-To provide examples, we define the standard augmented $n$-semi-simplex, taking into account the shift by one in the numbering.
-
-\begin{definition}[$\DeltaPlus^n$]
-  The standard augmented $(n-1)$-semi-simplex $\DeltaPlus^{n-1}$ is defined as the Yoneda embedding of $n \in \Obj(\DeltaPlus)$:
-  \begin{align*}
-    \DeltaPlus^{n-1}    & : \SSSet                   \\
-    \DeltaPlus^{n-1}(p) & := \Hom(p, n)              \\
-    \DeltaPlus^{n-1}(f) & := \lambda g .\, g \circ f
-  \end{align*}
-\end{definition}
-
-The standard augmented $(-1)$-semi-simplex is a singleton made of one colour (in this case, black).
-Standard augmented $n$-semi-simplices for $n \geq 0$ have a geometric interpretation, and we illustrate them for dimensions $0$, $1$, and $2$.
-
-\begin{example}[$\DeltaPlus^0$]
-  The standard augmented $0$-semi-simplex can be pictured as a point, coloured black, corresponding to the unique morphism in $\Hom(0, 1)$.
-This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$.
-  \begin{equation*}
-    \begin{tikzcd}
-      \kstar
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-\begin{example}[$\DeltaPlus^1$]
-  The standard augmented $1$-semi-simplex is drawn as two points, given by $\Hom(1, 2)$, along with a line connecting them, given by $\Hom(2, 2)$.
-We use black to denote the unique morphisms in $\Hom(0, 1)$ and $\Hom(0, 2)$.
-  \begin{equation*}
-    \begin{tikzcd}
-      \kstar0 \arrow[r, dash, "\kstar\kstar"] & 0\kstar
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-\begin{example}[$\DeltaPlus^2$]
-  $\DeltaPlus^2$ is drawn as three points, given by $\Hom(1, 3)$, three lines connecting them, given by $\Hom(2, 3)$, and a triangular filler given by $\Hom(3, 3)$.
-  \begin{equation*}
-    \begin{tikzcd}
-      & |[alias=F]|00\kstar \arrow[ddr, dash, "0\kstar\kstar"] & \\\\
-      \kstar00 \arrow[rr, dash, "\kstar\kstar0"{name=T, below}]\arrow[uur, dash, "\kstar0\kstar"] && 0\kstar0 \\
-      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar\kstar" description]
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base, and gluing on top of it another copy lifted by one dimension.
-In the second copy, the colour becomes an extra point, the points become lines connecting the points of the base to the extra point, and so on.
-In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by $\kstar$.
-Note that the components may be oriented by letting each $n$-dimensional component point to the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ of the $n$-dimensional component with $0$.
-
-\subsection*{Semi-cubical sets}
-Semi-cubical sets are defined like augmented semi-simplicial sets except that $\DeltaPlus$ is replaced by $\Cube$ in which we take sequences of $L$, $R$ and $\kstar$, instead of sequences of $0$ and $\kstar$.
-
-\begin{definition}[\Cube]
-  The definition of $\Cube$ is shown below. The symbols $L$ and $R$ indicate opposite faces of a cube.
-
-  \begin{align*}
-    \Obj_{\Cube}       & := \Nat                                                                   \\
-    \Hom_{\Cube}(p, n) & := \{l \in \{L, R, \kstar\}^n \mid \text{number of $\kstar$ in $l = p$}\} \\
-    g \circ f          & :=
-    \begin{cases}
-      f                & \text{if $g = \epsilon$}                                                 \\
-      a\,(g' \circ f)  & \text{if $g = a\,g'$}, \text{where $a = L$ or $R$}                       \\
-      a\,(g' \circ f') & \text{if $g = \kstar\,g'$, $f = a\,f'$, where $a = L$, $R$, or $\kstar$} \\
-    \end{cases}    \\
-    \id                & := \kstar \ldots \kstar \text{ $n$ times}
-  \end{align*}
-
-  Again, if $g \circ f$ is well-defined, then the length of $f$ is less than or equal to that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
-\end{definition}
-
-\begin{definition}[\CSet]
-  We define the category of semi-cubical sets as the functor category:
-  \begin{equation*}
-    \CSet := \Set^{\op{\Cube}}
-  \end{equation*}
-\end{definition}
-
-\begin{definition}[$\Cube^n$]
-  The standard semi-cube $\Cube^n$ is defined as the Yoneda embedding of $n \in \Obj(\Cube)$:
-  \begin{align*}
-    \Cube^n    & : \CSet                    \\
-    \Cube^n(p) & := \Hom(p, n)              \\
-    \Cube^n(f) & := \lambda g .\, g \circ f
-  \end{align*}
-\end{definition}
-
-Standard $n$-semi-cubes have a geometric interpretation, which we illustrate for dimensions $0$, $1$, and $2$.
-
-\begin{example}[$\Cube^0$]
-  $\Cube^0$ is $\Hom(0, 0)$, or the singleton set of the empty sequence:
-  \begin{equation*}
-    \begin{tikzcd}
-      \epsilon
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-\begin{example}[$\Cube^1$]
-  $\Cube^1$ consists of two points, given by $\Hom(0, 1)$, and a line, given by $\Hom(1, 1)$.
-  \begin{equation*}
-    \begin{tikzcd}
-      L \arrow[r, "\kstar", dash] & R
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-\begin{example}[$\Cube^2$]
-  $\Cube^2$ consists of four points, given by $\Hom(0, 2)$, four lines connecting the four points, given by $\Hom(1, 2)$, and a filler, given by $\Hom(2, 2)$:
-  \begin{equation*}
-    \begin{tikzcd}
-      LR \arrow[r, dash, "\kstar R"{name=F}] \arrow[d, dash, "L\kstar" left] & RR \arrow[d, dash, "R\kstar"] \\
-      LL \arrow[r, dash, "\kstar L"{name=T, below}] & RL \\
-      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar" description]
-    \end{tikzcd}
-  \end{equation*}
-\end{example}
-
-More generally, the standard $(n + 1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them on their border by a prism obtained as a third copy stretched in the new dimension.
-The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the prism is obtained by postfixing with $\kstar$.
-Note that the components can be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$, to the one obtained by replacing the leftmost $\kstar$ with $R$.
-
-\subsection*{\texorpdfstring{$\nu$}{ν}-sets}
-Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets obtained by building on an arbitrary alphabet $\nu$, so that the following holds:
-
-\begin{center}
-  \begin{tabularx}{\linewidth}{X|X|X}
-    \toprule
-    Cardinal of $\nu$ & 1                              & 2                 \\
-    \graymidrule
-    Interpretation    & Augmented semi-simplicial sets & Semi-cubical sets \\
-    \bottomrule
-  \end{tabularx}
-\end{center}
-
-To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\hexagon$.
-
-\begin{definition}[$\hexagon$]
-  The definition of $\nu$-semi-shape category is shown below.
-Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than or equal to that of $g$.
-It can be shown that composition is associative and that $\id$ is neutral.
-  \begin{align*}
-    \Obj_{\hexagon}       & := \Nat                                                                          \\
-    \Hom_{\hexagon}(p, n) & := \{l \in (\nu \sqcup \{\kstar\})^n \mid \text{number of $\kstar$ in $l = p$}\} \\
-    g \circ f             & :=
-    \begin{cases}
-      f                & \text{if $g = \epsilon$}                                                   \\
-      a\,(g' \circ f)  & \text{if $g = a\,g'$}, \text{where $a \in \nu$}                            \\
-      a\,(g' \circ f') & \text{if $g = \kstar\,g'$, $f = a\,f'$, where $a \in \nu$ or $a = \kstar$} \\
-    \end{cases}            \\
-    \id                   & := \kstar \ldots \kstar \text{ $n$ times for $\id \in \Hom_{\hexagon}(n, n)$}
-  \end{align*}
-\end{definition}
-
-A $\nu$-set is thus a contravariant functor $\phi$ from the $\nu$-semi-shape category to $\Set$ and we call $n$-$\nu$-semi-shape an element of $\phi(n)$.
-As in the augmented semi-simplicial and semi-cubical cases, the standard $(n + 1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in the new dimension.
-We clarify in the next sections, how this process of construction is similar to the parametricity translation developed for functional programming~\cite{reynolds83} and more generally for type theory~\cite{bernardy10,bernardy11,atkey14,bernardy15}.
-
-\section{Type theory\label{sec:tt}}
-Martin-Löf's Type theory~(\cite{martinlof75,martinlof84}) is a logical formalism based on the notion of a \emph{type} rather than that of a \emph{set}.
-It can be seen as a foundation of mathematics alternative to set theory and is the core of several tools for the formalization of mathematics such as Agda, Coq and Lean.
-In type theory, propositions are types and proofs are programs.
-Type theory includes \emph{definitional equality}, by which all propositions and proofs are quotiented.
-
-Type theory is a flexible formalism supporting different models.
-Some models come from homotopy theory, and are based on simplicial sets or related structures~\cite{HofmannStreicher94,kapulkin21,BezemCoquandHuber13,cchm}: in these models, equality is interpreted as paths, and they support the univalence principle stating that equality of types mimics equivalence of types, leading to the development of Homotopy Type Theory~\cite{hottbook}.
-
-Types are organized in a hierarchy of universes written $\Type_m$ for $m$ a natural number.
-The main types in type theory are the type of dependent pairs, written $\Sigma a : A.\,B(a)$, the type of dependent functions, written $\Pi a : A.\,B(a)$, for $A$ a type and $B(a)$ a type dependent on the inhabitant $a$ of $A$, and the type of propositional equalities, written $t = u$.
-As a notation, the type of dependent pairs when $B$ is not dependent on $A$ is shortened into $A \times B$ and the type of dependent functions when $B$ is not dependent on $A$ is written $A \rightarrow B$.
-We assume our type theory to also include a distinguished singleton type, written $\unittype$, and with inhabitant $\unitpoint$, the type of boolean values, and the type of natural numbers.
-We write $\hd$ and $\tl$ the projections of dependent pairs, and $\refl$ for reflexivity.
-Logical propositions being types themselves, we use $\Pi$ to represent universal quantification and $\Sigma$ to represent existential quantification.
-We also assume that our type theory includes a coinductively-defined notion of dependent streams described in the Appendix.
-
-A type-theoretic notion of sets can be recovered in each universe as $\U[m]$, denoting the subtype of $\Type_m$ for which paths are degenerated, using Uniqueness of Identity Proofs (UIP).
-Technically, this is expressed as a structure equipping a domain $\Dom$ with the property $\UIP$:
-\begin{align*}
-  \Dom & : \Type_m                                  \\
-  \UIP & : \Pi x y: \Dom.\, \Pi p q: x = y.\, p = q
-\end{align*}
-
-In $\U[m]$, the following properties hold:
-\begin{enumerate}
-  \item UIP holds on the unit type, bool type, as well as all types of finite cardinal $\nu$.
-  \item UIP propagates to $\Sigma$-types.
-  \item UIP propagates to $\Pi$-types, with some additional functional extensionality axioms.
-\end{enumerate}
-
-By notation, $\Type$ and $\U$ mean $\Type_m$ and $\U[m]$ at some unspecified universe level $m$.
-
-We are also interested in \emph{extensional} type theory, a type theory with the following reflection rule, where $=$ is propositional equality in some type and $\equiv$ is definitional equality~\cite{martinlof84}:
-\begin{equation*}
-  \seqr{}{\Gamma \vdash p: t = u}{\Gamma \vdash t \equiv u}
-\end{equation*}
-
-Note that the reflection rule implies UIP so that $\U$ and $\Type$ are equivalent in extensional type theory.
-The rule also implies functional extensionality.
-Extensional type theory is logically equivalent to intensional type theory extended with UIP and functional extensionality~\cite{HofmannPhd}.
-
-\section{Relating to parametricity\label{sec:rel-param}}
-Recall from the introduction, the form taken by the indexed presentation of a semi-cubical set:
-\begin{equation*}
-  \begin{array}{lll}
-    X_0 & :               \U                                                                         \\
-    X_1 & :               X_0 \times X_0 \rightarrow \U                                              \\
-    X_2 & : \Pi a b c d.\, X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
+  \begin{array}{llr}
+    X_0 & :              & \U                                                                        \\
+    X_1 & :              & X_0 \times X_0 \rightarrow  \U                                            \\
+    X_2 & : \Pi a b c d. & X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
     \ldots
@@
 
-Here, the process of construction of the type of $X_1$ from that of $X_0$, and of the type of $X_2$ from that of $X_1$, is similar to iteratively applying a binary parametricity translation.
-The binary parametricity which we consider interprets a closed type $A$ by a family $A_\kstar$ over $A \times A$, and this can be seen as a graph whose vertices are in $A$.
-Each type constructor is associated with the construction of a graph.
-To start with, the type of types $\U$ is interpreted as the family of type of families ${\U}_\kstar$, which takes $A_L$ and $A_R$ in $\U$ and returns the type $A_L \times A_R \rightarrow \U$ of families over $A_L$ and $A_R$.
-Also, for $A$ interpreted by $A_\kstar$ and $B(a)$, for $a:A$, interpreted by $B_\kstar((a_L,a_R),a_\kstar)$ with $a_\kstar:A_\kstar(a_L,a_R)$, a dependent function type $\Pi a: A.\, B(a)$ is interpreted as the graph $(\Pi a: A.\, B(a))_\kstar$ that takes two functions $f_L$ and $f_R$ of type $\Pi a: A.\, B(a)$, and expresses that these functions map related arguments in $A$ to related arguments in $B$:
-\begin{equation*}
+Such family can be recursively described by the equations given on Table ?.
+
+The well-foundedness of the construction can be justified by the observation that:
+\begin{itemize}
+  \item Defining $\framep[n][p]$ for $p \leq n$ requires the definition
+        of $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing
+        dependency, as well as $\restrf[n][p-1]$, where
+        $\restrf[n][p-1]$ in turn depends in $\framep[n][p-1]$ for its
+        typing.
+
+        Moreover, $\framep[n][p]$ depends on $\framep[n][p-1]$, so these
+        dependencies are between the blocks of $\framep[n][k]$ for all
+        $k\leq p$, as well as $\framep[n-1][k]$, $\painting[n-1][k]$ and
+        $\restrf[n][k]$ for all $k\leq p-1$, which we respectively
+        abbreviate as $\framep[n][0,...,p]$,
+        $\framep[n-1][0,...,p-1]$, $\painting[n-1][0,...,p-1]$ and
+        $\restrf[n][0,...,p-1]$.
+
+        Also, $\restrf[n][p-1]$ depends on $n$.
+
+        Schematically, using dotted arrows for dependencies in
+        the type and plain arrows for dependencies in the definition, this
+        gives the following dependencies for $p\leq n$ fixed:
+        \begin{center}
+          \begin{tikzcd}
+            \framep[n][0,...,p] \arrow[d] \arrow[ddr]\\
+            \painting[n-1][0,...,p-1] \arrow[d, dotted] \\
+            \framep[n-1][0,...,p-1] &
+            \restrf[n][0,...,p-1] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[0,...,p-1]$}"', near start, shift right=2mm, hook']\\
+          \end{tikzcd}
+        \end{center}
+
+        In particular, the mutual dependency on one side of
+        $\framep[n][0,...,p-1]$ within the type of
+        $\restrf[n][0,...,p-1]$ and on the other side of
+        $\restrf[n][0,...,p-1]$ within the definition of
+        $\framep[n][0,...,p]$ requires to mutually define the type of
+        $\restrf[n][0,...,p-1]$ together with $\framep[n][p]$ (or
+        $\framep[n][0,...,p]$) as a function from
+        $\restrf[n][0,...,p-1]$.
+
+        To talk about sequences of $\framep$, $\painting$ or $\restrf$,
+        we need to specify their types. The type of $\restrf$ will be
+        defined mutually with $\framep$ of the same level, but the type of
+        $\framep$, $\painting$ can be defined in advance, the second one
+        being however dependent on the first one. In general, components of
+        such sequences will have a type dependent on the previous components
+        of the sequence, as it is the case for $\restrf$. So, the type of
+        a sequence of length $p$ will be expressed as a $n$-iterated
+        $\Sigma$-type. In the case of $\framep$ and $\painting$, there will
+        be however no dependency, so an ordinary product can be used. If
+        $\framep[n][0,...,p]$ is such a sequence of length $p+1$, we write
+        $\framep[n][0,...,p-1]$ for its immediate subsequence of length $p$
+        and $\framep[n][p]$ for its last component. We can now define the
+        types of sequences of $\framep$ and $\painting$ as follows:
+
+        $$
+          \begin{array}{llcl}
+            \frametype^{n,[0,...,p]}  &                                                     & :      & Type_{l+1}                                                               \\
+            \frametype^{n,[]}         &                                                     & \defeq & unit                                                                     \\
+            \frametype^{n,[0,...,p]}  &                                                     & \defeq & \frametype^{n,[0,...,p-1]} \times Type_l                               \\
+            \\
+            \paintingtype^{n,[0,...,p]} & (\framep[n][0,...,p]:\frametype^{n,[0,...,p]}) & :      & Type_{l+1}                                                               \\
+            \paintingtype^{n,[]}        & \star                                               & \defeq & unit                                                                     \\
+            \paintingtype^{n,[0,...,p]} & (\framep[n][0,...,p])                            & \defeq & \paintingtype^{n,[0,...,p-1]}(\framep[n][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
+          \end{array}
+        $$
+
+        Formally, this can be described as:
+        $$
+          \begin{array}{llcl}
+            \framep[n][0,...,p]                                     &
+            \multicolumn{3}{l}{
+              \left(\begin{array}{l}
+                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
+                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\
+                        \restrf[n][0,...,p-1]:\restrftype^{n,[0,...,p-1]}
+                                \left(\begin{array}{l}
+                                    \framep[n-1][0,...,p-1]  \\
+                                    \painting[n-1][0,...,p-1] \\
+                                  \end{array}\right)                             \\
+                      \end{array}\right) : \frametype^{n-1,[0,...,p]}
+            }                                                                                         \\
+            \framep[n][0]                                           &
+            \left(\begin{array}{l}
+                      \star \\
+                      \star \\
+                      \star \\
+                    \end{array}\right)                                     & \defeq & (\star,unit)      \\
+            \framep[n][0,...,p+1]                                   &
+            \left(\begin{array}{l}
+                      \framep[n-1][0,...,p]  \\
+                      \painting[n-1][0,...,p] \\
+                      \restrf[n][0,...,p] \\
+                    \end{array}\right) & \defeq &
+            \left(\begin{array}{l}
+                      \framep[n][0,...,p]
+                      \left(\begin{array}{l}
+                          \framep[n-1][0,...,p-1]  \\
+                          \painting[n-1][0,...,p-1] \\
+                          \restrf[n][0,...,p-1] \\
+                        \end{array}\right)     , \\
+                      \Sigma d:\framep[n][0,...,p]
+                      \left(\begin{array}{l}
+                          \framep[n-1][0,...,p-1]  \\
+                          \painting[n-1][0,...,p-1] \\
+                          \restrf[n][0,...,p-1] \\
+                        \end{array}\right).\, \\
+                      \quad \Pi\omega.\,\painting[n-1][p](\restrf[n][p](d))     \\
+                    \end{array}\right)                    \\
+            \restrftype^{n,[0,...,p-1]}                            &
+            \multicolumn{3}{l}{
+              \left(\begin{array}{l}
+                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
+                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\
+                      \end{array}\right) : Type_{l}
+            }                                                                                         \\
+            \restrftype^{n,[]}                                     &
+            \left(\begin{array}{l}
+                      \star \\
+                      \star \\
+                    \end{array}\right)                                     & \defeq &
+            unit                                                                                      \\
+            \restrftype^{n,[0,...,p]}                              &
+            \left(\begin{array}{l}
+                      \framep[n-1][0,...,p]  \\
+                      \painting[n-1][0,...,p] \\
+                    \end{array}\right) & \defeq &
             \begin{array}{l}
-    (\Pi a: A.\, B(a))_\kstar(f_L,f_R) \; \defeq \\
-    \multicolumn{1}{r}{\qquad\Pi (a_L,a_R): (A \times A).\, \Pi a_\kstar: (A_\kstar(a_L,a_R)\, B_\kstar((a_L,a_R),a_\kstar)(f_L(a_L),f_R(a_R)))}
+              \Sigma \restrf[n][0,...,p-1]                            \\
+              \quad:\restrftype^{n,[0,...,p-1]}
+              \left(\begin{array}{l}
+                        \framep[n-1][0,...,p-1]  \\
+                        \painting[n-1][0,...,p-1] \\
+                      \end{array}\right)
+              .\,                                                           \\
+              \Pi q\leq n.\,\Pi \omega.\,\framep[n][0,...,p]
+              \left(\begin{array}{l}
+                        \framep[n-1][0,...,p-1]  \\
+                        \painting[n-1][0,...,p-1] \\
+                        \restrf[n][0,...,p-1] \\
+                      \end{array}\right) \\
+            \end{array} \\
           \end{array}
-\end{equation*}
+        $$
+          \item Defining $\painting[n][p]$, in addition to the type dependency
+        in $\framep[n][p]$, requires the definition of
+        $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing
+        dependency, as well as $\restrf[n][p-1]$. Since
+        $\painting[n][p]$ also depends on $\painting[n][p+1]$ when $p<n$,
+        these dependencies are actually between $\painting[n][p,...,n]$,
+        $\painting[n-1][p,...,n-1]$, $\framep[n][p,...,n]$,
+        $\framep[n-1][p,...,n-1]$ and $\restrf[n][p,...,n]$. Also,
+        for the case $p=n$, this also requires the assumption of an
+        inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally,
+        $\framep[n][p,...,n]$, $\framep[n-1][p,...,n-1]$ and
+        $\restrf[n][p,...,n-1]$ respectively depend on the earlier
+        values $\framep[n][0,...,p-1]$, $\framep[n-1][0,...,p-1]$ and
+        $\restrf[n][0,...,p-1]$.  Below, we use dashed underline and
+        dashed arrows for dependencies in subconstructions, here in the
+        construction of $\framep$ at level $n-1$ and $\restrftype$ at
+        level $n$:
+        \begin{center}
+          \begin{tikzcd}
+            & & \painting[n][p,...,n] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
+            \udensdash{\framep}^{n,[0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
+            \udensdash{\framep}^{n,[p,...,n]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
+            \painting[n-1][0,...,p-1] \arrow[d, dotted] & &
+            \painting[n-1][p,...,n-1] \arrow[ll, dotted] \arrow[d, dotted] \\
+            \framep[n-1][0,...,p-1] &
+            \udensdash{\restrf}^{n,[0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
+            \framep[n-1][p,...,n-1] \arrow[ll, dotted, bend left=15] &
+            \udensdash{\restrf}^{n,[p,...,n-1]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
+          \end{tikzcd}
+        \end{center}
 
-Similarly, a product type $A \times B$ is interpreted as the graph $(A \times B)_\kstar$ that relates two tuples $(a_L,b_L)$ and $(a_R,b_R)$ in $A \times B$ as follows:
-\begin{align*}
-  (A \times B)_\kstar((a_L,b_L),(a_R,b_R)) \; \defeq \; A_\kstar(a_L,a_R) \times B_\kstar(b_L,b_R)
-\end{align*}
+To define $\painting$ formally, we need to define $\framep[n][p,...,n]$, $\painting[n][p,...,n]$ and $\restrf[n][p,...,n]$:
 
-In particular, for $X: \U$, applying our parametricity translation is about associating to $X$ an inhabitant $X_\kstar$ of ${\U}_\kstar(X,X)$ i.e.
-of $X \times X \rightarrow \U$.
-In turn, applying the translation again to $X_\kstar: X \times X \rightarrow \U$ is about associating to $X_\kstar$ an inhabitant $X_{\kstar\kstar}$ of $(X \times X \rightarrow \U)_\kstar(X_\kstar,X_\kstar)$ i.e.
-of:
-\begin{align*}
-  \Pi ((x_{LL},x_{LR}),(x_{RL},x_{RR})): ((X \times X) \times (X \times X)). \\
-  (X_\kstar(x_{LL},x_{LR}) \times X_\kstar(x_{RL},x_{RR})
-  \rightarrow X_\kstar(x_{LL}, x_{RL}) \times X_\kstar(x_{LR},x_{RR})  \rightarrow \U)
-\end{align*}
-which hints us at how the sequence $X_0$, $X_1$, $X_2$ can be seen as a sequence of inhabitants of the iteration of the composition of binary parametricity with the diagonal on types and type families, applied to an initial $X: \U$:
-\begin{equation*}
-  \begin{array}{lllll}
-    X_0 & \defeq & X                & : & \U                                             \\
-    X_1 & \defeq & X_\kstar         & : & {\U}_\kstar(X,X)                               \\
-    X_2 & \defeq & X_{\kstar\kstar} & : & ({\U}_\kstar(X,X))_{\kstar}(X_\kstar,X_\kstar) \\
-    \ldots
+        $$
+          \begin{array}{llcl}
+            \frametype^{n,[p,...,n]}  &                                                     & :      & Type_{l+1}                                                               \\
+            \frametype^{n,[]}         &                                                     & \defeq & unit                                                                     \\
+            \frametype^{n,[p,...,n]}  &                                                     & \defeq & Type_l \times \frametype^{n,[p+1,...,n-1]}                               \\
+            \\
+            \paintingtype^{n,[p,...,n]} & (\framep[n][p,...,n]:\frametype^{n,[p,...,n]}) & :      & Type_{l+1}                                                               \\
+            \paintingtype^{n,[]}        & \star                                               & \defeq & unit                                                                     \\
+            \paintingtype^{n,[p,...,n]}_{p<n} & (\framep[n][p,...,n])                            & \defeq & (\framep[n][p] \rightarrow Type_l) \times \paintingtype^{n,[p+1,...,n]}(\framep[n][p+1,...,n]) \\
+            \\
+            \restrftype^{n,[p,...,n]} &
+            \multicolumn{3}{l}{
+              \left(\begin{array}{l}
+                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
+                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\
+                        \framep[n-1][p,...,n-1]:\frametype^{n-1,[p,...,n-1]}                                     \\
+                        \painting[n-1][p,...,n-1]:\paintingtype^{n-1,[p,...,n-1]}(\framep[n-1][p,...,n-1])           \\
+                        \restrf[n][0,...,p-1]:\restrftype^{n,[0,...,p-1]}
+                                \left(\begin{array}{l}
+                                    \framep[n-1][0,...,p-1]  \\
+                                    \painting[n-1][0,...,p-1] \\
+                                  \end{array}\right) \\
+                      \end{array}\right) : Type_{l}
+            }    \\
+            \restrftype^{n,[]}        &
+            \left(\begin{array}{l}
+                      \framep[n-1][0,...,n-1] \\
+                      \painting[n-1][0,...,n-1] \\
+                      \star \\
+                      \star \\
+                      \restrp[n][0,...,n-1] \\
+                    \end{array}\right)                                     & \defeq & unit \\
+            \restrftype^{n,[p,...,n-1]} &
+                                \left(\begin{array}{l}
+                                    \framep[n-1][0,...,p-1]  \\
+                                    \painting[n-1][0,...,p-1] \\
+                                    \framep[n-1][p,...,n-1]  \\
+                                    \painting[n-1][p,...,n-1] \\
+                                    \restrf[n][0,...,p-1] \\
+                                  \end{array}\right)
+            & \defeq & 
+                                \begin{array}{l}
+                                  \framep[n][p]
+                                  \left(\begin{array}{l}
+                                    \framep[n-1][0,...,p-1]  \\
+                                    \painting[n-1][0,...,p-1] \\
+                                    \restrf[n][0,...,p-1] \\
+                                  \end{array}\right)
+                                \rightarrow \framep[n-1][p]\\
+                                \times \\
+                                \restrftype^{n,[p+1,...,n]}
+                                \left(\begin{array}{l}
+                                    \framep[n-1][0,...,p]  \\
+                                    \painting[n-1][0,...,p] \\
+                                    \framep[n-1][p+1,...,n-1]  \\
+                                    \painting[n-1][p+1,...,n-1] \\
+                                    \restrf[n][0,...,p] \\
+                                  \end{array}\right)
                                 \end{array}
-\end{equation*}
+          \end{array}
+        $$
 
-This tells us how the informal type given to $X_2$ in the previous section could be rephrased so that it comes as the instance of a general recipe characterizing the type of all $X_i$.
+        This allows to define $\painting[n][p]$ formally:
+        $$
+          \begin{array}{llcl}
+            \painting[n][p]                                     &
+            \multicolumn{3}{l}{
+              \left(\begin{array}{l}
+                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
+                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\
+                        \framep[n-1][p,...,n-1]:\frametype^{n-1,[p,...,n-1]}                                     \\
+                        \painting[n-1][p,...,n-1]:\paintingtype^{n-1,[p,...,n-1]}(\framep[n-1][p,...,n-1])           \\
+                        \restrf[n][0,...,p-1]:\restrftype^{n,[0,...,p-1]}
+                                \left(\begin{array}{l}
+                                    \framep[n-1][0,...,p-1]  \\
+                                    \painting[n-1][0,...,p-1] \\
+                                  \end{array}\right) \\
+                        \restrf[n][p,...,n-1]:\restrftype^{n,[p,...,n-1]}
+                                \left(\begin{array}{l}
+                                    \framep[n-1][0,...,p-1]  \\
+                                    \painting[n-1][0,...,p-1] \\
+                                    \framep[n-1][p,...,n-2]  \\
+                                    \painting[n-1][p,...,n-2] \\
+                                    \restrf[n][0,...,p-1] \\
+                                  \end{array}\right) \\
+                        E:\framep[n-1][n-1]\rightarrow Type_l\\
+                      \end{array}\right) : \framep[n-1][n-1]\rightarrow Type_l
+            }    \\
+            \painting[n][n]                                           &
+            \left(\begin{array}{l}
+                      \framep[n-1][0,...,n-1] \\
+                      \painting[n-1][0,...,n-1] \\
+                      \star \\
+                      \star \\
+                      \restrp[n][0,...,n-1] \\
+                      \star \\
+                      E \\
+                    \end{array}\right)                                     & \defeq & E \\
+            \painting[n][p](p<n)                                   &
+                                \left(\begin{array}{l}
+                                    \framep[n-1][0,...,p-1]  \\
+                                    \painting[n-1][0,...,p-1] \\
+                                    \framep[n-1][p,...,n-1]  \\
+                                    \painting[n-1][p,...,n-1] \\
+                                    \restrf[n][0,...,p-1] \\
+                                    \restrf[n][p,...,n-1] \\
+                                    E \\
+                                  \end{array}\right) & \defeq & d \mapsto
+            \left(\begin{array}{l}
+              \Sigma l:(\Pi q\leq n.\,\Pi \omega.\
+                      \painting[n-1][0,...,p](\restrf[n][p](d))). \\
+                      \painting[n][p+1,...,n-1]
+                      \left(\begin{array}{l}
+                                    \framep[n-1][0,...,p]  \\
+                                    \painting[n-1][0,...,p] \\
+                                    \framep[n-1][p+1,...,n-1]  \\
+                                    \painting[n-1][p+1,...,n-1] \\
+                                    \restrf[n][0,...,p] \\
+                                    \restrf[n][p+1,...,n-1] \\
+                                    E \\
+                        \end{array}\right)(d,l) \\
+                    \end{array}\right)                    \\
+          \end{array}
+          $$
 
-Notice, however, that the recipe obtained so far, $X_{n + 1}: ({S_n})_\kstar(X_n,X_n)$ for $X_n: S_n$, applies parametricity on the \emph{syntax} of the type of $X_n$.
-It does not directly yield a characterization of $S_n$ as a function from $n$.
-Reformulating the recipe as an explicit recursive construction, without requiring an interpretation of the syntax of types, is the main outcome of this work, together with the mechanization and the uniform treatment of augmented semi-simplicial and semi-cubical sets by means of the generalization to $\nu$-sets.
+          From which we can deduce $\painting[n][0,...,p]$ by recursion on $p$.
+
+        \end{itemize}
 
 \section{Our construction}
-In this section, we describe our parametricity-based construction of $\nu$-sets in indexed form at two levels of formality.
-
-Sections~\ref{sec:ett} and~\ref{sec:itt} describe the construction at an informal level of discourse:
-\begin{enumerate}
-  \item In~\ref{sec:ett}, we present it in informal extensional type theory where equational reasoning is left implicit, and we give an intuition for the construction in~\ref{sec:intuition}.
-  \item While reasoning in extensional type theory is similar to reasoning in set theory regarding how equality is handled, extensional type theory has two limitations.
-The first limitation is that it enforces the principle of Uniqueness of Identity Proofs and this is inconsistent with the Univalence principle, thus making it inexpressible in Homotopy Type Theory.
-The second limitation is that we want the construction to be formalizable in the Coq proof assistant whose underlying type theory is intensional.
-Section~\ref{sec:itt} thus rephrases the construction in (informal) intensional type theory.
-Since $\nu$-sets are $0$-truncated types, we compensate for the absence of UIP by assuming a ``local UIP'', requiring types to be \U.
-\end{enumerate}
-
-Sections~\ref{sec:wf},~\ref{sec:le}, and~\ref{sec:eqproperties} describe additional issues to be addressed in order to get a fully formal construction:
-\begin{enumerate}
-  \item The well-foundedness of the induction requires a special termination evidence which will be discussed in section~\ref{sec:wf}.
-  \item The construction is indexed over integers and holds under some constraints on the range of these integers.
-There is a standard formalization dilemma in this kind of situation: either the constraints on the range are embedded in the construction so that the construction makes sense only on the corresponding range, or the construction is made first on a more general domain than needed but restricted to a smaller domain at the time of use.
-We adopted the former approach, requiring the construction to be dependent on proofs of inequalities on natural numbers.
-We discuss how we deal with such dependencies in section~\ref{sec:le}.
-  \item A number of standard groupoid properties of equality as well as type isomorphisms have been left implicit in the informal definition. This is discussed in section~\ref{sec:eqproperties}.
-\end{enumerate}
-
-\subsection{The construction in informal type theory\label{sec:ett}}
 % Abbreviated tables in this section
@@
 \renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrp}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
 
@@
 
-Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets.
-
-Using the notations of Section~\ref{sec:tt}, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
+Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets: using the notations of Section~\ref{sec:tt}, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
 Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
@@
 A $\fullframe$ describes a boundary of a standard form (simplex, cube), which we decompose into $\layer$, and a $\painting$ corresponds to a filled frame.
-Notice that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table~\ref{tab:faces}, and this restriction operator is in turn defined using auxiliary definitions $\restrl$ and $\restrc$.
+Notice that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table~\ref{tab:faces}, and this restriction operator is in turn defined using auxiliary definitions $\restrl$ and $\restrp$.
 
@@
 More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be defined in one go by induction on $p$.
-Also, each of $\painting$, $\restrc$, and $\cohc$ is built by induction from $p$ to $n$.
+Also, each of $\painting$, $\restrp$, and $\cohc$ is built by induction from $p$ to $n$.
 The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but the converse dependency is only on lower $n$, so this is well-founded.
@@
 
-\subsection{Intuition for our formal construction\label{sec:intuition}}
-\renewcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}
-\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
-\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
-\renewcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
-\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
-\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
-\renewcommandx{\restrc}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
-\renewcommandx{\cohf}[1][1]{\coh{frame}[][][][][][#1][][]}
-\renewcommandx{\cohl}[1][1]{\coh{layer}[][][][][][#1][][]}
-\renewcommandx{\cohc}[1][1]{\coh{painting}[][][][][][#1][][]}
-\renewcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
-
-There is a $\fullframe$ for each dimension $n$, written $\fullframe[n]$, and every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$.
-Here, $\fullframe[n]$ is a ``telescope'' collecting all arguments of the type of $X_i$ in section~\ref{sec:rel-param} as a nesting of $\Sigma$-types.
-
-To illustrate how to recursively build $\fullframe[n]$, let us begin by setting $\fullframe[0] \defeq \unittype$, so that the type $\U$ given to $X_0$ in section~\ref{sec:rel-param} can be equivalently formulated as $\unittype \rightarrow \U$.
-Then, more generally, let each $\fullframe[n]$ consist of $n$ layers, written $\layer[n][p]$ with $p < n$, that we stack in order, starting from $\unittype$, and writing $\framep[n][p]$ for the $p$ first layers of a $\fullframe[n]$, so that $\fullframe[n]$ is $\framep[n][n]$.
-For instance, $X_1$ is made of one layer, so that it can be written as a $\Sigma$-type of an inhabitant of $\unittype$ and $\layer[1][0]$.
-Then, $X_2$ is similarly made of two layers.
-
-\begin{small}
-  \begin{equation*}
-    \begin{array}{ll}
-      X_0                                : \underbrace{\unittype}_{\framep[0][0]}                                                    \rightarrow \U \\
-      X_1                                : \underbrace{\Sigma \unitpoint: \unittype. \underbrace{\left(
-      \begin{array}{c}
-          \underbrace{X_0(\unitpoint)}_{\painting[0][0]}
-          \\ \times \\
-          \underbrace{X_0(\unitpoint)}_{\painting[0][0]}
-        \end{array}\right)}_{\layer[1][0]}}_{\framep[1][1]} \rightarrow \U                                                                            \\
-      X_2                                : \underbrace{\Sigma a: \underbrace{\left(\Sigma \unitpoint: \unittype. \underbrace{\left(
-          \begin{array}{c}
-            \underbrace{\Sigma b: \left(
-            \hspace{-0.4em}\begin{array}{c}
-                             X_0(\unitpoint)
-                             \\ \times \\
-                             X_0(\unitpoint)
-                           \end{array}\hspace{-0.4em}
-            \right).\, \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][L][0]}}_{\painting[1][1]}}_{\painting[1][0]}
-            \\ \times \\
-            \underbrace{\Sigma b: \left(
-            \hspace{-0.4em}\begin{array}{c}
-                             X_0(\unitpoint)
-                             \\ \times \\
-                             X_0(\unitpoint)
-                           \end{array}\hspace{-0.4em}
-            \right).\, \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][R][0]}}_{\painting[1][1]}}_{\painting[1][0]}
-          \end{array}
-          \right)}_{\layer[2][0]}\right)}_{\framep[2][1]}.\underbrace{\left(
-        \begin{array}{c}
-          \underbrace{X_1 \underbrace{\left(a.\hd, \left(
-              \hspace{-0.4em}\begin{array}{c}
-                               a.\tl.L.\hd.L, \\
-                               a.\tl.R.\hd.L
-                             \end{array}\hspace{-0.4em}
-              \right)\right)}_{\restrf[2][1][L][1]}}_{\painting[1][1]}
-          \\ \times \\
-          \underbrace{X_1 \underbrace{\left(a.\hd, \left(
-              \hspace{-0.4em}\begin{array}{c}
-                               a.\tl.L.\hd.R, \\
-                               a.\tl.R.\hd.R
-                             \end{array}\hspace{-0.4em}
-              \right)\right)}_{\restrf[2][1][R][1]}}_{\painting[1][1]}
-        \end{array}
-        \right)}_{\layer[2][1]}}_{\framep[2][2]}
-      \rightarrow \U                                                                                                                                \\
-      \ldots
-    \end{array}
-  \end{equation*}
-\end{small}
-
-Let us now illustrate the construction of $\fullframe[3]$, necessary to build the type of $X_3$.
-
-\begin{center}
-  \begin{tikzpicture}[scale=2]
-    \draw[spanish-blue, fill=spanish-blue] (0, 0) -- (1, 0) -- (1, 1) -- (0, 1) -- (0, 0);
-    \draw[spanish-blue, fill=spanish-blue, nearly transparent] (0.6, 1) -- (0.6, 1.6) -- (1.6, 1.6) -- (1.6, 0.6) -- (1, 0.6);
-  \end{tikzpicture}
-  \;\;
-  \begin{tikzpicture}[scale=2]
-    \draw[spanish-blue, fill=spanish-blue] (0, 0) -- (1, 0) -- (1, 1) -- (0, 1) -- (0, 0);
-    \draw[spanish-blue, fill=spanish-blue, nearly transparent] (0.6, 1) -- (0.6, 1.6) -- (1.6, 1.6) -- (1.6, 0.6) -- (1.0, 0.6);
-    \draw[raspeberry, pattern=dots] (1.1, 1.1) -- (1.5, 1.5) -- (1.5, 0.5) -- (1.1, 0.1) -- (1.1, 1.1);
-    \draw[raspeberry] (1.3, 1.3) -- (1.3, 0.3);
-    \draw[raspeberry, pattern=dots] (0.1, 1.1) -- (0.5, 1.5) -- (0.5, 1.1);
-    \draw[raspeberry] (0.3, 1.3) -- (0.3, 1.1);
-  \end{tikzpicture}
-  \;\;
-  \begin{tikzpicture}[scale=2]
-    \draw[spanish-blue, fill=spanish-blue] (0, 0) -- (1, 0) -- (1, 1) -- (0, 1) -- (0, 0);
-    \draw[spanish-blue, fill=spanish-blue, nearly transparent] (0.6, 1) -- (0.6, 1.6) -- (1.6, 1.6) -- (1.6, 0.6) -- (1.0, 0.6);
-    \draw[raspeberry, pattern=dots] (1.1, 1.1) -- (1.5, 1.5) -- (1.5, 0.5) -- (1.1, 0.1) -- (1.1, 1.1);
-    \draw[raspeberry] (1.3, 1.3) -- (1.3, 0.3);
-    \draw[raspeberry] (0.1, 1.1) -- (0.5, 1.5);
-    \draw[russian-green, pattern=dots] (0.2, 1.1) -- (1.0, 1.1) -- (1.4, 1.5) -- (0.6, 1.5) -- (0.2, 1.1);
-    \filldraw[russian-green] (0.8, 1.3) circle (0.6pt);
-  \end{tikzpicture}
-\end{center}
-
-The figure on the left is $\framep[3][1]$, in the middle is $\framep[3][2]$, and on the right is $\framep[3][3]$, which is full.
-Further, $\framep[3][1]$ is made of one layer, $\layer[3][0]$, shown as the front and back faces (blue boxes), $\framep[3][2]$ is made of one additional layer, $\layer[3][1]$, shown as the left and right faces (red boxes), $\framep[3][3]$ is made of one more layer, $\layer[3][2]$, shown as the top face (green box).
-
-We illustrated here the cubical case, that is $\nu = 2$, but, in general, a $\layer[n][p]$ is a product of $\nu$ $\painting[n - 1][p]$.
-A $\painting[n][0]$ is a $n$-dimensional object corresponding to a filled $\fullframe[n]$.
-More generally, a $\painting[n][p]$ is an $n$-dimensional object which has the form of a $\painting[n-p][0]$, thus of $(n-p)$-dimensional form, but shifted and living in dimensions $p$ to $n$.
-Such $\painting[n][p]$ fills a space framed by a partial $\framep[n][p]$ so that, together, they form a filled $\fullframe[n]$.
-For instance, in the picture, each of the two $\painting[2][0]$ of $\layer[3][0]$ is a filled blue square, each of the two $\painting[2][1]$ of $\layer[3][1]$ is a line, shown as lines across the left and right faces (red lines), stretched into a partial square filling the partial frames made of respectively, the left and right border of the front-back faces (blue), and each of the two $\painting[2][2]$ of $\layer[3][2]$ is the point shown on the top face (green point), stretched into a partial square filling the full frames made respectively of the upper and lower borders of the front-back and left-right faces (blue and red squares).
-A $\painting[n][p]$ complements a $\framep[n][p]$ by adding layers needed to form a $\fullframe[n]$ and by filling the resulting $\fullframe[n]$ with an inhabitant of $X_n$.
-Layers are added from dimension $n$ to dimension $p$, opposite to the order from $0$ to $p$ the $\framep[n][p]$ are built, as shown below.
-\begin{equation*}
-  \begin{array}{lll}
-    \framep[n][p]   & \defeq & \Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype .\, \layer[n][0]) \ldots) .\, \layer[n][p - 1] \\
-    \painting[n][p] & \defeq & \Sigma l_p: \layer[n][p]. (\ldots (\Sigma l_n: \layer[n][n - 1] .\, X_n) \ldots)
-  \end{array}
-\end{equation*}
-
-So far, we have not paid attention to the fact that we have a dependent type, shown as $\Sigma$.
-To be more precise, note that $\fullframe[n]$ depends on all $X_i$ up to $n - 1$.
-So, we need to package up $X_i$, for $i < n$, into a nesting of $\Sigma$-types, constituting the type of a $n$-truncated $\nu$-set, which we wrote $\X[][<n][]$.
-This allows us to give the type $\X[][<n][] \rightarrow \U$ to $\fullframe[n]$.
-Then, for $D: \X[][<n][]$, representing an initial prefix of $X_0, X_1, \ldots X_{n - 1}$, the indexed set $X_n$ has type $\fullframe[n](D) \rightarrow \U$.
-Thus, $\framep[n][p]$, $\layer[n][p]$ and $\painting[n][p]$ also depend on $D$.
-We can then reformulate the previous equation with its dependency on $D$.
-In particular, $X_n$ is just the last component of $D$, that is $D.\tl$.
-\begin{equation*}
-  \begin{array}{lll}
-    \framep[n][p](D)   & \defeq & \Sigma a_n: (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)) \ldots) .\,\layer[n][p - 1](D) \\
-    \painting[n][p](D) & \defeq & \Sigma l_p: \layer[n][p](D).\, (\ldots (\Sigma l_n: \layer[n][n - 1](D) .\, D.\tl) \ldots)
-  \end{array}
-\end{equation*}
-
-An extra refinement arises from the fact that each new layer of a frame has to be glued onto the border of the partial frame built so far.
-So, each $\layer[n][p]$ has to depend on $\framep[n][p]$.
-We also need a way to characterize the $\nu$ borders of each $\painting[n-1][p]$ that composes a $\layer[n][p]$, and this is where the restriction $\restrf[n][p][\epsilon][p]$ arrives, for each $\epsilon < \nu$.
-For instance, in the picture, the left and right faces (red), $\painting[2][1]$, are laid on respectively the left and right borders of the front and back faces (blue), and hence need to depend on $\framep[3][1]$.
-The left and right borders of the front and back faces are then extracted as $\restrf[2][1][L](D)(d)$ and $\restrf[2][1][R](D)(d)$.
-We can then refine again the previous equation by showing the dependencies on $d$, as shown below.
-\begin{equation*}
-  \begin{array}{llr}
-    \framep[n][p](D)      & \defeq & \Sigma d: (\ldots (\Sigma \unitpoint: \unittype.\, \layer[n][0](D)(\unitpoint)) \ldots).\, \layer[n][p](D)(d) \\
-    \painting[n][p](D)(d) & \defeq & \Sigma l_p: \layer[n][p](D)(d).\, (\ldots (\Sigma l_n: \layer[n][n - 1](D)(d, l_p, \ldots, l_{n - 1}).        \\
-                          &        & D.\tl(d, l_p, \ldots, l_n)) \ldots)                                                                           \\
-                          &        & \text{where } (d, l_p, \ldots, l_q) \text{ abbreviates } ((\ldots(d, l_p), \ldots), l_q)
-  \end{array}
-\end{equation*}
-
-When $\nu = 2$, using $L$ and $R$ to represent the sides, the formation of layers from paintings amounts to:
-\begin{equation*}
-  \begin{array}{llc}
-    \layer[n][p](D)(d) & \defeq & \painting[n-1][p](D.\hd)(\restrf[n][p][L][p](d)) \times \painting[n-1][p](D.\hd)(\restrf[n][p][R][p](d))
-  \end{array}
-\end{equation*}
-
-The operation $\restrf[n][p][\epsilon][q]$ restricts the $p$ first layers of a frame, and the construction is by recursion on the structure of a frame $d$.
-This necessitates the definitions $\restrl[n][p][\epsilon][q](d)(l)$ and $\restrc[n][p][\epsilon][q](d)(c)$, for $l$ a $\layer$, and $c$ a $\painting$.
-The key case is $\restrc[n][p][\epsilon][p](d)(c)$, where $c$, a $\painting[n][p]$, necessarily has the form of $((c_L, c_R), \_)$.
-Here, $\restrc[n][p][L][p]$ picks out $c_L$, a $\painting[n-1][p]$, $\restrc[n][p][R][p]$ picks out the $c_R$, also a $\painting[n-1][p]$, and the last component, shown as $\_$, a $\painting[n][p+1]$, is discarded.
-There is one last difficulty, which we illustrate by writing down expected and actual types.
-
-Given $c_\omega$ of type
-\begin{align*}
-  c_\omega & : \painting[n-1][p](D.\hd)(\restrf[n][p][\omega][p](d))
-\end{align*}
-$\restrl[n][p][\epsilon][q](d)(c_L, c_R)$ produces a layer in which the $\omega$-component has the type
-\begin{equation*}
-  \painting[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\epsilon][q](\restrf[n][p][\omega][p](d)))
-\end{equation*}
-while we expect a component of type
-\begin{equation*}
-  \painting[n-2][p](D.\hd.\hd)(\restrf[n-1][p][\omega][p](\restrf[n][p][\epsilon][q+1](d)))
-\end{equation*}
-
-Hence, we need a coherence condition to commute the restrictions.
-Coherence conditions similar to this necessitate what are shown as, $\cohf$, $\cohl$ and $\cohc$ in table~\ref{tab:coh}.
-These are by induction on the structure of $\framep$, $\layer$ and $\painting$.
-Note that, for the construction in intensional type theory, we further need a $2$-dimensional coherence condition, $\coht$, for $\cohl$, which is explained in the next section.
-
-\subsection{From extensional to intensional type theory\label{sec:itt}}
-\renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
-In this section, we intend to get rid of the reflection rule and make explicit the equational reasoning step needed to rephrase the construction in intensional type theory.
-For readability purposes, we make only explicit in this section the key coherence conditions of the construction.
-Other cases of equality reasoning would have to be made explicit to fully obtain a construction in intensional type theory, but these steps are standard enough to be omitted at this stage.
-See section~\ref{sec:eqproperties} for the details.
-
-The need for transport along a proof of commutation of $\restrf$ in the definition of $\restrl$ is made explicit in table~\ref{fulltab:faces}, where the arrow over $\cohf$ indicates the direction of rewrite.
-
-% Insert fulltab:faces and fulltab:coh, after overriding macros to make
-% everything but the universe letter explicit.
-\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
-\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
-\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
-\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrc}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
-\def\lab{fulltab:faces}
-\renewcommand{\thetable}{4'}
-\input{tab-faces.tex}
-\def\lab{fulltab:coh}
-\renewcommand{\thetable}{5'}
-\input{tab-coh.tex}
-
-\renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
-\renewcommandx{\cohl}{\coh{layer}[][][][][][][][]}
-\renewcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
-The proof of $\cohf$ itself requires making explicit several rewrites which were invisible in extensional type theory.
-The commutation of $\restrl$ lives in a type referring to $\cohf$, so we need a transport along the commutation of $\restrf$ in the statement of $\cohl$.
-The proof of $\cohl$ is the most involved proof of the construction, as it requires a higher-dimensional coherence condition, $\coht$, whose exact formulation is as follows.
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
-\begin{align*}
-  \cohf[m][\omega][\theta][r][p][n-1][p][][d = {\restrf[m][\epsilon][q+2][n][p][][d = \d]}]\;\bullet     \\
-  \ap \restrf[m][\omega][r][n-2][p][][]\;(\cohf[m][\epsilon][\theta][q+1][p][n][p][][d = \d])\;\bullet   \\
-  \cohf[m][\epsilon][\omega][q][r][n-1][p][][d = {\restrf[m][\theta][p][n][p][][d = \d]}] =              \\
-  \ap \restrf[m][\theta][p][n-2][p][][]\;(\cohf[m][\epsilon][\omega][q+1][r+1][n][p][][d = \d])\;\bullet \\
-  \cohf[m][\epsilon][\theta][q][p][n-1][p][][d = {\restrf[m][\omega][r+1][n][p][][d = \d]}]\;\bullet     \\
-  \ap \restrf[m][\epsilon][q][n-2][p][]\;(\cohf[m][\omega][\theta][r][p][n][p][][d = \d])
-\end{align*}
-where $\ap$ applies a function on two sides of an equality, and $\bullet$ is transitivity of equality.
-This property of equality proofs holds in \U, and since our construction is done in \U, the term is trivially discharged.
-
-\renewcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
-\renewcommandx{\restrf}{\restr{frame}[][][][][][][]}
-\renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
-\renewcommandx{\cohl}{\coh{layer}[][][][][][][][]}
-\renewcommandx{\cohc}{\coh{painting}[][][][][][][][]}
-
-Notice that each $\restrl$ in the type of $\cohl$ is hiding a $\cohf$ rewrite: this makes a sum total of three $\cohf$ rewrites on the left-hand side, and two $\cohf$ rewrites on the right-hand side.
-In the proof term of $\cohl$, $\cohc$ has one $\cohf$ rewrite on its left-hand side.
-This, combined with the two terms of the form $\ap \cohf$, matches our expectation of three $\cohf$ on the left-hand side, and two $\cohf$ on the right-hand side.
-Then, $\coht$ can be seen as expressing the commutation of these $\cohf$ terms.
-
-Finally, let us explain $\cohc$.
-The base case $p = r$ is the key case of the commutation of $\restrf$, when one of the $\restrc$ collapses, and the remaining equation holds trivially.
-The case of $p < r$ follows the structure of $\restrc$ by induction.
-
-If we were not working in \U, but in $\HGpd$ we would need to prove one more higher-dimensional coherence, and if we were working in \Type, we would need to prove arbitrarily many higher-dimensional coherences.
-Here, $\HGpd$ is the subset of types $A$ such that for all $x$ and $y$ in $A$, $x = y$ is in \U.
-See \cite{herbelin15,altenkirch16,kraus21} for a discussion on the need for recursive higher-dimensional coherence conditions in formulating higher-dimensional structures in type theory.
-
-\subsection{Well-foundedness of the construction\label{sec:wf}}
-\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
-\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
-\renewcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
-\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
-\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
-\renewcommandx{\restrc}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
-\renewcommandx{\cohf}[1][1]{\coh{frame}[][][][][][#1][][]}
-\renewcommandx{\cohl}[1][1]{\coh{layer}[][][][][][#1][][]}
-\renewcommandx{\cohc}[1][1]{\coh{painting}[][][][][][#1][][]}
-
-Since the construction shown in the previous sections is by induction on $n$, and dependencies are on lower $n$ and $p < n$, one would imagine formalizing this using well-founded induction in dependent type theory.
-We initially tried this approach, and had terms dependent on the proofs of the case distinction that $n' \leq n$ implies $n' < n$ or $n' = n$, but these proofs did not come with enough definitional properties to be usable in practice.
-Hence, we chose a different route: in practice, since $\restrf[n]$ depends on $\framep[n]$ and $\framep[n-1]$, while $\cohf[n]$ depends on $\framep[n]$, $\framep[n-1]$, and $\framep[n-2]$, we only need to keep track of three consecutive dimensions.
-Hence, what we build by induction at level $n$, is a structure made not only of the definitions shown in the tables~\ref{tab:frames},~\ref{fulltab:faces}, and~\ref{fulltab:coh}, but also of $\framep$, $\layer$, $\painting$ at levels $n - 1$ and $n - 2$, as well as $\restrf$, $\restrl$, and $\restrc$ at level $n - 1$, together with helper equations.
-
-\subsection{Dependencies in inequality proofs\label{sec:le}}
-The entire construction relies on inequalities over natural numbers, and we use two different definitions of $\leq$ addressing different concerns in our formalization.
-In order to build our first variant, we use an intermediate ``recursive definition'' phrased as:
-
-\begin{minted}{coq}
-Fixpoint leR (n m : nat) : SProp :=
-match n, m with
-| O, _ => STrue
-| S n, O => SFalse
-| S n, S m => leR n m
-end.
-\end{minted}
-
-Here, $\SProp$ is a definitionally proof-irrelevant impredicative universe morally\footnote{In Coq, it is however a stand-alone universe unrelated to the universe hierarchy.} living at the bottom of the universe hierarchy~\cite{gilbert19}.
-By placing the definition in \SProp, we have definitional equality of inequality proofs.
-However, for the purpose of unification, this definition does not go far enough.
-Consider the unification problems:
-
-\begin{minted}{coq}
-leR_trans ?p leR_refl = ?p
-leR_trans leR_refl ?p = ?p
-\end{minted}
-where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable.
-These two problems definitionally hold in \SProp, but equating them does not solve the existential variable.
-For unification to be useful in solving existential variables, we present our first variant of $\leq$, which we dub as the ``Yoneda variant'':
-
-\begin{minted}{coq}
-Definition leY n m :=
-  forall p, leR p n -> leR p m.
-\end{minted}
-
-This definition is an improvement over \texttt{leR} since reflexivity is now definitionally the neutral element of transitivity, and associativity of transitivity also holds definitionally.
-Although it significantly eases our proof, there are some instances where unification is unable to solve the existential variables, and we have to provide them explicitly.
-
-The second variant of $\leq$, the ``inductive variant'', is phrased as:
-
-\begin{minted}{coq}
-Inductive leI : nat -> nat -> Type :=
-| leI_refl n : n <~ n
-| leI_down {n p} : p.+1 <~ n -> p <~ n
-where "n <~ m" := (leI n m) : nat_scope.
-\end{minted}
-
-Compared to \texttt{leY}, \texttt{leI} has no proof-irrelevance properties.
-This definition is specially crafted for $\painting$, where we have to reason inductively from $p \leq n$ to $n$.
-In our usage, we have lemmas \texttt{leY\_of\_leI} and \texttt{leI\_of\_leY} in order to equip \texttt{leY} with the induction scheme of \texttt{leI}.
-The resulting induction scheme has computational rules holding propositionally.
-
-\subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
-The construction relies on groupoid properties of equality which are left implicit in table~\ref{fulltab:coh}.
-The use of the equivalence between $u = v$ and $\Sigma (p:u.\hd = v.\hd).
-(u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type is left implicit in the same table.
-Also implicit is the use of the equivalence between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, or functional extensionality, holds by default in extensional type theory.
-These have to be made explicit in the formalization.
-
-As a final remark, note that as a consequence of $\eta$-conversion for finite enumerated types, the requirement of functional extensionality disappears when $\nu$ is finite.
-However, this is a conversion which Coq does not implement, and the alternative would be to replace $\Pi a: \nu.\, B$ by a ``flat'' iterated product $B(1) \times B(2) \times \ldots \times B(\nu)$.
-
-\section{Future work}
-The construction could be extended with degeneracies as well as with permutations~\cite{grandis03}.
-Dependent $\nu$-sets could also be defined, opening the way to construct $\Pi$-types and $\Sigma$-types of $\nu$-sets.
-A $\nu$-set of $\nu$-sets representing a universe could also be defined as sketched in a talk at the HoTT-UF workshop for the bridge case~(\cite{herbelin-hott-uf}).
-More generally, we believe these lines of work would eventually provide alternative models to parametric type theories~\cite{nuyts17,cavallo19} where equality of types, now a family rather than the total space of a fibration, is not only definitionally isomorphic to bridges~\cite{bernardy15}, but definitionally the same as bridges.
-
-By equipping the universe construction with a structure of equivalences, as suggested along the lines of \cite{altenkirch15}, we also suspect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\cite{bezem13,cohen16,angiuli21}, saving the detour via the fibred approach inherent to usual presheaf models.
-In particular, we conjecture being able to justify univalence holding definitionally.
-Our approach would also firmly ground cubical type theory in iterated parametricity.
-
-Although prior approaches to constructing the indexed presentation of a presheaf over a direct category rely on it being evident by inspection that the fibred and indexed presentations are equivalent, no formal proof has been given, and this is a direction for future work.
-In our construction, we can check by computation of the first levels that it indeed computes the expected sets.
-
-\bibliographystyle{alpha}
+\newpage
+\bibliographystyle{msclike}
 \bibliography{paper}
 
-\newpage
-\appendix
-\fancyhead[L]{\footnotesize\textcolor{gray80}{{\MakeUppercase{Appendix}}}}
-\section*{Appendix: Definition of dependent stream}
-
-\begin{align*}
-  \mbox{\emph{type formation}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\
-  \seqr{}{\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u:A}
-  {\Gamma \vdash Stream_{A,B,f}\, u : \Type_m}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\
-  \mbox{\emph{introduction and eliminations}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     \\
-  \seqr{}{\!\!\!\begin{array}{l}\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u : A \\ \Gamma, a:A \vdash D(a) : \Type_m \qquad \Gamma \vdash w : D(u) \\ \Gamma, a:A, d:D(a) \vdash v(a,d) : B(a) \qquad \Gamma, a:A, d:D(a) \vdash s(a,d) : D(f(a,v(a,d))) \end{array}}{\Gamma \vdash \textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\} : Stream_{A,B,f}\, u}                                                                                                                                                      \\
-  \seqr{}{\Gamma \vdash t : Stream_{A,B,f}\, u}{\Gamma \vdash t.this : B(u)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      \\
-  \seqr{}{\Gamma \vdash t : Stream_{A,B,f}\, u}{\Gamma \vdash t.next : Stream_{A,B,f}\, f(u,t.this)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\
-  \mbox{\emph{computation}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       \\
-  \seqr{}{\!\!\!\begin{array}{l}\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u : A \\ \Gamma, a:A \vdash D(a) : \Type_m \qquad \Gamma \vdash w : D(u) \\ \Gamma, a:A, d:D(a) \vdash v(a,d) : B(a) \qquad \Gamma, a:A, d:D(a) \vdash s(a,d) : D(f(a,v(a,d))) \end{array}}{\Gamma \vdash \textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\}.this \equiv v(u,w) : B(u)}                                                                                                                                                 \\
-  \seqr{}{\!\!\!\begin{array}{l}\Gamma \vdash A : \Type_m \qquad \Gamma, a:A \vdash B(a) : \Type_m \qquad \Gamma, a:A, b:B(a) \vdash f(a,b):A \qquad \Gamma \vdash u : A \\ \Gamma, a:A \vdash D(a) : \Type_m \qquad \Gamma \vdash w : D(u) \\ \Gamma, a:A, d:D(a) \vdash v(a,d) : B(a) \qquad \Gamma, a:A, d:D(a) \vdash s(a,d) : D(f(a,v(a,d)))\end{array}}{\!\!\!\begin{array}{r}\Gamma \vdash \textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\}.next \equiv \\ \textsf{cofix}_{a,d,g}^{f(u,v(u,w)),s(u,w))}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\} \\ : Stream_{A,B,f}\,f(u,v(u,w))\end{array}} \\
-\end{align*}
-where $\textsf{cofix}_{a,d,g}^{u,w}\{this:=v(a,d); next:=g(f(a,v(a,d)),s(a,d))\}$ is a notation for the instantiation on parameter $u$ and internal value $w$ of the corecursive definition of a stream over an arbitrary $a$ generated by a recipe dependent on an arbitrary internal value $d:D(a)$ with first component given by $v(a,d)$ and second component given by $g(f(a,v(a,d)),s(a,d))$ where $g$, typed as $\Gamma, a:A, d:D(a) \vdash g(a,d): Stream_{A,B,f}\, (f(a,d))$, formally represents the recursive call, and where $s(a,d)$ tells how the internal value evolves.
 \end{document}

### 2025-09-28 paper/paper.tex
paper: typeset (frame|painting|restrf)type, adjust font-sz
paper: swap sections; first section reminder
paper: change convention n -> n+p in tables
paper: \cohc -> \cohp

@@
 
-\newcommand{\frametype}{\ensuremath{\mathsf{frametype}}}
-\newcommand{\paintingtype}{\ensuremath{\mathsf{paintingtype}}}
-\newcommand{\restrftype}{\ensuremath{\mathsf{restrftype}}}
-
 \newcommand{\udensdash}[1]{%
@@
 \newcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
+\newcommandx{\frametype}[2][1,2]{\prim{frametype}[][#1][#2][][]}
 \newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
 \newcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
+\newcommandx{\paintingtype}[2][1,2]{\prim{paintingtype}[][#1][#2][][]}
+\newcommandx{\restrftype}[2][1,2]{\prim{restrftype}[][#1][#2][][]}
 \newcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
@@
 \newcommandx{\cohl}{\coh{layer}[][][][][][][][]}
-\newcommandx{\cohc}{\coh{painting}[][][][][][][][]}
+\newcommandx{\cohp}{\coh{painting}[][][][][][][][]}
 \newcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
@@
 
+\section{Reminder of our construction}
+% Abbreviated tables in this section
+%
+% The rule for implicit arguments for each table:
+% show 1 explicit in first two parts
+% show E + 1 explicit in the third part
+\appendmask[bonak]{layer}[D]
+\appendmask[bonak]{painting}[D]
+\appendmask[bonak]{restrframe}[D]
+\appendmask[bonak]{restrlayer}[D, d]
+\appendmask[bonak]{restrpainting}[D, d]
+\appendmask[bonak]{cohframe}[D]
+\appendmask[bonak]{cohlayer}[D, d]
+\appendmask[bonak]{cohpainting}[D, d]
+
+% Truncated sets, otherwise referred to as X
+% Keep all arguments
+\newcommandx{\Xp}[1]{\X[#1][][]}
+\newcommandx{\Xto}[3][3=]{\X[#1][<#2][#3]}
+\newcommandx{\Xcomp}[3][3=]{\X[#1][=#2][#3]}
+\newcommandx{\Xfrom}[3][3=]{\X[#1][\geq#2][#3]}
+
+% Frame, layer, and painting
+% Drop the universe letter
+\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
+\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
+\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
+
+% Restriction for frame, layer, and painting
+% Drop the universe letter
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrp}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
+
+% Coherence conditions for frame, layer, and painting
+% Keep only ε, ω; n, p; proposition on n and p
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
+\renewcommandx{\cohp}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][][][][][#9]}
+
+A $\nu$-set in indexed form is a sequence of families of $\U$, that is $\U[m]$ for some universe level $m$. We call such sequence a $\nu$-set at level $m$, whose type thus lives in $\U[m+1]$.
+
+Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets: using the notations of Section~\ref{sec:tt}, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
+Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
+This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
+
+The definition of the type of a $n$-truncated $\nu$-set is in turn described in table~\ref{tab:core}.
+In the infinite sequence of type families representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$.
+It is recursively defined in table~\ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
+A $\fullframe$ describes a boundary of a standard form (simplex, cube), which we decompose into $\layer$, and a $\painting$ corresponds to a filled frame.
+Notice that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table~\ref{tab:faces}, and this restriction operator is in turn defined using auxiliary definitions $\restrl$ and $\restrp$.
+
+Notably, the definition of $\restrl$ relies on an equality expressing the commutation of the composition of two $\restrf$.
+The proof of this commutation is worth being made explicit, which we do in table~\ref{tab:coh} using proof-term notations.
+The proof requires an induction on the dimension and on the structure of $\framep$, $\layer$, and $\painting$.
+This is what $\cohf$ does using auxiliary proofs $\cohl$ and $\cohp$.
+Even though it looks independent of the definitions from the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
+More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be defined in one go by induction on $p$.
+Also, each of $\painting$, $\restrp$, and $\cohp$ is built by induction from $p$ to $n$.
+The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but the converse dependency is only on lower $n$, so this is well-founded.
+Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
+The exact way this mutual recursion is eventually formalized is explained in section~\ref{sec:wf}.
+
+Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that the construction builds an effective sequence of types not mentioning coherences anymore.
+\\
+
+\def\lab{tab:coind}
+\input{tab-coind.tex}
+
+% For just the second table, keep the universe letter in fullframe
+\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
+
+\def\lab{tab:core}
+\input{tab-core.tex}
+
+% Drop the universe letter in fullframe for all remaining tables
+\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
+\def\lab{tab:frames}
+\input{tab-frames.tex}
+
+% The third table mentions cohframe; keep ε, ω in this instance
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
+
+\def\lab{tab:faces}
+\input{tab-faces-ett.tex}
+
+% Restriction for frame, layer, and painting
+% Drop just the universe letter for the coh table
+\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
+\renewcommandx{\restrp}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
+
+% Coherence conditions for frame, layer, and painting
+\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\cohp}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
+\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
+
+\def\lab{tab:coh}
+\input{tab-coh-ett.tex}
+
+\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
+\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
+\renewcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
+\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
+\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
+\renewcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
+
 \section{The recursive structure of iterated parametricity}
@@
         \begin{center}
+          \fontsize{7.2}{9}\selectfont
           \begin{tikzcd}
@@
         $$
+          \fontsize{7.2}{9}\selectfont
           \begin{array}{llcl}
-            \frametype^{n,[0,...,p]}  &                                                     & :      & Type_{l+1}                                                               \\
-            \frametype^{n,[]}         &                                                     & \defeq & unit                                                                     \\
-            \frametype^{n,[0,...,p]}  &                                                     & \defeq & \frametype^{n,[0,...,p-1]} \times Type_l                               \\
+            \frametype[n][0,...,p]    &                                              & :      & Type_{l+1}                                                                                   \\
+            \frametype[n][]           &                                              & \defeq & unit                                                                                         \\
+            \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n][0,...,p-1] \times Type_l                                                       \\
             \\
-            \paintingtype^{n,[0,...,p]} & (\framep[n][0,...,p]:\frametype^{n,[0,...,p]}) & :      & Type_{l+1}                                                               \\
-            \paintingtype^{n,[]}        & \star                                               & \defeq & unit                                                                     \\
-            \paintingtype^{n,[0,...,p]} & (\framep[n][0,...,p])                            & \defeq & \paintingtype^{n,[0,...,p-1]}(\framep[n][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
+            \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & Type_{l+1}                                                                                   \\
+            \paintingtype[n][]        & \star                                        & \defeq & unit                                                                                         \\
+            \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
           \end{array}
@@
         $$
+          \fontsize{7.2}{9}\selectfont
           \begin{array}{llcl}
@@
               \left(\begin{array}{l}
-                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
-                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\
-                        \restrf[n][0,...,p-1]:\restrftype^{n,[0,...,p-1]}
+                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
+                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
+                        \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                         \left(\begin{array}{l}
@@
                           \end{array}\right)                                                  \\
-                      \end{array}\right) : \frametype^{n-1,[0,...,p]}
+                      \end{array}\right) : \frametype[n-1][0,...,p]
             }                                                                         \\
@@
                     \end{array}\right) \\
-            \restrftype^{n,[0,...,p-1]}                            &
+            \restrftype[n][0,...,p-1]  &
             \multicolumn{3}{l}{
               \left(\begin{array}{l}
-                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
-                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\
+                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
+                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                       \end{array}\right) : Type_{l}
             }                                                                         \\
-            \restrftype^{n,[]}                                     &
+            \restrftype[n][]           &
             \left(\begin{array}{l}
@@
             unit                                                                      \\
-            \restrftype^{n,[0,...,p]}                              &
+            \restrftype[n][0,...,p]    &
             \left(\begin{array}{l}
@@
               \Sigma \restrf[n][0,...,p-1]    \\
-              \quad:\restrftype^{n,[0,...,p-1]}
+              \quad:\restrftype[n][0,...,p-1]
               \left(\begin{array}{l}
@@
         $$
+          \fontsize{7.2}{9}\selectfont
           \begin{array}{llcl}
-            \frametype^{n,[p,...,n]}  &                                                     & :      & Type_{l+1}                                                               \\
-            \frametype^{n,[]}         &                                                     & \defeq & unit                                                                     \\
-            \frametype^{n,[p,...,n]}  &                                                     & \defeq & Type_l \times \frametype^{n,[p+1,...,n-1]}                               \\
+            \frametype[n][p,...,n]         &                                              & :      & Type_{l+1}                                                                                   \\
+            \frametype[n][]                &                                              & \defeq & unit                                                                                         \\
+            \frametype[n][p,...,n]         &                                              & \defeq & Type_l \times \frametype[n][p+1,...,n-1]                                                     \\
             \\
-            \paintingtype^{n,[p,...,n]} & (\framep[n][p,...,n]:\frametype^{n,[p,...,n]}) & :      & Type_{l+1}                                                               \\
-            \paintingtype^{n,[]}        & \star                                               & \defeq & unit                                                                     \\
-            \paintingtype^{n,[p,...,n]}_{p<n} & (\framep[n][p,...,n])                            & \defeq & (\framep[n][p] \rightarrow Type_l) \times \paintingtype^{n,[p+1,...,n]}(\framep[n][p+1,...,n]) \\
+            \paintingtype[n][p,...,n]      & (\framep[n][p,...,n]:\frametype[n][p,...,n]) & :      & Type_{l+1}                                                                                   \\
+            \paintingtype[n][]             & \star                                        & \defeq & unit                                                                                         \\
+            \paintingtype[n][p,...,n](p<n) & (\framep[n][p,...,n])                        & \defeq & (\framep[n][p] \rightarrow Type_l) \times \paintingtype[n][p+1,...,n](\framep[n][p+1,...,n]) \\
             \\
-            \restrftype^{n,[p,...,n]} &
+            \restrftype[n][p,...,n]        &
             \multicolumn{3}{l}{
               \left(\begin{array}{l}
-                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
-                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\
-                        \framep[n-1][p,...,n-1]:\frametype^{n-1,[p,...,n-1]}                                     \\
-                        \painting[n-1][p,...,n-1]:\paintingtype^{n-1,[p,...,n-1]}(\framep[n-1][p,...,n-1])           \\
-                        \restrf[n][0,...,p-1]:\restrftype^{n,[0,...,p-1]}
+                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
+                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
+                        \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
+                        \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
+                        \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                         \left(\begin{array}{l}
@@
             }                                                                                                                                                                                     \\
-            \restrftype^{n,[]}        &
+            \restrftype[n][]               &
             \left(\begin{array}{l}
@@
                     \end{array}\right)   & \defeq                                       & unit                                                                                                      \\
-            \restrftype^{n,[p,...,n-1]} &
+            \restrftype[n][p,...,n-1]      &
             \left(\begin{array}{l}
@@
                       \end{array}\right)
-                                \rightarrow \framep[n-1][p]\\
+              \rightarrow \framep[n-1][p] \\
               \times                      \\
-                                \restrftype^{n,[p+1,...,n]}
+              \restrftype[n][p+1,...,n]
               \left(\begin{array}{l}
@@
               \left(\begin{array}{l}
-                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
-                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\
-                        \framep[n-1][p,...,n-1]:\frametype^{n-1,[p,...,n-1]}                                     \\
-                        \painting[n-1][p,...,n-1]:\paintingtype^{n-1,[p,...,n-1]}(\framep[n-1][p,...,n-1])           \\
-                        \restrf[n][0,...,p-1]:\restrftype^{n,[0,...,p-1]}
+                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
+                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
+                        \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
+                        \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
+                        \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                         \left(\begin{array}{l}
@@
                           \end{array}\right)                                                  \\
-                        \restrf[n][p,...,n-1]:\restrftype^{n,[p,...,n-1]}
+                        \restrf[n][p,...,n-1]:\restrftype[n][p,...,n-1]
                         \left(\begin{array}{l}
@@
                           \end{array}\right)                                                  \\
-                        E:\framep[n-1][n-1]\rightarrow Type_l\\
+                        E:\framep[n-1][n-1]\rightarrow Type_l                                            \\
                       \end{array}\right) : \framep[n-1][n-1]\rightarrow Type_l
@@
 
-\section{Our construction}
-% Abbreviated tables in this section
-%
-% The rule for implicit arguments for each table:
-% show 1 explicit in first two parts
-% show E + 1 explicit in the third part
-\appendmask[bonak]{layer}[D]
-\appendmask[bonak]{painting}[D]
-\appendmask[bonak]{restrframe}[D]
-\appendmask[bonak]{restrlayer}[D, d]
-\appendmask[bonak]{restrpainting}[D, d]
-\appendmask[bonak]{cohframe}[D]
-\appendmask[bonak]{cohlayer}[D, d]
-\appendmask[bonak]{cohpainting}[D, d]
-
-% Truncated sets, otherwise referred to as X
-% Keep all arguments
-\newcommandx{\Xp}[1]{\X[#1][][]}
-\newcommandx{\Xto}[3][3=]{\X[#1][<#2][#3]}
-\newcommandx{\Xcomp}[3][3=]{\X[#1][=#2][#3]}
-\newcommandx{\Xfrom}[3][3=]{\X[#1][\geq#2][#3]}
-
-% Frame, layer, and painting
-% Drop the universe letter
-\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][#2][#3][#4][#5]}
-\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][#2][#3][#4][#5]}
-\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][#2][#3][#4][#5]}
-
-% Restriction for frame, layer, and painting
-% Drop the universe letter
-\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrp}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
-
-% Coherence conditions for frame, layer, and painting
-% Keep only ε, ω; n, p; proposition on n and p
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
-\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][][][][][#9]}
-
-A $\nu$-set in indexed form is a sequence of families of $\U$, that is $\U[m]$ for some universe level $m$. We call such sequence a $\nu$-set at level $m$, whose type thus lives in $\U[m+1]$.
-
-Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets: using the notations of Section~\ref{sec:tt}, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
-Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
-This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
-
-The definition of the type of a $n$-truncated $\nu$-set is in turn described in table~\ref{tab:core}.
-In the infinite sequence of type families representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$.
-It is recursively defined in table~\ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
-A $\fullframe$ describes a boundary of a standard form (simplex, cube), which we decompose into $\layer$, and a $\painting$ corresponds to a filled frame.
-Notice that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table~\ref{tab:faces}, and this restriction operator is in turn defined using auxiliary definitions $\restrl$ and $\restrp$.
-
-Notably, the definition of $\restrl$ relies on an equality expressing the commutation of the composition of two $\restrf$.
-The proof of this commutation is worth being made explicit, which we do in table~\ref{tab:coh} using proof-term notations.
-The proof requires an induction on the dimension and on the structure of $\framep$, $\layer$, and $\painting$.
-This is what $\cohf$ does using auxiliary proofs $\cohl$ and $\cohc$.
-Even though it looks independent of the definitions from the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
-More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be defined in one go by induction on $p$.
-Also, each of $\painting$, $\restrp$, and $\cohc$ is built by induction from $p$ to $n$.
-The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but the converse dependency is only on lower $n$, so this is well-founded.
-Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
-The exact way this mutual recursion is eventually formalized is explained in section~\ref{sec:wf}.
-
-Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that the construction builds an effective sequence of types not mentioning coherences anymore.
-\\
-
-\def\lab{tab:coind}
-\input{tab-coind.tex}
-
-% For just the second table, keep the universe letter in fullframe
-\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[#1][#2][][][#3]}
-
-\def\lab{tab:core}
-\input{tab-core.tex}
-
-% Drop the universe letter in fullframe for all remaining tables
-\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
-\def\lab{tab:frames}
-\input{tab-frames.tex}
-
-% Truncated sets, otherwise referred to as X
-% Drop the universe letter for the third and fourth tables
-\renewcommandx{\Xto}[3][3]{\X[][<#2][#3]}
-\renewcommandx{\Xcomp}[3][3]{\X[][=#2][#3]}
-\renewcommandx{\Xfrom}[3][3]{\X[][\geq#2][#3]}
-
-% The third table mentions cohframe; keep ε, ω in this instance
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
-
-\def\lab{tab:faces}
-\input{tab-faces-ett.tex}
-
-% Restriction for frame, layer, and painting
-% Drop just the universe letter for the coh table
-\renewcommandx{\restrf}[7][1,2,3,4,5,6,7]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrl}[7][1,2,3,4,5,6,7]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
-\renewcommandx{\restrp}[7][1,2,3,4,5,6,7]{\restr{painting}[][#2][#3][#4][#5][#6][#7]}
-
-% Frame, layer, and painting
-% Drop all arguments for coh table; they're not present in coind table.
-\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][][][][#5]}
-\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][][][][#5]}
-\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][][][][#5]}
-
-% Hack to remove , in \cohf
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
-
-% Coherence conditions for frame, layer, and painting
-\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
-
-\def\lab{tab:coh}
-\input{tab-coh-ett.tex}
-
 \newpage

### 2025-09-28 paper/paper.tex
paper: strip itemize, wrap

@@
 The well-foundedness of the construction can be justified by the observation that:
-\begin{itemize}
-  \item Defining $\framep[n][p]$ for $p \leq n$ requires the definition
-        of $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing
-        dependency, as well as $\restrf[n][p-1]$, where
-        $\restrf[n][p-1]$ in turn depends in $\framep[n][p-1]$ for its
-        typing.
 
-        Moreover, $\framep[n][p]$ depends on $\framep[n][p-1]$, so these
-        dependencies are between the blocks of $\framep[n][k]$ for all
-        $k\leq p$, as well as $\framep[n-1][k]$, $\painting[n-1][k]$ and
-        $\restrf[n][k]$ for all $k\leq p-1$, which we respectively
-        abbreviate as $\framep[n][0,...,p]$,
-        $\framep[n-1][0,...,p-1]$, $\painting[n-1][0,...,p-1]$ and
-        $\restrf[n][0,...,p-1]$.
+Defining $\framep[n][p]$ for $p \leq n$ requires the definition of $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$, where $\restrf[n][p-1]$ in turn depends in $\framep[n][p-1]$ for its typing.
+
+Moreover, $\framep[n][p]$ depends on $\framep[n][p-1]$, so these dependencies are between the blocks of $\framep[n][k]$ for all $k\leq p$, as well as $\framep[n-1][k]$, $\painting[n-1][k]$ and $\restrf[n][k]$ for all $k\leq p-1$, which we respectively abbreviate as $\framep[n][0,...,p]$, $\framep[n-1][0,...,p-1]$, $\painting[n-1][0,...,p-1]$ and $\restrf[n][0,...,p-1]$.
 
@@
 
-        Schematically, using dotted arrows for dependencies in
-        the type and plain arrows for dependencies in the definition, this
-        gives the following dependencies for $p\leq n$ fixed:
+Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n$ fixed:
 \begin{center}
@@
 
-        In particular, the mutual dependency on one side of
-        $\framep[n][0,...,p-1]$ within the type of
-        $\restrf[n][0,...,p-1]$ and on the other side of
-        $\restrf[n][0,...,p-1]$ within the definition of
-        $\framep[n][0,...,p]$ requires to mutually define the type of
-        $\restrf[n][0,...,p-1]$ together with $\framep[n][p]$ (or
-        $\framep[n][0,...,p]$) as a function from
-        $\restrf[n][0,...,p-1]$.
+In particular, the mutual dependency on one side of $\framep[n][0,...,p-1]$ within the type of $\restrf[n][0,...,p-1]$ and on the other side of $\restrf[n][0,...,p-1]$ within the definition of $\framep[n][0,...,p]$ requires to mutually define the type of $\restrf[n][0,...,p-1]$ together with $\framep[n][p]$ (or $\framep[n][0,...,p]$) as a function from $\restrf[n][0,...,p-1]$.
 
-        To talk about sequences of $\framep$, $\painting$ or $\restrf$,
-        we need to specify their types. The type of $\restrf$ will be
-        defined mutually with $\framep$ of the same level, but the type of
-        $\framep$, $\painting$ can be defined in advance, the second one
-        being however dependent on the first one. In general, components of
-        such sequences will have a type dependent on the previous components
-        of the sequence, as it is the case for $\restrf$. So, the type of
-        a sequence of length $p$ will be expressed as a $n$-iterated
-        $\Sigma$-type. In the case of $\framep$ and $\painting$, there will
-        be however no dependency, so an ordinary product can be used. If
-        $\framep[n][0,...,p]$ is such a sequence of length $p+1$, we write
-        $\framep[n][0,...,p-1]$ for its immediate subsequence of length $p$
-        and $\framep[n][p]$ for its last component. We can now define the
-        types of sequences of $\framep$ and $\painting$ as follows:
+To talk about sequences of $\framep$, $\painting$ or $\restrf$, we need to specify their types.
+The type of $\restrf$ will be defined mutually with $\framep$ of the same level, but the type of $\framep$, $\painting$ can be defined in advance, the second one being however dependent on the first one.
+In general, components of such sequences will have a type dependent on the previous components of the sequence, as it is the case for $\restrf$.
+So, the type of a sequence of length $p$ will be expressed as a $n$-iterated $\Sigma$-type.
+In the case of $\framep$ and $\painting$, there will be however no dependency, so an ordinary product can be used.
+If $\framep[n][0,...,p]$ is such a sequence of length $p+1$, we write $\framep[n][0,...,p-1]$ for its immediate subsequence of length $p$ and $\framep[n][p]$ for its last component.
+We can now define the types of sequences of $\framep$ and $\painting$ as follows:
 
-        $$
+\begin{equation*}
   \fontsize{7.2}{9}\selectfont
@@
   \end{array}
-        $$
+\end{equation*}
 
 Formally, this can be described as:
-        $$
+\begin{equation*}
   \fontsize{7.2}{9}\selectfont
@@
   \end{array}
-        $$
-  \item Defining $\painting[n][p]$, in addition to the type dependency
-        in $\framep[n][p]$, requires the definition of
-        $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing
-        dependency, as well as $\restrf[n][p-1]$. Since
-        $\painting[n][p]$ also depends on $\painting[n][p+1]$ when $p<n$,
-        these dependencies are actually between $\painting[n][p,...,n]$,
-        $\painting[n-1][p,...,n-1]$, $\framep[n][p,...,n]$,
-        $\framep[n-1][p,...,n-1]$ and $\restrf[n][p,...,n]$. Also,
-        for the case $p=n$, this also requires the assumption of an
-        inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally,
-        $\framep[n][p,...,n]$, $\framep[n-1][p,...,n-1]$ and
-        $\restrf[n][p,...,n-1]$ respectively depend on the earlier
-        values $\framep[n][0,...,p-1]$, $\framep[n-1][0,...,p-1]$ and
-        $\restrf[n][0,...,p-1]$.  Below, we use dashed underline and
-        dashed arrows for dependencies in subconstructions, here in the
-        construction of $\framep$ at level $n-1$ and $\restrftype$ at
-        level $n$:
+\end{equation*}
+
+Defining $\painting[n][p]$, in addition to the type dependency in $\framep[n][p]$, requires the definition of $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$.
+Since $\painting[n][p]$ also depends on $\painting[n][p+1]$ when $p<n$, these dependencies are actually between $\painting[n][p,...,n]$, $\painting[n-1][p,...,n-1]$, $\framep[n][p,...,n]$, $\framep[n-1][p,...,n-1]$ and $\restrf[n][p,...,n]$.
+Also, for the case $p=n$, this also requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$.
+Finally, $\framep[n][p,...,n]$, $\framep[n-1][p,...,n-1]$ and $\restrf[n][p,...,n-1]$ respectively depend on the earlier values $\framep[n][0,...,p-1]$, $\framep[n-1][0,...,p-1]$ and $\restrf[n][0,...,p-1]$.
+Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n-1$ and $\restrftype$ at level $n$:
 \begin{center}
@@
 
-        $$
+\begin{equation*}
   \fontsize{7.2}{9}\selectfont
@@
   \end{array}
-        $$
+\end{equation*}
 
 This allows to define $\painting[n][p]$ formally:
-        $$
+\begin{equation*}
   \fontsize{7.2}{9}\selectfont
@@
   \end{array}
-        $$
+\end{equation*}
 
@@
 
-\end{itemize}
-
-\newpage
 \bibliographystyle{msclike}

### 2025-09-28 paper/paper.tex
paper: typesetting improvements, dce

@@
     \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4][#5][#6]}^{\joinargs[#7][#8]}}
-  \setkeys*[bonak]{coh#1}{#9}
-}
-
-\newcommandx{\cohtwo}[9][2,3,4,5,6,7,8,9]{
-  \ensuremath{\mathsf{\color{chestnut}{coh2}}_{
-    \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4][#5][#6][#7]}^{\joinargs[#8]}}
   \setkeys*[bonak]{coh#1}{#9}
@@
 
-% Drop the universe letter in fullframe for all remaining tables
-\renewcommandx{\fullframe}[3][1,2,3]{\prim{fullframe}[][#2][][][#3]}
 \def\lab{tab:frames}
@@
 \renewcommandx{\cohp}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
-\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}
 
@@
     & & \painting[n][p,...,n] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
-    \udensdash{\framep}^{n,[0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
-    \udensdash{\framep}^{n,[p,...,n]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
+    \udensdash{\framep[n][0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
+    \udensdash{\framep[n][p,...,n]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
     \painting[n-1][0,...,p-1] \arrow[d, dotted] & &
@@
     \framep[n-1][0,...,p-1] &
-    \udensdash{\restrf}^{n,[0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
+    \udensdash{\restrf[n][0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
     \framep[n-1][p,...,n-1] \arrow[ll, dotted, bend left=15] &
-    \udensdash{\restrf}^{n,[p,...,n-1]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
+    \udensdash{\restrf[n][p,...,n-1]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
   \end{tikzcd}
@@
                                    & \defeq                                       &
-    \begin{array}{l}
+    \begin{array}{c}
       \framep[n][p]

### 2025-09-28 paper/paper.tex
paper: fix a couple of broken refs

@@
 
-Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets: using the notations of Section~\ref{sec:tt}, the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
+Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets: the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
 Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
@@
 Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
-The exact way this mutual recursion is eventually formalized is explained in section~\ref{sec:wf}.
 

### 2025-10-05 paper/paper.tex
paper: fix typos in frame, painting
paper: work on intro

@@
 \newcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
-\newcommandx{\frametype}[2][1,2]{\prim{frametype}[][#1][#2][][]}
+\newcommandx{\frametype}[2][1,2]{\prim{frametype}[][][#2][][]}
 \newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
 \newcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
-\newcommandx{\paintingtype}[2][1,2]{\prim{paintingtype}[][#1][#2][][]}
-\newcommandx{\restrftype}[2][1,2]{\prim{restrftype}[][#1][#2][][]}
+\newcommandx{\paintingtype}[2][1,2]{\prim{paintingtype}[][][#2][][]}
+\newcommandx{\restrftype}[2][1,2]{\prim{restrftype}[][][#2][][]}
 \newcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
@@
 \section{Introduction}
-A family of sets can commonly be represented in two ways: as a family properly speaking, indexed by the elements of a given set $S$, or as a set $T$ together with a map from $T$ to $S$, which specifies for each element of $T$ its dependency on $S$.
-In the former case, we call it an \emph{indexed} presentation.
-In the latter case, the set associated to a given element of $S$ is the fibre of this element, so we call it a \emph{fibred} presentation.
-The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\citep{hottbook} as the fibred/indexed equivalence\footnote{In an informal discussion, alternative nomenclatures were proposed: fibration/family equivalence and unbundled/bundled equivalence.
-The fibred/indexed nomenclature echoes the Grothendieck construction of fibred categories from indexed categories.
-The most elementary instance of the equivalence, with $\Type$ instead of $\U$, is sometimes called ``Grothendieck construction for dummies'', and its proof requires univalence~\citep{hottbook}.}.
-\begin{equation*}
-  \mbox{(fibred)}\qquad(\Sigma T: \U. (T \rightarrow S)) ~\simeq~ (S \rightarrow \U)\qquad \mbox{(indexed)}
-\end{equation*}
-Here, $\U$ represents in homotopy type theory the subset of types within a given universe where equality of any two elements has at most one proof.
-
-A \emph{presheaf} on an category is a family of sets indexed by the object of the category with maps indexed by the morphisms.
-As such, it lives on the indexed side of the equivalence, contrasting with the fibred side, where we have \emph{discrete Grothendieck fibrations}~\citep{LoregianRiehl20}.
-However, there are situations where a presheaf can also be seen as living on the fibred side of the equivalence.
-This happens when the indexing category is \emph{direct}, or has a downwards-well-founded collection of non-identity morphisms.
-Let us consider, for instance, the case of a semi-cubical set~\citep{grandis03,buchholtz17} presented with $2n$ face maps from the set of $n$-cubes to the set of $(n-1)$-cubes.
-Formulated in type theory, the corresponding presheaf definition of a semi-cubical set prescribes a family of sets and face maps between them as follows.
+In the previous paper~\citep{hr25}, we described the construction of augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity, meaning that instead of the following illustration of the cubical case (upto faces identities),
 
@@
 \end{equation*}
-up to cubical faces identities.
-Here, $X_1$ can be seen as a family over $X_0 \times X_0$, and $X_2$ can be seen as a family over $X_1 \times X_1 \times X_1 \times X_1$, in the fibred presentation, together with coherence conditions between the $X_1$ seen as families over $X_0 \times X_0$.
-This suggests an alternative indexed presentation of the presheaf as a stratified sequence of families indexed by families of lower rank, taking into account those coherence conditions to prevent duplications.
-Formulated in type theory, it takes the form:
+we consider a family of families as shown below:
 \begin{equation*}
@@
 
-The idea for such an indexed presentation of presheaves over a direct category was mentioned at the Univalent Foundations year in the context of defining semi-simplicial types\footnote{\href{https://ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}{ncatlab.org/nlab/show/semi-simplicial+types+in+homotopy+type+theory}}.
-A few constructions have been proposed since then.
-The first construction by \cite{voevodsky12} relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals.
-The second, by \cite{herbelin15}\footnote{In hindsight, the title of the paper ``A dependently-typed construction of semi-simplicial types'' is somewhat confusing: it implicitly claimed to construct semi-simplicial types, but the construction was done in a type theory with Uniqueness of Identity Proofs.
-Consequently, what was really obtained was an indexed presentation of semi-simplicial sets.
-The confusion was however, common at the time.} formalized in the Coq proof assistant, relies on the presentation of semi-simplicial sets as a presheaf over face maps.
-Another by \cite{part15} formalized in an emulation of logic-enriched homotopy type theory in the Plastic proof assistant, and yet another by \cite{altenkirch16} formalized in an emulation of a two-level type theory in the Agda proof assistant\footnote{\href{https://github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}{github.com/nicolaikraus/HoTT-Agda/blob/master/nicolai/SemiSimp/SStypes.agda}}, rely, like in Voevodsky, on the presentation of the semi-simplicial category from increasing injective maps between finite ordinals.
-The latter constructions, besides being stated as providing semi-simplicial types (thanks to an extension of the type theory), are particularly concise, taking advantage of a definition of increasing injective maps between finite ordinals as type-theoretic functions to inherit the associativity of composition directly from it holding in type theory.
-This contrasts with the combinatorial construction in \cite{herbelin15} where equations over face maps have to be proved by induction.
-
-By taking the sum of each component of an indexed presentation over the indexing set of this component, one obtains back a presheaf in the ordinary sense that has a property of \emph{Reedy fibrancy}, that is whose morphisms are projections in the set-theoretic sense.
-Such Reedy fibrant presheaves over a direct category have been studied in e.g.
-\cite{shulman15}, \cite{kraus17} and \cite{annenkovCK17,AnnenkovCKS2023}, presenting generic constructions over such presheaves.
-
-The indexed definition of a presheaf over a direct category is technically more involved than the presheaf definition, as it requires hard-wiring in the structure the dependencies between elements of the sets of the presheaf, including the coherence conditions between these dependencies, such as taking the $i$-th face of the $j$-th face of a $n$-simplex being the same as taking the $(j-1)$-th face of the $i$-th face (when $j>i$).
-However, exhibiting a concrete instance of a presheaf in indexed form only requires providing the families, since the responsibility of defining maps and showing the coherence conditions is already accounted for in the definition of the structure.
-
-\section{Reminder of our construction}
 % Abbreviated tables in this section
@@
     \frametype[n][0,...,p]    &                                              & :      & Type_{l+1}                                                                                       \\
-    \frametype[n][]           &                                              & \defeq & unit                                                                                         \\
-    \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n][0,...,p-1] \times Type_l                                                       \\
+    \frametype[n][]           &                                              & \defeq & \unittype                                                                                        \\
+    \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n+1][0,...,p-1] \times Type_l                                                         \\
     \\
     \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & Type_{l+1}                                                                                       \\
-    \paintingtype[n][]        & \star                                        & \defeq & unit                                                                                         \\
-    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
+    \paintingtype[n][]        & \unitpoint                                   & \defeq & \unittype                                                                                        \\
+    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n+1][0,...,p-1](\framep[n+1][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
   \end{array}
@@
       \left(\begin{array}{l}
-                \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
-                \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
+                \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
+                \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
                 \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                 \left(\begin{array}{l}
-                    \framep[n-1][0,...,p-1]   \\
-                    \painting[n-1][0,...,p-1] \\
+                    \framep[n][0,...,p-1]   \\
+                    \painting[n][0,...,p-1] \\
                   \end{array}\right)                                              \\
-              \end{array}\right) : \frametype[n-1][0,...,p]
+              \end{array}\right) : \frametype[n][0,...,p]
     }                                                                       \\
@@
     \left(\begin{array}{l}
-              \star \\
-              \star \\
-              \star \\
-            \end{array}\right)     & \defeq & (\star,unit)                      \\
+              \unitpoint \\
+              \unitpoint \\
+              \unitpoint \\
+            \end{array}\right)        & \defeq & (\unitpoint,unit)            \\
     \framep[n][0,...,p+1]         &
     \left(\begin{array}{l}
-              \framep[n-1][0,...,p]   \\
-              \painting[n-1][0,...,p] \\
+              \framep[n][0,...,p]   \\
+              \painting[n][0,...,p] \\
               \restrf[n][0,...,p]   \\
@@
     \left(\begin{array}{l}
-              \framep[n][0,...,p]
+              \framep[n+1][0,...,p]
               \left(\begin{array}{l}
-                  \framep[n-1][0,...,p-1]   \\
-                  \painting[n-1][0,...,p-1] \\
-                  \restrf[n][0,...,p-1]     \\
+                  \framep[n+1][0,...,p-1]   \\
+                  \painting[n+1][0,...,p-1] \\
+                  \restrf[n+1][0,...,p-1]   \\
                 \end{array}\right)     ,                     \\
-              \Sigma d:\framep[n][0,...,p]
+              \Sigma d:\framep[n+1][0,...,p]
               \left(\begin{array}{l}
-                  \framep[n-1][0,...,p-1]   \\
-                  \painting[n-1][0,...,p-1] \\
-                  \restrf[n][0,...,p-1]     \\
+                  \framep[n+1][0,...,p-1]   \\
+                  \painting[n+1][0,...,p-1] \\
+                  \restrf[n+1][0,...,p-1]   \\
                 \end{array}\right).\,                     \\
-              \quad \Pi\omega.\,\painting[n-1][p](\restrf[n][p](d)) \\
+              \quad \Pi\omega.\,\painting[n][p](\restrf[n][p](d)) \\
             \end{array}\right) \\
@@
       \left(\begin{array}{l}
-                \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
-                \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
+                \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
+                \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
               \end{array}\right) : Type_{l}
     }                                                                       \\
-    \restrftype[n][]           &
+    \restrftype[n][0,...,0-1]     &
     \left(\begin{array}{l}
-              \star \\
-              \star \\
+              \unitpoint \\
+              \unitpoint \\
             \end{array}\right)        & \defeq &
-    unit                                                                      \\
-    \restrftype[n][0,...,p]    &
+    \unittype                                                               \\
+    \restrftype[n][0,...,(p+1)-1] &
     \left(\begin{array}{l}
-              \framep[n-1][0,...,p]   \\
-              \painting[n-1][0,...,p] \\
+              \framep[n][0,...,p]   \\
+              \painting[n][0,...,p] \\
             \end{array}\right)      & \defeq &
     \begin{array}{l}
-      \Sigma \restrf[n][0,...,p-1]    \\
-      \quad:\restrftype[n][0,...,p-1]
+      \Sigma \restrf[n+1][0,...,p-1]
+      :\restrftype[n+1][0,...,p-1]
       \left(\begin{array}{l}
-                \framep[n-1][0,...,p-1]   \\
-                \painting[n-1][0,...,p-1] \\
-              \end{array}\right)
-      .\,                             \\
-      \Pi q\leq n.\,\Pi \omega.\,\framep[n][0,...,p]
+                \framep[n+1][0,...,p-1]   \\
+                \painting[n+1][0,...,p-1] \\
+              \end{array}\right)                         .  \\
+      \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]
       \left(\begin{array}{l}
-                \framep[n-1][0,...,p-1]   \\
-                \painting[n-1][0,...,p-1] \\
-                \restrf[n][0,...,p-1]     \\
-              \end{array}\right) \\
+                \framep[n+1][0,...,p-1]   \\
+                \painting[n+1][0,...,p-1] \\
+                \restrf[n+1][0,...,p-1]   \\
+              \end{array}\right) \rightarrow  \framep[n][p] \\
     \end{array}      \\
@@
     \frametype[n][p,...,n]         &                                              & :         & Type_{l+1}                                                                                   \\
-    \frametype[n][]                &                                              & \defeq & unit                                                                                         \\
+    \frametype[n][]                &                                              & \defeq    & \unittype                                                                                    \\
     \frametype[n][p,...,n]         &                                              & \defeq    & Type_l \times \frametype[n][p+1,...,n-1]                                                     \\
@@
     \paintingtype[n][p,...,n]      & (\framep[n][p,...,n]:\frametype[n][p,...,n]) & :         & Type_{l+1}                                                                                   \\
-    \paintingtype[n][]             & \star                                        & \defeq & unit                                                                                         \\
+    \paintingtype[n][]             & \unitpoint                                   & \defeq    & \unittype                                                                                    \\
     \paintingtype[n][p,...,n](p<n) & (\framep[n][p,...,n])                        & \defeq    & (\framep[n][p] \rightarrow Type_l) \times \paintingtype[n][p+1,...,n](\framep[n][p+1,...,n]) \\
@@
               \painting[n-1][0,...,n-1] \\
-              \star                     \\
-              \star                     \\
+              \unitpoint                \\
+              \unitpoint                \\
               \restrp[n][0,...,n-1]     \\
-            \end{array}\right)   & \defeq                                       & unit                                                                                                      \\
+            \end{array}\right)   & \defeq                                       & \unittype                                                                                                    \\
     \restrftype[n][p,...,n-1]      &
@@
               \painting[n-1][0,...,n-1] \\
-              \star                     \\
-              \star                     \\
+              \unitpoint                \\
+              \unitpoint                \\
               \restrp[n][0,...,n-1]     \\
-              \star                     \\
+              \unitpoint                \\
               E                         \\

### 2025-10-05 paper/paper.tex
paper: alternate, simpler explanation

@@
   In a previous paper, we gave equations describing the construction of semi-simplicial and semi-cubical sets via iterated parametricity.
-The construction was formalised in the Rocq (formerly known as Coq) proof assistant building $n$-truncated sets using an induction on a large structure embedding equational reasoning.
+The construction was formalised in the Rocq (formerly, Coq) proof assistant building $n$-truncated sets using an induction on a large structure embedding equational reasoning.
 
@@
 \renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
-\renewcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
+\renewcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#4][][]}
+\renewcommandx{\cohf}[6][1,2,3,4,5,6]{\coh{frame}[][#3][#4][#5][#6][#1,#2][][]}
+\renewcommandx{\cohl}[6][1,2,3,4,5,6]{\coh{layer}[][#3][#4][#5][#6][#1,#2][][]}
+\renewcommandx{\cohp}[6][1,2,3,4,5,6]{\coh{painting}[][#3][#4][#5][#6][#1,#2][][]}
 
-\section{The recursive structure of iterated parametricity}
-Iterated parametricity (in indexed form) produces a family of type
-families of the following form:
-\begin{equation*}
-  \begin{array}{llr}
-    X_0 & :              & \U                                                                        \\
-    X_1 & :              & X_0 \times X_0 \rightarrow  \U                                            \\
-    X_2 & : \Pi a b c d. & X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
-    \ldots
-  \end{array}
-\end{equation*}
+In \citep{hr25}, the well-foundedness was justified by induction on $n$ and subinductions, one on $p$ to mutually build $\framep[n][p]$, $\restrf[n][p]$ and $\cohf[n][p]$, and three others to build each of $\painting[n][p]$, $\restrp[n][p]$ and $\cohp[n][p]$ by induction on $n-p$.
 
-Such family can be recursively described by the equations given on Table ?.
+Since $\restrf[n][p]$ is referring to $\framep[n][p]$ and $\framep[n-1][p]$, and $\cohf[n][p]$ is referring to $\restrf[n][p]$ and $\restrf[n-1][p]$, thus also to $\framep[n][p]$, $\framep[n-1][p]$ and $\framep[n-2][p]$, we built all of these 6 components at the same time.
+But equations were also needed to state the properties of $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ so that we were building by induction on $n+p$ (that is on $n$, using the convention of \citep{hr25}) the following block of information:
+
+\begin{align*}
+  \framep[n][p]      & : \U                                                                                                                 \\
+  \framep[n-1][p]    & :  \U                                                                                                                \\
+  \framep[n-2][p]    & : \U                                                                                                                 \\
+  \restrf[n][p]      & : \Pi q.\, \Pi \omega.\, \framep[n][p] \rightarrow \framep[n-1][p]                                                   \\
+  \restrf[n-1][p]    & : \Pi q.\, \Pi \omega.\, \framep[n-1][p] \rightarrow \framep[n-2][p]                                                 \\                                                                 \\
+  \cohf[n][p]        & : \Pi qr\epsilon\omega.\, \restrf[n-1][p][\epsilon][q] \circ \restrf[n][p][\omega][r] =                              \\
+                     & \;\;\;\;\restrf[n-1][p][\omega][r] \circ \restrf[n][p][\epsilon][q+1]                                                \\
+  \mathsf{hypF0}     & : \framep[n][0]         = \unitpoint
+  \\
+  \mathsf{hypFS0}    & : \framep[n][p+1]       = \Sigma d: \framep[n+1][p]. \Pi \omega.\, \painting[n][p] (\restrf[n+1][p](d))              \\
+  \mathsf{hypPrevF}  & : \framep[n-1][0]                                                                                       = \unitpoint \\
+  \mathsf{hypPrevFS} & : \framep[n-1][p+1] = \Sigma d: \framep[n][p]. \Pi \omega.\, \painting[n-1][p] (\restrf[n][p](d))                    \\
+  \mathsf{hypRF0}    & : \restrf[n][0]        = \ldots \texttt{depending on hypF0}                                                          \\
+  \mathsf{hypRFS}    & : \restrf[n][p+1]      = \ldots \texttt{depending on hypFS and hypPrevFS}                                            \\
+  \ldots             & \;\;\;\;\texttt{fields for painting, restrf, cohp}
+\end{align*}
+
+In the current paper and associated formalisation, we replace the equational properties by definitions, building instead by induction a block of the form:
+
+\begin{align*}
+  \framep[n-2][p] & : \U                                                                                    \\
+  \restrf[n-1][p] & : \Pi q \leq n+p.\, \framep[n-1][p] \rightarrow \framep[n-2][p]                         \\
+  \cohf[n][p]     & : \Pi qr\epsilon\omega.\, \restrf[n-1][p][\epsilon][q] \circ \restrf[n][p][\omega][r] = \\
+                  & \;\;\;\;\restrf[n-1][p][\omega][r] \circ \restrf[n][p][\epsilon][q+1]                   \\
+  \ldots          & \;\;\;\;\texttt{fields for painting, restrf, cohp}
+\end{align*}
+where $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ are now appropriate definitions.
+
+Turning $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ into definitions is however tricky: the definition of $\framep[n-1][p]$, which is by induction on $p$ (for all $n$), depends on $\restrf[n-1][p]$ whose type depends on $\framep[n][p-1]$.
+This means that $\framep[n-1][p]$ and the type of $\restrf[n-1][p]$ have to be mutually defined.
 

### 2025-10-12 paper/paper.tex
paper: skeleton progress

@@
 \newcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
-\newcommandx{\frametype}[2][1,2]{\prim{frametype}[][][#2][][]}
 \newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
 \newcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
-\newcommandx{\paintingtype}[2][1,2]{\prim{paintingtype}[][][#2][][]}
-\newcommandx{\restrftype}[2][1,2]{\prim{restrftype}[][][#2][][]}
 \newcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
@@
 \newcommandx{\cohp}{\coh{painting}[][][][][][][][]}
-\newcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
 \newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}
+
+\newcommandx{\frametype}[2][1,2]{\prim{frametype}[][#1][#2][][]}
+\newcommandx{\layertype}[2][1,2]{\prim{layertype}[][#1][#2][][]}
+\newcommandx{\paintingtype}[2][1,2]{\prim{paintingtype}[][#1][#2][][]}
+\newcommandx{\restrftype}[2][1,2]{\prim{restrftype}[][#1][#2][][]}
+\newcommandx{\restrltype}[2][1,2]{\prim{restrltype}[][#1][#2][][]}
+\newcommandx{\restrptype}[2][1,2]{\prim{restrptype}[][#1][#2][][]}
+\newcommandx{\cohftype}[2][1,2]{\prim{cohftype}[][#1][#2][][]}
+\newcommandx{\cohltype}[2][1,2]{\prim{cohltype}[][#1][#2][][]}
+\newcommandx{\cohptype}[2][1,2]{\prim{cohptype}[][#1][#2][][]}
+
+\newcommandx{\deps}[2][1,2]{\prim{deps}[][#1][#2][][]}
+\newcommandx{\extradeps}[2][1,2]{\prim{deps}[][#1][#2][][]}
+\newcommandx{\depstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
+\newcommandx{\extradepstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
 
@@
     \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n+1][0,...,p-1](\framep[n+1][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
+    \layertype[n][p]          & \framep[n][p]                                & :      & Type_{l+1}                                                                                       \\
   \end{array}
@@
                   \restrf[n+1][0,...,p-1]   \\
-                \end{array}\right)     ,                     \\
+                \end{array}\right), \\
               \Sigma d:\framep[n+1][0,...,p]
@@
                 \end{array}\right).\, \\
-              \quad \Pi\omega.\,\painting[n][p](\restrf[n][p](d)) \\
+              \quad \layer[n][p]
+              \left(\begin{array}{l}
+                  \framep[n+1][0,...,p-1]   \\
+                  \painting[n+1][0,...,p-1] \\
+                  \restrf[n+1][0,...,p-1]   \\
+                \end{array}\right) \\
             \end{array}\right)                   \\
@@
     \end{array} \\
+    \layer[n][p]                  &
+    \left(\begin{array}{l}
+              \framep[n][0,...,p]     \\
+              \painting[n][0,...,p]   \\
+              \restrf[n+1][0,...,p-1] \\
+            \end{array}\right)    & \defeq &
+    \Pi\omega.\,\painting[n][p](\restrf[n][p](d))
   \end{array}
 \end{equation*}
+
+At this stage, it is convenient to use an abbreviation to combine a $\framep$, a $\painting$ and a $\restrf$ in one block, which we call deps:
+
+\begin{align*}
+  \deps[n][0,..,p-1] \defeq
+  \left(\begin{array}{l}
+            \framep[n][0,...,p-1] :\frametype[n][0,...,p-1]      \\
+            \painting[n][0,...,p-1] :\paintingtype[n][0,...,p-1] \\
+            \restrf[n][0,...,p-1]  :\restrftype[n][0,...,p-1]    \\
+          \end{array}\right)
+\end{align*}
+so that $\framep[n][0,...,p]$ has type $\deps[n][0,..,p-1] \rightarrow \frametype[n][0,...,p]$.
 
@@
 
+At this stage, it is also convenient to use an abbreviation to combine the extra parts of $\framep$, a $\painting$ and a $\restrf$ in one block, which we call $\extradeps[n][p,...,n-1]$:
+
+\begin{align*}
+  \extradeps[n][p,..,n-1] (\deps[n][0,...,p-1]) \defeq
+  \left(\begin{array}{l}
+            \framep[n][p,...,n-1] :\frametype[n][p,...,n-1]      \\
+            \painting[n][p,...,n-1] :\paintingtype[n][p,...,n-1] \\
+            \restrf[n][p,...,n-1]  :\restrftype[n][p,...,n-1]    \\
+          \end{array}\right)
+\end{align*}
+
 This allows to define $\painting[n][p]$ formally:
@@
       \left(\begin{array}{l}
-                \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
-                \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
+                \deps[n-1][0,...,p-1]:\depstype[n-1][0,...,p-1]                                \\
                 \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                             \\
-                \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
-                \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
+                \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\deps[n-1][p,...,n-1]) \\
                 \left(\begin{array}{l}
@@
                 \left(\begin{array}{l}
-                    \framep[n-1][0,...,p-1]   \\
-                    \painting[n-1][0,...,p-1] \\
+                    \deps[n-1][0,...,p-1]     \\
                     \framep[n-1][p,...,n-2]   \\
                     \painting[n-1][p,...,n-2] \\
-                    \restrf[n][0,...,p-1]     \\
                   \end{array}\right)                                                \\
@@
 
+\section{...}
+
+We can now define the types of sequences of $\framep$ and $\painting$ as follows:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \frametype[n][0,...,p]    &                                              & :      & Type_{l+1}                                                                                       \\
+    \frametype[n][]           &                                              & \defeq & \unittype                                                                                        \\
+    \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n+1][0,...,p-1] \times Type_l                                                         \\
+    \\
+    \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & Type_{l+1}                                                                                       \\
+    \paintingtype[n][]        & \unitpoint                                   & \defeq & \unittype                                                                                        \\
+    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n+1][0,...,p-1](\framep[n+1][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
+  \end{array}
+\end{equation*}
+
+to do : def of restrptype
+
+Mutual definition of \restrf and cohframetype
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \restrf[n][0,...,p]                                                           &
+    \multicolumn{3}{l}{
+      \left(\begin{array}{l}
+                \deps[n][0,...,p-2]:\depstype[n][0,...,p-2]                                \\
+                \extradeps[n][p-1,...,n]:\extradepstype[n][0,...,p-2](\deps[n][0,...,p-1]) \\
+                \restrp[n][0,...,p-2]:\restrptype[n][0,...,p-1]
+                \left(\begin{array}{l}
+                    \deps[n][0,...,p-1]      \\
+                    \extradeps[n][p-1,...,n] \\
+                  \end{array}\right)                                             \\
+                \cohf[n][0,...,p]:\cohftype[n][0,...,p]
+              \end{array}\right) : \restrftype[n][0,...,p]
+    }                                                                                                                                                         \\
+    \restrf[n][0]                                                                 &
+    \left(\begin{array}{l}
+              \unitpoint \\
+              \unitpoint \\
+              \unitpoint \\
+            \end{array}\right)                                                        & \defeq & (\unitpoint,\lambda q. \lambda\epsilon. \lambda \_.\unitpoint) \\
+    \restrf[n][0,...,p+1]                                                         &
+    \left(\begin{array}{l}
+              \deps[n][0,...,p]        \\
+              \extradeps[n][p-1,...,n] \\
+              \restrp[n][0,...,p]      \\
+              \cohf[n][0,...,p]        \\
+            \end{array}\right)                                                   & \defeq &
+    \begin{array}{l}
+      \restrf[n+1][0,...,p]
+      \left(\begin{array}{l}
+                \deps[n+1][0,...,p-1]    \\
+                \extradeps[n][p-1,...,n] \\
+                \restrp[n+1][0,...,p-1]  \\
+                \cohf[n+1][0,...,p-1]    \\
+              \end{array}\right)     ,                                            \\
+      \lambda q.\lambda \epsilon.\lambda (\framep[n+1][0,...,p], \layer[n][p]). \\
+      \left(\restrf[n][0,...,p]
+      \left(\begin{array}{l}
+                  \deps[n+1][0,...,p-1]    \\
+                  \extradeps[n][p-1,...,n] \\
+                  \restrp[n+1][0,...,p-1]  \\
+                  \cohf[n+1][0,...,p-1]    \\
+                \end{array}\right), \restrl[n][p](...)(l)\right)                    \\
+    \end{array}                                                                  \\
+    \cohftype[n][0,...,p-1]                                                       &
+    \multicolumn{3}{l}{
+      \left(\begin{array}{l}
+                \deps[n][0,...,p-1]:\depstype[n][0,...,p-1]                                \\
+                \extradeps[n][p-1,...,n]:\extradepstype[n][0,...,p-2](\deps[n][0,...,p-1]) \\
+                \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1])       \\
+              \end{array}\right) : Type_{l}
+    }                                                                                                                                                         \\
+    \cohftype[n][0,...,0-1]                                                       &
+    \left(\begin{array}{l}
+              \unitpoint \\
+              \unitpoint \\
+              \unitpoint \\
+            \end{array}\right)                                                        & \defeq &
+    \unittype                                                                                                                                                 \\
+    \cohftype[n][0,...,(p+1)-1]                                                   &
+    \left(\begin{array}{l}
+              \deps[n][0,...,p]        \\
+              \extradeps[n][p-1,...,n] \\
+              \restrp[n][0,...,p]      \\
+            \end{array}\right)                                                   & \defeq &
+    \begin{array}{l}
+      \Sigma \cohf[n+1][0,...,p-1]
+      :\cohftype[n+1][0,...,p-1]
+      \left(\begin{array}{l}
+                \deps[n+1][0,...,p-1]    \\
+                \extradeps[n][p-1,...,n] \\
+                \restrp[n+1][0,...,p-1]  \\
+              \end{array}\right)                         .     \\
+      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
+      \restrf[n][p][q][\epsilon](\restrf[n+1][p][r][\omega]
+      \left(\begin{array}{l}
+                \deps[n+1][0,...,p-1]    \\
+                \extradeps[n][p-1,...,n] \\
+                \restrp[n+1][0,...,p-1]  \\
+              \end{array}\right)(d)) =                         \\
+      \restrf[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon]
+      \left(\begin{array}{l}
+                \deps[n+1][0,...,p-1]    \\
+                \extradeps[n][p-1,...,n] \\
+                \restrp[n+1][0,...,p-1]  \\
+              \end{array}\right)(d))                         \\
+    \end{array}                                                                                     \\
+    \restrl[n][p][q][\epsilon]                                                    &
+    \left(\begin{array}{l}
+              \deps[n][0,...,p]:\depstype[n][0,...,p]                                    \\
+              \extradeps[n][p-1,...,n]:\extradepstype[n][0,...,p-2](\deps[n][0,...,p-1]) \\
+              \cohf[n][0,...,p]:\cohftype[n][0,...,p]                                    \\
+              \layer[n+1][p]:\layertype[n+1][p]                                          \\
+            \end{array}\right) & :      &
+    \layer[n][p]                                                                                                                                              \\
+    \restrl[n][p][q][\epsilon]                                                    &
+    \left(\begin{array}{l}
+              \deps[n][0,...,p]        \\
+              \extradeps[n][p-1,...,n] \\
+              \cohf[n][0,...,p]        \\
+              \layer[n][p]             \\
+            \end{array}\right)                                                   & \defeq &
+    \lambda\omega.\,\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega]}{\restrp[n][p](\layer[n][p])}                                                         \\
+  \end{array}
+\end{equation*}
+
 \bibliographystyle{msclike}

### 2025-10-19 paper/paper.tex
paper: progress

@@
 
+\newcommandx{\cohtwo}[9][2,3,4,5,6,7,8,9]{
+  \ensuremath{\mathsf{\color{chestnut}{coh2}}_{
+    \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4][#5][#6]}^{\joinargs[#7][#8]}}
+  \setkeys*[bonak]{coh#1}{#9}
+}
+
 % Simplicial and Cubical sets
@@
 \newcommandx{\cohptype}[2][1,2]{\prim{cohptype}[][#1][#2][][]}
+\newcommandx{\cohttype}[2][1,2]{\prim{cohttype}[][#1][#2][][]}
 
@@
 \newcommandx{\extradeps}[2][1,2]{\prim{deps}[][#1][#2][][]}
+\newcommandx{\depscohs}[2][1,2]{\prim{depscohs}[][#1][#2][][]}
+\newcommandx{\extradepscohs}[2][1,2]{\prim{depscohs}[][#1][#2][][]}
 \newcommandx{\depstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
 \newcommandx{\extradepstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
+\newcommandx{\depscohstype}[2][1,2]{\prim{depscohstype}[][#1][#2][][]}
+\newcommandx{\extradepscohstype}[2][1,2]{\prim{depscohstype}[][#1][#2][][]}
+
+\newcommandx{\coht}[6][1,2,3,4,5,6]{\cohtwo{frame}[][#3][#4][#5][#6][#1,#2][][]}
 
@@
 
-At this stage, it is convenient to use an abbreviation to combine a $\framep$, a $\painting$ and a $\restrf$ in one block, which we call deps:
+At this stage, it is convenient to use an abbreviation to combine sequences $\framep[n][0,..,p-1]$, $\painting[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$ in one block, which we call $\deps[n][0,...p-1]$:
 
@@
             \framep[n][0,...,p-1] :\frametype[n][0,...,p-1] \\
-            \painting[n][0,...,p-1] :\paintingtype[n][0,...,p-1] \\
-            \restrf[n][0,...,p-1]  :\restrftype[n][0,...,p-1]    \\
+            \painting[n][0,...,p-1] :\paintingtype[n][0,...,p-1]
+            (\framep[n][0,...,p-1])                         \\
+            \restrf[n][0,...,p-1]  :\restrftype[n][0,...,p-1]
+            \left(\begin{array}{l}
+                \framep[n][0,...,p-1]   \\
+                \painting[n][0,...,p-1] \\
+              \end{array}\right)                   \\
           \end{array}\right)
@@
 so that $\framep[n][0,...,p]$ has type $\deps[n][0,..,p-1] \rightarrow \frametype[n][0,...,p]$.
+Later, we shall write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the corresponding projections of a $\deps$.
 
@@
       \left(\begin{array}{l}
-                \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
-                \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
+                \deps[n-1][0,...,p-1]:\depstype[n-1][0,...,p-1]                                  \\
                 \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
                 \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
-                \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
-                \left(\begin{array}{l}
-                    \framep[n-1][0,...,p-1]   \\
-                    \painting[n-1][0,...,p-1] \\
-                  \end{array}\right)                                                  \\
               \end{array}\right) : Type_{l}
@@
     \left(\begin{array}{l}
-              \framep[n-1][0,...,n-1]   \\
-              \painting[n-1][0,...,n-1] \\
+              \deps[n-1][0,...,n-1] \\
               \unitpoint            \\
               \unitpoint            \\
-              \restrp[n][0,...,n-1]     \\
             \end{array}\right)       & \defeq                                       & \unittype                                                                                                \\
@@
     \left(\begin{array}{l}
-              \framep[n-1][0,...,p-1]   \\
-              \painting[n-1][0,...,p-1] \\
+              \deps[n-1][0,...,p-1]     \\
               \framep[n-1][p,...,n-1]   \\
               \painting[n-1][p,...,n-1] \\
-              \restrf[n][0,...,p-1]     \\
             \end{array}\right)
@@
       \left(\begin{array}{l}
-                \framep[n-1][0,...,p-1]   \\
-                \painting[n-1][0,...,p-1] \\
-                \restrf[n][0,...,p-1]     \\
+                \deps[n-1][0,...,p-1] \\
               \end{array}\right)
@@
       \left(\begin{array}{l}
-                \framep[n-1][0,...,p]       \\
-                \painting[n-1][0,...,p]     \\
+                \deps[n-1][0,...,p]         \\
                 \framep[n-1][p+1,...,n-1]   \\
                 \painting[n-1][p+1,...,n-1] \\
-                \restrf[n][0,...,p]         \\
               \end{array}\right)
@@
             \framep[n][p,...,n-1] :\frametype[n][p,...,n-1] \\
-            \painting[n][p,...,n-1] :\paintingtype[n][p,...,n-1] \\
-            \restrf[n][p,...,n-1]  :\restrftype[n][p,...,n-1]    \\
+            \painting[n][p,...,n-1] :\paintingtype[n][p,...,n-1]
+            (\framep[n][p,...,n-1])                         \\
+            \restrf[n][p,...,n-1]  :\restrftype[n][p,...,n-1]
+            \left(\begin{array}{l}
+                \deps[n-1][0,...,p]         \\
+                \framep[n-1][p+1,...,n-1]   \\
+                \painting[n-1][p+1,...,n-1] \\
+              \end{array}\right)               \\
           \end{array}\right)
@@
                 \deps[n-1][0,...,p-1]:\depstype[n-1][0,...,p-1]           \\
-                \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                             \\
-                \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\deps[n-1][p,...,n-1]) \\
-                \left(\begin{array}{l}
-                    \framep[n-1][0,...,p-1]   \\
-                    \painting[n-1][0,...,p-1] \\
-                  \end{array}\right)                                                \\
-                \restrf[n][p,...,n-1]:\restrftype[n][p,...,n-1]
-                \left(\begin{array}{l}
-                    \deps[n-1][0,...,p-1]     \\
-                    \framep[n-1][p,...,n-2]   \\
-                    \painting[n-1][p,...,n-2] \\
-                  \end{array}\right)                                                \\
+                \extradeps[n-1][p,...,n-1]:\extradepstype[n-1][p,...,n-1] \\
                 E:\framep[n-1][n-1]\rightarrow Type_l                     \\
@@
     \left(\begin{array}{l}
-              \framep[n-1][0,...,n-1]   \\
-              \painting[n-1][0,...,n-1] \\
-              \unitpoint                \\
-              \unitpoint                \\
-              \restrp[n][0,...,n-1]     \\
+              \deps[n-1][0,...,n-1] \\
               \unitpoint            \\
@@
     \left(\begin{array}{l}
-              \framep[n-1][0,...,p-1]   \\
-              \painting[n-1][0,...,p-1] \\
-              \framep[n-1][p,...,n-1]   \\
-              \painting[n-1][p,...,n-1] \\
-              \restrf[n][0,...,p-1]     \\
-              \restrf[n][p,...,n-1]     \\
+              \deps[n-1][0,...,p-1]      \\
+              \extradeps[n-1][p,...,n-1] \\
               E                          \\
@@
               \Sigma l:(\Pi q\leq n.\,\Pi \omega.\
-              \painting[n-1][0,...,p](\restrf[n][p](d))). \\
+              \deps.\painting[n-1][0,...,p](\extradeps.\restrf[n][p](d))). \\
               \painting[n][p+1,...,n-1]
               \left(\begin{array}{l}
-                  \framep[n-1][0,...,p]       \\
-                  \painting[n-1][0,...,p]     \\
-                  \framep[n-1][p+1,...,n-1]   \\
-                  \painting[n-1][p+1,...,n-1] \\
-                  \restrf[n][0,...,p]         \\
-                  \restrf[n][p+1,...,n-1]     \\
+                  \deps[n-1][0,...,p]          \\
+                  \extradeps[n-1][p+1,...,n-1] \\
                   E                            \\
@@
 \section{...}
-
-We can now define the types of sequences of $\framep$ and $\painting$ as follows:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \frametype[n][0,...,p]    &                                              & :      & Type_{l+1}                                                                                       \\
-    \frametype[n][]           &                                              & \defeq & \unittype                                                                                        \\
-    \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n+1][0,...,p-1] \times Type_l                                                         \\
-    \\
-    \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & Type_{l+1}                                                                                       \\
-    \paintingtype[n][]        & \unitpoint                                   & \defeq & \unittype                                                                                        \\
-    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n+1][0,...,p-1](\framep[n+1][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
-  \end{array}
-\end{equation*}
 
@@
                 \deps[n][0,...,p-2]:\depstype[n][0,...,p-2]                                \\
-                \extradeps[n][p-1,...,n]:\extradepstype[n][0,...,p-2](\deps[n][0,...,p-1]) \\
+                \extradeps[n][p-1,...,n]:\extradepstype[n][p-1,...,n](\deps[n][0,...,p-1]) \\
                 \restrp[n][0,...,p-2]:\restrptype[n][0,...,p-1]
@@
                   \cohf[n+1][0,...,p-1]    \\
-                \end{array}\right), \restrl[n][p](...)(l)\right)                    \\
+                \end{array}\right), \restrl[n][p]
+      \left(\begin{array}{l}
+                  \deps[n][0,...,p]        \\
+                  \extradeps[n][p-1,...,n] \\
+                  \layer[n+1][p]           \\
+                  \cohf[n][0,...,p]        \\
+                \end{array}\right) (l)\right)                                       \\
     \end{array}                                                                  \\
@@
                 \deps[n][0,...,p-1]:\depstype[n][0,...,p-1]                                \\
-                \extradeps[n][p-1,...,n]:\extradepstype[n][0,...,p-2](\deps[n][0,...,p-1]) \\
+                \extradeps[n][p-1,...,n]:\extradepstype[n][p-1,...,n](\deps[n][0,...,p-1]) \\
                 \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1])       \\
@@
               \deps[n][0,...,p]:\depstype[n][0,...,p]                                    \\
-              \extradeps[n][p-1,...,n]:\extradepstype[n][0,...,p-2](\deps[n][0,...,p-1]) \\
+              \extradeps[n][p-1,...,n]:\extradepstype[n][p-1,...,n](\deps[n][0,...,p-1]) \\
+              \layer[n+1][p]:\layertype[n+1][p]                                          \\
               \cohf[n][0,...,p]:\cohftype[n][0,...,p]                                    \\
-              \layer[n+1][p]:\layertype[n+1][p]                                          \\
             \end{array}\right) & :      &
-    \layer[n][p]                                                                                                                                              \\
+    \restrltype[n][p]                                                                                                                                         \\
     \restrl[n][p][q][\epsilon]                                                    &
@@
               \extradeps[n][p-1,...,n] \\
+              \layer[n][p]             \\
               \cohf[n][0,...,p]        \\
-              \layer[n][p]             \\
             \end{array}\right)                                                   & \defeq &
     \lambda\omega.\,\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega]}{\restrp[n][p](\layer[n][p])}                                                         \\
+  \end{array}
+\end{equation*}
+
+At this new stage, it is convenient to use an abbreviation to combine sequences $\deps[n][0,..,p-1]$, $\extradeps[n][p,...,n]$, $\restrp[n][0,...,p-1]$ and $\cohf[n][0,...,p-1]$ in one block, which we call $\depscohs[n][0,...p-1]$:
+
+\begin{align*}
+  \depscohs[n][0,..,p-1] \defeq
+  \left(\begin{array}{l}
+            \deps[n][0,...,p-1] :\depstype[n][0,...,p-1]    \\
+            \extradeps[n][0,...,p-1] :\extradepstype[n][p-1,...,n]
+            (\deps[n][0,...,p-1])                           \\
+            \restrp[n][0,...p-1]: \restrptype[n][0,...,p-1] \\
+            \cohf[n][0,...,p-1]: \cohftype[n][0,...,p-1]    \\
+          \end{array}\right)
+\end{align*}
+so that $\restrf[n][0,...,p]$ has type $\depscohs[n][0,..,p-1] \rightarrow \restrftype[n][0,...,p]$.
+Later, we shall write $\depscohs.\deps$, $\depscohs.\extradeps$, $\depscohs.\restrp$, and $\depscohs.\cohf$ for the corresponding projections of a $\depscohs$.
+
+\section{...}
+
+to do : def of cohptype
+
+Definition of \cohf, using $\UIP$ to solve the dependency in $\coht$.
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \cohf[n][0,...,p]                                                                         &
+    \multicolumn{3}{l}{
+      \left(\begin{array}{l}
+                \depscohs[n][0,...,p-2]:\depstype[n][0,...,p-2]                                \\
+                \extradepscohs[n][p-1,...,n]:\extradepstype[n][p-1,...,n](\deps[n][0,...,p-1]) \\
+                \cohp[n][0,...,p-2]:\restrptype[n][0,...,p-1]
+                \left(\begin{array}{l}
+                    \depscohs[n][0,...,p-1]      \\
+                    \extradepscohs[n][p-1,...,n] \\
+                  \end{array}\right)                                             \\
+                \coht[n][0,...,p]:\cohttype[n][0,...,p]
+              \end{array}\right) : \cohftype[n][0,...,p]
+    }                                                                                                                                                                                        \\
+    \cohf[n][0]                                                                               &
+    \left(\begin{array}{l}
+              \unitpoint \\
+              \unitpoint \\
+              \unitpoint \\
+            \end{array}\right)                                                                    & \defeq & (\unitpoint,\lambda q.\lambda r. \lambda\epsilon. \lambda\omega.\lambda \_.\refl) \\
+    \cohf[n][0,...,p+1]                                                                       &
+    \left(\begin{array}{l}
+              \depscohs[n][0,...,p]        \\
+              \extradepscohs[n][p-1,...,n] \\
+              \cohp[n][0,...,p]            \\
+              \coht[n][0,...,p]            \\
+            \end{array}\right)                                                           & \defeq &
+    \begin{array}{l}
+      \cohf[n+1][0,...,p]
+      \left(\begin{array}{l}
+                \depscohs[n+1][0,...,p-1]    \\
+                \extradepscohs[n][p-1,...,n] \\
+                \cohp[n+1][0,...,p-1]        \\
+                \coht[n+1][0,...,p-1]        \\
+              \end{array}\right)     ,                                                                            \\
+      (\cohf[n+1][0,...,p], \lambda q.\lambda r.\lambda \epsilon.\lambda \omega.\lambda (\cohf[n][p],\cohl[n][p])). \\
+      \left(\cohf[n][0,...,p]
+      \left(\begin{array}{l}
+                  \depscohs[n+1][0,...,p-1]    \\
+                  \extradepscohs[n][p-1,...,n] \\
+                  \cohp[n+1][0,...,p-1]        \\
+                  \coht[n+1][0,...,p-1]        \\
+                \end{array}\right), \restrl[n][p]
+      \left(\begin{array}{l}
+                  \depscohs[n][0,...,p]        \\
+                  \extradepscohs[n][p-1,...,n] \\
+                  \layer[n+1][p]               \\
+                  \cohf[n][0,...,p]            \\
+                \end{array}\right) (l)\right)                                                                           \\
+    \end{array}                                                                 \\
+    \cohttype[n][0,...,p-1]                                                                   &
+    \multicolumn{3}{l}{
+      \left(\begin{array}{l}
+                \depscohs[n][0,...,p-1]:\depscohstype[n][0,...,p-1]                                    \\
+                \extradepscohs[n][p-1,...,n]:\extradepscohstype[n][p-1,...,n](\depscohs[n][0,...,p-1]) \\
+                \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\depscohs[n][0,...,p-1])               \\
+              \end{array}\right) : Type_{l}
+    }                                                                                                                                                                                        \\
+    \cohttype[n][0,...,0-1]                                                                   &
+    \left(\begin{array}{l}
+              \unitpoint \\
+              \unitpoint \\
+              \unitpoint \\
+            \end{array}\right)                                                                    & \defeq &
+    \unittype                                                                                                                                                                                \\
+    \cohttype[n][0,...,(p+1)-1]                                                               &
+    \left(\begin{array}{l}
+              \depscohs[n][0,...,p]        \\
+              \extradepscohs[n][p-1,...,n] \\
+              \restrp[n][0,...,p]          \\
+            \end{array}\right)                                                           & \defeq &
+    \begin{array}{l}
+      \Sigma \coht[n+1][0,...,p-1]
+      :\cohttype[n+1][0,...,p-1]
+      \left(\begin{array}{l}
+                \depscohs[n+1][0,...,p-1]    \\
+                \extradepscohs[n][p-1,...,n] \\
+                \restrp[n+1][0,...,p-1]      \\
+              \end{array}\right)                         .     \\
+      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
+      \cohf[n][p][q][\epsilon](\cohf[n+1][p][r][\omega]
+      \left(\begin{array}{l}
+                \depscohs[n+1][0,...,p-1]    \\
+                \extradepscohs[n][p-1,...,n] \\
+                \restrp[n+1][0,...,p-1]      \\
+              \end{array}\right)(d)) =                     \\
+      \cohf[n][p][r][\omega](\cohf[n+1][p][q+1][\epsilon]
+      \left(\begin{array}{l}
+                \depscohs[n+1][0,...,p-1]    \\
+                \extradepscohs[n][p-1,...,n] \\
+                \restrp[n+1][0,...,p-1]      \\
+              \end{array}\right)(d))                     \\
+    \end{array}                                                                                                                    \\
+    \cohl[n][p][q][\epsilon]                                                                  &
+    \left(\begin{array}{l}
+              \depscohs[n][0,...,p]:\depscohstype[n][0,...,p]                                        \\
+              \extradepscohs[n][p-1,...,n]:\extradepscohstype[n][p-1,...,n](\depscohs[n][0,...,p-1]) \\
+              \cohp[n+1][p]:\cohptype[n+1][p]                                                        \\
+              \coht[n][0,...,p]:\cohttype[n][0,...,p]                                                \\
+            \end{array}\right) & :      &
+    \begin{array}{l}
+      \Pi d.\Pi l. \overrightarrow{\cohf[n][p][r+1][q+1][\epsilon][\omega]}{\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l))} = \\
+      \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))
+    \end{array}                                                                                                         \\
+    \cohl[n][p][q][\epsilon][r][\omega]                                                       &
+    \left(\begin{array}{l}
+              \depscohs[n][0,...,p]        \\
+              \extradepscohs[n][p-1,...,n] \\
+              \cohp[n][p]                  \\
+              \cohf[n][0,...,p]            \\
+            \end{array}\right)                                                           & \defeq &
+    \lambda d. \lambda l. \lambda \theta. (\cohp[n][p][q][\epsilon][r][\omega](l))                                                                                                           \\
   \end{array}

### 2025-10-26 paper/paper.tex
paper: strip extradeps(cohs)

@@
 \newcommandx{\deps}[2][1,2]{\prim{deps}[][#1][#2][][]}
-\newcommandx{\extradeps}[2][1,2]{\prim{deps}[][#1][#2][][]}
 \newcommandx{\depscohs}[2][1,2]{\prim{depscohs}[][#1][#2][][]}
-\newcommandx{\extradepscohs}[2][1,2]{\prim{depscohs}[][#1][#2][][]}
 \newcommandx{\depstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
-\newcommandx{\extradepstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
 \newcommandx{\depscohstype}[2][1,2]{\prim{depscohstype}[][#1][#2][][]}
-\newcommandx{\extradepscohstype}[2][1,2]{\prim{depscohstype}[][#1][#2][][]}
 
@@
                 \painting[n+1][0,...,p-1] \\
-              \end{array}\right)                         .  \\
+              \end{array}\right).                     \\
       \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]
@@
 
-At this stage, it is also convenient to use an abbreviation to combine the extra parts of $\framep$, a $\painting$ and a $\restrf$ in one block, which we call $\extradeps[n][p,...,n-1]$:
-
-\begin{align*}
-  \extradeps[n][p,..,n-1] (\deps[n][0,...,p-1]) \defeq
-  \left(\begin{array}{l}
-            \framep[n][p,...,n-1] :\frametype[n][p,...,n-1] \\
-            \painting[n][p,...,n-1] :\paintingtype[n][p,...,n-1]
-            (\framep[n][p,...,n-1])                         \\
-            \restrf[n][p,...,n-1]  :\restrftype[n][p,...,n-1]
-            \left(\begin{array}{l}
-                \deps[n-1][0,...,p]         \\
-                \framep[n-1][p+1,...,n-1]   \\
-                \painting[n-1][p+1,...,n-1] \\
-              \end{array}\right)               \\
-          \end{array}\right)
-\end{align*}
-
 This allows to define $\painting[n][p]$ formally:
@@
       \left(\begin{array}{l}
-                \deps[n-1][0,...,p-1]:\depstype[n-1][0,...,p-1]           \\
-                \extradeps[n-1][p,...,n-1]:\extradepstype[n-1][p,...,n-1] \\
+                \deps[n-1][0,...,n-1]:\depstype[n-1][0,...,n-1] \\
                 E:\framep[n-1][n-1]\rightarrow Type_l           \\
@@
               \deps[n-1][0,...,n-1] \\
-              \unitpoint            \\
               E                     \\
@@
     \left(\begin{array}{l}
-              \deps[n-1][0,...,p-1]      \\
-              \extradeps[n-1][p,...,n-1] \\
+              \deps[n-1][0,...,n-1] \\
               E                     \\
@@
     \left(\begin{array}{l}
-              \Sigma l:(\Pi q\leq n.\,\Pi \omega.\
-              \deps.\painting[n-1][0,...,p](\extradeps.\restrf[n][p](d))). \\
+              \Sigma l:\layer(\deps[n-1][0,...,p-1]). \\
               \painting[n][p+1,...,n-1]
               \left(\begin{array}{l}
-                  \deps[n-1][0,...,p]          \\
-                  \extradeps[n-1][p+1,...,n-1] \\
+                  \deps[n-1][0,...,n-1] \\
                   E                     \\
@@
       \left(\begin{array}{l}
-                \deps[n][0,...,p-2]:\depstype[n][0,...,p-2]                                \\
-                \extradeps[n][p-1,...,n]:\extradepstype[n][p-1,...,n](\deps[n][0,...,p-1]) \\
+                \deps[n][0,...,n]:\depstype[n][0,...,n] \\
                 \restrp[n][0,...,p-2]:\restrptype[n][0,...,p-1]
                 \left(\begin{array}{l}
-                    \deps[n][0,...,p-1]      \\
-                    \extradeps[n][p-1,...,n] \\
+                    \deps[n][0,...,n] \\
                   \end{array}\right)                \\
@@
               \unitpoint \\
-              \unitpoint \\
             \end{array}\right)                     & \defeq & (\unitpoint,\lambda q. \lambda\epsilon. \lambda \_.\unitpoint) \\
@@
     \left(\begin{array}{l}
-              \deps[n][0,...,p]        \\
-              \extradeps[n][p-1,...,n] \\
+              \deps[n][0,...,n]   \\
               \restrp[n][0,...,p] \\
@@
       \left(\begin{array}{l}
-                \deps[n+1][0,...,p-1]    \\
-                \extradeps[n][p-1,...,n] \\
+                \deps[n+1][0,...,n]     \\
                 \restrp[n+1][0,...,p-1] \\
                 \cohf[n+1][0,...,p-1]   \\
-              \end{array}\right)     ,                                            \\
+              \end{array}\right),                                             \\
       \lambda q.\lambda \epsilon.\lambda (\framep[n+1][0,...,p], \layer[n][p]). \\
@@
       \left(\begin{array}{l}
-                  \deps[n+1][0,...,p-1]    \\
-                  \extradeps[n][p-1,...,n] \\
+                  \deps[n+1][0,...,n]     \\
                   \restrp[n+1][0,...,p-1] \\
@@
       \left(\begin{array}{l}
-                  \deps[n][0,...,p]        \\
-                  \extradeps[n][p-1,...,n] \\
+                  \deps[n][0,...,n] \\
                   \layer[n+1][p]    \\
@@
       \left(\begin{array}{l}
-                \deps[n][0,...,p-1]:\depstype[n][0,...,p-1]                                \\
-                \extradeps[n][p-1,...,n]:\extradepstype[n][p-1,...,n](\deps[n][0,...,p-1]) \\
+                \deps[n][0,...,n]:\depstype[n][0,...,n]                              \\
                 \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1]) \\
@@
               \unitpoint \\
-              \unitpoint \\
             \end{array}\right)                     & \defeq &
@@
       \left(\begin{array}{l}
-                \deps[n+1][0,...,p-1]    \\
-                \extradeps[n][p-1,...,n] \\
+                \deps[n+1][0,...,n]     \\
                 \restrp[n+1][0,...,p-1] \\
-              \end{array}\right)                         .     \\
+              \end{array}\right).                          \\
       \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
@@
       \left(\begin{array}{l}
-                \deps[n+1][0,...,p-1]    \\
-                \extradeps[n][p-1,...,n] \\
+                \deps[n+1][0,...,n]     \\
                 \restrp[n+1][0,...,p-1] \\
@@
     \left(\begin{array}{l}
-              \deps[n][0,...,p]:\depstype[n][0,...,p]                                    \\
-              \extradeps[n][p-1,...,n]:\extradepstype[n][p-1,...,n](\deps[n][0,...,p-1]) \\
+              \deps[n][0,...,n]:\depstype[n][0,...,p] \\
               \layer[n+1][p]:\layertype[n+1][p]       \\
@@
     \left(\begin{array}{l}
-              \deps[n][0,...,p]        \\
-              \extradeps[n][p-1,...,n] \\
+              \deps[n][0,...,n] \\
               \layer[n][p]      \\
@@
 
-At this new stage, it is convenient to use an abbreviation to combine sequences $\deps[n][0,..,p-1]$, $\extradeps[n][p,...,n]$, $\restrp[n][0,...,p-1]$ and $\cohf[n][0,...,p-1]$ in one block, which we call $\depscohs[n][0,...p-1]$:
+At this new stage, it is convenient to use an abbreviation to combine sequences $\deps[n][0,..,n]$, $\restrp[n][0,...,p-1]$ and $\cohf[n][0,...,p-1]$ in one block, which we call $\depscohs[n][0,...p-1]$:
 
 \begin{align*}
-  \depscohs[n][0,..,p-1] \defeq
+  \depscohstype[n][0,..,p-1] \defeq
   \left(\begin{array}{l}
-            \deps[n][0,...,p-1] :\depstype[n][0,...,p-1]    \\
-            \extradeps[n][0,...,p-1] :\extradepstype[n][p-1,...,n]
-            (\deps[n][0,...,p-1])                           \\
+            \deps[n][0,...,n] :\depstype[n][0,...,n]        \\
             \restrp[n][0,...p-1]: \restrptype[n][0,...,p-1] \\
@@
 \end{align*}
-so that $\restrf[n][0,...,p]$ has type $\depscohs[n][0,..,p-1] \rightarrow \restrftype[n][0,...,p]$.
-Later, we shall write $\depscohs.\deps$, $\depscohs.\extradeps$, $\depscohs.\restrp$, and $\depscohs.\cohf$ for the corresponding projections of a $\depscohs$.
+so that the type of $\restrf[n][0,...,p]$ can be rephrased as $\depscohs[n][0,..,p-1] \rightarrow \restrftype[n][0,...,p]$.
+Later, we shall write $\depscohs.\deps$, $\depscohs.\restrp$, and $\depscohs.\cohf$ for the corresponding projections of a $\depscohs$.
 
@@
       \left(\begin{array}{l}
-                \depscohs[n][0,...,p-2]:\depstype[n][0,...,p-2]                                \\
-                \extradepscohs[n][p-1,...,n]:\extradepstype[n][p-1,...,n](\deps[n][0,...,p-1]) \\
+                \depscohs[n][0,...,n]:\depscohstype[n][0,...,n] \\
                 \cohp[n][0,...,p-2]:\restrptype[n][0,...,p-1]
                 \left(\begin{array}{l}
-                    \depscohs[n][0,...,p-1]      \\
-                    \extradepscohs[n][p-1,...,n] \\
+                    \depscohs[n][0,...,n] \\
                   \end{array}\right)                     \\
@@
               \unitpoint \\
-              \unitpoint \\
             \end{array}\right)                             & \defeq & (\unitpoint,\lambda q.\lambda r. \lambda\epsilon. \lambda\omega.\lambda \_.\refl) \\
@@
     \left(\begin{array}{l}
-              \depscohs[n][0,...,p]        \\
-              \extradepscohs[n][p-1,...,n] \\
+              \depscohs[n][0,...,n] \\
               \cohp[n][0,...,p]     \\
@@
       \left(\begin{array}{l}
-                \depscohs[n+1][0,...,p-1]    \\
-                \extradepscohs[n][p-1,...,n] \\
+                \depscohs[n+1][0,...,n] \\
                 \cohp[n+1][0,...,p-1]   \\
                 \coht[n+1][0,...,p-1]   \\
-              \end{array}\right)     ,                                                                            \\
+              \end{array}\right),                                                                                 \\
       (\cohf[n+1][0,...,p], \lambda q.\lambda r.\lambda \epsilon.\lambda \omega.\lambda (\cohf[n][p],\cohl[n][p])). \\
@@
       \left(\begin{array}{l}
-                  \depscohs[n+1][0,...,p-1]    \\
-                  \extradepscohs[n][p-1,...,n] \\
+                  \depscohs[n+1][0,...,n] \\
                   \cohp[n+1][0,...,p-1]   \\
@@
       \left(\begin{array}{l}
-                  \depscohs[n][0,...,p]        \\
-                  \extradepscohs[n][p-1,...,n] \\
+                  \depscohs[n][0,...,n] \\
                   \layer[n+1][p]        \\
@@
       \left(\begin{array}{l}
-                \depscohs[n][0,...,p-1]:\depscohstype[n][0,...,p-1]                                    \\
-                \extradepscohs[n][p-1,...,n]:\extradepscohstype[n][p-1,...,n](\depscohs[n][0,...,p-1]) \\
+                \depscohs[n][0,...,n]:\depscohstype[n][0,...,n]                          \\
                 \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\depscohs[n][0,...,p-1]) \\
@@
               \unitpoint \\
-              \unitpoint \\
             \end{array}\right)                             & \defeq &
@@
     \left(\begin{array}{l}
-              \depscohs[n][0,...,p]        \\
-              \extradepscohs[n][p-1,...,n] \\
+              \depscohs[n][0,...,n] \\
               \restrp[n][0,...,p]   \\
@@
       \left(\begin{array}{l}
-                \depscohs[n+1][0,...,p-1]    \\
-                \extradepscohs[n][p-1,...,n] \\
+                \depscohs[n+1][0,...,n] \\
                 \restrp[n+1][0,...,p-1] \\
-              \end{array}\right)                         .     \\
+              \end{array}\right).                          \\
       \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
@@
       \left(\begin{array}{l}
-                \depscohs[n+1][0,...,p-1]    \\
-                \extradepscohs[n][p-1,...,n] \\
+                \depscohs[n+1][0,...,n] \\
                 \restrp[n+1][0,...,p-1] \\
@@
     \left(\begin{array}{l}
-              \depscohs[n][0,...,p]:\depscohstype[n][0,...,p]                                        \\
-              \extradepscohs[n][p-1,...,n]:\extradepscohstype[n][p-1,...,n](\depscohs[n][0,...,p-1]) \\
+              \depscohs[n][0,...,n]:\depscohstype[n][0,...,n] \\
               \cohp[n+1][p]:\cohptype[n+1][p]                 \\
@@
     \left(\begin{array}{l}
-              \depscohs[n][0,...,p]        \\
-              \extradepscohs[n][p-1,...,n] \\
+              \depscohs[n][0,...,n] \\
               \cohp[n][p]           \\

### 2025-10-26 paper/paper.tex
paper: restrl is complex

@@
   \begin{array}{llcl}
-    \frametype[n][0,...,p]    &                                              & :      & Type_{l+1}                                                                                       \\
+    \frametype[n][0,...,p]    &                                              & :      & \U                                                                                           \\
     \frametype[n][]           &                                              & \defeq & \unittype                                                                                    \\
-    \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n+1][0,...,p-1] \times Type_l                                                         \\
+    \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n+1][0,...,p-1] \times \U                                                         \\
     \\
-    \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & Type_{l+1}                                                                                       \\
+    \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & \U                                                                                           \\
     \paintingtype[n][]        & \unitpoint                                   & \defeq & \unittype                                                                                    \\
-    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n+1][0,...,p-1](\framep[n+1][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
-    \layertype[n][p]          & \framep[n][p]                                & :      & Type_{l+1}                                                                                       \\
+    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n+1][0,...,p-1](\framep[n+1][0,...,p-1]) \times (\framep[n][p] \rightarrow \U) \\
   \end{array}
@@
                   \restrf[n+1][0,...,p-1]   \\
-                \end{array}\right) \\
+                \end{array}\right)(d) \\
             \end{array}\right)                                                                                     \\
@@
               \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
-              \end{array}\right) : Type_{l}
+            \end{array}\right) : \U
     }                                                                                                                                    \\
@@
     \end{array}                                                                   \\
+    \layertype[n][p]                                     & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & : \framep[n][p] \rightarrow \U \\
     \layer[n][p]                                         &
     \left(\begin{array}{l}
-              \framep[n][0,...,p]     \\
-              \painting[n][0,...,p]   \\
-              \restrf[n+1][0,...,p-1] \\
+              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
+              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
+              \restrf[n+1][0,...,p-1]:\restrftype[n][0,...,p-1] \\
             \end{array}\right) & \defeq                                       &
-    \Pi\omega.\,\painting[n][p](\restrf[n][p](d))
+    d \mapsto \Pi\omega.\,\painting[n][p](\restrf[n][p](d))
   \end{array}
@@
   \begin{array}{llcl}
-    \frametype[n][p,...,n]         &                                              & :         & Type_{l+1}                                                                                   \\
+    \frametype[n][p,...,n]         &                                              & :         & \U                                                                                       \\
     \frametype[n][]                &                                              & \defeq    & \unittype                                                                                \\
-    \frametype[n][p,...,n]         &                                              & \defeq    & Type_l \times \frametype[n][p+1,...,n-1]                                                     \\
+    \frametype[n][p,...,n]         &                                              & \defeq    & \U \times \frametype[n][p+1,...,n-1]                                                     \\
     \\
-    \paintingtype[n][p,...,n]      & (\framep[n][p,...,n]:\frametype[n][p,...,n]) & :         & Type_{l+1}                                                                                   \\
+    \paintingtype[n][p,...,n]      & (\framep[n][p,...,n]:\frametype[n][p,...,n]) & :         & \U                                                                                       \\
     \paintingtype[n][]             & \unitpoint                                   & \defeq    & \unittype                                                                                \\
-    \paintingtype[n][p,...,n](p<n) & (\framep[n][p,...,n])                        & \defeq    & (\framep[n][p] \rightarrow Type_l) \times \paintingtype[n][p+1,...,n](\framep[n][p+1,...,n]) \\
+    \paintingtype[n][p,...,n](p<n) & (\framep[n][p,...,n])                        & \defeq    & (\framep[n][p] \rightarrow \U) \times \paintingtype[n][p+1,...,n](\framep[n][p+1,...,n]) \\
     \\
@@
               \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
-              \end{array}\right) : Type_{l}
+            \end{array}\right) : \U
     }                                                                                                                                                                                    \\
@@
                 \deps[n-1][0,...,n-1]:\depstype[n-1][0,...,n-1] \\
-                E:\framep[n-1][n-1]\rightarrow Type_l           \\
-              \end{array}\right) : \framep[n-1][n-1]\rightarrow Type_l
+                E:\framep[n-1][n-1]\rightarrow \U               \\
+              \end{array}\right) : \framep[n-1][n-1]\rightarrow \U
     }                                                            \\
@@
 
-to do : def of restrptype
+At this stage, we are able to define $\framep$, $\painting$ and $\restrftype$ from $\deps$ at the previous level.
+To go further, we need to define the sequence $\restrptype$ of types of painting restrictions:
 
-Mutual definition of \restrf and cohframetype
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \restrptype[n][0,...,p] & (\deps[n][0,...,n]:\depstype[n][0,...,n]) & :      & \U                                        \\
+    \restrptype[n][]        & \unitpoint                                & \defeq & \unittype                                 \\
+    \restrptype[n][0,...,p] & (\deps[n][0,...,n])                       & \defeq & \restrptype[n+1][0,...,p-1] \times \left(
+    \begin{array}{l}
+        \deps[n+1][0,...,p-1].                            \\ \Pi q\leq n.\Pi \epsilon.\Pi d:\framep(\deps).\\
+        \painting[n][p](\deps[n][0,...,n])(d) \rightarrow \\ \deps.\painting[n][p](\deps.\restrf[n][p][q][\epsilon](d))\end{array}
+    \right)                                                                                                                  \\
+  \end{array}
+\end{equation*}
+
+Mutual definition of $\restrf$ and $\cohftype$
 
@@
                 \cohf[n][0,...,p]:\cohftype[n][0,...,p]
-              \end{array}\right) : \restrftype[n][0,...,p]
+              \end{array}\right) :
+      \restrftype[n][0,...,p]
+      \left(\begin{array}{l}
+                \deps.\frame[n][0,...,p]    \\
+                \deps.\painting[n][0,...,p] \\
+              \end{array}\right)
     }                                                                                                                      \\
@@
     \left(\begin{array}{l}
+              \unitpoint \\
               \unitpoint \\
@@
             \end{array}\right)                     & \defeq &
-    \begin{array}{l}
+    \left(\begin{array}{l}
               \restrf[n+1][0,...,p]
@@
                 \end{array}\right),              \\
-      \lambda q.\lambda \epsilon.\lambda (\framep[n+1][0,...,p], \layer[n][p]). \\
+              \lambda q.\lambda \epsilon.\lambda (d,l]). \\
               \left(\restrf[n][0,...,p]
@@
                     \cohf[n+1][0,...,p-1]   \\
-                \end{array}\right), \restrl[n][p]
+                  \end{array}\right)(d), \restrl[n][p]
               \left(\begin{array}{l}
@@
                     \cohf[n][0,...,p] \\
-                \end{array}\right) (l)\right)                                       \\
-    \end{array}                                   \\
+                  \end{array}\right)(d)(l)\right)      \\
+            \end{array} \right)                                                            \\
     \cohftype[n][0,...,p-1]                    &
@@
               \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1]) \\
-              \end{array}\right) : Type_{l}
+            \end{array}\right) : \U
     }                                                                                                                      \\
@@
     \end{array}                                                      \\
+    \restrltype[n][p]                          &
+    \left(\begin{array}{l}
+              \deps[n][0,...,n]:\depstype[n][0,...,n] \\
+              \cohf[n][0,...,p]:\cohftype[n][0,...,p] \\
+            \end{array}\right)
+                                               & :      & \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n][p].\left(
+    \begin{array}{l}
+        \layer[n][p]\left(
+        \begin{array}{l}
+            \framep[n][p](\deps[n][0,...,p])   \\
+            \painting[n][p](\deps[n][0,...,n]) \\
+            \restrf[n][p](\deps[n][0,...,p])   \\
+          \end{array}\right)(d) \rightarrow \\
+        \layer[n][p](\deps[n][0,...,n])(\restrf[n][p](d))
+      \end{array}\right)                                                          \\
     \restrl[n][p][q][\epsilon]                 &
     \left(\begin{array}{l}
-              \deps[n][0,...,n]:\depstype[n][0,...,p] \\
-              \layer[n+1][p]:\layertype[n+1][p]       \\
+              \deps[n][0,...,n]:\depstype[n][0,...,n] \\
               \cohf[n][0,...,p]:\cohftype[n][0,...,p] \\
             \end{array}\right) & :      &
-    \restrltype[n][p]                                                                                                      \\
+    \restrltype[n][p] \left(\begin{array}{l}
+                                \deps[n][0,...,n] \\
+                                \cohf[n][0,...,p] \\
+                              \end{array}
+    \right)                                                                                                                \\
     \restrl[n][p][q][\epsilon]                 &
@@
               \deps[n][0,...,n] \\
-              \layer[n][p]      \\
               \cohf[n][0,...,p] \\
             \end{array}\right)                     & \defeq &
-    \lambda\omega.\,\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega]}{\restrp[n][p](\layer[n][p])}                      \\
+    \lambda\omega.\,\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega]}{\restrp[n][p](l \omega)}                          \\
   \end{array}
@@
 
-Definition of \cohf, using $\UIP$ to solve the dependency in $\coht$.
+Definition of $\cohf[n][p]$, using $\UIP$ to solve the dependency in $\coht[n][p]$.
 
@@
               \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\depscohs[n][0,...,p-1]) \\
-              \end{array}\right) : Type_{l}
+            \end{array}\right) : \U
     }                                                                                                                                                 \\

### 2025-10-26 paper/paper.tex
paper: minor corrections
A bit further

@@
     \restrftype[n][0,...,p-1]                                                     &
-    \multicolumn{3}{l}{
     \left(\begin{array}{l}
@@
               \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
-            \end{array}\right) : \U
-    }                                                                                                                                    \\
+            \end{array}\right) & :                                            & \U                                                                                                                    \\
     \restrftype[n][0,...,0-1]                                                     &
@@
     \end{array}                                                                                                                                  \\
-    \layertype[n][p]                                     & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & : \framep[n][p] \rightarrow \U \\
+    \layertype[n][p]                                                              &
+    \left(\begin{array}{l}
+              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
+              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
+              \restrf[n+1][0,...,p-1]:\restrftype[n][0,...,p-1] \\
+            \end{array}\right)                          & :                                            &
+    & :                                     & \Type                        \\
+    \layertype[n][p]                                                              &
+    \left(\begin{array}{l}
+              \framep[n][0,...,p]     \\
+              \painting[n][0,...,p]   \\
+              \restrf[n+1][0,...,p-1] \\
+            \end{array}\right)
+    & \defeq                                & \framep[n][p]
+    \left(\begin{array}{l}
+              \framep[n][0,...,p]     \\
+              \painting[n][0,...,p]   \\
+              \restrf[n+1][0,...,p-1] \\
+            \end{array}\right) \rightarrow \U \\
     \layer[n][p]                                                                  &
@@
               \restrf[n+1][0,...,p-1]:\restrftype[n][0,...,p-1] \\
+            \end{array}\right)                          & :                                            & \layertype[n][p](\framep[n][0,...,p])                                                            \\
+    \layer[n][p]                                                                  &
+    \left(\begin{array}{l}
+              \framep[n][0,...,p]     \\
+              \painting[n][0,...,p]   \\
+              \restrf[n+1][0,...,p-1] \\
             \end{array}\right)                                                    & \defeq                                       &
@@
 \end{align*}
-so that $\framep[n][0,...,p]$ has type $\deps[n][0,..,p-1] \rightarrow \frametype[n][0,...,p]$.
+
+so that the type of $\framep[n][0,...,p]$ can be shortened into $\depstype[n][0,..,p-1] \rightarrow \frametype[n][0,...,p]$ and similarly for $\layertype[n][p]$ and $\layer[n][p]$.
 Later, we shall write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the corresponding projections of a $\deps$.
+By abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depstype[n][0,..,0-1]$.
 
@@
 
-To define $\painting$ formally, we need to define $\framep[n][p,...,n]$, $\painting[n][p,...,n]$ and $\restrf[n][p,...,n]$:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \frametype[n][p,...,n]         &                                              & :         & \U                                                                                       \\
-    \frametype[n][]                &                                              & \defeq    & \unittype                                                                                \\
-    \frametype[n][p,...,n]         &                                              & \defeq    & \U \times \frametype[n][p+1,...,n-1]                                                     \\
-    \\
-    \paintingtype[n][p,...,n]      & (\framep[n][p,...,n]:\frametype[n][p,...,n]) & :         & \U                                                                                       \\
-    \paintingtype[n][]             & \unitpoint                                   & \defeq    & \unittype                                                                                \\
-    \paintingtype[n][p,...,n](p<n) & (\framep[n][p,...,n])                        & \defeq    & (\framep[n][p] \rightarrow \U) \times \paintingtype[n][p+1,...,n](\framep[n][p+1,...,n]) \\
-    \\
-    \restrftype[n][p,...,n]        &
-    \multicolumn{3}{l}{
-      \left(\begin{array}{l}
-              \deps[n-1][0,...,p-1]:\depstype[n-1][0,...,p-1]                                  \\
-              \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
-              \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
-            \end{array}\right) : \U
-    }                                                                                                                                                                                    \\
-    \restrftype[n][]               &
-    \left(\begin{array}{l}
-              \deps[n-1][0,...,n-1] \\
-              \unitpoint            \\
-              \unitpoint            \\
-            \end{array}\right)       & \defeq                                       & \unittype                                                                                            \\
-    \restrftype[n][p,...,n-1]      &
-    \left(\begin{array}{l}
-              \deps[n-1][0,...,p-1]     \\
-              \framep[n-1][p,...,n-1]   \\
-              \painting[n-1][p,...,n-1] \\
-            \end{array}\right)
-                                   & \defeq                                       &
-    \begin{array}{c}
-      \framep[n][p]
-      \left(\begin{array}{l}
-                \deps[n-1][0,...,p-1] \\
-              \end{array}\right)
-      \rightarrow \framep[n-1][p] \\
-      \times                      \\
-      \restrftype[n][p+1,...,n]
-      \left(\begin{array}{l}
-                \deps[n-1][0,...,p]         \\
-                \framep[n-1][p+1,...,n-1]   \\
-                \painting[n-1][p+1,...,n-1] \\
-              \end{array}\right)
-    \end{array}
-  \end{array}
-\end{equation*}
-
-This allows to define $\painting[n][p]$ formally:
+We can now formally define $\painting[n][p]$ by recursion on $n-p$:
 \begin{equation*}
@@
 
-From which we can deduce $\painting[n][0,...,p]$ by recursion on $p$.
+From which we can deduce $\painting[n][0,...,p]$ by a second recursion, this time on $p$:
 
-\section{...}
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \painting[n][0,...,p]          &
+    \multicolumn{3}{l}{
+      \left(\begin{array}{l}
+                \deps[n-1][0,...,n-1]:\depstype[n-1][0,...,n-1] \\
+                E:\framep[n-1][n-1]\rightarrow \U               \\
+              \end{array}\right) : \paintingtype[n][0,...,p](\framep[n][0,...,p](\deps[n-1][0,...,p]))
+    }                                                            \\
+    \painting[n][0,...,0-1]          &
+    \left(\begin{array}{l}
+              \unitpoint \\
+              E                     \\
+            \end{array}\right) & \defeq & \unittype                        \\
+    \painting[n][0,...,p] &
+    \left(\begin{array}{l}
+              \deps[n-1][0,...,p-1] \\
+              E                     \\
+            \end{array}\right) & \defeq &
+       (\painting[n][0,...,p-1]
+       \left(\begin{array}{l}
+           \deps[n-1][0,...,n-1] \\
+           E                     \\
+         \end{array}\right),           \\
+       \painting[n][p]
+       \left(\begin{array}{l}
+           \deps[n-1][0,...,n-1] \\
+           E                     \\
+         \end{array}\right))           \\
+  \end{array}
+\end{equation*}
 
-At this stage, we are able to define $\framep$, $\painting$ and $\restrftype$ from $\deps$ at the previous level.
+At this stage, we are able to define $\framep$, $\painting$ and $\restrftype$ from $\deps$ at the respective previous level.
 To go further, we need to define the sequence $\restrptype$ of types of painting restrictions:
@@
     \restrptype[n][]                           & \unitpoint                                & \defeq & \unittype                                 \\
-    \restrptype[n][0,...,p] & (\deps[n][0,...,n])                       & \defeq & \restrptype[n+1][0,...,p-1] \times \left(
+    \restrptype[n][0,...,p](\deps[n][0,...,n]) & (\deps[n][0,...,n])                       & \defeq & \restrptype[n+1][0,...,p-1] \times \left(
     \begin{array}{l}
-        \deps[n+1][0,...,p-1].                            \\ \Pi q\leq n.\Pi \epsilon.\Pi d:\framep(\deps).\\
+        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep(\deps[n][0,...,p]). \\
         \painting[n][p](\deps[n][0,...,n])(d) \rightarrow          \\ \deps.\painting[n][p](\deps.\restrf[n][p][q][\epsilon](d))\end{array}
@@
 
-Mutual definition of $\restrf$ and $\cohftype$
+Thanks to $\restrptype$, we can mutually define $\restrf$ and $\cohftype$, using abbreviations in passing for $\layer$ and $\layertype$:
 
@@
                 \cohf[n][0,...,p]:\cohftype[n][0,...,p]
+                  \left(\begin{array}{l}
+                      \deps[n][0,...,n] \\
+                      \restrp[n][0,...,p-2] \\
+                    \end{array}\right)                \\
               \end{array}\right) :
@@
       \left(\begin{array}{l}
-                \deps.\frame[n][0,...,p]    \\
+                \deps.\framep[n][0,...,p]   \\
                 \deps.\painting[n][0,...,p] \\
@@
     }                                                                                                                               \\
-    \restrf[n][0]                              &
+    \restrf[n][0,...,0-1]                              &
     \left(\begin{array}{l}
@@
             \end{array}\right)                     & \defeq & (\unitpoint,\lambda q. \lambda\epsilon. \lambda \_.\unitpoint)          \\
-    \restrf[n][0,...,p+1]                      &
+    \restrf[n][0,...,(p+1)-1]                      &
     \left(\begin{array}{l}
@@
     \left(\begin{array}{l}
-              \restrf[n+1][0,...,p]
+              \restrf[n+1][0,...,p][q][\epsilon]
               \left(\begin{array}{l}
@@
                 \end{array}\right),             \\
-              \lambda q.\lambda \epsilon.\lambda (d,l]). \\
-              \left(\restrf[n][0,...,p]
+              \lambda q.\lambda \epsilon.\lambda (d,l). \\
+              \left(\restrf[n][p][q][\epsilon]
               \left(\begin{array}{l}
@@
                     \cohf[n+1][0,...,p-1]   \\
-                  \end{array}\right)(d), \restrl[n][p]
+                  \end{array}\right)(d), \restrl[n][p][q][\epsilon]
               \left(\begin{array}{l}
                     \deps[n][0,...,n] \\
-                    \layer[n+1][p]    \\
                     \cohf[n][0,...,p] \\
@@
       \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
-      \restrf[n][p][q][\epsilon](\restrf[n+1][p][r][\omega]
+      \deps.\restrf[n][p][q][\epsilon](\restrf[n+1][p][r][\omega]
       \left(\begin{array}{l}
@@
               \end{array}\right)(d)) =                         \\
-      \restrf[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon]
+      \deps.\restrf[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon]
       \left(\begin{array}{l}
@@
               \deps[n][0,...,n]:\depstype[n][0,...,n] \\
+              \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1]) \\
               \cohf[n][0,...,p]:\cohftype[n][0,...,p] \\
+            \end{array}\right) & :      & \U                                                                                   \\
+    \restrltype[n][p]                          &
+    \left(\begin{array}{l}
+              \deps[n][0,...,n] \\
+              \restrp[n][0,...,p-1] \\
+              \cohf[n][0,...,p] \\
             \end{array}\right)
-                                               & :      & \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n][p].\left(
+                                               & \defeq & \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n][p].\left(
     \begin{array}{l}
@@
             \painting[n][p](\deps[n][0,...,n]) \\
-            \restrf[n][p](\deps[n][0,...,p])   \\
+            \restrf[n][p]
+            \left(\begin{array}{l}
+              \deps[n][0,...,p]   \\
+              \restrp[n][0,...,p-1] \\
+              \cohf[n][0,...,p]
+            \end{array}\right)           \\
           \end{array}\right)(d) \rightarrow \\
-        \layer[n][p](\deps[n][0,...,n])(\restrf[n][p](d))
+        \deps.layer[n][p](\deps[n][0,...,n])(\restrf[n][p]
+            \left(\begin{array}{l}
+              \deps[n][0,...,p]   \\
+              \restrp[n][0,...,p-1] \\
+              \cohf[n][0,...,p]
+            \end{array}\right)(d))
       \end{array}\right)                                                                   \\
-    \restrl[n][p][q][\epsilon]                 &
+    \restrl[n][p]                              &
     \left(\begin{array}{l}
               \deps[n][0,...,n]:\depstype[n][0,...,n] \\
-              \cohf[n][0,...,p]:\cohftype[n][0,...,p] \\
+              \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1]) \\
+              \cohf[n][0,...,p-1]:\cohftype[n][0,...,p-1] \\
             \end{array}\right) & :      &
@@
     \right)                                                                                                                         \\
-    \restrl[n][p][q][\epsilon]                 &
+    \restrl[n][p]                              &
     \left(\begin{array}{l}
               \deps[n][0,...,n] \\
+              \restrp[n][0,...,p-1] \\
               \cohf[n][0,...,p] \\
             \end{array}\right)                     & \defeq &
-    \lambda\omega.\,\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega]}{\restrp[n][p](l \omega)}                          \\
+    \lambda q\leq n. \lambda \epsilon.\lambda\omega.\,\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega]}{\restrp[n][p](l \omega)} \\
   \end{array}
@@
 
-At this new stage, it is convenient to use an abbreviation to combine sequences $\deps[n][0,..,n]$, $\restrp[n][0,...,p-1]$ and $\cohf[n][0,...,p-1]$ in one block, which we call $\depscohs[n][0,...p-1]$:
+At this new stage, it is convenient to use a new abbreviation to combine sequences of $\deps[n][0,..,n]$, $\restrp[n][0,...,p-1]$ and $\cohf[n][0,...,p-1]$ in one block, which we call $\depscohstype[n][0,...p-1]$:
 
@@
 \end{align*}
-so that the type of $\restrf[n][0,...,p]$ can be rephrased as $\depscohs[n][0,..,p-1] \rightarrow \restrftype[n][0,...,p]$.
-Later, we shall write $\depscohs.\deps$, $\depscohs.\restrp$, and $\depscohs.\cohf$ for the corresponding projections of a $\depscohs$.
+so that the type of $\restrf[n][0,...,p]$ can be rephrased as $\depscohstype[n][0,..,p-1] \rightarrow \restrftype[n][0,...,p]      \left(\begin{array}{l}
+                \deps.\framep[n][0,...,p]   \\
+                \deps.\painting[n][0,...,p] \\
+              \end{array}\right)$, and similarly for $\restrltype$ and $\restrl$.
+Later, we shall write $\depscohs.\deps$, $\depscohs.\restrp$, and $\depscohs.\cohf$ for the corresponding projections of an element $\depscohs$ in $\depscohstype$.
+By abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depscohstype[n][0,..,0-1]$.
+
+It is also convenient to abbreviate:
+
+\begin{align*}
+  \overline{\deps}(\depscohs:\depscohstype) : \depstype\\
+  \overline{\deps}(\depscohs) \defeq
+\left(\begin{array}{l}
+            \framep[n][p](\depscohs.\deps[n][0,...,p])   \\
+            \painting[n][p](\depscohs.\deps[n][0,...,n]) \\
+            \restrf[n][p](\depscohs[n][0,...,p])\\
+      \end{array}\right)\\
+\end{align*}
+
+Armed with $\restrframe$ and $\cohftype$, it is now possible to define
+$\restrp[n][p]$ by recursion on $n-p$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \restrp[n][p]          &
+    \multicolumn{3}{l}{
+      \left(\begin{array}{l}
+                \depscohs[n][0,...,n]:\depscohstype[n][0,...,n] \\
+                E:\framep[n-1][n-1]\rightarrow \U               \\
+                E':\framep[n][n]\rightarrow \U               \\
+      \end{array}\right) & : &
+      \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n][p]
+      \left(\begin{array}{l}
+                \overline{\deps}(\depscohs)\\
+                E':\framep[n][n]\rightarrow \U               \\
+      \end{array}\right).\,
+      \painting[n][p]
+      \left(\begin{array}{l}
+                \overline{\deps}(\depscohs)\\
+                E':\framep[n][n]\rightarrow \U               \\
+      \end{array}\right)(d) \rightarrow
+      \painting[n-1][p]
+      \left(\begin{array}{l}
+                \depscohs[n][0,...,n].\deps\\
+                E:\framep[n-1][n-1]\rightarrow \U               \\
+      \end{array}\right)(\restrf[n][p](\depscohs[n][0,...,n].deps)(d))
+    }                                                            \\
+    \restrp[n][n]          &
+    \left(\begin{array}{l}
+              \depscohs[n][0,...,n] \\
+              E                     \\
+              E'                    \\
+            \end{array}\right) & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon                     \\
+    \restrp[n][p](p<n)     &
+    \left(\begin{array}{l}
+              \depscohs[n][0,...,n] \\
+              E                     \\
+              E'                    \\
+            \end{array}\right) & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
+    \left(\begin{array}{l}
+              \restrl[n][p][q][\epsilon](\depscohs[n-1][0,...,p-1])(l), \\
+              \restrp[n][p][q][\epsilon]
+              \left(\begin{array}{l}
+                  \depscohs[n][0,...,n] \\
+                  E                     \\
+                  E'                    \\
+                \end{array}\right)(\restrf[n][p](\depscohs[n][0,...,p])(d))(c)           \\
+            \end{array}\right) \\
+  \end{array}
+\end{equation*}
+
+From which we can deduce $\restrp[n][0,...,p]$ again by a second recursion, this time on $p$:
+
+...
 
@@
 
-to do : def of cohptype
+At this stage, we are then able to define $\restrf$, $\restrp$ and $\cohftype$
+from $\depscohs$ at the previous level. To go further, we need to define the
+sequence $\cohptype$ of types of painting coherence laws:
 
-Definition of $\cohf[n][p]$, using $\UIP$ to solve the dependency in $\coht[n][p]$.
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \cohptype[n][0,...,p]                    & (\depscohs[n][0,...,n]:\depscohstype[n][0,...,n]) & :      & \U                                        \\
+    \cohptype[n][]                           & \unitpoint                                & \defeq & \unittype                                 \\
+    \cohptype[n][0,...,p](\depscohs[n][0,...,n]) & (\depscohs[n][0,...,n])                       & \defeq & \cohptype[n+1][0,...,p-1] \times \left(
+    \begin{array}{l}
+        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep(\depscohs[n][0,...,p]). \\
+        \painting[n][p](\depscohs[n][0,...,n])(d) \rightarrow          \\ \depscohs.\painting[n][p](\depscohs.\restrf[n][p][q][\epsilon](d))\end{array}
+    \right)                                                                                                                                     \\
+  \end{array}
+\end{equation*}
+
+This is enough to define $\cohf[n][p]$, using $\UIP$ to solve the dependency in $\coht[n][p]$.
 
@@
               \end{array}\right),                                                                                 \\
-      (\cohf[n+1][0,...,p], \lambda q.\lambda r.\lambda \epsilon.\lambda \omega.\lambda (\cohf[n][p],\cohl[n][p])). \\
-      \left(\cohf[n][0,...,p]
+      (\cohf[n+1][0,...,p], \lambda q.\lambda r.\lambda \epsilon.\lambda \omega.\lambda (d,l). \\
+      \left(\cohf[n][0,...,p][q][r][\epsilon][\omega]
       \left(\begin{array}{l}
@@
                   \coht[n+1][0,...,p-1]   \\
-                \end{array}\right), \restrl[n][p]
+                \end{array}\right)(d), \cohl[n][p][q][r][\epsilon][\omega]
       \left(\begin{array}{l}
                   \depscohs[n][0,...,n] \\
-                  \layer[n+1][p]        \\
-                  \cohf[n][0,...,p]     \\
-                \end{array}\right) (l)\right)                                                                           \\
+                  \cohp[n+1][0,...,p-1]   \\
+                  \coht[n][0,...,p]     \\
+                \end{array}\right) (d)(l)\right)                                                                           \\
     \end{array}                          \\
@@
               \depscohs[n][0,...,n]:\depscohstype[n][0,...,n]                          \\
-              \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\depscohs[n][0,...,p-1]) \\
+              \cohp[n][0,...,p-1]:\cohptype[n][0,...,p-1](\depscohs[n][0,...,p-1]) \\
             \end{array}\right) : \U
@@
               \depscohs[n][0,...,n] \\
-              \restrp[n][0,...,p]   \\
+              \cohp[n][0,...,p]   \\
             \end{array}\right)                           & \defeq &
@@
               \end{array}\right).                          \\
-      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
-      \cohf[n][p][q][\epsilon](\cohf[n+1][p][r][\omega]
+      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta \\
+      \depscohs.\cohf[n][p][r][p][\omega][\theta] \circ \cohf[n+1][p][q+1][p][\epsilon][\theta]
       \left(\begin{array}{l}
                 \depscohs[n+1][0,...,n] \\
-                \restrp[n+1][0,...,p-1] \\
-              \end{array}\right)(d)) =                         \\
-      \cohf[n][p][r][\omega](\cohf[n+1][p][q+1][\epsilon]
+                \cohp[n+1][0,...,p-1] \\
+                \coht[n+1][0,...,p-1]
+      \end{array}\right)
+      \circ \depscohs.\cohf[n][p][q][r][\epsilon][\omega] =                         \\
+      \cohf[n+1][p][q+1][r+1][\epsilon][\omega]
         \left(\begin{array}{l}
                 \depscohs[n+1][0,...,n] \\
-                \restrp[n+1][0,...,p-1] \\
-              \end{array}\right)(d))                          \\
+                \cohp[n+1][0,...,p-1] \\
+                \coht[n+1][0,...,p-1]
+        \end{array}\right)
+      \circ \depscohs.\cohf[n][p][q][p][\epsilon][\theta]
+      \circ \cohf[n+1][p][r][p][\omega][\theta]
+            \left(\begin{array}{l}
+                \depscohs[n+1][0,...,n] \\
+                \cohp[n+1][0,...,p-1] \\
+                \coht[n+1][0,...,p-1]
+      \end{array}\right)\\
     \end{array}                                                                                 \\
-    \cohl[n][p][q][\epsilon]                           &
+    \cohl[n][p]                           &
     \left(\begin{array}{l}
@@
     \begin{array}{l}
-      \Pi d.\Pi l. \overrightarrow{\cohf[n][p][r+1][q+1][\epsilon][\omega]}{\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l))} = \\
+      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
+      \Pi d.\Pi l. \overrightarrow{\cohf[n][p][r+1][q+1][\epsilon][\omega]}{(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} = \\
       \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))

### 2025-11-09 paper/paper.tex
paper: near functional completion

@@
 \newcommandx{\depscohs}[2][1,2]{\prim{depscohs}[][#1][#2][][]}
+\newcommandx{\depscoht}[2][1,2]{\prim{depscoht}[][#1][#2][][]}
 \newcommandx{\depstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
 \newcommandx{\depscohstype}[2][1,2]{\prim{depscohstype}[][#1][#2][][]}
+\newcommandx{\depscohttype}[2][1,2]{\prim{depscohttype}[][#1][#2][][]}
 
@@
 \renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
-\renewcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#4][][]}
+\renewcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
 \renewcommandx{\cohf}[6][1,2,3,4,5,6]{\coh{frame}[][#3][#4][#5][#6][#1,#2][][]}
@@
     \framep[n][0,...,p]                                                                    &
-    \multicolumn{3}{l}{
     \left(\begin{array}{l}
@@
                 \end{array}\right)                                              \\
-              \end{array}\right) : \frametype[n][0,...,p]
-    }                                                                                                                                                                                                   \\
+            \end{array}\right) & :      & \frametype[n][0,...,p]                             \\
     \framep[n][0]                                                                          &
@@
               \restrf[n+1][0,...,p-1]:\restrftype[n][0,...,p-1] \\
-            \end{array}\right)                          & :                                            &
+            \end{array}\right)
                                                                                            & :      & \Type               \\
@@
     \painting[n][0,...,p]                              &
-    \multicolumn{3}{l}{
     \left(\begin{array}{l}
@@
               E:\framep[n-1][n-1]\rightarrow \U               \\
-              \end{array}\right) : \paintingtype[n][0,...,p](\framep[n][0,...,p](\deps[n-1][0,...,p]))
-    }                                                            \\
+            \end{array}\right) & :      & \paintingtype[n][0,...,p](\framep[n][0,...,p](\deps[n-1][0,...,p])) \\
     \painting[n][0,...,0-1]                            &
@@
     \painting[n][0,...,p]                              &
-    \left(\begin{array}{l}
+    \begin{array}{l}
       \deps[n-1][0,...,p-1] \\
       E                     \\
-            \end{array}\right) & \defeq &
-       (\painting[n][0,...,p-1]
+    \end{array}                           & \defeq &
+    \left(\painting[n][0,...,p-1]
     \left(\begin{array}{l}
@@
                 E                     \\
-         \end{array}\right),           \\
+              \end{array}\right),\,
     \painting[n][p]
@@
                 E                     \\
-         \end{array}\right))           \\
+              \end{array}\right)\right)                                                                         \\
   \end{array}
@@
           \end{array}\right)(d) \rightarrow \\
-        \deps.layer[n][p](\deps[n][0,...,n])(\restrf[n][p]
+        \deps.\layer[n][p](\deps[n][0,...,n])(\restrf[n][p]
         \left(\begin{array}{l}
@@
 \begin{align*}
-  \overline{\deps}(\depscohs:\depscohstype) : \depstype\\
+  \overline{\deps}(\depscohs:\depscohstype) : \depstype \\
   \overline{\deps}(\depscohs) \defeq
@@
             \painting[n][p](\depscohs.\deps[n][0,...,n]) \\
-            \restrf[n][p](\depscohs[n][0,...,p])\\
-      \end{array}\right)\\
+            \restrf[n][p](\depscohs[n][0,...,p])         \\
+          \end{array}\right)    \\
 \end{align*}
 
-Armed with $\restrframe$ and $\cohftype$, it is now possible to define
+Armed with $\restrf$ and $\cohftype$, it is now possible to define
 $\restrp[n][p]$ by recursion on $n-p$:
@@
     \restrp[n][p]                                      &
-    \multicolumn{3}{l}{
     \left(\begin{array}{l}
@@
             \end{array}\right) & :      &
+    \left(
+    \begin{array}{l}
         \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n][p]
         \left(\begin{array}{l}
-                \overline{\deps}(\depscohs)\\
+                  \overline{\deps}(\depscohs)    \\
                   E':\framep[n][n]\rightarrow \U \\
-      \end{array}\right).\,
+                \end{array}\right).    \\
         \painting[n][p]
         \left(\begin{array}{l}
-                \overline{\deps}(\depscohs)\\
+                  \overline{\deps}(\depscohs)    \\
                   E':\framep[n][n]\rightarrow \U \\
-      \end{array}\right)(d) \rightarrow
+                \end{array}\right)(d) \rightarrow \\
         \painting[n-1][p]
         \left(\begin{array}{l}
-                \depscohs[n][0,...,n].\deps\\
+                  \depscohs[n][0,...,n].\deps       \\
                   E:\framep[n-1][n-1]\rightarrow \U \\
-      \end{array}\right)(\restrf[n][p](\depscohs[n][0,...,n].deps)(d))
-    }                                                            \\
+                \end{array}\right)(\restrf[n][p](\depscohs[n][0,...,n].deps)(d))\end{array}\right)                                                  \\
     \restrp[n][n]                                      &
@@
     \cohptype[n][]        & \unitpoint                                        & \defeq & \unittype                               \\
-    \cohptype[n][0,...,p](\depscohs[n][0,...,n]) & (\depscohs[n][0,...,n])                       & \defeq & \cohptype[n+1][0,...,p-1] \times \left(
+    \cohptype[n][0,...,p] & (\depscohs[n][0,...,n])                           & \defeq & \cohptype[n+1][0,...,p-1] \times \left(
     \begin{array}{l}
-        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep(\depscohs[n][0,...,p]). \\
+        \Pi q\leq n.\Pi r\leq q.\Pi \epsilon.\Pi \omega.\Pi d:\framep(\depscohs[n][0,...,p]). \\
         \painting[n][p](\depscohs[n][0,...,n])(d) \rightarrow                                 \\ \depscohs.\painting[n][p](\depscohs.\restrf[n][p][q][\epsilon](d))\end{array}
@@
     \cohf[n][0,...,p]                                                       &
-    \multicolumn{3}{l}{
     \left(\begin{array}{l}
@@
               \coht[n][0,...,p]:\cohttype[n][0,...,p]
-              \end{array}\right) : \cohftype[n][0,...,p]
-    }                                                                                                                                                 \\
+            \end{array}\right)          & :      & \cohftype[n][0,...,p]                                                                                                     \\
     \cohf[n][0]                                                             &
     \left(\begin{array}{l}
+              \unitpoint \\
               \unitpoint \\
@@
             \end{array}\right)                                                & \defeq &
-    \begin{array}{l}
+    \left(\begin{array}{l}
               \cohf[n+1][0,...,p]
@@
                 \end{array}\right),                                      \\
-      (\cohf[n+1][0,...,p], \lambda q.\lambda r.\lambda \epsilon.\lambda \omega.\lambda (d,l). \\
-      \left(\cohf[n][0,...,p][q][r][\epsilon][\omega]
+              \lambda q.\lambda r.\lambda \epsilon.\lambda \omega.\lambda (d,l). \\
+              \cohf[n][0,...,p][q][r][\epsilon][\omega]
               \left(\begin{array}{l}
@@
                   \coht[n][0,...,p]     \\
-                \end{array}\right) (d)(l)\right)                                                                           \\
-    \end{array}                          \\
+                \end{array}\right)(d)(l)                                     \\
+            \end{array}\right)                                                                                \\
     \cohttype[n][0,...,p-1]                                                 &
-    \multicolumn{3}{l}{
     \left(\begin{array}{l}
@@
               \cohp[n][0,...,p-1]:\cohptype[n][0,...,p-1](\depscohs[n][0,...,p-1]) \\
-            \end{array}\right) : \U
-    }                                                                                                                                                 \\
+            \end{array}\right) & :      & \U                                                                                             \\
     \cohttype[n][0,...,0-1]                                                 &
@@
             \end{array}\right)                                                & \defeq &
-    \begin{array}{l}
+    \left(\begin{array}{l}
               \Sigma \coht[n+1][0,...,p-1]
@@
                   \coht[n+1][0,...,p-1]
-      \end{array}\right)\\
-    \end{array}                                                                                 \\
+                \end{array}\right)                                      \\
+            \end{array}\right)                                                                         \\
     \cohl[n][p]                                                             &
@@
             \end{array}\right)                                                & \defeq &
-    \lambda d. \lambda l. \lambda \theta. (\cohp[n][p][q][\epsilon][r][\omega](l))                                                                    \\
-  \end{array}
-\end{equation*}
-
+    \lambda d. \lambda l. \lambda \theta. (\cohp[n][p][q][\epsilon][r][\omega](l))  ...                                                                                    \\
+  \end{array}
+\end{equation*}
+
+This is time for a new abbreviation:
+
+\begin{align*}
+  \depscohttype[n][0,..,p-1] \defeq
+  \left(\begin{array}{l}
+            \depscohs[n][0,...,n] :\depscohstype[n][0,...,n] \\
+            \cohp[n][0,...p-1]: \cohptype[n][0,...,p-1]      \\
+            \coht[n][0,...,p-1]: \cohttype[n][0,...,p-1]     \\
+          \end{array}\right)
+\end{align*}
+
+The next step is to define $\cohp[n][p]$ by recursion on $n-p$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \cohp[n][p]                                        &
+    \left(\begin{array}{l}
+              \depscoht[n][0,...,n]:\depscohttype[n][0,...,n] \\
+              E:\framep[n-2][n-2]\rightarrow \U               \\
+              E':\framep[n-1][n-1]\rightarrow \U              \\
+              E'':\framep[n][n]\rightarrow \U                 \\
+            \end{array}\right) & :      &
+    \left(
+    \begin{array}{l}
+        \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n][p]
+        \left(\begin{array}{l}
+                  \overline{\depscohs}(\depscoht) \\
+                  E':\framep[n][n]\rightarrow \U  \\
+                \end{array}\right).   \\
+        \painting[n][p]
+        \left(\begin{array}{l}
+                  \overline{\depscohs}(\depscoht) \\
+                  E':\framep[n][n]\rightarrow \U  \\
+                \end{array}\right)(d) \rightarrow \\
+        \painting[n-1][p]
+        \left(\begin{array}{l}
+                  \depscoht[n][0,...,n].\deps       \\
+                  E:\framep[n-1][n-1]\rightarrow \U \\
+                \end{array}\right)(\cohf[n][p](\depscoht[n][0,...,n].deps)(d))\end{array}\right)                                                  \\
+    \cohp[n][n]                                        &
+    \left(\begin{array}{l}
+              \depscoht[n][0,...,n] \\
+              E                     \\
+              E'                    \\
+            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
+    \cohp[n][p](p<n)                                   &
+    \left(\begin{array}{l}
+              \depscoht[n][0,...,n] \\
+              E                     \\
+              E'                    \\
+            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
+    \left(\begin{array}{l}
+              \cohl[n][p][q][\epsilon](\depscoht[n-1][0,...,p-1])(l),            \\
+              \cohp[n][p][q][\epsilon]
+              \left(\begin{array}{l}
+                  \depscoht[n][0,...,n] \\
+                  E                     \\
+                  E'                    \\
+                \end{array}\right)(\cohf[n][p](\depscoht[n][0,...,p])(d))(c) \\
+            \end{array}\right)                                                           \\
+  \end{array}
+\end{equation*}
+
+From which we can deduce $\cohp[n][0,...,p]$ again by a second recursion, this time on $p$:
+
+Armed with all the constructions we can now define
 \bibliographystyle{msclike}

### 2025-11-09 paper/paper.tex
paper: introduce fulldeps to include E, fix errors

@@
 \newcommandx{\deps}[2][1,2]{\prim{deps}[][#1][#2][][]}
+\newcommandx{\fulldeps}[2][1,2]{\prim{fulldeps}[][#1][][][]}
 \newcommandx{\depscohs}[2][1,2]{\prim{depscohs}[][#1][#2][][]}
@@
 \newcommandx{\depstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
+\newcommandx{\fulldepstype}[2][1,2]{\prim{fulldepstype}[][#1][][][]}
 \newcommandx{\depscohstype}[2][1,2]{\prim{depscohstype}[][#1][#2][][]}
@@
 
-At this stage, it is convenient to use an abbreviation to combine sequences $\framep[n][0,..,p-1]$, $\painting[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$ in one block, which we call $\deps[n][0,...p-1]$:
+At this stage, it is convenient to use an abbreviation to combine sequences $\framep[n][0,..,p-1]$, $\painting[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$ in one block, which we call $\depstype[n][0,...p-1]$:
 
 \begin{align*}
-  \deps[n][0,..,p-1] \defeq
+  \depstype[n][0,..,p-1] \defeq
   \left(\begin{array}{l}
@@
 \end{align*}
-
 so that the type of $\framep[n][0,...,p]$ can be shortened into $\depstype[n][0,..,p-1] \rightarrow \frametype[n][0,...,p]$ and similarly for $\layertype[n][p]$ and $\layer[n][p]$.
@@
 
+Let us introduce another abbreviation to combine a full $\deps[n][0,n]$ with a family $E:\framep[n-1][n-1]\rightarrow \U$:
+\begin{align*}
+  \fulldepstype[n] \defeq
+  \left(\begin{array}{l}
+            \deps[n][0,...,n-1] :\depstype[n][0,...,n-1] \\
+            E:\frametype[n-1][n-1]\rightarrow \U         \\
+          \end{array}\right)
+\end{align*}
+TODO: say the convention on projection in the Introduction
+
+Also, when $n$ is 0, we write $E$ to denote an element $(\unitpoint, E)$ of $\fulldepstype[0]$.
+
 We can now formally define $\painting[n][p]$ by recursion on $n-p$:
@@
     \painting[n][p]      &
-    \multicolumn{3}{l}{
-      \left(\begin{array}{l}
-                \deps[n-1][0,...,n-1]:\depstype[n-1][0,...,n-1] \\
-                E:\framep[n-1][n-1]\rightarrow \U               \\
-              \end{array}\right) : \framep[n-1][n-1]\rightarrow \U
-    }                                                            \\
+    (\fulldeps[n-1]:\fulldepstype[n-1])           \\
     \painting[n][n]      &
-    \left(\begin{array}{l}
-              \deps[n-1][0,...,n-1] \\
-              E                     \\
-            \end{array}\right) & \defeq & E                        \\
+    (\fulldeps[n-1])     & \defeq & \fulldeps.E   \\
     \painting[n][p](p<n) &
-    \left(\begin{array}{l}
-              \deps[n-1][0,...,n-1] \\
-              E                     \\
-            \end{array}\right) & \defeq & d \mapsto
+    (\fulldeps[n-1])     & \defeq & d \mapsto
     \left(\begin{array}{l}
@@
               \painting[n][p+1,...,n-1]
-              \left(\begin{array}{l}
-                  \deps[n-1][0,...,n-1] \\
-                  E                     \\
-                \end{array}\right)(d,l)           \\
+              (\fulldeps[n-1])(d,l)                   \\
             \end{array}\right) \\
@@
     \painting[n][0,...,p]   &
-    \left(\begin{array}{l}
-              \deps[n-1][0,...,n-1]:\depstype[n-1][0,...,n-1] \\
-              E:\framep[n-1][n-1]\rightarrow \U               \\
-            \end{array}\right) & :      & \paintingtype[n][0,...,p](\framep[n][0,...,p](\deps[n-1][0,...,p])) \\
+    (\fulldeps[n-1])        & :      & \paintingtype[n][0,...,p](\framep[n][0,...,p](\fulldeps.\deps[n-1][0,...,p])) \\
     \painting[n][0,...,0-1] &
@@
     \painting[n][0,...,p]   &
-    \begin{array}{l}
-      \deps[n-1][0,...,p-1] \\
-      E                     \\
-    \end{array}                           & \defeq &
+    (\fulldeps[n-1])                                                                                                 \\
+                            & \defeq &
     \left(\painting[n][0,...,p-1]
-    \left(\begin{array}{l}
-                \deps[n-1][0,...,n-1] \\
-                E                     \\
-              \end{array}\right),\,
+      (\fulldeps[n-1]),\,
     \painting[n][p]
-    \left(\begin{array}{l}
-                \deps[n-1][0,...,n-1] \\
-                E                     \\
-              \end{array}\right)\right)                                                                         \\
+    (\fulldeps[n-1])\right)                                                                                          \\
   \end{array}
@@
   \begin{array}{llcl}
-    \restrptype[n][0,...,p]                    & (\deps[n][0,...,n]:\depstype[n][0,...,n]) & :      & \U                                        \\
+    \restrptype[n][0,...,p]             &
+    (\fulldeps[n-1]:\fulldepstype[n-1]) & :          & \U                                                    \\
     \restrptype[n][]                    & \unitpoint & \defeq                                    & \unittype \\
-    \restrptype[n][0,...,p](\deps[n][0,...,n]) & (\deps[n][0,...,n])                       & \defeq & \restrptype[n+1][0,...,p-1] \times \left(
+    \restrptype[n][0,...,p]             &
+    (\fulldeps[n-1])
+                                        & \defeq     & \restrptype[n+1][0,...,p-1] \times \left(
     \begin{array}{l}
         \Pi q\leq n.\Pi \epsilon.\Pi d:\framep(\deps[n][0,...,p]). \\
-        \painting[n][p](\deps[n][0,...,n])(d) \rightarrow          \\ \deps.\painting[n][p](\deps.\restrf[n][p][q][\epsilon](d))\end{array}
+        \painting[n][p]
+        (\fulldeps[n-1])(d) \rightarrow                            \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
     \right)                                                                                                  \\
@@
       \left(\begin{array}{l}
-                \deps[n][0,...,n]:\depstype[n][0,...,n] \\
+                \fulldeps[n]:\depstype[n]   \\
                 \restrp[n][0,...,p-2]:\restrptype[n][0,...,p-1]
                 \left(\begin{array}{l}
-                    \deps[n][0,...,n] \\
+                    \fulldeps[n] \\
                   \end{array}\right)    \\
@@
                 \left(\begin{array}{l}
-                    \deps[n][0,...,n]     \\
+                    \fulldeps[n]          \\
                     \restrp[n][0,...,p-2] \\
@@
       \left(\begin{array}{l}
-                \deps.\framep[n][0,...,p]   \\
-                \deps.\painting[n][0,...,p] \\
+                \fulldeps.\deps.\framep[n][0,...,p]   \\
+                \fulldeps.\deps.\painting[n][0,...,p] \\
               \end{array}\right)
@@
     \left(\begin{array}{l}
-              \unitpoint \\
+              E          \\
               \unitpoint \\
@@
     \left(\begin{array}{l}
-              \deps[n][0,...,n]   \\
+              \fulldeps[n]        \\
               \restrp[n][0,...,p] \\
@@
               \left(\begin{array}{l}
-                  \deps[n+1][0,...,n]     \\
+                  \fulldeps[n+1]          \\
                   \restrp[n+1][0,...,p-1] \\
@@
               \left(\begin{array}{l}
-                    \deps[n+1][0,...,n]     \\
+                    \fulldeps[n+1]          \\
                     \restrp[n+1][0,...,p-1] \\
@@
               \left(\begin{array}{l}
-                    \deps[n][0,...,n] \\
+                    \fulldeps[n]      \\
                     \cohf[n][0,...,p] \\
@@
       \left(\begin{array}{l}
-              \deps[n][0,...,n]:\depstype[n][0,...,n]                              \\
-              \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1]) \\
+              \fulldeps[n]:\fulldepstype[n]                                 \\
+              \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\fulldeps[n]) \\
             \end{array}\right) : \U
@@
       \left(\begin{array}{l}
-                \deps[n+1][0,...,n]     \\
+                \fulldeps[n+1]          \\
                 \restrp[n+1][0,...,p-1] \\
@@
     \left(\begin{array}{l}
-              \deps[n][0,...,n]:\depstype[n][0,...,n]                              \\
+              \fulldeps[n]:\fulldepstype[n]                                        \\
               \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1]) \\
@@
     \left(\begin{array}{l}
-              \deps[n][0,...,n]     \\
+              \fulldeps[n]          \\
               \restrp[n][0,...,p-1] \\
@@
         \begin{array}{l}
-            \framep[n][p](\deps[n][0,...,p])   \\
-            \painting[n][p](\deps[n][0,...,n]) \\
+            \framep[n][p](\fulldeps.\deps[n][0,...,p])   \\
+            \painting[n][p](\fulldeps.\deps[n][0,...,n]) \\
             \restrf[n][p]
             \left(\begin{array}{l}
-                      \deps[n][0,...,p]     \\
+                      \fulldeps.\deps[n][0,...,p] \\
                       \restrp[n][0,...,p-1]       \\
@@
           \end{array}\right)(d) \rightarrow \\
-        \deps.\layer[n][p](\deps[n][0,...,n])(\restrf[n][p]
-        \left(\begin{array}{l}
-                  \deps[n][0,...,p]     \\
+        \fulldeps.\deps.\layer[n][p](\deps[n][0,...,n])(\restrf[n][p]
+        \left(\begin{array}{l}
+                  \fulldeps.\deps[n][0,...,p] \\
                   \restrp[n][0,...,p-1]       \\
@@
     \left(\begin{array}{l}
-              \deps[n][0,...,n]:\depstype[n][0,...,n]                              \\
-              \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1]) \\
-              \cohf[n][0,...,p-1]:\cohftype[n][0,...,p-1]                          \\
+              \fulldeps[n]:\fulldepstype[n]                                 \\
+              \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\fulldeps[n]) \\
+              \cohf[n][0,...,p-1]:\cohftype[n][0,...,p-1]
+              \left(\begin{array}{l}
+                  \fulldeps[n]          \\
+                  \restrp[n][0,...,p-1] \\
+                \end{array}\right)                                   \\
             \end{array}\right) & :      &
@@
 \end{align*}
-so that the type of $\restrf[n][0,...,p]$ can be rephrased as $\depscohstype[n][0,..,p-1] \rightarrow \restrftype[n][0,...,p]      \left(\begin{array}{l}
-      \deps.\framep[n][0,...,p]   \\
-      \deps.\painting[n][0,...,p] \\
+so that the type of $\restrf[n][0,...,p]$ can be rephrased as $\Pi \depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1]. \restrftype[n][0,...,p]      \left(\begin{array}{l}
+      \depscohs.\deps.\framep[n][0,...,p]   \\
+      \depscohs.\deps.\painting[n][0,...,p] \\
     \end{array}\right)$, and similarly for $\restrltype$ and $\restrl$.
@@
     \begin{array}{l}
-        \Pi q\leq n.\Pi r\leq q.\Pi \epsilon.\Pi \omega.\Pi d:\framep(\depscohs[n][0,...,p]). \\
-        \painting[n][p](\depscohs[n][0,...,n])(d) \rightarrow                                 \\ \depscohs.\painting[n][p](\depscohs.\restrf[n][p][q][\epsilon](d))\end{array}
+        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
+        \depscohs.\restrp[n][p][q][\epsilon](\restrp[n+1][p][r][\omega]
+        \left(\begin{array}{l}
+                  \depscohs[n+1][0,...,n] \\
+                  \cohp[n+1][0,...,p-1]   \\
+                \end{array}\right)(d)) =                         \\
+        \depscohs.\restrp[n][p][r][\omega](\restrp[n+1][p][q+1][\epsilon]
+        \left(\begin{array}{l}
+                  \depscohs[n+1][0,...,n] \\
+                  \cohp[n+1][0,...,p-1]   \\
+                \end{array}\right)(d))
+      \end{array}
     \right)                                                                                                                      \\
@@
     \begin{array}{l}
-        \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n][p]
-        \left(\begin{array}{l}
-                  \overline{\depscohs}(\depscoht) \\
-                  E':\framep[n][n]\rightarrow \U  \\
-                \end{array}\right).   \\
-        \painting[n][p]
-        \left(\begin{array}{l}
-                  \overline{\depscohs}(\depscoht) \\
-                  E':\framep[n][n]\rightarrow \U  \\
-                \end{array}\right)(d) \rightarrow \\
-        \painting[n-1][p]
-        \left(\begin{array}{l}
-                  \depscoht[n][0,...,n].\deps       \\
-                  E:\framep[n-1][n-1]\rightarrow \U \\
-                \end{array}\right)(\cohf[n][p](\depscoht[n][0,...,n].deps)(d))\end{array}\right)                                                  \\
+        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
+        \depscohs.\restrp[n][p][q][\epsilon](\restrp[n+1][p][r][\omega]
+        \left(\begin{array}{l}
+                  \depscohs[n+1][0,...,n] \\
+                  \cohp[n+1][0,...,p-1]   \\
+                \end{array}\right)(d)) =                         \\
+        \depscohs.\restrp[n][p][r][\omega](\restrp[n+1][p][q+1][\epsilon]
+        \left(\begin{array}{l}
+                  \depscohs[n+1][0,...,n] \\
+                  \cohp[n+1][0,...,p-1]   \\
+                \end{array}\right)(d))
+      \end{array}\right)                                                                                                       \\
     \cohp[n][n]                                        &
@@
               E'                    \\
-            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
+            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c). l\epsilon \\
     \cohp[n][p](p<n)                                   &
@@
               E'                    \\
-            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
+            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c).
     \left(\begin{array}{l}

### 2025-11-09 paper/paper.tex
paper: introduce more fulldeps

@@
 \newcommandx{\depscohs}[2][1,2]{\prim{depscohs}[][#1][#2][][]}
+\newcommandx{\fulldepscohs}[2][1,2]{\prim{fulldepscohs}[][#1][][][]}
 \newcommandx{\depscoht}[2][1,2]{\prim{depscoht}[][#1][#2][][]}
+\newcommandx{\fulldepscoht}[2][1,2]{\prim{fulldepscoht}[][#1][][][]}
 \newcommandx{\depstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
@@
 \newcommandx{\depscohstype}[2][1,2]{\prim{depscohstype}[][#1][#2][][]}
+\newcommandx{\fulldepscohstype}[2][1,2]{\prim{fulldepscohstype}[][#1][][][]}
 \newcommandx{\depscohttype}[2][1,2]{\prim{depscohttype}[][#1][#2][][]}
+\newcommandx{\fulldepscohttype}[2][1,2]{\prim{fulldepscohttype}[][#1][][][]}
 
@@
     \painting[n][0,...,p]   &
-    (\fulldeps[n-1])                                                                                                 \\
+    (\fulldeps[n-1])
                             & \defeq &
-    \left(\painting[n][0,...,p-1]
-      (\fulldeps[n-1]),\,
-    \painting[n][p]
-    (\fulldeps[n-1])\right)                                                                                          \\
+    (\painting[n][0,...,p-1](\fulldeps[n-1]),\painting[n][p](\fulldeps[n-1]))                                        \\
   \end{array}
@@
 so that the type of $\restrf[n][0,...,p]$ can be rephrased as $\Pi \depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1]. \restrftype[n][0,...,p]      \left(\begin{array}{l}
-      \depscohs.\deps.\framep[n][0,...,p]   \\
-      \depscohs.\deps.\painting[n][0,...,p] \\
+      \depscohs.\fulldeps.\deps.\framep[n][0,...,p]   \\
+      \depscohs.\fulldeps.\deps.\painting[n][0,...,p] \\
     \end{array}\right)$, and similarly for $\restrltype$ and $\restrl$.
@@
 \begin{align*}
-  \overline{\deps}(\depscohs:\depscohstype) : \depstype \\
-  \overline{\deps}(\depscohs) \defeq
+  \overline{\deps}(\depscohs:\depscohstype) & :      & \depstype \\
+  \overline{\deps}(\depscohs)               & \defeq &
   \left(\begin{array}{l}
@@
 
-Armed with $\restrf$ and $\cohftype$, it is now possible to define
-$\restrp[n][p]$ by recursion on $n-p$:
+We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][0,...,n]$ with a set $E:\framep[n][n](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$:
+\begin{align*}
+  \fulldepscohstype[n] \defeq
+  \left(\begin{array}{l}
+            \depscohs[n][0,...,n-1] :\depscohstype[n][0,...,n-1]                         \\
+            E:\framep[n-1][n-1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
+          \end{array}\right)
+\end{align*}
+TODO: say the convention on projection in the Introduction
+
+Also, when $n$ is 0, we write $(E',E)$ to denote an element $(E', E)$ of $\fulldepscohstype[0]$.
+
+Armed with $\restrf$, $\cohftype$ and these abbreviations, it is now possible to define $\restrp[n][p]$ by recursion on $n-p$:
 
@@
     \restrp[n][p]                           &
-    \left(\begin{array}{l}
-              \depscohs[n][0,...,n]:\depscohstype[n][0,...,n] \\
-              E:\framep[n-1][n-1]\rightarrow \U               \\
-              E':\framep[n][n]\rightarrow \U                  \\
-            \end{array}\right) & :      &
+    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      &
     \left(
@@
     \restrp[n][n]                           &
-    \left(\begin{array}{l}
-              \depscohs[n][0,...,n] \\
-              E                     \\
-              E'                    \\
-            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
+    (\fulldepscohs[n][0,...,n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
     \restrp[n][p](p<n)                      &
-    \left(\begin{array}{l}
-              \depscohs[n][0,...,n] \\
-              E                     \\
-              E'                    \\
-            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
-    \left(\begin{array}{l}
-              \restrl[n][p][q][\epsilon](\depscohs[n-1][0,...,p-1])(l),            \\
+    (\fulldepscohs[n][0,...,n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
+    \left(\begin{array}{l}
+              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n-1][0,...,p-1])(l),               \\
               \restrp[n][p][q][\epsilon]
-              \left(\begin{array}{l}
-                  \depscohs[n][0,...,n] \\
-                  E                     \\
-                  E'                    \\
-                \end{array}\right)(\restrf[n][p](\depscohs[n][0,...,p])(d))(c) \\
+              (\fulldepscohs[n][0,...,n])(\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,p])(d))(c) \\
             \end{array}\right)                              \\
@@
     \left(\begin{array}{l}
-              \depscohs[n][0,...,n]:\depscohstype[n][0,...,n] \\
-              \cohp[n][0,...,p-2]:\restrptype[n][0,...,p-1]
-              \left(\begin{array}{l}
-                  \depscohs[n][0,...,n] \\
-                \end{array}\right)                     \\
+              \fulldepscohs[n]:\fulldepscohstype[n]                                    \\
+              \cohp[n][0,...,p-2]:\restrptype[n][0,...,p-1](\fulldepscohs[n][0,...,n]) \\
               \coht[n][0,...,p]:\cohttype[n][0,...,p]
+              \left(\begin{array}{l}
+                  \fulldepscohs[n]    \\
+                  \cohp[n][0,...,p-1] \\
+                \end{array}\right)
             \end{array}\right) & :      & \cohftype[n][0,...,p]                                                                                             \\
@@
     \left(\begin{array}{l}
-              \depscohs[n][0,...,n] \\
+              \fulldepscohs[n]  \\
               \cohp[n][0,...,p] \\
@@
               \left(\begin{array}{l}
-                  \depscohs[n+1][0,...,n] \\
+                  \fulldepscohs[n+1]    \\
                   \cohp[n+1][0,...,p-1] \\
@@
               \left(\begin{array}{l}
-                  \depscohs[n][0,...,n] \\
+                  \fulldepscohs[n]      \\
                   \cohp[n+1][0,...,p-1] \\
@@
     \left(\begin{array}{l}
-              \depscohs[n][0,...,n]:\depscohstype[n][0,...,n]                      \\
-              \cohp[n][0,...,p-1]:\cohptype[n][0,...,p-1](\depscohs[n][0,...,p-1]) \\
+              \fulldepscohs[n]:\fulldepscohstype[n]                         \\
+              \cohp[n][0,...,p-1]:\cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
             \end{array}\right)            & :      & \U                                                                                                        \\
@@
     \left(\begin{array}{l}
-              \unitpoint \\
+              (E',E)     \\
               \unitpoint \\
@@
               \left(\begin{array}{l}
-                  \depscohs[n+1][0,...,n] \\
+                  \fulldepscohs[n+1]      \\
                   \restrp[n+1][0,...,p-1] \\
@@
               \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta  \\
-              \depscohs.\cohf[n][p][r][p][\omega][\theta] \circ \cohf[n+1][p][q+1][p][\epsilon][\theta]
-              \left(\begin{array}{l}
-                  \depscohs[n+1][0,...,n] \\
+              \fulldepscohs.\depscohs.\cohf[n][p][r][p][\omega][\theta] \circ \cohf[n+1][p][q+1][p][\epsilon][\theta]
+              \left(\begin{array}{l}
+                  \fulldepscohs[n+1]    \\
                   \cohp[n+1][0,...,p-1] \\
@@
                 \end{array}\right)
-              \circ \depscohs.\cohf[n][p][q][r][\epsilon][\omega] =              \\
+              \circ \fulldepscohs.\depscohs.\cohf[n][p][q][r][\epsilon][\omega] = \\
               \cohf[n+1][p][q+1][r+1][\epsilon][\omega]
               \left(\begin{array}{l}
-                  \depscohs[n+1][0,...,n] \\
+                  \fulldepscohs[n+1]    \\
                   \cohp[n+1][0,...,p-1] \\
@@
                 \end{array}\right)
-              \circ \depscohs.\cohf[n][p][q][p][\epsilon][\theta]
+              \circ \fulldepscohs.\depscohs.\cohf[n][p][q][p][\epsilon][\theta]
               \circ \cohf[n+1][p][r][p][\omega][\theta]
               \left(\begin{array}{l}
-                  \depscohs[n+1][0,...,n] \\
+                  \fulldepscohs[n+1]    \\
                   \cohp[n+1][0,...,p-1] \\
@@
     \left(\begin{array}{l}
-              \depscohs[n][0,...,n]:\depscohstype[n][0,...,n] \\
+              \fulldepscohs[n]:\fulldepscohstype[n]   \\
               \cohp[n+1][p]:\cohptype[n+1][p]         \\
@@
     \left(\begin{array}{l}
-              \depscohs[n][0,...,n] \\
+              \fulldepscohs[n]  \\
               \cohp[n][p]       \\
@@
   \left(\begin{array}{l}
-            \depscohs[n][0,...,n] :\depscohstype[n][0,...,n] \\
-            \cohp[n][0,...p-1]: \cohptype[n][0,...,p-1]      \\
-            \coht[n][0,...,p-1]: \cohttype[n][0,...,p-1]     \\
+            \fulldepscohs[n] :\fulldepscohstype[n]                        \\
+            \cohp[n][0,...p-1]: \cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
+            \coht[n][0,...,p-1]: \cohttype[n][0,...,p-1]
+            \left(\begin{array}{l}
+                \fulldepscohs[n]    \\
+                \cohp[n][0,...,p-1] \\
+              \end{array}\right)                                     \\
+          \end{array}\right)
+\end{align*}
+
+We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][0,...,n]$ with a set $E:\framep[n][n](\overline{\deps}(\overline{\deps}(\depscohs[n][0,...,n-1])))???
+\rightarrow \U$:
+\begin{align*}
+  \fulldepscohttype[n] \defeq
+  \left(\begin{array}{l}
+            \depscoht[n][0,...,n-1] :\depscohttype[n][0,...,n-1]    \\
+            E:\framep[n-1][n-1](\overline{\deps}(??))\rightarrow \U \\
           \end{array}\right)

### 2025-11-09 paper/paper.tex
A couple of fixes/additions

@@
             \end{array}\right) & :      & \frametype[n][0,...,p]                             \\
-    \framep[n][0]                                                                          &
+    \framep[n][0,]                                                                          &
     \left(\begin{array}{l}
@@
   \depstype[n][0,..,p-1] \defeq
-  \left(\begin{array}{l}
-            \framep[n][0,...,p-1] :\frametype[n][0,...,p-1] \\
-            \painting[n][0,...,p-1] :\paintingtype[n][0,...,p-1]
+  \left(\begin{array}{lll}
+            \framep[n][0,...,p-1] &:&\frametype[n][0,...,p-1] \\
+            \painting[n][0,...,p-1] &:&\paintingtype[n][0,...,p-1]
             (\framep[n][0,...,p-1])                         \\
-            \restrf[n][0,...,p-1]  :\restrftype[n][0,...,p-1]
+            \restrf[n][0,...,p-1]  &:&\restrftype[n][0,...,p-1]
             \left(\begin{array}{l}
@@
   \fulldepstype[n] \defeq
-  \left(\begin{array}{l}
-            \deps[n][0,...,n-1] :\depstype[n][0,...,n-1] \\
-            E:\frametype[n-1][n-1]\rightarrow \U         \\
+  \left(\begin{array}{lll}
+            \deps[n][0,...,n-1] &:&\depstype[n][0,...,n-1] \\
+            E&:&\frame[n-1][n-1](\deps[n][0,...,n-1]) \rightarrow \U         \\
           \end{array}\right)
@@
     \left(\begin{array}{l}
-              \Sigma l:\layer(\deps[n-1][0,...,p-1]). \\
+              \Sigma l:\layer(\fulldeps.\deps[n-1][0,...,p-1]). \\
               \painting[n][p+1,...,n-1]
@@
     \painting[n][0,...,0-1] &
-    \left(\begin{array}{l}
-              \unitpoint \\
-              E          \\
-            \end{array}\right)  & \defeq & \unittype                                                                   \\
+    E  & \defeq & \unittype                                                                   \\
     \painting[n][0,...,p]   &
@@
 
-At this stage, we are able to define $\framep$, $\painting$ and $\restrftype$ from $\deps$ at the respective previous level.
-To go further, we need to define the sequence $\restrptype$ of types of painting restrictions:
+At this stage, we are able to define $\framep[n][0,...,n]$, $\painting[n][0,...,n]$ and $\restrftype[n][0,...,n-1]$ from $\framep[n-1][0,...,n-1]$, $\painting[n-1][0,...,n-1]$ and $\restrf[n-1][0,...,n-1]$, that is from $\deps[n-1][0,...,n-1]$.
+To go further, we need to define the sequence $\restrptype[n][0,...,p]$ of types of painting restrictions:
 
@@
     (\fulldeps[n-1]:\fulldepstype[n-1]) & :          & \U                                                    \\
-    \restrptype[n][]                    & \unitpoint & \defeq                                    & \unittype \\
+    \restrptype[n][]                    & E & \defeq                                    & \unittype \\
     \restrptype[n][0,...,p]             &
@@
     \begin{array}{l}
-        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep(\deps[n][0,...,p]). \\
+        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep[n][p](\fulldeps.\deps[n][0,...,p]). \\
         \painting[n][p]
@@
 
-Thanks to $\restrptype$, we can mutually define $\restrf$ and $\cohftype$, using abbreviations in passing for $\layer$ and $\layertype$:
+Thanks to $\restrptype[n][0,...,n]$, we can mutually define $\restrf[n][p]$ and $\cohftype[n][p]$ from ``full dependencies'', that is from $\frame[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$ and some $E:\frame[n+1][n+1](\, using abbreviations in passing for $\layer$ and $\layertype$:
 
@@
       \left(\begin{array}{l}
-                \fulldeps[n]:\depstype[n]   \\
+                \fulldeps[n]:\fulldepstype[n]   \\
                 \restrp[n][0,...,p-2]:\restrptype[n][0,...,p-1]
@@
       \left(\begin{array}{l}
-                \fulldeps.\deps.\framep[n][0,...,p]   \\
-                \fulldeps.\deps.\painting[n][0,...,p] \\
+                \framep[n][0,...,p](\fulldeps.\deps[n][0,...,p])   \\
+                \painting[n][0,...,p](\fulldeps[n]) \\
               \end{array}\right)
@@
                     \fulldeps[n]      \\
+                    \restrp[n+1][0,...,p-1] \\
                     \cohf[n][0,...,p] \\
@@
               \end{array}\right).                          \\
-      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
-      \deps.\restrf[n][p][q][\epsilon](\restrf[n+1][p][r][\omega]
+      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n][p]
+      \left(\begin{array}{l}
+                \frame(\fulldeps.\deps[n][0,...,p])          \\
+                \painting[n+1][0,...,p-1](\fulldeps[n]) \\
+                \restrf[n][0,...,p]
                 \left(\begin{array}{l}
@@
                   \restrp[n+1][0,...,p-1] \\
-              \end{array}\right)(d)) =                         \\
-      \deps.\restrf[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon]
+                  \cohf[n][0,...,p] \\
+                \end{array}\right)                         \\
+              \end{array}\right).                         \\
+      \\
+      \fulldeps.\deps.\restrf[n][p][q][\epsilon](\restrf[n+1][p][r][\omega]
       \left(\begin{array}{l}
@@
                 \restrp[n+1][0,...,p-1] \\
+                \cohf[n][0,...,p] \\
+              \end{array}\right)(d)) =                         \\
+      \fulldeps.\deps.\restrf[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon]
+      \left(\begin{array}{l}
+                \fulldeps[n+1]          \\
+                \restrp[n+1][0,...,p-1] \\
+                \cohf[n][0,...,p] \\
               \end{array}\right)(d))                          \\
@@
             \framep[n][p](\fulldeps.\deps[n][0,...,p])   \\
-            \painting[n][p](\fulldeps.\deps[n][0,...,n]) \\
+            \painting[n][p](\fulldeps[n]) \\
             \restrf[n][p]
             \left(\begin{array}{l}
-                      \fulldeps.\deps[n][0,...,p] \\
+                      \fulldeps[n] \\
                       \restrp[n][0,...,p-1]       \\
@@
           \end{array}\right)(d) \rightarrow \\
-        \fulldeps.\deps.\layer[n][p](\deps[n][0,...,n])(\restrf[n][p]
-        \left(\begin{array}{l}
-                  \fulldeps.\deps[n][0,...,p] \\
+        \layer[n][p](\fulldeps.\deps[n][0,...,n])(\restrf[n][p]
+        \left(\begin{array}{l}
+                  \fulldeps[n] \\
                   \restrp[n][0,...,p-1]       \\
@@
                                 \deps[n][0,...,n] \\
+                                \restrp[n][0,...,p-1] \\
                                 \cohf[n][0,...,p] \\
@@
             \end{array}\right)                                                     & \defeq &
-    \lambda q\leq n. \lambda \epsilon.\lambda\omega.\,\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega]}{\restrp[n][p](l \omega)}                          \\
+    \lambda q\leq n.
+\lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon])(l \omega)}                          \\
   \end{array}
@@
   \left(\begin{array}{l}
-            \deps[n][0,...,n] :\depstype[n][0,...,n]        \\
-            \restrp[n][0,...p-1]: \restrptype[n][0,...,p-1] \\
-            \cohf[n][0,...,p-1]: \cohftype[n][0,...,p-1]    \\
+            \fulldeps[n][0,...,n] &:&\fulldepstype[n][0,...,n]        \\
+            \restrp[n][0,...p-1]&:& \restrptype[n][0,...,p-1] \\
+            \cohf[n][0,...,p-1]&:& \cohftype[n][0,...,p-1]    \\
           \end{array}\right)
@@
   \left(\begin{array}{l}
-            \framep[n][p](\depscohs.\deps[n][0,...,p])   \\
-            \painting[n][p](\depscohs.\deps[n][0,...,n]) \\
+            \framep[n][p](\depscohs.\fulldeps.\deps[n][0,...,p])   \\
+            \painting[n][p](\depscohs.\fulldeps[n][0,...,n]) \\
             \restrf[n][p](\depscohs[n][0,...,p])         \\
+          \end{array}\right)             \\
+\end{align*}
+
+\begin{align*}
+  \overline{\fulldeps}(\fulldepscohs:\fulldepscohstype) & :      & \fulldepstype \\
+  \overline{\fulldeps}(\fulldepscohs)               & \defeq &
+  \left(\begin{array}{l}
+            \overline{\deps}(\depscohs)\\
+            \depscohs.\fulldeps.E\\
           \end{array}\right)             \\
@@
   \left(\begin{array}{l}
-            \depscohs[n][0,...,n-1] :\depscohstype[n][0,...,n-1]                         \\
-            E:\framep[n-1][n-1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
+            \depscohs[n][0,...,n-1] &:&\depscohstype[n][0,...,n-1]                         \\
+            E&:&\framep[n-1][n-1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
           \end{array}\right)
@@
         \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n][p]
-        \left(\begin{array}{l}
-                  \overline{\deps}(\depscohs)    \\
-                  E':\framep[n][n]\rightarrow \U \\
-                \end{array}\right).    \\
+        (\overline{\deps}(\depscohs)).    \\
         \painting[n][p]
-        \left(\begin{array}{l}
-                  \overline{\deps}(\depscohs)    \\
-                  E':\framep[n][n]\rightarrow \U \\
-                \end{array}\right)(d) \rightarrow \\
-        \painting[n-1][p]
-        \left(\begin{array}{l}
-                  \depscohs[n][0,...,n].\deps       \\
-                  E:\framep[n-1][n-1]\rightarrow \U \\
-                \end{array}\right)(\restrf[n][p](\depscohs[n][0,...,n].deps)(d))\end{array}\right)                                       \\
+        (\overline{\fulldeps}(\fulldepscohs[n])(d) \rightarrow \\
+        \painting[n-1][p](\fulldepscohs.\depscohs.\fulldeps[n])
+          (\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,n])(d))\end{array}\right)                                       \\
     \restrp[n][n]                           &
@@
               \restrp[n][p][q][\epsilon]
-              (\fulldepscohs[n][0,...,n])(\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,p])(d))(c) \\
+              (\fulldepscohs[n])(\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,p])(d))(c) \\
             \end{array}\right)                              \\
@@
   \begin{array}{llcl}
-    \cohptype[n][0,...,p] & (\depscohs[n][0,...,n]:\depscohstype[n][0,...,n]) & :      & \U                                      \\
+    \cohptype[n][0,...,p] & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                      \\
     \cohptype[n][]        & \unitpoint                                        & \defeq & \unittype                               \\
-    \cohptype[n][0,...,p] & (\depscohs[n][0,...,n])                           & \defeq & \cohptype[n+1][0,...,p-1] \times \left(
+    \cohptype[n][0,...,p] & (\fulldepscohs[n])                           & \defeq & \cohptype[n+1][0,...,p-1] \times \left(
     \begin{array}{l}
-        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
-        \depscohs.\restrp[n][p][q][\epsilon](\restrp[n+1][p][r][\omega]
-        \left(\begin{array}{l}
-                  \depscohs[n+1][0,...,n] \\
-                  \cohp[n+1][0,...,p-1]   \\
-                \end{array}\right)(d)) =                         \\
-        \depscohs.\restrp[n][p][r][\omega](\restrp[n+1][p][q+1][\epsilon]
-        \left(\begin{array}{l}
-                  \depscohs[n+1][0,...,n] \\
-                  \cohp[n+1][0,...,p-1]   \\
-                \end{array}\right)(d))
+        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:...\,\Pi c \\
+        \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf(d))(\restrp[n+1][p][r][\omega]
+        (\fulldepscohs[n+1])(d)(c)) =                         \\
+        \fulldepscohs.\depscohs.\restrp[n][p][r][\omega](\restrf(d))(\restrp[n+1][p][q+1][\epsilon]
+        (\fulldepscohs[n+1])(d)(c))
       \end{array}

### 2025-11-10 paper/paper.tex
Another bunch of fixes/additions

@@
             \deps[n][0,...,n-1] &:&\depstype[n][0,...,n-1] \\
-            E&:&\frame[n-1][n-1](\deps[n][0,...,n-1]) \rightarrow \U         \\
+            E&:&\frame[n][n](\deps[n][0,...,n-1]) \rightarrow \U         \\
           \end{array}\right)
@@
               \Sigma l:\layer(\fulldeps.\deps[n-1][0,...,p-1]). \\
-              \painting[n][p+1,...,n-1]
+              \painting[n][p+1]
               (\fulldeps[n-1])(d,l)                   \\
@@
 
-It is also convenient to abbreviate:
+It is also convenient to build $\deps$ from $\depscohs$ at the previous level:
 
@@
   \left(\begin{array}{l}
-            \overline{\deps}(\depscohs)\\
-            \depscohs.\fulldeps.E\\
+            \overline{\deps}(\fulldepscohs.\depscohs)\\
+            \fulldepscohs.\depscohs.\fulldeps.E\\
           \end{array}\right)             \\
@@
             \depscohs[n][0,...,n-1] &:&\depscohstype[n][0,...,n-1]                         \\
-            E&:&\framep[n-1][n-1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
+            E&:&\framep[n+1][n+1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
           \end{array}\right)
@@
     \left(\begin{array}{l}
-              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n-1][0,...,p-1])(l),               \\
+              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n-1][0,...,p-1])(...)(l),               \\
               \restrp[n][p][q][\epsilon]
@@
               \lambda q.\lambda r.\lambda \epsilon.\lambda \omega.\lambda (d,l). \\
-              \cohf[n][0,...,p][q][r][\epsilon][\omega]
+              (\cohf[n][0,...,p][q][r][\epsilon][\omega]
               \left(\begin{array}{l}
@@
                   \coht[n][0,...,p]     \\
-                \end{array}\right)(d)(l)                                     \\
+                \end{array}\right)(d)(l))                                     \\
             \end{array}\right)                                                                                    \\
@@
   \depscohttype[n][0,..,p-1] \defeq
-  \left(\begin{array}{l}
-            \fulldepscohs[n] :\fulldepscohstype[n]                        \\
-            \cohp[n][0,...p-1]: \cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
-            \coht[n][0,...,p-1]: \cohttype[n][0,...,p-1]
+  \left(\begin{array}{lll}
+            \fulldepscohs[n] &:&\fulldepscohstype[n]                        \\
+            \cohp[n][0,...p-1]&:& \cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
+            \coht[n][0,...,p-1]&:& \cohttype[n][0,...,p-1]
             \left(\begin{array}{l}
@@
 
-We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][0,...,n]$ with a set $E:\framep[n][n](\overline{\deps}(\overline{\deps}(\depscohs[n][0,...,n-1])))???
-\rightarrow \U$:
+It is also convenient to build $\depscohs$ from $\depscohtt$ at the previous level:
+
+\begin{align*}
+  \overline{\depscohs}(\depscoht:\depscohttype) & :      & \depscohstype \\
+  \overline{\depscohs}(\depscoht)               & \defeq &
+  \left(\begin{array}{l}
+            \overline{\deps}[n][p](\depscoht.\fulldepscohs.\depcohs[n][0,...,p])   \\
+            \restrpainting[n][p](\depscoht.\fulldepscohs[n][0,...,n]) \\
+            \cohf[n][p](\depscoht[n][0,...,p])         \\
+          \end{array}\right)             \\
+\end{align*}
+
+\begin{align*}
+  \overline{\fulldepscohs}(\fulldepscoht:\fulldepscohstype) & :      & \fulldepscohstype \\
+  \overline{\fulldepscohs}(\fulldepscoht)               & \defeq &
+  \left(\begin{array}{l}
+            \overline{\depscohs}(\fulldepscoht.\depscoht)\\
+            \fulldepscoht.\depscoht.\fulldepscohs.E\\
+          \end{array}\right)             \\
+\end{align*}
+
+We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][0,...,n]$ with a set $E:\framep[n][n](\overline{\depscohs}(\depscoht[n][0,...,n-1])) \rightarrow \U$:
 \begin{align*}
   \fulldepscohttype[n] \defeq
-  \left(\begin{array}{l}
-            \depscoht[n][0,...,n-1] :\depscohttype[n][0,...,n-1]    \\
-            E:\framep[n-1][n-1](\overline{\deps}(??))\rightarrow \U \\
+  \left(\begin{array}{lll}
+            \depscoht[n][0,...,n-1] &:&\depscohttype[n][0,...,n-1]    \\
+            E&:&\framep[n+2][n+2](\overline{\depscohs}(\depscoht[n][0,...,n-1]))\rightarrow \U \\
           \end{array}\right)
@@
     \cohp[n][p]                                        &
-    \left(\begin{array}{l}
-              \depscoht[n][0,...,n]:\depscohttype[n][0,...,n] \\
-              E:\framep[n-2][n-2]\rightarrow \U               \\
-              E':\framep[n-1][n-1]\rightarrow \U              \\
-              E'':\framep[n][n]\rightarrow \U                 \\
-            \end{array}\right) & :      &
+    (\fulldepscoht[n][0,...,n]:\fulldepscohttype[n][0,...,n]) & :      &
     \left(
     \begin{array}{l}
-        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
-        \depscohs.\restrp[n][p][q][\epsilon](\restrp[n+1][p][r][\omega]
-        \left(\begin{array}{l}
-                  \depscohs[n+1][0,...,n] \\
-                  \cohp[n+1][0,...,p-1]   \\
-                \end{array}\right)(d)) =                         \\
-        \depscohs.\restrp[n][p][r][\omega](\restrp[n+1][p][q+1][\epsilon]
-        \left(\begin{array}{l}
-                  \depscohs[n+1][0,...,n] \\
-                  \cohp[n+1][0,...,p-1]   \\
-                \end{array}\right)(d))
+        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d.\,\Pi c.\, \\
+        \restrp[n][p][q][\epsilon](\overline{\fulldeps}(\depscoht))(\restrp[n+1][p][r][\omega]
+        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][0,...,n])(d)(c)) =                         \\
+        \restrp[n][p][r][\omega](\overline{\fulldeps}(\depscoht))(\restrp[n+1][p][q+1][\epsilon]
+        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][0,...,n])(d)(c))                         \\
       \end{array}\right)                                                                                                       \\
     \cohp[n][n]                                        &
-    \left(\begin{array}{l}
-              \depscoht[n][0,...,n] \\
-              E                     \\
-              E'                    \\
-            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c). l\epsilon \\
+    (\fulldepscoht[n][0,...,n])
+       & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c). l\epsilon \\
     \cohp[n][p](p<n)                                   &
-    \left(\begin{array}{l}
-              \depscoht[n][0,...,n] \\
-              E                     \\
-              E'                    \\
-            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c).
-    \left(\begin{array}{l}
-              \cohl[n][p][q][\epsilon](\depscoht[n-1][0,...,p-1])(l),            \\
+    (\fulldepscoht[n][0,...,n])
+       & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c).
+    \left(\begin{array}{l}
+              \cohl[n][p][q][\epsilon](\fulldepscoht.\depscoht[n-1][0,...,p-1])(...)(l),            \\
               \cohp[n][p][q][\epsilon]
-              \left(\begin{array}{l}
-                  \depscoht[n][0,...,n] \\
-                  E                     \\
-                  E'                    \\
-                \end{array}\right)(\cohf[n][p](\depscoht[n][0,...,p])(d))(c) \\
+              (\fulldepscoht[n][0,...,n])(\cohf[n][p](\fulldepscoht.\depscoht[n][0,...,p])(d))(c) \\
             \end{array}\right)                                                                                         \\

### 2025-11-10 paper/paper.tex
paper: fix compile errors, send Hugo PDF

@@
   \left(\begin{array}{lll}
-            \framep[n][0,...,p-1] &:&\frametype[n][0,...,p-1] \\
-            \painting[n][0,...,p-1] &:&\paintingtype[n][0,...,p-1]
+            \framep[n][0,...,p-1]   & : & \frametype[n][0,...,p-1]    \\
+            \painting[n][0,...,p-1] & : & \paintingtype[n][0,...,p-1]
             (\framep[n][0,...,p-1])                                   \\
-            \restrf[n][0,...,p-1]  &:&\restrftype[n][0,...,p-1]
+            \restrf[n][0,...,p-1]   & : & \restrftype[n][0,...,p-1]
             \left(\begin{array}{l}
@@
   \left(\begin{array}{lll}
-            \deps[n][0,...,n-1] &:&\depstype[n][0,...,n-1] \\
-            E&:&\frame[n][n](\deps[n][0,...,n-1]) \rightarrow \U         \\
+            \deps[n][0,...,n-1] & : & \depstype[n][0,...,n-1]                          \\
+            E                   & : & \frame[n][n](\deps[n][0,...,n-1]) \rightarrow \U \\
           \end{array}\right)
@@
 
-Thanks to $\restrptype[n][0,...,n]$, we can mutually define $\restrf[n][p]$ and $\cohftype[n][p]$ from ``full dependencies'', that is from $\frame[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$ and some $E:\frame[n+1][n+1](\, using abbreviations in passing for $\layer$ and $\layertype$:
+Thanks to $\restrptype[n][0,...,n]$, we can mutually define $\restrf[n][p]$ and $\cohftype[n][p]$ from ``full dependencies'', that is from $\frame[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$ and some $E:\frame[n+1][n+1]$, using abbreviations in passing for $\layer$ and $\layertype$:
 
@@
             \end{array}\right)                                                     & \defeq &
-    \lambda q\leq n.
-\lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon])(l \omega)}                          \\
+    \lambda q\leq n. \lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon])(l \omega)} \\
   \end{array}
@@
   \depscohstype[n][0,..,p-1] \defeq
-  \left(\begin{array}{l}
-            \fulldeps[n][0,...,n] &:&\fulldepstype[n][0,...,n]        \\
-            \restrp[n][0,...p-1]&:& \restrptype[n][0,...,p-1] \\
-            \cohf[n][0,...,p-1]&:& \cohftype[n][0,...,p-1]    \\
+  \left(\begin{array}{lcl}
+            \fulldeps[n][0,...,n] & : & \fulldepstype[n][0,...,n] \\
+            \restrp[n][0,...p-1]  & : & \restrptype[n][0,...,p-1] \\
+            \cohf[n][0,...,p-1]   & : & \cohftype[n][0,...,p-1]   \\
           \end{array}\right)
@@
   \left(\begin{array}{l}
-            \overline{\deps}(\fulldepscohs.\depscohs)\\
-            \fulldepscohs.\depscohs.\fulldeps.E\\
+            \overline{\deps}(\fulldepscohs.\depscohs) \\
+            \fulldepscohs.\depscohs.\fulldeps.E       \\
           \end{array}\right)                                \\
@@
   \fulldepscohstype[n] \defeq
-  \left(\begin{array}{l}
-            \depscohs[n][0,...,n-1] &:&\depscohstype[n][0,...,n-1]                         \\
-            E&:&\framep[n+1][n+1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
+  \left(\begin{array}{lcl}
+            \depscohs[n][0,...,n-1] & : & \depscohstype[n][0,...,n-1]                                                \\
+            E                       & : & \framep[n+1][n+1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
           \end{array}\right)
@@
   \left(\begin{array}{lll}
-            \fulldepscohs[n] &:&\fulldepscohstype[n]                        \\
-            \cohp[n][0,...p-1]&:& \cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
-            \coht[n][0,...,p-1]&:& \cohttype[n][0,...,p-1]
+            \fulldepscohs[n]    & : & \fulldepscohstype[n]                      \\
+            \cohp[n][0,...p-1]  & : & \cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
+            \coht[n][0,...,p-1] & : & \cohttype[n][0,...,p-1]
             \left(\begin{array}{l}
@@
 
-It is also convenient to build $\depscohs$ from $\depscohtt$ at the previous level:
+It is also convenient to build $\depscohs$ from $\depscoht$ at the previous level:
 
@@
   \left(\begin{array}{l}
-            \overline{\deps}[n][p](\depscoht.\fulldepscohs.\depcohs[n][0,...,p])   \\
-            \restrpainting[n][p](\depscoht.\fulldepscohs[n][0,...,n]) \\
+            \overline{\deps}[n][p](\depscoht.\fulldepscohs.\depscohs[n][0,...,p]) \\
+            \restrp[n][p](\depscoht.\fulldepscohs[n][0,...,n])                    \\
             \cohf[n][p](\depscoht[n][0,...,p])                                    \\
@@
   \left(\begin{array}{l}
-            \overline{\depscohs}(\fulldepscoht.\depscoht)\\
-            \fulldepscoht.\depscoht.\fulldepscohs.E\\
+            \overline{\depscohs}(\fulldepscoht.\depscoht) \\
+            \fulldepscoht.\depscoht.\fulldepscohs.E       \\
           \end{array}\right)                                    \\
@@
   \left(\begin{array}{lll}
-            \depscoht[n][0,...,n-1] &:&\depscohttype[n][0,...,n-1]    \\
-            E&:&\framep[n+2][n+2](\overline{\depscohs}(\depscoht[n][0,...,n-1]))\rightarrow \U \\
+            \depscoht[n][0,...,n-1] & : & \depscohttype[n][0,...,n-1]                                                    \\
+            E                       & : & \framep[n+2][n+2](\overline{\depscohs}(\depscoht[n][0,...,n-1]))\rightarrow \U \\
           \end{array}\right)

### 2025-11-11 paper/paper.tex
Mostly completing definitions + checking the indices

@@
 
-Formally, this can be described as:
+Formally, this can be described as: (NOTE: in frame, p should be understood as (p+1)-1)
 \begin{equation*}
@@
   \begin{array}{llcl}
-    \framep[n][0,...,p]                                                                    &
+    \framep[n+1][0,...,p]                                                                    &
     \left(\begin{array}{l}
@@
                 \end{array}\right)                                              \\
-            \end{array}\right) & :      & \frametype[n][0,...,p]                             \\
-    \framep[n][0,]                                                                         &
+            \end{array}\right) & :      & \frametype[n+1][0,...,p]                             \\
+    \framep[n+1][0,...,(0+1)-1]                                                                          &
     \left(\begin{array}{l}
@@
             \end{array}\right)                                                                 & \defeq & (\unitpoint,unit) \\
-    \framep[n][0,...,p+1]                                                                  &
+    \framep[n+1][0,...,((p+1)+1)-1]                                                                  &
     \left(\begin{array}{l}
@@
               \left(\begin{array}{l}
-                  \framep[n+1][0,...,p-1]   \\
-                  \painting[n+1][0,...,p-1] \\
-                  \restrf[n+1][0,...,p-1]   \\
+                  \framep[n][0,...,p-1]   \\
+                  \painting[n][0,...,p-1] \\
+                  \restrf[n][0,...,p-1]   \\
                 \end{array}\right), \\
@@
               \left(\begin{array}{l}
-                  \framep[n+1][0,...,p-1]   \\
-                  \painting[n+1][0,...,p-1] \\
-                  \restrf[n+1][0,...,p-1]   \\
+                  \framep[n][0,...,p]   \\
+                  \painting[n][0,...,p] \\
+                  \restrf[n][0,...,p]   \\
                 \end{array}\right)(d) \\
@@
     \begin{array}{l}
-      \Sigma \restrf[n+1][0,...,p-1]
-      :\restrftype[n+1][0,...,p-1]
+      \Sigma \restrf[n][0,...,p-1]
+      :\restrftype[n][0,...,p-1]
       \left(\begin{array}{l}
@@
       \left(\begin{array}{l}
-                \framep[n+1][0,...,p-1]   \\
-                \painting[n+1][0,...,p-1] \\
-                \restrf[n+1][0,...,p-1]   \\
+                \framep[n][0,...,p-1]   \\
+                \painting[n][0,...,p-1] \\
+                \restrf[n][0,...,p-1]   \\
               \end{array}\right) \rightarrow  \framep[n][p] \\
@@
               \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
-              \restrf[n+1][0,...,p-1]:\restrftype[n][0,...,p-1] \\
+              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\
             \end{array}\right)
@@
               \painting[n][0,...,p]   \\
-              \restrf[n+1][0,...,p-1] \\
-            \end{array}\right)
-                                                                                           & \defeq & \framep[n][p]
+              \restrf[n][0,...,p] \\
+            \end{array}\right)
+                                                                                           & \defeq & \framep[n+1][p]
+    \left(\begin{array}{l}
+              \framep[n][0,...,p-1]     \\
+              \painting[n][0,...,p-1]   \\
+              \restrf[n][0,...,p-1] \\
+            \end{array}\right) \rightarrow \U                                                                               \\
+    \layer[n][p]                                                                           &
+    \left(\begin{array}{l}
+              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
+              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
+              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\
+            \end{array}\right)                                   & :      & \layertype[n][p]
+    \left(\begin{array}{l}
+              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
+              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
+              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\
+            \end{array}\right) \\
+    \layer[n][p]                                                                           &
     \left(\begin{array}{l}
@@
               \painting[n][0,...,p]   \\
-              \restrf[n+1][0,...,p-1] \\
-            \end{array}\right) \rightarrow \U                                                                               \\
-    \layer[n][p]                                                                           &
-    \left(\begin{array}{l}
-              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
-              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
-              \restrf[n+1][0,...,p-1]:\restrftype[n][0,...,p-1] \\
-            \end{array}\right)                                   & :      & \layertype[n][p](\framep[n][0,...,p])           \\
-    \layer[n][p]                                                                           &
-    \left(\begin{array}{l}
-              \framep[n][0,...,p]     \\
-              \painting[n][0,...,p]   \\
-              \restrf[n+1][0,...,p-1] \\
+              \restrf[n][0,...,p] \\
             \end{array}\right)                                                             & \defeq &
@@
 \end{align*}
-so that the type of $\framep[n][0,...,p]$ can be shortened into $\depstype[n][0,..,p-1] \rightarrow \frametype[n][0,...,p]$ and similarly for $\layertype[n][p]$ and $\layer[n][p]$.
+so that the type of $\framep[n+1][0,...,p]$ can be shortened into $\depstype[n][0,..,p-1] \rightarrow \frametype[n+1][0,...,p]$ and similarly for $\layertype[n][p]$ and $\layer[n][p]$.
 Later, we shall write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the corresponding projections of a $\deps$.
@@
 
-Defining $\painting[n][p]$, in addition to the type dependency in $\framep[n][p]$, requires the definition of $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$.
-Since $\painting[n][p]$ also depends on $\painting[n][p+1]$ when $p<n$, these dependencies are actually between $\painting[n][p,...,n]$, $\painting[n-1][p,...,n-1]$, $\framep[n][p,...,n]$, $\framep[n-1][p,...,n-1]$ and $\restrf[n][p,...,n]$.
-Also, for the case $p=n$, this also requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$.
-Finally, $\framep[n][p,...,n]$, $\framep[n-1][p,...,n-1]$ and $\restrf[n][p,...,n-1]$ respectively depend on the earlier values $\framep[n][0,...,p-1]$, $\framep[n-1][0,...,p-1]$ and $\restrf[n][0,...,p-1]$.
-Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n-1$ and $\restrftype$ at level $n$:
+Defining $\painting[n+1][p]$, in addition to the type dependency in $\framep[n+1][p]$, requires the definition of $\painting[n][p-1]$, thus also $\framep[n][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$.
+Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][p,...,n+1]$, $\painting[n][p,...,n]$, $\framep[n+1][p,...,n+1]$, $\framep[n][p,...,n]$ and $\restrf[n][p,...,n]$.
+Also, for the case $p=n$, this requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$.
+Finally, $\framep[n+1][p,...,n+1]$, $\framep[n+1][p,...,n]$ and $\restrf[n][p,...,n]$ respectively depend on the earlier values $\framep[n+1][0,...,p-1]$, $\framep[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$.
+Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n$ and $\restrftype$ at level $n$:
 \begin{center}
@@
   \begin{tikzcd}
-    & & \painting[n][p,...,n] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
-    \udensdash{\framep[n][0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
-    \udensdash{\framep[n][p,...,n]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
-    \painting[n-1][0,...,p-1] \arrow[d, dotted] & &
-    \painting[n-1][p,...,n-1] \arrow[ll, dotted] \arrow[d, dotted] \\
-    \framep[n-1][0,...,p-1] &
+    & & \painting[n+1][p,...,n+1] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
+    \udensdash{\framep[n+1][0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
+    \udensdash{\framep[n+1][p,...,n+1]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
+    \painting[n][0,...,p-1] \arrow[d, dotted] & &
+    \painting[n][p,...,n-1] \arrow[ll, dotted] \arrow[d, dotted] \\
+    \framep[n][0,...,p-1] &
     \udensdash{\restrf[n][0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
-    \framep[n-1][p,...,n-1] \arrow[ll, dotted, bend left=15] &
-    \udensdash{\restrf[n][p,...,n-1]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
+    \framep[n][p,...,n] \arrow[ll, dotted, bend left=15] &
+    \udensdash{\restrf[n+1][p,...,n]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
   \end{tikzcd}
@@
 
-Let us introduce another abbreviation to combine a full $\deps[n][0,n]$ with a family $E:\framep[n-1][n-1]\rightarrow \U$:
+Let us introduce another abbreviation to combine a full $\deps[n][0,...,n-1]:\depstype[n][0,...,n-1]$ with a family $E:\framep[n+1][n](\deps[n][0,...,n-1])\rightarrow \U$:
 \begin{align*}
@@
             \deps[n][0,...,n-1] & : & \depstype[n][0,...,n-1]                          \\
-            E                   & : & \frame[n][n](\deps[n][0,...,n-1]) \rightarrow \U \\
+            E                   & : & \framep[n+1][n](\deps[n][0,...,n-1]) \rightarrow \U \\
           \end{array}\right)
@@
 
-We can now formally define $\painting[n][p]$ by recursion on $n-p$:
+We can now formally define $\painting[n+1][p]$ by recursion on $n+1-p$:
 \begin{equation*}
@@
   \begin{array}{llcl}
-    \painting[n][p]      &
-    (\fulldeps[n-1]:\fulldepstype[n-1])                     \\
-    \painting[n][n]      &
-    (\fulldeps[n-1])     & \defeq & \fulldeps.E             \\
-    \painting[n][p](p<n) &
-    (\fulldeps[n-1])     & \defeq & d \mapsto
-    \left(\begin{array}{l}
-              \Sigma l:\layer(\fulldeps.\deps[n-1][0,...,p-1]). \\
-              \painting[n][p+1]
-              (\fulldeps[n-1])(d,l)                             \\
-            \end{array}\right) \\
-  \end{array}
-\end{equation*}
-
-From which we can deduce $\painting[n][0,...,p]$ by a second recursion, this time on $p$:
+    \painting[n+1][p]      &
+    (\fulldeps[n]:\fulldepstype[n])                     \\
+    \painting[n+1][n]      &
+    (\fulldeps[n])     & \defeq & \fulldeps.E             \\
+    \painting[n+1][p](p<n) &
+    (\fulldeps[n])     & \defeq & d \mapsto
+    \left(\begin{array}{l}
+              \Sigma l:\layer[n][p](\fulldeps.\deps[n][0,...,p]). \\
+              \painting[n+1][p+1]
+              (\fulldeps[n])(d,l)                             \\
+            \end{array}\right) \\
+  \end{array}
+\end{equation*}
+
+From which we can deduce $\painting[n+1][0,...,p]$ by a second recursion, this time on $p$:
 
@@
   \begin{array}{llcl}
-    \painting[n][0,...,p]   &
-    (\fulldeps[n-1])        & :      & \paintingtype[n][0,...,p](\framep[n][0,...,p](\fulldeps.\deps[n-1][0,...,p])) \\
-    \painting[n][0,...,0-1] &
+    \painting[n+1][0,...,p]   &
+    (\fulldeps[n-1])        & :      & \paintingtype[n+1][0,...,p](\framep[n+1][0,...,p](\fulldeps.\deps[n-1][0,...,p])) \\
+    \painting[n+1][0,...,0-1] &
     E                       & \defeq & \unittype                                                                     \\
-    \painting[n][0,...,p]   &
+    \painting[n+1][0,...,p]   &
     (\fulldeps[n-1])
                             & \defeq &
-    (\painting[n][0,...,p-1](\fulldeps[n-1]),\painting[n][p](\fulldeps[n-1]))                                        \\
-  \end{array}
-\end{equation*}
-
-At this stage, we are able to define $\framep[n][0,...,n]$, $\painting[n][0,...,n]$ and $\restrftype[n][0,...,n-1]$ from $\framep[n-1][0,...,n-1]$, $\painting[n-1][0,...,n-1]$ and $\restrf[n-1][0,...,n-1]$, that is from $\deps[n-1][0,...,n-1]$.
+    (\painting[n+1][0,...,p-1](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n-1]))                                        \\
+  \end{array}
+\end{equation*}
+
+At this stage, we are able to define $\framep[n+1][0,...,n]$, $\painting[n+1][0,...,n]$ and $\restrftype[n][0,...,n-1]$ from $\framep[n][0,...,n-1]$, $\painting[n][0,...,n-1]$ and $\restrf[n][0,...,n-1]$, that is from $\deps[n][0,...,n-1]$.
 To go further, we need to define the sequence $\restrptype[n][0,...,p]$ of types of painting restrictions:
@@
   \begin{array}{llcl}
-    \restrptype[n][0,...,p]             &
-    (\fulldeps[n-1]:\fulldepstype[n-1]) & :      & \U                                                    \\
-    \restrptype[n][]                    & E      & \defeq                                    & \unittype \\
-    \restrptype[n][0,...,p]             &
-    (\fulldeps[n-1])
+    \restrptype[n][0,...,p-1]             &
+    (\fulldeps[n]:\fulldepstype[n]) & :      & \U                                                    \\
+    \restrptype[n][0,...,0-1]                & E      & \defeq                                    & \unittype \\
+    \restrptype[n][0,...,(p+1)-1]            &
+    (\fulldeps[n])
                                         & \defeq & \restrptype[n+1][0,...,p-1] \times \left(
     \begin{array}{l}
-        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep[n][p](\fulldeps.\deps[n][0,...,p]). \\
-        \painting[n][p]
-        (\fulldeps[n-1])(d) \rightarrow                                            \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
+        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][0,...,p-1]). \\
+        \painting[n+1][p]
+        (\fulldeps[n])(d) \rightarrow                                            \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
     \right)                                                                                              \\
@@
 
-Thanks to $\restrptype[n][0,...,n]$, we can mutually define $\restrf[n][p]$ and $\cohftype[n][p]$ from ``full dependencies'', that is from $\frame[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$ and some $E:\frame[n+1][n+1]$, using abbreviations in passing for $\layer$ and $\layertype$:
+Thanks to $\restrptype[n][0,...,p-1]$, we can mutually define $\restrf[n+1][0,...,p]$ and $\cohftype[n][0,...,p-1]$ from ``full dependencies'', that is from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$ and some $E:\framep[n+1][n](\deps[n][0,...,n-1]) \rightarrow \U$, using abbreviations in passing for $\restrl$ and $\restrltype$:
 
@@
   \begin{array}{llcl}
-    \restrf[n][0,...,p]                                                          &
+    \restrf[n+1][0,...,(p+1)-1]                                                          &
     \multicolumn{3}{l}{
@@
                 \fulldeps[n]:\fulldepstype[n]   \\
-                \restrp[n][0,...,p-2]:\restrptype[n][0,...,p-1]
-                \left(\begin{array}{l}
-                    \fulldeps[n] \\
-                  \end{array}\right)      \\
-                \cohf[n][0,...,p]:\cohftype[n][0,...,p]
-                \left(\begin{array}{l}
-                    \fulldeps[n]          \\
-                    \restrp[n][0,...,p-2] \\
+                \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1]
+                (\fulldeps[n])    \\
+                \cohf[n][0,...,p-1]:\cohftype[n][0,...,p-1]
+                \left(\begin{array}{l}
+                    \fulldeps[n]          \\
+                    \restrp[n][0,...,p-1] \\
                   \end{array}\right) \\
               \end{array}\right) :
-      \restrftype[n][0,...,p]
-      \left(\begin{array}{l}
-                \framep[n][0,...,p](\fulldeps.\deps[n][0,...,p]) \\
-                \painting[n][0,...,p](\fulldeps[n])              \\
+      \restrftype[n+1][0,...,p]
+      \left(\begin{array}{l}
+                \framep[n+1][0,...,p](\fulldeps.\deps[n][0,...,p])   \\
+                \painting[n+1][0,...,p](\fulldeps[n]) \\
               \end{array}\right)
     }                                                                                                                                                        \\
-    \restrf[n][0,...,0-1]                                                        &
+    \restrf[n+1][0,...,(0+1)-1]                                                        &
     \left(\begin{array}{l}
@@
             \end{array}\right)                                                       & \defeq & (\unitpoint,\lambda q. \lambda\epsilon. \lambda \_.\unitpoint) \\
-    \restrf[n][0,...,(p+1)-1]                                                    &
+    \restrf[n+1][0,...,((p+1)+1)-1]                                                    &
     \left(\begin{array}{l}
@@
               \left(\begin{array}{l}
-                  \fulldeps[n+1]          \\
-                  \restrp[n+1][0,...,p-1] \\
-                  \cohf[n+1][0,...,p-1]   \\
+                  \fulldeps[n]          \\
+                  \restrp[n][0,...,p-1] \\
+                  \cohf[n][0,...,p-1]   \\
                 \end{array}\right),             \\
@@
               \left(\begin{array}{l}
-                    \fulldeps[n+1]          \\
-                    \restrp[n+1][0,...,p-1] \\
-                    \cohf[n+1][0,...,p-1]   \\
+                    \fulldeps[n]          \\
+                    \restrp[n][0,...,p-1] \\
+                    \cohf[n][0,...,p-1]   \\
                   \end{array}\right)(d), \restrl[n][p][q][\epsilon]
@@
                     \fulldeps[n]      \\
-                    \restrp[n+1][0,...,p-1] \\
+                    \restrp[n][0,...,p] \\
                     \cohf[n][0,...,p] \\
@@
             \end{array}\right)                                                       & \defeq &
-    \begin{array}{l}
-      \Sigma \cohf[n+1][0,...,p-1]
-      :\cohftype[n+1][0,...,p-1]
-      \left(\begin{array}{l}
-                \fulldeps[n+1]          \\
-                \restrp[n+1][0,...,p-1] \\
+    \left\{\begin{array}{l}
+      \Sigma \cohf[n][0,...,p-1]
+      :\cohftype[n][0,...,p-1]
+      \left(\begin{array}{l}
+                \fulldeps[n]          \\
+                \restrp[n][0,...,p-1] \\
               \end{array}\right).                          \\
-      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n][p]
-      \left(\begin{array}{l}
-                \frame(\fulldeps.\deps[n][0,...,p])     \\
-                \painting[n+1][0,...,p-1](\fulldeps[n]) \\
-                \restrf[n][0,...,p]
-                \left(\begin{array}{l}
-                    \fulldeps[n+1]          \\
-                    \restrp[n+1][0,...,p-1] \\
-                    \cohf[n][0,...,p]       \\
+      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p]
+      \left(\begin{array}{l}
+                \framep[n+1][p](\fulldeps.\deps[n][0,...,p-1])          \\
+                \painting[n+1][0,...,p](\fulldeps[n]) \\
+                \restrf[n+1][0,...,p]
+                \left(\begin{array}{l}
+                  \fulldeps[n]          \\
+                  \restrp[n][0,...,p-1] \\
+                  \cohf[n][0,...,p-1] \\
                 \end{array}\right)                         \\
@@
       \left(\begin{array}{l}
-                \fulldeps[n+1]          \\
-                \restrp[n+1][0,...,p-1] \\
-                \cohf[n][0,...,p]       \\
+                \fulldeps[n]          \\
+                \restrp[n][0,...,p-1] \\
+                \cohf[n][0,...,p-1] \\
               \end{array}\right)(d)) =                         \\
@@
       \left(\begin{array}{l}
-                \fulldeps[n+1]          \\
-                \restrp[n+1][0,...,p-1] \\
-                \cohf[n][0,...,p]       \\
+                \fulldeps[n]          \\
+                \restrp[n][0,...,p-1] \\
+                \cohf[n][0,...,p-1] \\
               \end{array}\right)(d))                          \\
-    \end{array}                                                                                                        \\
+    \end{array}\right.                                                                                        \\
     \restrltype[n][p]                                                            &
@@
               \fulldeps[n]:\fulldepstype[n]                                        \\
-              \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1]) \\
-              \cohf[n][0,...,p]:\cohftype[n][0,...,p]                              \\
+              \restrp[n][0,...,p]:\restrptype[n][0,...,p](\fulldeps[n]) \\
+              \cohf[n][0,...,p]:\cohftype[n][0,...,p]
+                \left(\begin{array}{l}
+                  \fulldeps[n]          \\
+                  \restrp[n][0,...,p] \\
+                \end{array}\right)                                   \\
+\\
             \end{array}\right)      & :      & \U                                                                               \\
@@
               \fulldeps[n]          \\
-              \restrp[n][0,...,p-1] \\
+              \restrp[n][0,...,p] \\
               \cohf[n][0,...,p]     \\
             \end{array}\right)
-                                                                                 & \defeq & \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n][p].\left(
-    \begin{array}{l}
-        \layer[n][p]\left(
+    & \defeq & \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+1][p]
+    \left(
         \begin{array}{l}
@@
           \end{array}\right)(d) \rightarrow \\
-        \layer[n][p](\fulldeps.\deps[n][0,...,n])(\restrf[n][p]
+        \layer[n][p](\fulldeps.\deps[n][0,...,p])(\restrf[n][p]
         \left(\begin{array}{l}
@@
                   \restrp[n][0,...,p-1]       \\
-                  \cohf[n][0,...,p]
+                  \cohf[n][0,...,p-1]
                 \end{array}\right)(d))
@@
               \fulldeps[n]:\fulldepstype[n]                                 \\
-              \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\fulldeps[n]) \\
-              \cohf[n][0,...,p-1]:\cohftype[n][0,...,p-1]
-              \left(\begin{array}{l}
-                  \fulldeps[n]          \\
-                  \restrp[n][0,...,p-1] \\
+              \restrp[n][0,...,p]:\restrptype[n][0,...,p](\fulldeps[n]) \\
+              \cohf[n][0,...,p]:\cohftype[n][0,...,p]
+              \left(\begin{array}{l}
+                  \fulldeps[n]          \\
+                  \restrp[n][0,...,p] \\
                 \end{array}\right)                                   \\
@@
     \restrltype[n][p] \left(\begin{array}{l}
-                                \deps[n][0,...,n]     \\
-                                \restrp[n][0,...,p-1] \\
+                                \fulldeps[n] \\
+                                \restrp[n][0,...,p] \\
                                 \cohf[n][0,...,p] \\
@@
             \end{array}\right)                                                     & \defeq &
-    \lambda q\leq n. \lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon])(l \omega)} \\
+    \lambda q\leq n. \lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon]\left(\begin{array}{l}
+                  \fulldeps[n] \\
+                  \restrp[n][0,...,p-1]       \\
+                  \cohf[n][0,...,p-1]
+                \end{array}\right)(d))(l \omega)}                          \\
   \end{array}
@@
 \end{align*}
-so that the type of $\restrf[n][0,...,p]$ can be rephrased as $\Pi \depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1]. \restrftype[n][0,...,p]      \left(\begin{array}{l}
-      \depscohs.\fulldeps.\deps.\framep[n][0,...,p]   \\
-      \depscohs.\fulldeps.\deps.\painting[n][0,...,p] \\
+so that the type of $\restrf[n+1][0,...,p]$ can be rephrased as $\Pi \depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1]. \restrftype[n+1][0,...,p]
+      \left(\begin{array}{l}
+                \framep[n+1][0,...,p](\fulldeps.\deps[n][0,...,p])   \\
+                \painting[n+1][0,...,p](\fulldeps[n]) \\
               \end{array}\right)$, and similarly for $\restrltype$ and $\restrl$.
 Later, we shall write $\depscohs.\deps$, $\depscohs.\restrp$, and $\depscohs.\cohf$ for the corresponding projections of an element $\depscohs$ in $\depscohstype$.
-By abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depscohstype[n][0,..,0-1]$.
-
-It is also convenient to build $\deps$ from $\depscohs$ at the previous level:
-
+By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n][0,..,0-1]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).
+
+It is also convenient to build $\deps$ from $\depscohs$ at the
+previous level:
 \begin{align*}
-  \overline{\deps}(\depscohs:\depscohstype) & :      & \depstype \\
+  \overline{\deps}(\depscohs[n][0,...,p-1]:\depscohstype[n][0,...,p-1]) & :      & \depstype[n+1][0,...,p] \\
   \overline{\deps}(\depscohs)               & \defeq &
   \left(\begin{array}{l}
-            \framep[n][p](\depscohs.\fulldeps.\deps[n][0,...,p]) \\
-            \painting[n][p](\depscohs.\fulldeps[n][0,...,n])     \\
-            \restrf[n][p](\depscohs[n][0,...,p])                 \\
+            \framep[n+1][0,...,p](\depscohs.\fulldeps.\deps[n][0,...,p-1])   \\
+            \painting[n+1][0,...,p](\depscohs.\fulldeps[n]) \\
+            \restrf[n+1][0,...,p](\depscohs[n][0,...,p-1])         \\
           \end{array}\right)             \\
@@
 
-\begin{align*}
-  \overline{\fulldeps}(\fulldepscohs:\fulldepscohstype) & :      & \fulldepstype \\
-  \overline{\fulldeps}(\fulldepscohs)                   & \defeq &
-  \left(\begin{array}{l}
-            \overline{\deps}(\fulldepscohs.\depscohs) \\
-            \fulldepscohs.\depscohs.\fulldeps.E       \\
-          \end{array}\right)                                \\
-\end{align*}
-
-We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][0,...,n]$ with a set $E:\framep[n][n](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$:
+We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][0,...,n]$ with a set $E:\framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$:
 \begin{align*}
@@
             \depscohs[n][0,...,n-1] & : & \depscohstype[n][0,...,n-1]                         \\
-            E                       & : & \framep[n+1][n+1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
+            E                       & : & \framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
           \end{array}\right)
@@
 
+We can then extend $\overline{\deps}$ to build $\fulldeps$ from $\fulldepscohs$:
+\begin{align*}
+  \overline{\fulldeps}(\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \fulldepstype[n+1] \\
+  \overline{\fulldeps}(\fulldepscohs[n])               & \defeq &
+  \left(\begin{array}{l}
+            \overline{\deps}(\fulldepscohs.\depscohs[n][0,...,n-1])\\
+            \fulldepscohs.\depscohs.\fulldeps.E\\
+          \end{array}\right)             \\
+\end{align*}
+
 Also, when $n$ is 0, we write $(E',E)$ to denote an element $(E', E)$ of $\fulldepscohstype[0]$.
@@
   \begin{array}{llcl}
-    \restrp[n][p]                           &
+    \restrp[n+1][p]                           &
     (\fulldepscohs[n]:\fulldepscohstype[n]) & :      &
@@
     \begin{array}{l}
-        \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n][p]
-        (\overline{\deps}(\depscohs)).                         \\
-        \painting[n][p]
-        (\overline{\fulldeps}(\fulldepscohs[n])(d) \rightarrow \\
-        \painting[n-1][p](\fulldepscohs.\depscohs.\fulldeps[n])
-        (\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,n])(d))\end{array}\right)                                                        \\
-    \restrp[n][n]                           &
-    (\fulldepscohs[n][0,...,n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
-    \restrp[n][p](p<n)                      &
-    (\fulldepscohs[n][0,...,n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
-    \left(\begin{array}{l}
-              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n-1][0,...,p-1])(...)(l), \\
-              \restrp[n][p][q][\epsilon]
-              (\fulldepscohs[n])(\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,p])(d))(c) \\
+        \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n+2][p]
+        (\overline{\deps}(\fulldepscohs.\depscohs[n][0,...,p-1])).    \\
+        \painting[n+2][p]
+        (\overline{\fulldeps}(\fulldepscohs[n]))(d) \rightarrow \\
+        \painting[n+1][p](\fulldepscohs.\depscohs.\fulldeps[n])
+          (\restrf[n+1][p](\fulldepscohs.\depscohs[n][0,...,p-1])(d))\end{array}\right)                                       \\
+    \restrp[n+1][n]                           &
+    (\fulldepscohs[n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
+    \restrp[n+1][p](p<n)                      &
+    (\fulldepscohs[n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
+    \left(\begin{array}{l}
+      \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n][0,...,p])(d)(l),               \\
+              \restrp[n+1][p+1][q][\epsilon](\fulldepscohs[n])(d,l)(c) \\
             \end{array}\right)                              \\
@@
 
-...
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \restrp[n+1][0,...,p]   &
+    (\fulldepscohs[n])        & :      & \restrptype[n+1][0,...,p](\fulldepscohs.\depscohs.\fulldeps[n])) \\
+    \restrp[n+1][0,...,0-1] &
+    E  & \defeq & \unittype                                                                   \\
+    \restrp[n+1][0,...,p]   &
+    (\fulldepscohs[n])
+                            & \defeq &
+    (\restrp[n+1][0,...,p-1](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))                                        \\
+  \end{array}
+\end{equation*}
 
@@
 
-At this stage, we are then able to define $\restrf$, $\restrp$ and $\cohftype$
-from $\depscohs$ at the previous level. To go further, we need to define the
-sequence $\cohptype$ of types of painting coherence laws:
+At this stage, we are then able to define $\restrf[n+1][0,...,p]$, $\restrp[n+1][0,...,p]$ and $\cohftype[n][0,...,p]$
+from $\depscohs[n][0,...,p-1]$ at the previous level. To go further, we need to define the
+sequence $\cohptype[n][0,...,p-1]$ of types of painting coherence laws:
 
@@
   \begin{array}{llcl}
-    \cohptype[n][0,...,p] & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                      \\
-    \cohptype[n][]        & \unitpoint                              & \defeq & \unittype                               \\
-    \cohptype[n][0,...,p] & (\fulldepscohs[n])                      & \defeq & \cohptype[n+1][0,...,p-1] \times \left(
+    \cohptype[n][0,...,p-1] & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                      \\
+    \cohptype[n][0,...,0-1]        & \unitpoint                                        & \defeq & \unittype                               \\
+    \cohptype[n][0,...,(p+1)-1] & (\fulldepscohs[n])                           & \defeq & \cohptype[n][0,...,p-1](\fulldepscohs[n]) \times \left(
     \begin{array}{l}
-        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:...\,\Pi c \\
-        \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf(d))(\restrp[n+1][p][r][\omega]
-        (\fulldepscohs[n+1])(d)(c)) =                                            \\
-        \fulldepscohs.\depscohs.\restrp[n][p][r][\omega](\restrf(d))(\restrp[n+1][p][q+1][\epsilon]
-        (\fulldepscohs[n+1])(d)(c))
+        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][0,...,p-1])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n]))\\
+        \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf[n+1][p](d))(\restrp[n+1][p][r][\omega]
+        (\fulldepscohs[n])(d)(c)) =                         \\
+        \fulldepscohs.\depscohs.\restrp[n][p][r][\omega](\restrf[n+1][p](d))(\restrp[n+1][p][q+1][\epsilon]
+        (\fulldepscohs[n])(d)(c))
       \end{array}
@@
   \begin{array}{llcl}
-    \cohf[n][0,...,p]                                                           &
+    \cohf[n+1][0,...,p]                                                           &
     \left(\begin{array}{l}
               \fulldepscohs[n]:\fulldepscohstype[n]                                    \\
-              \cohp[n][0,...,p-2]:\restrptype[n][0,...,p-1](\fulldepscohs[n][0,...,n]) \\
-              \coht[n][0,...,p]:\cohttype[n][0,...,p]
+              \cohp[n][0,...,p-1]:\cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
+              \coht[n][0,...,p-1]:\cohttype[n][0,...,p-1]
               \left(\begin{array}{l}
@@
                 \end{array}\right)
-            \end{array}\right) & :      & \cohftype[n][0,...,p]                                                                                             \\
-    \cohf[n][0]                                                                 &
+            \end{array}\right) & :      & \cohftype[n+1][0,...,p]                                                                                             \\
+    \cohf[n][0,...,(0+1)-1]                                                           &
     \left(\begin{array}{l}
@@
             \end{array}\right)                                                      & \defeq & (\unitpoint,\lambda q.\lambda r. \lambda\epsilon. \lambda\omega.\lambda \_.\refl) \\
-    \cohf[n][0,...,p+1]                                                         &
+    \cohf[n][0,...,((p+1)+1)-1]                                                         &
     \left(\begin{array}{l}
@@
               \left(\begin{array}{l}
-                  \fulldepscohs[n+1]    \\
+                  \fulldepscohs[n]    \\
                   \cohp[n+1][0,...,p-1] \\
@@
                   \fulldepscohs[n]      \\
-                  \cohp[n+1][0,...,p-1] \\
+                  \cohp[n][0,...,p] \\
                   \coht[n][0,...,p]     \\
@@
     \left(\begin{array}{l}
-              \Sigma \coht[n+1][0,...,p-1]
-              :\cohttype[n+1][0,...,p-1]
+              \Sigma \coht[n][0,...,p-1]
+              :\cohttype[n][0,...,p-1]
               \left(\begin{array}{l}
@@
               \left(\begin{array}{l}
-                  \fulldepscohs[n+1]    \\
-                  \cohp[n+1][0,...,p-1] \\
-                  \coht[n+1][0,...,p-1]
+                  \fulldepscohs[n]    \\
+                  \cohp[n][0,...,p-1] \\
+                  \coht[n][0,...,p-1]
                 \end{array}\right)
@@
                   \fulldepscohs[n+1]    \\
-                  \cohp[n+1][0,...,p-1] \\
-                  \coht[n+1][0,...,p-1]
+                  \cohp[n][0,...,p-1] \\
+                  \coht[n][0,...,p-1]
                 \end{array}\right)
@@
               \left(\begin{array}{l}
-                  \fulldepscohs[n+1]    \\
-                  \cohp[n+1][0,...,p-1] \\
-                  \coht[n+1][0,...,p-1]
+                  \fulldepscohs[n]    \\
+                  \cohp[n][0,...,p-1] \\
+                  \coht[n][0,...,p-1]
                 \end{array}\right)                                         \\
@@
               \fulldepscohs[n]:\fulldepscohstype[n]   \\
-              \cohp[n+1][p]:\cohptype[n+1][p]         \\
+              \cohp[n][0,...,p]:\cohptype[n][0,...,p]         \\
               \coht[n][0,...,p]:\cohttype[n][0,...,p] \\
@@
               \fulldepscohs[n]  \\
-              \cohp[n][p]       \\
+              \cohp[n][0,...,p]       \\
               \cohf[n][0,...,p] \\
@@
 
-It is also convenient to build $\depscohs$ from $\depscoht$ at the previous level:
+It is also convenient to build $\depscohs[n+1][0,...,p]$ from $\depscoht[n][0,...,p]$ at the previous level:
 
 \begin{align*}
-  \overline{\depscohs}(\depscoht:\depscohttype) & :      & \depscohstype      \\
-  \overline{\depscohs}(\depscoht)               & \defeq &
-  \left(\begin{array}{l}
-            \overline{\deps}[n][p](\depscoht.\fulldepscohs.\depscohs[n][0,...,p]) \\
-            \restrp[n][p](\depscoht.\fulldepscohs[n][0,...,n])                    \\
-            \cohf[n][p](\depscoht[n][0,...,p])                                    \\
+  \overline{\depscohs}(\depscoht[n][0,...,p]:\depscohttype[n][0,...,p]) & :      & \depscohstype[n+1][0,...,p] \\
+  \overline{\depscohs}(\depscoht[n][0,...,p])               & \defeq &
+  \left(\begin{array}{l}
+            \overline{\deps}(\depscoht.\fulldepscohs.\depscohs[n][0,...,p-1])   \\
+            \restrp[n+1][p](\depscoht.\fulldepscohs[n][0,...,n]) \\
+            \cohf[n+1][p](\depscoht[n][0,...,p-1])         \\
           \end{array}\right)             \\
 \end{align*}
+
+We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][0,...,n]$ with a set $E:\framep[n+3][n+2](\overline{\depscohs}(\depscoht[n][0,...,n-1])) \rightarrow \U$:
+\begin{align*}
+  \fulldepscohttype[n] \defeq
+  \left(\begin{array}{lll}
+            \depscoht[n][0,...,n-1] &:&\depscohttype[n][0,...,n-1]    \\
+            E&:&\framep[n+3][n+2](\overline{\depscohs}(\depscoht[n][0,...,n-1]))\rightarrow \U \\
+          \end{array}\right)
+\end{align*}
+
+We can then extend $\overline{\depscohs}$ to build $\fulldepscohs$ from $\fulldepscoht$:
 
@@
             \overline{\depscohs}(\fulldepscoht.\depscoht) \\
-            \fulldepscoht.\depscoht.\fulldepscohs.E       \\
+            \overline{\depscohs}(\fulldepscoht.\depscoht[n][0,...,n-1])\\
+            \fulldepscoht.\depscoht.\fulldepscohs.E\\
           \end{array}\right)             \\
@@
 
-We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][0,...,n]$ with a set $E:\framep[n][n](\overline{\depscohs}(\depscoht[n][0,...,n-1])) \rightarrow \U$:
-\begin{align*}
-  \fulldepscohttype[n] \defeq
-  \left(\begin{array}{lll}
-            \depscoht[n][0,...,n-1] & : & \depscohttype[n][0,...,n-1]                                                    \\
-            E                       & : & \framep[n+2][n+2](\overline{\depscohs}(\depscoht[n][0,...,n-1]))\rightarrow \U \\
-          \end{array}\right)
-\end{align*}
-
-The next step is to define $\cohp[n][p]$ by recursion on $n-p$:
+The last key construction we need is $\cohp[n+1][p]$, which is by recursion on $n-p$:
 
@@
   \begin{array}{llcl}
-    \cohp[n][p]                                               &
-    (\fulldepscoht[n][0,...,n]:\fulldepscohttype[n][0,...,n]) & :      &
+    \cohp[n+1][p]                                        &
+    (\fulldepscoht[n]:\fulldepscohttype[n]) & :      &
     \left(
@@
         (\fulldepscoht.\depscoht.\fulldepscohs[n+1][0,...,n])(d)(c))             \\
-      \end{array}\right)                                                                                 \\
-    \cohp[n][n]                                               &
-    (\fulldepscoht[n][0,...,n])
+        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][0,...,n])(d)(c))                         \\
+      \end{array}\right)                                                                                                       \\
+    \cohp[n+1][n]                                        &
+    (\fulldepscoht[n])
        & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c). l\epsilon \\
-    \cohp[n][p](p<n)                                          &
-    (\fulldepscoht[n][0,...,n])
+    \cohp[n+1][p](p<n)                                   &
+    (\fulldepscoht[n])
        & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c).
     \left(\begin{array}{l}
-              \cohl[n][p][q][\epsilon](\fulldepscoht.\depscoht[n-1][0,...,p-1])(...)(l),          \\
-              \cohp[n][p][q][\epsilon]
-              (\fulldepscoht[n][0,...,n])(\cohf[n][p](\fulldepscoht.\depscoht[n][0,...,p])(d))(c) \\
-            \end{array}\right)                                                                                \\
-  \end{array}
-\end{equation*}
-
-From which we can deduce $\cohp[n][0,...,p]$ again by a second recursion, this time on $p$:
-
-Armed with all the constructions we can now define
+              \cohl[n][p][q][r][\epsilon][\omega](\fulldepscoht.\depscoht[n][0,...,p-1])(d)(l),            \\
+              \cohp[n+1][p+1][q][r][\epsilon][\omega](\fulldepscoht[n])(d,l))(c) \\
+            \end{array}\right)                                                                                         \\
+  \end{array}
+\end{equation*}
+
+From which we can deduce $\cohp[n+1][0,...,p]$ again by a second recursion, this time on $p$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \cohp[n+1][0,...,p]   &
+    (\fulldepscoht[n])        & :      & \cohptype[n+1][0,...,p](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
+    \cohp[n+1][0,...,0-1] &
+    E  & \defeq & \unittype                                                                   \\
+    \cohp[n+1][0,...,p]   &
+    (\fulldepscoht[n])
+                            & \defeq &
+    (\cohp[n+1][0,...,p-1](\fulldepscoht[n]),\cohp[n+1][p](\fulldepscoht[n]))                                        \\
+  \end{array}
+\end{equation*}
+
+Armed with all the constructions and assuming enough $E:\framep[n][n-1]
+\rightarrow \U$ given, we can now define $\framep[n][p]$,
+$\painting[n][p]$, $\restrf[n][p]$, $\restrp[n][p]$, $\cohf[n][p]$,
+and $\cohp[n][p]$ for all $n$ and $p$. It is indeed enough to build
+$\fulldepscoht[n]$ by induction on $n$:
+\begin{itemize}
+\item $\fulldepscohs[n+1]$ is $\overline{\fulldepscohs}(\fulldepscoht[n])$
+\item $\cohp[n+1][0,...,n]$ is given from $\fulldepscoht$ as above
+\item $\coht[n+1][0,...,n]$ is given by uniqueness of identity proofs
+\end{itemize}
+
 \bibliographystyle{msclike}

### 2025-11-11 paper/paper.tex
Add for all p in previous nuset record for mscs
Structuring the construction into subsections

@@
 
+\section{Outline of the recursive structure of iterated parametricity construction}
+
 In \citep{hr25}, the well-foundedness was justified by induction on $n$ and subinductions, one on $p$ to mutually build $\framep[n][p]$, $\restrf[n][p]$ and $\cohf[n][p]$, and three others to build each of $\painting[n][p]$, $\restrp[n][p]$ and $\cohp[n][p]$ by induction on $n-p$.
@@
 \begin{align*}
-  \framep[n][p]      & : \U                                                                                                                 \\
-  \framep[n-1][p]    & :  \U                                                                                                                \\
-  \framep[n-2][p]    & : \U                                                                                                                 \\
-  \restrf[n][p]      & : \Pi q.\, \Pi \omega.\, \framep[n][p] \rightarrow \framep[n-1][p]                                                   \\
-  \restrf[n-1][p]    & : \Pi q.\, \Pi \omega.\, \framep[n-1][p] \rightarrow \framep[n-2][p]                                                 \\                                                                 \\
+  \framep[n][p]      & : \U & \mbox{for all $p\leq n$}                                                                                      \\
+  \framep[n-1][p]    & : \U & \mbox{for all $p\leq n-1$}                                                                                    \\
+  \framep[n-2][p]    & : \U & \mbox{for all $p\leq n-2$}                                                                                    \\
+  \restrf[n][p]      & : \Pi q.\, \Pi \omega.\, \framep[n][p] \rightarrow \framep[n-1][p] & \mbox{for all $p\leq n$}                        \\
+  \restrf[n-1][p]    & : \Pi q.\, \Pi \omega.\, \framep[n-1][p] \rightarrow \framep[n-2][p] & \mbox{for all $p\leq n-1$}                    \\
   \cohf[n][p]        & : \Pi qr\epsilon\omega.\, \restrf[n-1][p][\epsilon][q] \circ \restrf[n][p][\omega][r] =                              \\
-                     & \;\;\;\;\restrf[n-1][p][\omega][r] \circ \restrf[n][p][\epsilon][q+1]                                                \\
+                     & \;\;\;\;\restrf[n-1][p][\omega][r] \circ \restrf[n][p][\epsilon][q+1] & \mbox{for all $p\leq n$}                     \\
   \mathsf{hypF0}     & : \framep[n][0]         = \unitpoint
   \\
-  \mathsf{hypFS0}    & : \framep[n][p+1]       = \Sigma d: \framep[n+1][p]. \Pi \omega.\, \painting[n][p] (\restrf[n+1][p](d))              \\
-  \mathsf{hypPrevF}  & : \framep[n-1][0]                                                                                       = \unitpoint \\
-  \mathsf{hypPrevFS} & : \framep[n-1][p+1] = \Sigma d: \framep[n][p]. \Pi \omega.\, \painting[n-1][p] (\restrf[n][p](d))                    \\
+  \mathsf{hypFS}     & : \framep[n][p+1]       = \Sigma d: \framep[n+1][p]. \Pi \omega.\, \painting[n][p] (\restrf[n+1][p](d)) & \mbox{for all $p\leq n-1$} \\
+  \mathsf{hypPrevF0} & : \framep[n-1][0]                                                                                       = \unitpoint \\
+  \mathsf{hypPrevFS} & : \framep[n-1][p+1] = \Sigma d: \framep[n][p]. \Pi \omega.\, \painting[n-1][p] (\restrf[n][p](d)) & \mbox{for all $p\leq n-2$}    \\
   \mathsf{hypRF0}    & : \restrf[n][0]        = \ldots \texttt{depending on hypF0}                                                          \\
-  \mathsf{hypRFS}    & : \restrf[n][p+1]      = \ldots \texttt{depending on hypFS and hypPrevFS}                                            \\
+  \mathsf{hypRFS}    & : \restrf[n][p+1]      = \ldots \texttt{depending on hypFS and hypPrevFS} & \mbox{for all $p\leq n-1$}               \\
   \ldots             & \;\;\;\;\texttt{fields for painting, restrf, cohp}
@@
 If $\framep[n][0,...,p]$ is such a sequence of length $p+1$, we write $\framep[n][0,...,p-1]$ for its immediate subsequence of length $p$ and $\framep[n][p]$ for its last component.
+
+\section{The construction}
+
+\subsection{Specifying frames and paintings}
+
 We can now define the types of sequences of $\framep$ and $\painting$ as follows:
@@
 
-Formally, this can be described as: (NOTE: in frame, p should be understood as (p+1)-1)
+\subsection{Defining frames and specifying frame restrictions}
+
+Frames are defined mutually with the types of frame restrictions,
+using auxiliary definitions for the types and definitions of layers:
 \begin{equation*}
@@
   \begin{array}{llcl}
-    \framep[n+1][0,...,p]                                                                    &
+    \framep[n+1][0,...,(p+1)-1]                                                                    &
     \left(\begin{array}{l}
@@
 By abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depstype[n][0,..,0-1]$.
+
+\subsection{Defining paintings}
 
@@
 
+\subsection{Specifying painting restrictions}
+
 At this stage, we are able to define $\framep[n+1][0,...,n]$, $\painting[n+1][0,...,n]$ and $\restrftype[n][0,...,n-1]$ from $\framep[n][0,...,n-1]$, $\painting[n][0,...,n-1]$ and $\restrf[n][0,...,n-1]$, that is from $\deps[n][0,...,n-1]$.
@@
 
+\subsection{Defining frame restrictions and specifying frame coherence laws}
+
 Thanks to $\restrptype[n][0,...,p-1]$, we can mutually define $\restrf[n+1][0,...,p]$ and $\cohftype[n][0,...,p-1]$ from ``full dependencies'', that is from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$ and some $E:\framep[n+1][n](\deps[n][0,...,n-1]) \rightarrow \U$, using abbreviations in passing for $\restrl$ and $\restrltype$:
@@
 Also, when $n$ is 0, we write $(E',E)$ to denote an element $(E', E)$ of $\fulldepscohstype[0]$.
+
+\subsection{Defining painting restrictions}
 
@@
 
-\section{...}
+\subsection{Specifying painting coherence laws}
 
@@
 
+\subsection{Defining frame coherence laws and specifying frame 2-dimensional coherence laws}
+
 This is enough to define $\cohf[n][p]$, using $\UIP$ to solve the dependency in $\coht[n][p]$.
@@
 \end{align*}
+
+\subsection{Defining painting coherence laws}
 
@@
 
+\subsection{Completing the construction by induction}
+
 Armed with all the constructions and assuming enough $E:\framep[n][n-1]

### 2025-11-11 paper/paper.tex
Reworking text + fixing layout and compilation

@@
 \begin{align*}
-  \framep[n-2][p] & : \U                                                                                    \\
-  \restrf[n-1][p] & : \Pi q \leq n+p.\, \framep[n-1][p] \rightarrow \framep[n-2][p]                         \\
-  \cohf[n][p]     & : \Pi qr\epsilon\omega.\, \restrf[n-1][p][\epsilon][q] \circ \restrf[n][p][\omega][r] = \\
-                  & \;\;\;\;\restrf[n-1][p][\omega][r] \circ \restrf[n][p][\epsilon][q+1]                   \\
-  \ldots          & \;\;\;\;\texttt{fields for painting, restrf, cohp}
-\end{align*}
-where $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ are now appropriate definitions.
-
-Turning $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ into definitions is however tricky: the definition of $\framep[n-1][p]$, which is by induction on $p$ (for all $n$), depends on $\restrf[n-1][p]$ whose type depends on $\framep[n][p-1]$.
-This means that $\framep[n-1][p]$ and the type of $\restrf[n-1][p]$ have to be mutually defined.
-
-The well-foundedness of the construction can be justified by the observation that:
-
-Defining $\framep[n][p]$ for $p \leq n$ requires the definition of $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$, where $\restrf[n][p-1]$ in turn depends in $\framep[n][p-1]$ for its typing.
-
-Moreover, $\framep[n][p]$ depends on $\framep[n][p-1]$, so these dependencies are between the blocks of $\framep[n][k]$ for all $k\leq p$, as well as $\framep[n-1][k]$, $\painting[n-1][k]$ and $\restrf[n][k]$ for all $k\leq p-1$, which we respectively abbreviate as $\framep[n][0,...,p]$, $\framep[n-1][0,...,p-1]$, $\painting[n-1][0,...,p-1]$ and $\restrf[n][0,...,p-1]$.
-
-Also, $\restrf[n][p-1]$ depends on $n$.
-
+  \framep[n][p] & : \U & \mbox{for all $p\leq n$}                                                                                      \\
+  \painting[n][p] & : \framep[n][p] \rightarrow \U & \mbox{for all $p\leq n$}                                                          \\
+  \restrf[n][p] & : \Pi q \leq n+p.\, \framep[n+1][p] \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                         \\
+  \restrp[n][p] & : \Pi q \leq n+p.\, \Pi d:\framep[n+1][p]\, \painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d)) & \mbox{for all $p\leq n$} \\
+  \cohf[n][p]   & : \Pi qr\epsilon\omega.\, \restrf[n][p][\epsilon][q] \circ \restrf[n+1][p][\omega][r] = \\
+                  & \;\;\;\;\restrf[n][p][\omega][r] \circ \restrf[n+1][p][\epsilon][q+1] & \mbox{for all $p\leq n$}                   \\
+  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\, \restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) = \\
+                  & \;\;\;\;\restrp[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon](d)) \circ \restrp[n+1][p][q+1][\epsilon](d) & \mbox{for all $p\leq n$}                 \\
+\end{align*}
+where $\framep[n+2][p]$, $\framep[n+1][p]$ and $\restrf[n+1][p]$, as
+well as $\painting[n+2][p]$, $\painting[n+1][p]$ and $\restrp[n+1][p]$
+are now appropriate definitions.
+
+Turning $\framep[n+2][p]$, $\framep[n+1][p]$ and $\restrf[n+1][p]$ into definitions involves however circularities.
+To start with, the definition of $\framep[n+1][p]$, which is by induction on $p$, depends on $\restrf[n][p-1]$ whose type depends in turn on $\framep[n+1][p-1]$.
+This means that $\framep[n+1][p]$ and the type of $\restrf[n][p]$ have to be mutually defined.
+
+The definition of $\framep[n+1][p]$ also depends, via $\layer[n][p-1]$, on $\painting[n][p-1]$.
+Both via $\painting[n][p-1]$ and $\restrf[n][p-1]$, it depends also on $\framep[n][p-1]$ by typing dependency.
+This requires to assume $\framep[n][p-1]$ and $\painting[n][p-1]$ known in advance.
+Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][0,...,p-1]$, $\painting[n][0,...,p-1]$ and $\restrf[n][p-1]$.
 Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n$ fixed:
@@
   \begin{tikzcd}
-    \framep[n][0,...,p] \arrow[d] \arrow[ddr]\\
-    \painting[n-1][0,...,p-1] \arrow[d, dotted] \\
-    \framep[n-1][0,...,p-1] &
+    \framep[n+1][0,...,p] \arrow[d] \arrow[ddr]\\
+    \painting[n][0,...,p-1] \arrow[d, dotted] \\
+    \framep[n][0,...,p-1] &
     \restrf[n][0,...,p-1] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[0,...,p-1]$}"', near start, shift right=2mm, hook']\\
@@
 
-In particular, the mutual dependency on one side of $\framep[n][0,...,p-1]$ within the type of $\restrf[n][0,...,p-1]$ and on the other side of $\restrf[n][0,...,p-1]$ within the definition of $\framep[n][0,...,p]$ requires to mutually define the type of $\restrf[n][0,...,p-1]$ together with $\framep[n][p]$ (or $\framep[n][0,...,p]$) as a function from $\restrf[n][0,...,p-1]$.
-
-To talk about sequences of $\framep$, $\painting$ or $\restrf$, we need to specify their types.
-The type of $\restrf$ will be defined mutually with $\framep$ of the same level, but the type of $\framep$, $\painting$ can be defined in advance, the second one being however dependent on the first one.
-In general, components of such sequences will have a type dependent on the previous components of the sequence, as it is the case for $\restrf$.
-So, the type of a sequence of length $p$ will be expressed as a $n$-iterated $\Sigma$-type.
+In particular, the mutual dependency on one side of $\framep[n][0,...,p-1]$ within the type of $\restrf[n][0,...,p-1]$ and on the other side of $\restrf[n][0,...,p-1]$ within the definition of $\framep[n][0,...,p]$ requires to mutually define the type of $\restrf[n][0,...,p-1]$ together with $\framep[n][p]$ (or $\framep[n][0,...,p]$) as a \emph{function} from $\restrf[n][0,...,p-1]$.
+
+So far, this means that we are able to specify a dependent structure of the form:
+\begin{align*}
+  \framep[n][p] & : \U & \mbox{for all $p\leq n$}                                                                                      \\
+  \painting[n][p] & : \framep[n][p] \rightarrow \U & \mbox{for all $p\leq n$}                                                          \\
+  \restrf[n][p] & : \Pi q \leq n+p.\, \framep[n+1][p]
+    \left(\begin{array}{l}
+      \framep[n][0,...,p-1]   \\
+      \painting[n][0,...,p-1] \\
+      \restrf[n][0,...,p-1]   \\
+    \end{array}\right)
+  \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                         \\
+\end{align*}
+which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][0,...,p]$, $\paintingtype[n][0,...,p]$ and $\restrftype[n][0,...,p]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][0,...,p-1]$ makes it a very dependent function~\cite{Hickey96}:
+\begin{align*}
+  \framep[n][0,...,p] & : \frametype[n][0,...,p]                                                                                       \\
+  \painting[n][0,...,p] & : \paintingtype[n][0,...,p](\framep[n][0,...,p])                                                         \\
+  \restrf[n][0,...,p] & : \restrftype[n][0,...,p]
+    \left(\begin{array}{l}
+      \framep[n][0,...,p-1]   \\
+      \painting[n][0,...,p-1] \\
+      \restrf[n][0,...,p-1]   \\
+    \end{array}\right)\\
+\end{align*}
+
+In general, the types of sequences such as $\restrf[n][0,...,p]$ will be nested since components, such as $\restrf[n][p]$, may depend on previous components of the sequence.
+So, the type of a sequence of length $p$ will be expressed as a $p$-iterated $\Sigma$-type.
 In the case of $\framep$ and $\painting$, there will be however no dependency, so an ordinary product can be used.
-If $\framep[n][0,...,p]$ is such a sequence of length $p+1$, we write $\framep[n][0,...,p-1]$ for its immediate subsequence of length $p$ and $\framep[n][p]$ for its last component.
+If $\framep[n][0,...,p]$ is such a sequence of length $p+1$, we write $\framep[n][0,...,p-1]$ for its immediate subsequence of length $p$ and $\framep[n][p]$ for its last component, and similarly for all such sequences.
 
@@
 
-\subsection{Specifying frames and paintings}
-
-We can now define the types of sequences of $\framep$ and $\painting$ as follows:
+\subsection{Specifying frames}
+
+Assuming $\framep[n][0,...,p]$ only requires to define the type of frames, which are just finite products of $\U$:
 
@@
     \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n+1][0,...,p-1] \times \U                                                         \\
-    \\
+  \end{array}
+\end{equation*}
+
+\subsection{Specifying paintings}
+
+The types $\paintingtype[n][0,...,p]$ of $\painting[n][0,...,p]$
+are type families over frames, so $\framep[n][0,...,p]$ needs to be assumed
+beforehand:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
     \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & \U                                                                                           \\
@@
 
-Frames are defined mutually with the types of frame restrictions,
-using auxiliary definitions for the types and definitions of layers:
+Assuming $\framep[n][0,...,p-1]$ and $\painting[n][0,...,p-1]$,
+we can mutually define the types $\restrftype[n][0,...,p-1]$ of frame
+restrictions together with $\framep[n+1][0,...p]$ as a function
+from $\restrf[n][0,...,p-1]$, using auxiliary definitions for the
+types and definitions of layers:
 \begin{equation*}
@@
             \end{array}\right)
-    & \defeq & \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+1][p]
+    & \defeq &
+    \left\{\begin{array}{l}
+    \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+1][p].\\
     \left(
@@
         \end{array}\right)(d))
-      \end{array}\right)                                                                                                            \\
+    \end{array}\right.\\
     \restrl[n][p]                                                                &

### 2025-11-11 paper/paper.tex
Adding E, E' in the νSetAux record

@@
 \begin{align*}
-  \framep[n][p] & : \U & \mbox{for all $p\leq n$}                                                                                      \\
-  \painting[n][p] & : \framep[n][p] \rightarrow \U & \mbox{for all $p\leq n$}                                                          \\
+  \framep[n][p] & : \U[m] & \mbox{for all $p\leq n$}                                                                                      \\
+  \painting[n][p] & : \framep[n][p] \rightarrow \U[m] & \mbox{for all $p\leq n$}                                                          \\
   \restrf[n][p] & : \Pi q \leq n+p.\, \framep[n+1][p] \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                         \\
-  \restrp[n][p] & : \Pi q \leq n+p.\, \Pi d:\framep[n+1][p]\, \painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d)) & \mbox{for all $p\leq n$} \\
+  E & : \fullframe[m][n+1] \imp \U[m] \\
+  \restrp[n][p] & : \Pi q \leq n+p.\, \Pi d:\framep[n+1][p].\,\\
+                  & \;\;\;\;\painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d)) & \mbox{for all $p\leq n$} \\
   \cohf[n][p]   & : \Pi qr\epsilon\omega.\, \restrf[n][p][\epsilon][q] \circ \restrf[n+1][p][\omega][r] = \\
                   & \;\;\;\;\restrf[n][p][\omega][r] \circ \restrf[n+1][p][\epsilon][q+1] & \mbox{for all $p\leq n$}                   \\
-  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\, \restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) = \\
+  E' & : \fullframe[m][n+2] \imp \U[m] \\
+  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,
+                  & \;\;\;\;\restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) = \\
                   & \;\;\;\;\restrp[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon](d)) \circ \restrp[n+1][p][q+1][\epsilon](d) & \mbox{for all $p\leq n$}                 \\
@@
 \end{align*}
-which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][0,...,p]$, $\paintingtype[n][0,...,p]$ and $\restrftype[n][0,...,p]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][0,...,p-1]$ makes it a very dependent function~\cite{Hickey96}:
+which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][0,...,p]$, $\paintingtype[n][0,...,p]$ and $\restrftype[n][0,...,p]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][0,...,p-1]$ makes it a very dependent function~\citep{Hickey96}:
 \begin{align*}

### 2025-11-11 paper/paper.tex
Experimenting abbreviating deps already in the mutual definition of frame and restrftype

@@
 
-Assuming $\framep[n][0,...,p-1]$ and $\painting[n][0,...,p-1]$,
-we can mutually define the types $\restrftype[n][0,...,p-1]$ of frame
-restrictions together with $\framep[n+1][0,...p]$ as a function
-from $\restrf[n][0,...,p-1]$, using auxiliary definitions for the
-types and definitions of layers:
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \framep[n+1][0,...,(p+1)-1]                                                                    &
-    \left(\begin{array}{l}
-              \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
-              \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
-              \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
+Assuming $\framep[n][0,...,p-1]$ and $\painting[n][0,...,p-1]$, we can
+mutually define the types $\restrftype[n][0,...,p-1]$ of frame
+restrictions together with $\framep[n+1][0,...p]$ as a function from
+$\restrf[n][0,...,p-1]$, introducing also abbreviations for the types
+and definitions of layers, as well as for the combination of sequences
+of $\framep[n][0,..,p-1]$, $\painting[n][0,...,p-1]$ and
+$\restrf[n][0,...,p-1]$ in one block, which we call
+$\depstype[n][0,...p-1]$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \depstype[n][0,..,p-1] & \defeq &
+    \left(\begin{array}{lll}
+              \framep[n][0,...,p-1]   & : & \frametype[n][0,...,p-1]    \\
+              \painting[n][0,...,p-1] & : & \paintingtype[n][0,...,p-1]
+              (\framep[n][0,...,p-1])                                   \\
+              \restrf[n][0,...,p-1]   & : & \restrftype[n][0,...,p-1]
               \left(\begin{array}{l}
@@
                 \end{array}\right)                             \\
-            \end{array}\right) & :      & \frametype[n+1][0,...,p]                             \\
+            \end{array}\right) \\
+    \framep[n+1][0,...,(p+1)-1]                                                                    &
+    (\deps[n][0,...,p-1]:\depstype[n][0,...,p-1]) & :      & \frametype[n+1][0,...,p]                             \\
     \framep[n+1][0,...,(0+1)-1]                                                                          &
-    \left(\begin{array}{l}
-              \unitpoint \\
-              \unitpoint \\
-              \unitpoint \\
-            \end{array}\right)                                                                 & \defeq & (\unitpoint,unit) \\
+    (\unitpoint)                                                                 & \defeq & (\unitpoint,unit) \\
     \framep[n+1][0,...,((p+1)+1)-1]                                                                  &
-    \left(\begin{array}{l}
-              \framep[n][0,...,p]   \\
-              \painting[n][0,...,p] \\
-              \restrf[n][0,...,p]   \\
-            \end{array}\right)                                                               & \defeq &
+    (\deps)                                                               & \defeq &
     \left(\begin{array}{l}
               \framep[n+1][0,...,p]
-              \left(\begin{array}{l}
-                  \framep[n][0,...,p-1]   \\
-                  \painting[n][0,...,p-1] \\
-                  \restrf[n][0,...,p-1]   \\
-                \end{array}\right), \\
+              (\deps[n][0,...,p-1]), \\
               \Sigma d:\framep[n+1][0,...,p]
-              \left(\begin{array}{l}
-                  \framep[n+1][0,...,p-1]   \\
-                  \painting[n+1][0,...,p-1] \\
-                  \restrf[n+1][0,...,p-1]   \\
-                \end{array}\right).\, \\
+              (\deps[n][0,...,p-1]) \\
               \quad \layer[n][p]
-              \left(\begin{array}{l}
-                  \framep[n][0,...,p]   \\
-                  \painting[n][0,...,p] \\
-                  \restrf[n][0,...,p]   \\
-                \end{array}\right)(d) \\
+              (\deps[n][0,...,p])
+              (d) \\
             \end{array}\right)                                                                      \\
@@
     \layertype[n][p]                                                                       &
-    \left(\begin{array}{l}
-              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
-              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
-              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\
-            \end{array}\right)
+    (\deps[n][0,...,p]:\depstype[n][0,...,p])
     & :      & \Type               \\
     \layertype[n][p]                                                                       &
-    \left(\begin{array}{l}
-              \framep[n][0,...,p]     \\
-              \painting[n][0,...,p]   \\
-              \restrf[n][0,...,p] \\
-            \end{array}\right)
+    (\deps[n][0,...,p])
     & \defeq & \framep[n+1][p]
-    \left(\begin{array}{l}
-              \framep[n][0,...,p-1]     \\
-              \painting[n][0,...,p-1]   \\
-              \restrf[n][0,...,p-1] \\
-            \end{array}\right) \rightarrow \U                                                                               \\
+    (\deps[n][0,...,p-1])
+    \rightarrow \U                                                                               \\
     \layer[n][p]                                                                           &
-    \left(\begin{array}{l}
-              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
-              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
-              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\
-            \end{array}\right)                                   & :      & \layertype[n][p]
-    \left(\begin{array}{l}
-              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
-              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
-              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\
-            \end{array}\right) \\
+    (\deps[n][0,...,p]:\depstype[n][0,...,p])
+    & :      & \layertype[n][p]
+    (\deps[n][0,...,p])
+    \\
     \layer[n][p]                                                                           &
-    \left(\begin{array}{l}
-              \framep[n][0,...,p]     \\
-              \painting[n][0,...,p]   \\
-              \restrf[n][0,...,p] \\
-            \end{array}\right)                                                             & \defeq &
-    d \mapsto \Pi\omega.\,\painting[n][p](\restrf[n][p](d))
-  \end{array}
-\end{equation*}
-
-At this stage, it is convenient to use an abbreviation to combine sequences $\framep[n][0,..,p-1]$, $\painting[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$ in one block, which we call $\depstype[n][0,...p-1]$:
-
-\begin{align*}
-  \depstype[n][0,..,p-1] \defeq
-  \left(\begin{array}{lll}
-            \framep[n][0,...,p-1]   & : & \frametype[n][0,...,p-1]    \\
-            \painting[n][0,...,p-1] & : & \paintingtype[n][0,...,p-1]
-            (\framep[n][0,...,p-1])                                   \\
-            \restrf[n][0,...,p-1]   & : & \restrftype[n][0,...,p-1]
-            \left(\begin{array}{l}
-                \framep[n][0,...,p-1]   \\
-                \painting[n][0,...,p-1] \\
-              \end{array}\right)                             \\
-          \end{array}\right)
-\end{align*}
-so that the type of $\framep[n+1][0,...,p]$ can be shortened into $\depstype[n][0,..,p-1] \rightarrow \frametype[n+1][0,...,p]$ and similarly for $\layertype[n][p]$ and $\layer[n][p]$.
-Later, we shall write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the corresponding projections of a $\deps$.
-By abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depstype[n][0,..,0-1]$.
+    (\deps[n][0,...,p])
+    & \defeq &
+    d \mapsto \Pi\omega.\,\painting[n][p](\restrf[n][p](d))\\
+  \end{array}
+\end{equation*}
+
+Later, we shall write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the projections of a $\deps$.
+Note that by abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depstype[n][0,..,0-1]$.
 

### 2025-11-11 paper/paper.tex
Postit
Experimenting abbreviating depscohs and overline{deps} already in the mutual definition of restrframe and cohftype + fixes

@@
 
+TODO: talk about unfoldPaintingProj.
+
 \subsection{Specifying painting restrictions}
@@
 
-Thanks to $\restrptype[n][0,...,p-1]$, we can mutually define $\restrf[n+1][0,...,p]$ and $\cohftype[n][0,...,p-1]$ from ``full dependencies'', that is from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$ and some $E:\framep[n+1][n](\deps[n][0,...,n-1]) \rightarrow \U$, using abbreviations in passing for $\restrl$ and $\restrltype$:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
+Thanks to $\restrptype[n][0,...,p-1]$, we can mutually define $\restrf[n+1][0,...,p]$ and $\cohftype[n][0,...,p-1]$ from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$, $\restrptype[n][0,...,p-1]$ and some $E:\framep[n+1][n](\deps[n][0,...,n-1]) \rightarrow \U$, abbreviating these dependencies and the dependency in a $\cohf[n][0,...,p-1]$ as $\depscohttype[n][0,...,p-1]$, and using also abbreviations in passing for $\restrl$ and $\restrltype$.
+It is also convenient to build $\deps[n+1][0,...,p]$ from $\depscohs[n][0,...,p-1]$, so that we can now build $\framep[n+2][p]$ one step further.
+Thus, we also include this abbreviation in the definition:
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \depscohstype[n][0,..,p-1] & \defeq &
+    \left(\begin{array}{lcl}
+              \fulldeps[n][0,...,n] & : & \fulldepstype[n][0,...,n] \\
+              \restrp[n][0,...p-1]  & : & \restrptype[n][0,...,p-1](\fulldeps[n]) \\
+              \cohf[n][0,...,p-1]   & : & \cohftype[n][0,...,p-1]
+                \left(\begin{array}{l}
+                    \fulldeps[n]          \\
+                    \restrp[n][0,...,p-1] \\
+                  \end{array}\right) \\
+            \end{array}\right) \\
+    \overline{\deps}(\depscohs[n][0,...,p-1]:\depscohstype[n][0,...,p-1]) & :      & \depstype[n+1][0,...,p] \\
+    \overline{\deps}(\depscohs)               & \defeq &
+    \left(\begin{array}{l}
+              \framep[n+1][0,...,p](\depscohs.\fulldeps.\deps[n][0,...,p-1])   \\
+              \painting[n+1][0,...,p](\depscohs.\fulldeps[n]) \\
+              \restrf[n+1][0,...,p](\depscohs[n][0,...,p-1])         \\
+            \end{array}\right)             \\
     \restrf[n+1][0,...,(p+1)-1]                                                          &
     \multicolumn{3}{l}{
-      \left(\begin{array}{l}
-                \fulldeps[n]:\fulldepstype[n]   \\
-                \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1]
-                (\fulldeps[n])    \\
-                \cohf[n][0,...,p-1]:\cohftype[n][0,...,p-1]
-                \left(\begin{array}{l}
-                    \fulldeps[n]          \\
-                    \restrp[n][0,...,p-1] \\
-                  \end{array}\right) \\
-              \end{array}\right) :
+      (\depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1]) :
       \restrftype[n+1][0,...,p]
       \left(\begin{array}{l}
-                \framep[n+1][0,...,p](\fulldeps.\deps[n][0,...,p])   \\
-                \painting[n+1][0,...,p](\fulldeps[n]) \\
+                \framep[n+1][0,...,p](\depscohs.\fulldeps.\deps[n][0,...,p])   \\
+                \painting[n+1][0,...,p](\depscohs.\fulldeps[n]) \\
               \end{array}\right)
@@
     \restrf[n+1][0,...,(0+1)-1]                                                        &
-    \left(\begin{array}{l}
-              E          \\
-              \unitpoint \\
-              \unitpoint \\
-            \end{array}\right)                                                       & \defeq & (\unitpoint,\lambda q. \lambda\epsilon. \lambda \_.\unitpoint) \\
+    (E)
+    & \defeq & (\unitpoint,\lambda q. \lambda\epsilon. \lambda \_.\unitpoint) \\
     \restrf[n+1][0,...,((p+1)+1)-1]                                                    &
-    \left(\begin{array}{l}
-              \fulldeps[n]        \\
-              \restrp[n][0,...,p] \\
-              \cohf[n][0,...,p]   \\
-            \end{array}\right)                                                       & \defeq &
+    (\depscohs[n][0,..,p])                                                       & \defeq &
       \left(\begin{array}{l}
               \restrf[n+1][0,...,p][q][\epsilon]
-              \left(\begin{array}{l}
-                  \fulldeps[n]          \\
-                  \restrp[n][0,...,p-1] \\
-                  \cohf[n][0,...,p-1]   \\
-                \end{array}\right),             \\
+              (\depscohs[n][0,..,p-1]),             \\
               \lambda q.\lambda \epsilon.\lambda (d,l). \\
               \left(\restrf[n][p][q][\epsilon]
-              \left(\begin{array}{l}
-                    \fulldeps[n]          \\
-                    \restrp[n][0,...,p-1] \\
-                    \cohf[n][0,...,p-1]   \\
-                  \end{array}\right)(d), \restrl[n][p][q][\epsilon]
-              \left(\begin{array}{l}
-                    \fulldeps[n]      \\
-                    \restrp[n][0,...,p] \\
-                    \cohf[n][0,...,p] \\
-                  \end{array}\right)(d)(l)\right)     \\
+              (\depscohs[n][0,..,p-1])(d), \restrl[n][p][q][\epsilon]
+              (\depscohs[n][0,..,p])(d)(l)\right)     \\
             \end{array} \right)                                                                                                                        \\
@@
             \end{array}\right) : \U
-    }                                                                                                                                                                                 \\
+    }                                                                                                                  n                                                               \\
     \cohftype[n][0,...,0-1]                                                      &
@@
       \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p]
-      \left(\begin{array}{l}
-                \framep[n+1][p](\fulldeps.\deps[n][0,...,p-1])          \\
-                \painting[n+1][0,...,p](\fulldeps[n]) \\
-                \restrf[n+1][0,...,p]
-                \left(\begin{array}{l}
+      (\overline{\deps}\left(\begin{array}{l}
                       \fulldeps[n]          \\
                       \restrp[n][0,...,p-1] \\
-                  \cohf[n][0,...,p-1] \\
-                \end{array}\right)                         \\
-              \end{array}\right).                         \\
+                      \cohf[n][0,...,p]
+                    \end{array}\right)          .                         \\
       \\
@@
                       \restrp[n][0,...,p-1] \\
-                \cohf[n][0,...,p-1] \\
+                      \cohf[n][0,...,p]
                     \end{array}\right)(d)) =                         \\
@@
                       \restrp[n][0,...,p-1] \\
-                \cohf[n][0,...,p-1] \\
+                      \cohf[n][0,...,p]
                     \end{array}\right)(d))                          \\
@@
     \restrltype[n][p]                                                            &
-    \left(\begin{array}{l}
-              \fulldeps[n]:\fulldepstype[n]                                        \\
-              \restrp[n][0,...,p]:\restrptype[n][0,...,p](\fulldeps[n]) \\
-              \cohf[n][0,...,p]:\cohftype[n][0,...,p]
-                \left(\begin{array}{l}
-                  \fulldeps[n]          \\
-                  \restrp[n][0,...,p] \\
-                \end{array}\right)                                   \\
-\\
-            \end{array}\right)      & :      & \U                                                                               \\
+      (\depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1])
+      & :      & \U                                                                               \\
     \restrltype[n][p]                                                            &
-    \left(\begin{array}{l}
-              \fulldeps[n]          \\
-              \restrp[n][0,...,p] \\
-              \cohf[n][0,...,p]     \\
-            \end{array}\right)
+      (\depscohs[n][0,..,p-1])
     & \defeq &
     \left\{\begin{array}{l}
-    \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+1][p].\\
-    \left(
-        \begin{array}{l}
-            \framep[n][p](\fulldeps.\deps[n][0,...,p]) \\
-            \painting[n][p](\fulldeps[n])              \\
-            \restrf[n][p]
-            \left(\begin{array}{l}
-                      \fulldeps[n]          \\
-                      \restrp[n][0,...,p-1] \\
-                      \cohf[n][0,...,p]
-                    \end{array}\right)                \\
-          \end{array}\right)(d) \rightarrow \\
+    \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+2][p](\overline{\deps}(\depscohs[n][0,..,p-1])).\, \\
+        \layer[n+1][p](\overline{\deps}(\depscohs[n][0,..,p-1])(d) \rightarrow \\
         \layer[n][p](\fulldeps.\deps[n][0,...,p])(\restrf[n][p]
-        \left(\begin{array}{l}
-                  \fulldeps[n] \\
-                  \restrp[n][0,...,p-1]       \\
-                  \cohf[n][0,...,p-1]
-        \end{array}\right)(d))
+        (\depscohs[n][0,..,p-1])(d))
     \end{array}\right.\\
     \restrl[n][p]                                                                &
-    \left(\begin{array}{l}
-              \fulldeps[n]:\fulldepstype[n]                                 \\
-              \restrp[n][0,...,p]:\restrptype[n][0,...,p](\fulldeps[n]) \\
-              \cohf[n][0,...,p]:\cohftype[n][0,...,p]
-              \left(\begin{array}{l}
-                  \fulldeps[n]          \\
-                  \restrp[n][0,...,p] \\
-                \end{array}\right)                                   \\
-            \end{array}\right) & :      &
-    \restrltype[n][p] \left(\begin{array}{l}
-                                \fulldeps[n] \\
-                                \restrp[n][0,...,p] \\
-                                \cohf[n][0,...,p] \\
-                              \end{array}
-    \right)                                                                                                                                                                           \\
+      (\depscohs[n][0,..,p]:\depscohstype[n][0,..,p]) & :      &
+    \restrltype[n][p] (\depscohs[n][0,..,p])                                                   \\
     \restrl[n][p]                                                                &
-    \left(\begin{array}{l}
-              \fulldeps[n]          \\
-              \restrp[n][0,...,p-1] \\
-              \cohf[n][0,...,p]     \\
-            \end{array}\right)                                                     & \defeq &
-    \lambda q\leq n. \lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon]\left(\begin{array}{l}
-                  \fulldeps[n] \\
-                  \restrp[n][0,...,p-1]       \\
-                  \cohf[n][0,...,p-1]
-                \end{array}\right)(d))(l \omega)}                          \\
-  \end{array}
-\end{equation*}
-
-At this new stage, it is convenient to use a new abbreviation to combine sequences of $\deps[n][0,..,n]$, $\restrp[n][0,...,p-1]$ and $\cohf[n][0,...,p-1]$ in one block, which we call $\depscohstype[n][0,...p-1]$:
-
-\begin{align*}
-  \depscohstype[n][0,..,p-1] \defeq
-  \left(\begin{array}{lcl}
-            \fulldeps[n][0,...,n] & : & \fulldepstype[n][0,...,n] \\
-            \restrp[n][0,...p-1]  & : & \restrptype[n][0,...,p-1] \\
-            \cohf[n][0,...,p-1]   & : & \cohftype[n][0,...,p-1]   \\
-          \end{array}\right)
-\end{align*}
-so that the type of $\restrf[n+1][0,...,p]$ can be rephrased as $\Pi \depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1]. \restrftype[n+1][0,...,p]
-      \left(\begin{array}{l}
-                \framep[n+1][0,...,p](\fulldeps.\deps[n][0,...,p])   \\
-                \painting[n+1][0,...,p](\fulldeps[n]) \\
-              \end{array}\right)$, and similarly for $\restrltype$ and $\restrl$.
-Later, we shall write $\depscohs.\deps$, $\depscohs.\restrp$, and $\depscohs.\cohf$ for the corresponding projections of an element $\depscohs$ in $\depscohstype$.
+    (\depscohs[n][0,..,p])                                                     & \defeq &
+    \lambda q\leq n.
+\lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][0,..,p-1])(d))(l \omega)}                          \\
+  \end{array}
+\end{equation*}
+
 By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n][0,..,0-1]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).
-
-It is also convenient to build $\deps$ from $\depscohs$ at the
-previous level:
-\begin{align*}
-  \overline{\deps}(\depscohs[n][0,...,p-1]:\depscohstype[n][0,...,p-1]) & :      & \depstype[n+1][0,...,p] \\
-  \overline{\deps}(\depscohs)               & \defeq &
-  \left(\begin{array}{l}
-            \framep[n+1][0,...,p](\depscohs.\fulldeps.\deps[n][0,...,p-1])   \\
-            \painting[n+1][0,...,p](\depscohs.\fulldeps[n]) \\
-            \restrf[n+1][0,...,p](\depscohs[n][0,...,p-1])         \\
-          \end{array}\right)             \\
-\end{align*}
 
@@
     \cohptype[n][0,...,0-1]        & \unitpoint                                        & \defeq & \unittype                               \\
-    \cohptype[n][0,...,(p+1)-1] & (\fulldepscohs[n])                           & \defeq & \cohptype[n][0,...,p-1](\fulldepscohs[n]) \times \left(
+    \cohptype[n][0,...,(p+1)-1] & (\fulldepscohs[n])                           & \defeq & \cohptype[n][0,...,p-1](\fulldepscohs[n]) \times \\
+    & & & \;\;\;\;\left\{
     \begin{array}{l}
@@
       \end{array}
-    \right)                                                                                                            \\
+    \right.                                                                                                           \\
   \end{array}
@@
                   \fulldepscohs[n+1]      \\
-                  \restrp[n+1][0,...,p-1] \\
+                  \cohp[n+1][0,...,p-1] \\
                 \end{array}\right).                                       \\
-              \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta  \\
+              \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.\,  \\
               \fulldepscohs.\depscohs.\cohf[n][p][r][p][\omega][\theta] \circ \cohf[n+1][p][q+1][p][\epsilon][\theta]

### 2025-11-16 paper/paper.tex
Layout
paper: NFC whitespace changes
paper: remove unused \ap macro
Corrections, especially on the final step

@@
 \renewcommand{\E}{E}
-\newcommand{\ap}{\mathsf{ap}\;}
 \renewcommand{\l}{l}
@@
 Since $\restrf[n][p]$ is referring to $\framep[n][p]$ and $\framep[n-1][p]$, and $\cohf[n][p]$ is referring to $\restrf[n][p]$ and $\restrf[n-1][p]$, thus also to $\framep[n][p]$, $\framep[n-1][p]$ and $\framep[n-2][p]$, we built all of these 6 components at the same time.
-But equations were also needed to state the properties of $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ so that we were building by induction on $n+p$ (that is on $n$, using the convention of \citep{hr25}) the following block of information:
+But equations were also needed to state the properties of $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ so that we were building by induction on $n+p$ (that is on $n$, using the convention of \cite{hr25}), for any $D:\Xto{m}{n}$, the following block of information:
 
@@
 
-In the current paper and associated formalisation, we replace the equational properties by definitions, building instead by induction a block of the form:
+In the current paper and associated formalisation, we switch the point
+of view, take $\framep[n-2][p]$ $\painting[n-2][p]$, $\restrf[n-1][p]$
+and $\restrp[n-1][p]$ as references and renaming them respectively as
+$\framep[n][p]$, $\painting[n][p]$, $\restrf[n][p]$ and
+$\restrp[n][p]$, replace the equational properties of $\framep[n][p]$,
+$\framep[n-1][p]$, $\restrf[n][p]$, $\painting[n][p]$,
+$\painting[n-1][p]$ and $\restrp[n][p]$ as definitions of objects
+respectively renamed to $\framep[n+2][p]$, $\framep[n+1][p]$,
+$\restrf[n+1][p]$, $\painting[n+2][p]$, $\painting[n+1][p]$ and
+$\restrp[n+1][p]$, building instead by induction a block of the form:
 
@@
   \painting[n][p] & : \framep[n][p] \rightarrow \U[m]                                                                           & \mbox{for all $p\leq n$} \\
-  \restrf[n][p] & : \Pi q \leq n+p.\, \framep[n+1][p] \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                         \\
-  E & : \fullframe[m][n+1] \imp \U[m] \\
-  \restrp[n][p] & : \Pi q \leq n+p.\, \Pi d:\framep[n+1][p].\,\\
+  \restrf[n][p]   & : \Pi q \leq n+p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]                                               & \mbox{for all $p\leq n$} \\
+  \restrp[n][p]   & : \Pi q \leq n+p.\, \Pi \epsilon.\, \Pi d:\framep[n+1][p].\,                                                                                           \\
                   & \;\;\;\;\painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d))                                  & \mbox{for all $p\leq n$} \\
@@
                   & \;\;\;\;\restrf[n][p][\omega][r] \circ \restrf[n+1][p][\epsilon][q+1]                                       & \mbox{for all $p\leq n$} \\
-  E' & : \fullframe[m][n+2] \imp \U[m] \\
-  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,
+  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,\\
                   & \;\;\;\;\restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) =                                \\
@@
 \end{align*}
-where $\framep[n+2][p]$, $\framep[n+1][p]$ and $\restrf[n+1][p]$, as
-well as $\painting[n+2][p]$, $\painting[n+1][p]$ and $\restrp[n+1][p]$
-are now appropriate definitions.
 
@@
 
-So far, this means that we are able to specify a dependent structure of the form:
+So far, using this recursive definition of  $\framep[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$, we are able to specify the three first component of the exected dependent structure:
 \begin{align*}
@@
             \restrf[n][0,...,p-1]   \\
-    \end{array}\right)\\
+          \end{array}\right)                                            \\
 \end{align*}
 
-In general, the types of sequences such as $\restrf[n][0,...,p]$ will be nested since components, such as $\restrf[n][p]$, may depend on previous components of the sequence.
-So, the type of a sequence of length $p$ will be expressed as a $p$-iterated $\Sigma$-type.
-In the case of $\framep$ and $\painting$, there will be however no dependency, so an ordinary product can be used.
-If $\framep[n][0,...,p]$ is such a sequence of length $p+1$, we write $\framep[n][0,...,p-1]$ for its immediate subsequence of length $p$ and $\framep[n][p]$ for its last component, and similarly for all such sequences.
+The type of sequences such as $\restrf[n][0,...,p]$ will be represented by iterated $\Sigma$-types since each $\restrf[n][p]$ may depend on the previous components of the sequence.
+In the case of $\framep$ and $\painting$, there will be however no dependency, so an ordinary product can be used to represent $\framep[n][0,...,p]$ and $\painting[n][0,...,p]$.
+Later on, we will write $\framep[n][0,...,p-1]$ for the immediate subsequence of length $p$ of $\framep[n][0,...,p]$ and $\framep[n][p]$ for its last component, and similarly for $\painting[n][0,...,p]$, $\restrf[n][0,...,p]$, etc.
 
@@
   \begin{array}{llcl}
-    \depstype[n][0,..,p-1] & \defeq &
+    \depstype[n][0,..,p-1]          &        & \defeq            &
     \left(\begin{array}{lll}
@@
     \framep[n+1][0,...,(p+1)-1]     &
-    (\deps[n][0,...,p-1]:\depstype[n][0,...,p-1]) & :      & \frametype[n+1][0,...,p]                             \\
+    \multicolumn{3}{l}{
+    (\deps[n][0,...,p-1]:\depstype[n][0,...,p-1]) :\frametype[n+1][0,...,p]}         \\
     \framep[n+1][0,...,(0+1)-1]     &
@@
     \framep[n+1][0,...,((p+1)+1)-1] &
-    (\deps)                                                               & \defeq &
+    \deps[n][0,...,p]               & \defeq &
     \left(\begin{array}{l}
@@
     \restrftype[n][0,...,p-1]       &
+    \multicolumn{3}{l}{
     \left(\begin{array}{l}
@@
               \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
-            \end{array}\right)          & :      & \U                                      \\
+            \end{array}\right) : \U} \\
     \restrftype[n][0,...,0-1]       &
@@
     \layertype[n][p]                &
+    \multicolumn{3}{l}{
       (\deps[n][0,...,p]:\depstype[n][0,...,p])
-    & :      & \Type               \\
+    : \U}                                                                            \\
     \layertype[n][p]                &
-    (\deps[n][0,...,p])
+    \deps[n][0,...,p]
                                     & \defeq & \framep[n+1][p]
@@
     \layer[n][p]                    &
+    \multicolumn{3}{l}{
       (\deps[n][0,...,p]:\depstype[n][0,...,p])
-    & :      & \layertype[n][p]
-    (\deps[n][0,...,p])
+      : \layertype[n][p]
+      (\deps[n][0,...,p])}
     \\
     \layer[n][p]                    &
-    (\deps[n][0,...,p])
+    \deps[n][0,...,p]
                                     & \defeq &
-    d \mapsto \Pi\omega.\,\painting[n][p](\restrf[n][p](d))\\
+    d \mapsto \Pi\omega.\,\painting[n][p](\restrf[n][p](d))                          \\
   \end{array}
@@
     \painting[n+1][n]      &
-    (\fulldeps[n])     & \defeq & \fulldeps.E             \\
+    \fulldeps[n]         & \defeq & \fulldeps.E             \\
     \painting[n+1][p](p<n) &
-    (\fulldeps[n])     & \defeq & d \mapsto
+    \fulldeps[n]         & \defeq & d \mapsto
     \left(\begin{array}{l}
@@
     \painting[n+1][0,...,p]   &
-    (\fulldeps[n-1])        & :      & \paintingtype[n+1][0,...,p](\framep[n+1][0,...,p](\fulldeps.\deps[n-1][0,...,p])) \\
+    (\fulldeps[n]:\fulldepstype[n])          & :      & \paintingtype[n+1][0,...,p](\framep[n+1][0,...,p](\fulldeps.\deps[n-1][0,...,p])) \\
     \painting[n+1][0,...,0-1] &
-    E                       & \defeq & \unittype                                                                     \\
+    \fulldeps[n]                         & \defeq & \unittype                                                                         \\
     \painting[n+1][0,...,p]   &
-    (\fulldeps[n-1])
+    \fulldeps[n]
                               & \defeq &
-    (\painting[n+1][0,...,p-1](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n-1]))                                        \\
+    (\painting[n+1][0,...,p-1](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n]))                                          \\
   \end{array}
@@
   \begin{array}{llcl}
-    \depscohstype[n][0,..,p-1] & \defeq &
+    \depscohstype[n][0,..,p-1]      &                         & \defeq                                                         &
     \left(\begin{array}{lcl}
@@
             \end{array}\right)                                                                                                                        \\
-    \overline{\deps}(\depscohs[n][0,...,p-1]:\depscohstype[n][0,...,p-1]) & :      & \depstype[n+1][0,...,p] \\
-    \overline{\deps}(\depscohs)               & \defeq &
+    \overline{\deps}                &
+    \multicolumn{3}{l}{
+    (\depscohs[n][0,...,p-1]:\depscohstype[n][0,...,p-1]) : \depstype[n+1][0,...,p]}                                                                                                                             \\
+    \overline{\deps}                & \depscohs[n][0,...,p-1] & \defeq                                                         &
     \left(\begin{array}{l}
@@
     \restrf[n+1][0,...,(0+1)-1]     &
-    (E)
-    & \defeq & (\unitpoint,\lambda q. \lambda\epsilon. \lambda \_.\unitpoint) \\
+    E
+                                    & \defeq                  & (\unitpoint,\lambda q.
+\lambda\epsilon.
+\lambda \_.\unitpoint)                                                                                   \\
     \restrf[n+1][0,...,((p+1)+1)-1] &
@@
     \restrltype[n][p]               &
+    \multicolumn{3}{l}{
       (\depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1])
-      & :      & \U                                                                               \\
+    : \U}                                                                                                                                                                                                        \\
     \restrltype[n][p]               &
-      (\depscohs[n][0,..,p-1])
+    \depscohs[n][0,..,p-1]
                                     & \defeq                  &
@@
              (\depscohs[n][0,..,p-1])(d))
-    \end{array}\right.\\
+           \end{array}\right.                                                                                                       \\
     \restrl[n][p]                   &
-      (\depscohs[n][0,..,p]:\depscohstype[n][0,..,p]) & :      &
-    \restrltype[n][p] (\depscohs[n][0,..,p])                                                   \\
+    \multicolumn{3}{l}{
+      (\depscohs[n][0,..,p]:\depscohstype[n][0,..,p]) :
+    \restrltype[n][p] (\depscohs[n][0,..,p])}                                                                                                                                                                    \\
     \restrl[n][p]                   &
-    (\depscohs[n][0,..,p])                                                     & \defeq &
+    \depscohs[n][0,..,p]            & \defeq                  &
     \lambda q\leq n.
@@
   \left(\begin{array}{l}
-            \overline{\deps}(\fulldepscohs.\depscohs[n][0,...,n-1])\\
-            \fulldepscohs.\depscohs.\fulldeps.E\\
+            \overline{\deps}(\fulldepscohs.\depscohs[n][0,...,n-1]) \\
+            \fulldepscohs.\depscohs.\fulldeps.E                     \\
           \end{array}\right)                             \\
@@
     \restrp[n+1][0,...,p]   &
-    (\fulldepscohs[n])        & :      & \restrptype[n+1][0,...,p](\fulldepscohs.\depscohs.\fulldeps[n])) \\
+    (\fulldepscohs[n]:\fulldepscohstype[n])      & :      & \restrptype[n+1][0,...,p](\fulldepscohs.\depscohs.\fulldeps[n])) \\
     \restrp[n+1][0,...,0-1] &
-    E  & \defeq & \unittype                                                                   \\
+    \fulldepscohs[n]                       & \defeq & \unittype                                                        \\
     \restrp[n+1][0,...,p]   &
-    (\fulldepscohs[n])
+    \fulldepscohs[n]
                             & \defeq &
@@
     \begin{array}{l}
-        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][0,...,p-1])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n]))\\
+      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][0,...,p-1])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
       \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf[n+1][p](d))(\restrp[n+1][p][r][\omega]
@@
     \cohf[n+1][0,...,p]                 &
+    \multicolumn{3}{l}{
     \left(\begin{array}{l}
@@
                   \end{array}\right)
-            \end{array}\right) & :      & \cohftype[n+1][0,...,p]                                                                                             \\
+              \end{array}\right) : \cohftype[n+1][0,...,p]}                                                                \\
     \cohf[n][0,...,(0+1)-1]             &
@@
     \cohttype[n][0,...,p-1]             &
+    \multicolumn{3}{l}{
     \left(\begin{array}{l}
@@
               \cohp[n][0,...,p-1]:\cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
-            \end{array}\right)            & :      & \U                                                                                                        \\
+            \end{array}\right)      : \U}                                                                \\
     \cohttype[n][0,...,0-1]             &
@@
     \cohl[n][p]                         &
+    \multicolumn{3}{l}{
       \left(\begin{array}{l}
@@
               \coht[n][0,...,p]:\cohttype[n][0,...,p] \\
-            \end{array}\right)                                  & :      &
+            \end{array}\right)                                 :
     \begin{array}{l}
@@
         \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))
-    \end{array}                                         \\
+      \end{array}} \\
     \cohl[n][p][q][\epsilon][r][\omega] &
@@
   \left(\begin{array}{lll}
-            \depscoht[n][0,...,n-1] &:&\depscohttype[n][0,...,n-1]    \\
-            E&:&\framep[n+3][n+2](\overline{\depscohs}(\depscoht[n][0,...,n-1]))\rightarrow \U \\
+            \depscoht[n][0,...,n-1] & : & \depscohttype[n][0,...,n-1]                                                    \\
+            E                       & : & \framep[n+3][n+2](\overline{\depscohs}(\depscoht[n][0,...,n-1]))\rightarrow \U \\
           \end{array}\right)
@@
             \overline{\depscohs}(\fulldepscoht.\depscoht)               \\
-            \overline{\depscohs}(\fulldepscoht.\depscoht[n][0,...,n-1])\\
-            \fulldepscoht.\depscoht.\fulldepscohs.E\\
+            \overline{\depscohs}(\fulldepscoht.\depscoht[n][0,...,n-1]) \\
+            \fulldepscoht.\depscoht.\fulldepscohs.E                     \\
           \end{array}\right)                      \\
@@
     \cohp[n+1][0,...,p]   &
-    (\fulldepscoht[n])        & :      & \cohptype[n+1][0,...,p](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
+    (\fulldepscoht[n]:\fulldepscohttype[n])    & :      & \cohptype[n+1][0,...,p](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
     \cohp[n+1][0,...,0-1] &
-    E  & \defeq & \unittype                                                                   \\
+    \fulldepscohs[n]      & \defeq & \unittype                                                          \\
     \cohp[n+1][0,...,p]   &
-    (\fulldepscoht[n])
+    \fulldepscoht[n]
                           & \defeq &
@@
 
-Armed with all the constructions and assuming enough $E:\framep[n][n-1]
-\rightarrow \U$ given, we can now define $\framep[n][p]$,
-$\painting[n][p]$, $\restrf[n][p]$, $\restrp[n][p]$, $\cohf[n][p]$,
-and $\cohp[n][p]$ for all $n$ and $p$. It is indeed enough to build
-$\fulldepscoht[n]$ by induction on $n$:
+Armed with all the constructions, we are now able to specify the whole
+structure on which we can reason by induction, for $D:\Xto{m}{n}$
+given:
+
+\begin{align*}
+  \framep[n][0,...,n-1]   & : \frametype[n][0,...,n-1]                         \\
+  \painting[n][0,...,n-1] & : \paintingtype[n][0,...,n-1](\framep[n][0,...,n-1]) \\
+  \restrf[n][0,...,n-1]   & : \restrftype[n][0,...,n-1]
+    \left(\begin{array}{l}
+              \framep[n][0,...,n-1]   \\
+              \painting[n][0,...,n-1] \\
+    \end{array}\right)                                            \\
+  \restrp[n][0,...,n-1](E:\framep[n+1][n]
+    \left(\begin{array}{l}
+              \framep[n][0,...,n-1]   \\
+              \painting[n][0,...,n-1] \\
+              \restrf[n][0,...,n-1]   \\
+    \end{array}\right)\rightarrow \U) & : \restrptype[n][0,...,n-1]
+    \left(\begin{array}{l}
+              \framep[n][0,...,n-1]   \\
+              \painting[n][0,...,n-1] \\
+              \restrf[n][0,...,n-1]   \\
+              E\\
+    \end{array}\right)                                            \\
+  \cohf[n][0,...,n-1](E:\framep[n+1][n]
+    \left(\begin{array}{l}
+              \framep[n][0,...,n-1]   \\
+              \painting[n][0,...,n-1] \\
+              \restrf[n][0,...,n-1]   \\
+    \end{array}\right)\rightarrow \U) & : \cohftype[n][0,...,n-1]
+    \left(\begin{array}{l}
+              \framep[n][0,...,n-1]   \\
+              \painting[n][0,...,n-1] \\
+              \restrf[n][0,...,n-1]   \\
+              E\\
+              \restrp[n][0,...,n-1]   \\
+    \end{array}\right)                                            \\
+    \cohp[n][0,...,n-1]
+      \left(\begin{array}{l}
+              E:\framep[n+1][n]
+                \left(\begin{array}{l}
+              \framep[n][0,...,n-1]   \\
+              \painting[n][0,...,n-1] \\
+              \restrf[n][0,...,n-1]   \\
+        \end{array}\right)\rightarrow \U \\
+              E':\framep[n+2][n+1](\overline{\deps}
+              \left(\begin{array}{l}
+              \framep[n][0,...,n-1]   \\
+              \painting[n][0,...,n-1] \\
+              \restrf[n][0,...,n-1]   \\
+              E\\
+              \restrp[n][0,...,n-1]   \\
+              \cohf[n][0,...,n-1]   \\
+        \end{array}\right))\rightarrow \U
+      \end{array}\right)                                            \\
+      & : \cohptype[n][0,...,n-1]
+      \left(\begin{array}{l}
+              \framep[n][0,...,n-1]   \\
+              \painting[n][0,...,n-1] \\
+              \restrf[n][0,...,n-1]   \\
+              E\\
+              \restrp[n][0,...,n-1]   \\
+              \cohf[n][0,...,n-1]   \\
+              E'\\
+      \end{array}\right)                                            \\
+\end{align*}
+
+Indeed, to build this structure at level $n+1$, from level $n$, it is
+enough to assume $E:\framep[n+1][n](\deps[n]) \rightarrow \U$ (where
+$\deps[n]$ come from the assumptions at level $n$) and to build the
+following:
 \begin{itemize}
-\item $\fulldepscohs[n+1]$ is $\overline{\fulldepscohs}(\fulldepscoht[n])$
-\item $\cohp[n+1][0,...,n]$ is given from $\fulldepscoht$ as above
-\item $\coht[n+1][0,...,n]$ is given by uniqueness of identity proofs
+  \item $\framep[n+1][0,...,n]$ comes from $\deps[n]$ which holds by assumptions (using $\framep[n][0,...,n-1]$, $\painting[n][0,...,n-1]$ and $\restrf[n][0,...,n-1]$)
+  \item $\painting[n+1][0,...,n]$ comes from $\fulldeps[n]$ which holds by assumptions (also using $E$)
+  \item $\restrf[n+1][0,...,n]$ comes from $\depscohs[n][0,...,n-1]$ which holds by assumptions (additionally using the assumptions of $\restrp[n][0,...,n-1]$ and $\cohf[n][0,...,n-1]$)
+  \item $\restrp[n+1][0,...,n]$ assuming $E':\framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$ comes from $\fulldepscohs[n][0,...,n-1]$ which holds by assumptions (additionally using $E'$)
+  \item $\cohf[n+1][0,...,n]$ assuming $E'$ comes from $\depscoht[n][0,...,n-1]$ which holds by assumptions (additionally using the assumption of $\cohp[n][0,...,n-1]$ and proving $\coht[n][0,...,n-1]$ by uniqueness of identity proofs)
+  \item $\cohp[n+1][0,...,n]$ assuming $E'$ and $E'': \framep[n+3][n+2](\overline{\deps}(\overline{\depscohs}(\depscoht[n][0,...,n-1]))) \rightarrow \U$ comes from $\fulldepscoht[n][0,...,n-1]$ which holds by assumptions (additionally using $E''$)
 \end{itemize}
+
+Therefore, assuming a construction of $\framep[n][n-1]$ from
+$D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n]$ from $D$
+extended with some $E:\framep[n+1][n](\deps[n]) \rightarrow \U$. This
+is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus
+$\Xp{m}$, by starting with an empty $D$.
 

### 2025-11-16 paper/paper.tex
paper: use uppercase for types
paper: use a nice begin cases

@@
 
-\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, lmodern, mathpazo, anyfontsize, xargs, environ, multirow, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
+\usepackage{amsmath, amssymb, mathrsfs, mathtools, wasysym, tikz, tikz-cd, lmodern, mathpazo, anyfontsize, xargs, environ, multirow, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
 \usepackage[utf8]{inputenc}
@@
   \setkeys*[bonak]{restr#1}{#8}
+}
+
+\newcommandx{\depsp}[8][2,3,4,5,6,7,8]{
+  \ensuremath{\mathsf{\color{russian-green}{deps}}_{
+    \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4]}^{\joinargs[#5][#6][#7]}}
+}
+
+\newcommandx{\depstypep}[8][2,3,4,5,6,7,8]{
+  \ensuremath{\mathsf{\color{russian-green}{DEPS}}_{
+    \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4]}^{\joinargs[#5][#6][#7]}}
 }
@@
 
-\newcommandx{\frametype}[2][1,2]{\prim{frametype}[][#1][#2][][]}
-\newcommandx{\layertype}[2][1,2]{\prim{layertype}[][#1][#2][][]}
-\newcommandx{\paintingtype}[2][1,2]{\prim{paintingtype}[][#1][#2][][]}
-\newcommandx{\restrftype}[2][1,2]{\prim{restrftype}[][#1][#2][][]}
-\newcommandx{\restrltype}[2][1,2]{\prim{restrltype}[][#1][#2][][]}
-\newcommandx{\restrptype}[2][1,2]{\prim{restrptype}[][#1][#2][][]}
-\newcommandx{\cohftype}[2][1,2]{\prim{cohftype}[][#1][#2][][]}
-\newcommandx{\cohltype}[2][1,2]{\prim{cohltype}[][#1][#2][][]}
-\newcommandx{\cohptype}[2][1,2]{\prim{cohptype}[][#1][#2][][]}
-\newcommandx{\cohttype}[2][1,2]{\prim{cohttype}[][#1][#2][][]}
-
-\newcommandx{\deps}[2][1,2]{\prim{deps}[][#1][#2][][]}
-\newcommandx{\fulldeps}[2][1,2]{\prim{fulldeps}[][#1][][][]}
-\newcommandx{\depscohs}[2][1,2]{\prim{depscohs}[][#1][#2][][]}
-\newcommandx{\fulldepscohs}[2][1,2]{\prim{fulldepscohs}[][#1][][][]}
-\newcommandx{\depscoht}[2][1,2]{\prim{depscoht}[][#1][#2][][]}
-\newcommandx{\fulldepscoht}[2][1,2]{\prim{fulldepscoht}[][#1][][][]}
-\newcommandx{\depstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
-\newcommandx{\fulldepstype}[2][1,2]{\prim{fulldepstype}[][#1][][][]}
-\newcommandx{\depscohstype}[2][1,2]{\prim{depscohstype}[][#1][#2][][]}
-\newcommandx{\fulldepscohstype}[2][1,2]{\prim{fulldepscohstype}[][#1][][][]}
-\newcommandx{\depscohttype}[2][1,2]{\prim{depscohttype}[][#1][#2][][]}
-\newcommandx{\fulldepscohttype}[2][1,2]{\prim{fulldepscohttype}[][#1][][][]}
+\newcommandx{\frametype}[2][1,2]{\prim{FRAME}[][#1][#2][][]}
+\newcommandx{\layertype}[2][1,2]{\prim{LAYER}[][#1][#2][][]}
+\newcommandx{\paintingtype}[2][1,2]{\prim{PAINTING}[][#1][#2][][]}
+\newcommandx{\restrftype}[2][1,2]{\restr{FRAME}[][][][#1][#2][][]}
+\newcommandx{\restrltype}[2][1,2]{\restr{LAYER}[][][][#1][#2][][]}
+\newcommandx{\restrptype}[2][1,2]{\restr{PAINTING}[][][][#1][#2][][]}
+\newcommandx{\cohftype}[2][1,2]{\coh{FRAME}[][][][][][#1,#2][][]}
+\newcommandx{\cohltype}[2][1,2]{\coh{LAYER}[][][][][][#1,#2][][]}
+\newcommandx{\cohptype}[2][1,2]{\coh{PAINTING}[][][][][][#1,#2][][]}
+\newcommandx{\cohttype}[2][1,2]{\cohtwo{FRAME}[][][][][][#1,#2][][]}
+
+\newcommandx{\deps}[2][1,2]{\depsp{}[][][][#1][#2][][]}
+\newcommandx{\fulldeps}[1][1]{\depsp{full}[][][][#1][][][]}
+\newcommandx{\depscohs}[2][1,2]{\depsp{cohs}[][][][#1][#2][][]}
+\newcommandx{\fulldepscohs}[1][1]{\depsp{fullcohs}[][#1][][][]}
+\newcommandx{\depscoht}[2][1,2]{\depsp{coht}[][][][#1][#2][][]}
+\newcommandx{\fulldepscoht}[1][1]{\depsp{fullcoht}[][][][#1][][][]}
+\newcommandx{\depstype}[2][1,2]{\depstypep{}[][][][#1][#2][][]}
+\newcommandx{\fulldepstype}[2][1,2]{\depstypep{full}[][][][#1][][][]}
+\newcommandx{\depscohstype}[2][1,2]{\depstypep{cohs}[][][][#1][#2][][]}
+\newcommandx{\fulldepscohstype}[1][1]{\depstypep{fullcohs}[][][][#1][][][]}
+\newcommandx{\depscohttype}[2][1,2]{\depstypep{coht}[][][][#1][#2][][]}
+\newcommandx{\fulldepscohttype}[1][1]{\depstypep{fullcoht}[][][][#1][][][]}
 
@@
                   & \;\;\;\;\restrf[n][p][\omega][r] \circ \restrf[n+1][p][\epsilon][q+1]                                       & \mbox{for all $p\leq n$} \\
-  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,\\
+  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,                                                                                        \\
                   & \;\;\;\;\restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) =                                \\
@@
 \begin{align*}
+  \depscohs[n][p]\begin{cases}
+                   \deps[n][p]\begin{cases}
                  \framep[n][0,...,n-1]   & : \frametype[n][0,...,n-1]                           \\
@@
                 \painting[n][0,...,n-1] \\
-    \end{array}\right)                                            \\
+              \end{array}\right)
+               \end{cases} \\
                    \restrp[n][0,...,n-1](E:\framep[n+1][n]
@@
               \restrf[n][0,...,n-1]   \\
-              E\\
+              E                       \\
             \end{array}\right)                                                             \\
@@
               \restrf[n][0,...,n-1]   \\
-              E\\
+              E                       \\
               \restrp[n][0,...,n-1]   \\
-    \end{array}\right)                                            \\
+            \end{array}\right)
+                 \end{cases} \\
   \cohp[n][0,...,n-1]
@@
                 \restrf[n][0,...,n-1]   \\
-              E\\
+                E                       \\
                 \restrp[n][0,...,n-1]   \\
@@
               \end{array}\right))\rightarrow \U
-      \end{array}\right)                                            \\
-      & : \cohptype[n][0,...,n-1]
+          \end{array}\right)
+  : \cohptype[n][0,...,n-1]
   \left(\begin{array}{l}
@@
             \restrf[n][0,...,n-1]   \\
-              E\\
+            E                       \\
             \restrp[n][0,...,n-1]   \\
             \cohf[n][0,...,n-1]     \\
-              E'\\
+            E'                      \\
           \end{array}\right)                                                                           \\

### 2025-11-16 paper/paper.tex
paper: improve last equation
paper: abbreviate with depscoht

@@
 \newcommandx{\depscohs}[2][1,2]{\depsp{cohs}[][][][#1][#2][][]}
-\newcommandx{\fulldepscohs}[1][1]{\depsp{fullcohs}[][#1][][][]}
+\newcommandx{\fulldepscohs}[1][1]{\depsp{fullcohs}[][][][#1][][][]}
 \newcommandx{\depscoht}[2][1,2]{\depsp{coht}[][][][#1][#2][][]}
@@
 
-This is enough to define $\cohf[n][p]$, using $\UIP$ to solve the dependency in $\coht[n][p]$.
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
+Thanks to $\cohptype[n][0,...,p-1]$, we can mutually define $\cohf[n+1][0,...,p]$ and $\cohttype[n][0,...,p-1]$ from $\fulldepscohs[n][0,...,p-1]$, abbreviating this and the dependency in a $\coht[n][0,...,p-1]$ as $\depscohttype[n][0,...,p-1]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$.
+It is also convenient to build $\depscohs[n+1][0,...,p]$ from $\depscoht[n][0,...,p-1]$, so that we can now build $\framep[n+3][p]$.
+Thus, we also include this abbreviation in the definition:
+
+\begin{align*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \depscohttype[n][0,..,p-1]                                       &                                                   & \defeq                                                                            &
+    \left(\begin{array}{lll}
+              \fulldepscohs[n]    & : & \fulldepscohstype[n]                      \\
+              \cohp[n][0,...p-1]  & : & \cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
+              \coht[n][0,...,p-1] & : & \cohttype[n][0,...,p-1]
+              \left(\begin{array}{l}
+                  \fulldepscohs[n]    \\
+                  \cohp[n][0,...,p-1] \\
+                \end{array}\right)                                           \\
+            \end{array}\right)                                                                                                                                                \\
+    \overline{\depscohs}                                             & (\depscoht[n][0,...,p]:\depscohttype[n][0,...,p]) & :                                                                                 & \depscohstype[n+1][0,...,p] \\
+    \overline{\depscohs}                                             & \depscoht[n][0,...,p]                             & \defeq                                                                            &
+    \left(\begin{array}{l}
+              \overline{\deps}(\depscoht.\fulldepscohs.\depscohs[n][0,...,p-1]) \\
+              \restrp[n+1][p](\depscoht.\fulldepscohs[n][0,...,n])              \\
+              \cohf[n+1][p](\depscoht[n][0,...,p-1])                            \\
+            \end{array}\right)                                                                                                                                                                \\
     \cohf[n+1][0,...,p]                                              &
-    \multicolumn{3}{l}{
+    (\fulldepscoht[n]:\fulldepscohttype[n])                          & :                                                 & \cohftype[n+1][0,...,p]                                                                                         \\
+    \cohf[n][0,...,(0+1)-1]                                          &
+    (\unitpoint)                                                     & \defeq                                            & (\unitpoint,\lambda q.\lambda r.
+\lambda\epsilon.
+\lambda\omega.\lambda \_.\refl)                               \\
+    \cohf[n][0,...,((p+1)+1)-1]                                      &
+    (\fulldepscoht[n])                                               & \defeq                                            &
+    \left(\begin{array}{l}
+              \cohf[n+1][0,...,p]
+              (\fulldepscoht[n]),                                                \\
+              \lambda q.\lambda r.\lambda \epsilon.\lambda \omega.\lambda (d,l). \\
+              (\cohf[n][0,...,p][q][r][\epsilon][\omega]
+              (\fulldepscoht[n])(d), \cohl[n][p][q][r][\epsilon][\omega]
+              (
+              \fulldepscoht[n])(d)(l))                                           \\
+            \end{array}\right)                                                                                                                                                               \\
+    \cohttype[n][0,...,p-1]                                          &
     \left(\begin{array}{l}
@@
               \cohp[n][0,...,p-1]:\cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
-                \coht[n][0,...,p-1]:\cohttype[n][0,...,p-1]
-                \left(\begin{array}{l}
-                    \fulldepscohs[n]    \\
-                    \cohp[n][0,...,p-1] \\
-                  \end{array}\right)
-              \end{array}\right) : \cohftype[n+1][0,...,p]}                                                                \\
-    \cohf[n][0,...,(0+1)-1]             &
-    \left(\begin{array}{l}
-              \unitpoint \\
-              \unitpoint \\
-              \unitpoint \\
-            \end{array}\right)              & \defeq & (\unitpoint,\lambda q.\lambda r. \lambda\epsilon. \lambda\omega.\lambda \_.\refl) \\
-    \cohf[n][0,...,((p+1)+1)-1]         &
-    \left(\begin{array}{l}
-              \fulldepscohs[n]  \\
-              \cohp[n][0,...,p] \\
-              \coht[n][0,...,p] \\
-            \end{array}\right)              & \defeq &
-    \left(\begin{array}{l}
-              \cohf[n+1][0,...,p]
-              \left(\begin{array}{l}
-                  \fulldepscohs[n]      \\
-                  \cohp[n+1][0,...,p-1] \\
-                  \coht[n+1][0,...,p-1] \\
-                \end{array}\right),                                        \\
-              \lambda q.\lambda r.\lambda \epsilon.\lambda \omega.\lambda (d,l). \\
-              (\cohf[n][0,...,p][q][r][\epsilon][\omega]
-              \left(\begin{array}{l}
-                  \fulldepscohs[n]      \\
-                  \cohp[n+1][0,...,p-1] \\
-                  \coht[n+1][0,...,p-1] \\
-                \end{array}\right)(d), \cohl[n][p][q][r][\epsilon][\omega]
-              \left(\begin{array}{l}
-                  \fulldepscohs[n]  \\
-                  \cohp[n][0,...,p] \\
-                  \coht[n][0,...,p] \\
-                \end{array}\right)(d)(l))                                    \\
-            \end{array}\right)                                            \\
-    \cohttype[n][0,...,p-1]             &
-    \multicolumn{3}{l}{
-    \left(\begin{array}{l}
-              \fulldepscohs[n]:\fulldepscohstype[n]                         \\
-              \cohp[n][0,...,p-1]:\cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
-            \end{array}\right)      : \U}                                                                \\
+            \end{array}\right) & :                                                 & \U                                                                                                                                                      \\
     \cohttype[n][0,...,0-1]                                          &
@@
               \fulldepscohs.\depscohs.\cohf[n][p][r][p][\omega][\theta] \circ \cohf[n+1][p][q+1][p][\epsilon][\theta]
-              \left(\begin{array}{l}
-                  \fulldepscohs[n]    \\
-                  \cohp[n][0,...,p-1] \\
-                  \coht[n][0,...,p-1]
-                \end{array}\right)
+              (\fulldepscoht[n])
               \circ \fulldepscohs.\depscohs.\cohf[n][p][q][r][\epsilon][\omega] =   \\
               \cohf[n+1][p][q+1][r+1][\epsilon][\omega]
-              \left(\begin{array}{l}
-                  \fulldepscohs[n+1]  \\
-                  \cohp[n][0,...,p-1] \\
-                  \coht[n][0,...,p-1]
-                \end{array}\right)
+              (\fulldepscoht[n+1])
               \circ \fulldepscohs.\depscohs.\cohf[n][p][q][p][\epsilon][\theta]
               \circ \cohf[n+1][p][r][p][\omega][\theta]
-              \left(\begin{array}{l}
-                  \fulldepscohs[n]    \\
-                  \cohp[n][0,...,p-1] \\
-                  \coht[n][0,...,p-1]
-                \end{array}\right)                                             \\
+              (\fulldepscoht[n])                                                    \\
             \end{array}\right)                                                                                                                           \\
     \cohl[n][p]                                                      &
-    \multicolumn{3}{l}{
-      \left(\begin{array}{l}
-              \fulldepscohs[n]:\fulldepscohstype[n]   \\
-              \cohp[n][0,...,p]:\cohptype[n][0,...,p] \\
-              \coht[n][0,...,p]:\cohttype[n][0,...,p] \\
-            \end{array}\right)                                 :
+    (\fulldepscoht[n]:\fulldepscohttype[n])                          & :                                                 &
     \begin{array}{l}
@@
       \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))
-      \end{array}} \\
+    \end{array}                                                                                                     \\
     \cohl[n][p][q][\epsilon][r][\omega]                              &
-    \left(\begin{array}{l}
-              \fulldepscohs[n]  \\
-              \cohp[n][0,...,p] \\
-              \cohf[n][0,...,p] \\
-            \end{array}\right)              & \defeq &
-    \lambda d. \lambda l. \lambda \theta. (\cohp[n][p][q][\epsilon][r][\omega](l))  ...                                                \\
-  \end{array}
-\end{equation*}
-
-This is time for a new abbreviation:
-
-\begin{align*}
-  \depscohttype[n][0,..,p-1] \defeq
-  \left(\begin{array}{lll}
-            \fulldepscohs[n]    & : & \fulldepscohstype[n]                      \\
-            \cohp[n][0,...p-1]  & : & \cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
-            \coht[n][0,...,p-1] & : & \cohttype[n][0,...,p-1]
-            \left(\begin{array}{l}
-                \fulldepscohs[n]    \\
-                \cohp[n][0,...,p-1] \\
-              \end{array}\right)                                           \\
-          \end{array}\right)
-\end{align*}
-
-It is also convenient to build $\depscohs[n+1][0,...,p]$ from $\depscoht[n][0,...,p]$ at the previous level:
-
-\begin{align*}
-  \overline{\depscohs}(\depscoht[n][0,...,p]:\depscohttype[n][0,...,p]) & :      & \depscohstype[n+1][0,...,p] \\
-  \overline{\depscohs}(\depscoht[n][0,...,p])                           & \defeq &
-  \left(\begin{array}{l}
-            \overline{\deps}(\depscoht.\fulldepscohs.\depscohs[n][0,...,p-1]) \\
-            \restrp[n+1][p](\depscoht.\fulldepscohs[n][0,...,n])              \\
-            \cohf[n+1][p](\depscoht[n][0,...,p-1])                            \\
-          \end{array}\right)                                      \\
+    (\fulldepscoht[n])                                               & \defeq                                            &
+    \lambda d.
+\lambda l.
+\lambda \theta.
+(\cohp[n][p][q][\epsilon][r][\omega](l))  ...
+\\
+  \end{array}
 \end{align*}
@@
 \begin{align*}
-  \depscohs[n][p]\begin{cases}
-                   \deps[n][p]\begin{cases}
-                 \framep[n][0,...,n-1]   & : \frametype[n][0,...,n-1]                           \\
-                 \painting[n][0,...,n-1] & : \paintingtype[n][0,...,n-1](\framep[n][0,...,n-1]) \\
-                 \restrf[n][0,...,n-1]   & : \restrftype[n][0,...,n-1]
+  \rotatebox[origin=c]{90}{\depscohs[n][0,...,n-1]}\begin{cases}
+                                                     \rotatebox[origin=c]{90}{\deps[n][0,...,n-1]}\begin{cases}
+                                                   \framep[n][0,...,n-1]   : \frametype[n][0,...,n-1]                           \\
+                                                   \painting[n][0,...,n-1] : \paintingtype[n][0,...,n-1](\framep[n][0,...,n-1]) \\
+                                                   \restrf[n][0,...,n-1]   : \restrftype[n][0,...,n-1]
                                                    \left(\begin{array}{l}
@@
                                                  \end{cases} \\
-                   \restrp[n][0,...,n-1](E:\framep[n+1][n]
-                   \left(\begin{array}{l}
-              \framep[n][0,...,n-1]   \\
-              \painting[n][0,...,n-1] \\
-              \restrf[n][0,...,n-1]   \\
-            \end{array}\right)\rightarrow \U) & : \restrptype[n][0,...,n-1]
-                   \left(\begin{array}{l}
-              \framep[n][0,...,n-1]   \\
-              \painting[n][0,...,n-1] \\
-              \restrf[n][0,...,n-1]   \\
+                                                     E:\framep[n+1][n]
+                                                     (\deps[n][0,...,n-1])\rightarrow \U                                                                                       \\
+                                                     \restrp[n][0,...,n-1](E) : \restrptype[n][0,...,n-1]
+                                                     \left(\begin{array}{l}
+              \deps[n][0,...,n-1] \\
               E                   \\
             \end{array}\right)                                                                                                 \\
-                   \cohf[n][0,...,n-1](E:\framep[n+1][n]
-                   \left(\begin{array}{l}
-              \framep[n][0,...,n-1]   \\
-              \painting[n][0,...,n-1] \\
-              \restrf[n][0,...,n-1]   \\
-            \end{array}\right)\rightarrow \U) & : \cohftype[n][0,...,n-1]
-                   \left(\begin{array}{l}
-              \framep[n][0,...,n-1]   \\
-              \painting[n][0,...,n-1] \\
-              \restrf[n][0,...,n-1]   \\
-              E                       \\
+                                                     \cohf[n][0,...,n-1](E)   : \cohftype[n][0,...,n-1]
+                                                     \left(\begin{array}{l}
+              \deps[n][0,...,n-1]                 \\
+              E:\framep[n+1][n]
+              (\deps[n][0,...,n-1])\rightarrow \U \\
               \restrp[n][0,...,n-1]               \\
@@
                                                    \end{cases} \\
+  E': \framep[n+2][n+1](\overline{\deps}
+  (\depscohs[n][0,...,n-1])\rightarrow \U                                                                                                                                                  \\
   \cohp[n][0,...,n-1]
   \left(\begin{array}{l}
-            E:\framep[n+1][n]
-            \left(\begin{array}{l}
-                \framep[n][0,...,n-1]   \\
-                \painting[n][0,...,n-1] \\
-                \restrf[n][0,...,n-1]   \\
-              \end{array}\right)\rightarrow \U \\
-            E':\framep[n+2][n+1](\overline{\deps}
-            \left(\begin{array}{l}
-                \framep[n][0,...,n-1]   \\
-                \painting[n][0,...,n-1] \\
-                \restrf[n][0,...,n-1]   \\
             E  \\
-                \restrp[n][0,...,n-1]   \\
-                \cohf[n][0,...,n-1]     \\
-              \end{array}\right))\rightarrow \U
+            E' \\
           \end{array}\right)
@@
   \left(\begin{array}{l}
-            \framep[n][0,...,n-1]   \\
-            \painting[n][0,...,n-1] \\
-            \restrf[n][0,...,n-1]   \\
-            E                       \\
-            \restrp[n][0,...,n-1]   \\
-            \cohf[n][0,...,n-1]     \\
+            \depscohs[n][0,...,n-1] \\
             E'                      \\

### 2025-11-16 paper/paper.tex
paper: minor corrections
Use again n instead of n-p in tables

@@
   \begin{array}{lll}
-    X_0 & :               \U                                                                          \\
-    X_1 & :               X_0 \times X_0 \rightarrow  \U                                              \\
-    X_2 & : \Pi a b c d.\,  X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
+    E_0 & :               \U                                                                          \\
+    E_1 & :               E_0 \times X_0 \rightarrow  \U                                              \\
+    E_2 & : \Pi a b c d.\,  E_1(a,b) \times E_1 (c,d) \times E_1(a,c) \times E_1 (b,d) \rightarrow \U \\
     \ldots
@@
 of view, take $\framep[n-2][p]$ $\painting[n-2][p]$, $\restrf[n-1][p]$
-and $\restrp[n-1][p]$ as references and renaming them respectively as
+and $\restrp[n-1][p]$ as references and rename them respectively as
 $\framep[n][p]$, $\painting[n][p]$, $\restrf[n][p]$ and
-$\restrp[n][p]$, replace the equational properties of $\framep[n][p]$,
+$\restrp[n][p]$. We replace the equational properties of $\framep[n][p]$,
 $\framep[n-1][p]$, $\restrf[n][p]$, $\painting[n][p]$,
-$\painting[n-1][p]$ and $\restrp[n][p]$ as definitions of objects
-respectively renamed to $\framep[n+2][p]$, $\framep[n+1][p]$,
+$\painting[n-1][p]$ and $\restrp[n][p]$ with definitions, renaming them
+respectively to $\framep[n+2][p]$, $\framep[n+1][p]$,
 $\restrf[n+1][p]$, $\painting[n+2][p]$, $\painting[n+1][p]$ and
-$\restrp[n+1][p]$, building instead by induction a block of the form:
+$\restrp[n+1][p]$. This means that we build instead by induction a block of the form:
 
@@
               \overline{\deps}(\depscoht.\fulldepscohs.\depscohs[n][0,...,p-1]) \\
-              \restrp[n+1][p](\depscoht.\fulldepscohs[n][0,...,n])              \\
+              \restrp[n+1][p](\depscoht.\fulldepscohs[n])                       \\
               \cohf[n+1][p](\depscoht[n][0,...,p-1])                            \\
@@
     \cohf[n][0,...,(0+1)-1]                                          &
-    (\unitpoint)                                                     & \defeq                                            & (\unitpoint,\lambda q.\lambda r.
+    \unitpoint                                                       & \defeq                                            & (\unitpoint,\lambda q.\lambda r.
 \lambda\epsilon.
@@
               (\fulldepscoht[n])(d), \cohl[n][p][q][r][\epsilon][\omega]
-              (
-              \fulldepscoht[n])(d)(l))                                           \\
+              (\fulldepscoht[n])(d)(l))                                          \\
             \end{array}\right)                                                                                                                                                               \\
@@
   \item $\restrf[n+1][0,...,n]$ comes from $\depscohs[n][0,...,n-1]$ which holds by assumptions (additionally using the assumptions of $\restrp[n][0,...,n-1]$ and $\cohf[n][0,...,n-1]$)
-  \item $\restrp[n+1][0,...,n]$ assuming $E':\framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$ comes from $\fulldepscohs[n][0,...,n-1]$ which holds by assumptions (additionally using $E'$)
+  \item $\restrp[n+1][0,...,n]$ assuming $E':\framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$ comes from $\fulldepscohs[n]$ which holds by assumptions (additionally using $E'$)
   \item $\cohf[n+1][0,...,n]$ assuming $E'$ comes from $\depscoht[n][0,...,n-1]$ which holds by assumptions (additionally using the assumption of $\cohp[n][0,...,n-1]$ and proving $\coht[n][0,...,n-1]$ by uniqueness of identity proofs)

### 2025-12-04 paper/paper.tex
paper: drop some univ subscripts
Many fixes in paper

--- 2025-11-16 paper/paper.tex
@@
 \begin{document}
-\title{On the specific recursive structure of iterated parametricity}
+\title{The very dependent recursive structure of iterated parametricity in indexed form}
 \begin{authgrp}
@@
 \begin{align*}
-  \framep[n][p]   & : \U[m]                                                                                                     & \mbox{for all $p\leq n$} \\
-  \painting[n][p] & : \framep[n][p] \rightarrow \U[m]                                                                           & \mbox{for all $p\leq n$} \\
+  \framep[n][p]   & : \U                                                                                                        & \mbox{for all $p\leq n$} \\
+  \painting[n][p] & : \framep[n][p] \rightarrow \U                                                                              & \mbox{for all $p\leq n$} \\
   \restrf[n][p]   & : \Pi q \leq n+p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]                               & \mbox{for all $p\leq n$} \\
@@
 Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][0,...,p-1]$, $\painting[n][0,...,p-1]$ and $\restrf[n][p-1]$.
-Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n$ fixed:
+Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n+1$ fixed:
 \begin{center}
@@
 
-Assuming $\framep[n][0,...,p]$ only requires to define the type of frames, which are just finite products of $\U$:
+Assuming $\framep[n][0,...,p]$ for $p \leq n$ only requires to define the type of frames, which are just finite products of $\U$:
 
@@
 
-The types $\paintingtype[n][0,...,p]$ of $\painting[n][0,...,p]$
+The types $\paintingtype[n][0,...,p]$ of $\painting[n][0,...,p]$ for $p \leq n$
 are type families over frames, so $\framep[n][0,...,p]$ needs to be assumed
@@
 
-Assuming $\framep[n][0,...,p-1]$ and $\painting[n][0,...,p-1]$, we can
+Assuming $\framep[n][0,...,p-1]$ and $\painting[n][0,...,p-1]$ for $p \leq n+1$, we can
 mutually define the types $\restrftype[n][0,...,p-1]$ of frame
@@
             \end{array}\right)        \\
-    \framep[n+1][0,...,(p+1)-1]     &
+    \framep[n+1][0,...,p]     &
     \multicolumn{3}{l}{
     (\deps[n][0,...,p-1]:\depstype[n][0,...,p-1]) :\frametype[n+1][0,...,p]}         \\
-    \framep[n+1][0,...,(0+1)-1]     &
-    (\unitpoint)                    & \defeq & (\unitpoint,unit)                     \\
-    \framep[n+1][0,...,((p+1)+1)-1] &
+    \framep[n+1][0,...,0]     &
+    \unitpoint                    & \defeq & (\unitpoint,unit)                     \\
+    \framep[n+1][0,...,p+1] &
     \deps[n][0,...,p]               & \defeq &
@@
               (\deps[n][0,...,p-1]), \\
-              \Sigma d:\framep[n+1][0,...,p]
-              (\deps[n][0,...,p-1])  \\
-              \quad \layer[n][p]
+              \Sigma d:\framep[n+1][p]
+              (\deps[n][0,...,p-1]).
+              \, \layer[n][p]
               (\deps[n][0,...,p])
@@
                                     & \defeq &
-    d \mapsto \Pi\omega.\,\painting[n][p](\restrf[n][p](d))                          \\
-  \end{array}
-\end{equation*}
-
-Later, we shall write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the projections of a $\deps$.
-Note that by abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depstype[n][0,..,0-1]$.
+    d \mapsto \Pi\omega.\,\painting[n][p](\deps.\restrf[n][p][0][\omega](d))                          \\
+  \end{array}
+\end{equation*}
+
+Note that we write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the
+projections of a $\deps$. Also, by abuse of notation, we write $\unitpoint$ for
+the only inhabitant of $\depstype[n][0,..,0-1]$.
 
@@
 
-Defining $\painting[n+1][p]$, in addition to the type dependency in $\framep[n+1][p]$, requires the definition of $\painting[n][p-1]$, thus also $\framep[n][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$.
+Defining $\painting[n+1][p]$ for $p \leq n+1$, in addition to the type dependency in $\framep[n+1][p]$, requires the definition of $\painting[n][p-1]$, thus also $\framep[n][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$.
 Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][p,...,n+1]$, $\painting[n][p,...,n]$, $\framep[n+1][p,...,n+1]$, $\framep[n][p,...,n]$ and $\restrf[n][p,...,n]$.
@@
 
-Let us introduce another abbreviation to combine a full $\deps[n][0,...,n-1]:\depstype[n][0,...,n-1]$ with a family $E:\framep[n+1][n](\deps[n][0,...,n-1])\rightarrow \U$:
+Let us introduce another abbreviation to combine a full $\deps[n][0,...,n]:\depstype[n][0,...,n]$ with a family $E:\framep[n+1][n+1](\deps[n][0,...,n])\rightarrow \U$:
 \begin{align*}
@@
   \left(\begin{array}{lll}
-            \deps[n][0,...,n-1] & : & \depstype[n][0,...,n-1]                             \\
-            E                   & : & \framep[n+1][n](\deps[n][0,...,n-1]) \rightarrow \U \\
+            \deps[n][0,...,n] & : & \depstype[n][0,...,n]                             \\
+            E                   & : & \framep[n+1][n+1](\deps[n][0,...,n]) \rightarrow \U \\
           \end{array}\right)
@@
     (\fulldeps[n]:\fulldepstype[n])                           \\
-    \painting[n+1][n]      &
+    \painting[n+1][n+1]      &
     \fulldeps[n]           & \defeq & \fulldeps.E             \\
-    \painting[n+1][p](p<n) &
+    \painting[n+1][p](p\leq n) &
     \fulldeps[n]           & \defeq & d \mapsto
@@
 
-From which we can deduce $\painting[n+1][0,...,p]$ by a second recursion, this time on $p$:
+From which we can deduce $\painting[n+1][0,...,p]$ for $p \leq n+1$ by a second recursion, this time on $p$:
 
@@
 
-At this stage, we are able to define $\framep[n+1][0,...,n]$, $\painting[n+1][0,...,n]$ and $\restrftype[n][0,...,n-1]$ from $\framep[n][0,...,n-1]$, $\painting[n][0,...,n-1]$ and $\restrf[n][0,...,n-1]$, that is from $\deps[n][0,...,n-1]$.
-To go further, we need to define the sequence $\restrptype[n][0,...,p]$ of types of painting restrictions:
+At this stage, we are able to define $\framep[n+1][0,...,n+1]$, $\painting[n+1][0,...,n+1]$ and $\restrftype[n][0,...,n]$ from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$ and $\restrf[n][0,...,n]$, that is from $\deps[n][0,...,n]$.
+To go further, we need to define the sequence $\restrptype[n][0,...,p-1]$ of types of painting restrictions, for $p \leq n+1$:
 
@@
 
-Thanks to $\restrptype[n][0,...,p-1]$, we can mutually define $\restrf[n+1][0,...,p]$ and $\cohftype[n][0,...,p-1]$ from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$, $\restrptype[n][0,...,p-1]$ and some $E:\framep[n+1][n](\deps[n][0,...,n-1]) \rightarrow \U$, abbreviating these dependencies and the dependency in a $\cohf[n][0,...,p-1]$ as $\depscohttype[n][0,...,p-1]$, and using also abbreviations in passing for $\restrl$ and $\restrltype$.
+Thanks to $\restrptype[n][0,...,p-1]$ for $p \leq n+1$, we can mutually define $\restrf[n+1][0,...,p]$ and $\cohftype[n][0,...,p-1]$ from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$, $\restrptype[n][0,...,p-1]$ and some $E:\framep[n+1][n+1](\deps[n][0,...,n]) \rightarrow \U$, abbreviating these dependencies and the dependency in a $\cohf[n][0,...,p-1]$ as $\depscohstype[n][0,...,p-1]$, and using also abbreviations in passing for $\restrl$ and $\restrltype$.
 It is also convenient to build $\deps[n+1][0,...,p]$ from $\depscohs[n][0,...,p-1]$, so that we can now build $\framep[n+2][p]$ one step further.
@@
             \end{array}\right)                                                                                                                                         \\
-    \restrf[n+1][0,...,(p+1)-1]     &
+    \restrf[n+1][0,...,p]     &
     \multicolumn{3}{l}{
@@
     }                                                                                                                                                                                                            \\
-    \restrf[n+1][0,...,(0+1)-1]     &
+    \restrf[n+1][0,...,0]     &
     E
@@
 \lambda \_.\unitpoint)                                                                                   \\
-    \restrf[n+1][0,...,((p+1)+1)-1] &
+    \restrf[n+1][0,...,p+1] &
     (\depscohs[n][0,..,p])          & \defeq                  &
@@
 
-We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][0,...,n]$ with a set $E:\framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$:
+We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][0,...,n]$ with a set $E:\framep[n+2][n+2](\overline{\deps}(\depscohs[n][0,...,n])) \rightarrow \U$:
 \begin{align*}
@@
   \left(\begin{array}{lcl}
-            \depscohs[n][0,...,n-1] & : & \depscohstype[n][0,...,n-1]                                                \\
-            E                       & : & \framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
+            \depscohs[n][0,...,n-1] & : & \depscohstype[n][0,...,n]                                                \\
+            E                       & : & \framep[n+2][n+2](\overline{\deps}(\depscohs[n][0,...,n]))\rightarrow \U \\
           \end{array}\right)
@@
   \left(\begin{array}{l}
-            \overline{\deps}(\fulldepscohs.\depscohs[n][0,...,n-1]) \\
-            \fulldepscohs.\depscohs.\fulldeps.E                     \\
+            \overline{\deps}(\fulldepscohs.\depscohs[n][0,...,n]) \\
+            \fulldepscohs.E                     \\
           \end{array}\right)                             \\
@@
 
-Also, when $n$ is 0, we write $(E',E)$ to denote an element $(E', E)$ of $\fulldepscohstype[0]$.
+Also, when $n$ is 0, we write $(E,E')$ to denote an element $(E, E')$ of $\fulldepscohstype[0]$.
 
@@
 
-Armed with $\restrf$, $\cohftype$ and these abbreviations, it is now possible to define $\restrp[n][p]$ by recursion on $n-p$:
+Armed with $\restrf$, $\cohftype$ and these abbreviations, it is now possible to define $\restrp[n+1][p]$ for $p \leq n+1$ by recursion on $n-p$:
 
@@
         (\restrf[n+1][p](\fulldepscohs.\depscohs[n][0,...,p-1])(d))\end{array}\right)                                                        \\
-    \restrp[n+1][n]                         &
+    \restrp[n+1][n+1]                         &
     (\fulldepscohs[n])                      & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
-    \restrp[n+1][p](p<n)                    &
+    \restrp[n+1][p](p\leq n)                    &
     (\fulldepscohs[n])                      & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
@@
 
-From which we can deduce $\restrp[n][0,...,p]$ again by a second recursion, this time on $p$:
+From which we can deduce $\restrp[n+1][0,...,p]$ for $p \leq n+1$ again by a second recursion, this time on $p$:
 
@@
 
-At this stage, we are then able to define $\restrf[n+1][0,...,p]$, $\restrp[n+1][0,...,p]$ and $\cohftype[n][0,...,p]$
+At this stage, we are then able to define $\restrf[n+1][0,...,p]$, $\restrp[n+1][0,...,p]$ and $\cohftype[n][0,...,p-1]$ for $p \leq n+1$
 from $\depscohs[n][0,...,p-1]$ at the previous level. To go further, we need to define the
@@
 
-Thanks to $\cohptype[n][0,...,p-1]$, we can mutually define $\cohf[n+1][0,...,p]$ and $\cohttype[n][0,...,p-1]$ from $\fulldepscohs[n][0,...,p-1]$, abbreviating this and the dependency in a $\coht[n][0,...,p-1]$ as $\depscohttype[n][0,...,p-1]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$.
+Thanks to $\cohptype[n][0,...,p-1]$, we can mutually define $\cohf[n+1][0,...,p]$ and $\cohttype[n][0,...,p-1]$ for $p \leq n+1$ from $\fulldepscohs[n][0,...,p-1]$, abbreviating this and the dependency in a $\coht[n][0,...,p-1]$ as $\depscohttype[n][0,...,p-1]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$.
 It is also convenient to build $\depscohs[n+1][0,...,p]$ from $\depscoht[n][0,...,p-1]$, so that we can now build $\framep[n+3][p]$.
@@
             \end{array}\right)                                                                                                                                                \\
-    \overline{\depscohs}                                             & (\depscoht[n][0,...,p]:\depscohttype[n][0,...,p]) & :                                                                                 & \depscohstype[n+1][0,...,p] \\
-    \overline{\depscohs}                                             & \depscoht[n][0,...,p]                             & \defeq                                                                            &
+    \overline{\depscohs}                                             & (\depscoht[n][0,...,p-1]:\depscohttype[n][0,...,p-1]) & :                                                                                 & \depscohstype[n+1][0,...,p] \\
+    \overline{\depscohs}                                             & \depscoht[n][0,...,p-1]                             & \defeq                                                                            &
     \left(\begin{array}{l}
@@
     \cohf[n+1][0,...,p]                                              &
-    (\fulldepscoht[n]:\fulldepscohttype[n])                          & :                                                 & \cohftype[n+1][0,...,p]                                                                                         \\
-    \cohf[n][0,...,(0+1)-1]                                          &
+    (\depscoht[n][0,...,p-1]:\depscohttype[n][0,...,p-1])                          & :                                                 & \cohftype[n+1][0,...,p]
+           \left(\begin{array}{l}
+              \overline{\fulldeps}(\depscoht.\fulldepscohs[n])                         \\
+              \restrp[n+1][0,...,p](\depscoht.\fulldepscohs[n]) \\
+            \end{array}\right) \\
+                                                                                         \\
+    \cohf[n][0,...,0]                                          &
     \unitpoint                                                       & \defeq                                            & (\unitpoint,\lambda q.\lambda r.
@@
 \lambda\omega.\lambda \_.\refl)                               \\
-    \cohf[n][0,...,((p+1)+1)-1]                                      &
-    (\fulldepscoht[n])                                               & \defeq                                            &
+    \cohf[n][0,...,p+1]                                      &
+    (\depscoht[n][0,...,p-1])                                               & \defeq                                            &
     \left(\begin{array}{l}
               \cohf[n+1][0,...,p]
-              (\fulldepscoht[n]),                                                \\
+              (\depscoht[n]),                                                \\
               \lambda q.\lambda r.\lambda \epsilon.\lambda \omega.\lambda (d,l). \\
               (\cohf[n][0,...,p][q][r][\epsilon][\omega]
-              (\fulldepscoht[n])(d), \cohl[n][p][q][r][\epsilon][\omega]
-              (\fulldepscoht[n])(d)(l))                                          \\
+              (\depscoht[n])(d), \cohl[n][p][q][r][\epsilon][\omega]
+              (\depscoht[n])(d)(l))                                          \\
             \end{array}\right)                                                                                                                                                               \\
@@
     \left(\begin{array}{l}
-              (E',E)     \\
+              (E,E')     \\
               \unitpoint \\
@@
     \cohl[n][p]                                                      &
-    (\fulldepscoht[n]:\fulldepscohttype[n])                          & :                                                 &
+    (\depscoht[n][0,...,p-1]:\depscohttype[n][0,...,p-1])                          & :                                                 &
     \begin{array}{l}
@@
     \cohl[n][p][q][\epsilon][r][\omega]                              &
-    (\fulldepscoht[n])                                               & \defeq                                            &
+    (\depscoht[n][0,...,p-1])                                               & \defeq                                            &
     \lambda d.
@@
 
-We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][0,...,n]$ with a set $E:\framep[n+3][n+2](\overline{\depscohs}(\depscoht[n][0,...,n-1])) \rightarrow \U$:
+We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][0,...,n]$ with a set $E:\framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][0,...,n]))) \rightarrow \U$:
 \begin{align*}
@@
   \left(\begin{array}{lll}
-            \depscoht[n][0,...,n-1] & : & \depscohttype[n][0,...,n-1]                                                    \\
-            E                       & : & \framep[n+3][n+2](\overline{\depscohs}(\depscoht[n][0,...,n-1]))\rightarrow \U \\
+            \depscoht[n][0,...,n] & : & \depscohttype[n][0,...,n]                                                    \\
+            E                       & : & \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][0,...,n])))\rightarrow \U \\
           \end{array}\right)
@@
 \begin{align*}
-  \overline{\fulldepscohs}(\fulldepscoht:\fulldepscohstype) & :      & \fulldepscohstype \\
-  \overline{\fulldepscohs}(\fulldepscoht)                   & \defeq &
-  \left(\begin{array}{l}
-            \overline{\depscohs}(\fulldepscoht.\depscoht)               \\
-            \overline{\depscohs}(\fulldepscoht.\depscoht[n][0,...,n-1]) \\
-            \fulldepscoht.\depscoht.\fulldepscohs.E                     \\
+  \overline{\fulldepscohs}(\fulldepscoht[n]:\fulldepscohstype[n]) & :      & \fulldepscohstype[n+1] \\
+  \overline{\fulldepscohs}(\fulldepscoht[n])                   & \defeq &
+  \left(\begin{array}{l}
+            \overline{\depscohs}(\fulldepscoht.\depscoht[n][0,...,n]) \\
+            \fulldepscoht.E                     \\
           \end{array}\right)                      \\

### 2025-12-07 paper/paper.tex
Make `unfoldPaintingProj` and `unfoldRestrPaintings` equalities definitional (#6)
paper: attempt interval-based notation

--- 2025-12-04 paper/paper.tex
@@
 This requires to assume $\framep[n][p-1]$ and $\painting[n][p-1]$ known in advance.
-Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][0,...,p-1]$, $\painting[n][0,...,p-1]$ and $\restrf[n][p-1]$.
+Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][p-1]$.
 Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n+1$ fixed:
@@
   \begin{tikzcd}
-    \framep[n+1][0,...,p] \arrow[d] \arrow[ddr]\\
-    \painting[n][0,...,p-1] \arrow[d, dotted] \\
-    \framep[n][0,...,p-1] &
-    \restrf[n][0,...,p-1] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[0,...,p-1]$}"', near start, shift right=2mm, hook']\\
+    \framep[n+1][\lbrack 0,p \rbrack] \arrow[d] \arrow[ddr]\\
+    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] \\
+    \framep[n][\lbrack 0,p-1 \rbrack] &
+    \restrf[n][\lbrack 0,p-1 \rbrack] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[\lbrack 0,p-1 \rbrack]$}"', near start, shift right=2mm, hook']\\
   \end{tikzcd}
@@
 
-In particular, the mutual dependency on one side of $\framep[n][0,...,p-1]$ within the type of $\restrf[n][0,...,p-1]$ and on the other side of $\restrf[n][0,...,p-1]$ within the definition of $\framep[n][0,...,p]$ requires to mutually define the type of $\restrf[n][0,...,p-1]$ together with $\framep[n][p]$ (or $\framep[n][0,...,p]$) as a \emph{function} from $\restrf[n][0,...,p-1]$.
-
-So far, using this recursive definition of  $\framep[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$, we are able to specify the three first component of the exected dependent structure:
+In particular, the mutual dependency on one side of $\framep[n][\lbrack 0,p-1 \rbrack]$ within the type of $\restrf[n][\lbrack 0,p-1 \rbrack]$ and on the other side of $\restrf[n][\lbrack 0,p-1 \rbrack]$ within the definition of $\framep[n][\lbrack 0,p \rbrack]$ requires to mutually define the type of $\restrf[n][\lbrack 0,p-1 \rbrack]$ together with $\framep[n][p]$ (or $\framep[n][\lbrack 0,p \rbrack]$) as a \emph{function} from $\restrf[n][\lbrack 0,p-1 \rbrack]$.
+
+So far, using this recursive definition of  $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$, we are able to specify the three first component of the exected dependent structure:
 \begin{align*}
@@
   \left(\begin{array}{l}
-            \framep[n][0,...,p-1]   \\
-            \painting[n][0,...,p-1] \\
-            \restrf[n][0,...,p-1]   \\
+            \framep[n][\lbrack 0,p-1 \rbrack]   \\
+            \painting[n][\lbrack 0,p-1 \rbrack] \\
+            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
           \end{array}\right)
@@
 \end{align*}
-which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][0,...,p]$, $\paintingtype[n][0,...,p]$ and $\restrftype[n][0,...,p]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][0,...,p-1]$ makes it a very dependent function~\citep{Hickey96}:
+which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][\lbrack 0,p \rbrack]$, $\paintingtype[n][\lbrack 0,p \rbrack]$ and $\restrftype[n][\lbrack 0,p \rbrack]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][\lbrack 0,p-1 \rbrack]$ makes it a very dependent function~\citep{Hickey96}:
 \begin{align*}
-  \framep[n][0,...,p]   & : \frametype[n][0,...,p]                         \\
-  \painting[n][0,...,p] & : \paintingtype[n][0,...,p](\framep[n][0,...,p]) \\
-  \restrf[n][0,...,p]   & : \restrftype[n][0,...,p]
-  \left(\begin{array}{l}
-            \framep[n][0,...,p-1]   \\
-            \painting[n][0,...,p-1] \\
-            \restrf[n][0,...,p-1]   \\
+  \framep[n][\lbrack 0,p \rbrack]   & : \frametype[n][\lbrack 0,p \rbrack]                                     \\
+  \painting[n][\lbrack 0,p \rbrack] & : \paintingtype[n][\lbrack 0,p \rbrack](\framep[n][\lbrack 0,p \rbrack]) \\
+  \restrf[n][\lbrack 0,p \rbrack]   & : \restrftype[n][\lbrack 0,p \rbrack]
+  \left(\begin{array}{l}
+            \framep[n][\lbrack 0,p-1 \rbrack]   \\
+            \painting[n][\lbrack 0,p-1 \rbrack] \\
+            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
           \end{array}\right)                                                                    \\
@@
 
-The type of sequences such as $\restrf[n][0,...,p]$ will be represented by iterated $\Sigma$-types since each $\restrf[n][p]$ may depend on the previous components of the sequence.
-In the case of $\framep$ and $\painting$, there will be however no dependency, so an ordinary product can be used to represent $\framep[n][0,...,p]$ and $\painting[n][0,...,p]$.
-Later on, we will write $\framep[n][0,...,p-1]$ for the immediate subsequence of length $p$ of $\framep[n][0,...,p]$ and $\framep[n][p]$ for its last component, and similarly for $\painting[n][0,...,p]$, $\restrf[n][0,...,p]$, etc.
+The type of sequences such as $\restrf[n][\lbrack 0,p \rbrack]$ will be represented by iterated $\Sigma$-types since each $\restrf[n][p]$ may depend on the previous components of the sequence.
+In the case of $\framep$ and $\painting$, there will be however no dependency, so an ordinary product can be used to represent $\framep[n][\lbrack 0,p \rbrack]$ and $\painting[n][\lbrack 0,p \rbrack]$.
+Later on, we will write $\framep[n][\lbrack 0,p-1 \rbrack]$ for the immediate subsequence of length $p$ of $\framep[n][\lbrack 0,p \rbrack]$ and $\framep[n][p]$ for its last component, and similarly for $\painting[n][\lbrack 0,p \rbrack]$, $\restrf[n][\lbrack 0,p \rbrack]$, etc.
 
@@
 
-Assuming $\framep[n][0,...,p]$ for $p \leq n$ only requires to define the type of frames, which are just finite products of $\U$:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \frametype[n][0,...,p] &  & :      & \U                                   \\
+Assuming $\framep[n][\lbrack 0,p \rbrack]$ for $p \leq n$ only requires to define the type of frames, which are just finite products of $\U$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \frametype[n][\lbrack 0,p \rbrack] &  & :      & \U                                               \\
     \frametype[n][]                    &  & \defeq & \unittype                                        \\
-    \frametype[n][0,...,p] &  & \defeq & \frametype[n+1][0,...,p-1] \times \U \\
+    \frametype[n][\lbrack 0,p \rbrack] &  & \defeq & \frametype[n+1][\lbrack 0,p-1 \rbrack] \times \U \\
   \end{array}
@@
 
-The types $\paintingtype[n][0,...,p]$ of $\painting[n][0,...,p]$ for $p \leq n$
-are type families over frames, so $\framep[n][0,...,p]$ needs to be assumed
+The types $\paintingtype[n][\lbrack 0,p \rbrack]$ of $\painting[n][\lbrack 0,p \rbrack]$ for $p \leq n$
+are type families over frames, so $\framep[n][\lbrack 0,p \rbrack]$ needs to be assumed
 beforehand:
@@
   \begin{array}{llcl}
-    \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & \U                                                                                           \\
+    \paintingtype[n][\lbrack 0,p \rbrack] & (\framep[n][\lbrack 0,p \rbrack]:\frametype[n][\lbrack 0,p \rbrack]) & :      & \U                                                                                                                   \\
     \paintingtype[n][]                    & \unitpoint                                                           & \defeq & \unittype                                                                                                            \\
-    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n+1][0,...,p-1](\framep[n+1][0,...,p-1]) \times (\framep[n][p] \rightarrow \U) \\
+    \paintingtype[n][\lbrack 0,p \rbrack] & (\framep[n][\lbrack 0,p \rbrack])                                    & \defeq & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack]) \times (\framep[n][p] \rightarrow \U) \\
   \end{array}
@@
 
-Assuming $\framep[n][0,...,p-1]$ and $\painting[n][0,...,p-1]$ for $p \leq n+1$, we can
-mutually define the types $\restrftype[n][0,...,p-1]$ of frame
+Assuming $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\painting[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$, we can
+mutually define the types $\restrftype[n][\lbrack 0,p-1 \rbrack]$ of frame
 restrictions together with $\framep[n+1][0,...p]$ as a function from
-$\restrf[n][0,...,p-1]$, introducing also abbreviations for the types
+$\restrf[n][\lbrack 0,p-1 \rbrack]$, introducing also abbreviations for the types
 and definitions of layers, as well as for the combination of sequences
-of $\framep[n][0,..,p-1]$, $\painting[n][0,...,p-1]$ and
-$\restrf[n][0,...,p-1]$ in one block, which we call
+of $\framep[n][0,..,p-1]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and
+$\restrf[n][\lbrack 0,p-1 \rbrack]$ in one block, which we call
 $\depstype[n][0,...p-1]$:
@@
     \left(\begin{array}{lll}
-              \framep[n][0,...,p-1]   & : & \frametype[n][0,...,p-1]    \\
-              \painting[n][0,...,p-1] & : & \paintingtype[n][0,...,p-1]
-              (\framep[n][0,...,p-1])                                   \\
-              \restrf[n][0,...,p-1]   & : & \restrftype[n][0,...,p-1]
-              \left(\begin{array}{l}
-                  \framep[n][0,...,p-1]   \\
-                  \painting[n][0,...,p-1] \\
-                \end{array}\right)                             \\
-            \end{array}\right)        \\
-    \framep[n+1][0,...,p]     &
+              \framep[n][\lbrack 0,p-1 \rbrack]   & : & \frametype[n][\lbrack 0,p-1 \rbrack]    \\
+              \painting[n][\lbrack 0,p-1 \rbrack] & : & \paintingtype[n][\lbrack 0,p-1 \rbrack]
+              (\framep[n][\lbrack 0,p-1 \rbrack])                                               \\
+              \restrf[n][\lbrack 0,p-1 \rbrack]   & : & \restrftype[n][\lbrack 0,p-1 \rbrack]
+              \left(\begin{array}{l}
+                  \framep[n][\lbrack 0,p-1 \rbrack]   \\
+                  \painting[n][\lbrack 0,p-1 \rbrack] \\
+                \end{array}\right)                                         \\
+            \end{array}\right)                              \\
+    \framep[n+1][\lbrack 0,p \rbrack]         &
     \multicolumn{3}{l}{
-    (\deps[n][0,...,p-1]:\depstype[n][0,...,p-1]) :\frametype[n+1][0,...,p]}         \\
-    \framep[n+1][0,...,0]     &
+    (\deps[n][\lbrack 0,p-1 \rbrack]:\depstype[n][\lbrack 0,p-1 \rbrack]) :\frametype[n+1][\lbrack 0,p \rbrack]}         \\
+    \framep[n+1][\lbrack 0,0 \rbrack]         &
     \unitpoint                                & \defeq & (\unitpoint,unit)                                               \\
-    \framep[n+1][0,...,p+1] &
-    \deps[n][0,...,p]               & \defeq &
-    \left(\begin{array}{l}
-              \framep[n+1][0,...,p]
-              (\deps[n][0,...,p-1]), \\
+    \framep[n+1][\lbrack 0,p+1 \rbrack]       &
+    \deps[n][\lbrack 0,p \rbrack]             & \defeq &
+    \left(\begin{array}{l}
+              \framep[n+1][\lbrack 0,p \rbrack]
+              (\deps[n][\lbrack 0,p-1 \rbrack]), \\
               \Sigma d:\framep[n+1][p]
-              (\deps[n][0,...,p-1]).
+              (\deps[n][\lbrack 0,p-1 \rbrack]).
               \, \layer[n][p]
-              (\deps[n][0,...,p])
+              (\deps[n][\lbrack 0,p \rbrack])
               (d)                                \\
             \end{array}\right)                                                                             \\
-    \restrftype[n][0,...,p-1]       &
+    \restrftype[n][\lbrack 0,p-1 \rbrack]     &
     \multicolumn{3}{l}{
     \left(\begin{array}{l}
-              \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
-              \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
+              \framep[n][\lbrack 0,p-1 \rbrack]:\frametype[n][\lbrack 0,p-1 \rbrack]                                         \\
+              \painting[n][\lbrack 0,p-1 \rbrack]:\paintingtype[n][\lbrack 0,p-1 \rbrack](\framep[n][\lbrack 0,p-1 \rbrack]) \\
             \end{array}\right) : \U} \\
-    \restrftype[n][0,...,0-1]       &
+    \restrftype[n][\lbrack 0,0-1 \rbrack]     &
     \left(\begin{array}{l}
@@
     \unittype                                                                                                            \\
-    \restrftype[n][0,...,(p+1)-1]   &
-    \left(\begin{array}{l}
-              \framep[n][0,...,p]   \\
-              \painting[n][0,...,p] \\
+    \restrftype[n][\lbrack 0,(p+1)-1 \rbrack] &
+    \left(\begin{array}{l}
+              \framep[n][\lbrack 0,p \rbrack]   \\
+              \painting[n][\lbrack 0,p \rbrack] \\
             \end{array}\right)      & \defeq &
     \begin{array}{l}
-      \Sigma \restrf[n][0,...,p-1]
-      :\restrftype[n][0,...,p-1]
-      \left(\begin{array}{l}
-                \framep[n+1][0,...,p-1]   \\
-                \painting[n+1][0,...,p-1] \\
+      \Sigma \restrf[n][\lbrack 0,p-1 \rbrack]
+      :\restrftype[n][\lbrack 0,p-1 \rbrack]
+      \left(\begin{array}{l}
+                \framep[n+1][\lbrack 0,p-1 \rbrack]   \\
+                \painting[n+1][\lbrack 0,p-1 \rbrack] \\
               \end{array}\right).         \\
@@
       \left(\begin{array}{l}
-                \framep[n][0,...,p-1]   \\
-                \painting[n][0,...,p-1] \\
-                \restrf[n][0,...,p-1]   \\
+                \framep[n][\lbrack 0,p-1 \rbrack]   \\
+                \painting[n][\lbrack 0,p-1 \rbrack] \\
+                \restrf[n][\lbrack 0,p-1 \rbrack]   \\
               \end{array}\right) \rightarrow  \framep[n][p] \\
@@
     \multicolumn{3}{l}{
-      (\deps[n][0,...,p]:\depstype[n][0,...,p])
+      (\deps[n][\lbrack 0,p \rbrack]:\depstype[n][\lbrack 0,p \rbrack])
     : \U}                                                                                                                \\
     \layertype[n][p]                          &
-    \deps[n][0,...,p]
+    \deps[n][\lbrack 0,p \rbrack]
                                               & \defeq & \framep[n+1][p]
-    (\deps[n][0,...,p-1])
+    (\deps[n][\lbrack 0,p-1 \rbrack])
     \rightarrow \U                                                                                                       \\
@@
     \multicolumn{3}{l}{
-      (\deps[n][0,...,p]:\depstype[n][0,...,p])
+      (\deps[n][\lbrack 0,p \rbrack]:\depstype[n][\lbrack 0,p \rbrack])
       : \layertype[n][p]
-      (\deps[n][0,...,p])}
+      (\deps[n][\lbrack 0,p \rbrack])}
     \\
     \layer[n][p]                              &
-    \deps[n][0,...,p]
+    \deps[n][\lbrack 0,p \rbrack]
                                               & \defeq &
@@
 Defining $\painting[n+1][p]$ for $p \leq n+1$, in addition to the type dependency in $\framep[n+1][p]$, requires the definition of $\painting[n][p-1]$, thus also $\framep[n][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$.
-Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][p,...,n+1]$, $\painting[n][p,...,n]$, $\framep[n+1][p,...,n+1]$, $\framep[n][p,...,n]$ and $\restrf[n][p,...,n]$.
+Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][\lbrack p,n+1 \rbrack]$, $\painting[n][\lbrack p,n \rbrack]$, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$.
 Also, for the case $p=n$, this requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$.
-Finally, $\framep[n+1][p,...,n+1]$, $\framep[n+1][p,...,n]$ and $\restrf[n][p,...,n]$ respectively depend on the earlier values $\framep[n+1][0,...,p-1]$, $\framep[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$.
+Finally, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n+1][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$ respectively depend on the earlier values $\framep[n+1][\lbrack 0,p-1 \rbrack]$, $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$.
 Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n$ and $\restrftype$ at level $n$:
@@
   \begin{tikzcd}
-    & & \painting[n+1][p,...,n+1] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
-    \udensdash{\framep[n+1][0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
-    \udensdash{\framep[n+1][p,...,n+1]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
-    \painting[n][0,...,p-1] \arrow[d, dotted] & &
-    \painting[n][p,...,n-1] \arrow[ll, dotted] \arrow[d, dotted] \\
-    \framep[n][0,...,p-1] &
-    \udensdash{\restrf[n][0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
-    \framep[n][p,...,n] \arrow[ll, dotted, bend left=15] &
-    \udensdash{\restrf[n+1][p,...,n]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
+    & & \painting[n+1][\lbrack p,n+1 \rbrack] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
+    \udensdash{\framep[n+1][\lbrack 0,p-1 \rbrack]} \arrow[d, dashed] \arrow[ddr, dashed] & &
+    \udensdash{\framep[n+1][\lbrack p,n+1 \rbrack]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
+    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] & &
+    \painting[n][\lbrack p,n-1 \rbrack] \arrow[ll, dotted] \arrow[d, dotted] \\
+    \framep[n][\lbrack 0,p-1 \rbrack] &
+    \udensdash{\restrf[n][\lbrack 0,p-1 \rbrack]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
+    \framep[n][\lbrack p,n \rbrack] \arrow[ll, dotted, bend left=15] &
+    \udensdash{\restrf[n+1][\lbrack p,n \rbrack]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
   \end{tikzcd}
@@
 
-Let us introduce another abbreviation to combine a full $\deps[n][0,...,n]:\depstype[n][0,...,n]$ with a family $E:\framep[n+1][n+1](\deps[n][0,...,n])\rightarrow \U$:
+Let us introduce another abbreviation to combine a full $\deps[n][\lbrack 0,n \rbrack]:\depstype[n][\lbrack 0,n \rbrack]$ with a family $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U$:
 \begin{align*}
@@
   \left(\begin{array}{lll}
-            \deps[n][0,...,n] & : & \depstype[n][0,...,n]                             \\
-            E                   & : & \framep[n+1][n+1](\deps[n][0,...,n]) \rightarrow \U \\
+            \deps[n][\lbrack 0,n \rbrack] & : & \depstype[n][\lbrack 0,n \rbrack]                               \\
+            E                             & : & \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U \\
           \end{array}\right)
@@
     \left(\begin{array}{l}
-              \Sigma l:\layer[n][p](\fulldeps.\deps[n][0,...,p]). \\
+              \Sigma l:\layer[n][p](\fulldeps.\deps[n][\lbrack 0,p \rbrack]). \\
               \painting[n+1][p+1]
@@
 
-From which we can deduce $\painting[n+1][0,...,p]$ for $p \leq n+1$ by a second recursion, this time on $p$:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \painting[n+1][0,...,p]         &
-    (\fulldeps[n]:\fulldepstype[n]) & :      & \paintingtype[n+1][0,...,p](\framep[n+1][0,...,p](\fulldeps.\deps[n-1][0,...,p])) \\
-    \painting[n+1][0,...,0-1]       &
+From which we can deduce $\painting[n+1][\lbrack 0,p \rbrack]$ for $p \leq n+1$ by a second recursion, this time on $p$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \painting[n+1][\lbrack 0,p \rbrack]   &
+    (\fulldeps[n]:\fulldepstype[n])       & :      & \paintingtype[n+1][\lbrack 0,p \rbrack](\framep[n+1][\lbrack 0,p \rbrack](\fulldeps.\deps[n-1][\lbrack 0,p \rbrack])) \\
+    \painting[n+1][\lbrack 0,0-1 \rbrack] &
     \fulldeps[n]                          & \defeq & \unittype                                                                                                             \\
-    \painting[n+1][0,...,p]         &
+    \painting[n+1][\lbrack 0,p \rbrack]   &
     \fulldeps[n]
                                           & \defeq &
-    (\painting[n+1][0,...,p-1](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n]))                                                  \\
-  \end{array}
-\end{equation*}
-
-TODO: talk about unfoldPaintingProj.
+    (\painting[n+1][\lbrack 0,p-1 \rbrack](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n]))                                                                                \\
+  \end{array}
+\end{equation*}
 
@@
 
-At this stage, we are able to define $\framep[n+1][0,...,n+1]$, $\painting[n+1][0,...,n+1]$ and $\restrftype[n][0,...,n]$ from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$ and $\restrf[n][0,...,n]$, that is from $\deps[n][0,...,n]$.
-To go further, we need to define the sequence $\restrptype[n][0,...,p-1]$ of types of painting restrictions, for $p \leq n+1$:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \restrptype[n][0,...,p-1]       &
+At this stage, we are able to define $\framep[n+1][\lbrack 0,n+1 \rbrack]$, $\painting[n+1][\lbrack 0,n+1 \rbrack]$ and $\restrftype[n][\lbrack 0,n \rbrack]$ from $\framep[n][\lbrack 0,n \rbrack]$, $\painting[n][\lbrack 0,n \rbrack]$ and $\restrf[n][\lbrack 0,n \rbrack]$, that is from $\deps[n][\lbrack 0,n \rbrack]$.
+To go further, we need to define the sequence $\restrptype[n][\lbrack 0,p-1 \rbrack]$ of types of painting restrictions, for $p \leq n+1$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \restrptype[n][\lbrack 0,p-1 \rbrack]     &
     (\fulldeps[n]:\fulldepstype[n])           & :      & \U                                                                \\
-    \restrptype[n][0,...,0-1]       & E      & \defeq                                    & \unittype \\
-    \restrptype[n][0,...,(p+1)-1]   &
+    \restrptype[n][\lbrack 0,0-1 \rbrack]     & E      & \defeq                                                & \unittype \\
+    \restrptype[n][\lbrack 0,(p+1)-1 \rbrack] &
     (\fulldeps[n])
-                                    & \defeq & \restrptype[n+1][0,...,p-1] \times \left(
+                                              & \defeq & \restrptype[n+1][\lbrack 0,p-1 \rbrack] \times \left(
     \begin{array}{l}
-        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][0,...,p-1]). \\
+        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack]). \\
         \painting[n+1][p]
@@
 
-Thanks to $\restrptype[n][0,...,p-1]$ for $p \leq n+1$, we can mutually define $\restrf[n+1][0,...,p]$ and $\cohftype[n][0,...,p-1]$ from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$, $\restrptype[n][0,...,p-1]$ and some $E:\framep[n+1][n+1](\deps[n][0,...,n]) \rightarrow \U$, abbreviating these dependencies and the dependency in a $\cohf[n][0,...,p-1]$ as $\depscohstype[n][0,...,p-1]$, and using also abbreviations in passing for $\restrl$ and $\restrltype$.
-It is also convenient to build $\deps[n+1][0,...,p]$ from $\depscohs[n][0,...,p-1]$, so that we can now build $\framep[n+2][p]$ one step further.
+Thanks to $\restrptype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$, we can mutually define $\restrf[n+1][\lbrack 0,p \rbrack]$ and $\cohftype[n][\lbrack 0,p-1 \rbrack]$ from $\framep[n][\lbrack 0,n \rbrack]$, $\painting[n][\lbrack 0,n \rbrack]$, $\restrf[n][\lbrack 0,n \rbrack]$, $\restrptype[n][\lbrack 0,p-1 \rbrack]$ and some $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$, abbreviating these dependencies and the dependency in a $\cohf[n][\lbrack 0,p-1 \rbrack]$ as $\depscohstype[n][\lbrack 0,p-1 \rbrack]$, and using also abbreviations in passing for $\restrl$ and $\restrltype$.
+It is also convenient to build $\deps[n+1][\lbrack 0,p \rbrack]$ from $\depscohs[n][\lbrack 0,p-1 \rbrack]$, so that we can now build $\framep[n+2][p]$ one step further.
 Thus, we also include this abbreviation in the definition:
@@
     \left(\begin{array}{lcl}
-              \fulldeps[n][0,...,n] & : & \fulldepstype[n][0,...,n]               \\
-              \restrp[n][0,...p-1]  & : & \restrptype[n][0,...,p-1](\fulldeps[n]) \\
-              \cohf[n][0,...,p-1]   & : & \cohftype[n][0,...,p-1]
+              \fulldeps[n][\lbrack 0,n \rbrack] & : & \fulldepstype[n][\lbrack 0,n \rbrack]               \\
+              \restrp[n][0,...p-1]              & : & \restrptype[n][\lbrack 0,p-1 \rbrack](\fulldeps[n]) \\
+              \cohf[n][\lbrack 0,p-1 \rbrack]   & : & \cohftype[n][\lbrack 0,p-1 \rbrack]
               \left(\begin{array}{l}
                   \fulldeps[n]                      \\
-                  \restrp[n][0,...,p-1] \\
+                  \restrp[n][\lbrack 0,p-1 \rbrack] \\
                 \end{array}\right)                                                     \\
@@
     \multicolumn{3}{l}{
-    (\depscohs[n][0,...,p-1]:\depscohstype[n][0,...,p-1]) : \depstype[n+1][0,...,p]}                                                                                                                             \\
-    \overline{\deps}                & \depscohs[n][0,...,p-1] & \defeq                                                         &
-    \left(\begin{array}{l}
-              \framep[n+1][0,...,p](\depscohs.\fulldeps.\deps[n][0,...,p-1]) \\
-              \painting[n+1][0,...,p](\depscohs.\fulldeps[n])                \\
-              \restrf[n+1][0,...,p](\depscohs[n][0,...,p-1])                 \\
-            \end{array}\right)                                                                                                                                         \\
-    \restrf[n+1][0,...,p]     &
+    (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack]) : \depstype[n+1][\lbrack 0,p \rbrack]}                                                                                         \\
+    \overline{\deps}                        & \depscohs[n][\lbrack 0,p-1 \rbrack] & \defeq                                                         &
+    \left(\begin{array}{l}
+              \framep[n+1][\lbrack 0,p \rbrack](\depscohs.\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack]) \\
+              \painting[n+1][\lbrack 0,p \rbrack](\depscohs.\fulldeps[n])                            \\
+              \restrf[n+1][\lbrack 0,p \rbrack](\depscohs[n][\lbrack 0,p-1 \rbrack])                 \\
+            \end{array}\right)                                                                                                                 \\
+    \restrf[n+1][\lbrack 0,p \rbrack]       &
     \multicolumn{3}{l}{
-      (\depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1]) :
-      \restrftype[n+1][0,...,p]
-      \left(\begin{array}{l}
-                \framep[n+1][0,...,p](\depscohs.\fulldeps.\deps[n][0,...,p]) \\
-                \painting[n+1][0,...,p](\depscohs.\fulldeps[n])              \\
+      (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][0,..,p-1]) :
+      \restrftype[n+1][\lbrack 0,p \rbrack]
+      \left(\begin{array}{l}
+                \framep[n+1][\lbrack 0,p \rbrack](\depscohs.\fulldeps.\deps[n][\lbrack 0,p \rbrack]) \\
+                \painting[n+1][\lbrack 0,p \rbrack](\depscohs.\fulldeps[n])                          \\
               \end{array}\right)
     }                                                                                                                                                                                                            \\
-    \restrf[n+1][0,...,0]     &
+    \restrf[n+1][\lbrack 0,0 \rbrack]       &
     E
@@
 \lambda \_.\unitpoint)                                                               \\
-    \restrf[n+1][0,...,p+1] &
+    \restrf[n+1][\lbrack 0,p+1 \rbrack]     &
     (\depscohs[n][0,..,p])                  & \defeq                              &
     \left(\begin{array}{l}
-              \restrf[n+1][0,...,p][q][\epsilon]
+              \restrf[n+1][\lbrack 0,p \rbrack][q][\epsilon]
               (\depscohs[n][0,..,p-1]),                 \\
@@
             \end{array} \right)                                                                                                                                    \\
-    \cohftype[n][0,...,p-1]         &
+    \cohftype[n][\lbrack 0,p-1 \rbrack]     &
     \multicolumn{3}{l}{
@@
               \fulldeps[n]:\fulldepstype[n]                                                         \\
-              \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\fulldeps[n]) \\
+              \restrp[n][\lbrack 0,p-1 \rbrack]:\restrptype[n][\lbrack 0,p-1 \rbrack](\fulldeps[n]) \\
             \end{array}\right) : \U
     }                                                                                                                  n                                                                                         \\
-    \cohftype[n][0,...,0-1]         &
+    \cohftype[n][\lbrack 0,0-1 \rbrack]     &
     \left(\begin{array}{l}
@@
     \unittype                                                                                                                                                                                                    \\
-    \cohftype[n][0,...,(p+1)-1]     &
+    \cohftype[n][\lbrack 0,(p+1)-1 \rbrack] &
     \left(\begin{array}{l}
               \fulldeps[n]                    \\
-              \restrp[n][0,...,p] \\
+              \restrp[n][\lbrack 0,p \rbrack] \\
             \end{array}\right)      & \defeq                              &
     \left\{\begin{array}{l}
-             \Sigma \cohf[n][0,...,p-1]
-             :\cohftype[n][0,...,p-1]
+             \Sigma \cohf[n][\lbrack 0,p-1 \rbrack]
+             :\cohftype[n][\lbrack 0,p-1 \rbrack]
              \left(\begin{array}{l}
                 \fulldeps[n]                      \\
-                \restrp[n][0,...,p-1] \\
+                \restrp[n][\lbrack 0,p-1 \rbrack] \\
               \end{array}\right).                  \\
@@
                                  \fulldeps[n]                      \\
-                                 \restrp[n][0,...,p-1] \\
-                                 \cohf[n][0,...,p]
+                                 \restrp[n][\lbrack 0,p-1 \rbrack] \\
+                                 \cohf[n][\lbrack 0,p \rbrack]
                                \end{array}\right)          . \\
@@
                 \fulldeps[n]                      \\
-                \restrp[n][0,...,p-1] \\
-                \cohf[n][0,...,p]
+                \restrp[n][\lbrack 0,p-1 \rbrack] \\
+                \cohf[n][\lbrack 0,p \rbrack]
               \end{array}\right)(d)) =                  \\
@@
                 \fulldeps[n]                      \\
-                \restrp[n][0,...,p-1] \\
-                \cohf[n][0,...,p]
+                \restrp[n][\lbrack 0,p-1 \rbrack] \\
+                \cohf[n][\lbrack 0,p \rbrack]
               \end{array}\right)(d))                  \\
@@
     \multicolumn{3}{l}{
-      (\depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1])
+      (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][0,..,p-1])
     : \U}                                                                                                                                                                                                        \\
@@
              \layer[n+1][p](\overline{\deps}(\depscohs[n][0,..,p-1])(d) \rightarrow                          \\
-             \layer[n][p](\fulldeps.\deps[n][0,...,p])(\restrf[n][p]
+             \layer[n][p](\fulldeps.\deps[n][\lbrack 0,p \rbrack])(\restrf[n][p]
              (\depscohs[n][0,..,p-1])(d))
@@
 
-We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][0,...,n]$ with a set $E:\framep[n+2][n+2](\overline{\deps}(\depscohs[n][0,...,n])) \rightarrow \U$:
+We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$:
 \begin{align*}
@@
   \left(\begin{array}{lcl}
-            \depscohs[n][0,...,n-1] & : & \depscohstype[n][0,...,n]                                                \\
-            E                       & : & \framep[n+2][n+2](\overline{\deps}(\depscohs[n][0,...,n]))\rightarrow \U \\
+            \depscohs[n][\lbrack 0,n-1 \rbrack] & : & \depscohstype[n][\lbrack 0,n \rbrack]                                                \\
+            E                                   & : & \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack]))\rightarrow \U \\
           \end{array}\right)
@@
   \left(\begin{array}{l}
-            \overline{\deps}(\fulldepscohs.\depscohs[n][0,...,n]) \\
+            \overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,n \rbrack]) \\
             \fulldepscohs.E                                                   \\
@@
         \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n+2][p]
-        (\overline{\deps}(\fulldepscohs.\depscohs[n][0,...,p-1])). \\
+        (\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])). \\
         \painting[n+2][p]
@@
         \painting[n+1][p](\fulldepscohs.\depscohs.\fulldeps[n])
-        (\restrf[n+1][p](\fulldepscohs.\depscohs[n][0,...,p-1])(d))\end{array}\right)                                                        \\
+        (\restrf[n+1][p](\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])(d))\end{array}\right)                                                        \\
     \restrp[n+1][n+1]                       &
@@
     \left(\begin{array}{l}
-              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n][0,...,p])(d)(l), \\
+              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n][\lbrack 0,p \rbrack])(d)(l), \\
               \restrp[n+1][p+1][q][\epsilon](\fulldepscohs[n])(d,l)(c)                           \\
@@
 
-From which we can deduce $\restrp[n+1][0,...,p]$ for $p \leq n+1$ again by a second recursion, this time on $p$:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \restrp[n+1][0,...,p]                   &
-    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \restrptype[n+1][0,...,p](\fulldepscohs.\depscohs.\fulldeps[n])) \\
-    \restrp[n+1][0,...,0-1]                 &
+From which we can deduce $\restrp[n+1][\lbrack 0,p \rbrack]$ for $p \leq n+1$ again by a second recursion, this time on $p$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \restrp[n+1][\lbrack 0,p \rbrack]       &
+    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \restrptype[n+1][\lbrack 0,p \rbrack](\fulldepscohs.\depscohs.\fulldeps[n])) \\
+    \restrp[n+1][\lbrack 0,0-1 \rbrack]     &
     \fulldepscohs[n]                        & \defeq & \unittype                                                                    \\
-    \restrp[n+1][0,...,p]                   &
+    \restrp[n+1][\lbrack 0,p \rbrack]       &
     \fulldepscohs[n]
                                             & \defeq &
-    (\restrp[n+1][0,...,p-1](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))                                       \\
+    (\restrp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))                                       \\
   \end{array}
@@
 
-At this stage, we are then able to define $\restrf[n+1][0,...,p]$, $\restrp[n+1][0,...,p]$ and $\cohftype[n][0,...,p-1]$ for $p \leq n+1$
-from $\depscohs[n][0,...,p-1]$ at the previous level. To go further, we need to define the
-sequence $\cohptype[n][0,...,p-1]$ of types of painting coherence laws:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \cohptype[n][0,...,p-1]     & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                               \\
-    \cohptype[n][0,...,0-1]     & \unitpoint                              & \defeq & \unittype                                        \\
-    \cohptype[n][0,...,(p+1)-1] & (\fulldepscohs[n])                      & \defeq & \cohptype[n][0,...,p-1](\fulldepscohs[n]) \times \\
+At this stage, we are then able to define $\restrf[n+1][\lbrack 0,p \rbrack]$, $\restrp[n+1][\lbrack 0,p \rbrack]$ and $\cohftype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$
+from $\depscohs[n][\lbrack 0,p-1 \rbrack]$ at the previous level. To go further, we need to define the
+sequence $\cohptype[n][\lbrack 0,p-1 \rbrack]$ of types of painting coherence laws:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \cohptype[n][\lbrack 0,p-1 \rbrack]     & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                                           \\
+    \cohptype[n][\lbrack 0,0-1 \rbrack]     & \unitpoint                              & \defeq & \unittype                                                    \\
+    \cohptype[n][\lbrack 0,(p+1)-1 \rbrack] & (\fulldepscohs[n])                      & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
                                             &                                         &        & \;\;\;\;\left\{
     \begin{array}{l}
-      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][0,...,p-1])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
+      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
       \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf[n+1][p](d))(\restrp[n+1][p][r][\omega]
@@
 
-Thanks to $\cohptype[n][0,...,p-1]$, we can mutually define $\cohf[n+1][0,...,p]$ and $\cohttype[n][0,...,p-1]$ for $p \leq n+1$ from $\fulldepscohs[n][0,...,p-1]$, abbreviating this and the dependency in a $\coht[n][0,...,p-1]$ as $\depscohttype[n][0,...,p-1]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$.
-It is also convenient to build $\depscohs[n+1][0,...,p]$ from $\depscoht[n][0,...,p-1]$, so that we can now build $\framep[n+3][p]$.
+Thanks to $\cohptype[n][\lbrack 0,p-1 \rbrack]$, we can mutually define $\cohf[n+1][\lbrack 0,p \rbrack]$ and $\cohttype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ from $\fulldepscohs[n][\lbrack 0,p-1 \rbrack]$, abbreviating this and the dependency in a $\coht[n][\lbrack 0,p-1 \rbrack]$ as $\depscohttype[n][\lbrack 0,p-1 \rbrack]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$.
+It is also convenient to build $\depscohs[n+1][\lbrack 0,p \rbrack]$ from $\depscoht[n][\lbrack 0,p-1 \rbrack]$, so that we can now build $\framep[n+3][p]$.
 Thus, we also include this abbreviation in the definition:
@@
               \fulldepscohs[n]                & : & \fulldepscohstype[n]                                  \\
-              \cohp[n][0,...p-1]  & : & \cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
-              \coht[n][0,...,p-1] & : & \cohttype[n][0,...,p-1]
+              \cohp[n][0,...p-1]              & : & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \\
+              \coht[n][\lbrack 0,p-1 \rbrack] & : & \cohttype[n][\lbrack 0,p-1 \rbrack]
               \left(\begin{array}{l}
                   \fulldepscohs[n]                \\
-                  \cohp[n][0,...,p-1] \\
-                \end{array}\right)                                           \\
-            \end{array}\right)                                                                                                                                                \\
-    \overline{\depscohs}                                             & (\depscoht[n][0,...,p-1]:\depscohttype[n][0,...,p-1]) & :                                                                                 & \depscohstype[n+1][0,...,p] \\
-    \overline{\depscohs}                                             & \depscoht[n][0,...,p-1]                             & \defeq                                                                            &
-    \left(\begin{array}{l}
-              \overline{\deps}(\depscoht.\fulldepscohs.\depscohs[n][0,...,p-1]) \\
+                  \cohp[n][\lbrack 0,p-1 \rbrack] \\
+                \end{array}\right)                                                       \\
+            \end{array}\right)                                                                                                                                                                                                                \\
+    \overline{\depscohs}                                                                     & (\depscoht[n][\lbrack 0,p-1 \rbrack]:\depscohttype[n][\lbrack 0,p-1 \rbrack]) & :                                                                                 & \depscohstype[n+1][\lbrack 0,p \rbrack] \\
+    \overline{\depscohs}                                                                     & \depscoht[n][\lbrack 0,p-1 \rbrack]                                           & \defeq                                                                            &
+    \left(\begin{array}{l}
+              \overline{\deps}(\depscoht.\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack]) \\
               \restrp[n+1][p](\depscoht.\fulldepscohs[n])                                   \\
-              \cohf[n+1][p](\depscoht[n][0,...,p-1])                            \\
-            \end{array}\right)                                                                                                                                                                \\
-    \cohf[n+1][0,...,p]                                              &
-    (\depscoht[n][0,...,p-1]:\depscohttype[n][0,...,p-1])                          & :                                                 & \cohftype[n+1][0,...,p]
+              \cohf[n+1][p](\depscoht[n][\lbrack 0,p-1 \rbrack])                            \\
+            \end{array}\right)                                                                                                                                                                                                                    \\
+    \cohf[n+1][\lbrack 0,p \rbrack]                                                          &
+    (\depscoht[n][\lbrack 0,p-1 \rbrack]:\depscohttype[n][\lbrack 0,p-1 \rbrack])            & :                                                                             & \cohftype[n+1][\lbrack 0,p \rbrack]
     \left(\begin{array}{l}
               \overline{\fulldeps}(\depscoht.\fulldepscohs[n])              \\
-              \restrp[n+1][0,...,p](\depscoht.\fulldepscohs[n]) \\
+              \restrp[n+1][\lbrack 0,p \rbrack](\depscoht.\fulldepscohs[n]) \\
             \end{array}\right)                                                                                                                                                                                                                                    \\
     \\
-    \cohf[n][0,...,0]                                          &
+    \cohf[n][\lbrack 0,0 \rbrack]                                                            &
     \unitpoint                                                                               & \defeq                                                                        & (\unitpoint,\lambda q.\lambda r.
@@
 \lambda\omega.\lambda \_.\refl)                                           \\
-    \cohf[n][0,...,p+1]                                      &
-    (\depscoht[n][0,...,p-1])                                               & \defeq                                            &
-    \left(\begin{array}{l}
-              \cohf[n+1][0,...,p]
+    \cohf[n][\lbrack 0,p+1 \rbrack]                                                          &
+    (\depscoht[n][\lbrack 0,p-1 \rbrack])                                                    & \defeq                                                                        &
+    \left(\begin{array}{l}
+              \cohf[n+1][\lbrack 0,p \rbrack]
               (\depscoht[n]),                                                    \\
               \lambda q.\lambda r.\lambda \epsilon.\lambda \omega.\lambda (d,l). \\
-              (\cohf[n][0,...,p][q][r][\epsilon][\omega]
+              (\cohf[n][\lbrack 0,p \rbrack][q][r][\epsilon][\omega]
               (\depscoht[n])(d), \cohl[n][p][q][r][\epsilon][\omega]
@@
             \end{array}\right)                                                                                                                                                                                                                               \\
-    \cohttype[n][0,...,p-1]                                          &
+    \cohttype[n][\lbrack 0,p-1 \rbrack]                                                      &
     \left(\begin{array}{l}
               \fulldepscohs[n]:\fulldepscohstype[n]                                                 \\
-              \cohp[n][0,...,p-1]:\cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
+              \cohp[n][\lbrack 0,p-1 \rbrack]:\cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \\
             \end{array}\right) & :                                                                             & \U                                                                                                                                                                                          \\
-    \cohttype[n][0,...,0-1]                                          &
+    \cohttype[n][\lbrack 0,0-1 \rbrack]                                                      &
     \left(\begin{array}{l}
@@
     \unittype                                                                                                                                                                                                                                                                                              \\
-    \cohttype[n][0,...,(p+1)-1]                                      &
+    \cohttype[n][\lbrack 0,(p+1)-1 \rbrack]                                                  &
     \left(\begin{array}{l}
               \fulldepscohs[n]              \\
-              \cohp[n][0,...,p] \\
+              \cohp[n][\lbrack 0,p \rbrack] \\
             \end{array}\right)                                                         & \defeq                                                                        &
     \left(\begin{array}{l}
-              \Sigma \coht[n][0,...,p-1]
-              :\cohttype[n][0,...,p-1]
+              \Sigma \coht[n][\lbrack 0,p-1 \rbrack]
+              :\cohttype[n][\lbrack 0,p-1 \rbrack]
               \left(\begin{array}{l}
                   \fulldepscohs[n+1]                \\
-                  \cohp[n+1][0,...,p-1] \\
+                  \cohp[n+1][\lbrack 0,p-1 \rbrack] \\
                 \end{array}\right).                               \\
@@
     \cohl[n][p]                                                                              &
-    (\depscoht[n][0,...,p-1]:\depscohttype[n][0,...,p-1])                          & :                                                 &
+    (\depscoht[n][\lbrack 0,p-1 \rbrack]:\depscohttype[n][\lbrack 0,p-1 \rbrack])            & :                                                                             &
     \begin{array}{l}
@@
     \cohl[n][p][q][\epsilon][r][\omega]                                                      &
-    (\depscoht[n][0,...,p-1])                                               & \defeq                                            &
+    (\depscoht[n][\lbrack 0,p-1 \rbrack])                                                    & \defeq                                                                        &
     \lambda d.
@@
 
-We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][0,...,n]$ with a set $E:\framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][0,...,n]))) \rightarrow \U$:
+We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$:
 \begin{align*}
@@
   \left(\begin{array}{lll}
-            \depscoht[n][0,...,n] & : & \depscohttype[n][0,...,n]                                                    \\
-            E                       & : & \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][0,...,n])))\rightarrow \U \\
+            \depscoht[n][\lbrack 0,n \rbrack] & : & \depscohttype[n][\lbrack 0,n \rbrack]                                                                      \\
+            E                                 & : & \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack])))\rightarrow \U \\
           \end{array}\right)
@@
   \left(\begin{array}{l}
-            \overline{\depscohs}(\fulldepscoht.\depscoht[n][0,...,n]) \\
+            \overline{\depscohs}(\fulldepscoht.\depscoht[n][\lbrack 0,n \rbrack]) \\
             \fulldepscoht.E                                                       \\
@@
         \restrp[n][p][q][\epsilon](\overline{\fulldeps}(\depscoht))(\restrp[n+1][p][r][\omega]
-        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][0,...,n])(d)(c)) =           \\
+        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][\lbrack 0,n \rbrack])(d)(c)) = \\
         \restrp[n][p][r][\omega](\overline{\fulldeps}(\depscoht))(\restrp[n+1][p][q+1][\epsilon]
-        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][0,...,n])(d)(c))             \\
-        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][0,...,n])(d)(c))             \\
+        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][\lbrack 0,n \rbrack])(d)(c))   \\
+        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][\lbrack 0,n \rbrack])(d)(c))   \\
       \end{array}\right)                                                                         \\
@@
     \left(\begin{array}{l}
-              \cohl[n][p][q][r][\epsilon][\omega](\fulldepscoht.\depscoht[n][0,...,p-1])(d)(l), \\
+              \cohl[n][p][q][r][\epsilon][\omega](\fulldepscoht.\depscoht[n][\lbrack 0,p-1 \rbrack])(d)(l), \\
               \cohp[n+1][p+1][q][r][\epsilon][\omega](\fulldepscoht[n])(d,l))(c)                            \\
@@
 
-From which we can deduce $\cohp[n+1][0,...,p]$ again by a second recursion, this time on $p$:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \cohp[n+1][0,...,p]                     &
-    (\fulldepscoht[n]:\fulldepscohttype[n]) & :      & \cohptype[n+1][0,...,p](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
-    \cohp[n+1][0,...,0-1]                   &
+From which we can deduce $\cohp[n+1][\lbrack 0,p \rbrack]$ again by a second recursion, this time on $p$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \cohp[n+1][\lbrack 0,p \rbrack]         &
+    (\fulldepscoht[n]:\fulldepscohttype[n]) & :      & \cohptype[n+1][\lbrack 0,p \rbrack](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
+    \cohp[n+1][\lbrack 0,0-1 \rbrack]       &
     \fulldepscohs[n]                        & \defeq & \unittype                                                                      \\
-    \cohp[n+1][0,...,p]                     &
+    \cohp[n+1][\lbrack 0,p \rbrack]         &
     \fulldepscoht[n]
                                             & \defeq &
-    (\cohp[n+1][0,...,p-1](\fulldepscoht[n]),\cohp[n+1][p](\fulldepscoht[n]))                                             \\
+    (\cohp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht[n]),\cohp[n+1][p](\fulldepscoht[n]))                                             \\
   \end{array}
@@
 \begin{align*}
-  \rotatebox[origin=c]{90}{\depscohs[n][0,...,n-1]}\begin{cases}
-                                                     \rotatebox[origin=c]{90}{\deps[n][0,...,n-1]}\begin{cases}
-                                                   \framep[n][0,...,n-1]   : \frametype[n][0,...,n-1]                           \\
-                                                   \painting[n][0,...,n-1] : \paintingtype[n][0,...,n-1](\framep[n][0,...,n-1]) \\
-                                                   \restrf[n][0,...,n-1]   : \restrftype[n][0,...,n-1]
-                                                   \left(\begin{array}{l}
-                \framep[n][0,...,n-1]   \\
-                \painting[n][0,...,n-1] \\
+  \rotatebox[origin=c]{90}{\depscohs[n][\lbrack 0,n-1 \rbrack]}\begin{cases}
+                                                                 \rotatebox[origin=c]{90}{\deps[n][\lbrack 0,n-1 \rbrack]}\begin{cases}
+                                                               \framep[n][\lbrack 0,n-1 \rbrack]   : \frametype[n][\lbrack 0,n-1 \rbrack]                                       \\
+                                                               \painting[n][\lbrack 0,n-1 \rbrack] : \paintingtype[n][\lbrack 0,n-1 \rbrack](\framep[n][\lbrack 0,n-1 \rbrack]) \\
+                                                               \restrf[n][\lbrack 0,n-1 \rbrack]   : \restrftype[n][\lbrack 0,n-1 \rbrack]
+                                                               \left(\begin{array}{l}
+                \framep[n][\lbrack 0,n-1 \rbrack]   \\
+                \painting[n][\lbrack 0,n-1 \rbrack] \\
               \end{array}\right)
@@
                                                                  E:\framep[n+1][n]
-                                                     (\deps[n][0,...,n-1])\rightarrow \U                                                                                       \\
-                                                     \restrp[n][0,...,n-1](E) : \restrptype[n][0,...,n-1]
-                                                     \left(\begin{array}{l}
-              \deps[n][0,...,n-1] \\
+                                                                 (\deps[n][\lbrack 0,n-1 \rbrack])\rightarrow \U                                                                                                                           \\
+                                                                 \restrp[n][\lbrack 0,n-1 \rbrack](E) : \restrptype[n][\lbrack 0,n-1 \rbrack]
+                                                                 \left(\begin{array}{l}
+              \deps[n][\lbrack 0,n-1 \rbrack] \\
               E                               \\
             \end{array}\right)                                                                                                                                     \\
-                                                     \cohf[n][0,...,n-1](E)   : \cohftype[n][0,...,n-1]
-                                                     \left(\begin{array}{l}
-              \deps[n][0,...,n-1]                 \\
+                                                                 \cohf[n][\lbrack 0,n-1 \rbrack](E)   : \cohftype[n][\lbrack 0,n-1 \rbrack]
+                                                                 \left(\begin{array}{l}
+              \deps[n][\lbrack 0,n-1 \rbrack]                 \\
               E:\framep[n+1][n]
-              (\deps[n][0,...,n-1])\rightarrow \U \\
-              \restrp[n][0,...,n-1]               \\
+              (\deps[n][\lbrack 0,n-1 \rbrack])\rightarrow \U \\
+              \restrp[n][\lbrack 0,n-1 \rbrack]               \\
             \end{array}\right)
@@
   E': \framep[n+2][n+1](\overline{\deps}
-  (\depscohs[n][0,...,n-1])\rightarrow \U                                                                                                                                                  \\
-  \cohp[n][0,...,n-1]
+  (\depscohs[n][\lbrack 0,n-1 \rbrack])\rightarrow \U                                                                                                                                                  \\
+  \cohp[n][\lbrack 0,n-1 \rbrack]
   \left(\begin{array}{l}
@@
           \end{array}\right)
-  : \cohptype[n][0,...,n-1]
-  \left(\begin{array}{l}
-            \depscohs[n][0,...,n-1] \\
+  : \cohptype[n][\lbrack 0,n-1 \rbrack]
+  \left(\begin{array}{l}
+            \depscohs[n][\lbrack 0,n-1 \rbrack] \\
             E'                                  \\
@@
 \begin{itemize}
-  \item $\framep[n+1][0,...,n]$ comes from $\deps[n]$ which holds by assumptions (using $\framep[n][0,...,n-1]$, $\painting[n][0,...,n-1]$ and $\restrf[n][0,...,n-1]$)
-  \item $\painting[n+1][0,...,n]$ comes from $\fulldeps[n]$ which holds by assumptions (also using $E$)
-  \item $\restrf[n+1][0,...,n]$ comes from $\depscohs[n][0,...,n-1]$ which holds by assumptions (additionally using the assumptions of $\restrp[n][0,...,n-1]$ and $\cohf[n][0,...,n-1]$)
-  \item $\restrp[n+1][0,...,n]$ assuming $E':\framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$ comes from $\fulldepscohs[n]$ which holds by assumptions (additionally using $E'$)
-  \item $\cohf[n+1][0,...,n]$ assuming $E'$ comes from $\depscoht[n][0,...,n-1]$ which holds by assumptions (additionally using the assumption of $\cohp[n][0,...,n-1]$ and proving $\coht[n][0,...,n-1]$ by uniqueness of identity proofs)
-  \item $\cohp[n+1][0,...,n]$ assuming $E'$ and $E'': \framep[n+3][n+2](\overline{\deps}(\overline{\depscohs}(\depscoht[n][0,...,n-1]))) \rightarrow \U$ comes from $\fulldepscoht[n][0,...,n-1]$ which holds by assumptions (additionally using $E''$)
+  \item $\framep[n+1][\lbrack 0,n \rbrack]$ comes from $\deps[n]$ which holds by assumptions (using $\framep[n][\lbrack 0,n-1 \rbrack]$, $\painting[n][\lbrack 0,n-1 \rbrack]$ and $\restrf[n][\lbrack 0,n-1 \rbrack]$)
+  \item $\painting[n+1][\lbrack 0,n \rbrack]$ comes from $\fulldeps[n]$ which holds by assumptions (also using $E$)
+  \item $\restrf[n+1][\lbrack 0,n \rbrack]$ comes from $\depscohs[n][\lbrack 0,n-1 \rbrack]$ which holds by assumptions (additionally using the assumptions of $\restrp[n][\lbrack 0,n-1 \rbrack]$ and $\cohf[n][\lbrack 0,n-1 \rbrack]$)
+  \item $\restrp[n+1][\lbrack 0,n \rbrack]$ assuming $E':\framep[n+2][n+1](\overline{\deps}(\depscohs[n][\lbrack 0,n-1 \rbrack])) \rightarrow \U$ comes from $\fulldepscohs[n]$ which holds by assumptions (additionally using $E'$)
+  \item $\cohf[n+1][\lbrack 0,n \rbrack]$ assuming $E'$ comes from $\depscoht[n][\lbrack 0,n-1 \rbrack]$ which holds by assumptions (additionally using the assumption of $\cohp[n][\lbrack 0,n-1 \rbrack]$ and proving $\coht[n][\lbrack 0,n-1 \rbrack]$ by uniqueness of identity proofs)
+  \item $\cohp[n+1][\lbrack 0,n \rbrack]$ assuming $E'$ and $E'': \framep[n+3][n+2](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n-1 \rbrack]))) \rightarrow \U$ comes from $\fulldepscoht[n][\lbrack 0,n-1 \rbrack]$ which holds by assumptions (additionally using $E''$)
 \end{itemize}

### 2025-12-07 paper/paper.tex
paper: commit to intervals for now

@@
 and definitions of layers, as well as for the combination of sequences
-of $\framep[n][0,..,p-1]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and
+of $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and
 $\restrf[n][\lbrack 0,p-1 \rbrack]$ in one block, which we call
@@
   \begin{array}{llcl}
-    \depstype[n][0,..,p-1]                    &        & \defeq            &
+    \depstype[n][\lbrack 0,p-1 \rbrack]       &        & \defeq            &
     \left(\begin{array}{lll}
@@
 projections of a $\deps$. Also, by abuse of notation, we write $\unitpoint$ for
-the only inhabitant of $\depstype[n][0,..,0-1]$.
+the only inhabitant of $\depstype[n][\lbrack 0,0-1 \rbrack]$.
 
@@
   \begin{array}{llcl}
-    \depscohstype[n][0,..,p-1]              &                                     & \defeq                                                         &
+    \depscohstype[n][\lbrack 0,p-1 \rbrack] &                                     & \defeq                                                         &
     \left(\begin{array}{lcl}
@@
     \multicolumn{3}{l}{
-      (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][0,..,p-1]) :
+      (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack]) :
       \restrftype[n+1][\lbrack 0,p \rbrack]
@@
     \restrf[n+1][\lbrack 0,p+1 \rbrack]     &
-    (\depscohs[n][0,..,p])                  & \defeq                              &
+    (\depscohs[n][\lbrack 0,p \rbrack])     & \defeq                              &
     \left(\begin{array}{l}
               \restrf[n+1][\lbrack 0,p \rbrack][q][\epsilon]
-              (\depscohs[n][0,..,p-1]),                 \\
+              (\depscohs[n][\lbrack 0,p-1 \rbrack]),           \\
               \lambda q.\lambda \epsilon.\lambda (d,l).        \\
               \left(\restrf[n][p][q][\epsilon]
-                (\depscohs[n][0,..,p-1])(d), \restrl[n][p][q][\epsilon]
-              (\depscohs[n][0,..,p])(d)(l)\right)       \\
+                (\depscohs[n][\lbrack 0,p-1 \rbrack])(d), \restrl[n][p][q][\epsilon]
+              (\depscohs[n][\lbrack 0,p \rbrack])(d)(l)\right) \\
             \end{array} \right)                                                                                                                                                       \\
@@
     \multicolumn{3}{l}{
-      (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][0,..,p-1])
+      (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack])
     : \U}                                                                                                                                                                                                                     \\
     \restrltype[n][p]                       &
-    \depscohs[n][0,..,p-1]
+    \depscohs[n][\lbrack 0,p-1 \rbrack]
                                             & \defeq                              &
     \left\{\begin{array}{l}
-             \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+2][p](\overline{\deps}(\depscohs[n][0,..,p-1])).\, \\
-             \layer[n+1][p](\overline{\deps}(\depscohs[n][0,..,p-1])(d) \rightarrow                          \\
+             \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\, \\
+             \layer[n+1][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])(d) \rightarrow                          \\
              \layer[n][p](\fulldeps.\deps[n][\lbrack 0,p \rbrack])(\restrf[n][p]
-             (\depscohs[n][0,..,p-1])(d))
+             (\depscohs[n][\lbrack 0,p-1 \rbrack])(d))
            \end{array}\right.                                                                                                       \\
@@
     \multicolumn{3}{l}{
-      (\depscohs[n][0,..,p]:\depscohstype[n][0,..,p]) :
-    \restrltype[n][p] (\depscohs[n][0,..,p])}                                                                                                                                                                    \\
+      (\depscohs[n][\lbrack 0,p \rbrack]:\depscohstype[n][\lbrack 0,p \rbrack]) :
+    \restrltype[n][p] (\depscohs[n][\lbrack 0,p \rbrack])}                                                                                                                                                                    \\
     \restrl[n][p]                           &
-    \depscohs[n][0,..,p]                    & \defeq                              &
+    \depscohs[n][\lbrack 0,p \rbrack]       & \defeq                              &
     \lambda q\leq n.
-\lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][0,..,p-1])(d))(l \omega)} \\
-  \end{array}
-\end{equation*}
-
-By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n][0,..,0-1]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).
+\lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(l \omega)} \\
+  \end{array}
+\end{equation*}
+
+By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n][\lbrack 0,0-1 \rbrack]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).
 
@@
   \begin{array}{llcl}
-    \depscohttype[n][0,..,p-1]                                                               &                                                                               & \defeq                                                                            &
+    \depscohttype[n][\lbrack 0,p-1 \rbrack]                                                  &                                                                               & \defeq                                                                            &
     \left(\begin{array}{lll}

### 2025-12-07 paper/paper.tex
paper: corrections

@@
 \newcommandx{\depstype}[2][1,2]{\depstypep{}[][][][#1][#2][][]}
-\newcommandx{\fulldepstype}[2][1,2]{\depstypep{full}[][][][#1][][][]}
+\newcommandx{\fulldepstype}[1][1]{\depstypep{full}[][][][#1][][][]}
 \newcommandx{\depscohstype}[2][1,2]{\depstypep{cohs}[][][][#1][#2][][]}
@@
 
-Assuming $\framep[n][\lbrack 0,p \rbrack]$ for $p \leq n$ only requires to define the type of frames, which are just finite products of $\U$:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \frametype[n][\lbrack 0,p \rbrack] &  & :      & \U                                               \\
-    \frametype[n][]                    &  & \defeq & \unittype                                        \\
+Assuming $\framep[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ only requires to define the type of frames, which are just finite products of $\U$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \frametype[n][\lbrack 0,p-1 \rbrack] &  & :      & \U                                               \\
+    \frametype[n][\lbrack \rbrack]       &  & \defeq & \unittype                                        \\
     \frametype[n][\lbrack 0,p \rbrack]   &  & \defeq & \frametype[n+1][\lbrack 0,p-1 \rbrack] \times \U \\
@@
 
-The types $\paintingtype[n][\lbrack 0,p \rbrack]$ of $\painting[n][\lbrack 0,p \rbrack]$ for $p \leq n$
-are type families over frames, so $\framep[n][\lbrack 0,p \rbrack]$ needs to be assumed
-beforehand:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \paintingtype[n][\lbrack 0,p \rbrack] & (\framep[n][\lbrack 0,p \rbrack]:\frametype[n][\lbrack 0,p \rbrack]) & :      & \U                                                                                                                   \\
-    \paintingtype[n][]                    & \unitpoint                                                           & \defeq & \unittype                                                                                                            \\
+The types $\paintingtype[n][\lbrack 0,p-1 \rbrack]$ of $\painting[n][\lbrack 0,p \rbrack]$ for $p \leq n+1$ are type families over frames, so $\framep[n][\lbrack 0,p-1 \rbrack]$ needs to be assumed beforehand:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \paintingtype[n][\lbrack 0,p-1 \rbrack] & (\framep[n][\lbrack 0,p \rbrack]:\frametype[n][\lbrack 0,p-1 \rbrack]) & :      & \U                                                                                                                   \\
+    \paintingtype[n][\lbrack \rbrack]       & \unitpoint                                                             & \defeq & \unittype                                                                                                            \\
     \paintingtype[n][\lbrack 0,p \rbrack]   & (\framep[n][\lbrack 0,p \rbrack])                                      & \defeq & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack]) \times (\framep[n][p] \rightarrow \U) \\
@@
 mutually define the types $\restrftype[n][\lbrack 0,p-1 \rbrack]$ of frame
-restrictions together with $\framep[n+1][0,...p]$ as a function from
+restrictions together with $\framep[n+1][\lbrack 0,p-1 \rbrack]$ as a function from
 $\restrf[n][\lbrack 0,p-1 \rbrack]$, introducing also abbreviations for the types
@@
 
-From which we can deduce $\painting[n+1][\lbrack 0,p \rbrack]$ for $p \leq n+1$ by a second recursion, this time on $p$:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \painting[n+1][\lbrack 0,p \rbrack]   &
-    (\fulldeps[n]:\fulldepstype[n])       & :      & \paintingtype[n+1][\lbrack 0,p \rbrack](\framep[n+1][\lbrack 0,p \rbrack](\fulldeps.\deps[n-1][\lbrack 0,p \rbrack])) \\
-    \painting[n+1][\lbrack 0,0-1 \rbrack] &
+From which we can deduce $\painting[n+1][\lbrack 0,p-1 \rbrack]$ for $p \leq n+2$ by a second recursion, this time on $p$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \painting[n+1][\lbrack 0,p-1 \rbrack] &
+    (\fulldeps[n]:\fulldepstype[n])       & :      & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack])) \\
+    \painting[n+1][\lbrack \rbrack]       &
     \fulldeps[n]                          & \defeq & \unittype                                                                                                                 \\
@@
     (\fulldeps[n]:\fulldepstype[n])       & :      & \U                                                                \\
-    \restrptype[n][\lbrack 0,0-1 \rbrack]     & E      & \defeq                                                & \unittype \\
-    \restrptype[n][\lbrack 0,(p+1)-1 \rbrack] &
+    \restrptype[n][\lbrack \rbrack]       & E      & \defeq                                                & \unittype \\
+    \restrptype[n][\lbrack 0,p \rbrack]   &
     (\fulldeps[n])
@@
     \left(\begin{array}{lcl}
-              \fulldeps[n][\lbrack 0,n \rbrack] & : & \fulldepstype[n][\lbrack 0,n \rbrack]               \\
+              \fulldeps[n]                    & : & \fulldepstype[n]                                    \\
               \restrp[n][0,...p-1]            & : & \restrptype[n][\lbrack 0,p-1 \rbrack](\fulldeps[n]) \\
@@
     }                                                                                                                  n                                                                                                      \\
-    \cohftype[n][\lbrack 0,0-1 \rbrack]     &
+    \cohftype[n][\lbrack \rbrack]           &
     \left(\begin{array}{l}
@@
     \unittype                                                                                                                                                                                                                 \\
-    \cohftype[n][\lbrack 0,(p+1)-1 \rbrack] &
+    \cohftype[n][\lbrack 0,p \rbrack]       &
     \left(\begin{array}{l}
@@
 
-From which we can deduce $\restrp[n+1][\lbrack 0,p \rbrack]$ for $p \leq n+1$ again by a second recursion, this time on $p$:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \restrp[n+1][\lbrack 0,p \rbrack]       &
-    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \restrptype[n+1][\lbrack 0,p \rbrack](\fulldepscohs.\depscohs.\fulldeps[n])) \\
-    \restrp[n+1][\lbrack 0,0-1 \rbrack]     &
+From which we can deduce $\restrp[n+1][\lbrack 0,p-1 \rbrack]$ for $p \leq n+2$ again by a second recursion, this time on $p$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \restrp[n+1][\lbrack 0,p-1 \rbrack]     &
+    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs.\depscohs.\fulldeps[n])) \\
+    \restrp[n+1][\lbrack \rbrack]           &
     \fulldepscohs[n]                        & \defeq & \unittype                                                                      \\
@@
 
-Thanks to $\cohptype[n][\lbrack 0,p-1 \rbrack]$, we can mutually define $\cohf[n+1][\lbrack 0,p \rbrack]$ and $\cohttype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ from $\fulldepscohs[n][\lbrack 0,p-1 \rbrack]$, abbreviating this and the dependency in a $\coht[n][\lbrack 0,p-1 \rbrack]$ as $\depscohttype[n][\lbrack 0,p-1 \rbrack]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$.
+Thanks to $\cohptype[n][\lbrack 0,p-1 \rbrack]$, we can mutually define $\cohf[n+1][\lbrack 0,p \rbrack]$ and $\cohttype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ from $\fulldepscohs[n]$, abbreviating this and the dependency in a $\coht[n][\lbrack 0,p-1 \rbrack]$ as $\depscohttype[n][\lbrack 0,p-1 \rbrack]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$.
 It is also convenient to build $\depscohs[n+1][\lbrack 0,p \rbrack]$ from $\depscoht[n][\lbrack 0,p-1 \rbrack]$, so that we can now build $\framep[n+3][p]$.
@@
             \end{array}\right) & :                                                                             & \U                                                                                                                                                                                          \\
-    \cohttype[n][\lbrack 0,0-1 \rbrack]                                                      &
+    \cohttype[n][\lbrack \rbrack]                                                            &
     \left(\begin{array}{l}
@@
     \unittype                                                                                                                                                                                                                                                                                              \\
-    \cohttype[n][\lbrack 0,(p+1)-1 \rbrack]                                                  &
+    \cohttype[n][\lbrack 0,p \rbrack]                                                        &
     \left(\begin{array}{l}
@@
         \restrp[n][p][q][\epsilon](\overline{\fulldeps}(\depscoht))(\restrp[n+1][p][r][\omega]
-        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][\lbrack 0,n \rbrack])(d)(c)) = \\
+        (\fulldepscoht.\depscoht.\fulldepscohs[n+1])(d)(c)) =                    \\
         \restrp[n][p][r][\omega](\overline{\fulldeps}(\depscoht))(\restrp[n+1][p][q+1][\epsilon]
-        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][\lbrack 0,n \rbrack])(d)(c))   \\
-        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][\lbrack 0,n \rbrack])(d)(c))   \\
+        (\fulldepscoht.\depscoht.\fulldepscohs[n+1])(d)(c))                      \\
+        (\fulldepscoht.\depscoht.\fulldepscohs[n+1])(d)(c))                      \\
       \end{array}\right)                                                      \\
@@
 
-From which we can deduce $\cohp[n+1][\lbrack 0,p \rbrack]$ again by a second recursion, this time on $p$:
-
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
-    \cohp[n+1][\lbrack 0,p \rbrack]         &
-    (\fulldepscoht[n]:\fulldepscohttype[n]) & :      & \cohptype[n+1][\lbrack 0,p \rbrack](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
-    \cohp[n+1][\lbrack 0,0-1 \rbrack]       &
+From which we can deduce $\cohp[n+1][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ again by a second recursion, this time on $p$:
+
+\begin{equation*}
+  \fontsize{7.2}{9}\selectfont
+  \begin{array}{llcl}
+    \cohp[n+1][\lbrack 0,p-1 \rbrack]       &
+    (\fulldepscoht[n]:\fulldepscohttype[n]) & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
+    \cohp[n+1][\lbrack \rbrack]             &
     \fulldepscohs[n]                        & \defeq & \unittype                                                                        \\

### 2025-12-22 paper/paper.tex
paper, tab-frames: work on consistency, fixing errors

@@
 Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
-This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
+This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}\lbrack 0,0 \rbrack$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
 
@@
 Since $\restrf[n][p]$ is referring to $\framep[n][p]$ and $\framep[n-1][p]$, and $\cohf[n][p]$ is referring to $\restrf[n][p]$ and $\restrf[n-1][p]$, thus also to $\framep[n][p]$, $\framep[n-1][p]$ and $\framep[n-2][p]$, we built all of these 6 components at the same time.
-But equations were also needed to state the properties of $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ so that we were building by induction on $n+p$ (that is on $n$, using the convention of \cite{hr25}), for any $D:\Xto{m}{n}$, the following block of information:
+But equations were also needed to state the properties of $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ so that we were building by induction on $n$, for any $D:\Xto{m}{n}$, the following block of information:
 
@@
   \painting[n][p] & : \framep[n][p] \rightarrow \U                                                                              & \mbox{for all $p\leq n$} \\
-  \restrf[n][p]   & : \Pi q \leq n+p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]                               & \mbox{for all $p\leq n$} \\
-  \restrp[n][p]   & : \Pi q \leq n+p.\, \Pi \epsilon.\, \Pi d:\framep[n+1][p].\,                                                                           \\
+  \restrf[n][p]   & : \Pi q \leq n-p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]                               & \mbox{for all $p\leq n$} \\
+  \restrp[n][p]   & : \Pi q \leq n-p.\, \Pi \epsilon.\, \Pi d:\framep[n+1][p].\,                                                                           \\
                   & \;\;\;\;\painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d))                                  & \mbox{for all $p\leq n$} \\
@@
     \framep[n][\lbrack 0,p-1 \rbrack] &
-    \restrf[n][\lbrack 0,p-1 \rbrack] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[\lbrack 0,p-1 \rbrack]$}"', near start, shift right=2mm, hook']\\
+    \restrf[n][\lbrack 0,p-1 \rbrack] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[0,p-1]$}"', near start, shift right=2mm, hook']\\
   \end{tikzcd}
@@
   \painting[n][p]           & : \framep[n][p] \rightarrow \U                     & \mbox{for all $p\leq n$} \\
-  \restrf[n][p]             & : \Pi q \leq n+p.\, \framep[n+1][p]
+  \restrf[n][p]             & : \Pi q \leq n-p.\, Pi \epsilon.\, \framep[n+1][p]
   \left(\begin{array}{l}
@@
     \frametype[n][\lbrack 0,p-1 \rbrack] &  & :      & \U                                               \\
-    \frametype[n][\lbrack \rbrack]       &  & \defeq & \unittype                                        \\
+    \frametype[n]                        &  & \defeq & \unittype                                        \\
     \frametype[n][\lbrack 0,p \rbrack]   &  & \defeq & \frametype[n+1][\lbrack 0,p-1 \rbrack] \times \U \\
@@
     \paintingtype[n][\lbrack 0,p-1 \rbrack] & (\framep[n][\lbrack 0,p \rbrack]:\frametype[n][\lbrack 0,p-1 \rbrack]) & :      & \U                                                                                                                   \\
-    \paintingtype[n][\lbrack \rbrack]       & \unitpoint                                                             & \defeq & \unittype                                                                                                            \\
+    \paintingtype[n]                        & \unitpoint                                                             & \defeq & \unittype                                                                                                            \\
     \paintingtype[n][\lbrack 0,p \rbrack]   & (\framep[n][\lbrack 0,p \rbrack])                                      & \defeq & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack]) \times (\framep[n][p] \rightarrow \U) \\
@@
             \end{array}\right) : \U} \\
-    \restrftype[n][\lbrack 0,0-1 \rbrack]     &
+    \restrftype[n]                        &
     \left(\begin{array}{l}
@@
     \unittype                                                                                                            \\
-    \restrftype[n][\lbrack 0,(p+1)-1 \rbrack] &
+    \restrftype[n][\lbrack 0,p \rbrack]   &
     \left(\begin{array}{l}
@@
               \end{array}\right).         \\
-      \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]
+      \Pi q \leq n-p.\,\Pi \epsilon.\,\framep[n+1][p]
       \left(\begin{array}{l}
@@
                                           & \defeq &
-    d \mapsto \Pi\omega.\,\painting[n][p](\deps.\restrf[n][p][0][\omega](d))                                             \\
+    d \mapsto \Pi\epsilon.\,\painting[n][p](\deps.\restrf[n][p][0][\epsilon](d))                                         \\
   \end{array}
@@
 projections of a $\deps$. Also, by abuse of notation, we write $\unitpoint$ for
-the only inhabitant of $\depstype[n][\lbrack 0,0-1 \rbrack]$.
+the only inhabitant of $\depstype[n]$.
 
@@
 
-We can now formally define $\painting[n+1][p]$ by recursion on $n+1-p$:
+We can now formally define $\painting[n+1][p]$ for $p \leq n+1$ by recursion on $n-p$:
 \begin{equation*}
@@
     \painting[n+1][p]               &
-    (\fulldeps[n]:\fulldepstype[n])                                       \\
+    (\fulldeps[n]:\fulldepstype[n]) & :      & \paintingtype[n+1][p]      \\
     \painting[n+1][n+1]             &
     \fulldeps[n]                    & \defeq & \fulldeps.E                \\
-    \painting[n+1][p](p\leq n) &
+    \painting[n+1][p \leq n]        &
     \fulldeps[n]                    & \defeq & d \mapsto
@@
     (\fulldeps[n]:\fulldepstype[n])       & :      & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack])) \\
-    \painting[n+1][\lbrack \rbrack]       &
+    \painting[n+1]                        &
     \fulldeps[n]                          & \defeq & \unittype                                                                                                                 \\
@@
     (\fulldeps[n]:\fulldepstype[n])       & :      & \U                                                                \\
-    \restrptype[n][\lbrack \rbrack]       & E      & \defeq                                                & \unittype \\
+    \restrptype[n]                        & E      & \defeq                                                & \unittype \\
     \restrptype[n][\lbrack 0,p \rbrack]   &
@@
     \begin{array}{l}
-        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack]). \\
+        \Pi q \leq n-p.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack]). \\
         \painting[n+1][p]
@@
     }                                                                                                                  n                                                                                                         \\
-    \cohftype[n][\lbrack \rbrack]           &
+    \cohftype[n]                            &
     \left(\begin{array}{l}
@@
               \end{array}\right).                  \\
-             \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p]
+             \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p]
              (\overline{\deps}\left(\begin{array}{l}
@@
     \left\{\begin{array}{l}
-             \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\, \\
+             \Pi q \leq n-p. \Pi \epsilon. \Pi d: \framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\, \\
              \layer[n+1][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])(d) \rightarrow                            \\
@@
     \depscohs[n][\lbrack 0,p \rbrack]       & \defeq                              &
-    \lambda q\leq n.
+    \lambda q \leq n-p.
 \lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(l \omega)} \\
@@
 
-By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n][\lbrack 0,0-1 \rbrack]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).
+By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).
 
@@
     \begin{array}{l}
-        \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n+2][p]
+        \Pi q \leq n-p. \Pi \epsilon. \Pi d:\framep[n+2][p]
         (\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])). \\
@@
     \restrp[n+1][n+1]                       &
-    (\fulldepscohs[n])                      & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
-    \restrp[n+1][p](p\leq n)                &
-    (\fulldepscohs[n])                      & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
+    (\fulldepscohs[n])                      & \defeq & \lambda q \leq n-p.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
+    \restrp[n+1][p \leq n]                  &
+    (\fulldepscohs[n])                      & \defeq & \lambda q \leq n-p.\lambda \epsilon. \lambda d. \lambda (l,c).
     \left(\begin{array}{l}
@@
     (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs.\depscohs.\fulldeps[n])) \\
-    \restrp[n+1][\lbrack \rbrack]           &
+    \restrp[n+1]                            &
     \fulldepscohs[n]                        & \defeq & \unittype                                                                      \\
@@
     \cohptype[n][\lbrack 0,p-1 \rbrack] & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                                           \\
-    \cohptype[n][\lbrack 0,0-1 \rbrack]     & \unitpoint                              & \defeq & \unittype                                                    \\
-    \cohptype[n][\lbrack 0,(p+1)-1 \rbrack] & (\fulldepscohs[n])                      & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
+    \cohptype[n]                        & \unitpoint                              & \defeq & \unittype                                                    \\
+    \cohptype[n][\lbrack 0,p \rbrack]   & (\fulldepscohs[n])                      & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
                                         &                                         &        & \;\;\;\;\left\{
     \begin{array}{l}
-      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
+      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
       \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf[n+1][p](d))(\restrp[n+1][p][r][\omega]
@@
             \end{array}\right) & :                                                                             & \U                                                                                                                                                                                          \\
-    \cohttype[n][\lbrack \rbrack]                                                            &
+    \cohttype[n]                                                                             &
     \left(\begin{array}{l}
@@
                 \end{array}\right).                                    \\
-              \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.\, \\
+              \Pi q \leq n - p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.\, \\
               \fulldepscohs.\depscohs.\cohf[n][p][r][p][\omega][\theta] \circ \cohf[n+1][p][q+1][p][\epsilon][\theta]
@@
     \begin{array}{l}
-      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                             \\
+      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                          \\
       \Pi d.\Pi l. \overrightarrow{\cohf[n][p][r+1][q+1][\epsilon][\omega]}{(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} = \\
@@
 
-The last key construction we need is $\cohp[n+1][p]$, which is by recursion on $n-p$:
+The last key construction we need is $\cohp[n+1][p]$ for $p \leq n+1$, which is by recursion on $n-p$:
 
@@
     (\fulldepscoht[n]:\fulldepscohttype[n]) & :      &
-    \left(
-    \begin{array}{l}
-        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d.\,\Pi c.\, \\
-        \restrp[n][p][q][\epsilon](\overline{\fulldeps}(\depscoht))(\restrp[n+1][p][r][\omega]
-        (\fulldepscoht.\depscoht.\fulldepscohs[n+1])(d)(c)) =                    \\
-        \restrp[n][p][r][\omega](\overline{\fulldeps}(\depscoht))(\restrp[n+1][p][q+1][\epsilon]
-        (\fulldepscoht.\depscoht.\fulldepscohs[n+1])(d)(c))                      \\
-        (\fulldepscoht.\depscoht.\fulldepscohs[n+1])(d)(c))                      \\
-      \end{array}\right)                                                      \\
-    \cohp[n+1][n]                           &
+    \cohptype[n+1][p](\overline{\fulldepscohs}(\fulldepscoht[n]))                                                                                             \\
+    \cohp[n+1][n+1]                         &
     (\fulldepscoht[n])
-                                            & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c). l\epsilon \\
-    \cohp[n+1][p](p<n)                      &
+                                            & \defeq & \lambda q \leq n-p.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c). l\epsilon \\
+    \cohp[n+1][p \leq n]                    &
     (\fulldepscoht[n])
-                                            & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c).
+                                            & \defeq & \lambda q \leq n-p.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c).
     \left(\begin{array}{l}
@@
 
-From which we can deduce $\cohp[n+1][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ again by a second recursion, this time on $p$:
+From which we can deduce $\cohp[n+1][\lbrack 0,p-1 \rbrack]$ for $p \leq n+2$ again by a second recursion, this time on $p$:
 
@@
     (\fulldepscoht[n]:\fulldepscohttype[n]) & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
-    \cohp[n+1][\lbrack \rbrack]             &
+    \cohp[n+1]                              &
     \fulldepscohs[n]                        & \defeq & \unittype                                                                        \\
@@
 \begin{align*}
-  \rotatebox[origin=c]{90}{\depscohs[n][\lbrack 0,n-1 \rbrack]}\begin{cases}
-                                                                 \rotatebox[origin=c]{90}{\deps[n][\lbrack 0,n-1 \rbrack]}\begin{cases}
+  \rotatebox[origin=c]{90}{\depscohs[n][\lbrack 0,n-1 \rbrack]}
+  \begin{cases}
+    \rotatebox[origin=c]{90}{\deps[n][\lbrack 0,n-1 \rbrack]}
+    \begin{cases}
       \framep[n][\lbrack 0,n-1 \rbrack]   : \frametype[n][\lbrack 0,n-1 \rbrack]                                       \\
@@
       \restrf[n][\lbrack 0,n-1 \rbrack]   : \restrftype[n][\lbrack 0,n-1 \rbrack]
-                                                               \left(\begin{array}{l}
+      \left(
+      \begin{array}{l}
           \framep[n][\lbrack 0,n-1 \rbrack]   \\
@@
     \restrp[n][\lbrack 0,n-1 \rbrack](E) : \restrptype[n][\lbrack 0,n-1 \rbrack]
-                                                                 \left(\begin{array}{l}
+    \left(
+    \begin{array}{l}
         \deps[n][\lbrack 0,n-1 \rbrack] \\
@@
     \cohf[n][\lbrack 0,n-1 \rbrack](E)   : \cohftype[n][\lbrack 0,n-1 \rbrack]
-                                                                 \left(\begin{array}{l}
+    \left(
+    \begin{array}{l}
         \deps[n][\lbrack 0,n-1 \rbrack]                 \\
@@
   \item $\cohf[n+1][\lbrack 0,n \rbrack]$ assuming $E'$ comes from $\depscoht[n][\lbrack 0,n-1 \rbrack]$ which holds by assumptions (additionally using the assumption of $\cohp[n][\lbrack 0,n-1 \rbrack]$ and proving $\coht[n][\lbrack 0,n-1 \rbrack]$ by uniqueness of identity proofs)
-  \item $\cohp[n+1][\lbrack 0,n \rbrack]$ assuming $E'$ and $E'': \framep[n+3][n+2](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n-1 \rbrack]))) \rightarrow \U$ comes from $\fulldepscoht[n][\lbrack 0,n-1 \rbrack]$ which holds by assumptions (additionally using $E''$)
+  \item $\cohp[n+1][\lbrack 0,n \rbrack]$ assuming $E'$ and $E'': \framep[n+3][n+2](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n-1 \rbrack]))) \rightarrow \U$ comes from $\fulldepscoht[n]$ which holds by assumptions (additionally using $E''$)
 \end{itemize}

### 2025-12-22 paper/paper.tex
paper: use macros to clean up out-of-line args
paper: simplify to singular coht

@@
 \newcommandx{\restrptype}[2][1,2]{\restr{PAINTING}[][][][#1][#2][][]}
-\newcommandx{\cohftype}[2][1,2]{\coh{FRAME}[][][][][][#1,#2][][]}
-\newcommandx{\cohltype}[2][1,2]{\coh{LAYER}[][][][][][#1,#2][][]}
-\newcommandx{\cohptype}[2][1,2]{\coh{PAINTING}[][][][][][#1,#2][][]}
-\newcommandx{\cohttype}[2][1,2]{\cohtwo{FRAME}[][][][][][#1,#2][][]}
+\newcommandx{\cohftype}[2][1,2]{\coh{FRAME}[][][][][][#1][#2][]}
+\newcommandx{\cohltype}[2][1,2]{\coh{LAYER}[][][][][][#1][#2][]}
+\newcommandx{\cohptype}[2][1,2]{\coh{PAINTING}[][][][][][#1][#2][]}
+\newcommandx{\cohttype}[2][1,2]{\cohtwo{FRAME}[][][][][][#1][#2][]}
 
@@
 
-\newcommandx{\coht}[6][1,2,3,4,5,6]{\cohtwo{frame}[][#3][#4][#5][#6][#1,#2][][]}
+\newcommandx{\coht}[7][1,2,3,4,5,6,7]{\cohtwo{frame}[#3][#4][#5][#6][#7][#1][#2][]}
 
@@
   \restrf[n-1][p]    & : \Pi q.\, \Pi \omega.\, \framep[n-1][p] \rightarrow \framep[n-2][p]                                                 & \mbox{for all $p\leq n-1$} \\
-  \cohf[n][p]        & : \Pi qr\epsilon\omega.\, \restrf[n-1][p][\epsilon][q] \circ \restrf[n][p][\omega][r] =                                                           \\
-                     & \;\;\;\;\restrf[n-1][p][\omega][r] \circ \restrf[n][p][\epsilon][q+1]                                                & \mbox{for all $p\leq n$}   \\
+  \cohf[n][p]        & : \Pi qr\epsilon\omega.\, \restrf[n-1][p][q][\epsilon] \circ \restrf[n][p][\omega][r] =                                                           \\
+                     & \;\;\;\;\restrf[n-1][p][r][\omega] \circ \restrf[n][p][\epsilon][q+1]                                                & \mbox{for all $p\leq n$}   \\
   \mathsf{hypF0}     & : \framep[n][0]         = \unitpoint
@@
                   & \;\;\;\;\painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d))                                  & \mbox{for all $p\leq n$} \\
-  \cohf[n][p]     & : \Pi qr\epsilon\omega.\, \restrf[n][p][\epsilon][q] \circ \restrf[n+1][p][\omega][r] =                                                \\
-                  & \;\;\;\;\restrf[n][p][\omega][r] \circ \restrf[n+1][p][\epsilon][q+1]                                       & \mbox{for all $p\leq n$} \\
+  \cohf[n][p]     & : \Pi qr\epsilon\omega.\, \restrf[n][p][q][\epsilon] \circ \restrf[n+1][p][\omega][r] =                                                \\
+                  & \;\;\;\;\restrf[n][p][\omega][r] \circ \restrf[n+1][p][q+1][\epsilon]                                       & \mbox{for all $p\leq n$} \\
   \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,                                                                                        \\
@@
     \left\{\begin{array}{l}
-             \Sigma \cohf[n][\lbrack 0,p-1 \rbrack]
+             \Sigma \cohf[n][\lbrack 0,p-1 \rbrack][q][r][\epsilon][\omega]
              :\cohftype[n][\lbrack 0,p-1 \rbrack]
@@
               \end{array}\right).                  \\
-             \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p]
+             \Pi d:\framep[n+2][p]
              (\overline{\deps}\left(\begin{array}{l}
@@
     \restrltype[n][p] (\depscohs[n][\lbrack 0,p \rbrack])}                                                                                                                                              \\
-    \restrl[n][p]                           &
+    \restrl[n][p][q][\epsilon]              &
     \depscohs[n][\lbrack 0,p \rbrack]       & \defeq                              &
-    \lambda q \leq n-p.
-\lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(l \omega)} \\
+    \lambda d.\lambda l.\lambda \omega\overrightarrow{\cohf[n][p][q][0][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(l_\omega)} \\
   \end{array}
@@
   \begin{array}{llcl}
-    \restrp[n+1][p]                         &
+    \restrp[n+1][p][q][\epsilon]            &
     (\fulldepscohs[n]:\fulldepscohstype[n]) & :      &
@@
     \begin{array}{l}
-        \Pi q \leq n-p. \Pi \epsilon. \Pi d:\framep[n+2][p]
+        \Pi d:\framep[n+2][p]
         (\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])). \\
@@
         (\restrf[n+1][p](\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])(d))\end{array}\right)                        \\
-    \restrp[n+1][n+1]                       &
-    (\fulldepscohs[n])                      & \defeq & \lambda q \leq n-p.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
-    \restrp[n+1][p \leq n]                  &
-    (\fulldepscohs[n])                      & \defeq & \lambda q \leq n-p.\lambda \epsilon. \lambda d. \lambda (l,c).
+    \restrp[n+1][n+1][q][\epsilon]          &
+    (\fulldepscohs[n])                      & \defeq & \lambda d. \lambda (l,c). l\epsilon   \\
+    \restrp[n+1][p \leq n][q][\epsilon]     &
+    (\fulldepscohs[n])                      & \defeq & \lambda d. \lambda (l,c).
     \left(\begin{array}{l}
@@
 
-\begin{align*}
+\begin{equation*}
   \fontsize{7.2}{9}\selectfont
@@
               \cohp[n][0,...p-1] & : & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \\
-              \coht[n][\lbrack 0,p-1 \rbrack] & : & \cohttype[n][\lbrack 0,p-1 \rbrack]
-              \left(\begin{array}{l}
-                  \fulldepscohs[n]                \\
-                  \cohp[n][\lbrack 0,p-1 \rbrack] \\
-                \end{array}\right)                                                       \\
-            \end{array}\right)                                                                                                                                                                                                    \\
+            \end{array}
+    \right)                                                                                                                                                                                                                                                                                     \\
     \overline{\depscohs}                                                          & (\depscoht[n][\lbrack 0,p-1 \rbrack]:\depscohttype[n][\lbrack 0,p-1 \rbrack]) & :                                                                                 & \depscohstype[n+1][\lbrack 0,p \rbrack] \\
@@
             \end{array}\right)                                                                                                                                                                                                                    \\
-    \cohttype[n][\lbrack 0,p-1 \rbrack]                                                      &
-    \left(\begin{array}{l}
-              \fulldepscohs[n]:\fulldepscohstype[n]                                                 \\
-              \cohp[n][\lbrack 0,p-1 \rbrack]:\cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \\
-            \end{array}\right) & :                                                                             & \U                                                                                                                                                                                          \\
-    \cohttype[n]                                                                             &
-    \left(\begin{array}{l}
-              (E,E')     \\
-              \unitpoint \\
-            \end{array}\right)                                                                   & \defeq                                                                        &
-    \unittype                                                                                                                                                                                                                                                                                              \\
-    \cohttype[n][\lbrack 0,p \rbrack]                                                        &
-    \left(\begin{array}{l}
-              \fulldepscohs[n]              \\
-              \cohp[n][\lbrack 0,p \rbrack] \\
-            \end{array}\right)                                                         & \defeq                                                                        &
-    \left(\begin{array}{l}
-              \Sigma \coht[n][\lbrack 0,p-1 \rbrack]
-              :\cohttype[n][\lbrack 0,p-1 \rbrack]
-              \left(\begin{array}{l}
-                  \fulldepscohs[n+1]                \\
-                  \cohp[n+1][\lbrack 0,p-1 \rbrack] \\
-                \end{array}\right).                                    \\
-              \Pi q \leq n - p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.\, \\
-              \fulldepscohs.\depscohs.\cohf[n][p][r][p][\omega][\theta] \circ \cohf[n+1][p][q+1][p][\epsilon][\theta]
+    \cohttype[n][p]                                                               &
+    \fulldepscohs[n]                                                              & \defeq                                                                        &
+    \left(\begin{array}{l}
+              \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.\, \\
+              \fulldepscohs.\depscohs.\cohf[n][p][r][0][\omega][\theta] \circ \cohf[n+1][p][q+1][0][\epsilon][\theta]
               (\fulldepscoht[n])
@@
               (\fulldepscoht[n+1])
-              \circ \fulldepscohs.\depscohs.\cohf[n][p][q][p][\epsilon][\theta]
-              \circ \cohf[n+1][p][r][p][\omega][\theta]
+              \circ \fulldepscohs.\depscohs.\cohf[n][p][q][0][\epsilon][\theta]
+              \circ \cohf[n+1][p][r][0][\omega][\theta]
               (\fulldepscoht[n])                                                       \\
             \end{array}\right)                                                                                                                                                                                \\
+    \coht[n][p]                                                                   &
+    \fulldepscohs[n]                                                              & :                                                                             & \cohttype[n][p](\fulldepscohs[n])                                                                                           \\
+    \coht[n][p]                                                                   &
+    \fulldepscohs[n]                                                              & \defeq                                                                        & \UIP                                                                                                                        \\
+
     \cohl[n][p]                                                                   &
@@
     \end{array}                                                                                                                                                          \\
-    \cohl[n][p][q][\epsilon][r][\omega]                                                      &
+    \cohl[n][p][q][r][\epsilon][\omega]                                           &
     (\depscoht[n][\lbrack 0,p-1 \rbrack])                                         & \defeq                                                                        &
@@
 \lambda \theta.
-(\cohp[n][p][q][\epsilon][r][\omega](l))  ...
-\\
-  \end{array}
-\end{align*}
-
+\overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])}{(\cohp[n][p][q][r][\epsilon][\omega](l_\theta))}                                                                                                                       \\
+  \end{array}
+\end{equation*}
 We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$:
@@
     \cohptype[n+1][p](\overline{\fulldepscohs}(\fulldepscoht[n]))                                       \\
-    \cohp[n+1][n+1]                         &
+    \cohp[n+1][n+1][q][r][\epsilon][\omega]      &
     (\fulldepscoht[n])
-                                            & \defeq & \lambda q \leq n-p.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c). l\epsilon \\
-    \cohp[n+1][p \leq n]                    &
+                                                 & \defeq & \lambda d. \lambda (l,c). l\epsilon         \\
+    \cohp[n+1][p \leq n][q][r][\epsilon][\omega] &
     (\fulldepscoht[n])
-                                            & \defeq & \lambda q \leq n-p.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c).
+                                                 & \defeq & \lambda d. \lambda (l,c).
     \left(\begin{array}{l}

### 2025-12-22 paper/paper.tex
paper: progress on completing construction (now flat)
paper: accumulate deps in completion of constr
paper: polish completion
paper: fix minor errors in completion
paper: work some more on conclusion

@@
               \cohf[n+1][p][q+1][r+1][\epsilon][\omega]
-              (\fulldepscoht[n+1])
+              (\fulldepscoht[n])
               \circ \fulldepscohs.\depscohs.\cohf[n][p][q][0][\epsilon][\theta]
@@
     \fulldepscohs[n]                                                              & :                                                                             & \cohttype[n][p](\fulldepscohs[n])                                                                                           \\
-    \coht[n][p]                                                                   &
+    \coht[n][p][q][r][\epsilon][\omega][\theta]                                   &
     \fulldepscohs[n]                                                              & \defeq                                                                        & \UIP                                                                                                                        \\
@@
 \lambda \theta.
-\overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])}{(\cohp[n][p][q][r][\epsilon][\omega](l_\theta))}                                                                                                                       \\
+\overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\depscoht.\fulldepscohs[n])}{(\depscoht.\cohp[n][p][q][r][\epsilon][\omega](l_\theta))}                                                                                                   \\
   \end{array}
@@
 \begin{align*}
-  \rotatebox[origin=c]{90}{\depscohs[n][\lbrack 0,n-1 \rbrack]}
-  \begin{cases}
-    \rotatebox[origin=c]{90}{\deps[n][\lbrack 0,n-1 \rbrack]}
-    \begin{cases}
-      \framep[n][\lbrack 0,n-1 \rbrack]   : \frametype[n][\lbrack 0,n-1 \rbrack]                                       \\
-      \painting[n][\lbrack 0,n-1 \rbrack] : \paintingtype[n][\lbrack 0,n-1 \rbrack](\framep[n][\lbrack 0,n-1 \rbrack]) \\
-      \restrf[n][\lbrack 0,n-1 \rbrack]   : \restrftype[n][\lbrack 0,n-1 \rbrack]
+  \framep[n][\lbrack 0,n \rbrack]                                                                      & :      & \frametype[n][\lbrack 0,n-1 \rbrack]                                       \\
+  \painting[n][\lbrack 0,n \rbrack]                                                                    & :      & \paintingtype[n][\lbrack 0,n-1 \rbrack](\framep[n][\lbrack 0,n-1 \rbrack]) \\
+  \restrf[n][\lbrack 0,n \rbrack]                                                                      & :      & \restrftype[n][\lbrack 0,n-1 \rbrack]
   \left(
   \begin{array}{l}
-          \framep[n][\lbrack 0,n-1 \rbrack]   \\
-          \painting[n][\lbrack 0,n-1 \rbrack] \\
-        \end{array}\right)
-    \end{cases} \\
-    E:\framep[n+1][n]
-    (\deps[n][\lbrack 0,n-1 \rbrack])\rightarrow \U                                                                  \\
-    \restrp[n][\lbrack 0,n-1 \rbrack](E) : \restrptype[n][\lbrack 0,n-1 \rbrack]
+      \framep[n][\lbrack 0,n \rbrack]   \\
+      \painting[n][\lbrack 0,n \rbrack] \\
+    \end{array}\right)                                                                                                                                                          \\
+  \deps[n][\lbrack 0,n \rbrack]                                                                        & \defeq &
   \left(
   \begin{array}{l}
-        \deps[n][\lbrack 0,n-1 \rbrack] \\
-        E                               \\
-      \end{array}\right)                                                                                  \\
-    \cohf[n][\lbrack 0,n-1 \rbrack](E)   : \cohftype[n][\lbrack 0,n-1 \rbrack]
+      \framep[n][\lbrack 0,n \rbrack]   \\
+      \painting[n][\lbrack 0,n \rbrack] \\
+      \restrf[n][\lbrack 0,n \rbrack]   \\
+    \end{array}\right)                                                                                                                                                          \\
+  \fulldeps[n](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U)                      & \defeq &
   \left(
   \begin{array}{l}
-        \deps[n][\lbrack 0,n-1 \rbrack]                 \\
-        E:\framep[n+1][n]
-        (\deps[n][\lbrack 0,n-1 \rbrack])\rightarrow \U \\
-        \restrp[n][\lbrack 0,n-1 \rbrack]               \\
-      \end{array}\right)
-  \end{cases} \\
-  E': \framep[n+2][n+1](\overline{\deps}
-  (\depscohs[n][\lbrack 0,n-1 \rbrack])\rightarrow \U                                                                \\
-  \cohp[n][\lbrack 0,n-1 \rbrack]
-  \left(\begin{array}{l}
+      \deps[n][\lbrack 0,n \rbrack] \\
       E                             \\
+    \end{array}\right)                                                                                                                                                              \\
+  \restrp[n][\lbrack 0,n \rbrack](E)                                                                   & :      & \restrptype[n][\lbrack 0,n \rbrack]
+  (\fulldeps[n](E))                                                                                                                                                                          \\
+  \cohf[n][\lbrack 0,n \rbrack](E)                                                                     & :      & \cohftype[n][\lbrack 0,n \rbrack]
+  \left(
+  \begin{array}{l}
+      \fulldeps[n](E)                    \\
+      \restrp[n][\lbrack 0,n \rbrack](E) \\
+    \end{array}\right)                                                                                                                                                         \\
+  \depscohs[n][\lbrack 0,n \rbrack](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U) & \defeq &
+  \left(
+  \begin{array}{l}
+      \fulldeps[n](E)                    \\
+      \restrp[n][\lbrack 0,n \rbrack](E) \\
+      \cohf[n][\lbrack 0,n \rbrack](E)   \\
+    \end{array}\right)                                                                                                                                                         \\
+  \fulldepscohs[n]
+  \left(\begin{array}{l}
+            E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U                        \\
+            E': \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack]))\rightarrow \U \\
+          \end{array}\right)          & \defeq &
+  \left(
+  \begin{array}{l}
+      \depscohs[n][\lbrack 0,n \rbrack](E) \\
       E'                                   \\
-          \end{array}\right)
-  : \cohptype[n][\lbrack 0,n-1 \rbrack]
-  \left(\begin{array}{l}
-            \depscohs[n][\lbrack 0,n-1 \rbrack] \\
-            E'                                  \\
-          \end{array}\right)                                                                          \\
+    \end{array}\right)                                                                                                                                                       \\
+  \cohp[n][\lbrack 0,n-1 \rbrack](E)(E')                                                               & :      & \cohptype[n][\lbrack 0,n \rbrack]
+  (\fulldepscohs[n](E)(E'))                                                                                                                                                                  \\
 \end{align*}
@@
 Indeed, to build this structure at level $n+1$, from level $n$, it is
-enough to assume $E:\framep[n+1][n](\deps[n]) \rightarrow \U$ (where
-$\deps[n]$ come from the assumptions at level $n$) and to build the
-following:
+enough to assume $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$ (where $\deps[n][\lbrack 0,n \rbrack]$ come from the assumptions at level $n$) and to build the following:
 \begin{itemize}
-  \item $\framep[n+1][\lbrack 0,n \rbrack]$ comes from $\deps[n]$ which holds by assumptions (using $\framep[n][\lbrack 0,n-1 \rbrack]$, $\painting[n][\lbrack 0,n-1 \rbrack]$ and $\restrf[n][\lbrack 0,n-1 \rbrack]$)
-  \item $\painting[n+1][\lbrack 0,n \rbrack]$ comes from $\fulldeps[n]$ which holds by assumptions (also using $E$)
-  \item $\restrf[n+1][\lbrack 0,n \rbrack]$ comes from $\depscohs[n][\lbrack 0,n-1 \rbrack]$ which holds by assumptions (additionally using the assumptions of $\restrp[n][\lbrack 0,n-1 \rbrack]$ and $\cohf[n][\lbrack 0,n-1 \rbrack]$)
-  \item $\restrp[n+1][\lbrack 0,n \rbrack]$ assuming $E':\framep[n+2][n+1](\overline{\deps}(\depscohs[n][\lbrack 0,n-1 \rbrack])) \rightarrow \U$ comes from $\fulldepscohs[n]$ which holds by assumptions (additionally using $E'$)
-  \item $\cohf[n+1][\lbrack 0,n \rbrack]$ assuming $E'$ comes from $\depscoht[n][\lbrack 0,n-1 \rbrack]$ which holds by assumptions (additionally using the assumption of $\cohp[n][\lbrack 0,n-1 \rbrack]$ and proving $\coht[n][\lbrack 0,n-1 \rbrack]$ by uniqueness of identity proofs)
-  \item $\cohp[n+1][\lbrack 0,n \rbrack]$ assuming $E'$ and $E'': \framep[n+3][n+2](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n-1 \rbrack]))) \rightarrow \U$ comes from $\fulldepscoht[n]$ which holds by assumptions (additionally using $E''$)
+  \item $\framep[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\deps[n][\lbrack 0,n \rbrack]$.
+  \item $\painting[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\fulldeps[n](E)$.
+  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack]$.
+  \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$.
+  \item $\depscoht[n][\lbrack 0,n+1 \rbrack](E)(E')$ comes from $\fulldepscohs[n](E)(E')$ and $\restrp[n][\lbrack 0,n \rbrack](E)$.
+  \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$.
+  \item $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, comes from $\depscoht[n](E)(E')$, $\cohp[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
+  \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$.
 \end{itemize}
 
-Therefore, assuming a construction of $\framep[n][n-1]$ from
-$D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n]$ from $D$
-extended with some $E:\framep[n+1][n](\deps[n]) \rightarrow \U$. This
-is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus
-$\Xp{m}$, by starting with an empty $D$.
+Therefore, assuming a construction of $\framep[n][n]$ from $D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n+1]$ from $D$ extended with some $E:\framep[n+1][n+1](\deps[n+1][\lbrack 0,n+1 \rbrack]) \rightarrow \U$.
+This is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus $\Xp{m}$, by starting with an empty $D$.
 

### 2025-12-22 paper/paper.tex
paper: fix minor errors in conclusion
paper: fix typesetting a pi
A few mmore typos

@@
   \painting[n][p]           & : \framep[n][p] \rightarrow \U                      & \mbox{for all $p\leq n$} \\
-  \restrf[n][p]             & : \Pi q \leq n-p.\, Pi \epsilon.\, \framep[n+1][p]
+  \restrf[n][p]             & : \Pi q \leq n-p.\, \Pi \epsilon.\, \framep[n+1][p]
   \left(\begin{array}{l}
@@
 \begin{align*}
-  \framep[n][\lbrack 0,n \rbrack]                                                                      & :      & \frametype[n][\lbrack 0,n-1 \rbrack]                                       \\
-  \painting[n][\lbrack 0,n \rbrack]                                                                    & :      & \paintingtype[n][\lbrack 0,n-1 \rbrack](\framep[n][\lbrack 0,n-1 \rbrack]) \\
-  \restrf[n][\lbrack 0,n \rbrack]                                                                      & :      & \restrftype[n][\lbrack 0,n-1 \rbrack]
+  \framep[n][\lbrack 0,n \rbrack]                                                                      & :      & \frametype[n][\lbrack 0,n \rbrack]                                       \\
+  \painting[n][\lbrack 0,n \rbrack]                                                                    & :      & \paintingtype[n][\lbrack 0,n \rbrack](\framep[n][\lbrack 0,n \rbrack]) \\
+  \restrf[n][\lbrack 0,n \rbrack]                                                                      & :      & \restrftype[n][\lbrack 0,n \rbrack]
   \left(
@@
             E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U                           \\
-            E': \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack]))\rightarrow \U \\
+            E': \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack](E)))\rightarrow \U \\
           \end{array}\right)       & \defeq &
@@
     \end{array}\right)                                                                                                                                                       \\
-  \cohp[n][\lbrack 0,n-1 \rbrack](E)(E')                                                               & :      & \cohptype[n][\lbrack 0,n \rbrack]
+  \cohp[n][\lbrack 0,n \rbrack](E)(E')                                                               & :      & \cohptype[n][\lbrack 0,n \rbrack]
   (\fulldepscohs[n](E)(E'))                                                                                                                                                                  \\
@@
   \item $\painting[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\fulldeps[n](E)$.
-  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack]$.
+  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack](E)$.
   \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$.
-  \item $\depscoht[n][\lbrack 0,n+1 \rbrack](E)(E')$ comes from $\fulldepscohs[n](E)(E')$ and $\restrp[n][\lbrack 0,n \rbrack](E)$.
+  \item $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ comes from $\fulldepscohs[n](E)(E')$ and $\cohp[n][\lbrack 0,n \rbrack](E)(E')$.
   \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$.
-  \item $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, comes from $\depscoht[n](E)(E')$, $\cohp[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
+  \item $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
   \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$.
@@
 
-Therefore, assuming a construction of $\framep[n][n]$ from $D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n+1]$ from $D$ extended with some $E:\framep[n+1][n+1](\deps[n+1][\lbrack 0,n+1 \rbrack]) \rightarrow \U$.
+Therefore, assuming a construction of $\framep[n][n]$ from $D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n+1]$ from $D$ extended with some $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$.
 This is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus $\Xp{m}$, by starting with an empty $D$.

### 2025-12-23 paper/paper.tex
paper: lots of miscellanous progress

@@
 \newcommand{\overright}[1]{\overrightarrow{#1}}
+\newcommand{\ap}{\mathsf{ap}\;}
 \renewcommand{\D}{D}
@@
 \renewcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
-\renewcommandx{\cohf}[6][1,2,3,4,5,6]{\coh{frame}[][#3][#4][#5][#6][#1,#2][][]}
-\renewcommandx{\cohl}[6][1,2,3,4,5,6]{\coh{layer}[][#3][#4][#5][#6][#1,#2][][]}
-\renewcommandx{\cohp}[6][1,2,3,4,5,6]{\coh{painting}[][#3][#4][#5][#6][#1,#2][][]}
+\renewcommandx{\cohf}[6][1,2,3,4,5,6]{\coh{frame}[][#3][#4][#5][#6][#1][#2][]}
+\renewcommandx{\cohl}[6][1,2,3,4,5,6]{\coh{layer}[][#3][#4][#5][#6][#1][#2][]}
+\renewcommandx{\cohp}[6][1,2,3,4,5,6]{\coh{painting}[][#3][#4][#5][#6][#1][#2][]}
 
@@
 \begin{center}
-  \fontsize{7.2}{9}\selectfont
   \begin{tikzcd}
@@
 \begin{equation*}
-  \fontsize{7.2}{9}\selectfont
   \begin{array}{llcl}
@@
 Let us introduce another abbreviation to combine a full $\deps[n][\lbrack 0,n \rbrack]:\depstype[n][\lbrack 0,n \rbrack]$ with a family $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U$:
-\begin{align*}
+\begin{gather*}
   \fulldepstype[n] \defeq
@@
     \end{array}\right)
-\end{align*}
+\end{gather*}
+
 TODO: say the convention on projection in the Introduction
@@
 We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$:
-\begin{align*}
+\begin{equation*}
   \fulldepscohstype[n] \defeq
@@
     \end{array}\right)
-\end{align*}
+\end{equation*}
 TODO: say the convention on projection in the Introduction
@@
 
-\begin{equation*}
-  \fontsize{7.2}{9}\selectfont
-  \begin{array}{llcl}
+\begin{align*}{4}
   \restrp[n+1][\lbrack 0,p-1 \rbrack]     &
@@
   (\restrp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))                                         \\
-  \end{array}
-\end{equation*}
+\end{align*}
 
@@
     \cohptype[n][\lbrack 0,p \rbrack]   & (\fulldepscohs[n])                      & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
-                                        &                                         &        & \;\;\;\;\left\{
-    \begin{array}{l}
-      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
+                                        &                                         &        & \left\{
+    \begin{array}{l}
+      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                                                    \\
+      \Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
       \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf[n+1][p](d))(\restrp[n+1][p][r][\omega]
@@
               \fulldepscohs[n]                & : & \fulldepscohstype[n]                                  \\
-              \cohp[n][0,...p-1] & : & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \\
+              \cohp[n][\lbrack 0,p-1 \rbrack] & : & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \\
             \end{array}
@@
               (\depscoht[n])(d)(l))                                              \\
-            \end{array}\right)                                                                                                                                                                                                                    \\
-    \cohttype[n][p]                                                               &
-    \fulldepscohs[n]                                                              & \defeq                                                                        &
-    \left(\begin{array}{l}
-              \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.\, \\
-              \fulldepscohs.\depscohs.\cohf[n][p][r][0][\omega][\theta] \circ \cohf[n+1][p][q+1][0][\epsilon][\theta]
-              (\fulldepscoht[n])
-              \circ \fulldepscohs.\depscohs.\cohf[n][p][q][r][\epsilon][\omega] =      \\
-              \cohf[n+1][p][q+1][r+1][\epsilon][\omega]
-              (\fulldepscoht[n])
-              \circ \fulldepscohs.\depscohs.\cohf[n][p][q][0][\epsilon][\theta]
-              \circ \cohf[n+1][p][r][0][\omega][\theta]
-              (\fulldepscoht[n])                                                       \\
             \end{array}\right)                                                                                                                                                                                                                    \\
@@
 \end{equation*}
-We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$:
-\begin{align*}
+where $\cohttype$ is:
+\begin{equation*}
+  \cohttype[n][p](\fulldepscohs[n]) \defeq
+  \begin{array}{l}
+    \Pi q \leq n-p.\,\Pi r \leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.                         \\
+    \fulldepscohs.\depscohs.\cohf[n][p][r][0][\omega][\theta](\restrf[n+1][p][q+2][\epsilon]) \circ \\
+    \ap\restrf[n][p][r][\omega](\cohf[n+1][p][q+1][0][\epsilon][\theta]
+    (\fulldepscoht[n]))
+    \circ                                                                                           \\
+    \fulldepscohs.\depscohs.\cohf[n][p][q][r][\epsilon][\omega](\restrf[n+1][p][0][\theta]) =       \\
+    \ap\restrf[n][p][0][\theta](\cohf[n+1][p][q+1][r+1][\epsilon][\omega]
+    (\fulldepscoht[n]))
+    \circ                                                                                           \\
+    \fulldepscohs.\depscohs.\cohf[n][p][q][0][\epsilon][\theta](\restrf[n+1][p][r+1][\omega])
+    \circ                                                                                           \\
+    \ap\restrf[n][p][q][\epsilon](\cohf[n+1][p][r][0][\omega][\theta]
+    (\fulldepscoht[n]))
+  \end{array}
+\end{equation*}
+
+It is also convenient to introduce a notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$:
+\begin{equation*}
   \fulldepscohttype[n] \defeq
@@
     \end{array}\right)
-\end{align*}
+\end{equation*}
 

### 2025-12-23 paper/paper.tex
paper: better typesetting with some error fixes

@@
 
-The types $\paintingtype[n][\lbrack 0,p-1 \rbrack]$ of $\painting[n][\lbrack 0,p \rbrack]$ for $p \leq n+1$ are type families over frames, so $\framep[n][\lbrack 0,p-1 \rbrack]$ needs to be assumed beforehand:
+The types $\paintingtype[n][\lbrack 0,p-1 \rbrack]$ of $\painting[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ are type families over frames, so $\framep[n][\lbrack 0,p-1 \rbrack]$ needs to be assumed beforehand:
 
@@
     \framep[n+1][\lbrack 0,p \rbrack]                                                                                 &
-    \multicolumn{3}{l}{
-    (\deps[n][\lbrack 0,p-1 \rbrack]:\depstype[n][\lbrack 0,p-1 \rbrack]) :\frametype[n+1][\lbrack 0,p \rbrack]}         \\
+    (\deps[n][\lbrack 0,p-1 \rbrack]:\depstype[n][\lbrack 0,p-1 \rbrack])                                             & :      & \frametype[n+1][\lbrack 0,p \rbrack]   \\
     \framep[n+1][\lbrack 0,0 \rbrack]                                                                                 &
-    \unitpoint                            & \defeq & (\unitpoint,unit)                                                   \\
+    \unitpoint                                                                                                        & \defeq & (\unitpoint,\unittype)                 \\
     \framep[n+1][\lbrack 0,p+1 \rbrack]                                                                               &
@@
     \restrftype[n][\lbrack 0,p-1 \rbrack]                                                                             &
-    \multicolumn{3}{l}{
     \left(\begin{array}{l}
@@
               \painting[n][\lbrack 0,p-1 \rbrack]:\paintingtype[n][\lbrack 0,p-1 \rbrack](\framep[n][\lbrack 0,p-1 \rbrack]) \\
-            \end{array}\right) : \U} \\
+            \end{array}\right) & :      & \U                                                \\
     \restrftype[n]                                                                                                    &
@@
     \layertype[n][p]                                                                                                  &
-    \multicolumn{3}{l}{
     (\deps[n][\lbrack 0,p \rbrack]:\depstype[n][\lbrack 0,p \rbrack])
-    : \U}                                                                                                                \\
+                                                                                                                      & :      & \U                                     \\
     \layertype[n][p]                                                                                                  &
@@
     \layer[n][p]                                                                                                      &
-    \multicolumn{3}{l}{
     (\deps[n][\lbrack 0,p \rbrack]:\depstype[n][\lbrack 0,p \rbrack])
-      : \layertype[n][p]
-      (\deps[n][\lbrack 0,p \rbrack])}
+                                                                                                                      & :      & \layertype[n][p]
+    (\deps[n][\lbrack 0,p \rbrack])
     \\
@@
 Let us introduce another abbreviation to combine a full $\deps[n][\lbrack 0,n \rbrack]:\depstype[n][\lbrack 0,n \rbrack]$ with a family $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U$:
-\begin{gather*}
+\begin{equation*}
   \fulldepstype[n] \defeq
-  \left(\begin{array}{lll}
+  \left(\begin{array}{lcl}
       \deps[n][\lbrack 0,n \rbrack] & : & \depstype[n][\lbrack 0,n \rbrack]                               \\
@@
     \end{array}\right)
-\end{gather*}
+\end{equation*}
 
@@
     (\fulldeps[n])
-                                          & \defeq & \restrptype[n+1][\lbrack 0,p-1 \rbrack] \times \left(
+                                          & \defeq & \restrptype[n+1][\lbrack 0,p-1 \rbrack] \times             \\
+                                          &        &                                                & \left(
     \begin{array}{l}
@@
     \overline{\deps}                                                                         &
-    \multicolumn{3}{l}{
-    (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack]) : \depstype[n+1][\lbrack 0,p \rbrack]}                                                                                \\
+    (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack])            & :                                   & \depstype[n+1][\lbrack 0,p \rbrack]                                \\
     \overline{\deps}                                                                         & \depscohs[n][\lbrack 0,p-1 \rbrack] & \defeq                                                         &
@@
     \restrf[n+1][\lbrack 0,p \rbrack]                                                        &
-    \multicolumn{3}{l}{
-      (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack]) :
+    (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack])            & :                                   &
     \restrftype[n+1][\lbrack 0,p \rbrack]
@@
               \painting[n+1][\lbrack 0,p \rbrack](\depscohs.\fulldeps[n])                          \\
-              \end{array}\right)
-    }                                                                                                                                                                                                   \\
+            \end{array}\right)                                                                                                          \\
     \restrf[n+1][\lbrack 0,0 \rbrack]                                                        &
@@
     \cohftype[n][\lbrack 0,p-1 \rbrack]                                                      &
-    \multicolumn{3}{l}{
     \left(\begin{array}{l}
@@
               \restrp[n][\lbrack 0,p-1 \rbrack]:\restrptype[n][\lbrack 0,p-1 \rbrack](\fulldeps[n]) \\
-            \end{array}\right) : \U
-    }                                                                                                                  n                                                                                \\
+            \end{array}\right) & :                                   & \U                                                                                                         \\
     \cohftype[n]                                                                             &
@@
                                  \cohf[n][\lbrack 0,p \rbrack]
-                               \end{array}\right)          . \\
+                               \end{array}\right))          . \\
              \\
@@
     \restrltype[n][p]                                                                        &
-    \multicolumn{3}{l}{
     (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack])
-    : \U}                                                                                                                                                                                               \\
+                                                                                             & :                                   & \U                                                                 \\
     \restrltype[n][p]                                                                        &
@@
     \restrl[n][p]                                                                            &
-    \multicolumn{3}{l}{
-      (\depscohs[n][\lbrack 0,p \rbrack]:\depscohstype[n][\lbrack 0,p \rbrack]) :
-    \restrltype[n][p] (\depscohs[n][\lbrack 0,p \rbrack])}                                                                                                                                              \\
+    (\depscohs[n][\lbrack 0,p \rbrack]:\depscohstype[n][\lbrack 0,p \rbrack])                & :                                   &
+    \restrltype[n][p] (\depscohs[n][\lbrack 0,p \rbrack])                                                                                                                                               \\
     \restrl[n][p][q][\epsilon]                                                               &
@@
 \begin{align*}
-  \overline{\fulldeps}(\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \fulldepstype[n+1] \\
-  \overline{\fulldeps}(\fulldepscohs[n])                      & \defeq &
-  \left(\begin{array}{l}
+  \overline{\fulldeps}(\fulldepscohs[n]:\fulldepscohstype[n]) & :     \fulldepstype[n+1]                                                       \\
+  \overline{\fulldeps}(\fulldepscohs[n])                      & \defeq \left(\begin{array}{l}
                                                                                  \overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,n \rbrack]) \\
@@
 
-\begin{align*}{4}
+\begin{equation*}
+  \begin{array}{llcl}
     \restrp[n+1][\lbrack 0,p-1 \rbrack]     &
@@
     (\restrp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))                                         \\
-\end{align*}
+  \end{array}
+\end{equation*}
 
@@
 \begin{align*}
-  \overline{\fulldepscohs}(\fulldepscoht[n]:\fulldepscohstype[n]) & :      & \fulldepscohstype[n+1] \\
-  \overline{\fulldepscohs}(\fulldepscoht[n])                      & \defeq &
-  \left(\begin{array}{l}
+  \overline{\fulldepscohs}(\fulldepscoht[n]:\fulldepscohstype[n]) & :     \fulldepscohstype[n+1]                                                       \\
+  \overline{\fulldepscohs}(\fulldepscoht[n])                      & \defeq \left(\begin{array}{l}
                                                                                      \overline{\depscohs}(\fulldepscoht.\depscoht[n][\lbrack 0,n \rbrack]) \\

### 2025-12-23 paper/paper.tex
paper: strip redundant types in args

@@
   \begin{array}{llcl}
-    \paintingtype[n][\lbrack 0,p-1 \rbrack] & (\framep[n][\lbrack 0,p \rbrack]:\frametype[n][\lbrack 0,p-1 \rbrack]) & :      & \U                                                                                                                   \\
+    \paintingtype[n][\lbrack 0,p-1 \rbrack] & \framep[n][\lbrack 0,p \rbrack]   & :      & \U                                                                                                                   \\
     \paintingtype[n]                        & \unitpoint                        & \defeq & \unittype                                                                                                            \\
@@
 $\restrf[n][\lbrack 0,p-1 \rbrack]$ in one block, which we call
-$\depstype[n][0,...p-1]$:
+$\depstype[n][\lbrack 0,p-1 \rbrack]$:
 
@@
     \framep[n+1][\lbrack 0,p \rbrack]      &
-    (\deps[n][\lbrack 0,p-1 \rbrack]:\depstype[n][\lbrack 0,p-1 \rbrack])                                             & :      & \frametype[n+1][\lbrack 0,p \rbrack]   \\
+    \deps[n][\lbrack 0,p-1 \rbrack]        & :      & \frametype[n+1][\lbrack 0,p \rbrack]   \\
     \framep[n+1][\lbrack 0,0 \rbrack]      &
@@
     \left(\begin{array}{l}
-              \framep[n][\lbrack 0,p-1 \rbrack]:\frametype[n][\lbrack 0,p-1 \rbrack]                                         \\
-              \painting[n][\lbrack 0,p-1 \rbrack]:\paintingtype[n][\lbrack 0,p-1 \rbrack](\framep[n][\lbrack 0,p-1 \rbrack]) \\
+              \framep[n][\lbrack 0,p-1 \rbrack]   \\
+              \painting[n][\lbrack 0,p-1 \rbrack] \\
             \end{array}\right) & :      & \U                                                \\
@@
     \layertype[n][p]                       &
-    (\deps[n][\lbrack 0,p \rbrack]:\depstype[n][\lbrack 0,p \rbrack])
+    \deps[n][\lbrack 0,p \rbrack]
                                            & :      & \U                                     \\
@@
     \layer[n][p]                           &
-    (\deps[n][\lbrack 0,p \rbrack]:\depstype[n][\lbrack 0,p \rbrack])
+    \deps[n][\lbrack 0,p \rbrack]
                                            & :      & \layertype[n][p]
@@
     \painting[n+1][p]        &
-    (\fulldeps[n]:\fulldepstype[n]) & :      & \paintingtype[n+1][p]      \\
+    \fulldeps[n]             & :      & \paintingtype[n+1][p]             \\
     \painting[n+1][n+1]      &
@@
     \painting[n+1][\lbrack 0,p-1 \rbrack] &
-    (\fulldeps[n]:\fulldepstype[n])       & :      & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack])) \\
+    \fulldeps[n]                          & :      & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack])) \\
     \painting[n+1]                        &
@@
     \restrptype[n][\lbrack 0,p-1 \rbrack] &
-    (\fulldeps[n]:\fulldepstype[n])       & :      & \U                                                         \\
+    \fulldeps[n]                          & :      & \U                                                         \\
     \restrptype[n]                        & E      & \defeq                                         & \unittype \\
@@
               \fulldeps[n]                      & : & \fulldepstype[n]                                    \\
-              \restrp[n][0,...p-1]            & : & \restrptype[n][\lbrack 0,p-1 \rbrack](\fulldeps[n]) \\
+              \restrp[n][\lbrack 0,p-1 \rbrack] & : & \restrptype[n][\lbrack 0,p-1 \rbrack](\fulldeps[n]) \\
               \cohf[n][\lbrack 0,p-1 \rbrack]   & : & \cohftype[n][\lbrack 0,p-1 \rbrack]
@@
     \overline{\deps}                        &
-    (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack])            & :                                   & \depstype[n+1][\lbrack 0,p \rbrack]                                \\
+    \depscohs[n][\lbrack 0,p-1 \rbrack]     & :                                   & \depstype[n+1][\lbrack 0,p \rbrack]                                                                                 \\
     \overline{\deps}                        & \depscohs[n][\lbrack 0,p-1 \rbrack] & \defeq                                                         &
@@
     \restrf[n+1][\lbrack 0,p \rbrack]       &
-    (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack])            & :                                   &
+    \depscohs[n][\lbrack 0,p-1 \rbrack]     & :                                   &
     \restrftype[n+1][\lbrack 0,p \rbrack]
@@
     \left(\begin{array}{l}
-              \fulldeps[n]:\fulldepstype[n]                                                         \\
-              \restrp[n][\lbrack 0,p-1 \rbrack]:\restrptype[n][\lbrack 0,p-1 \rbrack](\fulldeps[n]) \\
+              \fulldeps[n]                      \\
+              \restrp[n][\lbrack 0,p-1 \rbrack] \\
             \end{array}\right)    & :                                   & \U                                                                                                                              \\
@@
     \restrltype[n][p]                       &
-    (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack])
+    \depscohs[n][\lbrack 0,p-1 \rbrack]
                                             & :                                   & \U                                                                                                                  \\
@@
     \restrl[n][p]                           &
-    (\depscohs[n][\lbrack 0,p \rbrack]:\depscohstype[n][\lbrack 0,p \rbrack])                & :                                   &
+    \depscohs[n][\lbrack 0,p \rbrack]       & :                                   &
     \restrltype[n][p] (\depscohs[n][\lbrack 0,p \rbrack])                                                                                                                                               \\
@@
 \begin{align*}
-  \overline{\fulldeps}(\fulldepscohs[n]:\fulldepscohstype[n]) & :     \fulldepstype[n+1]                                                       \\
+  \overline{\fulldeps}(\fulldepscohs[n]) & :     \fulldepstype[n+1]                                                       \\
   \overline{\fulldeps}(\fulldepscohs[n]) & \defeq \left(\begin{array}{l}
@@
     \restrp[n+1][p][q][\epsilon]        &
-    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      &
+    \fulldepscohs[n]                    & :      &
     \left(
@@
     \restrp[n+1][\lbrack 0,p-1 \rbrack] &
-    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs.\depscohs.\fulldeps[n])) \\
+    \fulldepscohs[n]                    & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs.\depscohs.\fulldeps[n])) \\
     \restrp[n+1]                        &
@@
   \begin{array}{llcl}
-    \cohptype[n][\lbrack 0,p-1 \rbrack] & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                                           \\
+    \cohptype[n][\lbrack 0,p-1 \rbrack] & \fulldepscohs[n]   & :      & \U                                                           \\
     \cohptype[n]                        & \unitpoint         & \defeq & \unittype                                                    \\
@@
     \right)                                                                                                                                                                                                         \\
-    \overline{\depscohs}                                                          & (\depscoht[n][\lbrack 0,p-1 \rbrack]:\depscohttype[n][\lbrack 0,p-1 \rbrack]) & :                                                                                 & \depscohstype[n+1][\lbrack 0,p \rbrack] \\
+    \overline{\depscohs}                        & \depscoht[n][\lbrack 0,p-1 \rbrack] & :                                                                                 & \depscohstype[n+1][\lbrack 0,p \rbrack] \\
     \overline{\depscohs}                        & \depscoht[n][\lbrack 0,p-1 \rbrack] & \defeq                                                                            &
@@
     \cohf[n+1][\lbrack 0,p \rbrack]             &
-    (\depscoht[n][\lbrack 0,p-1 \rbrack]:\depscohttype[n][\lbrack 0,p-1 \rbrack]) & :                                                                             & \cohftype[n+1][\lbrack 0,p \rbrack]
+    \depscoht[n][\lbrack 0,p-1 \rbrack]         & :                                   & \cohftype[n+1][\lbrack 0,p \rbrack]
     \left(\begin{array}{l}
@@
     \cohl[n][p]                                 &
-    (\depscoht[n][\lbrack 0,p-1 \rbrack]:\depscohttype[n][\lbrack 0,p-1 \rbrack]) & :                                                                             &
+    \depscoht[n][\lbrack 0,p-1 \rbrack]         & :                                   &
     \begin{array}{l}
@@
 \begin{align*}
-  \overline{\fulldepscohs}(\fulldepscoht[n]:\fulldepscohstype[n]) & :     \fulldepscohstype[n+1]                                                       \\
+  \overline{\fulldepscohs}(\fulldepscoht[n]) & :     \fulldepscohstype[n+1]                                                       \\
   \overline{\fulldepscohs}(\fulldepscoht[n]) & \defeq \left(\begin{array}{l}
@@
     \cohp[n+1][p]                                &
-    (\fulldepscoht[n]:\fulldepscohttype[n])      & :      &
+    \fulldepscoht[n]                             & :      &
     \cohptype[n+1][p](\overline{\fulldepscohs}(\fulldepscoht[n]))                                       \\
@@
     \cohp[n+1][\lbrack 0,p-1 \rbrack] &
-    (\fulldepscoht[n]:\fulldepscohttype[n]) & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
+    \fulldepscoht[n]                  & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
     \cohp[n+1]                        &

### 2025-12-23 paper/paper.tex
paper: make projections implicit, coh2frame corrections
paper: corrections, better typesetting, deps it
paper: strip deps it, tweak color instead
paper: tweak deps colors
paper: fix sub-super-script in deps
paper: adding missing args for depsrestr
paper: replace remaining aligns with arrays

@@
 
-\newcommandx{\depsp}[8][2,3,4,5,6,7,8]{
-  \ensuremath{\mathsf{\color{russian-green}{deps}}_{
-    \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4]}^{\joinargs[#5][#6][#7]}}
-}
-
-\newcommandx{\depstypep}[8][2,3,4,5,6,7,8]{
-  \ensuremath{\mathsf{\color{russian-green}{DEPS}}_{
-    \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4]}^{\joinargs[#5][#6][#7]}}
+\newcommandx{\depsmacro}[5][4,5]{
+  \ensuremath{\mathsf{\color{strawberry}{#1}}_{
+    \joinargs[\mathsf{\color{#3}{#2}}]}^{\joinargs[#4][#5]}}
 }
@@
 
-\newcommandx{\deps}[2][1,2]{\depsp{}[][][][#1][#2][][]}
-\newcommandx{\fulldeps}[1][1]{\depsp{full}[][][][#1][][][]}
-\newcommandx{\depscohs}[2][1,2]{\depsp{cohs}[][][][#1][#2][][]}
-\newcommandx{\fulldepscohs}[1][1]{\depsp{fullcohs}[][][][#1][][][]}
-\newcommandx{\depscoht}[2][1,2]{\depsp{coht}[][][][#1][#2][][]}
-\newcommandx{\fulldepscoht}[1][1]{\depsp{fullcoht}[][][][#1][][][]}
-\newcommandx{\depstype}[2][1,2]{\depstypep{}[][][][#1][#2][][]}
-\newcommandx{\fulldepstype}[1][1]{\depstypep{full}[][][][#1][][][]}
-\newcommandx{\depscohstype}[2][1,2]{\depstypep{cohs}[][][][#1][#2][][]}
-\newcommandx{\fulldepscohstype}[1][1]{\depstypep{fullcohs}[][][][#1][][][]}
-\newcommandx{\depscohttype}[2][1,2]{\depstypep{coht}[][][][#1][#2][][]}
-\newcommandx{\fulldepscohttype}[1][1]{\depstypep{fullcoht}[][][][#1][][][]}
+\newcommandx{\deps}[2][1,2]{\depsmacro{deps}{restr}{russian-green}[#1][#2]}
+\newcommandx{\fulldeps}[1][1]{\depsmacro{deps}{fullrestr}{russian-green}[#1]}
+\newcommandx{\depscohs}[2][1,2]{\depsmacro{deps}{coh}{chestnut}[#1][#2]}
+\newcommandx{\fulldepscohs}[1][1]{\depsmacro{deps}{fullcoh}{chestnut}[#1]}
+\newcommandx{\depscoht}[2][1,2]{\depsmacro{deps}{coht}{chestnut}[#1][#2]}
+\newcommandx{\fulldepscoht}[1][1]{\depsmacro{deps}{fullcoht}{chestnut}[#1]}
+\newcommandx{\depstype}[2][1,2]{\depsmacro{DEPS}{restr}{russian-green}[#1][#2]}
+\newcommandx{\fulldepstype}[1][1]{\depsmacro{DEPS}{fullrestr}{russian-green}[#1]}
+\newcommandx{\depscohstype}[2][1,2]{\depsmacro{DEPS}{coh}{chestnut}[#1][#2]}
+\newcommandx{\fulldepscohstype}[1][1]{\depsmacro{DEPS}{fullcoh}{chestnut}[#1]}
+\newcommandx{\depscohttype}[2][1,2]{\depsmacro{DEPS}{coht}{chestnut}[#1][#2]}
+\newcommandx{\fulldepscohttype}[1][1]{\depsmacro{DEPS}{fullcoht}{chestnut}[#1]}
 
@@
 
-\begin{align*}
-  \framep[n][p]      & : \U                                                                                                                 & \mbox{for all $p\leq n$}   \\
-  \framep[n-1][p]    & : \U                                                                                                                 & \mbox{for all $p\leq n-1$} \\
-  \framep[n-2][p]    & : \U                                                                                                                 & \mbox{for all $p\leq n-2$} \\
-  \restrf[n][p]      & : \Pi q.\, \Pi \omega.\, \framep[n][p] \rightarrow \framep[n-1][p]                                                   & \mbox{for all $p\leq n$}   \\
-  \restrf[n-1][p]    & : \Pi q.\, \Pi \omega.\, \framep[n-1][p] \rightarrow \framep[n-2][p]                                                 & \mbox{for all $p\leq n-1$} \\
-  \cohf[n][p]        & : \Pi qr\epsilon\omega.\, \restrf[n-1][p][q][\epsilon] \circ \restrf[n][p][\omega][r] =                                                           \\
-                     & \;\;\;\;\restrf[n-1][p][r][\omega] \circ \restrf[n][p][\epsilon][q+1]                                                & \mbox{for all $p\leq n$}   \\
-  \mathsf{hypF0}     & : \framep[n][0]         = \unitpoint
+\begin{equation*}
+  \begin{array}{lclr}
+    \framep[n][p]      & : & \U                                                                                                                 & \mbox{for all $p\leq n$}   \\
+    \framep[n-1][p]    & : & \U                                                                                                                 & \mbox{for all $p\leq n-1$} \\
+    \framep[n-2][p]    & : & \U                                                                                                                 & \mbox{for all $p\leq n-2$} \\
+    \restrf[n][p]      & : & \Pi q.\, \Pi \omega.\, \framep[n][p] \rightarrow \framep[n-1][p]                                                   & \mbox{for all $p\leq n$}   \\
+    \restrf[n-1][p]    & : & \Pi q.\, \Pi \omega.\, \framep[n-1][p] \rightarrow \framep[n-2][p]                                                 & \mbox{for all $p\leq n-1$} \\
+    \cohf[n][p]        & : & \Pi qr\epsilon\omega.\, \restrf[n-1][p][q][\epsilon] \circ \restrf[n][p][\omega][r] =                                                           \\
+                       &   & \restrf[n-1][p][r][\omega] \circ \restrf[n][p][\epsilon][q+1]                                                      & \mbox{for all $p\leq n$}   \\
+    \mathsf{hypF0}     & : & \framep[n][0]         = \unitpoint
     \\
-  \mathsf{hypFS}     & : \framep[n][p+1]       = \Sigma d: \framep[n+1][p]. \Pi \omega.\, \painting[n][p] (\restrf[n+1][p](d))              & \mbox{for all $p\leq n-1$} \\
-  \mathsf{hypPrevF0} & : \framep[n-1][0]                                                                                       = \unitpoint                              \\
-  \mathsf{hypPrevFS} & : \framep[n-1][p+1] = \Sigma d: \framep[n][p]. \Pi \omega.\, \painting[n-1][p] (\restrf[n][p](d))                    & \mbox{for all $p\leq n-2$} \\
-  \mathsf{hypRF0}    & : \restrf[n][0]        = \ldots \texttt{depending on hypF0}                                                                                       \\
-  \mathsf{hypRFS}    & : \restrf[n][p+1]      = \ldots \texttt{depending on hypFS and hypPrevFS}                                            & \mbox{for all $p\leq n-1$} \\
-  \ldots             & \;\;\;\;\texttt{fields for painting, restrf, cohp}
-\end{align*}
+    \mathsf{hypFS}     & : & \framep[n][p+1]       = \Sigma d: \framep[n+1][p]. \Pi \omega.\, \painting[n][p] (\restrf[n+1][p](d))              & \mbox{for all $p\leq n-1$} \\
+    \mathsf{hypPrevF0} & : & \framep[n-1][0]                                                                                       = \unitpoint                              \\
+    \mathsf{hypPrevFS} & : & \framep[n-1][p+1] = \Sigma d: \framep[n][p]. \Pi \omega.\, \painting[n-1][p] (\restrf[n][p](d))                    & \mbox{for all $p\leq n-2$} \\
+    \mathsf{hypRF0}    & : & \restrf[n][0]        = \ldots \texttt{depending on hypF0}                                                                                       \\
+    \mathsf{hypRFS}    & : & \restrf[n][p+1]      = \ldots \texttt{depending on hypFS and hypPrevFS}                                            & \mbox{for all $p\leq n-1$} \\
+    \ldots             &   & \texttt{fields for painting, restrf, cohp}
+  \end{array}
+\end{equation*}
 
@@
 
-\begin{align*}
-  \framep[n][p]   & :                                                                                                           \U                                                                                    & \mbox{for all $p\leq n$} \\
-  \painting[n][p] & :                                                                                                           \framep[n][p] \rightarrow \U                                                          & \mbox{for all $p\leq n$} \\
-  \restrf[n][p]   & :                                                                                                           \Pi q \leq n-p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]           & \mbox{for all $p\leq n$} \\
-  \restrp[n][p]   & :                                                                                                           \Pi q \leq n-p.\, \Pi \epsilon.\, \Pi d:\framep[n+1][p].\,                                                       \\
-                  & \;\;\;\;\painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d))                                                                                                                        & \mbox{for all $p\leq n$} \\
-  \cohf[n][p]     & :                                                                                                           \Pi qr\epsilon\omega.\, \restrf[n][p][q][\epsilon] \circ \restrf[n+1][p][\omega][r] =                            \\
-                  & \;\;\;\;\restrf[n][p][\omega][r] \circ \restrf[n+1][p][q+1][\epsilon]                                                                                                                             & \mbox{for all $p\leq n$} \\
-  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,                                                                                                                                                                              \\
-                  & \;\;\;\;\restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) =                                                                                                                      \\
-                  & \;\;\;\;\restrp[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon](d)) \circ \restrp[n+1][p][q+1][\epsilon](d)                                                                                       & \mbox{for all $p\leq n$} \\
-\end{align*}
+\begin{equation*}
+  \begin{array}{lclr}
+    \framep[n][p]   & : & \U                                                                                                  & \mbox{for all $p\leq n$} \\
+    \painting[n][p] & : & \framep[n][p] \rightarrow \U                                                                        & \mbox{for all $p\leq n$} \\
+    \restrf[n][p]   & : & \Pi q \leq n-p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]                         & \mbox{for all $p\leq n$} \\
+    \restrp[n][p]   & : & \Pi q \leq n-p.\, \Pi \epsilon.\, \Pi d:\framep[n+1][p].\,                                                                     \\
+                    &   & \painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d))                                  & \mbox{for all $p\leq n$} \\
+    \cohf[n][p]     & : & \Pi qr\epsilon\omega.\, \restrf[n][p][q][\epsilon] \circ \restrf[n+1][p][\omega][r] =                                          \\
+                    &   & \restrf[n][p][\omega][r] \circ \restrf[n+1][p][q+1][\epsilon]                                       & \mbox{for all $p\leq n$} \\
+    \cohp[n][p]     & : & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,                                                                                \\
+                    &   & \restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) =                                \\
+                    &   & \restrp[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon](d)) \circ \restrp[n+1][p][q+1][\epsilon](d) & \mbox{for all $p\leq n$} \\
+  \end{array}
+\end{equation*}
 
@@
 So far, using this recursive definition of  $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$, we are able to specify the three first component of the exected dependent structure:
-\begin{align*}
-  \framep[n][p]             & :                        \U                                                & \mbox{for all $p\leq n$} \\
-  \painting[n][p]           & :                        \framep[n][p] \rightarrow \U                      & \mbox{for all $p\leq n$} \\
-  \restrf[n][p]             & :                        \Pi q \leq n-p.\, \Pi \epsilon.\, \framep[n+1][p]
+\begin{equation*}
+  \begin{array}{lclr}
+    \framep[n][p]             & :                        & \U                                                & \mbox{for all $p\leq n$} \\
+    \painting[n][p]           & :                        & \framep[n][p] \rightarrow \U                      & \mbox{for all $p\leq n$} \\
+    \restrf[n][p]             & :                        & \Pi q \leq n-p.\, \Pi \epsilon.\, \framep[n+1][p]
     \left(\begin{array}{l}
@@
     \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                                                                                \\
-\end{align*}
+  \end{array}
+\end{equation*}
 which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][\lbrack 0,p \rbrack]$, $\paintingtype[n][\lbrack 0,p \rbrack]$ and $\restrftype[n][\lbrack 0,p \rbrack]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][\lbrack 0,p-1 \rbrack]$ makes it a very dependent function~\citep{Hickey96}:
-\begin{align*}
-  \framep[n][\lbrack 0,p \rbrack]   & : \frametype[n][\lbrack 0,p \rbrack]                                     \\
-  \painting[n][\lbrack 0,p \rbrack] & : \paintingtype[n][\lbrack 0,p \rbrack](\framep[n][\lbrack 0,p \rbrack]) \\
-  \restrf[n][\lbrack 0,p \rbrack]   & : \restrftype[n][\lbrack 0,p \rbrack]
+\begin{equation*}
+  \begin{array}{lcl}
+    \framep[n][\lbrack 0,p \rbrack]   & : & \frametype[n][\lbrack 0,p \rbrack]                                     \\
+    \painting[n][\lbrack 0,p \rbrack] & : & \paintingtype[n][\lbrack 0,p \rbrack](\framep[n][\lbrack 0,p \rbrack]) \\
+    \restrf[n][\lbrack 0,p \rbrack]   & : & \restrftype[n][\lbrack 0,p \rbrack]
     \left(\begin{array}{l}
@@
             \end{array}\right)                                                                      \\
-\end{align*}
+  \end{array}
+\end{equation*}
 
@@
     \paintingtype[n]                        & \unitpoint                      & \defeq & \unittype                                                                                                            \\
-    \paintingtype[n][\lbrack 0,p \rbrack]   & (\framep[n][\lbrack 0,p \rbrack]) & \defeq & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack]) \times (\framep[n][p] \rightarrow \U) \\
+    \paintingtype[n][\lbrack 0,p \rbrack]   & \framep[n][\lbrack 0,p \rbrack] & \defeq & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack]) \times (\framep[n][p] \rightarrow \U) \\
   \end{array}
@@
                                            & \defeq &
-    d \mapsto \Pi\epsilon.\,\painting[n][p](\deps.\restrf[n][p][0][\epsilon](d))             \\
-  \end{array}
-\end{equation*}
-
-Note that we write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the
+    d \mapsto \Pi\epsilon.\,\painting[n][p](\restrf[n][p][0][\epsilon](d))                   \\
+  \end{array}
+\end{equation*}
+
+Note that we write $\framep$, $\painting$, $\restrf$ for the
 projections of a $\deps$. Also, by abuse of notation, we write $\unitpoint$ for
@@
     \painting[n+1][n+1]      &
-    \fulldeps[n]             & \defeq & \fulldeps.E                       \\
+    \fulldeps[n]             & \defeq & E                       \\
     \painting[n+1][p \leq n] &
@@
     \left(\begin{array}{l}
-              \Sigma l:\layer[n][p](\fulldeps.\deps[n][\lbrack 0,p \rbrack]). \\
+              \Sigma l:\layer[n][p](\deps[n][\lbrack 0,p \rbrack]). \\
               \painting[n+1][p+1]
@@
     \painting[n+1][\lbrack 0,p-1 \rbrack] &
-    \fulldeps[n]                          & :      & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack])) \\
+    \fulldeps[n]                          & :      & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack](\deps[n][\lbrack 0,p-1 \rbrack])) \\
     \painting[n+1]                        &
@@
     \begin{array}{l}
-        \Pi q \leq n-p.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack]). \\
+        \Pi q \leq n-p.\Pi \epsilon.\Pi d:\framep[n+1][p](\deps[n][\lbrack 0,p-1 \rbrack]). \\
         \painting[n+1][p]
-        (\fulldeps[n])(d) \rightarrow                                                                 \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
+        (\fulldeps[n])(d) \rightarrow                                                       \\ \painting[n][p](\restrf[n][p][q][\epsilon](d))\end{array}
     \right)                                                                                                     \\
@@
     \left(\begin{array}{l}
-              \framep[n+1][\lbrack 0,p \rbrack](\depscohs.\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack]) \\
-              \painting[n+1][\lbrack 0,p \rbrack](\depscohs.\fulldeps[n])                            \\
+              \framep[n+1][\lbrack 0,p \rbrack](\deps[n][\lbrack 0,p-1 \rbrack])     \\
+              \painting[n+1][\lbrack 0,p \rbrack](\fulldeps[n])                      \\
               \restrf[n+1][\lbrack 0,p \rbrack](\depscohs[n][\lbrack 0,p-1 \rbrack]) \\
@@
     \left(\begin{array}{l}
-              \framep[n+1][\lbrack 0,p \rbrack](\depscohs.\fulldeps.\deps[n][\lbrack 0,p \rbrack]) \\
-              \painting[n+1][\lbrack 0,p \rbrack](\depscohs.\fulldeps[n])                          \\
+              \framep[n+1][\lbrack 0,p \rbrack](\deps[n][\lbrack 0,p \rbrack]) \\
+              \painting[n+1][\lbrack 0,p \rbrack](\fulldeps[n])                \\
             \end{array}\right)                                                                                                                              \\
@@
              \\
-             \fulldeps.\deps.\restrf[n][p][q][\epsilon](\restrf[n+1][p][r][\omega]
+             \restrf[n][p][q][\epsilon](\restrf[n+1][p][r][\omega]
              \left(\begin{array}{l}
@@
               \end{array}\right)(d)) =                  \\
-             \fulldeps.\deps.\restrf[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon]
+             \restrf[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon]
              \left(\begin{array}{l}
@@
              \layer[n+1][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])(d) \rightarrow                            \\
-             \layer[n][p](\fulldeps.\deps[n][\lbrack 0,p \rbrack])(\restrf[n][p]
+             \layer[n][p](\deps[n][\lbrack 0,p \rbrack])(\restrf[n][p]
              (\depscohs[n][\lbrack 0,p-1 \rbrack])(d))
@@
 We can then extend $\overline{\deps}$ to build $\fulldeps$ from $\fulldepscohs$:
-\begin{align*}
-  \overline{\fulldeps}(\fulldepscohs[n]) & :     \fulldepstype[n+1]                                                       \\
-  \overline{\fulldeps}(\fulldepscohs[n]) & \defeq \left(\begin{array}{l}
-                                                            \overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,n \rbrack]) \\
-                                                            \fulldepscohs.E                                                   \\
-                                                          \end{array}\right) \\
-\end{align*}
+\begin{equation*}
+  \begin{array}{lcl}
+    \overline{\fulldeps}(\fulldepscohs[n]) & :      & \fulldepstype[n+1]                                        \\
+    \overline{\fulldeps}(\fulldepscohs[n]) & \defeq & \left(\begin{array}{l}
+                                                                \overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack]) \\
+                                                                E                                                   \\
+                                                              \end{array}\right) \\
+  \end{array}
+\end{equation*}
 
@@
         \Pi d:\framep[n+2][p]
-        (\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])). \\
+        (\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])). \\
         \painting[n+2][p]
         (\overline{\fulldeps}(\fulldepscohs[n]))(d) \rightarrow  \\
-        \painting[n+1][p](\fulldepscohs.\depscohs.\fulldeps[n])
-        (\restrf[n+1][p](\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])(d))\end{array}\right)                        \\
+        \painting[n+1][p](\fulldeps[n])
+        (\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))\end{array}\right)                                        \\
     \restrp[n+1][n+1][q][\epsilon]      &
@@
     \left(\begin{array}{l}
-              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n][\lbrack 0,p \rbrack])(d)(l), \\
+              \restrl[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p \rbrack])(d)(l), \\
               \restrp[n+1][p+1][q][\epsilon](\fulldepscohs[n])(d,l)(c)             \\
@@
     \restrp[n+1][\lbrack 0,p-1 \rbrack] &
-    \fulldepscohs[n]                    & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs.\depscohs.\fulldeps[n])) \\
+    \fulldepscohs[n]                    & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldeps[n])) \\
     \restrp[n+1]                        &
@@
     \cohptype[n]                        & \unitpoint       & \defeq & \unittype                                                    \\
-    \cohptype[n][\lbrack 0,p \rbrack]   & (\fulldepscohs[n]) & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
+    \cohptype[n][\lbrack 0,p \rbrack]   & \fulldepscohs[n] & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
                                         &                  &        & \left\{
@@
       \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                                      \\
-      \Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
-      \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf[n+1][p](d))(\restrp[n+1][p][r][\omega]
+      \Pi d:\framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
+      \restrp[n][p][q][\epsilon](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][r][\omega]
       (\fulldepscohs[n])(d)(c)) =                                                                                                                    \\
-      \fulldepscohs.\depscohs.\restrp[n][p][r][\omega](\restrf[n+1][p](d))(\restrp[n+1][p][q+1][\epsilon]
+      \restrp[n][p][r][\omega](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][q+1][\epsilon]
       (\fulldepscohs[n])(d)(c))
@@
     \left(\begin{array}{l}
-              \overline{\deps}(\depscoht.\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack]) \\
-              \restrp[n+1][p](\depscoht.\fulldepscohs[n])                                   \\
+              \overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack]) \\
+              \restrp[n+1][p](\fulldepscohs[n])                     \\
               \cohf[n+1][p](\depscoht[n][\lbrack 0,p-1 \rbrack])    \\
@@
     \left(\begin{array}{l}
-              \overline{\fulldeps}(\depscoht.\fulldepscohs[n])              \\
-              \restrp[n+1][\lbrack 0,p \rbrack](\depscoht.\fulldepscohs[n]) \\
+              \overline{\fulldeps}(\fulldepscohs[n])              \\
+              \restrp[n+1][\lbrack 0,p \rbrack](\fulldepscohs[n]) \\
             \end{array}\right)                                                                                                                                                       \\
@@
     \cohf[n][\lbrack 0,p+1 \rbrack]             &
-    (\depscoht[n][\lbrack 0,p-1 \rbrack])       & \defeq                              &
+    \depscoht[n][\lbrack 0,p-1 \rbrack]         & \defeq                              &
     \left(\begin{array}{l}
@@
     \coht[n][p][q][r][\epsilon][\omega][\theta] &
-    \fulldepscohs[n]                            & \defeq                              & \UIP                                                                                                                        \\
+    \fulldepscohs[n]                            & \defeq                              & \lambda d.\,\UIP                                                                                                            \\
 
@@
     \cohl[n][p][q][r][\epsilon][\omega]         &
-    (\depscoht[n][\lbrack 0,p-1 \rbrack])       & \defeq                              &
+    \depscoht[n][\lbrack 0,p-1 \rbrack]         & \defeq                              &
     \lambda d.
@@
 \lambda \theta.
-\overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\depscoht.\fulldepscohs[n])}{(\depscoht.\cohp[n][p][q][r][\epsilon][\omega](l_\theta))}                       \\
+\overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])}{(\cohp[n][p][q][r][\epsilon][\omega](l_\theta))}                                           \\
   \end{array}
@@
 \begin{equation*}
-  \cohttype[n][p](\fulldepscohs[n]) \defeq
+  \cohttype[n][p](\depscoht[n][\lbrack 0,p \rbrack]) \defeq
   \begin{array}{l}
     \Pi q \leq n-p.\,\Pi r \leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.                                                          \\
-    \fulldepscohs.\depscohs.\cohf[n][p][r][0][\omega][\theta](\restrf[n+1][p][q+2][\epsilon]) \circ \\
+    \cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))) \circ \\
     \ap\restrf[n][p][r][\omega](\cohf[n+1][p][q+1][0][\epsilon][\theta]
-    (\fulldepscoht[n]))
+    (\depscoht[n][p]))
     \circ                                                                                                                            \\
-    \fulldepscohs.\depscohs.\cohf[n][p][q][r][\epsilon][\omega](\restrf[n+1][p][0][\theta]) =       \\
+    \cohf[n][p][q][r][\epsilon][\omega](\restrf[n+2][p][0][\theta](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))) =       \\
     \ap\restrf[n][p][0][\theta](\cohf[n+1][p][q+1][r+1][\epsilon][\omega]
-    (\fulldepscoht[n]))
+    (\depscoht[n][p]))
     \circ                                                                                                                            \\
-    \fulldepscohs.\depscohs.\cohf[n][p][q][0][\epsilon][\theta](\restrf[n+1][p][r+1][\omega])
+    \cohf[n][p][q][0][\epsilon][\theta](\restrf[n+2][p][r+1][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack])))
     \circ                                                                                                                            \\
     \ap\restrf[n][p][q][\epsilon](\cohf[n+1][p][r][0][\omega][\theta]
-    (\fulldepscoht[n]))
+    (\depscoht[n][p]))
   \end{array}
@@
 
-\begin{align*}
-  \overline{\fulldepscohs}(\fulldepscoht[n]) & :     \fulldepscohstype[n+1]                                                       \\
-  \overline{\fulldepscohs}(\fulldepscoht[n]) & \defeq \left(\begin{array}{l}
-                                                                \overline{\depscohs}(\fulldepscoht.\depscoht[n][\lbrack 0,n \rbrack]) \\
-                                                                \fulldepscoht.E                                                       \\
-                                                              \end{array}\right) \\
-\end{align*}
+\begin{equation*}
+  \begin{array}{lcl}
+    \overline{\fulldepscohs}(\fulldepscoht[n]) & :      & \fulldepscohstype[n+1]                                        \\
+    \overline{\fulldepscohs}(\fulldepscoht[n]) & \defeq & \left(\begin{array}{l}
+                                                                    \overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]) \\
+                                                                    E                                                       \\
+                                                                  \end{array}\right) \\
+  \end{array}
+\end{equation*}
 
@@
     \cohp[n+1][n+1][q][r][\epsilon][\omega]      &
-    (\fulldepscoht[n])
+    \fulldepscoht[n]
                                                  & \defeq & \lambda d. \lambda (l,c). l\epsilon \\
     \cohp[n+1][p \leq n][q][r][\epsilon][\omega] &
-    (\fulldepscoht[n])
+    \fulldepscoht[n]
                                                  & \defeq & \lambda d. \lambda (l,c).
     \left(\begin{array}{l}
-              \cohl[n][p][q][r][\epsilon][\omega](\fulldepscoht.\depscoht[n][\lbrack 0,p-1 \rbrack])(d)(l), \\
+              \cohl[n][p][q][r][\epsilon][\omega](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)(l), \\
               \cohp[n+1][p+1][q][r][\epsilon][\omega](\fulldepscoht[n])(d,l))(c)              \\
@@
     \cohp[n+1][\lbrack 0,p-1 \rbrack] &
-    \fulldepscoht[n]                  & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
+    \fulldepscoht[n]                  & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n])) \\
     \cohp[n+1]                        &
@@
 
-\begin{align*}
+\begin{equation*}
+  \begin{array}{lcl}
     \framep[n][\lbrack 0,n \rbrack]                                                                      & :      & \frametype[n][\lbrack 0,n \rbrack]                                     \\
@@
     (\fulldepscohs[n](E)(E'))                                                                                                                                                              \\
-\end{align*}
+  \end{array}
+\end{equation*}
 

### 2025-12-24 paper/paper.tex
paper: paren fixes
paper: increase size of tables
paper: explain cohl rewriting in all details (appendix?)
paper: more details in cohl
paper: corrections to verbose details of cohl
paper: use equality transports
paper: tweak breaks
paper: minor explanation

@@
 
-% For typesetting type theory rules
-\newcommand \seqr[3]
-  {\shortstack{$#2$ \\ \mbox{}\\
-                   \mbox{}\hrulefill\mbox{}\\ \mbox{}\\ $#3$} \raisebox{2ex}{$\;\;\mbox{$#1$}$}}
-
 % Kerning for star
@@
     \restrptype[n][\lbrack 0,p \rbrack]   &
-    (\fulldeps[n])
+    \fulldeps[n]
                                           & \defeq & \restrptype[n+1][\lbrack 0,p-1 \rbrack] \times             \\
@@
     E
-                                            & \defeq                              & (\unitpoint,\lambda q.
-\lambda\epsilon.
-\lambda \_.\unitpoint)                                                      \\
+                                            & \defeq                              & (\unitpoint,\lambda q. \lambda\epsilon. \lambda \_.\unitpoint)   \\
     \restrf[n+1][\lbrack 0,p+1 \rbrack]     &
-    (\depscohs[n][\lbrack 0,p \rbrack])     & \defeq                              &
+    \depscohs[n][\lbrack 0,p \rbrack]       & \defeq                              &
     \left(\begin{array}{l}
@@
              \Pi d:\framep[n+2][p]
-             (\overline{\deps}\left(\begin{array}{l}
+             \left(\overline{\deps}\left(\begin{array}{l}
                                         \fulldeps[n]                      \\
@@
                                         \cohf[n][\lbrack 0,p \rbrack]
-                               \end{array}\right))          . \\
+                                      \end{array}\right)\right)          . \\
              \\
@@
     \depscohs[n][\lbrack 0,p \rbrack]       & \defeq                              &
-    \lambda d.\lambda l.\lambda \omega\overrightarrow{\cohf[n][p][q][0][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(l_\omega)} \\
+    \begin{array}{l}
+      \lambda d.\lambda l.\lambda \omega.\overrightarrow{\cohf[n][p][q][0][\epsilon][\omega](d)}               \\
+      \restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(l_\omega) \\
+    \end{array}
   \end{array}
@@
     \restrp[n+1][n+1][q][\epsilon]      &
-    (\fulldepscohs[n])                  & \defeq & \lambda d. \lambda (l,c). l\epsilon \\
+    \fulldepscohs[n]                    & \defeq & \lambda d. \lambda (l,c). l_\epsilon \\
     \restrp[n+1][p \leq n][q][\epsilon] &
-    (\fulldepscohs[n])                  & \defeq & \lambda d. \lambda (l,c).
+    \fulldepscohs[n]                    & \defeq & \lambda d. \lambda (l,c).
     \left(\begin{array}{l}
@@
     \restrp[n+1][\lbrack 0,p-1 \rbrack] &
-    \fulldepscohs[n]                    & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldeps[n])) \\
+    \fulldepscohs[n]                    & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldeps[n]) \\
     \restrp[n+1]                        &
@@
       \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                                       \\
-      \Pi d:\framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
+      \Pi d:\framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])). \\
       \restrp[n][p][q][\epsilon](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][r][\omega]
-      (\fulldepscohs[n])(d)(c)) =                                                                                                                    \\
+      (\fulldepscohs[n])(d)(c)) =_{\cohf[n][p][q][r][\epsilon][\omega]}                                                                               \\
       \restrp[n][p][r][\omega](\restrf[n+1][p](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(\restrp[n+1][p][q+1][\epsilon]
@@
 \end{equation*}
-
+where we use the ``equality over'' notation $t =_e u$ to mean $\overrightarrow{e}(t) = u$ whenever $t$ is of some type $P(a)$, $u$ of type $P(b)$ and $e$ a proof of $a = b$.
 \subsection{Defining frame coherence laws and specifying frame 2-dimensional coherence laws}
@@
       \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                            \\
-      \Pi d.\Pi l. \overrightarrow{\cohf[n][p][r+1][q+1][\epsilon][\omega]}{(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} = \\
+      \Pi d.\Pi l. {(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} =_{\cohf[n][p][r+1][q+1][\epsilon][\omega]} \\
       \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))
@@
     \depscoht[n][\lbrack 0,p-1 \rbrack]         & \defeq                              &
+    \begin{array}{l}
       \lambda d.
@@
 \lambda \theta.
-\overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])}{(\cohp[n][p][q][r][\epsilon][\omega](l_\theta))}                                           \\
+\overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])}                                                                                         \\
+      (\ap \overrightarrow{\cohf[n][p][r][0][\omega][\theta]} (\ap \overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta](\depscoht[n][\lbrack 0,p-1 \rbrack])} (\cohp[n][p][q][r][\epsilon][\omega](l_\theta)))) \\
+    \end{array}
   \end{array}
@@
   \cohttype[n][p](\depscoht[n][\lbrack 0,p \rbrack]) \defeq
+  \left(
   \begin{array}{l}
@@
     \end{array}
-\end{equation*}
+  \right)
+\end{equation*}
+and where the functoriality of equality and transport was used to go from (omitting the $\framep$ argument of $\restrp$ and the deps argument)
+\begin{equation*}
+  \Pi \theta.\left(
+  \begin{array}{lcl}
+    \begin{array}{l}
+      \overrightarrow{\cohf[n][p][q][0][\epsilon][\theta]}
+      \overrightarrow{\cohf[n+1][p][r][0][\omega][\theta]} \\
+      (\restrp[n][p][q][\epsilon](\restrp[n+1][p][r][\omega](l_\theta)))
+    \end{array} & =_{\cohf[n+1][p][q+1][r+1][\epsilon][\omega]} &
+    \begin{array}{l}
+      \overrightarrow{\cohf[n][p][r][0][\omega][\theta]}\overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta]} \\
+      (\restrp[n][p][r][\omega](\restrp[n+1][p][q+1][\epsilon](l_\theta)))
+    \end{array}
+  \end{array}
+  \right)
+\end{equation*}
+to
+\begin{equation*}
+  \Pi \theta.\left(
+  \begin{array}{lcl}
+    \begin{array}{l}
+      \overrightarrow{\cohf[n][p][q][0][\epsilon][\theta]}(\restrp[n][p][q][\epsilon] \\
+      (\overrightarrow{\cohf[n+1][p][r][0][\omega][\theta]}\restrp[n+1][p][r][\omega](l_\theta)))
+    \end{array} & =_{\cohf[n+1][p][q+1][r+1][\epsilon][\omega]} &
+    \begin{array}{l}
+      \overrightarrow{\cohf[n][p][r][0][\omega][\theta]}(\restrp[n][p][r][\omega] \\
+      (\overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta]}\restrp[n+1][p][q+1][\epsilon](l_\theta)))
+    \end{array}
+  \end{array}
+  \right)
+\end{equation*}
+which is exactly the type of $\cohl[n][p][q][r][\epsilon][\omega]$, up to functional extensionality relative to $\theta$.
 
@@
     \fulldepscoht[n]
-                                                 & \defeq & \lambda d. \lambda (l,c). l\epsilon \\
+                                                 & \defeq & \lambda d. \lambda (l,c). l_\epsilon \\
     \cohp[n+1][p \leq n][q][r][\epsilon][\omega] &
@@
     \cohp[n+1][\lbrack 0,p-1 \rbrack] &
-    \fulldepscoht[n]                  & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n])) \\
+    \fulldepscoht[n]                  & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \\
     \cohp[n+1]                        &
@@
       \end{array}\right)                                                                                      \\
-    \fulldeps[n](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U)                      & \defeq &
+    \fulldeps[n](E)                      & \defeq &
     \left(
@@
       \end{array}\right)                                                                                     \\
-    \depscohs[n][\lbrack 0,n \rbrack](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U) & \defeq &
+    \depscohs[n][\lbrack 0,n \rbrack](E) & \defeq &
     \left(
@@
       \end{array}\right)                                                                                     \\
-    \fulldepscohs[n]
-    \left(\begin{array}{l}
-              E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U                           \\
-              E': \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack](E)))\rightarrow \U \\
-            \end{array}\right)       & \defeq &
+    \fulldepscohs[n](E)(E')              & \defeq &
     \left(
@@
 \end{equation*}
+where
+\begin{align*}
+  E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U \\
+  E': \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack](E)))\rightarrow \U
+\end{align*}
 

### 2025-12-24 paper/paper.tex
Experimenting coht -> coh2
Missing arguments, refinements, typos...

@@
 \newcommandx{\fulldepscohs}[1][1]{\depsmacro{deps}{fullcoh}{chestnut}[#1]}
-\newcommandx{\depscoht}[2][1,2]{\depsmacro{deps}{coht}{chestnut}[#1][#2]}
-\newcommandx{\fulldepscoht}[1][1]{\depsmacro{deps}{fullcoht}{chestnut}[#1]}
+\newcommandx{\depscoht}[2][1,2]{\depsmacro{deps}{coh2}{chestnut}[#1][#2]}
+\newcommandx{\fulldepscoht}[1][1]{\depsmacro{deps}{fullcoh2}{chestnut}[#1]}
 \newcommandx{\depstype}[2][1,2]{\depsmacro{DEPS}{restr}{russian-green}[#1][#2]}
@@
 \newcommandx{\fulldepscohstype}[1][1]{\depsmacro{DEPS}{fullcoh}{chestnut}[#1]}
-\newcommandx{\depscohttype}[2][1,2]{\depsmacro{DEPS}{coht}{chestnut}[#1][#2]}
-\newcommandx{\fulldepscohttype}[1][1]{\depsmacro{DEPS}{fullcoht}{chestnut}[#1]}
+\newcommandx{\depscohttype}[2][1,2]{\depsmacro{DEPS}{coh2}{chestnut}[#1][#2]}
+\newcommandx{\fulldepscohttype}[1][1]{\depsmacro{DEPS}{fullcoh2}{chestnut}[#1]}
 
@@
                 \painting[n][\lbrack 0,p-1 \rbrack] \\
-                \restrf[n][\lbrack 0,p-1 \rbrack]   \\
+                \restrf[n+1][\lbrack 0,p-1 \rbrack]   \\
               \end{array}\right) \rightarrow  \framep[n][p] \\
@@
 It is also convenient to build $\depscohs[n+1][\lbrack 0,p \rbrack]$ from $\depscoht[n][\lbrack 0,p-1 \rbrack]$, so that we can now build $\framep[n+3][p]$.
-Thus, we also include this abbreviation in the definition:
+Thus, we also include this abbreviation in the definition.
+Implicitly using in $\cohf[n+1][\lbrack 0,p \rbrack]$ that equalities in a $\Sigma$-type are equivalent to a $\Sigma$-type of the underlying equalities, we altogether have:
 
@@
     \begin{array}{l}
-      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                            \\
-      \Pi d.\Pi l. {(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} =_{\cohf[n][p][r+1][q+1][\epsilon][\omega]} \\
-      \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))
+      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d.\,\Pi l.                                                             \\
+      \restrl[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(\restrl[n+1][p][r][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p-1 \rbrack]))(l))\\ =_{\cohf[n+1][p][r+1][q+1][\epsilon][\omega](\depscoht[n][\lbrack 0,p-1 \rbrack])} \\
+      \restrl[n][p][r][\omega](\depscohs[n][\lbrack 0,p-1 \rbrack])(\restrl[n+1][p][q+1][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p-1 \rbrack]))(l))
     \end{array}                                                                                            \\
@@
 \lambda \theta.
-\overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])}                                                                                         \\
-      (\ap \overrightarrow{\cohf[n][p][r][0][\omega][\theta]} (\ap \overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta](\depscoht[n][\lbrack 0,p-1 \rbrack])} (\cohp[n][p][q][r][\epsilon][\omega](l_\theta)))) \\
+\overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])(d)}                                                                                         \\
+      (\ap \overrightarrow{\cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))(d))}\\ (\ap \overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)} \\(\cohp[n][p][q][r][\epsilon][\omega](l_\theta)))) \\
     \end{array}
@@
   \begin{array}{l}
-      \Pi q \leq n-p.\,\Pi r \leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.                                                          \\
-      \cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))) \circ \\
+      \Pi q \leq n-p.\,\Pi r \leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.\,\Pi d.                                                          \\
+      \cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))(d)) \circ \\
       \ap\restrf[n][p][r][\omega](\cohf[n+1][p][q+1][0][\epsilon][\theta]
-      (\depscoht[n][p]))
+      (\depscoht[n][p])(d))
       \circ                                                                                                                            \\
-      \cohf[n][p][q][r][\epsilon][\omega](\restrf[n+2][p][0][\theta](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))) =       \\
+      \cohf[n][p][q][r][\epsilon][\omega](\restrf[n+2][p][0][\theta](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))(d)) =       \\
       \ap\restrf[n][p][0][\theta](\cohf[n+1][p][q+1][r+1][\epsilon][\omega]
-      (\depscoht[n][p]))
+      (\depscoht[n][p])(d))
       \circ                                                                                                                            \\
-      \cohf[n][p][q][0][\epsilon][\theta](\restrf[n+2][p][r+1][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack])))
+      \cohf[n][p][q][0][\epsilon][\theta](\restrf[n+2][p][r+1][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))(d))
       \circ                                                                                                                            \\
       \ap\restrf[n][p][q][\epsilon](\cohf[n+1][p][r][0][\omega][\theta]
-      (\depscoht[n][p]))
+      (\depscoht[n][p])(d))
     \end{array}
@@
 \end{equation*}
-and where the functoriality of equality and transport was used to go from (omitting the $\framep$ argument of $\restrp$ and the deps argument)
+and where the functoriality of equality and transport was used to go from (omitting the $\framep$ argument of $\restrp$ and the deps argument):
 \begin{equation*}
@@
 \end{equation*}
-to
+to:
 \begin{equation*}
@@
       \overrightarrow{\cohf[n][p][q][0][\epsilon][\theta]}(\restrp[n][p][q][\epsilon] \\
-      (\overrightarrow{\cohf[n+1][p][r][0][\omega][\theta]}\restrp[n+1][p][r][\omega](l_\theta)))
+      (\overrightarrow{\cohf[n+1][p][r][0][\omega][\theta]}(\restrp[n+1][p][r][\omega](l_\theta))))
     \end{array} & =_{\cohf[n+1][p][q+1][r+1][\epsilon][\omega]} &
@@
       \overrightarrow{\cohf[n][p][r][0][\omega][\theta]}(\restrp[n][p][r][\omega] \\
-      (\overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta]}\restrp[n+1][p][q+1][\epsilon](l_\theta)))
+      (\overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta]}(\restrp[n+1][p][q+1][\epsilon](l_\theta))))
     \end{array}
@@
 \end{equation*}
-
-From which we can deduce $\cohp[n+1][\lbrack 0,p-1 \rbrack]$ for $p \leq n+2$ again by a second recursion, this time on $p$:
+where we again implicitly used that equalities in a $\Sigma$-type are equivalent to a $\Sigma$-type of the underlying equalities, componentwise.
+
+From the latter we can deduce $\cohp[n+1][\lbrack 0,p-1 \rbrack]$ for $p \leq n+2$, again by a second recursion, this time on $p$:
 
@@
   \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$.
-  \item $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ comes from $\fulldepscohs[n](E)(E')$ and $\cohp[n][\lbrack 0,n \rbrack](E)(E')$.
+  \item we define $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ from $\fulldepscohs[n](E)(E')$ and $\cohp[n][\lbrack 0,n \rbrack](E)(E')$.
   \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$.
-  \item $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
+  \item we define $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
   \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$.

### 2025-12-25 paper/paper.tex
Typos, clarifications
Attempt to develop an informative introduction on parametricity

@@
 \begin{abstract}
-  In a previous paper, we gave equations describing the construction of semi-simplicial and semi-cubical sets via iterated parametricity.
-The construction was formalised in the Rocq (formerly, Coq) proof assistant building $n$-truncated sets using an induction on a large structure embedding equational reasoning.
-
-  The current paper describes a new and lighter presentation of the construction where equational reasoning is replaced by definition.
-Being lighter, it can now be described in full details, closely following the corresponding new machine-checked formalisation.
+  Reynolds' parametricity originally eequips types with binary propositional relations over the types.
+Such relations can be taken proof-relevant, or unary, and described either in an indexed or fibered way.
+Parametricity can be iterated, and when types are sets, this results in an interpretation of sets as augmented semi-simplicial sets (unary case) or semi-cubical sets (binary case).
+  In a previous paper, we gave equations describing $n$-ary iterated parametricity in indexed form.
+The construction was formalised in the Rocq (formerly, Coq) proof assistant using a rather complex induction on a large structure embedding equational reasoning.
+
+  The current paper analyses the very dependent recursive structure of the equations of the former paper leading to a new terse presentation of the construction where all equational reasoning is replaced by definitions.
+Now reduced to its computational essence, it can be described in full details, closely following the corresponding new machine-checked formalisation.
 \end{abstract}
@@
 \section{Introduction}
-In the previous paper~\citep{hr25}, we described the construction of augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity, meaning that instead of the following illustration of the cubical case (upto faces identities),
+
+\paragraph*{Parametricity and its ramifications.}
+
+Introduced by Reynolds in the context of programming language semantics~\cite{Reynolds}, relational parametricity happens to be connected to several similar concepts in logic and mathematics.
+Associating binary propositional relations to types in its original formulation, it can also associate proof-relevant relations~\cite{GhaniNordvallOrsanigo16} or unary relations, that is predicates (proof-irrelevant case) or families (relevant case).
+These unary or binary, relevant or proof-irrelevant relations express what it means to belong in a type (unary case) or to be equal in a type (binary case) from an observational point of view.
+For instance, the canonical predicate associated to $A \rightarrow B$ is the predicate over functions $f$ in $A \rightarrow B$ such that, for all $a$ in the canonical predicate associated to $A$, $f(a)$ is in the canonical predicate associated to $B$.
+And, similarly, the canonical relation associated to $A \rightarrow B$ is the relations over functions $f$ and $f'$ in $A \rightarrow B$ such that, for all $a$ and $a'$ related through the canonical relation associated to $A$, $f(a)$and $f'(a')$ are related through the canonical relation associated to $B$.
+
+\newcommand{\real}{\textsf{r}}
+
+From the point of view of realisability, unary parametricity over a language is a realisability using the language itself as language of realisers.
+Like parametricity, realisability can be expressed in a syntactic way, that is as an interpretation from one language to another (i.e.
+mapping an expression $t$ of $\vdash A$ in some formal system to a derivation $t^*$ of $\vdash' |t| \real A$ in some other formal system, for some program $|t|$ extracted from $t$ -- namely $t$ itself in the case of parametricity), or a semantic way\footnote{This distinction between syntactic realisability and semantic realisability is itself connected to the difference between relative and absolute consistency.
+In the relative case, consistency of a formal system is reduced to the consistency of another formal system, and this can be done in a very weak logical system such as Primitive Recursive Arithmetic (PRA).
+On the other side, in the absolute case, consistency of a formal system is reduced to the consistency of the language of discourse, which, by G\"odel incompleteness theorem, if actually consistent, necessarily has to be as strong as the modelled formal system.}, that is as an interpretation in the language of discourse, which we could call in term the ``metalanguage'' (i.e.
+interpreting $A$ as a set $\textbf{A}$ or a relation $=_A$ of the language of discourse and interpreting a derivation $t$ of $\vdash A$ as an expression $|t|$ such that, respectively, $|t| \in \textbf{A}$ or $|t| =_A |t|$).
+Thus, the comparison between parametricity and realisability includes the case of reducibility~\cite{Tait}, which is a semantic form of realisability.
+In the same vein, binary parametricity over a language can be seen as defining logical relations~\cite{Plotkin} over itself, since logical relations are a binary form of reducibility.
+
+\newcommand{\Prop}{\textsf{Prop}}
+\newcommand{\MySet}{\textsf{Set}}
+
+Parametricity, like realisability, reductibility, and logical relations, was most commonly handled in an indexed form, that is, using a type-theoretic language, considering predicates of type $A \rightarrow \Prop$, or families of type $A \rightarrow \MySet$, or relations of type $A \times A \rightarrow \Prop$, or relevant relations -- sometimes called \emph{correspondences} -- of type $A \times A \rightarrow \MySet$, where $\Prop$ and $\MySet$ are types representing, that is classifying -- in category theory terminology --, propositions or sets, respectively.
+Along the indexed-fibered correspondence, that is along the equivalence between the types $A \rightarrow \Prop$ and $\Sigma B:\MySet.
+(B \stackrel{inj}{\rightarrow} A)$ (proof-irrelevant case) and $A \rightarrow \MySet$ and $\Sigma B:\MySet.
+(B \rightarrow A)$ (proof-relevant case), for $A:\MySet$, everything told in the indexed form can morally also be told in fibered form.
+Such fibered approach to parametricity was for instance considered in Ghani \cite{Ghani...}, who also suggested to iterate parametricity.
+
+\paragraph*{Iterated parametricity.}
+
+A type-theoretic analysis of parametricity in unary indexed form was obtained in \cite{Moulin}, together with an interpretation in a ``unary'' form of cubical set, thus implicitly in fibered form, in \cite{BernardyCoquandMoulin}.
+The connection between iterated binary parametricity in fibered form and cubical sets can also be found in Johann and Sojakova~\cite{JohannSojakova}.
+In particular, it became clear at this point that iterated binary parametricity produces semi-cubical sets while it was also observed\footnote{The authors learned it from Hugo Moeneclaye and Thorsten Altenkirch.} that iterated unary parametricity produces augmented semi-simplicial sets.
+
+...
+
+In a previous paper~\citep{hr25}, we exploited this correspondence to construct at the same time augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity.
+That is, instead of the following illustration of the cubical case (upto faces identities),
 
@@
       \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d.\,\Pi l.                                                             \\
-      \restrl[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(\restrl[n+1][p][r][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p-1 \rbrack]))(l))\\ =_{\cohf[n+1][p][r+1][q+1][\epsilon][\omega](\depscoht[n][\lbrack 0,p-1 \rbrack])} \\
+      \restrl[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(\restrl[n+1][p][r][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p-1 \rbrack]))(l))\\ =_{\cohf[n+1][p][r+1][q+1][\epsilon][\omega](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)} \\
       \restrl[n][p][r][\omega](\depscohs[n][\lbrack 0,p-1 \rbrack])(\restrl[n+1][p][q+1][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p-1 \rbrack]))(l))
@@
 \end{equation*}
-and where the functoriality of equality and transport was used to go from (omitting the $\framep$ argument of $\restrp$ and the deps argument):
+and where the functoriality of equality and transport was used to go from (omitting the $\framep$ argument and the deps argument of $\restrp$ and $\cohf$):
 \begin{equation*}

### 2025-12-26 paper/paper.tex
Intro: Minor corrections + synthetic table

@@
 From the point of view of realisability, unary parametricity over a language is a realisability using the language itself as language of realisers.
-Like parametricity, realisability can be expressed in a syntactic way, that is as an interpretation from one language to another (i.e.
-mapping an expression $t$ of $\vdash A$ in some formal system to a derivation $t^*$ of $\vdash' |t| \real A$ in some other formal system, for some program $|t|$ extracted from $t$ -- namely $t$ itself in the case of parametricity), or a semantic way\footnote{This distinction between syntactic realisability and semantic realisability is itself connected to the difference between relative and absolute consistency.
+Like parametricity, realisability can be expressed in a \emph{syntactic} way, that is as an interpretation from one language to another (i.e.
+mapping an expression $t$ of $\vdash A$ in some formal system to a derivation $t^*$ of $\vdash' |t| \real A$ in some other formal system, for some program $|t|$ extracted from $t$ -- namely $t$ itself in the case of parametricity), or a \emph{semantic} way\footnote{This distinction between syntactic realisability and semantic realisability is itself connected to the difference between relative and absolute consistency.
 In the relative case, consistency of a formal system is reduced to the consistency of another formal system, and this can be done in a very weak logical system such as Primitive Recursive Arithmetic (PRA).
@@
 interpreting $A$ as a set $\textbf{A}$ or a relation $=_A$ of the language of discourse and interpreting a derivation $t$ of $\vdash A$ as an expression $|t|$ such that, respectively, $|t| \in \textbf{A}$ or $|t| =_A |t|$).
-Thus, the comparison between parametricity and realisability includes the case of reducibility~\cite{Tait}, which is a semantic form of realisability.
-In the same vein, binary parametricity over a language can be seen as defining logical relations~\cite{Plotkin} over itself, since logical relations are a binary form of reducibility.
+Thus, the comparison between parametricity and realisability includes the case of \emph{reducibility}~\cite{Tait}, which is a semantic form of realisability, also known as \emph{glueing} in the context of category theory.
+In the same vein, binary parametricity over a language can be seen as defining \emph{logical relations}~\cite{Plotkin} over itself, since logical relations are a binary form of reducibility.
 
@@
 
-Parametricity, like realisability, reductibility, and logical relations, was most commonly handled in an indexed form, that is, using a type-theoretic language, considering predicates of type $A \rightarrow \Prop$, or families of type $A \rightarrow \MySet$, or relations of type $A \times A \rightarrow \Prop$, or relevant relations -- sometimes called \emph{correspondences} -- of type $A \times A \rightarrow \MySet$, where $\Prop$ and $\MySet$ are types representing, that is classifying -- in category theory terminology --, propositions or sets, respectively.
+Parametricity, like realisability, reducibility, and logical relations, was most commonly handled in an \emph{indexed} form, that is, using a type-theoretic language, considering predicates of type $A \rightarrow \Prop$, or families of type $A \rightarrow \MySet$, or relations of type $A \times A \rightarrow \Prop$, or relevant relations -- sometimes called \emph{correspondences} -- of type $A \times A \rightarrow \MySet$, where $\Prop$ and $\MySet$ are types representing, that is classifying -- in category theory terminology --, propositions or sets, respectively.
 Along the indexed-fibered correspondence, that is along the equivalence between the types $A \rightarrow \Prop$ and $\Sigma B:\MySet.
 (B \stackrel{inj}{\rightarrow} A)$ (proof-irrelevant case) and $A \rightarrow \MySet$ and $\Sigma B:\MySet.
-(B \rightarrow A)$ (proof-relevant case), for $A:\MySet$, everything told in the indexed form can morally also be told in fibered form.
+(B \rightarrow A)$ (proof-relevant case), for $A:\MySet$, everything told in the indexed form can morally also be told in \emph{fibered} form.
 Such fibered approach to parametricity was for instance considered in Ghani \cite{Ghani...}, who also suggested to iterate parametricity.
@@
 
-A type-theoretic analysis of parametricity in unary indexed form was obtained in \cite{Moulin}, together with an interpretation in a ``unary'' form of cubical set, thus implicitly in fibered form, in \cite{BernardyCoquandMoulin}.
-The connection between iterated binary parametricity in fibered form and cubical sets can also be found in Johann and Sojakova~\cite{JohannSojakova}.
-In particular, it became clear at this point that iterated binary parametricity produces semi-cubical sets while it was also observed\footnote{The authors learned it from Hugo Moeneclaye and Thorsten Altenkirch.} that iterated unary parametricity produces augmented semi-simplicial sets.
-
-...
+The internalisation of parametricity in unary indexed form was studied by \cite{Moulin,Bernardy} directly leading to a type theory of iterated parametricity.
+Such type theory could be interpreted in a ``unary'' form of cubical set~\cite{BernardyCoquandMoulin}, thus implicitly in fibered form since, in a binary cubical set (resp.
+in a unary cubical set and simplicial set as well), a set of segments over two points, that is a relevant relation, is given by first and second projection rather than as a function to $\MySet$ (resp.
+a family is given as a \emph{total space} projected over a set of points $A:\MySet$ rather than a family of type $A \rightarrow \MySet$.
+This connection between iterated binary parametricity in fibered form and cubical sets includes an identification of degeneracies and reflexivity proofs, which can also be found in Johann and Sojakova~\cite{JohannSojakova}.
+In particular, it became clear at this point that iterated binary parametricity (without reflexivity) produces semi-cubical sets while it was also observed\footnote{The authors learned it from Hugo Moeneclaye and Thorsten Altenkirch.} that iterated unary parametricity produces augmented semi-simplicial sets.
+
+$$
+\begin{tabular}{lllllll}
+                           &                            &                                 &                   & structure & kind of semantics \\
+ \hline
+ \multirow{6}{1cm}{unary}  & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant  & predicate &        reducibility \\
+                           &                            &                                 & relevant          & family & \\
+                           &                            & \multicolumn{2}{l}{iterated}                        & \emph{this work}       & \\
+                           & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant  & subobject & \\
+                           &                            &                                 & relevant          & fibration & \\
+                           &                            & \multicolumn{2}{l}{iterated}                        & augmented semi-simplicial set & \\
+ \hline
+ \multirow{6}{1cm}{binary} & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant  & relation & logical relation \\
+                           &                            &                                 & relevant          & correspondence (relevant relation) & \\
+                           &                            & \multicolumn{2}{l}{iterated}                        & \emph{this work}       & \\
+                           & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant  & fibered relation ? & \\
+                           &                            &                                 & relevant          & span & & \\
+                           &                            & \multicolumn{2}{l}{iterated}                        & semi-cubical set & \\
+ \hline
+\end{tabular}
+$$
 
 In a previous paper~\citep{hr25}, we exploited this correspondence to construct at the same time augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity.
-That is, instead of the following illustration of the cubical case (upto faces identities),
+That is, instead of the following illustration of the semi-cubical case (upto faces identities),
 
@@
 \end{equation*}
-we consider a family of families as shown below:
+we consider a family of relevant relations as shown below:
 \begin{equation*}

### 2025-12-29 paper/paper.tex
Bib item names

@@
 
-Introduced by Reynolds in the context of programming language semantics~\cite{Reynolds}, relational parametricity happens to be connected to several similar concepts in logic and mathematics.
+Introduced by Reynolds in the context of programming language semantics~\cite{reynolds83}, relational parametricity happens to be connected to several similar concepts in logic and mathematics.
 Associating binary propositional relations to types in its original formulation, it can also associate proof-relevant relations~\cite{GhaniNordvallOrsanigo16} or unary relations, that is predicates (proof-irrelevant case) or families (relevant case).
@@
 The internalisation of parametricity in unary indexed form was studied by \cite{Moulin,Bernardy} directly leading to a type theory of iterated parametricity.
-Such type theory could be interpreted in a ``unary'' form of cubical set~\cite{BernardyCoquandMoulin}, thus implicitly in fibered form since, in a binary cubical set (resp.
+Such type theory could be interpreted in a ``unary'' form of cubical set~\cite{bernardy15}, thus implicitly in fibered form since, in a binary cubical set (resp.
 in a unary cubical set and simplicial set as well), a set of segments over two points, that is a relevant relation, is given by first and second projection rather than as a function to $\MySet$ (resp.
 a family is given as a \emph{total space} projected over a set of points $A:\MySet$ rather than a family of type $A \rightarrow \MySet$.
-This connection between iterated binary parametricity in fibered form and cubical sets includes an identification of degeneracies and reflexivity proofs, which can also be found in Johann and Sojakova~\cite{JohannSojakova}.
+This connection between iterated binary parametricity in fibered form and cubical sets includes an identification of degeneracies and reflexivity proofs, which can also be found in Johann and Sojakova~\cite{johann17}.
 In particular, it became clear at this point that iterated binary parametricity (without reflexivity) produces semi-cubical sets while it was also observed\footnote{The authors learned it from Hugo Moeneclaye and Thorsten Altenkirch.} that iterated unary parametricity produces augmented semi-simplicial sets.

### 2025-12-29 paper/paper.tex
paper: minor change, whitespace
paper: strip a block of equations

@@
 
-\newcommand{\Prop}{\textsf{Prop}}
-\newcommand{\MySet}{\textsf{Set}}
-
-Parametricity, like realisability, reducibility, and logical relations, was most commonly handled in an \emph{indexed} form, that is, using a type-theoretic language, considering predicates of type $A \rightarrow \Prop$, or families of type $A \rightarrow \MySet$, or relations of type $A \times A \rightarrow \Prop$, or relevant relations -- sometimes called \emph{correspondences} -- of type $A \times A \rightarrow \MySet$, where $\Prop$ and $\MySet$ are types representing, that is classifying -- in category theory terminology --, propositions or sets, respectively.
-Along the indexed-fibered correspondence, that is along the equivalence between the types $A \rightarrow \Prop$ and $\Sigma B:\MySet.
-(B \stackrel{inj}{\rightarrow} A)$ (proof-irrelevant case) and $A \rightarrow \MySet$ and $\Sigma B:\MySet.
-(B \rightarrow A)$ (proof-relevant case), for $A:\MySet$, everything told in the indexed form can morally also be told in \emph{fibered} form.
+Parametricity, like realisability, reducibility, and logical relations, was most commonly handled in an \emph{indexed} form, that is, using a type-theoretic language, considering predicates of type $A \rightarrow \Prop$, or families of type $A \rightarrow \Set$, or relations of type $A \times A \rightarrow \Prop$, or relevant relations -- sometimes called \emph{correspondences} -- of type $A \times A \rightarrow \Set$, where $\Prop$ and $\Set$ are types representing, that is classifying -- in category theory terminology --, propositions or sets, respectively.
+Along the indexed-fibered correspondence, that is along the equivalence between the types $A \rightarrow \Prop$ and $\Sigma B:\Set.
+(B \stackrel{inj}{\rightarrow} A)$ (proof-irrelevant case) and $A \rightarrow \Set$ and $\Sigma B:\Set.
+(B \rightarrow A)$ (proof-relevant case), for $A:\Set$, everything told in the indexed form can morally also be told in \emph{fibered} form.
 Such fibered approach to parametricity was for instance considered in Ghani \cite{Ghani...}, who also suggested to iterate parametricity.
@@
 Such type theory could be interpreted in a ``unary'' form of cubical set~\cite{bernardy15}, thus implicitly in fibered form since, in a binary cubical set (resp.
-in a unary cubical set and simplicial set as well), a set of segments over two points, that is a relevant relation, is given by first and second projection rather than as a function to $\MySet$ (resp.
-a family is given as a \emph{total space} projected over a set of points $A:\MySet$ rather than a family of type $A \rightarrow \MySet$.
-This connection between iterated binary parametricity in fibered form and cubical sets includes an identification of degeneracies and reflexivity proofs, which can also be found in Johann and Sojakova~\cite{johann17}.
+in a unary cubical set and simplicial set as well), a set of segments over two points, that is a relevant relation, is given by first and second projection rather than as a function to $\Set$ (resp.
+a family is given as a \emph{total space} projected over a set of points $A:\Set$ rather than a family of type $A \rightarrow \Set$.
+This connection between iterated binary parametricity in fibered form and cubical sets includes an identification of degeneracies and reflexivity proofs, which can also be found in \cite{johann17}.
 In particular, it became clear at this point that iterated binary parametricity (without reflexivity) produces semi-cubical sets while it was also observed\footnote{The authors learned it from Hugo Moeneclaye and Thorsten Altenkirch.} that iterated unary parametricity produces augmented semi-simplicial sets.
 
-$$
 \begin{tabular}{lllllll}
@@
 \end{tabular}
-$$
 
@@
 Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
-This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}\lbrack 0,0 \rbrack$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
+This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
 
@@
 
-Since $\restrf[n][p]$ is referring to $\framep[n][p]$ and $\framep[n-1][p]$, and $\cohf[n][p]$ is referring to $\restrf[n][p]$ and $\restrf[n-1][p]$, thus also to $\framep[n][p]$, $\framep[n-1][p]$ and $\framep[n-2][p]$, we built all of these 6 components at the same time.
-But equations were also needed to state the properties of $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ so that we were building by induction on $n$, for any $D:\Xto{m}{n}$, the following block of information:
-
-\begin{equation*}
-  \begin{array}{lclr}
-    \framep[n][p]      & : & \U                                                                                                                 & \mbox{for all $p\leq n$}   \\
-    \framep[n-1][p]    & : & \U                                                                                                                 & \mbox{for all $p\leq n-1$} \\
-    \framep[n-2][p]    & : & \U                                                                                                                 & \mbox{for all $p\leq n-2$} \\
-    \restrf[n][p]      & : & \Pi q.\, \Pi \omega.\, \framep[n][p] \rightarrow \framep[n-1][p]                                                   & \mbox{for all $p\leq n$}   \\
-    \restrf[n-1][p]    & : & \Pi q.\, \Pi \omega.\, \framep[n-1][p] \rightarrow \framep[n-2][p]                                                 & \mbox{for all $p\leq n-1$} \\
-    \cohf[n][p]        & : & \Pi qr\epsilon\omega.\, \restrf[n-1][p][q][\epsilon] \circ \restrf[n][p][\omega][r] =                                                           \\
-                       &   & \restrf[n-1][p][r][\omega] \circ \restrf[n][p][\epsilon][q+1]                                                      & \mbox{for all $p\leq n$}   \\
-    \mathsf{hypF0}     & : & \framep[n][0]         = \unitpoint
-    \\
-    \mathsf{hypFS}     & : & \framep[n][p+1]       = \Sigma d: \framep[n+1][p]. \Pi \omega.\, \painting[n][p] (\restrf[n+1][p](d))              & \mbox{for all $p\leq n-1$} \\
-    \mathsf{hypPrevF0} & : & \framep[n-1][0]                                                                                       = \unitpoint                              \\
-    \mathsf{hypPrevFS} & : & \framep[n-1][p+1] = \Sigma d: \framep[n][p]. \Pi \omega.\, \painting[n-1][p] (\restrf[n][p](d))                    & \mbox{for all $p\leq n-2$} \\
-    \mathsf{hypRF0}    & : & \restrf[n][0]        = \ldots \texttt{depending on hypF0}                                                                                       \\
-    \mathsf{hypRFS}    & : & \restrf[n][p+1]      = \ldots \texttt{depending on hypFS and hypPrevFS}                                            & \mbox{for all $p\leq n-1$} \\
-    \ldots             &   & \texttt{fields for painting, restrf, cohp}
-  \end{array}
-\end{equation*}
-
-In the current paper and associated formalisation, we switch the point
-of view, take $\framep[n-2][p]$ $\painting[n-2][p]$, $\restrf[n-1][p]$
-and $\restrp[n-1][p]$ as references and rename them respectively as
-$\framep[n][p]$, $\painting[n][p]$, $\restrf[n][p]$ and
-$\restrp[n][p]$. We replace the equational properties of $\framep[n][p]$,
-$\framep[n-1][p]$, $\restrf[n][p]$, $\painting[n][p]$,
-$\painting[n-1][p]$ and $\restrp[n][p]$ with definitions, renaming them
-respectively to $\framep[n+2][p]$, $\framep[n+1][p]$,
-$\restrf[n+1][p]$, $\painting[n+2][p]$, $\painting[n+1][p]$ and
-$\restrp[n+1][p]$. This means that we build instead by induction a block of the form:
+In the current paper and associated formalisation, we take $\framep[n-2][p]$ $\painting[n-2][p]$, $\restrf[n-1][p]$ and $\restrp[n-1][p]$ as references and rename them respectively as $\framep[n][p]$, $\painting[n][p]$, $\restrf[n][p]$ and $\restrp[n][p]$.
+We replace the equational properties of $\framep[n][p]$, $\framep[n-1][p]$, $\restrf[n][p]$, $\painting[n][p]$, $\painting[n-1][p]$ and $\restrp[n][p]$ with definitions, renaming them respectively to $\framep[n+2][p]$, $\framep[n+1][p]$, $\restrf[n+1][p]$, $\painting[n+2][p]$, $\painting[n+1][p]$ and $\restrp[n+1][p]$.
+This means that we build instead by induction a block of the form:
 
@@
 
-Assuming $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\painting[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$, we can
-mutually define the types $\restrftype[n][\lbrack 0,p-1 \rbrack]$ of frame
-restrictions together with $\framep[n+1][\lbrack 0,p-1 \rbrack]$ as a function from
-$\restrf[n][\lbrack 0,p-1 \rbrack]$, introducing also abbreviations for the types
-and definitions of layers, as well as for the combination of sequences
-of $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and
-$\restrf[n][\lbrack 0,p-1 \rbrack]$ in one block, which we call
-$\depstype[n][\lbrack 0,p-1 \rbrack]$:
+Assuming $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\painting[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$, we can mutually define the types $\restrftype[n][\lbrack 0,p-1 \rbrack]$ of frame restrictions together with $\framep[n+1][\lbrack 0,p-1 \rbrack]$ as a function from $\restrf[n][\lbrack 0,p-1 \rbrack]$, introducing also abbreviations for the types and definitions of layers, as well as for the combination of sequences of $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$ in one block, which we call $\depstype[n][\lbrack 0,p-1 \rbrack]$:
 
@@
               \restrf[n+1][\lbrack 0,p \rbrack][q][\epsilon]
-              (\depscohs[n][\lbrack 0,p-1 \rbrack]),           \\
+              (\depscohs[n][\lbrack 0,p-1 \rbrack]),
               \lambda q.\lambda \epsilon.\lambda (d,l).        \\
@@
       \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d.\,\Pi l.                                                                                 \\
-      \restrl[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(\restrl[n+1][p][r][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p-1 \rbrack]))(l))\\ =_{\cohf[n+1][p][r+1][q+1][\epsilon][\omega](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)} \\
+      \restrl[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(\restrl[n+1][p][r][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p-1 \rbrack]))(l)) \\ =_{\cohf[n+1][p][r+1][q+1][\epsilon][\omega](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)} \\
       \restrl[n][p][r][\omega](\depscohs[n][\lbrack 0,p-1 \rbrack])(\restrl[n+1][p][q+1][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p-1 \rbrack]))(l))
@@
     \begin{array}{l}
-      \lambda d.
-\lambda l.
-\lambda \theta.
-\overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])(d)}                                                                                         \\
-      (\ap \overrightarrow{\cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))(d))}\\ (\ap \overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)} \\(\cohp[n][p][q][r][\epsilon][\omega](l_\theta)))) \\
+      \lambda d. \lambda l. \lambda \theta. \overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])(d)}                             \\
+      (\ap \overrightarrow{\cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))(d))} \\ (\ap \overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)} \\(\cohp[n][p][q][r][\epsilon][\omega](l_\theta)))) \\
     \end{array}

### 2025-12-29 paper/paper.tex
paper: s/tabular/tabularx/
paper: tweak experimental table

@@
 This connection between iterated binary parametricity in fibered form and cubical sets includes an identification of degeneracies and reflexivity proofs, which can also be found in \cite{johann17}.
-In particular, it became clear at this point that iterated binary parametricity (without reflexivity) produces semi-cubical sets while it was also observed\footnote{The authors learned it from Hugo Moeneclaye and Thorsten Altenkirch.} that iterated unary parametricity produces augmented semi-simplicial sets.
-
-\begin{tabular}{lllllll}
-                            &                              &                                 &                               & structure                          & kind of semantics   \\
-  \hline
+In particular, it became clear at this point that iterated binary parametricity (without reflexivity) produces semi-cubical sets while it was also observed\footnote{The authors learned it from Hugo Moeneclaey and Thorsten Altenkirch.} that iterated unary parametricity produces augmented semi-simplicial sets.
+
+\begin{tabularx}{\linewidth}{lYcYYYl}
+  \toprule
+  arity                     & formalisation style          & iteration                       & relevance                     & structure          & name of semantics   \\
+  \midrule
   \multirow{6}{1cm}{unary}  & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & predicate          & reducibility        \\
@@
                             &                              & \multicolumn{2}{l}{iterated}    & augmented semi-simplicial set &                                          \\
-  \hline
+  \midrule
   \multirow{6}{1cm}{binary} & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & relation           & logical relation    \\
-                            &                              &                                 & relevant                      & correspondence (relevant relation) &                     \\
+                            &                              &                                 & relevant                      & correspondence     &                     \\
                             &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}              &                                          \\
@@
                             &                              & \multicolumn{2}{l}{iterated}    & semi-cubical set              &                                          \\
-  \hline
-\end{tabular}
+  \bottomrule
+\end{tabularx}
 

### 2025-12-29 paper/paper.tex
paper: strip last column in comparison table

@@
 
-\begin{tabularx}{\linewidth}{lYcYYYl}
+\begin{tabularx}{\linewidth}{lYcYYl}
   \toprule
-  arity                     & formalisation style          & iteration                       & relevance                     & structure          & name of semantics   \\
+  arity                     & formalisation style          & iteration                       & relevance                     & logical structure    \\
   \midrule
-  \multirow{6}{1cm}{unary}  & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & predicate          & reducibility        \\
-                            &                              &                                 & relevant                      & family             &                     \\
-                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}              &                                          \\
-                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & subobject          &                     \\
-                            &                              &                                 & relevant                      & fibration          &                     \\
-                            &                              & \multicolumn{2}{l}{iterated}    & augmented semi-simplicial set &                                          \\
+  \multirow{6}{1cm}{unary}  & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & predicate            \\
+                            &                              &                                 & relevant                      & family               \\
+                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}                                     \\
+                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & subobject            \\
+                            &                              &                                 & relevant                      & fibration            \\
+                            &                              & \multicolumn{2}{l}{iterated}    & augmented semi-simplicial set                        \\
   \midrule
-  \multirow{6}{1cm}{binary} & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & relation           & logical relation    \\
-                            &                              &                                 & relevant                      & correspondence     &                     \\
-                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}              &                                          \\
-                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & fibered relation ? &                     \\
-                            &                              &                                 & relevant                      & span               &                   & \\
-                            &                              & \multicolumn{2}{l}{iterated}    & semi-cubical set              &                                          \\
+  \multirow{6}{1cm}{binary} & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & relation             \\
+                            &                              &                                 & relevant                      & correspondence       \\
+                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}                                     \\
+                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & fibered relation ?   \\
+                            &                              &                                 & relevant                      & span               & \\
+                            &                              & \multicolumn{2}{l}{iterated}    & semi-cubical set                                     \\
   \bottomrule

### 2025-12-29 paper/paper.tex
paper: improvements to comparison table

@@
 
-\begin{tabularx}{\linewidth}{lYcYYl}
+\begin{tabularx}{\linewidth}{cYcYYl}
   \toprule
@@
   \midrule
-  \multirow{6}{1cm}{unary}  & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & predicate            \\
+  \multirow{6}{0.6cm}{unary}  & \multirow{3}{1cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & predicate                       \\
                               &                            &                                 & relevant         & family                          \\
-                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}                                     \\
-                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & subobject            \\
+                              &                            & iterated                        & relevant         & \emph{this work}                \\
+                              & \multirow{3}{1cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & subobject                       \\
                               &                            &                                 & relevant         & fibration                       \\
-                            &                              & \multicolumn{2}{l}{iterated}    & augmented semi-simplicial set                        \\
+                              &                            & iterated                        & relevant         & augmented semi-simplicial set   \\
   \midrule
-  \multirow{6}{1cm}{binary} & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & relation             \\
+  \multirow{6}{0.6cm}{binary} & \multirow{3}{1cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & relation                        \\
                               &                            &                                 & relevant         & correspondence                  \\
-                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}                                     \\
-                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & fibered relation ?   \\
+                              &                            & iterated                        & relevant         & \emph{this work}                \\
+                              & \multirow{3}{1cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & fibered relation ?              \\
                               &                            &                                 & relevant         & span                          & \\
-                            &                              & \multicolumn{2}{l}{iterated}    & semi-cubical set                                     \\
+                              &                            & iterated                        & relevant         & semi-cubical set                \\
   \bottomrule
@@
 
-In a previous paper~\citep{hr25}, we exploited this correspondence to construct at the same time augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity.
+In~\citep{hr25}, this correspondence was exploited to construct at the same time augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity.
 That is, instead of the following illustration of the semi-cubical case (upto faces identities),
@@
 \end{equation*}
-we consider a family of relevant relations as shown below:
+a family of relevant relations was considered, as shown below:
 \begin{equation*}
@@
 \renewcommandx{\cohp}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][][][][][#9]}
+
+For $\nu$ an arity, that is $1$ in the case of predicates, families and augmented semi-simplicial sets or $2$ in the case of relations, correspondences and semi-cubical sets, such sequence of was called a $\nu$-set.
+Equations specifying such sequence of relevant relations were given in \cite{hr25}.
+Because of the dependency of $E_{n+1}$ into all $E_p$ for $p \leq n$, the family could not be expressed as a function.
+Instead, it was expressed as a stream whose $(n+1)$-th element $E_{n+1}$ was dependent on the bundle of all previous elements of the stream.
 

### 2025-12-29 paper/paper.tex
paper: prose progress

@@
 
-The internalisation of parametricity in unary indexed form was studied by \cite{Moulin,Bernardy} directly leading to a type theory of iterated parametricity.
-Such type theory could be interpreted in a ``unary'' form of cubical set~\cite{bernardy15}, thus implicitly in fibered form since, in a binary cubical set (resp.
+The internalisation of parametricity in unary indexed form was studied by \cite{bernardy12} directly leading to a type theory of iterated parametricity.
+Such type theory could be interpreted in a ``unary'' form of cubical set~\citep{bernardy15}, thus implicitly in fibered form since, in a binary cubical set (resp.
 in a unary cubical set and simplicial set as well), a set of segments over two points, that is a relevant relation, is given by first and second projection rather than as a function to $\Set$ (resp.
@@
 
-\begin{tabularx}{\linewidth}{cYcYYl}
+\begin{tabularx}{0.94\linewidth}{cYcYYl}
   \toprule
@@
   \midrule
-  \multirow{6}{0.6cm}{unary}  & \multirow{3}{1cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & predicate                       \\
+  \multirow{6}{0.4cm}{unary}  & \multirow{3}{1cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & predicate                       \\
                               &                            &                                 & relevant         & family                          \\
@@
   \midrule
-  \multirow{6}{0.6cm}{binary} & \multirow{3}{1cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & relation                        \\
+  \multirow{6}{0.4cm}{binary} & \multirow{3}{1cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & relation                        \\
                               &                            &                                 & relevant         & correspondence                  \\
                               &                            & iterated                        & relevant         & \emph{this work}                \\
-                              & \multirow{3}{1cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & fibered relation ?              \\
+                              & \multirow{3}{1cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant & fibered relation                \\
                               &                            &                                 & relevant         & span                          & \\
@@
 
-In~\citep{hr25}, this correspondence was exploited to construct at the same time augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity.
+In \cite{hr25}, this correspondence was exploited to construct at the same time augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity.
 That is, instead of the following illustration of the semi-cubical case (upto faces identities),
@@
 For $\nu$ an arity, that is $1$ in the case of predicates, families and augmented semi-simplicial sets or $2$ in the case of relations, correspondences and semi-cubical sets, such sequence of was called a $\nu$-set.
-Equations specifying such sequence of relevant relations were given in \cite{hr25}.
+Equations specifying $\nu$-sets were given in \cite{hr25}.
 Because of the dependency of $E_{n+1}$ into all $E_p$ for $p \leq n$, the family could not be expressed as a function.
 Instead, it was expressed as a stream whose $(n+1)$-th element $E_{n+1}$ was dependent on the bundle of all previous elements of the stream.
-
-A $\nu$-set in indexed form is a sequence of families of $\U$, that is $\U[m]$ for some universe level $m$. We call such sequence a $\nu$-set at level $m$, whose type thus lives in $\U[m+1]$.
-
-Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets: the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$.
-Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$.
-This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.
-
-The definition of the type of a $n$-truncated $\nu$-set is in turn described in table~\ref{tab:core}.
-In the infinite sequence of type families representing a $\nu$-set, the $n$-th component is a type dependent over a $\fullframe$.
+Such a bundle was called $\Xto{m}{n}$ while the residual stream of all $E_{n}$, $E_{n+1}$, ..., all of them precisely dependent on the bundle $E:\Xto{m}{n}$ of previous $E_0$, ..., $E_{n-1}$, was called $\Xfrom{m}{n}{D}$.
+The type of $E_n$, also dependent on a bundle $D:\Xto{m}{n}$, was denoted $\Xcomp{m}{n}[D=\D]$, as shown on tables~\ref{tab:coind} and~\ref{tab:core}.
+When $n$ is $0$, $\Xto{m}{0}$ is degenerated, that is reduced to the canonical inhabitant $\kstar$ of $\unittype$.
+Then, $\Xfrom{m}{0}{\kstar}$ denotes the full stream $E_0, E_1, \ldots$.
+
+The type $\Xcomp{m}{n}[D=E_0,\ldots,E_{n-1}]$ of $E_n$ represents a family whose type can be presented into the form $\fullframe(E_0,\ldots,E_{n-1}) \rightarrow \U$ where $\fullframe$ collects all the components on which $E_n$ is expected to depend.
 It is recursively defined in table~\ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
@@
 The proof of this commutation is worth being made explicit, which we do in table~\ref{tab:coh} using proof-term notations.
-The proof requires an induction on the dimension and on the structure of $\framep$, $\layer$, and $\painting$.
+The proof is by recursion on the structure of $\framep$, $\layer$, and $\painting$.
 This is what $\cohf$ does using auxiliary proofs $\cohl$ and $\cohp$.
-Even though it looks independent of the definitions from the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.
-More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be defined in one go by induction on $p$.
-Also, each of $\painting$, $\restrp$, and $\cohp$ is built by induction from $p$ to $n$.
-The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but the converse dependency is only on lower $n$, so this is well-founded.
-Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations.
-
 Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that the construction builds an effective sequence of types not mentioning coherences anymore.
-\\
+
+TODO: say that the table are relative to ETT and that many type coercions are implicit.
+
+Due to the intricate dependencies, the reason the whole construction is recursively well-defined is not simple.
+The formalisation in \cite{hr25} was recursively building a complex structure involving $3$ levels of the construction at once.
+In the present paper, we untangle the previous construction, making the dependencies explicit, and the new construction lends itself to a simple and complete explanation.
 

### 2025-12-29 paper/paper.tex
paper, tab*: fix order of epislon, omega in tables

@@
 Such a bundle was called $\Xto{m}{n}$ while the residual stream of all $E_{n}$, $E_{n+1}$, ..., all of them precisely dependent on the bundle $E:\Xto{m}{n}$ of previous $E_0$, ..., $E_{n-1}$, was called $\Xfrom{m}{n}{D}$.
-The type of $E_n$, also dependent on a bundle $D:\Xto{m}{n}$, was denoted $\Xcomp{m}{n}[D=\D]$, as shown on tables~\ref{tab:coind} and~\ref{tab:core}.
+The type of $E_n$, also dependent on a bundle $D:\Xto{m}{n}$, was denoted $\Xcomp{m}{n}[D=\D]$, as shown on tables~\ref{tab:coind} and~\ref{tab:core}, using type theory as language of discourse.
 When $n$ is $0$, $\Xto{m}{0}$ is degenerated, that is reduced to the canonical inhabitant $\kstar$ of $\unittype$.
@@
 Notably, the definition of $\restrl$ relies on an equality expressing the commutation of the composition of two $\restrf$.
-The proof of this commutation is worth being made explicit, which we do in table~\ref{tab:coh} using proof-term notations.
+The proof of this commutation is worth being made explicit, which we do in table~\ref{tab:coh} using proof-term notations\footnote{We however omit type conversions}.
 The proof is by recursion on the structure of $\framep$, $\layer$, and $\painting$.

### 2025-12-29 paper/paper.tex
paper: more prose

--- 2025-12-29 paper/paper.tex
@@
 Such a bundle was called $\Xto{m}{n}$ while the residual stream of all $E_{n}$, $E_{n+1}$, ..., all of them precisely dependent on the bundle $E:\Xto{m}{n}$ of previous $E_0$, ..., $E_{n-1}$, was called $\Xfrom{m}{n}{D}$.
-The type of $E_n$, also dependent on a bundle $D:\Xto{m}{n}$, was denoted $\Xcomp{m}{n}[D=\D]$, as shown on tables~\ref{tab:coind} and~\ref{tab:core}.
+The type of $E_n$, also dependent on a bundle $D:\Xto{m}{n}$, was denoted $\Xcomp{m}{n}[D=\D]$, as shown on tables~\ref{tab:coind} and~\ref{tab:core}, using an type theory as language of discourse.
 When $n$ is $0$, $\Xto{m}{0}$ is degenerated, that is reduced to the canonical inhabitant $\kstar$ of $\unittype$.
@@
 Notably, the definition of $\restrl$ relies on an equality expressing the commutation of the composition of two $\restrf$.
-The proof of this commutation is worth being made explicit, which we do in table~\ref{tab:coh} using proof-term notations.
+The proof of this commutation is worth being made explicit, which we do in table~\ref{tab:coh} using proof-term notations\footnote{We however omit type conversions, as if working in extensional type theory.
+E.g.
+the definition of $\restrl$ implicitly use $\cohf$ so that the type of $\restrp$ gets its expected type.}.
 The proof is by recursion on the structure of $\framep$, $\layer$, and $\painting$.
@@
 Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that the construction builds an effective sequence of types not mentioning coherences anymore.
-
-TODO: say that the table are relative to ETT and that many type coercions are implicit.
 

### 2025-12-29 paper/paper.tex
paper: some prose changes, structurally ready

@@
 
-The type $\Xcomp{m}{n}[D=E_0,\ldots,E_{n-1}]$ of $E_n$ represents a family whose type can be presented into the form $\fullframe(E_0,\ldots,E_{n-1}) \rightarrow \U$ where $\fullframe$ collects all the components on which $E_n$ is expected to depend.
+The type $\Xcomp{m}{n}[D=E_0,\ldots,E_{n-1}]$ of $E_n$ represents a family whose type can be presented into the form $\fullframe(E_0,\ldots,E_{n-1}) \rightarrow \U$ where $\fullframe$ collects all the dependencies of $E_n$.
 It is recursively defined in table~\ref{tab:frames}, using the auxiliary definitions of $\framep$, $\layer$ and $\painting$.
-A $\fullframe$ describes a boundary of a standard form (simplex, cube), which we decompose into $\layer$, and a $\painting$ corresponds to a filled frame.
-Notice that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table~\ref{tab:faces}, and this restriction operator is in turn defined using auxiliary definitions $\restrl$ and $\restrp$.
+A $\fullframe$ describes a boundary of a standard form (simplex, cube), which we decompose into $\layer$ themselves made of $\nu$ $\painting$ ($\nu=1$, $\nu=2$, ...), where a $\painting$ corresponds to a filled frame.
+Notice that the type $\layer$ relies on an operator of frame restriction $\restrf$ which is defined in table~\ref{tab:faces}, and this restriction operator is in turn defined using auxiliary definitions $\restrl$ and $\restrp$ (see \cite{hr25} for details).
 
@@
 
-In \citep{hr25}, the well-foundedness was justified by induction on $n$ and subinductions, one on $p$ to mutually build $\framep[n][p]$, $\restrf[n][p]$ and $\cohf[n][p]$, and three others to build each of $\painting[n][p]$, $\restrp[n][p]$ and $\cohp[n][p]$ by induction on $n-p$.
-
-In the current paper and associated formalisation, we take $\framep[n-2][p]$ $\painting[n-2][p]$, $\restrf[n-1][p]$ and $\restrp[n-1][p]$ as references and rename them respectively as $\framep[n][p]$, $\painting[n][p]$, $\restrf[n][p]$ and $\restrp[n][p]$.
-We replace the equational properties of $\framep[n][p]$, $\framep[n-1][p]$, $\restrf[n][p]$, $\painting[n][p]$, $\painting[n-1][p]$ and $\restrp[n][p]$ with definitions, renaming them respectively to $\framep[n+2][p]$, $\framep[n+1][p]$, $\restrf[n+1][p]$, $\painting[n+2][p]$, $\painting[n+1][p]$ and $\restrp[n+1][p]$.
-This means that we build instead by induction a block of the form:
+To build $\framep[n+1]$ from $\frame[n]$, it happens to be enough to assume the following built at level $n$:
 
@@
 \end{equation*}
-
-Turning $\framep[n+2][p]$, $\framep[n+1][p]$ and $\restrf[n+1][p]$ into definitions involves however circularities.
-To start with, the definition of $\framep[n+1][p]$, which is by induction on $p$, depends on $\restrf[n][p-1]$ whose type depends in turn on $\framep[n+1][p-1]$.
+and to build it at level $n+1$.
+This is however not so easy because some components of this structure, e.g.
+$\restrf$ and further fields, depend on $\framep[n+1]$, that is already depend on the ability of building the $\framep$ component of the structure at level $n+1$.
+We are thus facing an interdependency between specifying the structure assumed at level $n$ and defining from it the structure at level $n+1$.
+So, we have to proceed in order: specifying $\framep[n]$, from which $\painting[n]$ can be specified, from which $\framep[n+1]$ can be built and thus $\restrf[n+1]$ be specified.
+Now, the definition of $\framep[n+1][p]$, which is by induction on $p$, itself depends on $\restrf[n][p-1]$ whose type depends in turn on $\framep[n+1][p-1]$.
 This means that $\framep[n+1][p]$ and the type of $\restrf[n][p]$ have to be mutually defined.
@@
 This requires to assume $\framep[n][p-1]$ and $\painting[n][p-1]$ known in advance.
-Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][p-1]$.
+Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$.
 Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n+1$ fixed:
+
 \begin{center}
@@
 
-Note that we write $\framep$, $\painting$, $\restrf$ for the
-projections of a $\deps$. Also, by abuse of notation, we write $\unitpoint$ for
-the only inhabitant of $\depstype[n]$.
+Note that $\deps$ behaves here as an abbreviation for a sequence of assumptions.
+In particular, once a $\deps:\depstype$ is assumed, we can freely refer to $\framep$, $\painting$, $\restrf$.
+Also, by abuse of notation, we write $\unitpoint$ for the only inhabitant of $\depstype[n][0]$.
 
@@
 \end{equation*}
-
-TODO: say the convention on projection in the Introduction
 
@@
 \end{equation*}
-TODO: say the convention on projection in the Introduction
 

### 2025-12-29 paper/paper.tex
paper: use section labels

@@
 
-\subsection{Defining frames and specifying frame restrictions}
+\subsection{Defining frames and specifying frame restrictions\label{sec:mkframe}}
 
@@
 
-\subsection{Defining paintings}
+\subsection{Defining paintings\label{sec:mkpainting}}
 
@@
 
-\subsection{Defining frame restrictions and specifying frame coherence laws}
+\subsection{Defining frame restrictions and specifying frame coherence laws\label{sec:mkrestrf}}
 
@@
 
-\subsection{Defining painting restrictions}
+\subsection{Defining painting restrictions\label{sec:mkrestrp}}
 
@@
 where we use the ``equality over'' notation $t =_e u$ to mean $\overrightarrow{e}(t) = u$ whenever $t$ is of some type $P(a)$, $u$ of type $P(b)$ and $e$ a proof of $a = b$.
-\subsection{Defining frame coherence laws and specifying frame 2-dimensional coherence laws}
+\subsection{Defining frame coherence laws and specifying frame 2-dimensional coherence laws\label{sec:mkcohf}}
 
@@
 
-\subsection{Defining painting coherence laws}
+\subsection{Defining painting coherence laws\label{sec:mkcohp}}
 
@@
 \begin{itemize}
-  \item $\framep[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\deps[n][\lbrack 0,n \rbrack]$.
-  \item $\painting[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\fulldeps[n](E)$.
-  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack](E)$.
-  \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$.
+  \item $\framep[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\deps[n][\lbrack 0,n \rbrack]$ (section~\ref{sec:mkframe}).
+  \item $\painting[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\fulldeps[n](E)$ (section~\ref{sec:mkpainting}).
+  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack](E)$ (section~\ref{sec:mkrestrf}).
+  \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$ (section~\ref{sec:mkrestrp}).
   \item we define $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ from $\fulldepscohs[n](E)(E')$ and $\cohp[n][\lbrack 0,n \rbrack](E)(E')$.
-  \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$.
+  \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ (section~\ref{sec:mkcohf}).
   \item we define $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
-  \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$.
+  \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$ (section~\ref{sec:mkcohp}).
 \end{itemize}

### 2025-12-29 paper/paper.tex
paper: typesetting improvements

@@
 Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][\lbrack p,n+1 \rbrack]$, $\painting[n][\lbrack p,n \rbrack]$, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$.
-Also, for the case $p=n$, this requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$.
+Also, for the case $p=n$, this requires the assumption of an inhabitant $E_n$ of $\nu$Set$^{=n}$.
 Finally, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n+1][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$ respectively depend on the earlier values $\framep[n+1][\lbrack 0,p-1 \rbrack]$, $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$.
@@
 
-Thanks to $\cohptype[n][\lbrack 0,p-1 \rbrack]$, we can mutually define $\cohf[n+1][\lbrack 0,p \rbrack]$ and $\cohttype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ from $\fulldepscohs[n]$, abbreviating this and the dependency in a $\coht[n][\lbrack 0,p-1 \rbrack]$ as $\depscohttype[n][\lbrack 0,p-1 \rbrack]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$.
+Thanks to $\cohptype[n][\lbrack 0,p-1 \rbrack]$, we can mutually define $\cohf[n+1][\lbrack 0,p \rbrack]$ and $\cohttype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ from $\fulldepscohs[n]$, abbreviating the dependency as $\depscohttype[n][\lbrack 0,p-1 \rbrack]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$.
+Note however that, due to reasoning with $\U$, we do not need to have $\cohf[n+1][\lbrack 0,p \rbrack]$ depending on a proof of $\cohttype[n][\lbrack 0,p-1 \rbrack]$ as the latter can be proved at once by uniqueness of identity proofs.
+
 It is also convenient to build $\depscohs[n+1][\lbrack 0,p \rbrack]$ from $\depscoht[n][\lbrack 0,p-1 \rbrack]$, so that we can now build $\framep[n+3][p]$.
 Thus, we also include this abbreviation in the definition.
-Implicitly using in $\cohf[n+1][\lbrack 0,p \rbrack]$ that equalities in a $\Sigma$-type are equivalent to a $\Sigma$-type of the underlying equalities, we altogether have:
+Implicitly using in $\cohf[n+1][\lbrack 0,p \rbrack]$ that equalities in a $\Sigma$-type are equivalent to the $\Sigma$-type of the underlying equalities, we altogether have:
 
@@
     \depscoht[n][\lbrack 0,p-1 \rbrack]         & :                                   &
-    \begin{array}{l}
+    \left\{\begin{array}{l}
              \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d.\,\Pi l.                                                                                 \\
@@
              \restrl[n][p][r][\omega](\depscohs[n][\lbrack 0,p-1 \rbrack])(\restrl[n+1][p][q+1][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p-1 \rbrack]))(l))
-    \end{array}                                           \\
+           \end{array}\right.                                    \\
     \cohl[n][p][q][r][\epsilon][\omega]         &
     \depscoht[n][\lbrack 0,p-1 \rbrack]         & \defeq                              &
-    \begin{array}{l}
+    \left\{\begin{array}{l}
              \lambda d. \lambda l. \lambda \theta. \overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])(d)}                             \\
              (\ap \overrightarrow{\cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))(d))} \\ (\ap \overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)} \\(\cohp[n][p][q][r][\epsilon][\omega](l_\theta)))) \\
-    \end{array}
+           \end{array}\right.
   \end{array}
@@
   \cohttype[n][p](\depscoht[n][\lbrack 0,p \rbrack]) \defeq
-  \left(
+  \left\{
   \begin{array}{l}
@@
   \end{array}
-  \right)
+  \right.
 \end{equation*}

### 2025-12-29 paper/paper.tex
paper: minor tweaks; simplification effort in progress

@@
 
-Also, when $n$ is 0, we write $E$ to denote an element $(\unitpoint, E)$ of $\fulldepstype[0]$.
+Also, when $n$ is $0$, we write $E$ to denote an element of $\fulldepstype[0]$ where all other components are degenerate.
 
@@
 
-By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).
-
 We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$:
@@
     \overline{\fulldepscohs}(\fulldepscoht[n]) & :      & \fulldepscohstype[n+1] \\
-    \overline{\fulldepscohs}(\fulldepscoht[n]) & \defeq & \left(\begin{array}{l}
+    \overline{\fulldepscohs}(\fulldepscoht[n]) & \defeq & \left(
+    \begin{array}{l}
         \overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]) \\

### 2025-12-29 paper/paper.tex
paper: minor paragraph section

@@
 
+\paragraph*{Iterated parametricity in indexed form.}
 In \cite{hr25}, this correspondence was exploited to construct at the same time augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity.

### 2025-12-29 paper/paper.tex
paper: minor corrections

@@
 
-For $\nu$ an arity, that is $1$ in the case of predicates, families and augmented semi-simplicial sets or $2$ in the case of relations, correspondences and semi-cubical sets, such sequence of was called a $\nu$-set.
+For $\nu$ an arity, that is $1$ in the case of predicates, families and augmented semi-simplicial sets, or $2$ in the case of relations, correspondences and semi-cubical sets, such sequence of was called a $\nu$-set.
 Equations specifying $\nu$-sets were given in \cite{hr25}.
@@
 
-To build $\framep[n+1]$ from $\frame[n]$, it happens to be enough to assume the following built at level $n$:
-
-\begin{equation*}
-  \begin{array}{lclr}
-    \framep[n][p]   & : & \U                                                                                                  & \mbox{for all $p\leq n$} \\
-    \painting[n][p] & : & \framep[n][p] \rightarrow \U                                                                        & \mbox{for all $p\leq n$} \\
-    \restrf[n][p]   & : & \Pi q \leq n-p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]                         & \mbox{for all $p\leq n$} \\
+To build $\framep[n+1]$ from $\framep[n]$, it happens to be enough to assume the following built at level $n$, for all $p \leq n$:
+
+\begin{equation*}
+  \begin{array}{lcl}
+    \framep[n][p]   & : & \U                                                                                                  \\
+    \painting[n][p] & : & \framep[n][p] \rightarrow \U                                                                        \\
+    \restrf[n][p]   & : & \Pi q \leq n-p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]                         \\
     \restrp[n][p]   & : & \Pi q \leq n-p.\, \Pi \epsilon.\, \Pi d:\framep[n+1][p].\,                                          \\
-                    &   & \painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d))                                  & \mbox{for all $p\leq n$} \\
+                    &   & \painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d))                                  \\
     \cohf[n][p]     & : & \Pi qr\epsilon\omega.\, \restrf[n][p][q][\epsilon] \circ \restrf[n+1][p][\omega][r] =               \\
-                    &   & \restrf[n][p][\omega][r] \circ \restrf[n+1][p][q+1][\epsilon]                                       & \mbox{for all $p\leq n$} \\
+                    &   & \restrf[n][p][\omega][r] \circ \restrf[n+1][p][q+1][\epsilon]                                       \\
     \cohp[n][p]     & : & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,                                                     \\
                     &   & \restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) =     \\
-                    &   & \restrp[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon](d)) \circ \restrp[n+1][p][q+1][\epsilon](d) & \mbox{for all $p\leq n$} \\
+                    &   & \restrp[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon](d)) \circ \restrp[n+1][p][q+1][\epsilon](d) \\
   \end{array}
@@
 Now, the definition of $\framep[n+1][p]$, which is by induction on $p$, itself depends on $\restrf[n][p-1]$ whose type depends in turn on $\framep[n+1][p-1]$.
-This means that $\framep[n+1][p]$ and the type of $\restrf[n][p]$ have to be mutually defined.
+This means that $\framep[n+1][p]$ and the type of $\restrf[n][p]$ actually have to be mutually defined.
 
@@
 Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$.
-Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n+1$ fixed:
+Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following graph of dependencies for $p\leq n+1$ fixed:
 
@@
 
-So far, using this recursive definition of  $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$, we are able to specify the three first component of the exected dependent structure:
-\begin{equation*}
-  \begin{array}{lclr}
-    \framep[n][p]             & :                        & \U                                                & \mbox{for all $p\leq n$} \\
-    \painting[n][p]           & :                        & \framep[n][p] \rightarrow \U                      & \mbox{for all $p\leq n$} \\
+So far, using this recursive definition of  $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$, we are able to specify the three first component of the expected dependent structure, for $p \leq n$:
+\begin{equation*}
+  \begin{array}{lcl}
+    \framep[n][p]   & : & \U                                                \\
+    \painting[n][p] & : & \framep[n][p] \rightarrow \U                      \\
     \restrf[n][p]   & : & \Pi q \leq n-p.\, \Pi \epsilon.\, \framep[n+1][p]
@@
             \end{array}\right)
-    \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                                                                                \\
+    \rightarrow \framep[n][p]                                               \\
   \end{array}

### 2025-12-29 paper/paper.tex
paper: s/Set/HSet/

@@
 
-Parametricity, like realisability, reducibility, and logical relations, was most commonly handled in an \emph{indexed} form, that is, using a type-theoretic language, considering predicates of type $A \rightarrow \Prop$, or families of type $A \rightarrow \Set$, or relations of type $A \times A \rightarrow \Prop$, or relevant relations -- sometimes called \emph{correspondences} -- of type $A \times A \rightarrow \Set$, where $\Prop$ and $\Set$ are types representing, that is classifying -- in category theory terminology --, propositions or sets, respectively.
-Along the indexed-fibered correspondence, that is along the equivalence between the types $A \rightarrow \Prop$ and $\Sigma B:\Set.
-(B \stackrel{inj}{\rightarrow} A)$ (proof-irrelevant case) and $A \rightarrow \Set$ and $\Sigma B:\Set.
-(B \rightarrow A)$ (proof-relevant case), for $A:\Set$, everything told in the indexed form can morally also be told in \emph{fibered} form.
+Parametricity, like realisability, reducibility, and logical relations, was most commonly handled in an \emph{indexed} form, that is, using a type-theoretic language, considering predicates of type $A \rightarrow \Prop$, or families of type $A \rightarrow \U$, or relations of type $A \times A \rightarrow \Prop$, or relevant relations -- sometimes called \emph{correspondences} -- of type $A \times A \rightarrow \U$, where $\Prop$ and $\U$ are types representing, that is classifying -- in category theory terminology --, propositions or sets, respectively.
+Along the indexed-fibered correspondence, that is along the equivalence between the types $A \rightarrow \Prop$ and $\Sigma B:\U.
+(B \stackrel{inj}{\rightarrow} A)$ (proof-irrelevant case) and $A \rightarrow \U$ and $\Sigma B:\U.
+(B \rightarrow A)$ (proof-relevant case), for $A:\U$, everything told in the indexed form can morally also be told in \emph{fibered} form.
 Such fibered approach to parametricity was for instance considered in Ghani \cite{Ghani...}, who also suggested to iterate parametricity.
@@
 Such type theory could be interpreted in a ``unary'' form of cubical set~\citep{bernardy15}, thus implicitly in fibered form since, in a binary cubical set (resp.
-in a unary cubical set and simplicial set as well), a set of segments over two points, that is a relevant relation, is given by first and second projection rather than as a function to $\Set$ (resp.
-a family is given as a \emph{total space} projected over a set of points $A:\Set$ rather than a family of type $A \rightarrow \Set$.
+in a unary cubical set and simplicial set as well), a set of segments over two points, that is a relevant relation, is given by first and second projection rather than as a function to $\U$ (resp.
+a family is given as a \emph{total space} projected over a set of points $A:\U$ rather than a family of type $A \rightarrow \U$.
 This connection between iterated binary parametricity in fibered form and cubical sets includes an identification of degeneracies and reflexivity proofs, which can also be found in \cite{johann17}.

### 2025-12-29 paper/paper.tex
paper: prose refinements

@@
 
-\newcommand{\real}{\textsf{r}}
-
 From the point of view of realisability, unary parametricity over a language is a realisability using the language itself as language of realisers.
 Like parametricity, realisability can be expressed in a \emph{syntactic} way, that is as an interpretation from one language to another (i.e.
-mapping an expression $t$ of $\vdash A$ in some formal system to a derivation $t^*$ of $\vdash' |t| \real A$ in some other formal system, for some program $|t|$ extracted from $t$ -- namely $t$ itself in the case of parametricity), or a \emph{semantic} way\footnote{This distinction between syntactic realisability and semantic realisability is itself connected to the difference between relative and absolute consistency.
+mapping an expression $t$ of $\vdash A$ in some formal system to a derivation $t^*$ of $\vdash' |t| \textsf{r} A$ in some other formal system, for some program $|t|$ extracted from $t$ -- namely $t$ itself in the case of parametricity), or a \emph{semantic} way\footnote{This distinction between syntactic realisability and semantic realisability is itself connected to the difference between relative and absolute consistency.
 In the relative case, consistency of a formal system is reduced to the consistency of another formal system, and this can be done in a very weak logical system such as Primitive Recursive Arithmetic (PRA).
@@
 
-Parametricity, like realisability, reducibility, and logical relations, was most commonly handled in an \emph{indexed} form, that is, using a type-theoretic language, considering predicates of type $A \rightarrow \Prop$, or families of type $A \rightarrow \U$, or relations of type $A \times A \rightarrow \Prop$, or relevant relations -- sometimes called \emph{correspondences} -- of type $A \times A \rightarrow \U$, where $\Prop$ and $\U$ are types representing, that is classifying -- in category theory terminology --, propositions or sets, respectively.
+Parametricity, like realisability, reducibility, and logical relations, was most commonly handled in an \emph{indexed} form.
+To express it, let us use a type-theoretic language featuring a type of propositions $\Prop$, a type of sets $\U$, as well, as the standard $\Sigma$ and $\Pi$ constructions.
+In such language, predicates have type $A \rightarrow \Prop$, families have type $A \rightarrow \U$, relations have type $A \times A \rightarrow \Prop$, relevant relations -- sometimes called \emph{correspondences} -- have type $A \times A \rightarrow \U$.
 Along the indexed-fibered correspondence, that is along the equivalence between the types $A \rightarrow \Prop$ and $\Sigma B:\U.
@@
 For $\nu$ an arity, that is $1$ in the case of predicates, families and augmented semi-simplicial sets, or $2$ in the case of relations, correspondences and semi-cubical sets, such sequence of was called a $\nu$-set.
-Equations specifying $\nu$-sets were given in \cite{hr25}.
+Equations specifying $\nu$-sets were given in \cite{hr25} with an accompanying formalisation in Rocq.
+The argument used to justify the well-foundedness of the construction was however heavy.
+In this paper, we present a refined well-foundedness argument which reflects the recursive essence of the construction.
+
+\section{Description of iterated parametricity in indexed form\label{sec:reminder}}
+
 Because of the dependency of $E_{n+1}$ into all $E_p$ for $p \leq n$, the family could not be expressed as a function.
@@
 Note that for a fixed constant $n$, relying on the evaluation rules of type theory, the coherence conditions degenerate to a reflexivity proof, so that the construction builds an effective sequence of types not mentioning coherences anymore.
-
-Due to the intricate dependencies, the reason the whole construction is recursively well-defined is not simple.
-The formalisation in \cite{hr25} was recursively building a complex structure involving $3$ levels of the construction at once.
-In the present paper, we untangle the previous construction, making the dependencies explicit, and the new construction lends itself to a simple and complete explanation.
 

### 2025-12-29 paper/paper.tex
paper: mention zero case when finalizing construction

@@
 Therefore, assuming a construction of $\framep[n][n]$ from $D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n+1]$ from $D$ extended with some $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$.
-This is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus $\Xp{m}$, by starting with an empty $D$.
+This is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus $\Xp{m}$, by starting with an empty $D$, since, obviously, all fields of the structure are trivially inhabited by $\kstar$ when $n$ is $0$.
 

### 2025-12-29 paper/paper.tex
A few refinements

@@
 
-\section{Description of iterated parametricity in indexed form\label{sec:reminder}}
+\section{High-level description of iterated parametricity in indexed form\label{sec:reminder}}
 
@@
 
-\section{Outline of the recursive structure of iterated parametricity construction}
+\section{Analysis of the recursive structure of iterated parametricity in indexed form}
 
@@
 
-\section{The construction}
+\section{Detailed construction}
 
@@
             \end{array}\right)   & \defeq &
-    \begin{array}{l}
+    \left\{\begin{array}{l}
       \Sigma \restrf[n][\lbrack 0,p-1 \rbrack]
@@
               \end{array}\right) \rightarrow  \framep[n][p] \\
-    \end{array}                       \\
+    \end{array}\right.                       \\
     \layertype[n][p]                       &
@@
     \painting[n+1][p \leq n] &
-    \fulldeps[n]             & \defeq & d \mapsto
-    \left(\begin{array}{l}
-              \Sigma l:\layer[n][p](\deps[n][\lbrack 0,p \rbrack]). \\
+    \fulldeps[n]             & \defeq & \lambda d.\,
+              \Sigma l:\layer[n][p](\deps[n][\lbrack 0,p \rbrack]). 
               \painting[n+1][p+1]
               (\fulldeps[n])(d,l)                                   \\
-            \end{array}\right) \\
   \end{array}

### 2025-12-31 gendoc.sh
gendoc.sh: s/vType/vSet/

@@ -1,3 +1,3 @@
 #!/usr/bin/env sh
 
-coqdoc -t Bonak --no-lib-name --parse-comments --utf8 -d docs -Q _build/default/theories Bonak _build/default/theories/νType/*.v
+coqdoc -t Bonak --no-lib-name --parse-comments --utf8 -d docs -Q _build/default/theories Bonak _build/default/theories/νSet/*.v

### 2025-12-31 paper/paper.tex
paper: whitespace wrapping (NFC)
paper: strip outdated note on omitting deps arg
paper: minor errors near beginning

@@
 \begin{abstract}
-  Reynolds' parametricity originally eequips types with binary propositional relations over the types.
+  Reynolds' parametricity originally equips types with binary propositional relations over the types.
 Such relations can be taken proof-relevant, or unary, and described either in an indexed or fibered way.
@@
 
-Introduced by Reynolds in the context of programming language semantics~\cite{reynolds83}, relational parametricity happens to be connected to several similar concepts in logic and mathematics.
+Introduced by Reynolds in the context of programming language semantics~\citep{reynolds83}, relational parametricity happens to be connected to several similar concepts in logic and mathematics.
 Associating binary propositional relations to types in its original formulation, it can also associate proof-relevant relations~\cite{GhaniNordvallOrsanigo16} or unary relations, that is predicates (proof-irrelevant case) or families (relevant case).
@@
     \overline{\fulldeps}(\fulldepscohs[n]) & :      & \fulldepstype[n+1] \\
-    \overline{\fulldeps}(\fulldepscohs[n]) & \defeq & \left(\begin{array}{l}
+    \overline{\fulldeps}(\fulldepscohs[n]) & \defeq & \left(
+    \begin{array}{l}
         \overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack]) \\
@@
 \end{equation*}
-and where the functoriality of equality and transport was used to go from (omitting the $\framep$ argument and the deps argument of $\restrp$ and $\cohf$):
+and where the functoriality of equality and transport was used to go from (omitting the $\framep$ argument):
 \begin{equation*}

### 2025-12-31 paper/paper.tex
paper: prose improvements near start

@@
 Introduced by Reynolds in the context of programming language semantics~\citep{reynolds83}, relational parametricity happens to be connected to several similar concepts in logic and mathematics.
-Associating binary propositional relations to types in its original formulation, it can also associate proof-relevant relations~\cite{GhaniNordvallOrsanigo16} or unary relations, that is predicates (proof-irrelevant case) or families (relevant case).
+Associating binary propositional relations to types in its original formulation, it can also associate proof-relevant relations~\citep{GhaniNordvallOrsanigo16} or unary relations, that is predicates (proof-irrelevant case) or families (relevant case).
 These unary or binary, relevant or proof-irrelevant relations express what it means to belong in a type (unary case) or to be equal in a type (binary case) from an observational point of view.
@@
 interpreting $A$ as a set $\textbf{A}$ or a relation $=_A$ of the language of discourse and interpreting a derivation $t$ of $\vdash A$ as an expression $|t|$ such that, respectively, $|t| \in \textbf{A}$ or $|t| =_A |t|$).
-Thus, the comparison between parametricity and realisability includes the case of \emph{reducibility}~\cite{Tait}, which is a semantic form of realisability, also known as \emph{glueing} in the context of category theory.
-In the same vein, binary parametricity over a language can be seen as defining \emph{logical relations}~\cite{Plotkin} over itself, since logical relations are a binary form of reducibility.
+Thus, the comparison between parametricity and realisability includes the case of \emph{reducibility}~\citep{Tait67}, which is a semantic form of realisability, also known as \emph{glueing} in the context of category theory.
+In the same vein, binary parametricity over a language can be seen as defining \emph{logical relations}~\citep{Plotkin73} over itself, since logical relations are a binary form of reducibility.
 
@@
 (B \rightarrow A)$ (proof-relevant case), for $A:\U$, everything told in the indexed form can morally also be told in \emph{fibered} form.
-Such fibered approach to parametricity was for instance considered in Ghani \cite{Ghani...}, who also suggested to iterate parametricity.
+Such fibered approach to parametricity was for instance considered in~\cite{atkey14}, who also suggested to iterate parametricity.
 
